### 2015-10-25 template.tex
Initialize

%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% First comes an example EPS file -- just ignore it and
% proceed on the \documentclass line
% your LaTeX will extract the file if required
\begin{filecontents*}{example.eps}
%!PS-Adobe-3.0 EPSF-3.0
%%BoundingBox: 19 19 221 221
%%CreationDate: Mon Sep 29 1997
%%Creator: programmed by hand (JK)
%%EndComments
gsave
newpath
  20 20 moveto
  20 220 lineto
  220 220 lineto
  220 20 lineto
closepath
2 setlinewidth
gsave
  .4 setgray fill
grestore
stroke
grestore
\end{filecontents*}
%
\RequirePackage{fix-cm}
%
%\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
\documentclass[smallextended]{svjour3}       % onecolumn (second format)
%\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{amsmath}
\usepackage{graphicx} % Allows including images
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage[round]{natbib}
\setcitestyle{aysep={ }} %Author-Year SEParator
%
% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
%\usepackage{latexsym}
% etc.
%
% please place your own definitions here and don't use \def but
% \newcommand{}{}
%
% Insert the name of "your journal" with
% \journalname{myjournal}
%
\begin{document}

\title{Learning Discrete-valued Bayesian Network from Mixed Data%\thanks{Grants or other notes
%about the article that should go on the front page should be
%placed here. General acknowledgments should be placed at the end of the article.}
}
%\subtitle{Do you have a subtitle?\\ If so, write it here}

%\titlerunning{Short form of title}        % if too long for running head

\author{First Author         \and
        Second Author %etc.
}

%\authorrunning{Short form of author list} % if too long for running head

\institute{F. Author \at
              first address \\
              Tel.: +123-45-678910\\
              Fax: +123-45-678910\\
              \email{fauthor@example.com}           %  \\
%             \emph{Present address:} of F. Author  %  if needed
           \and
           S. Author \at
              second address
}

\date{Received: date / Accepted: date}
% The correct dates will be entered by the editor

\maketitle

\begin{abstract}
Insert your abstract here. Include keywords, PACS and mathematical
subject classification numbers as needed.
\keywords{Discretization \and Bayesian Network \and More}
% \PACS{PACS code1 \and PACS code2 \and more}
% \subclass{MSC code1 \and MSC code2 \and more}
\end{abstract}

\section{Introduction}
\label{intro}
Bayesian networks \citep{Pearl_1988, PGM_2009}  are an increasingly popular methods for modeling uncertainty and causality in science and engineering. They provide an efficient factorization of the joint probability distribution over a set of random variables. Bayesian networks first emerge from artificial intelligence research and have been applied to a wide variety of problems, ranging from decision-making systems \citep{DMU_2015} to medical diagnoses. In most cases, we assume that all random variables in Bayesian networks are discrete, since many algorithms on Bayesian networks are unable to deal with continuous variables efficiently. However, this assumption is often too restrictive. For example, in the decision-making system of autonomous cars, it is inevitable to deal with continuous variables such as position and velocity.

There are two solutions around this assumption. The first one is to model conditional probability density of each continuous variable by specific families of parametric distributions, then redesign algorithms on Bayesian networks based on these parameters. One successful example is the belief propagation in Gaussian graphical models \citep{Weiss_2011}. Nevertheless, for other shapes of particles \citep{Ihler_2009} or non-linear functions, algorithms are computationally expensive and do not perform well.

The second solution is to discretize continuous variables. Discretization that learns from data has developed well and discussed \citep{Dougherty_1995} in the fields of machine learning and statistics for many year. Most of these discretization methods are designed for classification problems. They search the best discretization of a continuous attribute by considering its interation with the class variable of interest. However, these discretization methods do not apply to continuous variables in Bayesian network. In Bayesian network, interations and dependencies between variables are determined by graph structure. Therefore, if a discretization method only uses the interation between a continuous variable and its class variable of interest, instead of considering the graph structure, then it is not an appropriate discretization method for Bayesian networks. There are some reseach on discretizating continuous variables in naive Bayesian network and tree augmented network \citep{Fried_naive}. Nevertheless, only few discretization methods on general Bayesian netowrk have been proposed \citep{Friedman_1996, Kozlov_1997, Monti_1998}.

The discretization technique proposed by N. Friedman and M. Goldszmidt \citet{Friedman_1996} is the most successful and practical one among these methods. It is based on minimum description length principle (MDL): optimal discretization policy minimizes the description length of Bayesian network and data information. If there is only one continuous variable in Bayesian network and other variables are discrete, MDL discretization method takes running time $O(N^3 + n_c {v_{max}}^{(n_c^p)_{max}} \cdot N^2 + {v_{max}}^{n_p} \cdot N^2)$, where $N$ is the number of data instances for learning the discretization, $n_p$ and $n_c$ are the numbers of parent and children variables for the continuous variable, $v_{max}$ is the largest cardinality number over all variables in Markov blanket, and  ${(n_c^p)_{max}}$ is the largest number of parent variables of the continuous variable's children.

In this paper, we propose a new discretization method for continuous variables in Bayesian network by learning from mixed data. This method is a generalized version of  \citet{Boulle_2006} and \citet{Lustgarten_2011}, which are both discretization methods of a continuous attribute with one class variable. We begin our method with the situation that only one variable in a given Bayesian network is continuous and other variable are discrete. Under this situation, we look for the most possible discretization policy $M$ given the data on other discrete variables. That is to say, the desired policy is $\textrm{arg}_M P(M|D)$. With Bayes rule, $P(M|D) = P(M) \cdot P(D|M) / P(D) \propto P(M)\cdot P(D|M)$. Usually, $P(D|M)$ increases as number of discretized intervals increases, since more intervals can provide more accuracy. Therefore, we design probability priors of $P(M)$ to decrease as number of intervals rises. As a result, we obtain a nature trade-off to determine the number of intervals after discretization. Besides, the $P(D|M)$ can be factorized according to Bayesian network structure. On the other hand, with the proposed priors, we are able to restrict the number of discretized intervals not exceeding the largest cardinality number of variable in Markov blanket too much. This is important, since for most algorithms on Bayesian network, their running times exponentially depend on the cardinality of variables. Another advantage of our algorithm is running time. If there is only one continuous variable, the running time is $O(n_c  {v_{max}} \cdot N^2 + {v_{max}}^{n_p} \cdot N^2)$, which beats the running time of MDL principle discretization \citep{Friedman_1996}. With an effective approximation proposed in this paper, we can further reduce running time to $O({v_{max}}(n_p+n_c)N^2)$.

For a Bayesian network with multiple continuous variables, we apply the discretization method discussed above iteratively. In the beginning, we discretize each continuous variable by equal-width method. Number of intervals for equal-width discretization is equal to largest cardinality of discrete variables. Then we iterate the one-variable discretization on each continuous variable by the following order: from the variable with highest topological order (leaves) to the variable with lowest topological order (root). Everytime when we finish a discretization procedure on one variable, we store the discretization result and this discretization result will be used for later discretization on another variable. Experiments on real data show that with same iteration order, our discretization provides better discretization result than MDL principle method in terms of likelihood. The latter is easily catched by local minima and thus produce non-necessarily low number of intervals after discretization.

Finally, we can combine the new discretization method with K2 structure learning alorithm \citep{K2}. We first prediscretize all continuous variables before K2 learning, since K2 algorithm requires all variables are discrete. Everytime when an edge is added by K2 algorithm procedure, we rediscretize the relevant variables in Bayesian network and store the result for next K2 algorithm iteration. By this principle, we are able to learn a discrete-valued Bayesian network from mixed data.

The rest of the paper is organized as follows: we prepare the preliminaries and notations of Bayesian network in Section 2. Related work, including MDL principle discretization \citep{Friedman_1996} and MODL discretization by \citet{Boulle_2006}, are summarized in Section 3. In Section 4, we introduce the new discretization method, including formulation of objective function and algorithms. One continuous variable case and multiple continuous variable case are also included in this section. Finally, in Section 5, we apply the new discretization method to real-world data and show the result.
%
%\section{Related Work}
%\label{relat_work}
%
%\section{Notation and Preliminaries}
%\label{notat_pre}
%\subsection{Bayesian Network}
%\label{BN}
%A Bayesian network $B$ is defined by a pair $(G,\Theta)$, where $G = (X,E)$ is a directed acyclic graph whose nodes correspond to a set of random variable $X = \{  X_1, X_2, \cdots, X_n \}$, and whose edges $E$ represents probabilistic dependencies among nodes. The graph structure $G$ encodes the Markov property: each node $X_i$ is independent of its non-descendants given its parents in $G$. The second component of $B$, namely $\Theta$, contains a set of parameter that qualifies the network. Elements of $\Theta$ take the form $\theta_{x_i|\Pi_{x_i}} = P(x_i|\Pi_{x_i})$ for each possible value $x_i$ of $X_i$, and $\Pi_{x_i}$ of $\Pi_{X_i}$ (the set of parents of $X_i$ in $G$). Due to Markov property, we can represent the multivariate joint distribution over $X$ as
%\begin{equation*}
%P_B (X_1 , \cdots, X_n) = \prod_{i=1}^{n} P_B (X_i | \Pi_{X_i}) = \prod_{i=1}^{n} \theta_{x_i|\Pi_{x_i}}
%\end{equation*}\\
%For a Bayesian network, we can generate its data instances by forward sampling, i.e., sampling variables one by one in a topological order. A topological order is obtained by breadth-first search. Given a instance of $X_i$'s parent set $\Pi_{X_i}$, value of $X_i$ can be sampled according to conditional probability relation $P(X_i | \Pi_{X_i})$. Furthermore, this parent-child sampling order can be reversed if we know the marginal probability of child variable $P(X_i)$. By Bayes rule,
%\begin{equation*}
%P(X_i | \Pi_{X_i}) \cdot \prod_{j = 1}^{ Pa( X_i)} P( \{ \Pi_{X_i} \}_j) = P(X_i) \cdot P(\Pi_{X_i} | X_i),
%\end{equation*}
%where $Pa( X_i)$ is the number of parents of $X_i$, we can first sample $X_i$ by $P(X_i)$, then sample the parent varaibles simultaneously by $P(\Pi_{X_i} | X_i)$. That is to say, $X_i$ becomes the starting point for sampling. $X_i$'s descendants are sampled in the same way as forward sampling. $X_i$'s ancestors are sampled in a reverse order.
%\subsection{K2 Structure Learning}
%\label{K2}
%
%\section{Section title}
%\label{sec:1}
%\subsection{Subsection title}
%\label{sec:2}
%as required. Don't forget to give each section
%and subsection a unique label (see Sect.~\ref{sec:1}).
%\paragraph{Paragraph headings} Use paragraph headings as needed.
%\begin{equation}
%a^2+b^2=c^2
%\end{equation}

% For one-column wide figures use
\begin{figure}
% Use the relevant command to insert your figure file.
% For example, with the graphicx package use
  \includegraphics{example.eps}
% figure caption is below the figure
\caption{Please write your figure caption here}
\label{fig:1}       % Give a unique label
\end{figure}
%
% For two-column wide figures use
\begin{figure*}
% Use the relevant command to insert your figure file.
% For example, with the graphicx package use
  \includegraphics[width=0.75\textwidth]{example.eps}
% figure caption is below the figure
\caption{Please write your figure caption here}
\label{fig:2}       % Give a unique label
\end{figure*}
%
% For tables use
\begin{table}
% table caption is above the table
\caption{Please write your table caption here}
\label{tab:1}       % Give a unique label
% For LaTeX tables use
\begin{tabular}{lll}
\hline\noalign{\smallskip}
first & second & third  \\
\noalign{\smallskip}\hline\noalign{\smallskip}
number & number & number \\
number & number & number \\
\noalign{\smallskip}\hline
\end{tabular}
\end{table}

%\begin{acknowledgements}
%If you'd like to thank anyone, place your comments here
%and remove the percent signs.
%\end{acknowledgements}

% BibTeX users please use one of
%\bibliographystyle{spbasic}      % basic style, author-year citations
%\bibliographystyle{spmpsci}      % mathematics and physical sciences
%\bibliographystyle{spphys}       % APS-like style for physics
%\bibliography{}   % name your BibTeX data base

% Non-BibTeX users please use
%\begin{thebibliography}{}
\bibliographystyle{plainnat}
\bibliography{my_bib}

\end{document}
% end of file template.tex

### 2015-10-25 BN_discretizer_paper.tex
initialize
update

--- 2015-10-25 template.tex
@@
 
-The rest of the paper is organized as follows: we prepare the preliminaries and notations of Bayesian network in Section 2.
+The rest of the paper is organized as follows: we prepare the preliminaries of Bayesian network in Section 2.
 Related work, including MDL principle discretization \citep{Friedman_1996} and MODL discretization by \citet{Boulle_2006}, are summarized in Section 3.
@@
 Finally, in Section 5, we apply the new discretization method to real-world data and show the result.
-%
-%\section{Related Work}
-%\label{relat_work}
-%
-%\section{Notation and Preliminaries}
-%\label{notat_pre}
-%\subsection{Bayesian Network}
-%\label{BN}
-%A Bayesian network $B$ is defined by a pair $(G,\Theta)$, where $G = (X,E)$ is a directed acyclic graph whose nodes correspond to a set of random variable $X = \{  X_1, X_2, \cdots, X_n \}$, and whose edges $E$ represents probabilistic dependencies among nodes.
+
+\section{Preliminaries}
+\label{Prelim}
+\subsection{Bayesian Network}
+\label{BN_basic}
+A Bayesian network $B$ is defined by a pair $(G,\Theta)$, where $G = (X,E)$ is a directed acyclic graph whose nodes correspond to a set of random variable $X = \{  X_1, X_2, \cdots, X_n \}$, and whose edges $E$ represents probabilistic dependencies among nodes.
 The graph structure $G$ encodes the Markov property: each node $X_i$ is independent of its non-descendants given its parents in $G$.
@@
 Due to Markov property, we can represent the multivariate joint distribution over $X$ as
-%\begin{equation*}
-%P_B (X_1 , \cdots, X_n) = \prod_{i=1}^{n} P_B (X_i | \Pi_{X_i}) = \prod_{i=1}^{n} \theta_{x_i|\Pi_{x_i}}
-%\end{equation*}\\
-%For a Bayesian network, we can generate its data instances by forward sampling, i.e., sampling variables one by one in a topological order.
-A topological order is obtained by breadth-first search.
-Given a instance of $X_i$'s parent set $\Pi_{X_i}$, value of $X_i$ can be sampled according to conditional probability relation $P(X_i | \Pi_{X_i})$.
+\begin{equation*}
+P_B (X_1 , \cdots, X_n) = \prod_{i=1}^{n} P_B (X_i | \Pi_{X_i}) = \prod_{i=1}^{n} \theta_{x_i|\Pi_{x_i}}
+\end{equation*}\\
+For a given Bayesian network, we can generate its data instances by forward sampling, i.e., sampling variables one by one in a topological order \citep[see][chap.~22]{algo_2009}.
+Given a instance of $X_i$'s parent set $\Pi_{X_i}$, value of $X_i$ can be sampled according to the conditional probability table $P(X_i | \Pi_{X_i})$.
 Furthermore, this parent-child sampling order can be reversed if we know the marginal probability of child variable $P(X_i)$.
 By Bayes rule,
-%\begin{equation*}
-%P(X_i | \Pi_{X_i}) \cdot \prod_{j = 1}^{ Pa( X_i)} P( \{ \Pi_{X_i} \}_j) = P(X_i) \cdot P(\Pi_{X_i} | X_i),
-%\end{equation*}
-%where $Pa( X_i)$ is the number of parents of $X_i$, we can first sample $X_i$ by $P(X_i)$, then sample the parent varaibles simultaneously by $P(\Pi_{X_i} | X_i)$.
+\begin{equation*}
+P(X_i | \Pi_{X_i}) \cdot \prod_{j = 1}^{ Pa( X_i)} P( \{ \Pi_{X_i} \}_j) = P(X_i) \cdot P(\Pi_{X_i} | X_i),
+\end{equation*}
+where $Pa( X_i)$ is the number of parents of $X_i$, and $\{ \Pi_{X_i} \}_j$ is the $j$th parent of $X_i$.
+We can first sample $X_i$ by $P(X_i)$, then sample all the parent varaibles simultaneously by $P(\Pi_{X_i} | X_i)$.
 That is to say, $X_i$ becomes the starting point for sampling.
-$X_i$'s descendants are sampled in the same way as forward sampling.
-$X_i$'s ancestors are sampled in a reverse order.
-%\subsection{K2 Structure Learning}
-%\label{K2}
-%
-%\section{Section title}
-%\label{sec:1}
-%\subsection{Subsection title}
-%\label{sec:2}
-%as required. Don't forget to give each section
-%and subsection a unique label (see Sect.~\ref{sec:1}).
-%\paragraph{Paragraph headings} Use paragraph headings as needed.
-%\begin{equation}
-%a^2+b^2=c^2
-%\end{equation}
 
-% For one-column wide figures use
-\begin{figure}
-% Use the relevant command to insert your figure file.
-% For example, with the graphicx package use
-  \includegraphics{example.eps}
-% figure caption is below the figure
-\caption{Please write your figure caption here}
-\label{fig:1}       % Give a unique label
-\end{figure}
-%
-% For two-column wide figures use
-\begin{figure*}
-% Use the relevant command to insert your figure file.
-% For example, with the graphicx package use
-  \includegraphics[width=0.75\textwidth]{example.eps}
-% figure caption is below the figure
-\caption{Please write your figure caption here}
-\label{fig:2}       % Give a unique label
-\end{figure*}
-%
-% For tables use
-\begin{table}
-% table caption is above the table
-\caption{Please write your table caption here}
-\label{tab:1}       % Give a unique label
-% For LaTeX tables use
-\begin{tabular}{lll}
-\hline\noalign{\smallskip}
-first & second & third  \\
-\noalign{\smallskip}\hline\noalign{\smallskip}
-number & number & number \\
-number & number & number \\
-\noalign{\smallskip}\hline
-\end{tabular}
-\end{table}
+\subsection{K2 Structure Learning}
+\label{intro_K2}
+K2 ...
+
+\section{Related Work}
+\label{relat_work}
+\subsection{MDL Principle Discretization}
+\label{MDL}
+
+\subsection{MODL Discretization}
+\label{MODL}
+
+\section{Discretize One Continuous Variable}
+\label{one-conti}
+
+\subsection{Notations}
+\label{Notation}
+
+\subsection{Objective Function}
+\label{obj}
+
+\subsection{Algorithm}
+\label{algo}
+
+\subsection{Approximation}
+\label{approx}
+
+\section{Discretizing Multiple Continuous Variable with Structure Learning}
+\label{multiple-conti}
+
+\section{Experiments}
 

### 2015-10-26 BN_discretizer_paper.tex
update

@@
 There are some reseach on discretizating continuous variables in naive Bayesian network and tree augmented network \citep{Fried_naive}.
-Nevertheless, only few discretization methods on general Bayesian netowrk have been proposed \citep{Friedman_1996, Kozlov_1997, Monti_1998}.
+Nevertheless, only few discretization methods on general Bayesian netowrk have been proposed \citep{Friedman_1996, Kozlov_1997, Monti_1998, Steck_2007}.
 
@@
 Friedman and M.
-Goldszmidt \citet{Friedman_1996} is the most successful and practical one among these methods.
+Goldszmidt \citet{Friedman_1996} is the most well-known one among these methods.
 It is based on minimum description length principle (MDL): optimal discretization policy minimizes the description length of Bayesian network and data information.
@@
 We begin our method with the situation that only one variable in a given Bayesian network is continuous and other variable are discrete.
+Furthermore we assume that the network structure is known in advance.
 Under this situation, we look for the most possible discretization policy $M$ given the data on other discrete variables.
@@
 \section{Preliminaries}
+In this section we provide a brief review of Bayesian network, including the factorization of joint probability distribution, sampling from a given network, and strucutre learning.
+These concepts will be used in later sections.
 \label{Prelim}
@@
 \label{intro_K2}
-K2 ...
+Roughly speaking, there are three approaches to learn a Bayesian network structure from data \citep[see][chap.~18]{PGM_2009}.
+They are constraint-based structure learning, score-based structure learning, and Bayesian model averaging.
+Here we review K2 structure learning algorithm \citep{K2}, which is
+one of the most successful score-based structure learning method.
+Same as most structure learning algorithms, K2 algorithm requires all variables are discrete.
+The score of a learned network is defined as $\prod_i f(X_i, \Pi_{X_i})$, where
+\begin{align}
+f(X_i, \Pi_{X_i}) = \prod_{j=1}^{|\Pi_{X_i}|} {{(|X_i|-1)!}\over{(N_{ij} + |X_i|-1)!}} \prod_{k=1}^{|X_i|} \alpha_{ijk}!.
+\end{align}
+$|X_i|$ is the cardinality of variable $X_i$.
+$|\Pi_{X_i}|$ is number of all possible instantiations of the parent variables of $X_i$, i.e., $|\Pi_{X_i}| = \prod_{Y \in \Pi_{X_i}} |Y|$.
+$\alpha_{ijk}$ is number of instances in data set that variable $X_i$ is instantiated with its $k$th value, and the parent of $X_i$ are instantiated with the $j$th value of $\Pi_{X_i}$.
+$N_{ij} = \sum_{k=1}^{|X_i|} \alpha_{ijk}$.
+K2 algorithm searchs the network structure with highest score, which can be interpreted as the most probable network with the given data.
+Besides, K2 requires the topological order of variables be known before scoring can start.
+This constraint can prevents cycles from being introduced.
+The searching for high-score network is a iterative process.
+There is no way to find the optimal network directly, since there are $2^{O(n^2)}$ possible structures, where $n$ is number of variables.
+In order to compensate for this, we run K2 algorithm for many times, and each time we start with a different order of variables.
+The network with highest score in iterations is the desired one.
 
@@
 \label{relat_work}
+In these section we review two related works: MDL principle discretization \citep{Friedman_1996} and MODL discretization \citep{Boulle_2006}.
+The former is the most famous discretization method for continuous variables in Bayesian network, and we will compare it with our proposed method in Section 6.
+The latter is a discretization method for one continuous attribute according to a target class.
+Our proposed method is a generalization of this method.
 \subsection{MDL Principle Discretization}

### 2015-11-03 BN_discretizer_paper.tex
update

--- 2015-10-25 BN_discretizer_paper.tex
@@
 \usepackage{amsmath}
+\usepackage{bm}
 \usepackage{graphicx} % Allows including images
@@
 
-\title{Learning Discrete-valued Bayesian Network from Mixed Data%\thanks{Grants or other notes
+\title{Learning Discrete-valued Bayesian Networks from Mixed Data%\thanks{Grants or other notes
 %about the article that should go on the front page should be
@@
 \author{First Author         \and
-        Second Author %etc.
+        Second Author         \and
+        Third Author%etc.
 }
@@
 subject classification numbers as needed.
-\keywords{Discretization \and Bayesian Network \and More}
+\keywords{Discretization \and Bayesian Network \and Continuous Variable}
 % \PACS{PACS code1 \and PACS code2 \and more}
@@
 \label{intro}
-Bayesian networks \citep{Pearl_1988, PGM_2009}  are an increasingly popular methods for modeling uncertainty and causality in science and engineering.
+Bayesian networks \citep{Pearl_1988, PGM_2009}  are an increasingly popular method for modeling uncertainty and causality in science and engineering.
 They provide an efficient factorization of the joint probability distribution over a set of random variables.
-Bayesian networks first emerge from artificial intelligence research and have been applied to a wide variety of problems, ranging from decision-making systems \citep{DMU_2015} to medical diagnoses.
+Bayesian networks first emerged from artificial intelligence research and have been applied to a wide variety of problems, ranging from decision-making systems \citep{DMU_2015} to medical diagnoses.
 In most cases, we assume that all random variables in Bayesian networks are discrete, since many algorithms on Bayesian networks are unable to deal with continuous variables efficiently.
-However, this assumption is often too restrictive.
-For example, in the decision-making system of autonomous cars, it is inevitable to deal with continuous variables such as position and velocity.
+However, the assumption that all variables are discrete is often too restrictive.
+For example, in the decision-making system of autonomous cars, it is imperative to deal with continuous variables such as position and velocity.
 
-There are two solutions around this assumption.
+There are two methods around this assumption.
 The first one is to model conditional probability density of each continuous variable by specific families of parametric distributions, then redesign algorithms on Bayesian networks based on these parameters.
-One successful example is the belief propagation in Gaussian graphical models \citep{Weiss_2011}.
-Nevertheless, for other shapes of particles \citep{Ihler_2009} or non-linear functions, algorithms are computationally expensive and do not perform well.
+One successful example is belief propagation in Gaussian graphical models \citep{Weiss_2011}.
+Nevertheless, for other shapes of particles \citep{Ihler_2009} or non-linear functions, these redesigned algorithms are computationally expensive and do not perform well.
 
-The second solution is to discretize continuous variables.
-Discretization that learns from data has developed well and discussed \citep{Dougherty_1995} in the fields of machine learning and statistics for many year.
+The second method around continuous variables is to discretize them.
+Discretization that learns from data has been developed well and discussed in the fields of machine learning and statistics for many years \citep{Dougherty_1995, Kerber_1992, Holte_1993, Fayyad_1993} .
 Most of these discretization methods are designed for classification problems.
-They search the best discretization of a continuous attribute by considering its interation with the class variable of interest.
-However, these discretization methods do not apply to continuous variables in Bayesian network.
-In Bayesian network, interations and dependencies between variables are determined by graph structure.
-Therefore, if a discretization method only uses the interation between a continuous variable and its class variable of interest, instead of considering the graph structure, then it is not an appropriate discretization method for Bayesian networks.
-There are some reseach on discretizating continuous variables in naive Bayesian network and tree augmented network \citep{Fried_naive}.
-Nevertheless, only few discretization methods on general Bayesian netowrk have been proposed \citep{Friedman_1996, Kozlov_1997, Monti_1998}.
+They search the best discretization policy of a continuous attribute by considering its interation with the class variable of interest.
+However, these discretization methods do not apply to continuous variables in Bayesian networks.
+In Bayesian networks, interations and dependencies between variables are determined by graph structure.
+Therefore, if a method discretizes continuous variables according to graph structure, instead of assigning one variable as a class variable, then it would be more appropriate.
+There is some reseach on discretizing continuous variables in naive Bayesian networks and tree augmented networks \citep{Fried_naive}, but only a few discretization methods on general Bayesian netowrk have been proposed \citep{Friedman_1996, Kozlov_1997, Monti_1998, Steck_2007}.
 
-The discretization technique proposed by N.
-Friedman and M.
-Goldszmidt \citet{Friedman_1996} is the most successful and practical one among these methods.
+The discretization technique proposed by \citet{Friedman_1996} is the most well-known one among these few methods.
 It is based on minimum description length principle (MDL): optimal discretization policy minimizes the description length of Bayesian network and data information.
-If there is only one continuous variable in Bayesian network and other variables are discrete, MDL discretization method takes running time $O(N^3 + n_c {v_{max}}^{(n_c^p)_{max}} \cdot N^2 + {v_{max}}^{n_p} \cdot N^2)$, where $N$ is the number of data instances for learning the discretization, $n_p$ and $n_c$ are the numbers of parent and children variables for the continuous variable, $v_{max}$ is the largest cardinality number over all variables in Markov blanket, and  ${(n_c^p)_{max}}$ is the largest number of parent variables of the continuous variable's children.
+If there is only one continuous variable in Bayesian network and other variables are discrete, this MDL discretization method takes running time $O(N^3 + n_c {v_{max}}^{(n_c^p)_{max}} \cdot N^2 + {v_{max}}^{n_p} \cdot N^2)$, where $N$ is the number of data instances for learning the discretization, $n_p$ and $n_c$ are the numbers of parent and children variables for the continuous variable, $v_{max}$ is the largest cardinality number over all variables in Markov blanket, and  ${(n_c^p)_{max}}$ is the largest number of parent variables of the continuous variable's children.
+If there are multiple continuous variables in the network, the method iterates over all continuous variables until convergence.
+In our test on real world data, the iterations converge in a few cycles.
+However, the number of intervals after discretization is too small.
 
-In this paper, we propose a new discretization method for continuous variables in Bayesian network by learning from mixed data.
+In this paper, we propose a new discretization method for continuous variables in Bayesian networks by learning from mixed data.
 This method is a generalized version of  \citet{Boulle_2006} and \citet{Lustgarten_2011}, which are both discretization methods of a continuous attribute with one class variable.
-We begin our method with the situation that only one variable in a given Bayesian network is continuous and other variable are discrete.
-Under this situation, we look for the most possible discretization policy $M$ given the data on other discrete variables.
-That is to say, the desired policy is $\textrm{arg}_M P(M|D)$.
-With Bayes rule, $P(M|D) = P(M) \cdot P(D|M) / P(D) \propto P(M)\cdot P(D|M)$.
-Usually, $P(D|M)$ increases as number of discretized intervals increases, since more intervals can provide more accuracy.
-Therefore, we design probability priors of $P(M)$ to decrease as number of intervals rises.
-As a result, we obtain a nature trade-off to determine the number of intervals after discretization.
-Besides, the $P(D|M)$ can be factorized according to Bayesian network structure.
-On the other hand, with the proposed priors, we are able to restrict the number of discretized intervals not exceeding the largest cardinality number of variable in Markov blanket too much.
-This is important, since for most algorithms on Bayesian network, their running times exponentially depend on the cardinality of variables.
-Another advantage of our algorithm is running time.
-If there is only one continuous variable, the running time is $O(n_c  {v_{max}} \cdot N^2 + {v_{max}}^{n_p} \cdot N^2)$, which beats the running time of MDL principle discretization \citep{Friedman_1996}.
-With an effective approximation proposed in this paper, we can further reduce running time to $O({v_{max}}(n_p+n_c)N^2)$.
+We begin our method with the assumption that only one variable in a given Bayesian network is continuous and other variables are discrete.
+Furthermore we assume that the network structure is known in advance.
+Under this situation, we look for the most probable discretization policy $M$ given the data $D$ on other discrete variables.
+That is to say, the desired policy is $\textrm{arg}_M P(M \mid D)$.
+With Bayes' rule, $P(M \mid D) $ can be rewritten as $P(M) \cdot P(D \mid M) / P(D)$ , which is proportional to $P(M)\cdot P(D \mid M)$.
+Usually, $P(D \mid M)$ increases as the number of discretized intervals increases, since more intervals can provide more accuracy.
+$P(M)$, on the other hand, is designed to decrease as the number of intervals rises.
+As a result, we can automatically determine the number of intervals after discretization by maximizing  $P(M)\cdot P(D \mid M)$.
+In addition, the $P(D \mid M)$ can be factorized according to Bayesian network structure.
+With the proposed priors, we are able to restrict the number of discretized intervals so that it will not exceed the largest cardinality number of variables in the Markov blanket by too much.
+This is important, since for most algorithms on Bayesian networks, their running times exponentially depend on the cardinality of variables.
+Another advantage of our method is the running time for learning.
+If there is only one continuous variable, the running time is $O(n_c  {v_{max}} \cdot N^2 + {v_{max}}^{n_p} \cdot N^2)$, which is significiantly shorter than the running time of MDL principle discretization \citep{Friedman_1996}.
+With the approximation proposed in this paper, we can further reduce running time to $O({v_{max}}(n_p+n_c)N^2)$.
 
 For a Bayesian network with multiple continuous variables, we apply the discretization method discussed above iteratively.
-In the beginning, we discretize each continuous variable by equal-width method.
-Number of intervals for equal-width discretization is equal to largest cardinality of discrete variables.
-Then we iterate the one-variable discretization on each continuous variable by the following order: from the variable with highest topological order (leaves) to the variable with lowest topological order (root).
-Everytime when we finish a discretization procedure on one variable, we store the discretization result and this discretization result will be used for later discretization on another variable.
-Experiments on real data show that with same iteration order, our discretization provides better discretization result than MDL principle method in terms of likelihood.
-The latter is easily catched by local minima and thus produce non-necessarily low number of intervals after discretization.
+In the beginning, we prediscretize each continuous variable by equal-width method.
+The number of intervals for equal-width discretization is equal to largest cardinality of discrete variables.
+Then we iterate the one-variable discretization on each continuous variable in the following order: from the variable with highest topological order (leaves) to the variable with lowest topological order (root).
+Each time we finish a discretization procedure on one variable, we store the discretization result for later iterations.
+Experiments on real data show that with the same iteration order, our discretization method provides better discretization results than MDL principle method in terms of likelihood.
+The MDL principle method is easily stuck at local minima and also discretizes variables into too few intervals.
 
-Finally, we can combine the new discretization method with K2 structure learning alorithm \citep{K2}.
-We first prediscretize all continuous variables before K2 learning, since K2 algorithm requires all variables are discrete.
-Everytime when an edge is added by K2 algorithm procedure, we rediscretize the relevant variables in Bayesian network and store the result for next K2 algorithm iteration.
+Finally, we can combine the our new discretization method with K2 structure learning alorithm \citep{K2}.
+We first prediscretize all continuous variables before K2 learning, since the K2 algorithm requires all variables to be discrete.
+Each time an edge is added in the K2 algorithm procedure, we rediscretize the relevant variables in the learned Bayesian network and store the result for next K2 algorithm iteration.
 By this principle, we are able to learn a discrete-valued Bayesian network from mixed data.
 
-The rest of the paper is organized as follows: we prepare the preliminaries of Bayesian network in Section 2.
-Related work, including MDL principle discretization \citep{Friedman_1996} and MODL discretization by \citet{Boulle_2006}, are summarized in Section 3.
-In Section 4, we introduce the new discretization method, including formulation of objective function and algorithms.
-One continuous variable case and multiple continuous variable case are also included in this section.
-Finally, in Section 5, we apply the new discretization method to real-world data and show the result.
+The rest of the paper is organized as follows: related works, including MDL principle discretization \citep{Friedman_1996} and MODL discretization by \citet{Boulle_2006}, are summarized in Section 2.
+We prepare the preliminaries and notations in Section 3.
+In Section 4, we introduce the new discretization method for the case that only one variable is continuous, including the derivation of objective function and the algorithms.
+Section 5 is a discussion about multiple continuous variables in a Bayesian network and how to discretize them.
+The combination of our proposed discretization and K2 structure learning is also introduced.
+Finally, in Section 6, we apply the proposed discretization method to real-world data and show the result.
+
+\section{Related Work}
+\label{relat_work}
+In this section we review two related works: MDL principle discretization \citep{Friedman_1996} and MODL discretization \citep{Boulle_2006}.
+The former is the most famous discretization method for continuous variables in Bayesian networks, and we will compare it with our proposed method in Section 6.
+The latter is a discretization method for one continuous attribute according to a target class.
+Our proposed method is a generalization of this method.
+Note that MODL discretization is a Bayesian approach.
+The asymptotical equivalence between MDL approach and Bayesian approach has been examined in \citep{VL_2000}.
+\subsection{MDL Principle Discretization}
+\label{MDL}
+The MDL principle was first proposed by \cite{MDL_1978}.
+It provides a way to compress data, that is to say, describe data with fewer number of symbols than the number of symbols needed to describe the data literally \citep{Grunwald_2009}.
+MDL chooses a model that trades off goodness-of-fit for the complexity of model.
+Therefore it has an advantage that automatically avoids overfitting.
+In the case of Bayesian networks, \citep{Friedman_1996} applied the MDL concept to determine the number of intervals of each continuous variable after discretization and also the positions of discretization boundaries.
+Here is the mechanism: MDL principle discretization selects a discretization policy that minimizes sum of description lengths of discretized Bayesian network and the necessary information that recovers original data from discretized data.
+If there is only one continuous variable and other variables are discrete, the objective function is
+\begin{equation}
+\begin{aligned}
+&{1 \over 2} log(N) \{  \lVert \Pi_{X_i} \rVert (\lVert X^*_i \rVert - 1) +
+ {\sum_{j,X_i \in \Pi_{X_i}}} \lVert \Pi_{X^*_j} \rVert (\lVert X_j \rVert - 1) \} + \\
+& log(\lVert {X^*_i} \rVert) + log{{N_{i}-1}\choose{\lVert {X^*_i} \rVert -1}}  -N \cdot [I(X^*_i,\Pi_{X_i}) + {\sum_{j,X_i \in \Pi_{X_i}}} I(X_j, \Pi_{X^*_j})],
+\end{aligned}
+\end{equation}
+where function $I(\boldsymbol{A},\boldsymbol{B}) = \sum_{\boldsymbol{a},\boldsymbol{b}} \hat{P}_D (\boldsymbol{a},\boldsymbol{b}) log {{\hat{P}_D (\boldsymbol{a},\boldsymbol{b})}\over{\hat{P}_D (\boldsymbol{a}),\hat{P}_D (\boldsymbol{b})}}$ is the mutual information between two sets of variables $\boldsymbol{A}$ and $\boldsymbol{B}$, $||\boldsymbol{X}||$ means the cardinality of variable $\boldsymbol{X}$ and $X^*_i$ is the discretized version of continuous variable $X_i$.
+The optimal discretization policy can be found by dynamical programming.
+If there are multiple continuous variables in Bayesian network, we apply the algorithm on one variable at a time and iterate over all continuous variables.
+While iterating, only one variable is treated as continuous and other continuous variables are discretized based on initial prediscretization or the discretization result of previous iteration.
+
+For the above discretization processes, the network structure is known in advance.
+If the network structure is not given, we can alternate between structure learning and discretization learning.
+We start with some discretization, and learn a network structure given this discretization.
+Then, we rediscretize based on the learned network.
+This cycle continues until no improvement in objective function is made.
+\subsection{MODL Discretization}
+\label{MODL}
+MODL discretization \cite{Boulle_2006} is a Bayesian-approach discretization.
+It discretizes a continuous feature according to a class variable.
+The best discretization model is found by maximizing the probability $P(\textit{Model} \mid \textit{Data})$ of the model given the data.
+Using the Bayesian rule and since $P(\textit{Data})$ is a constant while varying the discretization model, this is equivalent to maximize:
+\begin{align}
+P(\textit{Model}) \cdot P(\textit{Data} \mid \textit{Model}).
+\end{align}
+Once the prior distribution of the discretization model is fixed, each term in Eq (3) can be evaluated.
+Usually, $P(\textit{Data} \mid \textit{Model})$ increases as the number of intervals of discretization model increases, since more intervals means that the model contains more information and thus it is easier to reproduce the original data.
+On the other hand, $P(\textit{Model})$ decreases as the number of intervals increases.
+Thus, maximizing $P(\textit{Model}) \cdot P(\textit{Data} \mid \textit{Model})$ provides a trade-off to determine number of intervals after discretization.
+
+The MODL method adapts dynamical programming to find the optimal discretization model, and it takes running time $O(N^3 + ||\text{Class}|| \cdot N^2)$, where $N$ is number of data instances.
+\cite{Lustgarten_2011} provide a different prior to evaluate $P(\text{Model})$ term.
+This prior could include the assumption of uniform prior probabilities over discretization in MODL as a special case.
+Additionally, it reduces runing time to $O(||\text{Class}|| \cdot N^2)$.
 
 \section{Preliminaries}
-\label{Prelim}
-\subsection{Bayesian Network}
+\label{Prelim_Notation}
+In this section we provide a brief review of Bayesian networks, including the factorization of joint probability distribution, sampling from a given network, and structure learning.
+These concepts will be used in later sections.
+
+\subsection{Bayesian Network and Structure Learning}
 \label{BN_basic}
@@
 The graph structure $G$ encodes the Markov property: each node $X_i$ is independent of its non-descendants given its parents in $G$.
-The second component of $B$, namely $\Theta$, contains a set of parameter that qualifies the network.
-Elements of $\Theta$ take the form $\theta_{x_i|\Pi_{x_i}} = P(x_i|\Pi_{x_i})$ for each possible value $x_i$ of $X_i$, and $\Pi_{x_i}$ of $\Pi_{X_i}$ (the set of parents of $X_i$ in $G$).
-Due to Markov property, we can represent the multivariate joint distribution over $X$ as
-\begin{equation*}
-P_B (X_1 , \cdots, X_n) = \prod_{i=1}^{n} P_B (X_i | \Pi_{X_i}) = \prod_{i=1}^{n} \theta_{x_i|\Pi_{x_i}}
-\end{equation*}\\
+The second component of $B$, namely $\Theta$, contains a set of parameters that qualify the network.
+Elements of $\Theta$ take the form $\theta_{x_i \mid \Pi_{x_i}} = P(x_i \mid \Pi_{x_i})$ for each possible value $x_i$ of $X_i$, and $\Pi_{x_i}$ of $\Pi_{X_i}$ (the set of parents of $X_i$ in $G$).
+Applying Markov property, we can represent the multivariate joint distribution over $X$ as
+\begin{equation}
+P_B (X_1 , \cdots, X_n) = \prod_{i=1}^{n} P_B (X_i \mid \Pi_{X_i}) = \prod_{i=1}^{n} \theta_{x_i \mid \Pi_{x_i}}
+\end{equation}
+
 For a given Bayesian network, we can generate its data instances by forward sampling, i.e., sampling variables one by one in a topological order \citep[see][chap.~22]{algo_2009}.
-Given a instance of $X_i$'s parent set $\Pi_{X_i}$, value of $X_i$ can be sampled according to the conditional probability table $P(X_i | \Pi_{X_i})$.
+Given an instance of $X_i$'s parent set, $\Pi_{X_i}$, values of $X_i$ can be sampled according to the conditional probability table $P(X_i \mid \Pi_{X_i})$.
 Furthermore, this parent-child sampling order can be reversed if we know the marginal probability of child variable $P(X_i)$.
 By Bayes rule,
-\begin{equation*}
-P(X_i | \Pi_{X_i}) \cdot \prod_{j = 1}^{ Pa( X_i)} P( \{ \Pi_{X_i} \}_j) = P(X_i) \cdot P(\Pi_{X_i} | X_i),
-\end{equation*}
+\begin{equation}
+P(X_i \mid \Pi_{X_i}) \cdot \prod_{j = 1}^{ Pa( X_i)} P( \{ \Pi_{X_i} \}_j) = P(X_i) \cdot P(\Pi_{X_i} \mid X_i),
+\end{equation}
 where $Pa( X_i)$ is the number of parents of $X_i$, and $\{ \Pi_{X_i} \}_j$ is the $j$th parent of $X_i$.
-We can first sample $X_i$ by $P(X_i)$, then sample all the parent varaibles simultaneously by $P(\Pi_{X_i} | X_i)$.
+We can first sample $X_i$ by $P(X_i)$, then sample all the parent variables simultaneously by $P(\Pi_{X_i} \mid X_i)$.
 That is to say, $X_i$ becomes the starting point for sampling.
 
-\subsection{K2 Structure Learning}
-\label{intro_K2}
-K2 ...
+If we don't know the structure of the Bayesian network in advance, then we need to learn it from data.
+Roughly speaking, there are three approaches to learn a Bayesian network structure from data \citep[see][chap.~18]{PGM_2009}: constraint-based structure learning, score-based structure learning, and Bayesian model averaging.
+Here we review K2 structure learning algorithm \citep{K2}, which is one of the most successful score-based structure learning methods.
+Similar to most structure learning algorithms, the K2 algorithm requires all variables to be discrete.
+The score of a learned network is defined as $\prod_i f(X_i, \Pi_{X_i})$, where
+\begin{align}
+f(X_i, \Pi_{X_i}) = \prod_{j=1}^{||\Pi_{X_i}||} {{(||X_i||-1)!}\over{(N_{ij} + ||X_i||-1)!}} \prod_{k=1}^{||X_i||} \alpha_{ijk}!.
+\end{align}
+$||X_i||$ is the cardinality of variable $X_i$.
+$||\Pi_{X_i}||$ is number of all possible instantiations of the parent variables of $X_i$, i.e., $|\Pi_{X_i}| = \prod_{Y \in \Pi_{X_i}} |Y|$.
+$\alpha_{ijk}$ is the number of instances in a data set that variable $X_i$ is instantiated with its $k$th value, and the parent of $X_i$ are instantiated with the $j$th value of $\Pi_{X_i}$.
+$N_{ij} = \sum_{k=1}^{|X_i|} \alpha_{ijk}$.
 
-\section{Related Work}
-\label{relat_work}
-\subsection{MDL Principle Discretization}
-\label{MDL}
+K2 algorithm searches the network structure with the highest score, which can be interpreted as the most probable network with the given data.
+In addition, K2 requires a topological order of variables to be known before scoring can start.
+This constraint can prevent cycles from being introduced.
+The searching for high-score network is an iterative process.
+There is no way to find the optimal network directly, since there are $2^{O(n^2)}$ possible structures, where $n$ is number of variables.
+In order to compensate for this, we run K2 algorithm many times, and each time we start with a different order of variables.
+The network with the highest score in iterations is the desired one.
 
-\subsection{MODL Discretization}
-\label{MODL}
+\subsection{Discretization Policy}
+\label{Disc_p}
+A Discretization Policy $M_C = < t_1,t_2, ..., t_{k-1} >$ on a continuous variable $C$ is a mapping from $\boldsymbol{R}$ to $\{1,2,3,...,k \}$ such that
+\begin{equation}
+  M_C (x)=\begin{cases}
+    1, & \text{if $x<t_1$}.\\
+    i, & \text{if $t_{i-1} \leq x < t_i$}.\\
+    k, & \text{if $t_k \leq x$}
+  \end{cases}
+\end{equation}
+That is to say, the policy discretizes the continuous variable $C$ into $k$ intervals.
+Furthermore, we assume that the discretization edge $t_i$ can only take values on middle points of two consective values of data of $C$.
+By this assumption, we can obtain an integer representation of $M_C$ as follows:
+we sort the data of continuous variable $C$ in an increasing order, $\{ c_1,c_2,...,c_N \}$, and if $t_i = (c_{s_{i}} + c_{s_{i}+1})/2$ for $i=1,2,...,k$, then $M_C = < t_1,t_2, ..., t_{k-1} > \equiv [n_1,n_2,..n_k]$, where $n_1 = s_1$ and $n_i = s_{i} - s_{i-1}$ for $i = 2,...,k$.\\
 
@@
 \label{one-conti}
-
+In this section, we consider the case that only one variable in a Bayesian network is continuous and the others are discrete.
+Before we formulate the objective function, we introduce some notations that will make the following calculation easier.
 \subsection{Notations}
 \label{Notation}
+Assume the continuous variable is $X$.
+It has $n_p$ parent variables, $\Pi_X = \{ P_1, P_2, P_3,...,P_{n_p}\}$.
+It also has $n_c$ child variables $\{ C_1, C_2,...,C_{n_c}\}$.
+Each child variable $C_i$ of $X$ has other parent variables, which forms a set $\boldsymbol{S_i}$.
+Before we do the discretization, we sort the data instances by its attribute of $X$.
 
-\subsection{Objective Function}
+Let $D \cup D_X$ be a dataset of $N$ instances which we plan to learn discretization from.
+$D_X$ only contains the data of $X$.
+$D$ contains the data of all variables except $X$.
+Assume $D \cup D_X$ has been sorted in the ascending order of $D_X$.
+In the following content, $D_{\boldsymbol{Y}}$ means the data instances of a set of variable $\boldsymbol{Y}$.
+Let $D_X = \{ x_1,x_2,x_3,...,x_N \}$.
+In order to make the discretization mechanism more understandable, we temporarily assume there is no repeated values in $D_X$, i.e., $x_1 < x_2 < ...
+< x_N$.
+We will remove this assumption later in the algorithm section.
+Therefore, a discretization policy $M$ on $X$ can be written as $M = [n_1,n_2,...,n_k]$, where $k$, $n_1$, $n_2$,..., and $n_k$ are positive integers satisfying $N = \sum_{i=1}^k n_i$.
+
+%Furthermore, since there might have repeated values for $D_x$, we assume there are $N'$ unique values of $D_x$ and $N' \leq N$.
+Note that the allowable discretization edges happens between two consective values of non-repeated value of $D_x$.
+For example, if $D_X = \{ 1.0,1.0,2.0\}$, then the only possible discretization edge is on $1.5$.
+
+\subsection{Priors and Objective Function}
 \label{obj}
+We have the following four priors for the discretization model $M$ that enable us to evaluate $P(M)$ and $P(D \mid M)$:\\
+\begin{enumerate}
+\item For a discretization edge locating at $(x_i + x_{i+1})/2$ has probability
+\begin{equation}
+1 - {exp(- M \cdot {{x_{i+1} - x_i}\over{x_N - x_1}})},
+\end{equation}
+where $M$ is the largest cardinality number of discrete variables in $X$'s Markov blanket.
+\item For a given interval of $M$, every distribution of $\Pi_X$ is equiprobable.
+\item For each pair of $(C_i,\boldsymbol{S_i})$ and a given interval of $M$, every distribution of $C_i$ with a value of $\boldsymbol{S_i}$ is equiprobable.
+\item The distributions of each $C_i$ and $\Pi_X$ in each interval of $M$ are independent from each other.
+\end{enumerate}
 
+Owing to these priors, we are able to evaluate $P(M)$ and $P(D \mid M)$. For the former, we have
+\begin{equation}
+P(M) = \prod_{i=1}^k \{ [1 - {exp(- M \cdot {{x_{s_i+1} - c_{x_i}}\over{x_N - x_1}})}] \cdot exp(M \cdot {{x_{s_{i}} - x_{s_{i-1} + 1}}\over{x_N - x_1}}) \},
+\end{equation}
+where $s_i = \sum_{j=1}^k n_j$ and $s_k = N$, $s_0 = 0$. Before evaluating $P(D \mid M)$, notice that
+\begin{equation}
+P(D \mid M) \propto P(D_{\Pi_x} \mid M) \cdot \prod_{i = 1}^{n_c} P(D_{C_i} \mid M, D_{\boldsymbol{S_i}}).
+\end{equation}
+The graph structure allows us to only consider the interations between $X$ and other variables in its Markov blanket and also make the factorization.
+For example, in Figure 1., the corresponding $P(D \mid M)$ is factorized as
+\begin{equation}
+P(D_{ P_1,P_2,P_3 } \mid M) \cdot P( D_{ C_1 } \mid M,D_{\boldsymbol{S_1}}) \cdot P(D_{C_2} \mid M,D_{ S_2  }).
+\end{equation}
+
+% For one-column wide figures use
+\begin{figure}
+% Use the relevant command to insert your figure file.
+% For example, with the graphicx package use
+  \includegraphics[width=6cm]{graph1.png}
+% figure caption is below the figure
+\caption{Factorization of $P(D \mid M)$}
+\label{fig:1}       % Give a unique label
+\end{figure}
+
+The concept behind the factorization is similar to sampling in a Bayesian network.
+Once we have the distribution of $X$ and sample $X$ for it, then we can further sample $\Pi_x$.
+Since the samples of variables in $\Pi_x$ are not independent, we can not further factorize $P(D_{\Pi_x} \mid M)$ into $\prod_i P(D_{P_i} \mid M)$.
+Similarly, once we have a set of samples of $X$ and $\boldsymbol{S_i}$, we can sample $C_i$.
+Since the sampling processes of child variables are independent from each other, we have the product $\prod_{i = 1}^{n_c} P(D_{C_i} \mid M, D_{\boldsymbol{S_i}})$.\\
+
+For the following part, we evaluate $P(D_{\Pi_x} \mid M)$  and $P(D_{C_i} \mid M, D_{\boldsymbol{S_i}})$ based on discretization policy $M = [n_1,n_2,...,n_k]$ and dataset $D$.
+\subsubsection{Evaluate $P(D_{\Pi_x} \mid M)$}
+Assume that $J_P = \prod_{i=1}^{n_p} || P_i ||$. Then we have:
+\begin{equation}
+P(D_{\Pi_X} \mid M) = \prod_{i=1}^k  {{1}\over{{n_i + J_P - 1}\choose{J_P -1}}}
+{{1}\over{ {{{n}_i}!}\over{ {n^{(p)}_{i,1} !} {n^{(p)}_{i,2} !} \cdots {n^{(p)}_{i,J_P} !}}  }},
+\end{equation}
+where $n^{(p)}_{i,j}$ is the number of instances in $i$th discretized interval with $j$th value of $\Pi_X$.
+Note that $n_i = \sum_{j=1}^{|| \Pi_x ||} n^{(p)}_{i,j}$.
+The two factors on RHS comes from the second prior: all distributions of values of $\Pi_X$ in a given interval are equiprobable.
+According to the forth prior, the distribution in each interval is independent, so we multiply all the two factors together.
+\subsubsection{Evaluate $P(D_{C_i} \mid M, D_{\boldsymbol{S_i}})$}
+Assume for each pair of $(C_j, \boldsymbol{S_j})$, we have $||C_j || = J_j$ and $|| \boldsymbol{S_j} || = L_j = \prod_{v \in \boldsymbol{S_j}} || v ||$. Therefore,
+\begin{equation}
+P(D_{C_j}  \mid M, D_{S_j}) =
+\prod_{i=1}^{k} \prod_{l=1}^{L_j} {{1}\over{{n_{i,l} + J_j - 1}\choose{J_j-1}}}
+{{1}\over{ {{n_{i,l}}!}\over{ {n^{(j)}_{i,1,l} !} {n^{(j)}_{i,2,l} !} \cdots {n^{(j)}_{i,J_j,l} !}}  }},
+\end{equation}
+where $n^{(j)}_{i,m,l}$ is the number of instances in $i$th interval with $m$th value of $C_j$ and $l$th value of $\boldsymbol{S_j}$, $n_{i,l} = \sum_{m=1}^{J_j} n^{(j)}_{i,m,l}$, and $n_i = \sum_{l=1}^{L_j} n_{i,l}$.
+The two factors on RHS comes from the third prior: all distribution of values of $C_j$ in a given interval and with a given value of $S_j$ are equiprobable.
+According to the forth prior, these distributions are independent from each other, therefore we multiply all factors.
+If $S_j = \emptyset$, then Equation 13.
+is equivalent to
+\begin{equation}
+P(D_{C_j}  \mid M) =
+\prod_{i=1}^{k}  {{1}\over{{n_{i} + J_j - 1}\choose{J_j-1}}}
+{{1}\over{ {{n_{i}}!}\over{ {n^{(j)}_{i,1,\emptyset} !} {n^{(j)}_{i,2,\emptyset} !} \cdots {n^{(j)}_{i,J_j,\emptyset} !}}  }},
+\end{equation}
+where $n^{(j)}_{i,m,\emptyset}$ is the number of instances in $i$th interval with $m$th value of $C_j$, and $\sum_{m=1}^{J_j} n^{(j)}_{i,m,\emptyset} = n_i$. \\
+
+With Equation 8,9,11,12, and 13, now we are able to write down the objective function. Instead of maximizing $P(M) \cdot P(D|M)$, we minimize its log-inverse for convenience. The objective function is
+\begin{equation}
+\begin{aligned}
+& \sum_{i=1}^{k-1} - log(1 - {exp(- M \cdot {{x_{s_i+1} - x_{s_i}}\over{x_N - x_1}})}) +  \sum_{i=1}^{k} M \cdot {{x_{s_{i}} - x_{s_{i-1} + 1}}\over{x_N - x_1}} +\\
+&  \sum_{j=1}^{n_c} \sum_{i=1}^{k}  \sum_{l=1}^{L_j} \left[  log{{n_{i,l} + J_j - 1}\choose{J_j-1}} + log \left( { {{n_{i,l}}!}\over{ {n^{(j)}_{i,1,l} !} {n^{(j)}_{i,2,l} !} \cdots {n^{(j)}_{i,J_j,l} !}} } \right) \right] + \\
+& \sum_{i=1}^k \left[  log {{n_{i} + J_P - 1}\choose{J_P-1}} + log \left( { {{n_i}!}\over{ {n^{(p)}_{i,1} !} {n^{(p)}_{i,2} !} \cdots {n^{(p)}_{i,J_p} !}} } \right) \right].
+\end{aligned}
+\end{equation}
+All parameters and variables in the objective function are explained in previous subsections.
 \subsection{Algorithm}
 \label{algo}
+Once the objective function is established, the next problem is how to find a discretization model that minimizes the objective function.
+Note that the objective function is cumulative on intervals.
+Therefore, if a partition of continuous variable $X$ into $I$ intervals with lengths $n_1,n_2,...,n_k$ is an optimal discretization policy, then $\{ n_2, n_3,...,n_k \}$ is optimal for the subproblem, i.e., the last $N - n_1$ instances of the dataset which has been sorted in ascending order of $D_X$.
+With this property, we can adapt dynamical programming to solve this optimization problem.
+
+If there is no repeated value in $D_X$, all middle points of two consecutive values can be discretization edges.
+If there exists repeated values in $D_X$, only the middle points of two consecutive and different values can be discretization edges.
+Assume there are $M$ unique values in $D_X$, then ${D'_X} = \{ x'_1,x'_2,...,x'_M \}$ are the unique values in ascending order.
+Since $D_X$ is also sorted, let $b = \{ b_0,b_1,b_2,...,b_M \}$ be an increasing sequence of integers such that $b_0 = 0$ and $x'_i = x_{b_{i-1} + 1} = x_{b_{i-1} + 2} = ...
+= x_{{b_i}}$.
+By this definition, the allowable discretization positions are $d_i = (x_{{b_i}+1} + x_{b_{i}})/2$ for all $i = 1,2,...,M-1$.
+
+In order to save runtime, we first calculate the following function $g(u,v)$ for a interval $I_q$ starting from $x_{u}$ to $x_{v}$ with all $u$,$v$ satisfying $u \leq v$:
+\begin{equation}
+\begin{aligned}
+g_p(u,v) &=  log {{n_{q} + J_P - 1}\choose{J_P-1}} + log \left( { {{n_q}!}\over{ {n^{(p)}_{q,1} !} {n^{(p)}_{q,2} !} \cdots {n^{(p)}_{q,J_p} !}} } \right) \\
+g_c(u,v) &= \sum_{j=1}^{n_c} \sum_{l=1}^{L_j} \left[  log{{n_{q,l} + J_j - 1}\choose{J_j-1}} + log \left( { {{n_{q,l}}!}\over{ {n^{(j)}_{q,1,l} !} {n^{(j)}_{q,2,l} !} \cdots {n^{(j)}_{q,J_j,l} !}} } \right) \right] \\
+g(u,v) &= g_p(u,v) + g_c(u,v).
+\end{aligned}
+\end{equation}
+
+The evaluation of function $g_p(u,v)$ and $g_c(u,v)$ can be done as Algorithm 1 and Algorithm 2, respectively.
+Algorithm 2 is an illustrative version of calculation $g_c(u,v)$.
+The more time-efficient but structurely complicated algorithm for calculating $g_c(u,v)$ is shown in Appendix.
+Notice that due to repeated values in $D_X$, for some pairs of $u$ and $v$, $g(u,v)$ might depend on the sorting method.
+However, this doesn't influence the optimization result, since these pairs of $u$ and $v$ will not form valid intervals.
+Now we are able to solve the optimization problem with the objective function in Equation 14.
+The dynamical programming procedure is shown in Algorithm 3.
+As discussed before, the runtime of Algorithm 3 is $O(n_c  {v_{max}} \cdot N^2 + {v_{max}}^{n_p} \cdot N^2)$, where $v_{max}$ is the largest cardinality number of variables that directly connects $X$.
+There are other methods that lead to suboptimal results but runs faster than dynamical programming method.
+Please refer to \citep{Boulle_2006}.
+\begin{algorithm}
+\caption{ Calculation of function $g_p(u,v)$ for all $u \leq v$}\label{euclid}
+\begin{algorithmic}[1]
+\State Initialize $g_p$ as an $N$ by $N$ matrix that all elements are 0.
+\State $count_p$ is an N by N by $||\Pi_X||$ matrix such that $count_p (u,v,w)$ is the number of instances from $x_u$ to $x_v$ with $w$th value of $\Pi_X$.
+This matrix can be calculated in $O(||\Pi_X|| \cdot N^2)$
+\For {$u = 1$ to $N$}
+\For {$v = u$ to $N$}
+\State $g_p(u,v) \leftarrow g_p(u,v) + log((v-u + J_p)!) - log((J_p -1)!)$
+\For {$w = 1$ to $||\Pi_X||$}
+\State $g_p(u,v) \leftarrow g_p(u,v) - log( count_p(u,v,w)!)$
+\EndFor 
+\EndFor
+\EndFor
+\end{algorithmic}
+\end{algorithm}
+
+\begin{algorithm}
+\caption{ Calculation of function $g_c(u,v)$ for all $u \leq v$}\label{euclid}
+\begin{algorithmic}[1]
+\For {$j = 1$ to $n_c$}
+\State $count_j$ is an N by N by $||\boldsymbol{S_j}||$ by $||C_j||$ matrix such that $count_j (u,v,q,r)$ is the number of instances from $x_u$ to $x_v$ with $q$th value of $\boldsymbol{S_j}$ and $r$th value of $C_j$.
+\For {$u=1$ to $N$}
+\For {$v = u$ to $N$}
+\For {$q = 1$ to $||\boldsymbol{S_j}||$}
+\State $n' \leftarrow  \sum_{r=1}^{J_j} count_j (u,v,q,r)$
+\State $g(u,v) \leftarrow g(u,v) + log(( v - u + 1 + n')!) - log((v-u+1)!)$
+\For {$r = 1$ to $J_j$}
+\State $g(u,v) \leftarrow g(u,v) - log((count_j (u,v,q,r))!)$
+\EndFor
+\EndFor
+\EndFor
+\EndFor
+\EndFor
+\end{algorithmic}
+\end{algorithm}
+
+\begin{algorithm}
+\caption{ Discretization of one continuous variable}\label{euclid}
+\begin{algorithmic}[1]
+\State Let $S(u)$ be the optimal objective function value of a subproblem starting from instance $1$ to instance $u$.
+\State Let $Disc(u)$ be the optimal discretization of a subproblem starting from instance $1$ to instance $u$.
+\State Let $L(u) = - log(1 - {exp(- M \cdot {{x_{b(u)+1} - x_{b(u)}}\over{x_N - x_1}})})$ for $u = 1,2...,M-1$ and $L(M) = 0$. 
+\State Calculate $g(u,v)$ for all $u \leq v$ as Algorithm 1.
+\For {$v = 1$ to $M$}
+\If {$v = 1$}
+\State $S(v) = g \left(1,b(v) \right) + L(v)$
+\State $Disc(v) = \{ ({x_{b(v)} + x_{b(v)+1}}) / 2\}$
+\Else
+\State $s = \infty$ and $boundary = \infty$
+\For {$u = 1$ to $v$}
+\State $s' \leftarrow S(u) + g \left( b(u)+1,b(v) \right) +  {M({x_{b(v)} - x_{b(u) + 1}})\over{x_N - x_1}} + L(v)$
+\If {$s' < s$}
+\State $s \leftarrow s'$
+\State $boundary = ({x_{b(u)} + x_{b(u)+1}}) / 2$
+\EndIf
+\EndFor
+\State $S(v) = s$
+\State $Disc(v) = Disc(u) \cup \{ boundary\}$
+\EndIf
+\EndFor
+
+\end{algorithmic}
+\end{algorithm}
 
@@
 \label{approx}
+Notice that Algorithm1 leads to the non-polynomial runtime $O({v_{max}}^{n_p} \cdot N^2)$ in the discretization process.
+Therefore, we have an empirical approximation to the objective function that can reduce runtime and still preserve the quality of discretization.
+As shown in Section 6, the approximated algorithm is more sensitive to the distribution of other variables' values and usually leads to slightly more discretization edges.
+With the approximation, we can reduce runtime of Algorithm 1 from $O({v_{max}}^{n_p} \cdot N^2)$ to $O({v_{max}} \cdot {n_p} \cdot N^2)$.
+The rigorous proof of the approximation have not been proposed.
+
+For the dominator of the last factor in Equation 11, we have the following approximation
+\begin{equation}
+{{{{n}_i}!}\over{ {{n^{(p)}}_{i,1} !} {n^{(p)}_{i,2} !} \cdots {n^{(p)}_{i,J_P} !}}} \approx \prod_{q=1}^{n_p} { {{{n}_i}!}\over{ {n^{(p_q)}_{i,1} !} {n^{(p_q)}_{i,2} !} \cdots {n^{(p_q)}_{i,J_{p_q}} !}}},
+\end{equation}
+where $J_{p_q} = || P_q||$ and ${n^{(p_q)}_{i,j} !}$ is the number of instances in $i$th interval with $j$th value of $P_q$.
+Then the calculation of corresponding approximated $g_p(u,v)$ can be done as Algorithm 4.
+With the approximation, the approximate objective function is
+\begin{equation}
+\begin{aligned}
+& \sum_{i=1}^{k-1} - log(1 - {exp(- M \cdot {{x_{s_i+1} - x_{s_i}}\over{x_N - x_1}})}) +  \sum_{i=1}^{k} M \cdot {{x_{s_{i}} - x_{s_{i-1} + 1}}\over{x_N - x_1}} +\\
+&  \sum_{j=1}^{n_c} \sum_{i=1}^{k}  \sum_{l=1}^{L_j} \left[  log{{n_{i,l} + J_j - 1}\choose{J_j-1}} + log \left( { {{n_{i,l}}!}\over{ {n^{(j)}_{i,1,l} !} {n^{(j)}_{i,2,l} !} \cdots {n^{(j)}_{i,J_j,l} !}} } \right) \right] + \\
+& \sum_{i=1}^k \left[  log {{n_{i} + J_P - 1}\choose{J_P-1}} + \sum_{q=1}^{n_p} log \left( { {{{n}_i}!}\over{ {n^{(p_q)}_{i,1} !} {n^{(p_q)}_{i,2} !} \cdots {n^{(p_q)}_{i,J_{p_q}} !}}} \right) \right].
+\end{aligned}
+\end{equation}
+
+\begin{algorithm}
+\caption{ Calculation of approximated function $g_p(u,v)$ for all $u \leq v$}\label{euclid}
+\begin{algorithmic}[1]
+\State Initialize $g_p$ as an $N$ by $N$ matrix that all elements are 0.
+\For {$q = 1$ to $n_p$}
+\State $count_{p_q}$ is an N by N by $||P_q||$ matrix such that $count_{p_q} (u,v,w)$ is the number of instances from $x_u$ to $x_v$ with $w$th value of $P_q$.
+This matrix can be calculated in $O(||P_q|| \cdot N^2)$
+\For {$u = 1$ to $N$}
+\For {$v = u$ to $N$}
+\State $g_p(u,v) \leftarrow g_p(u,v) + log((v-u + ||P_q||)!) - log((||P_q|| -1)!)$
+\For {$w = 1$ to $||P_q||$}
+\State $g_p(u,v) \leftarrow g_p(u,v) - log( count_p(u,v,w)!)$
+\EndFor 
+\EndFor
+\EndFor
+\EndFor
+\end{algorithmic}
+\end{algorithm}
+
+With Equation 17, we have a more clear way to see that how child variables and parent variables contribute to the objective function differently.
+For example, in the left graph of Figure 2, the corresponding sqaure bracket in Equation 17 is
+\begin{equation}
+\begin{aligned}
+ \sum_{i=1}^k & \left\lbrace   \left[ log{{n_{i} + J_{C_1} - 1}\choose{J_{C_1}-1}} + log \left(  {{{n_i}!} \over { {n^{(1)}_{i,1,\emptyset} !} \cdots {n^{(1)}_{i,J_{C_1},\emptyset} !}} }  \right)  +  \right.
+\right.\\
+& \left.  log{{n_{i} + J_{C_2} - 1}\choose{J_{C_2}-1}} + log \left(  {{{n_i}!} \over { {n^{(2)}_{i,1,\emptyset} !} \cdots {n^{(2)}_{i,J_{C_1},\emptyset} !}} }  \right)  \right] + \\
+&  \left.
+\left[  log {{n_{i} + J_P - 1}\choose{J_P-1}} +  log \left( { {{{n}_i}!}\over{ {n^{(p_1)}_{i,1} !}\cdots {n^{(p_1)}_{i,J_{p_1}} !}}} \right) +{ {{{n}_i}!}\over{ {n^{(p_2}_{i,1} !}\cdots {n^{(p_2)}_{i,J_{p_2}} !}}}  \right] \right\rbrace\\ .
+\end{aligned}
+\end{equation}
+In Equation18, each child variable carries two terms as the first square bracket, and two parent variables only carry three terms as the second square bracket.
+Therefore, in this case, child variables are more determinative than parent variables, even though the number of child variables is same as the number of parent variables.
+However, if $C_2$ has another parent variables, as shown in the right graph of Figure 2, the importances of $C_2$ will be debiliated, since the information from $C_2$ is now adulterated by $S_2$.
+These argument shows that our proposed method, either before or after approximation, indeed involves graph structures to discretize continuous variables.
+
+\begin{figure}
+% Use the relevant command to insert your figure file.
+% For example, with the graphicx package use
+  \includegraphics[width=9cm]{graph2.png}
+% figure caption is below the figure
+\caption{Two example networks}
+\label{fig:2}       % Give a unique label
+\end{figure}
 
 \section{Discretizing Multiple Continuous Variable with Structure Learning}
-\label{multiple-conti}
+\label{DMC_SL}
+\subsection{Discretization of Multiple Continuous Variables}
+\label{DMC}
+If there are multiple continuous variables in a Bayesian network, we iterate the one-variable discretization method discussed above for all continuous variables.
+While discretizing a continuous variable, other continuous variables must be discretized, either by prediscretization before the iteration starts or by the discretization results of previous iteration.
+The prediscretization here can be done by equal-width discretization, which is defined as follows:
+\begin{equation}
+M_X =  \{ min_X, min_X + \delta, min_X + 2\delta, ..., \delta, max_X \},
+\end{equation}
+where $min_X$ and $max_X$ are minimal and maximal values of $D_X$, respectively, $\delta =  (max_X - min_X)/k$ and $k$ is the desired number of intervals after equal-width discretization.
+$k$ is same for all continuous variables and is set to be median value of all discrete variables' cardinalities.
+After prediscretization, we iterate the one-variable discretization on each continuous variable in the following order: from the continuous variable with highest topological order (leaves) to the continuous variable with lowest topological order (root).
+We call a series of the iterations that follows this order one time as a cycle.
+The advange of the order is that, for the first cycle of iteration, we can use less number of unsupervised discretization result.
+For example, in the right graph of Figure 2, assume $S_2$ is the only discrete variable.
+If we begin the iteration with $P_1$, then the discretization of $P_1$ will involve the prediscretization results of $P_2$ and $X$.
+However, if we begin the iteration with $C_1$, then the discretization of $C_1$ will only involve the prediscretization result of $X$.
+
+We stop the iterations and output the discretization result on each continuous variable when the number of intervals and the positions of discretization edges converge.
+Since the convergence is not guaranteed, we also set up a maximal number of cycles to prevent infinite iterations.
+In our test on real-world data, the iteration results usually converge within few cycles.
+Even if it does not converge, 10 cycles usually produce good enough discretization result.
+The summary of multi-variable discretization is shown as Algorithm 5.
+
+\begin{algorithm}
+\caption{ Discretization of multiple continuous variables}
+\begin{algorithmic}[1]
+\State Let $Disc(i)$ is the discretization on $i$th continuous variable. If variable $i$ is discrete, $Disc(i)$ contains no information. 
+\State Let $D^*_i$ is the discrete data of $i$th variable. If variable $i$ is continuous, then $D*_i$ is discretized $D_i$ by $Disc(i)$.
+\State Let $C$ be the set of continuous variables in a reverse topological order.
+\State Let $n$ be the number of variables in the given Bayesian network, $k$ is the largest cardinality number of discrete variables.
+\State \% Prediscretize continuous variables, $bound_{cycle}$ is the upper bound of cycles.
+\For {$i = 1$ to $n$}
+\If {$i \in C$}
+\State {$Disc(i)$ = prediscretization result of $k$ intervals}
+\EndIf
+\EndFor
+\State \% Iterate one-variable discretization until converge
+\State $cycle = 0$
+\While {$Disc$ is not converged  $\&$ $cycle \leq bound_{cycle}$}
+\State {$cycle  \leftarrow cycle  + 1$}
+\For {$j = 1$ to $||C||$}
+\State {Let $D^*_{\backslash C(j)}$ be the discrete data of all variables except $D^*_{C(j)}$.}
+\State {$Disc(C(j)) = $ one-varaible discretization result with $D_{C(j)}$ and  $D^*_{ \backslash C(j)}$.}
+\State {$D^*_{C(j)} =$ the discretized data of $D_{C(j)}$ by lastest discetization policy $Disc(C(j)) $}
+\EndFor
+\EndWhile
+\end{algorithmic}
+\end{algorithm}
+
+\subsection{Discretization of Continuous Variables While Structure Learning}
+\label{SL}
 
@@
 
+\section*{Appendices}
 \end{document}

### 2015-11-06 BN_discretizer_paper.tex
update 11/6

@@
 \usepackage{algorithm}
-\usepackage{algpseudocode}
+\usepackage[noend]{algpseudocode}
 \usepackage[round]{natbib}
@@
 It is based on minimum description length principle (MDL): optimal discretization policy minimizes the description length of Bayesian network and data information.
-If there is only one continuous variable in Bayesian network and other variables are discrete, this MDL discretization method takes running time $O(N^3 + n_c {v_{max}}^{(n_c^p)_{max}} \cdot N^2 + {v_{max}}^{n_p} \cdot N^2)$, where $N$ is the number of data instances for learning the discretization, $n_p$ and $n_c$ are the numbers of parent and children variables for the continuous variable, $v_{max}$ is the largest cardinality number over all variables in Markov blanket, and  ${(n_c^p)_{max}}$ is the largest number of parent variables of the continuous variable's children.
+If there is only one continuous variable in a Bayesian network and other variables are discrete, this MDL discretization method takes running time $O(N^3 + n_c {v_{max}}^{(n_c^p)_{max}} \cdot N^2 + {v_{max}}^{n_p} \cdot N^2)$, where $N$ is the number of data instances for learning the discretization, $n_p$ and $n_c$ are the numbers of parent and children variables for the continuous variable, $v_{max}$ is the largest cardinality over all variables in the Markov blanket, and  ${(n_c^p)_{max}}$ is the largest number of parent variables of the continuous variable's children.
 If there are multiple continuous variables in the network, the method iterates over all continuous variables until convergence.
-In our test on real world data, the iterations converge in a few cycles.
-However, the number of intervals after discretization is too small.
+In our test on real-world data, the iterations converge in a few cycles.
+However, the number of intervals after discretization is usually too small.
 
@@
 In addition, the $P(D \mid M)$ can be factorized according to Bayesian network structure.
-With the proposed priors, we are able to restrict the number of discretized intervals so that it will not exceed the largest cardinality number of variables in the Markov blanket by too much.
+With the proposed priors, we are able to restrict the number of discretized intervals so that it will not exceed the largest cardinality of variables in the Markov blanket by too much.
 This is important, since for most algorithms on Bayesian networks, their running times exponentially depend on the cardinality of variables.
 Another advantage of our method is the running time for learning.
-If there is only one continuous variable, the running time is $O(n_c  {v_{max}} \cdot N^2 + {v_{max}}^{n_p} \cdot N^2)$, which is significiantly shorter than the running time of MDL principle discretization \citep{Friedman_1996}.
+If there is only one continuous variable, the running time is $O(n_c  {v_{max}} \cdot N^2 + {v_{max}}^{n_p} \cdot N^2)$, which is significantly shorter than the running time of MDL principle discretization \citep{Friedman_1996}.
 With the approximation proposed in this paper, we can further reduce running time to $O({v_{max}}(n_p+n_c)N^2)$.
@@
 Each time we finish a discretization procedure on one variable, we store the discretization result for later iterations.
-Experiments on real data show that with the same iteration order, our discretization method provides better discretization results than MDL principle method in terms of likelihood.
+Experiments on real-world data show that with the same iteration order, our discretization method provides better discretization results than MDL principle method in terms of likelihood.
 The MDL principle method is easily stuck at local minima and also discretizes variables into too few intervals.
 
-Finally, we can combine the our new discretization method with K2 structure learning alorithm \citep{K2}.
-We first prediscretize all continuous variables before K2 learning, since the K2 algorithm requires all variables to be discrete.
-Each time an edge is added in the K2 algorithm procedure, we rediscretize the relevant variables in the learned Bayesian network and store the result for next K2 algorithm iteration.
+Finally, we can combine the our new discretization method with the K2 structure learning alorithm \citep{K2}.
+We first prediscretize all continuous variables before the K2 learning, since the K2 algorithm requires all variables to be discrete.
+Each time an edge is added in the K2 algorithm procedure, we rediscretize the continuous variables based on the updated Bayesian network and store the result for the next K2 algorithm iteration.
 By this principle, we are able to learn a discrete-valued Bayesian network from mixed data.
@@
 Section 5 is a discussion about multiple continuous variables in a Bayesian network and how to discretize them.
-The combination of our proposed discretization and K2 structure learning is also introduced.
+The combination of our proposed discretization and the K2 structure learning is also introduced.
 Finally, in Section 6, we apply the proposed discretization method to real-world data and show the result.
@@
 Therefore it has an advantage that automatically avoids overfitting.
-In the case of Bayesian networks, \citep{Friedman_1996} applied the MDL concept to determine the number of intervals of each continuous variable after discretization and also the positions of discretization boundaries.
+In the case of Bayesian networks, \cite{Friedman_1996} applied the MDL concept to determine the number of intervals of each continuous variable after discretization and also the positions of discretization boundaries.
 Here is the mechanism: MDL principle discretization selects a discretization policy that minimizes sum of description lengths of discretized Bayesian network and the necessary information that recovers original data from discretized data.
@@
 \begin{aligned}
-&{1 \over 2} log(N) \{  \lVert \Pi_{X_i} \rVert (\lVert X^*_i \rVert - 1) +
- {\sum_{j,X_i \in \Pi_{X_i}}} \lVert \Pi_{X^*_j} \rVert (\lVert X_j \rVert - 1) \} + \\
-& log(\lVert {X^*_i} \rVert) + log{{N_{i}-1}\choose{\lVert {X^*_i} \rVert -1}}  -N \cdot [I(X^*_i,\Pi_{X_i}) + {\sum_{j,X_i \in \Pi_{X_i}}} I(X_j, \Pi_{X^*_j})],
+&{1 \over 2} \log(N) \left\lbrace  \lVert \Pi_{X_i} \rVert (\lVert X^*_i \rVert - 1) +
+ {\sum_{j,X_i \in \Pi_{X_i}}} \lVert \Pi_{X^*_j} \rVert (\lVert X_j \rVert - 1) \right\rbrace + \log(\lVert {X^*_i} \rVert) \\
+& + (N_i-1) H \left( {{||X^*_i|| - 1}\over{N_i -1}}  \right) -N \cdot \left[ I(X^*_i,\Pi_{X_i}) + {\sum_{j,X_i \in \Pi_{X_i}}} I(X_j, \Pi_{X^*_j}) \right],
 \end{aligned}
 \end{equation}
-where function $I(\boldsymbol{A},\boldsymbol{B}) = \sum_{\boldsymbol{a},\boldsymbol{b}} \hat{P}_D (\boldsymbol{a},\boldsymbol{b}) log {{\hat{P}_D (\boldsymbol{a},\boldsymbol{b})}\over{\hat{P}_D (\boldsymbol{a}),\hat{P}_D (\boldsymbol{b})}}$ is the mutual information between two sets of variables $\boldsymbol{A}$ and $\boldsymbol{B}$, $||\boldsymbol{X}||$ means the cardinality of variable $\boldsymbol{X}$ and $X^*_i$ is the discretized version of continuous variable $X_i$.
+where function $I(\boldsymbol{A},\boldsymbol{B}) = \sum_{\boldsymbol{a},\boldsymbol{b}} \hat{P}_D (\boldsymbol{a},\boldsymbol{b}) \log {{\hat{P}_D (\boldsymbol{a},\boldsymbol{b})}\over{\hat{P}_D (\boldsymbol{a}),\hat{P}_D (\boldsymbol{b})}}$ is the mutual information between two sets of variables $\boldsymbol{A}$ and $\boldsymbol{B}$, $||\boldsymbol{X}||$ means the cardinality of a variable set $\boldsymbol{X}$, $X^*_i$ is the discretized version of continuous variable $X_i$ and $H(p) = -p \log(p) - (1-p) \log(1-p)$.
 The optimal discretization policy can be found by dynamical programming.
-If there are multiple continuous variables in Bayesian network, we apply the algorithm on one variable at a time and iterate over all continuous variables.
+If there are multiple continuous variables in a Bayesian network, we apply the algorithm on one variable at a time and iterate over all continuous variables.
 While iterating, only one variable is treated as continuous and other continuous variables are discretized based on initial prediscretization or the discretization result of previous iteration.
@@
 \label{MODL}
-MODL discretization \cite{Boulle_2006} is a Bayesian-approach discretization.
+MODL discretization \citep{Boulle_2006} is a Bayesian-approach discretization.
 It discretizes a continuous feature according to a class variable.
 The best discretization model is found by maximizing the probability $P(\textit{Model} \mid \textit{Data})$ of the model given the data.
-Using the Bayesian rule and since $P(\textit{Data})$ is a constant while varying the discretization model, this is equivalent to maximize:
+Using Bayes' rule and since $P(\textit{Data})$ is a constant while varying the discretization model, this is equivalent to maximize:
 \begin{align}
@@
 These concepts will be used in later sections.
+In addition, the formal definition of a discretization policy on a continuous variable is also introduced.
 
@@
 Furthermore, this parent-child sampling order can be reversed if we know the marginal probability of child variable $P(X_i)$.
-By Bayes rule,
+By Bayes' rule,
 \begin{equation}
@@
 We can first sample $X_i$ by $P(X_i)$, then sample all the parent variables simultaneously by $P(\Pi_{X_i} \mid X_i)$.
-That is to say, $X_i$ becomes the starting point for sampling.
+That is to say, $X_i$ becomes the starting point of sampling.
 
@@
 Roughly speaking, there are three approaches to learn a Bayesian network structure from data \citep[see][chap.~18]{PGM_2009}: constraint-based structure learning, score-based structure learning, and Bayesian model averaging.
-Here we review K2 structure learning algorithm \citep{K2}, which is one of the most successful score-based structure learning methods.
+Here we review the K2 structure learning algorithm \citep{K2}, which is one of the most successful score-based structure learning methods.
 Similar to most structure learning algorithms, the K2 algorithm requires all variables to be discrete.
@@
 
-K2 algorithm searches the network structure with the highest score, which can be interpreted as the most probable network with the given data.
-In addition, K2 requires a topological order of variables to be known before scoring can start.
+The K2 algorithm searches the network structure with the highest score, which can be interpreted as the most probable network with the given data.
+In addition, the K2 requires a topological order of variables to be known before the scoring can start.
 This constraint can prevent cycles from being introduced.
@@
 There is no way to find the optimal network directly, since there are $2^{O(n^2)}$ possible structures, where $n$ is number of variables.
-In order to compensate for this, we run K2 algorithm many times, and each time we start with a different order of variables.
+In order to compensate for this, we run the K2 algorithm many times, and each time we start with a different order of variables.
 The network with the highest score in iterations is the desired one.
@@
 \label{Disc_p}
-A Discretization Policy $M_C = < t_1,t_2, ..., t_{k-1} >$ on a continuous variable $C$ is a mapping from $\boldsymbol{R}$ to $\{1,2,3,...,k \}$ such that
+A Discretization Policy $M_C = < t_1,t_2, \ldots, t_{k-1} >$ on a continuous variable $C$ is a mapping from $\boldsymbol{R}$ to $\{1,2,3,\ldots,k \}$ such that
 \begin{equation}
@@
 By this assumption, we can obtain an integer representation of $M_C$ as follows:
-we sort the data of continuous variable $C$ in an increasing order, $\{ c_1,c_2,...,c_N \}$, and if $t_i = (c_{s_{i}} + c_{s_{i}+1})/2$ for $i=1,2,...,k$, then $M_C = < t_1,t_2, ..., t_{k-1} > \equiv [n_1,n_2,..n_k]$, where $n_1 = s_1$ and $n_i = s_{i} - s_{i-1}$ for $i = 2,...,k$.\\
+we sort the data of continuous variable $C$ in an increasing order, $\{ c_1,c_2,\ldots,c_N \}$, and if $t_i = (c_{s_{i}} + c_{s_{i}+1})/2$ for $i=1,2,\ldots,k$, then $M_C = < t_1,t_2, \ldots, t_{k-1} > \equiv [n_1,n_2,..n_k]$, where $n_1 = s_1$ and $n_i = s_{i} - s_{i-1}$ for $i = 2,\ldots,k$.\\
 
@@
 Assume the continuous variable is $X$.
-It has $n_p$ parent variables, $\Pi_X = \{ P_1, P_2, P_3,...,P_{n_p}\}$.
-It also has $n_c$ child variables $\{ C_1, C_2,...,C_{n_c}\}$.
+It has $n_p$ parent variables, $\Pi_X = \{ P_1, P_2, P_3,\ldots,P_{n_p}\}$.
+It also has $n_c$ child variables $\{ C_1, C_2,\ldots,C_{n_c}\}$.
 Each child variable $C_i$ of $X$ has other parent variables, which forms a set $\boldsymbol{S_i}$.
@@
 In the following content, $D_{\boldsymbol{Y}}$ means the data instances of a set of variable $\boldsymbol{Y}$.
-Let $D_X = \{ x_1,x_2,x_3,...,x_N \}$.
-In order to make the discretization mechanism more understandable, we temporarily assume there is no repeated values in $D_X$, i.e., $x_1 < x_2 < ...
-< x_N$.
+Let $D_X = \{ x_1,x_2,x_3,\ldots,x_N \}$.
+In order to make the discretization mechanism more understandable, we temporarily assume there is no repeated values in $D_X$, i.e., $x_1 < x_2 < \ldots < x_N$.
 We will remove this assumption later in the algorithm section.
-Therefore, a discretization policy $M$ on $X$ can be written as $M = [n_1,n_2,...,n_k]$, where $k$, $n_1$, $n_2$,..., and $n_k$ are positive integers satisfying $N = \sum_{i=1}^k n_i$.
+Therefore, a discretization policy $M$ on $X$ can be written as $M = [n_1,n_2,\ldots,n_k]$, where $k$, $n_1$, $n_2$, $\ldots,n_k$ are positive integers satisfying $N = \sum_{i=1}^k n_i$.
 
@@
 \begin{equation}
-1 - {exp(- M \cdot {{x_{i+1} - x_i}\over{x_N - x_1}})},
+1 - {\exp(- L \cdot {{x_{i+1} - x_i}\over{x_N - x_1}})},
 \end{equation}
-where $M$ is the largest cardinality number of discrete variables in $X$'s Markov blanket.
+where $L$ is the largest cardinality number of discrete variables in $X$'s Markov blanket.
 \item For a given interval of $M$, every distribution of $\Pi_X$ is equiprobable.
 \item For each pair of $(C_i,\boldsymbol{S_i})$ and a given interval of $M$, every distribution of $C_i$ with a value of $\boldsymbol{S_i}$ is equiprobable.
-\item The distributions of each $C_i$ and $\Pi_X$ in each interval of $M$ are independent from each other.
+\item The distributions of each $C_i$ and $\Pi_X$ in each interval of $M$ with each value of $\boldsymbol{S_i}$ are independent from each other.
 \end{enumerate}
@@
 \begin{equation}
-P(M) = \prod_{i=1}^k \{ [1 - {exp(- M \cdot {{x_{s_i+1} - c_{x_i}}\over{x_N - x_1}})}] \cdot exp(M \cdot {{x_{s_{i}} - x_{s_{i-1} + 1}}\over{x_N - x_1}}) \},
+P(M) = \prod_{i=1}^k \{ [1 - {\exp(- L \cdot {{x_{s_i+1} - x_{s_i}}\over{x_N - x_1}})}] \cdot \exp(L \cdot {{x_{s_{i}} - x_{s_{i-1} + 1}}\over{x_N - x_1}}) \},
 \end{equation}
@@
 \end{equation}
-The graph structure allows us to only consider the interations between $X$ and other variables in its Markov blanket and also make the factorization.
+The graph structure allows us to only consider the interations between $X$ and other variables in its Markov blanket and thus leads to the factorization.
 For example, in Figure 1., the corresponding $P(D \mid M)$ is factorized as
@@
 Once we have the distribution of $X$ and sample $X$ for it, then we can further sample $\Pi_x$.
-Since the samples of variables in $\Pi_x$ are not independent, we can not further factorize $P(D_{\Pi_x} \mid M)$ into $\prod_i P(D_{P_i} \mid M)$.
-Similarly, once we have a set of samples of $X$ and $\boldsymbol{S_i}$, we can sample $C_i$.
+Since the samples of $P_1,P_2,\ldots,P_{n_p}$ given a value of $X$ are not independent, we can not further factorize $P(D_{\Pi_x} \mid M)$ into $\prod_i P(D_{P_i} \mid M)$.
+Similarly, once we have samples of $X$ and $\boldsymbol{S_i}$, we can sample $C_i$.
 Since the sampling processes of child variables are independent from each other, we have the product $\prod_{i = 1}^{n_c} P(D_{C_i} \mid M, D_{\boldsymbol{S_i}})$.\\
 
-For the following part, we evaluate $P(D_{\Pi_x} \mid M)$  and $P(D_{C_i} \mid M, D_{\boldsymbol{S_i}})$ based on discretization policy $M = [n_1,n_2,...,n_k]$ and dataset $D$.
+For the following part, we evaluate $P(D_{\Pi_x} \mid M)$  and $P(D_{C_i} \mid M, D_{\boldsymbol{S_i}})$ based on discretization policy $M = [n_1,n_2,\ldots,n_k]$ and dataset $D$.
 \subsubsection{Evaluate $P(D_{\Pi_x} \mid M)$}
@@
 \begin{aligned}
-& \sum_{i=1}^{k-1} - log(1 - {exp(- M \cdot {{x_{s_i+1} - x_{s_i}}\over{x_N - x_1}})}) +  \sum_{i=1}^{k} M \cdot {{x_{s_{i}} - x_{s_{i-1} + 1}}\over{x_N - x_1}} +\\
-&  \sum_{j=1}^{n_c} \sum_{i=1}^{k}  \sum_{l=1}^{L_j} \left[  log{{n_{i,l} + J_j - 1}\choose{J_j-1}} + log \left( { {{n_{i,l}}!}\over{ {n^{(j)}_{i,1,l} !} {n^{(j)}_{i,2,l} !} \cdots {n^{(j)}_{i,J_j,l} !}} } \right) \right] + \\
-& \sum_{i=1}^k \left[  log {{n_{i} + J_P - 1}\choose{J_P-1}} + log \left( { {{n_i}!}\over{ {n^{(p)}_{i,1} !} {n^{(p)}_{i,2} !} \cdots {n^{(p)}_{i,J_p} !}} } \right) \right].
+& \sum_{i=1}^{k-1} - \log(1 - {\exp(- L \cdot {{x_{s_i+1} - x_{s_i}}\over{x_N - x_1}})}) +  \sum_{i=1}^{k} L \cdot {{x_{s_{i}} - x_{s_{i-1} + 1}}\over{x_N - x_1}} +\\
+&  \sum_{j=1}^{n_c} \sum_{i=1}^{k}  \sum_{l=1}^{L_j} \left[  \log{{n_{i,l} + J_j - 1}\choose{J_j-1}} + \log \left( { {{n_{i,l}}!}\over{ {n^{(j)}_{i,1,l} !} {n^{(j)}_{i,2,l} !} \cdots {n^{(j)}_{i,J_j,l} !}} } \right) \right] + \\
+& \sum_{i=1}^k \left[  \log {{n_{i} + J_P - 1}\choose{J_P-1}} + \log \left( { {{n_i}!}\over{ {n^{(p)}_{i,1} !} {n^{(p)}_{i,2} !} \cdots {n^{(p)}_{i,J_p} !}} } \right) \right].
 \end{aligned}
@@
 Note that the objective function is cumulative on intervals.
-Therefore, if a partition of continuous variable $X$ into $I$ intervals with lengths $n_1,n_2,...,n_k$ is an optimal discretization policy, then $\{ n_2, n_3,...,n_k \}$ is optimal for the subproblem, i.e., the last $N - n_1$ instances of the dataset which has been sorted in ascending order of $D_X$.
+Therefore, if a partition of continuous variable $X$ into $k$ intervals with lengths $n_1,n_2,\ldots,n_k$ is an optimal discretization policy, then $\{ n_2, n_3,\ldots,n_k \}$ is optimal for the subproblem, i.e., the last $N - n_1$ instances of the dataset which has been sorted in ascending order of $D_X$.
 With this property, we can adapt dynamical programming to solve this optimization problem.
 
-If there is no repeated value in $D_X$, all middle points of two consecutive values can be discretization edges.
-If there exists repeated values in $D_X$, only the middle points of two consecutive and different values can be discretization edges.
-Assume there are $M$ unique values in $D_X$, then ${D'_X} = \{ x'_1,x'_2,...,x'_M \}$ are the unique values in ascending order.
-Since $D_X$ is also sorted, let $b = \{ b_0,b_1,b_2,...,b_M \}$ be an increasing sequence of integers such that $b_0 = 0$ and $x'_i = x_{b_{i-1} + 1} = x_{b_{i-1} + 2} = ...
-= x_{{b_i}}$.
-By this definition, the allowable discretization positions are $d_i = (x_{{b_i}+1} + x_{b_{i}})/2$ for all $i = 1,2,...,M-1$.
+If there is no repeated value in $D_X$, all middle points of two consecutive values can a discretization edge.
+If there exists repeated values in $D_X$, only the middle points of two consecutive and different values can be a discretization edge.
+Assume there are $M$ unique values in $D_X$, then ${D'_X} = \{ x'_1,x'_2,\ldots,x'_M \}$ is the set of unique values of $D_X$ in ascending order.
+Since $D_X$ is also sorted, let $b = \{ b_0,b_1,b_2,\ldots,b_M \}$ be an increasing sequence of integers such that $b_0 = 0$ and $x_{b_{i-1} + 1} = x_{b_{i-1} + 2} = \ldots = x_{{b_i}} = x'_i$.
+By this definition, the allowable discretization positions are $d_i = ( x_{b_{i}} + x_{{b_i}+1})/2$ for all $i = 1,2,\ldots,M-1$.
 
-In order to save runtime, we first calculate the following function $g(u,v)$ for a interval $I_q$ starting from $x_{u}$ to $x_{v}$ with all $u$,$v$ satisfying $u \leq v$:
+Before doing the dynamical programming, in order to save runtime, we first calculate the following function $h(u,v)$ for a interval $I_q$ starting from $x_{u}$ to $x_{v}$ with all $u$,$v$ satisfying $u \leq v$:
 \begin{equation}
 \begin{aligned}
-g_p(u,v) &=  log {{n_{q} + J_P - 1}\choose{J_P-1}} + log \left( { {{n_q}!}\over{ {n^{(p)}_{q,1} !} {n^{(p)}_{q,2} !} \cdots {n^{(p)}_{q,J_p} !}} } \right) \\
-g_c(u,v) &= \sum_{j=1}^{n_c} \sum_{l=1}^{L_j} \left[  log{{n_{q,l} + J_j - 1}\choose{J_j-1}} + log \left( { {{n_{q,l}}!}\over{ {n^{(j)}_{q,1,l} !} {n^{(j)}_{q,2,l} !} \cdots {n^{(j)}_{q,J_j,l} !}} } \right) \right] \\
-g(u,v) &= g_p(u,v) + g_c(u,v).
+h(u,v) &=  \log {{n_{q} + J_P - 1}\choose{J_P-1}} + \log \left( { {{n_q}!}\over{ {n^{(p)}_{q,1} !} {n^{(p)}_{q,2} !} \cdots {n^{(p)}_{q,J_p} !}} } \right) \\
+& + \sum_{j=1}^{n_c} \sum_{l=1}^{L_j} \left[  \log{{n_{q,l} + J_j - 1}\choose{J_j-1}} + \log \left( { {{n_{q,l}}!}\over{ {n^{(j)}_{q,1,l} !} {n^{(j)}_{q,2,l} !} \cdots {n^{(j)}_{q,J_j,l} !}} } \right) \right]
 \end{aligned}
@@
 
-The evaluation of function $g_p(u,v)$ and $g_c(u,v)$ can be done as Algorithm 1 and Algorithm 2, respectively.
-Algorithm 2 is an illustrative version of calculation $g_c(u,v)$.
-The more time-efficient but structurely complicated algorithm for calculating $g_c(u,v)$ is shown in Appendix.
-Notice that due to repeated values in $D_X$, for some pairs of $u$ and $v$, $g(u,v)$ might depend on the sorting method.
-However, this doesn't influence the optimization result, since these pairs of $u$ and $v$ will not form valid intervals.
+The evaluation of function $h(u,v)$ for all $u \leq v$ is summerized in Algorithm 4 in Appendix.
+The calculation can be done in $O(n_c  {v'_{max}} \cdot N^2 + {v'_{max}}^{n_p} \cdot N^2)$, where $n_c$ and $n_p$ are the numbers of child and parent variables, respectively, and $v'_{max}$ is the largest cardinality of variables that directly connects to $X$.
+Notice that due to repeated values in $D_X$, for some pairs of $u$ and $v$, the value of $h(u,v)$ might depend on the sorting method of $D_X$ and $D$.
+However, this does not influence the optimization result, since these pairs of $u$ and $v$ will not form valid intervals.
+
 Now we are able to solve the optimization problem with the objective function in Equation 14.
-The dynamical programming procedure is shown in Algorithm 3.
-As discussed before, the runtime of Algorithm 3 is $O(n_c  {v_{max}} \cdot N^2 + {v_{max}}^{n_p} \cdot N^2)$, where $v_{max}$ is the largest cardinality number of variables that directly connects $X$.
+The dynamical programming procedure is shown in Algorithm 1.
+We have three inputs: $D_X$, the data of continuous variable $X$ in the ascending order, $D$, the data of other variables and sorted according to $D_X$, and $G$, the network structure.
+The runtime of Algorithm 1 is also $O(n_c  {v'_{max}} \cdot N^2 + {v'_{max}}^{n_p} \cdot N^2)$, since the dynamical programming procedure does not increase the time complexity beyond the calculation of $h(u,v)$.
 There are other methods that lead to suboptimal results but runs faster than dynamical programming method.
 Please refer to \citep{Boulle_2006}.
-\begin{algorithm}
-\caption{ Calculation of function $g_p(u,v)$ for all $u \leq v$}\label{euclid}
-\begin{algorithmic}[1]
-\State Initialize $g_p$ as an $N$ by $N$ matrix that all elements are 0.
-\State $count_p$ is an N by N by $||\Pi_X||$ matrix such that $count_p (u,v,w)$ is the number of instances from $x_u$ to $x_v$ with $w$th value of $\Pi_X$.
-This matrix can be calculated in $O(||\Pi_X|| \cdot N^2)$
-\For {$u = 1$ to $N$}
-\For {$v = u$ to $N$}
-\State $g_p(u,v) \leftarrow g_p(u,v) + log((v-u + J_p)!) - log((J_p -1)!)$
-\For {$w = 1$ to $||\Pi_X||$}
-\State $g_p(u,v) \leftarrow g_p(u,v) - log( count_p(u,v,w)!)$
-\EndFor 
-\EndFor
-\EndFor
-\end{algorithmic}
-\end{algorithm}
-
-\begin{algorithm}
-\caption{ Calculation of function $g_c(u,v)$ for all $u \leq v$}\label{euclid}
-\begin{algorithmic}[1]
-\For {$j = 1$ to $n_c$}
-\State $count_j$ is an N by N by $||\boldsymbol{S_j}||$ by $||C_j||$ matrix such that $count_j (u,v,q,r)$ is the number of instances from $x_u$ to $x_v$ with $q$th value of $\boldsymbol{S_j}$ and $r$th value of $C_j$.
-\For {$u=1$ to $N$}
-\For {$v = u$ to $N$}
-\For {$q = 1$ to $||\boldsymbol{S_j}||$}
-\State $n' \leftarrow  \sum_{r=1}^{J_j} count_j (u,v,q,r)$
-\State $g(u,v) \leftarrow g(u,v) + log(( v - u + 1 + n')!) - log((v-u+1)!)$
-\For {$r = 1$ to $J_j$}
-\State $g(u,v) \leftarrow g(u,v) - log((count_j (u,v,q,r))!)$
-\EndFor
-\EndFor
-\EndFor
-\EndFor
-\EndFor
-\end{algorithmic}
-\end{algorithm}
 
@@
 \caption{ Discretization of one continuous variable}\label{euclid}
-\begin{algorithmic}[1]
-\State Let $S(u)$ be the optimal objective function value of a subproblem starting from instance $1$ to instance $u$.
-\State Let $Disc(u)$ be the optimal discretization of a subproblem starting from instance $1$ to instance $u$.
-\State Let $L(u) = - log(1 - {exp(- M \cdot {{x_{b(u)+1} - x_{b(u)}}\over{x_N - x_1}})})$ for $u = 1,2...,M-1$ and $L(M) = 0$. 
-\State Calculate $g(u,v)$ for all $u \leq v$ as Algorithm 1.
-\For {$v = 1$ to $M$}
+\begin{algorithmic}[5]
+\Function{Discretize}{$D_X$, $D$, $G$}
+\State
+\State $N \leftarrow$ the number of instances
+\State $N' \leftarrow$ the number of non-repeated values of $D_X$
+\State $H \leftarrow$ an $N \times N$ matrix such that $H[u,v] = h(u,v)$ as Algorithm 4 in Appendix
+\State $b \leftarrow$ the increasing sequence of $M$ integers defined in the previous discussion
+\State $L \leftarrow$ the largest cardinality over all discrete variables in the Markov blanket
+\State $S[u] \leftarrow$ the optimal objective value of a subproblem with instances from $1$ to $u$
+\State $M[u] \leftarrow$ the optimal discretization of a subproblem with instances from $1$ to $u$
+\State $W[u]  \leftarrow - \log(1 - {\exp(- L \cdot{ {{x_{b(u)+1} - x_{b(u)}}\over{x_N - x_1}})}})$ for $u = 1,2, \ldots,N'-1$ and $L(N') \leftarrow 0$
+\State 
+\For {$v = 1$ to $N'$}
 \If {$v = 1$}
-\State $S(v) = g \left(1,b(v) \right) + L(v)$
-\State $Disc(v) = \{ ({x_{b(v)} + x_{b(v)+1}}) / 2\}$
+\State $S[v] = g \left(1,b[v] \right) + L[v]$
+\State $M[v] = \{ ({x_{b[v]} + x_{b[v]+1}}) / 2\}$
 \Else
-\State $s = \infty$ and $boundary = \infty$
+\State $s \leftarrow \infty$ and $boundary \leftarrow \infty$
 \For {$u = 1$ to $v$}
-\State $s' \leftarrow S(u) + g \left( b(u)+1,b(v) \right) +  {M({x_{b(v)} - x_{b(u) + 1}})\over{x_N - x_1}} + L(v)$
+\State $s' \leftarrow S[u] + g \left( b[u]+1,b[v] \right) +  {L \cdot {{x_{b[v]} - x_{b[u] + 1}}\over{x_N - x_1}}} + W[v]$
 \If {$s' < s$}
 \State $s \leftarrow s'$
-\State $boundary = ({x_{b(u)} + x_{b(u)+1}}) / 2$
+\State $boundary \leftarrow ({x_{b[u]} + x_{b[u]+1}}) / 2$
 \EndIf
 \EndFor
-\State $S(v) = s$
-\State $Disc(v) = Disc(u) \cup \{ boundary\}$
+\State $S[v] \leftarrow s$
+\State $M[v] \leftarrow M[u] \cup \{ boundary\}$
 \EndIf
 \EndFor
-
+ \State \Return $M$
+\EndFunction
 \end{algorithmic}
@@
 \label{approx}
-Notice that Algorithm1 leads to the non-polynomial runtime $O({v_{max}}^{n_p} \cdot N^2)$ in the discretization process.
+Notice that Algorithm1 leads to the non-polynomial runtime $O({v'_{max}}^{n_p} \cdot N^2)$ in the discretization process.
 Therefore, we have an empirical approximation to the objective function that can reduce runtime and still preserve the quality of discretization.
-As shown in Section 6, the approximated algorithm is more sensitive to the distribution of other variables' values and usually leads to slightly more discretization edges.
-With the approximation, we can reduce runtime of Algorithm 1 from $O({v_{max}}^{n_p} \cdot N^2)$ to $O({v_{max}} \cdot {n_p} \cdot N^2)$.
-The rigorous proof of the approximation have not been proposed.
-
-For the dominator of the last factor in Equation 11, we have the following approximation
+The approximation is as follows: for the dominator of the last factor in Equation 11, we have
 \begin{equation}
-{{{{n}_i}!}\over{ {{n^{(p)}}_{i,1} !} {n^{(p)}_{i,2} !} \cdots {n^{(p)}_{i,J_P} !}}} \approx \prod_{q=1}^{n_p} { {{{n}_i}!}\over{ {n^{(p_q)}_{i,1} !} {n^{(p_q)}_{i,2} !} \cdots {n^{(p_q)}_{i,J_{p_q}} !}}},
+{{{{n}_i}!}\over{ {{n^{(p)}}_{i,1} !} {n^{(p)}_{i,2} !} \cdots {n^{(p)}_{i,J_P} !}}} \approx \prod_{r=1}^{n_p} { {{{n}_i}!}\over{ {n^{(p_r)}_{i,1} !} {n^{(p_r)}_{i,2} !} \cdots {n^{(p_r)}_{i,J_{p_r}} !}}},
 \end{equation}
-where $J_{p_q} = || P_q||$ and ${n^{(p_q)}_{i,j} !}$ is the number of instances in $i$th interval with $j$th value of $P_q$.
-Then the calculation of corresponding approximated $g_p(u,v)$ can be done as Algorithm 4.
-With the approximation, the approximate objective function is
+where $J_{p_r} = || P_r||$ and ${n^{(p_r)}_{i,j} !}$ is the number of instances in $i$th interval with $j$th value of $P_r$. Applying this approximation, the approximated objective function is
 \begin{equation}
 \begin{aligned}
-& \sum_{i=1}^{k-1} - log(1 - {exp(- M \cdot {{x_{s_i+1} - x_{s_i}}\over{x_N - x_1}})}) +  \sum_{i=1}^{k} M \cdot {{x_{s_{i}} - x_{s_{i-1} + 1}}\over{x_N - x_1}} +\\
-&  \sum_{j=1}^{n_c} \sum_{i=1}^{k}  \sum_{l=1}^{L_j} \left[  log{{n_{i,l} + J_j - 1}\choose{J_j-1}} + log \left( { {{n_{i,l}}!}\over{ {n^{(j)}_{i,1,l} !} {n^{(j)}_{i,2,l} !} \cdots {n^{(j)}_{i,J_j,l} !}} } \right) \right] + \\
-& \sum_{i=1}^k \left[  log {{n_{i} + J_P - 1}\choose{J_P-1}} + \sum_{q=1}^{n_p} log \left( { {{{n}_i}!}\over{ {n^{(p_q)}_{i,1} !} {n^{(p_q)}_{i,2} !} \cdots {n^{(p_q)}_{i,J_{p_q}} !}}} \right) \right].
+& \sum_{i=1}^{k-1} - \log(1 - {\exp(- L \cdot {{x_{s_i+1} - x_{s_i}}\over{x_N - x_1}})}) +  \sum_{i=1}^{k} L \cdot {{x_{s_{i}} - x_{s_{i-1} + 1}}\over{x_N - x_1}} +\\
+&  \sum_{j=1}^{n_c} \sum_{i=1}^{k}  \sum_{l=1}^{L_j} \left[  \log{{n_{i,l} + J_j - 1}\choose{J_j-1}} + \log \left( { {{n_{i,l}}!}\over{ {n^{(j)}_{i,1,l} !} {n^{(j)}_{i,2,l} !} \cdots {n^{(j)}_{i,J_j,l} !}} } \right) \right] + \\
+& \sum_{i=1}^k \left[  \log {{n_{i} + J_P - 1}\choose{J_P-1}} + \sum_{q=1}^{n_p} \log \left( { {{{n}_i}!}\over{ {n^{(p_q)}_{i,1} !} {n^{(p_q)}_{i,2} !} \cdots {n^{(p_q)}_{i,J_{p_q}} !}}} \right) \right].
 \end{aligned}
@@
 
-\begin{algorithm}
-\caption{ Calculation of approximated function $g_p(u,v)$ for all $u \leq v$}\label{euclid}
-\begin{algorithmic}[1]
-\State Initialize $g_p$ as an $N$ by $N$ matrix that all elements are 0.
-\For {$q = 1$ to $n_p$}
-\State $count_{p_q}$ is an N by N by $||P_q||$ matrix such that $count_{p_q} (u,v,w)$ is the number of instances from $x_u$ to $x_v$ with $w$th value of $P_q$.
-This matrix can be calculated in $O(||P_q|| \cdot N^2)$
-\For {$u = 1$ to $N$}
-\For {$v = u$ to $N$}
-\State $g_p(u,v) \leftarrow g_p(u,v) + log((v-u + ||P_q||)!) - log((||P_q|| -1)!)$
-\For {$w = 1$ to $||P_q||$}
-\State $g_p(u,v) \leftarrow g_p(u,v) - log( count_p(u,v,w)!)$
-\EndFor 
-\EndFor
-\EndFor
-\EndFor
-\end{algorithmic}
-\end{algorithm}
+As we will see in Section 6, the approximated algorithm is more sensitive to the distribution of other variables' values and usually leads to slightly more discretization edges.
+With the approximation, we can reduce runtime of Algorithm 1 from $O(n_c  {v'_{max}} \cdot N^2 + {v'_{max}}^{n_p} \cdot N^2)$ to $O( {v'_{max}} (n_c + n_p) \cdot N^2)$.
+The rigorous proof of the approximation have not been proposed.
 
-With Equation 17, we have a more clear way to see that how child variables and parent variables contribute to the objective function differently.
-For example, in the left graph of Figure 2, the corresponding sqaure bracket in Equation 17 is
+With the approximated objective function, Equation 17, we now have a more clear way to see that how child variables and parent variables contribute to the objective function differently.
+For example, in the left graph of Figure 2, the corresponding sqaure brackets in Equation 17 are
 \begin{equation}
 \begin{aligned}
- \sum_{i=1}^k & \left\lbrace   \left[ log{{n_{i} + J_{C_1} - 1}\choose{J_{C_1}-1}} + log \left(  {{{n_i}!} \over { {n^{(1)}_{i,1,\emptyset} !} \cdots {n^{(1)}_{i,J_{C_1},\emptyset} !}} }  \right)  +  \right.
+ \sum_{i=1}^k & \left\lbrace   \left[ \log{{n_{i} + J_{C_1} - 1}\choose{J_{C_1}-1}} + \log \left(  {{{n_i}!} \over { {n^{(1)}_{i,1,\emptyset} !} \cdots {n^{(1)}_{i,J_{C_1},\emptyset} !}} }  \right)  +  \right.
 \right.\\
-& \left.  log{{n_{i} + J_{C_2} - 1}\choose{J_{C_2}-1}} + log \left(  {{{n_i}!} \over { {n^{(2)}_{i,1,\emptyset} !} \cdots {n^{(2)}_{i,J_{C_1},\emptyset} !}} }  \right)  \right] + \\
+& \left.  \log{{n_{i} + J_{C_2} - 1}\choose{J_{C_2}-1}} + \log \left(  {{{n_i}!} \over { {n^{(2)}_{i,1,\emptyset} !} \cdots {n^{(2)}_{i,J_{C_1},\emptyset} !}} }  \right)  \right] + \\
 &  \left.
-\left[  log {{n_{i} + J_P - 1}\choose{J_P-1}} +  log \left( { {{{n}_i}!}\over{ {n^{(p_1)}_{i,1} !}\cdots {n^{(p_1)}_{i,J_{p_1}} !}}} \right) +{ {{{n}_i}!}\over{ {n^{(p_2}_{i,1} !}\cdots {n^{(p_2)}_{i,J_{p_2}} !}}}  \right] \right\rbrace\\ .
+\left[  \log {{n_{i} + J_P - 1}\choose{J_P-1}} +  \log \left( { {{{n}_i}!}\over{ {n^{(p_1)}_{i,1} !}\cdots {n^{(p_1)}_{i,J_{p_1}} !}}} \right) +{ {{{n}_i}!}\over{ {n^{(p_2}_{i,1} !}\cdots {n^{(p_2)}_{i,J_{p_2}} !}}}  \right] \right\rbrace\\ .
 \end{aligned}
 \end{equation}
-In Equation18, each child variable carries two terms as the first square bracket, and two parent variables only carry three terms as the second square bracket.
-Therefore, in this case, child variables are more determinative than parent variables, even though the number of child variables is same as the number of parent variables.
-However, if $C_2$ has another parent variables, as shown in the right graph of Figure 2, the importances of $C_2$ will be debiliated, since the information from $C_2$ is now adulterated by $S_2$.
+In Equation18, each child variable carries two terms, as shown in the first square bracket, and two parent variables only carry three terms, as shown in the second square bracket.
+Therefore, in this case, child variables are more determinative than parent variables even though the numbers of child variables and parent variables are equal.
+However, if $C_2$ has the other parent variable $S_2$, as shown in the right graph of Figure 2, the importances of $C_2$ will be debiliated, since the information from $C_2$ is now adulterated by $S_2$.
 These argument shows that our proposed method, either before or after approximation, indeed involves graph structures to discretize continuous variables.
@@
 If there are multiple continuous variables in a Bayesian network, we iterate the one-variable discretization method discussed above for all continuous variables.
-While discretizing a continuous variable, other continuous variables must be discretized, either by prediscretization before the iteration starts or by the discretization results of previous iteration.
-The prediscretization here can be done by equal-width discretization, which is defined as follows:
+While discretizing a continuous variable, other continuous variables must be discretized, either by a prediscretization that was done before the first iteration or by the discretization result of the lastest iteration.
+The prediscretization can be done by equal-width discretization, which is defined as follows:
 \begin{equation}
-M_X =  \{ min_X, min_X + \delta, min_X + 2\delta, ..., \delta, max_X \},
+M_X =  \{ min_X, min_X + \delta, min_X + 2\delta, \ldots, \delta, max_X \},
 \end{equation}
-where $min_X$ and $max_X$ are minimal and maximal values of $D_X$, respectively, $\delta =  (max_X - min_X)/k$ and $k$ is the desired number of intervals after equal-width discretization.
+where $min_X$ and $max_X$ are minimal and maximal values of $D_X$, respectively, $\delta =  (max_X - min_X)/k$, and $k$ is the desired number of intervals after equal-width discretization.
 $k$ is same for all continuous variables and is set to be median value of all discrete variables' cardinalities.
 After prediscretization, we iterate the one-variable discretization on each continuous variable in the following order: from the continuous variable with highest topological order (leaves) to the continuous variable with lowest topological order (root).
-We call a series of the iterations that follows this order one time as a cycle.
+We call one such series of discretizations as a cycle.
 The advange of the order is that, for the first cycle of iteration, we can use less number of unsupervised discretization result.
 For example, in the right graph of Figure 2, assume $S_2$ is the only discrete variable.
-If we begin the iteration with $P_1$, then the discretization of $P_1$ will involve the prediscretization results of $P_2$ and $X$.
+If we begin the iteration with $P_1$, then the discretization of $P_1$ will involve the prediscretization results of both $P_2$ and $X$.
 However, if we begin the iteration with $C_1$, then the discretization of $C_1$ will only involve the prediscretization result of $X$.
 
-We stop the iterations and output the discretization result on each continuous variable when the number of intervals and the positions of discretization edges converge.
+When the number of intervals after discretization and the positions of discretization edges converge, we stop the iterations and output the discretization policy on each continuous variable.
 Since the convergence is not guaranteed, we also set up a maximal number of cycles to prevent infinite iterations.
@@
 Even if it does not converge, 10 cycles usually produce good enough discretization result.
-The summary of multi-variable discretization is shown as Algorithm 5.
+The pseudocode of multi-variable discretization is shown in Algorithm 2, where we require four inputs: $D''$, the mixed data of all variables that we plan to learn from, $G$, the network structure, $C$, the set of all continuous variables in a reverse topological order, and $u_{cycle}$, the upper bound of times of cycles.
 
@@
 \caption{ Discretization of multiple continuous variables}
-\begin{algorithmic}[1]
-\State Let $Disc(i)$ is the discretization on $i$th continuous variable. If variable $i$ is discrete, $Disc(i)$ contains no information. 
-\State Let $D^*_i$ is the discrete data of $i$th variable. If variable $i$ is continuous, then $D*_i$ is discretized $D_i$ by $Disc(i)$.
-\State Let $C$ be the set of continuous variables in a reverse topological order.
-\State Let $n$ be the number of variables in the given Bayesian network, $k$ is the largest cardinality number of discrete variables.
-\State \% Prediscretize continuous variables, $bound_{cycle}$ is the upper bound of cycles.
+\begin{algorithmic}[5]
+\Function{Discretize}{$D''$, $G$, $C$, $u_{cycle}$}
+\State
+\State $M[i] \leftarrow$ the discretization policy of $i$th variable
+\State $n \leftarrow$ the number of variables in Bayesian network
+\State $D^*_i \leftarrow M[i] (D_i)$, the discretized $D_i$ by $M[i]$
+\State $D^* \leftarrow $ the discretized data for all variables, where $D^*_i \leftarrow D''_i$ if $i \notin C$
+\State $k \leftarrow median\{ ||v||, v\notin C\}$
+\State
 \For {$i = 1$ to $n$}
 \If {$i \in C$}
-\State {$Disc(i)$ = prediscretization result of $k$ intervals}
+\State $M[i] \leftarrow$  equal-width discretization with $k$ intervals
+\State $D^*_i \leftarrow  M[i] (D''_i)$
 \EndIf
 \EndFor
-\State \% Iterate one-variable discretization until converge
-\State $cycle = 0$
-\While {$Disc$ is not converged  $\&$ $cycle \leq bound_{cycle}$}
+\State
+\State $cycle \leftarrow 0$
+\While {$M$ is not converged  \textbf{and} $cycle \leq u_{cycle}$}
 \State {$cycle  \leftarrow cycle  + 1$}
 \For {$j = 1$ to $||C||$}
-\State {Let $D^*_{\backslash C(j)}$ be the discrete data of all variables except $D^*_{C(j)}$.}
-\State {$Disc(C(j)) = $ one-varaible discretization result with $D_{C(j)}$ and  $D^*_{ \backslash C(j)}$.}
-\State {$D^*_{C(j)} =$ the discretized data of $D_{C(j)}$ by lastest discetization policy $Disc(C(j)) $}
+\State $D^*_{\backslash C(j)} \leftarrow D^*$ without $D^*_{C(j)}$.
+\State {$M[C(j)] \leftarrow $ DISCRETIZE($D_{C(j)}$,$D^*_{ \backslash C(j)}$,graph)}
+\State {$D^*_{C(j)}  \leftarrow$ $M[C(j)](D''_{C(j)}) $}
 \EndFor
 \EndWhile
+\State \Return $M$
+\EndFunction
 \end{algorithmic}
@@
 \label{SL}
+In many situations the network structure is not known in advance, then we need to learn it from data.
+We use an alternative approach to combine our proposed discretization method with the K2 structure learning algorithm \citep{K2}.
+That is to say, we start with some prediscretizations on continuous variables and run the K2 algorithm given the discretized data.
+Each time an edge is added by the K2 algorithm, we rediscretize the continuous variables based on the current network.
+Then the new discretization policies update the discretized data of all continuous variables, and we continue the next K2 step with the updated discretized data.
+This cycle is repeated until no edge is added by the K2 algorithm.
+The detail of the procedure is shown in Algorithm 3.
+Here we have five inputs: $D'$, the mixed data we plan to learn from, $C$, the set of all continuous variables, $order$, the variable order which is required by the $K2$, $u_{parent}$, the upper bound of number of parents which is also required by the $K2$, and $u_{cycle}$, the upper bound of times of cycles.
+Notice that in the usual structure learning from discrete data, one usually run the K2 algorithm many times with different orders, and choose the structure with the highest K2 score.
+We do the same thing: run Algorithm 3 many times, each time with a different order, and pick the discretized Bayesian network with the highest K2 score.
+\begin{algorithm}
+\caption{ Learning a discrete-valued Bayesian network}
+\begin{algorithmic}[5]
+\Function{Learn\_DBN}{$D''$, $C$, $order$, $u_{parent}$, $C$, $u_{cycle}$}
+\State
+
+\State $n \leftarrow$ the number of variables in Bayesian network
+\State $k \leftarrow median\{ ||v||, v\notin C\}$
+\State $M[i] \leftarrow$ the discretization policy of $i$th variable
+\State $D^*_i \leftarrow M[i] (D_i)$, the discretized $D_i$ by $M[i]$
+\State $D^* \leftarrow $ the discretized data for all variables, where $D^*_i \leftarrow D''_i$ if $i \notin C$
+\State $G \leftarrow$ the initial graph (no edges between nodes)
+\State
+\For {$i = 1$ to $n$}
+\If {$i \in C$}
+\State $M[i] \leftarrow$  equal-width discretization with $k$ intervals
+\State $D^*_i \leftarrow  M[i] (D''_i)$
+\EndIf
+\EndFor
+\State
+\For {$i =1$ to $n$}
+\State $P_{old} \leftarrow f(X^*_i,\Pi_{X^*_i})$: Equation 5
+\State OKToProceed $\leftarrow$ \textbf{true}
+\While OKToProceed \textbf{and} $||\Pi_{X^*_i}|| < u_{parent}$
+\State $Y \leftarrow$ an element from the set $order[1:i] \backslash \Pi_X$
+\State $P_{new} \leftarrow f(X^*_i,\Pi_{X^*_i} \cup Y)$
+\If {$P_{new} > P_{old}$}
+\State $P_{old} \leftarrow P_{new}$
+\State $\Pi_{X_i} \leftarrow \Pi_{X_i} \cup Y $
+\State $M \leftarrow$ {DISCRETIZE}({$D''$, $G$, $C$, $u_{cycle}$}): Algorithm 2
+\State $D* = M(D'')$
+\Else
+\State OKToProceed $\leftarrow$ \textbf{false}
+\EndIf
+\EndWhile
+\EndFor
+\State \Return $G$, $M$
+\EndFunction
+\end{algorithmic}
+\end{algorithm}
 
@@
 \section*{Appendices}
+
+\begin{algorithm}
+\caption{ Calculation of function $h(u,v)$ for all $u \leq v$}\label{euclid}
+\begin{algorithmic}[1]
+\State Initialize $H$ as an $N \times N$ matrix that all elements are 0.
+\State $count_p$ is an $N \times N \times ||\Pi_X||$ matrix such that $count_p [u,v,w]$ is the number of instances from $x_u$ to $x_v$ with $w$th value of $\Pi_X$.
+This matrix can be calculated in $O(||\Pi_X|| \cdot N^2)$
+\For {$u = 1$ to $N$}
+\For {$v = u$ to $N$}
+\State $H(u,v) \leftarrow H(u,v) + \log((v-u + J_p)!) - \log((J_p -1)!)$
+\For {$w = 1$ to $||\Pi_X||$}
+\State $H(u,v) \leftarrow H(u,v) - \log( count_p(u,v,w)!)$
+\EndFor 
+\EndFor
+\EndFor
+
+\For {$j = 1$ to $n_c$}
+\State XXX
+\EndFor
+\end{algorithmic}
+\end{algorithm}
+
 \end{document}

### 2015-11-06 BN_discretizer_paper.tex
check one word

@@
 If there are multiple continuous variables in a Bayesian network, we iterate the one-variable discretization method discussed above for all continuous variables.
-While discretizing a continuous variable, other continuous variables must be discretized, either by a prediscretization that was done before the first iteration or by the discretization result of the lastest iteration.
+While discretizing a continuous variable, other continuous variables must be discretized, either by a prediscretization that was done before the first iteration or by the discretization result of the latest iteration.
 The prediscretization can be done by equal-width discretization, which is defined as follows:

### 2015-11-07 BN_discretizer_paper.tex
delete a reductant "the"
png figures to eps figures
change figure files

@@
 \usepackage{graphicx} % Allows including images
+\usepackage{epstopdf}
 \usepackage{algorithm}
@@
 \usepackage[round]{natbib}
+\usepackage{tikz}
+\usetikzlibrary{bayesnet}
 \setcitestyle{aysep={ }} %Author-Year SEParator
@@
 
-Finally, we can combine the our new discretization method with the K2 structure learning alorithm \citep{K2}.
+Finally, we can combine our new discretization method with the K2 structure learning alorithm \citep{K2}.
 We first prediscretize all continuous variables before the K2 learning, since the K2 algorithm requires all variables to be discrete.
@@
 
-% For one-column wide figures use
-\begin{figure}
-% Use the relevant command to insert your figure file.
-% For example, with the graphicx package use
-  \includegraphics[width=6cm]{graph1.png}
-% figure caption is below the figure
+\begin{figure}[ht]
+    \begin{tabular}{cc}
+      \input{graph1}
+    \end{tabular}
   \caption{Factorization of $P(D \mid M)$}
-\label{fig:1}       % Give a unique label
 \end{figure}
@@
 \end{equation}
+
 In Equation18, each child variable carries two terms, as shown in the first square bracket, and two parent variables only carry three terms, as shown in the second square bracket.
@@
 
-\begin{figure}
-% Use the relevant command to insert your figure file.
-% For example, with the graphicx package use
-  \includegraphics[width=9cm]{graph2.png}
-% figure caption is below the figure
+\begin{figure}[ht]
+    \begin{tabular}{cc}
+      \input{graph2_left} 
+      \end{tabular}
+     \hspace{5em}
+      \begin{tabular}{cc}
+      \input{graph2_right} 
+    \end{tabular}
   \caption{Two example networks}
-\label{fig:2}       % Give a unique label
 \end{figure}

### 2015-11-11 BN_discretizer_paper.tex
started going through it

@@
 \usetikzlibrary{bayesnet}
-\setcitestyle{aysep={ }} %Author-Year SEParator
+\setcitestyle{aysep={ }} %Author-Year Separator
 %
@@
 %
+
+\newcommand{\todo}[1]{\textcolor{magenta}{#1}}
+\newcommand{\tim}[1]{\textit{\textcolor{blue}{#1}}}
+
 \begin{document}
@@
 \begin{abstract}
+\todo{
 Insert your abstract here. Include keywords, PACS and mathematical
 subject classification numbers as needed.
+}
 \keywords{Discretization \and Bayesian Network \and Continuous Variable}
@@
 They provide an efficient factorization of the joint probability distribution over a set of random variables.
-Bayesian networks first emerged from artificial intelligence research and have been applied to a wide variety of problems, ranging from decision-making systems \citep{DMU_2015} to medical diagnoses.
-In most cases, we assume that all random variables in Bayesian networks are discrete, since many algorithms on Bayesian networks are unable to deal with continuous variables efficiently.
-However, the assumption that all variables are discrete is often too restrictive.
-For example, in the decision-making system of autonomous cars, it is imperative to deal with continuous variables such as position and velocity.
+Bayesian networks first emerged from artificial intelligence research and have been applied to a wide variety of problems, ranging from decision-making systems \citep{DMU_2015} to medical diagnoses~\todo{[cite]}.
+In most cases, we assume that all random variables in Bayesian networks are discrete, since many Bayesian network learning algorithms are unable to deal with continuous variables efficiently.
+However, many applications
+require the use of continuous variables, such as position and velocity in dynamic systems.
 
-There are two methods around this assumption.
-The first one is to model conditional probability density of each continuous variable by specific families of parametric distributions, then redesign algorithms on Bayesian networks based on these parameters.
+There are two common approaches to extending Bayesian networks to continuous variables.
+The first is to model the conditional probability density of each continuous variable using specific families of parametric distributions, and then to redesign Bayesian network learning algorithms based on their parameters.
 One successful example is belief propagation in Gaussian graphical models \citep{Weiss_2011}.
-Nevertheless, for other shapes of particles \citep{Ihler_2009} or non-linear functions, these redesigned algorithms are computationally expensive and do not perform well.
+For other particle shapes \citep{Ihler_2009} and non-linear functions \tim{cite if you can}, these redesigned algorithms are computationally expensive and do not perform well.
+\tim{Not sure what `particle shapes' are. Do you mean other parametric distributions?}
 
-The second method around continuous variables is to discretize them.
-Discretization that learns from data has been developed well and discussed in the fields of machine learning and statistics for many years \citep{Dougherty_1995, Kerber_1992, Holte_1993, Fayyad_1993} .
-Most of these discretization methods are designed for classification problems.
-They search the best discretization policy of a continuous attribute by considering its interation with the class variable of interest.
-However, these discretization methods do not apply to continuous variables in Bayesian networks.
-In Bayesian networks, interations and dependencies between variables are determined by graph structure.
-Therefore, if a method discretizes continuous variables according to graph structure, instead of assigning one variable as a class variable, then it would be more appropriate.
-There is some reseach on discretizing continuous variables in naive Bayesian networks and tree augmented networks \citep{Fried_naive}, but only a few discretization methods on general Bayesian netowrk have been proposed \citep{Friedman_1996, Kozlov_1997, Monti_1998, Steck_2007}.
+The second approach is discretization.
+Automated discretization methods have been studied in machine learning and statistics for many years \citep{Dougherty_1995, Kerber_1992, Holte_1993, Fayyad_1993}.
+Most discretization methods were designed for classification problems.
+They search for the best discretization policy\tim{maybe `scheme' is a better word than `policy', which in machine learning means something else.} of a continuous attribute by considering its interation with the target class variable.
+These discretization methods do not apply to continuous variables in Bayesian networks, where interations and dependencies between variables are more complicated.
+Discretization of a continuous variable in a Bayesian network requires considering the impact on the entire network.
+There is prior work on discretizing continuous variables in naive Bayesian networks and tree-augmented networks \citep{Fried_naive}, but only a few discretization methods for general Bayesian networks have been proposed \citep{Friedman_1996, Kozlov_1997, Monti_1998, Steck_2007}.
 
-The discretization technique proposed by \citet{Friedman_1996} is the most well-known one among these few methods.
-It is based on minimum description length principle (MDL): optimal discretization policy minimizes the description length of Bayesian network and data information.
-If there is only one continuous variable in a Bayesian network and other variables are discrete, this MDL discretization method takes running time $O(N^3 + n_c {v_{max}}^{(n_c^p)_{max}} \cdot N^2 + {v_{max}}^{n_p} \cdot N^2)$, where $N$ is the number of data instances for learning the discretization, $n_p$ and $n_c$ are the numbers of parent and children variables for the continuous variable, $v_{max}$ is the largest cardinality over all variables in the Markov blanket, and  ${(n_c^p)_{max}}$ is the largest number of parent variables of the continuous variable's children.
-If there are multiple continuous variables in the network, the method iterates over all continuous variables until convergence.
-In our test on real-world data, the iterations converge in a few cycles.
-However, the number of intervals after discretization is usually too small.
+The discretization technique proposed by \citet{Friedman_1996} is the most well-known of these methods.
+It is based on the minimum description length principle (MDL): the optimal discretization policy minimizes the description length of the Bayesian network and discretization scheme.
+The MDL algorithm has a $O(N^3 + n_c {v_{max}}^{(n_c^p)_{max}} \cdot N^2 + {v_{max}}^{n_p} \cdot N^2)$ run time on a Bayesian network with a single continuous variable and multiple discrete variables, where $N$ is the number of data samples from the joint distribution, $n_p$ and $n_c$ are the numbers of parent and children variables for the continuous variable, $v_{max}$ is the largest cardinality over all variables in the Markov blanket, and  ${(n_c^p)_{max}}$ is the largest number of parent variables of the continuous variable's children.
+The MDL method iterates over all continuous variables until convergence in the case of multiple continuous variables, converging in a few cycles according to our tests of real-world data.
+Unfortunately, MDL tends to produce discrete variables with low cardinality.
 
-In this paper, we propose a new discretization method for continuous variables in Bayesian networks by learning from mixed data.
-This method is a generalized version of  \citet{Boulle_2006} and \citet{Lustgarten_2011}, which are both discretization methods of a continuous attribute with one class variable.
-We begin our method with the assumption that only one variable in a given Bayesian network is continuous and other variables are discrete.
+In this paper, we propose a new Bayesian discretization method for continuous variables in Bayesian networks.
+This method extends the Bayesian single-variable discretization methods from \citet{Boulle_2006} and \citet{Lustgarten_2011}.
+
+% We begin our method with the assumption that only one variable in a given Bayesian network is continuous and other variables are discrete.
 Furthermore we assume that the network structure is known in advance.
@@
 
-For a Bayesian network with multiple continuous variables, we apply the discretization method discussed above iteratively.
+% For a Bayesian network with multiple continuous variables, we apply the discretization method discussed above iteratively.
 In the beginning, we prediscretize each continuous variable by equal-width method.
@@
 
-Finally, we can combine our new discretization method with the K2 structure learning alorithm \citep{K2}.
+% Finally, we can combine our new discretization method with the K2 structure learning alorithm \citep{K2}.
 We first prediscretize all continuous variables before the K2 learning, since the K2 algorithm requires all variables to be discrete.
@@
 %\begin{thebibliography}{}
-\bibliographystyle{plainnat}
+\bibliographystyle{spbasic}
 \bibliography{my_bib}

### 2015-11-11 BN_discretizer_paper.tex
more updates

@@
 \usepackage{tikz}
+\usepackage{cleverref}
 \usetikzlibrary{bayesnet}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% CUSTOM COMMANDS
+
+\newcommand{\bigo}{\mathcal{O}} % NOTE(tim): if you prefer normal O change it here.
+
+\newcommand{\paren}[1]{\mathopen{}\mathclose\bgroup\left(#1\aftergroup\egroup\right)}
+\newcommand{\brock}[1]{\mathopen{}\mathclose\bgroup\left[#1\aftergroup\egroup\right\right]}
+\newcommand{\curly}[1]{\mathopen{}\mathclose\bgroup\left\{#1\aftergroup\egroup\right\right\}}
+\newcommand{\anglebrackets}[1]{\langle #1 \rangle}
+\newcommand{\ceil}[1]{\lceil #1 \rceil}
+\newcommand{\floor}[1]{\lfloor #1 \rfloor}
+
+\DeclareMathOperator*{\argmin}{arg\,min}
+\DeclareMathOperator*{\argmax}{arg\,max}
+
 \newcommand{\todo}[1]{\textcolor{magenta}{#1}}
 \newcommand{\tim}[1]{\textit{\textcolor{blue}{#1}}}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 It is based on the minimum description length principle (MDL): the optimal discretization policy minimizes the description length of the Bayesian network and discretization scheme.
-The MDL algorithm has a $O(N^3 + n_c {v_{max}}^{(n_c^p)_{max}} \cdot N^2 + {v_{max}}^{n_p} \cdot N^2)$ run time on a Bayesian network with a single continuous variable and multiple discrete variables, where $N$ is the number of data samples from the joint distribution, $n_p$ and $n_c$ are the numbers of parent and children variables for the continuous variable, $v_{max}$ is the largest cardinality over all variables in the Markov blanket, and  ${(n_c^p)_{max}}$ is the largest number of parent variables of the continuous variable's children.
+The MDL algorithm has a $\bigo\paren{N^3 + \paren{n_c {v_\text{max}}^{(n_c^p)_\text{max}} + {v_\text{max}}^{n_p}} \cdot N^2}$ runtime on Bayesian networks with a single continuous variable and multiple discrete variables, where $N$ is the number of data samples from the joint distribution, $n_p$ and $n_c$ are the numbers of parent and children variables for the continuous variable, $v_\text{max}$ is the largest cardinality over all variables in the Markov blanket, and  ${(n_c^p)_\text{max}}$ is the largest number of parent variables of the continuous variable's children.
 The MDL method iterates over all continuous variables until convergence in the case of multiple continuous variables, converging in a few cycles according to our tests of real-world data.
 Unfortunately, MDL tends to produce discrete variables with low cardinality.
+\tim{Note: use $\text{thing}$ for subscripts such as $n_\text{max}$.}
 
-In this paper, we propose a new Bayesian discretization method for continuous variables in Bayesian networks.
+\tim{Motivate / introduce Bayesian discretization methods perhaps? This would be a good place to cite Boulle and Lustgarten}
+
+\tim{
+The commented material below is good, but feels like too much detail for the intro. Is it possible to move it to later sections?
+I recommend having one paragraph that starts with `In this paper we propose \ldots' and then lists the specific contributions.
+(Bayesian discretization for arbitrary networks, a faster algorithm, demonstrate that performance is preserved, etc.).
+Then we should have the final paragraph below that discusses organization.}
+
+% In this paper, we propose a new Bayesian discretization method for continuous variables in Bayesian networks.
 This method extends the Bayesian single-variable discretization methods from \citet{Boulle_2006} and \citet{Lustgarten_2011}.
-
-% We begin our method with the assumption that only one variable in a given Bayesian network is continuous and other variables are discrete.
+We begin our method with the assumption that only one variable in a given Bayesian network is continuous and other variables are discrete.
 Furthermore we assume that the network structure is known in advance.
@@
 
-The rest of the paper is organized as follows: related works, including MDL principle discretization \citep{Friedman_1996} and MODL discretization by \citet{Boulle_2006}, are summarized in Section 2.
-We prepare the preliminaries and notations in Section 3.
-In Section 4, we introduce the new discretization method for the case that only one variable is continuous, including the derivation of objective function and the algorithms.
-Section 5 is a discussion about multiple continuous variables in a Bayesian network and how to discretize them.
-The combination of our proposed discretization and the K2 structure learning is also introduced.
-Finally, in Section 6, we apply the proposed discretization method to real-world data and show the result.
+\tim{Is the long citation format required?)
+The rest of the paper is organized as follows: related work, including MDL principle discretization \citep{Friedman_1996} and MODL discretization \citet{Boulle_2006} are summarized in \todo{Section 2.
+replace all of these throughout the paper with cref, ex: \cref{relat_work}} Preliminaries and notation are covered in Section 3.
+The proposed single-variable discretization method is derived in Section 4 and is extended to Bayesian networks with multiple continuous variables and combined with Bayesian structure learning in Section 5.
+The paper concludes with the comparison of the proposed methods against prior work on real-world data in Section 6.
 
 \section{Related Work}
-\label{relat_work}
-In this section we review two related works: MDL principle discretization \citep{Friedman_1996} and MODL discretization \citep{Boulle_2006}.
-The former is the most famous discretization method for continuous variables in Bayesian networks, and we will compare it with our proposed method in Section 6.
+\label{relat_work} % NOTE(tim): I recommend doing \label{sec:relat_work} for sections, eq: for equations, fig: for figures, etc.
+\tim{Try to avoid `we'}
+In this section reviews MDL principle discretization \citep{Friedman_1996} and MODL discretization \citep{Boulle_2006}.
+The former is the predominant discretization method for continuous variables in Bayesian networks, and we will compare it with our proposed method in Section 6.
 The latter is a discretization method for one continuous attribute according to a target class.

### 2015-11-11 BN_discretizer_paper.tex
more comments

@@
 \usepackage{tikz}
-\usepackage{cleverref}
+% \usepackage[capitalize]{cleveref}
 \usetikzlibrary{bayesnet}
@@
 
-\tim{Is the long citation format required?)
+\tim{Is the long citation format required?}
 The rest of the paper is organized as follows: related work, including MDL principle discretization \citep{Friedman_1996} and MODL discretization \citet{Boulle_2006} are summarized in \todo{Section 2.
-replace all of these throughout the paper with cref, ex: \cref{relat_work}} Preliminaries and notation are covered in Section 3.
+replace all of these throughout the paper with cref, ex: $cref{relat_work}$} Preliminaries and notation are covered in Section 3.
 The proposed single-variable discretization method is derived in Section 4 and is extended to Bayesian networks with multiple continuous variables and combined with Bayesian structure learning in Section 5.
@@
 \label{relat_work} % NOTE(tim): I recommend doing \label{sec:relat_work} for sections, eq: for equations, fig: for figures, etc.
-\tim{Try to avoid `we'}
-In this section reviews MDL principle discretization \citep{Friedman_1996} and MODL discretization \citep{Boulle_2006}.
-The former is the predominant discretization method for continuous variables in Bayesian networks, and we will compare it with our proposed method in Section 6.
-The latter is a discretization method for one continuous attribute according to a target class.
-Our proposed method is a generalization of this method.
-Note that MODL discretization is a Bayesian approach.
-The asymptotical equivalence between MDL approach and Bayesian approach has been examined in \citep{VL_2000}.
+\tim{Try to avoid we}
+This section reviews MDL principle discretization \citep{Friedman_1996} and MODL discretization \citep{Boulle_2006}.
+The former is the predominant discretization method for continuous variables in Bayesian networks, and we will compare it to our proposed method in Section 6.
+The latter is a discretization method for one continuous variable against a discrete target class.
+Our proposed method generalizes the MODL Bayesian discretization approach to Bayesian networks.
+The asymptotical equivalence between the MDL and MODL methods were examined in \citep{VL_2000}.
+
 \subsection{MDL Principle Discretization}
 \label{MDL}
-The MDL principle was first proposed by \cite{MDL_1978}.
-It provides a way to compress data, that is to say, describe data with fewer number of symbols than the number of symbols needed to describe the data literally \citep{Grunwald_2009}.
-MDL chooses a model that trades off goodness-of-fit for the complexity of model.
-Therefore it has an advantage that automatically avoids overfitting.
-In the case of Bayesian networks, \cite{Friedman_1996} applied the MDL concept to determine the number of intervals of each continuous variable after discretization and also the positions of discretization boundaries.
-Here is the mechanism: MDL principle discretization selects a discretization policy that minimizes sum of description lengths of discretized Bayesian network and the necessary information that recovers original data from discretized data.
-If there is only one continuous variable and other variables are discrete, the objective function is
+The MDL principle was first proposed by \cite{MDL_1978}, and states that the best model for a dataset is one which minimizes the amount of information needed to describe it \citep{Grunwald_2009}.
+MDL methods trade off goodness-of-fit against model complexity to avoid overfitting.
+In the context of Bayesian networks, \cite{Friedman_1996} applied the MDL principle to determine the optimal number of discretization intervals for continuous variables and optimal the positions of their discretization boundaries.
+Their approach selects a discretization policy that minimizes the sum of the description length of discretized Bayesian network and the description length of the information necessary for recovering the original continuous values from the discretized data.
+In the single continuous variable case, the objective function is
+\tim{Do you need double vertical bars? If we use single bars it might fit without having to use the small font size.}
+
+\begin{small}
 \begin{equation}
 \begin{aligned}
-&{1 \over 2} \log(N) \left\lbrace  \lVert \Pi_{X_i} \rVert (\lVert X^*_i \rVert - 1) +
+\frac{1}{2} \log(N) \left\lbrace  \lVert \Pi_{X_i} \rVert (\lVert X^*_i \rVert - 1) +
  {\sum_{j,X_i \in \Pi_{X_i}}} \lVert \Pi_{X^*_j} \rVert (\lVert X_j \rVert - 1) \right\rbrace + \log(\lVert {X^*_i} \rVert) \\
-& + (N_i-1) H \left( {{||X^*_i|| - 1}\over{N_i -1}}  \right) -N \cdot \left[ I(X^*_i,\Pi_{X_i}) + {\sum_{j,X_i \in \Pi_{X_i}}} I(X_j, \Pi_{X^*_j}) \right],
+ + (N_i-1) H \left( {{||X^*_i|| - 1}\over{N_i -1}}  \right) -N \cdot \left[ I(X^*_i,\Pi_{X_i}) + {\sum_{j,X_i \in \Pi_{X_i}}} I(X_j, \Pi_{X^*_j}) \right],
 \end{aligned}
 \end{equation}
-where function $I(\boldsymbol{A},\boldsymbol{B}) = \sum_{\boldsymbol{a},\boldsymbol{b}} \hat{P}_D (\boldsymbol{a},\boldsymbol{b}) \log {{\hat{P}_D (\boldsymbol{a},\boldsymbol{b})}\over{\hat{P}_D (\boldsymbol{a}),\hat{P}_D (\boldsymbol{b})}}$ is the mutual information between two sets of variables $\boldsymbol{A}$ and $\boldsymbol{B}$, $||\boldsymbol{X}||$ means the cardinality of a variable set $\boldsymbol{X}$, $X^*_i$ is the discretized version of continuous variable $X_i$ and $H(p) = -p \log(p) - (1-p) \log(1-p)$.
+\end{small}
+
+\noindent
+where $I(\boldsymbol{A},\boldsymbol{B}) = \sum_{\boldsymbol{a},\boldsymbol{b}} \hat{P}_D (\boldsymbol{a},\boldsymbol{b}) \log {{\hat{P}_D (\boldsymbol{a},\boldsymbol{b})}\over{\hat{P}_D (\boldsymbol{a}),\hat{P}_D (\boldsymbol{b})}}$ \tim{consider deleting the right half of equation} is the mutual information between two discrete variables $\boldsymbol{A}$ and $\boldsymbol{B}$, $||\boldsymbol{X}||$ is the cardinality of discrete variable $\boldsymbol{X}$, $X^*_i$ is the discretized version of continuous variable $X_i$ and $H(p) = -p \log(p) - (1-p) \log(1-p)$.
 The optimal discretization policy can be found by dynamical programming.

### 2015-11-12 BN_discretizer_paper.tex
made it through section 3

@@
 \usepackage[round]{natbib}
+\usepackage{amsfonts} % for mathbb
 \usepackage{tikz}
@@
 \newcommand{\paren}[1]{\mathopen{}\mathclose\bgroup\left(#1\aftergroup\egroup\right)}
-\newcommand{\brock}[1]{\mathopen{}\mathclose\bgroup\left[#1\aftergroup\egroup\right\right]}
-\newcommand{\curly}[1]{\mathopen{}\mathclose\bgroup\left\{#1\aftergroup\egroup\right\right\}}
+\newcommand{\brock}[1]{\mathopen{}\mathclose\bgroup\left[#1\aftergroup\egroup\right]}
+\newcommand{\curly}[1]{\mathopen{}\mathclose\bgroup\left\{#1\aftergroup\egroup\right\}}
 \newcommand{\anglebrackets}[1]{\langle #1 \rangle}
@@
 
-\author{First Author         \and
-        Second Author         \and
-        Third Author%etc.
+\author{Yi-Chun Chen           \and
+        Tim A. Wheeler         \and
+        Mykel J. Kochenderfer
 }
@@
 \end{abstract}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-\tim{Is the long citation format required?}
-The rest of the paper is organized as follows: related work, including MDL principle discretization \citep{Friedman_1996} and MODL discretization \citet{Boulle_2006} are summarized in \todo{Section 2.
-replace all of these throughout the paper with cref, ex: $cref{relat_work}$} Preliminaries and notation are covered in Section 3.
-The proposed single-variable discretization method is derived in Section 4 and is extended to Bayesian networks with multiple continuous variables and combined with Bayesian structure learning in Section 5.
-The paper concludes with the comparison of the proposed methods against prior work on real-world data in Section 6.
+The rest of the paper is organized as follows: related work, including MDL principle discretization \citep{Friedman_1996} and MODL discretization \citet{Boulle_2006} are summarized in Section \ref{sec:related_work}.
+Preliminaries and notation are covered in Section \ref{sec:preliminaries}.
+The proposed single-variable discretization method is derived in Section \ref{sec:single_var} and is extended to Bayesian networks with multiple continuous variables and combined with Bayesian structure learning in Section \ref{sec:multi_var}.
+The paper concludes with the comparison of the proposed methods against prior work on real-world data in Section \ref{sec:experiments}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
 \section{Related Work}
-\label{relat_work} % NOTE(tim): I recommend doing \label{sec:relat_work} for sections, eq: for equations, fig: for figures, etc.
-\tim{Try to avoid we}
+\label{sec:related_work}
 This section reviews MDL principle discretization \citep{Friedman_1996} and MODL discretization \citep{Boulle_2006}.
-The former is the predominant discretization method for continuous variables in Bayesian networks, and we will compare it to our proposed method in Section 6.
+The former is the predominant discretization method for continuous variables in Bayesian networks, and is compared to our proposed method in Section \ref{sec:experiments}.
 The latter is a discretization method for one continuous variable against a discrete target class.
@@
 \subsection{MDL Principle Discretization}
-\label{MDL}
 The MDL principle was first proposed by \cite{MDL_1978}, and states that the best model for a dataset is one which minimizes the amount of information needed to describe it \citep{Grunwald_2009}.
@@
  {\sum_{j,X_i \in \Pi_{X_i}}} \lVert \Pi_{X^*_j} \rVert (\lVert X_j \rVert - 1) \right\rbrace + \log(\lVert {X^*_i} \rVert) \\
- + (N_i-1) H \left( {{||X^*_i|| - 1}\over{N_i -1}}  \right) -N \cdot \left[ I(X^*_i,\Pi_{X_i}) + {\sum_{j,X_i \in \Pi_{X_i}}} I(X_j, \Pi_{X^*_j}) \right],
+ + (N_i-1) H \left( {{\|X^*_i\| - 1}\over{N_i -1}}  \right) -N \cdot \left[ I(X^*_i,\Pi_{X_i}) + {\sum_{j,X_i \in \Pi_{X_i}}} I(X_j, \Pi_{X^*_j}) \right],
 \end{aligned}
@@
 \noindent
-where $I(\boldsymbol{A},\boldsymbol{B}) = \sum_{\boldsymbol{a},\boldsymbol{b}} \hat{P}_D (\boldsymbol{a},\boldsymbol{b}) \log {{\hat{P}_D (\boldsymbol{a},\boldsymbol{b})}\over{\hat{P}_D (\boldsymbol{a}),\hat{P}_D (\boldsymbol{b})}}$ \tim{consider deleting the right half of equation} is the mutual information between two discrete variables $\boldsymbol{A}$ and $\boldsymbol{B}$, $||\boldsymbol{X}||$ is the cardinality of discrete variable $\boldsymbol{X}$, $X^*_i$ is the discretized version of continuous variable $X_i$ and $H(p) = -p \log(p) - (1-p) \log(1-p)$.
-The optimal discretization policy can be found by dynamical programming.
-If there are multiple continuous variables in a Bayesian network, we apply the algorithm on one variable at a time and iterate over all continuous variables.
-While iterating, only one variable is treated as continuous and other continuous variables are discretized based on initial prediscretization or the discretization result of previous iteration.
+where $I(\boldsymbol{A},\boldsymbol{B}) = \sum_{\boldsymbol{a},\boldsymbol{b}} \hat{P}_D (\boldsymbol{a},\boldsymbol{b}) \log {{\hat{P}_D (\boldsymbol{a},\boldsymbol{b})}\over{\hat{P}_D (\boldsymbol{a}),\hat{P}_D (\boldsymbol{b})}}$ \tim{consider deleting the right half of equation} is the mutual information between two discrete variables $\boldsymbol{A}$ and $\boldsymbol{B}$, $\|\boldsymbol{X}\|$ is the cardinality of discrete variable $\boldsymbol{X}$, $X^*_i$ is the discretized version of continuous variable $X_i$ and $H(p) = -p \log(p) - (1-p) \log(1-p)$.
+The optimal discretization policy is found with dynamical programming.
+If there are multiple continuous variables in a Bayesian network, we apply the algorithm to one variable at a time and iterate over all continuous variables.
+While iterating, only one variable is treated as continuous and other continuous variables are discretized based on an initial discretization scheme or the discretization result from a previous iteration.
 
-For the above discretization processes, the network structure is known in advance.
-If the network structure is not given, we can alternate between structure learning and discretization learning.
-We start with some discretization, and learn a network structure given this discretization.
-Then, we rediscretize based on the learned network.
-This cycle continues until no improvement in objective function is made.
+The network structure is not always known in advance.
+Bayesian network structure learning can be extended to distributions including continuous variables by alternating between traditional discrete structure learning and optimal discretization.
+Starting with some preliminary discretization scheme, one applys a structure learning algorithm to identify the locally optimal graph structure.
+The discretization scheme is refined based on the learned network.
+The cycle is continued until convergence.
+
 \subsection{MODL Discretization}
-\label{MODL}
-MODL discretization \citep{Boulle_2006} is a Bayesian-approach discretization.
-It discretizes a continuous feature according to a class variable.
-The best discretization model is found by maximizing the probability $P(\textit{Model} \mid \textit{Data})$ of the model given the data.
-Using Bayes' rule and since $P(\textit{Data})$ is a constant while varying the discretization model, this is equivalent to maximize:
+\tim{Does MODL stand for something?}
+MODL discretization \citep{Boulle_2006} is a Bayesian method for discretizing a continuous feature according to a class variable.
+Bayesian methods maximize the probability of the model given the data, $P(\textit{Model} \mid \textit{Data})$.
+An application of Bayes' rule and constant $P(\textit{Data})$ shows that this is equivalent to maximizing:
 \begin{align}
-P(\textit{Model}) \cdot P(\textit{Data} \mid \textit{Model}).
+P(\textit{Model}) \cdot P(\textit{Data} \mid \textit{Model})\text{,}
 \end{align}
-Once the prior distribution of the discretization model is fixed, each term in Eq (3) can be evaluated.
-Usually, $P(\textit{Data} \mid \textit{Model})$ increases as the number of intervals of discretization model increases, since more intervals means that the model contains more information and thus it is easier to reproduce the original data.
-On the other hand, $P(\textit{Model})$ decreases as the number of intervals increases.
-Thus, maximizing $P(\textit{Model}) \cdot P(\textit{Data} \mid \textit{Model})$ provides a trade-off to determine number of intervals after discretization.
 
-The MODL method adapts dynamical programming to find the optimal discretization model, and it takes running time $O(N^3 + ||\text{Class}|| \cdot N^2)$, where $N$ is number of data instances.
-\cite{Lustgarten_2011} provide a different prior to evaluate $P(\text{Model})$ term.
-This prior could include the assumption of uniform prior probabilities over discretization in MODL as a special case.
-Additionally, it reduces runing time to $O(||\text{Class}|| \cdot N^2)$.
+\noindent
+where $P(\textit{Model})$ is a prior over models and $P(\textit{Data} \mid \textit{Model})$ is the data likelihood.
+The data likelihood usually increases with the number of discretization intervals, as more intervals allow for more detailed representations.
+The prior usually decreases as the number of discretization intervals increases to favor simpler models and penalize overfitting.
+Thus, maximizing $P(\textit{Model}) \cdot P(\textit{Data} \mid \textit{Model})$ requires a trade-off when determining the number of discretization intervals.
+
+The MODL method uses dynamic programming to find the optimal discretization scheme, and has a $\bigo\paren{N^3 + \|\text{Class}\| \cdot N^2}$ runtime, where $N$ is the of number of data instances.
+\cite{Lustgarten_2011} suggest several formulations for the prior term $P(\text{Model})$\tim{Did I state this correctly?}.
+If the prior is chosen to reflect uniform prior probability over discretizations the runtime can be reduced to $\bigo\paren{\|\text{Class}\| \cdot N^2}$.\tim{Is a sacrifice made?
+It is sub-optimal, right?}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
 \section{Preliminaries}
-\label{Prelim_Notation}
-In this section we provide a brief review of Bayesian networks, including the factorization of joint probability distribution, sampling from a given network, and structure learning.
+\label{sec:preliminaries}
+This section provides a brief overview of Bayesian networks, including the factorization of joint probability distributions, sampling from a Bayesian network, and structure learning.
 These concepts will be used in later sections.
-In addition, the formal definition of a discretization policy on a continuous variable is also introduced.
+The formal definition of a discretization policy for a continuous variable is also given.
 
-\subsection{Bayesian Network and Structure Learning}
-\label{BN_basic}
-A Bayesian network $B$ is defined by a pair $(G,\Theta)$, where $G = (X,E)$ is a directed acyclic graph whose nodes correspond to a set of random variable $X = \{  X_1, X_2, \cdots, X_n \}$, and whose edges $E$ represents probabilistic dependencies among nodes.
-The graph structure $G$ encodes the Markov property: each node $X_i$ is independent of its non-descendants given its parents in $G$.
-The second component of $B$, namely $\Theta$, contains a set of parameters that qualify the network.
-Elements of $\Theta$ take the form $\theta_{x_i \mid \Pi_{x_i}} = P(x_i \mid \Pi_{x_i})$ for each possible value $x_i$ of $X_i$, and $\Pi_{x_i}$ of $\Pi_{X_i}$ (the set of parents of $X_i$ in $G$).
-Applying Markov property, we can represent the multivariate joint distribution over $X$ as
+\subsection{Bayesian Networks and Structure Learning}
+
+A Bayesian network $B$ is defined by a pair $(G,\Theta)$, where $G = (X,E)$ is a directed acyclic graph whose nodes correspond to a set of random variables $X = \brock{X_1, X_2, \cdots, X_n}$, and whose edges $E$ represent probabilistic dependencies among nodes.
+The graph structure $G$ encodes the Markov property: each node $X_i$ is independent of its non-descendants given its parents $\Pi{X_i}$ in $G$.
+The conditional relations are parameterized by the elements of $\Theta$, which take the form $\theta_{x_i \mid \Pi_{x_i}} = P(x_i \mid \Pi_{x_i})$ for each possible value $x_i$ of $X_i$, and $\Pi_{x_i}$ of $\Pi_{X_i}$.
+The joint distribution over $X$ factors according to the Markov property:
 \begin{equation}
-P_B (X_1 , \cdots, X_n) = \prod_{i=1}^{n} P_B (X_i \mid \Pi_{X_i}) = \prod_{i=1}^{n} \theta_{x_i \mid \Pi_{x_i}}
+P_B (X_1 , \cdots, X_n) = \prod_{i=1}^{n} P_B (X_i \mid \Pi_{X_i}) = \prod_{i=1}^{n} \theta_{x_i \mid \Pi_{x_i}}\text{.}
 \end{equation}
 
-For a given Bayesian network, we can generate its data instances by forward sampling, i.e., sampling variables one by one in a topological order \citep[see][chap.~22]{algo_2009}.
-Given an instance of $X_i$'s parent set, $\Pi_{X_i}$, values of $X_i$ can be sampled according to the conditional probability table $P(X_i \mid \Pi_{X_i})$.
-Furthermore, this parent-child sampling order can be reversed if we know the marginal probability of child variable $P(X_i)$.
+Samples can be drawn from the joint distribution represented by a Bayesian network by forward sampling.
+Variables are sampled in topological order such that parental instantiations are always known~\citep[see][chap.~22]{algo_2009}.
+Furthermore, the parent\rightarrow child sampling order can be reversed if the marginal probability of child variable $P(X_i)$ is known.\tim{Do we use this later?}
 By Bayes' rule,
+
 \begin{equation}
@@
 \end{equation}
-where $Pa( X_i)$ is the number of parents of $X_i$, and $\{ \Pi_{X_i} \}_j$ is the $j$th parent of $X_i$.
-We can first sample $X_i$ by $P(X_i)$, then sample all the parent variables simultaneously by $P(\Pi_{X_i} \mid X_i)$.
-That is to say, $X_i$ becomes the starting point of sampling.
 
-If we don't know the structure of the Bayesian network in advance, then we need to learn it from data.
-Roughly speaking, there are three approaches to learn a Bayesian network structure from data \citep[see][chap.~18]{PGM_2009}: constraint-based structure learning, score-based structure learning, and Bayesian model averaging.
-Here we review the K2 structure learning algorithm \citep{K2}, which is one of the most successful score-based structure learning methods.
-Similar to most structure learning algorithms, the K2 algorithm requires all variables to be discrete.
-The score of a learned network is defined as $\prod_i f(X_i, \Pi_{X_i})$, where
+\noindent
+where $Pa(X_i)$ is the number of parents of $X_i$ and $\brock{\Pi_{X_i}}_j$ is the $j$th parent of $X_i$.
+% One can first sample $X_i$ by $P(X_i)$, then sample all the parent variables simultaneously by $P(\Pi_{X_i} \mid X_i)$. That is to say, $X_i$ becomes the starting point of sampling.
+
+It is often necessary to infer the structure of a Bayesian network from data.
+Three common approaches to Bayesian network structure learning are constraint-based structure learning, score-based structure learning, and Bayesian model averaging \citep[see][chap.~18]{PGM_2009}.
+This work uses the K2 structure learning algorithm \citep{K2}, one of the most successful score-based structure learning methods.
+Score-based structure learning methods over discrete variables commonly evaluate candidate structures are scored according to their likelihood, $\prod_i f(X_i, \Pi_{X_i})$, where
+
 \begin{align}
-f(X_i, \Pi_{X_i}) = \prod_{j=1}^{||\Pi_{X_i}||} {{(||X_i||-1)!}\over{(N_{ij} + ||X_i||-1)!}} \prod_{k=1}^{||X_i||} \alpha_{ijk}!.
+f(X_i, \Pi_{X_i}) = \prod_{j=1}^{\|\Pi_{X_i}\|} {{(\|X_i\|-1)!}\over{(N_{ij} + \|X_i\|-1)!}} \prod_{k=1}^{\|X_i\|} \alpha_{ijk}!\text{.}
 \end{align}
-$||X_i||$ is the cardinality of variable $X_i$.
-$||\Pi_{X_i}||$ is number of all possible instantiations of the parent variables of $X_i$, i.e., $|\Pi_{X_i}| = \prod_{Y \in \Pi_{X_i}} |Y|$.
-$\alpha_{ijk}$ is the number of instances in a data set that variable $X_i$ is instantiated with its $k$th value, and the parent of $X_i$ are instantiated with the $j$th value of $\Pi_{X_i}$.
-$N_{ij} = \sum_{k=1}^{|X_i|} \alpha_{ijk}$.
 
-The K2 algorithm searches the network structure with the highest score, which can be interpreted as the most probable network with the given data.
-In addition, the K2 requires a topological order of variables to be known before the scoring can start.
-This constraint can prevent cycles from being introduced.
-The searching for high-score network is an iterative process.
-There is no way to find the optimal network directly, since there are $2^{O(n^2)}$ possible structures, where $n$ is number of variables.
-In order to compensate for this, we run the K2 algorithm many times, and each time we start with a different order of variables.
-The network with the highest score in iterations is the desired one.
+\noindent
+$\|X_i\|$ is the cardinality of $X_i$, $\|\Pi_{X_i}\|$ is number of possible instantiations of the parent variables of $X_i$, $\alpha_{ijk}$ is the number of instances of the $k$th value of $X_i$ and the $j$th parental instantiation, and $N_{ij} = \sum_{k=1}^{|X_i|} \alpha_{ijk}$.\tim{Mykel uses $\alpha_{ij0}$}
+The optimal structure is the most probably structure given the data.
+The space of acyclic graphcs is superexponential in the number of nodes \citep{PGM_2009} so it is common to rely on heuristic search strategies.
 
-\subsection{Discretization Policy}
-\label{Disc_p}
-A Discretization Policy $M_C = < t_1,t_2, \ldots, t_{k-1} >$ on a continuous variable $C$ is a mapping from $\boldsymbol{R}$ to $\{1,2,3,\ldots,k \}$ such that
+The K2 algorithm assumes a topological ordering of variables and greedily adds parents to nodes to maximally increase the likelihood score.
+A fixed ordering ensures acyclicity but does not guarantee a globally optimal network structure.
+K2 is typically run multiple times with random topological orderings and the network with the highest likelihood is retained.
+
+\subsection{Discretization Policies}
+
+A discretization policy $M_C = \anglebrackets{t_1 < t_2 < \ldots < t_{k-1}}$ for a continuous variable $C$ is a mapping from $\mathbb{R}$ to $\brock{1,2,3,\ldots,k}$ such that
 \begin{equation}
@@
     1, & \text{if $x<t_1$}.\\
-    i, & \text{if $t_{i-1} \leq x < t_i$}.\\
-    k, & \text{if $t_k \leq x$}
+    i, & \text{if $t_{i-1} \leq x < t_i$}\text{.}\\
+    k, & \text{if $t_{k-1} \leq x$}
   \end{cases}
 \end{equation}
-That is to say, the policy discretizes the continuous variable $C$ into $k$ intervals.
-Furthermore, we assume that the discretization edge $t_i$ can only take values on middle points of two consective values of data of $C$.
-By this assumption, we can obtain an integer representation of $M_C$ as follows:
-we sort the data of continuous variable $C$ in an increasing order, $\{ c_1,c_2,\ldots,c_N \}$, and if $t_i = (c_{s_{i}} + c_{s_{i}+1})/2$ for $i=1,2,\ldots,k$, then $M_C = < t_1,t_2, \ldots, t_{k-1} > \equiv [n_1,n_2,..n_k]$, where $n_1 = s_1$ and $n_i = s_{i} - s_{i-1}$ for $i = 2,\ldots,k$.\\
 
-\section{Discretize One Continuous Variable}
-\label{one-conti}
+\noindent
+The policy discretizes the continuous variable $C$ into $k$ intervals.
+Furthermore, we restrict the discretization edges $t_\cdot$ to midpoints between two sorted instances of $C$.
+An integer representation of $M_C$ can be obtained by sorting the samples of $C$ in an increasing order, $\curly{c_1,c_2,\ldots,c_N}$, and if $t_i = (c_{s_{i}} + c_{s_{i}+1})/2$ for $i=1,2,\ldots,k$, then $M_C = \anglebrackets{t_1,t_2, \ldots, t_{k-1}} \equiv \brock{n_1,n_2,..n_k}$, where $n_1 = s_1$ and $n_i = s_{i} - s_{i-1}$ for all $i = 2,\ldots,k$.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Discretization of a Single Continuous Variable}
+\label{sec:single_var}
+
 In this section, we consider the case that only one variable in a Bayesian network is continuous and the others are discrete.
@@
 \subsubsection{Evaluate $P(D_{\Pi_x} \mid M)$}
-Assume that $J_P = \prod_{i=1}^{n_p} || P_i ||$. Then we have:
+Assume that $J_P = \prod_{i=1}^{n_p} \| P_i \|$. Then we have:
 \begin{equation}
@@
 where $n^{(p)}_{i,j}$ is the number of instances in $i$th discretized interval with $j$th value of $\Pi_X$.
-Note that $n_i = \sum_{j=1}^{|| \Pi_x ||} n^{(p)}_{i,j}$.
+Note that $n_i = \sum_{j=1}^{\| \Pi_x \|} n^{(p)}_{i,j}$.
 The two factors on RHS comes from the second prior: all distributions of values of $\Pi_X$ in a given interval are equiprobable.
@@
 \subsubsection{Evaluate $P(D_{C_i} \mid M, D_{\boldsymbol{S_i}})$}
-Assume for each pair of $(C_j, \boldsymbol{S_j})$, we have $||C_j || = J_j$ and $|| \boldsymbol{S_j} || = L_j = \prod_{v \in \boldsymbol{S_j}} || v ||$. Therefore,
+Assume for each pair of $(C_j, \boldsymbol{S_j})$, we have $\|C_j \| = J_j$ and $\| \boldsymbol{S_j} \| = L_j = \prod_{v \in \boldsymbol{S_j}} \| v \|$. Therefore,
 \begin{equation}
@@
 \end{equation}
-where $J_{p_r} = || P_r||$ and ${n^{(p_r)}_{i,j} !}$ is the number of instances in $i$th interval with $j$th value of $P_r$. Applying this approximation, the approximated objective function is
+where $J_{p_r} = \| P_r\|$ and ${n^{(p_r)}_{i,j} !}$ is the number of instances in $i$th interval with $j$th value of $P_r$. Applying this approximation, the approximated objective function is
 \begin{equation}
@@
 
-As we will see in Section 6, the approximated algorithm is more sensitive to the distribution of other variables' values and usually leads to slightly more discretization edges.
+As we will see in Section \ref{sec:experiments}, the approximated algorithm is more sensitive to the distribution of other variables' values and usually leads to slightly more discretization edges.
 With the approximation, we can reduce runtime of Algorithm 1 from $O(n_c  {v'_{max}} \cdot N^2 + {v'_{max}}^{n_p} \cdot N^2)$ to $O( {v'_{max}} (n_c + n_p) \cdot N^2)$.
@@
 
-\section{Discretizing Multiple Continuous Variable with Structure Learning}
-\label{DMC_SL}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Extension to Multiple Continuous Variables}
+\label{sec:multi_var}
+
 \subsection{Discretization of Multiple Continuous Variables}
-\label{DMC}
+
 If there are multiple continuous variables in a Bayesian network, we iterate the one-variable discretization method discussed above for all continuous variables.
@@
 \State $D^* \leftarrow $ the discretized data for all variables, where $D^*_i \leftarrow D''_i$ if $i \notin C$
-\State $k \leftarrow median\{ ||v||, v\notin C\}$
+\State $k \leftarrow median\{ \|v\|, v\notin C\}$
 \State
@@
 \State {$cycle  \leftarrow cycle  + 1$}
-\For {$j = 1$ to $||C||$}
+\For {$j = 1$ to $\|C\|$}
 \State $D^*_{\backslash C(j)} \leftarrow D^*$ without $D^*_{C(j)}$.
@@
 \subsection{Discretization of Continuous Variables While Structure Learning}
-\label{SL}
+
 In many situations the network structure is not known in advance, then we need to learn it from data.
@@
 \State $n \leftarrow$ the number of variables in Bayesian network
-\State $k \leftarrow median\{ ||v||, v\notin C\}$
+\State $k \leftarrow median\{ \|v\|, v\notin C\}$
 \State $M[i] \leftarrow$ the discretization policy of $i$th variable
@@
 \State OKToProceed $\leftarrow$ \textbf{true}
-\While OKToProceed \textbf{and} $||\Pi_{X^*_i}|| < u_{parent}$
+\While OKToProceed \textbf{and} $\|\Pi_{X^*_i}\| < u_{parent}$
 \State $Y \leftarrow$ an element from the set $order[1:i] \backslash \Pi_X$
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Experiments}
+\label{sec:experiments}
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section*{Appendices}
@@
 \State Initialize $H$ as an $N \times N$ matrix that all elements are 0.
-\State $count_p$ is an $N \times N \times ||\Pi_X||$ matrix such that $count_p [u,v,w]$ is the number of instances from $x_u$ to $x_v$ with $w$th value of $\Pi_X$.
-This matrix can be calculated in $O(||\Pi_X|| \cdot N^2)$
+\State $count_p$ is an $N \times N \times \|\Pi_X\|$ matrix such that $count_p [u,v,w]$ is the number of instances from $x_u$ to $x_v$ with $w$th value of $\Pi_X$.
+This matrix can be calculated in $O(\|\Pi_X\| \cdot N^2)$
 \For {$u = 1$ to $N$}
@@
 \State $H(u,v) \leftarrow H(u,v) + \log((v-u + J_p)!) - \log((J_p -1)!)$
-\For {$w = 1$ to $||\Pi_X||$}
+\For {$w = 1$ to $\|\Pi_X\|$}
 \State $H(u,v) \leftarrow H(u,v) - \log( count_p(u,v,w)!)$

### 2015-11-12 BN_discretizer_paper.tex
misc

@@
 
-In this section, we consider the case that only one variable in a Bayesian network is continuous and the others are discrete.
+This section covers discretization of a single continuous variable in a Bayesian network where all other variables are discrete.
 Before we formulate the objective function, we introduce some notations that will make the following calculation easier.
+
 \subsection{Notations}
-\label{Notation}
-Assume the continuous variable is $X$.
-It has $n_p$ parent variables, $\Pi_X = \{ P_1, P_2, P_3,\ldots,P_{n_p}\}$.
-It also has $n_c$ child variables $\{ C_1, C_2,\ldots,C_{n_c}\}$.
-Each child variable $C_i$ of $X$ has other parent variables, which forms a set $\boldsymbol{S_i}$.
-Before we do the discretization, we sort the data instances by its attribute of $X$.
 
-Let $D \cup D_X$ be a dataset of $N$ instances which we plan to learn discretization from.
-$D_X$ only contains the data of $X$.
-$D$ contains the data of all variables except $X$.
-Assume $D \cup D_X$ has been sorted in the ascending order of $D_X$.
-In the following content, $D_{\boldsymbol{Y}}$ means the data instances of a set of variable $\boldsymbol{Y}$.
-Let $D_X = \{ x_1,x_2,x_3,\ldots,x_N \}$.
-In order to make the discretization mechanism more understandable, we temporarily assume there is no repeated values in $D_X$, i.e., $x_1 < x_2 < \ldots < x_N$.
-We will remove this assumption later in the algorithm section.
-Therefore, a discretization policy $M$ on $X$ can be written as $M = [n_1,n_2,\ldots,n_k]$, where $k$, $n_1$, $n_2$, $\ldots,n_k$ are positive integers satisfying $N = \sum_{i=1}^k n_i$.
+\tim{We should move the notation section to preliminaries}
+
+\tim{Earlier the continuous variable was denoted $C$. Now it is $X$. Slightly confusing with $c$ also meaning child.}
+
+Consider continuous variable $X$.
+It has $n_p$ parents, $\Pi_X = \{ P_1, P_2, P_3,\ldots,P_{n_p}\}$ and $n_c$ children, $\{ C_1, C_2,\ldots,C_{n_c}\}$.
+Each child $C_i$ of $X$ may possess other parents, our spouses of $X$, whose set is denoted $\boldsymbol{S_i}$.
+
+Let $D$ be a dataset of $N$ joint instances from which discretization will be learned, sorted in ascending order according to $X$.
+Let $D_{\boldsymbol{Y}}$ will refer to the data instances associated with variables $\boldsymbol{Y}$.
+Thus $D_X = \{ x_1,x_2,x_3,\ldots,x_N \}$.
+In order to facilitate understanding, we temporarily assume all values in $D_X$ are unique, that is, $x_1 < x_2 < \ldots < x_N$.
+It follows that a discretization policy $M$ on $X$ can be written as $M_X = \brock{n_1,n_2,\ldots,n_k}$, where $k$, $n_1$, $n_2$, $\ldots,n_k$ are positive integers satisfying $N = \sum_{i=1}^k n_i$.
+The optimal discretization policy maximizes $P(M)\cdot P(D\mid M)$.
 
@@
 \subsection{Priors and Objective Function}
-\label{obj}
+
 We have the following four priors for the discretization model $M$ that enable us to evaluate $P(M)$ and $P(D \mid M)$:\\

### 2015-11-12 BN_discretizer_paper.tex
more

@@
 Variables are sampled in topological order such that parental instantiations are always known~\citep[see][chap.~22]{algo_2009}.
-Furthermore, the parent\rightarrow child sampling order can be reversed if the marginal probability of child variable $P(X_i)$ is known.\tim{Do we use this later?}
+Furthermore, the parent\rightarrow child sampling order can be reversed if the marginal probability of child variable $P(X_i)$ is known.
 By Bayes' rule,
@@
 
-We have the following four priors for the discretization model $M$ that enable us to evaluate $P(M)$ and $P(D \mid M)$:\\
+Four prior principles adapted from the MODL approach define $P(M)$ and $P(D \mid M)$:
 \begin{enumerate}
-\item For a discretization edge locating at $(x_i + x_{i+1})/2$ has probability
+\item A discretization edge at $(x_i + x_{i+1})/2$ has probability
 \begin{equation}
@@
 \end{equation}
-where $L$ is the largest cardinality number of discrete variables in $X$'s Markov blanket.
+where $L$ is the largest cardinality of discrete variables in $X$'s Markov blanket.
 \item For a given interval of $M$, every distribution of $\Pi_X$ is equiprobable.
-\item For each pair of $(C_i,\boldsymbol{S_i})$ and a given interval of $M$, every distribution of $C_i$ with a value of $\boldsymbol{S_i}$ is equiprobable.
-\item The distributions of each $C_i$ and $\Pi_X$ in each interval of $M$ with each value of $\boldsymbol{S_i}$ are independent from each other.
+\item For each pair $(C_i,\boldsymbol{S_i})$ and a given interval of $M$, every distribution over $C_i$ given $\boldsymbol{S_i}$ is equiprobable.
+\item The distributions over each $C_i$ and $\Pi_X$ in each interval of $M$ given each instantiation of $\boldsymbol{S_i}$ are independent.
 \end{enumerate}
 
-Owing to these priors, we are able to evaluate $P(M)$ and $P(D \mid M)$. For the former, we have
+The prior term $P(M)$ has the form:
+
 \begin{equation}
@@
 \end{equation}
-where $s_i = \sum_{j=1}^k n_j$ and $s_k = N$, $s_0 = 0$. Before evaluating $P(D \mid M)$, notice that
+where $s_i = \sum_{j=1}^k n_j$, $s_k = N$, and $s_0 = 0$. Before evaluating $P(D \mid M)$, note that
 \begin{equation}
-P(D \mid M) \propto P(D_{\Pi_x} \mid M) \cdot \prod_{i = 1}^{n_c} P(D_{C_i} \mid M, D_{\boldsymbol{S_i}}).
+P(D \mid M) \propto P(D_{\Pi_x} \mid M) \cdot \prod_{i = 1}^{n_c} P(D_{C_i} \mid M, D_{\boldsymbol{S_i}})\text{.}
 \end{equation}
-The graph structure allows us to only consider the interations between $X$ and other variables in its Markov blanket and thus leads to the factorization.
-For example, in Figure 1., the corresponding $P(D \mid M)$ is factorized as
+The graph structure allows us to only consider the interations between $X$ and the other variables in its Markov blanket, thus allowing for convenient factorization.
+For example, $P(D \mid M)$ for Figure \ref{fig:one} factors according to
 \begin{equation}
-P(D_{ P_1,P_2,P_3 } \mid M) \cdot P( D_{ C_1 } \mid M,D_{\boldsymbol{S_1}}) \cdot P(D_{C_2} \mid M,D_{ S_2  }).
+P(D_{ P_1,P_2,P_3 } \mid M) \cdot P( D_{ C_1 } \mid M,D_{\boldsymbol{S_1}}) \cdot P(D_{C_2} \mid M,D_{ S_2  })\text{.}
 \end{equation}
@@
   \caption{Factorization of $P(D \mid M)$}
+  \label{fig:one}
 \end{figure}
 
-The concept behind the factorization is similar to sampling in a Bayesian network.
-Once we have the distribution of $X$ and sample $X$ for it, then we can further sample $\Pi_x$.
-Since the samples of $P_1,P_2,\ldots,P_{n_p}$ given a value of $X$ are not independent, we can not further factorize $P(D_{\Pi_x} \mid M)$ into $\prod_i P(D_{P_i} \mid M)$.
-Similarly, once we have samples of $X$ and $\boldsymbol{S_i}$, we can sample $C_i$.
-Since the sampling processes of child variables are independent from each other, we have the product $\prod_{i = 1}^{n_c} P(D_{C_i} \mid M, D_{\boldsymbol{S_i}})$.\\
+The factorization arises from the conditional independencies in the Bayesian network.
+Given a distribution over $X$ and a specific instance $x$, one can directly determine the conditional distribution over the parents $\Pi_x$.
+The parents given $x$ are dependent, in general one cannot further factorize $P(D_{\Pi_x} \mid M)$.
+Similarly, a distribution over $C_i$ is fully defined given $x$ and $\boldsymbol{S_i}$.
+The children are independent given $X$, and thus factorize according to $\prod_{i = 1}^{n_c} P(D_{C_i} \mid M, D_{\boldsymbol{S_i}})$.
 
-For the following part, we evaluate $P(D_{\Pi_x} \mid M)$  and $P(D_{C_i} \mid M, D_{\boldsymbol{S_i}})$ based on discretization policy $M = [n_1,n_2,\ldots,n_k]$ and dataset $D$.
-\subsubsection{Evaluate $P(D_{\Pi_x} \mid M)$}
-Assume that $J_P = \prod_{i=1}^{n_p} \| P_i \|$. Then we have:
+It is thus necessary to formulate $P(D_{\Pi_x} \mid M)$  and $P(D_{C_i} \mid M, D_{\boldsymbol{S_i}})$ based on discretization policy $M = [n_1,n_2,\ldots,n_k]$ in order to compute the likelihood term, $P(D \mid M)$.
+These components are outlined below.
+
+\subsubsection{Evaluation of $P(D_{\Pi_x} \mid M)$}
+
+Let $J_P = \prod_{i=1}^{n_p} \| P_i \|$. It follows that
+
 \begin{equation}
 P(D_{\Pi_X} \mid M) = \prod_{i=1}^k  {{1}\over{{n_i + J_P - 1}\choose{J_P -1}}}
-{{1}\over{ {{{n}_i}!}\over{ {n^{(p)}_{i,1} !} {n^{(p)}_{i,2} !} \cdots {n^{(p)}_{i,J_P} !}}  }},
+{{1}\over{ {{{n}_i}!}\over{ {n^{(p)}_{i,1} !} {n^{(p)}_{i,2} !} \cdots {n^{(p)}_{i,J_P} !}}  }}\text{,}
 \end{equation}
-where $n^{(p)}_{i,j}$ is the number of instances in $i$th discretized interval with $j$th value of $\Pi_X$.
+
+\noindent
+where $n^{(p)}_{i,j}$ is the number of instances in the $i$th discretized interval with the $j$th value of $\Pi_X$.
 Note that $n_i = \sum_{j=1}^{\| \Pi_x \|} n^{(p)}_{i,j}$.
-The two factors on RHS comes from the second prior: all distributions of values of $\Pi_X$ in a given interval are equiprobable.
-According to the forth prior, the distribution in each interval is independent, so we multiply all the two factors together.
-\subsubsection{Evaluate $P(D_{C_i} \mid M, D_{\boldsymbol{S_i}})$}
-Assume for each pair of $(C_j, \boldsymbol{S_j})$, we have $\|C_j \| = J_j$ and $\| \boldsymbol{S_j} \| = L_j = \prod_{v \in \boldsymbol{S_j}} \| v \|$. Therefore,
+The two factors on the right hand side comes from the second prior: all distributions of values of $\Pi_X$ in a given interval are equiprobable.
+According to the fourth prior, the distribution in each interval is independent, so the two factors are multiplied together.
+
+\subsubsection{Evaluation of $P(D_{C_i} \mid M, D_{\boldsymbol{S_i}})$}
+
+For each pair $(C_j, \boldsymbol{S_j})$, let $\|C_j \| = J_j$ and $\| \boldsymbol{S_j} \| = L_j = \prod_{v \in \boldsymbol{S_j}} \| v \|$. It follows that
+
 \begin{equation}
+\label{eq:likelihood_two}
 P(D_{C_j}  \mid M, D_{S_j}) =
 \prod_{i=1}^{k} \prod_{l=1}^{L_j} {{1}\over{{n_{i,l} + J_j - 1}\choose{J_j-1}}}
-{{1}\over{ {{n_{i,l}}!}\over{ {n^{(j)}_{i,1,l} !} {n^{(j)}_{i,2,l} !} \cdots {n^{(j)}_{i,J_j,l} !}}  }},
+{{1}\over{ {{n_{i,l}}!}\over{ {n^{(j)}_{i,1,l} !} {n^{(j)}_{i,2,l} !} \cdots {n^{(j)}_{i,J_j,l} !}}  }}\text{,}
 \end{equation}
+
+\noindent
 where $n^{(j)}_{i,m,l}$ is the number of instances in $i$th interval with $m$th value of $C_j$ and $l$th value of $\boldsymbol{S_j}$, $n_{i,l} = \sum_{m=1}^{J_j} n^{(j)}_{i,m,l}$, and $n_i = \sum_{l=1}^{L_j} n_{i,l}$.
-The two factors on RHS comes from the third prior: all distribution of values of $C_j$ in a given interval and with a given value of $S_j$ are equiprobable.
-According to the forth prior, these distributions are independent from each other, therefore we multiply all factors.
-If $S_j = \emptyset$, then Equation 13.
-is equivalent to
+The two factors on the right hand side come from the third prior: all distribution of values of $C_j$ in a given interval and with a given value of $S_j$ are equiprobable.
+According to the forth prior, these distributions are independent from each other, and one thus takes their product.
+If $S_j = \emptyset$, then Equation \ref{eq:likelihood_two} is equivalent to
+
 \begin{equation}
@@
 \prod_{i=1}^{k}  {{1}\over{{n_{i} + J_j - 1}\choose{J_j-1}}}
-{{1}\over{ {{n_{i}}!}\over{ {n^{(j)}_{i,1,\emptyset} !} {n^{(j)}_{i,2,\emptyset} !} \cdots {n^{(j)}_{i,J_j,\emptyset} !}}  }},
+{{1}\over{ {{n_{i}}!}\over{ {n^{(j)}_{i,1,\emptyset} !} {n^{(j)}_{i,2,\emptyset} !} \cdots {n^{(j)}_{i,J_j,\emptyset} !}}  }}\text{,}
 \end{equation}
-where $n^{(j)}_{i,m,\emptyset}$ is the number of instances in $i$th interval with $m$th value of $C_j$, and $\sum_{m=1}^{J_j} n^{(j)}_{i,m,\emptyset} = n_i$. \\
 
-With Equation 8,9,11,12, and 13, now we are able to write down the objective function. Instead of maximizing $P(M) \cdot P(D|M)$, we minimize its log-inverse for convenience. The objective function is
+\noindent
+where $n^{(j)}_{i,m,\emptyset}$ is the number of instances in the $i$th interval with the $m$th value of $C_j$, and $\sum_{m=1}^{J_j} n^{(j)}_{i,m,\emptyset} = n_i$.
+
+The objective function can be formulated given equations \todo{8,9,11,12}, and \ref{eq:likelihood_two}.
+Instead of maximizing $P(M) \cdot P(D|M)$, the log-inverse is minimized for computational convenience.
+The objective function is
+
 \begin{equation}

### 2015-11-12 BN_discretizer_paper.tex
more

@@
 Another advantage of our method is the running time for learning.
-If there is only one continuous variable, the running time is $O(n_c  {v_{max}} \cdot N^2 + {v_{max}}^{n_p} \cdot N^2)$, which is significantly shorter than the running time of MDL principle discretization \citep{Friedman_1996}.
-With the approximation proposed in this paper, we can further reduce running time to $O({v_{max}}(n_p+n_c)N^2)$.
+If there is only one continuous variable, the running time is $O(n_c  {v_\text{max}} \cdot N^2 + {v_\text{max}}^{n_p} \cdot N^2)$, which is significantly shorter than the running time of MDL principle discretization \citep{Friedman_1996}.
+With the approximation proposed in this paper, we can further reduce running time to $O({v_\text{max}}(n_p+n_c)N^2)$.
 
@@
 \begin{equation}
-P(M) = \prod_{i=1}^k \{ [1 - {\exp(- L \cdot {{x_{s_i+1} - x_{s_i}}\over{x_N - x_1}})}] \cdot \exp(L \cdot {{x_{s_{i}} - x_{s_{i-1} + 1}}\over{x_N - x_1}}) \},
+\label{eq:p_M}
+P(M) = \prod_{i=1}^k \brock{ [1 - {\exp(- L \cdot {{x_{s_i+1} - x_{s_i}}\over{x_N - x_1}})}] \cdot \exp(L \cdot {{x_{s_{i}} - x_{s_{i-1} + 1}}\over{x_N - x_1}}) }\text{,}
 \end{equation}
+
+\noindent
 where $s_i = \sum_{j=1}^k n_j$, $s_k = N$, and $s_0 = 0$. Before evaluating $P(D \mid M)$, note that
+
 \begin{equation}
+\label{eq:p_D_given_M}
 P(D \mid M) \propto P(D_{\Pi_x} \mid M) \cdot \prod_{i = 1}^{n_c} P(D_{C_i} \mid M, D_{\boldsymbol{S_i}})\text{.}
 \end{equation}
+
 The graph structure allows us to only consider the interations between $X$ and the other variables in its Markov blanket, thus allowing for convenient factorization.
@@
 \begin{equation}
+\label{eq:likelihood_one}
 P(D_{\Pi_X} \mid M) = \prod_{i=1}^k  {{1}\over{{n_i + J_P - 1}\choose{J_P -1}}}
@@
 \begin{equation}
+\label{eq:likelihood_three}
 P(D_{C_j}  \mid M) =
@@
 
-The objective function can be formulated given equations \todo{8,9,11,12}, and \ref{eq:likelihood_two}.
-Instead of maximizing $P(M) \cdot P(D|M)$, the log-inverse is minimized for computational convenience.
-The objective function is
+The objective function can be formulated given equations \ref{eq:p_M}, \ref{eq:p_D_given_M},\ref{eq:likelihood_one}, and \ref{eq:likelihood_three}.
+The log-inverse of $P(M) \cdot P(D|M)$ is minimized for computational convenience:
 
 \begin{equation}
+\label{eq:opt_prob}
 \begin{aligned}
@@
 &  \sum_{j=1}^{n_c} \sum_{i=1}^{k}  \sum_{l=1}^{L_j} \left[  \log{{n_{i,l} + J_j - 1}\choose{J_j-1}} + \log \left( { {{n_{i,l}}!}\over{ {n^{(j)}_{i,1,l} !} {n^{(j)}_{i,2,l} !} \cdots {n^{(j)}_{i,J_j,l} !}} } \right) \right] + \\
-& \sum_{i=1}^k \left[  \log {{n_{i} + J_P - 1}\choose{J_P-1}} + \log \left( { {{n_i}!}\over{ {n^{(p)}_{i,1} !} {n^{(p)}_{i,2} !} \cdots {n^{(p)}_{i,J_p} !}} } \right) \right].
+& \sum_{i=1}^k \left[  \log {{n_{i} + J_P - 1}\choose{J_P-1}} + \log \left( { {{n_i}!}\over{ {n^{(p)}_{i,1} !} {n^{(p)}_{i,2} !} \cdots {n^{(p)}_{i,J_p} !}} } \right) \right]\text{.}
 \end{aligned}
 \end{equation}
-All parameters and variables in the objective function are explained in previous subsections.
+
 \subsection{Algorithm}
-\label{algo}
-Once the objective function is established, the next problem is how to find a discretization model that minimizes the objective function.
-Note that the objective function is cumulative on intervals.
-Therefore, if a partition of continuous variable $X$ into $k$ intervals with lengths $n_1,n_2,\ldots,n_k$ is an optimal discretization policy, then $\{ n_2, n_3,\ldots,n_k \}$ is optimal for the subproblem, i.e., the last $N - n_1$ instances of the dataset which has been sorted in ascending order of $D_X$.
-With this property, we can adapt dynamical programming to solve this optimization problem.
 
-If there is no repeated value in $D_X$, all middle points of two consecutive values can a discretization edge.
-If there exists repeated values in $D_X$, only the middle points of two consecutive and different values can be a discretization edge.
-Assume there are $M$ unique values in $D_X$, then ${D'_X} = \{ x'_1,x'_2,\ldots,x'_M \}$ is the set of unique values of $D_X$ in ascending order.
-Since $D_X$ is also sorted, let $b = \{ b_0,b_1,b_2,\ldots,b_M \}$ be an increasing sequence of integers such that $b_0 = 0$ and $x_{b_{i-1} + 1} = x_{b_{i-1} + 2} = \ldots = x_{{b_i}} = x'_i$.
-By this definition, the allowable discretization positions are $d_i = ( x_{b_{i}} + x_{{b_i}+1})/2$ for all $i = 1,2,\ldots,M-1$.
+This section describes the procedure used to minimize the objective function.
+Note that the objective function is cumulative over intervals, thus, if a partition of $X$ into $k$ intervals with lengths $n_1,n_2,\ldots,n_k$ is an optimal discretization policy, then any subinterval is optimal for the corresponding subproblem.
+It follows that dynamic programming can be used to solve the optimization problem exactly.
 
-Before doing the dynamical programming, in order to save runtime, we first calculate the following function $h(u,v)$ for a interval $I_q$ starting from $x_{u}$ to $x_{v}$ with all $u$,$v$ satisfying $u \leq v$:
+Every midpoint between two nonequal consecutive values in $D_X$ is a candidate discretization edge.
+Let ${D'_X} = \brock{x'_1,x'_2,\ldots,x'_M}$ be the set of unique values of $D_X$ sorted in ascending order, where $M$ is the number unique values in $D_X$.
+Recall that $D_X$ is also sorted.
+Let $b = \brock{b_0,b_1,b_2,\ldots,b_M}$ be an increasing sequence of integers marking the repeated value intervals in $D_X$ such that $b_0 = 0$ and $x_{b_{i-1} + 1} = x_{b_{i-1} + 2} = \ldots = x_{b_i} = x'_i$.
+By this definition, the allowable discretization positions are $d_i = \paren{x_{b_{i}} + x_{{b_i}+1}}/2$ for all $i = 1,2,\ldots,M-1$.
+
+Precomutation can be done to reduce runtime.
+Compute $h(u,v)$ for each interval $I_q$ starting from $x_{u}$ to $x_{v}$ for all $(u,v)$ satisfying $u \leq v$:
+
+\begin{small}
 \begin{equation}
@@
 \end{equation}
+\end{small}
 
-The evaluation of function $h(u,v)$ for all $u \leq v$ is summerized in Algorithm 4 in Appendix.
-The calculation can be done in $O(n_c  {v'_{max}} \cdot N^2 + {v'_{max}}^{n_p} \cdot N^2)$, where $n_c$ and $n_p$ are the numbers of child and parent variables, respectively, and $v'_{max}$ is the largest cardinality of variables that directly connects to $X$.
-Notice that due to repeated values in $D_X$, for some pairs of $u$ and $v$, the value of $h(u,v)$ might depend on the sorting method of $D_X$ and $D$.
-However, this does not influence the optimization result, since these pairs of $u$ and $v$ will not form valid intervals.
+The evaluation of $h(u,v)$ for all $u \leq v$ is summarized in Algorithm \ref{alg:h} in the appendix.
+The calculation has a $O(n_c  {v'_\text{max}} \cdot N^2 + {v'_\text{max}}^{n_p} \cdot N^2)$ runtime, where $n_c$ and $n_p$ are the numbers of child and parent variables respectively, and $v'_\text{max}$ is the largest cardinality of variables that directly connect to $X$.
 
-Now we are able to solve the optimization problem with the objective function in Equation 14.
-The dynamical programming procedure is shown in Algorithm 1.
-We have three inputs: $D_X$, the data of continuous variable $X$ in the ascending order, $D$, the data of other variables and sorted according to $D_X$, and $G$, the network structure.
-The runtime of Algorithm 1 is also $O(n_c  {v'_{max}} \cdot N^2 + {v'_{max}}^{n_p} \cdot N^2)$, since the dynamical programming procedure does not increase the time complexity beyond the calculation of $h(u,v)$.
-There are other methods that lead to suboptimal results but runs faster than dynamical programming method.
-Please refer to \citep{Boulle_2006}.
+% \tim{I think we can leave this out if it doesn't affect the algorithm results, and people will always sort in ascending order}
+% Due to repeated values in $D_X$, for some pairs $(u,v)$, $h(u,v)$ may depend on the sorting method of $D_X$ and $D$.
+% However, this does not influence the optimization result, since these pairs of $u$ and $v$ will not form valid intervals.
+
+Now we are able to solve the optimization problem over Equation \ref{eq:opt_prob}.
+The dynamic programming procedure is shown in Algorithm \ref{alg:disc_one}.
+It takes two inputs: $D$, the joint samples over all variables sorted in ascending order according to $D_X$, and $G$, the network structure.
+The runtime of Algorithm \ref{alg:disc_one} is also $O(n_c  {v'_\text{max}} \cdot N^2 + {v'_\text{max}}^{n_p} \cdot N^2)$, because the runtime of the dynamic programming procedure is less than the runtime for computing $h(u,v)$.
+Algorithm \ref{alg:disc_one} is guaranteed to be optimal.
+For faster methods with suboptimal results please refer to \citep{Boulle_2006}.
 
 \begin{algorithm}
-\caption{ Discretization of one continuous variable}\label{euclid}
+\caption{Discretization of one continuous variable in a Bayesian network}
+\label{alg:disc_one}
 \begin{algorithmic}[5]
-\Function{Discretize}{$D_X$, $D$, $G$}
+\Function{Discretize}{$D$, $G$}
 \State
 \State $N \leftarrow$ the number of instances
-\State $N' \leftarrow$ the number of non-repeated values of $D_X$
-\State $H \leftarrow$ an $N \times N$ matrix such that $H[u,v] = h(u,v)$ as Algorithm 4 in Appendix
-\State $b \leftarrow$ the increasing sequence of $M$ integers defined in the previous discussion
-\State $L \leftarrow$ the largest cardinality over all discrete variables in the Markov blanket
-\State $S[u] \leftarrow$ the optimal objective value of a subproblem with instances from $1$ to $u$
-\State $M[u] \leftarrow$ the optimal discretization of a subproblem with instances from $1$ to $u$
+\State $N' \leftarrow$ the number of unique values in $D_X$
+\State $H \leftarrow$ an $N \times N$ matrix such that $H[u,v] = h(u,v)$ per Algorithm \ref{alg:h} in the appendix
+\State $b \leftarrow$ the increasing sequence of $M$ integers as previously defined
+\State $L \leftarrow$ the largest cardinality over all discrete variables in the Markov blanket of $X$
+\State $S[u] \leftarrow$ the optimal objective value of subproblems with instances from $1$ to $u$
+\State $M[u] \leftarrow$ the optimal discretization for subproblems with instances from $1$ to $u$
 \State $W[u]  \leftarrow - \log(1 - {\exp(- L \cdot{ {{x_{b(u)+1} - x_{b(u)}}\over{x_N - x_1}})}})$ for $u = 1,2, \ldots,N'-1$ and $L(N') \leftarrow 0$
@@
 \If {$v = 1$}
-\State $S[v] = g \left(1,b[v] \right) + L[v]$
-\State $M[v] = \{ ({x_{b[v]} + x_{b[v]+1}}) / 2\}$
+\State $S[v] \leftarrow g \left(1,b[v] \right) + L[v]$
+\State $M[v] \leftarrow \{ ({x_{b[v]} + x_{b[v]+1}}) / 2\}$
 \Else
@@
 \subsection{Approximation}
-\label{approx}
-Notice that Algorithm1 leads to the non-polynomial runtime $O({v'_{max}}^{n_p} \cdot N^2)$ in the discretization process.
-Therefore, we have an empirical approximation to the objective function that can reduce runtime and still preserve the quality of discretization.
-The approximation is as follows: for the dominator of the last factor in Equation 11, we have
+
+Algorithm \ref{alg:disc_one} has an exponential $\bigo\paren{\paren{v'_\text{max}}^{n_p} \cdot N^2}$ runtime.
+This exponential runtime is severely limiting for networks with a large number of discretization edges.
+This section introduces an approximation to the objective function that significantly reduces the runtime and still preserves the quality of discretization.
+The approximation replaces the dominator of the last factor in Equation \ref{eq:likelihood_one} with
+
 \begin{equation}
-{{{{n}_i}!}\over{ {{n^{(p)}}_{i,1} !} {n^{(p)}_{i,2} !} \cdots {n^{(p)}_{i,J_P} !}}} \approx \prod_{r=1}^{n_p} { {{{n}_i}!}\over{ {n^{(p_r)}_{i,1} !} {n^{(p_r)}_{i,2} !} \cdots {n^{(p_r)}_{i,J_{p_r}} !}}},
+{\frac{{n_i}!}{ {n^{(p)}_{i,1} !} {n^{(p)}_{i,2} !} \cdots {n^{(p)}_{i,J_P} !}}} \approx \prod_{r=1}^{n_p} { {{{n}_i}!}\over{ {n^{(p_r)}_{i,1} !} {n^{(p_r)}_{i,2} !} \cdots {n^{(p_r)}_{i,J_{p_r}} !}}}\text{,}
 \end{equation}
-where $J_{p_r} = \| P_r\|$ and ${n^{(p_r)}_{i,j} !}$ is the number of instances in $i$th interval with $j$th value of $P_r$. Applying this approximation, the approximated objective function is
+
+\noindent
+where $J_{p_r} = \| P_r\|$ and ${n^{(p_r)}_{i,j} !}$ is the number of instances in the $i$th interval with the $j$th value of $P_r$.
+The approximated objective function is
+
 \begin{equation}
 \begin{aligned}
+\label{eq:opt_prob_approx}
 & \sum_{i=1}^{k-1} - \log(1 - {\exp(- L \cdot {{x_{s_i+1} - x_{s_i}}\over{x_N - x_1}})}) +  \sum_{i=1}^{k} L \cdot {{x_{s_{i}} - x_{s_{i-1} + 1}}\over{x_N - x_1}} +\\
 &  \sum_{j=1}^{n_c} \sum_{i=1}^{k}  \sum_{l=1}^{L_j} \left[  \log{{n_{i,l} + J_j - 1}\choose{J_j-1}} + \log \left( { {{n_{i,l}}!}\over{ {n^{(j)}_{i,1,l} !} {n^{(j)}_{i,2,l} !} \cdots {n^{(j)}_{i,J_j,l} !}} } \right) \right] + \\
-& \sum_{i=1}^k \left[  \log {{n_{i} + J_P - 1}\choose{J_P-1}} + \sum_{q=1}^{n_p} \log \left( { {{{n}_i}!}\over{ {n^{(p_q)}_{i,1} !} {n^{(p_q)}_{i,2} !} \cdots {n^{(p_q)}_{i,J_{p_q}} !}}} \right) \right].
+& \sum_{i=1}^k \left[  \log {{n_{i} + J_P - 1}\choose{J_P-1}} + \sum_{q=1}^{n_p} \log \left( { {{{n}_i}!}\over{ {n^{(p_q)}_{i,1} !} {n^{(p_q)}_{i,2} !} \cdots {n^{(p_q)}_{i,J_{p_q}} !}}} \right) \right]\text{.}
 \end{aligned}
@@
 
-As we will see in Section \ref{sec:experiments}, the approximated algorithm is more sensitive to the distribution of other variables' values and usually leads to slightly more discretization edges.
-With the approximation, we can reduce runtime of Algorithm 1 from $O(n_c  {v'_{max}} \cdot N^2 + {v'_{max}}^{n_p} \cdot N^2)$ to $O( {v'_{max}} (n_c + n_p) \cdot N^2)$.
-The rigorous proof of the approximation have not been proposed.
+The approximation reduces the runtime of Algorithm \ref{alg:disc_one} to a polynomial, $\bigo\paren{ {v'_\text{max}} \cdot (n_c + n_p) \cdot N^2}$.
+\tim{`The rigorous proof of the approximation have not been proposed.' Do you mean that we are not proving that the approximation always holds, or that the algorithm conserves optimality, or something else?}
+It will be shown in Section \ref{sec:experiments} that the approximation is more sensitive to the distribution over other variables and is biased towards slightly higher interval counts.
 
-With the approximated objective function, Equation 17, we now have a more clear way to see that how child variables and parent variables contribute to the objective function differently.
+With the approximated objective function, Equation \ref{eq:opt_prob_approx}, we now have a more clear way to see that how child variables and parent variables contribute to the objective function differently.
 For example, in the left graph of Figure 2, the corresponding sqaure brackets in Equation 17 are
@@
 \begin{algorithm}
-\caption{ Calculation of function $h(u,v)$ for all $u \leq v$}\label{euclid}
+\caption{ Calculation of function $h(u,v)$ for all $u \leq v$}
+\label{alg:h}
 \begin{algorithmic}[1]

### 2015-11-12 BN_discretizer_paper.tex
done with section 4

@@
 
-With the approximated objective function, Equation \ref{eq:opt_prob_approx}, we now have a more clear way to see that how child variables and parent variables contribute to the objective function differently.
-For example, in the left graph of Figure 2, the corresponding sqaure brackets in Equation 17 are
+With the approximated objective function, Equation \ref{eq:opt_prob_approx}, provides intuition into how child and parent variables contribute to the objective function.
+For example, in the left graph of Figure \ref{fig:example_networks}, the corresponding square brackets in the approximated object function are
+
 \begin{equation}
 \begin{aligned}
+\label{eq:example_approx}
  \sum_{i=1}^k & \left\lbrace   \left[ \log{{n_{i} + J_{C_1} - 1}\choose{J_{C_1}-1}} + \log \left(  {{{n_i}!} \over { {n^{(1)}_{i,1,\emptyset} !} \cdots {n^{(1)}_{i,J_{C_1},\emptyset} !}} }  \right)  +  \right.
@@
 &  \left.
-\left[  \log {{n_{i} + J_P - 1}\choose{J_P-1}} +  \log \left( { {{{n}_i}!}\over{ {n^{(p_1)}_{i,1} !}\cdots {n^{(p_1)}_{i,J_{p_1}} !}}} \right) +{ {{{n}_i}!}\over{ {n^{(p_2}_{i,1} !}\cdots {n^{(p_2)}_{i,J_{p_2}} !}}}  \right] \right\rbrace\\ .
+\left[  \log {{n_{i} + J_P - 1}\choose{J_P-1}} +  \log \left( { {{{n}_i}!}\over{ {n^{(p_1)}_{i,1} !}\cdots {n^{(p_1)}_{i,J_{p_1}} !}}} \right) +{ {{{n}_i}!}\over{ {n^{(p_2}_{i,1} !}\cdots {n^{(p_2)}_{i,J_{p_2}} !}}}  \right] \right\rbrace \text{.}
 \end{aligned}
@@
 
-In Equation18, each child variable carries two terms, as shown in the first square bracket, and two parent variables only carry three terms, as shown in the second square bracket.
-Therefore, in this case, child variables are more determinative than parent variables even though the numbers of child variables and parent variables are equal.
-However, if $C_2$ has the other parent variable $S_2$, as shown in the right graph of Figure 2, the importances of $C_2$ will be debiliated, since the information from $C_2$ is now adulterated by $S_2$.
-These argument shows that our proposed method, either before or after approximation, indeed involves graph structures to discretize continuous variables.
+In Equation \ref{eq:example_approx}, each child carries two terms, as shown in the first set of square brackets, but the two parent variables only carry a total of three terms, as shown in the second set of square brackets.
+In this case the child variables have greater effect than the parent variables even though the number of child and parent variables are the same.
+However, if $C_2$ has an additional parent $S_2$, as shown in the right graph of Figure \ref{fig:example_networks}, the importances of $C_2$ will be reduced, because the information from $C_2$ is now affected by $S_2$.
+This argument shows that the proposed method, both before and after approximation, indeed incorporates graph structure when discretizing continuous variables.
 
 \begin{figure}[ht]
+  \label{fig:example_networks}
     \begin{tabular}{cc}

### 2015-11-12 BN_discretizer_paper.tex
first complete readthrough complete

@@
 \begin{align}
+\label{eq:f_x_p}
 f(X_i, \Pi_{X_i}) = \prod_{j=1}^{\|\Pi_{X_i}\|} {{(\|X_i\|-1)!}\over{(N_{ij} + \|X_i\|-1)!}} \prod_{k=1}^{\|X_i\|} \alpha_{ijk}!\text{.}
@@
 
-If there are multiple continuous variables in a Bayesian network, we iterate the one-variable discretization method discussed above for all continuous variables.
-While discretizing a continuous variable, other continuous variables must be discretized, either by a prediscretization that was done before the first iteration or by the discretization result of the latest iteration.
-The prediscretization can be done by equal-width discretization, which is defined as follows:
+The single-variable discretization method can be extended to Bayesian networks with multiple continuous variables by iteratively discretizing variables individually.
+The discretization process for a single variable requires that all other variables be discrete.
+The iterative approach thus requires a prediscretization policy from which to initialize the process.
+This work uses prediscretization with equal-width intervals, defined by
+
 \begin{equation}
-M_X =  \{ min_X, min_X + \delta, min_X + 2\delta, \ldots, \delta, max_X \},
+M_X =  \curly{X_\text{min}, X_\text{min} + \delta, X_\text{min} + 2\delta, \ldots, \delta, X_\text{max}}\text{,}
 \end{equation}
-where $min_X$ and $max_X$ are minimal and maximal values of $D_X$, respectively, $\delta =  (max_X - min_X)/k$, and $k$ is the desired number of intervals after equal-width discretization.
-$k$ is same for all continuous variables and is set to be median value of all discrete variables' cardinalities.
-After prediscretization, we iterate the one-variable discretization on each continuous variable in the following order: from the continuous variable with highest topological order (leaves) to the continuous variable with lowest topological order (root).
-We call one such series of discretizations as a cycle.
-The advange of the order is that, for the first cycle of iteration, we can use less number of unsupervised discretization result.
-For example, in the right graph of Figure 2, assume $S_2$ is the only discrete variable.
-If we begin the iteration with $P_1$, then the discretization of $P_1$ will involve the prediscretization results of both $P_2$ and $X$.
-However, if we begin the iteration with $C_1$, then the discretization of $C_1$ will only involve the prediscretization result of $X$.
 
-When the number of intervals after discretization and the positions of discretization edges converge, we stop the iterations and output the discretization policy on each continuous variable.
-Since the convergence is not guaranteed, we also set up a maximal number of cycles to prevent infinite iterations.
-In our test on real-world data, the iteration results usually converge within few cycles.
-Even if it does not converge, 10 cycles usually produce good enough discretization result.
-The pseudocode of multi-variable discretization is shown in Algorithm 2, where we require four inputs: $D''$, the mixed data of all variables that we plan to learn from, $G$, the network structure, $C$, the set of all continuous variables in a reverse topological order, and $u_{cycle}$, the upper bound of times of cycles.
+\noindent
+where $X_\text{min}$ and $X_\text{max}$ are the extrema values of $D_X$, $\delta = (X_\text{max} - X_\text{min})/k$, and $k$ is the desired number of intervals.
+This work sets $k$ to the median value of the cardinalities of initially discrete variables in the network.
+After prediscretization, the one-variable discretization methis is iteratively applied over each continuous variable in reverse topoligical order, from the leaves to the root.
+Let one such series of discretizations be a cycle.
+Reverse topological order has the advantage of using less prediscretized instantiations during the first cycle.
+For example, in the right-hand graph of Figure \ref{fig:example_networks}, assume $S_2$ is the only discrete variable.
+The discretization of $P_1$ involves both $P_2$ and $X$, whereas the discretization of $C_1$ only involves $X$.
+
+The algorithm is terminated when the number of discretization intervals and their associated edges converge for all variables.
+A maximum cycle count is enforced to prevent infinite iterations when convergence does not occur.
+The algorithm typically converges within a few cycles when tested on real-world data.
+In cases where it does not converge, ten cycles usually produce decent discretization results.
+
+The pseudocode for the multi-variable discretization procedure is shown in Algorithm \ref{alg:disc_two}.
+It requires four inputs: $D''$, the joint samples from all network variables; $G$, the network structure; $C$, the set of all continuous variables in a reverse topological order; and $u_{cycle}$, the upper bound of times of cycles.
 
 \begin{algorithm}
-\caption{ Discretization of multiple continuous variables}
+\label{alg:disc_two}
+\caption{Discretization of multiple continuous variables \todo{Fix label reference number}}
 \begin{algorithmic}[5]
@@
 \State
-\State $M[i] \leftarrow$ the discretization policy of $i$th variable
-\State $n \leftarrow$ the number of variables in Bayesian network
-\State $D^*_i \leftarrow M[i] (D_i)$, the discretized $D_i$ by $M[i]$
+\State $M[i] \leftarrow$ the discretization policy for the $i$th variable
+\State $n \leftarrow$ the number of variables in the Bayesian network
+\State $D^*_i \leftarrow M[i] (D_i)$, list of samples $D_i$ discretized according to $M[i]$
 \State $D^* \leftarrow $ the discretized data for all variables, where $D^*_i \leftarrow D''_i$ if $i \notin C$
@@
 \State {$M[C(j)] \leftarrow $ DISCRETIZE($D_{C(j)}$,$D^*_{ \backslash C(j)}$,graph)}
-\State {$D^*_{C(j)}  \leftarrow$ $M[C(j)](D''_{C(j)}) $}
+\State {$D^*_{C(j)}  \leftarrow$ $M[C(j)](D''_{C(j)})$}
 \EndFor
@@
 
-\subsection{Discretization of Continuous Variables While Structure Learning}
+\subsection{Combining Discretization with Structure Learning}
 
-In many situations the network structure is not known in advance, then we need to learn it from data.
-We use an alternative approach to combine our proposed discretization method with the K2 structure learning algorithm \citep{K2}.
-That is to say, we start with some prediscretizations on continuous variables and run the K2 algorithm given the discretized data.
-Each time an edge is added by the K2 algorithm, we rediscretize the continuous variables based on the current network.
-Then the new discretization policies update the discretized data of all continuous variables, and we continue the next K2 step with the updated discretized data.
-This cycle is repeated until no edge is added by the K2 algorithm.
-The detail of the procedure is shown in Algorithm 3.
-Here we have five inputs: $D'$, the mixed data we plan to learn from, $C$, the set of all continuous variables, $order$, the variable order which is required by the $K2$, $u_{parent}$, the upper bound of number of parents which is also required by the $K2$, and $u_{cycle}$, the upper bound of times of cycles.
-Notice that in the usual structure learning from discrete data, one usually run the K2 algorithm many times with different orders, and choose the structure with the highest K2 score.
-We do the same thing: run Algorithm 3 many times, each time with a different order, and pick the discretized Bayesian network with the highest K2 score.
+In many situations the network structure is not known in advance and must be learned from data.
+Traditional Bayesian structure learning algorithms require discretized data, whereas the proposed discretization algorithm requires a network structure.
+This section combines the proposed discretization method with the K2 structure learning algorithm \citep{K2} in an interative fassion to simultaneously perform Bayesian structure learning and discretization of continuous variables.
+
+The proposed algorithm alternates between K2 structure learning and discretization.
+K2 is run on the discretized dataset corresponding to prediscretizations for all continuous variables.
+The affected continuous variables are rediscretized every time an edge is added by K2.
+The resulting discretization policies are used to update the discretized dataset, and the next step of the K2 algorithm is executed.
+This cycle is repeated until the K2 algorithm reaches a local maximum.
+
+This procedure is given in Algorithm \ref{alg:structure_learn}.
+It takes five inputs: $D'$, the joint samples from all network variables; $C$, the set of all continuous variables; $order$, the permutation of variable for $K2$; $u_{parent}$, the upper bound on the number of parents per node for $K2$; and $u_{cycle}$, the upper bound on the cycle count.
+It is common practice to run K2 multiple times with different permutations of the variables and to then choose the structure with the highest score.
+This work runs Algorithm \ref{alg:structure_learn} multiple times, each with a different order, and picks the discretized Bayesian network with the highest score.
+
 \begin{algorithm}
+\label{alg:structure_learn}
 \caption{ Learning a discrete-valued Bayesian network}
@@
 \Function{Learn\_DBN}{$D''$, $C$, $order$, $u_{parent}$, $C$, $u_{cycle}$}
-\State
-
-\State $n \leftarrow$ the number of variables in Bayesian network
+  \State $n \leftarrow$ the number of variables in the Bayesian network
   \State $k \leftarrow median\{ \|v\|, v\notin C\}$
-\State $M[i] \leftarrow$ the discretization policy of $i$th variable
-\State $D^*_i \leftarrow M[i] (D_i)$, the discretized $D_i$ by $M[i]$
+  \State $M[i] \leftarrow$ the discretization policy for the $i$th variable
+  \State $D^*_i \leftarrow M[i] (D_i)$, list of samples $D_i$ discretized according to $M[i]$
   \State $D^* \leftarrow $ the discretized data for all variables, where $D^*_i \leftarrow D''_i$ if $i \notin C$
-\State $G \leftarrow$ the initial graph (no edges between nodes)
+  \State $G \leftarrow$ the initial edgeless graph structure
   \State
@@
   \For {$i =1$ to $n$}
-\State $P_{old} \leftarrow f(X^*_i,\Pi_{X^*_i})$: Equation 5
+    \State $P_{old} \leftarrow f(X^*_i,\Pi_{X^*_i})$: Equation \ref{eq:f_x_p}
     \State OKToProceed $\leftarrow$ \textbf{true}
-\While OKToProceed \textbf{and} $\|\Pi_{X^*_i}\| < u_{parent}$
+    \While {OKToProceed \textbf{and} $\|\Pi_{X^*_i}\| < u_{parent}$}
       \State $Y \leftarrow$ an element from the set $order[1:i] \backslash \Pi_X$
@@
         \State $\Pi_{X_i} \leftarrow \Pi_{X_i} \cup Y $
-\State $M \leftarrow$ {DISCRETIZE}({$D''$, $G$, $C$, $u_{cycle}$}): Algorithm 2
+        \State $M \leftarrow$ {DISCRETIZE}({$D''$, $G$, $C$, $u_{cycle}$}): Algorithm \ref{alg:disc_two}
         \State $D* = M(D'')$
@@
 \begin{algorithm}
-\caption{ Calculation of function $h(u,v)$ for all $u \leq v$}
+  \caption{ Calculation of $h(u,v)$ for all $u \leq v$}
   \label{alg:h}
   \begin{algorithmic}[1]
-\State Initialize $H$ as an $N \times N$ matrix that all elements are 0.
+    \State Initialize $H$ as an $N \times N$ matrix such that all elements are 0.
     \State $count_p$ is an $N \times N \times \|\Pi_X\|$ matrix such that $count_p [u,v,w]$ is the number of instances from $x_u$ to $x_v$ with $w$th value of $\Pi_X$.

### 2015-11-13 BN_discretizer_paper.tex
misc updates

--- 2015-11-12 BN_discretizer_paper.tex
@@
 They provide an efficient factorization of the joint probability distribution over a set of random variables.
-Bayesian networks first emerged from artificial intelligence research and have been applied to a wide variety of problems, ranging from decision-making systems \citep{DMU_2015} to medical diagnoses~\todo{[cite]}.
+Bayesian networks first emerged from artificial intelligence research and have been applied to a wide variety of problems, ranging from decision-making systems \citep{DMU_2015} to medical diagnoses \citep{Lustgarten_2011}.
 In most cases, we assume that all random variables in Bayesian networks are discrete, since many Bayesian network learning algorithms are unable to deal with continuous variables efficiently.
@@
 One successful example is belief propagation in Gaussian graphical models \citep{Weiss_2011}.
-For other particle shapes \citep{Ihler_2009} and non-linear functions \tim{cite if you can}, these redesigned algorithms are computationally expensive and do not perform well.
+For other particle shapes \citep{Ihler_2009} and non-linear functions~\todo{[cite]}, these redesigned algorithms are computationally expensive and do not perform well.
 \tim{Not sure what `particle shapes' are. Do you mean other parametric distributions?}
@@
 The second approach is discretization.
-Automated discretization methods have been studied in machine learning and statistics for many years \citep{Dougherty_1995, Kerber_1992, Holte_1993, Fayyad_1993}.
-Most discretization methods were designed for classification problems.
-They search for the best discretization policy\tim{maybe `scheme' is a better word than `policy', which in machine learning means something else.} of a continuous attribute by considering its interation with the target class variable.
-These discretization methods do not apply to continuous variables in Bayesian networks, where interations and dependencies between variables are more complicated.
-Discretization of a continuous variable in a Bayesian network requires considering the impact on the entire network.
-There is prior work on discretizing continuous variables in naive Bayesian networks and tree-augmented networks \citep{Fried_naive}, but only a few discretization methods for general Bayesian networks have been proposed \citep{Friedman_1996, Kozlov_1997, Monti_1998, Steck_2007}.
+Automated discretization methods have been studied in machine learning and statistics for many years \citep{Dougherty_1995, Kerber_1992, Holte_1993, Fayyad_1993}, primarily for classification problems.
+They search for the best discretization policy of a continuous attribute by considering its interation with the target class variable.
+Interations and dependencies between variables in Bayesian networks are more complicated, where discretization requires considering the impact on the variable's Markov blanket.
+Prior work exists for discretizing continuous variables in naive Bayesian networks and tree-augmented networks \citep{Fried_naive}, but only a few discretization methods for general Bayesian networks have been proposed \citep{Friedman_1996, Kozlov_1997, Monti_1998, Steck_2007}.
 
-The discretization technique proposed by \citet{Friedman_1996} is the most well-known of these methods.
-It is based on the minimum description length principle (MDL): the optimal discretization policy minimizes the description length of the Bayesian network and discretization scheme.
-The MDL algorithm has a $\bigo\paren{N^3 + \paren{n_c {v_\text{max}}^{(n_c^p)_\text{max}} + {v_\text{max}}^{n_p}} \cdot N^2}$ runtime on Bayesian networks with a single continuous variable and multiple discrete variables, where $N$ is the number of data samples from the joint distribution, $n_p$ and $n_c$ are the numbers of parent and children variables for the continuous variable, $v_\text{max}$ is the largest cardinality over all variables in the Markov blanket, and  ${(n_c^p)_\text{max}}$ is the largest number of parent variables of the continuous variable's children.
-The MDL method iterates over all continuous variables until convergence in the case of multiple continuous variables, converging in a few cycles according to our tests of real-world data.
-Unfortunately, MDL tends to produce discrete variables with low cardinality.
-\tim{Note: use $\text{thing}$ for subscripts such as $n_\text{max}$.}
-
-\tim{Motivate / introduce Bayesian discretization methods perhaps? This would be a good place to cite Boulle and Lustgarten}
-
-\tim{
-The commented material below is good, but feels like too much detail for the intro. Is it possible to move it to later sections?
-I recommend having one paragraph that starts with `In this paper we propose \ldots' and then lists the specific contributions.
-(Bayesian discretization for arbitrary networks, a faster algorithm, demonstrate that performance is preserved, etc.).
-Then we should have the final paragraph below that discusses organization.}
-
-% In this paper, we propose a new Bayesian discretization method for continuous variables in Bayesian networks.
-This method extends the Bayesian single-variable discretization methods from \citet{Boulle_2006} and \citet{Lustgarten_2011}.
-We begin our method with the assumption that only one variable in a given Bayesian network is continuous and other variables are discrete.
-Furthermore we assume that the network structure is known in advance.
-Under this situation, we look for the most probable discretization policy $M$ given the data $D$ on other discrete variables.
-That is to say, the desired policy is $\textrm{arg}_M P(M \mid D)$.
-With Bayes' rule, $P(M \mid D) $ can be rewritten as $P(M) \cdot P(D \mid M) / P(D)$ , which is proportional to $P(M)\cdot P(D \mid M)$.
-Usually, $P(D \mid M)$ increases as the number of discretized intervals increases, since more intervals can provide more accuracy.
-$P(M)$, on the other hand, is designed to decrease as the number of intervals rises.
-As a result, we can automatically determine the number of intervals after discretization by maximizing  $P(M)\cdot P(D \mid M)$.
-In addition, the $P(D \mid M)$ can be factorized according to Bayesian network structure.
-With the proposed priors, we are able to restrict the number of discretized intervals so that it will not exceed the largest cardinality of variables in the Markov blanket by too much.
-This is important, since for most algorithms on Bayesian networks, their running times exponentially depend on the cardinality of variables.
-Another advantage of our method is the running time for learning.
-If there is only one continuous variable, the running time is $O(n_c  {v_\text{max}} \cdot N^2 + {v_\text{max}}^{n_p} \cdot N^2)$, which is significantly shorter than the running time of MDL principle discretization \citep{Friedman_1996}.
-With the approximation proposed in this paper, we can further reduce running time to $O({v_\text{max}}(n_p+n_c)N^2)$.
-
-% For a Bayesian network with multiple continuous variables, we apply the discretization method discussed above iteratively.
-In the beginning, we prediscretize each continuous variable by equal-width method.
-The number of intervals for equal-width discretization is equal to largest cardinality of discrete variables.
-Then we iterate the one-variable discretization on each continuous variable in the following order: from the variable with highest topological order (leaves) to the variable with lowest topological order (root).
-Each time we finish a discretization procedure on one variable, we store the discretization result for later iterations.
-Experiments on real-world data show that with the same iteration order, our discretization method provides better discretization results than MDL principle method in terms of likelihood.
-The MDL principle method is easily stuck at local minima and also discretizes variables into too few intervals.
-
-% Finally, we can combine our new discretization method with the K2 structure learning alorithm \citep{K2}.
-We first prediscretize all continuous variables before the K2 learning, since the K2 algorithm requires all variables to be discrete.
-Each time an edge is added in the K2 algorithm procedure, we rediscretize the continuous variables based on the updated Bayesian network and store the result for the next K2 algorithm iteration.
-By this principle, we are able to learn a discrete-valued Bayesian network from mixed data.
-
-The rest of the paper is organized as follows: related work, including MDL principle discretization \citep{Friedman_1996} and MODL discretization \citet{Boulle_2006} are summarized in Section \ref{sec:related_work}.
-Preliminaries and notation are covered in Section \ref{sec:preliminaries}.
-The proposed single-variable discretization method is derived in Section \ref{sec:single_var} and is extended to Bayesian networks with multiple continuous variables and combined with Bayesian structure learning in Section \ref{sec:multi_var}.
-The paper concludes with the comparison of the proposed methods against prior work on real-world data in Section \ref{sec:experiments}.
+This paper describes a new Bayesian discretization method for continuous variables in Bayesian networks, extending prior work on single-variable discretization methods from \citet{Boulle_2006} and \citet{Lustgarten_2011}.
+The proposed method optimizes the discretization policy relative to the network and takes parents, children, and spouse variables into account.
+The optimal single-variable discretization method is derived in Section \ref{sec:single_var}, and a second heuristic method is proposed which reduces the exponential runtime to polynomial.
+Section \ref{sec:multi_var} covers Bayesian networks with multiple continuous variables and discretization while simultaneously learning network structure.
+The paper concludes with a comparison against existing minimum-description length \citep{Friedman_1996} and MODL \citet{Boulle_2006} methods on real-world datasets in Section \ref{sec:experiments}.
 
@@
 \label{sec:related_work}
-This section reviews MDL principle discretization \citep{Friedman_1996} and MODL discretization \citep{Boulle_2006}.
+This section reviews the minimum description length (MDL) principle discretization \citep{Friedman_1996} and MODL discretization \citep{Boulle_2006}.
 The former is the predominant discretization method for continuous variables in Bayesian networks, and is compared to our proposed method in Section \ref{sec:experiments}.
-The latter is a discretization method for one continuous variable against a discrete target class.
-Our proposed method generalizes the MODL Bayesian discretization approach to Bayesian networks.
-The asymptotical equivalence between the MDL and MODL methods were examined in \citep{VL_2000}.
+The latter is a discretization method for one continuous variable against a discrete target class, which our proposed method generalizes to Bayesian networks.
+The asymptotical equivalence between MDL and MODL was examined in \citep{VL_2000}.
 
@@
 The MDL principle was first proposed by \cite{MDL_1978}, and states that the best model for a dataset is one which minimizes the amount of information needed to describe it \citep{Grunwald_2009}.
-MDL methods trade off goodness-of-fit against model complexity to avoid overfitting.
+MDL methods trade off goodness-of-fit against model complexity to reduce generalization error.
 In the context of Bayesian networks, \cite{Friedman_1996} applied the MDL principle to determine the optimal number of discretization intervals for continuous variables and optimal the positions of their discretization boundaries.
-Their approach selects a discretization policy that minimizes the sum of the description length of discretized Bayesian network and the description length of the information necessary for recovering the original continuous values from the discretized data.
+Their approach selects a discretization policy that minimizes the sum of the description lengths of the discretized Bayesian network and the information necessary for recovering the continuous values from the discretized data.
 In the single continuous variable case, the objective function is
-\tim{Do you need double vertical bars? If we use single bars it might fit without having to use the small font size.}
 
@@
 \noindent
-where $I(\boldsymbol{A},\boldsymbol{B}) = \sum_{\boldsymbol{a},\boldsymbol{b}} \hat{P}_D (\boldsymbol{a},\boldsymbol{b}) \log {{\hat{P}_D (\boldsymbol{a},\boldsymbol{b})}\over{\hat{P}_D (\boldsymbol{a}),\hat{P}_D (\boldsymbol{b})}}$ \tim{consider deleting the right half of equation} is the mutual information between two discrete variables $\boldsymbol{A}$ and $\boldsymbol{B}$, $\|\boldsymbol{X}\|$ is the cardinality of discrete variable $\boldsymbol{X}$, $X^*_i$ is the discretized version of continuous variable $X_i$ and $H(p) = -p \log(p) - (1-p) \log(1-p)$.
-The optimal discretization policy is found with dynamical programming.
-If there are multiple continuous variables in a Bayesian network, we apply the algorithm to one variable at a time and iterate over all continuous variables.
-While iterating, only one variable is treated as continuous and other continuous variables are discretized based on an initial discretization scheme or the discretization result from a previous iteration.
+% $I(\boldsymbol{A},\boldsymbol{B}) =  \sum_{\boldsymbol{a},\boldsymbol{b}} \hat{P}_D (\boldsymbol{a},\boldsymbol{b}) \log {{\hat{P}_D (\boldsymbol{a},\boldsymbol{b})}\over{\hat{P}_D (\boldsymbol{a}),\hat{P}_D (\boldsymbol{b})}}$
+where $I(\boldsymbol{A},\boldsymbol{B})$ is the mutual information between the discrete variables $\boldsymbol{A}$ and $\boldsymbol{B}$, $\|\boldsymbol{X}\|$ is the cardinality of discrete variable $\boldsymbol{X}$, $X^*_i$ is the discretized version of continuous variable $X_i$, and $H(p) = -p \log(p) - (1-p) \log(1-p)$.
+The optimal discretization policy can be found with dynamical programming.
+For Bayesian networks with multiple continuous variables, the algorithm is applied to one variable at a time iteratively over all continuous variables.
+While iterating, only one variable is treated as continuous and other continuous variables are discretized based on an initial discretization policy or the discretization result from a previous iteration.
 
@@
 Bayesian network structure learning can be extended to distributions including continuous variables by alternating between traditional discrete structure learning and optimal discretization.
-Starting with some preliminary discretization scheme, one applys a structure learning algorithm to identify the locally optimal graph structure.
-The discretization scheme is refined based on the learned network.
+Starting with some preliminary discretization policy, one applys a structure learning algorithm to identify the locally optimal graph structure.
+The discretization policy is refined based on the learned network.
 The cycle is continued until convergence.
+
+% The discretization technique proposed by \citet{Friedman_1996} is the most well-known of these methods.
+It is based on the minimum description length principle (MDL): the optimal discretization policy minimizes the description length of the Bayesian network and discretization policy.
+The MDL algorithm has a $\bigo\paren{N^3 + \paren{n_c {v_\text{max}}^{(n_c^p)_\text{max}} + {v_\text{max}}^{n_p}} \cdot N^2}$ runtime on Bayesian networks with a single continuous variable and multiple discrete variables, where $N$ is the number of data samples from the joint distribution, $n_p$ and $n_c$ are the numbers of parent and children variables for the continuous variable, $v_\text{max}$ is the largest cardinality over all variables in the Markov blanket, and  ${(n_c^p)_\text{max}}$ is the largest number of parent variables of the continuous variable's children.
+The MDL method iterates over all continuous variables until convergence in the case of multiple continuous variables, converging in a few cycles according to our tests of real-world data.
+Unfortunately, MDL tends to produce discrete variables with low cardinality~\todo{[cite]}.
 
@@
 
-The MODL method uses dynamic programming to find the optimal discretization scheme, and has a $\bigo\paren{N^3 + \|\text{Class}\| \cdot N^2}$ runtime, where $N$ is the of number of data instances.
+The MODL method uses dynamic programming to find the optimal discretization policy, and has a $\bigo\paren{N^3 + \|\text{Class}\| \cdot N^2}$ runtime, where $N$ is the of number of data instances.
 \cite{Lustgarten_2011} suggest several formulations for the prior term $P(\text{Model})$\tim{Did I state this correctly?}.
@@
 Variables are sampled in topological order such that parental instantiations are always known~\citep[see][chap.~22]{algo_2009}.
-Furthermore, the parent\rightarrow child sampling order can be reversed if the marginal probability of child variable $P(X_i)$ is known.
+Furthermore, the parent\rightarrow child sampling order can be reversed if the marginal probability of child variable $P(X_i)$ is known.\tim{Do we use this later?}
 By Bayes' rule,
@@
 
-Four prior principles adapted from the MODL approach define $P(M)$ and $P(D \mid M)$:
+We have the following four priors for the discretization model $M$ that enable us to evaluate $P(M)$ and $P(D \mid M)$:\\
 \begin{enumerate}
-\item A discretization edge at $(x_i + x_{i+1})/2$ has probability
+\item For a discretization edge locating at $(x_i + x_{i+1})/2$ has probability
 \begin{equation}
@@
 \end{equation}
-where $L$ is the largest cardinality of discrete variables in $X$'s Markov blanket.
+where $L$ is the largest cardinality number of discrete variables in $X$'s Markov blanket.
 \item For a given interval of $M$, every distribution of $\Pi_X$ is equiprobable.
-\item For each pair $(C_i,\boldsymbol{S_i})$ and a given interval of $M$, every distribution over $C_i$ given $\boldsymbol{S_i}$ is equiprobable.
-\item The distributions over each $C_i$ and $\Pi_X$ in each interval of $M$ given each instantiation of $\boldsymbol{S_i}$ are independent.
+\item For each pair of $(C_i,\boldsymbol{S_i})$ and a given interval of $M$, every distribution of $C_i$ with a value of $\boldsymbol{S_i}$ is equiprobable.
+\item The distributions of each $C_i$ and $\Pi_X$ in each interval of $M$ with each value of $\boldsymbol{S_i}$ are independent from each other.
 \end{enumerate}
 
-The prior term $P(M)$ has the form:
-
+Owing to these priors, we are able to evaluate $P(M)$ and $P(D \mid M)$. For the former, we have
 \begin{equation}
-\label{eq:p_M}
-P(M) = \prod_{i=1}^k \brock{ [1 - {\exp(- L \cdot {{x_{s_i+1} - x_{s_i}}\over{x_N - x_1}})}] \cdot \exp(L \cdot {{x_{s_{i}} - x_{s_{i-1} + 1}}\over{x_N - x_1}}) }\text{,}
+P(M) = \prod_{i=1}^k \{ [1 - {\exp(- L \cdot {{x_{s_i+1} - x_{s_i}}\over{x_N - x_1}})}] \cdot \exp(L \cdot {{x_{s_{i}} - x_{s_{i-1} + 1}}\over{x_N - x_1}}) \},
 \end{equation}
-
-\noindent
-where $s_i = \sum_{j=1}^k n_j$, $s_k = N$, and $s_0 = 0$. Before evaluating $P(D \mid M)$, note that
-
+where $s_i = \sum_{j=1}^k n_j$ and $s_k = N$, $s_0 = 0$. Before evaluating $P(D \mid M)$, notice that
 \begin{equation}
-\label{eq:p_D_given_M}
-P(D \mid M) \propto P(D_{\Pi_x} \mid M) \cdot \prod_{i = 1}^{n_c} P(D_{C_i} \mid M, D_{\boldsymbol{S_i}})\text{.}
+P(D \mid M) \propto P(D_{\Pi_x} \mid M) \cdot \prod_{i = 1}^{n_c} P(D_{C_i} \mid M, D_{\boldsymbol{S_i}}).
 \end{equation}
-
-The graph structure allows us to only consider the interations between $X$ and the other variables in its Markov blanket, thus allowing for convenient factorization.
-For example, $P(D \mid M)$ for Figure \ref{fig:one} factors according to
+The graph structure allows us to only consider the interations between $X$ and other variables in its Markov blanket and thus leads to the factorization.
+For example, in Figure 1., the corresponding $P(D \mid M)$ is factorized as
 \begin{equation}
-P(D_{ P_1,P_2,P_3 } \mid M) \cdot P( D_{ C_1 } \mid M,D_{\boldsymbol{S_1}}) \cdot P(D_{C_2} \mid M,D_{ S_2  })\text{.}
+P(D_{ P_1,P_2,P_3 } \mid M) \cdot P( D_{ C_1 } \mid M,D_{\boldsymbol{S_1}}) \cdot P(D_{C_2} \mid M,D_{ S_2  }).
 \end{equation}
@@
   \caption{Factorization of $P(D \mid M)$}
-  \label{fig:one}
 \end{figure}
 
-The factorization arises from the conditional independencies in the Bayesian network.
-Given a distribution over $X$ and a specific instance $x$, one can directly determine the conditional distribution over the parents $\Pi_x$.
-The parents given $x$ are dependent, in general one cannot further factorize $P(D_{\Pi_x} \mid M)$.
-Similarly, a distribution over $C_i$ is fully defined given $x$ and $\boldsymbol{S_i}$.
-The children are independent given $X$, and thus factorize according to $\prod_{i = 1}^{n_c} P(D_{C_i} \mid M, D_{\boldsymbol{S_i}})$.
+The concept behind the factorization is similar to sampling in a Bayesian network.
+Once we have the distribution of $X$ and sample $X$ for it, then we can further sample $\Pi_x$.
+Since the samples of $P_1,P_2,\ldots,P_{n_p}$ given a value of $X$ are not independent, we can not further factorize $P(D_{\Pi_x} \mid M)$ into $\prod_i P(D_{P_i} \mid M)$.
+Similarly, once we have samples of $X$ and $\boldsymbol{S_i}$, we can sample $C_i$.
+Since the sampling processes of child variables are independent from each other, we have the product $\prod_{i = 1}^{n_c} P(D_{C_i} \mid M, D_{\boldsymbol{S_i}})$.\\
 
-It is thus necessary to formulate $P(D_{\Pi_x} \mid M)$  and $P(D_{C_i} \mid M, D_{\boldsymbol{S_i}})$ based on discretization policy $M = [n_1,n_2,\ldots,n_k]$ in order to compute the likelihood term, $P(D \mid M)$.
-These components are outlined below.
-
-\subsubsection{Evaluation of $P(D_{\Pi_x} \mid M)$}
-
-Let $J_P = \prod_{i=1}^{n_p} \| P_i \|$. It follows that
-
+For the following part, we evaluate $P(D_{\Pi_x} \mid M)$  and $P(D_{C_i} \mid M, D_{\boldsymbol{S_i}})$ based on discretization policy $M = [n_1,n_2,\ldots,n_k]$ and dataset $D$.
+\subsubsection{Evaluate $P(D_{\Pi_x} \mid M)$}
+Assume that $J_P = \prod_{i=1}^{n_p} \| P_i \|$. Then we have:
 \begin{equation}
-\label{eq:likelihood_one}
 P(D_{\Pi_X} \mid M) = \prod_{i=1}^k  {{1}\over{{n_i + J_P - 1}\choose{J_P -1}}}
-{{1}\over{ {{{n}_i}!}\over{ {n^{(p)}_{i,1} !} {n^{(p)}_{i,2} !} \cdots {n^{(p)}_{i,J_P} !}}  }}\text{,}
+{{1}\over{ {{{n}_i}!}\over{ {n^{(p)}_{i,1} !} {n^{(p)}_{i,2} !} \cdots {n^{(p)}_{i,J_P} !}}  }},
 \end{equation}
-
-\noindent
-where $n^{(p)}_{i,j}$ is the number of instances in the $i$th discretized interval with the $j$th value of $\Pi_X$.
+where $n^{(p)}_{i,j}$ is the number of instances in $i$th discretized interval with $j$th value of $\Pi_X$.
 Note that $n_i = \sum_{j=1}^{\| \Pi_x \|} n^{(p)}_{i,j}$.
-The two factors on the right hand side comes from the second prior: all distributions of values of $\Pi_X$ in a given interval are equiprobable.
-According to the fourth prior, the distribution in each interval is independent, so the two factors are multiplied together.
-
-\subsubsection{Evaluation of $P(D_{C_i} \mid M, D_{\boldsymbol{S_i}})$}
-
-For each pair $(C_j, \boldsymbol{S_j})$, let $\|C_j \| = J_j$ and $\| \boldsymbol{S_j} \| = L_j = \prod_{v \in \boldsymbol{S_j}} \| v \|$. It follows that
-
+The two factors on RHS comes from the second prior: all distributions of values of $\Pi_X$ in a given interval are equiprobable.
+According to the forth prior, the distribution in each interval is independent, so we multiply all the two factors together.
+\subsubsection{Evaluate $P(D_{C_i} \mid M, D_{\boldsymbol{S_i}})$}
+Assume for each pair of $(C_j, \boldsymbol{S_j})$, we have $\|C_j \| = J_j$ and $\| \boldsymbol{S_j} \| = L_j = \prod_{v \in \boldsymbol{S_j}} \| v \|$. Therefore,
 \begin{equation}
-\label{eq:likelihood_two}
 P(D_{C_j}  \mid M, D_{S_j}) =
 \prod_{i=1}^{k} \prod_{l=1}^{L_j} {{1}\over{{n_{i,l} + J_j - 1}\choose{J_j-1}}}
-{{1}\over{ {{n_{i,l}}!}\over{ {n^{(j)}_{i,1,l} !} {n^{(j)}_{i,2,l} !} \cdots {n^{(j)}_{i,J_j,l} !}}  }}\text{,}
+{{1}\over{ {{n_{i,l}}!}\over{ {n^{(j)}_{i,1,l} !} {n^{(j)}_{i,2,l} !} \cdots {n^{(j)}_{i,J_j,l} !}}  }},
 \end{equation}
-
-\noindent
 where $n^{(j)}_{i,m,l}$ is the number of instances in $i$th interval with $m$th value of $C_j$ and $l$th value of $\boldsymbol{S_j}$, $n_{i,l} = \sum_{m=1}^{J_j} n^{(j)}_{i,m,l}$, and $n_i = \sum_{l=1}^{L_j} n_{i,l}$.
-The two factors on the right hand side come from the third prior: all distribution of values of $C_j$ in a given interval and with a given value of $S_j$ are equiprobable.
-According to the forth prior, these distributions are independent from each other, and one thus takes their product.
-If $S_j = \emptyset$, then Equation \ref{eq:likelihood_two} is equivalent to
-
+The two factors on RHS comes from the third prior: all distribution of values of $C_j$ in a given interval and with a given value of $S_j$ are equiprobable.
+According to the forth prior, these distributions are independent from each other, therefore we multiply all factors.
+If $S_j = \emptyset$, then Equation 13.
+is equivalent to
 \begin{equation}
-\label{eq:likelihood_three}
 P(D_{C_j}  \mid M) =
 \prod_{i=1}^{k}  {{1}\over{{n_{i} + J_j - 1}\choose{J_j-1}}}
-{{1}\over{ {{n_{i}}!}\over{ {n^{(j)}_{i,1,\emptyset} !} {n^{(j)}_{i,2,\emptyset} !} \cdots {n^{(j)}_{i,J_j,\emptyset} !}}  }}\text{,}
+{{1}\over{ {{n_{i}}!}\over{ {n^{(j)}_{i,1,\emptyset} !} {n^{(j)}_{i,2,\emptyset} !} \cdots {n^{(j)}_{i,J_j,\emptyset} !}}  }},
 \end{equation}
+where $n^{(j)}_{i,m,\emptyset}$ is the number of instances in $i$th interval with $m$th value of $C_j$, and $\sum_{m=1}^{J_j} n^{(j)}_{i,m,\emptyset} = n_i$. \\
 
-\noindent
-where $n^{(j)}_{i,m,\emptyset}$ is the number of instances in the $i$th interval with the $m$th value of $C_j$, and $\sum_{m=1}^{J_j} n^{(j)}_{i,m,\emptyset} = n_i$.
-
-The objective function can be formulated given equations \ref{eq:p_M}, \ref{eq:p_D_given_M},\ref{eq:likelihood_one}, and \ref{eq:likelihood_three}.
-The log-inverse of $P(M) \cdot P(D|M)$ is minimized for computational convenience:
-
+With Equation 8,9,11,12, and 13, now we are able to write down the objective function. Instead of maximizing $P(M) \cdot P(D|M)$, we minimize its log-inverse for convenience. The objective function is
 \begin{equation}
-\label{eq:opt_prob}
 \begin{aligned}
@@
 &  \sum_{j=1}^{n_c} \sum_{i=1}^{k}  \sum_{l=1}^{L_j} \left[  \log{{n_{i,l} + J_j - 1}\choose{J_j-1}} + \log \left( { {{n_{i,l}}!}\over{ {n^{(j)}_{i,1,l} !} {n^{(j)}_{i,2,l} !} \cdots {n^{(j)}_{i,J_j,l} !}} } \right) \right] + \\
-& \sum_{i=1}^k \left[  \log {{n_{i} + J_P - 1}\choose{J_P-1}} + \log \left( { {{n_i}!}\over{ {n^{(p)}_{i,1} !} {n^{(p)}_{i,2} !} \cdots {n^{(p)}_{i,J_p} !}} } \right) \right]\text{.}
+& \sum_{i=1}^k \left[  \log {{n_{i} + J_P - 1}\choose{J_P-1}} + \log \left( { {{n_i}!}\over{ {n^{(p)}_{i,1} !} {n^{(p)}_{i,2} !} \cdots {n^{(p)}_{i,J_p} !}} } \right) \right].
 \end{aligned}
 \end{equation}
+All parameters and variables in the objective function are explained in previous subsections.
+\subsection{Algorithm}
+\label{algo}
+Once the objective function is established, the next problem is how to find a discretization model that minimizes the objective function.
+Note that the objective function is cumulative on intervals.
+Therefore, if a partition of continuous variable $X$ into $k$ intervals with lengths $n_1,n_2,\ldots,n_k$ is an optimal discretization policy, then $\{ n_2, n_3,\ldots,n_k \}$ is optimal for the subproblem, i.e., the last $N - n_1$ instances of the dataset which has been sorted in ascending order of $D_X$.
+With this property, we can adapt dynamical programming to solve this optimization problem.
 
-\subsection{Algorithm}
+If there is no repeated value in $D_X$, all middle points of two consecutive values can a discretization edge.
+If there exists repeated values in $D_X$, only the middle points of two consecutive and different values can be a discretization edge.
+Assume there are $M$ unique values in $D_X$, then ${D'_X} = \{ x'_1,x'_2,\ldots,x'_M \}$ is the set of unique values of $D_X$ in ascending order.
+Since $D_X$ is also sorted, let $b = \{ b_0,b_1,b_2,\ldots,b_M \}$ be an increasing sequence of integers such that $b_0 = 0$ and $x_{b_{i-1} + 1} = x_{b_{i-1} + 2} = \ldots = x_{{b_i}} = x'_i$.
+By this definition, the allowable discretization positions are $d_i = ( x_{b_{i}} + x_{{b_i}+1})/2$ for all $i = 1,2,\ldots,M-1$.
 
-This section describes the procedure used to minimize the objective function.
-Note that the objective function is cumulative over intervals, thus, if a partition of $X$ into $k$ intervals with lengths $n_1,n_2,\ldots,n_k$ is an optimal discretization policy, then any subinterval is optimal for the corresponding subproblem.
-It follows that dynamic programming can be used to solve the optimization problem exactly.
-
-Every midpoint between two nonequal consecutive values in $D_X$ is a candidate discretization edge.
-Let ${D'_X} = \brock{x'_1,x'_2,\ldots,x'_M}$ be the set of unique values of $D_X$ sorted in ascending order, where $M$ is the number unique values in $D_X$.
-Recall that $D_X$ is also sorted.
-Let $b = \brock{b_0,b_1,b_2,\ldots,b_M}$ be an increasing sequence of integers marking the repeated value intervals in $D_X$ such that $b_0 = 0$ and $x_{b_{i-1} + 1} = x_{b_{i-1} + 2} = \ldots = x_{b_i} = x'_i$.
-By this definition, the allowable discretization positions are $d_i = \paren{x_{b_{i}} + x_{{b_i}+1}}/2$ for all $i = 1,2,\ldots,M-1$.
-
-Precomutation can be done to reduce runtime.
-Compute $h(u,v)$ for each interval $I_q$ starting from $x_{u}$ to $x_{v}$ for all $(u,v)$ satisfying $u \leq v$:
-
-\begin{small}
+Before doing the dynamical programming, in order to save runtime, we first calculate the following function $h(u,v)$ for a interval $I_q$ starting from $x_{u}$ to $x_{v}$ with all $u$,$v$ satisfying $u \leq v$:
 \begin{equation}
@@
 \end{equation}
-\end{small}
 
-The evaluation of $h(u,v)$ for all $u \leq v$ is summarized in Algorithm \ref{alg:h} in the appendix.
-The calculation has a $O(n_c  {v'_\text{max}} \cdot N^2 + {v'_\text{max}}^{n_p} \cdot N^2)$ runtime, where $n_c$ and $n_p$ are the numbers of child and parent variables respectively, and $v'_\text{max}$ is the largest cardinality of variables that directly connect to $X$.
+The evaluation of function $h(u,v)$ for all $u \leq v$ is summerized in Algorithm 4 in Appendix.
+The calculation can be done in $O(n_c  {v'_{max}} \cdot N^2 + {v'_{max}}^{n_p} \cdot N^2)$, where $n_c$ and $n_p$ are the numbers of child and parent variables, respectively, and $v'_{max}$ is the largest cardinality of variables that directly connects to $X$.
+Notice that due to repeated values in $D_X$, for some pairs of $u$ and $v$, the value of $h(u,v)$ might depend on the sorting method of $D_X$ and $D$.
+However, this does not influence the optimization result, since these pairs of $u$ and $v$ will not form valid intervals.
 
-% \tim{I think we can leave this out if it doesn't affect the algorithm results, and people will always sort in ascending order}
-% Due to repeated values in $D_X$, for some pairs $(u,v)$, $h(u,v)$ may depend on the sorting method of $D_X$ and $D$.
-% However, this does not influence the optimization result, since these pairs of $u$ and $v$ will not form valid intervals.
-
-Now we are able to solve the optimization problem over Equation \ref{eq:opt_prob}.
-The dynamic programming procedure is shown in Algorithm \ref{alg:disc_one}.
-It takes two inputs: $D$, the joint samples over all variables sorted in ascending order according to $D_X$, and $G$, the network structure.
-The runtime of Algorithm \ref{alg:disc_one} is also $O(n_c  {v'_\text{max}} \cdot N^2 + {v'_\text{max}}^{n_p} \cdot N^2)$, because the runtime of the dynamic programming procedure is less than the runtime for computing $h(u,v)$.
-Algorithm \ref{alg:disc_one} is guaranteed to be optimal.
-For faster methods with suboptimal results please refer to \citep{Boulle_2006}.
+Now we are able to solve the optimization problem with the objective function in Equation 14.
+The dynamical programming procedure is shown in Algorithm 1.
+We have three inputs: $D_X$, the data of continuous variable $X$ in the ascending order, $D$, the data of other variables and sorted according to $D_X$, and $G$, the network structure.
+The runtime of Algorithm 1 is also $O(n_c  {v'_{max}} \cdot N^2 + {v'_{max}}^{n_p} \cdot N^2)$, since the dynamical programming procedure does not increase the time complexity beyond the calculation of $h(u,v)$.
+There are other methods that lead to suboptimal results but runs faster than dynamical programming method.
+Please refer to \citep{Boulle_2006}.
 
 \begin{algorithm}
-\caption{Discretization of one continuous variable in a Bayesian network}
-\label{alg:disc_one}
+\caption{ Discretization of one continuous variable}\label{euclid}
 \begin{algorithmic}[5]
-\Function{Discretize}{$D$, $G$}
+\Function{Discretize}{$D_X$, $D$, $G$}
 \State
 \State $N \leftarrow$ the number of instances
-\State $N' \leftarrow$ the number of unique values in $D_X$
-\State $H \leftarrow$ an $N \times N$ matrix such that $H[u,v] = h(u,v)$ per Algorithm \ref{alg:h} in the appendix
-\State $b \leftarrow$ the increasing sequence of $M$ integers as previously defined
-\State $L \leftarrow$ the largest cardinality over all discrete variables in the Markov blanket of $X$
-\State $S[u] \leftarrow$ the optimal objective value of subproblems with instances from $1$ to $u$
-\State $M[u] \leftarrow$ the optimal discretization for subproblems with instances from $1$ to $u$
+\State $N' \leftarrow$ the number of non-repeated values of $D_X$
+\State $H \leftarrow$ an $N \times N$ matrix such that $H[u,v] = h(u,v)$ as Algorithm 4 in Appendix
+\State $b \leftarrow$ the increasing sequence of $M$ integers defined in the previous discussion
+\State $L \leftarrow$ the largest cardinality over all discrete variables in the Markov blanket
+\State $S[u] \leftarrow$ the optimal objective value of a subproblem with instances from $1$ to $u$
+\State $M[u] \leftarrow$ the optimal discretization of a subproblem with instances from $1$ to $u$
 \State $W[u]  \leftarrow - \log(1 - {\exp(- L \cdot{ {{x_{b(u)+1} - x_{b(u)}}\over{x_N - x_1}})}})$ for $u = 1,2, \ldots,N'-1$ and $L(N') \leftarrow 0$
@@
 \If {$v = 1$}
-\State $S[v] \leftarrow g \left(1,b[v] \right) + L[v]$
-\State $M[v] \leftarrow \{ ({x_{b[v]} + x_{b[v]+1}}) / 2\}$
+\State $S[v] = g \left(1,b[v] \right) + L[v]$
+\State $M[v] = \{ ({x_{b[v]} + x_{b[v]+1}}) / 2\}$
 \Else
@@
 \subsection{Approximation}
-
-Algorithm \ref{alg:disc_one} has an exponential $\bigo\paren{\paren{v'_\text{max}}^{n_p} \cdot N^2}$ runtime.
-This exponential runtime is severely limiting for networks with a large number of discretization edges.
-This section introduces an approximation to the objective function that significantly reduces the runtime and still preserves the quality of discretization.
-The approximation replaces the dominator of the last factor in Equation \ref{eq:likelihood_one} with
-
+\label{approx}
+Notice that Algorithm1 leads to the non-polynomial runtime $O({v'_{max}}^{n_p} \cdot N^2)$ in the discretization process.
+Therefore, we have an empirical approximation to the objective function that can reduce runtime and still preserve the quality of discretization.
+The approximation is as follows: for the dominator of the last factor in Equation 11, we have
 \begin{equation}
-{\frac{{n_i}!}{ {n^{(p)}_{i,1} !} {n^{(p)}_{i,2} !} \cdots {n^{(p)}_{i,J_P} !}}} \approx \prod_{r=1}^{n_p} { {{{n}_i}!}\over{ {n^{(p_r)}_{i,1} !} {n^{(p_r)}_{i,2} !} \cdots {n^{(p_r)}_{i,J_{p_r}} !}}}\text{,}
+{{{{n}_i}!}\over{ {{n^{(p)}}_{i,1} !} {n^{(p)}_{i,2} !} \cdots {n^{(p)}_{i,J_P} !}}} \approx \prod_{r=1}^{n_p} { {{{n}_i}!}\over{ {n^{(p_r)}_{i,1} !} {n^{(p_r)}_{i,2} !} \cdots {n^{(p_r)}_{i,J_{p_r}} !}}},
 \end{equation}
-
-\noindent
-where $J_{p_r} = \| P_r\|$ and ${n^{(p_r)}_{i,j} !}$ is the number of instances in the $i$th interval with the $j$th value of $P_r$.
-The approximated objective function is
-
+where $J_{p_r} = \| P_r\|$ and ${n^{(p_r)}_{i,j} !}$ is the number of instances in $i$th interval with $j$th value of $P_r$. Applying this approximation, the approximated objective function is
 \begin{equation}
 \begin{aligned}
-\label{eq:opt_prob_approx}
 & \sum_{i=1}^{k-1} - \log(1 - {\exp(- L \cdot {{x_{s_i+1} - x_{s_i}}\over{x_N - x_1}})}) +  \sum_{i=1}^{k} L \cdot {{x_{s_{i}} - x_{s_{i-1} + 1}}\over{x_N - x_1}} +\\
 &  \sum_{j=1}^{n_c} \sum_{i=1}^{k}  \sum_{l=1}^{L_j} \left[  \log{{n_{i,l} + J_j - 1}\choose{J_j-1}} + \log \left( { {{n_{i,l}}!}\over{ {n^{(j)}_{i,1,l} !} {n^{(j)}_{i,2,l} !} \cdots {n^{(j)}_{i,J_j,l} !}} } \right) \right] + \\
-& \sum_{i=1}^k \left[  \log {{n_{i} + J_P - 1}\choose{J_P-1}} + \sum_{q=1}^{n_p} \log \left( { {{{n}_i}!}\over{ {n^{(p_q)}_{i,1} !} {n^{(p_q)}_{i,2} !} \cdots {n^{(p_q)}_{i,J_{p_q}} !}}} \right) \right]\text{.}
+& \sum_{i=1}^k \left[  \log {{n_{i} + J_P - 1}\choose{J_P-1}} + \sum_{q=1}^{n_p} \log \left( { {{{n}_i}!}\over{ {n^{(p_q)}_{i,1} !} {n^{(p_q)}_{i,2} !} \cdots {n^{(p_q)}_{i,J_{p_q}} !}}} \right) \right].
 \end{aligned}
@@
 
-The approximation reduces the runtime of Algorithm \ref{alg:disc_one} to a polynomial, $\bigo\paren{ {v'_\text{max}} \cdot (n_c + n_p) \cdot N^2}$.
-\tim{`The rigorous proof of the approximation have not been proposed.' Do you mean that we are not proving that the approximation always holds, or that the algorithm conserves optimality, or something else?}
-It will be shown in Section \ref{sec:experiments} that the approximation is more sensitive to the distribution over other variables and is biased towards slightly higher interval counts.
+As we will see in Section \ref{sec:experiments}, the approximated algorithm is more sensitive to the distribution of other variables' values and usually leads to slightly more discretization edges.
+With the approximation, we can reduce runtime of Algorithm 1 from $O(n_c  {v'_{max}} \cdot N^2 + {v'_{max}}^{n_p} \cdot N^2)$ to $O( {v'_{max}} (n_c + n_p) \cdot N^2)$.
+The rigorous proof of the approximation have not been proposed.
 
-With the approximated objective function, Equation \ref{eq:opt_prob_approx}, we now have a more clear way to see that how child variables and parent variables contribute to the objective function differently.
+With the approximated objective function, Equation 17, we now have a more clear way to see that how child variables and parent variables contribute to the objective function differently.
 For example, in the left graph of Figure 2, the corresponding sqaure brackets in Equation 17 are
@@
 \begin{algorithm}
-\caption{ Calculation of function $h(u,v)$ for all $u \leq v$}
-\label{alg:h}
+\caption{ Calculation of function $h(u,v)$ for all $u \leq v$}\label{euclid}
 \begin{algorithmic}[1]

### 2015-11-13 BN_discretizer_paper.tex
cleaned up intro, removed tim comments, fixed notation section, replaced double verts with single

@@
 One successful example is belief propagation in Gaussian graphical models \citep{Weiss_2011}.
-For other particle shapes \citep{Ihler_2009} and non-linear functions~\todo{[cite]}, these redesigned algorithms are computationally expensive and do not perform well.
-\tim{Not sure what `particle shapes' are. Do you mean other parametric distributions?}
+For other parametric distributions \citep{Ihler_2009} and non-linear functions~\todo{[cite]}, these redesigned algorithms are computationally expensive and do not perform well.
 
@@
 The proposed method optimizes the discretization policy relative to the network and takes parents, children, and spouse variables into account.
-The optimal single-variable discretization method is derived in Section \ref{sec:single_var}, and a second heuristic method is proposed which reduces the exponential runtime to polynomial.
+The optimal single-variable discretization method is derived in Section \ref{sec:single_var}, and a second heuristic method is proposed which reduces the runtime from exponential to polynomial.
 Section \ref{sec:multi_var} covers Bayesian networks with multiple continuous variables and discretization while simultaneously learning network structure.
-The paper concludes with a comparison against existing minimum-description length \citep{Friedman_1996} and MODL \citet{Boulle_2006} methods on real-world datasets in Section \ref{sec:experiments}.
+The paper concludes with a comparison against the existing minimum-description length \citep{Friedman_1996} method on real-world datasets in Section \ref{sec:experiments}.
 
@@
 \label{sec:related_work}
-This section reviews the minimum description length (MDL) principle discretization \citep{Friedman_1996} and MODL discretization \citep{Boulle_2006}.
+This section reviews the minimum description length (MDL) principle discretization \citep{Friedman_1996} and MODL discretization \citep{Boulle_2006} methods.
 The former is the predominant discretization method for continuous variables in Bayesian networks, and is compared to our proposed method in Section \ref{sec:experiments}.
@@
 
-\begin{small}
+% \begin{small}
 \begin{equation}
 \begin{aligned}
-\frac{1}{2} \log(N) \left\lbrace  \lVert \Pi_{X_i} \rVert (\lVert X^*_i \rVert - 1) +
- {\sum_{j,X_i \in \Pi_{X_i}}} \lVert \Pi_{X^*_j} \rVert (\lVert X_j \rVert - 1) \right\rbrace + \log(\lVert {X^*_i} \rVert) \\
- + (N_i-1) H \left( {{\|X^*_i\| - 1}\over{N_i -1}}  \right) -N \cdot \left[ I(X^*_i,\Pi_{X_i}) + {\sum_{j,X_i \in \Pi_{X_i}}} I(X_j, \Pi_{X^*_j}) \right],
+\frac{1}{2} \log(N) \left\lbrace  \lvert \Pi_{X_i} \rvert (\lvert X^*_i \rvert - 1) +
+ {\sum_{j,X_i \in \Pi_{X_i}}} \lvert \Pi_{X^*_j} \rvert (\lvert X_j \rvert - 1) \right\rbrace + \log(\lvert {X^*_i} \rvert) \\
+ + (N_i-1) H \left( {{|X^*_i| - 1}\over{N_i -1}}  \right) -N \cdot \left[ I(X^*_i,\Pi_{X_i}) + {\sum_{j,X_i \in \Pi_{X_i}}} I(X_j, \Pi_{X^*_j}) \right],
 \end{aligned}
 \end{equation}
-\end{small}
+% \end{small}
 
@@
 % $I(\boldsymbol{A},\boldsymbol{B}) =  \sum_{\boldsymbol{a},\boldsymbol{b}} \hat{P}_D (\boldsymbol{a},\boldsymbol{b}) \log {{\hat{P}_D (\boldsymbol{a},\boldsymbol{b})}\over{\hat{P}_D (\boldsymbol{a}),\hat{P}_D (\boldsymbol{b})}}$
-where $I(\boldsymbol{A},\boldsymbol{B})$ is the mutual information between the discrete variables $\boldsymbol{A}$ and $\boldsymbol{B}$, $\|\boldsymbol{X}\|$ is the cardinality of discrete variable $\boldsymbol{X}$, $X^*_i$ is the discretized version of continuous variable $X_i$, and $H(p) = -p \log(p) - (1-p) \log(1-p)$.
+where $I(\boldsymbol{A},\boldsymbol{B})$ is the mutual information between the discrete variables $\boldsymbol{A}$ and $\boldsymbol{B}$, ${H(p) = -p \log(p) - (1-p) \log(1-p)}$, $|\boldsymbol{X}|$ is the cardinality of discrete variable $\boldsymbol{X}$, and $X^*_i$ is the discretized version of the $i$th sample of continuous variable $X$.
 The optimal discretization policy can be found with dynamical programming.
@@
 \subsection{MODL Discretization}
-\tim{Does MODL stand for something?}
 MODL discretization \citep{Boulle_2006} is a Bayesian method for discretizing a continuous feature according to a class variable.
@@
 \noindent
-where $P(\textit{Model})$ is a prior over models and $P(\textit{Data} \mid \textit{Model})$ is the data likelihood.
-The data likelihood usually increases with the number of discretization intervals, as more intervals allow for more detailed representations.
-The prior usually decreases as the number of discretization intervals increases to favor simpler models and penalize overfitting.
-Thus, maximizing $P(\textit{Model}) \cdot P(\textit{Data} \mid \textit{Model})$ requires a trade-off when determining the number of discretization intervals.
+where $P(\textit{Model})$ is a prior over models and ${P(\textit{Data} \mid \textit{Model})}$ is the data likelihood.
+The data likelihood usually increases with the number of discretization intervals, as more intervals allow for richer representations.
+The prior decreases as the number of discretization intervals increases to favor simpler models and prevent overfitting.
+Maximizing ${P(\textit{Model}) \cdot P(\textit{Data} \mid \textit{Model})}$ requires a trade-off when determining the number of discretization intervals.
 
-The MODL method uses dynamic programming to find the optimal discretization policy, and has a $\bigo\paren{N^3 + \|\text{Class}\| \cdot N^2}$ runtime, where $N$ is the of number of data instances.
-\cite{Lustgarten_2011} suggest several formulations for the prior term $P(\text{Model})$\tim{Did I state this correctly?}.
-If the prior is chosen to reflect uniform prior probability over discretizations the runtime can be reduced to $\bigo\paren{\|\text{Class}\| \cdot N^2}$.\tim{Is a sacrifice made?
-It is sub-optimal, right?}
+The MODL method uses dynamic programming to find the optimal discretization policy, and has a $\bigo\paren{N^3 + |\text{Class}| \cdot N^2}$ runtime, where $N$ is the of number of data instances.
+\cite{Lustgarten_2011} suggest several formulations for the prior term $P(\text{Model})$.
+Under a uniform prior probability over discretizations the runtime can be reduced to $\bigo\paren{|\text{Class}| \cdot N^2}$ without sacrificing optimality.
 
@@
 A Bayesian network $B$ is defined by a pair $(G,\Theta)$, where $G = (X,E)$ is a directed acyclic graph whose nodes correspond to a set of random variables $X = \brock{X_1, X_2, \cdots, X_n}$, and whose edges $E$ represent probabilistic dependencies among nodes.
-The graph structure $G$ encodes the Markov property: each node $X_i$ is independent of its non-descendants given its parents $\Pi{X_i}$ in $G$.
+The graph structure $G$ encodes the Markov property: each node $X_i$ is independent of its non-descendants given its parents $\Pi_{X_i}$ in $G$.
 The conditional relations are parameterized by the elements of $\Theta$, which take the form $\theta_{x_i \mid \Pi_{x_i}} = P(x_i \mid \Pi_{x_i})$ for each possible value $x_i$ of $X_i$, and $\Pi_{x_i}$ of $\Pi_{X_i}$.
@@
 
-Samples can be drawn from the joint distribution represented by a Bayesian network by forward sampling.
+Forward sampling is used to draw samples from the joint distribution represented by a Bayesian network.
 Variables are sampled in topological order such that parental instantiations are always known~\citep[see][chap.~22]{algo_2009}.
-Furthermore, the parent\rightarrow child sampling order can be reversed if the marginal probability of child variable $P(X_i)$ is known.\tim{Do we use this later?}
+Furthermore, the parent\rightarrow child sampling order can be reversed if the marginal probability of the child variable is known.
 By Bayes' rule,
@@
 It is often necessary to infer the structure of a Bayesian network from data.
-Three common approaches to Bayesian network structure learning are constraint-based structure learning, score-based structure learning, and Bayesian model averaging \citep[see][chap.~18]{PGM_2009}.
+Three common approaches to Bayesian network structure learning are constraint-based, score-based, and Bayesian model averaging \citep[see][chap.~18]{PGM_2009}.
 This work uses the K2 structure learning algorithm \citep{K2}, one of the most successful score-based structure learning methods.
-Score-based structure learning methods over discrete variables commonly evaluate candidate structures are scored according to their likelihood, $\prod_i f(X_i, \Pi_{X_i})$, where
+Score-based structure learning methods over discrete variables commonly evaluate candidate structures according to their likelihood, $\prod_i f(X_i, \Pi_{X_i})$, where
 
 \begin{align}
-f(X_i, \Pi_{X_i}) = \prod_{j=1}^{\|\Pi_{X_i}\|} {{(\|X_i\|-1)!}\over{(N_{ij} + \|X_i\|-1)!}} \prod_{k=1}^{\|X_i\|} \alpha_{ijk}!\text{.}
+f(X_i, \Pi_{X_i}) = \prod_{j=1}^{|\Pi_{X_i}|} {{(|X_i|-1)!}\over{(N_{ij} + |X_i|-1)!}} \prod_{k=1}^{|X_i|} \alpha_{ijk}!\text{,}
 \end{align}
@@
 \noindent
-$\|X_i\|$ is the cardinality of $X_i$, $\|\Pi_{X_i}\|$ is number of possible instantiations of the parent variables of $X_i$, $\alpha_{ijk}$ is the number of instances of the $k$th value of $X_i$ and the $j$th parental instantiation, and $N_{ij} = \sum_{k=1}^{|X_i|} \alpha_{ijk}$.\tim{Mykel uses $\alpha_{ij0}$}
+where $|X_i|$ is the cardinality of $X_i$, $|\Pi_{X_i}|$ is number of possible instantiations of the parent variables of $X_i$, $\alpha_{ijk}$ is the number of instances of the $k$th value of $X_i$ with the $j$th parental instantiation, and $N_{ij} = \sum_{k=1}^{|X_i|} \alpha_{ijk}$.
 The optimal structure is the most probably structure given the data.
-The space of acyclic graphcs is superexponential in the number of nodes \citep{PGM_2009} so it is common to rely on heuristic search strategies.
+The space of acyclic graphcs is superexponential in the number of nodes so it is common to rely on heuristic search strategies \citep{PGM_2009}.
 
@@
 A fixed ordering ensures acyclicity but does not guarantee a globally optimal network structure.
-K2 is typically run multiple times with random topological orderings and the network with the highest likelihood is retained.
+K2 is typically run multiple times with random variable orderings and the network with the highest likelihood is retained.
 
@@
 The policy discretizes the continuous variable $C$ into $k$ intervals.
-Furthermore, we restrict the discretization edges $t_\cdot$ to midpoints between two sorted instances of $C$.
-An integer representation of $M_C$ can be obtained by sorting the samples of $C$ in an increasing order, $\curly{c_1,c_2,\ldots,c_N}$, and if $t_i = (c_{s_{i}} + c_{s_{i}+1})/2$ for $i=1,2,\ldots,k$, then $M_C = \anglebrackets{t_1,t_2, \ldots, t_{k-1}} \equiv \brock{n_1,n_2,..n_k}$, where $n_1 = s_1$ and $n_i = s_{i} - s_{i-1}$ for all $i = 2,\ldots,k$.
+The discretization edges $t_\cdot$ are restricted to the midpoints between two sorted instances of $C$.
+An integer representation of $M_C$ can be obtained by sorting the samples of $C$ in an increasing order, $\curly{c_1,c_2,\ldots,c_N}$, and if $t_i = (c_{s_{i}} + c_{s_{i}+1})/2$ for $i=1,2,\ldots,k$, then $M_C = \anglebrackets{t_1,t_2, \ldots, t_{k-1}} \equiv \brock{n_1,n_2,..n_k}$, where $n_1 = s_1$ and $n_i = s_{i} - s_{i-1}$.
 
@@
 
-This section covers discretization of a single continuous variable in a Bayesian network where all other variables are discrete.
-Before we formulate the objective function, we introduce some notations that will make the following calculation easier.
+This section covers discretization of a single continuous variable $X$ in a Bayesian network where all other variables are discrete.
+Let $n_p$ and $n_c$ respectively refer to the number of parents and number of children of $X$.
+Each child $C_i$ of $X$ may possess other parents, referred to as spouses of $X$.
+The set of spouses of $X$ is denoted $\boldsymbol{S_i}$.
 
-\subsection{Notations}
-
-\tim{We should move the notation section to preliminaries}
-
-\tim{Earlier the continuous variable was denoted $C$. Now it is $X$. Slightly confusing with $c$ also meaning child.}
-
-Consider continuous variable $X$.
-It has $n_p$ parents, $\Pi_X = \{ P_1, P_2, P_3,\ldots,P_{n_p}\}$ and $n_c$ children, $\{ C_1, C_2,\ldots,C_{n_c}\}$.
-Each child $C_i$ of $X$ may possess other parents, our spouses of $X$, whose set is denoted $\boldsymbol{S_i}$.
-
-Let $D$ be a dataset of $N$ joint instances from which discretization will be learned, sorted in ascending order according to $X$.
-Let $D_{\boldsymbol{Y}}$ will refer to the data instances associated with variables $\boldsymbol{Y}$.
-Thus $D_X = \{ x_1,x_2,x_3,\ldots,x_N \}$.
+Let $D$ be a dataset of $N$ samples from which the discretization will be learned, sorted in ascending order according to $X$.
+Let $D_{\boldsymbol{Y}}$ will refer to the data instances associated with variables $\boldsymbol{Y}$, thus $D_X = \{ x_1,x_2,x_3,\ldots,x_N \}$.
 In order to facilitate understanding, we temporarily assume all values in $D_X$ are unique, that is, $x_1 < x_2 < \ldots < x_N$.
 It follows that a discretization policy $M$ on $X$ can be written as $M_X = \brock{n_1,n_2,\ldots,n_k}$, where $k$, $n_1$, $n_2$, $\ldots,n_k$ are positive integers satisfying $N = \sum_{i=1}^k n_i$.
-The optimal discretization policy maximizes $P(M)\cdot P(D\mid M)$.
+An optimal discretization policy maximizes $P(M)\cdot P(D\mid M)$ for some prior $P(M)$ and likelihood $P(D\mid M)$.
 
@@
 \subsubsection{Evaluate $P(D_{\Pi_x} \mid M)$}
-Assume that $J_P = \prod_{i=1}^{n_p} \| P_i \|$. Then we have:
+Assume that $J_P = \prod_{i=1}^{n_p} | P_i |$. Then we have:
 \begin{equation}
@@
 where $n^{(p)}_{i,j}$ is the number of instances in $i$th discretized interval with $j$th value of $\Pi_X$.
-Note that $n_i = \sum_{j=1}^{\| \Pi_x \|} n^{(p)}_{i,j}$.
+Note that $n_i = \sum_{j=1}^{| \Pi_x |} n^{(p)}_{i,j}$.
 The two factors on RHS comes from the second prior: all distributions of values of $\Pi_X$ in a given interval are equiprobable.
@@
 \subsubsection{Evaluate $P(D_{C_i} \mid M, D_{\boldsymbol{S_i}})$}
-Assume for each pair of $(C_j, \boldsymbol{S_j})$, we have $\|C_j \| = J_j$ and $\| \boldsymbol{S_j} \| = L_j = \prod_{v \in \boldsymbol{S_j}} \| v \|$. Therefore,
+Assume for each pair of $(C_j, \boldsymbol{S_j})$, we have $|C_j | = J_j$ and $| \boldsymbol{S_j} | = L_j = \prod_{v \in \boldsymbol{S_j}} | v |$. Therefore,
 \begin{equation}
@@
 The evaluation of function $h(u,v)$ for all $u \leq v$ is summerized in Algorithm 4 in Appendix.
-The calculation can be done in $O(n_c  {v'_{max}} \cdot N^2 + {v'_{max}}^{n_p} \cdot N^2)$, where $n_c$ and $n_p$ are the numbers of child and parent variables, respectively, and $v'_{max}$ is the largest cardinality of variables that directly connects to $X$.
+The calculation can be done in $\bigo\paren{n_c  {v'_\text{max}} \cdot N^2 + {v'_\text{max}}^{n_p} \cdot N^2}$, where $n_c$ and $n_p$ are the numbers of child and parent variables, respectively, and $v'_\text{max}$ is the largest cardinality of variables that directly connects to $X$.
 Notice that due to repeated values in $D_X$, for some pairs of $u$ and $v$, the value of $h(u,v)$ might depend on the sorting method of $D_X$ and $D$.
@@
 We have three inputs: $D_X$, the data of continuous variable $X$ in the ascending order, $D$, the data of other variables and sorted according to $D_X$, and $G$, the network structure.
-The runtime of Algorithm 1 is also $O(n_c  {v'_{max}} \cdot N^2 + {v'_{max}}^{n_p} \cdot N^2)$, since the dynamical programming procedure does not increase the time complexity beyond the calculation of $h(u,v)$.
+The runtime of Algorithm 1 is also $\bigo\paren{n_c  {v'_\text{max}} \cdot N^2 + {v'_\text{max}}^{n_p} \cdot N^2}$, since the dynamical programming procedure does not increase the time complexity beyond the calculation of $h(u,v)$.
 There are other methods that lead to suboptimal results but runs faster than dynamical programming method.
@@
 \label{approx}
-Notice that Algorithm1 leads to the non-polynomial runtime $O({v'_{max}}^{n_p} \cdot N^2)$ in the discretization process.
+Notice that Algorithm1 leads to the non-polynomial runtime $\bigo\paren{{v'_\text{max}}^{n_p} \cdot N^2}$ in the discretization process.
 Therefore, we have an empirical approximation to the objective function that can reduce runtime and still preserve the quality of discretization.
@@
 \end{equation}
-where $J_{p_r} = \| P_r\|$ and ${n^{(p_r)}_{i,j} !}$ is the number of instances in $i$th interval with $j$th value of $P_r$. Applying this approximation, the approximated objective function is
+where $J_{p_r} = | P_r|$ and ${n^{(p_r)}_{i,j} !}$ is the number of instances in $i$th interval with $j$th value of $P_r$. Applying this approximation, the approximated objective function is
 \begin{equation}
@@
 As we will see in Section \ref{sec:experiments}, the approximated algorithm is more sensitive to the distribution of other variables' values and usually leads to slightly more discretization edges.
-With the approximation, we can reduce runtime of Algorithm 1 from $O(n_c  {v'_{max}} \cdot N^2 + {v'_{max}}^{n_p} \cdot N^2)$ to $O( {v'_{max}} (n_c + n_p) \cdot N^2)$.
+With the approximation, we can reduce runtime of Algorithm 1 from $\bigo\paren{n_c  {v'_\text{max}} \cdot N^2 + {v'_\text{max}}^{n_p} \cdot N^2}$ to $\bigo\paren{v'_\text{max} (n_c + n_p) \cdot N^2}$.
 The rigorous proof of the approximation have not been proposed.
@@
 \State $D^* \leftarrow $ the discretized data for all variables, where $D^*_i \leftarrow D''_i$ if $i \notin C$
-\State $k \leftarrow median\{ \|v\|, v\notin C\}$
+\State $k \leftarrow median\{ |v|, v\notin C\}$
 \State
@@
 \State {$cycle  \leftarrow cycle  + 1$}
-\For {$j = 1$ to $\|C\|$}
+\For {$j = 1$ to $|C|$}
 \State $D^*_{\backslash C(j)} \leftarrow D^*$ without $D^*_{C(j)}$.
@@
 \State $n \leftarrow$ the number of variables in Bayesian network
-\State $k \leftarrow median\{ \|v\|, v\notin C\}$
+\State $k \leftarrow median\{ |v|, v\notin C\}$
 \State $M[i] \leftarrow$ the discretization policy of $i$th variable
@@
 \State OKToProceed $\leftarrow$ \textbf{true}
-\While OKToProceed \textbf{and} $\|\Pi_{X^*_i}\| < u_{parent}$
+\While OKToProceed \textbf{and} $|\Pi_{X^*_i}| < u_{parent}$
 \State $Y \leftarrow$ an element from the set $order[1:i] \backslash \Pi_X$
@@
 \State Initialize $H$ as an $N \times N$ matrix that all elements are 0.
-\State $count_p$ is an $N \times N \times \|\Pi_X\|$ matrix such that $count_p [u,v,w]$ is the number of instances from $x_u$ to $x_v$ with $w$th value of $\Pi_X$.
-This matrix can be calculated in $O(\|\Pi_X\| \cdot N^2)$
+\State $count_p$ is an $N \times N \times |\Pi_X|$ matrix such that $count_p [u,v,w]$ is the number of instances from $x_u$ to $x_v$ with $w$th value of $\Pi_X$.
+This matrix can be calculated in $\bigo\paren{|\Pi_X| \cdot N^2}$
 \For {$u = 1$ to $N$}
@@
 \State $H(u,v) \leftarrow H(u,v) + \log((v-u + J_p)!) - \log((J_p -1)!)$
-\For {$w = 1$ to $\|\Pi_X\|$}
+\For {$w = 1$ to $|\Pi_X|$}
 \State $H(u,v) \leftarrow H(u,v) - \log( count_p(u,v,w)!)$

### 2015-11-13 BN_discretizer_paper.tex
misc

@@
 
-We have the following four priors for the discretization model $M$ that enable us to evaluate $P(M)$ and $P(D \mid M)$:\\
+The following four principles for the optimal discretization policy, modivated by MODL, enable the formulation of $P(M)$ and $P(D \mid M)$:
 \begin{enumerate}
-\item For a discretization edge locating at $(x_i + x_{i+1})/2$ has probability
+\item A discretization edge located at $(x_i + x_{i+1})/2$ has probability
 \begin{equation}
@@
 \end{equation}
-where $L$ is the largest cardinality number of discrete variables in $X$'s Markov blanket.
+where $L$ is the largest cardinality number of discrete variables in $X$'s Markov blanket. \tim{Where does this come from? Is there an intuitive explanation?}
 \item For a given interval of $M$, every distribution of $\Pi_X$ is equiprobable.
@@
 
-Owing to these priors, we are able to evaluate $P(M)$ and $P(D \mid M)$. For the former, we have
+From the first principle one obtains
 \begin{equation}
-P(M) = \prod_{i=1}^k \{ [1 - {\exp(- L \cdot {{x_{s_i+1} - x_{s_i}}\over{x_N - x_1}})}] \cdot \exp(L \cdot {{x_{s_{i}} - x_{s_{i-1} + 1}}\over{x_N - x_1}}) \},
+P(M) = \prod_{i=1}^k \curly{ \brock{1 - {\exp(- L \cdot {{x_{s_i+1} - x_{s_i}}\over{x_N - x_1}})}} \cdot \exp\paren{L \cdot {{x_{s_{i}} - x_{s_{i-1} + 1}}\over{x_N - x_1}}}},
 \end{equation}
-where $s_i = \sum_{j=1}^k n_j$ and $s_k = N$, $s_0 = 0$. Before evaluating $P(D \mid M)$, notice that
+
+\noindent
+where $s_i = \sum_{j=1}^k n_j$ and $s_k = N$, $s_0 = 0$.
+The Bayesian network graph structure causes the likelihood term $P(D \mid M)$ to factorizes according to $X$'s Markov blanket:
+
 \begin{equation}
-P(D \mid M) \propto P(D_{\Pi_x} \mid M) \cdot \prod_{i = 1}^{n_c} P(D_{C_i} \mid M, D_{\boldsymbol{S_i}}).
+P\paren{D \mid M} \propto P\paren{D_{\Pi_x} \mid M} \cdot \prod_{i = 1}^{n_c} P\paren{D_{C_i} \mid M, D_{\boldsymbol{S_i}}}\text{.}
 \end{equation}
-The graph structure allows us to only consider the interations between $X$ and other variables in its Markov blanket and thus leads to the factorization.
+
 For example, in Figure 1., the corresponding $P(D \mid M)$ is factorized as
 \begin{equation}
-P(D_{ P_1,P_2,P_3 } \mid M) \cdot P( D_{ C_1 } \mid M,D_{\boldsymbol{S_1}}) \cdot P(D_{C_2} \mid M,D_{ S_2  }).
+P\paren{D_{ P_1,P_2,P_3 } \mid M} \cdot P\paren{ D_{ C_1 } \mid M,D_{\boldsymbol{S_1}}} \cdot P\paren{D_{C_2} \mid M,D_{ S_2  }}\text{.}
 \end{equation}
@@
 
-The concept behind the factorization is similar to sampling in a Bayesian network.
-Once we have the distribution of $X$ and sample $X$ for it, then we can further sample $\Pi_x$.
-Since the samples of $P_1,P_2,\ldots,P_{n_p}$ given a value of $X$ are not independent, we can not further factorize $P(D_{\Pi_x} \mid M)$ into $\prod_i P(D_{P_i} \mid M)$.
-Similarly, once we have samples of $X$ and $\boldsymbol{S_i}$, we can sample $C_i$.
-Since the sampling processes of child variables are independent from each other, we have the product $\prod_{i = 1}^{n_c} P(D_{C_i} \mid M, D_{\boldsymbol{S_i}})$.\\
+The concept behind the factorization also the motivation behind forward sampling in a Bayesian network.
+The parents of $X$ are independent of the children given $X$.
+The parents are not necessarily individually independent, and thus the parental term $P(D_{\Pi_x} \mid M)$ cannot be factored further.
+The children of $X$ are similarly independent given $X$ and its spouses $\boldsymbol{S_i}$, leading to their factored product $\prod_{i = 1}^{n_c} P(D_{C_i} \mid M, D_{\boldsymbol{S_i}})$.
+Each component in the decomposition be evaluated based on a discretization policy $M = [n_1,n_2,\ldots,n_k]$ and dataset $D$.
 
-For the following part, we evaluate $P(D_{\Pi_x} \mid M)$  and $P(D_{C_i} \mid M, D_{\boldsymbol{S_i}})$ based on discretization policy $M = [n_1,n_2,\ldots,n_k]$ and dataset $D$.
-\subsubsection{Evaluate $P(D_{\Pi_x} \mid M)$}
-Assume that $J_P = \prod_{i=1}^{n_p} | P_i |$. Then we have:
+\subsubsection{Evaluation of $P(D_{\Pi_x} \mid M)$}
+Assume that $J_P = \prod_{i=1}^{n_p} | P_i |$. Then:
 \begin{equation}
@@
 According to the forth prior, the distribution in each interval is independent, so we multiply all the two factors together.
-\subsubsection{Evaluate $P(D_{C_i} \mid M, D_{\boldsymbol{S_i}})$}
-Assume for each pair of $(C_j, \boldsymbol{S_j})$, we have $|C_j | = J_j$ and $| \boldsymbol{S_j} | = L_j = \prod_{v \in \boldsymbol{S_j}} | v |$. Therefore,
+
+\subsubsection{Evaluation of $P(D_{C_i} \mid M, D_{\boldsymbol{S_i}})$}
+Assume for each pair of $(C_j, \boldsymbol{S_j})$, one has $|C_j | = J_j$ and $|\boldsymbol{S_j}| = L_j = \prod_{v \in \boldsymbol{S_j}} | v |$. Therefore,
 \begin{equation}

### 2015-11-16 auto_MPG/tikz_gridmap.jl
initial commit

@@ -1,0 +1,103 @@
+using DataFrames
+using Discretizers
+
+const OUTPUT_FILE = "output.tex"
+
+raw = readtable("autoMPG_raw.dat", header=false)
+our1 = readtable("autoMPG_exp1_ourmethod.dat", header=false)
+our2 = readtable("autoMPG_exp2_ourmethod.dat", header=false)
+MDL1 = readtable("autoMPG_exp1_MDLmethod.dat", header=false)
+
+disc_our1 = Dict{Int, LinearDiscretizer}()
+disc_our1[1] = LinearDiscretizer([9.0,15.25,17.65,20.9,25.65,28.9,46.6])
+disc_our1[3] = LinearDiscretizer([68.0,70.5,93.5,109.0,159.5,259.0,284.5,455.0])
+disc_our1[4] = LinearDiscretizer([46.0,71.5,99.0,127.0,230.0])
+disc_our1[5] = LinearDiscretizer([1613.0,2115.0,2480.5,2959.5,3657.5,5140.0])
+disc_our1[6] = LinearDiscretizer([8.0,12.35,13.75,16.05,22.85,24.8])
+
+
+function export_plot(
+	io::IO,
+	var_x::Int, # variable for x axis
+	var_y::Int, # variable for y axis
+	disc::Dict{Int, LinearDiscretizer}, # set of linear discretizers
+	pdf_pts::DataFrame, # points used to compute heatmap pdf
+	scatter_pts::DataFrame; # points we will scatter on top
+	colorbar_max::Float64=0.25
+	)
+
+
+	disc_x = disc[var_x]
+	disc_y = disc[var_y]
+
+	nbins_x = nlabels(disc_x)
+	nbins_y = nlabels(disc_y)
+	counts = zeros(Float64, nbins_x, nbins_y)
+	for i in 1 : nrow(pdf_pts)
+		x = encode(disc_x, pdf_pts[i, var_x])
+		y = encode(disc_y, pdf_pts[i, var_y])
+		counts[x,y] += 1
+	end
+	counts ./= sum(counts)
+
+	varnamex = string('A' - 1 + var_x)
+	varnamey = string('A' - 1 + var_y)
+
+	println(io, "\\documentclass[crop,tikz]{standalone}\n")
+	println(io, "\\usepackage{pgfplots}")
+	println(io, "\\pgfplotsset{compat=1.12}")
+	println(io, "\\begin{document}")
[…]

### 2015-11-16 BN_discretizer_paper.tex
merged in changes

@@
 
-For example, in Figure 1., the corresponding $P(D \mid M)$ is factorized as
+For example, in Figure 1., the corresponding $P(D \mid M)$ is factorized according to
 \begin{equation}
@@
 \subsubsection{Evaluation of $P(D_{\Pi_x} \mid M)$}
-Assume that $J_P = \prod_{i=1}^{n_p} | P_i |$. Then:
+Let $J_P = \prod_{i=1}^{n_p} \| P_i \|$. It follows that
+
 \begin{equation}
+\label{eq:likelihood_one}
 P(D_{\Pi_X} \mid M) = \prod_{i=1}^k  {{1}\over{{n_i + J_P - 1}\choose{J_P -1}}}
-{{1}\over{ {{{n}_i}!}\over{ {n^{(p)}_{i,1} !} {n^{(p)}_{i,2} !} \cdots {n^{(p)}_{i,J_P} !}}  }},
+{{1}\over{ {{{n}_i}!}\over{ {n^{(p)}_{i,1} !} {n^{(p)}_{i,2} !} \cdots {n^{(p)}_{i,J_P} !}}  }}\text{,}
 \end{equation}
-where $n^{(p)}_{i,j}$ is the number of instances in $i$th discretized interval with $j$th value of $\Pi_X$.
-Note that $n_i = \sum_{j=1}^{| \Pi_x |} n^{(p)}_{i,j}$.
-The two factors on RHS comes from the second prior: all distributions of values of $\Pi_X$ in a given interval are equiprobable.
-According to the forth prior, the distribution in each interval is independent, so we multiply all the two factors together.
+
+\noindent
+where $n^{(p)}_{i,j}$ is the number of instances in the $i$th discretized interval with the $j$th value of $\Pi_X$.
+Note that $n_i = \sum_{j=1}^{\| \Pi_x \|} n^{(p)}_{i,j}$.
+The two factors on the right hand side comes from the second prior: all distributions of values of $\Pi_X$ in a given interval are equiprobable.
+According to the fourth prior, the distribution in each interval is independent, so the two factors are multiplied together.
 
 \subsubsection{Evaluation of $P(D_{C_i} \mid M, D_{\boldsymbol{S_i}})$}
-Assume for each pair of $(C_j, \boldsymbol{S_j})$, one has $|C_j | = J_j$ and $|\boldsymbol{S_j}| = L_j = \prod_{v \in \boldsymbol{S_j}} | v |$. Therefore,
+For each pair $(C_j, \boldsymbol{S_j})$, let $\|C_j \| = J_j$ and $\| \boldsymbol{S_j} \| = L_j = \prod_{v \in \boldsymbol{S_j}} \| v \|$. It follows that
+
 \begin{equation}
+\label{eq:likelihood_two}
 P(D_{C_j}  \mid M, D_{S_j}) =
 \prod_{i=1}^{k} \prod_{l=1}^{L_j} {{1}\over{{n_{i,l} + J_j - 1}\choose{J_j-1}}}
-{{1}\over{ {{n_{i,l}}!}\over{ {n^{(j)}_{i,1,l} !} {n^{(j)}_{i,2,l} !} \cdots {n^{(j)}_{i,J_j,l} !}}  }},
+{{1}\over{ {{n_{i,l}}!}\over{ {n^{(j)}_{i,1,l} !} {n^{(j)}_{i,2,l} !} \cdots {n^{(j)}_{i,J_j,l} !}}  }}\text{,}
 \end{equation}
+
+\noindent
 where $n^{(j)}_{i,m,l}$ is the number of instances in $i$th interval with $m$th value of $C_j$ and $l$th value of $\boldsymbol{S_j}$, $n_{i,l} = \sum_{m=1}^{J_j} n^{(j)}_{i,m,l}$, and $n_i = \sum_{l=1}^{L_j} n_{i,l}$.
-The two factors on RHS comes from the third prior: all distribution of values of $C_j$ in a given interval and with a given value of $S_j$ are equiprobable.
-According to the forth prior, these distributions are independent from each other, therefore we multiply all factors.
-If $S_j = \emptyset$, then Equation 13.
-is equivalent to
+The two factors on the right hand side come from the third prior: all distribution of values of $C_j$ in a given interval and with a given value of $S_j$ are equiprobable.
+According to the forth prior, these distributions are independent from each other, and one thus takes their product.
+If $S_j = \emptyset$, then Equation \ref{eq:likelihood_two} is equivalent to
+
 \begin{equation}
+\label{eq:likelihood_three}
 P(D_{C_j}  \mid M) =
 \prod_{i=1}^{k}  {{1}\over{{n_{i} + J_j - 1}\choose{J_j-1}}}
-{{1}\over{ {{n_{i}}!}\over{ {n^{(j)}_{i,1,\emptyset} !} {n^{(j)}_{i,2,\emptyset} !} \cdots {n^{(j)}_{i,J_j,\emptyset} !}}  }},
+{{1}\over{ {{n_{i}}!}\over{ {n^{(j)}_{i,1,\emptyset} !} {n^{(j)}_{i,2,\emptyset} !} \cdots {n^{(j)}_{i,J_j,\emptyset} !}}  }}\text{,}
 \end{equation}
-where $n^{(j)}_{i,m,\emptyset}$ is the number of instances in $i$th interval with $m$th value of $C_j$, and $\sum_{m=1}^{J_j} n^{(j)}_{i,m,\emptyset} = n_i$. \\
 
-With Equation 8,9,11,12, and 13, now we are able to write down the objective function. Instead of maximizing $P(M) \cdot P(D|M)$, we minimize its log-inverse for convenience. The objective function is
+\noindent
+where $n^{(j)}_{i,m,\emptyset}$ is the number of instances in the $i$th interval with the $m$th value of $C_j$, and $\sum_{m=1}^{J_j} n^{(j)}_{i,m,\emptyset} = n_i$.
+
+The objective function can be formulated given equations \ref{eq:p_M}, \ref{eq:p_D_given_M},\ref{eq:likelihood_one}, and \ref{eq:likelihood_three}.
+The log-inverse of $P(M) \cdot P(D|M)$ is minimized for computational convenience:
+
 \begin{equation}
+\label{eq:opt_prob}
 \begin{aligned}
@@
 &  \sum_{j=1}^{n_c} \sum_{i=1}^{k}  \sum_{l=1}^{L_j} \left[  \log{{n_{i,l} + J_j - 1}\choose{J_j-1}} + \log \left( { {{n_{i,l}}!}\over{ {n^{(j)}_{i,1,l} !} {n^{(j)}_{i,2,l} !} \cdots {n^{(j)}_{i,J_j,l} !}} } \right) \right] + \\
-& \sum_{i=1}^k \left[  \log {{n_{i} + J_P - 1}\choose{J_P-1}} + \log \left( { {{n_i}!}\over{ {n^{(p)}_{i,1} !} {n^{(p)}_{i,2} !} \cdots {n^{(p)}_{i,J_p} !}} } \right) \right].
+& \sum_{i=1}^k \left[  \log {{n_{i} + J_P - 1}\choose{J_P-1}} + \log \left( { {{n_i}!}\over{ {n^{(p)}_{i,1} !} {n^{(p)}_{i,2} !} \cdots {n^{(p)}_{i,J_p} !}} } \right) \right]\text{.}
 \end{aligned}
 \end{equation}
+
 All parameters and variables in the objective function are explained in previous subsections.
+
 \subsection{Algorithm}
-\label{algo}
-Once the objective function is established, the next problem is how to find a discretization model that minimizes the objective function.
-Note that the objective function is cumulative on intervals.
-Therefore, if a partition of continuous variable $X$ into $k$ intervals with lengths $n_1,n_2,\ldots,n_k$ is an optimal discretization policy, then $\{ n_2, n_3,\ldots,n_k \}$ is optimal for the subproblem, i.e., the last $N - n_1$ instances of the dataset which has been sorted in ascending order of $D_X$.
-With this property, we can adapt dynamical programming to solve this optimization problem.
 
-If there is no repeated value in $D_X$, all middle points of two consecutive values can a discretization edge.
-If there exists repeated values in $D_X$, only the middle points of two consecutive and different values can be a discretization edge.
-Assume there are $M$ unique values in $D_X$, then ${D'_X} = \{ x'_1,x'_2,\ldots,x'_M \}$ is the set of unique values of $D_X$ in ascending order.
-Since $D_X$ is also sorted, let $b = \{ b_0,b_1,b_2,\ldots,b_M \}$ be an increasing sequence of integers such that $b_0 = 0$ and $x_{b_{i-1} + 1} = x_{b_{i-1} + 2} = \ldots = x_{{b_i}} = x'_i$.
-By this definition, the allowable discretization positions are $d_i = ( x_{b_{i}} + x_{{b_i}+1})/2$ for all $i = 1,2,\ldots,M-1$.
+This section describes the procedure used to minimize the objective function.
+Note that the objective function is cumulative over intervals, thus, if a partition of $X$ into $k$ intervals with lengths $n_1,n_2,\ldots,n_k$ is an optimal discretization policy, then any subinterval is optimal for the corresponding subproblem.
+It follows that dynamic programming can be used to solve the optimization problem exactly.
 
-Before doing the dynamical programming, in order to save runtime, we first calculate the following function $h(u,v)$ for a interval $I_q$ starting from $x_{u}$ to $x_{v}$ with all $u$,$v$ satisfying $u \leq v$:
+Every midpoint between two nonequal consecutive values in $D_X$ is a candidate discretization edge.
+Let ${D'_X} = \brock{x'_1,x'_2,\ldots,x'_M}$ be the set of unique values of $D_X$ sorted in ascending order, where $M$ is the number unique values in $D_X$.
+Recall that $D_X$ is also sorted.
+Let $b = \brock{b_0,b_1,b_2,\ldots,b_M}$ be an increasing sequence of integers marking the repeated value intervals in $D_X$ such that $b_0 = 0$ and $x_{b_{i-1} + 1} = x_{b_{i-1} + 2} = \ldots = x_{b_i} = x'_i$.
+By this definition, the allowable discretization positions are $d_i = \paren{x_{b_{i}} + x_{{b_i}+1}}/2$ for all $i = 1,2,\ldots,M-1$.
+
+Precomutation reduces runtime.
+Compute $h(u,v)$ for each interval $I_q$ starting from $x_{u}$ to $x_{v}$ for all $(u,v)$ satisfying $u \leq v$:
+
+\begin{small}
 \begin{equation}
@@
 \end{equation}
+\end{small}
 
-The evaluation of function $h(u,v)$ for all $u \leq v$ is summerized in Algorithm 4 in Appendix.
-The calculation can be done in $\bigo\paren{n_c  {v'_\text{max}} \cdot N^2 + {v'_\text{max}}^{n_p} \cdot N^2}$, where $n_c$ and $n_p$ are the numbers of child and parent variables, respectively, and $v'_\text{max}$ is the largest cardinality of variables that directly connects to $X$.
-Notice that due to repeated values in $D_X$, for some pairs of $u$ and $v$, the value of $h(u,v)$ might depend on the sorting method of $D_X$ and $D$.
-However, this does not influence the optimization result, since these pairs of $u$ and $v$ will not form valid intervals.
+The evaluation of $h(u,v)$ for all $u \leq v$ is summarized in Algorithm \ref{alg:h} in the appendix.
+The calculation has a $O(n_c  {v'_\text{max}} \cdot N^2 + {v'_\text{max}}^{n_p} \cdot N^2)$ runtime, where $n_c$ and $n_p$ are the numbers of child and parent variables respectively, and $v'_\text{max}$ is the largest cardinality of variables that directly connect to $X$.
 
-Now we are able to solve the optimization problem with the objective function in Equation 14.
-The dynamical programming procedure is shown in Algorithm 1.
-We have three inputs: $D_X$, the data of continuous variable $X$ in the ascending order, $D$, the data of other variables and sorted according to $D_X$, and $G$, the network structure.
-The runtime of Algorithm 1 is also $\bigo\paren{n_c  {v'_\text{max}} \cdot N^2 + {v'_\text{max}}^{n_p} \cdot N^2}$, since the dynamical programming procedure does not increase the time complexity beyond the calculation of $h(u,v)$.
-There are other methods that lead to suboptimal results but runs faster than dynamical programming method.
-Please refer to \citep{Boulle_2006}.
+Now we are able to solve the optimization problem over Equation \ref{eq:opt_prob}.
+The dynamic programming procedure is shown in Algorithm \ref{alg:disc_one}.
+It takes two inputs: $D$, the joint samples over all variables sorted in ascending order according to $D_X$, and $G$, the network structure.
+The runtime of Algorithm \ref{alg:disc_one} is also $O(n_c  {v'_\text{max}} \cdot N^2 + {v'_\text{max}}^{n_p} \cdot N^2)$, because the runtime of the dynamic programming procedure is less than the runtime for computing $h(u,v)$.
+Algorithm \ref{alg:disc_one} is guaranteed to be optimal.
+For faster methods with suboptimal results please refer to \citep{Boulle_2006}.
 
 \begin{algorithm}
-\caption{ Discretization of one continuous variable}\label{euclid}
+\caption{Discretization of one continuous variable in a Bayesian network}
+\label{alg:disc_one}
 \begin{algorithmic}[5]
-\Function{Discretize}{$D_X$, $D$, $G$}
+\Function{Discretize}{$D$, $G$}
 \State
 \State $N \leftarrow$ the number of instances
-\State $N' \leftarrow$ the number of non-repeated values of $D_X$
-\State $H \leftarrow$ an $N \times N$ matrix such that $H[u,v] = h(u,v)$ as Algorithm 4 in Appendix
-\State $b \leftarrow$ the increasing sequence of $M$ integers defined in the previous discussion
-\State $L \leftarrow$ the largest cardinality over all discrete variables in the Markov blanket
-\State $S[u] \leftarrow$ the optimal objective value of a subproblem with instances from $1$ to $u$
-\State $M[u] \leftarrow$ the optimal discretization of a subproblem with instances from $1$ to $u$
-\State $W[u]  \leftarrow - \log(1 - {\exp(- L \cdot{ {{x_{b(u)+1} - x_{b(u)}}\over{x_N - x_1}})}})$ for $u = 1,2, \ldots,N'-1$ and $L(N') \leftarrow 0$
+\State $N' \leftarrow$ the number of unique values in $D_X$
+\State $H \leftarrow$ an $N \times N$ matrix such that $H[u,v] = h(u,v)$ per Algorithm \ref{alg:h} in the appendix
+\State $b \leftarrow$ the increasing sequence of $M$ integers as previously defined
+\State $L \leftarrow$ the largest cardinality over all discrete variables in the Markov blanket of $X$
+\State $S[u] \leftarrow$ the optimal objective value of subproblems with instances from $1$ to $u$
+\State $M[u] \leftarrow$ the optimal discretization for subproblems with instances from $1$ to $u$
+\State $W[u]  \leftarrow - \log\brock{1 - {\exp\paren{- L \cdot{ {{x_{b(u)+1} - x_{b(u)}}\over{x_N - x_1}}}}}}$ for $u = 1,2, \ldots,N'-1$ and $L(N') \leftarrow 0$
 \State
@@
 \subsection{Approximation}
-\label{approx}
-Notice that Algorithm1 leads to the non-polynomial runtime $\bigo\paren{{v'_\text{max}}^{n_p} \cdot N^2}$ in the discretization process.
-Therefore, we have an empirical approximation to the objective function that can reduce runtime and still preserve the quality of discretization.
-The approximation is as follows: for the dominator of the last factor in Equation 11, we have
+
+Algorithm \ref{alg:disc_one} has an exponential $\bigo\paren{\paren{v'_\text{max}}^{n_p} \cdot N^2}$ runtime.
+This exponential runtime is severely limiting for networks with a large number of discretization edges.
+This section introduces an approximation to the objective function that significantly reduces the runtime and still preserves the quality of discretization.
+The approximation replaces the dominator of the last factor in Equation \ref{eq:likelihood_one} with
+
 \begin{equation}
-{{{{n}_i}!}\over{ {{n^{(p)}}_{i,1} !} {n^{(p)}_{i,2} !} \cdots {n^{(p)}_{i,J_P} !}}} \approx \prod_{r=1}^{n_p} { {{{n}_i}!}\over{ {n^{(p_r)}_{i,1} !} {n^{(p_r)}_{i,2} !} \cdots {n^{(p_r)}_{i,J_{p_r}} !}}},
+{\frac{{n_i}!}{ {n^{(p)}_{i,1} !} {n^{(p)}_{i,2} !} \cdots {n^{(p)}_{i,J_P} !}}} \approx \prod_{r=1}^{n_p} { {{{n}_i}!}\over{ {n^{(p_r)}_{i,1} !} {n^{(p_r)}_{i,2} !} \cdots {n^{(p_r)}_{i,J_{p_r}} !}}}\text{,}
 \end{equation}
-where $J_{p_r} = | P_r|$ and ${n^{(p_r)}_{i,j} !}$ is the number of instances in $i$th interval with $j$th value of $P_r$. Applying this approximation, the approximated objective function is
+
+\noindent
+where $J_{p_r} = \| P_r\|$ and ${n^{(p_r)}_{i,j} !}$ is the number of instances in the $i$th interval with the $j$th value of $P_r$.
+The approximated objective function is
+
+\begin{small}
 \begin{equation}
 \begin{aligned}
+\label{eq:opt_prob_approx}
 & \sum_{i=1}^{k-1} - \log(1 - {\exp(- L \cdot {{x_{s_i+1} - x_{s_i}}\over{x_N - x_1}})}) +  \sum_{i=1}^{k} L \cdot {{x_{s_{i}} - x_{s_{i-1} + 1}}\over{x_N - x_1}} +\\
 &  \sum_{j=1}^{n_c} \sum_{i=1}^{k}  \sum_{l=1}^{L_j} \left[  \log{{n_{i,l} + J_j - 1}\choose{J_j-1}} + \log \left( { {{n_{i,l}}!}\over{ {n^{(j)}_{i,1,l} !} {n^{(j)}_{i,2,l} !} \cdots {n^{(j)}_{i,J_j,l} !}} } \right) \right] + \\
-& \sum_{i=1}^k \left[  \log {{n_{i} + J_P - 1}\choose{J_P-1}} + \sum_{q=1}^{n_p} \log \left( { {{{n}_i}!}\over{ {n^{(p_q)}_{i,1} !} {n^{(p_q)}_{i,2} !} \cdots {n^{(p_q)}_{i,J_{p_q}} !}}} \right) \right].
+& \sum_{i=1}^k \left[  \log {{n_{i} + J_P - 1}\choose{J_P-1}} + \sum_{q=1}^{n_p} \log \left( { {{{n}_i}!}\over{ {n^{(p_q)}_{i,1} !} {n^{(p_q)}_{i,2} !} \cdots {n^{(p_q)}_{i,J_{p_q}} !}}} \right) \right]\text{.}
 \end{aligned}
 \end{equation}
+\end{small}
 
-As we will see in Section \ref{sec:experiments}, the approximated algorithm is more sensitive to the distribution of other variables' values and usually leads to slightly more discretization edges.
-With the approximation, we can reduce runtime of Algorithm 1 from $\bigo\paren{n_c  {v'_\text{max}} \cdot N^2 + {v'_\text{max}}^{n_p} \cdot N^2}$ to $\bigo\paren{v'_\text{max} (n_c + n_p) \cdot N^2}$.
-The rigorous proof of the approximation have not been proposed.
+The approximation reduces the runtime of Algorithm \ref{alg:disc_one} to a polynomial, $\bigo\paren{ {v'_\text{max}} \cdot (n_c + n_p) \cdot N^2}$.
+It will be shown in Section \ref{sec:experiments} that the approximation is more sensitive to the distribution over other variables and is biased towards slightly higher interval counts.
+\tim{We need to have a more specific thing to say along the lines of When does it fail?}
 
-With the approximated objective function, Equation 17, we now have a more clear way to see that how child variables and parent variables contribute to the objective function differently.
-For example, in the left graph of Figure 2, the corresponding sqaure brackets in Equation 17 are
+With the approximated objective function, Equation \ref{eq:opt_prob_approx}, provides intuition into how child and parent variables contribute to the objective function.
+For example, in the left graph of Figure \ref{fig:example_networks}, the corresponding square brackets in the approximated objective function are
+
+\begin{small}
 \begin{equation}
 \begin{aligned}
+\label{eq:example_approx}
  \sum_{i=1}^k & \left\lbrace   \left[ \log{{n_{i} + J_{C_1} - 1}\choose{J_{C_1}-1}} + \log \left(  {{{n_i}!} \over { {n^{(1)}_{i,1,\emptyset} !} \cdots {n^{(1)}_{i,J_{C_1},\emptyset} !}} }  \right)  +  \right.
@@
 &  \left.
-\left[  \log {{n_{i} + J_P - 1}\choose{J_P-1}} +  \log \left( { {{{n}_i}!}\over{ {n^{(p_1)}_{i,1} !}\cdots {n^{(p_1)}_{i,J_{p_1}} !}}} \right) +{ {{{n}_i}!}\over{ {n^{(p_2}_{i,1} !}\cdots {n^{(p_2)}_{i,J_{p_2}} !}}}  \right] \right\rbrace\\ .
+\left[  \log {{n_{i} + J_P - 1}\choose{J_P-1}} +  \log \left( { {{{n}_i}!}\over{ {n^{(p_1)}_{i,1} !}\cdots {n^{(p_1)}_{i,J_{p_1}} !}}} \right) +{ {{{n}_i}!}\over{ {n^{(p_2}_{i,1} !}\cdots {n^{(p_2)}_{i,J_{p_2}} !}}}  \right] \right\rbrace \text{.}
 \end{aligned}
 \end{equation}
+\end{small}
 
-In Equation18, each child variable carries two terms, as shown in the first square bracket, and two parent variables only carry three terms, as shown in the second square bracket.
-Therefore, in this case, child variables are more determinative than parent variables even though the numbers of child variables and parent variables are equal.
-However, if $C_2$ has the other parent variable $S_2$, as shown in the right graph of Figure 2, the importances of $C_2$ will be debiliated, since the information from $C_2$ is now adulterated by $S_2$.
-These argument shows that our proposed method, either before or after approximation, indeed involves graph structures to discretize continuous variables.
+In Equation \ref{eq:example_approx}, each child carries two terms, as shown in the first set of square brackets, but the two parent variables only carry a total of three terms, as shown in the second set of square brackets.
+In this case the child variables have greater effect than the parent variables even though the number of child and parent variables are the same.
+However, if $C_2$ has an additional parent $S_2$, as shown in the right graph of Figure \ref{fig:example_networks}, the importances of $C_2$ will be reduced, because the information from $C_2$ is now affected by $S_2$.
+This argument shows that the proposed method, both before and after approximation, indeed incorporates graph structure when discretizing continuous variables.
 
 \begin{figure}[ht]
+  \label{fig:example_networks}
   \begin{tabular}{cc}
@@
 
-If there are multiple continuous variables in a Bayesian network, we iterate the one-variable discretization method discussed above for all continuous variables.
-While discretizing a continuous variable, other continuous variables must be discretized, either by a prediscretization that was done before the first iteration or by the discretization result of the latest iteration.
-The prediscretization can be done by equal-width discretization, which is defined as follows:
+The single-variable discretization method can be extended to Bayesian networks with multiple continuous variables by iteratively discretizing variables individually.
+The discretization process for a single variable requires that all other variables be discrete.
+The iterative approach thus requires a prediscretization policy from which to initialize the process.
+This work uses prediscretization with equal-width intervals, defined by
+
 \begin{equation}
-M_X =  \{ min_X, min_X + \delta, min_X + 2\delta, \ldots, \delta, max_X \},
+M_X = \curly{X_\text{min}, X_\text{min} + \delta, X_\text{min} + 2\delta, \ldots, \delta, X_\text{max}}\text{,}
 \end{equation}
-where $min_X$ and $max_X$ are minimal and maximal values of $D_X$, respectively, $\delta =  (max_X - min_X)/k$, and $k$ is the desired number of intervals after equal-width discretization.
-$k$ is same for all continuous variables and is set to be median value of all discrete variables' cardinalities.
-After prediscretization, we iterate the one-variable discretization on each continuous variable in the following order: from the continuous variable with highest topological order (leaves) to the continuous variable with lowest topological order (root).
-We call one such series of discretizations as a cycle.
-The advange of the order is that, for the first cycle of iteration, we can use less number of unsupervised discretization result.
-For example, in the right graph of Figure 2, assume $S_2$ is the only discrete variable.
-If we begin the iteration with $P_1$, then the discretization of $P_1$ will involve the prediscretization results of both $P_2$ and $X$.
-However, if we begin the iteration with $C_1$, then the discretization of $C_1$ will only involve the prediscretization result of $X$.
 
-When the number of intervals after discretization and the positions of discretization edges converge, we stop the iterations and output the discretization policy on each continuous variable.
-Since the convergence is not guaranteed, we also set up a maximal number of cycles to prevent infinite iterations.
-In our test on real-world data, the iteration results usually converge within few cycles.
-Even if it does not converge, 10 cycles usually produce good enough discretization result.
-The pseudocode of multi-variable discretization is shown in Algorithm 2, where we require four inputs: $D''$, the mixed data of all variables that we plan to learn from, $G$, the network structure, $C$, the set of all continuous variables in a reverse topological order, and $u_{cycle}$, the upper bound of times of cycles.
+\noindent
+where $X_\text{min}$ and $X_\text{max}$ are the extrema values of $D_X$, $\delta = (X_\text{max} - X_\text{min})/k$, and $k$ is the desired number of intervals.
+This work sets $k$ to the median value of the cardinalities of initially discrete variables in the network.
+After prediscretization, the one-variable discretization methis is iteratively applied over each continuous variable in reverse topoligical order, from the leaves to the root.
+Let one such series of discretizations be a cycle.
+Reverse topological order has the advantage of using less prediscretized instantiations during the first cycle.
+For example, in the right-hand graph of Figure \ref{fig:example_networks}, assume $S_2$ is the only discrete variable.
+The discretization of $P_1$ involves both $P_2$ and $X$, whereas the discretization of $C_1$ only involves $X$.
+
+The algorithm is terminated when the number of discretization intervals and their associated edges converge for all variables.
+A maximum cycle count is enforced to prevent infinite iterations when convergence does not occur.
+The algorithm typically converges within a few cycles when tested on real-world data.
+In cases where it does not converge, ten cycles usually produce decent discretization results.
+
+The pseudocode for the multi-variable discretization procedure is shown in Algorithm \ref{alg:disc_two}.
+It requires four inputs: $D''$, the joint samples from all network variables; $G$, the network structure; $C$, the set of all continuous variables in a reverse topological order; and $u_{cycle}$, the upper bound of times of cycles.
 
 \begin{algorithm}
-\caption{ Discretization of multiple continuous variables}
+\label{alg:disc_two}
+\caption{Discretization of multiple continuous variables \todo{Fix label reference number}}
 \begin{algorithmic}[5]
@@
 
-\subsection{Discretization of Continuous Variables While Structure Learning}
+\subsection{Combining Discretization with Structure Learning}
 
-In many situations the network structure is not known in advance, then we need to learn it from data.
-We use an alternative approach to combine our proposed discretization method with the K2 structure learning algorithm \citep{K2}.
-That is to say, we start with some prediscretizations on continuous variables and run the K2 algorithm given the discretized data.
-Each time an edge is added by the K2 algorithm, we rediscretize the continuous variables based on the current network.
-Then the new discretization policies update the discretized data of all continuous variables, and we continue the next K2 step with the updated discretized data.
-This cycle is repeated until no edge is added by the K2 algorithm.
-The detail of the procedure is shown in Algorithm 3.
-Here we have five inputs: $D'$, the mixed data we plan to learn from, $C$, the set of all continuous variables, $order$, the variable order which is required by the $K2$, $u_{parent}$, the upper bound of number of parents which is also required by the $K2$, and $u_{cycle}$, the upper bound of times of cycles.
-Notice that in the usual structure learning from discrete data, one usually run the K2 algorithm many times with different orders, and choose the structure with the highest K2 score.
-We do the same thing: run Algorithm 3 many times, each time with a different order, and pick the discretized Bayesian network with the highest K2 score.
+In many situations the network structure is not known in advance and must be learned from data.
+Traditional Bayesian structure learning algorithms require discretized data, whereas the proposed discretization algorithm requires a network structure.
+This section combines the proposed discretization method with the K2 structure learning algorithm \citep{K2} in an interative fassion to simultaneously perform Bayesian structure learning and discretization of continuous variables.
+
+The proposed algorithm alternates between K2 structure learning and discretization.
+K2 is run on the discretized dataset corresponding to prediscretizations for all continuous variables.
+The affected continuous variables are rediscretized every time an edge is added by K2.
+The resulting discretization policies are used to update the discretized dataset, and the next step of the K2 algorithm is executed.
+This cycle is repeated until the K2 algorithm reaches a local maximum.
+
+This procedure is given in Algorithm \ref{alg:structure_learn}.
+It takes five inputs: $D'$, the joint samples from all network variables; $C$, the set of all continuous variables; $order$, the permutation of variable for $K2$; $u_{parent}$, the upper bound on the number of parents per node for $K2$; and $u_{cycle}$, the upper bound on the cycle count.
+It is common practice to run K2 multiple times with different permutations of the variables and to then choose the structure with the highest score.
+This work runs Algorithm \ref{alg:structure_learn} multiple times, each with a different order, and picks the discretized Bayesian network with the highest score.
+
 \begin{algorithm}
+  \label{alg:structure_learn}
   \caption{ Learning a discrete-valued Bayesian network}
@@
   \Function{Learn\_DBN}{$D''$, $C$, $order$, $u_{parent}$, $C$, $u_{cycle}$}
-\State
-
-\State $n \leftarrow$ the number of variables in Bayesian network
-\State $k \leftarrow median\{ |v|, v\notin C\}$
-\State $M[i] \leftarrow$ the discretization policy of $i$th variable
-\State $D^*_i \leftarrow M[i] (D_i)$, the discretized $D_i$ by $M[i]$
+    \State $n \leftarrow$ the number of variables in the Bayesian network
+    \State $k \leftarrow median\{ \|v\|, v\notin C\}$
+    \State $M[i] \leftarrow$ the discretization policy for the $i$th variable
+    \State $D^*_i \leftarrow M[i] (D_i)$, list of samples $D_i$ discretized according to $M[i]$
     \State $D^* \leftarrow $ the discretized data for all variables, where $D^*_i \leftarrow D''_i$ if $i \notin C$
-\State $G \leftarrow$ the initial graph (no edges between nodes)
-\State
+    \State $G \leftarrow$ the initial edgeless graph structure
     \For {$i = 1$ to $n$}
@@
     \EndFor
-\State
     \For {$i =1$ to $n$}
-\State $P_{old} \leftarrow f(X^*_i,\Pi_{X^*_i})$: Equation 5
+      \State $P_{old} \leftarrow f(X^*_i,\Pi_{X^*_i})$: Equation \ref{eq:f_x_p}
       \State OKToProceed $\leftarrow$ \textbf{true}
-\While OKToProceed \textbf{and} $|\Pi_{X^*_i}| < u_{parent}$
+      \While {OKToProceed \textbf{and} $\|\Pi_{X^*_i}\| < u_{parent}$}
         \State $Y \leftarrow$ an element from the set $order[1:i] \backslash \Pi_X$
@@
           \State $\Pi_{X_i} \leftarrow \Pi_{X_i} \cup Y $
-\State $M \leftarrow$ {DISCRETIZE}({$D''$, $G$, $C$, $u_{cycle}$}): Algorithm 2
+          \State $M \leftarrow$ {DISCRETIZE}({$D''$, $G$, $C$, $u_{cycle}$}): Algorithm \ref{alg:disc_two}
           \State $D* = M(D'')$
@@
 \begin{algorithm}
-\caption{ Calculation of function $h(u,v)$ for all $u \leq v$}\label{euclid}
+  \caption{ Calculation of $h(u,v)$ for all $u \leq v$}
+  \label{alg:h}
   \begin{algorithmic}[1]
-\State Initialize $H$ as an $N \times N$ matrix that all elements are 0.
-\State $count_p$ is an $N \times N \times |\Pi_X|$ matrix such that $count_p [u,v,w]$ is the number of instances from $x_u$ to $x_v$ with $w$th value of $\Pi_X$.
-This matrix can be calculated in $\bigo\paren{|\Pi_X| \cdot N^2}$
+  \State Initialize $H$ as an $N \times N$ matrix such that all elements are 0.
+  \State $count_p$ is an $N \times N \times \|\Pi_X\|$ matrix such that $count_p [u,v,w]$ is the number of instances from $x_u$ to $x_v$ with $w$th value of $\Pi_X$.
+This matrix can be calculated in $O(\|\Pi_X\| \cdot N^2)$
   \For {$u = 1$ to $N$}
@@
       \State $H(u,v) \leftarrow H(u,v) + \log((v-u + J_p)!) - \log((J_p -1)!)$
-\For {$w = 1$ to $|\Pi_X|$}
+      \For {$w = 1$ to $\|\Pi_X\|$}
         \State $H(u,v) \leftarrow H(u,v) - \log( count_p(u,v,w)!)$
@@
   \EndFor
-
   \For {$j = 1$ to $n_c$}
-\State XXX
+    \State \todo{XXX}
   \EndFor

### 2015-11-16 BN_discretizer_paper.tex
add $$
Add experiment part

@@
 \usepackage{bm}
-\usepackage{graphicx} % Allows including images
+\usepackage{graphicx}
 \usepackage{epstopdf}
@@
 \usepackage[round]{natbib}
-\usepackage{amsfonts} % for mathbb
+\usepackage{multirow}
+\usepackage{pgfplots}
 \usepackage{tikz}
+\usepackage{lscape}
+\usepackage{caption}
 % \usepackage[capitalize]{cleveref}
@@
 Variables are sampled in topological order such that parental instantiations are always known~\citep[see][chap.~22]{algo_2009}.
-Furthermore, the parent\rightarrow child sampling order can be reversed if the marginal probability of the child variable is known.
+Furthermore, the parent $\rightarrow$ child sampling order can be reversed if the marginal probability of the child variable is known.
 By Bayes' rule,
@@
 
-A discretization policy $M_C = \anglebrackets{t_1 < t_2 < \ldots < t_{k-1}}$ for a continuous variable $C$ is a mapping from $\mathbb{R}$ to $\brock{1,2,3,\ldots,k}$ such that
+A discretization policy $M_C = \anglebrackets{t_1 < t_2 < \ldots < t_{k-1}}$ for a continuous variable $C$ is a mapping from !!! mathbb{R} !!! to $\brock{1,2,3,\ldots,k}$ such that
 \begin{equation}
@@
 
+The section describes experiments designed to test the soundness of the proposed method.
+The experiments were run on four datasets from the Irvine repository \citep{Lichman:2013}.
+For each dataset, the experiment consists of two parts.
+In the first part, the Bayesian network structure is known in advance, which is obtained by equal-width prediscretization and the K2 algorithm.
+In the second part, the Bayesian netowrk structure is not provided in advance, and it is learned along with the discretization process.
+
+For the case that network structure is given, a comparison between the proposed method and the MDL principle discretization is made.
+10-fold cross validation of log-likelihood on data set $D_{\text{all}}$ is calculated as follows: firstly, learn discretization policies of each continuous variables from train data $D_{\text{train}}$.
+Secondly, obtain conditional probability tables $\phi_{x^* \mid \Pi^*_x}$ from the discretized train data $D^*_{\text{train}}$.
+Thirdly, For a test data instance $(x_1,x_2, \ldots, x_n)$ from $D_{\text{test}}$, the likelihood is
+\begin{equation}
+P(x_1, \ldots, x_n) = \prod_{i=1}^{n} \phi_{x^*_i \mid \Pi^*_{x_i}} \cdot \left( {1\over{M'_{X_i}[j_i+1] - M'_{X_i}[j_i]}} \right)^{\boldsymbol{1}_{ \left\lbrace X_i \text{ is continuous}  \right\rbrace }}
+\end{equation}
+, where $M'_{X_i}$ is the augmented discretization policy on continuous variable $X_i$ such that $M'_{X_i}[1] = min(D_{\text{all},X})$, $M'_{X_i}[j] = M_{X_i}[j-1]$ for $j=2,...,k_i$, and $M'_{X_i}[k_i+1] = max(D_{\text{all},X})$, $k$ is the number of intervals of continuous variable $X_i$ after discretization.
+Furthermore, $M'_{X_i}[j_i] \leq x_i < M'_{X_i}[j_i +1]$.
+This can be interpreted as follows: once a discrete-valued Bayesian network is learned from train data, test data are sampled from the learned network.
+If data is continuous, then it is uniformly sampled from the corresponding discretization interval.
+
+\subsection{Dataset 1: Auto MPG} 
+\label{subsec:autompg}
+
+In this subsection, two experiments are conducted on the Auto MPG dataset from the Irvine repository \citep{Lichman:2013}.
+This dataset has 392 instances (delete the 6 instance with missing data) and eight variables.
+Three variables are discrete: $B$, $G$, and $H$ (in the following experiment, variables are named and ordered according to the dataset information webpage).
+They have 5, 13, and 3 cardinality numbers, respectively.
+In the first experiment, the network structure is given.
+In the second experiment, the network structure is not provided.
+
+\subsubsection{Experiment 1 on Auto MPG dataset}
+\label{subsubsec:autompg_exp1}
+The proposed discretization method and the MDL discretization method are tested on the Bayesian network structure in Fig.
+\ref{Auto_graph_1}, which is obtained by running K2 algorithm 1000 times on prediscretized data, each time with a random restart.
+The prediscretization is done by equal-width discretization on continuous variables by 5 intervals (median of cardinalities of discrete variables).
+Shaded nodes in Fig.
+\ref{Auto_graph_1} means that they are discrete-valued variables.
+
+\begin{figure}[ht]
+\centering
+    \begin{tabular}{cc}
+      \input{graph_autocar_1}
+    \end{tabular}
+  \caption{The Bayesian network obatined by K2 algorithm and prediscretization on Auto MPG dataset}
+  \label{Auto_graph_1}
+\end{figure}
+
+Table \ref{Auto_MPG_disc_table_1} shows the numbers of intervals after discretization, the positions of discretization edges, and log-likelihood of 10-fold cross validation.
+For the Bayesian network in Fig.
+\ref{Auto_graph_1}, the approximation only reduces runtime of proposed method and has no influence on discretization result.
+MDL principle discretization works not well, since it discretizes all variables with only one interval.
+For a Bayesian network on thie Auto MPG data set that MDL principle discretization has non-trivial result, please reference to Appendix.
+
+\begin{table}
+\centering
+\scalebox{1.0}{
+\input{table_autoMPG_1.tex}
+}
+\caption{Discretization result of Auto MPG dataset based on the graph in Fig. \ref{Auto_graph_1}}
+\label{Auto_MPG_disc_table_1}
+\end{table}
+
+Figure \ref{auto_exp1_distr_1_3} compares the discretization result on continuous variables $A$ and $C$ with the raw data of Auto MPG data set.
+The color of discretized area shows the probability of a sample being in the discretized area.
+The black dots in Figure \ref{auto_exp1_distr_1_3} demonstrate the distribution of the raw data.
+As shown in the figure, the discretization edges and the resulting marginalized probability match the raw data very well.
+
+\begin{figure}[ht]
+    \begin{tabular}{cc}
+      \input{graph_auto_exp1_distr_1_3}
+    \end{tabular}
+  \caption{Comparison of the raw data and discretization result on variable $A$ and $C$}
+  \label{auto_exp1_distr_1_3}
+\end{figure}
+
+\subsubsection{Experiment 2 on Auto MPG dataset}
+\label{subsubsec:autompg_exp2}
+
+If the network structure is not known in advance, it should be learned along with the discretization process.
+Figure \ref{Auto_graph_2} and Table \ref{Auto_MPG_disc_table_2} show a learned discrete-valued Bayesian network and the corresponding discretization edges of each continuous variable.
+This result is obtained by running Algorithm \ref{Learn_DBN} fifty times and choosing the one with the highest K2 score.
+\newline
+
+ {\centering
+\begin{minipage}{0.50\textwidth}
+  \centering
+  \scalebox{0.7}{
+  \input{graph_autocar_2}}
+  \captionof{figure}{The learned discrete-\newline valued Bayesian network}
+  \label{Auto_graph_2}
+\end{minipage}
+\begin{minipage}{0.50\textwidth}
+  \raggedleft
+  \input{table_autoMPG_2.tex}
+  \captionof{table}{The discretization edges of variables in Fig \ref{Auto_graph_2}}
+  \label{Auto_MPG_disc_table_2}
+\end{minipage}
+}
+
+Figure \ref{auto_exp2_distr_1_3} compares the result of Figure \ref{Auto_graph_2} and Table \ref{Auto_MPG_disc_table_2} with the raw data on variables $A$ and $C$.
+Again, the black dots are raw data points.
+Although the numbers of discretization edges of $A$ and $C$ shown in Table \ref{Auto_MPG_disc_table_2} are less than Table \ref{Auto_MPG_disc_table_1}, they still have a good capture of raw data distribution.
+
+\begin{figure}[ht]
+    \begin{tabular}{cc}
+      \input{graph_auto_exp2_distr_1_3}
+    \end{tabular}
+  \caption{Comparison of the raw data and discretization result on variable $A$ and $C$ according to Figure \ref{Auto_graph_2} and Table \ref{Auto_MPG_disc_table_2}}
+  \label{auto_exp2_distr_1_3}
+\end{figure}
+
+\subsection{Dataset 2: Wine} 
+\label{subsec:wine}
+
+In this subsection, two experiments are conducted on the Wine dataset from the Irvine repository \citep{Lichman:2013}.
+This dataset has 178 instances and 14 variables.
+Only variable $A$ is discrete-valued with cardinality number 3.
+Again, in the first experiment, the network structure is given.
+In the second experiment, the network structure is not provided.
+
+\subsubsection{Experiment 1 on Wine dataset}
+\label{subsubsec:wine_exp2}
+
+Figure \ref{Wine_graph_1} is obtained by equal-width discretizing each continuous variable into 3 intervals and running K2 1000 times.
+Table \ref{Wine_disc_table_1} shows a comparison between the proposed method and the MDL principle discretization method.
+The proposed method is still better than MDL principle discretization in terms of likelihood, although the latter returns non-trivial result in this experiment.
+Furthermore, the proposed method with the approximation has more intervals after discretization, thus it has a slightly better result.
+However, as shown in next dataset, the approximation might cut continuous variables into too many intervals.
+Therefore, the proposed method without the approximation should be still considered a better approach.
+
+\begin{figure}[ht]
+    \begin{tabular}{cc}
+      \input{graph_wine_1}
+    \end{tabular}
+  \caption{K2 structure learning with prediscretization on Wine dataset}
+  \label{Wine_graph_1}
+\end{figure}
+
+\begin{table}
+\centering
+\scalebox{1.0}{
+\input{table_wine_1.tex}
+}
+\caption{Discretization result of Wine dataset based on the graph Fig. \ref{Wine_graph_1}}
+\label{Wine_disc_table_1}
+\end{table}
+
+\begin{figure}[ht]
+    \begin{tabular}{cc}
+      \input{graph_wine_2}
+    \end{tabular}
+  \caption{K2 structure learning with the proposed discretization method on Wine dataset}
+  \label{Wine_graph_2}
+\end{figure}
+
+\subsection{Data 3: Housing}
+\label{subsec:housing}
+
+\begin{figure}[ht]
+    \begin{tabular}{cc}
+      \input{graph_housing_1}
+    \end{tabular}
+  \caption{K2 structure learning with prediscretization on Housing dataset}
+  \label{Housing_graph_1}
+\end{figure}
+
+\begin{table}
+\centering
+\scalebox{1.0}{
+\input{table_housing_1.tex}
+}
+\caption{Discretization result of Housing dataset based on the graph Fig. \ref{Housing_graph_1}}
+\label{Housing_disc_table_1}
+\end{table}
+
+\begin{figure}[ht]
+    \begin{tabular}{cc}
+      \input{graph_housing_2}
+    \end{tabular}
+  \caption{K2 structure learning with the proposed discretization method on Housing dataset}
+  \label{Housing_graph_2}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %\begin{acknowledgements}

### 2015-11-16 graph_auto_exp1_distr_1_3.tex
Add experiment part

\begin{tikzpicture}
		\begin{axis}[
			view={0}{90},
			enlargelimits=0,
			zmin=0.0, zmax=1.0,
			xlabel=A,
			ylabel=C,
			colorbar,
			point meta min=0, point meta max=0.5,
			colormap={}{ gray(0cm)=(1); gray(1cm)=(0);},
			colorbar style={
			        ytick={0,0.05,...,0.5},
			        yticklabel style={
			            text width=2.5em,
			            align=right,
			            /pgf/number format/.cd,
			                fixed,
			                fixed zerofill
			        }
			    }
			]

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,68.0000,0.0000) (15.2500,68.0000,0.0000) (15.2500,70.5000,0.0000) (9.0000,70.5000,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,70.5000,0.0000) (15.2500,70.5000,0.0000) (15.2500,93.5000,0.0000) (9.0000,93.5000,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,93.5000,0.0000) (15.2500,93.5000,0.0000) (15.2500,109.0000,0.0000) (9.0000,109.0000,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,109.0000,0.0020) (15.2500,109.0000,0.0020) (15.2500,159.5000,0.0020) (9.0000,159.5000,0.0020)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,159.5000,0.0235) (15.2500,159.5000,0.0235) (15.2500,259.0000,0.0235) (9.0000,259.0000,0.0235)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,259.0000,0.0030) (15.2500,259.0000,0.0030) (15.2500,284.5000,0.0030) (9.0000,284.5000,0.0030)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,284.5000,0.1345) (15.2500,284.5000,0.1345) (15.2500,455.0000,0.1345) (9.0000,455.0000,0.1345)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(15.2500,68.0000,0.0000) (17.6500,68.0000,0.0000) (17.6500,70.5000,0.0000) (15.2500,70.5000,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(15.2500,70.5000,0.0000) (17.6500,70.5000,0.0000) (17.6500,93.5000,0.0000) (15.2500,93.5000,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(15.2500,93.5000,0.0000) (17.6500,93.5000,0.0000) (17.6500,109.0000,0.0000) (15.2500,109.0000,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(15.2500,109.0000,0.0020) (17.6500,109.0000,0.0020) (17.6500,159.5000,0.0020) (15.2500,159.5000,0.0020)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(15.2500,159.5000,0.0230) (17.6500,159.5000,0.0230) (17.6500,259.0000,0.0230) (15.2500,259.0000,0.0230)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(15.2500,259.0000,0.0030) (17.6500,259.0000,0.0030) (17.6500,284.5000,0.0030) (15.2500,284.5000,0.0030)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(15.2500,284.5000,0.0625) (17.6500,284.5000,0.0625) (17.6500,455.0000,0.0625) (15.2500,455.0000,0.0625)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.6500,68.0000,0.0000) (20.9000,68.0000,0.0000) (20.9000,70.5000,0.0000) (17.6500,70.5000,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.6500,70.5000,0.0000) (20.9000,70.5000,0.0000) (20.9000,93.5000,0.0000) (17.6500,93.5000,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.6500,93.5000,0.0070) (20.9000,93.5000,0.0070) (20.9000,109.0000,0.0070) (17.6500,109.0000,0.0070)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.6500,109.0000,0.0430) (20.9000,109.0000,0.0430) (20.9000,159.5000,0.0430) (17.6500,159.5000,0.0430)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.6500,159.5000,0.0880) (20.9000,159.5000,0.0880) (20.9000,259.0000,0.0880) (17.6500,259.0000,0.0880)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.6500,259.0000,0.0095) (20.9000,259.0000,0.0095) (20.9000,284.5000,0.0095) (17.6500,284.5000,0.0095)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.6500,284.5000,0.0225) (20.9000,284.5000,0.0225) (20.9000,455.0000,0.0225) (17.6500,455.0000,0.0225)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.9000,68.0000,0.0015) (25.6500,68.0000,0.0015) (25.6500,70.5000,0.0015) (20.9000,70.5000,0.0015)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.9000,70.5000,0.0060) (25.6500,70.5000,0.0060) (25.6500,93.5000,0.0060) (20.9000,93.5000,0.0060)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.9000,93.5000,0.0320) (25.6500,93.5000,0.0320) (25.6500,109.0000,0.0320) (20.9000,109.0000,0.0320)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.9000,109.0000,0.0945) (25.6500,109.0000,0.0945) (25.6500,159.5000,0.0945) (20.9000,159.5000,0.0945)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.9000,159.5000,0.0455) (25.6500,159.5000,0.0455) (25.6500,259.0000,0.0455) (20.9000,259.0000,0.0455)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.9000,259.0000,0.0000) (25.6500,259.0000,0.0000) (25.6500,284.5000,0.0000) (20.9000,284.5000,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.9000,284.5000,0.0070) (25.6500,284.5000,0.0070) (25.6500,455.0000,0.0070) (20.9000,455.0000,0.0070)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(25.6500,68.0000,0.0055) (28.9000,68.0000,0.0055) (28.9000,70.5000,0.0055) (25.6500,70.5000,0.0055)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(25.6500,70.5000,0.0110) (28.9000,70.5000,0.0110) (28.9000,93.5000,0.0110) (25.6500,93.5000,0.0110)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(25.6500,93.5000,0.0375) (28.9000,93.5000,0.0375) (28.9000,109.0000,0.0375) (25.6500,109.0000,0.0375)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(25.6500,109.0000,0.0545) (28.9000,109.0000,0.0545) (28.9000,159.5000,0.0545) (25.6500,159.5000,0.0545)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(25.6500,159.5000,0.0165) (28.9000,159.5000,0.0165) (28.9000,259.0000,0.0165) (25.6500,259.0000,0.0165)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(25.6500,259.0000,0.0000) (28.9000,259.0000,0.0000) (28.9000,284.5000,0.0000) (25.6500,284.5000,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(25.6500,284.5000,0.0035) (28.9000,284.5000,0.0035) (28.9000,455.0000,0.0035) (25.6500,455.0000,0.0035)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(28.9000,68.0000,0.0030) (46.6000,68.0000,0.0030) (46.6000,70.5000,0.0030) (28.9000,70.5000,0.0030)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(28.9000,70.5000,0.0995) (46.6000,70.5000,0.0995) (46.6000,93.5000,0.0995) (28.9000,93.5000,0.0995)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(28.9000,93.5000,0.0860) (46.6000,93.5000,0.0860) (46.6000,109.0000,0.0860) (28.9000,109.0000,0.0860)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(28.9000,109.0000,0.0605) (46.6000,109.0000,0.0605) (46.6000,159.5000,0.0605) (28.9000,159.5000,0.0605)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(28.9000,159.5000,0.0120) (46.6000,159.5000,0.0120) (46.6000,259.0000,0.0120) (28.9000,259.0000,0.0120)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(28.9000,259.0000,0.0000) (46.6000,259.0000,0.0000) (46.6000,284.5000,0.0000) (28.9000,284.5000,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(28.9000,284.5000,0.0005) (46.6000,284.5000,0.0005) (46.6000,455.0000,0.0005) (28.9000,455.0000,0.0005)};

			\addplot3[mark=+, draw=none, mark size=0.7] coordinates {
(18.000,307.000,1) (15.000,350.000,1) (18.000,318.000,1) (16.000,304.000,1) (17.000,302.000,1) (15.000,429.000,1) (14.000,454.000,1) (14.000,440.000,1) (14.000,455.000,1) (15.000,390.000,1) (15.000,383.000,1) (14.000,340.000,1) (15.000,400.000,1) (14.000,455.000,1) (24.000,113.000,1) (22.000,198.000,1) (18.000,199.000,1) (21.000,200.000,1) (27.000,97.000,1) (26.000,97.000,1) (25.000,110.000,1) (24.000,107.000,1) (25.000,104.000,1) (26.000,121.000,1) (21.000,199.000,1) (10.000,360.000,1) (10.000,307.000,1) (11.000,318.000,1) (9.000,304.000,1) (27.000,97.000,1) (28.000,140.000,1) (25.000,113.000,1) (19.000,232.000,1) (16.000,225.000,1) (17.000,250.000,1) (19.000,250.000,1) (18.000,232.000,1) (14.000,350.000,1) (14.000,400.000,1) (14.000,351.000,1) (14.000,318.000,1) (12.000,383.000,1) (13.000,400.000,1) (13.000,400.000,1) (18.000,258.000,1) (22.000,140.000,1) (19.000,250.000,1) (18.000,250.000,1) (23.000,122.000,1) (28.000,116.000,1) (30.000,79.000,1) (30.000,88.000,1) (31.000,71.000,1) (35.000,72.000,1) (27.000,97.000,1) (26.000,91.000,1) (24.000,113.000,1) (25.000,97.500,1) (23.000,97.000,1) (20.000,140.000,1) (21.000,122.000,1) (13.000,350.000,1) (14.000,400.000,1) (15.000,318.000,1) (14.000,351.000,1) (17.000,304.000,1) (11.000,429.000,1) (13.000,350.000,1) (12.000,350.000,1) (13.000,400.000,1) (19.000,70.000,1) (15.000,304.000,1) (13.000,307.000,1) (13.000,302.000,1) (14.000,318.000,1) (18.000,121.000,1) (22.000,121.000,1) (21.000,120.000,1) (26.000,96.000,1) (22.000,122.000,1) (28.000,97.000,1) (23.000,120.000,1) (28.000,98.000,1) (27.000,97.000,1) (13.000,350.000,1) (14.000,304.000,1) (13.000,350.000,1) (14.000,302.000,1) (15.000,318.000,1) (12.000,429.000,1) (13.000,400.000,1) (13.000,351.000,1) (14.000,318.000,1) (13.000,440.000,1) (12.000,455.000,1) (13.000,360.000,1) (18.000,225.000,1) (16.000,250.000,1) (18.000,232.000,1) (18.000,250.000,1) (23.000,198.000,1) (26.000,97.000,1) (11.000,400.000,1) (12.000,400.000,1) (13.000,360.000,1) (12.000,350.000,1) (18.000,232.000,1) (20.000,97.000,1) (21.000,140.000,1) (22.000,108.000,1) (18.000,70.000,1) (19.000,122.000,1) (21.000,155.000,1) (26.000,98.000,1) (15.000,350.000,1) (16.000,400.000,1) (29.000,68.000,1) (24.000,116.000,1) (20.000,114.000,1) (19.000,121.000,1) (15.000,318.000,1) (24.000,121.000,1) (20.000,156.000,1) (11.000,350.000,1) (20.000,198.000,1) (19.000,232.000,1) (15.000,250.000,1) (31.000,79.000,1) (26.000,122.000,1) (32.000,71.000,1) (25.000,140.000,1) (16.000,250.000,1) (16.000,258.000,1) (18.000,225.000,1) (16.000,302.000,1) (13.000,350.000,1) (14.000,318.000,1) (14.000,302.000,1) (14.000,304.000,1) (29.000,98.000,1) (26.000,79.000,1) (26.000,97.000,1) (31.000,76.000,1) (32.000,83.000,1) (28.000,90.000,1) (24.000,90.000,1) (26.000,116.000,1) (24.000,120.000,1) (26.000,108.000,1) (31.000,79.000,1) (19.000,225.000,1) (18.000,250.000,1) (15.000,250.000,1) (15.000,250.000,1) (16.000,400.000,1) (15.000,350.000,1) (16.000,318.000,1) (14.000,351.000,1) (17.000,231.000,1) (16.000,250.000,1) (15.000,258.000,1) (18.000,225.000,1) (21.000,231.000,1) (20.000,262.000,1) (13.000,302.000,1) (29.000,97.000,1) (23.000,140.000,1) (20.000,232.000,1) (23.000,140.000,1) (24.000,134.000,1) (25.000,90.000,1) (24.000,119.000,1) (18.000,171.000,1) (29.000,90.000,1) (19.000,232.000,1) (23.000,115.000,1) (23.000,120.000,1) (22.000,121.000,1) (25.000,121.000,1) (33.000,91.000,1) (28.000,107.000,1) (25.000,116.000,1) (25.000,140.000,1) (26.000,98.000,1) (27.000,101.000,1) (17.500,305.000,1) (16.000,318.000,1) (15.500,304.000,1) (14.500,351.000,1) (22.000,225.000,1) (22.000,250.000,1) (24.000,200.000,1) (22.500,232.000,1) (29.000,85.000,1) (24.500,98.000,1) (29.000,90.000,1) (33.000,91.000,1) (20.000,225.000,1) (18.000,250.000,1) (18.500,250.000,1) (17.500,258.000,1) (29.500,97.000,1) (32.000,85.000,1) (28.000,97.000,1) (26.500,140.000,1) (20.000,130.000,1) (13.000,318.000,1) (19.000,120.000,1) (19.000,156.000,1) (16.500,168.000,1) (16.500,350.000,1) (13.000,350.000,1) (13.000,302.000,1) (13.000,318.000,1) (31.500,98.000,1) (30.000,111.000,1) (36.000,79.000,1) (25.500,122.000,1) (33.500,85.000,1) (17.500,305.000,1) (17.000,260.000,1) (15.500,318.000,1) (15.000,302.000,1) (17.500,250.000,1) (20.500,231.000,1) (19.000,225.000,1) (18.500,250.000,1) (16.000,400.000,1) (15.500,350.000,1) (15.500,400.000,1) (16.000,351.000,1) (29.000,97.000,1) (24.500,151.000,1) (26.000,97.000,1) (25.500,140.000,1) (30.500,98.000,1) (33.500,98.000,1) (30.000,97.000,1) (30.500,97.000,1) (22.000,146.000,1) (21.500,121.000,1) (21.500,80.000,1) (43.100,90.000,1) (36.100,98.000,1) (32.800,78.000,1) (39.400,85.000,1) (36.100,91.000,1) (19.900,260.000,1) (19.400,318.000,1) (20.200,302.000,1) (19.200,231.000,1) (20.500,200.000,1) (20.200,200.000,1) (25.100,140.000,1) (20.500,225.000,1) (19.400,232.000,1) (20.600,231.000,1) (20.800,200.000,1) (18.600,225.000,1) (18.100,258.000,1) (19.200,305.000,1) (17.700,231.000,1) (18.100,302.000,1) (17.500,318.000,1) (30.000,98.000,1) (27.500,134.000,1) (27.200,119.000,1) (30.900,105.000,1) (21.100,134.000,1) (23.200,156.000,1) (23.800,151.000,1) (23.900,119.000,1) (20.300,131.000,1) (17.000,163.000,1) (21.600,121.000,1) (16.200,163.000,1) (31.500,89.000,1) (29.500,98.000,1) (21.500,231.000,1) (19.800,200.000,1) (22.300,140.000,1) (20.200,232.000,1) (20.600,225.000,1) (17.000,305.000,1) (17.600,302.000,1) (16.500,351.000,1) (18.200,318.000,1) (16.900,350.000,1) (15.500,351.000,1) (19.200,267.000,1) (18.500,360.000,1) (31.900,89.000,1) (34.100,86.000,1) (35.700,98.000,1) (27.400,121.000,1) (25.400,183.000,1) (23.000,350.000,1) (27.200,141.000,1) (23.900,260.000,1) (34.200,105.000,1) (34.500,105.000,1) (31.800,85.000,1) (37.300,91.000,1) (28.400,151.000,1) (28.800,173.000,1) (26.800,173.000,1) (33.500,151.000,1) (41.500,98.000,1) (38.100,89.000,1) (32.100,98.000,1) (37.200,86.000,1) (28.000,151.000,1) (26.400,140.000,1) (24.300,151.000,1) (19.100,225.000,1) (34.300,97.000,1) (29.800,134.000,1) (31.300,120.000,1) (37.000,119.000,1) (32.200,108.000,1) (46.600,86.000,1) (27.900,156.000,1) (40.800,85.000,1) (44.300,90.000,1) (43.400,90.000,1) (36.400,121.000,1) (30.000,146.000,1) (44.600,91.000,1) (33.800,97.000,1) (29.800,89.000,1) (32.700,168.000,1) (23.700,70.000,1) (35.000,122.000,1) (32.400,107.000,1) (27.200,135.000,1) (26.600,151.000,1) (25.800,156.000,1) (23.500,173.000,1) (30.000,135.000,1) (39.100,79.000,1) (39.000,86.000,1) (35.100,81.000,1) (32.300,97.000,1) (37.000,85.000,1) (37.700,89.000,1) (34.100,91.000,1) (34.700,105.000,1) (34.400,98.000,1) (29.900,98.000,1) (33.000,105.000,1) (33.700,107.000,1) (32.400,108.000,1) (32.900,119.000,1) (31.600,120.000,1) (28.100,141.000,1) (30.700,145.000,1) (25.400,168.000,1) (24.200,146.000,1) (22.400,231.000,1) (26.600,350.000,1) (20.200,200.000,1) (17.600,225.000,1) (28.000,112.000,1) (27.000,112.000,1) (34.000,112.000,1) (31.000,112.000,1) (29.000,135.000,1) (27.000,151.000,1) (24.000,140.000,1) (36.000,105.000,1) (37.000,91.000,1) (31.000,91.000,1) (38.000,105.000,1) (36.000,98.000,1) (36.000,120.000,1) (36.000,107.000,1) (34.000,108.000,1) (38.000,91.000,1) (32.000,91.000,1) (38.000,91.000,1) (25.000,181.000,1) (38.000,262.000,1) (26.000,156.000,1) (22.000,232.000,1) (32.000,144.000,1) (36.000,135.000,1) (27.000,151.000,1) (27.000,140.000,1) (44.000,97.000,1) (32.000,135.000,1) (28.000,120.000,1) (31.000,119.000,1) };
		\end{axis}
	\end{tikzpicture}

### 2015-11-16 graph_auto_exp2_distr_1_3.tex
Add experiment part

--- 2015-11-16 graph_auto_exp1_distr_1_3.tex
@@
 
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,68.0000,0.0000) (15.2500,68.0000,0.0000) (15.2500,70.5000,0.0000) (9.0000,70.5000,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,70.5000,0.0000) (15.2500,70.5000,0.0000) (15.2500,93.5000,0.0000) (9.0000,93.5000,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,93.5000,0.0000) (15.2500,93.5000,0.0000) (15.2500,109.0000,0.0000) (9.0000,109.0000,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,109.0000,0.0020) (15.2500,109.0000,0.0020) (15.2500,159.5000,0.0020) (9.0000,159.5000,0.0020)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,159.5000,0.0235) (15.2500,159.5000,0.0235) (15.2500,259.0000,0.0235) (9.0000,259.0000,0.0235)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,259.0000,0.0030) (15.2500,259.0000,0.0030) (15.2500,284.5000,0.0030) (9.0000,284.5000,0.0030)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,284.5000,0.1345) (15.2500,284.5000,0.1345) (15.2500,455.0000,0.1345) (9.0000,455.0000,0.1345)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,68.0000,0.0000) (17.5500,68.0000,0.0000) (17.5500,134.5000,0.0000) (9.0000,134.5000,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,134.5000,0.0010) (17.5500,134.5000,0.0010) (17.5500,159.5000,0.0010) (9.0000,159.5000,0.0010)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,159.5000,0.0010) (17.5500,159.5000,0.0010) (17.5500,169.5000,0.0010) (9.0000,169.5000,0.0010)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,169.5000,0.0395) (17.5500,169.5000,0.0395) (17.5500,259.0000,0.0395) (9.0000,259.0000,0.0395)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,259.0000,0.0045) (17.5500,259.0000,0.0045) (17.5500,264.5000,0.0045) (9.0000,264.5000,0.0045)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,264.5000,0.2220) (17.5500,264.5000,0.2220) (17.5500,455.0000,0.2220) (9.0000,455.0000,0.2220)};
 
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(15.2500,68.0000,0.0000) (17.6500,68.0000,0.0000) (17.6500,70.5000,0.0000) (15.2500,70.5000,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(15.2500,70.5000,0.0000) (17.6500,70.5000,0.0000) (17.6500,93.5000,0.0000) (15.2500,93.5000,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(15.2500,93.5000,0.0000) (17.6500,93.5000,0.0000) (17.6500,109.0000,0.0000) (15.2500,109.0000,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(15.2500,109.0000,0.0020) (17.6500,109.0000,0.0020) (17.6500,159.5000,0.0020) (15.2500,159.5000,0.0020)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(15.2500,159.5000,0.0230) (17.6500,159.5000,0.0230) (17.6500,259.0000,0.0230) (15.2500,259.0000,0.0230)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(15.2500,259.0000,0.0030) (17.6500,259.0000,0.0030) (17.6500,284.5000,0.0030) (15.2500,284.5000,0.0030)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(15.2500,284.5000,0.0625) (17.6500,284.5000,0.0625) (17.6500,455.0000,0.0625) (15.2500,455.0000,0.0625)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.5500,68.0000,0.0765) (23.9500,68.0000,0.0765) (23.9500,134.5000,0.0765) (17.5500,134.5000,0.0765)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.5500,134.5000,0.0260) (23.9500,134.5000,0.0260) (23.9500,159.5000,0.0260) (17.5500,159.5000,0.0260)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.5500,159.5000,0.0085) (23.9500,159.5000,0.0085) (23.9500,169.5000,0.0085) (17.5500,169.5000,0.0085)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.5500,169.5000,0.1225) (23.9500,169.5000,0.1225) (23.9500,259.0000,0.1225) (17.5500,259.0000,0.1225)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.5500,259.0000,0.0070) (23.9500,259.0000,0.0070) (23.9500,264.5000,0.0070) (17.5500,264.5000,0.0070)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.5500,264.5000,0.0355) (23.9500,264.5000,0.0355) (23.9500,455.0000,0.0355) (17.5500,455.0000,0.0355)};
 
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.6500,68.0000,0.0000) (20.9000,68.0000,0.0000) (20.9000,70.5000,0.0000) (17.6500,70.5000,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.6500,70.5000,0.0000) (20.9000,70.5000,0.0000) (20.9000,93.5000,0.0000) (17.6500,93.5000,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.6500,93.5000,0.0070) (20.9000,93.5000,0.0070) (20.9000,109.0000,0.0070) (17.6500,109.0000,0.0070)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.6500,109.0000,0.0430) (20.9000,109.0000,0.0430) (20.9000,159.5000,0.0430) (17.6500,159.5000,0.0430)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.6500,159.5000,0.0880) (20.9000,159.5000,0.0880) (20.9000,259.0000,0.0880) (17.6500,259.0000,0.0880)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.6500,259.0000,0.0095) (20.9000,259.0000,0.0095) (20.9000,284.5000,0.0095) (17.6500,284.5000,0.0095)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.6500,284.5000,0.0225) (20.9000,284.5000,0.0225) (20.9000,455.0000,0.0225) (17.6500,455.0000,0.0225)};
-
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.9000,68.0000,0.0015) (25.6500,68.0000,0.0015) (25.6500,70.5000,0.0015) (20.9000,70.5000,0.0015)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.9000,70.5000,0.0060) (25.6500,70.5000,0.0060) (25.6500,93.5000,0.0060) (20.9000,93.5000,0.0060)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.9000,93.5000,0.0320) (25.6500,93.5000,0.0320) (25.6500,109.0000,0.0320) (20.9000,109.0000,0.0320)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.9000,109.0000,0.0945) (25.6500,109.0000,0.0945) (25.6500,159.5000,0.0945) (20.9000,159.5000,0.0945)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.9000,159.5000,0.0455) (25.6500,159.5000,0.0455) (25.6500,259.0000,0.0455) (20.9000,259.0000,0.0455)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.9000,259.0000,0.0000) (25.6500,259.0000,0.0000) (25.6500,284.5000,0.0000) (20.9000,284.5000,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.9000,284.5000,0.0070) (25.6500,284.5000,0.0070) (25.6500,455.0000,0.0070) (20.9000,455.0000,0.0070)};
-
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(25.6500,68.0000,0.0055) (28.9000,68.0000,0.0055) (28.9000,70.5000,0.0055) (25.6500,70.5000,0.0055)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(25.6500,70.5000,0.0110) (28.9000,70.5000,0.0110) (28.9000,93.5000,0.0110) (25.6500,93.5000,0.0110)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(25.6500,93.5000,0.0375) (28.9000,93.5000,0.0375) (28.9000,109.0000,0.0375) (25.6500,109.0000,0.0375)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(25.6500,109.0000,0.0545) (28.9000,109.0000,0.0545) (28.9000,159.5000,0.0545) (25.6500,159.5000,0.0545)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(25.6500,159.5000,0.0165) (28.9000,159.5000,0.0165) (28.9000,259.0000,0.0165) (25.6500,259.0000,0.0165)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(25.6500,259.0000,0.0000) (28.9000,259.0000,0.0000) (28.9000,284.5000,0.0000) (25.6500,284.5000,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(25.6500,284.5000,0.0035) (28.9000,284.5000,0.0035) (28.9000,455.0000,0.0035) (25.6500,455.0000,0.0035)};
-
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(28.9000,68.0000,0.0030) (46.6000,68.0000,0.0030) (46.6000,70.5000,0.0030) (28.9000,70.5000,0.0030)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(28.9000,70.5000,0.0995) (46.6000,70.5000,0.0995) (46.6000,93.5000,0.0995) (28.9000,93.5000,0.0995)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(28.9000,93.5000,0.0860) (46.6000,93.5000,0.0860) (46.6000,109.0000,0.0860) (28.9000,109.0000,0.0860)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(28.9000,109.0000,0.0605) (46.6000,109.0000,0.0605) (46.6000,159.5000,0.0605) (28.9000,159.5000,0.0605)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(28.9000,159.5000,0.0120) (46.6000,159.5000,0.0120) (46.6000,259.0000,0.0120) (28.9000,259.0000,0.0120)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(28.9000,259.0000,0.0000) (46.6000,259.0000,0.0000) (46.6000,284.5000,0.0000) (28.9000,284.5000,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(28.9000,284.5000,0.0005) (46.6000,284.5000,0.0005) (46.6000,455.0000,0.0005) (28.9000,455.0000,0.0005)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.9500,68.0000,0.3525) (46.6000,68.0000,0.3525) (46.6000,134.5000,0.3525) (23.9500,134.5000,0.3525)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.9500,134.5000,0.0770) (46.6000,134.5000,0.0770) (46.6000,159.5000,0.0770) (23.9500,159.5000,0.0770)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.9500,159.5000,0.0020) (46.6000,159.5000,0.0020) (46.6000,169.5000,0.0020) (23.9500,169.5000,0.0020)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.9500,169.5000,0.0210) (46.6000,169.5000,0.0210) (46.6000,259.0000,0.0210) (23.9500,259.0000,0.0210)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.9500,259.0000,0.0000) (46.6000,259.0000,0.0000) (46.6000,264.5000,0.0000) (23.9500,264.5000,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.9500,264.5000,0.0035) (46.6000,264.5000,0.0035) (46.6000,455.0000,0.0035) (23.9500,455.0000,0.0035)};
 

### 2015-11-16 test.tex
Add experiment part

 \begin{tikzpicture}
        \begin{axis}%[
            view={0}{90},
            xlabel=quantity of wine,
            ylabel=grape quality,
            colorbar,
            colormap/blackwhite
            ]
			%\addplot[color=red]{exp(x)};
            \addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0,0,   1) (1,0,   0) (1,1.25,0) (0,1.25,0.1)};
            \addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0,1.25,1) (1,1.25,0) (1,2,   0) (0,2,   0.2)};
            \addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0,2,   1) (1,2,   0) (1,3,   0) (0,3,   0.3)};
            \addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1,0,   1) (2.5,0,   0) (2.5,1.25,0) (1,1.25,0.15)};
            \addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1,1.25,1) (2.5,1.25,0) (2.5,2,   0) (1,2,   0.25)};
            \addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1,2,   1) (2.5,2,   0) (2.5,3,   0) (1,3,   0.05)};
            \addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5,0,   1) (3,0,   0) (3,1.25,0) (2.5,1.25,0.25)};
            \addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5,1.25,1) (3,1.25,0) (3,2,   0) (2.5,2,   0.1)};
            \addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5,2,   1) (3,2,   0) (3,3,   0) (2.5,3,   0.3)};
        \end{axis}
\end{tikzpicture}

### 2015-11-16 test2.tex
Add experiment part

--- 2015-11-16 graph_auto_exp1_distr_1_3.tex
@@
 			colorbar,
-			point meta min=0, point meta max=0.5,
+			point meta min=0, point meta max=0.25,
 			colormap={}{ gray(0cm)=(1); gray(1cm)=(0);},
 			colorbar style={
-			        ytick={0,0.05,...,0.5},
+			        ytick={0,0.05,...,0.25},
 			        yticklabel style={

### 2015-11-16 test_2.tex
Add experiment part

--- 2015-11-16 test.tex
@@
+\documentclass[crop,tikz]{standalone}
+
+\usepackage{pgfplots}
+\usepackage[separate-uncertainty=true,detect-mode=true]{siunitx}
+
+\begin{document}
+
     \begin{tikzpicture}
-        \begin{axis}%[
+        \begin{axis}[
             view={0}{90},
@@
             ]
-			%\addplot[color=red]{exp(x)};
-            \addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0,0,   1) (1,0,   0) (1,1.25,0) (0,1.25,0.1)};
+
+            \addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0,0,   1) (1,0,   1) (1,1.25,1) (0,1.25, 1)};
             \addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0,1.25,1) (1,1.25,0) (1,2,   0) (0,2,   0.2)};
             \addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0,2,   1) (1,2,   0) (1,3,   0) (0,3,   0.3)};
-            \addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1,0,   1) (2.5,0,   0) (2.5,1.25,0) (1,1.25,0.15)};
+
+            \addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1,0,   0) (2.5,0,   0) (2.5,1.25,0) (1,1.25,0)};
             \addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1,1.25,1) (2.5,1.25,0) (2.5,2,   0) (1,2,   0.25)};
             \addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1,2,   1) (2.5,2,   0) (2.5,3,   0) (1,3,   0.05)};
+
             \addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5,0,   1) (3,0,   0) (3,1.25,0) (2.5,1.25,0.25)};
@@
     \end{tikzpicture}
+
+    % \label{fig:plot_label}
+    % \caption{Probability density under MODL discretization for two variables from the Wine dataset}
+\end{document}

### 2015-11-16 BN_discretizer_paper.tex
misc

@@
 \usepackage{caption}
+\usepackage{siunitx}
+\usepackage{booktabs}
 % \usepackage[capitalize]{cleveref}
@@
 \newcommand{\floor}[1]{\lfloor #1 \rfloor}
+
+\newcommand{\discset}{\mathcal{M}}
 
@@
 
-Algorithm \ref{alg:disc_one} has an exponential $\bigo\paren{\paren{v'_\text{max}}^{n_p} \cdot N^2}$ runtime.
-This exponential runtime is severely limiting for networks with a large number of discretization edges.
+Algorithm \ref{alg:disc_one} has an exponential $\bigo\paren{\paren{v'_\text{max}}^{n_p} \cdot N^2}$ runtime which severely limits discretization in networks with a large number of discretization intervals or parent variables.
 This section introduces an approximation to the objective function that significantly reduces the runtime and still preserves the quality of discretization.
@@
 
-In Equation \ref{eq:example_approx}, each child carries two terms, as shown in the first set of square brackets, but the two parent variables only carry a total of three terms, as shown in the second set of square brackets.
+In Equation~\ref{eq:example_approx}, each child carries two terms, as shown in the first set of square brackets, but the two parent variables only carry a total of three terms, as shown in the second set of square brackets.
 In this case the child variables have greater effect than the parent variables even though the number of child and parent variables are the same.
-However, if $C_2$ has an additional parent $S_2$, as shown in the right graph of Figure \ref{fig:example_networks}, the importances of $C_2$ will be reduced, because the information from $C_2$ is now affected by $S_2$.
+However, if $C_2$ has an additional parent $S_2$, as shown in the right graph of Figure~\ref{fig:example_networks}, the importances of $C_2$ will be reduced, because the information from $C_2$ is now affected by $S_2$.
 This argument shows that the proposed method, both before and after approximation, indeed incorporates graph structure when discretizing continuous variables.
@@
 \begin{figure}[ht]
-  \label{fig:example_networks}
+  \centering
   \begin{tabular}{cc}
@@
   \caption{Two example networks}
+  \label{fig:example_networks}
 \end{figure}
@@
 \begin{equation}
-M_X = \curly{X_\text{min}, X_\text{min} + \delta, X_\text{min} + 2\delta, \ldots, \delta, X_\text{max}}\text{,}
+M_X = \curly{X_\text{min}, X_\text{min} + \delta, X_\text{min} + 2\delta, \ldots, X_\text{max}}\text{,}
 \end{equation}
@@
 
-The section describes experiments designed to test the soundness of the proposed method.
-The experiments were run on four datasets from the Irvine repository \citep{Lichman:2013}.
+This section describes experiments conducted to evaluate the proposed methods.
+All experiments were run on datasets from the publically available Irvine machine learning repository \citep{Lichman:2013}.
+Variables are labelled alphabetically in the order given on the dataset information webpage.
+Subscripts inducate the number of discretized intervals.
+Shaded nodes are originally discrete and unshaded nodes are originally continuous.
+
 For each dataset, the experiment consists of two parts.
@@
 In the second part, the Bayesian netowrk structure is not provided in advance, and it is learned along with the discretization process.
+\tim{We may not want to state this up front so we can modify what we show for each dataset.}
 
-For the case that network structure is given, a comparison between the proposed method and the MDL principle discretization is made.
-10-fold cross validation of log-likelihood on data set $D_{\text{all}}$ is calculated as follows: firstly, learn discretization policies of each continuous variables from train data $D_{\text{train}}$.
-Secondly, obtain conditional probability tables $\phi_{x^* \mid \Pi^*_x}$ from the discretized train data $D^*_{\text{train}}$.
-Thirdly, For a test data instance $(x_1,x_2, \ldots, x_n)$ from $D_{\text{test}}$, the likelihood is
+The discretizations are compared using the mean cross validated log-likelihood of the data set $D$ given the resulting graph structure $G$ and discretization policy set $\discset$.
+The log-likelihood contains two components,
+
 \begin{equation}
-P(x_1, \ldots, x_n) = \prod_{i=1}^{n} \phi_{x^*_i \mid \Pi^*_{x_i}} \cdot \left( {1\over{M'_{X_i}[j_i+1] - M'_{X_i}[j_i]}} \right)^{\boldsymbol{1}_{ \left\lbrace X_i \text{ is continuous}  \right\rbrace }}
+\ln p(D\mid G, \discset) = \ln P(D^*\mid G) + \ln p(D\mid \discset, D^*)\text{,}
 \end{equation}
-, where $M'_{X_i}$ is the augmented discretization policy on continuous variable $X_i$ such that $M'_{X_i}[1] = min(D_{\text{all},X})$, $M'_{X_i}[j] = M_{X_i}[j-1]$ for $j=2,...,k_i$, and $M'_{X_i}[k_i+1] = max(D_{\text{all},X})$, $k$ is the number of intervals of continuous variable $X_i$ after discretization.
-Furthermore, $M'_{X_i}[j_i] \leq x_i < M'_{X_i}[j_i +1]$.
-This can be interpreted as follows: once a discrete-valued Bayesian network is learned from train data, test data are sampled from the learned network.
-If data is continuous, then it is uniformly sampled from the corresponding discretization interval.
 
-\subsection{Dataset 1: Auto MPG} 
-\label{subsec:autompg}
+\noindent
+where $D$ is the original dataset and $D^*$ is the dataset discretized according to $\discset$.
+The log-likelihood of the discretized dataset is the Bayesian score evaluated with a uniform prior~\citep{neapolitan2004learning}:
+
+\begin{equation}
+  \ln P(D^*\mid G) = \sum_{i=1}^n \sum_{j=1}^{q_i} \ln\paren{
+    \frac{
+      \Gamma\paren{\alpha_{ij0}}
+    }{
+      \Gamma\paren{\alpha_{ij0} + m_{ij0}}
+    }
+  } + \sum_{k=1}^{r_i} \ln\paren{
+    \frac{
+      \Gamma\paren{\alpha_{ijk} + m_{ijk}}
+    }{
+      \Gamma\paren{\alpha_{ijk}}
+    }
+  }\text{.}
+\end{equation}
+
+\tim{We need to make sure everything is defined.}
+
+The log-likelihood of the original dataset given the discrete dataset is
+
+\begin{equation}
+  \ln p(D\mid \discset, D^*) = \sum_{i=1}^n \sum_{j=1}^{q_i} \sum_{k=1}^{r_i} m_{ijk} \ln\paren{
+    \frac{
+      1
+    }{
+      \discset^{(ij)}_{k+1} - \discset^{(ij)}_{k}
+    }
+  }\text{.}
+\end{equation}
+
+\subsection{Auto MPG Dataset}
 
 In this subsection, two experiments are conducted on the Auto MPG dataset from the Irvine repository \citep{Lichman:2013}.
-This dataset has 392 instances (delete the 6 instance with missing data) and eight variables.
-Three variables are discrete: $B$, $G$, and $H$ (in the following experiment, variables are named and ordered according to the dataset information webpage).
-They have 5, 13, and 3 cardinality numbers, respectively.
-In the first experiment, the network structure is given.
-In the second experiment, the network structure is not provided.
+The dataset has \num{392} instances after deleting the six instances with missing data, and eight variables.
+Three variables are discrete: $B$, $G$, and $H$ with cardinality 5, 13, and 3 respectively.
+Two expiriments are conducted, one with a given network structure and one in which the structure is learned.
 
-\subsubsection{Experiment 1 on Auto MPG dataset}
-\label{subsubsec:autompg_exp1}
-The proposed discretization method and the MDL discretization method are tested on the Bayesian network structure in Fig.
-\ref{Auto_graph_1}, which is obtained by running K2 algorithm 1000 times on prediscretized data, each time with a random restart.
-The prediscretization is done by equal-width discretization on continuous variables by 5 intervals (median of cardinalities of discrete variables).
-Shaded nodes in Fig.
-\ref{Auto_graph_1} means that they are discrete-valued variables.
+\subsubsection{Structure is Given}
+
+The proposed discretization method and the MDL discretization method are tested on Auto MPG data given the network network in Fig. \ref{Auto_graph_1}.
+The structure was obtained by prediscretizing each continuous variable into five uniform-width intervals, where five is the median cardinality of the discrete variables, and then taking the most frequent structure from a thousand runs of K2.
 
@@
   \end{tabular}
-  \caption{The Bayesian network obatined by K2 algorithm and prediscretization on Auto MPG dataset}
+  \caption{The Bayesian network obtained with K2 on the prediscretized Auto MPG dataset}
   \label{Auto_graph_1}
@@
 
-\begin{table}
+\begin{table}[h]
   \centering
-\scalebox{1.0}{
   \input{table_autoMPG_1.tex}
-}
-\caption{Discretization result of Auto MPG dataset based on the graph in Fig. \ref{Auto_graph_1}}
+  \caption{Discretization result of Auto MPG dataset based on the graph in Fig.
+\ref{Auto_graph_1}.
+The discretization policy for the heuristic matches that for the optimal Bayesian approach.
+\todo{Need to explain why MDL fails}}
   \label{Auto_MPG_disc_table_1}
@@
 
-\subsubsection{Experiment 2 on Auto MPG dataset}
-\label{subsubsec:autompg_exp2}
+\subsubsection{Structure is Learned}
 

### 2015-11-16 BN_discretizer_paper.tex
fixed mathbb err

@@
 \usepackage{amsmath}
+\usepackage{amssymb}
 \usepackage{bm}
@@
 
-A discretization policy $M_C = \anglebrackets{t_1 < t_2 < \ldots < t_{k-1}}$ for a continuous variable $C$ is a mapping from !!! mathbb{R} !!! to $\brock{1,2,3,\ldots,k}$ such that
+A discretization policy $M_C = \anglebrackets{t_1 < t_2 < \ldots < t_{k-1}}$ for a continuous variable $C$ is a mapping from $\mathbb{R}$ to $\brock{1,2,3,\ldots,k}$ such that
 \begin{equation}

### 2015-11-17 BN_discretizer_paper.tex
looking at variable definitions

@@
 \newcommand{\tim}[1]{\textit{\textcolor{blue}{#1}}}
+\newcommand{\mykel}[1]{\textit{\textcolor{cyan}{#1}}}
 
@@
 They provide an efficient factorization of the joint probability distribution over a set of random variables.
-Bayesian networks first emerged from artificial intelligence research and have been applied to a wide variety of problems, ranging from decision-making systems \citep{DMU_2015} to medical diagnoses \citep{Lustgarten_2011}.
+Bayesian networks first emerged from artificial intelligence research and have been applied to a wide variety of problems, ranging from decision-making systems \citep{DMU_2015}\mykel{better to use a primary source} to medical diagnoses \citep{Lustgarten_2011}.
 In most cases, we assume that all random variables in Bayesian networks are discrete, since many Bayesian network learning algorithms are unable to deal with continuous variables efficiently.
 However, many applications
-require the use of continuous variables, such as position and velocity in dynamic systems.
+require the use of continuous variables, such as position and velocity in dynamic systems \mykel{cite Kochenderfer JGCD article on encounter modeling}.
 
@@
 For other parametric distributions \citep{Ihler_2009} and non-linear functions~\todo{[cite]}, these redesigned algorithms are computationally expensive and do not perform well.
+\mykel{$\bigstar$ We need to discuss this; talk about algorithms for inference and structure learning, expectation propagation, Gibbs, BVGS}
 
@@
 
-\subsection{MDL Principle Discretization}
-The MDL principle was first proposed by \cite{MDL_1978}, and states that the best model for a dataset is one which minimizes the amount of information needed to describe it \citep{Grunwald_2009}.
+\subsection{MDL Discretization}
+The MDL principle was first proposed by \cite{MDL_1978} and states that the best model for a dataset is one that minimizes the amount of information needed to describe it \citep{Grunwald_2009}.
 MDL methods trade off goodness-of-fit against model complexity to reduce generalization error.
-In the context of Bayesian networks, \cite{Friedman_1996} applied the MDL principle to determine the optimal number of discretization intervals for continuous variables and optimal the positions of their discretization boundaries.
+In the context of Bayesian networks, \cite{Friedman_1996} applied the MDL principle to determine the optimal number of discretization intervals for continuous variables and the optimal positions of their discretization boundaries.
 Their approach selects a discretization policy that minimizes the sum of the description lengths of the discretized Bayesian network and the information necessary for recovering the continuous values from the discretized data.
-In the single continuous variable case, the objective function is
+For a Bayesian network with a single continuous variable $X$, the objective function is
 
@@
 
+\mykel{$\bigstar\Pi_{X_i}$ is not defined until later}
+\tim{$\Pi_{X_i}$ may be confusing with our use of $\prod_{i=1}^n$ later on.}
+
 \noindent
 % $I(\boldsymbol{A},\boldsymbol{B}) =  \sum_{\boldsymbol{a},\boldsymbol{b}} \hat{P}_D (\boldsymbol{a},\boldsymbol{b}) \log {{\hat{P}_D (\boldsymbol{a},\boldsymbol{b})}\over{\hat{P}_D (\boldsymbol{a}),\hat{P}_D (\boldsymbol{b})}}$
-where $I(\boldsymbol{A},\boldsymbol{B})$ is the mutual information between the discrete variables $\boldsymbol{A}$ and $\boldsymbol{B}$, ${H(p) = -p \log(p) - (1-p) \log(1-p)}$, $|\boldsymbol{X}|$ is the cardinality of discrete variable $\boldsymbol{X}$, and $X^*_i$ is the discretized version of the $i$th sample of continuous variable $X$.
+where $I(A,B)$ is the mutual information between the discrete variables $A$ and $B$, ${H(p) = -p \log(p) - (1-p) \log(1-p)}$ \tim{does $H(p)$ have a name?
+Entropy?}, $|A|$ is the cardinality of a discrete variable $A$, and $X^*_i$ is the discretized version of the $i$th sample of $X$.
+\tim{What are $N$, and $N_i$?}
 The optimal discretization policy can be found with dynamical programming.
@@
 It is based on the minimum description length principle (MDL): the optimal discretization policy minimizes the description length of the Bayesian network and discretization policy.
-The MDL algorithm has a $\bigo\paren{N^3 + \paren{n_c {v_\text{max}}^{(n_c^p)_\text{max}} + {v_\text{max}}^{n_p}} \cdot N^2}$ runtime on Bayesian networks with a single continuous variable and multiple discrete variables, where $N$ is the number of data samples from the joint distribution, $n_p$ and $n_c$ are the numbers of parent and children variables for the continuous variable, $v_\text{max}$ is the largest cardinality over all variables in the Markov blanket, and  ${(n_c^p)_\text{max}}$ is the largest number of parent variables of the continuous variable's children.
+The MDL algorithm has an $\bigo\paren{N^3 + \paren{n_c {v_\text{max}}^{(n_c^p)_\text{max}} + {v_\text{max}}^{n_p}} \cdot N^2}$ runtime on Bayesian networks with a single continuous variable and multiple discrete variables, where $N$ is the number of data samples from the joint distribution, $n_p$ and $n_c$ are the numbers of parent and children variables for the continuous variable, $v_\text{max}$ is the largest cardinality over all variables in the Markov blanket, and  ${(n_c^p)_\text{max}}$ is the largest number of parent variables of the continuous variable's children.
 The MDL method iterates over all continuous variables until convergence in the case of multiple continuous variables, converging in a few cycles according to our tests of real-world data.
-Unfortunately, MDL tends to produce discrete variables with low cardinality~\todo{[cite]}.
+Unfortunately, MDL tends to produce discrete variables with low cardinality~\todo{[cite]}\mykel{don't like low-cardinality.
+Maybe 'intervals' or something instead}.
 
@@
 
-The MODL method uses dynamic programming to find the optimal discretization policy, and has a $\bigo\paren{N^3 + |\text{Class}| \cdot N^2}$ runtime, where $N$ is the of number of data instances.
+The MODL method uses dynamic programming to find the optimal discretization policy, and has an $\bigo\paren{N^3 + |\text{Class}| \cdot N^2}$ runtime, where $N$ is the of number of data instances.
 \cite{Lustgarten_2011} suggest several formulations for the prior term $P(\text{Model})$.
@@
 
-A Bayesian network $B$ is defined by a pair $(G,\Theta)$, where $G = (X,E)$ is a directed acyclic graph whose nodes correspond to a set of random variables $X = \brock{X_1, X_2, \cdots, X_n}$, and whose edges $E$ represent probabilistic dependencies among nodes.
+\mykel{This all needs to be explained better. Too many variables are being defined at once.}
+A Bayesian network $B$ is defined by a pair $(G,\Theta)$, where $G = (X,E)$ is a directed acyclic graph whose nodes correspond to a set of random variables $X = \brock{X_1, X_2, \ldots, X_n}$, and whose edges $E$ represent probabilistic dependencies among nodes.
 The graph structure $G$ encodes the Markov property: each node $X_i$ is independent of its non-descendants given its parents $\Pi_{X_i}$ in $G$.
@@
 The joint distribution over $X$ factors according to the Markov property:
+
 \begin{equation}
-P_B (X_1 , \cdots, X_n) = \prod_{i=1}^{n} P_B (X_i \mid \Pi_{X_i}) = \prod_{i=1}^{n} \theta_{x_i \mid \Pi_{x_i}}\text{.}
+P_B (X_1 , \ldots, X_n) = \prod_{i=1}^{n} P_B (X_i \mid \Pi_{X_i}) = \prod_{i=1}^{n} \theta_{x_i \mid \Pi_{x_i}}\text{.}
 \end{equation}
@@
 Variables are sampled in topological order such that parental instantiations are always known~\citep[see][chap.~22]{algo_2009}.
+\mykel{I think this ref is just for the topological sort; for sampling, cite DMU or PGM}
 Furthermore, the parent $\rightarrow$ child sampling order can be reversed if the marginal probability of the child variable is known.
@@
 \begin{equation}
-P(X_i \mid \Pi_{X_i}) \cdot \prod_{j = 1}^{ Pa( X_i)} P( \{ \Pi_{X_i} \}_j) = P(X_i) \cdot P(\Pi_{X_i} \mid X_i),
+P(X_i \mid \Pi_{X_i}) \cdot \prod_{j = 1}^{ Pa( X_i)} P( \brock{\Pi_{X_i} }_j) = P(X_i) \cdot P(\Pi_{X_i} \mid X_i),
 \end{equation}
@@
 where $Pa(X_i)$ is the number of parents of $X_i$ and $\brock{\Pi_{X_i}}_j$ is the $j$th parent of $X_i$.
+\mykel{this may be messed up. Maybe use DMU notation?}
 % One can first sample $X_i$ by $P(X_i)$, then sample all the parent variables simultaneously by $P(\Pi_{X_i} \mid X_i)$. That is to say, $X_i$ becomes the starting point of sampling.
@@
 
+\tim{We need to adopt the same notation everywhere; $C$ should be a child, not a continuous variable}.
 A discretization policy $M_C = \anglebrackets{t_1 < t_2 < \ldots < t_{k-1}}$ for a continuous variable $C$ is a mapping from $\mathbb{R}$ to $\brock{1,2,3,\ldots,k}$ such that
@@
 The policy discretizes the continuous variable $C$ into $k$ intervals.
-The discretization edges $t_\cdot$ are restricted to the midpoints between two sorted instances of $C$.
+The discretization edges $t_{1:k-1}$ are restricted to the midpoints between two sorted instances of $C$.
 An integer representation of $M_C$ can be obtained by sorting the samples of $C$ in an increasing order, $\curly{c_1,c_2,\ldots,c_N}$, and if $t_i = (c_{s_{i}} + c_{s_{i}+1})/2$ for $i=1,2,\ldots,k$, then $M_C = \anglebrackets{t_1,t_2, \ldots, t_{k-1}} \equiv \brock{n_1,n_2,..n_k}$, where $n_1 = s_1$ and $n_i = s_{i} - s_{i-1}$.
+\mykel{Where did $s_i$ come from?}
 
@@
 
-\section{Discretization of a Single Continuous Variable}
+\section{Single Variable Discretization}
 \label{sec:single_var}
@@
 It follows that a discretization policy $M$ on $X$ can be written as $M_X = \brock{n_1,n_2,\ldots,n_k}$, where $k$, $n_1$, $n_2$, $\ldots,n_k$ are positive integers satisfying $N = \sum_{i=1}^k n_i$.
+\mykel{$\bigstar$ This conflicts with Section 3.2, right?}
 An optimal discretization policy maximizes $P(M)\cdot P(D\mid M)$ for some prior $P(M)$ and likelihood $P(D\mid M)$.
@@
 
-The following four principles for the optimal discretization policy, modivated by MODL, enable the formulation of $P(M)$ and $P(D \mid M)$:
+The following four principles for the optimal discretization policy, motivated by MODL, enable the formulation of $P(M)$ and $P(D \mid M)$:
 \begin{enumerate}
@@
 \end{equation}
-where $L$ is the largest cardinality number of discrete variables in $X$'s Markov blanket. \tim{Where does this come from? Is there an intuitive explanation?}
+where $L$ is the largest cardinality number of discrete variables in $X$'s Markov blanket. \tim{Where does this come from? Is there an intuitive explanation?}\mykel{$\bigstar$}
 \item For a given interval of $M$, every distribution of $\Pi_X$ is equiprobable.
-\item For each pair of $(C_i,\boldsymbol{S_i})$ and a given interval of $M$, every distribution of $C_i$ with a value of $\boldsymbol{S_i}$ is equiprobable.
-\item The distributions of each $C_i$ and $\Pi_X$ in each interval of $M$ with each value of $\boldsymbol{S_i}$ are independent from each other.
+\item For each pair of $(C_i,\boldsymbol{S_i})$ and a given interval of $M$, every distribution of $C_i$ with a value of $\boldsymbol{S_i}$ is equiprobable.\mykel{$\bigstar$}
+\item The distributions of each $C_i$ and $\Pi_X$ in each interval of $M$ with each value of $\boldsymbol{S_i}$ are independent from each other.\mykel{$\bigstar$}
 \end{enumerate}
@@
 \begin{equation}
+\label{eq:p_M}
 P(M) = \prod_{i=1}^k \curly{ \brock{1 - {\exp(- L \cdot {{x_{s_i+1} - x_{s_i}}\over{x_N - x_1}})}} \cdot \exp\paren{L \cdot {{x_{s_{i}} - x_{s_{i-1} + 1}}\over{x_N - x_1}}}},
@@
 \begin{equation}
+\label{eq:p_D_given_M}
 P\paren{D \mid M} \propto P\paren{D_{\Pi_x} \mid M} \cdot \prod_{i = 1}^{n_c} P\paren{D_{C_i} \mid M, D_{\boldsymbol{S_i}}}\text{.}
@@
 According to the forth prior, these distributions are independent from each other, and one thus takes their product.
-If $S_j = \emptyset$, then Equation \ref{eq:likelihood_two} is equivalent to
+If $S_j = \emptyset$, then Equation~\ref{eq:likelihood_two} is equivalent to
 
@@
 
-The objective function can be formulated given equations \ref{eq:p_M}, \ref{eq:p_D_given_M},\ref{eq:likelihood_one}, and \ref{eq:likelihood_three}.
+The objective function can be formulated given equations \ref{eq:p_M}, \ref{eq:p_D_given_M}, \ref{eq:likelihood_one}, and \ref{eq:likelihood_three}.
 The log-inverse of $P(M) \cdot P(D|M)$ is minimized for computational convenience:
@@
 
-Now we are able to solve the optimization problem over Equation \ref{eq:opt_prob}.
-The dynamic programming procedure is shown in Algorithm \ref{alg:disc_one}.
+Now we are able to solve the optimization problem over Equation~\ref{eq:opt_prob}.
+The dynamic programming procedure is shown in Algorithm~\ref{alg:disc_one}.
 It takes two inputs: $D$, the joint samples over all variables sorted in ascending order according to $D_X$, and $G$, the network structure.
@@
 This section introduces an approximation to the objective function that significantly reduces the runtime and still preserves the quality of discretization.
-The approximation replaces the dominator of the last factor in Equation \ref{eq:likelihood_one} with
+The approximation replaces the dominator of the last factor in Equation~\ref{eq:likelihood_one} with
 
@@
 
-The approximation reduces the runtime of Algorithm \ref{alg:disc_one} to a polynomial, $\bigo\paren{ {v'_\text{max}} \cdot (n_c + n_p) \cdot N^2}$.
-It will be shown in Section \ref{sec:experiments} that the approximation is more sensitive to the distribution over other variables and is biased towards slightly higher interval counts.
+The approximation reduces the runtime of Algorithm~\ref{alg:disc_one} to a polynomial, $\bigo\paren{ {v'_\text{max}} \cdot (n_c + n_p) \cdot N^2}$.
+It will be shown in Section~\ref{sec:experiments} that the approximation is more sensitive to the distribution over other variables and is biased towards slightly higher interval counts.
 \tim{We need to have a more specific thing to say along the lines of When does it fail?}
 
-With the approximated objective function, Equation \ref{eq:opt_prob_approx}, provides intuition into how child and parent variables contribute to the objective function.
-For example, in the left graph of Figure \ref{fig:example_networks}, the corresponding square brackets in the approximated objective function are
+With the approximated objective function, Equation~\ref{eq:opt_prob_approx}, provides intuition into how child and parent variables contribute to the objective function.
+For example, in the left graph of Figure~\ref{fig:example_networks}, the corresponding square brackets in the approximated objective function are
 
@@
     \For {$i =1$ to $n$}
-      \State $P_{old} \leftarrow f(X^*_i,\Pi_{X^*_i})$: Equation \ref{eq:f_x_p}
+      \State $P_{old} \leftarrow f(X^*_i,\Pi_{X^*_i})$: Equation~\ref{eq:f_x_p}
       \State OKToProceed $\leftarrow$ \textbf{true}

### 2015-11-17 graph_wine_exp1_distr.tex
add wine exp plots

\begin{tikzpicture}
  \begin{groupplot}[group style={group size=1 by 2}]%,xmin=0,ymin=0,height=4cm,width=5cm,no markers]
  \nextgroupplot[
			view={0}{90},
			enlargelimits=0,
			zmin=0.0, zmax=1.0,
			ylabel=K,
			colorbar right,
    every colorbar/.append style={height=
        2*\pgfkeysvalueof{/pgfplots/parent axis height}+
        \pgfkeysvalueof{/pgfplots/group/vertical sep}},
			point meta min=0, point meta max=0.5,
			colormap={}{ gray(0cm)=(1); gray(1cm)=(0);},
			colorbar style={
			        ytick={0,0.05,...,0.5},
			        yticklabel style={
			            text width=2.5em,
			            align=right,
			            /pgf/number format/.cd,
			                fixed,
			                fixed zerofill
			        }
			    }
			]

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.6000,1.2800,0.0495) (17.9000,1.2800,0.0495) (17.9000,3.4600,0.0495) (10.6000,3.4600,0.0495)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.6000,3.4600,0.0725) (17.9000,3.4600,0.0725) (17.9000,4.8500,0.0725) (10.6000,4.8500,0.0725)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.6000,4.8500,0.1445) (17.9000,4.8500,0.1445) (17.9000,7.4000,0.1445) (10.6000,7.4000,0.1445)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.6000,7.4000,0.0205) (17.9000,7.4000,0.0205) (17.9000,13.0000,0.0205) (10.6000,13.0000,0.0205)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.9000,1.2800,0.2060) (23.2500,1.2800,0.2060) (23.2500,3.4600,0.2060) (17.9000,3.4600,0.2060)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.9000,3.4600,0.1095) (23.2500,3.4600,0.1095) (23.2500,4.8500,0.1095) (17.9000,4.8500,0.1095)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.9000,4.8500,0.1600) (23.2500,4.8500,0.1600) (23.2500,7.4000,0.1600) (17.9000,7.4000,0.1600)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.9000,7.4000,0.1100) (23.2500,7.4000,0.1100) (23.2500,13.0000,0.1100) (17.9000,13.0000,0.1100)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.2500,1.2800,0.0485) (30.0000,1.2800,0.0485) (30.0000,3.4600,0.0485) (23.2500,3.4600,0.0485)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.2500,3.4600,0.0255) (30.0000,3.4600,0.0255) (30.0000,4.8500,0.0255) (23.2500,4.8500,0.0255)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.2500,4.8500,0.0230) (30.0000,4.8500,0.0230) (30.0000,7.4000,0.0230) (23.2500,7.4000,0.0230)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.2500,7.4000,0.0305) (30.0000,7.4000,0.0305) (30.0000,13.0000,0.0305) (23.2500,13.0000,0.0305)};

			\addplot3[mark=+, draw=none, mark size=0.7] coordinates {
(15.600,5.640,1) (11.200,4.380,1) (18.600,5.680,1) (16.800,7.800,1) (21.000,4.320,1) (15.200,6.750,1) (14.600,5.250,1) (17.600,5.050,1) (14.000,5.200,1) (16.000,7.220,1) (18.000,5.750,1) (16.800,5.000,1) (16.000,5.600,1) (11.400,5.400,1) (12.000,7.500,1) (17.200,7.300,1) (20.000,6.200,1) (20.000,6.600,1) (16.500,8.700,1) (15.200,5.100,1) (16.000,5.650,1) (18.600,4.500,1) (16.600,3.800,1) (17.800,3.930,1) (20.000,3.520,1) (25.000,3.580,1) (16.100,4.800,1) (17.000,3.950,1) (19.400,4.500,1) (16.000,4.700,1) (22.500,5.700,1) (19.100,6.900,1) (17.200,3.840,1) (19.500,5.400,1) (19.000,4.200,1) (20.500,5.100,1) (15.500,4.600,1) (18.000,4.250,1) (15.500,3.700,1) (13.200,5.100,1) (16.200,6.130,1) (18.800,4.280,1) (15.000,5.430,1) (17.500,4.360,1) (17.000,5.040,1) (18.900,5.240,1) (16.000,4.900,1) (16.000,6.100,1) (18.800,6.200,1) (17.400,8.900,1) (12.400,7.200,1) (17.200,5.600,1) (14.000,7.050,1) (17.100,6.300,1) (16.400,5.850,1) (20.500,6.250,1) (16.300,6.380,1) (16.800,6.000,1) (16.700,6.800,1) (10.600,1.950,1) (16.000,3.270,1) (16.800,5.750,1) (18.000,3.800,1) (19.000,4.450,1) (19.000,2.950,1) (18.100,4.600,1) (15.000,5.300,1) (19.600,4.680,1) (17.000,3.170,1) (16.800,2.850,1) (20.400,3.050,1) (25.000,3.380,1) (24.000,3.740,1) (30.000,3.350,1) (21.000,3.210,1) (16.000,3.800,1) (16.000,4.600,1) (18.000,2.650,1) (14.800,3.400,1) (23.000,2.570,1) (19.000,2.500,1) (18.800,3.900,1) (24.000,2.200,1) (22.500,4.800,1) (18.000,3.050,1) (18.000,2.620,1) (22.800,2.450,1) (26.000,2.600,1) (21.600,2.800,1) (23.600,1.740,1) (18.500,2.400,1) (22.000,3.600,1) (20.700,3.050,1) (18.000,2.150,1) (18.000,3.250,1) (19.000,2.600,1) (21.500,2.500,1) (16.000,2.900,1) (18.500,4.500,1) (18.000,2.300,1) (17.500,3.300,1) (18.500,2.450,1) (21.000,2.800,1) (19.500,2.060,1) (20.500,2.940,1) (22.000,2.700,1) (19.000,3.400,1) (22.500,3.300,1) (19.000,2.700,1) (20.000,2.650,1) (19.500,2.900,1) (21.000,2.000,1) (20.000,3.800,1) (21.000,3.080,1) (22.500,2.900,1) (21.500,1.900,1) (20.800,1.950,1) (22.500,2.060,1) (16.000,3.400,1) (19.000,1.280,1) (20.000,3.250,1) (28.500,6.000,1) (26.500,2.080,1) (21.500,2.600,1) (21.000,2.800,1) (21.000,2.760,1) (21.500,3.940,1) (28.500,3.000,1) (24.500,2.120,1) (22.000,2.600,1) (18.000,4.100,1) (20.000,5.400,1) (24.000,5.700,1) (21.500,5.000,1) (17.500,5.450,1) (18.500,7.100,1) (21.000,3.850,1) (25.000,5.000,1) (19.500,5.700,1) (24.000,4.920,1) (21.000,4.600,1) (20.000,5.600,1) (23.500,4.350,1) (20.000,4.400,1) (18.500,8.210,1) (21.000,4.000,1) (20.000,4.900,1) (21.500,7.650,1) (21.500,8.420,1) (21.500,9.400,1) (24.000,8.600,1) (22.000,10.800,1) (25.500,7.100,1) (18.500,10.520,1) (20.000,7.600,1) (22.000,7.900,1) (19.500,9.010,1) (27.000,7.500,1) (25.000,13.000,1) (22.500,11.750,1) (21.000,7.650,1) (20.000,5.880,1) (22.000,5.580,1) (18.500,5.280,1) (22.000,9.580,1) (22.500,6.620,1) (23.000,10.680,1) (19.500,10.260,1) (24.500,8.660,1) (25.000,8.500,1) (19.000,5.500,1) (19.500,9.900,1) (20.000,9.700,1) (20.500,7.700,1) (23.000,7.300,1) (20.000,10.200,1) (20.000,9.300,1) (24.500,9.200,1) };

    \nextgroupplot[
			view={0}{90},
			enlargelimits=0,
			zmin=0.0, zmax=1.0,
			xlabel=E,
			ylabel=K,
			%colorbar,
			point meta min=0, point meta max=0.5,
			colormap={}{ gray(0cm)=(1); gray(1cm)=(0);}
			%colorbar style={
			 %       ytick={0,0.05,...,0.5},
			  %      yticklabel style={
			   %         text width=2.5em,
			    %        align=right,
			     %       /pgf/number format/.cd,
			      %          fixed,
			       %         fixed zerofill
			        %}
			    %}
			]

    		\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.6000,1.2800,0.0565) (17.9000,1.2800,0.0565) (17.9000,3.4600,0.0565) (10.6000,3.4600,0.0565)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.6000,3.4600,0.2210) (17.9000,3.4600,0.2210) (17.9000,7.5500,0.2210) (10.6000,7.5500,0.2210)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.6000,7.5500,0.0145) (17.9000,7.5500,0.0145) (17.9000,13.0000,0.0145) (10.6000,13.0000,0.0145)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.9000,1.2800,0.2440) (30.0000,1.2800,0.2440) (30.0000,3.4600,0.2440) (17.9000,3.4600,0.2440)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.9000,3.4600,0.3195) (30.0000,3.4600,0.3195) (30.0000,7.5500,0.3195) (17.9000,7.5500,0.3195)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.9000,7.5500,0.1445) (30.0000,7.5500,0.1445) (30.0000,13.0000,0.1445) (17.9000,13.0000,0.1445)};

			\addplot3[mark=+, draw=none, mark size=0.7] coordinates {
(15.600,5.640,1) (11.200,4.380,1) (18.600,5.680,1) (16.800,7.800,1) (21.000,4.320,1) (15.200,6.750,1) (14.600,5.250,1) (17.600,5.050,1) (14.000,5.200,1) (16.000,7.220,1) (18.000,5.750,1) (16.800,5.000,1) (16.000,5.600,1) (11.400,5.400,1) (12.000,7.500,1) (17.200,7.300,1) (20.000,6.200,1) (20.000,6.600,1) (16.500,8.700,1) (15.200,5.100,1) (16.000,5.650,1) (18.600,4.500,1) (16.600,3.800,1) (17.800,3.930,1) (20.000,3.520,1) (25.000,3.580,1) (16.100,4.800,1) (17.000,3.950,1) (19.400,4.500,1) (16.000,4.700,1) (22.500,5.700,1) (19.100,6.900,1) (17.200,3.840,1) (19.500,5.400,1) (19.000,4.200,1) (20.500,5.100,1) (15.500,4.600,1) (18.000,4.250,1) (15.500,3.700,1) (13.200,5.100,1) (16.200,6.130,1) (18.800,4.280,1) (15.000,5.430,1) (17.500,4.360,1) (17.000,5.040,1) (18.900,5.240,1) (16.000,4.900,1) (16.000,6.100,1) (18.800,6.200,1) (17.400,8.900,1) (12.400,7.200,1) (17.200,5.600,1) (14.000,7.050,1) (17.100,6.300,1) (16.400,5.850,1) (20.500,6.250,1) (16.300,6.380,1) (16.800,6.000,1) (16.700,6.800,1) (10.600,1.950,1) (16.000,3.270,1) (16.800,5.750,1) (18.000,3.800,1) (19.000,4.450,1) (19.000,2.950,1) (18.100,4.600,1) (15.000,5.300,1) (19.600,4.680,1) (17.000,3.170,1) (16.800,2.850,1) (20.400,3.050,1) (25.000,3.380,1) (24.000,3.740,1) (30.000,3.350,1) (21.000,3.210,1) (16.000,3.800,1) (16.000,4.600,1) (18.000,2.650,1) (14.800,3.400,1) (23.000,2.570,1) (19.000,2.500,1) (18.800,3.900,1) (24.000,2.200,1) (22.500,4.800,1) (18.000,3.050,1) (18.000,2.620,1) (22.800,2.450,1) (26.000,2.600,1) (21.600,2.800,1) (23.600,1.740,1) (18.500,2.400,1) (22.000,3.600,1) (20.700,3.050,1) (18.000,2.150,1) (18.000,3.250,1) (19.000,2.600,1) (21.500,2.500,1) (16.000,2.900,1) (18.500,4.500,1) (18.000,2.300,1) (17.500,3.300,1) (18.500,2.450,1) (21.000,2.800,1) (19.500,2.060,1) (20.500,2.940,1) (22.000,2.700,1) (19.000,3.400,1) (22.500,3.300,1) (19.000,2.700,1) (20.000,2.650,1) (19.500,2.900,1) (21.000,2.000,1) (20.000,3.800,1) (21.000,3.080,1) (22.500,2.900,1) (21.500,1.900,1) (20.800,1.950,1) (22.500,2.060,1) (16.000,3.400,1) (19.000,1.280,1) (20.000,3.250,1) (28.500,6.000,1) (26.500,2.080,1) (21.500,2.600,1) (21.000,2.800,1) (21.000,2.760,1) (21.500,3.940,1) (28.500,3.000,1) (24.500,2.120,1) (22.000,2.600,1) (18.000,4.100,1) (20.000,5.400,1) (24.000,5.700,1) (21.500,5.000,1) (17.500,5.450,1) (18.500,7.100,1) (21.000,3.850,1) (25.000,5.000,1) (19.500,5.700,1) (24.000,4.920,1) (21.000,4.600,1) (20.000,5.600,1) (23.500,4.350,1) (20.000,4.400,1) (18.500,8.210,1) (21.000,4.000,1) (20.000,4.900,1) (21.500,7.650,1) (21.500,8.420,1) (21.500,9.400,1) (24.000,8.600,1) (22.000,10.800,1) (25.500,7.100,1) (18.500,10.520,1) (20.000,7.600,1) (22.000,7.900,1) (19.500,9.010,1) (27.000,7.500,1) (25.000,13.000,1) (22.500,11.750,1) (21.000,7.650,1) (20.000,5.880,1) (22.000,5.580,1) (18.500,5.280,1) (22.000,9.580,1) (22.500,6.620,1) (23.000,10.680,1) (19.500,10.260,1) (24.500,8.660,1) (25.000,8.500,1) (19.000,5.500,1) (19.500,9.900,1) (20.000,9.700,1) (20.500,7.700,1) (23.000,7.300,1) (20.000,10.200,1) (20.000,9.300,1) (24.500,9.200,1) };
  \end{groupplot}
\end{tikzpicture}

### 2015-11-17 graph_wine_exp1_distr_5_11.tex
add wine exp plots

--- 2015-11-17 graph_wine_exp1_distr.tex
@@
 	\begin{tikzpicture}
-  \begin{groupplot}[group style={group size=1 by 2}]%,xmin=0,ymin=0,height=4cm,width=5cm,no markers]
-  \nextgroupplot[
+		\begin{axis}[
 			view={0}{90},
@@
 			zmin=0.0, zmax=1.0,
+			xlabel=E,
 			ylabel=K,
-			colorbar right,
-    every colorbar/.append style={height=
-        2*\pgfkeysvalueof{/pgfplots/parent axis height}+
-        \pgfkeysvalueof{/pgfplots/group/vertical sep}},
+			colorbar,
 			point meta min=0, point meta max=0.5,
@@
 (15.600,5.640,1) (11.200,4.380,1) (18.600,5.680,1) (16.800,7.800,1) (21.000,4.320,1) (15.200,6.750,1) (14.600,5.250,1) (17.600,5.050,1) (14.000,5.200,1) (16.000,7.220,1) (18.000,5.750,1) (16.800,5.000,1) (16.000,5.600,1) (11.400,5.400,1) (12.000,7.500,1) (17.200,7.300,1) (20.000,6.200,1) (20.000,6.600,1) (16.500,8.700,1) (15.200,5.100,1) (16.000,5.650,1) (18.600,4.500,1) (16.600,3.800,1) (17.800,3.930,1) (20.000,3.520,1) (25.000,3.580,1) (16.100,4.800,1) (17.000,3.950,1) (19.400,4.500,1) (16.000,4.700,1) (22.500,5.700,1) (19.100,6.900,1) (17.200,3.840,1) (19.500,5.400,1) (19.000,4.200,1) (20.500,5.100,1) (15.500,4.600,1) (18.000,4.250,1) (15.500,3.700,1) (13.200,5.100,1) (16.200,6.130,1) (18.800,4.280,1) (15.000,5.430,1) (17.500,4.360,1) (17.000,5.040,1) (18.900,5.240,1) (16.000,4.900,1) (16.000,6.100,1) (18.800,6.200,1) (17.400,8.900,1) (12.400,7.200,1) (17.200,5.600,1) (14.000,7.050,1) (17.100,6.300,1) (16.400,5.850,1) (20.500,6.250,1) (16.300,6.380,1) (16.800,6.000,1) (16.700,6.800,1) (10.600,1.950,1) (16.000,3.270,1) (16.800,5.750,1) (18.000,3.800,1) (19.000,4.450,1) (19.000,2.950,1) (18.100,4.600,1) (15.000,5.300,1) (19.600,4.680,1) (17.000,3.170,1) (16.800,2.850,1) (20.400,3.050,1) (25.000,3.380,1) (24.000,3.740,1) (30.000,3.350,1) (21.000,3.210,1) (16.000,3.800,1) (16.000,4.600,1) (18.000,2.650,1) (14.800,3.400,1) (23.000,2.570,1) (19.000,2.500,1) (18.800,3.900,1) (24.000,2.200,1) (22.500,4.800,1) (18.000,3.050,1) (18.000,2.620,1) (22.800,2.450,1) (26.000,2.600,1) (21.600,2.800,1) (23.600,1.740,1) (18.500,2.400,1) (22.000,3.600,1) (20.700,3.050,1) (18.000,2.150,1) (18.000,3.250,1) (19.000,2.600,1) (21.500,2.500,1) (16.000,2.900,1) (18.500,4.500,1) (18.000,2.300,1) (17.500,3.300,1) (18.500,2.450,1) (21.000,2.800,1) (19.500,2.060,1) (20.500,2.940,1) (22.000,2.700,1) (19.000,3.400,1) (22.500,3.300,1) (19.000,2.700,1) (20.000,2.650,1) (19.500,2.900,1) (21.000,2.000,1) (20.000,3.800,1) (21.000,3.080,1) (22.500,2.900,1) (21.500,1.900,1) (20.800,1.950,1) (22.500,2.060,1) (16.000,3.400,1) (19.000,1.280,1) (20.000,3.250,1) (28.500,6.000,1) (26.500,2.080,1) (21.500,2.600,1) (21.000,2.800,1) (21.000,2.760,1) (21.500,3.940,1) (28.500,3.000,1) (24.500,2.120,1) (22.000,2.600,1) (18.000,4.100,1) (20.000,5.400,1) (24.000,5.700,1) (21.500,5.000,1) (17.500,5.450,1) (18.500,7.100,1) (21.000,3.850,1) (25.000,5.000,1) (19.500,5.700,1) (24.000,4.920,1) (21.000,4.600,1) (20.000,5.600,1) (23.500,4.350,1) (20.000,4.400,1) (18.500,8.210,1) (21.000,4.000,1) (20.000,4.900,1) (21.500,7.650,1) (21.500,8.420,1) (21.500,9.400,1) (24.000,8.600,1) (22.000,10.800,1) (25.500,7.100,1) (18.500,10.520,1) (20.000,7.600,1) (22.000,7.900,1) (19.500,9.010,1) (27.000,7.500,1) (25.000,13.000,1) (22.500,11.750,1) (21.000,7.650,1) (20.000,5.880,1) (22.000,5.580,1) (18.500,5.280,1) (22.000,9.580,1) (22.500,6.620,1) (23.000,10.680,1) (19.500,10.260,1) (24.500,8.660,1) (25.000,8.500,1) (19.000,5.500,1) (19.500,9.900,1) (20.000,9.700,1) (20.500,7.700,1) (23.000,7.300,1) (20.000,10.200,1) (20.000,9.300,1) (24.500,9.200,1) };
-
-    \nextgroupplot[
-			view={0}{90},
-			enlargelimits=0,
-			zmin=0.0, zmax=1.0,
-			xlabel=E,
-			ylabel=K,
-			%colorbar,
-			point meta min=0, point meta max=0.5,
-			colormap={}{ gray(0cm)=(1); gray(1cm)=(0);}
-			%colorbar style={
-			 %       ytick={0,0.05,...,0.5},
-			  %      yticklabel style={
-			   %         text width=2.5em,
-			    %        align=right,
-			     %       /pgf/number format/.cd,
-			      %          fixed,
-			       %         fixed zerofill
-			        %}
-			    %}
-			]
-
-    		\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.6000,1.2800,0.0565) (17.9000,1.2800,0.0565) (17.9000,3.4600,0.0565) (10.6000,3.4600,0.0565)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.6000,3.4600,0.2210) (17.9000,3.4600,0.2210) (17.9000,7.5500,0.2210) (10.6000,7.5500,0.2210)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.6000,7.5500,0.0145) (17.9000,7.5500,0.0145) (17.9000,13.0000,0.0145) (10.6000,13.0000,0.0145)};
-
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.9000,1.2800,0.2440) (30.0000,1.2800,0.2440) (30.0000,3.4600,0.2440) (17.9000,3.4600,0.2440)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.9000,3.4600,0.3195) (30.0000,3.4600,0.3195) (30.0000,7.5500,0.3195) (17.9000,7.5500,0.3195)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.9000,7.5500,0.1445) (30.0000,7.5500,0.1445) (30.0000,13.0000,0.1445) (17.9000,13.0000,0.1445)};
-
-			\addplot3[mark=+, draw=none, mark size=0.7] coordinates {
-(15.600,5.640,1) (11.200,4.380,1) (18.600,5.680,1) (16.800,7.800,1) (21.000,4.320,1) (15.200,6.750,1) (14.600,5.250,1) (17.600,5.050,1) (14.000,5.200,1) (16.000,7.220,1) (18.000,5.750,1) (16.800,5.000,1) (16.000,5.600,1) (11.400,5.400,1) (12.000,7.500,1) (17.200,7.300,1) (20.000,6.200,1) (20.000,6.600,1) (16.500,8.700,1) (15.200,5.100,1) (16.000,5.650,1) (18.600,4.500,1) (16.600,3.800,1) (17.800,3.930,1) (20.000,3.520,1) (25.000,3.580,1) (16.100,4.800,1) (17.000,3.950,1) (19.400,4.500,1) (16.000,4.700,1) (22.500,5.700,1) (19.100,6.900,1) (17.200,3.840,1) (19.500,5.400,1) (19.000,4.200,1) (20.500,5.100,1) (15.500,4.600,1) (18.000,4.250,1) (15.500,3.700,1) (13.200,5.100,1) (16.200,6.130,1) (18.800,4.280,1) (15.000,5.430,1) (17.500,4.360,1) (17.000,5.040,1) (18.900,5.240,1) (16.000,4.900,1) (16.000,6.100,1) (18.800,6.200,1) (17.400,8.900,1) (12.400,7.200,1) (17.200,5.600,1) (14.000,7.050,1) (17.100,6.300,1) (16.400,5.850,1) (20.500,6.250,1) (16.300,6.380,1) (16.800,6.000,1) (16.700,6.800,1) (10.600,1.950,1) (16.000,3.270,1) (16.800,5.750,1) (18.000,3.800,1) (19.000,4.450,1) (19.000,2.950,1) (18.100,4.600,1) (15.000,5.300,1) (19.600,4.680,1) (17.000,3.170,1) (16.800,2.850,1) (20.400,3.050,1) (25.000,3.380,1) (24.000,3.740,1) (30.000,3.350,1) (21.000,3.210,1) (16.000,3.800,1) (16.000,4.600,1) (18.000,2.650,1) (14.800,3.400,1) (23.000,2.570,1) (19.000,2.500,1) (18.800,3.900,1) (24.000,2.200,1) (22.500,4.800,1) (18.000,3.050,1) (18.000,2.620,1) (22.800,2.450,1) (26.000,2.600,1) (21.600,2.800,1) (23.600,1.740,1) (18.500,2.400,1) (22.000,3.600,1) (20.700,3.050,1) (18.000,2.150,1) (18.000,3.250,1) (19.000,2.600,1) (21.500,2.500,1) (16.000,2.900,1) (18.500,4.500,1) (18.000,2.300,1) (17.500,3.300,1) (18.500,2.450,1) (21.000,2.800,1) (19.500,2.060,1) (20.500,2.940,1) (22.000,2.700,1) (19.000,3.400,1) (22.500,3.300,1) (19.000,2.700,1) (20.000,2.650,1) (19.500,2.900,1) (21.000,2.000,1) (20.000,3.800,1) (21.000,3.080,1) (22.500,2.900,1) (21.500,1.900,1) (20.800,1.950,1) (22.500,2.060,1) (16.000,3.400,1) (19.000,1.280,1) (20.000,3.250,1) (28.500,6.000,1) (26.500,2.080,1) (21.500,2.600,1) (21.000,2.800,1) (21.000,2.760,1) (21.500,3.940,1) (28.500,3.000,1) (24.500,2.120,1) (22.000,2.600,1) (18.000,4.100,1) (20.000,5.400,1) (24.000,5.700,1) (21.500,5.000,1) (17.500,5.450,1) (18.500,7.100,1) (21.000,3.850,1) (25.000,5.000,1) (19.500,5.700,1) (24.000,4.920,1) (21.000,4.600,1) (20.000,5.600,1) (23.500,4.350,1) (20.000,4.400,1) (18.500,8.210,1) (21.000,4.000,1) (20.000,4.900,1) (21.500,7.650,1) (21.500,8.420,1) (21.500,9.400,1) (24.000,8.600,1) (22.000,10.800,1) (25.500,7.100,1) (18.500,10.520,1) (20.000,7.600,1) (22.000,7.900,1) (19.500,9.010,1) (27.000,7.500,1) (25.000,13.000,1) (22.500,11.750,1) (21.000,7.650,1) (20.000,5.880,1) (22.000,5.580,1) (18.500,5.280,1) (22.000,9.580,1) (22.500,6.620,1) (23.000,10.680,1) (19.500,10.260,1) (24.500,8.660,1) (25.000,8.500,1) (19.000,5.500,1) (19.500,9.900,1) (20.000,9.700,1) (20.500,7.700,1) (23.000,7.300,1) (20.000,10.200,1) (20.000,9.300,1) (24.500,9.200,1) };
-  \end{groupplot}
+		\end{axis}
 	\end{tikzpicture}

### 2015-11-17 graph_wine_exp2_distr_5_11.tex
add wine exp plots

--- 2015-11-17 graph_wine_exp1_distr_5_11.tex
@@
 
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.6000,1.2800,0.0495) (17.9000,1.2800,0.0495) (17.9000,3.4600,0.0495) (10.6000,3.4600,0.0495)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.6000,3.4600,0.0725) (17.9000,3.4600,0.0725) (17.9000,4.8500,0.0725) (10.6000,4.8500,0.0725)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.6000,4.8500,0.1445) (17.9000,4.8500,0.1445) (17.9000,7.4000,0.1445) (10.6000,7.4000,0.1445)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.6000,7.4000,0.0205) (17.9000,7.4000,0.0205) (17.9000,13.0000,0.0205) (10.6000,13.0000,0.0205)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.6000,1.2800,0.0440) (17.9000,1.2800,0.0440) (17.9000,3.4600,0.0440) (10.6000,3.4600,0.0440)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.6000,3.4600,0.0820) (17.9000,3.4600,0.0820) (17.9000,4.8500,0.0820) (10.6000,4.8500,0.0820)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.6000,4.8500,0.1480) (17.9000,4.8500,0.1480) (17.9000,7.4000,0.1480) (10.6000,7.4000,0.1480)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.6000,7.4000,0.0195) (17.9000,7.4000,0.0195) (17.9000,13.0000,0.0195) (10.6000,13.0000,0.0195)};
 
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.9000,1.2800,0.2060) (23.2500,1.2800,0.2060) (23.2500,3.4600,0.2060) (17.9000,3.4600,0.2060)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.9000,3.4600,0.1095) (23.2500,3.4600,0.1095) (23.2500,4.8500,0.1095) (17.9000,4.8500,0.1095)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.9000,4.8500,0.1600) (23.2500,4.8500,0.1600) (23.2500,7.4000,0.1600) (17.9000,7.4000,0.1600)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.9000,7.4000,0.1100) (23.2500,7.4000,0.1100) (23.2500,13.0000,0.1100) (17.9000,13.0000,0.1100)};
-
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.2500,1.2800,0.0485) (30.0000,1.2800,0.0485) (30.0000,3.4600,0.0485) (23.2500,3.4600,0.0485)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.2500,3.4600,0.0255) (30.0000,3.4600,0.0255) (30.0000,4.8500,0.0255) (23.2500,4.8500,0.0255)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.2500,4.8500,0.0230) (30.0000,4.8500,0.0230) (30.0000,7.4000,0.0230) (23.2500,7.4000,0.0230)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.2500,7.4000,0.0305) (30.0000,7.4000,0.0305) (30.0000,13.0000,0.0305) (23.2500,13.0000,0.0305)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.9000,1.2800,0.2565) (30.0000,1.2800,0.2565) (30.0000,3.4600,0.2565) (17.9000,3.4600,0.2565)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.9000,3.4600,0.1320) (30.0000,3.4600,0.1320) (30.0000,4.8500,0.1320) (17.9000,4.8500,0.1320)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.9000,4.8500,0.1640) (30.0000,4.8500,0.1640) (30.0000,7.4000,0.1640) (17.9000,7.4000,0.1640)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.9000,7.4000,0.1540) (30.0000,7.4000,0.1540) (30.0000,13.0000,0.1540) (17.9000,13.0000,0.1540)};
 

### 2015-11-17 BN_discretizer_paper.tex
add wine exp plots
Modify exp part

--- 2015-11-16 BN_discretizer_paper.tex
@@
 \usepackage{pgfplots}
+\usepgfplotslibrary{groupplots}
 \usepackage{tikz}
@@
 
-\subsubsection{Structure is Given}
+\subsubsection{Experiment 1 on the Auto MPG dataset}
 
-The proposed discretization method and the MDL discretization method are tested on Auto MPG data given the network network in Fig. \ref{Auto_graph_1}.
-The structure was obtained by prediscretizing each continuous variable into five uniform-width intervals, where five is the median cardinality of the discrete variables, and then taking the most frequent structure from a thousand runs of K2.
+The proposed discretization method and the MDL discretization method are tested on Auto MPG data given the network network in Fig.
+\ref{fig:auto_graph_1}.
+This structure was obtained by prediscretizing each continuous variable into five uniform-width intervals, where five is the median cardinality of the discrete variables, and then taking the most frequent structure from a thousand runs of K2.
 
@@
   \caption{The Bayesian network obtained with K2 on the prediscretized Auto MPG dataset}
-  \label{Auto_graph_1}
+  \label{fig:auto_graph_1}
 \end{figure}
 
-Table \ref{Auto_MPG_disc_table_1} shows the numbers of intervals after discretization, the positions of discretization edges, and log-likelihood of 10-fold cross validation.
+Table \ref{table:auto_disc_table_1} shows the numbers of intervals after discretization, the positions of discretization edges, and log-likelihood of 10-fold cross validation.
 For the Bayesian network in Fig.
-\ref{Auto_graph_1}, the approximation only reduces runtime of proposed method and has no influence on discretization result.
+\ref{fig:auto_graph_1}, the approximation only reduces runtime of proposed method and has no influence on discretization result.
 MDL principle discretization works not well, since it discretizes all variables with only one interval.
-For a Bayesian network on thie Auto MPG data set that MDL principle discretization has non-trivial result, please reference to Appendix.
+For a Bayesian network on the Auto MPG data set that MDL principle discretization has non-trivial result, please reference to Appendix.
 
@@
   \caption{Discretization result of Auto MPG dataset based on the graph in Fig.
-\ref{Auto_graph_1}.
+\ref{fig:auto_graph_1}.
 The discretization policy for the heuristic matches that for the optimal Bayesian approach.
 \todo{Need to explain why MDL fails}}
-  \label{Auto_MPG_disc_table_1}
+  \label{table:auto_disc_table_1}
 \end{table}
 
-Figure \ref{auto_exp1_distr_1_3} compares the discretization result on continuous variables $A$ and $C$ with the raw data of Auto MPG data set.
+Figure \ref{fig:auto_exp1_distr_1_3} compares the discretization result on continuous variables $A$ and $C$ with the raw data of Auto MPG data set.
 The color of discretized area shows the probability of a sample being in the discretized area.
 The black dots in Figure \ref{auto_exp1_distr_1_3} demonstrate the distribution of the raw data.
-As shown in the figure, the discretization edges and the resulting marginalized probability match the raw data very well.
+As shown in the figure, the discretization edges and the resulting marginalized probability match the raw data well.
 
@@
   \caption{Comparison of the raw data and discretization result on variable $A$ and $C$}
-  \label{auto_exp1_distr_1_3}
+  \label{fig:auto_exp1_distr_1_3}
 \end{figure}
 
-\subsubsection{Structure is Learned}
+\subsubsection{Experiment 2 on the Auto MPG dataset}
 
 If the network structure is not known in advance, it should be learned along with the discretization process.
-Figure \ref{Auto_graph_2} and Table \ref{Auto_MPG_disc_table_2} show a learned discrete-valued Bayesian network and the corresponding discretization edges of each continuous variable.
-This result is obtained by running Algorithm \ref{Learn_DBN} fifty times and choosing the one with the highest K2 score.
-\newline
+Figure \ref{fig:auto_graph_2} show a learned discrete-valued Bayesian network and the corresponding discretization edges of each continuous variable.
+This result is obtained by running Algorithm \ref{alg:structure_learn} fifty times and choosing the one with the highest K2 score.
+The numbers next to the variables are cardinality numbers.
 
- {\centering
-\begin{minipage}{0.50\textwidth}
+\begin{figure}[ht]
 \centering
-  \scalebox{0.7}{
-  \input{graph_autocar_2}}
-  \captionof{figure}{The learned discrete-\newline valued Bayesian network}
-  \label{Auto_graph_2}
-\end{minipage}
-\begin{minipage}{0.50\textwidth}
-  \raggedleft
-  \input{table_autoMPG_2.tex}
-  \captionof{table}{The discretization edges of variables in Fig \ref{Auto_graph_2}}
-  \label{Auto_MPG_disc_table_2}
-\end{minipage}
-}
+    \begin{tabular}{cc}
+      \input{graph_autocar_2}
+    \end{tabular}
+  \caption{The learned discrete-valued Bayesian network from the Auto MPG dataset}
+  \label{fig:auto_graph_2}
+\end{figure}
 
-Figure \ref{auto_exp2_distr_1_3} compares the result of Figure \ref{Auto_graph_2} and Table \ref{Auto_MPG_disc_table_2} with the raw data on variables $A$ and $C$.
+ %{\centering
+%\begin{minipage}{0.50\textwidth}
+%  \centering
+%  \scalebox{0.7}{
+%  \input{graph_autocar_2}}
+%  \captionof{figure}{The learned discrete-\newline valued Bayesian network}
+%  \label{fig:auto_graph_2}
+%\end{minipage}
+%\begin{minipage}{0.50\textwidth}
+%  \raggedleft
+%  \input{table_autoMPG_2.tex}
+%  \captionof{table}{The discretization edges of variables in Fig \ref{Auto_graph_2}}
+%  \label{Auto_MPG_disc_table_2}
+%\end{minipage}
+%}
+
+Figure \ref{auto_exp2_distr_1_3} compares the edges of the learned network in Figure \ref{fig:auto_graph_2} with the raw data on variables $A$ and $C$.
 Again, the black dots are raw data points.
-Although the numbers of discretization edges of $A$ and $C$ shown in Table \ref{Auto_MPG_disc_table_2} are less than Table \ref{Auto_MPG_disc_table_1}, they still have a good capture of raw data distribution.
+Although the numbers of discretization edges of $A$ and $C$ shown in Figure \ref{fig:auto_graph_2} are less than Table \ref{table:auto_disc_table_1}, they still have a good capture of raw data distribution.
 
@@
     \end{tabular}
-  \caption{Comparison of the raw data and discretization result on variable $A$ and $C$ according to Figure \ref{Auto_graph_2} and Table \ref{Auto_MPG_disc_table_2}}
-  \label{auto_exp2_distr_1_3}
+  \caption{Comparison of the raw data and discretization result on variable $A$ and $C$ of the learned network in Figure \ref{fig:auto_graph_2}}.
+  \label{fig:auto_exp2_distr_1_3}
 \end{figure}
@@
 
-\subsubsection{Experiment 1 on Wine dataset}
-\label{subsubsec:wine_exp2}
+\subsubsection{Experiment 1 on the Wine dataset}
+\label{subsubsec:wine_exp1}
 
-Figure \ref{Wine_graph_1} is obtained by equal-width discretizing each continuous variable into 3 intervals and running K2 1000 times.
-Table \ref{Wine_disc_table_1} shows a comparison between the proposed method and the MDL principle discretization method.
+The Bayesian network in Figure \ref{fig:wine_graph_1} is obtained by equal-width discretizing each continuous variable into 3 intervals and running K2 1000 times.
+Table \ref{table:wine_disc_table_1} shows a comparison between the proposed method and the MDL principle discretization method.
 The proposed method is still better than MDL principle discretization in terms of likelihood, although the latter returns non-trivial result in this experiment.
-Furthermore, the proposed method with the approximation has more intervals after discretization, thus it has a slightly better result.
+Note that the proposed method with the approximation has more intervals after discretization, thus it has a slightly better result.
 However, as shown in next dataset, the approximation might cut continuous variables into too many intervals.
@@
 \begin{figure}[ht]
+\centering
     \begin{tabular}{cc}
@@
   \caption{K2 structure learning with prediscretization on Wine dataset}
-  \label{Wine_graph_1}
+  \label{fig:wine_graph_1}
 \end{figure}
@@
 \caption{Discretization result of Wine dataset based on the graph Fig. \ref{Wine_graph_1}}
-\label{Wine_disc_table_1}
+\label{table:wine_disc_table_1}
 \end{table}
@@
     \begin{tabular}{cc}
-      \input{graph_wine_2}
+      \input{graph_wine_exp1_distr}
     \end{tabular}
-  \caption{K2 structure learning with the proposed discretization method on Wine dataset}
+  \caption{Comparison of the raw data and discretization result on variable $A$ and $C$ according to Figure \ref{Auto_graph_2} and Table \ref{Auto_MPG_disc_table_2}}
+  \label{wine_exp1_distr}
+\end{figure}
+
+\subsubsection{Experiment 2 on the Wine dataset}
+\label{subsubsec:wine_exp2}
+
+Figure \ref{Wine_graph_2} is the learned discrete-valued Bayesian network, which is obtained by running Algorithm \ref{alg:structure_learn} 50 times.
+The integer numbers next to variables are cardinality numbers of variables.
+By comparing Figure \ref{Wine_graph_2} with \ref{Wine_graph_1}, it shows that the the Bayesian network obtained by \ref{alg:structure_learn} has more edges than the network obtained by prediscretization and the K2 algorithm.
+Furthermore, the cardinalitis of discretized variables in Figure \ref{Wine_graph_2} are smaller than the result in \ref{Wine_disc_table_1}.
+
+Figure \ref{wine_exp2_distr_5_11} shows the discretization result on variable $E$ and $K$.
+The discretization edge on variable $E$ is same as the edge found by the MDL principle and the proposed method in Figure \ref{wine_exp1_distr}.
+This indicates that some discretization edges are robust against the network structure.
+
+\begin{figure}[ht]
+    \begin{tabular}{cc}
+    \centering
+    \scalebox{0.7}{
+      \input{graph_wine_2}}
+    \end{tabular}
+  \caption{The learned discrete-valued Bayesian network from the Wine dataset}
+  \label{Wine_graph_2}
+\end{figure}
+
+\begin{figure}[ht]
+    \begin{tabular}{cc}
+      \input{graph_wine_exp2_distr_5_11}
+    \end{tabular}
+  \caption{Comparison of the raw data and discretization result on variable $E$ and $K$ according to Figure \ref{Auto_graph_2}}
   \label{Wine_graph_2}

### 2015-11-17 BN_discretizer_paper.tex
Exp part update

@@
 
+Figure \ref{fig:wine_exp1_distr} compares the discretization results by the proposed method and the MDL method.
+It shows the discretization edges on variable $E$ and $K$, and the probability of resulting discretized area.
+The proposed method has more discretization edges than the MDL method.
+Furthermore, the discretization edges on $E$ and $K$ obtained by the MDL method are either included in or close to the edges by obtained proposed method.
+This indicates that the proposed method can include the discretization result obtained by the MDL method and meanwhile, capture other discretization edges without significantly increase cardinality numbers of variables.
+
 \begin{figure}[ht]
@@
     \end{tabular}
-  \caption{Comparison of the raw data and discretization result on variable $A$ and $C$ according to Figure \ref{Auto_graph_2} and Table \ref{Auto_MPG_disc_table_2}}
-  \label{wine_exp1_distr}
+  \caption{Comparison of the discretization results on variable $A$ and $C$ obtained by the proposed method and the MDL method}
+  \label{fig:wine_exp1_distr}
 \end{figure}
@@
 
-Figure \ref{Wine_graph_2} is the learned discrete-valued Bayesian network, which is obtained by running Algorithm \ref{alg:structure_learn} 50 times.
+Figure \ref{fig:wine_graph_2} is the learned discrete-valued Bayesian network from the Wine dataset, and it is obtained by running Algorithm \ref{alg:structure_learn} 50 times.
 The integer numbers next to variables are cardinality numbers of variables.
-By comparing Figure \ref{Wine_graph_2} with \ref{Wine_graph_1}, it shows that the the Bayesian network obtained by \ref{alg:structure_learn} has more edges than the network obtained by prediscretization and the K2 algorithm.
-Furthermore, the cardinalitis of discretized variables in Figure \ref{Wine_graph_2} are smaller than the result in \ref{Wine_disc_table_1}.
+By comparing Figure \ref{fig:wine_graph_2} with \ref{fig:wine_graph_1}, it shows that the the Bayesian network obtained by \ref{alg:structure_learn} has more edges than the network obtained by prediscretization and the K2 algorithm.
+Furthermore, the cardinalitis of discretized variables in Figure \ref{fig:wine_graph_2} are smaller than the result in \ref{fig:wine_disc_table_1}.
 
-Figure \ref{wine_exp2_distr_5_11} shows the discretization result on variable $E$ and $K$.
+Figure \ref{fig:wine_exp2_distr} shows the discretization result on variable $E$ and $K$.
 The discretization edge on variable $E$ is same as the edge found by the MDL principle and the proposed method in Figure \ref{wine_exp1_distr}.
@@
   \caption{The learned discrete-valued Bayesian network from the Wine dataset}
-  \label{Wine_graph_2}
+  \label{fig:wine_graph_2}
 \end{figure}
@@
   \caption{Comparison of the raw data and discretization result on variable $E$ and $K$ according to Figure \ref{Auto_graph_2}}
-  \label{Wine_graph_2}
+  \label{fig:wine_exp2_distr}
 \end{figure}

### 2015-11-17 BN_discretizer_paper.tex
change caption

@@
 By comparing Figure \ref{fig:wine_graph_2} with \ref{fig:wine_graph_1}, it shows that the the Bayesian network obtained by \ref{alg:structure_learn} has more edges than the network obtained by prediscretization and the K2 algorithm.
-Furthermore, the cardinalitis of discretized variables in Figure \ref{fig:wine_graph_2} are smaller than the result in \ref{fig:wine_disc_table_1}.
+Furthermore, the cardinalitis of discretized variables in Figure \ref{fig:wine_graph_2} are smaller than the result in \ref{table:wine_disc_table_1}.
 
@@
     \end{tabular}
-  \caption{Comparison of the raw data and discretization result on variable $E$ and $K$ according to Figure \ref{Auto_graph_2}}
+  \caption{The discretization result on variable $E$ and $K$ of the learned network in Figure \ref{fig:wine_graph_2}}
   \label{fig:wine_exp2_distr}

### 2015-11-17 BN_discretizer_paper.tex
Experiment part

@@
 \usepackage{pgfplots}
+\usepackage{pgfplotstable}
 \usepgfplotslibrary{groupplots}
@@
 %
-
+\pgfplotsset{
+    jitter/.style={
+        x filter/.code={\pgfmathparse{\pgfmathresult+rnd*#1}}
+    },
+    jitter/.default=0.1
+}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \begin{algorithm}
+  \caption{Discretization of multiple continuous variables \todo{Fix label reference number}}
   \label{alg:disc_two}
-  \caption{Discretization of multiple continuous variables \todo{Fix label reference number}}
   \begin{algorithmic}[5]
@@
 \begin{algorithm}
+  \caption{ Learning a discrete-valued Bayesian network}
   \label{alg:structure_learn}
-  \caption{ Learning a discrete-valued Bayesian network}
   \begin{algorithmic}[5]
@@
 \subsection{Auto MPG Dataset}
-
-In this subsection, two experiments are conducted on the Auto MPG dataset from the Irvine repository \citep{Lichman:2013}.
+\label{subsec:auto}
+
+In this subsection, two experiments are conducted on the Auto MPG dataset from the Irvine repository \citep{Lichman_2013}.
 The dataset has \num{392} instances after deleting the six instances with missing data, and eight variables.
@@
 \subsubsection{Experiment 1 on the Auto MPG dataset}
+\label{subsubsec:auto_exp1}
 
@@
 The color of discretized area shows the probability of a sample being in the discretized area.
-The black dots in Figure \ref{auto_exp1_distr_1_3} demonstrate the distribution of the raw data.
+The black dots in Figure \ref{fig:auto_exp1_distr_1_3} demonstrate the distribution of the raw data.
 As shown in the figure, the discretization edges and the resulting marginalized probability match the raw data well.
@@
 \subsubsection{Experiment 2 on the Auto MPG dataset}
+\label{subsubsec:auto_exp2}
 
@@
 
-Figure \ref{auto_exp2_distr_1_3} compares the edges of the learned network in Figure \ref{fig:auto_graph_2} with the raw data on variables $A$ and $C$.
+Figure \ref{fig:auto_exp2_distr_1_3} compares the edges of the learned network in Figure \ref{fig:auto_graph_2} with the raw data on variables $A$ and $C$.
 Again, the black dots are raw data points.
@@
 
-In this subsection, two experiments are conducted on the Wine dataset from the Irvine repository \citep{Lichman:2013}.
+In this subsection, another two experiments are conducted on the Wine dataset from the Irvine repository \citep{Lichman_2013}.
 This dataset has 178 instances and 14 variables.
@@
 The proposed method is still better than MDL principle discretization in terms of likelihood, although the latter returns non-trivial result in this experiment.
-Note that the proposed method with the approximation has more intervals after discretization, thus it has a slightly better result.
-However, as shown in next dataset, the approximation might cut continuous variables into too many intervals.
+Note that the proposed method with the approximation has more intervals after discretization, and it has a slightly better result in terms of likelihood.
+However, the improvement is marginally small, which indicates that the proposed method without the approximation captures good enough discretization result even if the numbers of intervals after discretization are smaller.
+In addition, as shown in next dataset, the approximation might cut continuous variables into too many intervals.
 Therefore, the proposed method without the approximation should be still considered a better approach.
@@
     \end{tabular}
-  \caption{K2 structure learning with prediscretization on Wine dataset}
+  \caption{K2 structure learning with prediscretization on the Wine dataset}
   \label{fig:wine_graph_1}
@@
 }
-\caption{Discretization result of Wine dataset based on the graph Fig. \ref{Wine_graph_1}}
+\caption{Discretization result of Wine dataset based on the graph Fig. \ref{fig:wine_graph_1}}
 \label{table:wine_disc_table_1}
@@
 Figure \ref{fig:wine_exp2_distr} shows the discretization result on variable $E$ and $K$.
-The discretization edge on variable $E$ is same as the edge found by the MDL principle and the proposed method in Figure \ref{wine_exp1_distr}.
+The discretization edge on variable $E$ is same as the edge found by the MDL principle and the proposed method in Figure \ref{fig:wine_exp1_distr}.
 This indicates that some discretization edges are robust against the network structure.
@@
 
-\begin{figure}[ht]
+In this subsection, another two experiments are conducted on the Housing dataset from the Irvine repository \citep{Lichman_2013}.
+This dataset has 506 instances and 14 variables.
+Only variables $D$ and $I$ are discrete-valued with cardinality numbers 2 and 9, respectively.
+Again, in the first experiment, the network structure is given.
+In the second experiment, the network structure is not provided.
+
+\subsubsection{Experiment 1 on the Housing dataset}
+\label{subsubsec:housing_exp1}
+
+The Bayesian network structure in Figure \ref{fig:housing_graph_1} is obtained by prediscretizing each continuous variable into five uniform-width intervals, then running the K2 algorithm one thousands time and choosing the network with the highest K2 score.
+Table \ref{table:housing_disc_table_1} shows the numbers of intervals after discretization on each continuous variables.
+MDL method does not discretize most variables.
+The proposed method with the approximation discretizes variables into too many intervals.
+For example, it discretized $J$ into 58 intervals.
+The proposed method without the approximation has a good control of number of intervals.
+\begin{figure}[ht]
+\centering
     \begin{tabular}{cc}
@@
   \caption{K2 structure learning with prediscretization on Housing dataset}
-  \label{Housing_graph_1}
+  \label{fig:housing_graph_1}
 \end{figure}
@@
 }
-\caption{Discretization result of Housing dataset based on the graph Fig. \ref{Housing_graph_1}}
-\label{Housing_disc_table_1}
+\caption{Discretization result of Housing dataset based on the graph Fig. \ref{fig:housing_graph_1}}
+\label{table:housing_disc_table_1}
 \end{table}
 
+Figure \ref{fig:housing_exp1_distr_3_5} and Figure \ref{fig:housing_exp1_distr_8_5} show the discretization result by the propose method on the network in Figure \ref{fig:housing_graph_1}.
+In Figure \ref{fig:housing_exp1_distr_3_5}, the scatter points, which stands for the raw data, has been jittered, since there are many repeated values in the raw data on the variable pair $C$ and $E$.
+These repeating values cause the high number of intervals after discretization for both $C$ and $E$, because in some sense, each repeated-value point form a single discretized area.
+On the other hand, there is no such over-repeated values of the raw data on variable $H$.
+Thus, the numbers of intervals after discretization for variable $E$ remains normal, as what we have seen in previous datasets.
+
+\begin{figure}[ht]
+    \begin{tabular}{cc}
+      \input{graph_housing_exp1_distr_3_5}
+    \end{tabular}
+  \caption{The discretization result on variable $C$ and $E$ of the network in Figure \ref{fig:housing_graph_1}}
+  \label{fig:housing_exp1_distr_3_5}
+\end{figure}
+
+\begin{figure}[ht]
+    \begin{tabular}{cc}
+      \input{graph_housing_exp1_distr_8_5}
+    \end{tabular}
+  \caption{The discretization result on variable $H$ and $E$ of the network in Figure \ref{fig:housing_graph_1}}
+  \label{fig:housing_exp1_distr_8_5}
+\end{figure}
+
+\subsubsection{Experiment 2 on the Housing dataset}
+\label{subsubsec:housing_exp2}
+
+Figure \ref{fig:housing_graph_2} is the learned discrete-valued Bayesian network from the Housing dataset by running Algorithm \ref{alg:structure_learn} 50 times.
+In both Figure \ref{fig:housing_graph_1} and Figure \ref{fig:housing_graph_2}, the variable $D$ is not connected to any other variable.
+Continuous variables $C$, $E$, $J$ and $K$, which are all in a Markov blanket, have high cardinality numbers after discretization.
+This is reasonable, since when discretizing one variable, the expected cardinality is close to highest cardinality number in the Markov blanket.
+This will lead to a group of variables that are close to each other and all have high cardinalities.
+
 \begin{figure}[ht]
@@
     \end{tabular}
-  \caption{K2 structure learning with the proposed discretization method on Housing dataset}
-  \label{Housing_graph_2}
+  \caption{The learned discrete-valued Bayesian network from the Housing dataset}
+  \label{fig:housing_graph_2}
+\end{figure}
+
+Figure \ref{fig:housing_exp2_distr_3_5} and Figure \ref{fig:housing_exp2_distr_8_5} show the discretization result on variables of the network in Figure \ref{fig:housing_graph_2}.
+Again, variable $C$ and $E$ have many discretization edges due to the repeated values.
+Although the number of intervals after discretization on $H$ is not big, it captures the distribution of the raw data along with the discretization edges on $E$.
+
+\begin{figure}[ht]
+    \begin{tabular}{cc}
+      \input{graph_housing_exp2_distr_3_5}
+    \end{tabular}
+  \caption{The discretization result on variable $C$ and $E$ of the network in Figure \ref{fig:housing_graph_2}}
+  \label{fig:housing_exp2_distr_3_5}
+\end{figure}
+
+\begin{figure}[ht]
+    \begin{tabular}{cc}
+      \input{graph_housing_exp2_distr_8_5}
+    \end{tabular}
+  \caption{The discretization result on variable $H$ and $G$ of the network in Figure \ref{fig:housing_graph_2}}
+  \label{fig:housing_exp2_distr_8_5}
 \end{figure}

### 2015-11-17 graph_housing_exp1_distr_3_5.tex
Experiment part

	\begin{tikzpicture}
		\begin{axis}[
			view={0}{90},
			enlargelimits=0,
			zmin=0.0, zmax=1.0,
			xlabel=C,
			ylabel=E,
			colorbar,
			point meta min=0, point meta max=0.5,
			colormap={}{ gray(0cm)=(1); gray(1cm)=(0);},
			colorbar style={
			        ytick={0,0.05,...,0.5},
			        yticklabel style={
			            text width=2.5em,
			            align=right,
			            /pgf/number format/.cd,
			                fixed,
			                fixed zerofill
			        }
			    }
			]

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.3850,0.1710) (7.2250,0.3850,0.1710) (7.2250,0.4405,0.1710) (0.4600,0.4405,0.1710)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.4405,0.1080) (7.2250,0.4405,0.1080) (7.2250,0.4860,0.1080) (0.4600,0.4860,0.1080)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.4860,0.0250) (7.2250,0.4860,0.0250) (7.2250,0.4910,0.0250) (0.4600,0.4910,0.0250)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.4910,0.0000) (7.2250,0.4910,0.0000) (7.2250,0.4960,0.0000) (0.4600,0.4960,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.4960,0.0795) (7.2250,0.4960,0.0795) (7.2250,0.5190,0.0795) (0.4600,0.5190,0.0795)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.5190,0.0000) (7.2250,0.5190,0.0000) (7.2250,0.5220,0.0000) (0.4600,0.5220,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.5220,0.0000) (7.2250,0.5220,0.0000) (7.2250,0.5280,0.0000) (0.4600,0.5280,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.5280,0.0035) (7.2250,0.5280,0.0035) (7.2250,0.5410,0.0035) (0.4600,0.5410,0.0035)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.5410,0.0000) (7.2250,0.5410,0.0000) (7.2250,0.5455,0.0000) (0.4600,0.5455,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.5455,0.0045) (7.2250,0.5455,0.0045) (7.2250,0.5910,0.0045) (0.4600,0.5910,0.0045)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.5910,0.0000) (7.2250,0.5910,0.0000) (7.2250,0.6390,0.0000) (0.4600,0.6390,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.6390,0.0185) (7.2250,0.6390,0.0185) (7.2250,0.6510,0.0185) (0.4600,0.6510,0.0185)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.6510,0.0000) (7.2250,0.6510,0.0000) (7.2250,0.8205,0.0000) (0.4600,0.8205,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.8205,0.0000) (7.2250,0.8205,0.0000) (7.2250,0.8710,0.0000) (0.4600,0.8710,0.0000)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.3850,0.0000) (8.0050,0.3850,0.0000) (8.0050,0.4405,0.0000) (7.2250,0.4405,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.4405,0.0000) (8.0050,0.4405,0.0000) (8.0050,0.4860,0.0000) (7.2250,0.4860,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.4860,0.0000) (8.0050,0.4860,0.0000) (8.0050,0.4910,0.0000) (7.2250,0.4910,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.4910,0.0145) (8.0050,0.4910,0.0145) (8.0050,0.4960,0.0145) (7.2250,0.4960,0.0145)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.4960,0.0000) (8.0050,0.4960,0.0000) (8.0050,0.5190,0.0000) (7.2250,0.5190,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.5190,0.0000) (8.0050,0.5190,0.0000) (8.0050,0.5220,0.0000) (7.2250,0.5220,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.5220,0.0120) (8.0050,0.5220,0.0120) (8.0050,0.5280,0.0120) (7.2250,0.5280,0.0120)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.5280,0.0000) (8.0050,0.5280,0.0000) (8.0050,0.5410,0.0000) (7.2250,0.5410,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.5410,0.0000) (8.0050,0.5410,0.0000) (8.0050,0.5455,0.0000) (7.2250,0.5455,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.5455,0.0000) (8.0050,0.5455,0.0000) (8.0050,0.5910,0.0000) (7.2250,0.5910,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.5910,0.0000) (8.0050,0.5910,0.0000) (8.0050,0.6390,0.0000) (7.2250,0.6390,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.6390,0.0000) (8.0050,0.6390,0.0000) (8.0050,0.6510,0.0000) (7.2250,0.6510,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.6510,0.0000) (8.0050,0.6510,0.0000) (8.0050,0.8205,0.0000) (7.2250,0.8205,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.8205,0.0000) (8.0050,0.8205,0.0000) (8.0050,0.8710,0.0000) (7.2250,0.8710,0.0000)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.0050,0.3850,0.0000) (8.3500,0.3850,0.0000) (8.3500,0.4405,0.0000) (8.0050,0.4405,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.0050,0.4405,0.0000) (8.3500,0.4405,0.0000) (8.3500,0.4860,0.0000) (8.0050,0.4860,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.0050,0.4860,0.0000) (8.3500,0.4860,0.0000) (8.3500,0.4910,0.0000) (8.0050,0.4910,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.0050,0.4910,0.0000) (8.3500,0.4910,0.0000) (8.3500,0.4960,0.0000) (8.0050,0.4960,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.0050,0.4960,0.0000) (8.3500,0.4960,0.0000) (8.3500,0.5190,0.0000) (8.0050,0.5190,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.0050,0.5190,0.0000) (8.3500,0.5190,0.0000) (8.3500,0.5220,0.0000) (8.0050,0.5220,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.0050,0.5220,0.0000) (8.3500,0.5220,0.0000) (8.3500,0.5280,0.0000) (8.0050,0.5280,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.0050,0.5280,0.0455) (8.3500,0.5280,0.0455) (8.3500,0.5410,0.0455) (8.0050,0.5410,0.0455)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.0050,0.5410,0.0000) (8.3500,0.5410,0.0000) (8.3500,0.5455,0.0000) (8.0050,0.5455,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.0050,0.5455,0.0000) (8.3500,0.5455,0.0000) (8.3500,0.5910,0.0000) (8.0050,0.5910,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.0050,0.5910,0.0000) (8.3500,0.5910,0.0000) (8.3500,0.6390,0.0000) (8.0050,0.6390,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.0050,0.6390,0.0000) (8.3500,0.6390,0.0000) (8.3500,0.6510,0.0000) (8.0050,0.6510,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.0050,0.6510,0.0000) (8.3500,0.6510,0.0000) (8.3500,0.8205,0.0000) (8.0050,0.8205,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.0050,0.8205,0.0000) (8.3500,0.8205,0.0000) (8.3500,0.8710,0.0000) (8.0050,0.8710,0.0000)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.3500,0.3850,0.0000) (9.1250,0.3850,0.0000) (9.1250,0.4405,0.0000) (8.3500,0.4405,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.3500,0.4405,0.0000) (9.1250,0.4405,0.0000) (9.1250,0.4860,0.0000) (8.3500,0.4860,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.3500,0.4860,0.0000) (9.1250,0.4860,0.0000) (9.1250,0.4910,0.0000) (8.3500,0.4910,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.3500,0.4910,0.0000) (9.1250,0.4910,0.0000) (9.1250,0.4960,0.0000) (8.3500,0.4960,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.3500,0.4960,0.0000) (9.1250,0.4960,0.0000) (9.1250,0.5190,0.0000) (8.3500,0.5190,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.3500,0.5190,0.0150) (9.1250,0.5190,0.0150) (9.1250,0.5220,0.0150) (8.3500,0.5220,0.0150)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.3500,0.5220,0.0000) (9.1250,0.5220,0.0000) (9.1250,0.5280,0.0000) (8.3500,0.5280,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.3500,0.5280,0.0000) (9.1250,0.5280,0.0000) (9.1250,0.5410,0.0000) (8.3500,0.5410,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.3500,0.5410,0.0000) (9.1250,0.5410,0.0000) (9.1250,0.5455,0.0000) (8.3500,0.5455,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.3500,0.5455,0.0000) (9.1250,0.5455,0.0000) (9.1250,0.5910,0.0000) (8.3500,0.5910,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.3500,0.5910,0.0000) (9.1250,0.5910,0.0000) (9.1250,0.6390,0.0000) (8.3500,0.6390,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.3500,0.6390,0.0000) (9.1250,0.6390,0.0000) (9.1250,0.6510,0.0000) (8.3500,0.6510,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.3500,0.6510,0.0000) (9.1250,0.6510,0.0000) (9.1250,0.8205,0.0000) (8.3500,0.8205,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.3500,0.8205,0.0000) (9.1250,0.8205,0.0000) (9.1250,0.8710,0.0000) (8.3500,0.8710,0.0000)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.3850,0.0330) (16.5700,0.3850,0.0330) (16.5700,0.4405,0.0330) (9.1250,0.4405,0.0330)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.4405,0.0065) (16.5700,0.4405,0.0065) (16.5700,0.4860,0.0065) (9.1250,0.4860,0.0065)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.4860,0.0210) (16.5700,0.4860,0.0210) (16.5700,0.4910,0.0210) (9.1250,0.4910,0.0210)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.4910,0.0000) (16.5700,0.4910,0.0000) (16.5700,0.4960,0.0000) (9.1250,0.4960,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.4960,0.0000) (16.5700,0.4960,0.0000) (16.5700,0.5190,0.0000) (9.1250,0.5190,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.5190,0.0000) (16.5700,0.5190,0.0000) (16.5700,0.5220,0.0000) (9.1250,0.5220,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.5220,0.0000) (16.5700,0.5220,0.0000) (16.5700,0.5280,0.0000) (9.1250,0.5280,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.5280,0.0000) (16.5700,0.5280,0.0000) (16.5700,0.5410,0.0000) (9.1250,0.5410,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.5410,0.0220) (16.5700,0.5410,0.0220) (16.5700,0.5455,0.0220) (9.1250,0.5455,0.0220)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.5455,0.0490) (16.5700,0.5455,0.0490) (16.5700,0.5910,0.0490) (9.1250,0.5910,0.0490)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.5910,0.0000) (16.5700,0.5910,0.0000) (16.5700,0.6390,0.0000) (9.1250,0.6390,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.6390,0.0000) (16.5700,0.6390,0.0000) (16.5700,0.6510,0.0000) (9.1250,0.6510,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.6510,0.0000) (16.5700,0.6510,0.0000) (16.5700,0.8205,0.0000) (9.1250,0.8205,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.8205,0.0000) (16.5700,0.8205,0.0000) (16.5700,0.8710,0.0000) (9.1250,0.8710,0.0000)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.3850,0.0000) (18.8400,0.3850,0.0000) (18.8400,0.4405,0.0000) (16.5700,0.4405,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.4405,0.0000) (18.8400,0.4405,0.0000) (18.8400,0.4860,0.0000) (16.5700,0.4860,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.4860,0.0000) (18.8400,0.4860,0.0000) (18.8400,0.4910,0.0000) (16.5700,0.4910,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.4910,0.0000) (18.8400,0.4910,0.0000) (18.8400,0.4960,0.0000) (16.5700,0.4960,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.4960,0.0000) (18.8400,0.4960,0.0000) (18.8400,0.5190,0.0000) (16.5700,0.5190,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.5190,0.0000) (18.8400,0.5190,0.0000) (18.8400,0.5220,0.0000) (16.5700,0.5220,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.5220,0.0000) (18.8400,0.5220,0.0000) (18.8400,0.5280,0.0000) (16.5700,0.5280,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.5280,0.0095) (18.8400,0.5280,0.0095) (18.8400,0.5410,0.0095) (16.5700,0.5410,0.0095)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.5410,0.0000) (18.8400,0.5410,0.0000) (18.8400,0.5455,0.0000) (16.5700,0.5455,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.5455,0.0295) (18.8400,0.5455,0.0295) (18.8400,0.5910,0.0295) (16.5700,0.5910,0.0295)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.5910,0.0260) (18.8400,0.5910,0.0260) (18.8400,0.6390,0.0260) (16.5700,0.6390,0.0260)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.6390,0.0000) (18.8400,0.6390,0.0000) (18.8400,0.6510,0.0000) (16.5700,0.6510,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.6510,0.1955) (18.8400,0.6510,0.1955) (18.8400,0.8205,0.1955) (16.5700,0.8205,0.1955)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.8205,0.0000) (18.8400,0.8205,0.0000) (18.8400,0.8710,0.0000) (16.5700,0.8710,0.0000)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.3850,0.0000) (20.7350,0.3850,0.0000) (20.7350,0.4405,0.0000) (18.8400,0.4405,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.4405,0.0000) (20.7350,0.4405,0.0000) (20.7350,0.4860,0.0000) (18.8400,0.4860,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.4860,0.0000) (20.7350,0.4860,0.0000) (20.7350,0.4910,0.0000) (18.8400,0.4910,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.4910,0.0000) (20.7350,0.4910,0.0000) (20.7350,0.4960,0.0000) (18.8400,0.4960,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.4960,0.0000) (20.7350,0.4960,0.0000) (20.7350,0.5190,0.0000) (18.8400,0.5190,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.5190,0.0000) (20.7350,0.5190,0.0000) (20.7350,0.5220,0.0000) (18.8400,0.5220,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.5220,0.0000) (20.7350,0.5220,0.0000) (20.7350,0.5280,0.0000) (18.8400,0.5280,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.5280,0.0000) (20.7350,0.5280,0.0000) (20.7350,0.5410,0.0000) (18.8400,0.5410,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.5410,0.0000) (20.7350,0.5410,0.0000) (20.7350,0.5455,0.0000) (18.8400,0.5455,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.5455,0.0000) (20.7350,0.5455,0.0000) (20.7350,0.5910,0.0000) (18.8400,0.5910,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.5910,0.0335) (20.7350,0.5910,0.0335) (20.7350,0.6390,0.0335) (18.8400,0.6390,0.0335)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.6390,0.0000) (20.7350,0.6390,0.0000) (20.7350,0.6510,0.0000) (18.8400,0.6510,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.6510,0.0000) (20.7350,0.6510,0.0000) (20.7350,0.8205,0.0000) (18.8400,0.8205,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.8205,0.0300) (20.7350,0.8205,0.0300) (20.7350,0.8710,0.0300) (18.8400,0.8710,0.0300)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.3850,0.0000) (27.7400,0.3850,0.0000) (27.7400,0.4405,0.0000) (20.7350,0.4405,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.4405,0.0000) (27.7400,0.4405,0.0000) (27.7400,0.4860,0.0000) (20.7350,0.4860,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.4860,0.0000) (27.7400,0.4860,0.0000) (27.7400,0.4910,0.0000) (20.7350,0.4910,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.4910,0.0000) (27.7400,0.4910,0.0000) (27.7400,0.4960,0.0000) (20.7350,0.4960,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.4960,0.0000) (27.7400,0.4960,0.0000) (27.7400,0.5190,0.0000) (20.7350,0.5190,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.5190,0.0000) (27.7400,0.5190,0.0000) (27.7400,0.5220,0.0000) (20.7350,0.5220,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.5220,0.0000) (27.7400,0.5220,0.0000) (27.7400,0.5280,0.0000) (20.7350,0.5280,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.5280,0.0000) (27.7400,0.5280,0.0000) (27.7400,0.5410,0.0000) (20.7350,0.5410,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.5410,0.0000) (27.7400,0.5410,0.0000) (27.7400,0.5455,0.0000) (20.7350,0.5455,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.5455,0.0160) (27.7400,0.5455,0.0160) (27.7400,0.5910,0.0160) (20.7350,0.5910,0.0160)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.5910,0.0315) (27.7400,0.5910,0.0315) (27.7400,0.6390,0.0315) (20.7350,0.6390,0.0315)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.6390,0.0000) (27.7400,0.6390,0.0000) (27.7400,0.6510,0.0000) (20.7350,0.6510,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.6510,0.0000) (27.7400,0.6510,0.0000) (27.7400,0.8205,0.0000) (20.7350,0.8205,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.8205,0.0000) (27.7400,0.8205,0.0000) (27.7400,0.8710,0.0000) (20.7350,0.8710,0.0000)};

			\addplot3[mark=+, draw=none, mark size=0.7, jitter = 0.3] coordinates {
(2.310,0.538,1) (7.070,0.469,1) (7.070,0.469,1) (2.180,0.458,1) (2.180,0.458,1) (2.180,0.458,1) (7.870,0.524,1) (7.870,0.524,1) (7.870,0.524,1) (7.870,0.524,1) (7.870,0.524,1) (7.870,0.524,1) (7.870,0.524,1) (8.140,0.538,1) (8.140,0.538,1) (8.140,0.538,1) (8.140,0.538,1) (8.140,0.538,1) (8.140,0.538,1) (8.140,0.538,1) (8.140,0.538,1) (8.140,0.538,1) (8.140,0.538,1) (8.140,0.538,1) (8.140,0.538,1) (8.140,0.538,1) (8.140,0.538,1) (8.140,0.538,1) (8.140,0.538,1) (8.140,0.538,1) (8.140,0.538,1) (8.140,0.538,1) (8.140,0.538,1) (8.140,0.538,1) (8.140,0.538,1) (5.960,0.499,1) (5.960,0.499,1) (5.960,0.499,1) (5.960,0.499,1) (2.950,0.428,1) (2.950,0.428,1) (6.910,0.448,1) (6.910,0.448,1) (6.910,0.448,1) (6.910,0.448,1) (6.910,0.448,1) (6.910,0.448,1) (6.910,0.448,1) (6.910,0.448,1) (6.910,0.448,1) (5.640,0.439,1) (5.640,0.439,1) (5.640,0.439,1) (5.640,0.439,1) (4.000,0.410,1) (1.220,0.403,1) (0.740,0.410,1) (1.320,0.411,1) (5.130,0.453,1) (5.130,0.453,1) (5.130,0.453,1) (5.130,0.453,1) (5.130,0.453,1) (5.130,0.453,1) (1.380,0.416,1) (3.370,0.398,1) (3.370,0.398,1) (6.070,0.409,1) (6.070,0.409,1) (6.070,0.409,1) (10.810,0.413,1) (10.810,0.413,1) (10.810,0.413,1) (10.810,0.413,1) (12.830,0.437,1) (12.830,0.437,1) (12.830,0.437,1) (12.830,0.437,1) (12.830,0.437,1) (12.830,0.437,1) (4.860,0.426,1) (4.860,0.426,1) (4.860,0.426,1) (4.860,0.426,1) (4.490,0.449,1) (4.490,0.449,1) (4.490,0.449,1) (4.490,0.449,1) (3.410,0.489,1) (3.410,0.489,1) (3.410,0.489,1) (3.410,0.489,1) (15.040,0.464,1) (15.040,0.464,1) (15.040,0.464,1) (2.890,0.445,1) (2.890,0.445,1) (2.890,0.445,1) (2.890,0.445,1) (2.890,0.445,1) (8.560,0.520,1) (8.560,0.520,1) (8.560,0.520,1) (8.560,0.520,1) (8.560,0.520,1) (8.560,0.520,1) (8.560,0.520,1) (8.560,0.520,1) (8.560,0.520,1) (8.560,0.520,1) (8.560,0.520,1) (10.010,0.547,1) (10.010,0.547,1) (10.010,0.547,1) (10.010,0.547,1) (10.010,0.547,1) (10.010,0.547,1) (10.010,0.547,1) (10.010,0.547,1) (10.010,0.547,1) (25.650,0.581,1) (25.650,0.581,1) (25.650,0.581,1) (25.650,0.581,1) (25.650,0.581,1) (25.650,0.581,1) (25.650,0.581,1) (21.890,0.624,1) (21.890,0.624,1) (21.890,0.624,1) (21.890,0.624,1) (21.890,0.624,1) (21.890,0.624,1) (21.890,0.624,1) (21.890,0.624,1) (21.890,0.624,1) (21.890,0.624,1) (21.890,0.624,1) (21.890,0.624,1) (21.890,0.624,1) (21.890,0.624,1) (21.890,0.624,1) (19.580,0.871,1) (19.580,0.871,1) (19.580,0.871,1) (19.580,0.871,1) (19.580,0.871,1) (19.580,0.871,1) (19.580,0.871,1) (19.580,0.871,1) (19.580,0.871,1) (19.580,0.871,1) (19.580,0.871,1) (19.580,0.871,1) (19.580,0.871,1) (19.580,0.871,1) (19.580,0.871,1) (19.580,0.605,1) (19.580,0.605,1) (19.580,0.871,1) (19.580,0.605,1) (19.580,0.605,1) (19.580,0.605,1) (19.580,0.605,1) (19.580,0.605,1) (19.580,0.605,1) (19.580,0.605,1) (19.580,0.605,1) (19.580,0.605,1) (19.580,0.605,1) (19.580,0.605,1) (19.580,0.605,1) (4.050,0.510,1) (4.050,0.510,1) (4.050,0.510,1) (4.050,0.510,1) (4.050,0.510,1) (4.050,0.510,1) (4.050,0.510,1) (2.460,0.488,1) (2.460,0.488,1) (2.460,0.488,1) (2.460,0.488,1) (2.460,0.488,1) (2.460,0.488,1) (2.460,0.488,1) (2.460,0.488,1) (3.440,0.437,1) (3.440,0.437,1) (3.440,0.437,1) (3.440,0.437,1) (3.440,0.437,1) (3.440,0.437,1) (2.930,0.401,1) (2.930,0.401,1) (0.460,0.422,1) (1.520,0.404,1) (1.520,0.404,1) (1.520,0.404,1) (1.470,0.403,1) (1.470,0.403,1) (2.030,0.415,1) (2.030,0.415,1) (2.680,0.416,1) (2.680,0.416,1) (10.590,0.489,1) (10.590,0.489,1) (10.590,0.489,1) (10.590,0.489,1) (10.590,0.489,1) (10.590,0.489,1) (10.590,0.489,1) (10.590,0.489,1) (10.590,0.489,1) (10.590,0.489,1) (10.590,0.489,1) (13.890,0.550,1) (13.890,0.550,1) (13.890,0.550,1) (13.890,0.550,1) (6.200,0.507,1) (6.200,0.507,1) (6.200,0.507,1) (6.200,0.507,1) (6.200,0.504,1) (6.200,0.504,1) (6.200,0.504,1) (6.200,0.504,1) (6.200,0.504,1) (6.200,0.504,1) (6.200,0.504,1) (6.200,0.504,1) (6.200,0.507,1) (6.200,0.507,1) (6.200,0.507,1) (6.200,0.507,1) (6.200,0.507,1) (6.200,0.507,1) (4.930,0.428,1) (4.930,0.428,1) (4.930,0.428,1) (4.930,0.428,1) (4.930,0.428,1) (4.930,0.428,1) (5.860,0.431,1) (5.860,0.431,1) (5.860,0.431,1) (5.860,0.431,1) (5.860,0.431,1) (5.860,0.431,1) (5.860,0.431,1) (5.860,0.431,1) (5.860,0.431,1) (5.860,0.431,1) (3.640,0.392,1) (3.640,0.392,1) (3.750,0.394,1) (3.970,0.647,1) (3.970,0.647,1) (3.970,0.647,1) (3.970,0.647,1) (3.970,0.647,1) (3.970,0.647,1) (3.970,0.647,1) (3.970,0.647,1) (3.970,0.647,1) (3.970,0.647,1) (3.970,0.575,1) (3.970,0.575,1) (6.960,0.464,1) (6.960,0.464,1) (6.960,0.464,1) (6.960,0.464,1) (6.960,0.464,1) (6.410,0.447,1) (6.410,0.447,1) (6.410,0.447,1) (6.410,0.447,1) (6.410,0.447,1) (3.330,0.443,1) (3.330,0.443,1) (3.330,0.443,1) (3.330,0.443,1) (1.210,0.401,1) (2.970,0.400,1) (2.250,0.389,1) (1.760,0.385,1) (5.320,0.405,1) (5.320,0.405,1) (5.320,0.405,1) (4.950,0.411,1) (4.950,0.411,1) (4.950,0.411,1) (13.920,0.437,1) (13.920,0.437,1) (13.920,0.437,1) (13.920,0.437,1) (13.920,0.437,1) (2.240,0.400,1) (2.240,0.400,1) (2.240,0.400,1) (6.090,0.433,1) (6.090,0.433,1) (6.090,0.433,1) (2.180,0.472,1) (2.180,0.472,1) (2.180,0.472,1) (2.180,0.472,1) (9.900,0.544,1) (9.900,0.544,1) (9.900,0.544,1) (9.900,0.544,1) (9.900,0.544,1) (9.900,0.544,1) (9.900,0.544,1) (9.900,0.544,1) (9.900,0.544,1) (9.900,0.544,1) (9.900,0.544,1) (9.900,0.544,1) (7.380,0.493,1) (7.380,0.493,1) (7.380,0.493,1) (7.380,0.493,1) (7.380,0.493,1) (7.380,0.493,1) (7.380,0.493,1) (7.380,0.493,1) (3.240,0.460,1) (3.240,0.460,1) (3.240,0.460,1) (6.060,0.438,1) (6.060,0.438,1) (5.190,0.515,1) (5.190,0.515,1) (5.190,0.515,1) (5.190,0.515,1) (5.190,0.515,1) (5.190,0.515,1) (5.190,0.515,1) (5.190,0.515,1) (1.520,0.442,1) (1.890,0.518,1) (3.780,0.484,1) (3.780,0.484,1) (4.390,0.442,1) (4.390,0.442,1) (4.150,0.429,1) (2.010,0.435,1) (1.250,0.429,1) (1.250,0.429,1) (1.690,0.411,1) (1.690,0.411,1) (2.020,0.410,1) (1.910,0.413,1) (1.910,0.413,1) (18.100,0.770,1) (18.100,0.770,1) (18.100,0.770,1) (18.100,0.770,1) (18.100,0.770,1) (18.100,0.770,1) (18.100,0.770,1) (18.100,0.770,1) (18.100,0.718,1) (18.100,0.718,1) (18.100,0.718,1) (18.100,0.631,1) (18.100,0.631,1) (18.100,0.631,1) (18.100,0.631,1) (18.100,0.631,1) (18.100,0.668,1) (18.100,0.668,1) (18.100,0.668,1) (18.100,0.671,1) (18.100,0.671,1) (18.100,0.671,1) (18.100,0.671,1) (18.100,0.671,1) (18.100,0.671,1) (18.100,0.671,1) (18.100,0.700,1) (18.100,0.700,1) (18.100,0.700,1) (18.100,0.700,1) (18.100,0.700,1) (18.100,0.700,1) (18.100,0.700,1) (18.100,0.700,1) (18.100,0.700,1) (18.100,0.700,1) (18.100,0.700,1) (18.100,0.693,1) (18.100,0.693,1) (18.100,0.693,1) (18.100,0.693,1) (18.100,0.693,1) (18.100,0.693,1) (18.100,0.693,1) (18.100,0.693,1) (18.100,0.693,1) (18.100,0.693,1) (18.100,0.693,1) (18.100,0.693,1) (18.100,0.693,1) (18.100,0.659,1) (18.100,0.659,1) (18.100,0.597,1) (18.100,0.597,1) (18.100,0.597,1) (18.100,0.597,1) (18.100,0.597,1) (18.100,0.597,1) (18.100,0.693,1) (18.100,0.679,1) (18.100,0.679,1) (18.100,0.679,1) (18.100,0.679,1) (18.100,0.718,1) (18.100,0.718,1) (18.100,0.718,1) (18.100,0.614,1) (18.100,0.614,1) (18.100,0.584,1) (18.100,0.679,1) (18.100,0.584,1) (18.100,0.679,1) (18.100,0.679,1) (18.100,0.679,1) (18.100,0.584,1) (18.100,0.584,1) (18.100,0.584,1) (18.100,0.713,1) (18.100,0.713,1) (18.100,0.740,1) (18.100,0.740,1) (18.100,0.740,1) (18.100,0.740,1) (18.100,0.740,1) (18.100,0.740,1) (18.100,0.740,1) (18.100,0.740,1) (18.100,0.740,1) (18.100,0.740,1) (18.100,0.740,1) (18.100,0.740,1) (18.100,0.740,1) (18.100,0.713,1) (18.100,0.713,1) (18.100,0.713,1) (18.100,0.713,1) (18.100,0.713,1) (18.100,0.713,1) (18.100,0.713,1) (18.100,0.713,1) (18.100,0.713,1) (18.100,0.713,1) (18.100,0.713,1) (18.100,0.713,1) (18.100,0.713,1) (18.100,0.713,1) (18.100,0.713,1) (18.100,0.713,1) (18.100,0.655,1) (18.100,0.655,1) (18.100,0.655,1) (18.100,0.584,1) (18.100,0.580,1) (18.100,0.580,1) (18.100,0.580,1) (18.100,0.532,1) (18.100,0.580,1) (18.100,0.614,1) (18.100,0.584,1) (18.100,0.584,1) (18.100,0.614,1) (18.100,0.614,1) (18.100,0.614,1) (18.100,0.614,1) (18.100,0.532,1) (18.100,0.532,1) (18.100,0.532,1) (18.100,0.532,1) (18.100,0.583,1) (18.100,0.583,1) (18.100,0.583,1) (18.100,0.583,1) (27.740,0.609,1) (27.740,0.609,1) (27.740,0.609,1) (27.740,0.609,1) (27.740,0.609,1) (9.690,0.585,1) (9.690,0.585,1) (9.690,0.585,1) (9.690,0.585,1) (9.690,0.585,1) (9.690,0.585,1) (9.690,0.585,1) (9.690,0.585,1) (11.930,0.573,1) (11.930,0.573,1) (11.930,0.573,1) (11.930,0.573,1) (11.930,0.573,1) };
		\end{axis}
	\end{tikzpicture}

### 2015-11-17 graph_housing_exp1_distr_8_5.tex
Experiment part

\begin{tikzpicture}
		\begin{axis}[
			view={0}{90},
			enlargelimits=0,
			zmin=0.0, zmax=1.0,
			xlabel=H,
			ylabel=E,
			colorbar,
			point meta min=0, point meta max=0.5,
			colormap={}{ gray(0cm)=(1); gray(1cm)=(0);},
			colorbar style={
			        ytick={0,0.05,...,0.5},
			        yticklabel style={
			            text width=2.5em,
			            align=right,
			            /pgf/number format/.cd,
			                fixed,
			                fixed zerofill
			        }
			    }
			]

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.3850,0.0000) (1.9204,0.3850,0.0000) (1.9204,0.4405,0.0000) (1.1296,0.4405,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.4405,0.0000) (1.9204,0.4405,0.0000) (1.9204,0.4860,0.0000) (1.1296,0.4860,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.4860,0.0000) (1.9204,0.4860,0.0000) (1.9204,0.4910,0.0000) (1.1296,0.4910,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.4910,0.0000) (1.9204,0.4910,0.0000) (1.9204,0.4960,0.0000) (1.1296,0.4960,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.4960,0.0000) (1.9204,0.4960,0.0000) (1.9204,0.5190,0.0000) (1.1296,0.5190,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.5190,0.0000) (1.9204,0.5190,0.0000) (1.9204,0.5220,0.0000) (1.1296,0.5220,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.5220,0.0000) (1.9204,0.5220,0.0000) (1.9204,0.5280,0.0000) (1.1296,0.5280,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.5280,0.0000) (1.9204,0.5280,0.0000) (1.9204,0.5410,0.0000) (1.1296,0.5410,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.5410,0.0000) (1.9204,0.5410,0.0000) (1.9204,0.5455,0.0000) (1.1296,0.5455,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.5455,0.0025) (1.9204,0.5455,0.0025) (1.9204,0.5910,0.0025) (1.1296,0.5910,0.0025)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.5910,0.0425) (1.9204,0.5910,0.0425) (1.9204,0.6390,0.0425) (1.1296,0.6390,0.0425)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.6390,0.0065) (1.9204,0.6390,0.0065) (1.9204,0.6510,0.0065) (1.1296,0.6510,0.0065)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.6510,0.1040) (1.9204,0.6510,0.1040) (1.9204,0.8205,0.1040) (1.1296,0.8205,0.1040)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.8205,0.0300) (1.9204,0.8205,0.0300) (1.9204,0.8710,0.0300) (1.1296,0.8710,0.0300)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.3850,0.0000) (2.5884,0.3850,0.0000) (2.5884,0.4405,0.0000) (1.9204,0.4405,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.4405,0.0000) (2.5884,0.4405,0.0000) (2.5884,0.4860,0.0000) (1.9204,0.4860,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.4860,0.0000) (2.5884,0.4860,0.0000) (2.5884,0.4910,0.0000) (1.9204,0.4910,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.4910,0.0000) (2.5884,0.4910,0.0000) (2.5884,0.4960,0.0000) (1.9204,0.4960,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.4960,0.0000) (2.5884,0.4960,0.0000) (2.5884,0.5190,0.0000) (1.9204,0.5190,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.5190,0.0085) (2.5884,0.5190,0.0085) (2.5884,0.5220,0.0085) (1.9204,0.5220,0.0085)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.5220,0.0000) (2.5884,0.5220,0.0000) (2.5884,0.5280,0.0000) (1.9204,0.5280,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.5280,0.0000) (2.5884,0.5280,0.0000) (2.5884,0.5410,0.0000) (1.9204,0.5410,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.5410,0.0025) (2.5884,0.5410,0.0025) (2.5884,0.5455,0.0025) (1.9204,0.5455,0.0025)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.5455,0.0580) (2.5884,0.5455,0.0580) (2.5884,0.5910,0.0580) (1.9204,0.5910,0.0580)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.5910,0.0485) (2.5884,0.5910,0.0485) (2.5884,0.6390,0.0485) (1.9204,0.6390,0.0485)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.6390,0.0120) (2.5884,0.6390,0.0120) (2.5884,0.6510,0.0120) (1.9204,0.6510,0.0120)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.6510,0.0665) (2.5884,0.6510,0.0665) (2.5884,0.8205,0.0665) (1.9204,0.8205,0.0665)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.8205,0.0000) (2.5884,0.8205,0.0000) (2.5884,0.8710,0.0000) (1.9204,0.8710,0.0000)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.3850,0.0000) (3.0793,0.3850,0.0000) (3.0793,0.4405,0.0000) (2.5884,0.4405,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.4405,0.0000) (3.0793,0.4405,0.0000) (3.0793,0.4860,0.0000) (2.5884,0.4860,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.4860,0.0115) (3.0793,0.4860,0.0115) (3.0793,0.4910,0.0115) (2.5884,0.4910,0.0115)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.4910,0.0000) (3.0793,0.4910,0.0000) (3.0793,0.4960,0.0000) (2.5884,0.4960,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.4960,0.0160) (3.0793,0.4960,0.0160) (3.0793,0.5190,0.0160) (2.5884,0.5190,0.0160)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.5190,0.0065) (3.0793,0.5190,0.0065) (3.0793,0.5220,0.0065) (2.5884,0.5220,0.0065)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.5220,0.0000) (3.0793,0.5220,0.0000) (3.0793,0.5280,0.0000) (2.5884,0.5280,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.5280,0.0000) (3.0793,0.5280,0.0000) (3.0793,0.5410,0.0000) (2.5884,0.5410,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.5410,0.0040) (3.0793,0.5410,0.0040) (3.0793,0.5455,0.0040) (2.5884,0.5455,0.0040)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.5455,0.0250) (3.0793,0.5455,0.0250) (3.0793,0.5910,0.0250) (2.5884,0.5910,0.0250)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.5910,0.0000) (3.0793,0.5910,0.0000) (3.0793,0.6390,0.0000) (2.5884,0.6390,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.6390,0.0000) (3.0793,0.6390,0.0000) (3.0793,0.6510,0.0000) (2.5884,0.6510,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.6510,0.0250) (3.0793,0.6510,0.0250) (3.0793,0.8205,0.0250) (2.5884,0.8205,0.0250)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.8205,0.0000) (3.0793,0.8205,0.0000) (3.0793,0.8710,0.0000) (2.5884,0.8710,0.0000)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.3850,0.0100) (4.4802,0.3850,0.0100) (4.4802,0.4405,0.0100) (3.0793,0.4405,0.0100)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.4405,0.0495) (4.4802,0.4405,0.0495) (4.4802,0.4860,0.0495) (3.0793,0.4860,0.0495)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.4860,0.0345) (4.4802,0.4860,0.0345) (4.4802,0.4910,0.0345) (3.0793,0.4910,0.0345)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.4910,0.0000) (4.4802,0.4910,0.0000) (4.4802,0.4960,0.0000) (3.0793,0.4960,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.4960,0.0425) (4.4802,0.4960,0.0425) (4.4802,0.5190,0.0425) (3.0793,0.5190,0.0425)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.5190,0.0000) (4.4802,0.5190,0.0000) (4.4802,0.5220,0.0000) (3.0793,0.5220,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.5220,0.0000) (4.4802,0.5220,0.0000) (4.4802,0.5280,0.0000) (3.0793,0.5280,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.5280,0.0525) (4.4802,0.5280,0.0525) (4.4802,0.5410,0.0525) (3.0793,0.5410,0.0525)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.5410,0.0155) (4.4802,0.5410,0.0155) (4.4802,0.5455,0.0155) (3.0793,0.5455,0.0155)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.5455,0.0135) (4.4802,0.5455,0.0135) (4.4802,0.5910,0.0135) (3.0793,0.5910,0.0135)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.5910,0.0000) (4.4802,0.5910,0.0000) (4.4802,0.6390,0.0000) (3.0793,0.6390,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.6390,0.0000) (4.4802,0.6390,0.0000) (4.4802,0.6510,0.0000) (3.0793,0.6510,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.6510,0.0000) (4.4802,0.6510,0.0000) (4.4802,0.8205,0.0000) (3.0793,0.8205,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.8205,0.0000) (4.4802,0.8205,0.0000) (4.4802,0.8710,0.0000) (3.0793,0.8710,0.0000)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.3850,0.0080) (4.7503,0.3850,0.0080) (4.7503,0.4405,0.0080) (4.4802,0.4405,0.0080)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.4405,0.0035) (4.7503,0.4405,0.0035) (4.7503,0.4860,0.0035) (4.4802,0.4860,0.0035)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.4860,0.0000) (4.7503,0.4860,0.0000) (4.7503,0.4910,0.0000) (4.4802,0.4910,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.4910,0.0100) (4.7503,0.4910,0.0100) (4.7503,0.4960,0.0100) (4.4802,0.4960,0.0100)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.4960,0.0000) (4.7503,0.4960,0.0000) (4.7503,0.5190,0.0000) (4.4802,0.5190,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.5190,0.0000) (4.7503,0.5190,0.0000) (4.7503,0.5220,0.0000) (4.4802,0.5220,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.5220,0.0000) (4.7503,0.5220,0.0000) (4.7503,0.5280,0.0000) (4.4802,0.5280,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.5280,0.0060) (4.7503,0.5280,0.0060) (4.7503,0.5410,0.0060) (4.4802,0.5410,0.0060)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.5410,0.0000) (4.7503,0.5410,0.0000) (4.7503,0.5455,0.0000) (4.4802,0.5455,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.5455,0.0000) (4.7503,0.5455,0.0000) (4.7503,0.5910,0.0000) (4.4802,0.5910,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.5910,0.0000) (4.7503,0.5910,0.0000) (4.7503,0.6390,0.0000) (4.4802,0.6390,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.6390,0.0000) (4.7503,0.6390,0.0000) (4.7503,0.6510,0.0000) (4.4802,0.6510,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.6510,0.0000) (4.7503,0.6510,0.0000) (4.7503,0.8205,0.0000) (4.4802,0.8205,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.8205,0.0000) (4.7503,0.8205,0.0000) (4.7503,0.8710,0.0000) (4.4802,0.8710,0.0000)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.7503,0.3850,0.1860) (12.1265,0.3850,0.1860) (12.1265,0.4405,0.1860) (4.7503,0.4405,0.1860)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.7503,0.4405,0.0615) (12.1265,0.4405,0.0615) (12.1265,0.4860,0.0615) (4.7503,0.4860,0.0615)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.7503,0.4860,0.0000) (12.1265,0.4860,0.0000) (12.1265,0.4910,0.0000) (4.7503,0.4910,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.7503,0.4910,0.0045) (12.1265,0.4910,0.0045) (12.1265,0.4960,0.0045) (4.7503,0.4960,0.0045)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.7503,0.4960,0.0210) (12.1265,0.4960,0.0210) (12.1265,0.5190,0.0210) (4.7503,0.5190,0.0210)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.7503,0.5190,0.0000) (12.1265,0.5190,0.0000) (12.1265,0.5220,0.0000) (4.7503,0.5220,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.7503,0.5220,0.0120) (12.1265,0.5220,0.0120) (12.1265,0.5280,0.0120) (4.7503,0.5280,0.0120)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.7503,0.5280,0.0000) (12.1265,0.5280,0.0000) (12.1265,0.5410,0.0000) (4.7503,0.5410,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.7503,0.5410,0.0000) (12.1265,0.5410,0.0000) (12.1265,0.5455,0.0000) (4.7503,0.5455,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.7503,0.5455,0.0000) (12.1265,0.5455,0.0000) (12.1265,0.5910,0.0000) (4.7503,0.5910,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.7503,0.5910,0.0000) (12.1265,0.5910,0.0000) (12.1265,0.6390,0.0000) (4.7503,0.6390,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.7503,0.6390,0.0000) (12.1265,0.6390,0.0000) (12.1265,0.6510,0.0000) (4.7503,0.6510,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.7503,0.6510,0.0000) (12.1265,0.6510,0.0000) (12.1265,0.8205,0.0000) (4.7503,0.8205,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.7503,0.8205,0.0000) (12.1265,0.8205,0.0000) (12.1265,0.8710,0.0000) (4.7503,0.8710,0.0000)};

			\addplot3[mark=+, draw=none, mark size=0.7, jitter = 0.3] coordinates {
(4.090,0.538,1) (4.967,0.469,1) (4.967,0.469,1) (6.062,0.458,1) (6.062,0.458,1) (6.062,0.458,1) (5.561,0.524,1) (5.950,0.524,1) (6.082,0.524,1) (6.592,0.524,1) (6.347,0.524,1) (6.227,0.524,1) (5.451,0.524,1) (4.707,0.538,1) (4.462,0.538,1) (4.499,0.538,1) (4.499,0.538,1) (4.258,0.538,1) (3.796,0.538,1) (3.796,0.538,1) (3.798,0.538,1) (4.012,0.538,1) (3.977,0.538,1) (4.095,0.538,1) (4.400,0.538,1) (4.455,0.538,1) (4.682,0.538,1) (4.453,0.538,1) (4.455,0.538,1) (4.239,0.538,1) (4.233,0.538,1) (4.175,0.538,1) (3.990,0.538,1) (3.787,0.538,1) (3.760,0.538,1) (3.360,0.499,1) (3.378,0.499,1) (3.934,0.499,1) (3.847,0.499,1) (5.401,0.428,1) (5.401,0.428,1) (5.721,0.448,1) (5.721,0.448,1) (5.721,0.448,1) (5.721,0.448,1) (5.100,0.448,1) (5.100,0.448,1) (5.689,0.448,1) (5.870,0.448,1) (6.088,0.448,1) (6.815,0.439,1) (6.815,0.439,1) (6.815,0.439,1) (6.815,0.439,1) (7.320,0.410,1) (8.697,0.403,1) (9.188,0.410,1) (8.325,0.411,1) (7.815,0.453,1) (6.932,0.453,1) (7.225,0.453,1) (6.819,0.453,1) (7.226,0.453,1) (7.981,0.453,1) (9.223,0.416,1) (6.612,0.398,1) (6.612,0.398,1) (6.498,0.409,1) (6.498,0.409,1) (6.498,0.409,1) (5.287,0.413,1) (5.287,0.413,1) (5.287,0.413,1) (5.287,0.413,1) (4.252,0.437,1) (4.503,0.437,1) (4.052,0.437,1) (4.090,0.437,1) (5.014,0.437,1) (4.503,0.437,1) (5.401,0.426,1) (5.401,0.426,1) (5.401,0.426,1) (5.401,0.426,1) (4.779,0.449,1) (4.438,0.449,1) (4.427,0.449,1) (3.748,0.449,1) (3.422,0.489,1) (3.414,0.489,1) (3.092,0.489,1) (3.092,0.489,1) (3.666,0.464,1) (3.666,0.464,1) (3.615,0.464,1) (3.495,0.445,1) (3.495,0.445,1) (3.495,0.445,1) (3.495,0.445,1) (3.495,0.445,1) (2.778,0.520,1) (2.856,0.520,1) (2.715,0.520,1) (2.715,0.520,1) (2.421,0.520,1) (2.107,0.520,1) (2.211,0.520,1) (2.122,0.520,1) (2.433,0.520,1) (2.545,0.520,1) (2.778,0.520,1) (2.678,0.547,1) (2.353,0.547,1) (2.548,0.547,1) (2.256,0.547,1) (2.463,0.547,1) (2.730,0.547,1) (2.747,0.547,1) (2.478,0.547,1) (2.759,0.547,1) (2.258,0.581,1) (2.197,0.581,1) (2.087,0.581,1) (1.944,0.581,1) (2.006,0.581,1) (1.993,0.581,1) (1.757,0.581,1) (1.788,0.624,1) (1.813,0.624,1) (1.980,0.624,1) (2.119,0.624,1) (2.271,0.624,1) (2.327,0.624,1) (2.470,0.624,1) (2.346,0.624,1) (2.111,0.624,1) (1.967,0.624,1) (1.850,0.624,1) (1.669,0.624,1) (1.669,0.624,1) (1.612,0.624,1) (1.439,0.624,1) (1.322,0.871,1) (1.412,0.871,1) (1.346,0.871,1) (1.419,0.871,1) (1.517,0.871,1) (1.461,0.871,1) (1.530,0.871,1) (1.526,0.871,1) (1.618,0.871,1) (1.592,0.871,1) (1.610,0.871,1) (1.623,0.871,1) (1.749,0.871,1) (1.746,0.871,1) (1.736,0.871,1) (1.877,0.605,1) (1.757,0.605,1) (1.766,0.871,1) (1.798,0.605,1) (1.971,0.605,1) (2.041,0.605,1) (2.162,0.605,1) (2.422,0.605,1) (2.283,0.605,1) (2.046,0.605,1) (2.426,0.605,1) (2.100,0.605,1) (2.263,0.605,1) (2.426,0.605,1) (2.389,0.605,1) (2.596,0.510,1) (2.646,0.510,1) (2.702,0.510,1) (3.132,0.510,1) (3.555,0.510,1) (3.317,0.510,1) (2.915,0.510,1) (2.829,0.488,1) (2.741,0.488,1) (2.598,0.488,1) (2.701,0.488,1) (2.847,0.488,1) (2.988,0.488,1) (3.280,0.488,1) (3.199,0.488,1) (3.789,0.437,1) (4.567,0.437,1) (4.567,0.437,1) (6.480,0.437,1) (6.480,0.437,1) (6.480,0.437,1) (6.220,0.401,1) (6.220,0.401,1) (5.648,0.422,1) (7.309,0.404,1) (7.309,0.404,1) (7.309,0.404,1) (7.653,0.403,1) (7.653,0.403,1) (6.270,0.415,1) (6.270,0.415,1) (5.118,0.416,1) (5.118,0.416,1) (3.945,0.489,1) (4.355,0.489,1) (4.355,0.489,1) (4.239,0.489,1) (3.875,0.489,1) (3.877,0.489,1) (3.665,0.489,1) (3.653,0.489,1) (3.945,0.489,1) (3.587,0.489,1) (3.945,0.489,1) (3.112,0.550,1) (3.421,0.550,1) (2.889,0.550,1) (3.363,0.550,1) (2.862,0.507,1) (3.048,0.507,1) (3.272,0.507,1) (3.272,0.507,1) (2.894,0.504,1) (2.894,0.504,1) (3.216,0.504,1) (3.216,0.504,1) (3.375,0.504,1) (3.375,0.504,1) (3.671,0.504,1) (3.671,0.504,1) (3.838,0.507,1) (3.652,0.507,1) (3.652,0.507,1) (3.652,0.507,1) (4.148,0.507,1) (4.148,0.507,1) (6.190,0.428,1) (6.190,0.428,1) (6.336,0.428,1) (6.336,0.428,1) (7.035,0.428,1) (7.035,0.428,1) (7.955,0.431,1) (7.955,0.431,1) (8.056,0.431,1) (8.056,0.431,1) (7.827,0.431,1) (7.827,0.431,1) (7.397,0.431,1) (7.397,0.431,1) (8.907,0.431,1) (8.907,0.431,1) (9.220,0.392,1) (9.220,0.392,1) (6.336,0.394,1) (1.801,0.647,1) (1.895,0.647,1) (2.011,0.647,1) (2.112,0.647,1) (2.140,0.647,1) (2.288,0.647,1) (2.079,0.647,1) (1.930,0.647,1) (1.986,0.647,1) (2.133,0.647,1) (2.422,0.575,1) (2.872,0.575,1) (3.917,0.464,1) (4.429,0.464,1) (4.429,0.464,1) (3.917,0.464,1) (4.367,0.464,1) (4.078,0.447,1) (4.267,0.447,1) (4.787,0.447,1) (4.863,0.447,1) (4.140,0.447,1) (4.101,0.443,1) (4.695,0.443,1) (5.245,0.443,1) (5.212,0.443,1) (5.885,0.401,1) (7.307,0.400,1) (7.307,0.389,1) (9.089,0.385,1) (7.317,0.405,1) (7.317,0.405,1) (7.317,0.405,1) (5.117,0.411,1) (5.117,0.411,1) (5.117,0.411,1) (5.503,0.437,1) (5.503,0.437,1) (5.960,0.437,1) (5.960,0.437,1) (6.320,0.437,1) (7.828,0.400,1) (7.828,0.400,1) (7.828,0.400,1) (5.492,0.433,1) (5.492,0.433,1) (5.492,0.433,1) (4.022,0.472,1) (3.370,0.472,1) (3.099,0.472,1) (3.183,0.472,1) (3.317,0.544,1) (3.103,0.544,1) (2.519,0.544,1) (2.640,0.544,1) (2.834,0.544,1) (3.263,0.544,1) (3.602,0.544,1) (3.945,0.544,1) (3.999,0.544,1) (4.032,0.544,1) (3.533,0.544,1) (4.002,0.544,1) (4.540,0.493,1) (4.540,0.493,1) (4.721,0.493,1) (4.721,0.493,1) (4.721,0.493,1) (5.416,0.493,1) (5.416,0.493,1) (5.416,0.493,1) (5.215,0.460,1) (5.215,0.460,1) (5.874,0.460,1) (6.641,0.438,1) (6.641,0.438,1) (6.458,0.515,1) (6.458,0.515,1) (5.985,0.515,1) (5.231,0.515,1) (5.615,0.515,1) (4.812,0.515,1) (4.812,0.515,1) (4.812,0.515,1) (7.038,0.442,1) (6.267,0.518,1) (5.732,0.484,1) (6.465,0.484,1) (8.014,0.442,1) (8.014,0.442,1) (8.535,0.429,1) (8.344,0.435,1) (8.792,0.429,1) (8.792,0.429,1) (10.710,0.411,1) (10.710,0.411,1) (12.127,0.410,1) (10.586,0.413,1) (10.586,0.413,1) (2.122,0.770,1) (2.505,0.770,1) (2.723,0.770,1) (2.509,0.770,1) (2.518,0.770,1) (2.296,0.770,1) (2.104,0.770,1) (1.905,0.770,1) (1.905,0.718,1) (1.613,0.718,1) (1.752,0.718,1) (1.511,0.631,1) (1.333,0.631,1) (1.357,0.631,1) (1.202,0.631,1) (1.169,0.631,1) (1.130,0.668,1) (1.174,0.668,1) (1.137,0.668,1) (1.316,0.671,1) (1.345,0.671,1) (1.358,0.671,1) (1.386,0.671,1) (1.386,0.671,1) (1.417,0.671,1) (1.519,0.671,1) (1.580,0.700,1) (1.533,0.700,1) (1.440,0.700,1) (1.426,0.700,1) (1.467,0.700,1) (1.518,0.700,1) (1.589,0.700,1) (1.728,0.700,1) (1.927,0.700,1) (2.168,0.700,1) (1.770,0.700,1) (1.791,0.693,1) (1.782,0.693,1) (1.726,0.693,1) (1.677,0.693,1) (1.633,0.693,1) (1.490,0.693,1) (1.500,0.693,1) (1.589,0.693,1) (1.574,0.693,1) (1.639,0.693,1) (1.703,0.693,1) (1.607,0.693,1) (1.425,0.693,1) (1.178,0.659,1) (1.285,0.659,1) (1.455,0.597,1) (1.466,0.597,1) (1.413,0.597,1) (1.528,0.597,1) (1.554,0.597,1) (1.589,0.597,1) (1.658,0.693,1) (1.835,0.679,1) (1.819,0.679,1) (1.647,0.679,1) (1.803,0.679,1) (1.794,0.718,1) (1.859,0.718,1) (1.875,0.718,1) (1.951,0.614,1) (2.022,0.614,1) (2.063,0.584,1) (1.910,0.679,1) (1.998,0.584,1) (1.863,0.679,1) (1.936,0.679,1) (1.968,0.679,1) (2.053,0.584,1) (2.088,0.584,1) (2.200,0.584,1) (2.316,0.713,1) (2.222,0.713,1) (2.125,0.740,1) (2.003,0.740,1) (1.914,0.740,1) (1.821,0.740,1) (1.817,0.740,1) (1.866,0.740,1) (2.065,0.740,1) (2.005,0.740,1) (1.978,0.740,1) (1.896,0.740,1) (1.988,0.740,1) (2.072,0.740,1) (2.198,0.740,1) (2.262,0.713,1) (2.185,0.713,1) (2.324,0.713,1) (2.355,0.713,1) (2.368,0.713,1) (2.453,0.713,1) (2.496,0.713,1) (2.436,0.713,1) (2.581,0.713,1) (2.779,0.713,1) (2.783,0.713,1) (2.717,0.713,1) (2.598,0.713,1) (2.567,0.713,1) (2.734,0.713,1) (2.802,0.713,1) (2.963,0.655,1) (3.067,0.655,1) (2.872,0.655,1) (2.540,0.584,1) (2.908,0.580,1) (2.824,0.580,1) (3.033,0.580,1) (3.099,0.532,1) (2.897,0.580,1) (2.533,0.614,1) (2.430,0.584,1) (2.206,0.584,1) (2.305,0.614,1) (2.101,0.614,1) (2.171,0.614,1) (1.951,0.614,1) (3.424,0.532,1) (3.332,0.532,1) (3.411,0.532,1) (4.098,0.532,1) (3.724,0.583,1) (3.992,0.583,1) (3.546,0.583,1) (3.152,0.583,1) (1.821,0.609,1) (1.755,0.609,1) (1.823,0.609,1) (1.868,0.609,1) (2.110,0.609,1) (2.382,0.585,1) (2.382,0.585,1) (2.799,0.585,1) (2.799,0.585,1) (2.893,0.585,1) (2.409,0.585,1) (2.400,0.585,1) (2.498,0.585,1) (2.479,0.573,1) (2.288,0.573,1) (2.167,0.573,1) (2.389,0.573,1) (2.505,0.573,1) };
		\end{axis}
	\end{tikzpicture}

### 2015-11-17 graph_housing_exp2_distr_3_5.tex
Experiment part

\begin{tikzpicture}
		\begin{axis}[
			view={0}{90},
			enlargelimits=0,
			zmin=0.0, zmax=1.0,
			xlabel=C,
			ylabel=E,
			colorbar,
			point meta min=0, point meta max=0.5,
			colormap={}{ gray(0cm)=(1); gray(1cm)=(0);},
			colorbar style={
			        ytick={0,0.05,...,0.5},
			        yticklabel style={
			            text width=2.5em,
			            align=right,
			            /pgf/number format/.cd,
			                fixed,
			                fixed zerofill
			        }
			    }
			]

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.3850,0.1105) (3.8750,0.3850,0.1105) (3.8750,0.4460,0.1105) (0.4600,0.4460,0.1105)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.4460,0.0000) (3.8750,0.4460,0.0000) (3.8750,0.4485,0.0000) (0.4600,0.4485,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.4485,0.0000) (3.8750,0.4485,0.0000) (3.8750,0.4555,0.0000) (0.4600,0.4555,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.4555,0.0130) (3.8750,0.4555,0.0130) (3.8750,0.4620,0.0130) (0.4600,0.4620,0.0130)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.4620,0.0000) (3.8750,0.4620,0.0000) (3.8750,0.4705,0.0000) (0.4600,0.4705,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.4705,0.0285) (3.8750,0.4705,0.0285) (3.8750,0.4910,0.0285) (0.4600,0.4910,0.0285)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.4910,0.0000) (3.8750,0.4910,0.0000) (3.8750,0.4960,0.0000) (0.4600,0.4960,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.4960,0.0000) (3.8750,0.4960,0.0000) (3.8750,0.5015,0.0000) (0.4600,0.5015,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.5015,0.0000) (3.8750,0.5015,0.0000) (3.8750,0.5085,0.0000) (0.4600,0.5085,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.5085,0.0000) (3.8750,0.5085,0.0000) (3.8750,0.5165,0.0000) (0.4600,0.5165,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.5165,0.0025) (3.8750,0.5165,0.0025) (3.8750,0.5410,0.0025) (0.4600,0.5410,0.0025)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.5410,0.0000) (3.8750,0.5410,0.0000) (3.8750,0.5485,0.0000) (0.4600,0.5485,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.5485,0.0000) (3.8750,0.5485,0.0000) (3.8750,0.5775,0.0000) (0.4600,0.5775,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.5775,0.0000) (3.8750,0.5775,0.0000) (3.8750,0.6010,0.0000) (0.4600,0.6010,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.6010,0.0000) (3.8750,0.6010,0.0000) (3.8750,0.6070,0.0000) (0.4600,0.6070,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.6070,0.0000) (3.8750,0.6070,0.0000) (3.8750,0.6115,0.0000) (0.4600,0.6115,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.6115,0.0000) (3.8750,0.6115,0.0000) (3.8750,0.6190,0.0000) (0.4600,0.6190,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.6190,0.0000) (3.8750,0.6190,0.0000) (3.8750,0.6275,0.0000) (0.4600,0.6275,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.6275,0.0000) (3.8750,0.6275,0.0000) (3.8750,0.6390,0.0000) (0.4600,0.6390,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.6390,0.0000) (3.8750,0.6390,0.0000) (3.8750,0.6510,0.0000) (0.4600,0.6510,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.6510,0.0000) (3.8750,0.6510,0.0000) (3.8750,0.8205,0.0000) (0.4600,0.8205,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.8205,0.0000) (3.8750,0.8205,0.0000) (3.8750,0.8710,0.0000) (0.4600,0.8710,0.0000)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.3850,0.0000) (3.9850,0.3850,0.0000) (3.9850,0.4460,0.0000) (3.8750,0.4460,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.4460,0.0000) (3.9850,0.4460,0.0000) (3.9850,0.4485,0.0000) (3.8750,0.4485,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.4485,0.0000) (3.9850,0.4485,0.0000) (3.9850,0.4555,0.0000) (3.8750,0.4555,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.4555,0.0000) (3.9850,0.4555,0.0000) (3.9850,0.4620,0.0000) (3.8750,0.4620,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.4620,0.0000) (3.9850,0.4620,0.0000) (3.9850,0.4705,0.0000) (3.8750,0.4705,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.4705,0.0000) (3.9850,0.4705,0.0000) (3.9850,0.4910,0.0000) (3.8750,0.4910,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.4910,0.0000) (3.9850,0.4910,0.0000) (3.9850,0.4960,0.0000) (3.8750,0.4960,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.4960,0.0000) (3.9850,0.4960,0.0000) (3.9850,0.5015,0.0000) (3.8750,0.5015,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.5015,0.0000) (3.9850,0.5015,0.0000) (3.9850,0.5085,0.0000) (3.8750,0.5085,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.5085,0.0000) (3.9850,0.5085,0.0000) (3.9850,0.5165,0.0000) (3.8750,0.5165,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.5165,0.0000) (3.9850,0.5165,0.0000) (3.9850,0.5410,0.0000) (3.8750,0.5410,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.5410,0.0000) (3.9850,0.5410,0.0000) (3.9850,0.5485,0.0000) (3.8750,0.5485,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.5485,0.0035) (3.9850,0.5485,0.0035) (3.9850,0.5775,0.0035) (3.8750,0.5775,0.0035)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.5775,0.0000) (3.9850,0.5775,0.0000) (3.9850,0.6010,0.0000) (3.8750,0.6010,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.6010,0.0000) (3.9850,0.6010,0.0000) (3.9850,0.6070,0.0000) (3.8750,0.6070,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.6070,0.0000) (3.9850,0.6070,0.0000) (3.9850,0.6115,0.0000) (3.8750,0.6115,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.6115,0.0000) (3.9850,0.6115,0.0000) (3.9850,0.6190,0.0000) (3.8750,0.6190,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.6190,0.0000) (3.9850,0.6190,0.0000) (3.9850,0.6275,0.0000) (3.8750,0.6275,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.6275,0.0000) (3.9850,0.6275,0.0000) (3.9850,0.6390,0.0000) (3.8750,0.6390,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.6390,0.0225) (3.9850,0.6390,0.0225) (3.9850,0.6510,0.0225) (3.8750,0.6510,0.0225)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.6510,0.0000) (3.9850,0.6510,0.0000) (3.9850,0.8205,0.0000) (3.8750,0.8205,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.8205,0.0000) (3.9850,0.8205,0.0000) (3.9850,0.8710,0.0000) (3.8750,0.8710,0.0000)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.3850,0.0680) (6.1450,0.3850,0.0680) (6.1450,0.4460,0.0680) (3.9850,0.4460,0.0680)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.4460,0.0000) (6.1450,0.4460,0.0000) (6.1450,0.4485,0.0000) (3.9850,0.4485,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.4485,0.0210) (6.1450,0.4485,0.0210) (6.1450,0.4555,0.0210) (3.9850,0.4555,0.0210)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.4555,0.0000) (6.1450,0.4555,0.0000) (6.1450,0.4620,0.0000) (3.9850,0.4620,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.4620,0.0000) (6.1450,0.4620,0.0000) (6.1450,0.4705,0.0000) (3.9850,0.4705,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.4705,0.0000) (6.1450,0.4705,0.0000) (6.1450,0.4910,0.0000) (3.9850,0.4910,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.4910,0.0000) (6.1450,0.4910,0.0000) (6.1450,0.4960,0.0000) (3.9850,0.4960,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.4960,0.0095) (6.1450,0.4960,0.0095) (6.1450,0.5015,0.0095) (3.9850,0.5015,0.0095)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.5015,0.0000) (6.1450,0.5015,0.0000) (6.1450,0.5085,0.0000) (3.9850,0.5085,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.5085,0.0300) (6.1450,0.5085,0.0300) (6.1450,0.5165,0.0300) (3.9850,0.5165,0.0300)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.5165,0.0000) (6.1450,0.5165,0.0000) (6.1450,0.5410,0.0000) (3.9850,0.5410,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.5410,0.0000) (6.1450,0.5410,0.0000) (6.1450,0.5485,0.0000) (3.9850,0.5485,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.5485,0.0000) (6.1450,0.5485,0.0000) (6.1450,0.5775,0.0000) (3.9850,0.5775,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.5775,0.0000) (6.1450,0.5775,0.0000) (6.1450,0.6010,0.0000) (3.9850,0.6010,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.6010,0.0000) (6.1450,0.6010,0.0000) (6.1450,0.6070,0.0000) (3.9850,0.6070,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.6070,0.0000) (6.1450,0.6070,0.0000) (6.1450,0.6115,0.0000) (3.9850,0.6115,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.6115,0.0000) (6.1450,0.6115,0.0000) (6.1450,0.6190,0.0000) (3.9850,0.6190,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.6190,0.0000) (6.1450,0.6190,0.0000) (6.1450,0.6275,0.0000) (3.9850,0.6275,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.6275,0.0000) (6.1450,0.6275,0.0000) (6.1450,0.6390,0.0000) (3.9850,0.6390,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.6390,0.0000) (6.1450,0.6390,0.0000) (6.1450,0.6510,0.0000) (3.9850,0.6510,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.6510,0.0000) (6.1450,0.6510,0.0000) (6.1450,0.8205,0.0000) (3.9850,0.8205,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.8205,0.0000) (6.1450,0.8205,0.0000) (6.1450,0.8710,0.0000) (3.9850,0.8710,0.0000)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.1450,0.3850,0.0000) (6.3050,0.3850,0.0000) (6.3050,0.4460,0.0000) (6.1450,0.4460,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.1450,0.4460,0.0000) (6.3050,0.4460,0.0000) (6.3050,0.4485,0.0000) (6.1450,0.4485,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.1450,0.4485,0.0000) (6.3050,0.4485,0.0000) (6.3050,0.4555,0.0000) (6.1450,0.4555,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.1450,0.4555,0.0000) (6.3050,0.4555,0.0000) (6.3050,0.4620,0.0000) (6.1450,0.4620,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.1450,0.4620,0.0000) (6.3050,0.4620,0.0000) (6.3050,0.4705,0.0000) (6.1450,0.4705,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.1450,0.4705,0.0000) (6.3050,0.4705,0.0000) (6.3050,0.4910,0.0000) (6.1450,0.4910,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.1450,0.4910,0.0000) (6.3050,0.4910,0.0000) (6.3050,0.4960,0.0000) (6.1450,0.4960,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.1450,0.4960,0.0000) (6.3050,0.4960,0.0000) (6.3050,0.5015,0.0000) (6.1450,0.5015,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.1450,0.5015,0.0410) (6.3050,0.5015,0.0410) (6.3050,0.5085,0.0410) (6.1450,0.5085,0.0410)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.1450,0.5085,0.0000) (6.3050,0.5085,0.0000) (6.3050,0.5165,0.0000) (6.1450,0.5165,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.1450,0.5165,0.0000) (6.3050,0.5165,0.0000) (6.3050,0.5410,0.0000) (6.1450,0.5410,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.1450,0.5410,0.0000) (6.3050,0.5410,0.0000) (6.3050,0.5485,0.0000) (6.1450,0.5485,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.1450,0.5485,0.0000) (6.3050,0.5485,0.0000) (6.3050,0.5775,0.0000) (6.1450,0.5775,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.1450,0.5775,0.0000) (6.3050,0.5775,0.0000) (6.3050,0.6010,0.0000) (6.1450,0.6010,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.1450,0.6010,0.0000) (6.3050,0.6010,0.0000) (6.3050,0.6070,0.0000) (6.1450,0.6070,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.1450,0.6070,0.0000) (6.3050,0.6070,0.0000) (6.3050,0.6115,0.0000) (6.1450,0.6115,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.1450,0.6115,0.0000) (6.3050,0.6115,0.0000) (6.3050,0.6190,0.0000) (6.1450,0.6190,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.1450,0.6190,0.0000) (6.3050,0.6190,0.0000) (6.3050,0.6275,0.0000) (6.1450,0.6275,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.1450,0.6275,0.0000) (6.3050,0.6275,0.0000) (6.3050,0.6390,0.0000) (6.1450,0.6390,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.1450,0.6390,0.0000) (6.3050,0.6390,0.0000) (6.3050,0.6510,0.0000) (6.1450,0.6510,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.1450,0.6510,0.0000) (6.3050,0.6510,0.0000) (6.3050,0.8205,0.0000) (6.1450,0.8205,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.1450,0.8205,0.0000) (6.3050,0.8205,0.0000) (6.3050,0.8710,0.0000) (6.1450,0.8710,0.0000)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.3050,0.3850,0.0000) (7.2250,0.3850,0.0000) (7.2250,0.4460,0.0000) (6.3050,0.4460,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.3050,0.4460,0.0285) (7.2250,0.4460,0.0285) (7.2250,0.4485,0.0285) (6.3050,0.4485,0.0285)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.3050,0.4485,0.0000) (7.2250,0.4485,0.0000) (7.2250,0.4555,0.0000) (6.3050,0.4555,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.3050,0.4555,0.0000) (7.2250,0.4555,0.0000) (7.2250,0.4620,0.0000) (6.3050,0.4620,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.3050,0.4620,0.0165) (7.2250,0.4620,0.0165) (7.2250,0.4705,0.0165) (6.3050,0.4705,0.0165)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.3050,0.4705,0.0000) (7.2250,0.4705,0.0000) (7.2250,0.4910,0.0000) (6.3050,0.4910,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.3050,0.4910,0.0000) (7.2250,0.4910,0.0000) (7.2250,0.4960,0.0000) (6.3050,0.4960,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.3050,0.4960,0.0000) (7.2250,0.4960,0.0000) (7.2250,0.5015,0.0000) (6.3050,0.5015,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.3050,0.5015,0.0000) (7.2250,0.5015,0.0000) (7.2250,0.5085,0.0000) (6.3050,0.5085,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.3050,0.5085,0.0000) (7.2250,0.5085,0.0000) (7.2250,0.5165,0.0000) (6.3050,0.5165,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.3050,0.5165,0.0000) (7.2250,0.5165,0.0000) (7.2250,0.5410,0.0000) (6.3050,0.5410,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.3050,0.5410,0.0000) (7.2250,0.5410,0.0000) (7.2250,0.5485,0.0000) (6.3050,0.5485,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.3050,0.5485,0.0000) (7.2250,0.5485,0.0000) (7.2250,0.5775,0.0000) (6.3050,0.5775,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.3050,0.5775,0.0000) (7.2250,0.5775,0.0000) (7.2250,0.6010,0.0000) (6.3050,0.6010,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.3050,0.6010,0.0000) (7.2250,0.6010,0.0000) (7.2250,0.6070,0.0000) (6.3050,0.6070,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.3050,0.6070,0.0000) (7.2250,0.6070,0.0000) (7.2250,0.6115,0.0000) (6.3050,0.6115,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.3050,0.6115,0.0000) (7.2250,0.6115,0.0000) (7.2250,0.6190,0.0000) (6.3050,0.6190,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.3050,0.6190,0.0000) (7.2250,0.6190,0.0000) (7.2250,0.6275,0.0000) (6.3050,0.6275,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.3050,0.6275,0.0000) (7.2250,0.6275,0.0000) (7.2250,0.6390,0.0000) (6.3050,0.6390,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.3050,0.6390,0.0000) (7.2250,0.6390,0.0000) (7.2250,0.6510,0.0000) (6.3050,0.6510,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.3050,0.6510,0.0000) (7.2250,0.6510,0.0000) (7.2250,0.8205,0.0000) (6.3050,0.8205,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.3050,0.8205,0.0000) (7.2250,0.8205,0.0000) (7.2250,0.8710,0.0000) (6.3050,0.8710,0.0000)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.3850,0.0000) (7.6250,0.3850,0.0000) (7.6250,0.4460,0.0000) (7.2250,0.4460,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.4460,0.0000) (7.6250,0.4460,0.0000) (7.6250,0.4485,0.0000) (7.2250,0.4485,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.4485,0.0000) (7.6250,0.4485,0.0000) (7.6250,0.4555,0.0000) (7.2250,0.4555,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.4555,0.0000) (7.6250,0.4555,0.0000) (7.6250,0.4620,0.0000) (7.2250,0.4620,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.4620,0.0000) (7.6250,0.4620,0.0000) (7.6250,0.4705,0.0000) (7.2250,0.4705,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.4705,0.0000) (7.6250,0.4705,0.0000) (7.6250,0.4910,0.0000) (7.2250,0.4910,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.4910,0.0125) (7.6250,0.4910,0.0125) (7.6250,0.4960,0.0125) (7.2250,0.4960,0.0125)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.4960,0.0000) (7.6250,0.4960,0.0000) (7.6250,0.5015,0.0000) (7.2250,0.5015,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.5015,0.0000) (7.6250,0.5015,0.0000) (7.6250,0.5085,0.0000) (7.2250,0.5085,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.5085,0.0000) (7.6250,0.5085,0.0000) (7.6250,0.5165,0.0000) (7.2250,0.5165,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.5165,0.0000) (7.6250,0.5165,0.0000) (7.6250,0.5410,0.0000) (7.2250,0.5410,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.5410,0.0000) (7.6250,0.5410,0.0000) (7.6250,0.5485,0.0000) (7.2250,0.5485,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.5485,0.0000) (7.6250,0.5485,0.0000) (7.6250,0.5775,0.0000) (7.2250,0.5775,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.5775,0.0000) (7.6250,0.5775,0.0000) (7.6250,0.6010,0.0000) (7.2250,0.6010,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.6010,0.0000) (7.6250,0.6010,0.0000) (7.6250,0.6070,0.0000) (7.2250,0.6070,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.6070,0.0000) (7.6250,0.6070,0.0000) (7.6250,0.6115,0.0000) (7.2250,0.6115,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.6115,0.0000) (7.6250,0.6115,0.0000) (7.6250,0.6190,0.0000) (7.2250,0.6190,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.6190,0.0000) (7.6250,0.6190,0.0000) (7.6250,0.6275,0.0000) (7.2250,0.6275,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.6275,0.0000) (7.6250,0.6275,0.0000) (7.6250,0.6390,0.0000) (7.2250,0.6390,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.6390,0.0000) (7.6250,0.6390,0.0000) (7.6250,0.6510,0.0000) (7.2250,0.6510,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.6510,0.0000) (7.6250,0.6510,0.0000) (7.6250,0.8205,0.0000) (7.2250,0.8205,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.8205,0.0000) (7.6250,0.8205,0.0000) (7.6250,0.8710,0.0000) (7.2250,0.8710,0.0000)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.6250,0.3850,0.0000) (9.1250,0.3850,0.0000) (9.1250,0.4460,0.0000) (7.6250,0.4460,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.6250,0.4460,0.0000) (9.1250,0.4460,0.0000) (9.1250,0.4485,0.0000) (7.6250,0.4485,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.6250,0.4485,0.0000) (9.1250,0.4485,0.0000) (9.1250,0.4555,0.0000) (7.6250,0.4555,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.6250,0.4555,0.0000) (9.1250,0.4555,0.0000) (9.1250,0.4620,0.0000) (7.6250,0.4620,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.6250,0.4620,0.0000) (9.1250,0.4620,0.0000) (9.1250,0.4705,0.0000) (7.6250,0.4705,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.6250,0.4705,0.0000) (9.1250,0.4705,0.0000) (9.1250,0.4910,0.0000) (7.6250,0.4910,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.6250,0.4910,0.0000) (9.1250,0.4910,0.0000) (9.1250,0.4960,0.0000) (7.6250,0.4960,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.6250,0.4960,0.0000) (9.1250,0.4960,0.0000) (9.1250,0.5015,0.0000) (7.6250,0.5015,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.6250,0.5015,0.0000) (9.1250,0.5015,0.0000) (9.1250,0.5085,0.0000) (7.6250,0.5085,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.6250,0.5085,0.0000) (9.1250,0.5085,0.0000) (9.1250,0.5165,0.0000) (7.6250,0.5165,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.6250,0.5165,0.0820) (9.1250,0.5165,0.0820) (9.1250,0.5410,0.0820) (7.6250,0.5410,0.0820)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.6250,0.5410,0.0000) (9.1250,0.5410,0.0000) (9.1250,0.5485,0.0000) (7.6250,0.5485,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.6250,0.5485,0.0000) (9.1250,0.5485,0.0000) (9.1250,0.5775,0.0000) (7.6250,0.5775,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.6250,0.5775,0.0000) (9.1250,0.5775,0.0000) (9.1250,0.6010,0.0000) (7.6250,0.6010,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.6250,0.6010,0.0000) (9.1250,0.6010,0.0000) (9.1250,0.6070,0.0000) (7.6250,0.6070,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.6250,0.6070,0.0000) (9.1250,0.6070,0.0000) (9.1250,0.6115,0.0000) (7.6250,0.6115,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.6250,0.6115,0.0000) (9.1250,0.6115,0.0000) (9.1250,0.6190,0.0000) (7.6250,0.6190,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.6250,0.6190,0.0000) (9.1250,0.6190,0.0000) (9.1250,0.6275,0.0000) (7.6250,0.6275,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.6250,0.6275,0.0000) (9.1250,0.6275,0.0000) (9.1250,0.6390,0.0000) (7.6250,0.6390,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.6250,0.6390,0.0000) (9.1250,0.6390,0.0000) (9.1250,0.6510,0.0000) (7.6250,0.6510,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.6250,0.6510,0.0000) (9.1250,0.6510,0.0000) (9.1250,0.8205,0.0000) (7.6250,0.8205,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.6250,0.8205,0.0000) (9.1250,0.8205,0.0000) (9.1250,0.8710,0.0000) (7.6250,0.8710,0.0000)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.3850,0.0000) (9.7950,0.3850,0.0000) (9.7950,0.4460,0.0000) (9.1250,0.4460,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.4460,0.0000) (9.7950,0.4460,0.0000) (9.7950,0.4485,0.0000) (9.1250,0.4485,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.4485,0.0000) (9.7950,0.4485,0.0000) (9.7950,0.4555,0.0000) (9.1250,0.4555,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.4555,0.0000) (9.7950,0.4555,0.0000) (9.7950,0.4620,0.0000) (9.1250,0.4620,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.4620,0.0000) (9.7950,0.4620,0.0000) (9.7950,0.4705,0.0000) (9.1250,0.4705,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.4705,0.0000) (9.7950,0.4705,0.0000) (9.7950,0.4910,0.0000) (9.1250,0.4910,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.4910,0.0000) (9.7950,0.4910,0.0000) (9.7950,0.4960,0.0000) (9.1250,0.4960,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.4960,0.0000) (9.7950,0.4960,0.0000) (9.7950,0.5015,0.0000) (9.1250,0.5015,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.5015,0.0000) (9.7950,0.5015,0.0000) (9.7950,0.5085,0.0000) (9.1250,0.5085,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.5085,0.0000) (9.7950,0.5085,0.0000) (9.7950,0.5165,0.0000) (9.1250,0.5165,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.5165,0.0000) (9.7950,0.5165,0.0000) (9.7950,0.5410,0.0000) (9.1250,0.5410,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.5410,0.0000) (9.7950,0.5410,0.0000) (9.7950,0.5485,0.0000) (9.1250,0.5485,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.5485,0.0000) (9.7950,0.5485,0.0000) (9.7950,0.5775,0.0000) (9.1250,0.5775,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.5775,0.0200) (9.7950,0.5775,0.0200) (9.7950,0.6010,0.0200) (9.1250,0.6010,0.0200)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.6010,0.0000) (9.7950,0.6010,0.0000) (9.7950,0.6070,0.0000) (9.1250,0.6070,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.6070,0.0000) (9.7950,0.6070,0.0000) (9.7950,0.6115,0.0000) (9.1250,0.6115,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.6115,0.0000) (9.7950,0.6115,0.0000) (9.7950,0.6190,0.0000) (9.1250,0.6190,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.6190,0.0000) (9.7950,0.6190,0.0000) (9.7950,0.6275,0.0000) (9.1250,0.6275,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.6275,0.0000) (9.7950,0.6275,0.0000) (9.7950,0.6390,0.0000) (9.1250,0.6390,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.6390,0.0000) (9.7950,0.6390,0.0000) (9.7950,0.6510,0.0000) (9.1250,0.6510,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.6510,0.0000) (9.7950,0.6510,0.0000) (9.7950,0.8205,0.0000) (9.1250,0.8205,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.8205,0.0000) (9.7950,0.8205,0.0000) (9.7950,0.8710,0.0000) (9.1250,0.8710,0.0000)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.7950,0.3850,0.0000) (10.7000,0.3850,0.0000) (10.7000,0.4460,0.0000) (9.7950,0.4460,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.7950,0.4460,0.0000) (10.7000,0.4460,0.0000) (10.7000,0.4485,0.0000) (9.7950,0.4485,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.7950,0.4485,0.0000) (10.7000,0.4485,0.0000) (10.7000,0.4555,0.0000) (9.7950,0.4555,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.7950,0.4555,0.0000) (10.7000,0.4555,0.0000) (10.7000,0.4620,0.0000) (9.7950,0.4620,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.7950,0.4620,0.0000) (10.7000,0.4620,0.0000) (10.7000,0.4705,0.0000) (9.7950,0.4705,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.7950,0.4705,0.0230) (10.7000,0.4705,0.0230) (10.7000,0.4910,0.0230) (9.7950,0.4910,0.0230)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.7950,0.4910,0.0000) (10.7000,0.4910,0.0000) (10.7000,0.4960,0.0000) (9.7950,0.4960,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.7950,0.4960,0.0000) (10.7000,0.4960,0.0000) (10.7000,0.5015,0.0000) (9.7950,0.5015,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.7950,0.5015,0.0000) (10.7000,0.5015,0.0000) (10.7000,0.5085,0.0000) (9.7950,0.5085,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.7950,0.5085,0.0000) (10.7000,0.5085,0.0000) (10.7000,0.5165,0.0000) (9.7950,0.5165,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.7950,0.5165,0.0000) (10.7000,0.5165,0.0000) (10.7000,0.5410,0.0000) (9.7950,0.5410,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.7950,0.5410,0.0350) (10.7000,0.5410,0.0350) (10.7000,0.5485,0.0350) (9.7950,0.5485,0.0350)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.7950,0.5485,0.0000) (10.7000,0.5485,0.0000) (10.7000,0.5775,0.0000) (9.7950,0.5775,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.7950,0.5775,0.0000) (10.7000,0.5775,0.0000) (10.7000,0.6010,0.0000) (9.7950,0.6010,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.7950,0.6010,0.0000) (10.7000,0.6010,0.0000) (10.7000,0.6070,0.0000) (9.7950,0.6070,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.7950,0.6070,0.0000) (10.7000,0.6070,0.0000) (10.7000,0.6115,0.0000) (9.7950,0.6115,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.7950,0.6115,0.0000) (10.7000,0.6115,0.0000) (10.7000,0.6190,0.0000) (9.7950,0.6190,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.7950,0.6190,0.0000) (10.7000,0.6190,0.0000) (10.7000,0.6275,0.0000) (9.7950,0.6275,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.7950,0.6275,0.0000) (10.7000,0.6275,0.0000) (10.7000,0.6390,0.0000) (9.7950,0.6390,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.7950,0.6390,0.0000) (10.7000,0.6390,0.0000) (10.7000,0.6510,0.0000) (9.7950,0.6510,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.7950,0.6510,0.0000) (10.7000,0.6510,0.0000) (10.7000,0.8205,0.0000) (9.7950,0.8205,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.7950,0.8205,0.0000) (10.7000,0.8205,0.0000) (10.7000,0.8710,0.0000) (9.7950,0.8710,0.0000)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.7000,0.3850,0.0295) (16.5700,0.3850,0.0295) (16.5700,0.4460,0.0295) (10.7000,0.4460,0.0295)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.7000,0.4460,0.0000) (16.5700,0.4460,0.0000) (16.5700,0.4485,0.0000) (10.7000,0.4485,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.7000,0.4485,0.0000) (16.5700,0.4485,0.0000) (16.5700,0.4555,0.0000) (10.7000,0.4555,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.7000,0.4555,0.0000) (16.5700,0.4555,0.0000) (16.5700,0.4620,0.0000) (10.7000,0.4620,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.7000,0.4620,0.0060) (16.5700,0.4620,0.0060) (16.5700,0.4705,0.0060) (10.7000,0.4705,0.0060)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.7000,0.4705,0.0000) (16.5700,0.4705,0.0000) (16.5700,0.4910,0.0000) (10.7000,0.4910,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.7000,0.4910,0.0000) (16.5700,0.4910,0.0000) (16.5700,0.4960,0.0000) (10.7000,0.4960,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.7000,0.4960,0.0000) (16.5700,0.4960,0.0000) (16.5700,0.5015,0.0000) (10.7000,0.5015,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.7000,0.5015,0.0000) (16.5700,0.5015,0.0000) (16.5700,0.5085,0.0000) (10.7000,0.5085,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.7000,0.5085,0.0000) (16.5700,0.5085,0.0000) (16.5700,0.5165,0.0000) (10.7000,0.5165,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.7000,0.5165,0.0000) (16.5700,0.5165,0.0000) (16.5700,0.5410,0.0000) (10.7000,0.5410,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.7000,0.5410,0.0000) (16.5700,0.5410,0.0000) (16.5700,0.5485,0.0000) (10.7000,0.5485,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.7000,0.5485,0.0190) (16.5700,0.5485,0.0190) (16.5700,0.5775,0.0190) (10.7000,0.5775,0.0190)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.7000,0.5775,0.0000) (16.5700,0.5775,0.0000) (16.5700,0.6010,0.0000) (10.7000,0.6010,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.7000,0.6010,0.0000) (16.5700,0.6010,0.0000) (16.5700,0.6070,0.0000) (10.7000,0.6070,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.7000,0.6070,0.0000) (16.5700,0.6070,0.0000) (16.5700,0.6115,0.0000) (10.7000,0.6115,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.7000,0.6115,0.0000) (16.5700,0.6115,0.0000) (16.5700,0.6190,0.0000) (10.7000,0.6190,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.7000,0.6190,0.0000) (16.5700,0.6190,0.0000) (16.5700,0.6275,0.0000) (10.7000,0.6275,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.7000,0.6275,0.0000) (16.5700,0.6275,0.0000) (16.5700,0.6390,0.0000) (10.7000,0.6390,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.7000,0.6390,0.0000) (16.5700,0.6390,0.0000) (16.5700,0.6510,0.0000) (10.7000,0.6510,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.7000,0.6510,0.0000) (16.5700,0.6510,0.0000) (16.5700,0.8205,0.0000) (10.7000,0.8205,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.7000,0.8205,0.0000) (16.5700,0.8205,0.0000) (16.5700,0.8710,0.0000) (10.7000,0.8710,0.0000)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.3850,0.0000) (18.8400,0.3850,0.0000) (18.8400,0.4460,0.0000) (16.5700,0.4460,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.4460,0.0000) (18.8400,0.4460,0.0000) (18.8400,0.4485,0.0000) (16.5700,0.4485,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.4485,0.0000) (18.8400,0.4485,0.0000) (18.8400,0.4555,0.0000) (16.5700,0.4555,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.4555,0.0000) (18.8400,0.4555,0.0000) (18.8400,0.4620,0.0000) (16.5700,0.4620,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.4620,0.0000) (18.8400,0.4620,0.0000) (18.8400,0.4705,0.0000) (16.5700,0.4705,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.4705,0.0000) (18.8400,0.4705,0.0000) (18.8400,0.4910,0.0000) (16.5700,0.4910,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.4910,0.0000) (18.8400,0.4910,0.0000) (18.8400,0.4960,0.0000) (16.5700,0.4960,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.4960,0.0000) (18.8400,0.4960,0.0000) (18.8400,0.5015,0.0000) (16.5700,0.5015,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.5015,0.0000) (18.8400,0.5015,0.0000) (18.8400,0.5085,0.0000) (16.5700,0.5085,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.5085,0.0000) (18.8400,0.5085,0.0000) (18.8400,0.5165,0.0000) (16.5700,0.5165,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.5165,0.0135) (18.8400,0.5165,0.0135) (18.8400,0.5410,0.0135) (16.5700,0.5410,0.0135)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.5410,0.0000) (18.8400,0.5410,0.0000) (18.8400,0.5485,0.0000) (16.5700,0.5485,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.5485,0.0000) (18.8400,0.5485,0.0000) (18.8400,0.5775,0.0000) (16.5700,0.5775,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.5775,0.0445) (18.8400,0.5775,0.0445) (18.8400,0.6010,0.0445) (16.5700,0.6010,0.0445)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.6010,0.0000) (18.8400,0.6010,0.0000) (18.8400,0.6070,0.0000) (16.5700,0.6070,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.6070,0.0000) (18.8400,0.6070,0.0000) (18.8400,0.6115,0.0000) (16.5700,0.6115,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.6115,0.0120) (18.8400,0.6115,0.0120) (18.8400,0.6190,0.0120) (16.5700,0.6190,0.0120)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.6190,0.0000) (18.8400,0.6190,0.0000) (18.8400,0.6275,0.0000) (16.5700,0.6275,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.6275,0.0080) (18.8400,0.6275,0.0080) (18.8400,0.6390,0.0080) (16.5700,0.6390,0.0080)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.6390,0.0000) (18.8400,0.6390,0.0000) (18.8400,0.6510,0.0000) (16.5700,0.6510,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.6510,0.1855) (18.8400,0.6510,0.1855) (18.8400,0.8205,0.1855) (16.5700,0.8205,0.1855)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.8205,0.0000) (18.8400,0.8205,0.0000) (18.8400,0.8710,0.0000) (16.5700,0.8710,0.0000)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.3850,0.0000) (20.7350,0.3850,0.0000) (20.7350,0.4460,0.0000) (18.8400,0.4460,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.4460,0.0000) (20.7350,0.4460,0.0000) (20.7350,0.4485,0.0000) (18.8400,0.4485,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.4485,0.0000) (20.7350,0.4485,0.0000) (20.7350,0.4555,0.0000) (18.8400,0.4555,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.4555,0.0000) (20.7350,0.4555,0.0000) (20.7350,0.4620,0.0000) (18.8400,0.4620,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.4620,0.0000) (20.7350,0.4620,0.0000) (20.7350,0.4705,0.0000) (18.8400,0.4705,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.4705,0.0000) (20.7350,0.4705,0.0000) (20.7350,0.4910,0.0000) (18.8400,0.4910,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.4910,0.0000) (20.7350,0.4910,0.0000) (20.7350,0.4960,0.0000) (18.8400,0.4960,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.4960,0.0000) (20.7350,0.4960,0.0000) (20.7350,0.5015,0.0000) (18.8400,0.5015,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.5015,0.0000) (20.7350,0.5015,0.0000) (20.7350,0.5085,0.0000) (18.8400,0.5085,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.5085,0.0000) (20.7350,0.5085,0.0000) (20.7350,0.5165,0.0000) (18.8400,0.5165,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.5165,0.0000) (20.7350,0.5165,0.0000) (20.7350,0.5410,0.0000) (18.8400,0.5410,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.5410,0.0000) (20.7350,0.5410,0.0000) (20.7350,0.5485,0.0000) (18.8400,0.5485,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.5485,0.0000) (20.7350,0.5485,0.0000) (20.7350,0.5775,0.0000) (18.8400,0.5775,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.5775,0.0000) (20.7350,0.5775,0.0000) (20.7350,0.6010,0.0000) (18.8400,0.6010,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.6010,0.0260) (20.7350,0.6010,0.0260) (20.7350,0.6070,0.0260) (18.8400,0.6070,0.0260)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.6070,0.0000) (20.7350,0.6070,0.0000) (20.7350,0.6115,0.0000) (18.8400,0.6115,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.6115,0.0000) (20.7350,0.6115,0.0000) (20.7350,0.6190,0.0000) (18.8400,0.6190,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.6190,0.0000) (20.7350,0.6190,0.0000) (20.7350,0.6275,0.0000) (18.8400,0.6275,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.6275,0.0000) (20.7350,0.6275,0.0000) (20.7350,0.6390,0.0000) (18.8400,0.6390,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.6390,0.0000) (20.7350,0.6390,0.0000) (20.7350,0.6510,0.0000) (18.8400,0.6510,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.6510,0.0000) (20.7350,0.6510,0.0000) (20.7350,0.8205,0.0000) (18.8400,0.8205,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.8205,0.0370) (20.7350,0.8205,0.0370) (20.7350,0.8710,0.0370) (18.8400,0.8710,0.0370)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.3850,0.0000) (23.7700,0.3850,0.0000) (23.7700,0.4460,0.0000) (20.7350,0.4460,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.4460,0.0000) (23.7700,0.4460,0.0000) (23.7700,0.4485,0.0000) (20.7350,0.4485,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.4485,0.0000) (23.7700,0.4485,0.0000) (23.7700,0.4555,0.0000) (20.7350,0.4555,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.4555,0.0000) (23.7700,0.4555,0.0000) (23.7700,0.4620,0.0000) (20.7350,0.4620,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.4620,0.0000) (23.7700,0.4620,0.0000) (23.7700,0.4705,0.0000) (20.7350,0.4705,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.4705,0.0000) (23.7700,0.4705,0.0000) (23.7700,0.4910,0.0000) (20.7350,0.4910,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.4910,0.0000) (23.7700,0.4910,0.0000) (23.7700,0.4960,0.0000) (20.7350,0.4960,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.4960,0.0000) (23.7700,0.4960,0.0000) (23.7700,0.5015,0.0000) (20.7350,0.5015,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.5015,0.0000) (23.7700,0.5015,0.0000) (23.7700,0.5085,0.0000) (20.7350,0.5085,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.5085,0.0000) (23.7700,0.5085,0.0000) (23.7700,0.5165,0.0000) (20.7350,0.5165,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.5165,0.0000) (23.7700,0.5165,0.0000) (23.7700,0.5410,0.0000) (20.7350,0.5410,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.5410,0.0000) (23.7700,0.5410,0.0000) (23.7700,0.5485,0.0000) (20.7350,0.5485,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.5485,0.0000) (23.7700,0.5485,0.0000) (23.7700,0.5775,0.0000) (20.7350,0.5775,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.5775,0.0000) (23.7700,0.5775,0.0000) (23.7700,0.6010,0.0000) (20.7350,0.6010,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.6010,0.0000) (23.7700,0.6010,0.0000) (23.7700,0.6070,0.0000) (20.7350,0.6070,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.6070,0.0000) (23.7700,0.6070,0.0000) (23.7700,0.6115,0.0000) (20.7350,0.6115,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.6115,0.0000) (23.7700,0.6115,0.0000) (23.7700,0.6190,0.0000) (20.7350,0.6190,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.6190,0.0325) (23.7700,0.6190,0.0325) (23.7700,0.6275,0.0325) (20.7350,0.6275,0.0325)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.6275,0.0000) (23.7700,0.6275,0.0000) (23.7700,0.6390,0.0000) (20.7350,0.6390,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.6390,0.0000) (23.7700,0.6390,0.0000) (23.7700,0.6510,0.0000) (20.7350,0.6510,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.6510,0.0000) (23.7700,0.6510,0.0000) (23.7700,0.8205,0.0000) (20.7350,0.8205,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.8205,0.0000) (23.7700,0.8205,0.0000) (23.7700,0.8710,0.0000) (20.7350,0.8710,0.0000)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.7700,0.3850,0.0000) (27.7400,0.3850,0.0000) (27.7400,0.4460,0.0000) (23.7700,0.4460,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.7700,0.4460,0.0000) (27.7400,0.4460,0.0000) (27.7400,0.4485,0.0000) (23.7700,0.4485,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.7700,0.4485,0.0000) (27.7400,0.4485,0.0000) (27.7400,0.4555,0.0000) (23.7700,0.4555,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.7700,0.4555,0.0000) (27.7400,0.4555,0.0000) (27.7400,0.4620,0.0000) (23.7700,0.4620,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.7700,0.4620,0.0000) (27.7400,0.4620,0.0000) (27.7400,0.4705,0.0000) (23.7700,0.4705,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.7700,0.4705,0.0000) (27.7400,0.4705,0.0000) (27.7400,0.4910,0.0000) (23.7700,0.4910,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.7700,0.4910,0.0000) (27.7400,0.4910,0.0000) (27.7400,0.4960,0.0000) (23.7700,0.4960,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.7700,0.4960,0.0000) (27.7400,0.4960,0.0000) (27.7400,0.5015,0.0000) (23.7700,0.5015,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.7700,0.5015,0.0000) (27.7400,0.5015,0.0000) (27.7400,0.5085,0.0000) (23.7700,0.5085,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.7700,0.5085,0.0000) (27.7400,0.5085,0.0000) (27.7400,0.5165,0.0000) (23.7700,0.5165,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.7700,0.5165,0.0000) (27.7400,0.5165,0.0000) (27.7400,0.5410,0.0000) (23.7700,0.5410,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.7700,0.5410,0.0000) (27.7400,0.5410,0.0000) (27.7400,0.5485,0.0000) (23.7700,0.5485,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.7700,0.5485,0.0000) (27.7400,0.5485,0.0000) (27.7400,0.5775,0.0000) (23.7700,0.5775,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.7700,0.5775,0.0105) (27.7400,0.5775,0.0105) (27.7400,0.6010,0.0105) (23.7700,0.6010,0.0105)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.7700,0.6010,0.0000) (27.7400,0.6010,0.0000) (27.7400,0.6070,0.0000) (23.7700,0.6070,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.7700,0.6070,0.0085) (27.7400,0.6070,0.0085) (27.7400,0.6115,0.0085) (23.7700,0.6115,0.0085)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.7700,0.6115,0.0000) (27.7400,0.6115,0.0000) (27.7400,0.6190,0.0000) (23.7700,0.6190,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.7700,0.6190,0.0000) (27.7400,0.6190,0.0000) (27.7400,0.6275,0.0000) (23.7700,0.6275,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.7700,0.6275,0.0000) (27.7400,0.6275,0.0000) (27.7400,0.6390,0.0000) (23.7700,0.6390,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.7700,0.6390,0.0000) (27.7400,0.6390,0.0000) (27.7400,0.6510,0.0000) (23.7700,0.6510,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.7700,0.6510,0.0000) (27.7400,0.6510,0.0000) (27.7400,0.8205,0.0000) (23.7700,0.8205,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.7700,0.8205,0.0000) (27.7400,0.8205,0.0000) (27.7400,0.8710,0.0000) (23.7700,0.8710,0.0000)};

			\addplot3[mark=+, draw=none, mark size=0.7, jitter = 0.3] coordinates {
(2.310,0.538,1) (7.070,0.469,1) (7.070,0.469,1) (2.180,0.458,1) (2.180,0.458,1) (2.180,0.458,1) (7.870,0.524,1) (7.870,0.524,1) (7.870,0.524,1) (7.870,0.524,1) (7.870,0.524,1) (7.870,0.524,1) (7.870,0.524,1) (8.140,0.538,1) (8.140,0.538,1) (8.140,0.538,1) (8.140,0.538,1) (8.140,0.538,1) (8.140,0.538,1) (8.140,0.538,1) (8.140,0.538,1) (8.140,0.538,1) (8.140,0.538,1) (8.140,0.538,1) (8.140,0.538,1) (8.140,0.538,1) (8.140,0.538,1) (8.140,0.538,1) (8.140,0.538,1) (8.140,0.538,1) (8.140,0.538,1) (8.140,0.538,1) (8.140,0.538,1) (8.140,0.538,1) (8.140,0.538,1) (5.960,0.499,1) (5.960,0.499,1) (5.960,0.499,1) (5.960,0.499,1) (2.950,0.428,1) (2.950,0.428,1) (6.910,0.448,1) (6.910,0.448,1) (6.910,0.448,1) (6.910,0.448,1) (6.910,0.448,1) (6.910,0.448,1) (6.910,0.448,1) (6.910,0.448,1) (6.910,0.448,1) (5.640,0.439,1) (5.640,0.439,1) (5.640,0.439,1) (5.640,0.439,1) (4.000,0.410,1) (1.220,0.403,1) (0.740,0.410,1) (1.320,0.411,1) (5.130,0.453,1) (5.130,0.453,1) (5.130,0.453,1) (5.130,0.453,1) (5.130,0.453,1) (5.130,0.453,1) (1.380,0.416,1) (3.370,0.398,1) (3.370,0.398,1) (6.070,0.409,1) (6.070,0.409,1) (6.070,0.409,1) (10.810,0.413,1) (10.810,0.413,1) (10.810,0.413,1) (10.810,0.413,1) (12.830,0.437,1) (12.830,0.437,1) (12.830,0.437,1) (12.830,0.437,1) (12.830,0.437,1) (12.830,0.437,1) (4.860,0.426,1) (4.860,0.426,1) (4.860,0.426,1) (4.860,0.426,1) (4.490,0.449,1) (4.490,0.449,1) (4.490,0.449,1) (4.490,0.449,1) (3.410,0.489,1) (3.410,0.489,1) (3.410,0.489,1) (3.410,0.489,1) (15.040,0.464,1) (15.040,0.464,1) (15.040,0.464,1) (2.890,0.445,1) (2.890,0.445,1) (2.890,0.445,1) (2.890,0.445,1) (2.890,0.445,1) (8.560,0.520,1) (8.560,0.520,1) (8.560,0.520,1) (8.560,0.520,1) (8.560,0.520,1) (8.560,0.520,1) (8.560,0.520,1) (8.560,0.520,1) (8.560,0.520,1) (8.560,0.520,1) (8.560,0.520,1) (10.010,0.547,1) (10.010,0.547,1) (10.010,0.547,1) (10.010,0.547,1) (10.010,0.547,1) (10.010,0.547,1) (10.010,0.547,1) (10.010,0.547,1) (10.010,0.547,1) (25.650,0.581,1) (25.650,0.581,1) (25.650,0.581,1) (25.650,0.581,1) (25.650,0.581,1) (25.650,0.581,1) (25.650,0.581,1) (21.890,0.624,1) (21.890,0.624,1) (21.890,0.624,1) (21.890,0.624,1) (21.890,0.624,1) (21.890,0.624,1) (21.890,0.624,1) (21.890,0.624,1) (21.890,0.624,1) (21.890,0.624,1) (21.890,0.624,1) (21.890,0.624,1) (21.890,0.624,1) (21.890,0.624,1) (21.890,0.624,1) (19.580,0.871,1) (19.580,0.871,1) (19.580,0.871,1) (19.580,0.871,1) (19.580,0.871,1) (19.580,0.871,1) (19.580,0.871,1) (19.580,0.871,1) (19.580,0.871,1) (19.580,0.871,1) (19.580,0.871,1) (19.580,0.871,1) (19.580,0.871,1) (19.580,0.871,1) (19.580,0.871,1) (19.580,0.605,1) (19.580,0.605,1) (19.580,0.871,1) (19.580,0.605,1) (19.580,0.605,1) (19.580,0.605,1) (19.580,0.605,1) (19.580,0.605,1) (19.580,0.605,1) (19.580,0.605,1) (19.580,0.605,1) (19.580,0.605,1) (19.580,0.605,1) (19.580,0.605,1) (19.580,0.605,1) (4.050,0.510,1) (4.050,0.510,1) (4.050,0.510,1) (4.050,0.510,1) (4.050,0.510,1) (4.050,0.510,1) (4.050,0.510,1) (2.460,0.488,1) (2.460,0.488,1) (2.460,0.488,1) (2.460,0.488,1) (2.460,0.488,1) (2.460,0.488,1) (2.460,0.488,1) (2.460,0.488,1) (3.440,0.437,1) (3.440,0.437,1) (3.440,0.437,1) (3.440,0.437,1) (3.440,0.437,1) (3.440,0.437,1) (2.930,0.401,1) (2.930,0.401,1) (0.460,0.422,1) (1.520,0.404,1) (1.520,0.404,1) (1.520,0.404,1) (1.470,0.403,1) (1.470,0.403,1) (2.030,0.415,1) (2.030,0.415,1) (2.680,0.416,1) (2.680,0.416,1) (10.590,0.489,1) (10.590,0.489,1) (10.590,0.489,1) (10.590,0.489,1) (10.590,0.489,1) (10.590,0.489,1) (10.590,0.489,1) (10.590,0.489,1) (10.590,0.489,1) (10.590,0.489,1) (10.590,0.489,1) (13.890,0.550,1) (13.890,0.550,1) (13.890,0.550,1) (13.890,0.550,1) (6.200,0.507,1) (6.200,0.507,1) (6.200,0.507,1) (6.200,0.507,1) (6.200,0.504,1) (6.200,0.504,1) (6.200,0.504,1) (6.200,0.504,1) (6.200,0.504,1) (6.200,0.504,1) (6.200,0.504,1) (6.200,0.504,1) (6.200,0.507,1) (6.200,0.507,1) (6.200,0.507,1) (6.200,0.507,1) (6.200,0.507,1) (6.200,0.507,1) (4.930,0.428,1) (4.930,0.428,1) (4.930,0.428,1) (4.930,0.428,1) (4.930,0.428,1) (4.930,0.428,1) (5.860,0.431,1) (5.860,0.431,1) (5.860,0.431,1) (5.860,0.431,1) (5.860,0.431,1) (5.860,0.431,1) (5.860,0.431,1) (5.860,0.431,1) (5.860,0.431,1) (5.860,0.431,1) (3.640,0.392,1) (3.640,0.392,1) (3.750,0.394,1) (3.970,0.647,1) (3.970,0.647,1) (3.970,0.647,1) (3.970,0.647,1) (3.970,0.647,1) (3.970,0.647,1) (3.970,0.647,1) (3.970,0.647,1) (3.970,0.647,1) (3.970,0.647,1) (3.970,0.575,1) (3.970,0.575,1) (6.960,0.464,1) (6.960,0.464,1) (6.960,0.464,1) (6.960,0.464,1) (6.960,0.464,1) (6.410,0.447,1) (6.410,0.447,1) (6.410,0.447,1) (6.410,0.447,1) (6.410,0.447,1) (3.330,0.443,1) (3.330,0.443,1) (3.330,0.443,1) (3.330,0.443,1) (1.210,0.401,1) (2.970,0.400,1) (2.250,0.389,1) (1.760,0.385,1) (5.320,0.405,1) (5.320,0.405,1) (5.320,0.405,1) (4.950,0.411,1) (4.950,0.411,1) (4.950,0.411,1) (13.920,0.437,1) (13.920,0.437,1) (13.920,0.437,1) (13.920,0.437,1) (13.920,0.437,1) (2.240,0.400,1) (2.240,0.400,1) (2.240,0.400,1) (6.090,0.433,1) (6.090,0.433,1) (6.090,0.433,1) (2.180,0.472,1) (2.180,0.472,1) (2.180,0.472,1) (2.180,0.472,1) (9.900,0.544,1) (9.900,0.544,1) (9.900,0.544,1) (9.900,0.544,1) (9.900,0.544,1) (9.900,0.544,1) (9.900,0.544,1) (9.900,0.544,1) (9.900,0.544,1) (9.900,0.544,1) (9.900,0.544,1) (9.900,0.544,1) (7.380,0.493,1) (7.380,0.493,1) (7.380,0.493,1) (7.380,0.493,1) (7.380,0.493,1) (7.380,0.493,1) (7.380,0.493,1) (7.380,0.493,1) (3.240,0.460,1) (3.240,0.460,1) (3.240,0.460,1) (6.060,0.438,1) (6.060,0.438,1) (5.190,0.515,1) (5.190,0.515,1) (5.190,0.515,1) (5.190,0.515,1) (5.190,0.515,1) (5.190,0.515,1) (5.190,0.515,1) (5.190,0.515,1) (1.520,0.442,1) (1.890,0.518,1) (3.780,0.484,1) (3.780,0.484,1) (4.390,0.442,1) (4.390,0.442,1) (4.150,0.429,1) (2.010,0.435,1) (1.250,0.429,1) (1.250,0.429,1) (1.690,0.411,1) (1.690,0.411,1) (2.020,0.410,1) (1.910,0.413,1) (1.910,0.413,1) (18.100,0.770,1) (18.100,0.770,1) (18.100,0.770,1) (18.100,0.770,1) (18.100,0.770,1) (18.100,0.770,1) (18.100,0.770,1) (18.100,0.770,1) (18.100,0.718,1) (18.100,0.718,1) (18.100,0.718,1) (18.100,0.631,1) (18.100,0.631,1) (18.100,0.631,1) (18.100,0.631,1) (18.100,0.631,1) (18.100,0.668,1) (18.100,0.668,1) (18.100,0.668,1) (18.100,0.671,1) (18.100,0.671,1) (18.100,0.671,1) (18.100,0.671,1) (18.100,0.671,1) (18.100,0.671,1) (18.100,0.671,1) (18.100,0.700,1) (18.100,0.700,1) (18.100,0.700,1) (18.100,0.700,1) (18.100,0.700,1) (18.100,0.700,1) (18.100,0.700,1) (18.100,0.700,1) (18.100,0.700,1) (18.100,0.700,1) (18.100,0.700,1) (18.100,0.693,1) (18.100,0.693,1) (18.100,0.693,1) (18.100,0.693,1) (18.100,0.693,1) (18.100,0.693,1) (18.100,0.693,1) (18.100,0.693,1) (18.100,0.693,1) (18.100,0.693,1) (18.100,0.693,1) (18.100,0.693,1) (18.100,0.693,1) (18.100,0.659,1) (18.100,0.659,1) (18.100,0.597,1) (18.100,0.597,1) (18.100,0.597,1) (18.100,0.597,1) (18.100,0.597,1) (18.100,0.597,1) (18.100,0.693,1) (18.100,0.679,1) (18.100,0.679,1) (18.100,0.679,1) (18.100,0.679,1) (18.100,0.718,1) (18.100,0.718,1) (18.100,0.718,1) (18.100,0.614,1) (18.100,0.614,1) (18.100,0.584,1) (18.100,0.679,1) (18.100,0.584,1) (18.100,0.679,1) (18.100,0.679,1) (18.100,0.679,1) (18.100,0.584,1) (18.100,0.584,1) (18.100,0.584,1) (18.100,0.713,1) (18.100,0.713,1) (18.100,0.740,1) (18.100,0.740,1) (18.100,0.740,1) (18.100,0.740,1) (18.100,0.740,1) (18.100,0.740,1) (18.100,0.740,1) (18.100,0.740,1) (18.100,0.740,1) (18.100,0.740,1) (18.100,0.740,1) (18.100,0.740,1) (18.100,0.740,1) (18.100,0.713,1) (18.100,0.713,1) (18.100,0.713,1) (18.100,0.713,1) (18.100,0.713,1) (18.100,0.713,1) (18.100,0.713,1) (18.100,0.713,1) (18.100,0.713,1) (18.100,0.713,1) (18.100,0.713,1) (18.100,0.713,1) (18.100,0.713,1) (18.100,0.713,1) (18.100,0.713,1) (18.100,0.713,1) (18.100,0.655,1) (18.100,0.655,1) (18.100,0.655,1) (18.100,0.584,1) (18.100,0.580,1) (18.100,0.580,1) (18.100,0.580,1) (18.100,0.532,1) (18.100,0.580,1) (18.100,0.614,1) (18.100,0.584,1) (18.100,0.584,1) (18.100,0.614,1) (18.100,0.614,1) (18.100,0.614,1) (18.100,0.614,1) (18.100,0.532,1) (18.100,0.532,1) (18.100,0.532,1) (18.100,0.532,1) (18.100,0.583,1) (18.100,0.583,1) (18.100,0.583,1) (18.100,0.583,1) (27.740,0.609,1) (27.740,0.609,1) (27.740,0.609,1) (27.740,0.609,1) (27.740,0.609,1) (9.690,0.585,1) (9.690,0.585,1) (9.690,0.585,1) (9.690,0.585,1) (9.690,0.585,1) (9.690,0.585,1) (9.690,0.585,1) (9.690,0.585,1) (11.930,0.573,1) (11.930,0.573,1) (11.930,0.573,1) (11.930,0.573,1) (11.930,0.573,1) };
		\end{axis}
\end{tikzpicture}

### 2015-11-17 graph_housing_exp2_distr_8_5.tex
Experiment part

--- 2015-11-17 graph_housing_exp1_distr_8_5.tex
@@
 
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.3850,0.0000) (1.9204,0.3850,0.0000) (1.9204,0.4405,0.0000) (1.1296,0.4405,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.4405,0.0000) (1.9204,0.4405,0.0000) (1.9204,0.4860,0.0000) (1.1296,0.4860,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.4860,0.0000) (1.9204,0.4860,0.0000) (1.9204,0.4910,0.0000) (1.1296,0.4910,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.4910,0.0000) (1.9204,0.4910,0.0000) (1.9204,0.4960,0.0000) (1.1296,0.4960,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.4960,0.0000) (1.9204,0.4960,0.0000) (1.9204,0.5190,0.0000) (1.1296,0.5190,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.5190,0.0000) (1.9204,0.5190,0.0000) (1.9204,0.5220,0.0000) (1.1296,0.5220,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.5220,0.0000) (1.9204,0.5220,0.0000) (1.9204,0.5280,0.0000) (1.1296,0.5280,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.5280,0.0000) (1.9204,0.5280,0.0000) (1.9204,0.5410,0.0000) (1.1296,0.5410,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.5410,0.0000) (1.9204,0.5410,0.0000) (1.9204,0.5455,0.0000) (1.1296,0.5455,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.5455,0.0025) (1.9204,0.5455,0.0025) (1.9204,0.5910,0.0025) (1.1296,0.5910,0.0025)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.5910,0.0425) (1.9204,0.5910,0.0425) (1.9204,0.6390,0.0425) (1.1296,0.6390,0.0425)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.6390,0.0065) (1.9204,0.6390,0.0065) (1.9204,0.6510,0.0065) (1.1296,0.6510,0.0065)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.6510,0.1040) (1.9204,0.6510,0.1040) (1.9204,0.8205,0.1040) (1.1296,0.8205,0.1040)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.8205,0.0300) (1.9204,0.8205,0.0300) (1.9204,0.8710,0.0300) (1.1296,0.8710,0.0300)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.3850,0.0060) (2.5884,0.3850,0.0060) (2.5884,0.4460,0.0060) (1.1296,0.4460,0.0060)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.4460,0.0000) (2.5884,0.4460,0.0000) (2.5884,0.4485,0.0000) (1.1296,0.4485,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.4485,0.0000) (2.5884,0.4485,0.0000) (2.5884,0.4555,0.0000) (1.1296,0.4555,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.4555,0.0000) (2.5884,0.4555,0.0000) (2.5884,0.4620,0.0000) (1.1296,0.4620,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.4620,0.0025) (2.5884,0.4620,0.0025) (2.5884,0.4705,0.0025) (1.1296,0.4705,0.0025)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.4705,0.0040) (2.5884,0.4705,0.0040) (2.5884,0.4910,0.0040) (1.1296,0.4910,0.0040)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.4910,0.0000) (2.5884,0.4910,0.0000) (2.5884,0.4960,0.0000) (1.1296,0.4960,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.4960,0.0000) (2.5884,0.4960,0.0000) (2.5884,0.5015,0.0000) (1.1296,0.5015,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.5015,0.0000) (2.5884,0.5015,0.0000) (2.5884,0.5085,0.0000) (1.1296,0.5085,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.5085,0.0000) (2.5884,0.5085,0.0000) (2.5884,0.5165,0.0000) (1.1296,0.5165,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.5165,0.0215) (2.5884,0.5165,0.0215) (2.5884,0.5410,0.0215) (1.1296,0.5410,0.0215)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.5410,0.0055) (2.5884,0.5410,0.0055) (2.5884,0.5485,0.0055) (1.1296,0.5485,0.0055)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.5485,0.0070) (2.5884,0.5485,0.0070) (2.5884,0.5775,0.0070) (1.1296,0.5775,0.0070)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.5775,0.0645) (2.5884,0.5775,0.0645) (2.5884,0.6010,0.0645) (1.1296,0.6010,0.0645)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.6010,0.0260) (2.5884,0.6010,0.0260) (2.5884,0.6070,0.0260) (1.1296,0.6070,0.0260)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.6070,0.0085) (2.5884,0.6070,0.0085) (2.5884,0.6115,0.0085) (1.1296,0.6115,0.0085)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.6115,0.0100) (2.5884,0.6115,0.0100) (2.5884,0.6190,0.0100) (1.1296,0.6190,0.0100)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.6190,0.0325) (2.5884,0.6190,0.0325) (2.5884,0.6275,0.0325) (1.1296,0.6275,0.0325)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.6275,0.0060) (2.5884,0.6275,0.0060) (2.5884,0.6390,0.0060) (1.1296,0.6390,0.0060)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.6390,0.0210) (2.5884,0.6390,0.0210) (2.5884,0.6510,0.0210) (1.1296,0.6510,0.0210)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.6510,0.1560) (2.5884,0.6510,0.1560) (2.5884,0.8205,0.1560) (1.1296,0.8205,0.1560)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.8205,0.0370) (2.5884,0.8205,0.0370) (2.5884,0.8710,0.0370) (1.1296,0.8710,0.0370)};
 
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.3850,0.0000) (2.5884,0.3850,0.0000) (2.5884,0.4405,0.0000) (1.9204,0.4405,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.4405,0.0000) (2.5884,0.4405,0.0000) (2.5884,0.4860,0.0000) (1.9204,0.4860,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.4860,0.0000) (2.5884,0.4860,0.0000) (2.5884,0.4910,0.0000) (1.9204,0.4910,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.4910,0.0000) (2.5884,0.4910,0.0000) (2.5884,0.4960,0.0000) (1.9204,0.4960,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.4960,0.0000) (2.5884,0.4960,0.0000) (2.5884,0.5190,0.0000) (1.9204,0.5190,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.5190,0.0085) (2.5884,0.5190,0.0085) (2.5884,0.5220,0.0085) (1.9204,0.5220,0.0085)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.5220,0.0000) (2.5884,0.5220,0.0000) (2.5884,0.5280,0.0000) (1.9204,0.5280,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.5280,0.0000) (2.5884,0.5280,0.0000) (2.5884,0.5410,0.0000) (1.9204,0.5410,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.5410,0.0025) (2.5884,0.5410,0.0025) (2.5884,0.5455,0.0025) (1.9204,0.5455,0.0025)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.5455,0.0580) (2.5884,0.5455,0.0580) (2.5884,0.5910,0.0580) (1.9204,0.5910,0.0580)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.5910,0.0485) (2.5884,0.5910,0.0485) (2.5884,0.6390,0.0485) (1.9204,0.6390,0.0485)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.6390,0.0120) (2.5884,0.6390,0.0120) (2.5884,0.6510,0.0120) (1.9204,0.6510,0.0120)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.6510,0.0665) (2.5884,0.6510,0.0665) (2.5884,0.8205,0.0665) (1.9204,0.8205,0.0665)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.8205,0.0000) (2.5884,0.8205,0.0000) (2.5884,0.8710,0.0000) (1.9204,0.8710,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.3850,0.0775) (4.9150,0.3850,0.0775) (4.9150,0.4460,0.0775) (2.5884,0.4460,0.0775)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.4460,0.0150) (4.9150,0.4460,0.0150) (4.9150,0.4485,0.0150) (2.5884,0.4485,0.0150)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.4485,0.0050) (4.9150,0.4485,0.0050) (4.9150,0.4555,0.0050) (2.5884,0.4555,0.0050)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.4555,0.0040) (4.9150,0.4555,0.0040) (4.9150,0.4620,0.0040) (2.5884,0.4620,0.0040)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.4620,0.0080) (4.9150,0.4620,0.0080) (4.9150,0.4705,0.0080) (2.5884,0.4705,0.0080)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.4705,0.0290) (4.9150,0.4705,0.0290) (4.9150,0.4910,0.0290) (2.5884,0.4910,0.0290)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.4910,0.0095) (4.9150,0.4910,0.0095) (4.9150,0.4960,0.0095) (2.5884,0.4960,0.0095)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.4960,0.0025) (4.9150,0.4960,0.0025) (4.9150,0.5015,0.0025) (2.5884,0.5015,0.0025)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.5015,0.0410) (4.9150,0.5015,0.0410) (4.9150,0.5085,0.0410) (2.5884,0.5085,0.0410)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.5085,0.0100) (4.9150,0.5085,0.0100) (4.9150,0.5165,0.0100) (2.5884,0.5165,0.0100)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.5165,0.0605) (4.9150,0.5165,0.0605) (4.9150,0.5410,0.0605) (2.5884,0.5410,0.0605)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.5410,0.0295) (4.9150,0.5410,0.0295) (4.9150,0.5485,0.0295) (2.5884,0.5485,0.0295)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.5485,0.0095) (4.9150,0.5485,0.0095) (4.9150,0.5775,0.0095) (2.5884,0.5775,0.0095)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.5775,0.0105) (4.9150,0.5775,0.0105) (4.9150,0.6010,0.0105) (2.5884,0.6010,0.0105)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.6010,0.0000) (4.9150,0.6010,0.0000) (4.9150,0.6070,0.0000) (2.5884,0.6070,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.6070,0.0000) (4.9150,0.6070,0.0000) (4.9150,0.6115,0.0000) (2.5884,0.6115,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.6115,0.0020) (4.9150,0.6115,0.0020) (4.9150,0.6190,0.0020) (2.5884,0.6190,0.0020)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.6190,0.0000) (4.9150,0.6190,0.0000) (4.9150,0.6275,0.0000) (2.5884,0.6275,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.6275,0.0020) (4.9150,0.6275,0.0020) (4.9150,0.6390,0.0020) (2.5884,0.6390,0.0020)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.6390,0.0015) (4.9150,0.6390,0.0015) (4.9150,0.6510,0.0015) (2.5884,0.6510,0.0015)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.6510,0.0295) (4.9150,0.6510,0.0295) (4.9150,0.8205,0.0295) (2.5884,0.8205,0.0295)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.8205,0.0000) (4.9150,0.8205,0.0000) (4.9150,0.8710,0.0000) (2.5884,0.8710,0.0000)};
 
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.3850,0.0000) (3.0793,0.3850,0.0000) (3.0793,0.4405,0.0000) (2.5884,0.4405,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.4405,0.0000) (3.0793,0.4405,0.0000) (3.0793,0.4860,0.0000) (2.5884,0.4860,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.4860,0.0115) (3.0793,0.4860,0.0115) (3.0793,0.4910,0.0115) (2.5884,0.4910,0.0115)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.4910,0.0000) (3.0793,0.4910,0.0000) (3.0793,0.4960,0.0000) (2.5884,0.4960,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.4960,0.0160) (3.0793,0.4960,0.0160) (3.0793,0.5190,0.0160) (2.5884,0.5190,0.0160)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.5190,0.0065) (3.0793,0.5190,0.0065) (3.0793,0.5220,0.0065) (2.5884,0.5220,0.0065)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.5220,0.0000) (3.0793,0.5220,0.0000) (3.0793,0.5280,0.0000) (2.5884,0.5280,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.5280,0.0000) (3.0793,0.5280,0.0000) (3.0793,0.5410,0.0000) (2.5884,0.5410,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.5410,0.0040) (3.0793,0.5410,0.0040) (3.0793,0.5455,0.0040) (2.5884,0.5455,0.0040)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.5455,0.0250) (3.0793,0.5455,0.0250) (3.0793,0.5910,0.0250) (2.5884,0.5910,0.0250)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.5910,0.0000) (3.0793,0.5910,0.0000) (3.0793,0.6390,0.0000) (2.5884,0.6390,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.6390,0.0000) (3.0793,0.6390,0.0000) (3.0793,0.6510,0.0000) (2.5884,0.6510,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.6510,0.0250) (3.0793,0.6510,0.0250) (3.0793,0.8205,0.0250) (2.5884,0.8205,0.0250)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.8205,0.0000) (3.0793,0.8205,0.0000) (3.0793,0.8710,0.0000) (2.5884,0.8710,0.0000)};
-
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.3850,0.0100) (4.4802,0.3850,0.0100) (4.4802,0.4405,0.0100) (3.0793,0.4405,0.0100)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.4405,0.0495) (4.4802,0.4405,0.0495) (4.4802,0.4860,0.0495) (3.0793,0.4860,0.0495)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.4860,0.0345) (4.4802,0.4860,0.0345) (4.4802,0.4910,0.0345) (3.0793,0.4910,0.0345)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.4910,0.0000) (4.4802,0.4910,0.0000) (4.4802,0.4960,0.0000) (3.0793,0.4960,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.4960,0.0425) (4.4802,0.4960,0.0425) (4.4802,0.5190,0.0425) (3.0793,0.5190,0.0425)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.5190,0.0000) (4.4802,0.5190,0.0000) (4.4802,0.5220,0.0000) (3.0793,0.5220,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.5220,0.0000) (4.4802,0.5220,0.0000) (4.4802,0.5280,0.0000) (3.0793,0.5280,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.5280,0.0525) (4.4802,0.5280,0.0525) (4.4802,0.5410,0.0525) (3.0793,0.5410,0.0525)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.5410,0.0155) (4.4802,0.5410,0.0155) (4.4802,0.5455,0.0155) (3.0793,0.5455,0.0155)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.5455,0.0135) (4.4802,0.5455,0.0135) (4.4802,0.5910,0.0135) (3.0793,0.5910,0.0135)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.5910,0.0000) (4.4802,0.5910,0.0000) (4.4802,0.6390,0.0000) (3.0793,0.6390,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.6390,0.0000) (4.4802,0.6390,0.0000) (4.4802,0.6510,0.0000) (3.0793,0.6510,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.6510,0.0000) (4.4802,0.6510,0.0000) (4.4802,0.8205,0.0000) (3.0793,0.8205,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.8205,0.0000) (4.4802,0.8205,0.0000) (4.4802,0.8710,0.0000) (3.0793,0.8710,0.0000)};
-
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.3850,0.0080) (4.7503,0.3850,0.0080) (4.7503,0.4405,0.0080) (4.4802,0.4405,0.0080)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.4405,0.0035) (4.7503,0.4405,0.0035) (4.7503,0.4860,0.0035) (4.4802,0.4860,0.0035)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.4860,0.0000) (4.7503,0.4860,0.0000) (4.7503,0.4910,0.0000) (4.4802,0.4910,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.4910,0.0100) (4.7503,0.4910,0.0100) (4.7503,0.4960,0.0100) (4.4802,0.4960,0.0100)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.4960,0.0000) (4.7503,0.4960,0.0000) (4.7503,0.5190,0.0000) (4.4802,0.5190,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.5190,0.0000) (4.7503,0.5190,0.0000) (4.7503,0.5220,0.0000) (4.4802,0.5220,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.5220,0.0000) (4.7503,0.5220,0.0000) (4.7503,0.5280,0.0000) (4.4802,0.5280,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.5280,0.0060) (4.7503,0.5280,0.0060) (4.7503,0.5410,0.0060) (4.4802,0.5410,0.0060)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.5410,0.0000) (4.7503,0.5410,0.0000) (4.7503,0.5455,0.0000) (4.4802,0.5455,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.5455,0.0000) (4.7503,0.5455,0.0000) (4.7503,0.5910,0.0000) (4.4802,0.5910,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.5910,0.0000) (4.7503,0.5910,0.0000) (4.7503,0.6390,0.0000) (4.4802,0.6390,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.6390,0.0000) (4.7503,0.6390,0.0000) (4.7503,0.6510,0.0000) (4.4802,0.6510,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.6510,0.0000) (4.7503,0.6510,0.0000) (4.7503,0.8205,0.0000) (4.4802,0.8205,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.8205,0.0000) (4.7503,0.8205,0.0000) (4.7503,0.8710,0.0000) (4.4802,0.8710,0.0000)};
-
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.7503,0.3850,0.1860) (12.1265,0.3850,0.1860) (12.1265,0.4405,0.1860) (4.7503,0.4405,0.1860)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.7503,0.4405,0.0615) (12.1265,0.4405,0.0615) (12.1265,0.4860,0.0615) (4.7503,0.4860,0.0615)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.7503,0.4860,0.0000) (12.1265,0.4860,0.0000) (12.1265,0.4910,0.0000) (4.7503,0.4910,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.7503,0.4910,0.0045) (12.1265,0.4910,0.0045) (12.1265,0.4960,0.0045) (4.7503,0.4960,0.0045)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.7503,0.4960,0.0210) (12.1265,0.4960,0.0210) (12.1265,0.5190,0.0210) (4.7503,0.5190,0.0210)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.7503,0.5190,0.0000) (12.1265,0.5190,0.0000) (12.1265,0.5220,0.0000) (4.7503,0.5220,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.7503,0.5220,0.0120) (12.1265,0.5220,0.0120) (12.1265,0.5280,0.0120) (4.7503,0.5280,0.0120)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.7503,0.5280,0.0000) (12.1265,0.5280,0.0000) (12.1265,0.5410,0.0000) (4.7503,0.5410,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.7503,0.5410,0.0000) (12.1265,0.5410,0.0000) (12.1265,0.5455,0.0000) (4.7503,0.5455,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.7503,0.5455,0.0000) (12.1265,0.5455,0.0000) (12.1265,0.5910,0.0000) (4.7503,0.5910,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.7503,0.5910,0.0000) (12.1265,0.5910,0.0000) (12.1265,0.6390,0.0000) (4.7503,0.6390,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.7503,0.6390,0.0000) (12.1265,0.6390,0.0000) (12.1265,0.6510,0.0000) (4.7503,0.6510,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.7503,0.6510,0.0000) (12.1265,0.6510,0.0000) (12.1265,0.8205,0.0000) (4.7503,0.8205,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.7503,0.8205,0.0000) (12.1265,0.8205,0.0000) (12.1265,0.8710,0.0000) (4.7503,0.8710,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.3850,0.1245) (12.1265,0.3850,0.1245) (12.1265,0.4460,0.1245) (4.9150,0.4460,0.1245)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.4460,0.0135) (12.1265,0.4460,0.0135) (12.1265,0.4485,0.0135) (4.9150,0.4485,0.0135)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.4485,0.0160) (12.1265,0.4485,0.0160) (12.1265,0.4555,0.0160) (4.9150,0.4555,0.0160)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.4555,0.0090) (12.1265,0.4555,0.0090) (12.1265,0.4620,0.0090) (4.9150,0.4620,0.0090)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.4620,0.0120) (12.1265,0.4620,0.0120) (12.1265,0.4705,0.0120) (4.9150,0.4705,0.0120)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.4705,0.0185) (12.1265,0.4705,0.0185) (12.1265,0.4910,0.0185) (4.9150,0.4910,0.0185)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.4910,0.0030) (12.1265,0.4910,0.0030) (12.1265,0.4960,0.0030) (4.9150,0.4960,0.0030)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.4960,0.0070) (12.1265,0.4960,0.0070) (12.1265,0.5015,0.0070) (4.9150,0.5015,0.0070)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.5015,0.0000) (12.1265,0.5015,0.0000) (12.1265,0.5085,0.0000) (4.9150,0.5085,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.5085,0.0200) (12.1265,0.5085,0.0200) (12.1265,0.5165,0.0200) (4.9150,0.5165,0.0200)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.5165,0.0160) (12.1265,0.5165,0.0160) (12.1265,0.5410,0.0160) (4.9150,0.5410,0.0160)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.5410,0.0000) (12.1265,0.5410,0.0000) (12.1265,0.5485,0.0000) (4.9150,0.5485,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.5485,0.0060) (12.1265,0.5485,0.0060) (12.1265,0.5775,0.0060) (4.9150,0.5775,0.0060)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.5775,0.0000) (12.1265,0.5775,0.0000) (12.1265,0.6010,0.0000) (4.9150,0.6010,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.6010,0.0000) (12.1265,0.6010,0.0000) (12.1265,0.6070,0.0000) (4.9150,0.6070,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.6070,0.0000) (12.1265,0.6070,0.0000) (12.1265,0.6115,0.0000) (4.9150,0.6115,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.6115,0.0000) (12.1265,0.6115,0.0000) (12.1265,0.6190,0.0000) (4.9150,0.6190,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.6190,0.0000) (12.1265,0.6190,0.0000) (12.1265,0.6275,0.0000) (4.9150,0.6275,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.6275,0.0000) (12.1265,0.6275,0.0000) (12.1265,0.6390,0.0000) (4.9150,0.6390,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.6390,0.0000) (12.1265,0.6390,0.0000) (12.1265,0.6510,0.0000) (4.9150,0.6510,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.6510,0.0000) (12.1265,0.6510,0.0000) (12.1265,0.8205,0.0000) (4.9150,0.8205,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.8205,0.0000) (12.1265,0.8205,0.0000) (12.1265,0.8710,0.0000) (4.9150,0.8710,0.0000)};
 

### 2015-11-17 BN_discretizer_paper.tex
remerging Mykel's comments

@@
 \newcommand{\todo}[1]{\textcolor{magenta}{#1}}
+\newcommand{\yichun}[1]{\textit{\textcolor{green}{#1}}}
 \newcommand{\tim}[1]{\textit{\textcolor{blue}{#1}}}
+\newcommand{\mykel}[1]{\textit{\textcolor{cyan}{#1}}}
 
@@
 \section{Introduction}
-\label{intro}
+
+\begin{table}[H]
+  \centering
+  \begin{tabular}{@{}ccl@{}}
+    \toprule
+    Current & Mykel & Description \\
+    \midrule
+    $G$ & $G$ & BN graph structure \\
+    $P$ & $P$ & discrete probability \\
+    $p$ & $p$ & probability density \\
+    $D$ & $D$ & available data \\
+    $|D|$ & $n$ & number of variables in the BN \\
+    $D_{\bm{Y}}$ & & subset of data associated with $\bm{Y}$ \\
+    $X$ & $X_{1:n}$ & variables in BN (discrete) \\
+    $x_{1:n}$ & $x_{1:n}$ & a specific instance of vars in BN \\
+    $x'_{1:n}$ &  & unique instances of var in BN \\
+        & $r_i$ & number of instantiations of $i$th var \\
+    $J_p$ & $q_i$ & number of instantiations of parents of $i$th var \\
+        &       & $ = 1$ if no parents \\
+    $\brock{\Pi_{X_i}}_j$ & $\pi_{ij}$ & $j$th instantiation of $i$th var \\
+        & $\theta_{ijk}$ & probability of $i$th var $= k$ given $j$th parental inst. \\
+    $\Theta$ & $\bm{\theta}$ & set of all (non-independent) probability parameters \\
+    $n_{i,j}^{(k)}$ & $m_{ijk}$ & observation counts \\
+    $n_{i,j,l}^{(k)}$ & $m_{ijk}$ & observation counts with $l$th instance of spouse\\
+    $\alpha_{ijk}$ & $\alpha_{ijk}$ & Dirichlet prior counts \\
+    $N_{ij}$ & $\alpha_{ij0}$ & sum over Dirichlet prior counts for $k$ \\
+        & $m_{ij0}$ & sum over observations counts for $k$ \\
+        & $\Gamma$ & the Gamma function \\
+    $N$ &          & is the number of samples in dataset \\
+    $N_i$ &          & counts for $i$th instance of a specific var \\
+    $\Pi_X$ & $\text{pa}_{x_i}$ & parents of a variable or instance \\
+    $n_C$ & & number of children of a variable \\
+    $H(~)$ & & a function \\
+    $I(~,~)$ & & mutual information \\
+    $X_i$ & & $i$th variable in BN, may be cont or disc \\
+    $X_i^*$ & & discrete version of cont var \\
+    $E$ & & set of edges in BN \\
+    $\text{Pa}\paren{X_i}$, $n_p$ & & number of parents of $X_i$ \\
+    $f\paren{X_i, \Pi_{X_i}}$ & $f(G)$ & score function for K2 \\
+    $M_C$ & & discretization policy for $C$ \\
+    $C$ & & a continuous variable \\
+    $t_i$ & & the $i$th bin edge for a specific var \\
+    $d_i$ & & allowable discretization positions (between unique vals) \\
+    $k$ & & number of intervals for $M_C$ \\
+    $C_{1:N}$ & & sorted samples for $C$ \\
+    $n_i$ & & $n_1 = s_1$ and $n_i = s_{i} - s_{i-1}$ \\
+    $s_i$ & & $\sum_{j=1}^k n_j$ and $s_k = N$, $s_0 = 0$ \\
+    $C_i$ & & $i$th child of a specific var \\
+    $\boldsymbol{S_i}$ & & set of spouses associated with $i$th child of specific var \\
+    $L$ & & largest cardinality among discrete variables in BN \\
+    $I_q$ & & an interval from $u \rightarrow v$ \\
+    $v'_\text{max}$ & & largest cardinality of variables that directly connect to $X$ \\
+    $S[]$ & &  optimal objective value of subproblems with instances from $1$ to $u$ \\
+    \bottomrule
+  \end{tabular}
+\end{table}
+
 Bayesian networks \citep{Pearl_1988, PGM_2009} are an increasingly popular method for modeling uncertainty and causality in science and engineering.
+They provide an efficient factorization of the joint probability distribution over a set of random variables.
+Bayesian networks first emerged from artificial intelligence research and have been applied to a wide variety of problems, ranging from decision-making systems \citep{DMU_2015} \mykel{better to use a primary source} to medical diagnoses \citep{Lustgarten_2011}.
+In most cases, we assume that all random variables in Bayesian networks are discrete, since many Bayesian network learning algorithms are unable to deal with continuous variables efficiently.
+However, many applications   +Bayesian networks \citep{Pearl_1988, PGM_2009} are an increasingly popular method for modeling uncertainty and causality in science and engineering.
 They provide an efficient factorization of the joint probability distribution over a set of random variables.
@@
 In most cases, we assume that all random variables in Bayesian networks are discrete, since many Bayesian network learning algorithms are unable to deal with continuous variables efficiently.
-However, many applications
-require the use of continuous variables, such as position and velocity in dynamic systems.
+However, many applications require the use of continuous variables, such as position and velocity in dynamic systems \mykel{cite Kochenderfer JGCD article on encounter modeling}.
 
@@
 \subsection{MDL Principle Discretization}
-The MDL principle was first proposed by \cite{MDL_1978}, and states that the best model for a dataset is one which minimizes the amount of information needed to describe it \citep{Grunwald_2009}.
+The MDL principle was first proposed by \cite{MDL_1978} and states that the best model for a dataset is one that minimizes the amount of information needed to describe it \citep{Grunwald_2009}.
 MDL methods trade off goodness-of-fit against model complexity to reduce generalization error.
-In the context of Bayesian networks, \cite{Friedman_1996} applied the MDL principle to determine the optimal number of discretization intervals for continuous variables and optimal the positions of their discretization boundaries.
+In the context of Bayesian networks, \cite{Friedman_1996} applied the MDL principle to determine the optimal number of discretization intervals for continuous variables and the optimal positions of their discretization boundaries.
 Their approach selects a discretization policy that minimizes the sum of the description lengths of the discretized Bayesian network and the information necessary for recovering the continuous values from the discretized data.
-In the single continuous variable case, the objective function is
+For a Bayesian network with a single continuous variable $X$, the objective function is
 
@@
 It is based on the minimum description length principle (MDL): the optimal discretization policy minimizes the description length of the Bayesian network and discretization policy.
-The MDL algorithm has a $\bigo\paren{N^3 + \paren{n_c {v_\text{max}}^{(n_c^p)_\text{max}} + {v_\text{max}}^{n_p}} \cdot N^2}$ runtime on Bayesian networks with a single continuous variable and multiple discrete variables, where $N$ is the number of data samples from the joint distribution, $n_p$ and $n_c$ are the numbers of parent and children variables for the continuous variable, $v_\text{max}$ is the largest cardinality over all variables in the Markov blanket, and  ${(n_c^p)_\text{max}}$ is the largest number of parent variables of the continuous variable's children.
+The MDL algorithm has an $\bigo\paren{N^3 + \paren{n_c {v_\text{max}}^{(n_c^p)_\text{max}} + {v_\text{max}}^{n_p}} \cdot N^2}$ runtime on Bayesian networks with a single continuous variable and multiple discrete variables, where $N$ is the number of data samples from the joint distribution, $n_p$ and $n_c$ are the numbers of parent and children variables for the continuous variable, $v_\text{max}$ is the largest cardinality over all variables in the Markov blanket, and  ${(n_c^p)_\text{max}}$ is the largest number of parent variables of the continuous variable's children.
 The MDL method iterates over all continuous variables until convergence in the case of multiple continuous variables, converging in a few cycles according to our tests of real-world data.
-Unfortunately, MDL tends to produce discrete variables with low cardinality~\todo{[cite]}.
+Unfortunately, MDL tends to produce discrete variables with low cardinality~\todo{[cite]}
+\mykel{don't like low-cardinality. Maybe 'intervals' or something instead}.
 
@@
 
-A Bayesian network $B$ is defined by a pair $(G,\Theta)$, where $G = (X,E)$ is a directed acyclic graph whose nodes correspond to a set of random variables $X = \brock{X_1, X_2, \cdots, X_n}$, and whose edges $E$ represent probabilistic dependencies among nodes.
+\mykel{$\bigstar$ This all needs to be explained better. Too many variables are being defined at once.}
+
+A Bayesian network $B$ is defined by a pair $(G,\Theta)$, where $G = (X,E)$ is a directed acyclic graph whose nodes correspond to a set of random variables $X = \brock{X_1, X_2, \ldots, X_n}$, and whose edges $E$ represent probabilistic dependencies among nodes.
 The graph structure $G$ encodes the Markov property: each node $X_i$ is independent of its non-descendants given its parents $\Pi_{X_i}$ in $G$.
@@
 The joint distribution over $X$ factors according to the Markov property:
-\begin{equation}
-P_B (X_1 , \cdots, X_n) = \prod_{i=1}^{n} P_B (X_i \mid \Pi_{X_i}) = \prod_{i=1}^{n} \theta_{x_i \mid \Pi_{x_i}}\text{.}
+
+\begin{equation}
+P_B (X_1 , \ldots, X_n) = \prod_{i=1}^{n} P_B (X_i \mid \Pi_{X_i}) = \prod_{i=1}^{n} \theta_{x_i \mid \Pi_{x_i}}\text{.}
 \end{equation}
@@
 \begin{equation}
-P(X_i \mid \Pi_{X_i}) \cdot \prod_{j = 1}^{ Pa( X_i)} P( \{ \Pi_{X_i} \}_j) = P(X_i) \cdot P(\Pi_{X_i} \mid X_i),
+P(X_i \mid \Pi_{X_i}) \cdot \prod_{j = 1}^{ Pa( X_i)} P( \brock{\Pi_{X_i} }_j) = P(X_i) \cdot P(\Pi_{X_i} \mid X_i)\text{,}
 \end{equation}
@@
 \begin{equation}
+  \label{eq:p_M}
   P(M) = \prod_{i=1}^k \curly{ \brock{1 - {\exp(- L \cdot {{x_{s_i+1} - x_{s_i}}\over{x_N - x_1}})}} \cdot \exp\paren{L \cdot {{x_{s_{i}} - x_{s_{i-1} + 1}}\over{x_N - x_1}}}},
@@
 \begin{equation}
+  \label{eq:p_D_given_M}
   P\paren{D \mid M} \propto P\paren{D_{\Pi_x} \mid M} \cdot \prod_{i = 1}^{n_c} P\paren{D_{C_i} \mid M, D_{\boldsymbol{S_i}}}\text{.}
@@
 Let $b = \brock{b_0,b_1,b_2,\ldots,b_M}$ be an increasing sequence of integers marking the repeated value intervals in $D_X$ such that $b_0 = 0$ and $x_{b_{i-1} + 1} = x_{b_{i-1} + 2} = \ldots = x_{b_i} = x'_i$.
-By this definition, the allowable discretization positions are $d_i = \paren{x_{b_{i}} + x_{{b_i}+1}}/2$ for all $i = 1,2,\ldots,M-1$.
+By this definition, the allowable discretization positions are $d_i = \paren{x_{b_{i}} + x_{{b_i}+1}}/2$ for all \todo{$i = 1,2,\ldots,M-1$}.
 
@@
 The calculation has a $O(n_c  {v'_\text{max}} \cdot N^2 + {v'_\text{max}}^{n_p} \cdot N^2)$ runtime, where $n_c$ and $n_p$ are the numbers of child and parent variables respectively, and $v'_\text{max}$ is the largest cardinality of variables that directly connect to $X$.
-
-Now we are able to solve the optimization problem over Equation \ref{eq:opt_prob}.
-The dynamic programming procedure is shown in Algorithm \ref{alg:disc_one}.
+\tim{so parents and children, or parents, children and spouses?}
+
+The optimization problem over Equation~\ref{eq:opt_prob} can now be solved.
+The dynamic programming procedure is shown in Algorithm~\ref{alg:disc_one}.
 It takes two inputs: $D$, the joint samples over all variables sorted in ascending order according to $D_X$, and $G$, the network structure.
-The runtime of Algorithm \ref{alg:disc_one} is also $O(n_c  {v'_\text{max}} \cdot N^2 + {v'_\text{max}}^{n_p} \cdot N^2)$, because the runtime of the dynamic programming procedure is less than the runtime for computing $h(u,v)$.
-Algorithm \ref{alg:disc_one} is guaranteed to be optimal.
+The runtime of Algorithm~\ref{alg:disc_one} is also $O(n_c  {v'_\text{max}} \cdot N^2 + {v'_\text{max}}^{n_p} \cdot N^2)$, because the runtime of the dynamic programming procedure is less than the runtime for computing $h(u,v)$.
+Algorithm~\ref{alg:disc_one} is guaranteed to be optimal.
 For faster methods with suboptimal results please refer to \citep{Boulle_2006}.
@@
 \State $N' \leftarrow$ the number of unique values in $D_X$
-\State $H \leftarrow$ an $N \times N$ matrix such that $H[u,v] = h(u,v)$ per Algorithm \ref{alg:h} in the appendix
+\State $H \leftarrow$ an $N \times N$ matrix such that $H[u,v] = h(u,v)$ per Algorithm~\ref{alg:h} in the appendix
 \State $b \leftarrow$ the increasing sequence of $M$ integers as previously defined
@@
 
-\section{Extension to Multiple Continuous Variables}
+\section{Multiple Variable Discretization}
 \label{sec:multi_var}
@@
           \State $\Pi_{X_i} \leftarrow \Pi_{X_i} \cup Y $
-          \State $M \leftarrow$ {DISCRETIZE}({$D''$, $G$, $C$, $u_{cycle}$}): Algorithm \ref{alg:disc_two}
+          \State $M \leftarrow$ {DISCRETIZE}({$D''$, $G$, $C$, $u_{cycle}$}): Algorithm~\ref{alg:disc_two}
           \State $D* = M(D'')$
@@
 
-\subsubsection{Experiment 1 on the Auto MPG dataset}
+\subsubsection{Discretization with fixed Structure}
 \label{subsubsec:auto_exp1}
@@
 
-\subsubsection{Experiment 2 on the Auto MPG dataset}
+\subsubsection{Discretization while Learning Structure}
 \label{subsubsec:auto_exp2}
@@
 
-\subsubsection{Experiment 1 on the Wine dataset}
+\subsubsection{Discretization with fixed Structure}
 \label{subsubsec:wine_exp1}
@@
 The proposed method is still better than MDL principle discretization in terms of likelihood, although the latter returns non-trivial result in this experiment.
-Note that the proposed method with the approximation has more intervals after discretization, and it has a slightly better result in terms of likelihood.
-However, the improvement is marginally small, which indicates that the proposed method without the approximation captures good enough discretization result even if the numbers of intervals after discretization are smaller.
+\todo{Note that the proposed method with the approximation has more intervals after discretization, and it has a slightly better result in terms of likelihood.
+However, the improvement is marginally small, which indicates that the proposed method without the approximation captures good enough discretization result even if the numbers of intervals after discretization are smaller.}
 In addition, as shown in next dataset, the approximation might cut continuous variables into too many intervals.
@@
     \end{tabular}
-  \caption{K2 structure learning with prediscretization on the Wine dataset}
+  \caption{\tim{Structure from prediscretized K2 structure learning to compare the methods}}
   \label{fig:wine_graph_1}
@@
   }
-\caption{Discretization result of Wine dataset based on the graph Fig. \ref{fig:wine_graph_1}}
+  \caption{Discretization result of Wine dataset based on the graph Fig. \ref{fig:wine_graph_1}
+  \todo{MDL has bins, heuristic is slightly worse in logl but still good. MDL keeps all of its CPDs small, no neighboring vars both have more than 1 interval.}
+  \tim{Should we scale the logl? What is the best way to do that?}
+  }
   \label{table:wine_disc_table_1}
@@
 \begin{figure}[ht]
+  \centering
   \begin{tabular}{cc}
@@
 
-\subsubsection{Experiment 2 on the Wine dataset}
+\subsubsection{Discretization while Learning Structure}
 \label{subsubsec:wine_exp2}
 
-Figure \ref{fig:wine_graph_2} is the learned discrete-valued Bayesian network from the Wine dataset, and it is obtained by running Algorithm \ref{alg:structure_learn} 50 times.
+Figure \ref{fig:wine_graph_2} is the learned discrete-valued Bayesian network from the Wine dataset, and it is obtained by running Algorithm \ref{alg:structure_learn} fifty times.
 The integer numbers next to variables are cardinality numbers of variables.
-By comparing Figure \ref{fig:wine_graph_2} with \ref{fig:wine_graph_1}, it shows that the the Bayesian network obtained by \ref{alg:structure_learn} has more edges than the network obtained by prediscretization and the K2 algorithm.
+By comparing Figure \ref{fig:wine_graph_2} with \ref{fig:wine_graph_1}, it shows that the the Bayesian network obtained by Algorithm \ref{alg:structure_learn} has more edges than the network obtained by prediscretization and the K2 algorithm.
 Furthermore, the cardinalitis of discretized variables in Figure \ref{fig:wine_graph_2} are smaller than the result in \ref{table:wine_disc_table_1}.
@@
   \end{tabular}
-  \caption{The learned discrete-valued Bayesian network from the Wine dataset}
+  \caption{The learned discrete-valued Bayesian network from the Wine dataset \todo{using optimal Bayesian method}}
   \label{fig:wine_graph_2}
@@
   \end{tabular}
-  \caption{The discretization result on variable $E$ and $K$ of the learned network in Figure \ref{fig:wine_graph_2}}
+  \caption{The discretization result on variable $E$ and $K$ of the learned network in Figure \ref{fig:wine_graph_2}
+  \todo{Note unchanged discretization edge.}
+  }
   \label{fig:wine_exp2_distr}
@@
 
-\subsubsection{Experiment 1 on the Housing dataset}
+\subsubsection{Discretization with Fixed Structure}
 \label{subsubsec:housing_exp1}
@@
   \centering
-    \begin{tabular}{cc}
+  % \begin{tabular}{cc}
     \input{graph_housing_1}
-    \end{tabular}
-  \caption{K2 structure learning with prediscretization on Housing dataset}
+  % \end{tabular}
+  \caption{\todo{Structure from prediscretized K2 structure learning to compare the methods for Housing dataset}}
   \label{fig:housing_graph_1}
@@
   }
-\caption{Discretization result of Housing dataset based on the graph Fig. \ref{fig:housing_graph_1}}
+  \caption{Discretization result of Housing dataset based on the graph Figure~\ref{fig:housing_graph_1} \tim{Fig. vs. Figure}}
   \label{table:housing_disc_table_1}
@@
 
-Figure \ref{fig:housing_exp1_distr_3_5} and Figure \ref{fig:housing_exp1_distr_8_5} show the discretization result by the propose method on the network in Figure \ref{fig:housing_graph_1}.
-In Figure \ref{fig:housing_exp1_distr_3_5}, the scatter points, which stands for the raw data, has been jittered, since there are many repeated values in the raw data on the variable pair $C$ and $E$.
+Figure~\ref{fig:housing_exp1_distr_3_5} and Figure~\ref{fig:housing_exp1_distr_8_5} show the discretization result by the propose method on the network in Figure~\ref{fig:housing_graph_1}.
+In Figure~\ref{fig:housing_exp1_distr_3_5}, the scatter points, which stands for the raw data, has been jittered, since there are many repeated values in the raw data on the variable pair $C$ and $E$.
 These repeating values cause the high number of intervals after discretization for both $C$ and $E$, because in some sense, each repeated-value point form a single discretized area.
@@
 \begin{figure}[ht]
-    \begin{tabular}{cc}
+    % \begin{tabular}{cc}
       \input{graph_housing_exp1_distr_3_5}
-    \end{tabular}
-  \caption{The discretization result on variable $C$ and $E$ of the network in Figure \ref{fig:housing_graph_1}}
+    % \end{tabular}
+  \caption{The discretization result on variable $C$ and $E$ of the network in Figure~\ref{fig:housing_graph_1}}
   \label{fig:housing_exp1_distr_3_5}
@@
 \begin{figure}[ht]
-    \begin{tabular}{cc}
+    % \begin{tabular}{cc}
       \input{graph_housing_exp1_distr_8_5}
-    \end{tabular}
-  \caption{The discretization result on variable $H$ and $E$ of the network in Figure \ref{fig:housing_graph_1}}
+    % \end{tabular}
+  \caption{The discretization result on variable $H$ and $E$ of the network in Figure~\ref{fig:housing_graph_1}}
   \label{fig:housing_exp1_distr_8_5}
@@
 
-\subsubsection{Experiment 2 on the Housing dataset}
+\subsubsection{Discretization while Learning Structure}
 \label{subsubsec:housing_exp2}
 
-Figure \ref{fig:housing_graph_2} is the learned discrete-valued Bayesian network from the Housing dataset by running Algorithm \ref{alg:structure_learn} 50 times.
-In both Figure \ref{fig:housing_graph_1} and Figure \ref{fig:housing_graph_2}, the variable $D$ is not connected to any other variable.
+Figure~\ref{fig:housing_graph_2} is the learned discrete-valued Bayesian network from the Housing dataset by running Algorithm~\ref{alg:structure_learn} fifty times.
+In both Figure~\ref{fig:housing_graph_1} and Figure~\ref{fig:housing_graph_2}, the variable $D$ is not connected to any other variable.
 Continuous variables $C$, $E$, $J$ and $K$, which are all in a Markov blanket, have high cardinality numbers after discretization.
@@
 \begin{figure}[ht]
-    \begin{tabular}{cc}
+    % \begin{tabular}{cc}
       \input{graph_housing_2}
-    \end{tabular}
-  \caption{The learned discrete-valued Bayesian network from the Housing dataset}
+    % \end{tabular}
+  \caption{The learned discrete-valued Bayesian network from the Housing dataset
+  \todo{Mention that there are high-cardinality vars.}
+  \tim{Var with 1 interval?}
+  }
   \label{fig:housing_graph_2}
@@
 
-Figure \ref{fig:housing_exp2_distr_3_5} and Figure \ref{fig:housing_exp2_distr_8_5} show the discretization result on variables of the network in Figure \ref{fig:housing_graph_2}.
+Figure~\ref{fig:housing_exp2_distr_3_5} and Figure~\ref{fig:housing_exp2_distr_8_5} show the discretization result on variables of the network in Figure~\ref{fig:housing_graph_2}.
 Again, variable $C$ and $E$ have many discretization edges due to the repeated values.
@@
 \begin{figure}[ht]
-    \begin{tabular}{cc}
+    % \begin{tabular}{cc}
       \input{graph_housing_exp2_distr_3_5}
-    \end{tabular}
-  \caption{The discretization result on variable $C$ and $E$ of the network in Figure \ref{fig:housing_graph_2}}
+    % \end{tabular}
+  \caption{The discretization result on variable $C$ and $E$ of the network in Figure~\ref{fig:housing_graph_2}}
   \label{fig:housing_exp2_distr_3_5}
@@
 \begin{figure}[ht]
-    \begin{tabular}{cc}
+    % \begin{tabular}{cc}
       \input{graph_housing_exp2_distr_8_5}
-    \end{tabular}
-  \caption{The discretization result on variable $H$ and $G$ of the network in Figure \ref{fig:housing_graph_2}}
+    % \end{tabular}
+  \caption{The discretization result on variable $H$ and $G$ of the network in Figure~\ref{fig:housing_graph_2}}
   \label{fig:housing_exp2_distr_8_5}

### 2015-11-17 graph_wine_exp1_distr.tex
remerging Mykel's comments

@@
 			colorbar style={
-			        ytick={0,0.05,...,0.5},
+			        ytick={0,0.05,...,0.51},
 			        yticklabel style={

### 2015-11-17 BN_discretizer_paper.tex
pre-Mykel meeting

@@
 Bayesian networks first emerged from artificial intelligence research and have been applied to a wide variety of problems, ranging from decision-making systems \citep{DMU_2015} to medical diagnoses \citep{Lustgarten_2011}.
+\mykel{packages such as ....}
 In most cases, we assume that all random variables in Bayesian networks are discrete, since many Bayesian network learning algorithms are unable to deal with continuous variables efficiently.
-However, many applications require the use of continuous variables, such as position and velocity in dynamic systems \mykel{cite Kochenderfer JGCD article on encounter modeling}.
+However, many applications require the use of continuous variables, such as position and velocity in dynamic systems \citep{kochenderfer2010airspace}.
 
@@
 One successful example is belief propagation in Gaussian graphical models \citep{Weiss_2011}.
-For other parametric distributions \citep{Ihler_2009} and non-linear functions~\todo{[cite]}, these redesigned algorithms are computationally expensive and do not perform well.
+For other parametric distributions and non-linear functions \citep{Ihler_2009}, these redesigned algorithms are computationally expensive and do not perform well.
 \mykel{$\bigstar$ We need to discuss this; talk about algorithms for inference and structure learning, expectation propagation, Gibbs, BVGS}
@@
 This section describes experiments conducted to evaluate the proposed methods.
-All experiments were run on datasets from the publically available Irvine machine learning repository \citep{Lichman:2013}.
+All experiments were run on datasets from the publically available Irvine machine learning repository \citep{Lichman_2013}.
 Variables are labelled alphabetically in the order given on the dataset information webpage.

### 2015-11-17 BN_discretizer_paper.tex
Modify plots

@@
 The dataset has \num{392} instances after deleting the six instances with missing data, and eight variables.
-Three variables are discrete: $B$, $G$, and $H$ with cardinality 5, 13, and 3 respectively.
+Three variables are discrete: $B$, $G$, and $H$ with cardinality \num{5}, \num{13}, and \num{3} respectively.
 Two expiriments are conducted, one with a given network structure and one in which the structure is learned.
@@
 
-The proposed discretization method and the MDL discretization method are tested on Auto MPG data given the network network in Fig.
+The optimal Bayesian approach and the MDL discretization method are tested on Auto MPG data given the network network in Fig.
 \ref{fig:auto_graph_1}.
 This structure was obtained by prediscretizing each continuous variable into five uniform-width intervals, where five is the median cardinality of the discrete variables, and then taking the most frequent structure from a thousand runs of K2.
-
-\begin{figure}[ht]
-  \centering
-  \begin{tabular}{cc}
+\yichun{most frequent?}
+
+\begin{figure}[ht]
+  \centering
     \input{graph_autocar_1}
-  \end{tabular}
   \caption{The Bayesian network obtained with K2 on the prediscretized Auto MPG dataset}
@@
 For the Bayesian network in Fig.
-\ref{fig:auto_graph_1}, the approximation only reduces runtime of proposed method and has no influence on discretization result.
+\ref{fig:auto_graph_1}, the approximation \ref{eq:opt_prob_approx} only reduces runtime and has no influence on discretization result.
 MDL principle discretization works not well, since it discretizes all variables with only one interval.
-For a Bayesian network on the Auto MPG data set that MDL principle discretization has non-trivial result, please reference to Appendix.
+The reason that the MDL method discretizes variables into too few number of intervals is discussed in Section \ref{subsec:discuss_exp}.
 
@@
 The discretization policy for the heuristic matches that for the optimal Bayesian approach.
-\todo{Need to explain why MDL fails}}
+The MDL method is less sensitive to distribution of values of other variables, thus it fails to return discretization edges.
   \label{table:auto_disc_table_1}
@@
 The black dots in Figure \ref{fig:auto_exp1_distr_1_3} demonstrate the distribution of the raw data.
-As shown in the figure, the discretization edges and the resulting marginalized probability match the raw data well.
-
-\begin{figure}[ht]
-    \begin{tabular}{cc}
+As shown in the figure, the discretization edges obtained by the optimal Bayesian approach and the resulting marginalized probability match the raw data well.
+
+\begin{figure}[ht]
       \input{graph_auto_exp1_distr_1_3}
-    \end{tabular}
-  \caption{Comparison of the raw data and discretization result on variable $A$ and $C$}
+  \caption{Comparison of the raw data and discretization result on variable $A$ and $C$ by the optimal Bayesian approach.
+The marginal probabilities of discretized areas match the distribution of the taw data very well.}
   \label{fig:auto_exp1_distr_1_3}
@@
 If the network structure is not known in advance, it should be learned along with the discretization process.
-Figure \ref{fig:auto_graph_2} show a learned discrete-valued Bayesian network and the corresponding discretization edges of each continuous variable.
+Figure \ref{fig:auto_graph_2} show a learned discrete-valued Bayesian network and the corresponding numbers of intervals after discretization.
 This result is obtained by running Algorithm \ref{alg:structure_learn} fifty times and choosing the one with the highest K2 score.
-The numbers next to the variables are cardinality numbers.
-
-\begin{figure}[ht]
-\centering
-    \begin{tabular}{cc}
+
+\begin{figure}[ht]
+\centering
       \input{graph_autocar_2}
-    \end{tabular}
   \caption{The learned discrete-valued Bayesian network from the Auto MPG dataset}
@@
 \begin{figure}[ht]
-    \begin{tabular}{cc}
       \input{graph_auto_exp2_distr_1_3}
-    \end{tabular}
   \caption{Comparison of the raw data and discretization result on variable $A$ and $C$ of the learned network in Figure \ref{fig:auto_graph_2}}.
@@
   \centering
-    \begin{tabular}{cc}
       \input{graph_wine_1}
-    \end{tabular}
   \caption{\tim{Structure from prediscretized K2 structure learning to compare the methods}}
@@
   \centering
-  \begin{tabular}{cc}
     \input{graph_wine_exp1_distr}
-  \end{tabular}
   \caption{Comparison of the discretization results on variable $A$ and $C$ obtained by the proposed method and the MDL method}
@@
 \end{figure}
+
+\subsection{Experiment Discussions}
+\label{subsec:discuss_exp}
 

### 2015-11-17 graph_auto_exp1_distr_1_3.tex
Modify plots

@@
 			zmin=0.0, zmax=1.0,
-			xlabel=A,
-			ylabel=C,
+			xlabel=$A$,
+			ylabel=$C$,
 			colorbar,
@@
 
-			\addplot3[mark=+, draw=none, mark size=0.7] coordinates {
+			\addplot3[mark=+, draw=none, mark size=1.0] coordinates {
 (18.000,307.000,1) (15.000,350.000,1) (18.000,318.000,1) (16.000,304.000,1) (17.000,302.000,1) (15.000,429.000,1) (14.000,454.000,1) (14.000,440.000,1) (14.000,455.000,1) (15.000,390.000,1) (15.000,383.000,1) (14.000,340.000,1) (15.000,400.000,1) (14.000,455.000,1) (24.000,113.000,1) (22.000,198.000,1) (18.000,199.000,1) (21.000,200.000,1) (27.000,97.000,1) (26.000,97.000,1) (25.000,110.000,1) (24.000,107.000,1) (25.000,104.000,1) (26.000,121.000,1) (21.000,199.000,1) (10.000,360.000,1) (10.000,307.000,1) (11.000,318.000,1) (9.000,304.000,1) (27.000,97.000,1) (28.000,140.000,1) (25.000,113.000,1) (19.000,232.000,1) (16.000,225.000,1) (17.000,250.000,1) (19.000,250.000,1) (18.000,232.000,1) (14.000,350.000,1) (14.000,400.000,1) (14.000,351.000,1) (14.000,318.000,1) (12.000,383.000,1) (13.000,400.000,1) (13.000,400.000,1) (18.000,258.000,1) (22.000,140.000,1) (19.000,250.000,1) (18.000,250.000,1) (23.000,122.000,1) (28.000,116.000,1) (30.000,79.000,1) (30.000,88.000,1) (31.000,71.000,1) (35.000,72.000,1) (27.000,97.000,1) (26.000,91.000,1) (24.000,113.000,1) (25.000,97.500,1) (23.000,97.000,1) (20.000,140.000,1) (21.000,122.000,1) (13.000,350.000,1) (14.000,400.000,1) (15.000,318.000,1) (14.000,351.000,1) (17.000,304.000,1) (11.000,429.000,1) (13.000,350.000,1) (12.000,350.000,1) (13.000,400.000,1) (19.000,70.000,1) (15.000,304.000,1) (13.000,307.000,1) (13.000,302.000,1) (14.000,318.000,1) (18.000,121.000,1) (22.000,121.000,1) (21.000,120.000,1) (26.000,96.000,1) (22.000,122.000,1) (28.000,97.000,1) (23.000,120.000,1) (28.000,98.000,1) (27.000,97.000,1) (13.000,350.000,1) (14.000,304.000,1) (13.000,350.000,1) (14.000,302.000,1) (15.000,318.000,1) (12.000,429.000,1) (13.000,400.000,1) (13.000,351.000,1) (14.000,318.000,1) (13.000,440.000,1) (12.000,455.000,1) (13.000,360.000,1) (18.000,225.000,1) (16.000,250.000,1) (18.000,232.000,1) (18.000,250.000,1) (23.000,198.000,1) (26.000,97.000,1) (11.000,400.000,1) (12.000,400.000,1) (13.000,360.000,1) (12.000,350.000,1) (18.000,232.000,1) (20.000,97.000,1) (21.000,140.000,1) (22.000,108.000,1) (18.000,70.000,1) (19.000,122.000,1) (21.000,155.000,1) (26.000,98.000,1) (15.000,350.000,1) (16.000,400.000,1) (29.000,68.000,1) (24.000,116.000,1) (20.000,114.000,1) (19.000,121.000,1) (15.000,318.000,1) (24.000,121.000,1) (20.000,156.000,1) (11.000,350.000,1) (20.000,198.000,1) (19.000,232.000,1) (15.000,250.000,1) (31.000,79.000,1) (26.000,122.000,1) (32.000,71.000,1) (25.000,140.000,1) (16.000,250.000,1) (16.000,258.000,1) (18.000,225.000,1) (16.000,302.000,1) (13.000,350.000,1) (14.000,318.000,1) (14.000,302.000,1) (14.000,304.000,1) (29.000,98.000,1) (26.000,79.000,1) (26.000,97.000,1) (31.000,76.000,1) (32.000,83.000,1) (28.000,90.000,1) (24.000,90.000,1) (26.000,116.000,1) (24.000,120.000,1) (26.000,108.000,1) (31.000,79.000,1) (19.000,225.000,1) (18.000,250.000,1) (15.000,250.000,1) (15.000,250.000,1) (16.000,400.000,1) (15.000,350.000,1) (16.000,318.000,1) (14.000,351.000,1) (17.000,231.000,1) (16.000,250.000,1) (15.000,258.000,1) (18.000,225.000,1) (21.000,231.000,1) (20.000,262.000,1) (13.000,302.000,1) (29.000,97.000,1) (23.000,140.000,1) (20.000,232.000,1) (23.000,140.000,1) (24.000,134.000,1) (25.000,90.000,1) (24.000,119.000,1) (18.000,171.000,1) (29.000,90.000,1) (19.000,232.000,1) (23.000,115.000,1) (23.000,120.000,1) (22.000,121.000,1) (25.000,121.000,1) (33.000,91.000,1) (28.000,107.000,1) (25.000,116.000,1) (25.000,140.000,1) (26.000,98.000,1) (27.000,101.000,1) (17.500,305.000,1) (16.000,318.000,1) (15.500,304.000,1) (14.500,351.000,1) (22.000,225.000,1) (22.000,250.000,1) (24.000,200.000,1) (22.500,232.000,1) (29.000,85.000,1) (24.500,98.000,1) (29.000,90.000,1) (33.000,91.000,1) (20.000,225.000,1) (18.000,250.000,1) (18.500,250.000,1) (17.500,258.000,1) (29.500,97.000,1) (32.000,85.000,1) (28.000,97.000,1) (26.500,140.000,1) (20.000,130.000,1) (13.000,318.000,1) (19.000,120.000,1) (19.000,156.000,1) (16.500,168.000,1) (16.500,350.000,1) (13.000,350.000,1) (13.000,302.000,1) (13.000,318.000,1) (31.500,98.000,1) (30.000,111.000,1) (36.000,79.000,1) (25.500,122.000,1) (33.500,85.000,1) (17.500,305.000,1) (17.000,260.000,1) (15.500,318.000,1) (15.000,302.000,1) (17.500,250.000,1) (20.500,231.000,1) (19.000,225.000,1) (18.500,250.000,1) (16.000,400.000,1) (15.500,350.000,1) (15.500,400.000,1) (16.000,351.000,1) (29.000,97.000,1) (24.500,151.000,1) (26.000,97.000,1) (25.500,140.000,1) (30.500,98.000,1) (33.500,98.000,1) (30.000,97.000,1) (30.500,97.000,1) (22.000,146.000,1) (21.500,121.000,1) (21.500,80.000,1) (43.100,90.000,1) (36.100,98.000,1) (32.800,78.000,1) (39.400,85.000,1) (36.100,91.000,1) (19.900,260.000,1) (19.400,318.000,1) (20.200,302.000,1) (19.200,231.000,1) (20.500,200.000,1) (20.200,200.000,1) (25.100,140.000,1) (20.500,225.000,1) (19.400,232.000,1) (20.600,231.000,1) (20.800,200.000,1) (18.600,225.000,1) (18.100,258.000,1) (19.200,305.000,1) (17.700,231.000,1) (18.100,302.000,1) (17.500,318.000,1) (30.000,98.000,1) (27.500,134.000,1) (27.200,119.000,1) (30.900,105.000,1) (21.100,134.000,1) (23.200,156.000,1) (23.800,151.000,1) (23.900,119.000,1) (20.300,131.000,1) (17.000,163.000,1) (21.600,121.000,1) (16.200,163.000,1) (31.500,89.000,1) (29.500,98.000,1) (21.500,231.000,1) (19.800,200.000,1) (22.300,140.000,1) (20.200,232.000,1) (20.600,225.000,1) (17.000,305.000,1) (17.600,302.000,1) (16.500,351.000,1) (18.200,318.000,1) (16.900,350.000,1) (15.500,351.000,1) (19.200,267.000,1) (18.500,360.000,1) (31.900,89.000,1) (34.100,86.000,1) (35.700,98.000,1) (27.400,121.000,1) (25.400,183.000,1) (23.000,350.000,1) (27.200,141.000,1) (23.900,260.000,1) (34.200,105.000,1) (34.500,105.000,1) (31.800,85.000,1) (37.300,91.000,1) (28.400,151.000,1) (28.800,173.000,1) (26.800,173.000,1) (33.500,151.000,1) (41.500,98.000,1) (38.100,89.000,1) (32.100,98.000,1) (37.200,86.000,1) (28.000,151.000,1) (26.400,140.000,1) (24.300,151.000,1) (19.100,225.000,1) (34.300,97.000,1) (29.800,134.000,1) (31.300,120.000,1) (37.000,119.000,1) (32.200,108.000,1) (46.600,86.000,1) (27.900,156.000,1) (40.800,85.000,1) (44.300,90.000,1) (43.400,90.000,1) (36.400,121.000,1) (30.000,146.000,1) (44.600,91.000,1) (33.800,97.000,1) (29.800,89.000,1) (32.700,168.000,1) (23.700,70.000,1) (35.000,122.000,1) (32.400,107.000,1) (27.200,135.000,1) (26.600,151.000,1) (25.800,156.000,1) (23.500,173.000,1) (30.000,135.000,1) (39.100,79.000,1) (39.000,86.000,1) (35.100,81.000,1) (32.300,97.000,1) (37.000,85.000,1) (37.700,89.000,1) (34.100,91.000,1) (34.700,105.000,1) (34.400,98.000,1) (29.900,98.000,1) (33.000,105.000,1) (33.700,107.000,1) (32.400,108.000,1) (32.900,119.000,1) (31.600,120.000,1) (28.100,141.000,1) (30.700,145.000,1) (25.400,168.000,1) (24.200,146.000,1) (22.400,231.000,1) (26.600,350.000,1) (20.200,200.000,1) (17.600,225.000,1) (28.000,112.000,1) (27.000,112.000,1) (34.000,112.000,1) (31.000,112.000,1) (29.000,135.000,1) (27.000,151.000,1) (24.000,140.000,1) (36.000,105.000,1) (37.000,91.000,1) (31.000,91.000,1) (38.000,105.000,1) (36.000,98.000,1) (36.000,120.000,1) (36.000,107.000,1) (34.000,108.000,1) (38.000,91.000,1) (32.000,91.000,1) (38.000,91.000,1) (25.000,181.000,1) (38.000,262.000,1) (26.000,156.000,1) (22.000,232.000,1) (32.000,144.000,1) (36.000,135.000,1) (27.000,151.000,1) (27.000,140.000,1) (44.000,97.000,1) (32.000,135.000,1) (28.000,120.000,1) (31.000,119.000,1) };

### 2015-11-17 graph_housing_exp1_distr_3_5.tex
Modify plots

@@
 			zmin=0.0, zmax=1.0,
-			xlabel=C,
-			ylabel=E,
+			xlabel=$C$,
+			ylabel=$E$,
 			colorbar,
-			point meta min=0, point meta max=0.5,
+			point meta min=0, point meta max=0.50,
 			colormap={}{ gray(0cm)=(1); gray(1cm)=(0);},
 			colorbar style={
-			        ytick={0,0.05,...,0.5},
+			        ytick={0,0.05,...,0.51},
 			        yticklabel style={
@@
 
-			\addplot3[mark=+, draw=none, mark size=0.7, jitter = 0.3] coordinates {
+			\addplot3[mark=+, draw=none, mark size=1.0, jitter = 0.1] coordinates {
 (2.310,0.538,1) (7.070,0.469,1) (7.070,0.469,1) (2.180,0.458,1) (2.180,0.458,1) (2.180,0.458,1) (7.870,0.524,1) (7.870,0.524,1) (7.870,0.524,1) (7.870,0.524,1) (7.870,0.524,1) (7.870,0.524,1) (7.870,0.524,1) (8.140,0.538,1) (8.140,0.538,1) (8.140,0.538,1) (8.140,0.538,1) (8.140,0.538,1) (8.140,0.538,1) (8.140,0.538,1) (8.140,0.538,1) (8.140,0.538,1) (8.140,0.538,1) (8.140,0.538,1) (8.140,0.538,1) (8.140,0.538,1) (8.140,0.538,1) (8.140,0.538,1) (8.140,0.538,1) (8.140,0.538,1) (8.140,0.538,1) (8.140,0.538,1) (8.140,0.538,1) (8.140,0.538,1) (8.140,0.538,1) (5.960,0.499,1) (5.960,0.499,1) (5.960,0.499,1) (5.960,0.499,1) (2.950,0.428,1) (2.950,0.428,1) (6.910,0.448,1) (6.910,0.448,1) (6.910,0.448,1) (6.910,0.448,1) (6.910,0.448,1) (6.910,0.448,1) (6.910,0.448,1) (6.910,0.448,1) (6.910,0.448,1) (5.640,0.439,1) (5.640,0.439,1) (5.640,0.439,1) (5.640,0.439,1) (4.000,0.410,1) (1.220,0.403,1) (0.740,0.410,1) (1.320,0.411,1) (5.130,0.453,1) (5.130,0.453,1) (5.130,0.453,1) (5.130,0.453,1) (5.130,0.453,1) (5.130,0.453,1) (1.380,0.416,1) (3.370,0.398,1) (3.370,0.398,1) (6.070,0.409,1) (6.070,0.409,1) (6.070,0.409,1) (10.810,0.413,1) (10.810,0.413,1) (10.810,0.413,1) (10.810,0.413,1) (12.830,0.437,1) (12.830,0.437,1) (12.830,0.437,1) (12.830,0.437,1) (12.830,0.437,1) (12.830,0.437,1) (4.860,0.426,1) (4.860,0.426,1) (4.860,0.426,1) (4.860,0.426,1) (4.490,0.449,1) (4.490,0.449,1) (4.490,0.449,1) (4.490,0.449,1) (3.410,0.489,1) (3.410,0.489,1) (3.410,0.489,1) (3.410,0.489,1) (15.040,0.464,1) (15.040,0.464,1) (15.040,0.464,1) (2.890,0.445,1) (2.890,0.445,1) (2.890,0.445,1) (2.890,0.445,1) (2.890,0.445,1) (8.560,0.520,1) (8.560,0.520,1) (8.560,0.520,1) (8.560,0.520,1) (8.560,0.520,1) (8.560,0.520,1) (8.560,0.520,1) (8.560,0.520,1) (8.560,0.520,1) (8.560,0.520,1) (8.560,0.520,1) (10.010,0.547,1) (10.010,0.547,1) (10.010,0.547,1) (10.010,0.547,1) (10.010,0.547,1) (10.010,0.547,1) (10.010,0.547,1) (10.010,0.547,1) (10.010,0.547,1) (25.650,0.581,1) (25.650,0.581,1) (25.650,0.581,1) (25.650,0.581,1) (25.650,0.581,1) (25.650,0.581,1) (25.650,0.581,1) (21.890,0.624,1) (21.890,0.624,1) (21.890,0.624,1) (21.890,0.624,1) (21.890,0.624,1) (21.890,0.624,1) (21.890,0.624,1) (21.890,0.624,1) (21.890,0.624,1) (21.890,0.624,1) (21.890,0.624,1) (21.890,0.624,1) (21.890,0.624,1) (21.890,0.624,1) (21.890,0.624,1) (19.580,0.871,1) (19.580,0.871,1) (19.580,0.871,1) (19.580,0.871,1) (19.580,0.871,1) (19.580,0.871,1) (19.580,0.871,1) (19.580,0.871,1) (19.580,0.871,1) (19.580,0.871,1) (19.580,0.871,1) (19.580,0.871,1) (19.580,0.871,1) (19.580,0.871,1) (19.580,0.871,1) (19.580,0.605,1) (19.580,0.605,1) (19.580,0.871,1) (19.580,0.605,1) (19.580,0.605,1) (19.580,0.605,1) (19.580,0.605,1) (19.580,0.605,1) (19.580,0.605,1) (19.580,0.605,1) (19.580,0.605,1) (19.580,0.605,1) (19.580,0.605,1) (19.580,0.605,1) (19.580,0.605,1) (4.050,0.510,1) (4.050,0.510,1) (4.050,0.510,1) (4.050,0.510,1) (4.050,0.510,1) (4.050,0.510,1) (4.050,0.510,1) (2.460,0.488,1) (2.460,0.488,1) (2.460,0.488,1) (2.460,0.488,1) (2.460,0.488,1) (2.460,0.488,1) (2.460,0.488,1) (2.460,0.488,1) (3.440,0.437,1) (3.440,0.437,1) (3.440,0.437,1) (3.440,0.437,1) (3.440,0.437,1) (3.440,0.437,1) (2.930,0.401,1) (2.930,0.401,1) (0.460,0.422,1) (1.520,0.404,1) (1.520,0.404,1) (1.520,0.404,1) (1.470,0.403,1) (1.470,0.403,1) (2.030,0.415,1) (2.030,0.415,1) (2.680,0.416,1) (2.680,0.416,1) (10.590,0.489,1) (10.590,0.489,1) (10.590,0.489,1) (10.590,0.489,1) (10.590,0.489,1) (10.590,0.489,1) (10.590,0.489,1) (10.590,0.489,1) (10.590,0.489,1) (10.590,0.489,1) (10.590,0.489,1) (13.890,0.550,1) (13.890,0.550,1) (13.890,0.550,1) (13.890,0.550,1) (6.200,0.507,1) (6.200,0.507,1) (6.200,0.507,1) (6.200,0.507,1) (6.200,0.504,1) (6.200,0.504,1) (6.200,0.504,1) (6.200,0.504,1) (6.200,0.504,1) (6.200,0.504,1) (6.200,0.504,1) (6.200,0.504,1) (6.200,0.507,1) (6.200,0.507,1) (6.200,0.507,1) (6.200,0.507,1) (6.200,0.507,1) (6.200,0.507,1) (4.930,0.428,1) (4.930,0.428,1) (4.930,0.428,1) (4.930,0.428,1) (4.930,0.428,1) (4.930,0.428,1) (5.860,0.431,1) (5.860,0.431,1) (5.860,0.431,1) (5.860,0.431,1) (5.860,0.431,1) (5.860,0.431,1) (5.860,0.431,1) (5.860,0.431,1) (5.860,0.431,1) (5.860,0.431,1) (3.640,0.392,1) (3.640,0.392,1) (3.750,0.394,1) (3.970,0.647,1) (3.970,0.647,1) (3.970,0.647,1) (3.970,0.647,1) (3.970,0.647,1) (3.970,0.647,1) (3.970,0.647,1) (3.970,0.647,1) (3.970,0.647,1) (3.970,0.647,1) (3.970,0.575,1) (3.970,0.575,1) (6.960,0.464,1) (6.960,0.464,1) (6.960,0.464,1) (6.960,0.464,1) (6.960,0.464,1) (6.410,0.447,1) (6.410,0.447,1) (6.410,0.447,1) (6.410,0.447,1) (6.410,0.447,1) (3.330,0.443,1) (3.330,0.443,1) (3.330,0.443,1) (3.330,0.443,1) (1.210,0.401,1) (2.970,0.400,1) (2.250,0.389,1) (1.760,0.385,1) (5.320,0.405,1) (5.320,0.405,1) (5.320,0.405,1) (4.950,0.411,1) (4.950,0.411,1) (4.950,0.411,1) (13.920,0.437,1) (13.920,0.437,1) (13.920,0.437,1) (13.920,0.437,1) (13.920,0.437,1) (2.240,0.400,1) (2.240,0.400,1) (2.240,0.400,1) (6.090,0.433,1) (6.090,0.433,1) (6.090,0.433,1) (2.180,0.472,1) (2.180,0.472,1) (2.180,0.472,1) (2.180,0.472,1) (9.900,0.544,1) (9.900,0.544,1) (9.900,0.544,1) (9.900,0.544,1) (9.900,0.544,1) (9.900,0.544,1) (9.900,0.544,1) (9.900,0.544,1) (9.900,0.544,1) (9.900,0.544,1) (9.900,0.544,1) (9.900,0.544,1) (7.380,0.493,1) (7.380,0.493,1) (7.380,0.493,1) (7.380,0.493,1) (7.380,0.493,1) (7.380,0.493,1) (7.380,0.493,1) (7.380,0.493,1) (3.240,0.460,1) (3.240,0.460,1) (3.240,0.460,1) (6.060,0.438,1) (6.060,0.438,1) (5.190,0.515,1) (5.190,0.515,1) (5.190,0.515,1) (5.190,0.515,1) (5.190,0.515,1) (5.190,0.515,1) (5.190,0.515,1) (5.190,0.515,1) (1.520,0.442,1) (1.890,0.518,1) (3.780,0.484,1) (3.780,0.484,1) (4.390,0.442,1) (4.390,0.442,1) (4.150,0.429,1) (2.010,0.435,1) (1.250,0.429,1) (1.250,0.429,1) (1.690,0.411,1) (1.690,0.411,1) (2.020,0.410,1) (1.910,0.413,1) (1.910,0.413,1) (18.100,0.770,1) (18.100,0.770,1) (18.100,0.770,1) (18.100,0.770,1) (18.100,0.770,1) (18.100,0.770,1) (18.100,0.770,1) (18.100,0.770,1) (18.100,0.718,1) (18.100,0.718,1) (18.100,0.718,1) (18.100,0.631,1) (18.100,0.631,1) (18.100,0.631,1) (18.100,0.631,1) (18.100,0.631,1) (18.100,0.668,1) (18.100,0.668,1) (18.100,0.668,1) (18.100,0.671,1) (18.100,0.671,1) (18.100,0.671,1) (18.100,0.671,1) (18.100,0.671,1) (18.100,0.671,1) (18.100,0.671,1) (18.100,0.700,1) (18.100,0.700,1) (18.100,0.700,1) (18.100,0.700,1) (18.100,0.700,1) (18.100,0.700,1) (18.100,0.700,1) (18.100,0.700,1) (18.100,0.700,1) (18.100,0.700,1) (18.100,0.700,1) (18.100,0.693,1) (18.100,0.693,1) (18.100,0.693,1) (18.100,0.693,1) (18.100,0.693,1) (18.100,0.693,1) (18.100,0.693,1) (18.100,0.693,1) (18.100,0.693,1) (18.100,0.693,1) (18.100,0.693,1) (18.100,0.693,1) (18.100,0.693,1) (18.100,0.659,1) (18.100,0.659,1) (18.100,0.597,1) (18.100,0.597,1) (18.100,0.597,1) (18.100,0.597,1) (18.100,0.597,1) (18.100,0.597,1) (18.100,0.693,1) (18.100,0.679,1) (18.100,0.679,1) (18.100,0.679,1) (18.100,0.679,1) (18.100,0.718,1) (18.100,0.718,1) (18.100,0.718,1) (18.100,0.614,1) (18.100,0.614,1) (18.100,0.584,1) (18.100,0.679,1) (18.100,0.584,1) (18.100,0.679,1) (18.100,0.679,1) (18.100,0.679,1) (18.100,0.584,1) (18.100,0.584,1) (18.100,0.584,1) (18.100,0.713,1) (18.100,0.713,1) (18.100,0.740,1) (18.100,0.740,1) (18.100,0.740,1) (18.100,0.740,1) (18.100,0.740,1) (18.100,0.740,1) (18.100,0.740,1) (18.100,0.740,1) (18.100,0.740,1) (18.100,0.740,1) (18.100,0.740,1) (18.100,0.740,1) (18.100,0.740,1) (18.100,0.713,1) (18.100,0.713,1) (18.100,0.713,1) (18.100,0.713,1) (18.100,0.713,1) (18.100,0.713,1) (18.100,0.713,1) (18.100,0.713,1) (18.100,0.713,1) (18.100,0.713,1) (18.100,0.713,1) (18.100,0.713,1) (18.100,0.713,1) (18.100,0.713,1) (18.100,0.713,1) (18.100,0.713,1) (18.100,0.655,1) (18.100,0.655,1) (18.100,0.655,1) (18.100,0.584,1) (18.100,0.580,1) (18.100,0.580,1) (18.100,0.580,1) (18.100,0.532,1) (18.100,0.580,1) (18.100,0.614,1) (18.100,0.584,1) (18.100,0.584,1) (18.100,0.614,1) (18.100,0.614,1) (18.100,0.614,1) (18.100,0.614,1) (18.100,0.532,1) (18.100,0.532,1) (18.100,0.532,1) (18.100,0.532,1) (18.100,0.583,1) (18.100,0.583,1) (18.100,0.583,1) (18.100,0.583,1) (27.740,0.609,1) (27.740,0.609,1) (27.740,0.609,1) (27.740,0.609,1) (27.740,0.609,1) (9.690,0.585,1) (9.690,0.585,1) (9.690,0.585,1) (9.690,0.585,1) (9.690,0.585,1) (9.690,0.585,1) (9.690,0.585,1) (9.690,0.585,1) (11.930,0.573,1) (11.930,0.573,1) (11.930,0.573,1) (11.930,0.573,1) (11.930,0.573,1) };

### 2015-11-17 graph_housing_exp1_distr_8_5.tex
Modify plots

@@
 			zmin=0.0, zmax=1.0,
-			xlabel=H,
-			ylabel=E,
+			xlabel=$H$,
+			ylabel=$E$,
 			colorbar,
@@
 
-			\addplot3[mark=+, draw=none, mark size=0.7, jitter = 0.3] coordinates {
+			\addplot3[mark=+, draw=none, mark size=1.0, jitter = 0.1] coordinates {
 (4.090,0.538,1) (4.967,0.469,1) (4.967,0.469,1) (6.062,0.458,1) (6.062,0.458,1) (6.062,0.458,1) (5.561,0.524,1) (5.950,0.524,1) (6.082,0.524,1) (6.592,0.524,1) (6.347,0.524,1) (6.227,0.524,1) (5.451,0.524,1) (4.707,0.538,1) (4.462,0.538,1) (4.499,0.538,1) (4.499,0.538,1) (4.258,0.538,1) (3.796,0.538,1) (3.796,0.538,1) (3.798,0.538,1) (4.012,0.538,1) (3.977,0.538,1) (4.095,0.538,1) (4.400,0.538,1) (4.455,0.538,1) (4.682,0.538,1) (4.453,0.538,1) (4.455,0.538,1) (4.239,0.538,1) (4.233,0.538,1) (4.175,0.538,1) (3.990,0.538,1) (3.787,0.538,1) (3.760,0.538,1) (3.360,0.499,1) (3.378,0.499,1) (3.934,0.499,1) (3.847,0.499,1) (5.401,0.428,1) (5.401,0.428,1) (5.721,0.448,1) (5.721,0.448,1) (5.721,0.448,1) (5.721,0.448,1) (5.100,0.448,1) (5.100,0.448,1) (5.689,0.448,1) (5.870,0.448,1) (6.088,0.448,1) (6.815,0.439,1) (6.815,0.439,1) (6.815,0.439,1) (6.815,0.439,1) (7.320,0.410,1) (8.697,0.403,1) (9.188,0.410,1) (8.325,0.411,1) (7.815,0.453,1) (6.932,0.453,1) (7.225,0.453,1) (6.819,0.453,1) (7.226,0.453,1) (7.981,0.453,1) (9.223,0.416,1) (6.612,0.398,1) (6.612,0.398,1) (6.498,0.409,1) (6.498,0.409,1) (6.498,0.409,1) (5.287,0.413,1) (5.287,0.413,1) (5.287,0.413,1) (5.287,0.413,1) (4.252,0.437,1) (4.503,0.437,1) (4.052,0.437,1) (4.090,0.437,1) (5.014,0.437,1) (4.503,0.437,1) (5.401,0.426,1) (5.401,0.426,1) (5.401,0.426,1) (5.401,0.426,1) (4.779,0.449,1) (4.438,0.449,1) (4.427,0.449,1) (3.748,0.449,1) (3.422,0.489,1) (3.414,0.489,1) (3.092,0.489,1) (3.092,0.489,1) (3.666,0.464,1) (3.666,0.464,1) (3.615,0.464,1) (3.495,0.445,1) (3.495,0.445,1) (3.495,0.445,1) (3.495,0.445,1) (3.495,0.445,1) (2.778,0.520,1) (2.856,0.520,1) (2.715,0.520,1) (2.715,0.520,1) (2.421,0.520,1) (2.107,0.520,1) (2.211,0.520,1) (2.122,0.520,1) (2.433,0.520,1) (2.545,0.520,1) (2.778,0.520,1) (2.678,0.547,1) (2.353,0.547,1) (2.548,0.547,1) (2.256,0.547,1) (2.463,0.547,1) (2.730,0.547,1) (2.747,0.547,1) (2.478,0.547,1) (2.759,0.547,1) (2.258,0.581,1) (2.197,0.581,1) (2.087,0.581,1) (1.944,0.581,1) (2.006,0.581,1) (1.993,0.581,1) (1.757,0.581,1) (1.788,0.624,1) (1.813,0.624,1) (1.980,0.624,1) (2.119,0.624,1) (2.271,0.624,1) (2.327,0.624,1) (2.470,0.624,1) (2.346,0.624,1) (2.111,0.624,1) (1.967,0.624,1) (1.850,0.624,1) (1.669,0.624,1) (1.669,0.624,1) (1.612,0.624,1) (1.439,0.624,1) (1.322,0.871,1) (1.412,0.871,1) (1.346,0.871,1) (1.419,0.871,1) (1.517,0.871,1) (1.461,0.871,1) (1.530,0.871,1) (1.526,0.871,1) (1.618,0.871,1) (1.592,0.871,1) (1.610,0.871,1) (1.623,0.871,1) (1.749,0.871,1) (1.746,0.871,1) (1.736,0.871,1) (1.877,0.605,1) (1.757,0.605,1) (1.766,0.871,1) (1.798,0.605,1) (1.971,0.605,1) (2.041,0.605,1) (2.162,0.605,1) (2.422,0.605,1) (2.283,0.605,1) (2.046,0.605,1) (2.426,0.605,1) (2.100,0.605,1) (2.263,0.605,1) (2.426,0.605,1) (2.389,0.605,1) (2.596,0.510,1) (2.646,0.510,1) (2.702,0.510,1) (3.132,0.510,1) (3.555,0.510,1) (3.317,0.510,1) (2.915,0.510,1) (2.829,0.488,1) (2.741,0.488,1) (2.598,0.488,1) (2.701,0.488,1) (2.847,0.488,1) (2.988,0.488,1) (3.280,0.488,1) (3.199,0.488,1) (3.789,0.437,1) (4.567,0.437,1) (4.567,0.437,1) (6.480,0.437,1) (6.480,0.437,1) (6.480,0.437,1) (6.220,0.401,1) (6.220,0.401,1) (5.648,0.422,1) (7.309,0.404,1) (7.309,0.404,1) (7.309,0.404,1) (7.653,0.403,1) (7.653,0.403,1) (6.270,0.415,1) (6.270,0.415,1) (5.118,0.416,1) (5.118,0.416,1) (3.945,0.489,1) (4.355,0.489,1) (4.355,0.489,1) (4.239,0.489,1) (3.875,0.489,1) (3.877,0.489,1) (3.665,0.489,1) (3.653,0.489,1) (3.945,0.489,1) (3.587,0.489,1) (3.945,0.489,1) (3.112,0.550,1) (3.421,0.550,1) (2.889,0.550,1) (3.363,0.550,1) (2.862,0.507,1) (3.048,0.507,1) (3.272,0.507,1) (3.272,0.507,1) (2.894,0.504,1) (2.894,0.504,1) (3.216,0.504,1) (3.216,0.504,1) (3.375,0.504,1) (3.375,0.504,1) (3.671,0.504,1) (3.671,0.504,1) (3.838,0.507,1) (3.652,0.507,1) (3.652,0.507,1) (3.652,0.507,1) (4.148,0.507,1) (4.148,0.507,1) (6.190,0.428,1) (6.190,0.428,1) (6.336,0.428,1) (6.336,0.428,1) (7.035,0.428,1) (7.035,0.428,1) (7.955,0.431,1) (7.955,0.431,1) (8.056,0.431,1) (8.056,0.431,1) (7.827,0.431,1) (7.827,0.431,1) (7.397,0.431,1) (7.397,0.431,1) (8.907,0.431,1) (8.907,0.431,1) (9.220,0.392,1) (9.220,0.392,1) (6.336,0.394,1) (1.801,0.647,1) (1.895,0.647,1) (2.011,0.647,1) (2.112,0.647,1) (2.140,0.647,1) (2.288,0.647,1) (2.079,0.647,1) (1.930,0.647,1) (1.986,0.647,1) (2.133,0.647,1) (2.422,0.575,1) (2.872,0.575,1) (3.917,0.464,1) (4.429,0.464,1) (4.429,0.464,1) (3.917,0.464,1) (4.367,0.464,1) (4.078,0.447,1) (4.267,0.447,1) (4.787,0.447,1) (4.863,0.447,1) (4.140,0.447,1) (4.101,0.443,1) (4.695,0.443,1) (5.245,0.443,1) (5.212,0.443,1) (5.885,0.401,1) (7.307,0.400,1) (7.307,0.389,1) (9.089,0.385,1) (7.317,0.405,1) (7.317,0.405,1) (7.317,0.405,1) (5.117,0.411,1) (5.117,0.411,1) (5.117,0.411,1) (5.503,0.437,1) (5.503,0.437,1) (5.960,0.437,1) (5.960,0.437,1) (6.320,0.437,1) (7.828,0.400,1) (7.828,0.400,1) (7.828,0.400,1) (5.492,0.433,1) (5.492,0.433,1) (5.492,0.433,1) (4.022,0.472,1) (3.370,0.472,1) (3.099,0.472,1) (3.183,0.472,1) (3.317,0.544,1) (3.103,0.544,1) (2.519,0.544,1) (2.640,0.544,1) (2.834,0.544,1) (3.263,0.544,1) (3.602,0.544,1) (3.945,0.544,1) (3.999,0.544,1) (4.032,0.544,1) (3.533,0.544,1) (4.002,0.544,1) (4.540,0.493,1) (4.540,0.493,1) (4.721,0.493,1) (4.721,0.493,1) (4.721,0.493,1) (5.416,0.493,1) (5.416,0.493,1) (5.416,0.493,1) (5.215,0.460,1) (5.215,0.460,1) (5.874,0.460,1) (6.641,0.438,1) (6.641,0.438,1) (6.458,0.515,1) (6.458,0.515,1) (5.985,0.515,1) (5.231,0.515,1) (5.615,0.515,1) (4.812,0.515,1) (4.812,0.515,1) (4.812,0.515,1) (7.038,0.442,1) (6.267,0.518,1) (5.732,0.484,1) (6.465,0.484,1) (8.014,0.442,1) (8.014,0.442,1) (8.535,0.429,1) (8.344,0.435,1) (8.792,0.429,1) (8.792,0.429,1) (10.710,0.411,1) (10.710,0.411,1) (12.127,0.410,1) (10.586,0.413,1) (10.586,0.413,1) (2.122,0.770,1) (2.505,0.770,1) (2.723,0.770,1) (2.509,0.770,1) (2.518,0.770,1) (2.296,0.770,1) (2.104,0.770,1) (1.905,0.770,1) (1.905,0.718,1) (1.613,0.718,1) (1.752,0.718,1) (1.511,0.631,1) (1.333,0.631,1) (1.357,0.631,1) (1.202,0.631,1) (1.169,0.631,1) (1.130,0.668,1) (1.174,0.668,1) (1.137,0.668,1) (1.316,0.671,1) (1.345,0.671,1) (1.358,0.671,1) (1.386,0.671,1) (1.386,0.671,1) (1.417,0.671,1) (1.519,0.671,1) (1.580,0.700,1) (1.533,0.700,1) (1.440,0.700,1) (1.426,0.700,1) (1.467,0.700,1) (1.518,0.700,1) (1.589,0.700,1) (1.728,0.700,1) (1.927,0.700,1) (2.168,0.700,1) (1.770,0.700,1) (1.791,0.693,1) (1.782,0.693,1) (1.726,0.693,1) (1.677,0.693,1) (1.633,0.693,1) (1.490,0.693,1) (1.500,0.693,1) (1.589,0.693,1) (1.574,0.693,1) (1.639,0.693,1) (1.703,0.693,1) (1.607,0.693,1) (1.425,0.693,1) (1.178,0.659,1) (1.285,0.659,1) (1.455,0.597,1) (1.466,0.597,1) (1.413,0.597,1) (1.528,0.597,1) (1.554,0.597,1) (1.589,0.597,1) (1.658,0.693,1) (1.835,0.679,1) (1.819,0.679,1) (1.647,0.679,1) (1.803,0.679,1) (1.794,0.718,1) (1.859,0.718,1) (1.875,0.718,1) (1.951,0.614,1) (2.022,0.614,1) (2.063,0.584,1) (1.910,0.679,1) (1.998,0.584,1) (1.863,0.679,1) (1.936,0.679,1) (1.968,0.679,1) (2.053,0.584,1) (2.088,0.584,1) (2.200,0.584,1) (2.316,0.713,1) (2.222,0.713,1) (2.125,0.740,1) (2.003,0.740,1) (1.914,0.740,1) (1.821,0.740,1) (1.817,0.740,1) (1.866,0.740,1) (2.065,0.740,1) (2.005,0.740,1) (1.978,0.740,1) (1.896,0.740,1) (1.988,0.740,1) (2.072,0.740,1) (2.198,0.740,1) (2.262,0.713,1) (2.185,0.713,1) (2.324,0.713,1) (2.355,0.713,1) (2.368,0.713,1) (2.453,0.713,1) (2.496,0.713,1) (2.436,0.713,1) (2.581,0.713,1) (2.779,0.713,1) (2.783,0.713,1) (2.717,0.713,1) (2.598,0.713,1) (2.567,0.713,1) (2.734,0.713,1) (2.802,0.713,1) (2.963,0.655,1) (3.067,0.655,1) (2.872,0.655,1) (2.540,0.584,1) (2.908,0.580,1) (2.824,0.580,1) (3.033,0.580,1) (3.099,0.532,1) (2.897,0.580,1) (2.533,0.614,1) (2.430,0.584,1) (2.206,0.584,1) (2.305,0.614,1) (2.101,0.614,1) (2.171,0.614,1) (1.951,0.614,1) (3.424,0.532,1) (3.332,0.532,1) (3.411,0.532,1) (4.098,0.532,1) (3.724,0.583,1) (3.992,0.583,1) (3.546,0.583,1) (3.152,0.583,1) (1.821,0.609,1) (1.755,0.609,1) (1.823,0.609,1) (1.868,0.609,1) (2.110,0.609,1) (2.382,0.585,1) (2.382,0.585,1) (2.799,0.585,1) (2.799,0.585,1) (2.893,0.585,1) (2.409,0.585,1) (2.400,0.585,1) (2.498,0.585,1) (2.479,0.573,1) (2.288,0.573,1) (2.167,0.573,1) (2.389,0.573,1) (2.505,0.573,1) };

### 2015-11-17 graph_housing_exp2_distr_3_5.tex
Modify plots

@@
 			zmin=0.0, zmax=1.0,
-			xlabel=C,
-			ylabel=E,
+			xlabel=$C$,
+			ylabel=$E$,
 			colorbar,

### 2015-11-17 graph_wine_exp1_distr.tex
Modify plots

--- 2015-11-17 graph_wine_exp1_distr.tex
@@
 \begin{tikzpicture}
-  \begin{groupplot}[group style={group size=1 by 2}]%,xmin=0,ymin=0,height=4cm,width=5cm,no markers]
+  \begin{groupplot}[
+	  	group style={group size=2 by 1,horizontal sep=1cm,
+  		}, 
+  		width = 1/2*\textwidth - 1cm,
+  		height = 6 cm ]%,xmin=0,ymin=0,height=4cm,width=5cm,no markers]
   \nextgroupplot[
@@
 			zmin=0.0, zmax=1.0,
-			ylabel=K,
-			colorbar right,
-    every colorbar/.append style={height=
-        2*\pgfkeysvalueof{/pgfplots/parent axis height}+
-        \pgfkeysvalueof{/pgfplots/group/vertical sep}},
+			ylabel=$K$,
+			xlabel=$E$,
+			%colorbar,
+    %every colorbar/.append style={height=
+    %    2*\pgfkeysvalueof{/pgfplots/parent axis height}+
+     %   \pgfkeysvalueof{/pgfplots/group/vertical sep}},
 		    point meta min=0, point meta max=0.5,
-			colormap={}{ gray(0cm)=(1); gray(1cm)=(0);},
-			colorbar style={
-			        ytick={0,0.05,...,0.5},
-			        yticklabel style={
-			            text width=2.5em,
-			            align=right,
-			            /pgf/number format/.cd,
-			                fixed,
-			                fixed zerofill
-			        }
-			    }
+			colormap={}{ gray(0cm)=(1); gray(1cm)=(0);}
+			%colorbar style={
+			%        ytick={0,0.05,...,0.51},
+			%        yticklabel style={
+			%            text width=2.5em,
+			%            align=right,
+			%            /pgf/number format/.cd,
+			%                fixed,
+			%                fixed zerofill
+			%        }
+			%    }
 			]
@@
 
-			\addplot3[mark=+, draw=none, mark size=0.7] coordinates {
+			\addplot3[mark=+, draw=none, mark size=1.0] coordinates {
 (15.600,5.640,1) (11.200,4.380,1) (18.600,5.680,1) (16.800,7.800,1) (21.000,4.320,1) (15.200,6.750,1) (14.600,5.250,1) (17.600,5.050,1) (14.000,5.200,1) (16.000,7.220,1) (18.000,5.750,1) (16.800,5.000,1) (16.000,5.600,1) (11.400,5.400,1) (12.000,7.500,1) (17.200,7.300,1) (20.000,6.200,1) (20.000,6.600,1) (16.500,8.700,1) (15.200,5.100,1) (16.000,5.650,1) (18.600,4.500,1) (16.600,3.800,1) (17.800,3.930,1) (20.000,3.520,1) (25.000,3.580,1) (16.100,4.800,1) (17.000,3.950,1) (19.400,4.500,1) (16.000,4.700,1) (22.500,5.700,1) (19.100,6.900,1) (17.200,3.840,1) (19.500,5.400,1) (19.000,4.200,1) (20.500,5.100,1) (15.500,4.600,1) (18.000,4.250,1) (15.500,3.700,1) (13.200,5.100,1) (16.200,6.130,1) (18.800,4.280,1) (15.000,5.430,1) (17.500,4.360,1) (17.000,5.040,1) (18.900,5.240,1) (16.000,4.900,1) (16.000,6.100,1) (18.800,6.200,1) (17.400,8.900,1) (12.400,7.200,1) (17.200,5.600,1) (14.000,7.050,1) (17.100,6.300,1) (16.400,5.850,1) (20.500,6.250,1) (16.300,6.380,1) (16.800,6.000,1) (16.700,6.800,1) (10.600,1.950,1) (16.000,3.270,1) (16.800,5.750,1) (18.000,3.800,1) (19.000,4.450,1) (19.000,2.950,1) (18.100,4.600,1) (15.000,5.300,1) (19.600,4.680,1) (17.000,3.170,1) (16.800,2.850,1) (20.400,3.050,1) (25.000,3.380,1) (24.000,3.740,1) (30.000,3.350,1) (21.000,3.210,1) (16.000,3.800,1) (16.000,4.600,1) (18.000,2.650,1) (14.800,3.400,1) (23.000,2.570,1) (19.000,2.500,1) (18.800,3.900,1) (24.000,2.200,1) (22.500,4.800,1) (18.000,3.050,1) (18.000,2.620,1) (22.800,2.450,1) (26.000,2.600,1) (21.600,2.800,1) (23.600,1.740,1) (18.500,2.400,1) (22.000,3.600,1) (20.700,3.050,1) (18.000,2.150,1) (18.000,3.250,1) (19.000,2.600,1) (21.500,2.500,1) (16.000,2.900,1) (18.500,4.500,1) (18.000,2.300,1) (17.500,3.300,1) (18.500,2.450,1) (21.000,2.800,1) (19.500,2.060,1) (20.500,2.940,1) (22.000,2.700,1) (19.000,3.400,1) (22.500,3.300,1) (19.000,2.700,1) (20.000,2.650,1) (19.500,2.900,1) (21.000,2.000,1) (20.000,3.800,1) (21.000,3.080,1) (22.500,2.900,1) (21.500,1.900,1) (20.800,1.950,1) (22.500,2.060,1) (16.000,3.400,1) (19.000,1.280,1) (20.000,3.250,1) (28.500,6.000,1) (26.500,2.080,1) (21.500,2.600,1) (21.000,2.800,1) (21.000,2.760,1) (21.500,3.940,1) (28.500,3.000,1) (24.500,2.120,1) (22.000,2.600,1) (18.000,4.100,1) (20.000,5.400,1) (24.000,5.700,1) (21.500,5.000,1) (17.500,5.450,1) (18.500,7.100,1) (21.000,3.850,1) (25.000,5.000,1) (19.500,5.700,1) (24.000,4.920,1) (21.000,4.600,1) (20.000,5.600,1) (23.500,4.350,1) (20.000,4.400,1) (18.500,8.210,1) (21.000,4.000,1) (20.000,4.900,1) (21.500,7.650,1) (21.500,8.420,1) (21.500,9.400,1) (24.000,8.600,1) (22.000,10.800,1) (25.500,7.100,1) (18.500,10.520,1) (20.000,7.600,1) (22.000,7.900,1) (19.500,9.010,1) (27.000,7.500,1) (25.000,13.000,1) (22.500,11.750,1) (21.000,7.650,1) (20.000,5.880,1) (22.000,5.580,1) (18.500,5.280,1) (22.000,9.580,1) (22.500,6.620,1) (23.000,10.680,1) (19.500,10.260,1) (24.500,8.660,1) (25.000,8.500,1) (19.000,5.500,1) (19.500,9.900,1) (20.000,9.700,1) (20.500,7.700,1) (23.000,7.300,1) (20.000,10.200,1) (20.000,9.300,1) (24.500,9.200,1) };
@@
 			zmin=0.0, zmax=1.0,
-			xlabel=E,
-			ylabel=K,
-			%colorbar,
+			xlabel=$E$,
+			%ylabel=K,
+			colorbar,
 			point meta min=0, point meta max=0.5,
-			colormap={}{ gray(0cm)=(1); gray(1cm)=(0);}
-			%colorbar style={
-			 %       ytick={0,0.05,...,0.5},
-			  %      yticklabel style={
-			   %         text width=2.5em,
-			    %        align=right,
-			     %       /pgf/number format/.cd,
-			      %          fixed,
-			       %         fixed zerofill
-			        %}
-			    %}
+			colormap={}{ gray(0cm)=(1); gray(1cm)=(0);},
+			colorbar style={
+			        ytick={0,0.05,...,0.51},
+			        yticklabel style={
+			            text width=1.5em,
+			            align=right,
+			           /pgf/number format/.cd,
+			                fixed,
+			                fixed zerofill
+			        }
+			    }
 			]

### 2015-11-17 graph_wine_exp2_distr_5_11.tex
Modify plots

@@
 			zmin=0.0, zmax=1.0,
-			xlabel=E,
-			ylabel=K,
+			xlabel=$E$,
+			ylabel=$K$,
 			colorbar,

### 2015-11-18 BN_discretizer_paper.tex
Update experiment section

@@
 
-Figure \ref{fig:auto_exp2_distr_1_3} compares the edges of the learned network in Figure \ref{fig:auto_graph_2} with the raw data on variables $A$ and $C$.
+Figure \ref{fig:auto_exp2_distr_1_3} compares the discretization edges of variable $A$ and $C$ in the learned network in Figure \ref{fig:auto_graph_2} with the raw data.
 Again, the black dots are raw data points.
-Although the numbers of discretization edges of $A$ and $C$ shown in Figure \ref{fig:auto_graph_2} are less than Table \ref{table:auto_disc_table_1}, they still have a good capture of raw data distribution.
+Although the numbers of discretization edges of $A$ and $C$ shown in Figure \ref{fig:auto_exp2_distr_1_3} are less than Figure \ref{fig:auto_exp2_distr_1_3}, they still have a good capture of raw data distribution.
+This indicated that although the discretization result of the optimal Bayesian approach might vary according to the network structure, it still preserves the quality of discretization.
 
@@
       \input{graph_auto_exp2_distr_1_3}
-  \caption{Comparison of the raw data and discretization result on variable $A$ and $C$ of the learned network in Figure \ref{fig:auto_graph_2}}.
+  \caption{Comparison of the raw data and discretization result on variable $A$ and $C$ of the learned network in Figure \ref{fig:auto_graph_2}.
+Although the number of discretization edges is less than in Figure \ref{fig:auto_exp1_distr_1_3}, it still matches the raw data distribution very well.}
   \label{fig:auto_exp2_distr_1_3}
@@
 This dataset has 178 instances and 14 variables.
-Only variable $A$ is discrete-valued with cardinality number 3.
-Again, in the first experiment, the network structure is given.
-In the second experiment, the network structure is not provided.
+Only variable $A$ is discrete-valued with cardinality number \num{3}.
+Again, in the first experiment, the network structure is given in advance.
+In the second experiment, the network structure is not provided in advance.
 
@@
 
-The Bayesian network in Figure \ref{fig:wine_graph_1} is obtained by equal-width discretizing each continuous variable into 3 intervals and running K2 1000 times.
-Table \ref{table:wine_disc_table_1} shows a comparison between the proposed method and the MDL principle discretization method.
-The proposed method is still better than MDL principle discretization in terms of likelihood, although the latter returns non-trivial result in this experiment.
-\todo{Note that the proposed method with the approximation has more intervals after discretization, and it has a slightly better result in terms of likelihood.
-However, the improvement is marginally small, which indicates that the proposed method without the approximation captures good enough discretization result even if the numbers of intervals after discretization are smaller.}
-In addition, as shown in next dataset, the approximation might cut continuous variables into too many intervals.
-Therefore, the proposed method without the approximation should be still considered a better approach.
+The Bayesian network in Figure \ref{fig:wine_graph_1} is obtained by equal-width discretizing each continuous variable into 3 intervals and running K2 a thousand times.
+Table \ref{table:wine_disc_table_1} shows a comparison between the optimal Bayesian approach and the MDL principle discretization method.
+The discretization result obtained by the optimal Bayesian approach is better than the MDL discretization method in terms of likelihood, although the latter returns non-trivial result in this experiment.
+Note that the
+heuristic method discretizes variable $G$, $H$ and $J$ into one more interval than the optimal Bayesian approach, and has less number of intervals on variable $M$.
+Although the heuristic method has more intervals after discretization on all variables, it does not lead to a higher likelihood result.
+This can be interpreted as that the extra discretization edges on $G$, $H$ and $J$ are less necessary and the losing discretization edge on $M$ is important.
+In addition, as shown in next dataset, the heuristic method might cut continuous variables into too many intervals.
+Therefore, the optimal Bayesian approach should be considered a better method if the running time is not a concern.
 

### 2015-11-18 BN_discretizer_paper.tex
Update experiment section

@@
   \centering
-  \input{table_autoMPG_1.tex}
   \caption{Discretization result of Auto MPG dataset based on the graph in Fig.
@@
 The discretization policy for the heuristic matches that for the optimal Bayesian approach.
-The MDL method is less sensitive to distribution of values of other variables, thus it fails to return discretization edges.
+The MDL method is less sensitive to distribution of values of other variables, thus it fails to return discretization edges.}
+  \input{table_autoMPG_1.tex}
   \label{table:auto_disc_table_1}
@@
 %\begin{minipage}{0.50\textwidth}
-%  \centering
-%  \scalebox{0.7}{
-%  \input{graph_autocar_2}}
-%  \captionof{figure}{The learned discrete-\newline valued Bayesian network}
-%  \label{fig:auto_graph_2}
+  %\centering
+  %\scalebox{0.7}{
+  %\input{graph_autocar_2}}
+  %\captionof{figure}{The learned discrete-\newline valued Bayesian network}
+  %\label{fig:auto_graph_2}
 %\end{minipage}
 %\begin{minipage}{0.50\textwidth}
-%  \raggedleft
-%  \input{table_autoMPG_2.tex}
-%  \captionof{table}{The discretization edges of variables in Fig \ref{Auto_graph_2}}
+  %\raggedleft
+  %\input{table_autoMPG_2.tex}
+  %\captionof{table}{The discretization edges of variables in Fig \ref{Auto_graph_2}}
  % \label{Auto_MPG_disc_table_2}
@@
 This can be interpreted as that the extra discretization edges on $G$, $H$ and $J$ are less necessary and the losing discretization edge on $M$ is important.
-In addition, as shown in next dataset, the heuristic method might cut continuous variables into too many intervals.
-Therefore, the optimal Bayesian approach should be considered a better method if the running time is not a concern.
+On the other hand, if running time is a concern, then the heuristic method can be considered a better approach in this case, since its discretization result is nearly as good as the result of the optimal Bayesian approach.
+
+Notice that there are some discretization edges shown in all three discretization methods, such as \num{1.42} and \num{2.35} on variable $C$ and \num{0.785} on variable $L$.
+This indicates that MDL indeed can find some important discretization edges, but it is not sensitive enough to find other edges.
 
@@
   }
-  \caption{Discretization result of Wine dataset based on the graph Fig. \ref{fig:wine_graph_1}
+  \caption{Discretization result of Wine dataset based on the graph Fig.
+\ref{fig:wine_graph_1}.
+The optimal Bayesian approach has the best discretization result in terms of likelihood.
+The heuristic method obtains a result nearly as good as the Bayesian approach.
+The MDL method discretizes more than half of continuous variables but still does not discretize enough intervals.
+Some discretization edges are obtained by all three methods.
   \todo{MDL has bins, heuristic is slightly worse in logl but still good. MDL keeps all of its CPDs small, no neighboring vars both have more than 1 interval.}
@@
 
-\begin{figure}[ht]
-  \centering
-    \input{graph_wine_exp1_distr}
-  \caption{Comparison of the discretization results on variable $A$ and $C$ obtained by the proposed method and the MDL method}
-  \label{fig:wine_exp1_distr}
-\end{figure}
+%\begin{figure}[ht]
+%  \centering
+%    \input{graph_wine_exp1_distr}
+%  \caption{Comparison of the discretization results on variable $A$ and $C$ obtained by the proposed method and the MDL method}
+%  \label{fig:wine_exp1_distr}
+%\end{figure}
 
@@
   \centering
-  \begin{tabular}{cc}
-  \centering
   \scalebox{0.7}{
     \input{graph_wine_2}}
-  \end{tabular}
   \caption{The learned discrete-valued Bayesian network from the Wine dataset \todo{using optimal Bayesian method}}
@@
   \centering
-  % \begin{tabular}{cc}
+  \begin{tabular}{cc}
    \input{graph_housing_1}
-  % \end{tabular}
+   \end{tabular}
   \caption{\todo{Structure from prediscretized K2 structure learning to compare the methods for Housing dataset}}
@@
 \begin{figure}[ht]
-    % \begin{tabular}{cc}
+     %\begin{tabular}{cc}
     \input{graph_housing_exp1_distr_8_5}
-    % \end{tabular}
+     %\end{tabular}
   \caption{The discretization result on variable $H$ and $E$ of the network in Figure~\ref{fig:housing_graph_1}}
@@
 \begin{figure}[ht]
-    % \begin{tabular}{cc}
+     %\begin{tabular}{cc}
       \input{graph_housing_exp2_distr_3_5}
-    % \end{tabular}
+     %\end{tabular}
   \caption{The discretization result on variable $C$ and $E$ of the network in Figure~\ref{fig:housing_graph_2}}

### 2015-11-18 BN_discretizer_paper.tex
moved around the intro sections and started adding notation. Finished BN and structure learning

@@
 
+\DeclareMathOperator{\Pa}{pa}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\begin{table}[H]
-  \centering
-  \begin{tabular}{@{}ccl@{}}
-    \toprule
-    Current & Mykel & Description \\
-    \midrule
-    $G$ & $G$ & BN graph structure \\
-    $P$ & $P$ & discrete probability \\
-    $p$ & $p$ & probability density \\
-    $D$ & $D$ & available data \\
-    $|D|$ & $n$ & number of variables in the BN \\
-    $D_{\bm{Y}}$ & & subset of data associated with $\bm{Y}$ \\
-    $X$ & $X_{1:n}$ & variables in BN (discrete) \\
-    $x_{1:n}$ & $x_{1:n}$ & a specific instance of vars in BN \\
-    $x'_{1:n}$ &  & unique instances of var in BN \\
-        & $r_i$ & number of instantiations of $i$th var \\
-    $J_p$ & $q_i$ & number of instantiations of parents of $i$th var \\
-        &       & $ = 1$ if no parents \\
-    $\brock{\Pi_{X_i}}_j$ & $\pi_{ij}$ & $j$th instantiation of $i$th var \\
-        & $\theta_{ijk}$ & probability of $i$th var $= k$ given $j$th parental inst. \\
-    $\Theta$ & $\bm{\theta}$ & set of all (non-independent) probability parameters \\
-    $n_{i,j}^{(k)}$ & $m_{ijk}$ & observation counts \\
-    $n_{i,j,l}^{(k)}$ & $m_{ijk}$ & observation counts with $l$th instance of spouse\\
-    $\alpha_{ijk}$ & $\alpha_{ijk}$ & Dirichlet prior counts \\
-    $N_{ij}$ & $\alpha_{ij0}$ & sum over Dirichlet prior counts for $k$ \\
-        & $m_{ij0}$ & sum over observations counts for $k$ \\
-        & $\Gamma$ & the Gamma function \\
-    $N$ &          & is the number of samples in dataset \\
-    $N_i$ &          & counts for $i$th instance of a specific var \\
-    $\Pi_X$ & $\text{pa}_{x_i}$ & parents of a variable or instance \\
-    $n_C$ & & number of children of a variable \\
-    $H(~)$ & & a function \\
-    $I(~,~)$ & & mutual information \\
-    $X_i$ & & $i$th variable in BN, may be cont or disc \\
-    $X_i^*$ & & discrete version of cont var \\
-    $E$ & & set of edges in BN \\
-    $\text{Pa}\paren{X_i}$, $n_p$ & & number of parents of $X_i$ \\
-    $f\paren{X_i, \Pi_{X_i}}$ & $f(G)$ & score function for K2 \\
-    $M_C$ & & discretization policy for $C$ \\
-    $C$ & & a continuous variable \\
-    $t_i$ & & the $i$th bin edge for a specific var \\
-    $d_i$ & & allowable discretization positions (between unique vals) \\
-    $k$ & & number of intervals for $M_C$ \\
-    $C_{1:N}$ & & sorted samples for $C$ \\
-    $n_i$ & & $n_1 = s_1$ and $n_i = s_{i} - s_{i-1}$ \\
-    $s_i$ & & $\sum_{j=1}^k n_j$ and $s_k = N$, $s_0 = 0$ \\
-    $C_i$ & & $i$th child of a specific var \\
-    $\boldsymbol{S_i}$ & & set of spouses associated with $i$th child of specific var \\
-    $L$ & & largest cardinality among discrete variables in BN \\
-    $I_q$ & & an interval from $u \rightarrow v$ \\
-    $v'_\text{max}$ & & largest cardinality of variables that directly connect to $X$ \\
-    $S[]$ & &  optimal objective value of subproblems with instances from $1$ to $u$ \\
-    \bottomrule
-  \end{tabular}
-\end{table}
+% \begin{table}[H]
+%   \centering
+%   \begin{tabular}{@{}ccl@{}}
+%     \toprule
+%     Current & Mykel & Description \\
+%     \midrule
+%     $G$ & $G$ & BN graph structure \\
+%     $P$ & $P$ & discrete probability \\
+%     $p$ & $p$ & probability density \\
+%     $D$ & $D$ & available data \\
+%     $|D|$ & $n$ & number of variables in the BN \\
+%     $D_{\bm{Y}}$ & & subset of data associated with $\bm{Y}$ \\
+%     $X$ & $X_{1:n}$ & variables in BN (discrete) \\
+%     $x_{1:n}$ & $x_{1:n}$ & a specific instance of vars in BN \\
+%     $x'_{1:n}$ &  & unique instances of var in BN \\
+%         & $r_i$ & number of instantiations of $i$th var \\
+%     $J_p$ & $q_i$ & number of instantiations of parents of $i$th var \\
+%         &       & $ = 1$ if no parents \\
+%     $\brock{\Pi_{X_i}}_j$ & $\pi_{ij}$ & $j$th instantiation of $i$th var \\
+%         & $\theta_{ijk}$ & probability of $i$th var $= k$ given $j$th parental inst. \\
+%     $\Theta$ & $\bm{\theta}$ & set of all (non-independent) probability parameters \\
+%     $n_{i,j}^{(k)}$ & $m_{ijk}$ & observation counts \\
+%     $n_{i,j,l}^{(k)}$ & $m_{ijk}$ & observation counts with $l$th instance of spouse\\
+%     $\alpha_{ijk}$ & $\alpha_{ijk}$ & Dirichlet prior counts \\
+%     $N_{ij}$ & $\alpha_{ij0}$ & sum over Dirichlet prior counts for $k$ \\
+%         & $m_{ij0}$ & sum over observations counts for $k$ \\
+%         & $\Gamma$ & the Gamma function \\
+%     $N$ &          & is the number of samples in dataset \\
+%     $N_i$ &          & counts for $i$th instance of a specific var \\
+%     $\Pi_X$ & $\text{pa}_{x_i}$ & parents of a variable or instance \\
+%     $n_C$ & & number of children of a variable \\
+%     $H(~)$ & & a function \\
+%     $I(~,~)$ & & mutual information \\
+%     $X_i$ & & $i$th variable in BN, may be cont or disc \\
+%     $X_i^*$ & & discrete version of cont var \\
+%     $E$ & & set of edges in BN \\
+%     $\text{Pa}\paren{X_i}$, $n_p$ & & number of parents of $X_i$ \\
+%     $f\paren{X_i, \Pi_{X_i}}$ & $f(G)$ & score function for K2 \\
+%     $M_C$ & & discretization policy for $C$ \\
+%     $C$ & & a continuous variable \\
+%     $t_i$ & & the $i$th bin edge for a specific var \\
+%     $d_i$ & & allowable discretization positions (between unique vals) \\
+%     $k$ & & number of intervals for $M_C$ \\
+%     $C_{1:N}$ & & sorted samples for $C$ \\
+%     $n_i$ & & $n_1 = s_1$ and $n_i = s_{i} - s_{i-1}$ \\
+%     $s_i$ & & $\sum_{j=1}^k n_j$ and $s_k = N$, $s_0 = 0$ \\
+%     $C_i$ & & $i$th child of a specific var \\
+%     $\boldsymbol{S_i}$ & & set of spouses associated with $i$th child of specific var \\
+%     $L$ & & largest cardinality among discrete variables in BN \\
+%     $I_q$ & & an interval from $u \rightarrow v$ \\
+%     $v'_\text{max}$ & & largest cardinality of variables that directly connect to $X$ \\
+%     $S[]$ & &  optimal objective value of subproblems with instances from $1$ to $u$ \\
+%     \bottomrule
+%   \end{tabular}
+% \end{table}
 
@@
 
-There are two common approaches to extending Bayesian networks to continuous variables.
+There are three common approaches to extending Bayesian networks to continuous variables.
 The first is to model the conditional probability density of each continuous variable using specific families of parametric distributions, and then to redesign Bayesian network learning algorithms based on their parameters.
-One successful example is belief propagation in Gaussian graphical models \citep{Weiss_2011}.
+One successful example are Gaussian graphical models \citep{Weiss_2011}.
 For other parametric distributions and non-linear functions \citep{Ihler_2009}, these redesigned algorithms are computationally expensive and do not perform well.
-\mykel{$\bigstar$ We need to discuss this; talk about algorithms for inference and structure learning, expectation propagation, Gibbs, BVGS}
-
-The second approach is discretization.
+The second is to use nonparametric distributions, such as particle representations and Gaussian processes \todo{[cite]}.
+\todo{These have the advantage of BLAH BLAH, and their parameter set grows lineary with the amount of data.}
+
+The third approach is discretization.
 Automated discretization methods have been studied in machine learning and statistics for many years \citep{Dougherty_1995, Kerber_1992, Holte_1993, Fayyad_1993}, primarily for classification problems.
@@
 Prior work exists for discretizing continuous variables in naive Bayesian networks and tree-augmented networks \citep{Fried_naive}, but only a few discretization methods for general Bayesian networks have been proposed \citep{Friedman_1996, Kozlov_1997, Monti_1998, Steck_2007}.
+
+This work is primarily concerned with the minimum description length (MDL) principle discretization \citep{Friedman_1996} and MODL discretization \citep{Boulle_2006} methods.
+The former is the predominant discretization method for continuous variables in Bayesian networks, and is compared to our proposed Bayesian method in Section \ref{sec:experiments}.
+The latter is a Bayesian discretization method for one continuous variable against a discrete target class, which our proposed method generalizes to Bayesian networks.
+The asymptotical equivalence between MDL and MODL was examined in \citep{VL_2000}.
+
+The MDL principle was first proposed by \cite{MDL_1978} and states that the best model for a dataset is one that minimizes the amount of information needed to describe it \citep{Grunwald_2009}.
+MDL methods trade off goodness-of-fit against model complexity to reduce generalization error.
+In the context of Bayesian networks, \cite{Friedman_1996} applied the MDL principle to determine the optimal number of discretization intervals for continuous variables and the optimal positions of their discretization edges.
+Their approach selects a discretization policy that minimizes the sum of the description lengths of the discretized Bayesian network and the information necessary for recovering the continuous values from the discretized data.
+\todo{Results in this work suggest that the MDL method suffers from....}
+
+The optimal discretization policy is found with dynamic programming.
+For Bayesian networks with multiple continuous variables, MDL discretization is iteratively applied to each continuous variables.
+While iterating, only one variable is treated as continuous while all other continuous variables are treated as discretized based on an initial discretization policy or the discretization result from a previous iteration.
+
+The network structure is not always known in advance.
+Bayesian network structure learning can be extended to distributions including continuous variables by alternating between traditional discrete structure learning and optimal discretization.
+Starting with some preliminary discretization policy, one applys a structure learning algorithm to identify the locally optimal graph structure.
+The discretization policy is refined based on the learned network.
+The cycle is continued until convergence.
+
+MODL discretization \citep{Boulle_2006} is a Bayesian method for discretizing a continuous feature according to a class variable.
+Bayesian methods maximize the probability of the model given the data, $P(\textit{Model} \mid \textit{Data})$.
+An application of Bayes' rule and constant $P(\textit{Data})$ shows that this is equivalent to maximizing:
+
+\begin{align}
+P(\textit{Model}) \cdot P(\textit{Data} \mid \textit{Model})\text{,}
+\end{align}
+
+\noindent
+where $P(\textit{Model})$ is a prior over models and ${P(\textit{Data} \mid \textit{Model})}$ is the data likelihood.
+The data likelihood usually increases with the number of discretization intervals, as more intervals allow for richer representations.
+The prior is chosen to decrease as the number of discretization intervals increases to favor simpler models and prevent overfitting.
+Maximizing ${P(\textit{Model}) \cdot P(\textit{Data} \mid \textit{Model})}$ requires a trade-off when determining the number of discretization intervals.
+
+The MODL method uses dynamic programming to find the optimal discretization policy, and has an $\bigo\paren{N^3 + r \cdot N^2}$ runtime, where $N$ is the of number of data instances and $r$ is the number of instances for the class variable.
+\cite{Lustgarten_2011} suggest several formulations for the prior term $P(\text{Model})$.
+Under a uniform prior probability over discretizations the runtime can be reduced to $\bigo\paren{r \cdot N^2}$ without sacrificing optimality.
 
@@
 
-\section{Related Work}
-\label{sec:related_work}
-This section reviews the minimum description length (MDL) principle discretization \citep{Friedman_1996} and MODL discretization \citep{Boulle_2006} methods.
-The former is the predominant discretization method for continuous variables in Bayesian networks, and is compared to our proposed method in Section \ref{sec:experiments}.
-The latter is a discretization method for one continuous variable against a discrete target class, which our proposed method generalizes to Bayesian networks.
-The asymptotical equivalence between MDL and MODL was examined in \citep{VL_2000}.
-
-\subsection{MDL Principle Discretization}
-The MDL principle was first proposed by \cite{MDL_1978} and states that the best model for a dataset is one that minimizes the amount of information needed to describe it \citep{Grunwald_2009}.
-MDL methods trade off goodness-of-fit against model complexity to reduce generalization error.
-In the context of Bayesian networks, \cite{Friedman_1996} applied the MDL principle to determine the optimal number of discretization intervals for continuous variables and the optimal positions of their discretization boundaries.
-Their approach selects a discretization policy that minimizes the sum of the description lengths of the discretized Bayesian network and the information necessary for recovering the continuous values from the discretized data.
-For a Bayesian network with a single continuous variable $X$, the objective function is
-
-% \begin{small}
-\begin{equation}
-\begin{aligned}
-\frac{1}{2} \log(N) \left\lbrace  \lvert \Pi_{X_i} \rvert (\lvert X^*_i \rvert - 1) +
- {\sum_{j,X_i \in \Pi_{X_i}}} \lvert \Pi_{X^*_j} \rvert (\lvert X_j \rvert - 1) \right\rbrace + \log(\lvert {X^*_i} \rvert) \\
- + (N_i-1) H \left( {{|X^*_i| - 1}\over{N_i -1}}  \right) -N \cdot \left[ I(X^*_i,\Pi_{X_i}) + {\sum_{j,X_i \in \Pi_{X_i}}} I(X_j, \Pi_{X^*_j}) \right],
-\end{aligned}
-\end{equation}
-% \end{small}
-
-\mykel{$\bigstar\Pi_{X_i}$ is not defined until later}
-\tim{$\Pi_{X_i}$ may be confusing with our use of $\prod_{i=1}^n$ later on.}
-
-\noindent
-% $I(\boldsymbol{A},\boldsymbol{B}) =  \sum_{\boldsymbol{a},\boldsymbol{b}} \hat{P}_D (\boldsymbol{a},\boldsymbol{b}) \log {{\hat{P}_D (\boldsymbol{a},\boldsymbol{b})}\over{\hat{P}_D (\boldsymbol{a}),\hat{P}_D (\boldsymbol{b})}}$
-where $I(A,B)$ is the mutual information between the discrete variables $A$ and $B$, ${H(p) = -p \log(p) - (1-p) \log(1-p)}$ \tim{does $H(p)$ have a name?
-Entropy?}, $|A|$ is the cardinality of a discrete variable $A$, and $X^*_i$ is the discretized version of the $i$th sample of $X$.
-\tim{What are $N$, and $N_i$?}
-The optimal discretization policy can be found with dynamical programming.
-For Bayesian networks with multiple continuous variables, the algorithm is applied to one variable at a time iteratively over all continuous variables.
-While iterating, only one variable is treated as continuous and other continuous variables are discretized based on an initial discretization policy or the discretization result from a previous iteration.
-
-The network structure is not always known in advance.
-Bayesian network structure learning can be extended to distributions including continuous variables by alternating between traditional discrete structure learning and optimal discretization.
-Starting with some preliminary discretization policy, one applys a structure learning algorithm to identify the locally optimal graph structure.
-The discretization policy is refined based on the learned network.
-The cycle is continued until convergence.
-
-% The discretization technique proposed by \citet{Friedman_1996} is the most well-known of these methods.
-It is based on the minimum description length principle (MDL): the optimal discretization policy minimizes the description length of the Bayesian network and discretization policy.
-The MDL algorithm has an $\bigo\paren{N^3 + \paren{n_c {v_\text{max}}^{(n_c^p)_\text{max}} + {v_\text{max}}^{n_p}} \cdot N^2}$ runtime on Bayesian networks with a single continuous variable and multiple discrete variables, where $N$ is the number of data samples from the joint distribution, $n_p$ and $n_c$ are the numbers of parent and children variables for the continuous variable, $v_\text{max}$ is the largest cardinality over all variables in the Markov blanket, and  ${(n_c^p)_\text{max}}$ is the largest number of parent variables of the continuous variable's children.
-The MDL method iterates over all continuous variables until convergence in the case of multiple continuous variables, converging in a few cycles according to our tests of real-world data.
-Unfortunately, MDL tends to produce discrete variables with low cardinality~\todo{[cite]}
-\mykel{don't like low-cardinality. Maybe 'intervals' or something instead}.
-
-\subsection{MODL Discretization}
-MODL discretization \citep{Boulle_2006} is a Bayesian method for discretizing a continuous feature according to a class variable.
-Bayesian methods maximize the probability of the model given the data, $P(\textit{Model} \mid \textit{Data})$.
-An application of Bayes' rule and constant $P(\textit{Data})$ shows that this is equivalent to maximizing:
-\begin{align}
-P(\textit{Model}) \cdot P(\textit{Data} \mid \textit{Model})\text{,}
-\end{align}
-
-\noindent
-where $P(\textit{Model})$ is a prior over models and ${P(\textit{Data} \mid \textit{Model})}$ is the data likelihood.
-The data likelihood usually increases with the number of discretization intervals, as more intervals allow for richer representations.
-The prior decreases as the number of discretization intervals increases to favor simpler models and prevent overfitting.
-Maximizing ${P(\textit{Model}) \cdot P(\textit{Data} \mid \textit{Model})}$ requires a trade-off when determining the number of discretization intervals.
-
-The MODL method uses dynamic programming to find the optimal discretization policy, and has an $\bigo\paren{N^3 + |\text{Class}| \cdot N^2}$ runtime, where $N$ is the of number of data instances.
-\cite{Lustgarten_2011} suggest several formulations for the prior term $P(\text{Model})$.
-Under a uniform prior probability over discretizations the runtime can be reduced to $\bigo\paren{|\text{Class}| \cdot N^2}$ without sacrificing optimality.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \section{Preliminaries}
 \label{sec:preliminaries}
-This section provides a brief overview of Bayesian networks, including the factorization of joint probability distributions, sampling from a Bayesian network, and structure learning.
+This section covers the notation used throughout the paper and provides a brief overview of Bayesian networks, including the factorization of joint probability distributions, sampling from a Bayesian network, and structure learning.
 These concepts will be used in later sections.
@@
 
-\subsection{Bayesian Networks and Structure Learning}
-
-\mykel{$\bigstar$ This all needs to be explained better. Too many variables are being defined at once.}
-
-A Bayesian network $B$ is defined by a pair $(G,\Theta)$, where $G = (X,E)$ is a directed acyclic graph whose nodes correspond to a set of random variables $X = \brock{X_1, X_2, \ldots, X_n}$, and whose edges $E$ represent probabilistic dependencies among nodes.
-The graph structure $G$ encodes the Markov property: each node $X_i$ is independent of its non-descendants given its parents $\Pi_{X_i}$ in $G$.
-The conditional relations are parameterized by the elements of $\Theta$, which take the form $\theta_{x_i \mid \Pi_{x_i}} = P(x_i \mid \Pi_{x_i})$ for each possible value $x_i$ of $X_i$, and $\Pi_{x_i}$ of $\Pi_{X_i}$.
-The joint distribution over $X$ factors according to the Markov property:
-
-\begin{equation}
-P_B (X_1 , \ldots, X_n) = \prod_{i=1}^{n} P_B (X_i \mid \Pi_{X_i}) = \prod_{i=1}^{n} \theta_{x_i \mid \Pi_{x_i}}\text{.}
-\end{equation}
-
-Forward sampling is used to draw samples from the joint distribution represented by a Bayesian network.
-Variables are sampled in topological order such that parental instantiations are always known~\citep[see][chap.~22]{algo_2009}.
-\mykel{I think this ref is just for the topological sort; for sampling, cite DMU or PGM}
+\subsection{Bayesian Networks and Sampling}
+
+A Bayesian network $B$ is defined by a pair $(G,\bm{\theta})$, where $G$ is a directed acyclic graph whose $n$ nodes $X_{1:n}$ are random variables.
+The edges in a Bayesian network represent probabilistic dependencies among nodes and encode the Markov property: each node $X_i$ is independent of its non-descendants given its parents $\Pa_{X_i}$ in $G$.
+For a Bayesian network over discrete and discretized variables, let $r_i$ represent the number of instantiations of $X_i$, and let $q_i$ represent the number of instantiations of the parents of $X_i$.
+If $X_i$ has no parents, then $q_i = 1$.
+The $j$th instantiation of the parents of $X_i$ is denoted $\bm{\pi}_{ij}$.
+
+The conditional relations are parameterized by the elements of $\bm{\theta}$, written $\theta_{ij}^{(k)}$, which determines
+
+\begin{equation}
+P(X_i = k \mid \bm{\pi}_{ij}) = \theta_{ij}^{(k)}\text{.}
+\end{equation}
+
+The joint distribution over the variables in the Bayesian network factors according to the Markov property:
+
+\begin{equation}
+P(X_{1:n}) = \prod_{i=1}^n P(X_i \mid \Pa_{X_i})\text{.}
+\end{equation}
+
+Forward sampling is often used to draw samples from the joint distribution represented by a Bayesian network.
+Variables are sampled in topological order such that parental instantiations are always known~\citep{algo_2009}.
 Furthermore, the parent $\rightarrow$ child sampling order can be reversed if the marginal probability of the child variable is known.
-By Bayes' rule,
-
-\begin{equation}
-P(X_i \mid \Pi_{X_i}) \cdot \prod_{j = 1}^{ Pa( X_i)} P( \brock{\Pi_{X_i} }_j) = P(X_i) \cdot P(\Pi_{X_i} \mid X_i)\text{,}
-\end{equation}
-
-\noindent
-where $Pa(X_i)$ is the number of parents of $X_i$ and $\brock{\Pi_{X_i}}_j$ is the $j$th parent of $X_i$.
-\mykel{this may be messed up. Maybe use DMU notation?}
-% One can first sample $X_i$ by $P(X_i)$, then sample all the parent variables simultaneously by $P(\Pi_{X_i} \mid X_i)$. That is to say, $X_i$ becomes the starting point of sampling.
+% By Bayes' rule,
+
+% \begin{equation}
+% P(X_i \mid \Pa_{X_i}) \cdot \prod_{Y \in \Pa_{X_i}} P(Y) = P(X_i) \cdot P(\Pa_{X_i} \mid X_i)\text{.}
+% \end{equation}
+
+\subsection{Structure Learning}
 
@@
 This work uses the K2 structure learning algorithm \citep{K2}, one of the most successful score-based structure learning methods.
-Score-based structure learning methods over discrete variables commonly evaluate candidate structures according to their likelihood, $\prod_i f(X_i, \Pi_{X_i})$, where
-
-\begin{align}
-f(X_i, \Pi_{X_i}) = \prod_{j=1}^{|\Pi_{X_i}|} {{(|X_i|-1)!}\over{(N_{ij} + |X_i|-1)!}} \prod_{k=1}^{|X_i|} \alpha_{ijk}!\text{,}
-\end{align}
-
-\noindent
-where $|X_i|$ is the cardinality of $X_i$, $|\Pi_{X_i}|$ is number of possible instantiations of the parent variables of $X_i$, $\alpha_{ijk}$ is the number of instances of the $k$th value of $X_i$ with the $j$th parental instantiation, and $N_{ij} = \sum_{k=1}^{|X_i|} \alpha_{ijk}$.
-The optimal structure is the most probably structure given the data.
+Score-based structure learning methods over discrete variables commonly evaluate candidate structures according to their likelihood against a dataset $D$.
+Let $m_{ij}^{(k)}$ be the number of times $X_i = k$ given $\bm{\pi}_{ij}$ in $D$.
+The likelihood is given by
+
+\begin{equation}
+P(D\mid \bm{\theta}, G) = \prod_{i=1}^n \prod_{j=1}^{q_i} \prod_{k=1}^{r_i} \brock{\theta_{ij}^{(k)}}^{m_{ij}^{(k)}}\text{.}
+\end{equation}
+
+Structure search for a Bayesian network seeks the graph structure $G$ that maximizes ${P(G\mid D)}$.
+In practice one maximizes the log-likelihood, also known as the Bayesian score~\cite{cooper1992bayesian}:
+
+\begin{small}
+\begin{equation}
+\label{eq:BayesianScore}
+  \ln P(D\mid G) = \ln P(G) + \sum_{i=1}^n \sum_{j=1}^{q_i} \ln\paren{
+    \frac{
+      \Gamma\paren{\alpha_{ij}^{(0)}}
+    }{
+      \Gamma\paren{\alpha_{ij}^{(0)} + m_{ij}^{(0)}}
+    }
+  } + \sum_{k=1}^{r_i} \ln\paren{
+    \frac{
+      \Gamma\paren{\alpha_{ij}^{(k)} + m_{ij}^{(k)}}
+    }{
+      \Gamma\paren{\alpha_{ij}^{(k)}}
+    }
+  }\text{.}
+\end{equation}
+\end{small}
+
+In the equation above,
+
+\begin{equation}
+\alpha_{ij}^{(0)} = \sum_{k=1}^{r_i} \alpha_{ij}^{(k)} \quad \qquad m_{ij}^{(0)} = \sum_{k=1}^{r_i} m_{ij}^{(k)}\text{.}
+\end{equation}
+
 The space of acyclic graphcs is superexponential in the number of nodes so it is common to rely on heuristic search strategies \citep{PGM_2009}.
-
-The K2 algorithm assumes a topological ordering of variables and greedily adds parents to nodes to maximally increase the likelihood score.
+The K2 algorithm assumes a topological ordering of variables and greedily adds parents to nodes to maximally increase the Bayesian score.
 A fixed ordering ensures acyclicity but does not guarantee a globally optimal network structure.
@@
 
-\tim{We need to adopt the same notation everywhere; $C$ should be a child, not a continuous variable}.
+\todo{CONTINUE HERE}
 A discretization policy $M_C = \anglebrackets{t_1 < t_2 < \ldots < t_{k-1}}$ for a continuous variable $C$ is a mapping from $\mathbb{R}$ to $\brock{1,2,3,\ldots,k}$ such that
@@
 An integer representation of $M_C$ can be obtained by sorting the samples of $C$ in an increasing order, $\curly{c_1,c_2,\ldots,c_N}$, and if $t_i = (c_{s_{i}} + c_{s_{i}+1})/2$ for $i=1,2,\ldots,k$, then $M_C = \anglebrackets{t_1,t_2, \ldots, t_{k-1}} \equiv \brock{n_1,n_2,..n_k}$, where $n_1 = s_1$ and $n_i = s_{i} - s_{i-1}$.
-\mykel{Where did $s_i$ come from?}
 
@@
 In the first part, the Bayesian network structure is known in advance, which is obtained by equal-width prediscretization and the K2 algorithm.
-In the second part, the Bayesian netowrk structure is not provided in advance, and it is learned along with the discretization process.
-\tim{We may not want to state this up front so we can modify what we show for each dataset.}
+In the second part, the Bayesian netowrk structure is not provided in advance, and it is learned during the discretization process.
 
@@
 where $D$ is the original dataset and $D^*$ is the dataset discretized according to $\discset$.
-The log-likelihood of the discretized dataset is the Bayesian score evaluated with a uniform prior~\citep{neapolitan2004learning}:
-
-\begin{equation}
-  \ln P(D^*\mid G) = \sum_{i=1}^n \sum_{j=1}^{q_i} \ln\paren{
-    \frac{
-      \Gamma\paren{\alpha_{ij0}}
-    }{
-      \Gamma\paren{\alpha_{ij0} + m_{ij0}}
-    }
-  } + \sum_{k=1}^{r_i} \ln\paren{
-    \frac{
-      \Gamma\paren{\alpha_{ijk} + m_{ijk}}
-    }{
-      \Gamma\paren{\alpha_{ijk}}
-    }
-  }\text{.}
-\end{equation}
-
-\tim{We need to make sure everything is defined.}
-
+The log-likelihood of the discretized dataset is the Bayesian score (Equation ~\ref{eq:BayesianScore}) evaluated with a uniform prior.
 The log-likelihood of the original dataset given the discrete dataset is
@@
 \end{equation}
+
+The proposed Bayesian discretization method is compared against MDL.
+For a Bayesian network with a single continuous variable $X$, the MDL objective function is
+
+\begin{equation}
+\begin{aligned}
+\frac{1}{2} \log(N) \left\lbrace  \lvert \Pi_{X_i} \rvert (\lvert X^*_i \rvert - 1) +
+ {\sum_{j,X_i \in \Pi_{X_i}}} \lvert \Pi_{X^*_j} \rvert (\lvert X_j \rvert - 1) \right\rbrace + \log(\lvert {X^*_i} \rvert) \\
+ + (N_i-1) H \left( {{|X^*_i| - 1}\over{N_i -1}}  \right) -N \cdot \left[ I(X^*_i,\Pi_{X_i}) + {\sum_{j,X_i \in \Pi_{X_i}}} I(X_j, \Pi_{X^*_j}) \right]\text{,}
+\end{aligned}
+\end{equation}
+
+where $I(A,B)$ is the mutual information between the discrete variables $A$ and $B$, ${H(p) = -p \log(p) - (1-p) \log(1-p)}$ \tim{does $H(p)$ have a name?
+Entropy?}, and \todo{$X^*_i$ is the discretized version of the $i$th sample of $X$}.
+The optimal discretization policy is found with dynamic programming in a similar manner as with the Bayesian method.
 

### 2015-11-18 BN_discretizer_paper.tex
Update Experiment section

@@
    \input{graph_autocar_1}
-   \caption{The Bayesian network obtained with K2 on the prediscretized Auto MPG dataset}
+   \caption{Structure from prediscretized K2 structure learning to compare the methods for Auto MPG dataset}
   \label{fig:auto_graph_1}
@@
 
-Table \ref{table:auto_disc_table_1} shows the numbers of intervals after discretization, the positions of discretization edges, and log-likelihood of 10-fold cross validation.
+Table \ref{table:auto_disc_table_1} shows the positions of discretization edges, and log-likelihood of 10-fold cross validation by three discretization methods.
 For the Bayesian network in Fig.
 \ref{fig:auto_graph_1}, the approximation \ref{eq:opt_prob_approx} only reduces runtime and has no influence on discretization result.
-MDL principle discretization works not well, since it discretizes all variables with only one interval.
+MDL principle discretization works not well, since it discretizes each continuous variable by only one interval.
 The reason that the MDL method discretizes variables into too few number of intervals is discussed in Section \ref{subsec:discuss_exp}.
@@
   \centering
-  \caption{Discretization result of Auto MPG dataset based on the graph in Fig.
-\ref{fig:auto_graph_1}.
-The discretization policy for the heuristic matches that for the optimal Bayesian approach.
-The MDL method is less sensitive to distribution of values of other variables, thus it fails to return discretization edges.}
+  \caption{Discretization results of Auto MPG dataset based on the graph in Fig.
+\ref{fig:auto_graph_1} by the three methods.
+The first to fifth row are discretization edges on each continuous variable.
+The sixth row is the log-likelihood of the dataset based on the discretization results.
+The discretization result for the heuristic matches that for the optimal Bayesian approach.
+The MDL method is less sensitive to distribution of values of other variables and fails to return discretization edges.}
   \input{table_autoMPG_1.tex}
@@
 If the network structure is not known in advance, it should be learned along with the discretization process.
-Figure \ref{fig:auto_graph_2} show a learned discrete-valued Bayesian network and the corresponding numbers of intervals after discretization.
-This result is obtained by running Algorithm \ref{alg:structure_learn} fifty times and choosing the one with the highest K2 score.
+Figure \ref{fig:auto_graph_2} show a learned discrete-valued Bayesian network and the corresponding numbers of intervals after discretization for each continuous variable.
+This result is obtained by running Algorithm \ref{alg:structure_learn} fifty times (without the approximation) and choosing the one with the highest K2 score.
 
@@
 
- %{\centering
-%\begin{minipage}{0.50\textwidth}
-  %\centering
-  %\scalebox{0.7}{
-  %\input{graph_autocar_2}}
-  %\captionof{figure}{The learned discrete-\newline valued Bayesian network}
-  %\label{fig:auto_graph_2}
-%\end{minipage}
-%\begin{minipage}{0.50\textwidth}
-  %\raggedleft
-  %\input{table_autoMPG_2.tex}
-  %\captionof{table}{The discretization edges of variables in Fig \ref{Auto_graph_2}}
- % \label{Auto_MPG_disc_table_2}
-%\end{minipage}
-%}
-
-Figure \ref{fig:auto_exp2_distr_1_3} compares the discretization edges of variable $A$ and $C$ in the learned network in Figure \ref{fig:auto_graph_2} with the raw data.
+Figure \ref{fig:auto_exp2_distr_1_3} shows the discretization edges on variable $A$ and $C$ in Figure \ref{fig:auto_graph_2} along with the raw data.
 Again, the black dots are raw data points.
+The colors of discretized areas are the corresponding maginalized probability.
 Although the numbers of discretization edges of $A$ and $C$ shown in Figure \ref{fig:auto_exp2_distr_1_3} are less than Figure \ref{fig:auto_exp2_distr_1_3}, they still have a good capture of raw data distribution.
-This indicated that although the discretization result of the optimal Bayesian approach might vary according to the network structure, it still preserves the quality of discretization.
+This indicates that although the discretization result of the optimal Bayesian approach might vary according to the network structure, it still preserves the quality of discretization.
 
@@
       \input{graph_auto_exp2_distr_1_3}
-  \caption{Comparison of the raw data and discretization result on variable $A$ and $C$ of the learned network in Figure \ref{fig:auto_graph_2}.
+  \caption{Comparison of the raw data and discretization result on variable $A$ and $C$ in Figure \ref{fig:auto_graph_2}.
 Although the number of discretization edges is less than in Figure \ref{fig:auto_exp1_distr_1_3}, it still matches the raw data distribution very well.}
@@
 Table \ref{table:wine_disc_table_1} shows a comparison between the optimal Bayesian approach and the MDL principle discretization method.
-The discretization result obtained by the optimal Bayesian approach is better than the MDL discretization method in terms of likelihood, although the latter returns non-trivial result in this experiment.
-Note that the
-heuristic method discretizes variable $G$, $H$ and $J$ into one more interval than the optimal Bayesian approach, and has less number of intervals on variable $M$.
-Although the heuristic method has more intervals after discretization on all variables, it does not lead to a higher likelihood result.
-This can be interpreted as that the extra discretization edges on $G$, $H$ and $J$ are less necessary and the losing discretization edge on $M$ is important.
-On the other hand, if running time is a concern, then the heuristic method can be considered a better approach in this case, since its discretization result is nearly as good as the result of the optimal Bayesian approach.
-
-Notice that there are some discretization edges shown in all three discretization methods, such as \num{1.42} and \num{2.35} on variable $C$ and \num{0.785} on variable $L$.
-This indicates that MDL indeed can find some important discretization edges, but it is not sensitive enough to find other edges.
+The discretization result obtained by the optimal Bayesian approach is better than the MDL discretization method in terms of likelihood.
+The heuristic method discretizes variable $G$, $H$ and $J$ into one less interval than the optimal Bayesian approach, and has one more number of intervals on variable $M$.
+Although it returns different numbers of intervals and different positions of discretization edges with the optimal Bayesian approach, it still has a good discretization result in terms of likelihood.
+Furthermore, if running time is the main concern, the heuristic method can be considered a better approach in this case.
+
+Notice that there are some discretization edges appearing in all three discretization methods, such as \num{1.42} and \num{2.35} on variable $C$ and \num{0.785} on variable $L$.
+This indicates that MDL indeed can find some important discretization edges, but it is not sensitive enough to find more edges.
 
@@
       \input{graph_wine_1}
-  \caption{\tim{Structure from prediscretized K2 structure learning to compare the methods}}
+  \caption{Structure from prediscretized K2 structure learning to compare the methods for Wine dataset}
   \label{fig:wine_graph_1}
@@
   \centering
+  \caption{Discretization results of Wine dataset based on the graph Fig.
+\ref{fig:wine_graph_1} by the three different method.
+The first to the thirteenth row are discretization edges on each continuos variable.
+The fourteenth row is the log-likelihood of the dataset based on the discretization results.
+The optimal Bayesian approach has the best discretization result in terms of likelihood.
+The heuristic method obtains a result nearly as good as the Bayesian approach.
+The MDL method discretizes more than half of continuous variables but still does not discretize enough intervals.
+Some discretization edges appear in the results of all three methods, and indicate that they are the most determinant edges.}
   \scalebox{1.0}{
@@
   }
-  \caption{Discretization result of Wine dataset based on the graph Fig.
-\ref{fig:wine_graph_1}.
-The optimal Bayesian approach has the best discretization result in terms of likelihood.
-The heuristic method obtains a result nearly as good as the Bayesian approach.
-The MDL method discretizes more than half of continuous variables but still does not discretize enough intervals.
-Some discretization edges are obtained by all three methods.
-  \todo{MDL has bins, heuristic is slightly worse in logl but still good. MDL keeps all of its CPDs small, no neighboring vars both have more than 1 interval.}
-  \tim{Should we scale the logl? What is the best way to do that?}
-  }
   \label{table:wine_disc_table_1}
@@
 
-Figure \ref{fig:wine_exp1_distr} compares the discretization results by the proposed method and the MDL method.
-It shows the discretization edges on variable $E$ and $K$, and the probability of resulting discretized area.
-The proposed method has more discretization edges than the MDL method.
-Furthermore, the discretization edges on $E$ and $K$ obtained by the MDL method are either included in or close to the edges by obtained proposed method.
-This indicates that the proposed method can include the discretization result obtained by the MDL method and meanwhile, capture other discretization edges without significantly increase cardinality numbers of variables.
-
-%\begin{figure}[ht]
-%  \centering
-%    \input{graph_wine_exp1_distr}
-%  \caption{Comparison of the discretization results on variable $A$ and $C$ obtained by the proposed method and the MDL method}
-%  \label{fig:wine_exp1_distr}
-%\end{figure}
+Figure \ref{fig:wine_exp1_distr} compares the discretization results by the optimal Bayesian approach and the MDL method.
+The discretization edges \num{17.9} on $E$ and \num{34.6} on $K$ appear in both plots.
+This indicates that they are more necessary than other discretization edges on $E$ and $K$.
+On the other hand, the edge \num{23.25} on $E$ is also meaningful.
+For instance, after having an extra edge at \num{23.25}, the area from $E = 17.9$ to $30$ is divided two rectangles such that the one from $E=17.9$ to $23.25$ has relatively higher probability than $E=23.25$ to $30$.
+The MDL method does not capture this edge due to its low sensitivity toward distribution.
+For more discussion about the sensitivity, see Section \ref{subsec:discuss_exp}.
+
+\begin{figure}[ht]
+  \centering
+    \input{graph_wine_exp1_distr}
+  \caption{Comparison of the discretization results on variable $A$ and $C$ obtained by the optimal Bayesian approach and the MDL method}
+  \label{fig:wine_exp1_distr}
+\end{figure}
 
@@
 By comparing Figure \ref{fig:wine_graph_2} with \ref{fig:wine_graph_1}, it shows that the the Bayesian network obtained by Algorithm \ref{alg:structure_learn} has more edges than the network obtained by prediscretization and the K2 algorithm.
-Furthermore, the cardinalitis of discretized variables in Figure \ref{fig:wine_graph_2} are smaller than the result in \ref{table:wine_disc_table_1}.
+This is sensible, since when a network is learned along with discretization, variables have more freedom, by adjusting discretization edges, to construct the correlations with other variables and thus have more edges in the network.
 
 Figure \ref{fig:wine_exp2_distr} shows the discretization result on variable $E$ and $K$.
-The discretization edge on variable $E$ is same as the edge found by the MDL principle and the proposed method in Figure \ref{fig:wine_exp1_distr}.
+The discretization edge at \num{17.9} on variable $E$ also appers in Figure \ref{fig:wine_exp1_distr}.
 This indicates that some discretization edges are robust against the network structure.
+Furthermore, in Figure \ref{fig:wine_exp2_distr}, the discretization edge at \num{23.5} on $E$ is lost.
+This is due to the number of parents of $E$ in Figure \ref{fig:wine_graph_2} is twice as in \ref{fig:wine_graph_1}.
+Usually, if a variable has more parents, then less number of intervals after discretization it has, since the information from parents are adulterated together.
 
@@
  \end{tabular}
-  \caption{The discretization result on variable $E$ and $K$ of the learned network in Figure \ref{fig:wine_graph_2}
-  \todo{Note unchanged discretization edge.}
-  }
+  \caption{The discretization result on variable $E$ and $K$ of the learned network in Figure \ref{fig:wine_graph_2}.
+The discretization edge \num{17.9} on $E$ also appear in \ref{fig:wine_exp1_distr}.
+This indicates that some discretization edges are robust again the network structure.}
   \label{fig:wine_exp2_distr}
@@
 Only variables $D$ and $I$ are discrete-valued with cardinality numbers 2 and 9, respectively.
-Again, in the first experiment, the network structure is given.
-In the second experiment, the network structure is not provided.
+Again, in the first experiment, the network structure is given in advance.
+In the second experiment, the network structure is not provided in advance.
 
@@
 The Bayesian network structure in Figure \ref{fig:housing_graph_1} is obtained by prediscretizing each continuous variable into five uniform-width intervals, then running the K2 algorithm one thousands time and choosing the network with the highest K2 score.
-Table \ref{table:housing_disc_table_1} shows the numbers of intervals after discretization on each continuous variables.
-MDL method does not discretize most variables.
-The proposed method with the approximation discretizes variables into too many intervals.
-For example, it discretized $J$ into 58 intervals.
-The proposed method without the approximation has a good control of number of intervals.
+Table \ref{table:housing_disc_table_1} shows the numbers of intervals after discretization on each continuous variables and also the log-likelihood of the dataset based on the discretization results.
+MDL method again does not discretize most variables.
+The heuristic method discretizes variables into too many intervals due to repeated values in the dataset, as we will see in later discussion.
+The optimal Bayesian approach has a good control of number of intervals.
+These numbers of intervals returned by the three methods illustrate that the heuristic method is over sensitive and the MDL method is less sensitive.
+The properties of sensitivity of the three algorithms will be discussed in Section \ref{subsec:discuss_exp}.
+On the other hand, although the heuristic method leads to high number of intervals, its corresponding log-likelihood on the dataset is not significantly better than the optimal Bayesian approach.
+This shows that the optimal Bayesian approach captures the important discretization edges.
+
 \begin{figure}[ht]
@@
    \end{tabular}
-  \caption{\todo{Structure from prediscretized K2 structure learning to compare the methods for Housing dataset}}
+  \caption{Structure from prediscretized K2 structure learning to compare the methods for Housing dataset}
   \label{fig:housing_graph_1}
@@
 \begin{table}
-  \centering
+  \centering\caption{Discretization result of Housing dataset based on the graph in Figure~\ref{fig:housing_graph_1}.
+The first twelve rows show the numbers of intervals after discretization by the three method.
+The thirteenth row is the log-likelihood of the dataset based on the discretizatio results.
+The heuristic method is over sensitive and discretizes some variables into too many intervals.
+The MDL method is less sensitive and discretizes most variables by only one interval.
+The optimal Bayesian approach has a good control on number of intervals.
+\tim{Fig.
+vs.
+Figure}}
   \scalebox{1.0}{
@@
   }
-  \caption{Discretization result of Housing dataset based on the graph Figure~\ref{fig:housing_graph_1} \tim{Fig. vs. Figure}}
+
   \label{table:housing_disc_table_1}
@@
 
-Figure~\ref{fig:housing_exp1_distr_3_5} and Figure~\ref{fig:housing_exp1_distr_8_5} show the discretization result by the propose method on the network in Figure~\ref{fig:housing_graph_1}.
+Figure~\ref{fig:housing_exp1_distr_3_5} and Figure~\ref{fig:housing_exp1_distr_8_5} show the discretization result of the optimal Bayesian approach on the network in Figure~\ref{fig:housing_graph_1}.
 In Figure~\ref{fig:housing_exp1_distr_3_5}, the scatter points, which stands for the raw data, has been jittered, since there are many repeated values in the raw data on the variable pair $C$ and $E$.
-These repeating values cause the high number of intervals after discretization for both $C$ and $E$, because in some sense, each repeated-value point form a single discretized area.
-On the other hand, there is no such over-repeated values of the raw data on variable $H$.
-Thus, the numbers of intervals after discretization for variable $E$ remains normal, as what we have seen in previous datasets.
+These repeating values cause the high number of intervals for both $C$ and $E$, because in some sense, each repeated-value point form a single discretized area.
+On the other hand, there is no such over repeated values of the raw data on variable $H$.
+Thus, the numbers of intervals after discretization for variable $H$ remains normal, as what we have seen in previous datasets.
 
@@
     % \end{tabular}
-  \caption{The discretization result on variable $C$ and $E$ of the network in Figure~\ref{fig:housing_graph_1}}
+  \caption{The discretization result on variable $C$ and $E$ of the network in Figure~\ref{fig:housing_graph_1}.
+The scatter points are jittered due to the repeated values in the dataset.
+Furthermore, these repeated values lead to high number of discretization edges, since repeated values can easily form discretized areas by their own.}
   \label{fig:housing_exp1_distr_3_5}
@@
      %\end{tabular}
-  \caption{The discretization result on variable $H$ and $E$ of the network in Figure~\ref{fig:housing_graph_1}}
+  \caption{The discretization result on variable $H$ and $E$ of the network in Figure~\ref{fig:housing_graph_1}.
+Data points are not over repeated on $H$, thus the number of edges on $H$ remains desirable.}
   \label{fig:housing_exp1_distr_8_5}
@@
     % \end{tabular}
-  \caption{The learned discrete-valued Bayesian network from the Housing dataset
-  \todo{Mention that there are high-cardinality vars.}
+  \caption{The learned discrete-valued Bayesian network from the Housing dataset. Variables $C$, $E$, $J$, $K$ have high numbers of intervals after discretization, since they are in a Markov blanket.
   \tim{Var with 1 interval?}
@@
 Again, variable $C$ and $E$ have many discretization edges due to the repeated values.
-Although the number of intervals after discretization on $H$ is not big, it captures the distribution of the raw data along with the discretization edges on $E$.
+Although the number of intervals after discretization on $H$ is not large, it captures the distribution of the raw data along with the discretization edges on $E$.
 
@@
      %\end{tabular}
-  \caption{The discretization result on variable $C$ and $E$ of the network in Figure~\ref{fig:housing_graph_2}}
+  \caption{The discretization result on variable $C$ and $E$ of the network in Figure~\ref{fig:housing_graph_2}.
+The high number of discretization edges is due to the repeated values on the dataset in variable $C$ and $E$.}
   \label{fig:housing_exp2_distr_3_5}
@@
     % \end{tabular}
-  \caption{The discretization result on variable $H$ and $G$ of the network in Figure~\ref{fig:housing_graph_2}}
+  \caption{The discretization result on variable $H$ and $E$ of the network in Figure~\ref{fig:housing_graph_2}.
+Although the number of discretization edges on $H$ is not as large as $E$'s, they still match the distribution of the raw data very well.}
   \label{fig:housing_exp2_distr_8_5}
@@
 \label{subsec:discuss_exp}
+
+\begin{figure}[ht]
+    % \begin{tabular}{cc}
+      \input{graph_exp_discuss}
+    % \end{tabular}
+  \caption{A simple Bayesian network that is used to demonstrate the sensitivity of the three methods}
+  \label{fig:exp_discuss}
+\end{figure}
+
+To quantatively discuss the sensitivity of the three methods, consider the Bayesian network in Figure \ref{fig:exp_discuss}, where $X$ is continuous-valued and $P_1$ and $P_2$ is discrete-valued.
+Let $P = \{  P_1, P_2 \}$.
+Assume $D_X = \{1.0,2.0,3.0, \ldots N \}$.
+Therefore, the corresponding objective functions to discretize $X$ in the three methods are:
+\begin{equation}
+\begin{aligned}
+\text{Obj}_{\text{MDL}} & = Z_1 \cdot k + \log(N) \cdot \sum^k_{i=1} \sum^{J_P}_{j=1} I(a^*_i, (p_1,p_2)_j) \\
+\text{Obj}_{\text{Bayesian}} &= Z_2 \cdot k + \log {{n_i + J_P - 1}\choose{J_P -1}} + \sum^k_{i=1} \log \left(   {{n_i !}\over{n^{(P)}_{i,1}! n^{(P)}_{i,2}! \cdots n^{(P)}_{i,J_P}!    }} \right) \\
+\text{Obj}_{\text{Heuristic}} &= Z_2 \cdot k + \log {{n_i + J_{P_1} - 1}\choose{J_{P_1} -1}} + \log {{n_i + J_{P_2} - 1}\choose{J_{P_2} -1}} +\\
+& \sum^k_{i=1}  \left[ \log \left(   {{n_i !}\over{n^{(P_1)}_{i,1}!
+n^{(P_1)}_{i,2}!
+\cdots n^{(P_1)}_{i,J_{P_1}}    }} \right)  + \log \left(   {{n_i !}\over{n^{(P_2)}_{i,1}!
+n^{(P_2)}_{i,2} \cdots n^{(P_2)}_{i,J_{P_2}}    }} \right) \right]
+\end{aligned}
+\end{equation}
 

### 2015-11-18 BN_discretizer_paper.tex
Correct English mistakes

@@
 \ref{fig:auto_graph_1} by the three methods.
-The first to fifth row are discretization edges on each continuous variable.
+The first five rows are discretization edges on each continuous variable.
 The sixth row is the log-likelihood of the dataset based on the discretization results.
@@
   \centering
-  \caption{Discretization results of Wine dataset based on the graph Fig.
-\ref{fig:wine_graph_1} by the three different method.
-The first to the thirteenth row are discretization edges on each continuos variable.
+  \caption{Discretization results of Wine dataset based on the network in Fig.
+\ref{fig:wine_graph_1} by the three different methods.
+The first thirteen rows are discretization edges on each continuos variable.
 The fourteenth row is the log-likelihood of the dataset based on the discretization results.

### 2015-11-18 BN_discretizer_paper.tex
more notation changes

@@
 \usepackage{booktabs}
+\usepackage{boondox-cal} % for lowercase caligraphic
 % \usepackage[capitalize]{cleveref}
@@
 
-\DeclareMathOperator{\Pa}{pa}
+\DeclareMathOperator{\Pa}{pa} % parents of a var in a BN
+\newcommand{\cX}{\mathcal{X}} % continuous X
+\newcommand{\cx}{\mathcal{x}} % instance of x
+\newcommand{\cu}{\mathcal{u}} % unique sorted instances of x
 
@@
 
-\institute{F. Author \at
+\institute{\todo{Yi-Chun Chen \at
               first address \\
@@
            S. Author \at
-              second address
+              second address}
 }
@@
 
-% \begin{table}[H]
-%   \centering
-%   \begin{tabular}{@{}ccl@{}}
-%     \toprule
-%     Current & Mykel & Description \\
-%     \midrule
+\begin{table}[H]
+  \centering
+  \begin{tabular}{@{}ccl@{}}
+    \toprule
+    Current & Mykel & Description \\
+    \midrule
     % $G$ & $G$ & BN graph structure \\
@@
     % $D$ & $D$ & available data \\
-%     $|D|$ & $n$ & number of variables in the BN \\
-%     $D_{\bm{Y}}$ & & subset of data associated with $\bm{Y}$ \\
-%     $X$ & $X_{1:n}$ & variables in BN (discrete) \\
-%     $x_{1:n}$ & $x_{1:n}$ & a specific instance of vars in BN \\
-%     $x'_{1:n}$ &  & unique instances of var in BN \\
-%         & $r_i$ & number of instantiations of $i$th var \\
-%     $J_p$ & $q_i$ & number of instantiations of parents of $i$th var \\
-%         &       & $ = 1$ if no parents \\
-%     $\brock{\Pi_{X_i}}_j$ & $\pi_{ij}$ & $j$th instantiation of $i$th var \\
-%         & $\theta_{ijk}$ & probability of $i$th var $= k$ given $j$th parental inst. \\
-%     $\Theta$ & $\bm{\theta}$ & set of all (non-independent) probability parameters \\
-%     $n_{i,j}^{(k)}$ & $m_{ijk}$ & observation counts \\
-%     $n_{i,j,l}^{(k)}$ & $m_{ijk}$ & observation counts with $l$th instance of spouse\\
-%     $\alpha_{ijk}$ & $\alpha_{ijk}$ & Dirichlet prior counts \\
-%     $N_{ij}$ & $\alpha_{ij0}$ & sum over Dirichlet prior counts for $k$ \\
-%         & $m_{ij0}$ & sum over observations counts for $k$ \\
-%         & $\Gamma$ & the Gamma function \\
-%     $N$ &          & is the number of samples in dataset \\
-%     $N_i$ &          & counts for $i$th instance of a specific var \\
-%     $\Pi_X$ & $\text{pa}_{x_i}$ & parents of a variable or instance \\
-%     $n_C$ & & number of children of a variable \\
-%     $H(~)$ & & a function \\
-%     $I(~,~)$ & & mutual information \\
-%     $X_i$ & & $i$th variable in BN, may be cont or disc \\
-%     $X_i^*$ & & discrete version of cont var \\
-%     $E$ & & set of edges in BN \\
-%     $\text{Pa}\paren{X_i}$, $n_p$ & & number of parents of $X_i$ \\
-%     $f\paren{X_i, \Pi_{X_i}}$ & $f(G)$ & score function for K2 \\
-%     $M_C$ & & discretization policy for $C$ \\
-%     $C$ & & a continuous variable \\
-%     $t_i$ & & the $i$th bin edge for a specific var \\
-%     $d_i$ & & allowable discretization positions (between unique vals) \\
-%     $k$ & & number of intervals for $M_C$ \\
-%     $C_{1:N}$ & & sorted samples for $C$ \\
-%     $n_i$ & & $n_1 = s_1$ and $n_i = s_{i} - s_{i-1}$ \\
-%     $s_i$ & & $\sum_{j=1}^k n_j$ and $s_k = N$, $s_0 = 0$ \\
-%     $C_i$ & & $i$th child of a specific var \\
-%     $\boldsymbol{S_i}$ & & set of spouses associated with $i$th child of specific var \\
-%     $L$ & & largest cardinality among discrete variables in BN \\
-%     $I_q$ & & an interval from $u \rightarrow v$ \\
-%     $v'_\text{max}$ & & largest cardinality of variables that directly connect to $X$ \\
-%     $S[]$ & &  optimal objective value of subproblems with instances from $1$ to $u$ \\
-%     \bottomrule
-%   \end{tabular}
-% \end{table}
+    $|D|$ & $n$ & number of variables in the BN \\
+    $D_{\bm{Y}}$ & & subset of data associated with $\bm{Y}$ \\
+    $X$ & $X_{1:n}$ & variables in BN (discrete) \\
+    $x_{1:n}$ & $x_{1:n}$ & a specific instance of vars in BN \\
+    $x'_{1:n}$ &  & unique instances of var in BN \\
+        & $r_i$ & number of instantiations of $i$th var \\
+    $J_p$ & $q_i$ & number of instantiations of parents of $i$th var \\
+        &       & $ = 1$ if no parents \\
+    $\brock{\Pi_{X_i}}_j$ & $\pi_{ij}$ & $j$th instantiation of $i$th var \\
+        & $\theta_{ijk}$ & probability of $i$th var $= k$ given $j$th parental inst. \\
+    $\Theta$ & $\bm{\theta}$ & set of all (non-independent) probability parameters \\
+    $n_{i,j}^{(k)}$ & $m_{ijk}$ & observation counts \\
+    $n_{i,j,l}^{(k)}$ & $m_{ijk}$ & observation counts with $l$th instance of spouse\\
+    $\alpha_{ijk}$ & $\alpha_{ijk}$ & Dirichlet prior counts \\
+    $N_{ij}$ & $\alpha_{ij0}$ & sum over Dirichlet prior counts for $k$ \\
+        & $m_{ij0}$ & sum over observations counts for $k$ \\
+        & $\Gamma$ & the Gamma function \\
+    $N$ &          & is the number of samples in dataset \\
+    $N_i$ &          & counts for $i$th instance of a specific var \\
+    $\Pi_X$ & $\text{pa}_{x_i}$ & parents of a variable or instance \\
+    $n_C$ & & number of children of a variable \\
+    $H(~)$ & & a function \\
+    $I(~,~)$ & & mutual information \\
+    $X_i$ & & $i$th variable in BN, may be cont or disc \\
+    $X_i^*$ & & discrete version of cont var \\
+    $E$ & & set of edges in BN \\
+    $\text{Pa}\paren{X_i}$, $n_p$ & & number of parents of $X_i$ \\
+    $f\paren{X_i, \Pi_{X_i}}$ & $f(G)$ & score function for K2 \\
+    $M_C$ & & discretization policy for $C$ \\
+    $C$ & & a continuous variable \\
+    $t_i$ & & the $i$th bin edge for a specific var \\
+    $d_i$ & & allowable discretization positions (between unique vals) \\
+    $k$ & & number of intervals for $M_C$ \\
+    $C_{1:N}$ & & sorted samples for $C$ \\
+    $n_i$ & & $n_1 = s_1$ and $n_i = s_{i} - s_{i-1}$ \\
+    $s_i$ & & $\sum_{j=1}^k n_j$ and $s_k = N$, $s_0 = 0$ \\
+    $C_i$ & & $i$th child of a specific var \\
+    $\boldsymbol{S_i}$ & & set of spouses associated with $i$th child of specific var \\
+    $L$ & & largest cardinality among discrete variables in BN \\
+    $I_q$ & & an interval from $u \rightarrow v$ \\
+    $v'_\text{max}$ & & largest cardinality of variables that directly connect to $X$ \\
+    $S[]$ & &  optimal objective value of subproblems with instances from $1$ to $u$ \\
+    \bottomrule
+  \end{tabular}
+\end{table}
 
@@
 Bayesian methods maximize the probability of the model given the data, $P(\textit{Model} \mid \textit{Data})$.
-An application of Bayes' rule and constant $P(\textit{Data})$ shows that this is equivalent to maximizing:
+An application of Bayes' rule and constant $P(\textit{Data})$ shows that this is equivalent to maximizing
 
@@
 The edges in a Bayesian network represent probabilistic dependencies among nodes and encode the Markov property: each node $X_i$ is independent of its non-descendants given its parents $\Pa_{X_i}$ in $G$.
-For a Bayesian network over discrete and discretized variables, let $r_i$ represent the number of instantiations of $X_i$, and let $q_i$ represent the number of instantiations of the parents of $X_i$.
+For a Bayesian network over discrete and discretized variables, $r_i$ represents the number of instantiations of $X_i$, and $q_i$ represents the number of instantiations of the parents of $X_i$.
 If $X_i$ has no parents, then $q_i = 1$.
@@
 % \end{equation}
+
+\todo{
+Introduce P, C, and S for parents
+}
 
@@
 
-\todo{CONTINUE HERE}
-A discretization policy $M_C = \anglebrackets{t_1 < t_2 < \ldots < t_{k-1}}$ for a continuous variable $C$ is a mapping from $\mathbb{R}$ to $\brock{1,2,3,\ldots,k}$ such that
-\begin{equation}
-  M_C (x)=\begin{cases}
-    1, & \text{if $x<t_1$}.\\
-    i, & \text{if $t_{i-1} \leq x < t_i$}\text{.}\\
-    k, & \text{if $t_{k-1} \leq x$}
+Let $\cX$ be a continuous variable and let $\cx$ be a specific instance of $\cX$.
+A discretization policy $\Lambda_{\cX} = \curly{e_1 < e_2 < \ldots < e_{k-1}}$ for $\cX$ is a mapping from $\mathbb{R}$ to $\curly{1,2,3,\ldots,k}$ such that
+
+\begin{equation}
+  \Lambda_{\cX}(\cx) = \begin{cases}
+    1, & \text{if $x<e_1$}\\
+    i, & \text{if $e_{i-1} \leq x < e_i$}\\
+    k, & \text{otherwise.}
   \end{cases}
@@
 \noindent
-The policy discretizes the continuous variable $C$ into $k$ intervals.
-The discretization edges $t_{1:k-1}$ are restricted to the midpoints between two sorted instances of $C$.
-An integer representation of $M_C$ can be obtained by sorting the samples of $C$ in an increasing order, $\curly{c_1,c_2,\ldots,c_N}$, and if $t_i = (c_{s_{i}} + c_{s_{i}+1})/2$ for $i=1,2,\ldots,k$, then $M_C = \anglebrackets{t_1,t_2, \ldots, t_{k-1}} \equiv \brock{n_1,n_2,..n_k}$, where $n_1 = s_1$ and $n_i = s_{i} - s_{i-1}$.
+The discretization policy discretizes $\cX$ into $k$ intervals.
+Let the samples of $\cX$ in a given dataset $D$ be sorted in ascending order, ${\cx_{1:n} = \curly{\cx_1 \leq \cx_2 \leq \ldots \leq \cx_n}}$, and let the unique values be ${\cu_{1:n} = \curly{\cu_1 \leq \cu_2 \leq \ldots \leq \cu_n}}$.
+The index of the last occurence of $\cu_i$ in $\cx$ is denoted $s_i$.
+
+The discretization edges $e_{1:k-1}$ mark the boundaries between discretization intervals.
+In this work they are restricted to the midpoints between unique ascending instances of $\cX$.
+Thus, each edge $e_i = \paren{\cu_{s_{j+1}} - \cu_{s_j}}/2$ for some $s_j$.
+An integer representation of $\Lambda_{\cX}$ can thus be written $\Lambda_{\cX} = \curly{\lambda_1 < \lambda_2  < \ldots < \lambda_k}$, where $\lambda_1 = s_1$ and $\lambda_i \in s_{1:|\cu|}$.
 
@@
 
-This section covers discretization of a single continuous variable $X$ in a Bayesian network where all other variables are discrete.
+This section covers the discretization of a single continuous variable $\cX$ in a Bayesian network where all other variables are discrete.
 Let $n_p$ and $n_c$ respectively refer to the number of parents and number of children of $X$.
@@
 
-For example, in Figure 1., the corresponding $P(D \mid M)$ is factorized according to
+For example, in Figure~\ref{fig:example_factorization}, the corresponding $P(D \mid M)$ is factorized according to
 \begin{equation}
@@
 \begin{figure}[ht]
+  \label{fig:example_factorization}
   \begin{tabular}{cc}

### 2015-11-18 BN_discretizer_paper.tex
Rewrite graph1, center plots, add content to experiment part

@@
 \begin{figure}[ht]
+\centering
   \label{fig:example_factorization}
-  \begin{tabular}{cc}
+  %\begin{tabular}{cc}
     \input{graph1}
-  \end{tabular}
+  %\end{tabular}
   \caption{Factorization of $P(D \mid M)$}
@@
 \Function{Discretize}{$D$, $G$}
-\State
 \State $N \leftarrow$ the number of instances
@@
 \State $W[u]  \leftarrow - \log\brock{1 - {\exp\paren{- L \cdot{ {{x_{b(u)+1} - x_{b(u)}}\over{x_N - x_1}}}}}}$ for $u = 1,2, \ldots,N'-1$ and $L(N') \leftarrow 0$
-\State
-\For {$v = 1$ to $N'$}
+\For {$v \leftarrow 1$ to $N'$}
 \If {$v = 1$}
@@
 \State $s \leftarrow \infty$ and $boundary \leftarrow \infty$
-\For {$u = 1$ to $v$}
+\For {$u \leftarrow 1$ to $v$}
 \State $s' \leftarrow S[u] + g \left( b[u]+1,b[v] \right) +  {L \cdot {{x_{b[v]} - x_{b[u] + 1}}\over{x_N - x_1}}} + W[v]$
@@
 \begin{equation}
+\label{eqn:MDL}
 \begin{aligned}
@@
 \begin{figure}[ht]
+\centering
       \input{graph_auto_exp1_distr_1_3}
@@
 \begin{figure}[ht]
+\centering
       \input{graph_auto_exp2_distr_1_3}
@@
   \centering
-      \input{graph_wine_1}
+  \scalebox{0.8}{
+      \input{graph_wine_1}}
   \caption{Structure from prediscretized K2 structure learning to compare the methods for Wine dataset}
@@
   \centering
-  \begin{tabular}{cc}
-   \input{graph_housing_1}
-   \end{tabular}
+  %\begin{tabular}{cc}
+  \scalebox{0.8}{
+   \input{graph_housing_1}}
+   %\end{tabular}
   \caption{Structure from prediscretized K2 structure learning to compare the methods for Housing dataset}
@@
 \begin{table}
-  \centering\caption{Discretization result of Housing dataset based on the graph in Figure~\ref{fig:housing_graph_1}.
+  \centering
+  \caption{Discretization result of Housing dataset based on the graph in Figure~\ref{fig:housing_graph_1}.
 The first twelve rows show the numbers of intervals after discretization by the three method.
@@
 \begin{figure}[ht]
+\centering
     % \begin{tabular}{cc}
@@
 \begin{figure}[ht]
+\centering
      %\begin{tabular}{cc}
@@
     % \begin{tabular}{cc}
-      \input{graph_housing_2}
+    \centering
+    \scalebox{0.8}{
+      \input{graph_housing_2}}
     % \end{tabular}
@@
 To quantatively discuss the sensitivity of the three methods, consider the Bayesian network in Figure \ref{fig:exp_discuss}, where $X$ is continuous-valued and $P_1$ and $P_2$ is discrete-valued.
-Let $P = \{  P_1, P_2 \}$.
+Let $\Pi_X = \{  P_1, P_2 \}$.
 Assume $D_X = \{1.0,2.0,3.0, \ldots N \}$.
 Therefore, the corresponding objective functions to discretize $X$ in the three methods are:
+{\begin{small}
 \begin{equation}
 \begin{aligned}
-\text{Obj}_{\text{MDL}} & = Z_1 \cdot k + \log(N) \cdot \sum^k_{i=1} \sum^{J_P}_{j=1} I(a^*_i, (p_1,p_2)_j) \\
-\text{Obj}_{\text{Bayesian}} &= Z_2 \cdot k + \log {{n_i + J_P - 1}\choose{J_P -1}} + \sum^k_{i=1} \log \left(   {{n_i !}\over{n^{(P)}_{i,1}! n^{(P)}_{i,2}! \cdots n^{(P)}_{i,J_P}!    }} \right) \\
-\text{Obj}_{\text{Heuristic}} &= Z_2 \cdot k + \log {{n_i + J_{P_1} - 1}\choose{J_{P_1} -1}} + \log {{n_i + J_{P_2} - 1}\choose{J_{P_2} -1}} +\\
-& \sum^k_{i=1}  \left[ \log \left(   {{n_i !}\over{n^{(P_1)}_{i,1}!
+\text{Obj}_{\text{MDL}} & = \overbrace{Z_1 \cdot k + \log(k) + \log {{N +k - 1}\choose{k -1}} }^{\text{Penalty Term}}+   \overbrace{\log(N) \cdot I(X^*, \Pi_X)}^{\text{Disc. Edge Positions Term}} \\
+\text{Obj}_{\text{Bayesian}} &= \overbrace{Z_2 \cdot k + \log {{n_i + J_P - 1}\choose{J_P -1}}}^{\text{Penalty Term}} + \overbrace{\sum^k_{i=1} \log \left(   {{n_i !}\over{n^{(P)}_{i,1}!
+n^{(P)}_{i,2}!
+\cdots n^{(P)}_{i,J_P}!
+}} \right) }^{\text{Disc.
+Edge Positions Term}}\\
+\text{Obj}_{\text{Heuristic}} &= \overbrace{Z_2 \cdot k + \log {{n_i + J_{P_1} - 1}\choose{J_{P_1} -1}} + \log {{n_i + J_{P_2} - 1}\choose{J_{P_2} -1}} }^{\text{Penalty Term}}+\\
+& \overbrace{\sum^k_{i=1}  \left[ \log \left(   {{n_i !}\over{n^{(P_1)}_{i,1}!
 n^{(P_1)}_{i,2}!
 \cdots n^{(P_1)}_{i,J_{P_1}}    }} \right)  + \log \left(   {{n_i !}\over{n^{(P_2)}_{i,1}!
-n^{(P_2)}_{i,2} \cdots n^{(P_2)}_{i,J_{P_2}} }} \right) \right]
+n^{(P_2)}_{i,2} \cdots n^{(P_2)}_{i,J_{P_2}} }} \right) \right]}^{\text{Disc.
+Edge Positions Term}}
 \end{aligned}
 \end{equation}
-
+\end{small}}
+, where $Z_1$ and $Z_2$ are two constants, $k$ is the number of intervals after discretization, $X^*$ is the discretized version of $X$, and $I(X^*, \Pi_X)$ is the mutual information between $X^*$ and its parent variables.
+Note that the third term in $\text{Obj}_{\text{MDL}}$ is approximated by $H(p)$ as in Equation \ref{eqn:MDL} in the original paper \citep{Friedman_1996}.
+
+The sensitivities toward the value distribution in $D_{\Pi_X}$ are determined by the `` Disc.
+Edge Positions Term" in the three objective functions.
+Since the penaltis of the numbers of intervals after discretization in the three objective functions take the similar form, if the `` Disc.
+Edge Positions Term" varies more severely due to different positions of discretization edges, then the corresponding method is more sensitive.
+The `` Disc.
+Edge Positions Term" in $\text{Obj}_{\text{MDL}}$, which is made out of the mutual information, varies less severely than the terms in $\text{Obj}_{\text{Bayesian}}$ and $\text{Obj}_{\text{Heuristic}}$, since it senses the distribution in $D_{\Pi_X}$ by empirical probability distributions, instead of the factorial terms such in $\text{Obj}_{\text{Bayesian}}$ and $\text{Obj}_{\text{Heuristic}}$.
+Furthermore, the `` Disc.
+Edge Positions Term" in $\text{Obj}_{\text{Heuristic}}$ varies more aggressively than the term in $\text{Obj}_{\text{Bayesian}}$.
+Therefore, the MDL method is less sensitive and the heuristic is over sensitive toward the value distributions in other variables.
+The effect of sensitivity can be shown as the numbers of intervals after discretization in the previous experiment.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2015-11-18 BN_discretizer_paper.tex
Add conclusion

@@
 The first five rows are discretization edges on each continuous variable.
-The sixth row is the log-likelihood of the dataset based on the discretization results.
+The last row is the log-likelihood of the dataset based on the discretization results.
 The discretization result for the heuristic matches that for the optimal Bayesian approach.
@@
 
-\subsection{Experiment Discussions}
+\subsection{Discussions}
 \label{subsec:discuss_exp}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Conclusion}
+In this work, a new method for discretizating continuous varibles in Bayesian networks has been proposed.
+It is compatible with the K2 structure learning, i.e., it can discretize continuous variables along with the edge-adding process of the K2.
+Therefore, a discrete-valued Bayesian network can be learned from mix data.
+
+Experiments on three real-world dataset show that the new method returns to a better discretization result than previous research in terms of likelihood.
+The discretization edges and the resulting marginal probabilities of discretized regions returned by the new method can match the row data well.
+
+This work can extend the usage of Bayesian networks in science and engineering, especially for the fields that require discrete-valued variables but the learning data is mixed and numerical.
+In the future, we plan to generalize the work to the datast that has high dimensional variables, for example, 3 dimensional positions of drones, which makes the sorting in Equation \ref{eq:p_M} fails.
+
 %\begin{acknowledgements}

### 2015-11-18 BN_discretizer_paper.tex
woo

--- 2015-11-18 BN_discretizer_paper.tex
@@
 
-\begin{table}[H]
-  \centering
-  \begin{tabular}{@{}ccl@{}}
-    \toprule
-    Current & Mykel & Description \\
-    \midrule
-    % $G$ & $G$ & BN graph structure \\
-    % $P$ & $P$ & discrete probability \\
-    % $p$ & $p$ & probability density \\
-    % $D$ & $D$ & available data \\
-    $|D|$ & $n$ & number of variables in the BN \\
-    $D_{\bm{Y}}$ & & subset of data associated with $\bm{Y}$ \\
-    $X$ & $X_{1:n}$ & variables in BN (discrete) \\
-    $x_{1:n}$ & $x_{1:n}$ & a specific instance of vars in BN \\
-    $x'_{1:n}$ &  & unique instances of var in BN \\
-        & $r_i$ & number of instantiations of $i$th var \\
-    $J_p$ & $q_i$ & number of instantiations of parents of $i$th var \\
-        &       & $ = 1$ if no parents \\
-    $\brock{\Pi_{X_i}}_j$ & $\pi_{ij}$ & $j$th instantiation of $i$th var \\
-        & $\theta_{ijk}$ & probability of $i$th var $= k$ given $j$th parental inst. \\
-    $\Theta$ & $\bm{\theta}$ & set of all (non-independent) probability parameters \\
-    $n_{i,j}^{(k)}$ & $m_{ijk}$ & observation counts \\
-    $n_{i,j,l}^{(k)}$ & $m_{ijk}$ & observation counts with $l$th instance of spouse\\
-    $\alpha_{ijk}$ & $\alpha_{ijk}$ & Dirichlet prior counts \\
-    $N_{ij}$ & $\alpha_{ij0}$ & sum over Dirichlet prior counts for $k$ \\
-        & $m_{ij0}$ & sum over observations counts for $k$ \\
-        & $\Gamma$ & the Gamma function \\
-    $N$ &          & is the number of samples in dataset \\
-    $N_i$ &          & counts for $i$th instance of a specific var \\
-    $\Pi_X$ & $\text{pa}_{x_i}$ & parents of a variable or instance \\
-    $n_C$ & & number of children of a variable \\
-    $H(~)$ & & a function \\
-    $I(~,~)$ & & mutual information \\
-    $X_i$ & & $i$th variable in BN, may be cont or disc \\
-    $X_i^*$ & & discrete version of cont var \\
-    $E$ & & set of edges in BN \\
-    $\text{Pa}\paren{X_i}$, $n_p$ & & number of parents of $X_i$ \\
-    $f\paren{X_i, \Pi_{X_i}}$ & $f(G)$ & score function for K2 \\
-    $M_C$ & & discretization policy for $C$ \\
-    $C$ & & a continuous variable \\
-    $t_i$ & & the $i$th bin edge for a specific var \\
-    $d_i$ & & allowable discretization positions (between unique vals) \\
-    $k$ & & number of intervals for $M_C$ \\
-    $C_{1:N}$ & & sorted samples for $C$ \\
-    $n_i$ & & $n_1 = s_1$ and $n_i = s_{i} - s_{i-1}$ \\
-    $s_i$ & & $\sum_{j=1}^k n_j$ and $s_k = N$, $s_0 = 0$ \\
-    $C_i$ & & $i$th child of a specific var \\
-    $\boldsymbol{S_i}$ & & set of spouses associated with $i$th child of specific var \\
-    $L$ & & largest cardinality among discrete variables in BN \\
-    $I_q$ & & an interval from $u \rightarrow v$ \\
-    $v'_\text{max}$ & & largest cardinality of variables that directly connect to $X$ \\
-    $S[]$ & &  optimal objective value of subproblems with instances from $1$ to $u$ \\
-    \bottomrule
-  \end{tabular}
-\end{table}
+% \begin{table}[H]
+%   \centering
+%   \begin{tabular}{@{}ccl@{}}
+%     \toprule
+%     Current & Mykel & Description \\
+%     \midrule
+%     % $G$ & $G$ & BN graph structure \\
+%     % $P$ & $P$ & discrete probability \\
+%     % $p$ & $p$ & probability density \\
+%     % $D$ & $D$ & available data \\
+%     $|D|$ & $n$ & number of variables in the BN \\
+%     $D_{\bm{Y}}$ & & subset of data associated with $\bm{Y}$ \\
+%     $X$ & $X_{1:n}$ & variables in BN (discrete) \\
+%     $x_{1:n}$ & $x_{1:n}$ & a specific instance of vars in BN \\
+%     $x'_{1:n}$ &  & unique instances of var in BN \\
+%         & $r_i$ & number of instantiations of $i$th var \\
+%     $J_p$ & $q_i$ & number of instantiations of parents of $i$th var \\
+%         &       & $ = 1$ if no parents \\
+%     $\brock{\Pi_{X_i}}_j$ & $\pi_{ij}$ & $j$th instantiation of $i$th var \\
+%         & $\theta_{ijk}$ & probability of $i$th var $= k$ given $j$th parental inst. \\
+%     $\Theta$ & $\bm{\theta}$ & set of all (non-independent) probability parameters \\
+%     $n_{i,j}^{(k)}$ & $m_{ijk}$ & observation counts \\
+%     $n_{i,j,l}^{(k)}$ & $m_{ijk}$ & observation counts with $l$th instance of spouse\\
+%     $\alpha_{ijk}$ & $\alpha_{ijk}$ & Dirichlet prior counts \\
+%     $N_{ij}$ & $\alpha_{ij0}$ & sum over Dirichlet prior counts for $k$ \\
+%         & $m_{ij0}$ & sum over observations counts for $k$ \\
+%         & $\Gamma$ & the Gamma function \\
+%     $N$ &          & is the number of samples in dataset \\
+%     $N_i$ &          & counts for $i$th instance of a specific var \\
+%     $\Pi_X$ & $\text{pa}_{x_i}$ & parents of a variable or instance \\
+%     $n_C$ & & number of children of a variable \\
+%     $H(~)$ & & a function \\
+%     $I(~,~)$ & & mutual information \\
+%     $X_i$ & & $i$th variable in BN, may be cont or disc \\
+%     $X_i^*$ & & discrete version of cont var \\
+%     $E$ & & set of edges in BN \\
+%     $\text{Pa}\paren{X_i}$, $n_p$ & & number of parents of $X_i$ \\
+%     $f\paren{X_i, \Pi_{X_i}}$ & $f(G)$ & score function for K2 \\
+%     $M_C$ & & discretization policy for $C$ \\
+%     $C$ & & a continuous variable \\
+%     $t_i$ & & the $i$th bin edge for a specific var \\
+%     $d_i$ & & allowable discretization positions (between unique vals) \\
+%     $k$ & & number of intervals for $M_C$ \\
+%     $C_{1:N}$ & & sorted samples for $C$ \\
+%     $n_i$ & & $n_1 = s_1$ and $n_i = s_{i} - s_{i-1}$ \\
+%     $s_i$ & & $\sum_{j=1}^k n_j$ and $s_k = N$, $s_0 = 0$ \\
+%     $C_i$ & & $i$th child of a specific var \\
+%     $\bm{S}_i$ & & set of spouses associated with $i$th child of specific var \\
+%     $L$ & & largest cardinality among discrete variables in BN \\
+%     $I_q$ & & an interval from $u \rightarrow v$ \\
+%     $v'_\text{max}$ & & largest cardinality of variables that directly connect to $X$ \\
+%     $S[]$ & &  optimal objective value of subproblems with instances from $1$ to $u$ \\
+%     \bottomrule
+%   \end{tabular}
+% \end{table}
 
@@
 The second is to use nonparametric distributions, such as particle representations and Gaussian processes \todo{[cite]}.
-\todo{These have the advantage of BLAH BLAH, and their parameter set grows lineary with the amount of data.}
+Unlike parametric methods, nonparametric methods do not make assumptions about the probability distributions being used.
+Parametric models have a fixed number of parameters, whereas the number of parameters in a nonparametric model grow with the amount of training data.
 
@@
 Their approach selects a discretization policy that minimizes the sum of the description lengths of the discretized Bayesian network and the information necessary for recovering the continuous values from the discretized data.
-\todo{Results in this work suggest that the MDL method suffers from....}
+Results in this work suggest that the MDL method suffers from \todo{fill this out.}
 
@@
 
-\todo{
-Introduce P, C, and S for parents
-}
-
 \subsection{Structure Learning}
@@
 Score-based structure learning methods over discrete variables commonly evaluate candidate structures according to their likelihood against a dataset $D$.
-Let $m_{ij}^{(k)}$ be the number of times $X_i = k$ given $\bm{\pi}_{ij}$ in $D$.
+Let $\beta_{ij}^{(k)}$ be the number of times $X_i = k$ given $\bm{\pi}_{ij}$ in $D$.
 The likelihood is given by
@@
 \begin{equation}
-P(D\mid \bm{\theta}, G) = \prod_{i=1}^n \prod_{j=1}^{q_i} \prod_{k=1}^{r_i} \brock{\theta_{ij}^{(k)}}^{m_{ij}^{(k)}}\text{.}
+P(D\mid \bm{\theta}, G) = \prod_{i=1}^n \prod_{j=1}^{q_i} \prod_{k=1}^{r_i} \brock{\theta_{ij}^{(k)}}^{\beta_{ij}^{(k)}}\text{.}
 \end{equation}
@@
     }{
-      \Gamma\paren{\alpha_{ij}^{(0)} + m_{ij}^{(0)}}
+      \Gamma\paren{\alpha_{ij}^{(0)} + \beta_{ij}^{(0)}}
     }
@@
     \frac{
-      \Gamma\paren{\alpha_{ij}^{(k)} + m_{ij}^{(k)}}
+      \Gamma\paren{\alpha_{ij}^{(k)} + \beta_{ij}^{(k)}}
     }{
@@
 \begin{equation}
-\alpha_{ij}^{(0)} = \sum_{k=1}^{r_i} \alpha_{ij}^{(k)} \quad \qquad m_{ij}^{(0)} = \sum_{k=1}^{r_i} m_{ij}^{(k)}\text{.}
+\alpha_{ij}^{(0)} = \sum_{k=1}^{r_i} \alpha_{ij}^{(k)} \quad \qquad \beta_{ij}^{(0)} = \sum_{k=1}^{r_i} \beta_{ij}^{(k)}\text{.}
 \end{equation}
@@
 The discretization policy discretizes $\cX$ into $k$ intervals.
-Let the samples of $\cX$ in a given dataset $D$ be sorted in ascending order, ${\cx_{1:n} = \curly{\cx_1 \leq \cx_2 \leq \ldots \leq \cx_n}}$, and let the unique values be ${\cu_{1:n} = \curly{\cu_1 \leq \cu_2 \leq \ldots \leq \cu_n}}$.
-The index of the last occurence of $\cu_i$ in $\cx$ is denoted $s_i$.
+Let the samples of $\cX$ in a given dataset $D$ be sorted in ascending order, ${\cx_{1:n} = \curly{\cx_1 \leq \cx_2 \leq \ldots \leq \cx_n}}$, and let the unique values be ${\cu_{1:m} = \curly{\cu_1 \leq \cu_2 \leq \ldots \leq \cu_m}}$.
+The index of the last occurence of $\cu_i$ in $\cx_{1:n}$ is denoted $s_i$.
 
@@
 In this work they are restricted to the midpoints between unique ascending instances of $\cX$.
-Thus, each edge $e_i = \paren{\cu_{s_{j+1}} - \cu_{s_j}}/2$ for some $s_j$.
-An integer representation of $\Lambda_{\cX}$ can thus be written $\Lambda_{\cX} = \curly{\lambda_1 < \lambda_2  < \ldots < \lambda_k}$, where $\lambda_1 = s_1$ and $\lambda_i \in s_{1:|\cu|}$.
+Thus, each edge $e_i = \paren{\cu_{s_j} + \cu_{s_{j+1}}}/2$ for some $s_j$.
+An integer representation of $\Lambda_{\cX}$ can thus be written $\Lambda_{\cX} = \curly{\lambda_1 < \lambda_2  < \ldots < \lambda_k}$, where $\lambda_1 = s_1$ and $\lambda_i \in s_{1:m}$.
+
+Finally, when discussing the discretization of a particular continuous variable $\cX$, let $P_i$ be the $i$th parent of $\cX$, let $C_i$ be the $i$th child of $\cX$, and let $\bm{S}_i$ be set of spouses of $\cX$ corresponding to the $i$th child.
+Context should make it clear when $P$ refers to a discrete probability and when it refers to a variable's parent.
 
@@
 This section covers the discretization of a single continuous variable $\cX$ in a Bayesian network where all other variables are discrete.
-Let $n_p$ and $n_c$ respectively refer to the number of parents and number of children of $X$.
-Each child $C_i$ of $X$ may possess other parents, referred to as spouses of $X$.
-The set of spouses of $X$ is denoted $\boldsymbol{S_i}$.
-
-Let $D$ be a dataset of $N$ samples from which the discretization will be learned, sorted in ascending order according to $X$.
-Let $D_{\boldsymbol{Y}}$ will refer to the data instances associated with variables $\boldsymbol{Y}$, thus $D_X = \{ x_1,x_2,x_3,\ldots,x_N \}$.
-In order to facilitate understanding, we temporarily assume all values in $D_X$ are unique, that is, $x_1 < x_2 < \ldots < x_N$.
-It follows that a discretization policy $M$ on $X$ can be written as $M_X = \brock{n_1,n_2,\ldots,n_k}$, where $k$, $n_1$, $n_2$, $\ldots,n_k$ are positive integers satisfying $N = \sum_{i=1}^k n_i$.
-\mykel{$\bigstar$ This conflicts with Section 3.2, right?}
-An optimal discretization policy maximizes $P(M)\cdot P(D\mid M)$ for some prior $P(M)$ and likelihood $P(D\mid M)$.
+An optimal discretization policy for a dataset $D$ maximizes $P(\Lambda)\cdot P(D\mid \Lambda)$ for some prior $P(\Lambda)$ and likelihood $P(D\mid \Lambda)$.
+
+% Let $n_p$ and $n_c$ respectively refer to the number of parents and number of children of $X$.
+
+% Let $D$ be a dataset of $N$ samples from which the discretization will be learned, sorted in ascending order according to $X$.
+% Let $D_{\boldsymbol{Y}}$ will refer to the data instances associated with variables $\boldsymbol{Y}$, thus $D_X = \{ x_1,x_2,x_3,\ldots,x_N \}$.
+% In order to facilitate understanding, we temporarily assume all values in $D_X$ are unique, that is, $x_1 < x_2 < \ldots < x_N$.
+% It follows that a discretization policy $\Lambda$ on $X$ can be written as $M_X = \brock{n_1,n_2,\ldots,n_k}$, where $k$, $n_1$, $n_2$, $\ldots,n_k$ are positive integers satisfying $N = \sum_{i=1}^k n_i$.
 
@@
 
-The following four principles for the optimal discretization policy, motivated by MODL, enable the formulation of $P(M)$ and $P(D \mid M)$:
+Let $D_{\bm{Y}}$ be the subset of the data corresponding to $\bm{Y}$.
+Four principles for the optimal discretization policy enable the formulation of $P(\Lambda)$ and $P(D_{-\cX} \mid \Lambda)$, where the probability of the data associated with the target variable $P(D_{\cX})$ is already captured in $P(\Lambda)$.
+The four principles, motivated by MODL \todo{and Lustgarden}, are:
+
 \begin{enumerate}
-\item A discretization edge located at $(x_i + x_{i+1})/2$ has probability
-\begin{equation}
-1 - {\exp(- L \cdot {{x_{i+1} - x_i}\over{x_N - x_1}})},
-\end{equation}
-where $L$ is the largest cardinality number of discrete variables in $X$'s Markov blanket. \tim{Where does this come from? Is there an intuitive explanation?}\mykel{$\bigstar$}
-\item For a given interval of $M$, every distribution of $\Pi_X$ is equiprobable.
-\item For each pair of $(C_i,\boldsymbol{S_i})$ and a given interval of $M$, every distribution of $C_i$ with a value of $\boldsymbol{S_i}$ is equiprobable.\mykel{$\bigstar$}
-\item The distributions of each $C_i$ and $\Pi_X$ in each interval of $M$ with each value of $\boldsymbol{S_i}$ are independent from each other.\mykel{$\bigstar$}
+\item The prior probability of a discretization edge between two consecutive unique values $\cu_i$ and $\cu_{i+1}$ is proportional to their difference:
+
+  \begin{equation}
+  1 - {\exp(- L \cdot {\frac{\cu_{i+1} - \cu_i}{\cu_m - \cu_1}})}\text{,}
+  \end{equation}
+
+where $L$ is the largest number of intervals among discrete variables in $\cX$'s Markov blanket.
+This encourages edges between well-separated values over edges between closely packed samples.
+
+\item For a given discretization interval, every distribution over $\Pa_{\cX}$ is equiprobable.
+\item For each pair $\anglebrackets{C_i,\bm{S}_i}$ and a given discretization interval, every distribution over $C_i$ given an instance of $\bm{S}_i$ is equiprobable.
+\item The distributions over each child and each parent in each discretization interval with each instance of $\bm{S}_i$ are independent from each other.
 \end{enumerate}
@@
   \label{eq:p_M}
-  P(M) = \prod_{i=1}^k \curly{ \brock{1 - {\exp(- L \cdot {{x_{s_i+1} - x_{s_i}}\over{x_N - x_1}})}} \cdot \exp\paren{L \cdot {{x_{s_{i}} - x_{s_{i-1} + 1}}\over{x_N - x_1}}}},
-\end{equation}
-
-\noindent
-where $s_i = \sum_{j=1}^k n_j$ and $s_k = N$, $s_0 = 0$.
-The Bayesian network graph structure causes the likelihood term $P(D \mid M)$ to factorizes according to $X$'s Markov blanket:
+  P(\Lambda) = \prod_{i=1}^k
+  \curly{
+    \brock{
+      1 - \exp\paren{
+        - L \cdot \frac{
+                         \cu_{i+1} - \cu_i
+                       }{
+                         \cu_m - \cu_1
+                        }
+      }
+    } \cdot \exp\paren{
+      L \cdot \frac{\cx_{s_{i}} - \cx_{s_{i-1} + 1}}{\cx_n - \cx_1}}
+    }\text{.}
+\end{equation}
+
+The Bayesian network graph structure causes the likelihood term $P(D \mid \Lambda)$ to factorizes according to $\cX$'s Markov blanket:
 
@@
   \label{eq:p_D_given_M}
-  P\paren{D \mid M} \propto P\paren{D_{\Pi_x} \mid M} \cdot \prod_{i = 1}^{n_c} P\paren{D_{C_i} \mid M, D_{\boldsymbol{S_i}}}\text{.}
-\end{equation}
-
-For example, in Figure~\ref{fig:example_factorization}, the corresponding $P(D \mid M)$ is factorized according to
-\begin{equation}
-P\paren{D_{ P_1,P_2,P_3 } \mid M} \cdot P\paren{ D_{ C_1 } \mid M,D_{\boldsymbol{S_1}}} \cdot P\paren{D_{C_2} \mid M,D_{ S_2  }}\text{.}
+  P\paren{D_{-\cX} \mid \Lambda} \propto P\paren{D_{\Pa_\cX} \mid \Lambda} \cdot \prod_{C_i} P\paren{D_{C_i} \mid \Lambda, D_{\bm{S}_i}}\text{.}
+\end{equation}
+
+For example, in Figure~\ref{fig:example_factorization}, $P(D_{-\cX} \mid \Lambda)$ factors according to
+
+\begin{equation}
+  P\paren{D_{P_1,P_2,P_3} \mid \Lambda} \cdot P\paren{ D_{ C_1 } \mid \Lambda, D_{\bm{S}_1} } \cdot P\paren{D_{C_2} \mid \Lambda, D_{\bm{S}_2}}\text{.}
 \end{equation}
@@
 \begin{figure}[ht]
-  \label{fig:example_factorization}
+  \centering
   \begin{tabular}{cc}
@@
   \end{tabular}
-  \caption{Factorization of $P(D \mid M)$}
+  \caption{Factorization of $P(D \mid \Lambda)$}
+  \label{fig:example_factorization}
 \end{figure}
 
-The concept behind the factorization also the motivation behind forward sampling in a Bayesian network.
-The parents of $X$ are independent of the children given $X$.
-The parents are not necessarily individually independent, and thus the parental term $P(D_{\Pi_x} \mid M)$ cannot be factored further.
-The children of $X$ are similarly independent given $X$ and its spouses $\boldsymbol{S_i}$, leading to their factored product $\prod_{i = 1}^{n_c} P(D_{C_i} \mid M, D_{\boldsymbol{S_i}})$.
-Each component in the decomposition be evaluated based on a discretization policy $M = [n_1,n_2,\ldots,n_k]$ and dataset $D$.
-
-\subsubsection{Evaluation of $P(D_{\Pi_x} \mid M)$}
+The concept behind the factorization is also the motivation behind forward sampling in a Bayesian network.
+The parents of $\cX$ are independent of the children given $\cX$.
+The parents are not necessarily individually independent, and thus the parental term $P(D_{\Pa_{\cX}} \mid \Lambda)$ cannot be factored further.
+The children of $\cX$ are similarly independent given $\cX$ and the corresponding spouses, leading to their factored product $\prod_{C_i} P(D_{C_i} \mid \Lambda, D_{\bm{S}_i})$.
+Each component in the decomposition can be evaluated given a discretization policy and a dataset.
+
+\subsubsection{Evaluation of $P\paren{D_{\Pa_{\cX}} \mid \Lambda}$}
+
 Let $J_P = \prod_{i=1}^{n_p} \| P_i \|$. It follows that
@@
   \label{eq:likelihood_one}
-P(D_{\Pi_X} \mid M) = \prod_{i=1}^k  {{1}\over{{n_i + J_P - 1}\choose{J_P -1}}}
-{{1}\over{ {{{n}_i}!}\over{ {n^{(p)}_{i,1} !} {n^{(p)}_{i,2} !} \cdots {n^{(p)}_{i,J_P} !}}  }}\text{,}
+  P\paren{D_{\Pa_{\cX}} \mid \Lambda} = \prod_{i=1}^k
+    \frac{1}{{{n_i + J_P - 1}\choose{J_P - 1}}}
+    \frac{1}{
+      \frac{
+        {n_i}!
+      }{
+        {n^{(p)}_{i,1}}! \; {n^{(p)}_{i,2}}! \; \cdots \; {n^{(p)}_{i,J_P}}!
+      }
+    }\text{,}
 \end{equation}
@@
 
-\subsubsection{Evaluation of $P(D_{C_i} \mid M, D_{\boldsymbol{S_i}})$}
+\subsubsection{Evaluation of $P(D_{C_i} \mid \Lambda, D_{\bm{S}_i})$}
 For each pair $(C_j, \boldsymbol{S_j})$, let $\|C_j \| = J_j$ and $\| \boldsymbol{S_j} \| = L_j = \prod_{v \in \boldsymbol{S_j}} \| v \|$. It follows that
@@
 \label{eq:likelihood_two}
-P(D_{C_j}  \mid M, D_{S_j}) =
+P(D_{C_j}  \mid \Lambda, D_{S_j}) =
 \prod_{i=1}^{k} \prod_{l=1}^{L_j} {{1}\over{{n_{i,l} + J_j - 1}\choose{J_j-1}}}
@@
 \label{eq:likelihood_three}
-P(D_{C_j}  \mid M) =
+P(D_{C_j}  \mid \Lambda) =
 \prod_{i=1}^{k}  {{1}\over{{n_{i} + J_j - 1}\choose{J_j-1}}}
@@
 The objective function can be formulated given equations \ref{eq:p_M}, \ref{eq:p_D_given_M}, \ref{eq:likelihood_one}, and \ref{eq:likelihood_three}.
-The log-inverse of $P(M) \cdot P(D|M)$ is minimized for computational convenience:
+The log-inverse of $P(\Lambda) \cdot P(D|\Lambda)$ is minimized for computational convenience:
 
@@
 Every midpoint between two nonequal consecutive values in $D_X$ is a candidate discretization edge.
-Let ${D'_X} = \brock{x'_1,x'_2,\ldots,x'_M}$ be the set of unique values of $D_X$ sorted in ascending order, where $M$ is the number unique values in $D_X$.
+Let ${D'_X} = \brock{x'_1,x'_2,\ldots,x'_\Lambda}$ be the set of unique values of $D_X$ sorted in ascending order, where $\Lambda$ is the number unique values in $D_X$.
 Recall that $D_X$ is also sorted.
-Let $b = \brock{b_0,b_1,b_2,\ldots,b_M}$ be an increasing sequence of integers marking the repeated value intervals in $D_X$ such that $b_0 = 0$ and $x_{b_{i-1} + 1} = x_{b_{i-1} + 2} = \ldots = x_{b_i} = x'_i$.
+Let $b = \brock{b_0,b_1,b_2,\ldots,b_\Lambda}$ be an increasing sequence of integers marking the repeated value intervals in $D_X$ such that $b_0 = 0$ and $x_{b_{i-1} + 1} = x_{b_{i-1} + 2} = \ldots = x_{b_i} = x'_i$.
 By this definition, the allowable discretization positions are $d_i = \paren{x_{b_{i}} + x_{{b_i}+1}}/2$ for all \todo{$i = 1,2,\ldots,M-1$}.
@@
 \State $H \leftarrow$ an $N \times N$ matrix such that $H[u,v] = h(u,v)$ per Algorithm~\ref{alg:h} in the appendix
-\State $b \leftarrow$ the increasing sequence of $M$ integers as previously defined
+\State $b \leftarrow$ the increasing sequence of $\Lambda$ integers as previously defined
 \State $L \leftarrow$ the largest cardinality over all discrete variables in the Markov blanket of $X$
@@
 \EndFor
- \State \Return $M$
+ \State \Return $\Lambda$
 \EndFunction
@@
     \State $cycle \leftarrow 0$
-    \While {$M$ is not converged  \textbf{and} $cycle \leq u_{cycle}$}
+    \While {$\Lambda$ is not converged  \textbf{and} $cycle \leq u_{cycle}$}
       \State {$cycle  \leftarrow cycle  + 1$}
@@
     \EndWhile
-    \State \Return $M$
+    \State \Return $\Lambda$
   \EndFunction
@@
     \EndFor
-    \State \Return $G$, $M$
+    \State \Return $G$, $\Lambda$
   \EndFunction
@@
 
-\section{Experiments}
-\label{sec:experiments}
-
-This section describes experiments conducted to evaluate the proposed methods.
-All experiments were run on datasets from the publically available Irvine machine learning repository \citep{Lichman_2013}.
-Variables are labelled alphabetically in the order given on the dataset information webpage.
-Subscripts inducate the number of discretized intervals.
-Shaded nodes are originally discrete and unshaded nodes are originally continuous.
-
-For each dataset, the experiment consists of two parts.
-In the first part, the Bayesian network structure is known in advance, which is obtained by equal-width prediscretization and the K2 algorithm.
-In the second part, the Bayesian netowrk structure is not provided in advance, and it is learned during the discretization process.
-
-The discretizations are compared using the mean cross validated log-likelihood of the data set $D$ given the resulting graph structure $G$ and discretization policy set $\discset$.
-The log-likelihood contains two components,
-
-\begin{equation}
-\ln p(D\mid G, \discset) = \ln P(D^*\mid G) + \ln p(D\mid \discset, D^*)\text{,}
-\end{equation}
-
-\noindent
-where $D$ is the original dataset and $D^*$ is the dataset discretized according to $\discset$.
-The log-likelihood of the discretized dataset is the Bayesian score (Equation ~\ref{eq:BayesianScore}) evaluated with a uniform prior.
-The log-likelihood of the original dataset given the discrete dataset is
-
-\begin{equation}
-  \ln p(D\mid \discset, D^*) = \sum_{i=1}^n \sum_{j=1}^{q_i} \sum_{k=1}^{r_i} m_{ijk} \ln\paren{
-    \frac{
-      1
-    }{
-      \discset^{(ij)}_{k+1} - \discset^{(ij)}_{k}
-    }
-  }\text{.}
-\end{equation}
-
-The proposed Bayesian discretization method is compared against MDL.
-For a Bayesian network with a single continuous variable $X$, the MDL objective function is
-
-\begin{equation}
-\begin{aligned}
-\frac{1}{2} \log(N) \left\lbrace  \lvert \Pi_{X_i} \rvert (\lvert X^*_i \rvert - 1) +
- {\sum_{j,X_i \in \Pi_{X_i}}} \lvert \Pi_{X^*_j} \rvert (\lvert X_j \rvert - 1) \right\rbrace + \log(\lvert {X^*_i} \rvert) \\
- + (N_i-1) H \left( {{|X^*_i| - 1}\over{N_i -1}}  \right) -N \cdot \left[ I(X^*_i,\Pi_{X_i}) + {\sum_{j,X_i \in \Pi_{X_i}}} I(X_j, \Pi_{X^*_j}) \right]\text{,}
-\end{aligned}
-\end{equation}
-
-where $I(A,B)$ is the mutual information between the discrete variables $A$ and $B$, ${H(p) = -p \log(p) - (1-p) \log(1-p)}$ \tim{does $H(p)$ have a name?
-Entropy?}, and \todo{$X^*_i$ is the discretized version of the $i$th sample of $X$}.
-The optimal discretization policy is found with dynamic programming in a similar manner as with the Bayesian method.
-
-\subsection{Auto MPG Dataset}
-\label{subsec:auto}
-
-In this subsection, two experiments are conducted on the Auto MPG dataset from the Irvine repository \citep{Lichman_2013}.
+% \section{Experiments}
+% \label{sec:experiments}
+
+% This section describes experiments conducted to evaluate the proposed methods.
+% All experiments were run on datasets from the publically available Irvine machine learning repository \citep{Lichman_2013}.
+% Variables are labelled alphabetically in the order given on the dataset information webpage.
+% Subscripts inducate the number of discretized intervals.
+% Shaded nodes are originally discrete and unshaded nodes are originally continuous.
+
+% For each dataset, the experiment consists of two parts.
+% In the first part, the Bayesian network structure is known in advance, which is obtained by equal-width prediscretization and the K2 algorithm.
+% In the second part, the Bayesian netowrk structure is not provided in advance, and it is learned during the discretization process.
+
+% The discretizations are compared using the mean cross validated log-likelihood of the data set $D$ given the resulting graph structure $G$ and discretization policy set $\discset$.
+% The log-likelihood contains two components,
+
+% \begin{equation}
+% \ln p(D\mid G, \discset) = \ln P(D^*\mid G) + \ln p(D\mid \discset, D^*)\text{,}
+% \end{equation}
+
+% \noindent
+% where $D$ is the original dataset and $D^*$ is the dataset discretized according to $\discset$.
+% The log-likelihood of the discretized dataset is the Bayesian score (Equation ~\ref{eq:BayesianScore}) evaluated with a uniform prior.
+% The log-likelihood of the original dataset given the discrete dataset is
+
+% \begin{equation}
+%   \ln p(D\mid \discset, D^*) = \sum_{i=1}^n \sum_{j=1}^{q_i} \sum_{k=1}^{r_i} m_{ijk} \ln\paren{
+%     \frac{
+%       1
+%     }{
+%       \discset^{(ij)}_{k+1} - \discset^{(ij)}_{k}
+%     }
+%   }\text{.}
+% \end{equation}
+
+% The proposed Bayesian discretization method is compared against MDL.
+% For a Bayesian network with a single continuous variable $X$, the MDL objective function is
+
+% \begin{equation}
+% \begin{aligned}
+% \frac{1}{2} \log(N) \left\lbrace  \lvert \Pi_{X_i} \rvert (\lvert X^*_i \rvert - 1) +
+%  {\sum_{j,X_i \in \Pi_{X_i}}} \lvert \Pi_{X^*_j} \rvert (\lvert X_j \rvert - 1) \right\rbrace + \log(\lvert {X^*_i} \rvert) \\
+%  + (N_i-1) H \left( {{|X^*_i| - 1}\over{N_i -1}}  \right) -N \cdot \left[ I(X^*_i,\Pi_{X_i}) + {\sum_{j,X_i \in \Pi_{X_i}}} I(X_j, \Pi_{X^*_j}) \right]\text{,}
+% \end{aligned}
+% \end{equation}
+
+% where $I(A,B)$ is the mutual information between the discrete variables $A$ and $B$, ${H(p) = -p \log(p) - (1-p) \log(1-p)}$, and \todo{$X^*_i$ is the discretized version of the $i$th sample of $X$}.
+% The optimal discretization policy is found with dynamic programming in a similar manner as with the Bayesian method.
+
+% \subsection{Auto MPG Dataset}
+% \label{subsec:auto}
+
+% In this subsection, two experiments are conducted on the Auto MPG dataset from the Irvine repository \citep{Lichman_2013}.
 The dataset has \num{392} instances after deleting the six instances with missing data, and eight variables.
@@
 
-\subsubsection{Discretization with fixed Structure}
-\label{subsubsec:auto_exp1}
-
-The optimal Bayesian approach and the MDL discretization method are tested on Auto MPG data given the network network in Fig.
+% \subsubsection{Discretization with fixed Structure}
+% \label{subsubsec:auto_exp1}
+
+% The optimal Bayesian approach and the MDL discretization method are tested on Auto MPG data given the network network in Fig.
 \ref{fig:auto_graph_1}.
@@
 
-\begin{figure}[ht]
-  \centering
-   \input{graph_autocar_1}
-   \caption{Structure from prediscretized K2 structure learning to compare the methods for Auto MPG dataset}
-  \label{fig:auto_graph_1}
-\end{figure}
-
-Table \ref{table:auto_disc_table_1} shows the positions of discretization edges, and log-likelihood of 10-fold cross validation by three discretization methods.
+% \begin{figure}[ht]
+%   \centering
+%    \input{graph_autocar_1}
+%    \caption{Structure from prediscretized K2 structure learning to compare the methods for Auto MPG dataset}
+%   \label{fig:auto_graph_1}
+% \end{figure}
+
+% Table \ref{table:auto_disc_table_1} shows the positions of discretization edges, and log-likelihood of 10-fold cross validation by three discretization methods.
 For the Bayesian network in Fig.
@@
 
-\begin{table}[h]
-  \centering
-  \caption{Discretization results of Auto MPG dataset based on the graph in Fig.
+% \begin{table}[h]
+%   \centering
+%   \caption{Discretization results of Auto MPG dataset based on the graph in Fig.
 \ref{fig:auto_graph_1} by the three methods.
@@
 The MDL method is less sensitive to distribution of values of other variables and fails to return discretization edges.}
-  \input{table_autoMPG_1.tex}
-  \label{table:auto_disc_table_1}
-\end{table}
-
-Figure \ref{fig:auto_exp1_distr_1_3} compares the discretization result on continuous variables $A$ and $C$ with the raw data of Auto MPG data set.
+%   \input{table_autoMPG_1.tex}
+%   \label{table:auto_disc_table_1}
+% \end{table}
+
+% Figure \ref{fig:auto_exp1_distr_1_3} compares the discretization result on continuous variables $A$ and $C$ with the raw data of Auto MPG data set.
 The color of discretized area shows the probability of a sample being in the discretized area.
@@
 
-\begin{figure}[ht]
-      \input{graph_auto_exp1_distr_1_3}
-  \caption{Comparison of the raw data and discretization result on variable $A$ and $C$ by the optimal Bayesian approach.
+% \begin{figure}[ht]
+%       \input{graph_auto_exp1_distr_1_3}
+%   \caption{Comparison of the raw data and discretization result on variable $A$ and $C$ by the optimal Bayesian approach.
 The marginal probabilities of discretized areas match the distribution of the taw data very well.}
-  \label{fig:auto_exp1_distr_1_3}
-\end{figure}
-
-\subsubsection{Discretization while Learning Structure}
-\label{subsubsec:auto_exp2}
-
-If the network structure is not known in advance, it should be learned along with the discretization process.
+%   \label{fig:auto_exp1_distr_1_3}
+% \end{figure}
+
+% \subsubsection{Discretization while Learning Structure}
+% \label{subsubsec:auto_exp2}
+
+% If the network structure is not known in advance, it should be learned along with the discretization process.
 Figure \ref{fig:auto_graph_2} show a learned discrete-valued Bayesian network and the corresponding numbers of intervals after discretization for each continuous variable.
@@
 
-\begin{figure}[ht]
-\centering
-      \input{graph_autocar_2}
-  \caption{The learned discrete-valued Bayesian network from the Auto MPG dataset}
-  \label{fig:auto_graph_2}
-\end{figure}
-
-Figure \ref{fig:auto_exp2_distr_1_3} shows the discretization edges on variable $A$ and $C$ in Figure \ref{fig:auto_graph_2} along with the raw data.
+% \begin{figure}[ht]
+% \centering
+%       \input{graph_autocar_2}
+%   \caption{The learned discrete-valued Bayesian network from the Auto MPG dataset}
+%   \label{fig:auto_graph_2}
+% \end{figure}
+
+% Figure \ref{fig:auto_exp2_distr_1_3} shows the discretization edges on variable $A$ and $C$ in Figure \ref{fig:auto_graph_2} along with the raw data.
 Again, the black dots are raw data points.
@@
 
-\begin{figure}[ht]
-      \input{graph_auto_exp2_distr_1_3}
-  \caption{Comparison of the raw data and discretization result on variable $A$ and $C$ in Figure \ref{fig:auto_graph_2}.
+% \begin{figure}[ht]
+%       \input{graph_auto_exp2_distr_1_3}
+%   \caption{Comparison of the raw data and discretization result on variable $A$ and $C$ in Figure \ref{fig:auto_graph_2}.
 Although the number of discretization edges is less than in Figure \ref{fig:auto_exp1_distr_1_3}, it still matches the raw data distribution very well.}
-  \label{fig:auto_exp2_distr_1_3}
-\end{figure}
-
-\subsection{Dataset 2: Wine}
-\label{subsec:wine}
-
-In this subsection, another two experiments are conducted on the Wine dataset from the Irvine repository \citep{Lichman_2013}.
+%   \label{fig:auto_exp2_distr_1_3}
+% \end{figure}
+
+% \subsection{Dataset 2: Wine}
+% \label{subsec:wine}
+
+% In this subsection, another two experiments are conducted on the Wine dataset from the Irvine repository \citep{Lichman_2013}.
 This dataset has 178 instances and 14 variables.
@@
 
-\subsubsection{Discretization with fixed Structure}
-\label{subsubsec:wine_exp1}
-
-The Bayesian network in Figure \ref{fig:wine_graph_1} is obtained by equal-width discretizing each continuous variable into 3 intervals and running K2 a thousand times.
+% \subsubsection{Discretization with fixed Structure}
+% \label{subsubsec:wine_exp1}
+
+% The Bayesian network in Figure \ref{fig:wine_graph_1} is obtained by equal-width discretizing each continuous variable into 3 intervals and running K2 a thousand times.
 Table \ref{table:wine_disc_table_1} shows a comparison between the optimal Bayesian approach and the MDL principle discretization method.
-The discretization result obtained by the optimal Bayesian approach is better than the MDL discretization method in terms of likelihood.
-The heuristic method discretizes variable $G$, $H$ and $J$ into one less interval than the optimal Bayesian approach, and has one more number of intervals on variable $M$.
-Although it returns different numbers of intervals and different positions of discretization edges with the optimal Bayesian approach, it still has a good discretization result in terms of likelihood.
+% The discretization result obtained by the optimal Bayesian approach is better than the MDL discretization method in terms of likelihood.
+The heuristic method discretizes variable $G$, $H$ and $J$ into one less interval than the optimal Bayesian approach, and has one more number of intervals on variable $\Lambda$.
+% Although it returns different numbers of intervals and different positions of discretization edges with the optimal Bayesian approach, it still has a good discretization result in terms of likelihood.
 Furthermore, if running time is the main concern, the heuristic method can be considered a better approach in this case.
 
-Notice that there are some discretization edges appearing in all three discretization methods, such as \num{1.42} and \num{2.35} on variable $C$ and \num{0.785} on variable $L$.
+% Notice that there are some discretization edges appearing in all three discretization methods, such as \num{1.42} and \num{2.35} on variable $C$ and \num{0.785} on variable $L$.
 This indicates that MDL indeed can find some important discretization edges, but it is not sensitive enough to find more edges.
 
-\begin{figure}[ht]
-  \centering
-      \input{graph_wine_1}
-  \caption{Structure from prediscretized K2 structure learning to compare the methods for Wine dataset}
-  \label{fig:wine_graph_1}
-\end{figure}
-
-\begin{table}
-  \centering
-  \caption{Discretization results of Wine dataset based on the network in Fig.
+% \begin{figure}[ht]
+%   \centering
+%       \input{graph_wine_1}
+%   \caption{Structure from prediscretized K2 structure learning to compare the methods for Wine dataset}
+%   \label{fig:wine_graph_1}
+% \end{figure}
+
+% \begin{table}
+%   \centering
+%   \caption{Discretization results of Wine dataset based on the network in Fig.
 \ref{fig:wine_graph_1} by the three different methods.
@@
 Some discretization edges appear in the results of all three methods, and indicate that they are the most determinant edges.}
-  \scalebox{1.0}{
-  \input{table_wine_1.tex}
-  }
-  \label{table:wine_disc_table_1}
-\end{table}
-
-Figure \ref{fig:wine_exp1_distr} compares the discretization results by the optimal Bayesian approach and the MDL method.
+%   \scalebox{1.0}{
+%   \input{table_wine_1.tex}
+%   }
+%   \label{table:wine_disc_table_1}
+% \end{table}
+
+% Figure \ref{fig:wine_exp1_distr} compares the discretization results by the optimal Bayesian approach and the MDL method.
 The discretization edges \num{17.9} on $E$ and \num{34.6} on $K$ appear in both plots.
@@
 
-\begin{figure}[ht]
-  \centering
-    \input{graph_wine_exp1_distr}
-  \caption{Comparison of the discretization results on variable $A$ and $C$ obtained by the optimal Bayesian approach and the MDL method}
-  \label{fig:wine_exp1_distr}
-\end{figure}
-
-\subsubsection{Discretization while Learning Structure}
-\label{subsubsec:wine_exp2}
-
-Figure \ref{fig:wine_graph_2} is the learned discrete-valued Bayesian network from the Wine dataset, and it is obtained by running Algorithm \ref{alg:structure_learn} fifty times.
+% \begin{figure}[ht]
+%   \centering
+%     \input{graph_wine_exp1_distr}
+%   \caption{Comparison of the discretization results on variable $A$ and $C$ obtained by the optimal Bayesian approach and the MDL method}
+%   \label{fig:wine_exp1_distr}
+% \end{figure}
+
+% \subsubsection{Discretization while Learning Structure}
+% \label{subsubsec:wine_exp2}
+
+% Figure \ref{fig:wine_graph_2} is the learned discrete-valued Bayesian network from the Wine dataset, and it is obtained by running Algorithm \ref{alg:structure_learn} fifty times.
 The integer numbers next to variables are cardinality numbers of variables.
@@
 
-Figure \ref{fig:wine_exp2_distr} shows the discretization result on variable $E$ and $K$.
+% Figure \ref{fig:wine_exp2_distr} shows the discretization result on variable $E$ and $K$.
 The discretization edge at \num{17.9} on variable $E$ also appers in Figure \ref{fig:wine_exp1_distr}.
@@
 
-\begin{figure}[ht]
-  \centering
-  \scalebox{0.7}{
-    \input{graph_wine_2}}
-  \caption{The learned discrete-valued Bayesian network from the Wine dataset \todo{using optimal Bayesian method}}
-  \label{fig:wine_graph_2}
-\end{figure}
-
-\begin{figure}[ht]
-  \centering
-  \begin{tabular}{cc}
-    \input{graph_wine_exp2_distr_5_11}
- \end{tabular}
-  \caption{The discretization result on variable $E$ and $K$ of the learned network in Figure \ref{fig:wine_graph_2}.
+% \begin{figure}[ht]
+%   \centering
+%   \scalebox{0.7}{
+%     \input{graph_wine_2}}
+%   \caption{The learned discrete-valued Bayesian network from the Wine dataset \todo{using optimal Bayesian method}}
+%   \label{fig:wine_graph_2}
+% \end{figure}
+
+% \begin{figure}[ht]
+%   \centering
+%   \begin{tabular}{cc}
+%     \input{graph_wine_exp2_distr_5_11}
+%  \end{tabular}
+%   \caption{The discretization result on variable $E$ and $K$ of the learned network in Figure \ref{fig:wine_graph_2}.
 The discretization edge \num{17.9} on $E$ also appear in \ref{fig:wine_exp1_distr}.
 This indicates that some discretization edges are robust again the network structure.}
-  \label{fig:wine_exp2_distr}
-\end{figure}
-
-\subsection{Data 3: Housing}
-\label{subsec:housing}
-
-In this subsection, another two experiments are conducted on the Housing dataset from the Irvine repository \citep{Lichman_2013}.
+%   \label{fig:wine_exp2_distr}
+% \end{figure}
+
+% \subsection{Data 3: Housing}
+% \label{subsec:housing}
+
+% In this subsection, another two experiments are conducted on the Housing dataset from the Irvine repository \citep{Lichman_2013}.
 This dataset has 506 instances and 14 variables.
@@
 
-\subsubsection{Discretization with Fixed Structure}
-\label{subsubsec:housing_exp1}
-
-The Bayesian network structure in Figure \ref{fig:housing_graph_1} is obtained by prediscretizing each continuous variable into five uniform-width intervals, then running the K2 algorithm one thousands time and choosing the network with the highest K2 score.
+% \subsubsection{Discretization with Fixed Structure}
+% \label{subsubsec:housing_exp1}
+
+% The Bayesian network structure in Figure \ref{fig:housing_graph_1} is obtained by prediscretizing each continuous variable into five uniform-width intervals, then running the K2 algorithm one thousands time and choosing the network with the highest K2 score.
 Table \ref{table:housing_disc_table_1} shows the numbers of intervals after discretization on each continuous variables and also the log-likelihood of the dataset based on the discretization results.
@@
 
-\begin{figure}[ht]
-  \centering
-  \begin{tabular}{cc}
-   \input{graph_housing_1}
-   \end{tabular}
-  \caption{Structure from prediscretized K2 structure learning to compare the methods for Housing dataset}
-  \label{fig:housing_graph_1}
-\end{figure}
-
-\begin{table}
-  \centering\caption{Discretization result of Housing dataset based on the graph in Figure~\ref{fig:housing_graph_1}.
+% \begin{figure}[ht]
+%   \centering
+%   \begin{tabular}{cc}
+%    \input{graph_housing_1}
+%    \end{tabular}
+%   \caption{Structure from prediscretized K2 structure learning to compare the methods for Housing dataset}
+%   \label{fig:housing_graph_1}
+% \end{figure}
+
+% \begin{table}
+%   \centering\caption{Discretization result of Housing dataset based on the graph in Figure~\ref{fig:housing_graph_1}.
 The first twelve rows show the numbers of intervals after discretization by the three method.
@@
 Figure}}
-  \scalebox{1.0}{
-  \input{table_housing_1.tex}
-  }
-
-  \label{table:housing_disc_table_1}
-\end{table}
-
-Figure~\ref{fig:housing_exp1_distr_3_5} and Figure~\ref{fig:housing_exp1_distr_8_5} show the discretization result of the optimal Bayesian approach on the network in Figure~\ref{fig:housing_graph_1}.
-In Figure~\ref{fig:housing_exp1_distr_3_5}, the scatter points, which stands for the raw data, has been jittered, since there are many repeated values in the raw data on the variable pair $C$ and $E$.
+%   \scalebox{1.0}{
+%   \input{table_housing_1.tex}
+%   }
+
+%   \label{table:housing_disc_table_1}
+% \end{table}
+
+% Figure~\ref{fig:housing_exp1_distr_3_5} and Figure~\ref{fig:housing_exp1_distr_8_5} show the discretization result of the optimal Bayesian approach on the network in Figure~\ref{fig:housing_graph_1}.
+% In Figure~\ref{fig:housing_exp1_distr_3_5}, the scatter points, which stands for the raw data, has been jittered, since there are many repeated values in the raw data on the variable pair $C$ and $E$.
 These repeating values cause the high number of intervals for both $C$ and $E$, because in some sense, each repeated-value point form a single discretized area.
@@
 
-\begin{figure}[ht]
-    % \begin{tabular}{cc}
-      \input{graph_housing_exp1_distr_3_5}
-    % \end{tabular}
-  \caption{The discretization result on variable $C$ and $E$ of the network in Figure~\ref{fig:housing_graph_1}.
+% \begin{figure}[ht]
+%     % \begin{tabular}{cc}
+%       \input{graph_housing_exp1_distr_3_5}
+%     % \end{tabular}
+%   \caption{The discretization result on variable $C$ and $E$ of the network in Figure~\ref{fig:housing_graph_1}.
 The scatter points are jittered due to the repeated values in the dataset.
 Furthermore, these repeated values lead to high number of discretization edges, since repeated values can easily form discretized areas by their own.}
-  \label{fig:housing_exp1_distr_3_5}
-\end{figure}
-
-\begin{figure}[ht]
-     %\begin{tabular}{cc}
-    \input{graph_housing_exp1_distr_8_5}
-     %\end{tabular}
-  \caption{The discretization result on variable $H$ and $E$ of the network in Figure~\ref{fig:housing_graph_1}.
+%   \label{fig:housing_exp1_distr_3_5}
+% \end{figure}
+
+% \begin{figure}[ht]
+%      %\begin{tabular}{cc}
+%     \input{graph_housing_exp1_distr_8_5}
+%      %\end{tabular}
+%   \caption{The discretization result on variable $H$ and $E$ of the network in Figure~\ref{fig:housing_graph_1}.
 Data points are not over repeated on $H$, thus the number of edges on $H$ remains desirable.}
-  \label{fig:housing_exp1_distr_8_5}
-\end{figure}
-
-\subsubsection{Discretization while Learning Structure}
-\label{subsubsec:housing_exp2}
-
-Figure~\ref{fig:housing_graph_2} is the learned discrete-valued Bayesian network from the Housing dataset by running Algorithm~\ref{alg:structure_learn} fifty times.
-In both Figure~\ref{fig:housing_graph_1} and Figure~\ref{fig:housing_graph_2}, the variable $D$ is not connected to any other variable.
-Continuous variables $C$, $E$, $J$ and $K$, which are all in a Markov blanket, have high cardinality numbers after discretization.
-This is reasonable, since when discretizing one variable, the expected cardinality is close to highest cardinality number in the Markov blanket.
-This will lead to a group of variables that are close to each other and all have high cardinalities.
-
-\begin{figure}[ht]
-    % \begin{tabular}{cc}
-      \input{graph_housing_2}
-    % \end{tabular}
-  \caption{The learned discrete-valued Bayesian network from the Housing dataset. Variables $C$, $E$, $J$, $K$ have high numbers of intervals after discretization, since they are in a Markov blanket.
-  \tim{Var with 1 interval?}
-  }
-  \label{fig:housing_graph_2}
-\end{figure}
-
-Figure~\ref{fig:housing_exp2_distr_3_5} and Figure~\ref{fig:housing_exp2_distr_8_5} show the discretization result on variables of the network in Figure~\ref{fig:housing_graph_2}.
-Again, variable $C$ and $E$ have many discretization edges due to the repeated values.
-Although the number of intervals after discretization on $H$ is not large, it captures the distribution of the raw data along with the discretization edges on $E$.
-
-\begin{figure}[ht]
-     %\begin{tabular}{cc}
-      \input{graph_housing_exp2_distr_3_5}
-     %\end{tabular}
-  \caption{The discretization result on variable $C$ and $E$ of the network in Figure~\ref{fig:housing_graph_2}.
+%   \label{fig:housing_exp1_distr_8_5}
+% \end{figure}
+
+% \subsubsection{Discretization while Learning Structure}
+% \label{subsubsec:housing_exp2}
+
+% Figure~\ref{fig:housing_graph_2} is the learned discrete-valued Bayesian network from the Housing dataset by running Algorithm~\ref{alg:structure_learn} fifty times.
+% In both Figure~\ref{fig:housing_graph_1} and Figure~\ref{fig:housing_graph_2}, the variable $D$ is not connected to any other variable.
+% Continuous variables $C$, $E$, $J$ and $K$, which are all in a Markov blanket, have high cardinality numbers after discretization.
+% This is reasonable, since when discretizing one variable, the expected cardinality is close to highest cardinality number in the Markov blanket.
+% This will lead to a group of variables that are close to each other and all have high cardinalities.
+
+% \begin{figure}[ht]
+%     % \begin{tabular}{cc}
+%       \input{graph_housing_2}
+%     % \end{tabular}
+%   \caption{The learned discrete-valued Bayesian network from the Housing dataset.
+Variables $C$, $E$, $J$, $K$ have high numbers of intervals after discretization, since they are in a Markov blanket.
+%   \tim{Var with 1 interval?}
+%   }
+%   \label{fig:housing_graph_2}
+% \end{figure}
+
+% Figure~\ref{fig:housing_exp2_distr_3_5} and Figure~\ref{fig:housing_exp2_distr_8_5} show the discretization result on variables of the network in Figure~\ref{fig:housing_graph_2}.
+% Again, variable $C$ and $E$ have many discretization edges due to the repeated values.
+% Although the number of intervals after discretization on $H$ is not large, it captures the distribution of the raw data along with the discretization edges on $E$.
+
+% \begin{figure}[ht]
+%      %\begin{tabular}{cc}
+%       \input{graph_housing_exp2_distr_3_5}
+%      %\end{tabular}
+%   \caption{The discretization result on variable $C$ and $E$ of the network in Figure~\ref{fig:housing_graph_2}.
 The high number of discretization edges is due to the repeated values on the dataset in variable $C$ and $E$.}
-  \label{fig:housing_exp2_distr_3_5}
-\end{figure}
-
-\begin{figure}[ht]
-    % \begin{tabular}{cc}
-      \input{graph_housing_exp2_distr_8_5}
-    % \end{tabular}
-  \caption{The discretization result on variable $H$ and $E$ of the network in Figure~\ref{fig:housing_graph_2}.
+%   \label{fig:housing_exp2_distr_3_5}
+% \end{figure}
+
+% \begin{figure}[ht]
+%     % \begin{tabular}{cc}
+%       \input{graph_housing_exp2_distr_8_5}
+%     % \end{tabular}
+%   \caption{The discretization result on variable $H$ and $E$ of the network in Figure~\ref{fig:housing_graph_2}.
 Although the number of discretization edges on $H$ is not as large as $E$'s, they still match the distribution of the raw data very well.}
-  \label{fig:housing_exp2_distr_8_5}
-\end{figure}
-
-\subsection{Experiment Discussions}
-\label{subsec:discuss_exp}
-
-\begin{figure}[ht]
-    % \begin{tabular}{cc}
-      \input{graph_exp_discuss}
-    % \end{tabular}
-  \caption{A simple Bayesian network that is used to demonstrate the sensitivity of the three methods}
-  \label{fig:exp_discuss}
-\end{figure}
-
-To quantatively discuss the sensitivity of the three methods, consider the Bayesian network in Figure \ref{fig:exp_discuss}, where $X$ is continuous-valued and $P_1$ and $P_2$ is discrete-valued.
+%   \label{fig:housing_exp2_distr_8_5}
+% \end{figure}
+
+% \subsection{Experiment Discussions}
+% \label{subsec:discuss_exp}
+
+% \begin{figure}[ht]
+%     % \begin{tabular}{cc}
+%       \input{graph_exp_discuss}
+%     % \end{tabular}
+%   \caption{A simple Bayesian network that is used to demonstrate the sensitivity of the three methods}
+%   \label{fig:exp_discuss}
+% \end{figure}
+
+% To quantatively discuss the sensitivity of the three methods, consider the Bayesian network in Figure \ref{fig:exp_discuss}, where $X$ is continuous-valued and $P_1$ and $P_2$ is discrete-valued.
 Let $P = \{  P_1, P_2 \}$.
@@
 Therefore, the corresponding objective functions to discretize $X$ in the three methods are:
-\begin{equation}
-\begin{aligned}
-\text{Obj}_{\text{MDL}} & = Z_1 \cdot k + \log(N) \cdot \sum^k_{i=1} \sum^{J_P}_{j=1} I(a^*_i, (p_1,p_2)_j) \\
-\text{Obj}_{\text{Bayesian}} &= Z_2 \cdot k + \log {{n_i + J_P - 1}\choose{J_P -1}} + \sum^k_{i=1} \log \left(   {{n_i !}\over{n^{(P)}_{i,1}! n^{(P)}_{i,2}! \cdots n^{(P)}_{i,J_P}!    }} \right) \\
-\text{Obj}_{\text{Heuristic}} &= Z_2 \cdot k + \log {{n_i + J_{P_1} - 1}\choose{J_{P_1} -1}} + \log {{n_i + J_{P_2} - 1}\choose{J_{P_2} -1}} +\\
-& \sum^k_{i=1}  \left[ \log \left(   {{n_i !}\over{n^{(P_1)}_{i,1}!
+% \begin{equation}
+% \begin{aligned}
+% \text{Obj}_{\text{MDL}} & = Z_1 \cdot k + \log(N) \cdot \sum^k_{i=1} \sum^{J_P}_{j=1} I(a^*_i, (p_1,p_2)_j) \\
+% \text{Obj}_{\text{Bayesian}} &= Z_2 \cdot k + \log {{n_i + J_P - 1}\choose{J_P -1}} + \sum^k_{i=1} \log \left(   {{n_i !}\over{n^{(P)}_{i,1}! n^{(P)}_{i,2}! \cdots n^{(P)}_{i,J_P}!    }} \right) \\
+% \text{Obj}_{\text{Heuristic}} &= Z_2 \cdot k + \log {{n_i + J_{P_1} - 1}\choose{J_{P_1} -1}} + \log {{n_i + J_{P_2} - 1}\choose{J_{P_2} -1}} +\\
+% & \sum^k_{i=1}  \left[ \log \left(   {{n_i !}\over{n^{(P_1)}_{i,1}!
 n^{(P_1)}_{i,2}!
@@
 n^{(P_2)}_{i,2} \cdots n^{(P_2)}_{i,J_{P_2}} }} \right) \right]
-\end{aligned}
-\end{equation}
+% \end{aligned}
+% \end{equation}
 

### 2015-11-18 BN_discretizer_paper.tex
woo2

--- 2015-11-18 BN_discretizer_paper.tex
@@
   \centering
+  \begin{tabular}{cc}
+    \input{graph1}
+  \end{tabular}
+  \caption{Factorization of $P(D \mid \Lambda)$}
   \label{fig:example_factorization}
-  %\begin{tabular}{cc}
-    \input{graph1}
-  %\end{tabular}
-  \caption{Factorization of $P(D \mid M)$}
-\end{figure}
-
-The concept behind the factorization also the motivation behind forward sampling in a Bayesian network.
-The parents of $X$ are independent of the children given $X$.
-The parents are not necessarily individually independent, and thus the parental term $P(D_{\Pi_x} \mid M)$ cannot be factored further.
-The children of $X$ are similarly independent given $X$ and its spouses $\boldsymbol{S_i}$, leading to their factored product $\prod_{i = 1}^{n_c} P(D_{C_i} \mid M, D_{\boldsymbol{S_i}})$.
-Each component in the decomposition be evaluated based on a discretization policy $M = [n_1,n_2,\ldots,n_k]$ and dataset $D$.
-
-\subsubsection{Evaluation of $P(D_{\Pi_x} \mid M)$}
+\end{figure}
+
+The concept behind the factorization is also the motivation behind forward sampling in a Bayesian network.
+The parents of $\cX$ are independent of the children given $\cX$.
+The parents are not necessarily individually independent, and thus the parental term $P(D_{\Pa_{\cX}} \mid \Lambda)$ cannot be factored further.
+The children of $\cX$ are similarly independent given $\cX$ and the corresponding spouses, leading to their factored product $\prod_{C_i} P(D_{C_i} \mid \Lambda, D_{\bm{S}_i})$.
+Each component in the decomposition can be evaluated given a discretization policy and a dataset.
+
+\subsubsection{Evaluation of $P\paren{D_{\Pa_{\cX}} \mid \Lambda}$}
+
 Let $J_P = \prod_{i=1}^{n_p} \| P_i \|$. It follows that
@@
 \Function{Discretize}{$D$, $G$}
+\State
 \State $N \leftarrow$ the number of instances
@@
 \State $W[u]  \leftarrow - \log\brock{1 - {\exp\paren{- L \cdot{ {{x_{b(u)+1} - x_{b(u)}}\over{x_N - x_1}}}}}}$ for $u = 1,2, \ldots,N'-1$ and $L(N') \leftarrow 0$
-\For {$v \leftarrow 1$ to $N'$}
+\State
+\For {$v = 1$ to $N'$}
 \If {$v = 1$}
@@
 \State $s \leftarrow \infty$ and $boundary \leftarrow \infty$
-\For {$u \leftarrow 1$ to $v$}
+\For {$u = 1$ to $v$}
 \State $s' \leftarrow S[u] + g \left( b[u]+1,b[v] \right) +  {L \cdot {{x_{b[v]} - x_{b[u] + 1}}\over{x_N - x_1}}} + W[v]$
@@
 \begin{equation}
-\label{eqn:MDL}
 \begin{aligned}
@@
 
-where $I(A,B)$ is the mutual information between the discrete variables $A$ and $B$, ${H(p) = -p \log(p) - (1-p) \log(1-p)}$ \tim{does $H(p)$ have a name?
-Entropy?}, and \todo{$X^*_i$ is the discretized version of the $i$th sample of $X$}.
+where $I(A,B)$ is the mutual information between the discrete variables $A$ and $B$, ${H(p) = -p \log(p) - (1-p) \log(1-p)}$, and \todo{$X^*_i$ is the discretized version of the $i$th sample of $X$}.
 The optimal discretization policy is found with dynamic programming in a similar manner as with the Bayesian method.
@@
 \begin{figure}[ht]
-\centering
       \input{graph_auto_exp1_distr_1_3}
@@
 \begin{figure}[ht]
-\centering
       \input{graph_auto_exp2_distr_1_3}
@@
 The discretization result obtained by the optimal Bayesian approach is better than the MDL discretization method in terms of likelihood.
-The heuristic method discretizes variable $G$, $H$ and $J$ into one less interval than the optimal Bayesian approach, and has one more number of intervals on variable $M$.
+The heuristic method discretizes variable $G$, $H$ and $J$ into one less interval than the optimal Bayesian approach, and has one more number of intervals on variable $\Lambda$.
 Although it returns different numbers of intervals and different positions of discretization edges with the optimal Bayesian approach, it still has a good discretization result in terms of likelihood.
@@
   \centering
-  \scalebox{0.8}{
-      \input{graph_wine_1}}
+      \input{graph_wine_1}
   \caption{Structure from prediscretized K2 structure learning to compare the methods for Wine dataset}
@@
   \centering
-  %\begin{tabular}{cc}
-  \scalebox{0.8}{
-   \input{graph_housing_1}}
-   %\end{tabular}
+  \begin{tabular}{cc}
+   \input{graph_housing_1}
+   \end{tabular}
   \caption{Structure from prediscretized K2 structure learning to compare the methods for Housing dataset}
@@
 \begin{table}
-  \centering
-  \caption{Discretization result of Housing dataset based on the graph in Figure~\ref{fig:housing_graph_1}.
+  \centering\caption{Discretization result of Housing dataset based on the graph in Figure~\ref{fig:housing_graph_1}.
 The first twelve rows show the numbers of intervals after discretization by the three method.
@@
 \begin{figure}[ht]
-\centering
     % \begin{tabular}{cc}
@@
 \begin{figure}[ht]
-\centering
      %\begin{tabular}{cc}
@@
     % \begin{tabular}{cc}
-    \centering
-    \scalebox{0.8}{
-      \input{graph_housing_2}}
+      \input{graph_housing_2}
     % \end{tabular}
@@
 To quantatively discuss the sensitivity of the three methods, consider the Bayesian network in Figure \ref{fig:exp_discuss}, where $X$ is continuous-valued and $P_1$ and $P_2$ is discrete-valued.
-Let $\Pi_X = \{  P_1, P_2 \}$.
+Let $P = \{  P_1, P_2 \}$.
 Assume $D_X = \{1.0,2.0,3.0, \ldots N \}$.
 Therefore, the corresponding objective functions to discretize $X$ in the three methods are:
-{\begin{small}
 \begin{equation}
 \begin{aligned}
-\text{Obj}_{\text{MDL}} & = \overbrace{Z_1 \cdot k + \log(k) + \log {{N +k - 1}\choose{k -1}} }^{\text{Penalty Term}}+   \overbrace{\log(N) \cdot I(X^*, \Pi_X)}^{\text{Disc. Edge Positions Term}} \\
-\text{Obj}_{\text{Bayesian}} &= \overbrace{Z_2 \cdot k + \log {{n_i + J_P - 1}\choose{J_P -1}}}^{\text{Penalty Term}} + \overbrace{\sum^k_{i=1} \log \left(   {{n_i !}\over{n^{(P)}_{i,1}!
-n^{(P)}_{i,2}!
-\cdots n^{(P)}_{i,J_P}!
-}} \right) }^{\text{Disc.
-Edge Positions Term}}\\
-\text{Obj}_{\text{Heuristic}} &= \overbrace{Z_2 \cdot k + \log {{n_i + J_{P_1} - 1}\choose{J_{P_1} -1}} + \log {{n_i + J_{P_2} - 1}\choose{J_{P_2} -1}} }^{\text{Penalty Term}}+\\
-& \overbrace{\sum^k_{i=1}  \left[ \log \left(   {{n_i !}\over{n^{(P_1)}_{i,1}!
+\text{Obj}_{\text{MDL}} & = Z_1 \cdot k + \log(N) \cdot \sum^k_{i=1} \sum^{J_P}_{j=1} I(a^*_i, (p_1,p_2)_j) \\
+\text{Obj}_{\text{Bayesian}} &= Z_2 \cdot k + \log {{n_i + J_P - 1}\choose{J_P -1}} + \sum^k_{i=1} \log \left(   {{n_i !}\over{n^{(P)}_{i,1}! n^{(P)}_{i,2}! \cdots n^{(P)}_{i,J_P}!    }} \right) \\
+\text{Obj}_{\text{Heuristic}} &= Z_2 \cdot k + \log {{n_i + J_{P_1} - 1}\choose{J_{P_1} -1}} + \log {{n_i + J_{P_2} - 1}\choose{J_{P_2} -1}} +\\
+& \sum^k_{i=1}  \left[ \log \left(   {{n_i !}\over{n^{(P_1)}_{i,1}!
 n^{(P_1)}_{i,2}!
 \cdots n^{(P_1)}_{i,J_{P_1}}    }} \right)  + \log \left(   {{n_i !}\over{n^{(P_2)}_{i,1}!
-n^{(P_2)}_{i,2} \cdots n^{(P_2)}_{i,J_{P_2}} }} \right) \right]}^{\text{Disc.
-Edge Positions Term}}
+n^{(P_2)}_{i,2} \cdots n^{(P_2)}_{i,J_{P_2}} }} \right) \right]
 \end{aligned}
 \end{equation}
-\end{small}}
-, where $Z_1$ and $Z_2$ are two constants, $k$ is the number of intervals after discretization, $X^*$ is the discretized version of $X$, and $I(X^*, \Pi_X)$ is the mutual information between $X^*$ and its parent variables.
-Note that the third term in $\text{Obj}_{\text{MDL}}$ is approximated by $H(p)$ as in Equation \ref{eqn:MDL} in the original paper \citep{Friedman_1996}.
-
-The sensitivities toward the value distribution in $D_{\Pi_X}$ are determined by the `` Disc.
-Edge Positions Term" in the three objective functions.
-Since the penaltis of the numbers of intervals after discretization in the three objective functions take the similar form, if the `` Disc.
-Edge Positions Term" varies more severely due to different positions of discretization edges, then the corresponding method is more sensitive.
-The `` Disc.
-Edge Positions Term" in $\text{Obj}_{\text{MDL}}$, which is made out of the mutual information, varies less severely than the terms in $\text{Obj}_{\text{Bayesian}}$ and $\text{Obj}_{\text{Heuristic}}$, since it senses the distribution in $D_{\Pi_X}$ by empirical probability distributions, instead of the factorial terms such in $\text{Obj}_{\text{Bayesian}}$ and $\text{Obj}_{\text{Heuristic}}$.
-Furthermore, the `` Disc.
-Edge Positions Term" in $\text{Obj}_{\text{Heuristic}}$ varies more aggressively than the term in $\text{Obj}_{\text{Bayesian}}$.
-Therefore, the MDL method is less sensitive and the heuristic is over sensitive toward the value distributions in other variables.
-The effect of sensitivity can be shown as the numbers of intervals after discretization in the previous experiment.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2015-11-18 BN_discretizer_paper.tex

@@
   \centering
-  \begin{tabular}{cc}
   \input{graph1}
-  \end{tabular}
   \caption{Factorization of $P(D \mid \Lambda)$}
@@
 To quantatively discuss the sensitivity of the three methods, consider the Bayesian network in Figure \ref{fig:exp_discuss}, where $X$ is continuous-valued and $P_1$ and $P_2$ is discrete-valued.
-Let $P = \{  P_1, P_2 \}$.
+Let $\Pi_X = \{  P_1, P_2 \}$.
 Assume $D_X = \{1.0,2.0,3.0, \ldots N \}$.
 Therefore, the corresponding objective functions to discretize $X$ in the three methods are:
+{\begin{small}
 \begin{equation}
 \begin{aligned}
-\text{Obj}_{\text{MDL}} & = Z_1 \cdot k + \log(N) \cdot \sum^k_{i=1} \sum^{J_P}_{j=1} I(a^*_i, (p_1,p_2)_j) \\
-\text{Obj}_{\text{Bayesian}} &= Z_2 \cdot k + \log {{n_i + J_P - 1}\choose{J_P -1}} + \sum^k_{i=1} \log \left(   {{n_i !}\over{n^{(P)}_{i,1}! n^{(P)}_{i,2}! \cdots n^{(P)}_{i,J_P}!    }} \right) \\
-\text{Obj}_{\text{Heuristic}} &= Z_2 \cdot k + \log {{n_i + J_{P_1} - 1}\choose{J_{P_1} -1}} + \log {{n_i + J_{P_2} - 1}\choose{J_{P_2} -1}} +\\
-& \sum^k_{i=1}  \left[ \log \left(   {{n_i !}\over{n^{(P_1)}_{i,1}!
+\text{Obj}_{\text{MDL}} & = \overbrace{Z_1 \cdot k + \log(k) + \log {{N +k - 1}\choose{k -1}} }^{\text{Penalty Term}}+   \overbrace{\log(N) \cdot I(X^*, \Pi_X)}^{\text{Disc. Edge Positions Term}} \\
+\text{Obj}_{\text{Bayesian}} &= \overbrace{Z_2 \cdot k + \log {{n_i + J_P - 1}\choose{J_P -1}}}^{\text{Penalty Term}} + \overbrace{\sum^k_{i=1} \log \left(   {{n_i !}\over{n^{(P)}_{i,1}!
+n^{(P)}_{i,2}!
+\cdots n^{(P)}_{i,J_P}!
+}} \right) }^{\text{Disc.
+Edge Positions Term}}\\
+\text{Obj}_{\text{Heuristic}} &= \overbrace{Z_2 \cdot k + \log {{n_i + J_{P_1} - 1}\choose{J_{P_1} -1}} + \log {{n_i + J_{P_2} - 1}\choose{J_{P_2} -1}} }^{\text{Penalty Term}}+\\
+& \overbrace{\sum^k_{i=1}  \left[ \log \left(   {{n_i !}\over{n^{(P_1)}_{i,1}!
 n^{(P_1)}_{i,2}!
 \cdots n^{(P_1)}_{i,J_{P_1}}    }} \right)  + \log \left(   {{n_i !}\over{n^{(P_2)}_{i,1}!
-n^{(P_2)}_{i,2} \cdots n^{(P_2)}_{i,J_{P_2}} }} \right) \right]
+n^{(P_2)}_{i,2} \cdots n^{(P_2)}_{i,J_{P_2}} }} \right) \right]}^{\text{Disc.
+Edge Positions Term}}
 \end{aligned}
 \end{equation}
-
+\end{small}}
+, where $Z_1$ and $Z_2$ are two constants, $k$ is the number of intervals after discretization, $X^*$ is the discretized version of $X$, and $I(X^*, \Pi_X)$ is the mutual information between $X^*$ and its parent variables.
+Note that the third term in $\text{Obj}_{\text{MDL}}$ is approximated by $H(p)$ as in Equation \ref{eqn:MDL} in the original paper \citep{Friedman_1996}.
+
+The sensitivities toward the value distribution in $D_{\Pi_X}$ are determined by the `` Disc.
+Edge Positions Term" in the three objective functions.
+Since the penaltis of the numbers of intervals after discretization in the three objective functions take the similar form, if the `` Disc.
+Edge Positions Term" varies more severely due to different positions of discretization edges, then the corresponding method is more sensitive.
+The `` Disc.
+Edge Positions Term" in $\text{Obj}_{\text{MDL}}$, which is made out of the mutual information, varies less severely than the terms in $\text{Obj}_{\text{Bayesian}}$ and $\text{Obj}_{\text{Heuristic}}$, since it senses the distribution in $D_{\Pi_X}$ by empirical probability distributions, instead of the factorial terms such in $\text{Obj}_{\text{Bayesian}}$ and $\text{Obj}_{\text{Heuristic}}$.
+Furthermore, the `` Disc.
+Edge Positions Term" in $\text{Obj}_{\text{Heuristic}}$ varies more aggressively than the term in $\text{Obj}_{\text{Bayesian}}$.
+Therefore, the MDL method is less sensitive and the heuristic is over sensitive toward the value distributions in other variables.
+The effect of sensitivity can be shown as the numbers of intervals after discretization in the previous experiment.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Conclusion}
+In this work, a new method for discretizating continuous varibles in Bayesian networks has been proposed.
+It is compatible with the K2 structure learning, i.e., it can discretize continuous variables along with the edge-adding process of the K2.
+Therefore, a discrete-valued Bayesian network can be learned from mix data.
+
+Experiments on three real-world dataset show that the new method returns to a better discretization result than previous research in terms of likelihood.
+The discretization edges and the resulting marginal probabilities of discretized regions returned by the new method can match the row data well.
+
+This work can extend the usage of Bayesian networks in science and engineering, especially for the fields that require discrete-valued variables but the learning data is mixed and numerical.
+In the future, we plan to generalize the work to the datast that has high dimensional variables, for example, 3 dimensional positions of drones, which makes the sorting in Equation \ref{eq:p_M} fails.
+
 %\begin{acknowledgements}

### 2015-11-19 BN_discretizer_paper.tex
finished defining notation

@@
 Thus, each edge $e_i = \paren{\cu_{s_j} + \cu_{s_{j+1}}}/2$ for some $s_j$.
-An integer representation of $\Lambda_{\cX}$ can thus be written $\Lambda_{\cX} = \curly{\lambda_1 < \lambda_2  < \ldots < \lambda_k}$, where $\lambda_1 = s_1$ and $\lambda_i \in s_{1:m}$.
+Two useful integer representation of $\Lambda_{\cX}$ can be written
+
+\begin{equation}
+  \Lambda_{\cX} = \curly{\lambda_1 < \lambda_2  < \ldots < \lambda_k} \equiv \curly{\gamma_1 < \gamma_2  < \ldots < \gamma_k}\text{,}
+\end{equation}
+
+\noindent
+where $\lambda_1 = s_1$, $\lambda_i \in s_{1:m}$, $\gamma_1 = \lambda_1$, and $\gamma_i = \lambda_i - \lambda_{i-1}$.
+The $\lambda_{1:k}$ representation is the number of instances before every discretization edge whereas the $\lambda$ representation is the number of instances within each discretization interval.
 
@@
 Let $D_{\bm{Y}}$ be the subset of the data corresponding to $\bm{Y}$.
-Four principles for the optimal discretization policy enable the formulation of $P(\Lambda)$ and $P(D_{-\cX} \mid \Lambda)$, where the probability of the data associated with the target variable $P(D_{\cX})$ is already captured in $P(\Lambda)$.
+Four principles for the optimal discretization policy enable the formulation of $P(\Lambda)$ and $P(D_{-\cX} \mid \Lambda)$, where $D_{-\cX}$ is the subset of the dataset for all variables but $\cX$ and the probability of the data associated with the target variable $P(D_{\cX})$ is already captured in $P(\Lambda)$.
 The four principles, motivated by MODL \todo{and Lustgarden}, are:
@@
 
-The Bayesian network graph structure causes the likelihood term $P(D \mid \Lambda)$ to factorizes according to $\cX$'s Markov blanket:
+The Bayesian network graph structure causes the likelihood term $P(D_{-\cX} \mid \Lambda)$ to factorizes according to $\cX$'s Markov blanket:
 
@@
   \input{graph1}
-  \caption{Factorization of $P(D \mid \Lambda)$}
+  \caption{Factorization of $P(_{-\cX} \mid \Lambda)$}
   \label{fig:example_factorization}
@@
 
-Let $J_P = \prod_{i=1}^{n_p} \| P_i \|$. It follows that
+Let $J_P$ be the number of instantiations of the parents of $\cX$, and let $n^{(\text{p})}_{i,j}$ be the number of instances of $\cX$ within the $i$th discretization interval of $\Lambda$ given the $j$th parental instantiation.
+Note that $\lambda_i = \sum_j n^{(\text{p})}_{i,j}$.
+It follows that
 
@@
   \label{eq:likelihood_one}
-  P\paren{D_{\Pa_{\cX}} \mid \Lambda} = \prod_{i=1}^k
-    \frac{1}{{{n_i + J_P - 1}\choose{J_P - 1}}}
+  P\paren{D_{\Pa_{\cX}} \mid \Lambda} = \overbrace{\prod_{i=1}^k}^{\text{Principle 4}}
+    \overbrace{\rule{0pt}{2em}
+      \frac{1}{{{\lambda_i + J_P - 1}\choose{J_P - 1}}}
       \frac{1}{
         \frac{
-        {n_i}!
+          {\lambda_i}!
         }{
-        {n^{(p)}_{i,1}}! \; {n^{(p)}_{i,2}}! \; \cdots \; {n^{(p)}_{i,J_P}}!
+          {n^{(\text{p})}_{i,1}}! \; {n^{(\text{p})}_{i,2}}! \; \cdots \; {n^{(\text{p})}_{i,J_P}}!
+        }
+      }
+    }^{\text{Principle 2}}\text{.}
+\end{equation}
+
+The two factors on the right hand side comes from the second principle: all distributions of values of $\Pa_{\cX}$ in a given interval are equiprobable.
+According to the fourth principle, the distribution in each interval is independent, so the two factors can be multiplied together.
+
+\subsubsection{Evaluation of $P(D_{C_i} \mid \Lambda, D_{\bm{S}_i})$}
+Let $J_{C_j}$ be the number of instantiations of the $j$th child of $\cX$, let $J_S^{(j)}$ be the number instantiations of the $j$th spouse set $\bm{S}_j$, and let $n^{(j)}_{i,m,l}$ be the number of instances of $\cX$ in the $i$th discretization interval of $\Lambda$ given the $m$th instantiation of $C_j$ and the $l$th instantiation of $\boldsymbol{S_j}$.
+Let ${n^{(j)}_{i,l} = \sum_{m=1}^{J_j} n^{(j)}_{i,m,l}}$.
+Note that ${\lambda_i = \sum_l n^{(j)}_{i,l}}$.
+It follows that
+
+\begin{equation}
+  \label{eq:likelihood_two}
+  P(D_{C_j} \mid \Lambda, D_{\bm{S}_j}) =
+  \overbrace{\prod_{i=1}^{k} \prod_{l=1}^{J_S^{(j)}}}^{\text{Principle 4}}
+    \overbrace{\rule{0pt}{2.3em}
+      {
+        \frac{1}{
+          {{n^{(j)}_{i,l} + J_{C_j} - 1}\choose{J_{C_j}-1}}}
+        }
+        {\frac{
+          1
+        }{
+          \frac{
+            {n^{(j)}_{i,l}}!
+          }{
+            {n^{(j)}_{i,1,l}!} \; {n^{(j)}_{i,2,l}!} \; \cdots \; {n^{(j)}_{i,J_{C_j},l}!}
+          }
+        }
+      }
+    }^{\text{Principle 3}}
+    \text{.}
+\end{equation}
+
+The two factors on the right hand side come from the third principle: all distribution of values of $C_j$ in a given interval and with a given value of $S_j$ are equiprobable.
+According to the fourth prior, these distributions are independent from each other, and one can thus take their product.
+If $\bm{S}_j = \emptyset$, then Equation~\ref{eq:likelihood_two} is equivalent to
+
+\begin{equation}
+  \label{eq:likelihood_three}
+  P(D_{C_j} \mid \Lambda) = \prod_{i=1}^{k}
+  {
+    {1}\over{
+      {\lambda_i + J_{C_j} - 1}\choose{J_{C_j}-1}}
+    }
+    {{1}\over{
+      {{\lambda_i}!} \over {
+        {n^{(j)}_{i,1,\emptyset}!} \; {n^{(j)}_{i,2,\emptyset}!} \; \cdots \; {n^{(j)}_{i,J_{C_j},\emptyset} !}
+      }
     }
@@
 \noindent
-where $n^{(p)}_{i,j}$ is the number of instances in the $i$th discretized interval with the $j$th value of $\Pi_X$.
-Note that $n_i = \sum_{j=1}^{\| \Pi_x \|} n^{(p)}_{i,j}$.
-The two factors on the right hand side comes from the second prior: all distributions of values of $\Pi_X$ in a given interval are equiprobable.
-According to the fourth prior, the distribution in each interval is independent, so the two factors are multiplied together.
-
-\subsubsection{Evaluation of $P(D_{C_i} \mid \Lambda, D_{\bm{S}_i})$}
-For each pair $(C_j, \boldsymbol{S_j})$, let $\|C_j \| = J_j$ and $\| \boldsymbol{S_j} \| = L_j = \prod_{v \in \boldsymbol{S_j}} \| v \|$. It follows that
-
-\begin{equation}
-\label{eq:likelihood_two}
-P(D_{C_j}  \mid \Lambda, D_{S_j}) =
-\prod_{i=1}^{k} \prod_{l=1}^{L_j} {{1}\over{{n_{i,l} + J_j - 1}\choose{J_j-1}}}
-{{1}\over{ {{n_{i,l}}!}\over{ {n^{(j)}_{i,1,l} !} {n^{(j)}_{i,2,l} !} \cdots {n^{(j)}_{i,J_j,l} !}}  }}\text{,}
-\end{equation}
-
-\noindent
-where $n^{(j)}_{i,m,l}$ is the number of instances in $i$th interval with $m$th value of $C_j$ and $l$th value of $\boldsymbol{S_j}$, $n_{i,l} = \sum_{m=1}^{J_j} n^{(j)}_{i,m,l}$, and $n_i = \sum_{l=1}^{L_j} n_{i,l}$.
-The two factors on the right hand side come from the third prior: all distribution of values of $C_j$ in a given interval and with a given value of $S_j$ are equiprobable.
-According to the forth prior, these distributions are independent from each other, and one thus takes their product.
-If $S_j = \emptyset$, then Equation~\ref{eq:likelihood_two} is equivalent to
-
-\begin{equation}
-\label{eq:likelihood_three}
-P(D_{C_j}  \mid \Lambda) =
-\prod_{i=1}^{k}  {{1}\over{{n_{i} + J_j - 1}\choose{J_j-1}}}
-{{1}\over{ {{n_{i}}!}\over{ {n^{(j)}_{i,1,\emptyset} !} {n^{(j)}_{i,2,\emptyset} !} \cdots {n^{(j)}_{i,J_j,\emptyset} !}}  }}\text{,}
-\end{equation}
-
-\noindent
-where $n^{(j)}_{i,m,\emptyset}$ is the number of instances in the $i$th interval with the $m$th value of $C_j$, and $\sum_{m=1}^{J_j} n^{(j)}_{i,m,\emptyset} = n_i$.
+where $n^{(j)}_{i,m,\emptyset}$ is the number of instances of $\cX$ in the $i$th discretization interval of $\Lambda$ given the $m$th instantiation of $C_j$.
 
 The objective function can be formulated given equations \ref{eq:p_M}, \ref{eq:p_D_given_M}, \ref{eq:likelihood_one}, and \ref{eq:likelihood_three}.
-The log-inverse of $P(\Lambda) \cdot P(D|\Lambda)$ is minimized for computational convenience:
+The log-inverse of $P(\Lambda) \cdot P(D_{-\cX} \mid \Lambda)$ is minimized for computational convenience:
 
@@
   \begin{aligned}
-& \sum_{i=1}^{k-1} - \log(1 - {\exp(- L \cdot {{x_{s_i+1} - x_{s_i}}\over{x_N - x_1}})}) +  \sum_{i=1}^{k} L \cdot {{x_{s_{i}} - x_{s_{i-1} + 1}}\over{x_N - x_1}} +\\
-&  \sum_{j=1}^{n_c} \sum_{i=1}^{k}  \sum_{l=1}^{L_j} \left[  \log{{n_{i,l} + J_j - 1}\choose{J_j-1}} + \log \left( { {{n_{i,l}}!}\over{ {n^{(j)}_{i,1,l} !} {n^{(j)}_{i,2,l} !} \cdots {n^{(j)}_{i,J_j,l} !}} } \right) \right] + \\
-& \sum_{i=1}^k \left[  \log {{n_{i} + J_P - 1}\choose{J_P-1}} + \log \left( { {{n_i}!}\over{ {n^{(p)}_{i,1} !} {n^{(p)}_{i,2} !} \cdots {n^{(p)}_{i,J_p} !}} } \right) \right]\text{.}
+  \sum_{i=1}^{k-1} - \log(1 - {\exp(- L \cdot {{x_{s_i+1} - x_{s_i}}\over{x_N - x_1}})}) +  \sum_{i=1}^{k} L \cdot {{x_{s_{i}} - x_{s_{i-1} + 1}}\over{x_N - x_1}} +\\
+   \sum_{j=1}^{n_c} \sum_{i=1}^{k}  \sum_{l=1}^{L_j} \left[  \log{{n_{i,l} + J_j - 1}\choose{J_j-1}} + \log \left( { {{n_{i,l}}!}\over{ {n^{(j)}_{i,1,l} !} {n^{(j)}_{i,2,l} !} \cdots {n^{(j)}_{i,J_j,l} !}} } \right) \right] + \\
+  \sum_{i=1}^k \left[  \log {{n_{i} + J_P - 1}\choose{J_P-1}} + \log \left( { {{n_i}!}\over{ {n^{(p)}_{i,1} !} {n^{(p)}_{i,2} !} \cdots {n^{(p)}_{i,J_p} !}} } \right) \right]\text{.}
   \end{aligned}
@@
 The effect of sensitivity can be shown as the numbers of intervals after discretization in the previous experiment.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2015-11-19 BN_discretizer_paper.tex
Revise intro

@@
 
-\institute{\todo{Yi-Chun Chen \at
-              first address \\
-              Tel.: +123-45-678910\\
-              Fax: +123-45-678910\\
-              \email{fauthor@example.com}           %  \\
-%             \emph{Present address:} of F. Author  %  if needed
+\institute{Yi-Chun Chen \at
+              Institute of Computational and Mathematical Engineering, Stanford University \\
+              \email{yichunc@stanford.edu}  
            \and
-           S. Author \at
-              second address}
+              Tim A. Wheeler \at
+              Department of Aeronautics and Astronautics, Stanford University\\
+              \email{wheelert@stanford.edu}
+           \and
+              Mykel J. Kochenderfer \at
+              Department of Aeronautics and Astronautics, Stanford University\\
+              \email{mykel@stanford.edu}
 }
@@
 \begin{abstract}
-  \todo{
-  Insert your abstract here. Include keywords, PACS and mathematical
-  subject classification numbers as needed.
-  }
+Many applications of Bayesian networks assume all random variables are discrete.
+However, it is imperative to deal with continuous variables in the real-world data, such as positions and velocities of autonomous cars,  In this paper, a new method has been proposed to discretize continuous variables in Bayesian networks by learning from data.
+
+ In addition, the new method can be executed along with edge-adding steps in the K2 structure learning algorithm, and thus learn a discrete-valued Bayesian network.
+
   \keywords{Discretization \and Bayesian Network \and Continuous Variable}
@@
 Bayesian networks first emerged from artificial intelligence research and have been applied to a wide variety of problems, ranging from decision-making systems \citep{DMU_2015} \mykel{better to use a primary source} to medical diagnoses \citep{Lustgarten_2011}.
-In most cases, we assume that all random variables in Bayesian networks are discrete, since many Bayesian network learning algorithms are unable to deal with continuous variables efficiently.
-However, many applications   +Bayesian networks \citep{Pearl_1988, PGM_2009} are an increasingly popular method for modeling uncertainty and causality in science and engineering.
-They provide an efficient factorization of the joint probability distribution over a set of random variables.
-Bayesian networks first emerged from artificial intelligence research and have been applied to a wide variety of problems, ranging from decision-making systems \citep{DMU_2015} to medical diagnoses \citep{Lustgarten_2011}.
-\mykel{packages such as ....}
-In most cases, we assume that all random variables in Bayesian networks are discrete, since many Bayesian network learning algorithms are unable to deal with continuous variables efficiently.
-However, many applications require the use of continuous variables, such as position and velocity in dynamic systems \citep{kochenderfer2010airspace}.
+In many application, it is assume that all random variables in Bayesian networks are discrete, since many Bayesian network algorithms are unable to deal with continuous variables efficiently.
+In addition, many of the commonly used Bayesian network software packages, such as \todo{find packages}, assume discrete variables.
+However, various applications require the use of continuous variables, such as position and velocity in dynamic systems \citep{kochenderfer2010airspace}.
 

### 2015-11-19 BN_discretizer_paper.tex
Write all eqns and algos in new notations

@@
 Many applications of Bayesian networks assume all random variables are discrete.
-However, it is imperative to deal with continuous variables in the real-world data, such as positions and velocities of autonomous cars,  In this paper, a new method has been proposed to discretize continuous variables in Bayesian networks by learning from data.
-
- In addition, the new method can be executed along with edge-adding steps in the K2 structure learning algorithm, and thus learn a discrete-valued Bayesian network.
+However, it is imperative to deal with continuous variables in the real-world data, such as positions and velocities of dynamical systems.
+In this paper, a new method has been proposed to discretize continuous variables in Bayesian networks by learning from mixed data.
+The method adapts Bayesian statistics to find the most probable discretization policy on a continuous variable.
+In addition, it incorporates graph structure when discretizing continuous variables.
+When there are multiple continuous variables in a Bayesian network, the method iteratively discretizes each variable while treating other variables discrete by the previous discretization result.
+If the network structure is not given in advance, the method can be combined with the K2 structure learning algorithm to learn a discrete-valued Bayesian network.
+In the tests on real-world data, the method is shown that it can match the raw data distribution by providing sufficient numbers of intervals after discretization on continuous variables and also correct positions of discretization edges.
 
@@
 For other parametric distributions and non-linear functions \citep{Ihler_2009}, these redesigned algorithms are computationally expensive and do not perform well.
-The second is to use nonparametric distributions, such as particle representations and Gaussian processes \todo{[cite]}.
+The second is to use nonparametric distributions, such as particle representations and Gaussian processes \citep{Ickstadt_2010}.
 Unlike parametric methods, nonparametric methods do not make assumptions about the probability distributions being used.
@@
 \label{eq:BayesianScore}
-  \ln P(D\mid G) = \ln P(G) + \sum_{i=1}^n \sum_{j=1}^{q_i} \ln\paren{
+  \log P(D\mid G) = \log P(G) + \sum_{i=1}^n \sum_{j=1}^{q_i} \log \paren{
     \frac{
@@
     }
-  } + \sum_{k=1}^{r_i} \ln\paren{
+  } + \sum_{k=1}^{r_i} \log \paren{
     \frac{
@@
 \subsection{Discretization Policies}
+\label{subsec:disc_policy}
 
@@
 The discretization policy discretizes $\cX$ into $k$ intervals.
-Let the samples of $\cX$ in a given dataset $D$ be sorted in ascending order, ${\cx_{1:n} = \curly{\cx_1 \leq \cx_2 \leq \ldots \leq \cx_n}}$, and let the unique values be ${\cu_{1:m} = \curly{\cu_1 \leq \cu_2 \leq \ldots \leq \cu_m}}$.
+Let the samples of $\cX$ in a given dataset $D$ be sorted in ascending order, ${\cx_{1:n} = \curly{\cx_1 \leq \cx_2 \leq \ldots \leq \cx_n}}$, and let the unique values be ${\cu_{1:n'} = \curly{\cu_1 \leq \cu_2 \leq \ldots \leq \cu_{n'}}}$.
 The index of the last occurence of $\cu_i$ in $\cx_{1:n}$ is denoted $s_i$.
@@
 In this work they are restricted to the midpoints between unique ascending instances of $\cX$.
-Thus, each edge $e_i = \paren{\cu_{s_j} + \cu_{s_{j+1}}}/2$ for some $s_j$.
+Thus, each edge $e_i = \paren{\cu_{j} + \cu_{{j+1}}}/2$ for some $j$.
 Two useful integer representation of $\Lambda_{\cX}$ can be written
@@
 \begin{equation}
-  \Lambda_{\cX} = \curly{\lambda_1 < \lambda_2  < \ldots < \lambda_k} \equiv \curly{\gamma_1 < \gamma_2  < \ldots < \gamma_k}\text{,}
+\label{eq:disc_def}
+  \Lambda_{\cX} = \curly{\lambda_1 < \lambda_2  < \ldots < \lambda_k} \equiv \curly{\gamma_1 , \gamma_2  , \ldots , \gamma_k}\text{,}
 \end{equation}
@@
 \noindent
-where $\lambda_1 = s_1$, $\lambda_i \in s_{1:m}$, $\gamma_1 = \lambda_1$, and $\gamma_i = \lambda_i - \lambda_{i-1}$.
+where $\lambda_1 = s_1$, $\lambda_i \in s_{1:n'}$, $\gamma_1 = \lambda_1$, and $\gamma_i = \lambda_i - \lambda_{i-1}$.
 The $\lambda_{1:k}$ representation is the number of instances before every discretization edge whereas the $\lambda$ representation is the number of instances within each discretization interval.
@@
 Four principles for the optimal discretization policy enable the formulation of $P(\Lambda)$ and $P(D_{-\cX} \mid \Lambda)$, where $D_{-\cX}$ is the subset of the dataset for all variables but $\cX$ and the probability of the data associated with the target variable $P(D_{\cX})$ is already captured in $P(\Lambda)$.
-The four principles, motivated by MODL \todo{and Lustgarden}, are:
+The four principles, motivated by MODL and \cite{Lustgarten_2011}, are:
 
@@
 
-From the first principle one obtains
+From the first principle one obtains the $P(\Lambda)$ of $\Lambda$ described in Equation \ref{eq:disc_def}
 \begin{equation}
   \label{eq:p_M}
-  P(\Lambda) = \prod_{i=1}^k
-  \curly{
+  P(\Lambda) = \prod_{i=1}^{k-1}
     \brock{
@@
         - L \cdot \frac{
-                         \cu_{i+1} - \cu_i
-                       }{
-                         \cu_m - \cu_1
-                        }
-      }
-    } \cdot \exp\paren{
-      L \cdot \frac{\cx_{s_{i}} - \cx_{s_{i-1} + 1}}{\cx_n - \cx_1}}
+                         \cx_{\lambda_i +1} - \cx_{\lambda_i}
+                       }{
+                         \cx_n - \cx_1
+                        }
+      }
+    }     
+    \prod_{i=1}^{k}
+	\brock{    
+    \exp\paren{
+      -L \cdot \frac{\cx_{\lambda_{i}} - \cx_{\lambda_{i-1} + 1}}{\cx_n - \cx_1}}
     }\text{.}
@@
 Let $J_P$ be the number of instantiations of the parents of $\cX$, and let $n^{(\text{p})}_{i,j}$ be the number of instances of $\cX$ within the $i$th discretization interval of $\Lambda$ given the $j$th parental instantiation.
-Note that $\lambda_i = \sum_j n^{(\text{p})}_{i,j}$.
+Note that $\gamma_i = \sum_j n^{(\text{p})}_{i,j}$.
 It follows that
@@
     \overbrace{\rule{0pt}{2em}
-      \frac{1}{{{\lambda_i + J_P - 1}\choose{J_P - 1}}}
+      \frac{1}{{{\gamma_i + J_P - 1}\choose{J_P - 1}}}
       \frac{1}{
         \frac{
-          {\lambda_i}!
-        }{
-          {n^{(\text{p})}_{i,1}}! \; {n^{(\text{p})}_{i,2}}! \; \cdots \; {n^{(\text{p})}_{i,J_P}}!
+          {\gamma_i}!
+        }{
+          {n^{({P})}_{i,1}}! \; {n^{({P})}_{i,2}}! \; \cdots \; {n^{({P})}_{i,J_P}}!
         }
@@
 
-\subsubsection{Evaluation of $P(D_{C_i} \mid \Lambda, D_{\bm{S}_i})$}
+\subsubsection{Evaluation of $P(D_{C_j} \mid \Lambda, D_{\bm{S}_j})$}
 Let $J_{C_j}$ be the number of instantiations of the $j$th child of $\cX$, let $J_S^{(j)}$ be the number instantiations of the $j$th spouse set $\bm{S}_j$, and let $n^{(j)}_{i,m,l}$ be the number of instances of $\cX$ in the $i$th discretization interval of $\Lambda$ given the $m$th instantiation of $C_j$ and the $l$th instantiation of $\boldsymbol{S_j}$.
 Let ${n^{(j)}_{i,l} = \sum_{m=1}^{J_j} n^{(j)}_{i,m,l}}$.
-Note that ${\lambda_i = \sum_l n^{(j)}_{i,l}}$.
+Note that ${\gamma_i = \sum_l n^{(j)}_{i,l}}$.
 It follows that
@@
   \label{eq:likelihood_three}
-  P(D_{C_j} \mid \Lambda) = \prod_{i=1}^{k}
-  {
+  P(D_{C_j} \mid \Lambda) = 
+  \overbrace{\prod_{i=1}^{k}}^{\text{Principle 4}}
+  \overbrace{{
     {1}\over{
-      {\lambda_i + J_{C_j} - 1}\choose{J_{C_j}-1}}
+      {\gamma_i + J_{C_j} - 1}\choose{J_{C_j}-1}}
     }
     {{1}\over{
-      {{\lambda_i}!} \over {
+      {{\gamma_i}!} \over {
         {n^{(j)}_{i,1,\emptyset}!} \; {n^{(j)}_{i,2,\emptyset}!} \; \cdots \; {n^{(j)}_{i,J_{C_j},\emptyset} !}
@@
     }
-  }\text{,}
+  }}^{\text{Principle 3}}
+  \text{,}
 \end{equation}
@@
 \begin{aligned}
-  \sum_{i=1}^{k-1} - \log(1 - {\exp(- L \cdot {{x_{s_i+1} - x_{s_i}}\over{x_N - x_1}})}) +  \sum_{i=1}^{k} L \cdot {{x_{s_{i}} - x_{s_{i-1} + 1}}\over{x_N - x_1}} +\\
-   \sum_{j=1}^{n_c} \sum_{i=1}^{k}  \sum_{l=1}^{L_j} \left[  \log{{n_{i,l} + J_j - 1}\choose{J_j-1}} + \log \left( { {{n_{i,l}}!}\over{ {n^{(j)}_{i,1,l} !} {n^{(j)}_{i,2,l} !} \cdots {n^{(j)}_{i,J_j,l} !}} } \right) \right] + \\
-  \sum_{i=1}^k \left[  \log {{n_{i} + J_P - 1}\choose{J_P-1}} + \log \left( { {{n_i}!}\over{ {n^{(p)}_{i,1} !} {n^{(p)}_{i,2} !} \cdots {n^{(p)}_{i,J_p} !}} } \right) \right]\text{.}
+  & \sum_{i=1}^{k-1}
+   - \log
+    \paren{
+      1 - \exp
+      \paren{
+        - L \cdot  \frac{
+                         \cx_{\lambda_i +1} - \cx_{\lambda_i}
+                       }{
+                         \cx_n - \cx_1
+                        }
+      }
+    }
+      + \sum_{i=1}^{k}
+      L \cdot \frac{\cx_{\lambda_{i}} - \cx_{\lambda_{i-1} + 1}}{\cx_n - \cx_1} \\
+  & \sum_{i=1}^{k} \brock{
+  \log{{\gamma_i + J_P - 1}\choose{J_P - 1}}
+  +{ \log \paren{
+        \frac{
+          {\gamma_i}!
+        }{
+          {n^{({P})}_{i,1}}! \; {n^{({P})}_{i,2}}! \; \cdots \; {n^{({P})}_{i,J_P}}!
+        }
+      }}
+  } \\
+  & \sum_{j=1}^{n_c} \sum_{i=1}^k \sum_{l=1}^{J^{(j)}_S} \brock{
+  { \log
+          {{n^{(j)}_{i,l} + J_{C_j} - 1}\choose{J_{C_j}-1}}}        
+    +
+    \log \paren{ {
+          \frac{
+            {n^{(j)}_{i,l}}!
+          }{
+            {n^{(j)}_{i,1,l}!} \; {n^{(j)}_{i,2,l}!} \; \cdots \; {n^{(j)}_{i,J_{C_j},l}!}
+          }
+        }        
+        } }
 \end{aligned}
@@
 This section describes the procedure used to minimize the objective function.
-Note that the objective function is cumulative over intervals, thus, if a partition of $X$ into $k$ intervals with lengths $n_1,n_2,\ldots,n_k$ is an optimal discretization policy, then any subinterval is optimal for the corresponding subproblem.
+Note that the objective function is cumulative over intervals, thus, if a partition of $X$ into $k$ intervals by $\Lambda = \curly{\gamma_1 , \gamma_2  , \ldots , \gamma_k}$ is an optimal discretization policy, then any subinterval is optimal for the corresponding subproblem.
 It follows that dynamic programming can be used to solve the optimization problem exactly.
 
-Every midpoint between two nonequal consecutive values in $D_X$ is a candidate discretization edge.
-Let ${D'_X} = \brock{x'_1,x'_2,\ldots,x'_\Lambda}$ be the set of unique values of $D_X$ sorted in ascending order, where $\Lambda$ is the number unique values in $D_X$.
-Recall that $D_X$ is also sorted.
-Let $b = \brock{b_0,b_1,b_2,\ldots,b_\Lambda}$ be an increasing sequence of integers marking the repeated value intervals in $D_X$ such that $b_0 = 0$ and $x_{b_{i-1} + 1} = x_{b_{i-1} + 2} = \ldots = x_{b_i} = x'_i$.
-By this definition, the allowable discretization positions are $d_i = \paren{x_{b_{i}} + x_{{b_i}+1}}/2$ for all \todo{$i = 1,2,\ldots,M-1$}.
-
-Precomutation reduces runtime.
-Compute $h(u,v)$ for each interval $I_q$ starting from $x_{u}$ to $x_{v}$ for all $(u,v)$ satisfying $u \leq v$:
+Precomputation reduces runtime.
+Compute $h(u,v)$ for each interval $\gamma_q$ starting from $x_{u}$ to $x_{v}$ for all $u$, $v$ satisfying $u \leq v$:
 
@@
 \begin{aligned}
-h(u,v) &=  \log {{n_{q} + J_P - 1}\choose{J_P-1}} + \log \left( { {{n_q}!}\over{ {n^{(p)}_{q,1} !} {n^{(p)}_{q,2} !} \cdots {n^{(p)}_{q,J_p} !}} } \right) \\
-& + \sum_{j=1}^{n_c} \sum_{l=1}^{L_j} \left[  \log{{n_{q,l} + J_j - 1}\choose{J_j-1}} + \log \left( { {{n_{q,l}}!}\over{ {n^{(j)}_{q,1,l} !} {n^{(j)}_{q,2,l} !} \cdots {n^{(j)}_{q,J_j,l} !}} } \right) \right]
+h(u,v) &=  \log {{\gamma_{q} + J_P - 1}\choose{J_P-1}} + \log \left( { {{\gamma_q}!}\over{ {n^{(p)}_{q,1} !} {n^{(p)}_{q,2} !} \cdots {n^{(p)}_{q,J_p} !}} } \right) \\
+& + \sum_{j=1}^{n_c} \sum_{l=1}^{J^{(j)}_S} \brock{
+  { \log
+          {{n^{(j)}_{i,l} + J_{C_j} - 1}\choose{J_{C_j}-1}}}        
+    +
+    \log \paren{ {
+          \frac{
+            {n^{(j)}_{i,l}}!
+          }{
+            {n^{(j)}_{i,1,l}!} \; {n^{(j)}_{i,2,l}!} \; \cdots \; {n^{(j)}_{i,J_{C_j},l}!}
+          }
+        }        
+        } }
 \end{aligned}
@@
 The evaluation of $h(u,v)$ for all $u \leq v$ is summarized in Algorithm \ref{alg:h} in the appendix.
-The calculation has a $O(n_c  {v'_\text{max}} \cdot N^2 + {v'_\text{max}}^{n_p} \cdot N^2)$ runtime, where $n_c$ and $n_p$ are the numbers of child and parent variables respectively, and $v'_\text{max}$ is the largest cardinality of variables that directly connect to $X$.
+The calculation has a $\bigo \paren{ n_c  {L'} \cdot N^2 + {L'}^{n_p} \cdot N^2 }$ runtime, where $n_c$ and $n_p$ are the numbers of child and parent variables respectively, and $L'$ is the largest cardinality of variables that directly connect to $X$.
 \tim{so parents and children, or parents, children and spouses?}
@@
 The dynamic programming procedure is shown in Algorithm~\ref{alg:disc_one}.
-It takes two inputs: $D$, the joint samples over all variables sorted in ascending order according to $D_X$, and $G$, the network structure.
-The runtime of Algorithm~\ref{alg:disc_one} is also $O(n_c  {v'_\text{max}} \cdot N^2 + {v'_\text{max}}^{n_p} \cdot N^2)$, because the runtime of the dynamic programming procedure is less than the runtime for computing $h(u,v)$.
+It takes three inputs: $\cX$, the continuous variable, $D$, the joint data instances over all variables sorted in ascending order according to $D_X$, and $G$, the network structure.
+The runtime of Algorithm~\ref{alg:disc_one} is also $O(n_c  {L'} \cdot N^2 + {L'}^{n_p} \cdot N^2)$, because the runtime of the dynamic programming procedure is less than the runtime for computing $h(u,v)$.
 Algorithm~\ref{alg:disc_one} is guaranteed to be optimal.
@@
 \begin{algorithmic}[5]
-\Function{Discretize}{$D$, $G$}
-\State $N \leftarrow$ the number of instances
-\State $N' \leftarrow$ the number of unique values in $D_X$
-\State $H \leftarrow$ an $N \times N$ matrix such that $H[u,v] = h(u,v)$ per Algorithm~\ref{alg:h} in the appendix
-\State $b \leftarrow$ the increasing sequence of $\Lambda$ integers as previously defined
+\Function{DiscretizeOne}{$\cX$, $D$, $G$}
+\State $n \leftarrow$ the number of data instances
+\State $n' \leftarrow$ the number of unique values in $D_{\cX}$
+\State $H \leftarrow$ an $N \times N$ matrix such that $H[u,v] = h(u,v)$ (see Algorithm~\ref{alg:h} in Appendix)
+\State $s_{1:n'} \leftarrow$ an increasing sequence of integers defined in Section \ref{subsec:disc_policy}
 \State $L \leftarrow$ the largest cardinality over all discrete variables in the Markov blanket of $X$
-\State $S[u] \leftarrow$ the optimal objective value of subproblems with instances from $1$ to $u$
-\State $M[u] \leftarrow$ the optimal discretization for subproblems with instances from $1$ to $u$
-\State $W[u]  \leftarrow - \log\brock{1 - {\exp\paren{- L \cdot{ {{x_{b(u)+1} - x_{b(u)}}\over{x_N - x_1}}}}}}$ for $u = 1,2, \ldots,N'-1$ and $L(N') \leftarrow 0$
-\For {$v \leftarrow 1$ to $N'$}
+\State $S[u] \leftarrow$ the optimal objective value of subproblems from instance $1$ to $s_u$
+\State $\Lambda[u] \leftarrow$ the optimal discretization for subproblems from instance $1$ to $s_u$
+\State $W[u]  \leftarrow - \log\brock{1 - {\exp\paren{- L \cdot{ {{x_{s_u+1} - x_{s_u}}\over{x_N - x_1}}}}}}$ for $u = 1,2, \ldots,n'-1$ and $W[n] \leftarrow 0$
+\For {$v \leftarrow 1$ to $n'$}
 \If {$v = 1$}
-\State $S[v] \leftarrow g \left(1,b[v] \right) + L[v]$
-\State $M[v] \leftarrow \{ ({x_{b[v]} + x_{b[v]+1}}) / 2\}$
+\State $S[v] \leftarrow H \left(1,s_v \right) + L[v]$
+\State $\Lambda[v] \leftarrow \{ ({x_{s_v} + x_{s_v+1}}) / 2\}$
 \Else
-\State $s \leftarrow \infty$ and $boundary \leftarrow \infty$
+\State $s \leftarrow \infty$
+\State $\text{DiscEdge} \leftarrow \infty$
 \For {$u \leftarrow 1$ to $v$}
-\State $s' \leftarrow S[u] + g \left( b[u]+1,b[v] \right) +  {L \cdot {{x_{b[v]} - x_{b[u] + 1}}\over{x_N - x_1}}} + W[v]$
+\State $s' \leftarrow S[u] + H \left( s_u +1,s_v \right) +  {L \cdot {{x_{s_v} - x_{s_u + 1}}\over{x_N - x_1}}} + W[v]$
 \If {$s' < s$}
 \State $s \leftarrow s'$
-\State $boundary \leftarrow ({x_{b[u]} + x_{b[u]+1}}) / 2$
+\State $\text{DiscEdge} \leftarrow ({x_{s_u} + x_{s_u+1}}) / 2$
 \EndIf
@@
 \State $S[v] \leftarrow s$
-\State $M[v] \leftarrow M[u] \cup \{ boundary\}$
+\State $\Lambda[v] \leftarrow M[u] \cup \{ DiscEdge \}$
 \EndIf
 \EndFor
- \State \Return $\Lambda$
+ \State \Return $\Lambda[n']$
 \EndFunction
@@
 
-Algorithm \ref{alg:disc_one} has an exponential $\bigo\paren{\paren{v'_\text{max}}^{n_p} \cdot N^2}$ runtime which severely limits discretization in networks with a large number of discretization intervals or parent variables.
+Algorithm \ref{alg:disc_one} has an exponential $\bigo\paren{L'^{n_p} \cdot N^2}$ runtime which severely limits discretization in networks with a large number of discretization intervals or parent variables.
 This section introduces an approximation to the objective function that significantly reduces the runtime and still preserves the quality of discretization.
@@
 \begin{equation}
-{\frac{{n_i}!}{ {n^{(p)}_{i,1} !} {n^{(p)}_{i,2} !} \cdots {n^{(p)}_{i,J_P} !}}} \approx \prod_{r=1}^{n_p} { {{{n}_i}!}\over{ {n^{(p_r)}_{i,1} !} {n^{(p_r)}_{i,2} !} \cdots {n^{(p_r)}_{i,J_{p_r}} !}}}\text{,}
+{\frac{{\gamma_i}!}{ {n^{(P)}_{i,1} !} {n^{(P)}_{i,2} !} \cdots {n^{(P)}_{i,J_P} !}}} \approx \prod_{r=1}^{n_p} { {{{\gamma}_i}!}\over{ {n^{(P_r)}_{i,1} !} {n^{(P_r)}_{i,2} !} \cdots {n^{(P_r)}_{i,J_{P_r}} !}}}\text{,}
 \end{equation}
@@
 \noindent
-where $J_{p_r} = \| P_r\|$ and ${n^{(p_r)}_{i,j} !}$ is the number of instances in the $i$th interval with the $j$th value of $P_r$.
+where $P_r$ is the $r$th parent variable, $J_{p_r} = \| P_r\|$, and ${n^{(P_r)}_{i,j} !}$ is the number of instances in the $i$th interval with the $j$th value of $P_r$.
+Note that $\gamma_i = \sum_j {n^{(P_r)}_{i,j}}$ for all $r$.
 The approximated objective function is
@@
 \begin{equation}
+\label{eq:opt_prob_approx}
 \begin{aligned}
-\label{eq:opt_prob_approx}
-& \sum_{i=1}^{k-1} - \log(1 - {\exp(- L \cdot {{x_{s_i+1} - x_{s_i}}\over{x_N - x_1}})}) +  \sum_{i=1}^{k} L \cdot {{x_{s_{i}} - x_{s_{i-1} + 1}}\over{x_N - x_1}} +\\
-&  \sum_{j=1}^{n_c} \sum_{i=1}^{k}  \sum_{l=1}^{L_j} \left[  \log{{n_{i,l} + J_j - 1}\choose{J_j-1}} + \log \left( { {{n_{i,l}}!}\over{ {n^{(j)}_{i,1,l} !} {n^{(j)}_{i,2,l} !} \cdots {n^{(j)}_{i,J_j,l} !}} } \right) \right] + \\
-& \sum_{i=1}^k \left[  \log {{n_{i} + J_P - 1}\choose{J_P-1}} + \sum_{q=1}^{n_p} \log \left( { {{{n}_i}!}\over{ {n^{(p_q)}_{i,1} !} {n^{(p_q)}_{i,2} !} \cdots {n^{(p_q)}_{i,J_{p_q}} !}}} \right) \right]\text{.}
+  & \sum_{i=1}^{k-1}
+   - \log
+    \paren{
+      1 - \exp
+      \paren{
+        - L \cdot  \frac{
+                         \cx_{\lambda_i +1} - \cx_{\lambda_i}
+                       }{
+                         \cx_n - \cx_1
+                        }
+      }
+    }
+      + \sum_{i=1}^{k}
+      L \cdot \frac{\cx_{\lambda_{i}} - \cx_{\lambda_{i-1} + 1}}{\cx_n - \cx_1} \\
+  & \sum_{i=1}^{k} \brock{
+  \log{{\gamma_i + J_P - 1}\choose{J_P - 1}}
+  +{ \log \paren{
+        \frac{
+          {\gamma_i}!
+        }{ \sum_{r=1}^{n_p}
+          {n^{({P_r})}_{i,1}}! \; {n^{({P_r})}_{i,2}}! \; \cdots \; {n^{({P_r})}_{i,J_{P_r}}}!
+        }
+      }}
+  } \\
+  & \sum_{j=1}^{n_c} \sum_{i=1}^k \sum_{l=1}^{J^{(j)}_S} \brock{
+  { \log
+          {{n^{(j)}_{i,l} + J_{C_j} - 1}\choose{J_{C_j}-1}}}        
+    +
+    \log \paren{ {
+          \frac{
+            {n^{(j)}_{i,l}}!
+          }{
+            {n^{(j)}_{i,1,l}!} \; {n^{(j)}_{i,2,l}!} \; \cdots \; {n^{(j)}_{i,J_{C_j},l}!}
+          }
+        }        
+        } }
 \end{aligned}
@@
 
-With the approximated objective function, Equation~\ref{eq:opt_prob_approx}, provides intuition into how child and parent variables contribute to the objective function.
+The approximated objective function, Equation~\ref{eq:opt_prob_approx}, provides intuition into how child and parent variables contribute to the objective function.
 For example, in the left graph of Figure~\ref{fig:example_networks}, the corresponding square brackets in the approximated objective function are
@@
   \label{eq:example_approx}
-   \sum_{i=1}^k & \left\lbrace   \left[ \log{{n_{i} + J_{C_1} - 1}\choose{J_{C_1}-1}} + \log \left(  {{{n_i}!} \over { {n^{(1)}_{i,1,\emptyset} !} \cdots {n^{(1)}_{i,J_{C_1},\emptyset} !}} }  \right)  +  \right.
+   \sum_{i=1}^k & \left\lbrace   \left[ \log{{\gamma_{i} + J_{C_1} - 1}\choose{J_{C_1}-1}} + \log \left(  {{{\gamma_i}!} \over { {n^{(1)}_{i,1,\emptyset} !} \cdots {n^{(1)}_{i,J_{C_1},\emptyset} !}} }  \right)  +  \right.
 \right.\\
-  & \left.  \log{{n_{i} + J_{C_2} - 1}\choose{J_{C_2}-1}} + \log \left(  {{{n_i}!} \over { {n^{(2)}_{i,1,\emptyset} !} \cdots {n^{(2)}_{i,J_{C_1},\emptyset} !}} }  \right)  \right] + \\
+  & \left.  \log{{\gamma_{i} + J_{C_2} - 1}\choose{J_{C_2}-1}} + \log \left(  {{{n_i}!} \over { {n^{(2)}_{i,1,\emptyset} !} \cdots {n^{(2)}_{i,J_{C_1},\emptyset} !}} }  \right)  \right] + \\
   &  \left.
-\left[  \log {{n_{i} + J_P - 1}\choose{J_P-1}} +  \log \left( { {{{n}_i}!}\over{ {n^{(p_1)}_{i,1} !}\cdots {n^{(p_1)}_{i,J_{p_1}} !}}} \right) +{ {{{n}_i}!}\over{ {n^{(p_2}_{i,1} !}\cdots {n^{(p_2)}_{i,J_{p_2}} !}}}  \right] \right\rbrace \text{.}
+\left[  \log {{\gamma_{i} + J_P - 1}\choose{J_P-1}} +  \log \left( { {{{\gamma}_i}!}\over{ {n^{(P_1)}_{i,1} !}\cdots {n^{(P_1)}_{i,J_{P_1}} !}}} \right) +\log \paren{{ {{{\gamma}_i}!}\over{ {n^{(P_2}_{i,1} !}\cdots {n^{(P_2)}_{i,J_{P_2}} !}}} } \right] \right\rbrace \text{.}
   \end{aligned}
@@
 The pseudocode for the multi-variable discretization procedure is shown in Algorithm \ref{alg:disc_two}.
-It requires four inputs: $D''$, the joint samples from all network variables; $G$, the network structure; $C$, the set of all continuous variables in a reverse topological order; and $u_{cycle}$, the upper bound of times of cycles.
+It requires four inputs: $D$, the data instances from all network variables; $G$, the network structure; $C$, the set of all continuous variables in a reverse topological order, and $u_{cycle}$, the upper bound of times of cycles.
 
@@
   \begin{algorithmic}[5]
-  \Function{Discretize}{$D''$, $G$, $C$, $u_{cycle}$}
-    \State
-    \State $M[i] \leftarrow$ the discretization policy for the $i$th variable
-    \State $n \leftarrow$ the number of variables in the Bayesian network
-    \State $D^*_i \leftarrow M[i] (D_i)$, list of samples $D_i$ discretized according to $M[i]$
-    \State $D^* \leftarrow $ the discretized data for all variables, where $D^*_i \leftarrow D''_i$ if $i \notin C$
+  \Function{DiscretizeAll}{$D$, $G$, $C$, $u_{cycle}$}
+    \State $\Lambda^{(i)} \leftarrow$ the discretization policy for the $i$th variable
+    \State $m \leftarrow$ the number of variables in the Bayesian network
+    \State $D^*_{X_i} \leftarrow \Lambda^{(i)} (D_{X_i})$, list of data instances of ${X_i}$ discretized according to $\Lambda^{(i)}$
+    \State $D^* \leftarrow $ the discretized data for all variables, where $D^*_{X_j} \leftarrow D_{X_j}$ if $X_j \notin C$
     \State $k \leftarrow median\{ |v|, v\notin C\}$
-    \State
-    \For {$i = 1$ to $n$}
-      \If {$i \in C$}
-        \State $M[i] \leftarrow$  equal-width discretization with $k$ intervals
-        \State $D^*_i \leftarrow  M[i] (D''_i)$
+    \For {$i \leftarrow 1$ to $n$}
+      \If {$X_i \in C$}
+        \State $\Lambda^{(i)} \leftarrow$  equal-width discretization with $k$ intervals
+        \State $D^*_{X_i} \leftarrow  \Lambda^{(i)} (D_{X_i})$
       \EndIf
@@
     \State
-    \State $cycle \leftarrow 0$
-    \While {$\Lambda$ is not converged  \textbf{and} $cycle \leq u_{cycle}$}
-      \State {$cycle  \leftarrow cycle  + 1$}
-      \For {$j = 1$ to $|C|$}
-        \State $D^*_{\backslash C(j)} \leftarrow D^*$ without $D^*_{C(j)}$.
-        \State {$M[C(j)] \leftarrow $ DISCRETIZE($D_{C(j)}$,$D^*_{ \backslash C(j)}$,graph)}
-        \State {$D^*_{C(j)}  \leftarrow$ $M[C(j)](D''_{C(j)})$}
+    \State $n_{\text{{cycle}}} \leftarrow 0$
+    \While {$\Lambda$ is not converged  \textbf{and} $n_{\text{{cycle}}} \leq u_{cycle}$}
+      \State {$n_{\text{{cycle}}}  \leftarrow n_{\text{{cycle}}} + 1$}
+      \For {$X_j$ in $C$}
+        \State $D' \leftarrow D^*$
+        \State $D'_{X_j}$ is replaced by $D_{X_j}$
+        \State {$\Lambda^{(j)} \leftarrow $ \textsc{Discretize}\text{One}($X_j$, $D'$, $G$)}
+        \State {$D^*_{X_j}  \leftarrow$ $\Lambda^{(j)}(D_{X_j})$}
       \EndFor
     \EndWhile
-    \State \Return $\Lambda$
+    \State \Return $\Lambda^{(i)}$ for all $i$
   \EndFunction
@@
 This procedure is given in Algorithm \ref{alg:structure_learn}.
-It takes five inputs: $D'$, the joint samples from all network variables; $C$, the set of all continuous variables; $order$, the permutation of variable for $K2$; $u_{parent}$, the upper bound on the number of parents per node for $K2$; and $u_{cycle}$, the upper bound on the cycle count.
+It takes five inputs: $D$, the data instances of all network variables; $C$, the set of all continuous variables; $order$, the permutation of variable for $K2$; $u_{parent}$, the upper bound on the number of parents per node for $K2$; and $u_{cycle}$, the upper bound on the cycle count.
 It is common practice to run K2 multiple times with different permutations of the variables and to then choose the structure with the highest score.
-This work runs Algorithm \ref{alg:structure_learn} multiple times, each with a different order, and picks the discretized Bayesian network with the highest score.
+Note that the function $f$ in Algorithm \ref{alg:structure_learn} is defined as
+\begin{equation}
+\label{eq:B_Score_one}
+g(X_i, \Pi_{X_i}) =  \sum_{j=1}^{q_i} \log\paren{
+    \frac{
+      \Gamma\paren{\alpha_{ij}^{(0)}}
+    }{
+      \Gamma\paren{\alpha_{ij}^{(0)} + \beta_{ij}^{(0)}}
+    }
+  } + \sum_{k=1}^{r_i} \log \paren{
+    \frac{
+      \Gamma\paren{\alpha_{ij}^{(k)} + \beta_{ij}^{(k)}}
+    }{
+      \Gamma\paren{\alpha_{ij}^{(k)}}
+    }
+  },
+\end{equation}
+which can simplify Equation~\ref{eq:BayesianScore} as
+\begin{equation}
+\log P(D\mid G) = \log P(G) + \sum_{i=1}^n g(X_i, \Pi_{X_i}) \text{.}
+\end{equation}
+To obtain a discrete-valued Bayesian network from mixed data, this work runs Algorithm \ref{alg:structure_learn} multiple times, each with a different order, and picks the discretized Bayesian network with the highest score.
 
 \begin{algorithm}
-  \caption{ Learning a discrete-valued Bayesian network}
+  \caption{Learning a discrete-valued Bayesian network}
   \label{alg:structure_learn}
   \begin{algorithmic}[5]
-  \Function{Learn\_DBN}{$D''$, $C$, $order$, $u_{parent}$, $C$, $u_{cycle}$}
-    \State $n \leftarrow$ the number of variables in the Bayesian network
+  \Function{Learn\_DBN}{$D$, $C$, $order$, $u_{parent}$, $C$, $u_{cycle}$}
+    \State $m \leftarrow$ the number of variables in the Bayesian network
     \State $k \leftarrow median\{ \|v\|, v\notin C\}$
-    \State $M[i] \leftarrow$ the discretization policy for the $i$th variable
-    \State $D^*_i \leftarrow M[i] (D_i)$, list of samples $D_i$ discretized according to $M[i]$
-    \State $D^* \leftarrow $ the discretized data for all variables, where $D^*_i \leftarrow D''_i$ if $i \notin C$
+    \State $\Lambda^{(i)} \leftarrow$ the discretization policy for the continuous variable $X_i$
+    \State $D^*_{X_i} \leftarrow \Lambda^{(i)} (D_{X_i})$, list of instances of $X_i$ discretized by $\Lambda^{(i)}$
+    \State $D^* \leftarrow $ the discretized data for all variables, where $D^*_{X_j} \leftarrow D_{X_j}$ if $X_j \notin C$
     \State $G \leftarrow$ the initial edgeless graph structure
-    \For {$i = 1$ to $n$}
-      \If {$i \in C$}
-        \State $M[i] \leftarrow$  equal-width discretization with $k$ intervals
-        \State $D^*_i \leftarrow  M[i] (D''_i)$
+    \For {$i \leftarrow 1$ to $n$}
+      \If {$X_i \in C$}
+        \State $\Lambda^{(i)} \leftarrow$ equal-width discretization with $k$ intervals
+        \State $D^*_{X_i} \leftarrow  \Lambda^{(i)} (D_{X_i})$
       \EndIf
     \EndFor
-    \For {$i =1$ to $n$}
-      \State $P_{old} \leftarrow f(X^*_i,\Pi_{X^*_i})$: Equation~\ref{eq:f_x_p}
+    \For {$i \leftarrow 1$ to $n$}
+      \State $P_{old} \leftarrow g(X^*_i,\Pi^*_X)$ as Equation~\ref{eq:B_Score_one}
       \State OKToProceed $\leftarrow$ \textbf{true}
-      \While {OKToProceed \textbf{and} $\|\Pi_{X^*_i}\| < u_{parent}$}
+      \While {OKToProceed \textbf{and} $\|\Pi_{X_i}\| < u_{parent}$}
         \State $Y \leftarrow$ an element from the set $order[1:i] \backslash \Pi_X$
-        \State $P_{new} \leftarrow f(X^*_i,\Pi_{X^*_i} \cup Y)$
+        \State $P_{new} \leftarrow f(X^*_i,\Pi^*_{X_i} \cup Y^*)$
         \If {$P_{new} > P_{old}$}
@@
           \State $\Pi_{X_i} \leftarrow \Pi_{X_i} \cup Y $
-          \State $M \leftarrow$ {DISCRETIZE}({$D''$, $G$, $C$, $u_{cycle}$}): Algorithm~\ref{alg:disc_two}
-          \State $D* = M(D'')$
+          \State $C' \leftarrow$ sorting variables in $C$ by a reverse topological order of current $G$
+          \State $\Lambda \leftarrow$ \textsc{DiscretizeAll}({$D$, $G$, $C'$, $u_{cycle}$}): Algorithm~\ref{alg:disc_two}
+          \State $D*_{X_i} \leftarrow \Lambda^{(i)}(D_{X_i})$ for all $i$
         \Else
@@
 \centering
-    % \begin{tabular}{cc}
+%    % \begin{tabular}{cc}
       \input{graph_exp_discuss}
-    % \end{tabular}
+%    % \end{tabular}
   \caption{A simple Bayesian network that is used to demonstrate the sensitivity of the three methods}
@@
 Therefore, the corresponding objective functions to discretize $X$ in the three methods are:
+
 {\begin{small}
@@
 \begin{aligned}
-\text{Obj}_{\text{MDL}} & = \overbrace{Z_1 \cdot k + \log(k) + \log {{N +k - 1}\choose{k -1}} }^{\text{Penalty Term}}+   \overbrace{\log(N) \cdot I(X^*, \Pi_X)}^{\text{Disc. Edge Positions Term}} \\
-\text{Obj}_{\text{Bayesian}} &= \overbrace{Z_2 \cdot k + \log {{n_i + J_P - 1}\choose{J_P -1}}}^{\text{Penalty Term}} + \overbrace{\sum^k_{i=1} \log \left(   {{n_i !}\over{n^{(P)}_{i,1}!
+f_{\text{MDL}} & = \overbrace{Z_1 \cdot k + \log(k) + \log {{N +k - 1}\choose{k -1}} }^{\text{Penalty Term}}+   \overbrace{\rule{0pt}{1.35em} \log(N) \cdot I(X^*, \Pi_X)}^{\text{Disc.
+Edge Positions Term}} \\
+f_{\text{Bayesian}} &= \overbrace{\rule{0pt}{1.85em}  Z_2 \cdot k + \log {{\gamma_i + J_P - 1}\choose{J_P -1}}}^{\text{Penalty Term}} + \overbrace{\sum^k_{i=1} \log \left(   {{\gamma_i !}\over{n^{(P)}_{i,1}!
 n^{(P)}_{i,2}!
@@
 Edge Positions Term}}\\
-\text{Obj}_{\text{Heuristic}} &= \overbrace{Z_2 \cdot k + \log {{n_i + J_{P_1} - 1}\choose{J_{P_1} -1}} + \log {{n_i + J_{P_2} - 1}\choose{J_{P_2} -1}} }^{\text{Penalty Term}}+\\
-& \overbrace{\sum^k_{i=1}  \left[ \log \left(   {{n_i !}\over{n^{(P_1)}_{i,1}!
+f_{\text{Heuristic}} &= \overbrace{Z_2 \cdot k + \log {{\gamma_i + J_{P_1} - 1}\choose{J_{P_1} -1}} + \log {{\gamma_i + J_{P_2} - 1}\choose{J_{P_2} -1}} }^{\text{Penalty Term}}+\\
+& \overbrace{\sum^k_{i=1}  \left[ \log \left(   {{\gamma_i !}\over{n^{(P_1)}_{i,1}!
 n^{(P_1)}_{i,2}!
-\cdots n^{(P_1)}_{i,J_{P_1}}    }} \right)  + \log \left(   {{n_i !}\over{n^{(P_2)}_{i,1}!
+\cdots n^{(P_1)}_{i,J_{P_1}}    }} \right)  + \log \left(   {{\gamma_i !}\over{n^{(P_2)}_{i,1}!
 n^{(P_2)}_{i,2} \cdots n^{(P_2)}_{i,J_{P_2}} }} \right) \right]}^{\text{Disc.
@@
 \end{small}}
+
 , where $Z_1$ and $Z_2$ are two constants, $k$ is the number of intervals after discretization, $X^*$ is the discretized version of $X$, and $I(X^*, \Pi_X)$ is the mutual information between $X^*$ and its parent variables.
-Note that the third term in $\text{Obj}_{\text{MDL}}$ is approximated by $H(p)$ as in Equation \ref{eqn:MDL} in the original paper \citep{Friedman_1996}.
+Note that the third term in $f_{\text{MDL}}$ is approximated by $H(p)$ as in Equation \ref{eqn:MDL} in the original paper \citep{Friedman_1996}.
 
@@
 Since the penaltis of the numbers of intervals after discretization in the three objective functions take the similar form, if the `` Disc.
-Edge Positions Term" varies more severely due to different positions of discretization edges, then the corresponding method is more sensitive.
+Edge Positions Term" varies more severely due to positions of discretization edges, then the corresponding method is more sensitive.
 The `` Disc.
-Edge Positions Term" in $\text{Obj}_{\text{MDL}}$, which is made out of the mutual information, varies less severely than the terms in $\text{Obj}_{\text{Bayesian}}$ and $\text{Obj}_{\text{Heuristic}}$, since it senses the distribution in $D_{\Pi_X}$ by empirical probability distributions, instead of the factorial terms such in $\text{Obj}_{\text{Bayesian}}$ and $\text{Obj}_{\text{Heuristic}}$.
+Edge Positions Term" in $f_{\text{MDL}}$, which is made out of the mutual information, varies less severely than the terms in $f_{\text{Bayesian}}$ and $f_{\text{Heuristic}}$, since it senses the distribution in $D_{\Pi_X}$ by empirical probability distributions, instead of the factorial terms such in $f_{\text{Bayesian}}$ and $f_{\text{Heuristic}}$.
 Furthermore, the `` Disc.
-Edge Positions Term" in $\text{Obj}_{\text{Heuristic}}$ varies more aggressively than the term in $\text{Obj}_{\text{Bayesian}}$.
+Edge Positions Term" in $f_{\text{Heuristic}}$ varies more aggressively than the term in $f_{\text{Bayesian}}$.
 Therefore, the MDL method is less sensitive and the heuristic is over sensitive toward the value distributions in other variables.
@@
 
-\section*{Appendices}
+\section*{Appendix}
 

### 2015-11-19 BN_discretizer_paper.tex
fixed some notation in the algorithms. Still need to go through that in detail

@@
 \newcommand{\cu}{\mathcal{u}} % unique sorted instances of x
+\newcommand{\maxpasses}{\hat{n}_\text{cycle}}
 
@@
 
-% \begin{table}[H]
-%   \centering
-%   \begin{tabular}{@{}ccl@{}}
-%     \toprule
-%     Current & Mykel & Description \\
-%     \midrule
-%     % $G$ & $G$ & BN graph structure \\
-%     % $P$ & $P$ & discrete probability \\
-%     % $p$ & $p$ & probability density \\
-%     % $D$ & $D$ & available data \\
-%     $|D|$ & $n$ & number of variables in the BN \\
-%     $D_{\bm{Y}}$ & & subset of data associated with $\bm{Y}$ \\
-%     $X$ & $X_{1:n}$ & variables in BN (discrete) \\
-%     $x_{1:n}$ & $x_{1:n}$ & a specific instance of vars in BN \\
-%     $x'_{1:n}$ &  & unique instances of var in BN \\
-%         & $r_i$ & number of instantiations of $i$th var \\
-%     $J_p$ & $q_i$ & number of instantiations of parents of $i$th var \\
-%         &       & $ = 1$ if no parents \\
-%     $\brock{\Pi_{X_i}}_j$ & $\pi_{ij}$ & $j$th instantiation of $i$th var \\
-%         & $\theta_{ijk}$ & probability of $i$th var $= k$ given $j$th parental inst. \\
-%     $\Theta$ & $\bm{\theta}$ & set of all (non-independent) probability parameters \\
-%     $n_{i,j}^{(k)}$ & $m_{ijk}$ & observation counts \\
-%     $n_{i,j,l}^{(k)}$ & $m_{ijk}$ & observation counts with $l$th instance of spouse\\
-%     $\alpha_{ijk}$ & $\alpha_{ijk}$ & Dirichlet prior counts \\
-%     $N_{ij}$ & $\alpha_{ij0}$ & sum over Dirichlet prior counts for $k$ \\
-%         & $m_{ij0}$ & sum over observations counts for $k$ \\
-%         & $\Gamma$ & the Gamma function \\
-%     $N$ &          & is the number of samples in dataset \\
-%     $N_i$ &          & counts for $i$th instance of a specific var \\
-%     $\Pi_X$ & $\text{pa}_{x_i}$ & parents of a variable or instance \\
-%     $n_C$ & & number of children of a variable \\
-%     $H(~)$ & & a function \\
-%     $I(~,~)$ & & mutual information \\
-%     $X_i$ & & $i$th variable in BN, may be cont or disc \\
-%     $X_i^*$ & & discrete version of cont var \\
-%     $E$ & & set of edges in BN \\
-%     $\text{Pa}\paren{X_i}$, $n_p$ & & number of parents of $X_i$ \\
-%     $f\paren{X_i, \Pi_{X_i}}$ & $f(G)$ & score function for K2 \\
-%     $M_C$ & & discretization policy for $C$ \\
-%     $C$ & & a continuous variable \\
-%     $t_i$ & & the $i$th bin edge for a specific var \\
-%     $d_i$ & & allowable discretization positions (between unique vals) \\
-%     $k$ & & number of intervals for $M_C$ \\
-%     $C_{1:N}$ & & sorted samples for $C$ \\
-%     $n_i$ & & $n_1 = s_1$ and $n_i = s_{i} - s_{i-1}$ \\
-%     $s_i$ & & $\sum_{j=1}^k n_j$ and $s_k = N$, $s_0 = 0$ \\
-%     $C_i$ & & $i$th child of a specific var \\
-%     $\bm{S}_i$ & & set of spouses associated with $i$th child of specific var \\
-%     $L$ & & largest cardinality among discrete variables in BN \\
-%     $I_q$ & & an interval from $u \rightarrow v$ \\
-%     $v'_\text{max}$ & & largest cardinality of variables that directly connect to $X$ \\
-%     $S[]$ & &  optimal objective value of subproblems with instances from $1$ to $u$ \\
-%     \bottomrule
-%   \end{tabular}
-% \end{table}
-
 Bayesian networks \citep{Pearl_1988, PGM_2009} are an increasingly popular method for modeling uncertainty and causality in science and engineering.
@@
 
-The MODL method uses dynamic programming to find the optimal discretization policy, and has an $\bigo\paren{N^3 + r \cdot N^2}$ runtime, where $N$ is the of number of data instances and $r$ is the number of instances for the class variable.
+The MODL method uses dynamic programming to find the optimal discretization policy, and has an $\bigo\paren{n^3 + r \cdot n^2}$ runtime, where $n$ is the of number of data instances and $r$ is the number of instances for the class variable.
 \cite{Lustgarten_2011} suggest several formulations for the prior term $P(\text{Model})$.
-Under a uniform prior probability over discretizations the runtime can be reduced to $\bigo\paren{r \cdot N^2}$ without sacrificing optimality.
+Under a uniform prior probability over discretizations the runtime can be reduced to $\bigo\paren{r \cdot n^2}$ without sacrificing optimality.
 
@@
 \label{eq:BayesianScore}
-  \log P(D\mid G) = \log P(G) + \sum_{i=1}^n \sum_{j=1}^{q_i} \log \paren{
+  \ln P(D\mid G) = \ln P(G) + \sum_{i=1}^n \sum_{j=1}^{q_i} \ln \paren{
     \frac{
@@
     }
-  } + \sum_{k=1}^{r_i} \log \paren{
+  } + \sum_{k=1}^{r_i} \ln \paren{
     \frac{
@@
 The discretization policy discretizes $\cX$ into $k$ intervals.
-Let the samples of $\cX$ in a given dataset $D$ be sorted in ascending order, ${\cx_{1:n} = \curly{\cx_1 \leq \cx_2 \leq \ldots \leq \cx_n}}$, and let the unique values be ${\cu_{1:n'} = \curly{\cu_1 \leq \cu_2 \leq \ldots \leq \cu_{n'}}}$.
+Let the samples of $\cX$ in a given dataset $D$ be sorted in ascending order, ${\cx_{1:n} = \curly{\cx_1 \leq \cx_2 \leq \ldots \leq \cx_n}}$, and let the unique values be ${\cu_{1:m} = \curly{\cu_1 \leq \cu_2 \leq \ldots \leq \cu_{m}}}$.
 The index of the last occurence of $\cu_i$ in $\cx_{1:n}$ is denoted $s_i$.
@@
 \noindent
-where $\lambda_1 = s_1$, $\lambda_i \in s_{1:n'}$, $\gamma_1 = \lambda_1$, and $\gamma_i = \lambda_i - \lambda_{i-1}$.
+where $\lambda_1 = s_1$, $\lambda_i \in s_{1:m}$, $\gamma_1 = \lambda_1$, and $\gamma_i = \lambda_i - \lambda_{i-1}$.
 The $\lambda_{1:k}$ representation is the number of instances before every discretization edge whereas the $\lambda$ representation is the number of instances within each discretization interval.
@@
 % Let $D$ be a dataset of $N$ samples from which the discretization will be learned, sorted in ascending order according to $X$.
-% Let $D_{\boldsymbol{Y}}$ will refer to the data instances associated with variables $\boldsymbol{Y}$, thus $D_X = \{ x_1,x_2,x_3,\ldots,x_N \}$.
-% In order to facilitate understanding, we temporarily assume all values in $D_X$ are unique, that is, $x_1 < x_2 < \ldots < x_N$.
+% Let $D_{\boldsymbol{Y}}$ will refer to the data instances associated with variables $\boldsymbol{Y}$, thus $D_X = \{ x_1,x_2,x_3,\ldots,x_n \}$.
+% In order to facilitate understanding, we temporarily assume all values in $D_X$ are unique, that is, $x_1 < x_2 < \ldots < x_n$.
 % It follows that a discretization policy $\Lambda$ on $X$ can be written as $M_X = \brock{n_1,n_2,\ldots,n_k}$, where $k$, $n_1$, $n_2$, $\ldots,n_k$ are positive integers satisfying $N = \sum_{i=1}^k n_i$.
@@
 From the first principle one obtains the $P(\Lambda)$ of $\Lambda$ described in Equation \ref{eq:disc_def}
+
+\begin{small}
 \begin{equation}
@@
 \end{equation}
+\end{small}
 
@@
   & \sum_{i=1}^{k-1}
-   - \log
+   - \ln
     \paren{
@@
   & \sum_{i=1}^{k} \brock{
-  \log{{\gamma_i + J_P - 1}\choose{J_P - 1}}
-  +{ \log \paren{
+  \ln{{\gamma_i + J_P - 1}\choose{J_P - 1}}
+  +{ \ln \paren{
         \frac{
@@
   & \sum_{j=1}^{n_c} \sum_{i=1}^k \sum_{l=1}^{J^{(j)}_S} \brock{
-  { \log
+  { \ln
           {{n^{(j)}_{i,l} + J_{C_j} - 1}\choose{J_{C_j}-1}}}
     +
-    \log \paren{ {
+    \ln \paren{ {
           \frac{
@@
   \begin{aligned}
-h(u,v) &=  \log {{\gamma_{q} + J_P - 1}\choose{J_P-1}} + \log \left( { {{\gamma_q}!}\over{ {n^{(p)}_{q,1} !} {n^{(p)}_{q,2} !} \cdots {n^{(p)}_{q,J_p} !}} } \right) \\
+  h(u,v) &=  \ln {{\gamma_{q} + J_P - 1}\choose{J_P-1}} + \ln \left( { {{\gamma_q}!}\over{ {n^{(p)}_{q,1} !} {n^{(p)}_{q,2} !} \cdots {n^{(p)}_{q,J_p} !}} } \right) \\
   & + \sum_{j=1}^{n_c} \sum_{l=1}^{J^{(j)}_S} \brock{
-  { \log
+    { \ln
             {{n^{(j)}_{i,l} + J_{C_j} - 1}\choose{J_{C_j}-1}}}
       +
-    \log \paren{ {
+      \ln \paren{ {
             \frac{
@@
 
-The evaluation of $h(u,v)$ for all $u \leq v$ is summarized in Algorithm \ref{alg:h} in the appendix.
+The evaluation of $h(u,v)$ for all $u \leq v$ is summarized in Algorithm~\ref{alg:h} in the appendix.
 The calculation has a $\bigo \paren{ n_c  {L'} \cdot N^2 + {L'}^{n_p} \cdot N^2 }$ runtime, where $n_c$ and $n_p$ are the numbers of child and parent variables respectively, and $L'$ is the largest cardinality of variables that directly connect to $X$.
@@
       \State $n \leftarrow$ the number of data instances
-\State $n' \leftarrow$ the number of unique values in $D_{\cX}$
+      \State $m \leftarrow$ the number of unique values in $D_{\cX}$
       \State $H \leftarrow$ an $N \times N$ matrix such that $H[u,v] = h(u,v)$ (see Algorithm~\ref{alg:h} in Appendix)
-\State $s_{1:n'} \leftarrow$ an increasing sequence of integers defined in Section \ref{subsec:disc_policy}
+      \State $s_{1:m} \leftarrow$ an increasing sequence of integers defined in Section \ref{subsec:disc_policy}
       \State $L \leftarrow$ the largest cardinality over all discrete variables in the Markov blanket of $X$
@@
       \State $\Lambda[u] \leftarrow$ the optimal discretization for subproblems from instance $1$ to $s_u$
-\State $W[u]  \leftarrow - \log\brock{1 - {\exp\paren{- L \cdot{ {{x_{s_u+1} - x_{s_u}}\over{x_N - x_1}}}}}}$ for $u = 1,2, \ldots,n'-1$ and $W[n] \leftarrow 0$
-\For {$v \leftarrow 1$ to $n'$}
+      \State $W[u]  \leftarrow - \ln\brock{1 - {\exp\paren{- L \cdot{ {{\cx_{s_u+1} - \cx_{s_u}}\over{\cx_n - \cx_1}}}}}}$ for $u = 1,2, \ldots,m-1$ and $W[n] \leftarrow 0$
+      \For {$v \leftarrow 1$ to $m$}
         \If {$v = 1$}
-\State $S[v] \leftarrow H \left(1,s_v \right) + L[v]$
-\State $\Lambda[v] \leftarrow \{ ({x_{s_v} + x_{s_v+1}}) / 2\}$
+          \State $S[v] \leftarrow H \paren{1,s_v} + L[v]$
+          \State $\Lambda[v] \leftarrow \{ ({\cx_{s_v} + \cx_{s_v+1}}) / 2\}$
         \Else
@@
         \For {$u \leftarrow 1$ to $v$}
-\State $s' \leftarrow S[u] + H \left( s_u +1,s_v \right) +  {L \cdot {{x_{s_v} - x_{s_u + 1}}\over{x_N - x_1}}} + W[v]$
+        \State $s' \leftarrow S[u] + H \paren{s_u+1, s_v} +  {L \cdot {\frac{\cx_{s_v} - \cx_{s_u + 1}}{\cx_n - \cx_1}}} + W[v]$
         \If {$s' < s$}
@@
       \EndFor
- \State \Return $\Lambda[n']$
+      \State \Return $\Lambda[m]$
     \EndFunction
@@
     & \sum_{i=1}^{k-1}
-   - \log
+     - \ln
       \paren{
@@
     & \sum_{i=1}^{k} \brock{
-  \log{{\gamma_i + J_P - 1}\choose{J_P - 1}}
-  +{ \log \paren{
+    \ln{{\gamma_i + J_P - 1}\choose{J_P - 1}}
+    +{ \ln \paren{
           \frac{
@@
     & \sum_{j=1}^{n_c} \sum_{i=1}^k \sum_{l=1}^{J^{(j)}_S} \brock{
-  { \log
+    { \ln
             {{n^{(j)}_{i,l} + J_{C_j} - 1}\choose{J_{C_j}-1}}}
       +
-    \log \paren{ {
+      \ln \paren{ {
             \frac{
@@
 
-The approximation reduces the runtime of Algorithm~\ref{alg:disc_one} to a polynomial, $\bigo\paren{ {v'_\text{max}} \cdot (n_c + n_p) \cdot N^2}$.
+The approximation reduces the runtime of Algorithm~\ref{alg:disc_one} to a polynomial, $\todo{\bigo\paren{ {v'_\text{max}} \cdot (n_c + n_p) \cdot n^2}}$.
 It will be shown in Section~\ref{sec:experiments} that the approximation is more sensitive to the distribution over other variables and is biased towards slightly higher interval counts.
-\tim{We need to have a more specific thing to say along the lines of When does it fail?}
+\tim{We need to have a more specific thing to say along the lines of `When does it fail?'}
 
@@
   \label{eq:example_approx}
-   \sum_{i=1}^k & \left\lbrace   \left[ \log{{\gamma_{i} + J_{C_1} - 1}\choose{J_{C_1}-1}} + \log \left(  {{{\gamma_i}!} \over { {n^{(1)}_{i,1,\emptyset} !} \cdots {n^{(1)}_{i,J_{C_1},\emptyset} !}} }  \right)  +  \right.
+   \sum_{i=1}^k & \left\lbrace   \left[ \ln{{\gamma_{i} + J_{C_1} - 1}\choose{J_{C_1}-1}} + \ln \left(  {{{\gamma_i}!} \over { {n^{(1)}_{i,1,\emptyset} !} \cdots {n^{(1)}_{i,J_{C_1},\emptyset} !}} }  \right)  +  \right.
 \right.\\
-  & \left.  \log{{\gamma_{i} + J_{C_2} - 1}\choose{J_{C_2}-1}} + \log \left(  {{{n_i}!} \over { {n^{(2)}_{i,1,\emptyset} !} \cdots {n^{(2)}_{i,J_{C_1},\emptyset} !}} }  \right)  \right] + \\
+  & \left.  \ln{{\gamma_{i} + J_{C_2} - 1}\choose{J_{C_2}-1}} + \ln \left(  {{{n_i}!} \over { {n^{(2)}_{i,1,\emptyset} !} \cdots {n^{(2)}_{i,J_{C_1},\emptyset} !}} }  \right)  \right] + \\
   &  \left.
-\left[  \log {{\gamma_{i} + J_P - 1}\choose{J_P-1}} +  \log \left( { {{{\gamma}_i}!}\over{ {n^{(P_1)}_{i,1} !}\cdots {n^{(P_1)}_{i,J_{P_1}} !}}} \right) +\log \paren{{ {{{\gamma}_i}!}\over{ {n^{(P_2}_{i,1} !}\cdots {n^{(P_2)}_{i,J_{P_2}} !}}} } \right] \right\rbrace \text{.}
+\left[  \ln {{\gamma_{i} + J_P - 1}\choose{J_P-1}} +  \ln \left( { {{{\gamma}_i}!}\over{ {n^{(P_1)}_{i,1} !}\cdots {n^{(P_1)}_{i,J_{P_1}} !}}} \right) +\ln \paren{{ {{{\gamma}_i}!}\over{ {n^{(P_2}_{i,1} !}\cdots {n^{(P_2)}_{i,J_{P_2}} !}}} } \right] \right\rbrace \text{.}
   \end{aligned}
@@
 In Equation~\ref{eq:example_approx}, each child carries two terms, as shown in the first set of square brackets, but the two parent variables only carry a total of three terms, as shown in the second set of square brackets.
-In this case the child variables have greater effect than the parent variables even though the number of child and parent variables are the same.
-However, if $C_2$ has an additional parent $S_2$, as shown in the right graph of Figure~\ref{fig:example_networks}, the importances of $C_2$ will be reduced, because the information from $C_2$ is now affected by $S_2$.
-This argument shows that the proposed method, both before and after approximation, indeed incorporates graph structure when discretizing continuous variables.
+In this case the child variables have greater effect on the optimal discretization than the parent variables, even though the number of child and parent variables are the same.
+However, if $C_2$ has an additional parent $S_2$, as shown in the right graph of Figure~\ref{fig:example_networks}, the importances of $C_2$ will be reduced.
+This is due to the additional influence of $S_2$ on $C_2$.
+This phenomenon arrises because the Bayesian method, but with and without the heuristic, incorporates graph structure when discretizing continuous variables.
 
@@
 
-\section{Multiple Variable Discretization}
+\section{Multi-Variable Discretization}
 \label{sec:multi_var}
@@
 
-The single-variable discretization method can be extended to Bayesian networks with multiple continuous variables by iteratively discretizing variables individually.
+The single-variable discretization method can be extended to Bayesian networks with multiple continuous variables by iteratively discretizing individual variables.
 The discretization process for a single variable requires that all other variables be discrete.
-The iterative approach thus requires a prediscretization policy from which to initialize the process.
-This work uses prediscretization with equal-width intervals, defined by
-
-\begin{equation}
-M_X = \curly{X_\text{min}, X_\text{min} + \delta, X_\text{min} + 2\delta, \ldots, X_\text{max}}\text{,}
-\end{equation}
-
-\noindent
-where $X_\text{min}$ and $X_\text{max}$ are the extrema values of $D_X$, $\delta = (X_\text{max} - X_\text{min})/k$, and $k$ is the desired number of intervals.
-This work sets $k$ to the median value of the cardinalities of initially discrete variables in the network.
-After prediscretization, the one-variable discretization methis is iteratively applied over each continuous variable in reverse topoligical order, from the leaves to the root.
-Let one such series of discretizations be a cycle.
-Reverse topological order has the advantage of using less prediscretized instantiations during the first cycle.
-For example, in the right-hand graph of Figure \ref{fig:example_networks}, assume $S_2$ is the only discrete variable.
-The discretization of $P_1$ involves both $P_2$ and $X$, whereas the discretization of $C_1$ only involves $X$.
-
-The algorithm is terminated when the number of discretization intervals and their associated edges converge for all variables.
-A maximum cycle count is enforced to prevent infinite iterations when convergence does not occur.
-The algorithm typically converges within a few cycles when tested on real-world data.
-In cases where it does not converge, ten cycles usually produce decent discretization results.
-
-The pseudocode for the multi-variable discretization procedure is shown in Algorithm \ref{alg:disc_two}.
-It requires four inputs: $D$, the data instances from all network variables; $G$, the network structure; $C$, the set of all continuous variables in a reverse topological order, and $u_{cycle}$, the upper bound of times of cycles.
+The iterative approach uses a prediscretization policy in order to initialize the process.
+This work prediscretizes all continuous variables into $k$ equal-width intervals, where $k$ is the median value of the number of intervals of initially discrete variables in the network.
+
+After prediscretization, the one-variable discretization method is iteratively applied over each continuous variable in reverse topoligical order, from the leaves to the root.
+Reverse topological order has the advantage of relying on fewer prediscretizations of the continuous variables during the first pass.
+For example, in the right-hand graph of Figure~\ref{fig:example_networks}, assume $S_2$ is the only discrete variable.
+The discretization of $P_1$ involves both $P_2$ and $\cX$, whereas the discretization of $C_1$ only involves $\cX$.
+
+The algorithm is terminated when the number of discretization intervals and their associated edges converge for all variables, and a maximum number of complete passes is enforced to prevent infinite iterations when convergence does not occur.
+The algorithm typically converges within a few passes when tested on real-world data.
+In cases where it does not converge, \tim{when was this observed? What dataset?}, ten passes usually produce decent discretization results.
+
+The pseudocode for the multi-variable discretization procedure is shown in Algorithm~\ref{alg:disc_two}.
+It requires four inputs: $D$, a dataset of samples from the joint distribution; $G$, the fixed network structure; $\bm{\cX}$, the set of all continuous variables in reverse topological order, and $\maxpasses$, an upper bound on the number of complete passes.
 
@@
   \begin{algorithmic}[5]
-  \Function{DiscretizeAll}{$D$, $G$, $C$, $u_{cycle}$}
-    \State $\Lambda^{(i)} \leftarrow$ the discretization policy for the $i$th variable
-    \State $m \leftarrow$ the number of variables in the Bayesian network
-    \State $D^*_{X_i} \leftarrow \Lambda^{(i)} (D_{X_i})$, list of data instances of ${X_i}$ discretized according to $\Lambda^{(i)}$
-    \State $D^* \leftarrow $ the discretized data for all variables, where $D^*_{X_j} \leftarrow D_{X_j}$ if $X_j \notin C$
-    \State $k \leftarrow median\{ |v|, v\notin C\}$
-    \For {$i \leftarrow 1$ to $n$}
-      \If {$X_i \in C$}
-        \State $\Lambda^{(i)} \leftarrow$  equal-width discretization with $k$ intervals
-        \State $D^*_{X_i} \leftarrow  \Lambda^{(i)} (D_{X_i})$
-      \EndIf
+  \Function{DiscretizeAll}{$D$, $G$, $\bm{\cX}$, $\maxpasses$}
+    \State $\Lambda_{\bm{\cX}} \leftarrow$ the discretization policies for each $\cX$ in $\bm{\cX}$
+    \State $D^* \leftarrow $ the dataset $D$ discretized according to $\Lambda_{\bm{\cX}}$
+    \State $k \leftarrow \textsc{Median}\paren{\curly{ |X| \text{ s.t. } X \text{ does not have corresponding } \cX \text{ in } \bm{\cX} }}$
+    \For {$\paren{X, \cX}$ such that $\cX \in \bm{\cX}$}
+      \State $\Lambda_{\cX} \leftarrow$ equal-width discretization of $\cX$ with $k$ intervals
+      \State $D^*_{X} \leftarrow \Lambda_{\cX} \paren{D_{\cX}}$
     \EndFor
-    \State
-    \State $n_{\text{{cycle}}} \leftarrow 0$
-    \While {$\Lambda$ is not converged  \textbf{and} $n_{\text{{cycle}}} \leq u_{cycle}$}
-      \State {$n_{\text{{cycle}}}  \leftarrow n_{\text{{cycle}}} + 1$}
-      \For {$X_j$ in $C$}
-        \State $D' \leftarrow D^*$
-        \State $D'_{X_j}$ is replaced by $D_{X_j}$
-        \State {$\Lambda^{(j)} \leftarrow $ \textsc{Discretize}\text{One}($X_j$, $D'$, $G$)}
-        \State {$D^*_{X_j}  \leftarrow$ $\Lambda^{(j)}(D_{X_j})$}
+    \State $n_\text{cycle} \leftarrow 0$
+    \While {$\Lambda_{\bm{\cX}}$ has not converged \textbf{and} $n_\text{cycle} \leq \maxpasses$}
+      \State increment {$n_\text{cycle}$}
+      \For {$\paren{X, \cX}$ such that $\cX \in \bm{\cX}$}
+        \State {$D^*_X \leftarrow D_{\cX}$}
+        \State {$\Lambda_{\cX} \leftarrow \textsc{DiscretizeOne}(\cX, D^*, G)$}
+        \State {$D^*_X \leftarrow \Lambda_{\cX}\paren{D_{\cX}}$}
       \EndFor
     \EndWhile
-    \State \Return $\Lambda^{(i)}$ for all $i$
+    \State \Return $\Lambda_{\bm{\cX}}$
   \EndFunction
@@
 In many situations the network structure is not known in advance and must be learned from data.
-Traditional Bayesian structure learning algorithms require discretized data, whereas the proposed discretization algorithm requires a network structure.
+Traditional Bayesian structure learning algorithms require discretized data, whereas the proposed discretization algorithm requires a known network structure.
 This section combines the proposed discretization method with the K2 structure learning algorithm \citep{K2} in an interative fassion to simultaneously perform Bayesian structure learning and discretization of continuous variables.
@@
 
-This procedure is given in Algorithm \ref{alg:structure_learn}.
-It takes five inputs: $D$, the data instances of all network variables; $C$, the set of all continuous variables; $order$, the permutation of variable for $K2$; $u_{parent}$, the upper bound on the number of parents per node for $K2$; and $u_{cycle}$, the upper bound on the cycle count.
-It is common practice to run K2 multiple times with different permutations of the variables and to then choose the structure with the highest score.
-Note that the function $f$ in Algorithm \ref{alg:structure_learn} is defined as
-\begin{equation}
-\label{eq:B_Score_one}
-g(X_i, \Pi_{X_i}) =  \sum_{j=1}^{q_i} \log\paren{
-    \frac{
-      \Gamma\paren{\alpha_{ij}^{(0)}}
-    }{
-      \Gamma\paren{\alpha_{ij}^{(0)} + \beta_{ij}^{(0)}}
-    }
-  } + \sum_{k=1}^{r_i} \log \paren{
-    \frac{
-      \Gamma\paren{\alpha_{ij}^{(k)} + \beta_{ij}^{(k)}}
-    }{
-      \Gamma\paren{\alpha_{ij}^{(k)}}
-    }
-  },
-\end{equation}
-which can simplify Equation~\ref{eq:BayesianScore} as
-\begin{equation}
-\log P(D\mid G) = \log P(G) + \sum_{i=1}^n g(X_i, \Pi_{X_i}) \text{.}
-\end{equation}
-To obtain a discrete-valued Bayesian network from mixed data, this work runs Algorithm \ref{alg:structure_learn} multiple times, each with a different order, and picks the discretized Bayesian network with the highest score.
+This procedure is given in Algorithm~\ref{alg:structure_learn}.
+It takes five inputs: $D$, a dataset of samples from the joint distribution; $\bm{\cX}$, the set of all continuous variables; $\texttt{order}$, a permutation of the variables in $D$; $\hat{n}_\text{parent}$, an upper bound on the number of parents per node; and $\maxpasses$, an upper bound on the number of complete passes.
 
@@
   \begin{algorithmic}[5]
-  \Function{Learn\_DBN}{$D$, $C$, $order$, $u_{parent}$, $C$, $u_{cycle}$}
+  \Function{Learn\_DBN}{$D$, $C$, $order$, $u_{parent}$, $C$, $\maxpasses$}
     \State $m \leftarrow$ the number of variables in the Bayesian network
@@
     \For {$i \leftarrow 1$ to $n$}
-      \State $P_{old} \leftarrow g(X^*_i,\Pi^*_X)$ as Equation~\ref{eq:B_Score_one}
+      \State $P_{old} \leftarrow g(X^*_i,\Pa^*_X)$ as Equation~\ref{eq:B_Score_one}
       \State OKToProceed $\leftarrow$ \textbf{true}
-      \While {OKToProceed \textbf{and} $\|\Pi_{X_i}\| < u_{parent}$}
+      \While {OKToProceed \textbf{and} $\|\Pa_{X_i}\| < u_{parent}$}
         \State $Y \leftarrow$ an element from the set $order[1:i] \backslash \Pi_X$
-        \State $P_{new} \leftarrow f(X^*_i,\Pi^*_{X_i} \cup Y^*)$
+        \State $P_{new} \leftarrow f(X^*_i,\Pa^*_{X_i} \cup Y^*)$
         \If {$P_{new} > P_{old}$}
           \State $P_{old} \leftarrow P_{new}$
-          \State $\Pi_{X_i} \leftarrow \Pi_{X_i} \cup Y $
+          \State $\Pa_{X_i} \leftarrow \Pa_{X_i} \cup Y $
           \State $C' \leftarrow$ sorting variables in $C$ by a reverse topological order of current $G$
-          \State $\Lambda \leftarrow$ \textsc{DiscretizeAll}({$D$, $G$, $C'$, $u_{cycle}$}): Algorithm~\ref{alg:disc_two}
+          \State $\Lambda \leftarrow$ \textsc{DiscretizeAll}({$D$, $G$, $C'$, $\maxpasses$}): Algorithm~\ref{alg:disc_two}
           \State $D*_{X_i} \leftarrow \Lambda^{(i)}(D_{X_i})$ for all $i$
@@
 
+The function $f$ in Algorithm~\ref{alg:structure_learn} computes a component of the Bayesian score (Equation~\ref{eq:BayesianScore}):
+
+\begin{equation}
+  \label{eq:B_Score_one}
+  g\paren{X_i, \Pa_{X_i}} =  \sum_{j=1}^{q_i} \ln\paren{
+    \frac{
+      \Gamma\paren{\alpha_{ij}^{(0)}}
+    }{
+      \Gamma\paren{\alpha_{ij}^{(0)} + \beta_{ij}^{(0)}}
+    }
+  } + \sum_{k=1}^{r_i} \ln \paren{
+    \frac{
+      \Gamma\paren{\alpha_{ij}^{(k)} + \beta_{ij}^{(k)}}
+    }{
+      \Gamma\paren{\alpha_{ij}^{(k)}}
+    }
+  }\text{.}
+\end{equation}
+
+It is common practice to run K2 multiple times with different variable permutations and to then choose the structure with the highest score.
+As such, Algorithm \ref{alg:structure_learn} is run multiple times with different variable permutations and the discretized Bayesian network with the highest score is retaiend.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \begin{aligned}
-\frac{1}{2} \log(N) \left\lbrace  \lvert \Pi_{X_i} \rvert (\lvert X^*_i \rvert - 1) +
- {\sum_{j,X_i \in \Pi_{X_i}}} \lvert \Pi_{X^*_j} \rvert (\lvert X_j \rvert - 1) \right\rbrace + \log(\lvert {X^*_i} \rvert) \\
+\frac{1}{2} \ln(N) \left\lbrace  \lvert \Pi_{X_i} \rvert (\lvert X^*_i \rvert - 1) +
+ {\sum_{j,X_i \in \Pi_{X_i}}} \lvert \Pi_{X^*_j} \rvert (\lvert X_j \rvert - 1) \right\rbrace + \ln(\lvert {X^*_i} \rvert) \\
  + (N_i-1) H \left( {{|X^*_i| - 1}\over{N_i -1}}  \right) -N \cdot \left[ I(X^*_i,\Pi_{X_i}) + {\sum_{j,X_i \in \Pi_{X_i}}} I(X_j, \Pi_{X^*_j}) \right]\text{,}
@@
 
-where $I(A,B)$ is the mutual information between the discrete variables $A$ and $B$, ${H(p) = -p \log(p) - (1-p) \log(1-p)}$, and \todo{$X^*_i$ is the discretized version of the $i$th sample of $X$}.
+where $I(A,B)$ is the mutual information between the discrete variables $A$ and $B$, ${H(p) = -p \ln(p) - (1-p) \ln(1-p)}$, and \todo{$X^*_i$ is the discretized version of the $i$th sample of $X$}.
 The optimal discretization policy is found with dynamic programming in a similar manner as with the Bayesian method.
@@
 \begin{aligned}
-f_{\text{MDL}} & = \overbrace{Z_1 \cdot k + \log(k) + \log {{N +k - 1}\choose{k -1}} }^{\text{Penalty Term}}+   \overbrace{\rule{0pt}{1.35em} \log(N) \cdot I(X^*, \Pi_X)}^{\text{Disc.
+f_{\text{MDL}} & = \overbrace{Z_1 \cdot k + \ln(k) + \ln {{N +k - 1}\choose{k -1}} }^{\text{Penalty Term}}+   \overbrace{\rule{0pt}{1.35em} \ln(N) \cdot I(X^*, \Pi_X)}^{\text{Disc.
 Edge Positions Term}} \\
-f_{\text{Bayesian}} &= \overbrace{\rule{0pt}{1.85em}  Z_2 \cdot k + \log {{\gamma_i + J_P - 1}\choose{J_P -1}}}^{\text{Penalty Term}} + \overbrace{\sum^k_{i=1} \log \left(   {{\gamma_i !}\over{n^{(P)}_{i,1}!
+f_{\text{Bayesian}} &= \overbrace{\rule{0pt}{1.85em}  Z_2 \cdot k + \ln {{\gamma_i + J_P - 1}\choose{J_P -1}}}^{\text{Penalty Term}} + \overbrace{\sum^k_{i=1} \ln \left(   {{\gamma_i !}\over{n^{(P)}_{i,1}!
 n^{(P)}_{i,2}!
@@
 Edge Positions Term}}\\
-f_{\text{Heuristic}} &= \overbrace{Z_2 \cdot k + \log {{\gamma_i + J_{P_1} - 1}\choose{J_{P_1} -1}} + \log {{\gamma_i + J_{P_2} - 1}\choose{J_{P_2} -1}} }^{\text{Penalty Term}}+\\
-& \overbrace{\sum^k_{i=1}  \left[ \log \left(   {{\gamma_i !}\over{n^{(P_1)}_{i,1}!
+f_{\text{Heuristic}} &= \overbrace{Z_2 \cdot k + \ln {{\gamma_i + J_{P_1} - 1}\choose{J_{P_1} -1}} + \ln {{\gamma_i + J_{P_2} - 1}\choose{J_{P_2} -1}} }^{\text{Penalty Term}}+\\
+& \overbrace{\sum^k_{i=1}  \left[ \ln \left(   {{\gamma_i !}\over{n^{(P_1)}_{i,1}!
 n^{(P_1)}_{i,2}!
-\cdots n^{(P_1)}_{i,J_{P_1}}    }} \right)  + \log \left(   {{\gamma_i !}\over{n^{(P_2)}_{i,1}!
+\cdots n^{(P_1)}_{i,J_{P_1}}    }} \right)  + \ln \left(   {{\gamma_i !}\over{n^{(P_2)}_{i,1}!
 n^{(P_2)}_{i,2} \cdots n^{(P_2)}_{i,J_{P_2}} }} \right) \right]}^{\text{Disc.
@@
     \For {$v = u$ to $N$}
-      \State $H(u,v) \leftarrow H(u,v) + \log((v-u + J_p)!) - \log((J_p -1)!)$
+      \State $H(u,v) \leftarrow H(u,v) + \ln((v-u + J_p)!) - \ln((J_p -1)!)$
       \For {$w = 1$ to $\|\Pi_X\|$}
-        \State $H(u,v) \leftarrow H(u,v) - \log( count_p(u,v,w)!)$
+        \State $H(u,v) \leftarrow H(u,v) - \ln( count_p(u,v,w)!)$
       \EndFor

### 2015-11-19 BN_discretizer_paper.tex
Correct things

@@
           \State $S[v] \leftarrow s$
-          \State $\Lambda[v] \leftarrow M[u] \cup \{ DiscEdge \}$
+          \State $\Lambda[v] \leftarrow \Lambda[u] \cup \{ DiscEdge \}$
         \EndIf
@@
 For the Bayesian network in Fig.
-\ref{fig:auto_graph_1}, the approximation \ref{eq:opt_prob_approx} only reduces runtime and has no influence on discretization result.
+\ref{fig:auto_graph_1}, the approximation Equation \ref{eq:opt_prob_approx} only reduces runtime and has no influence on discretization result.
 MDL principle discretization works not well, since it discretizes each continuous variable by only one interval.
@@
 The discretization result obtained by the optimal Bayesian approach is better than the MDL discretization method in terms of likelihood.
-The heuristic method discretizes variable $G$, $H$ and $J$ into one less interval than the optimal Bayesian approach, and has one more number of intervals on variable $\Lambda$.
+The heuristic method discretizes variable $G$, $H$ and $J$ into one less interval than the optimal Bayesian approach, and has one more number of intervals on variable $M$.
 Although it returns different numbers of intervals and different positions of discretization edges with the optimal Bayesian approach, it still has a good discretization result in terms of likelihood.
@@
 This is due to the number of parents of $E$ in Figure \ref{fig:wine_graph_2} is twice as in \ref{fig:wine_graph_1}.
-Usually, if a variable has more parents, then less number of intervals after discretization it has, since the information from parents are adulterated together.
+Usually, if a variable has more parents, then less number of intervals after discretization it has, since the information from parents are mixed together.
 
@@
 These repeating values cause the high number of intervals for both $C$ and $E$, because in some sense, each repeated-value point form a single discretized area.
-On the other hand, there is no such over repeated values of the raw data on variable $H$.
-Thus, the numbers of intervals after discretization for variable $H$ remains normal, as what we have seen in previous datasets.
+On the other hand, the data instances on variable $H$ is less repeated.
+Thus, some resulting discretized areas cover larger space, instead of just covering a repeated value.
 
@@
 Again, variable $C$ and $E$ have many discretization edges due to the repeated values.
-Although the number of intervals after discretization on $H$ is not large, it captures the distribution of the raw data along with the discretization edges on $E$.
+Although the number of intervals after discretization on $H$ is less the number in Figure \ref{fig:housing_exp1_distr_8_5}, it still captures the distribution of the raw data along with the discretization edges on $E$.
 
@@
   \caption{The discretization result on variable $H$ and $E$ of the network in Figure~\ref{fig:housing_graph_2}.
-Although the number of discretization edges on $H$ is not as large as $E$'s, they still match the distribution of the raw data very well.}
+Although the number of discretization edges on $H$ is less than the number in Figure \ref{fig:housing_exp1_distr_8_5}, it still matches the distribution of the raw data well.}
   \label{fig:housing_exp2_distr_8_5}

### 2015-11-20 BN_discretizer_paper.tex
update

@@
 
-\newcommand{\discset}{\mathcal{M}}
-
 \DeclareMathOperator*{\argmin}{arg\,min}
@@
 \newcommand{\maxpasses}{\hat{n}_\text{cycle}}
+\newcommand{\discset}{\Lambda_{\bm{\cX}}}
 
@@
 They provide an efficient factorization of the joint probability distribution over a set of random variables.
-Bayesian networks first emerged from artificial intelligence research and have been applied to a wide variety of problems, ranging from decision-making systems \citep{DMU_2015} \mykel{better to use a primary source} to medical diagnoses \citep{Lustgarten_2011}.
+Bayesian networks first emerged from artificial intelligence research and have been applied to a wide variety of problems, ranging from decision-making systems \citep{kochenderfer2012next} to medical diagnoses \citep{Lustgarten_2011}.
 In many application, it is assume that all random variables in Bayesian networks are discrete, since many Bayesian network algorithms are unable to deal with continuous variables efficiently.
-In addition, many of the commonly used Bayesian network software packages, such as \todo{find packages}, assume discrete variables.
+In addition, many of the commonly used Bayesian network software packages, such as Netica \citep{netica1992}, SMILearn \citep{druzdzel1999smile}, and bnlearn \citep{bnlearn2010}, are geared towards discrete variables.
 However, various applications require the use of continuous variables, such as position and velocity in dynamic systems \citep{kochenderfer2010airspace}.
@@
 This work is primarily concerned with the minimum description length (MDL) principle discretization \citep{Friedman_1996} and MODL discretization \citep{Boulle_2006} methods.
-The former is the predominant discretization method for continuous variables in Bayesian networks, and is compared to our proposed Bayesian method in Section \ref{sec:experiments}.
+The former is the predominant discretization method for continuous variables in Bayesian networks, and is compared to our proposed Bayesian method in Section~\ref{sec:experiments}.
 The latter is a Bayesian discretization method for one continuous variable against a discrete target class, which our proposed method generalizes to Bayesian networks.
@@
 The proposed method optimizes the discretization policy relative to the network and takes parents, children, and spouse variables into account.
-The optimal single-variable discretization method is derived in Section \ref{sec:single_var}, and a second heuristic method is proposed which reduces the runtime from exponential to polynomial.
-Section \ref{sec:multi_var} covers Bayesian networks with multiple continuous variables and discretization while simultaneously learning network structure.
-The paper concludes with a comparison against the existing minimum-description length \citep{Friedman_1996} method on real-world datasets in Section \ref{sec:experiments}.
+The optimal single-variable discretization method is derived in Section~\ref{sec:single_var}, and a second heuristic method is proposed which reduces the runtime from exponential to polynomial.
+Section~\ref{sec:multi_var} covers Bayesian networks with multiple continuous variables and discretization while simultaneously learning network structure.
+The paper concludes with a comparison against the existing minimum-description length \citep{Friedman_1996} method on real-world datasets in Section~\ref{sec:experiments}.
 
@@
 
-From the first principle one obtains the $P(\Lambda)$ of $\Lambda$ described in Equation \ref{eq:disc_def}
+From the first principle one obtains the $P(\Lambda)$ of $\Lambda$ described in Equation~\ref{eq:disc_def}
 
@@
 
-The objective function can be formulated given equations \ref{eq:p_M}, \ref{eq:p_D_given_M}, \ref{eq:likelihood_one}, and \ref{eq:likelihood_three}.
+The objective function can be formulated given equations~\ref{eq:p_M},~\ref{eq:p_D_given_M},~\ref{eq:likelihood_one}, and~\ref{eq:likelihood_three}.
 The log-inverse of $P(\Lambda) \cdot P(D_{-\cX} \mid \Lambda)$ is minimized for computational convenience:
@@
       \State $H \leftarrow$ an $N \times N$ matrix such that $H[u,v] = h(u,v)$ (see Algorithm~\ref{alg:h} in Appendix)
-      \State $s_{1:m} \leftarrow$ an increasing sequence of integers defined in Section \ref{subsec:disc_policy}
+      \State $s_{1:m} \leftarrow$ an increasing sequence of integers defined in Section~\ref{subsec:disc_policy}
       \State $L \leftarrow$ the largest cardinality over all discrete variables in the Markov blanket of $X$
@@
 
-Algorithm \ref{alg:disc_one} has an exponential $\bigo\paren{L'^{n_p} \cdot N^2}$ runtime which severely limits discretization in networks with a large number of discretization intervals or parent variables.
+Algorithm~\ref{alg:disc_one} has an exponential $\bigo\paren{L'^{n_p} \cdot N^2}$ runtime which severely limits discretization in networks with a large number of discretization intervals or parent variables.
 This section introduces an approximation to the objective function that significantly reduces the runtime and still preserves the quality of discretization.
@@
 \begin{algorithm}
-  \caption{Discretization of multiple continuous variables \todo{Fix label reference number}}
+  \caption{Discretization of multiple continuous variables}
   \label{alg:disc_two}
@@
   \Function{DiscretizeAll}{$D$, $G$, $\bm{\cX}$, $\maxpasses$}
-    \State $\Lambda_{\bm{\cX}} \leftarrow$ the discretization policies for each $\cX$ in $\bm{\cX}$
-    \State $D^* \leftarrow $ the dataset $D$ discretized according to $\Lambda_{\bm{\cX}}$
+    \State $\discset \leftarrow$ the discretization policies for each $\cX$ in $\bm{\cX}$
+    \State $D^* \leftarrow $ the dataset $D$ discretized according to $\discset$
     \State $k \leftarrow \textsc{Median}\paren{\curly{ |X| \text{ s.t. } X \text{ does not have corresponding } \cX \text{ in } \bm{\cX} }}$
-    \For {$\paren{X, \cX}$ such that $\cX \in \bm{\cX}$}
+    \For {$\paren{\cX, X}$ such that $\cX \in \bm{\cX}$ and $X$ is the discretized version of $\cX$}
       \State $\Lambda_{\cX} \leftarrow$ equal-width discretization of $\cX$ with $k$ intervals
@@
     \State $n_\text{cycle} \leftarrow 0$
-    \While {$\Lambda_{\bm{\cX}}$ has not converged \textbf{and} $n_\text{cycle} \leq \maxpasses$}
+    \While {$\discset$ has not converged \textbf{and} $n_\text{cycle} \leq \maxpasses$}
       \State increment {$n_\text{cycle}$}
-      \For {$\paren{X, \cX}$ such that $\cX \in \bm{\cX}$}
+      \For {$\paren{\cX, X}$ such that $\cX \in \bm{\cX}$}
         \State {$D^*_X \leftarrow D_{\cX}$}
@@
     \EndWhile
-    \State \Return $\Lambda_{\bm{\cX}}$
+    \State \Return $\discset$
   \EndFunction
@@
 It is common practice to run K2 multiple times with different variable permutations and to then choose the structure with the highest score.
-As such, Algorithm \ref{alg:structure_learn} is run multiple times with different variable permutations and the discretized Bayesian network with the highest score is retaiend.
+As such, Algorithm~\ref{alg:structure_learn} is run multiple times with different variable permutations and the discretized Bayesian network with the highest score is retaiend.
 
@@
 All experiments were run on datasets from the publically available Irvine machine learning repository \citep{Lichman_2013}.
-Variables are labelled alphabetically in the order given on the dataset information webpage.
-Subscripts inducate the number of discretized intervals.
-Shaded nodes are originally discrete and unshaded nodes are originally continuous.
-
-For each dataset, the experiment consists of two parts.
-In the first part, the Bayesian network structure is known in advance, which is obtained by equal-width prediscretization and the K2 algorithm.
-In the second part, the Bayesian netowrk structure is not provided in advance, and it is learned during the discretization process.
-
-The discretizations are compared using the mean cross validated log-likelihood of the data set $D$ given the resulting graph structure $G$ and discretization policy set $\discset$.
-The log-likelihood contains two components,
+Variables are labelled alphabetically in the order given on the dataset information webpage
+In the figures that follow, shaded nodes correspond to initially discrete variables and the subscripts indicate the number of discrete instantiations.
+
+Two experiments were conducted on each dataset.
+The first experiment compares the performance of the optimal Bayesian discretization method, the heuristic Bayesian discretization method, and MDL on a known Bayesian network structure.
+The structure was obtained by prediscretizing each continuous variable into $k$ uniform-width intervals, where $k$ is the median number of instantiations of the discrete variables, and using the structure with the highest Bayesian score from one thousand runs of the K2 algorithm.
+The second experiment compares the same methods applied when simultaneously discretizing and learning network structure.
+
+The discretizations are compared using the mean cross validated log-likelihood of the data $D$ given the graph structure $G$ and discretization policies $\discset$.
+The log-likelihood has two components,
 
@@
 where $D$ is the original dataset and $D^*$ is the dataset discretized according to $\discset$.
-The log-likelihood of the discretized dataset is the Bayesian score (Equation ~\ref{eq:BayesianScore}) evaluated with a uniform prior.
+The log-likelihood of the discretized dataset is the Bayesian score (Equation~\ref{eq:BayesianScore}) evaluated with a uniform prior over graph structures and a uniform Dirichlet prior ($\alpha_{ijk} = 1$ for all $i$, $j$, and $k$).
 The log-likelihood of the original dataset given the discrete dataset is
@@
 \begin{equation}
-  \ln p(D\mid \discset, D^*) = \sum_{i=1}^n \sum_{j=1}^{q_i} \sum_{k=1}^{r_i} m_{ijk} \ln\paren{
+  \ln p\paren{D\mid \discset, D^*} = \sum_{i=1}^n
+  1\curly{X_i \text{ orig. cont.}}
+  \sum_{j=1}^{q_i} \sum_{k=1}^{r_i} m_{ijk} \ln\paren{
     \frac{
@@
     }{
-      \discset^{(ij)}_{k+1} - \discset^{(ij)}_{k}
+      e^{\Lambda_{\cX_i}}_{k+1} - e^{\Lambda_{\cX_i}}_{k}
     }
@@
 \end{equation}
-
-The proposed Bayesian discretization method is compared against MDL.
-For a Bayesian network with a single continuous variable $X$, the MDL objective function is
+\tim{The above equation needs work.}
+
+\noindent
+The mean cross-validated log-likelihood is the mean log-likelihood on the witheld dataset among cross-validation folds.
+Cross-validation directly estimates generalization error.
+\todo{Ten} folds were used in each experiment.
+
+The optimal discretization policy for MDL is found with dynamic programming in a similar manner as with the Bayesian method.
+For a Bayesian network with a single continuous variable $\cX$, the MDL objective function is
 
@@
   \label{eqn:MDL}
+  \todo{
   \begin{aligned}
-\frac{1}{2} \ln(N) \left\lbrace  \lvert \Pi_{X_i} \rvert (\lvert X^*_i \rvert - 1) +
- {\sum_{j,X_i \in \Pi_{X_i}}} \lvert \Pi_{X^*_j} \rvert (\lvert X_j \rvert - 1) \right\rbrace + \ln(\lvert {X^*_i} \rvert) \\
- + (N_i-1) H \left( {{|X^*_i| - 1}\over{N_i -1}}  \right) -N \cdot \left[ I(X^*_i,\Pi_{X_i}) + {\sum_{j,X_i \in \Pi_{X_i}}} I(X_j, \Pi_{X^*_j}) \right]\text{,}
+  \frac{1}{2} \ln(n) \left\lbrace  \lvert \Pa_{X_i} \rvert (\lvert X_i \rvert - 1) +
+   {\sum_{j,\cX_i \in \Pa_{X_i}}} \lvert \Pa_{X_j} \rvert (\lvert \cX_j \rvert - 1) \right\rbrace + \ln(\lvert {\cX_i} \rvert) \\
+   + (N_i-1) H \paren{\frac{|X^*_i| - 1}{N_i -1}} -n \cdot \left[ I(X_i,\Pa_{X_i}) + {\sum_{j,\cX_i \in \Pa_{\cX_i}}} I(\cX_j, \Pa_{X_j}) \right]\text{,}
   \end{aligned}
-\end{equation}
-
-where $I(A,B)$ is the mutual information between the discrete variables $A$ and $B$, ${H(p) = -p \ln(p) - (1-p) \ln(1-p)}$, and \todo{$X^*_i$ is the discretized version of the $i$th sample of $X$}.
-The optimal discretization policy is found with dynamic programming in a similar manner as with the Bayesian method.
+  }
+\end{equation}
+
+where $I(A,B)$ is the mutual information between two discrete variables $A$ and $B$, ${H(p) = -p \ln(p) - (1-p) \ln(1-p)}$, and \todo{$X^*_i$ is the discretized version of the $i$th sample of $X$}.
 
@@
 
-In this subsection, two experiments are conducted on the Auto MPG dataset from the Irvine repository \citep{Lichman_2013}.
-The dataset has \num{392} instances after deleting the six instances with missing data, and eight variables.
-Three variables are discrete: $B$, $G$, and $H$ with cardinality \num{5}, \num{13}, and \num{3} respectively.
-Two expiriments are conducted, one with a given network structure and one in which the structure is learned.
+The Auto MPG dataset contains variables related to the fuel consumption of automobiles in urban driving.
+The dataset has \num{392} samples over eight variables, not including six instances with missing data.
+Three variables are discrete: $B$, $G$, and $H$, with \num{5}, \num{13}, and \num{3} instantiations respectively.
 
@@
 
-The optimal Bayesian approach and the MDL discretization method are tested on Auto MPG data given the network network in Fig.
-\ref{fig:auto_graph_1}.
-This structure was obtained by prediscretizing each continuous variable into five uniform-width intervals, where five is the median cardinality of the discrete variables, and then taking the most frequent structure from a thousand runs of K2.
-\yichun{most frequent?}
+The optimal Bayesian approach and the MDL discretization method were tested on the Auto MPG data using the network network shown in Figure~\ref{fig:auto_graph_1}.
+This structure was obtained by prediscretizing each continuous variable into five uniform-width intervals, where five is the median cardinality of the discrete variables, and then taking the structure with highest likelihood from one thousand runs of K2.
 
@@
    \input{graph_autocar_1}
-   \caption{Structure from prediscretized K2 structure learning to compare the methods for Auto MPG dataset}
+   \caption{Bayesian network structure obtained from running K2 on the prediscretiszed Auto MPG dataset}
   \label{fig:auto_graph_1}
@@
 
-Table \ref{table:auto_disc_table_1} shows the positions of discretization edges, and log-likelihood of 10-fold cross validation by three discretization methods.
-For the Bayesian network in Fig.
-\ref{fig:auto_graph_1}, the approximation Equation \ref{eq:opt_prob_approx} only reduces runtime and has no influence on discretization result.
-MDL principle discretization works not well, since it discretizes each continuous variable by only one interval.
-The reason that the MDL method discretizes variables into too few number of intervals is discussed in Section \ref{subsec:discuss_exp}.
+Table~\ref{table:auto_disc_table_1} lists the discretization edges and mean log-likelihoods under 10-fold cross validation of the structure resulting from each discretization method.
+The results indicate that the heuristic Bayesian method produces exactly the same discretization policy as the optimal Bayesian method.
+The MDL method does not produce any discretization edges, assigning one continuous interval to each continuous variable, and produces the structure with the lowest score.
+The cause behind MDL's discretization policy is discussed in Section~\ref{subsec:discuss_exp}.
 
@@
   \centering
-  \caption{Discretization results of Auto MPG dataset based on the graph in Fig.
-\ref{fig:auto_graph_1} by the three methods.
-The first five rows are discretization edges on each continuous variable.
-The last row is the log-likelihood of the dataset based on the discretization results.
-The discretization result for the heuristic matches that for the optimal Bayesian approach.
-The MDL method is less sensitive to distribution of values of other variables and fails to return discretization edges.}
+  \caption{
+    Results from discretization of the Auto MPG dataset with fixed structure from Figure~\ref{fig:auto_graph_1}.
+    The first five rows list the discretization edges for each continuous variable.
+    The last row lists the mean cross-validated log-likelihood; positive values are better.
+    The optimal and heuristic Bayesian discretization policies are identical and the MDL method does not produce any discretization edges.
+  }
   \input{table_autoMPG_1.tex}
@@
 
-Figure \ref{fig:auto_exp1_distr_1_3} compares the discretization result on continuous variables $A$ and $C$ with the raw data of Auto MPG data set.
-The color of discretized area shows the probability of a sample being in the discretized area.
-The black dots in Figure \ref{fig:auto_exp1_distr_1_3} demonstrate the distribution of the raw data.
+Figure~\ref{fig:auto_exp1_distr_1_3} compares the Bayesian discretizaton policy for variables $A$ and $C$ with the original Auto MPG data.
+The color of discretized regions indicates the marginal probability of a sample from $P(A,C)$ being drawn from that region.
+The black dots in Figure~\ref{fig:auto_exp1_distr_1_3} demonstrate the distribution of the raw data.
 As shown in the figure, the discretization edges obtained by the optimal Bayesian approach and the resulting marginalized probability match the raw data well.
@@
   \input{graph_auto_exp1_distr_1_3}
-  \caption{Comparison of the raw data and discretization result on variable $A$ and $C$ by the optimal Bayesian approach.
-The marginal probabilities of discretized areas match the distribution of the taw data very well.}
+  \caption{
+    Comparison of the Bayesian discretization policy for variables $A$ and $C$ to the original Auto MPG data.
+    The marginal probabilities of discretized regions closely match the raw data.
+  }
   \label{fig:auto_exp1_distr_1_3}
@@
 If the network structure is not known in advance, it should be learned along with the discretization process.
-Figure \ref{fig:auto_graph_2} show a learned discrete-valued Bayesian network and the corresponding numbers of intervals after discretization for each continuous variable.
-This result is obtained by running Algorithm \ref{alg:structure_learn} fifty times (without the approximation) and choosing the one with the highest K2 score.
+Figure~\ref{fig:auto_graph_2} show a learned discrete-valued Bayesian network and the corresponding numbers of intervals after discretization for each continuous variable.
+This result is obtained by running Algorithm~\ref{alg:structure_learn} fifty times (without the approximation) and choosing the one with the highest K2 score.
 
@@
 
-Figure \ref{fig:auto_exp2_distr_1_3} shows the discretization edges on variable $A$ and $C$ in Figure \ref{fig:auto_graph_2} along with the raw data.
+Figure~\ref{fig:auto_exp2_distr_1_3} shows the discretization edges on variable $A$ and $C$ in Figure~\ref{fig:auto_graph_2} along with the raw data.
 Again, the black dots are raw data points.
 The colors of discretized areas are the corresponding maginalized probability.
-Although the numbers of discretization edges of $A$ and $C$ shown in Figure \ref{fig:auto_exp2_distr_1_3} are less than Figure \ref{fig:auto_exp2_distr_1_3}, they still have a good capture of raw data distribution.
+Although the numbers of discretization edges of $A$ and $C$ shown in Figure~\ref{fig:auto_exp2_distr_1_3} are less than Figure~\ref{fig:auto_exp2_distr_1_3}, they still have a good capture of raw data distribution.
 This indicates that although the discretization result of the optimal Bayesian approach might vary according to the network structure, it still preserves the quality of discretization.
@@
       \input{graph_auto_exp2_distr_1_3}
-  \caption{Comparison of the raw data and discretization result on variable $A$ and $C$ in Figure \ref{fig:auto_graph_2}.
-Although the number of discretization edges is less than in Figure \ref{fig:auto_exp1_distr_1_3}, it still matches the raw data distribution very well.}
+  \caption{Comparison of the raw data and discretization result on variable $A$ and $C$ in Figure~\ref{fig:auto_graph_2}.
+Although the number of discretization edges is less than in Figure~\ref{fig:auto_exp1_distr_1_3}, it still matches the raw data distribution very well.}
   \label{fig:auto_exp2_distr_1_3}
@@
 
-The Bayesian network in Figure \ref{fig:wine_graph_1} is obtained by equal-width discretizing each continuous variable into 3 intervals and running K2 a thousand times.
-Table \ref{table:wine_disc_table_1} shows a comparison between the optimal Bayesian approach and the MDL principle discretization method.
+The Bayesian network in Figure~\ref{fig:wine_graph_1} is obtained by equal-width discretizing each continuous variable into 3 intervals and running K2 one thousand times.
+Table~\ref{table:wine_disc_table_1} shows a comparison between the optimal Bayesian approach and the MDL principle discretization method.
 The discretization result obtained by the optimal Bayesian approach is better than the MDL discretization method in terms of likelihood.
@@
   \centering
-  \caption{Discretization results of Wine dataset based on the network in Fig.
-\ref{fig:wine_graph_1} by the three different methods.
+  \caption{Discretization results of Wine dataset based on the network in Figure~\ref{fig:wine_graph_1} by the three different methods.
 The first thirteen rows are discretization edges on each continuos variable.
@@
 
-Figure \ref{fig:wine_exp1_distr} compares the discretization results by the optimal Bayesian approach and the MDL method.
+Figure~\ref{fig:wine_exp1_distr} compares the discretization results by the optimal Bayesian approach and the MDL method.
 The discretization edges \num{17.9} on $E$ and \num{34.6} on $K$ appear in both plots.
@@
 The MDL method does not capture this edge due to its low sensitivity toward distribution.
-For more discussion about the sensitivity, see Section \ref{subsec:discuss_exp}.
+For more discussion about the sensitivity, see Section~\ref{subsec:discuss_exp}.
 
@@
 
-Figure \ref{fig:wine_graph_2} is the learned discrete-valued Bayesian network from the Wine dataset, and it is obtained by running Algorithm \ref{alg:structure_learn} fifty times.
+Figure~\ref{fig:wine_graph_2} is the learned discrete-valued Bayesian network from the Wine dataset, and it is obtained by running Algorithm~\ref{alg:structure_learn} fifty times.
 The integer numbers next to variables are cardinality numbers of variables.
-By comparing Figure \ref{fig:wine_graph_2} with \ref{fig:wine_graph_1}, it shows that the the Bayesian network obtained by Algorithm \ref{alg:structure_learn} has more edges than the network obtained by prediscretization and the K2 algorithm.
+By comparing Figure~\ref{fig:wine_graph_2} with~\ref{fig:wine_graph_1}, it shows that the the Bayesian network obtained by Algorithm~\ref{alg:structure_learn} has more edges than the network obtained by prediscretization and the K2 algorithm.
 This is sensible, since when a network is learned along with discretization, variables have more freedom, by adjusting discretization edges, to construct the correlations with other variables and thus have more edges in the network.
 
-Figure \ref{fig:wine_exp2_distr} shows the discretization result on variable $E$ and $K$.
-The discretization edge at \num{17.9} on variable $E$ also appers in Figure \ref{fig:wine_exp1_distr}.
+Figure~\ref{fig:wine_exp2_distr} shows the discretization result on variable $E$ and $K$.
+The discretization edge at \num{17.9} on variable $E$ also appers in Figure~\ref{fig:wine_exp1_distr}.
 This indicates that some discretization edges are robust against the network structure.
-Furthermore, in Figure \ref{fig:wine_exp2_distr}, the discretization edge at \num{23.5} on $E$ is lost.
-This is due to the number of parents of $E$ in Figure \ref{fig:wine_graph_2} is twice as in \ref{fig:wine_graph_1}.
+Furthermore, in Figure~\ref{fig:wine_exp2_distr}, the discretization edge at \num{23.5} on $E$ is lost.
+This is due to the number of parents of $E$ in Figure~\ref{fig:wine_graph_2} is twice as in~\ref{fig:wine_graph_1}.
 Usually, if a variable has more parents, then less number of intervals after discretization it has, since the information from parents are mixed together.
@@
  \end{tabular}
-  \caption{The discretization result on variable $E$ and $K$ of the learned network in Figure \ref{fig:wine_graph_2}.
-The discretization edge \num{17.9} on $E$ also appear in \ref{fig:wine_exp1_distr}.
+  \caption{The discretization result on variable $E$ and $K$ of the learned network in Figure~\ref{fig:wine_graph_2}.
+The discretization edge \num{17.9} on $E$ also appear in~\ref{fig:wine_exp1_distr}.
 This indicates that some discretization edges are robust again the network structure.}
@@
 
-The Bayesian network structure in Figure \ref{fig:housing_graph_1} is obtained by prediscretizing each continuous variable into five uniform-width intervals, then running the K2 algorithm one thousands time and choosing the network with the highest K2 score.
-Table \ref{table:housing_disc_table_1} shows the numbers of intervals after discretization on each continuous variables and also the log-likelihood of the dataset based on the discretization results.
+The Bayesian network structure in Figure~\ref{fig:housing_graph_1} is obtained by prediscretizing each continuous variable into five uniform-width intervals, then running the K2 algorithm one thousands time and choosing the network with the highest K2 score.
+Table~\ref{table:housing_disc_table_1} shows the numbers of intervals after discretization on each continuous variables and also the log-likelihood of the dataset based on the discretization results.
 MDL method again does not discretize most variables.
@@
 These numbers of intervals returned by the three methods illustrate that the heuristic method is over sensitive and the MDL method is less sensitive.
-The properties of sensitivity of the three algorithms will be discussed in Section \ref{subsec:discuss_exp}.
+The properties of sensitivity of the three algorithms will be discussed in Section~\ref{subsec:discuss_exp}.
 On the other hand, although the heuristic method leads to high number of intervals, its corresponding log-likelihood on the dataset is not significantly better than the optimal Bayesian approach.
@@
   \centering
-  %\begin{tabular}{cc}
-  \scalebox{0.8}{
-   \input{graph_housing_1}}
-   %\end{tabular}
+  \scalebox{0.8}{\input{graph_housing_1}}
   \caption{Structure from prediscretized K2 structure learning to compare the methods for Housing dataset}
@@
   \centering
-  \caption{Discretization result of Housing dataset based on the graph in Figure~\ref{fig:housing_graph_1}.
+  \caption{
+    Discretization result of Housing dataset based on the graph in Figure~\ref{fig:housing_graph_1}.
 The first twelve rows show the numbers of intervals after discretization by the three method.
@@
 The optimal Bayesian approach has a good control on number of intervals.
-\tim{Fig.
-vs.
-Figure}}
-  \scalebox{1.0}{
-  \input{table_housing_1.tex}
-  }
-
+  }
+  \scalebox{1.0}{\input{table_housing_1.tex}}
   \label{table:housing_disc_table_1}
@@
 Again, variable $C$ and $E$ have many discretization edges due to the repeated values.
-Although the number of intervals after discretization on $H$ is less the number in Figure \ref{fig:housing_exp1_distr_8_5}, it still captures the distribution of the raw data along with the discretization edges on $E$.
+Although the number of intervals after discretization on $H$ is less the number in Figure~\ref{fig:housing_exp1_distr_8_5}, it still captures the distribution of the raw data along with the discretization edges on $E$.
 
@@
   \caption{The discretization result on variable $H$ and $E$ of the network in Figure~\ref{fig:housing_graph_2}.
-Although the number of discretization edges on $H$ is less than the number in Figure \ref{fig:housing_exp1_distr_8_5}, it still matches the distribution of the raw data well.}
+Although the number of discretization edges on $H$ is less than the number in Figure~\ref{fig:housing_exp1_distr_8_5}, it still matches the distribution of the raw data well.}
   \label{fig:housing_exp2_distr_8_5}
@@
 
-\subsection{Discussions}
+\subsection{Discussion}
 \label{subsec:discuss_exp}
@@
 \centering
-%    % \begin{tabular}{cc}
   \input{graph_exp_discuss}
-%    % \end{tabular}
   \caption{A simple Bayesian network that is used to demonstrate the sensitivity of the three methods}
@@
 
-To quantatively discuss the sensitivity of the three methods, consider the Bayesian network in Figure \ref{fig:exp_discuss}, where $X$ is continuous-valued and $P_1$ and $P_2$ is discrete-valued.
-Let $\Pi_X = \{  P_1, P_2 \}$.
-Assume $D_X = \{1.0,2.0,3.0, \ldots N \}$.
-Therefore, the corresponding objective functions to discretize $X$ in the three methods are:
-
-{\begin{small}
+To quantatively discuss the sensitivity of the three methods to the number of discretization intervals, consider the Bayesian network in Figure~\ref{fig:exp_discuss}, where $\cX$ is continuous and $P_1$ and $P_2$ are discrete.
+If $\Pa_{\cX} = \curly{P_1, P_2}$ and $D_{\cX} = \curly{1.0,2.0,3.0, \ldots n}$, then the corresponding objective functions for the three discretization methods are:
+
+\begin{small}
   \begin{equation}
   \begin{aligned}
-f_{\text{MDL}} & = \overbrace{Z_1 \cdot k + \ln(k) + \ln {{N +k - 1}\choose{k -1}} }^{\text{Penalty Term}}+   \overbrace{\rule{0pt}{1.35em} \ln(N) \cdot I(X^*, \Pi_X)}^{\text{Disc.
-Edge Positions Term}} \\
-f_{\text{Bayesian}} &= \overbrace{\rule{0pt}{1.85em}  Z_2 \cdot k + \ln {{\gamma_i + J_P - 1}\choose{J_P -1}}}^{\text{Penalty Term}} + \overbrace{\sum^k_{i=1} \ln \left(   {{\gamma_i !}\over{n^{(P)}_{i,1}!
+  f_{\text{MDL}} & = \overbrace{Z_1 \cdot k + \ln(k) + \ln {{n +k - 1}\choose{k -1}} }^{\text{Penalty Term}}+   \overbrace{\rule{0pt}{1.35em} \ln(N) \cdot I(X^*, \Pi_X)}^{\text{Edge Position Term}} \\
+  f_{\text{Bayesian}} &= \overbrace{\rule{0pt}{1.85em}  Z_2 \cdot k + \sum_{i=1}^k \ln {{\gamma_i + J_P - 1}\choose{J_P -1}}}^{\text{Penalty Term}} + \overbrace{\sum^k_{i=1} \ln \left(   {{\gamma_i !}\over{n^{(P)}_{i,1}!
 n^{(P)}_{i,2}!
 \cdots n^{(P)}_{i,J_P}!
-}} \right) }^{\text{Disc.
-Edge Positions Term}}\\
-f_{\text{Heuristic}} &= \overbrace{Z_2 \cdot k + \ln {{\gamma_i + J_{P_1} - 1}\choose{J_{P_1} -1}} + \ln {{\gamma_i + J_{P_2} - 1}\choose{J_{P_2} -1}} }^{\text{Penalty Term}}+\\
+}} \right) }^{\text{Edge Position Term}}\\
+  f_{\text{Heuristic}} &= \overbrace{Z_2 \cdot k + \sum_{i=1}^k \ln {{\gamma_i + J_{P_1} - 1}\choose{J_{P_1} -1}} + \sum_{i=1}^k \ln {{\gamma_i + J_{P_2} - 1}\choose{J_{P_2} -1}} }^{\text{Penalty Term}}+\\
   & \overbrace{\sum^k_{i=1}  \left[ \ln \left(   {{\gamma_i !}\over{n^{(P_1)}_{i,1}!
@@
 \cdots n^{(P_1)}_{i,J_{P_1}}    }} \right)  + \ln \left(   {{\gamma_i !}\over{n^{(P_2)}_{i,1}!
-n^{(P_2)}_{i,2} \cdots n^{(P_2)}_{i,J_{P_2}} }} \right) \right]}^{\text{Disc.
-Edge Positions Term}}
-\end{aligned}
-\end{equation}
-\end{small}}
-
-, where $Z_1$ and $Z_2$ are two constants, $k$ is the number of intervals after discretization, $X^*$ is the discretized version of $X$, and $I(X^*, \Pi_X)$ is the mutual information between $X^*$ and its parent variables.
-Note that the third term in $f_{\text{MDL}}$ is approximated by $H(p)$ as in Equation \ref{eqn:MDL} in the original paper \citep{Friedman_1996}.
-
-The sensitivities toward the value distribution in $D_{\Pi_X}$ are determined by the `` Disc.
-Edge Positions Term" in the three objective functions.
-Since the penaltis of the numbers of intervals after discretization in the three objective functions take the similar form, if the `` Disc.
-Edge Positions Term" varies more severely due to positions of discretization edges, then the corresponding method is more sensitive.
-The `` Disc.
-Edge Positions Term" in $f_{\text{MDL}}$, which is made out of the mutual information, varies less severely than the terms in $f_{\text{Bayesian}}$ and $f_{\text{Heuristic}}$, since it senses the distribution in $D_{\Pi_X}$ by empirical probability distributions, instead of the factorial terms such in $f_{\text{Bayesian}}$ and $f_{\text{Heuristic}}$.
-Furthermore, the `` Disc.
-Edge Positions Term" in $f_{\text{Heuristic}}$ varies more aggressively than the term in $f_{\text{Bayesian}}$.
-Therefore, the MDL method is less sensitive and the heuristic is over sensitive toward the value distributions in other variables.
-The effect of sensitivity can be shown as the numbers of intervals after discretization in the previous experiment.
+n^{(P_2)}_{i,2} \cdots n^{(P_2)}_{i,J_{P_2}} }} \right) \right]}^{\text{Edge Position Term}}
+  \end{aligned}\text{,}
+\end{equation}
+\end{small}
+
+\noindent
+where $Z_1$ and $Z_2$ are constant over discretizations, $k$ is the number of discretization intervals, and $I\paren{A, B} = \sum_{a,b} \hat{P}(a,b) \ln\frac{\hat{P}(a,b)}{\hat{P}(a)p(b)}$ is the mutual information.
+Note that the third term of $f_\text{MDL}$ had been approximated using $H(p)$ (see Equation~\ref{eqn:MDL}) in the original work by \cite{Friedman_1996} but here is written without that approximation.
+
+The sensitivities of each method to the discretization edges are captured in the edge position terms, as the penalty terms are similar across methods.
+The value of the edge position term for MDL is primarly determined by the mutual information, which varies less severely than the corresponding terms for the Bayesian methods.
+The MDL term uses emperical probability distributions, based off of ratios of counts, whereas the Bayesian methods use factorial terms, and thus vary less severely.
+Futhermore, the term for the heuristic Bayesian method varies more aggresively than the term for the optimal Bayesian method, as it has two terms.
+The MDL method is thus the least sensitive to the discretization edges and the heuristic Bayesian method is over-sensitive.
+This sensitivity gives rise to the relative performance of each method in the experiments conducted above.
 
@@
 This work can extend the usage of Bayesian networks in science and engineering, especially for the fields that require discrete-valued variables but the learning data is mixed and numerical.
-In the future, we plan to generalize the work to the datast that has high dimensional variables, for example, 3 dimensional positions of drones, which makes the sorting in Equation \ref{eq:p_M} fails.
+In the future, we plan to generalize the work to the datast that has high dimensional variables, for example, 3 dimensional positions of drones, which makes the sorting in Equation~\ref{eq:p_M} fails.
 

### 2015-11-20 graph_auto_exp1_distr_1_3.tex
update

@@
 			        ytick={0,0.05,...,0.51},
+			        ylabel=marginal probability density,
 			        yticklabel style={

### 2015-11-20 BN_discretizer_paper.tex
worked through Discretization with Fixed Structure of Housing

@@
 
-The optimal Bayesian approach and the MDL discretization method were tested on the Auto MPG data using the network network shown in Figure~\ref{fig:auto_graph_1}.
+The Bayesian approaches and the MDL discretization method were tested on the Auto MPG data using the network network shown in Figure~\ref{fig:auto_graph_1}.
 This structure was obtained by prediscretizing each continuous variable into five uniform-width intervals, where five is the median cardinality of the discrete variables, and then taking the structure with highest likelihood from one thousand runs of K2.
@@
 
-Table~\ref{table:auto_disc_table_1} lists the discretization edges and mean log-likelihoods under 10-fold cross validation of the structure resulting from each discretization method.
+Table~\ref{table:auto_disc_table_1} lists the discretization edges and mean log-likelihoods under 10-fold cross validation of the discrete Bayesian network resulting from each discretization method.
 The results indicate that the heuristic Bayesian method produces exactly the same discretization policy as the optimal Bayesian method.
@@
 Figure~\ref{fig:auto_exp1_distr_1_3} compares the Bayesian discretizaton policy for variables $A$ and $C$ with the original Auto MPG data.
-The color of discretized regions indicates the marginal probability of a sample from $P(A,C)$ being drawn from that region.
-The black dots in Figure~\ref{fig:auto_exp1_distr_1_3} demonstrate the distribution of the raw data.
+The black marks are the original Auto MPG samples.
+The color of a discretized region indicates the marginal probability of a sample from $P(A,C)$ being drawn from that region.
 As shown in the figure, the discretization edges obtained by the optimal Bayesian approach and the resulting marginalized probability match the raw data well.
@@
   \caption{
-    Comparison of the Bayesian discretization policy for variables $A$ and $C$ to the original Auto MPG data.
+    Comparison of the Bayesian discretization policy for variables $A$ and $C$ to the original Auto MPG data learned with a fixed network.
     The marginal probabilities of discretized regions closely match the raw data.
@@
 
-If the network structure is not known in advance, it should be learned along with the discretization process.
-Figure~\ref{fig:auto_graph_2} show a learned discrete-valued Bayesian network and the corresponding numbers of intervals after discretization for each continuous variable.
-This result is obtained by running Algorithm~\ref{alg:structure_learn} fifty times (without the approximation) and choosing the one with the highest K2 score.
+In this experiment the network structure was not fixed in advance and was learned simultaneously with the discretization policies.
+Figure~\ref{fig:auto_graph_2} shows a learned Bayesian network structure and the corresponding numbers of intervals after discretization for each continuous variable.
+This result was obtained by running Algorithm~\ref{alg:structure_learn} fifty times using the optimal Bayesian method and choosing the structure with the highest likelihood.
 
@@
   \input{graph_autocar_2}
-  \caption{The learned discrete-valued Bayesian network from the Auto MPG dataset}
+  \caption{The discrete-valued Bayesian network learned from the Auto MPG dataset}
   \label{fig:auto_graph_2}
@@
 
-Figure~\ref{fig:auto_exp2_distr_1_3} shows the discretization edges on variable $A$ and $C$ in Figure~\ref{fig:auto_graph_2} along with the raw data.
-Again, the black dots are raw data points.
-The colors of discretized areas are the corresponding maginalized probability.
-Although the numbers of discretization edges of $A$ and $C$ shown in Figure~\ref{fig:auto_exp2_distr_1_3} are less than Figure~\ref{fig:auto_exp2_distr_1_3}, they still have a good capture of raw data distribution.
-This indicates that although the discretization result of the optimal Bayesian approach might vary according to the network structure, it still preserves the quality of discretization.
+Figure~\ref{fig:auto_exp2_distr_1_3} compares the Bayesian discretizaton policy for variables $A$ and $C$ in the learned network with the original Auto MPG data.
+The color of a discretized region indicates the marginal probability of a sample from $P(A,C)$ being drawn from that region.
+Although there are fewer discretization edges for $A$ and $C$ in the learned network, the marginal distribution is still captured.
+Although the discretization result of the optimal Bayesian approach may vary according to the network structure, it still produces high-quality discretizations.
 
@@
   \input{graph_auto_exp2_distr_1_3}
-  \caption{Comparison of the raw data and discretization result on variable $A$ and $C$ in Figure~\ref{fig:auto_graph_2}.
-Although the number of discretization edges is less than in Figure~\ref{fig:auto_exp1_distr_1_3}, it still matches the raw data distribution very well.}
+  \caption{
+    Comparison of the optimal Bayesian discretization policy for variables $A$ and $C$ to the original Auto MPG data learned along with the network structure.
+    Although the number of discretization edges is less than those in Figure~\ref{fig:auto_exp1_distr_1_3}, the probability distribution still closely matches the original data.
+  }
   \label{fig:auto_exp2_distr_1_3}
 \end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+% WINE
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-In this subsection, another two experiments are conducted on the Wine dataset from the Irvine repository \citep{Lichman_2013}.
-This dataset has 178 instances and 14 variables.
-Only variable $A$ is discrete-valued with cardinality number \num{3}.
-Again, in the first experiment, the network structure is given in advance.
-In the second experiment, the network structure is not provided in advance.
+The Wine dataset contains variables related to the chemical analysis of wines from three different Italian cultivars.
+The dataset has \num{178} samples over fourteen variables.
+Variable $A$ is the only discrete variable and has three instantiations.
 
@@
 
-The Bayesian network in Figure~\ref{fig:wine_graph_1} is obtained by equal-width discretizing each continuous variable into 3 intervals and running K2 one thousand times.
-Table~\ref{table:wine_disc_table_1} shows a comparison between the optimal Bayesian approach and the MDL principle discretization method.
-The discretization result obtained by the optimal Bayesian approach is better than the MDL discretization method in terms of likelihood.
-The heuristic method discretizes variable $G$, $H$ and $J$ into one less interval than the optimal Bayesian approach, and has one more number of intervals on variable $M$.
-Although it returns different numbers of intervals and different positions of discretization edges with the optimal Bayesian approach, it still has a good discretization result in terms of likelihood.
-Furthermore, if running time is the main concern, the heuristic method can be considered a better approach in this case.
-
-Notice that there are some discretization edges appearing in all three discretization methods, such as \num{1.42} and \num{2.35} on variable $C$ and \num{0.785} on variable $L$.
+The Bayesian approaches and the MDL discretization method were tested on the Wine data using the network network shown in Figure~\ref{fig:wine_graph_1}.
+This structure was obtained by prediscretizing each continuous variable into three uniform-width intervals, where three is the median cardinality of the discrete variables, and then taking the structure with highest likelihood from one thousand runs of K2.
+
+Table~\ref{table:wine_disc_table_1} lists the discretization edges and mean log-likelihoods under 10-fold cross validation of the discrete Bayesian network resulting from each discretization method.
+The Bayesian methods outperform the MDL method in likelihood by a significant margin.
+The heuristic method discretizes the variables $G$, $H$, and $J$ into one fewer interval and the variable $M$ into one more interval than the optimal Bayesian approach, resulting in a slightly lower mean cross validated log likelihood.
+The overall performance of the heuristic method is still very high, and if runtime is the primary concern, the heuristic method can be considered the better approach.
+\tim{Do we need to list runtime too?}
+
+Notice that there are some discretization edges which appear in all three discretization methods, such as \num{1.42} and \num{2.35} for variable $C$ and \num{0.785} for variable $L$.
 This indicates that MDL indeed can find some important discretization edges, but it is not sensitive enough to find more edges.
@@
   \centering
-  \scalebox{0.8}{
-      \input{graph_wine_1}}
+  \scalebox{0.8}{\input{graph_wine_1}}
   \caption{Structure from prediscretized K2 structure learning to compare the methods for Wine dataset}
@@
   \centering
-  \caption{Discretization results of Wine dataset based on the network in Figure~\ref{fig:wine_graph_1} by the three different methods.
-The first thirteen rows are discretization edges on each continuos variable.
-The fourteenth row is the log-likelihood of the dataset based on the discretization results.
-The optimal Bayesian approach has the best discretization result in terms of likelihood.
-The heuristic method obtains a result nearly as good as the Bayesian approach.
-The MDL method discretizes more than half of continuous variables but still does not discretize enough intervals.
-Some discretization edges appear in the results of all three methods, and indicate that they are the most determinant edges.}
+  \caption{
+    Results from discretization of the Wine MPG dataset with fixed structure from Figure~\ref{fig:wine_graph_1}.
+    The first thirteen rows list the discretization edges for each continuous variable.
+    The last row lists the mean cross-validated log-likelihood; positive values are better.
+    The optimal Bayesian approach has the best discretization result in terms of likelihood, but the heuristic method obtains a similar result with nearly the same likelihood.
+    The MDL method produces discretization edges for more than half of the continuous variables but does not produce enough discretization intervals.
+    Some discretization edges appear in the results of all three methods.
+  }
   \scalebox{1.0}{
@@
 
-Figure~\ref{fig:wine_exp1_distr} compares the discretization results by the optimal Bayesian approach and the MDL method.
-The discretization edges \num{17.9} on $E$ and \num{34.6} on $K$ appear in both plots.
-This indicates that they are more necessary than other discretization edges on $E$ and $K$.
-On the other hand, the edge \num{23.25} on $E$ is also meaningful.
-For instance, after having an extra edge at \num{23.25}, the area from $E = 17.9$ to $30$ is divided two rectangles such that the one from $E=17.9$ to $23.25$ has relatively higher probability than $E=23.25$ to $30$.
-The MDL method does not capture this edge due to its low sensitivity toward distribution.
-For more discussion about the sensitivity, see Section~\ref{subsec:discuss_exp}.
+Figure~\ref{fig:wine_exp1_distr} compares the optimal Bayesian and MODL discretizaton policies for variables $E$ and $K$ with the original Wine data.
+The discretization edges \num{17.9} for $E$ and \num{34.6} for $K$ appear in both plots.
+The MDL method creates fewer discretization edges than the optimal Bayesian method.
+Relative sensitivities of each method to the input data is discussed in Section~\ref{subsec:discuss_exp}.
 
@@
   \input{graph_wine_exp1_distr}
-  \caption{Comparison of the discretization results on variable $A$ and $C$ obtained by the optimal Bayesian approach and the MDL method}
+  \caption{Comparison of the discretization policies for variables $A$ and $C$ obtained using optimal Bayesian and MDL methods}
   \label{fig:wine_exp1_distr}
@@
 
-Figure~\ref{fig:wine_graph_2} is the learned discrete-valued Bayesian network from the Wine dataset, and it is obtained by running Algorithm~\ref{alg:structure_learn} fifty times.
-The integer numbers next to variables are cardinality numbers of variables.
-By comparing Figure~\ref{fig:wine_graph_2} with~\ref{fig:wine_graph_1}, it shows that the the Bayesian network obtained by Algorithm~\ref{alg:structure_learn} has more edges than the network obtained by prediscretization and the K2 algorithm.
-This is sensible, since when a network is learned along with discretization, variables have more freedom, by adjusting discretization edges, to construct the correlations with other variables and thus have more edges in the network.
-
-Figure~\ref{fig:wine_exp2_distr} shows the discretization result on variable $E$ and $K$.
-The discretization edge at \num{17.9} on variable $E$ also appers in Figure~\ref{fig:wine_exp1_distr}.
+Figure~\ref{fig:wine_graph_2} is the discrete-valued Bayesian network learned from the Wine dataset, obtained by running Algorithm~\ref{alg:structure_learn} fifty times.
+A comparison of Figures~\ref{fig:wine_graph_2} and \ref{fig:wine_graph_1} show that the Bayesian network learned during the discretization process has more edges than the network learned on the prediscretized data.
+When a network is learned along with discretization, the algorithm has more freedom to adjust the structure and the discretization policy simultaneously to identify useful correlations and produce a denser structure.
+
+Figure~\ref{fig:wine_exp2_distr} shows the discretization policy for variables $E$ and $K$ obtained with the \todo{heuristic Bayesian method).
+The discretization edge $E = 17.9$ also appears in all discretization policies from the fixed network (Figure~\ref{fig:wine_exp1_distr}).
 This indicates that some discretization edges are robust against the network structure.
-Furthermore, in Figure~\ref{fig:wine_exp2_distr}, the discretization edge at \num{23.5} on $E$ is lost.
-This is due to the number of parents of $E$ in Figure~\ref{fig:wine_graph_2} is twice as in~\ref{fig:wine_graph_1}.
-Usually, if a variable has more parents, then less number of intervals after discretization it has, since the information from parents are mixed together.
-
-\begin{figure}[ht]
-  \centering
-  \scalebox{0.7}{
-    \input{graph_wine_2}}
-  \caption{The learned discrete-valued Bayesian network from the Wine dataset \todo{using optimal Bayesian method}}
+Furthermore, the discretization edge at $E = 23.5$ present in the fixed-structure case is missing in the learned structure.
+This is caused by $E$ having twice as many parents in the learned network structure.
+The more parents a variable has, the less discretization intervals it will be able to support, as the set of statistics required to define the resulting distribution increases exponentially with the number of parents.
+
+\begin{figure}[ht]
+  \centering
+  \scalebox{0.7}{\input{graph_wine_2}}
+  \caption{The discrete-valued Bayesian network learned from the Wine dataset \todo{using the heuristic Bayesian method}.}
   \label{fig:wine_graph_2}
@@
   \centering
-  \begin{tabular}{cc}
   \input{graph_wine_exp2_distr_5_11}
- \end{tabular}
-  \caption{The discretization result on variable $E$ and $K$ of the learned network in Figure~\ref{fig:wine_graph_2}.
-The discretization edge \num{17.9} on $E$ also appear in~\ref{fig:wine_exp1_distr}.
-This indicates that some discretization edges are robust again the network structure.}
+  \caption{
+    The discretization policy for variables $E$ and $K$ on the learned network in Figure~\ref{fig:wine_graph_2}.
+    The discretization edge $E = 17.9$ also appears in the policies for the fixed network.
+    This indicates that some discretization edges are robust against changing network structure.
+  }
   \label{fig:wine_exp2_distr}
 \end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+% Housing
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-In this subsection, another two experiments are conducted on the Housing dataset from the Irvine repository \citep{Lichman_2013}.
-This dataset has 506 instances and 14 variables.
-Only variables $D$ and $I$ are discrete-valued with cardinality numbers 2 and 9, respectively.
-Again, in the first experiment, the network structure is given in advance.
-In the second experiment, the network structure is not provided in advance.
+The Housing dataset contains variables related to the values of houses in Boston suburbs.
+The dataset has \num{506} samples over fourteen variables.
+Only variables $D$ and $I$ are discrete-valued, with \num{2} and \num{9} instantiations, respectively.
+Variable $A$ is the only discrete variable and has three instantiations.
+Despite their being continuous, several variables in the Housing dataset possess many repeated values.
 
@@
 
-The Bayesian network structure in Figure~\ref{fig:housing_graph_1} is obtained by prediscretizing each continuous variable into five uniform-width intervals, then running the K2 algorithm one thousands time and choosing the network with the highest K2 score.
-Table~\ref{table:housing_disc_table_1} shows the numbers of intervals after discretization on each continuous variables and also the log-likelihood of the dataset based on the discretization results.
-MDL method again does not discretize most variables.
-The heuristic method discretizes variables into too many intervals due to repeated values in the dataset, as we will see in later discussion.
-The optimal Bayesian approach has a good control of number of intervals.
-These numbers of intervals returned by the three methods illustrate that the heuristic method is over sensitive and the MDL method is less sensitive.
-The properties of sensitivity of the three algorithms will be discussed in Section~\ref{subsec:discuss_exp}.
-On the other hand, although the heuristic method leads to high number of intervals, its corresponding log-likelihood on the dataset is not significantly better than the optimal Bayesian approach.
-This shows that the optimal Bayesian approach captures the important discretization edges.
+The Bayesian network structure in Figure~\ref{fig:housing_graph_1} was obtained by prediscretizing each continuous variable into five uniform-width interval and then running the K2 algorithm one thousand times and choosing the network with the highest likelihood.
+Table~\ref{table:housing_disc_table_1} shows the numbers of intervals after discretization for each continuous variables and the log-likelihood of the dataset based on each discretization method.
+MDL method does not produce any discretization edges for most variables.
+The heuristic Bayesian method produces far more discretization edges than the optimal Bayesian method due to repeated instances in the dataset.
+These numbers of intervals returned by the three methods illustrate the over-sensitive nature of the heuristic method and the under-sensitive nature of the MDL method.
+\tim{I am not sure we are using `sensitive' correctly. Sensitive to what? Perhaps `biased towards higher edge counts'?}
+The relative sensitivity of each algorithm will be discussed in Section~\ref{subsec:discuss_exp}.
+
+The heurstic method produces the discretization with the highest cross-validated log likelihood, but although the heuristic method leads to a higher number of intervals, its likelihood is not significantly better than the optimal Bayesian approach.
+This shows that the optimal Bayesian approach captures the most important discretization edges.
 
@@
   \caption{
-    Discretization result of Housing dataset based on the graph in Figure~\ref{fig:housing_graph_1}.
-The first twelve rows show the numbers of intervals after discretization by the three method.
-The thirteenth row is the log-likelihood of the dataset based on the discretizatio results.
-The heuristic method is over sensitive and discretizes some variables into too many intervals.
-The MDL method is less sensitive and discretizes most variables by only one interval.
-The optimal Bayesian approach has a good control on number of intervals.
+    Discretization policy summary of the Housing dataset based on the fixed network structure shown in Figure~\ref{fig:housing_graph_1}.
+    The first twelve rows show the numbers of intervals after discretization by each method.
+    The last row is the mean cross-validated log-likelihood of the dataset based on the discretization results.
+    The heuristic method is over-sensitive \todo{to what?} and discretizes some variables into too many intervals.
+    The MDL method is less sensitive and on many cases does not produce any discretization intervals.
+    The optimal Bayesian approach produces a reasonable number of discretization edges.
   }
@@
 
-Figure~\ref{fig:housing_exp1_distr_3_5} and Figure~\ref{fig:housing_exp1_distr_8_5} show the discretization result of the optimal Bayesian approach on the network in Figure~\ref{fig:housing_graph_1}.
-In Figure~\ref{fig:housing_exp1_distr_3_5}, the scatter points, which stands for the raw data, has been jittered, since there are many repeated values in the raw data on the variable pair $C$ and $E$.
-These repeating values cause the high number of intervals for both $C$ and $E$, because in some sense, each repeated-value point form a single discretized area.
-On the other hand, the data instances on variable $H$ is less repeated.
-Thus, some resulting discretized areas cover larger space, instead of just covering a repeated value.
-
-\begin{figure}[ht]
-\centering
-    % \begin{tabular}{cc}
+Figures~\ref{fig:housing_exp1_distr_3_5} and \ref{fig:housing_exp1_distr_8_5} show the discretization policy learned using the optimal Bayesian approach on the fixed network shown in Figure~\ref{fig:housing_graph_1}.
+In Figure~\ref{fig:housing_exp1_distr_3_5}, the scatter points corresponding to the original dataset have been jittered, because there are many repeated values for variables $C$ and $E$.
+Each repeated point forms a single discrete region, thereby encouraging discretization.
+In contrast, the samples for $H$ are well spread out, resulting in fewer discretization regions and larger discretization intervals.
+
+\begin{figure}[ht]
+  \centering
   \input{graph_housing_exp1_distr_3_5}
-    % \end{tabular}
-  \caption{The discretization result on variable $C$ and $E$ of the network in Figure~\ref{fig:housing_graph_1}.
-The scatter points are jittered due to the repeated values in the dataset.
-Furthermore, these repeated values lead to high number of discretization edges, since repeated values can easily form discretized areas by their own.}
+  \caption{
+    The discretization policies for variables $C$ and $E$ learned using the optimal Bayesian approach on the fixed network shown in Figure~\ref{fig:housing_graph_1}.
+    The scatter points were jittered to reveal the repeated values in the dataset.
+    The repeated values lead to a high number of discretization edges, because repeated values can easily form discretized regions by their own.
+  }
   \label{fig:housing_exp1_distr_3_5}
@@
   \centering
-     %\begin{tabular}{cc}
   \input{graph_housing_exp1_distr_8_5}
-     %\end{tabular}
-  \caption{The discretization result on variable $H$ and $E$ of the network in Figure~\ref{fig:housing_graph_1}.
-Data points are not over repeated on $H$, thus the number of edges on $H$ remains desirable.}
+  \caption{
+    The discretization policies for variables $H$ and $E$ learned using the optimal Bayesian approach on the fixed network shown in Figure~\ref{fig:housing_graph_1}.
+    The variable $H$ possesses no overly repeated values, thus producing a cleaner discretization policy.
+  }
   \label{fig:housing_exp1_distr_8_5}

### 2015-11-20 BN_discretizer_paper.tex
misc
change }
intro and concl

@@
 \begin{abstract}
-Many applications of Bayesian networks assume all random variables are discrete.
-However, it is imperative to deal with continuous variables in the real-world data, such as positions and velocities of dynamical systems.
-In this paper, a new method has been proposed to discretize continuous variables in Bayesian networks by learning from mixed data.
-The method adapts Bayesian statistics to find the most probable discretization policy on a continuous variable.
-In addition, it incorporates graph structure when discretizing continuous variables.
-When there are multiple continuous variables in a Bayesian network, the method iteratively discretizes each variable while treating other variables discrete by the previous discretization result.
-If the network structure is not given in advance, the method can be combined with the K2 structure learning algorithm to learn a discrete-valued Bayesian network.
-In the tests on real-world data, the method is shown that it can match the raw data distribution by providing sufficient numbers of intervals after discretization on continuous variables and also correct positions of discretization edges.
-
-  \keywords{Discretization \and Bayesian Network \and Continuous Variable}
+
+Real data often contains a mixture of discrete, continuous, and hybrid variables, but many Bayesian network structure learning and inference algorithms assume all random variables are discrete.
+Continuous and hybrid variables are often discretized, but the choice of discretization policy has significant impact on the accuracy, speed, and interpretability of the resulting models.
+This paper introduces a principled discretization method for continuous variables in Bayesian networks with quadratic complexity instead of the cubic complexity of other standard techniques.
+Emperical demonstrations show that the proposed method is superior to the state of the art.
+In addition, this paper shows how to incorporate existing methods into the structure learning process to discretize all continuous variables and simultaneously learn Bayesian network structures.
+The proposed method was incorporated and its superior performance was empirically demonstrated.
+All software is publically available to support discretization research.
+
+\keywords{Discretization \and Bayesian Network \and Continuous Variable \and }
   % \PACS{PACS code1 \and PACS code2 \and more}
@@
 The evaluation of $h(u,v)$ for all $u \leq v$ is summarized in Algorithm~\ref{alg:h} in the appendix.
-The calculation has a $\bigo \paren{ n_c  {L'} \cdot N^2 + {L'}^{n_p} \cdot N^2 }$ runtime, where $n_c$ and $n_p$ are the numbers of child and parent variables respectively, and $L'$ is the largest cardinality of variables that directly connect to $X$.
-\tim{so parents and children, or parents, children and spouses?}
+\todo{The calculation has a $\bigo \paren{ n_c  {L'} \cdot N^2 + {L'}^{n_p} \cdot N^2 }$ runtime, where $n_c$ and $n_p$ are the numbers of child and parent variables respectively, and $L'$ is the largest cardinality of variables that directly connect to $X$.}
 
@@
 The dynamic programming procedure is shown in Algorithm~\ref{alg:disc_one}.
-It takes three inputs: $\cX$, the continuous variable, $D$, the joint data instances over all variables sorted in ascending order according to $D_X$, and $G$, the network structure.
+It takes three inputs: $\cX$, the continuous variable; $D$, the joint data instances over all variables sorted in ascending order according to $D_X$; and $G$, the network structure.
 The runtime of Algorithm~\ref{alg:disc_one} is also $O(n_c  {L'} \cdot N^2 + {L'}^{n_p} \cdot N^2)$, because the runtime of the dynamic programming procedure is less than the runtime for computing $h(u,v)$.
 Algorithm~\ref{alg:disc_one} is guaranteed to be optimal.
-For faster methods with suboptimal results please refer to \citep{Boulle_2006}.
+For faster methods with suboptimal results please refer to the work of \cite{Boulle_2006}.
 
@@
 
-Algorithm~\ref{alg:disc_one} has an exponential $\bigo\paren{L'^{n_p} \cdot N^2}$ runtime which severely limits discretization in networks with a large number of discretization intervals or parent variables.
+Algorithm~\ref{alg:disc_one} has an exponential $\bigo\paren{\paren{L'}^{n_p} \cdot N^2}$ runtime which severely limits discretization in networks with a large number of discretization intervals or parent variables.
 This section introduces an approximation to the objective function that significantly reduces the runtime and still preserves the quality of discretization.
@@
 The algorithm typically converges within a few passes when tested on real-world data.
-In cases where it does not converge, \tim{when was this observed? What dataset?}, ten passes usually produce decent discretization results.
+In cases where it does not converge, \tim{only observed when also learning structure}, ten passes usually produce decent discretization results.
 
@@
       \While {OKToProceed \textbf{and} $\|\Pa_{X_i}\| < u_{parent}$}
-        \State $Y \leftarrow$ an element from the set $order[1:i] \backslash \Pi_X$
-        \State $P_{new} \leftarrow f(X^*_i,\Pa^*_{X_i} \cup Y^*)$
+        \State $Y \leftarrow$ an element from the set $order[1:i] \backslash \Pa_X$
+        \State $P_{new} \leftarrow g(X^*_i,\Pa^*_{X_i} \cup Y^*)$
         \If {$P_{new} > P_{old}$}
@@
 
-The function $f$ in Algorithm~\ref{alg:structure_learn} computes a component of the Bayesian score (Equation~\ref{eq:BayesianScore}):
+The function $g$ in Algorithm~\ref{alg:structure_learn} computes a component of the Bayesian score (Equation~\ref{eq:BayesianScore}):
 
@@
 This section describes experiments conducted to evaluate the proposed methods.
-All experiments were run on datasets from the publically available Irvine machine learning repository \citep{Lichman_2013}.
+All experiments were run on datasets from the publically available University of California, Irvine machine learning repository \citep{Lichman_2013}.
 Variables are labelled alphabetically in the order given on the dataset information webpage
@@
 The first experiment compares the performance of the optimal Bayesian discretization method, the heuristic Bayesian discretization method, and MDL on a known Bayesian network structure.
-The structure was obtained by prediscretizing each continuous variable into $k$ uniform-width intervals, where $k$ is the median number of instantiations of the discrete variables, and using the structure with the highest Bayesian score from one thousand runs of the K2 algorithm.
+The structure was obtained by prediscretizing each continuous variable into $k$ uniform-width intervals, where $k$ is the median number of instantiations of the discrete variables, and using the structure with the highest Bayesian score from one thousand runs of the K2 algorithm with random variable orderings.
 The second experiment compares the same methods applied when simultaneously discretizing and learning network structure.
@@
 
+\todo{
 \begin{equation}
@@
 \end{equation}
-\tim{The above equation needs work.}
+}
 
@@
 Cross-validation directly estimates generalization error.
-\todo{Ten} folds were used in each experiment.
+Ten folds were used in each experiment.
 
@@
    \input{graph_autocar_1}
-   \caption{Bayesian network structure obtained from running K2 on the prediscretiszed Auto MPG dataset}
+   \caption{Bayesian network structure obtained from running K2 on the prediscretized Auto MPG dataset}
   \label{fig:auto_graph_1}
@@
 The discretization edges \num{17.9} for $E$ and \num{34.6} for $K$ appear in both plots.
-The MDL method creates fewer discretization edges than the optimal Bayesian method.
+The MDL method does not use enough intervals for discretization.
 Relative sensitivities of each method to the input data is discussed in Section~\ref{subsec:discuss_exp}.
@@
 
-Figure~\ref{fig:wine_exp2_distr} shows the discretization policy for variables $E$ and $K$ obtained with the \todo{heuristic Bayesian method).
+Figure~\ref{fig:wine_exp2_distr} shows the discretization policy for variables $E$ and $K$ obtained with the optimal Bayesian method.
 The discretization edge $E = 17.9$ also appears in all discretization policies from the fixed network (Figure~\ref{fig:wine_exp1_distr}).
@@
   \scalebox{0.7}{\input{graph_wine_2}}
-  \caption{The discrete-valued Bayesian network learned from the Wine dataset \todo{using the heuristic Bayesian method}.}
+  \caption{The discrete-valued Bayesian network learned from the Wine dataset using the optimal Bayesian method.}
   \label{fig:wine_graph_2}
@@
 Despite their being continuous, several variables in the Housing dataset possess many repeated values.
+The following experiments were conducted with an upper limit of three on the number of parents per variable to prevent memory issues with MDL.
 
@@
 
-Figure~\ref{fig:housing_graph_2} is the learned discrete-valued Bayesian network from the Housing dataset by running Algorithm~\ref{alg:structure_learn} fifty times.
-In both Figure~\ref{fig:housing_graph_1} and Figure~\ref{fig:housing_graph_2}, the variable $D$ is not connected to any other variable.
-Continuous variables $C$, $E$, $J$ and $K$, which are all in a Markov blanket, have high cardinality numbers after discretization.
-This is reasonable, since when discretizing one variable, the expected cardinality is close to highest cardinality number in the Markov blanket.
-This will lead to a group of variables that are close to each other and all have high cardinalities.
-
-\begin{figure}[ht]
-    % \begin{tabular}{cc}
-    \centering
-    \scalebox{0.8}{
-      \input{graph_housing_2}}
-    % \end{tabular}
-  \caption{The learned discrete-valued Bayesian network from the Housing dataset. Variables $C$, $E$, $J$, $K$ have high numbers of intervals after discretization, since they are in a Markov blanket.
-  \tim{Var with 1 interval?}
+Figure~\ref{fig:housing_graph_2} shows a learned Bayesian network structure and the corresponding numbers of intervals after discretization for each continuous variable.
+Variable $D$ is neighborless is both the learned and fixed networks.
+The continuous variables $C$, $E$, $J$ and $K$, which are all connected through $C$, have many discretization intervals.
+Typically, when discretizing a variable, the expected number of discretization intervals is close to the highest cardinality among variables in its Markov blanket.
+This naturally leads to clusters of variables with high numbers of discretization intervals.
+
+\begin{figure}[ht]
+  \centering
+  \scalebox{0.8}{\input{graph_housing_2}}
+  \caption{
+    The discrete-valued Bayesian network learned from the Housing dataset using the optimal Bayesian method.
   }
@@
   \centering
-     %\begin{tabular}{cc}
   \input{graph_housing_exp2_distr_3_5}
-     %\end{tabular}
-  \caption{The discretization result on variable $C$ and $E$ of the network in Figure~\ref{fig:housing_graph_2}.
-The high number of discretization edges is due to the repeated values on the dataset in variable $C$ and $E$.}
+  \caption{
+    The discretization policy for variables $C$ and $E$ on the learned network in Figure~\ref{fig:housing_graph_2}.
+    The high number of discretization edges are caused by the repeated values in variables $C$ and $E$.
+  }
   \label{fig:housing_exp2_distr_3_5}
@@
   \centering
-    % \begin{tabular}{cc}
   \input{graph_housing_exp2_distr_8_5}
-    % \end{tabular}
-  \caption{The discretization result on variable $H$ and $E$ of the network in Figure~\ref{fig:housing_graph_2}.
-Although the number of discretization edges on $H$ is less than the number in Figure~\ref{fig:housing_exp1_distr_8_5}, it still matches the distribution of the raw data well.}
+  \caption{
+    The discretization policy for variables $H$ and $E$ on the learned network in Figure~\ref{fig:housing_graph_2}.
+    The number of discretization intervals for $H$ is less than it was for the fixed network structure in Figure~\ref{fig:housing_exp1_distr_8_5}, but the discretization policy still matches the raw data.
+  }
   \label{fig:housing_exp2_distr_8_5}
@@
   \begin{aligned}
-  f_{\text{MDL}} & = \overbrace{Z_1 \cdot k + \ln(k) + \ln {{n +k - 1}\choose{k -1}} }^{\text{Penalty Term}}+   \overbrace{\rule{0pt}{1.35em} \ln(N) \cdot I(X^*, \Pi_X)}^{\text{Edge Position Term}} \\
+  f_{\text{MDL}} & = \overbrace{Z_1 \cdot k + \ln(k) + \ln {{n +k - 1}\choose{k -1}} }^{\text{Penalty Term}}+   \overbrace{\rule{0pt}{1.35em} \ln(N) \cdot I(X^*, \Pa_X)}^{\text{Edge Position Term}} \\
   f_{\text{Bayesian}} &= \overbrace{\rule{0pt}{1.85em}  Z_2 \cdot k + \sum_{i=1}^k \ln {{\gamma_i + J_P - 1}\choose{J_P -1}}}^{\text{Penalty Term}} + \overbrace{\sum^k_{i=1} \ln \left(   {{\gamma_i !}\over{n^{(P)}_{i,1}!
@@
 \noindent
-where $Z_1$ and $Z_2$ are constant over discretizations, $k$ is the number of discretization intervals, and $I\paren{A, B} = \sum_{a,b} \hat{P}(a,b) \ln\frac{\hat{P}(a,b)}{\hat{P}(a)p(b)}$ is the mutual information.
+where $Z_1$ and $Z_2$ are constant over discretizations, $k$ is the number of discretization intervals, and $I\paren{A, B} = \sum_{a,b} \hat{P}(a,b) \ln\frac{\hat{P}(a,b)}{\hat{P}(a)\hat{P}(b)}$ is the mutual information based on estimated probability1ies.
 Note that the third term of $f_\text{MDL}$ had been approximated using $H(p)$ (see Equation~\ref{eqn:MDL}) in the original work by \cite{Friedman_1996} but here is written without that approximation.
@@
 \section{Conclusion}
-In this work, a new method for discretizating continuous varibles in Bayesian networks has been proposed.
-It is compatible with the K2 structure learning, i.e., it can discretize continuous variables along with the edge-adding process of the K2.
-Therefore, a discrete-valued Bayesian network can be learned from mix data.
-
-Experiments on three real-world dataset show that the new method returns to a better discretization result than previous research in terms of likelihood.
-The discretization edges and the resulting marginal probabilities of discretized regions returned by the new method can match the row data well.
-
-This work can extend the usage of Bayesian networks in science and engineering, especially for the fields that require discrete-valued variables but the learning data is mixed and numerical.
-In the future, we plan to generalize the work to the datast that has high dimensional variables, for example, 3 dimensional positions of drones, which makes the sorting in Equation~\ref{eq:p_M} fails.
+This paper introduced a principled discretization method for continuous variables in Bayesian networks with quadratic complexity instead of the cubic complexity of other standard techniques.
+Emperical demonstrations show that the proposed method is superior to the state of the art.
+In addition, this paper shows how to incorporate existing methods into the structure learning process to discretize all continuous variables and simultaneously learn Bayesian network structures.
+The proposed method was incorporated and its superior performance was empirically demonstrated.
+\todo{All software is publically available to support discretization research.}
+
+The methods developed in this paper increase the accuracy of Bayesian networks learned on datasets with continuous and mixed variables.
+An automated process for simultaneously constructing Bayesian networks and discretization policies is appearing because of the potential to significantly reduce development time and cost.
+Future work will investigate edge positions at locations other than the midpoints between samples and using different discretization policies for the same variable in different conditional probablity distributions.
 
@@
   \State Initialize $H$ as an $N \times N$ matrix such that all elements are 0.
-  \State $count_p$ is an $N \times N \times \|\Pi_X\|$ matrix such that $count_p [u,v,w]$ is the number of instances from $x_u$ to $x_v$ with $w$th value of $\Pi_X$.
-This matrix can be calculated in $O(\|\Pi_X\| \cdot N^2)$
+  \State $count_p$ is an $N \times N \times \|\Pa_X\|$ matrix such that $count_p [u,v,w]$ is the number of instances from $x_u$ to $x_v$ with $w$th value of $\Pa_X$.
+This matrix can be calculated in $O(\|\Pa_X\| \cdot N^2)$
   \For {$u = 1$ to $N$}
@@
       \State $H(u,v) \leftarrow H(u,v) + \ln((v-u + J_p)!) - \ln((J_p -1)!)$
-      \For {$w = 1$ to $\|\Pi_X\|$}
+      \For {$w = 1$ to $\|\Pa_X\|$}
         \State $H(u,v) \leftarrow H(u,v) - \ln( count_p(u,v,w)!)$

### 2015-11-20 graph_auto_exp1_distr_1_3.tex
updated graphs

--- 2015-11-17 graph_auto_exp1_distr_1_3.tex
@@
 			        ytick={0,0.05,...,0.51},
+			        % ylabel=marginal discrete probability,
 			        yticklabel style={

### 2015-11-20 BN_discretizer_paper.tex
fixed Alg 1 and commented out heuristic

@@
   \begin{algorithmic}[5]
-    \Function{DiscretizeOne}{$\cX$, $D$, $G$}
-      \State $n \leftarrow$ the number of data instances
-      \State $m \leftarrow$ the number of unique values in $D_{\cX}$
-      \State $H \leftarrow$ an $N \times N$ matrix such that $H[u,v] = h(u,v)$ (see Algorithm~\ref{alg:h} in Appendix)
-      \State $s_{1:m} \leftarrow$ an increasing sequence of integers defined in Section~\ref{subsec:disc_policy}
-      \State $L \leftarrow$ the largest cardinality over all discrete variables in the Markov blanket of $X$
-      \State $S[u] \leftarrow$ the optimal objective value of subproblems from instance $1$ to $s_u$
-      \State $\Lambda[u] \leftarrow$ the optimal discretization for subproblems from instance $1$ to $s_u$
-      \State $W[u]  \leftarrow - \ln\brock{1 - {\exp\paren{- L \cdot{ {{\cx_{s_u+1} - \cx_{s_u}}\over{\cx_n - \cx_1}}}}}}$ for $u = 1,2, \ldots,m-1$ and $W[n] \leftarrow 0$
+    \Function{DiscretizeOne}{$D$, $G$, $\cX$}
+      % \State $n \leftarrow$ the number of data instances
+      % \State $m \leftarrow$ the number of unique values in $D_{\cX}$
+      \State $H \leftarrow$ an $n \times n$ matrix such that $H[u,v] = h(u,v)$; can be precomputed
+      % \State $s_{1:m} \leftarrow$ an increasing sequence of integers defined in Section~\ref{subsec:disc_policy}; can be precomputed
+      \State $L \leftarrow$ the largest cardinality over all discrete variables in the Markov blanket of $\cX$
+      \State $S[i] \leftarrow$ the optimal objective value computed over samples $1$ to $s_i$
+      \State $\Lambda[i] \leftarrow$ the discretization policy for the subproblem over samples $1$ to $s_i$
+      \State $W[i]  \leftarrow - \ln\brock{1 - {\exp\paren{- L \cdot{ {{\cx_{s_i+1} - \cx_{s_i}}\over{\cu_m - \cu_1}}}}}}$ for $i \in [1,m-1]$ and $W[m] \leftarrow 0$
       \For {$v \leftarrow 1$ to $m$}
@@
           \State $S[v] \leftarrow H \paren{1,s_v} + L[v]$
-          \State $\Lambda[v] \leftarrow \{ ({\cx_{s_v} + \cx_{s_v+1}}) / 2\}$
+          \State $\Lambda[v] \leftarrow \curly{({\cu_v + \cu_{v+1}}) / 2}$
         \Else
-          \State $s \leftarrow \infty$
+          \State $\hat{S}, \hat{u} \leftarrow \infty, 0$
           \State $\text{DiscEdge} \leftarrow \infty$
           \For {$u \leftarrow 1$ to $v$}
-        \State $s' \leftarrow S[u] + H \paren{s_u+1, s_v} +  {L \cdot {\frac{\cx_{s_v} - \cx_{s_u + 1}}{\cx_n - \cx_1}}} + W[v]$
-        \If {$s' < s$}
-          \State $s \leftarrow s'$
+            \If {$u = v$}
+              \State $\tilde{S} \leftarrow W[v] + H \paren{1, s_v} +  {L \cdot {\frac{\cu_{v} - \cu_1}{\cu_m - \cu_1}}}$
+            \Else
+              \State $\tilde{S} \leftarrow W[v] + H \paren{s_u+1, s_v} +  {L \cdot {\frac{\cu_{v} - \cu_{u + 1}}{\cu_m - \cu_1}}} + S[u]$
+            \EndIf
+            \If {$\tilde{S} < \hat{S}$}
+              \State $\hat{S}, \hat{u} \leftarrow \tilde{S}, u$
               \State $\text{DiscEdge} \leftarrow ({x_{s_u} + x_{s_u+1}}) / 2$
@@
           \EndFor
-          \State $S[v] \leftarrow s$
-          \State $\Lambda[v] \leftarrow \Lambda[u] \cup \{ DiscEdge \}$
+          \State $S[v] \leftarrow \hat{S}$
+          \State $\Lambda[v] \leftarrow \Lambda[u] \cup \{ \text{DiscEdge} \}$
         \EndIf
@@
 
-\subsection{Approximation}
-
-Algorithm~\ref{alg:disc_one} has an exponential $\bigo\paren{\paren{L'}^{n_p} \cdot N^2}$ runtime which severely limits discretization in networks with a large number of discretization intervals or parent variables.
-This section introduces an approximation to the objective function that significantly reduces the runtime and still preserves the quality of discretization.
-The approximation replaces the dominator of the last factor in Equation~\ref{eq:likelihood_one} with
-
-\begin{equation}
-{\frac{{\gamma_i}!}{ {n^{(P)}_{i,1} !} {n^{(P)}_{i,2} !} \cdots {n^{(P)}_{i,J_P} !}}} \approx \prod_{r=1}^{n_p} { {{{\gamma}_i}!}\over{ {n^{(P_r)}_{i,1} !} {n^{(P_r)}_{i,2} !} \cdots {n^{(P_r)}_{i,J_{P_r}} !}}}\text{,}
-\end{equation}
-
-\noindent
-where $P_r$ is the $r$th parent variable, $J_{p_r} = \| P_r\|$, and ${n^{(P_r)}_{i,j} !}$ is the number of instances in the $i$th interval with the $j$th value of $P_r$.
+% \subsection{Approximation}
+
+% Algorithm~\ref{alg:disc_one} has an exponential $\bigo\paren{\paren{L'}^{n_p} \cdot N^2}$ runtime which severely limits discretization in networks with a large number of discretization intervals or parent variables.
+% This section introduces an approximation to the objective function that significantly reduces the runtime and still preserves the quality of discretization.
+% The approximation replaces the dominator of the last factor in Equation~\ref{eq:likelihood_one} with
+
+% \begin{equation}
+% {\frac{{\gamma_i}!}{ {n^{(P)}_{i,1} !} {n^{(P)}_{i,2} !} \cdots {n^{(P)}_{i,J_P} !}}} \approx \prod_{r=1}^{n_p} { {{{\gamma}_i}!}\over{ {n^{(P_r)}_{i,1} !} {n^{(P_r)}_{i,2} !} \cdots {n^{(P_r)}_{i,J_{P_r}} !}}}\text{,}
+% \end{equation}
+
+% \noindent
+% where $P_r$ is the $r$th parent variable, $J_{p_r} = \| P_r\|$, and ${n^{(P_r)}_{i,j} !}$ is the number of instances in the $i$th interval with the $j$th value of $P_r$.
 Note that $\gamma_i = \sum_j {n^{(P_r)}_{i,j}}$ for all $r$.
-The approximated objective function is
-
-\begin{small}
-  \begin{equation}
-  \label{eq:opt_prob_approx}
-  \begin{aligned}
-    & \sum_{i=1}^{k-1}
-     - \ln
-      \paren{
-        1 - \exp
-        \paren{
-          - L \cdot  \frac{
-                           \cx_{\lambda_i +1} - \cx_{\lambda_i}
-                         }{
-                           \cx_n - \cx_1
-                          }
-        }
-      }
-        + \sum_{i=1}^{k}
-        L \cdot \frac{\cx_{\lambda_{i}} - \cx_{\lambda_{i-1} + 1}}{\cx_n - \cx_1} \\
-    & \sum_{i=1}^{k} \brock{
-    \ln{{\gamma_i + J_P - 1}\choose{J_P - 1}}
-    +{ \ln \paren{
-          \frac{
-            {\gamma_i}!
-          }{ \sum_{r=1}^{n_p}
-            {n^{({P_r})}_{i,1}}! \; {n^{({P_r})}_{i,2}}! \; \cdots \; {n^{({P_r})}_{i,J_{P_r}}}!
-          }
-        }}
-    } \\
-    & \sum_{j=1}^{n_c} \sum_{i=1}^k \sum_{l=1}^{J^{(j)}_S} \brock{
-    { \ln
-            {{n^{(j)}_{i,l} + J_{C_j} - 1}\choose{J_{C_j}-1}}}
-      +
-      \ln \paren{ {
-            \frac{
-              {n^{(j)}_{i,l}}!
-            }{
-              {n^{(j)}_{i,1,l}!} \; {n^{(j)}_{i,2,l}!} \; \cdots \; {n^{(j)}_{i,J_{C_j},l}!}
-            }
-          }
-          } }
-  \end{aligned}
-  \end{equation}
-\end{small}
-
-The approximation reduces the runtime of Algorithm~\ref{alg:disc_one} to a polynomial, $\todo{\bigo\paren{ {v'_\text{max}} \cdot (n_c + n_p) \cdot n^2}}$.
-It will be shown in Section~\ref{sec:experiments} that the approximation is more sensitive to the distribution over other variables and is biased towards slightly higher interval counts.
-\tim{We need to have a more specific thing to say along the lines of `When does it fail?'}
-
-The approximated objective function, Equation~\ref{eq:opt_prob_approx}, provides intuition into how child and parent variables contribute to the objective function.
-For example, in the left graph of Figure~\ref{fig:example_networks}, the corresponding square brackets in the approximated objective function are
-
-\begin{small}
-  \begin{equation}
-  \begin{aligned}
-  \label{eq:example_approx}
-   \sum_{i=1}^k & \left\lbrace   \left[ \ln{{\gamma_{i} + J_{C_1} - 1}\choose{J_{C_1}-1}} + \ln \left(  {{{\gamma_i}!} \over { {n^{(1)}_{i,1,\emptyset} !} \cdots {n^{(1)}_{i,J_{C_1},\emptyset} !}} }  \right)  +  \right.
+% The approximated objective function is
+
+% \begin{small}
+%   \begin{equation}
+%   \label{eq:opt_prob_approx}
+%   \begin{aligned}
+%     & \sum_{i=1}^{k-1}
+%      - \ln
+%       \paren{
+%         1 - \exp
+%         \paren{
+%           - L \cdot  \frac{
+%                            \cx_{\lambda_i +1} - \cx_{\lambda_i}
+%                          }{
+%                            \cx_n - \cx_1
+%                           }
+%         }
+%       }
+%         + \sum_{i=1}^{k}
+%         L \cdot \frac{\cx_{\lambda_{i}} - \cx_{\lambda_{i-1} + 1}}{\cx_n - \cx_1} \\
+%     & \sum_{i=1}^{k} \brock{
+%     \ln{{\gamma_i + J_P - 1}\choose{J_P - 1}}
+%     +{ \ln \paren{
+%           \frac{
+%             {\gamma_i}!
+%           }{ \sum_{r=1}^{n_p}
+%             {n^{({P_r})}_{i,1}}! \; {n^{({P_r})}_{i,2}}! \; \cdots \; {n^{({P_r})}_{i,J_{P_r}}}!
+%           }
+%         }}
+%     } \\
+%     & \sum_{j=1}^{n_c} \sum_{i=1}^k \sum_{l=1}^{J^{(j)}_S} \brock{
+%     { \ln
+%             {{n^{(j)}_{i,l} + J_{C_j} - 1}\choose{J_{C_j}-1}}}
+%       +
+%       \ln \paren{ {
+%             \frac{
+%               {n^{(j)}_{i,l}}!
+%             }{
+%               {n^{(j)}_{i,1,l}!} \; {n^{(j)}_{i,2,l}!} \; \cdots \; {n^{(j)}_{i,J_{C_j},l}!}
+%             }
+%           }
+%           } }
+%   \end{aligned}
+%   \end{equation}
+% \end{small}
+
+% The approximation reduces the runtime of Algorithm~\ref{alg:disc_one} to a polynomial, $\todo{\bigo\paren{ {v'_\text{max}} \cdot (n_c + n_p) \cdot n^2}}$.
+% It will be shown in Section~\ref{sec:experiments} that the approximation is more sensitive to the distribution over other variables and is biased towards slightly higher interval counts.
+% \tim{We need to have a more specific thing to say along the lines of `When does it fail?'}
+
+% The approximated objective function, Equation~\ref{eq:opt_prob_approx}, provides intuition into how child and parent variables contribute to the objective function.
+% For example, in the left graph of Figure~\ref{fig:example_networks}, the corresponding square brackets in the approximated objective function are
+
+% \begin{small}
+%   \begin{equation}
+%   \begin{aligned}
+%   \label{eq:example_approx}
+%    \sum_{i=1}^k & \left\lbrace   \left[ \ln{{\gamma_{i} + J_{C_1} - 1}\choose{J_{C_1}-1}} + \ln \left(  {{{\gamma_i}!} \over { {n^{(1)}_{i,1,\emptyset} !} \cdots {n^{(1)}_{i,J_{C_1},\emptyset} !}} }  \right)  +  \right.
 \right.\\
-  & \left.  \ln{{\gamma_{i} + J_{C_2} - 1}\choose{J_{C_2}-1}} + \ln \left(  {{{n_i}!} \over { {n^{(2)}_{i,1,\emptyset} !} \cdots {n^{(2)}_{i,J_{C_1},\emptyset} !}} }  \right)  \right] + \\
-  &  \left.
+%   & \left.  \ln{{\gamma_{i} + J_{C_2} - 1}\choose{J_{C_2}-1}} + \ln \left(  {{{n_i}!} \over { {n^{(2)}_{i,1,\emptyset} !} \cdots {n^{(2)}_{i,J_{C_1},\emptyset} !}} }  \right)  \right] + \\
+%   &  \left.
 \left[  \ln {{\gamma_{i} + J_P - 1}\choose{J_P-1}} +  \ln \left( { {{{\gamma}_i}!}\over{ {n^{(P_1)}_{i,1} !}\cdots {n^{(P_1)}_{i,J_{P_1}} !}}} \right) +\ln \paren{{ {{{\gamma}_i}!}\over{ {n^{(P_2}_{i,1} !}\cdots {n^{(P_2)}_{i,J_{P_2}} !}}} } \right] \right\rbrace \text{.}
-  \end{aligned}
-  \end{equation}
-\end{small}
-
-In Equation~\ref{eq:example_approx}, each child carries two terms, as shown in the first set of square brackets, but the two parent variables only carry a total of three terms, as shown in the second set of square brackets.
-In this case the child variables have greater effect on the optimal discretization than the parent variables, even though the number of child and parent variables are the same.
-However, if $C_2$ has an additional parent $S_2$, as shown in the right graph of Figure~\ref{fig:example_networks}, the importances of $C_2$ will be reduced.
-This is due to the additional influence of $S_2$ on $C_2$.
-This phenomenon arrises because the Bayesian method, but with and without the heuristic, incorporates graph structure when discretizing continuous variables.
-
-\begin{figure}[ht]
-  \centering
-  \begin{tabular}{cc}
-    \input{graph2_left}
-    \end{tabular}
-    \hspace{5em}
-    \begin{tabular}{cc}
-    \input{graph2_right}
-  \end{tabular}
-  \caption{Two example networks}
-  \label{fig:example_networks}
-\end{figure}
+%   \end{aligned}
+%   \end{equation}
+% \end{small}
+
+% In Equation~\ref{eq:example_approx}, each child carries two terms, as shown in the first set of square brackets, but the two parent variables only carry a total of three terms, as shown in the second set of square brackets.
+% In this case the child variables have greater effect on the optimal discretization than the parent variables, even though the number of child and parent variables are the same.
+% However, if $C_2$ has an additional parent $S_2$, as shown in the right graph of Figure~\ref{fig:example_networks}, the importances of $C_2$ will be reduced.
+% This is due to the additional influence of $S_2$ on $C_2$.
+% This phenomenon arrises because the Bayesian method, but with and without the heuristic, incorporates graph structure when discretizing continuous variables.
+
+% \begin{figure}[ht]
+%   \centering
+%   \begin{tabular}{cc}
+%     \input{graph2_left}
+%     \end{tabular}
+%     \hspace{5em}
+%     \begin{tabular}{cc}
+%     \input{graph2_right}
+%   \end{tabular}
+%   \caption{Two example networks}
+%   \label{fig:example_networks}
+% \end{figure}
 
@@
         \State {$D^*_X \leftarrow D_{\cX}$}
-        \State {$\Lambda_{\cX} \leftarrow \textsc{DiscretizeOne}(\cX, D^*, G)$}
+        \State {$\Lambda_{\cX} \leftarrow \textsc{DiscretizeOne}(D^*, G, \cX)$}
         \State {$D^*_X \leftarrow \Lambda_{\cX}\paren{D_{\cX}}$}
@@
 
-\section{Experiments}
-\label{sec:experiments}
-
-This section describes experiments conducted to evaluate the proposed methods.
-All experiments were run on datasets from the publically available University of California, Irvine machine learning repository \citep{Lichman_2013}.
-Variables are labelled alphabetically in the order given on the dataset information webpage
-In the figures that follow, shaded nodes correspond to initially discrete variables and the subscripts indicate the number of discrete instantiations.
-
-Two experiments were conducted on each dataset.
-The first experiment compares the performance of the optimal Bayesian discretization method, the heuristic Bayesian discretization method, and MDL on a known Bayesian network structure.
-The structure was obtained by prediscretizing each continuous variable into $k$ uniform-width intervals, where $k$ is the median number of instantiations of the discrete variables, and using the structure with the highest Bayesian score from one thousand runs of the K2 algorithm with random variable orderings.
-The second experiment compares the same methods applied when simultaneously discretizing and learning network structure.
-
-The discretizations are compared using the mean cross validated log-likelihood of the data $D$ given the graph structure $G$ and discretization policies $\discset$.
-The log-likelihood has two components,
-
-\begin{equation}
-\ln p(D\mid G, \discset) = \ln P(D^*\mid G) + \ln p(D\mid \discset, D^*)\text{,}
-\end{equation}
-
-\noindent
-where $D$ is the original dataset and $D^*$ is the dataset discretized according to $\discset$.
-The log-likelihood of the discretized dataset is the Bayesian score (Equation~\ref{eq:BayesianScore}) evaluated with a uniform prior over graph structures and a uniform Dirichlet prior ($\alpha_{ijk} = 1$ for all $i$, $j$, and $k$).
-The log-likelihood of the original dataset given the discrete dataset is
-
-\todo{
-\begin{equation}
-  \ln p\paren{D\mid \discset, D^*} = \sum_{i=1}^n
-  1\curly{X_i \text{ orig. cont.}}
-  \sum_{j=1}^{q_i} \sum_{k=1}^{r_i} m_{ijk} \ln\paren{
-    \frac{
-      1
-    }{
-      e^{\Lambda_{\cX_i}}_{k+1} - e^{\Lambda_{\cX_i}}_{k}
-    }
-  }\text{.}
-\end{equation}
-}
-
-\noindent
-The mean cross-validated log-likelihood is the mean log-likelihood on the witheld dataset among cross-validation folds.
-Cross-validation directly estimates generalization error.
-Ten folds were used in each experiment.
-
-The optimal discretization policy for MDL is found with dynamic programming in a similar manner as with the Bayesian method.
-For a Bayesian network with a single continuous variable $\cX$, the MDL objective function is
-
-\begin{equation}
-  \label{eqn:MDL}
-  \todo{
-  \begin{aligned}
-  \frac{1}{2} \ln(n) \left\lbrace  \lvert \Pa_{X_i} \rvert (\lvert X_i \rvert - 1) +
-   {\sum_{j,\cX_i \in \Pa_{X_i}}} \lvert \Pa_{X_j} \rvert (\lvert \cX_j \rvert - 1) \right\rbrace + \ln(\lvert {\cX_i} \rvert) \\
-   + (N_i-1) H \paren{\frac{|X^*_i| - 1}{N_i -1}} -n \cdot \left[ I(X_i,\Pa_{X_i}) + {\sum_{j,\cX_i \in \Pa_{\cX_i}}} I(\cX_j, \Pa_{X_j}) \right]\text{,}
-  \end{aligned}
-  }
-\end{equation}
-
-where $I(A,B)$ is the mutual information between two discrete variables $A$ and $B$, ${H(p) = -p \ln(p) - (1-p) \ln(1-p)}$, and \todo{$X^*_i$ is the discretized version of the $i$th sample of $X$}.
-
-\subsection{Auto MPG Dataset}
-\label{subsec:auto}
-
-The Auto MPG dataset contains variables related to the fuel consumption of automobiles in urban driving.
-The dataset has \num{392} samples over eight variables, not including six instances with missing data.
-Three variables are discrete: $B$, $G$, and $H$, with \num{5}, \num{13}, and \num{3} instantiations respectively.
-
-\subsubsection{Discretization with fixed Structure}
-\label{subsubsec:auto_exp1}
-
-The Bayesian approaches and the MDL discretization method were tested on the Auto MPG data using the network network shown in Figure~\ref{fig:auto_graph_1}.
-This structure was obtained by prediscretizing each continuous variable into five uniform-width intervals, where five is the median cardinality of the discrete variables, and then taking the structure with highest likelihood from one thousand runs of K2.
-
-\begin{figure}[ht]
-  \centering
-   \input{graph_autocar_1}
-   \caption{Bayesian network structure obtained from running K2 on the prediscretized Auto MPG dataset}
-  \label{fig:auto_graph_1}
-\end{figure}
-
-Table~\ref{table:auto_disc_table_1} lists the discretization edges and mean log-likelihoods under 10-fold cross validation of the discrete Bayesian network resulting from each discretization method.
-The results indicate that the heuristic Bayesian method produces exactly the same discretization policy as the optimal Bayesian method.
-The MDL method does not produce any discretization edges, assigning one continuous interval to each continuous variable, and produces the structure with the lowest score.
-The cause behind MDL's discretization policy is discussed in Section~\ref{subsec:discuss_exp}.
-
-\begin{table}[h]
-  \centering
-  \caption{
-    Results from discretization of the Auto MPG dataset with fixed structure from Figure~\ref{fig:auto_graph_1}.
-    The first five rows list the discretization edges for each continuous variable.
-    The last row lists the mean cross-validated log-likelihood; positive values are better.
-    The optimal and heuristic Bayesian discretization policies are identical and the MDL method does not produce any discretization edges.
-  }
-  \input{table_autoMPG_1.tex}
-  \label{table:auto_disc_table_1}
-\end{table}
-
-Figure~\ref{fig:auto_exp1_distr_1_3} compares the Bayesian discretizaton policy for variables $A$ and $C$ with the original Auto MPG data.
-The black marks are the original Auto MPG samples.
-The color of a discretized region indicates the marginal probability of a sample from $P(A,C)$ being drawn from that region.
-As shown in the figure, the discretization edges obtained by the optimal Bayesian approach and the resulting marginalized probability match the raw data well.
-
-\begin{figure}[ht]
-\centering
-  \input{graph_auto_exp1_distr_1_3}
-  \caption{
-    Comparison of the Bayesian discretization policy for variables $A$ and $C$ to the original Auto MPG data learned with a fixed network.
-    The marginal probabilities of discretized regions closely match the raw data.
-  }
-  \label{fig:auto_exp1_distr_1_3}
-\end{figure}
-
-\subsubsection{Discretization while Learning Structure}
-\label{subsubsec:auto_exp2}
-
-In this experiment the network structure was not fixed in advance and was learned simultaneously with the discretization policies.
-Figure~\ref{fig:auto_graph_2} shows a learned Bayesian network structure and the corresponding numbers of intervals after discretization for each continuous variable.
-This result was obtained by running Algorithm~\ref{alg:structure_learn} fifty times using the optimal Bayesian method and choosing the structure with the highest likelihood.
-
-\begin{figure}[ht]
-  \centering
-  \input{graph_autocar_2}
-  \caption{The discrete-valued Bayesian network learned from the Auto MPG dataset}
-  \label{fig:auto_graph_2}
-\end{figure}
-
-Figure~\ref{fig:auto_exp2_distr_1_3} compares the Bayesian discretizaton policy for variables $A$ and $C$ in the learned network with the original Auto MPG data.
-The color of a discretized region indicates the marginal probability of a sample from $P(A,C)$ being drawn from that region.
-Although there are fewer discretization edges for $A$ and $C$ in the learned network, the marginal distribution is still captured.
-Although the discretization result of the optimal Bayesian approach may vary according to the network structure, it still produces high-quality discretizations.
-
-\begin{figure}[ht]
-  \centering
-  \input{graph_auto_exp2_distr_1_3}
-  \caption{
-    Comparison of the optimal Bayesian discretization policy for variables $A$ and $C$ to the original Auto MPG data learned along with the network structure.
-    Although the number of discretization edges is less than those in Figure~\ref{fig:auto_exp1_distr_1_3}, the probability distribution still closely matches the original data.
-  }
-  \label{fig:auto_exp2_distr_1_3}
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-% WINE
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Dataset 2: Wine}
-\label{subsec:wine}
-
-The Wine dataset contains variables related to the chemical analysis of wines from three different Italian cultivars.
-The dataset has \num{178} samples over fourteen variables.
-Variable $A$ is the only discrete variable and has three instantiations.
-
-\subsubsection{Discretization with fixed Structure}
-\label{subsubsec:wine_exp1}
-
-The Bayesian approaches and the MDL discretization method were tested on the Wine data using the network network shown in Figure~\ref{fig:wine_graph_1}.
-This structure was obtained by prediscretizing each continuous variable into three uniform-width intervals, where three is the median cardinality of the discrete variables, and then taking the structure with highest likelihood from one thousand runs of K2.
-
-Table~\ref{table:wine_disc_table_1} lists the discretization edges and mean log-likelihoods under 10-fold cross validation of the discrete Bayesian network resulting from each discretization method.
-The Bayesian methods outperform the MDL method in likelihood by a significant margin.
-The heuristic method discretizes the variables $G$, $H$, and $J$ into one fewer interval and the variable $M$ into one more interval than the optimal Bayesian approach, resulting in a slightly lower mean cross validated log likelihood.
-The overall performance of the heuristic method is still very high, and if runtime is the primary concern, the heuristic method can be considered the better approach.
-\tim{Do we need to list runtime too?}
-
-Notice that there are some discretization edges which appear in all three discretization methods, such as \num{1.42} and \num{2.35} for variable $C$ and \num{0.785} for variable $L$.
-This indicates that MDL indeed can find some important discretization edges, but it is not sensitive enough to find more edges.
-
-\begin{figure}[ht]
-  \centering
-  \scalebox{0.8}{\input{graph_wine_1}}
-  \caption{Structure from prediscretized K2 structure learning to compare the methods for Wine dataset}
-  \label{fig:wine_graph_1}
-\end{figure}
-
-\begin{table}
-  \centering
-  \caption{
-    Results from discretization of the Wine MPG dataset with fixed structure from Figure~\ref{fig:wine_graph_1}.
-    The first thirteen rows list the discretization edges for each continuous variable.
-    The last row lists the mean cross-validated log-likelihood; positive values are better.
-    The optimal Bayesian approach has the best discretization result in terms of likelihood, but the heuristic method obtains a similar result with nearly the same likelihood.
-    The MDL method produces discretization edges for more than half of the continuous variables but does not produce enough discretization intervals.
-    Some discretization edges appear in the results of all three methods.
-  }
-  \scalebox{1.0}{
-  \input{table_wine_1.tex}
-  }
-  \label{table:wine_disc_table_1}
-\end{table}
-
-Figure~\ref{fig:wine_exp1_distr} compares the optimal Bayesian and MODL discretizaton policies for variables $E$ and $K$ with the original Wine data.
-The discretization edges \num{17.9} for $E$ and \num{34.6} for $K$ appear in both plots.
-The MDL method does not use enough intervals for discretization.
-Relative sensitivities of each method to the input data is discussed in Section~\ref{subsec:discuss_exp}.
-
-\begin{figure}[ht]
-  \centering
-  \input{graph_wine_exp1_distr}
-  \caption{Comparison of the discretization policies for variables $A$ and $C$ obtained using optimal Bayesian and MDL methods}
-  \label{fig:wine_exp1_distr}
-\end{figure}
-
-\subsubsection{Discretization while Learning Structure}
-\label{subsubsec:wine_exp2}
-
-Figure~\ref{fig:wine_graph_2} is the discrete-valued Bayesian network learned from the Wine dataset, obtained by running Algorithm~\ref{alg:structure_learn} fifty times.
-A comparison of Figures~\ref{fig:wine_graph_2} and \ref{fig:wine_graph_1} show that the Bayesian network learned during the discretization process has more edges than the network learned on the prediscretized data.
-When a network is learned along with discretization, the algorithm has more freedom to adjust the structure and the discretization policy simultaneously to identify useful correlations and produce a denser structure.
-
-Figure~\ref{fig:wine_exp2_distr} shows the discretization policy for variables $E$ and $K$ obtained with the optimal Bayesian method.
-The discretization edge $E = 17.9$ also appears in all discretization policies from the fixed network (Figure~\ref{fig:wine_exp1_distr}).
-This indicates that some discretization edges are robust against the network structure.
-Furthermore, the discretization edge at $E = 23.5$ present in the fixed-structure case is missing in the learned structure.
-This is caused by $E$ having twice as many parents in the learned network structure.
-The more parents a variable has, the less discretization intervals it will be able to support, as the set of statistics required to define the resulting distribution increases exponentially with the number of parents.
-
-\begin{figure}[ht]
-  \centering
-  \scalebox{0.7}{\input{graph_wine_2}}
-  \caption{The discrete-valued Bayesian network learned from the Wine dataset using the optimal Bayesian method.}
-  \label{fig:wine_graph_2}
-\end{figure}
-
-\begin{figure}[ht]
-  \centering
-  \input{graph_wine_exp2_distr_5_11}
-  \caption{
-    The discretization policy for variables $E$ and $K$ on the learned network in Figure~\ref{fig:wine_graph_2}.
-    The discretization edge $E = 17.9$ also appears in the policies for the fixed network.
-    This indicates that some discretization edges are robust against changing network structure.
-  }
-  \label{fig:wine_exp2_distr}
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-% Housing
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Data 3: Housing}
-\label{subsec:housing}
-
-The Housing dataset contains variables related to the values of houses in Boston suburbs.
-The dataset has \num{506} samples over fourteen variables.
-Only variables $D$ and $I$ are discrete-valued, with \num{2} and \num{9} instantiations, respectively.
-Variable $A$ is the only discrete variable and has three instantiations.
-Despite their being continuous, several variables in the Housing dataset possess many repeated values.
-The following experiments were conducted with an upper limit of three on the number of parents per variable to prevent memory issues with MDL.
-
-\subsubsection{Discretization with Fixed Structure}
-\label{subsubsec:housing_exp1}
-
-The Bayesian network structure in Figure~\ref{fig:housing_graph_1} was obtained by prediscretizing each continuous variable into five uniform-width interval and then running the K2 algorithm one thousand times and choosing the network with the highest likelihood.
-Table~\ref{table:housing_disc_table_1} shows the numbers of intervals after discretization for each continuous variables and the log-likelihood of the dataset based on each discretization method.
-MDL method does not produce any discretization edges for most variables.
-The heuristic Bayesian method produces far more discretization edges than the optimal Bayesian method due to repeated instances in the dataset.
-These numbers of intervals returned by the three methods illustrate the over-sensitive nature of the heuristic method and the under-sensitive nature of the MDL method.
-\tim{I am not sure we are using `sensitive' correctly. Sensitive to what? Perhaps `biased towards higher edge counts'?}
-The relative sensitivity of each algorithm will be discussed in Section~\ref{subsec:discuss_exp}.
-
-The heurstic method produces the discretization with the highest cross-validated log likelihood, but although the heuristic method leads to a higher number of intervals, its likelihood is not significantly better than the optimal Bayesian approach.
-This shows that the optimal Bayesian approach captures the most important discretization edges.
-
-\begin{figure}[ht]
-  \centering
-  \scalebox{0.8}{\input{graph_housing_1}}
-  \caption{Structure from prediscretized K2 structure learning to compare the methods for Housing dataset}
-  \label{fig:housing_graph_1}
-\end{figure}
-
-\begin{table}
-  \centering
-  \caption{
-    Discretization policy summary of the Housing dataset based on the fixed network structure shown in Figure~\ref{fig:housing_graph_1}.
-    The first twelve rows show the numbers of intervals after discretization by each method.
-    The last row is the mean cross-validated log-likelihood of the dataset based on the discretization results.
-    The heuristic method is over-sensitive \todo{to what?} and discretizes some variables into too many intervals.
-    The MDL method is less sensitive and on many cases does not produce any discretization intervals.
-    The optimal Bayesian approach produces a reasonable number of discretization edges.
-  }
-  \scalebox{1.0}{\input{table_housing_1.tex}}
-  \label{table:housing_disc_table_1}
-\end{table}
-
-Figures~\ref{fig:housing_exp1_distr_3_5} and \ref{fig:housing_exp1_distr_8_5} show the discretization policy learned using the optimal Bayesian approach on the fixed network shown in Figure~\ref{fig:housing_graph_1}.
-In Figure~\ref{fig:housing_exp1_distr_3_5}, the scatter points corresponding to the original dataset have been jittered, because there are many repeated values for variables $C$ and $E$.
-Each repeated point forms a single discrete region, thereby encouraging discretization.
-In contrast, the samples for $H$ are well spread out, resulting in fewer discretization regions and larger discretization intervals.
-
-\begin{figure}[ht]
-  \centering
-  \input{graph_housing_exp1_distr_3_5}
-  \caption{
-    The discretization policies for variables $C$ and $E$ learned using the optimal Bayesian approach on the fixed network shown in Figure~\ref{fig:housing_graph_1}.
-    The scatter points were jittered to reveal the repeated values in the dataset.
-    The repeated values lead to a high number of discretization edges, because repeated values can easily form discretized regions by their own.
-  }
-  \label{fig:housing_exp1_distr_3_5}
-\end{figure}
-
-\begin{figure}[ht]
-  \centering
-  \input{graph_housing_exp1_distr_8_5}
-  \caption{
-    The discretization policies for variables $H$ and $E$ learned using the optimal Bayesian approach on the fixed network shown in Figure~\ref{fig:housing_graph_1}.
-    The variable $H$ possesses no overly repeated values, thus producing a cleaner discretization policy.
-  }
-  \label{fig:housing_exp1_distr_8_5}
-\end{figure}
-
-\subsubsection{Discretization while Learning Structure}
-\label{subsubsec:housing_exp2}
-
-Figure~\ref{fig:housing_graph_2} shows a learned Bayesian network structure and the corresponding numbers of intervals after discretization for each continuous variable.
-Variable $D$ is neighborless is both the learned and fixed networks.
-The continuous variables $C$, $E$, $J$ and $K$, which are all connected through $C$, have many discretization intervals.
-Typically, when discretizing a variable, the expected number of discretization intervals is close to the highest cardinality among variables in its Markov blanket.
-This naturally leads to clusters of variables with high numbers of discretization intervals.
-
-\begin{figure}[ht]
-  \centering
-  \scalebox{0.8}{\input{graph_housing_2}}
-  \caption{
-    The discrete-valued Bayesian network learned from the Housing dataset using the optimal Bayesian method.
-  }
-  \label{fig:housing_graph_2}
-\end{figure}
-
-Figure~\ref{fig:housing_exp2_distr_3_5} and Figure~\ref{fig:housing_exp2_distr_8_5} show the discretization result on variables of the network in Figure~\ref{fig:housing_graph_2}.
-Again, variable $C$ and $E$ have many discretization edges due to the repeated values.
-Although the number of intervals after discretization on $H$ is less the number in Figure~\ref{fig:housing_exp1_distr_8_5}, it still captures the distribution of the raw data along with the discretization edges on $E$.
-
-\begin{figure}[ht]
-  \centering
-  \input{graph_housing_exp2_distr_3_5}
-  \caption{
-    The discretization policy for variables $C$ and $E$ on the learned network in Figure~\ref{fig:housing_graph_2}.
-    The high number of discretization edges are caused by the repeated values in variables $C$ and $E$.
-  }
-  \label{fig:housing_exp2_distr_3_5}
-\end{figure}
-
-\begin{figure}[ht]
-  \centering
-  \input{graph_housing_exp2_distr_8_5}
-  \caption{
-    The discretization policy for variables $H$ and $E$ on the learned network in Figure~\ref{fig:housing_graph_2}.
-    The number of discretization intervals for $H$ is less than it was for the fixed network structure in Figure~\ref{fig:housing_exp1_distr_8_5}, but the discretization policy still matches the raw data.
-  }
-  \label{fig:housing_exp2_distr_8_5}
-\end{figure}
-
-\subsection{Discussion}
-\label{subsec:discuss_exp}
-
-\begin{figure}[ht]
-\centering
-  \input{graph_exp_discuss}
-  \caption{A simple Bayesian network that is used to demonstrate the sensitivity of the three methods}
-  \label{fig:exp_discuss}
-\end{figure}
-
-To quantatively discuss the sensitivity of the three methods to the number of discretization intervals, consider the Bayesian network in Figure~\ref{fig:exp_discuss}, where $\cX$ is continuous and $P_1$ and $P_2$ are discrete.
-If $\Pa_{\cX} = \curly{P_1, P_2}$ and $D_{\cX} = \curly{1.0,2.0,3.0, \ldots n}$, then the corresponding objective functions for the three discretization methods are:
-
-\begin{small}
-  \begin{equation}
-  \begin{aligned}
-  f_{\text{MDL}} & = \overbrace{Z_1 \cdot k + \ln(k) + \ln {{n +k - 1}\choose{k -1}} }^{\text{Penalty Term}}+   \overbrace{\rule{0pt}{1.35em} \ln(N) \cdot I(X^*, \Pa_X)}^{\text{Edge Position Term}} \\
-  f_{\text{Bayesian}} &= \overbrace{\rule{0pt}{1.85em}  Z_2 \cdot k + \sum_{i=1}^k \ln {{\gamma_i + J_P - 1}\choose{J_P -1}}}^{\text{Penalty Term}} + \overbrace{\sum^k_{i=1} \ln \left(   {{\gamma_i !}\over{n^{(P)}_{i,1}!
+% \section{Experiments}
+% \label{sec:experiments}
+
+% This section describes experiments conducted to evaluate the proposed methods.
+% All experiments were run on datasets from the publically available University of California, Irvine machine learning repository \citep{Lichman_2013}.
+% Variables are labelled alphabetically in the order given on the dataset information webpage
+% In the figures that follow, shaded nodes correspond to initially discrete variables and the subscripts indicate the number of discrete instantiations.
+
+% Two experiments were conducted on each dataset.
+% The first experiment compares the performance of the optimal Bayesian discretization method, the heuristic Bayesian discretization method, and MDL on a known Bayesian network structure.
+% The structure was obtained by prediscretizing each continuous variable into $k$ uniform-width intervals, where $k$ is the median number of instantiations of the discrete variables, and using the structure with the highest Bayesian score from one thousand runs of the K2 algorithm with random variable orderings.
+% The second experiment compares the same methods applied when simultaneously discretizing and learning network structure.
+
+% The discretizations are compared using the mean cross validated log-likelihood of the data $D$ given the graph structure $G$ and discretization policies $\discset$.
+% The log-likelihood has two components,
+
+% \begin{equation}
+% \ln p(D\mid G, \discset) = \ln P(D^*\mid G) + \ln p(D\mid \discset, D^*)\text{,}
+% \end{equation}
+
+% \noindent
+% where $D$ is the original dataset and $D^*$ is the dataset discretized according to $\discset$.
+% The log-likelihood of the discretized dataset is the Bayesian score (Equation~\ref{eq:BayesianScore}) evaluated with a uniform prior over graph structures and a uniform Dirichlet prior ($\alpha_{ijk} = 1$ for all $i$, $j$, and $k$).
+% The log-likelihood of the original dataset given the discrete dataset is
+
+% \todo{
+% \begin{equation}
+%   \ln p\paren{D\mid \discset, D^*} = \sum_{i=1}^n
+%   1\curly{X_i \text{ orig. cont.}}
+%   \sum_{j=1}^{q_i} \sum_{k=1}^{r_i} m_{ijk} \ln\paren{
+%     \frac{
+%       1
+%     }{
+%       e^{\Lambda_{\cX_i}}_{k+1} - e^{\Lambda_{\cX_i}}_{k}
+%     }
+%   }\text{.}
+% \end{equation}
+% }
+
+% \noindent
+% The mean cross-validated log-likelihood is the mean log-likelihood on the witheld dataset among cross-validation folds.
+% Cross-validation directly estimates generalization error.
+% Ten folds were used in each experiment.
+
+% The optimal discretization policy for MDL is found with dynamic programming in a similar manner as with the Bayesian method.
+% For a Bayesian network with a single continuous variable $\cX$, the MDL objective function is
+
+% \begin{equation}
+%   \label{eqn:MDL}
+%   \todo{
+%   \begin{aligned}
+%   \frac{1}{2} \ln(n) \left\lbrace  \lvert \Pa_{X_i} \rvert (\lvert X_i \rvert - 1) +
+%    {\sum_{j,\cX_i \in \Pa_{X_i}}} \lvert \Pa_{X_j} \rvert (\lvert \cX_j \rvert - 1) \right\rbrace + \ln(\lvert {\cX_i} \rvert) \\
+%    + (N_i-1) H \paren{\frac{|X^*_i| - 1}{N_i -1}} -n \cdot \left[ I(X_i,\Pa_{X_i}) + {\sum_{j,\cX_i \in \Pa_{\cX_i}}} I(\cX_j, \Pa_{X_j}) \right]\text{,}
+%   \end{aligned}
+%   }
+% \end{equation}
+
+% where $I(A,B)$ is the mutual information between two discrete variables $A$ and $B$, ${H(p) = -p \ln(p) - (1-p) \ln(1-p)}$, and \todo{$X^*_i$ is the discretized version of the $i$th sample of $X$}.
+
+% \subsection{Auto MPG Dataset}
+% \label{subsec:auto}
+
+% The Auto MPG dataset contains variables related to the fuel consumption of automobiles in urban driving.
+% The dataset has \num{392} samples over eight variables, not including six instances with missing data.
+% Three variables are discrete: $B$, $G$, and $H$, with \num{5}, \num{13}, and \num{3} instantiations respectively.
+
+% \subsubsection{Discretization with fixed Structure}
+% \label{subsubsec:auto_exp1}
+
+% The Bayesian approaches and the MDL discretization method were tested on the Auto MPG data using the network network shown in Figure~\ref{fig:auto_graph_1}.
+% This structure was obtained by prediscretizing each continuous variable into five uniform-width intervals, where five is the median cardinality of the discrete variables, and then taking the structure with highest likelihood from one thousand runs of K2.
+
+% \begin{figure}[ht]
+%   \centering
+%    \input{graph_autocar_1}
+%    \caption{Bayesian network structure obtained from running K2 on the prediscretized Auto MPG dataset}
+%   \label{fig:auto_graph_1}
+% \end{figure}
+
+% Table~\ref{table:auto_disc_table_1} lists the discretization edges and mean log-likelihoods under 10-fold cross validation of the discrete Bayesian network resulting from each discretization method.
+% The results indicate that the heuristic Bayesian method produces exactly the same discretization policy as the optimal Bayesian method.
+% The MDL method does not produce any discretization edges, assigning one continuous interval to each continuous variable, and produces the structure with the lowest score.
+% The cause behind MDL's discretization policy is discussed in Section~\ref{subsec:discuss_exp}.
+
+% \begin{table}[h]
+%   \centering
+%   \caption{
+%     Results from discretization of the Auto MPG dataset with fixed structure from Figure~\ref{fig:auto_graph_1}.
+%     The first five rows list the discretization edges for each continuous variable.
+%     The last row lists the mean cross-validated log-likelihood; positive values are better.
+%     The optimal and heuristic Bayesian discretization policies are identical and the MDL method does not produce any discretization edges.
+%   }
+%   \input{table_autoMPG_1.tex}
+%   \label{table:auto_disc_table_1}
+% \end{table}
+
+% Figure~\ref{fig:auto_exp1_distr_1_3} compares the Bayesian discretizaton policy for variables $A$ and $C$ with the original Auto MPG data.
+% The black marks are the original Auto MPG samples.
+% The color of a discretized region indicates the marginal probability of a sample from $P(A,C)$ being drawn from that region.
+% As shown in the figure, the discretization edges obtained by the optimal Bayesian approach and the resulting marginalized probability match the raw data well.
+
+% \begin{figure}[ht]
+% \centering
+%   \input{graph_auto_exp1_distr_1_3}
+%   \caption{
+%     Comparison of the Bayesian discretization policy for variables $A$ and $C$ to the original Auto MPG data learned with a fixed network.
+%     The marginal probabilities of discretized regions closely match the raw data.
+%   }
+%   \label{fig:auto_exp1_distr_1_3}
+% \end{figure}
+
+% \subsubsection{Discretization while Learning Structure}
+% \label{subsubsec:auto_exp2}
+
+% In this experiment the network structure was not fixed in advance and was learned simultaneously with the discretization policies.
+% Figure~\ref{fig:auto_graph_2} shows a learned Bayesian network structure and the corresponding numbers of intervals after discretization for each continuous variable.
+% This result was obtained by running Algorithm~\ref{alg:structure_learn} fifty times using the optimal Bayesian method and choosing the structure with the highest likelihood.
+
+% \begin{figure}[ht]
+%   \centering
+%   \input{graph_autocar_2}
+%   \caption{The discrete-valued Bayesian network learned from the Auto MPG dataset}
+%   \label{fig:auto_graph_2}
+% \end{figure}
+
+% Figure~\ref{fig:auto_exp2_distr_1_3} compares the Bayesian discretizaton policy for variables $A$ and $C$ in the learned network with the original Auto MPG data.
+% The color of a discretized region indicates the marginal probability of a sample from $P(A,C)$ being drawn from that region.
+% Although there are fewer discretization edges for $A$ and $C$ in the learned network, the marginal distribution is still captured.
+% Although the discretization result of the optimal Bayesian approach may vary according to the network structure, it still produces high-quality discretizations.
+
+% \begin{figure}[ht]
+%   \centering
+%   \input{graph_auto_exp2_distr_1_3}
+%   \caption{
+%     Comparison of the optimal Bayesian discretization policy for variables $A$ and $C$ to the original Auto MPG data learned along with the network structure.
+%     Although the number of discretization edges is less than those in Figure~\ref{fig:auto_exp1_distr_1_3}, the probability distribution still closely matches the original data.
+%   }
+%   \label{fig:auto_exp2_distr_1_3}
+% \end{figure}
+
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %
+% % WINE
+% %
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% \subsection{Dataset 2: Wine}
+% \label{subsec:wine}
+
+% The Wine dataset contains variables related to the chemical analysis of wines from three different Italian cultivars.
+% The dataset has \num{178} samples over fourteen variables.
+% Variable $A$ is the only discrete variable and has three instantiations.
+
+% \subsubsection{Discretization with fixed Structure}
+% \label{subsubsec:wine_exp1}
+
+% The Bayesian approaches and the MDL discretization method were tested on the Wine data using the network network shown in Figure~\ref{fig:wine_graph_1}.
+% This structure was obtained by prediscretizing each continuous variable into three uniform-width intervals, where three is the median cardinality of the discrete variables, and then taking the structure with highest likelihood from one thousand runs of K2.
+
+% Table~\ref{table:wine_disc_table_1} lists the discretization edges and mean log-likelihoods under 10-fold cross validation of the discrete Bayesian network resulting from each discretization method.
+% The Bayesian methods outperform the MDL method in likelihood by a significant margin.
+% The heuristic method discretizes the variables $G$, $H$, and $J$ into one fewer interval and the variable $M$ into one more interval than the optimal Bayesian approach, resulting in a slightly lower mean cross validated log likelihood.
+% The overall performance of the heuristic method is still very high, and if runtime is the primary concern, the heuristic method can be considered the better approach.
+% \tim{Do we need to list runtime too?}
+
+% Notice that there are some discretization edges which appear in all three discretization methods, such as \num{1.42} and \num{2.35} for variable $C$ and \num{0.785} for variable $L$.
+% This indicates that MDL indeed can find some important discretization edges, but it is not sensitive enough to find more edges.
+
+% \begin{figure}[ht]
+%   \centering
+%   \scalebox{0.8}{\input{graph_wine_1}}
+%   \caption{Structure from prediscretized K2 structure learning to compare the methods for Wine dataset}
+%   \label{fig:wine_graph_1}
+% \end{figure}
+
+% \begin{table}
+%   \centering
+%   \caption{
+%     Results from discretization of the Wine MPG dataset with fixed structure from Figure~\ref{fig:wine_graph_1}.
+%     The first thirteen rows list the discretization edges for each continuous variable.
+%     The last row lists the mean cross-validated log-likelihood; positive values are better.
+%     The optimal Bayesian approach has the best discretization result in terms of likelihood, but the heuristic method obtains a similar result with nearly the same likelihood.
+%     The MDL method produces discretization edges for more than half of the continuous variables but does not produce enough discretization intervals.
+%     Some discretization edges appear in the results of all three methods.
+%   }
+%   \scalebox{1.0}{
+%   \input{table_wine_1.tex}
+%   }
+%   \label{table:wine_disc_table_1}
+% \end{table}
+
+% Figure~\ref{fig:wine_exp1_distr} compares the optimal Bayesian and MODL discretizaton policies for variables $E$ and $K$ with the original Wine data.
+% The discretization edges \num{17.9} for $E$ and \num{34.6} for $K$ appear in both plots.
+% The MDL method does not use enough intervals for discretization.
+% Relative sensitivities of each method to the input data is discussed in Section~\ref{subsec:discuss_exp}.
+
+% \begin{figure}[ht]
+%   \centering
+%   \input{graph_wine_exp1_distr}
+%   \caption{Comparison of the discretization policies for variables $A$ and $C$ obtained using optimal Bayesian and MDL methods}
+%   \label{fig:wine_exp1_distr}
+% \end{figure}
+
+% \subsubsection{Discretization while Learning Structure}
+% \label{subsubsec:wine_exp2}
+
+% Figure~\ref{fig:wine_graph_2} is the discrete-valued Bayesian network learned from the Wine dataset, obtained by running Algorithm~\ref{alg:structure_learn} fifty times.
+% A comparison of Figures~\ref{fig:wine_graph_2} and \ref{fig:wine_graph_1} show that the Bayesian network learned during the discretization process has more edges than the network learned on the prediscretized data.
+% When a network is learned along with discretization, the algorithm has more freedom to adjust the structure and the discretization policy simultaneously to identify useful correlations and produce a denser structure.
+
+% Figure~\ref{fig:wine_exp2_distr} shows the discretization policy for variables $E$ and $K$ obtained with the optimal Bayesian method.
+% The discretization edge $E = 17.9$ also appears in all discretization policies from the fixed network (Figure~\ref{fig:wine_exp1_distr}).
+% This indicates that some discretization edges are robust against the network structure.
+% Furthermore, the discretization edge at $E = 23.5$ present in the fixed-structure case is missing in the learned structure.
+% This is caused by $E$ having twice as many parents in the learned network structure.
+% The more parents a variable has, the less discretization intervals it will be able to support, as the set of statistics required to define the resulting distribution increases exponentially with the number of parents.
+
+% \begin{figure}[ht]
+%   \centering
+%   \scalebox{0.7}{\input{graph_wine_2}}
+%   \caption{The discrete-valued Bayesian network learned from the Wine dataset using the optimal Bayesian method.}
+%   \label{fig:wine_graph_2}
+% \end{figure}
+
+% \begin{figure}[ht]
+%   \centering
+%   \input{graph_wine_exp2_distr_5_11}
+%   \caption{
+%     The discretization policy for variables $E$ and $K$ on the learned network in Figure~\ref{fig:wine_graph_2}.
+%     The discretization edge $E = 17.9$ also appears in the policies for the fixed network.
+%     This indicates that some discretization edges are robust against changing network structure.
+%   }
+%   \label{fig:wine_exp2_distr}
+% \end{figure}
+
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %
+% % Housing
+% %
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% \subsection{Data 3: Housing}
+% \label{subsec:housing}
+
+% The Housing dataset contains variables related to the values of houses in Boston suburbs.
+% The dataset has \num{506} samples over fourteen variables.
+% Only variables $D$ and $I$ are discrete-valued, with \num{2} and \num{9} instantiations, respectively.
+% Variable $A$ is the only discrete variable and has three instantiations.
+% Despite their being continuous, several variables in the Housing dataset possess many repeated values.
+% The following experiments were conducted with an upper limit of three on the number of parents per variable to prevent memory issues with MDL.
+
+% \subsubsection{Discretization with Fixed Structure}
+% \label{subsubsec:housing_exp1}
+
+% The Bayesian network structure in Figure~\ref{fig:housing_graph_1} was obtained by prediscretizing each continuous variable into five uniform-width interval and then running the K2 algorithm one thousand times and choosing the network with the highest likelihood.
+% Table~\ref{table:housing_disc_table_1} shows the numbers of intervals after discretization for each continuous variables and the log-likelihood of the dataset based on each discretization method.
+% MDL method does not produce any discretization edges for most variables.
+% The heuristic Bayesian method produces far more discretization edges than the optimal Bayesian method due to repeated instances in the dataset.
+% These numbers of intervals returned by the three methods illustrate the over-sensitive nature of the heuristic method and the under-sensitive nature of the MDL method.
+% \tim{I am not sure we are using `sensitive' correctly. Sensitive to what? Perhaps `biased towards higher edge counts'?}
+% The relative sensitivity of each algorithm will be discussed in Section~\ref{subsec:discuss_exp}.
+
+% The heurstic method produces the discretization with the highest cross-validated log likelihood, but although the heuristic method leads to a higher number of intervals, its likelihood is not significantly better than the optimal Bayesian approach.
+% This shows that the optimal Bayesian approach captures the most important discretization edges.
+
+% \begin{figure}[ht]
+%   \centering
+%   \scalebox{0.8}{\input{graph_housing_1}}
+%   \caption{Structure from prediscretized K2 structure learning to compare the methods for Housing dataset}
+%   \label{fig:housing_graph_1}
+% \end{figure}
+
+% \begin{table}
+%   \centering
+%   \caption{
+%     Discretization policy summary of the Housing dataset based on the fixed network structure shown in Figure~\ref{fig:housing_graph_1}.
+%     The first twelve rows show the numbers of intervals after discretization by each method.
+%     The last row is the mean cross-validated log-likelihood of the dataset based on the discretization results.
+%     The heuristic method is over-sensitive \todo{to what?} and discretizes some variables into too many intervals.
+%     The MDL method is less sensitive and on many cases does not produce any discretization intervals.
+%     The optimal Bayesian approach produces a reasonable number of discretization edges.
+%   }
+%   \scalebox{1.0}{\input{table_housing_1.tex}}
+%   \label{table:housing_disc_table_1}
+% \end{table}
+
+% Figures~\ref{fig:housing_exp1_distr_3_5} and \ref{fig:housing_exp1_distr_8_5} show the discretization policy learned using the optimal Bayesian approach on the fixed network shown in Figure~\ref{fig:housing_graph_1}.
+% In Figure~\ref{fig:housing_exp1_distr_3_5}, the scatter points corresponding to the original dataset have been jittered, because there are many repeated values for variables $C$ and $E$.
+% Each repeated point forms a single discrete region, thereby encouraging discretization.
+% In contrast, the samples for $H$ are well spread out, resulting in fewer discretization regions and larger discretization intervals.
+
+% \begin{figure}[ht]
+%   \centering
+%   \input{graph_housing_exp1_distr_3_5}
+%   \caption{
+%     The discretization policies for variables $C$ and $E$ learned using the optimal Bayesian approach on the fixed network shown in Figure~\ref{fig:housing_graph_1}.
+%     The scatter points were jittered to reveal the repeated values in the dataset.
+%     The repeated values lead to a high number of discretization edges, because repeated values can easily form discretized regions by their own.
+%   }
+%   \label{fig:housing_exp1_distr_3_5}
+% \end{figure}
+
+% \begin{figure}[ht]
+%   \centering
+%   \input{graph_housing_exp1_distr_8_5}
+%   \caption{
+%     The discretization policies for variables $H$ and $E$ learned using the optimal Bayesian approach on the fixed network shown in Figure~\ref{fig:housing_graph_1}.
+%     The variable $H$ possesses no overly repeated values, thus producing a cleaner discretization policy.
+%   }
+%   \label{fig:housing_exp1_distr_8_5}
+% \end{figure}
+
+% \subsubsection{Discretization while Learning Structure}
+% \label{subsubsec:housing_exp2}
+
+% Figure~\ref{fig:housing_graph_2} shows a learned Bayesian network structure and the corresponding numbers of intervals after discretization for each continuous variable.
+% Variable $D$ is neighborless is both the learned and fixed networks.
+% The continuous variables $C$, $E$, $J$ and $K$, which are all connected through $C$, have many discretization intervals.
+% Typically, when discretizing a variable, the expected number of discretization intervals is close to the highest cardinality among variables in its Markov blanket.
+% This naturally leads to clusters of variables with high numbers of discretization intervals.
+
+% \begin{figure}[ht]
+%   \centering
+%   \scalebox{0.8}{\input{graph_housing_2}}
+%   \caption{
+%     The discrete-valued Bayesian network learned from the Housing dataset using the optimal Bayesian method.
+%   }
+%   \label{fig:housing_graph_2}
+% \end{figure}
+
+% Figure~\ref{fig:housing_exp2_distr_3_5} and Figure~\ref{fig:housing_exp2_distr_8_5} show the discretization result on variables of the network in Figure~\ref{fig:housing_graph_2}.
+% Again, variable $C$ and $E$ have many discretization edges due to the repeated values.
+% Although the number of intervals after discretization on $H$ is less the number in Figure~\ref{fig:housing_exp1_distr_8_5}, it still captures the distribution of the raw data along with the discretization edges on $E$.
+
+% \begin{figure}[ht]
+%   \centering
+%   \input{graph_housing_exp2_distr_3_5}
+%   \caption{
+%     The discretization policy for variables $C$ and $E$ on the learned network in Figure~\ref{fig:housing_graph_2}.
+%     The high number of discretization edges are caused by the repeated values in variables $C$ and $E$.
+%   }
+%   \label{fig:housing_exp2_distr_3_5}
+% \end{figure}
+
+% \begin{figure}[ht]
+%   \centering
+%   \input{graph_housing_exp2_distr_8_5}
+%   \caption{
+%     The discretization policy for variables $H$ and $E$ on the learned network in Figure~\ref{fig:housing_graph_2}.
+%     The number of discretization intervals for $H$ is less than it was for the fixed network structure in Figure~\ref{fig:housing_exp1_distr_8_5}, but the discretization policy still matches the raw data.
+%   }
+%   \label{fig:housing_exp2_distr_8_5}
+% \end{figure}
+
+% \subsection{Discussion}
+% \label{subsec:discuss_exp}
+
+% \begin{figure}[ht]
+% \centering
+%   \input{graph_exp_discuss}
+%   \caption{A simple Bayesian network that is used to demonstrate the sensitivity of the three methods}
+%   \label{fig:exp_discuss}
+% \end{figure}
+
+% To quantatively discuss the sensitivity of the three methods to the number of discretization intervals, consider the Bayesian network in Figure~\ref{fig:exp_discuss}, where $\cX$ is continuous and $P_1$ and $P_2$ are discrete.
+% If $\Pa_{\cX} = \curly{P_1, P_2}$ and $D_{\cX} = \curly{1.0,2.0,3.0, \ldots n}$, then the corresponding objective functions for the three discretization methods are:
+
+% \begin{small}
+%   \begin{equation}
+%   \begin{aligned}
+%   f_{\text{MDL}} & = \overbrace{Z_1 \cdot k + \ln(k) + \ln {{n +k - 1}\choose{k -1}} }^{\text{Penalty Term}}+   \overbrace{\rule{0pt}{1.35em} \ln(N) \cdot I(X^*, \Pa_X)}^{\text{Edge Position Term}} \\
+%   f_{\text{Bayesian}} &= \overbrace{\rule{0pt}{1.85em}  Z_2 \cdot k + \sum_{i=1}^k \ln {{\gamma_i + J_P - 1}\choose{J_P -1}}}^{\text{Penalty Term}} + \overbrace{\sum^k_{i=1} \ln \left(   {{\gamma_i !}\over{n^{(P)}_{i,1}!
 n^{(P)}_{i,2}!
@@
 }} \right) }^{\text{Edge Position Term}}\\
-  f_{\text{Heuristic}} &= \overbrace{Z_2 \cdot k + \sum_{i=1}^k \ln {{\gamma_i + J_{P_1} - 1}\choose{J_{P_1} -1}} + \sum_{i=1}^k \ln {{\gamma_i + J_{P_2} - 1}\choose{J_{P_2} -1}} }^{\text{Penalty Term}}+\\
-  & \overbrace{\sum^k_{i=1}  \left[ \ln \left(   {{\gamma_i !}\over{n^{(P_1)}_{i,1}!
+%   f_{\text{Heuristic}} &= \overbrace{Z_2 \cdot k + \sum_{i=1}^k \ln {{\gamma_i + J_{P_1} - 1}\choose{J_{P_1} -1}} + \sum_{i=1}^k \ln {{\gamma_i + J_{P_2} - 1}\choose{J_{P_2} -1}} }^{\text{Penalty Term}}+\\
+%   & \overbrace{\sum^k_{i=1}  \left[ \ln \left(   {{\gamma_i !}\over{n^{(P_1)}_{i,1}!
 n^{(P_1)}_{i,2}!
@@
 n^{(P_2)}_{i,2} \cdots n^{(P_2)}_{i,J_{P_2}} }} \right) \right]}^{\text{Edge Position Term}}
-  \end{aligned}\text{,}
-  \end{equation}
-\end{small}
-
-\noindent
-where $Z_1$ and $Z_2$ are constant over discretizations, $k$ is the number of discretization intervals, and $I\paren{A, B} = \sum_{a,b} \hat{P}(a,b) \ln\frac{\hat{P}(a,b)}{\hat{P}(a)\hat{P}(b)}$ is the mutual information based on estimated probability1ies.
-Note that the third term of $f_\text{MDL}$ had been approximated using $H(p)$ (see Equation~\ref{eqn:MDL}) in the original work by \cite{Friedman_1996} but here is written without that approximation.
-
-The sensitivities of each method to the discretization edges are captured in the edge position terms, as the penalty terms are similar across methods.
-The value of the edge position term for MDL is primarly determined by the mutual information, which varies less severely than the corresponding terms for the Bayesian methods.
-The MDL term uses emperical probability distributions, based off of ratios of counts, whereas the Bayesian methods use factorial terms, and thus vary less severely.
-Futhermore, the term for the heuristic Bayesian method varies more aggresively than the term for the optimal Bayesian method, as it has two terms.
-The MDL method is thus the least sensitive to the discretization edges and the heuristic Bayesian method is over-sensitive.
-This sensitivity gives rise to the relative performance of each method in the experiments conducted above.
+%   \end{aligned}\text{,}
+%   \end{equation}
+% \end{small}
+
+% \noindent
+% where $Z_1$ and $Z_2$ are constant over discretizations, $k$ is the number of discretization intervals, and $I\paren{A, B} = \sum_{a,b} \hat{P}(a,b) \ln\frac{\hat{P}(a,b)}{\hat{P}(a)\hat{P}(b)}$ is the mutual information based on estimated probability1ies.
+% Note that the third term of $f_\text{MDL}$ had been approximated using $H(p)$ (see Equation~\ref{eqn:MDL}) in the original work by \cite{Friedman_1996} but here is written without that approximation.
+
+% The sensitivities of each method to the discretization edges are captured in the edge position terms, as the penalty terms are similar across methods.
+% The value of the edge position term for MDL is primarly determined by the mutual information, which varies less severely than the corresponding terms for the Bayesian methods.
+% The MDL term uses emperical probability distributions, based off of ratios of counts, whereas the Bayesian methods use factorial terms, and thus vary less severely.
+% Futhermore, the term for the heuristic Bayesian method varies more aggresively than the term for the optimal Bayesian method, as it has two terms.
+% The MDL method is thus the least sensitive to the discretization edges and the heuristic Bayesian method is over-sensitive.
+% This sensitivity gives rise to the relative performance of each method in the experiments conducted above.
 
@@
 
-\section*{Appendix}
-
-\begin{algorithm}
-  \caption{ Calculation of $h(u,v)$ for all $u \leq v$}
-  \label{alg:h}
-  \begin{algorithmic}[1]
-  \State Initialize $H$ as an $N \times N$ matrix such that all elements are 0.
-  \State $count_p$ is an $N \times N \times \|\Pa_X\|$ matrix such that $count_p [u,v,w]$ is the number of instances from $x_u$ to $x_v$ with $w$th value of $\Pa_X$.
+% \section*{Appendix}
+
+% \begin{algorithm}
+%   \caption{ Calculation of $h(u,v)$ for all $u \leq v$}
+%   \label{alg:h}
+%   \begin{algorithmic}[1]
+%   \State Initialize $H$ as an $N \times N$ matrix such that all elements are 0.
+%   \State $count_p$ is an $N \times N \times \|\Pa_X\|$ matrix such that $count_p [u,v,w]$ is the number of instances from $x_u$ to $x_v$ with $w$th value of $\Pa_X$.
 This matrix can be calculated in $O(\|\Pa_X\| \cdot N^2)$
-  \For {$u = 1$ to $N$}
-    \For {$v = u$ to $N$}
-      \State $H(u,v) \leftarrow H(u,v) + \ln((v-u + J_p)!) - \ln((J_p -1)!)$
-      \For {$w = 1$ to $\|\Pa_X\|$}
-        \State $H(u,v) \leftarrow H(u,v) - \ln( count_p(u,v,w)!)$
-      \EndFor
-    \EndFor
-  \EndFor
-  \For {$j = 1$ to $n_c$}
-    \State \todo{XXX}
-  \EndFor
-  \end{algorithmic}
-\end{algorithm}
+%   \For {$u = 1$ to $N$}
+%     \For {$v = u$ to $N$}
+%       \State $H(u,v) \leftarrow H(u,v) + \ln((v-u + J_p)!) - \ln((J_p -1)!)$
+%       \For {$w = 1$ to $\|\Pa_X\|$}
+%         \State $H(u,v) \leftarrow H(u,v) - \ln( count_p(u,v,w)!)$
+%       \EndFor
+%     \EndFor
+%   \EndFor
+%   \For {$j = 1$ to $n_c$}
+%     \State \todo{XXX}
+%   \EndFor
+%   \end{algorithmic}
+% \end{algorithm}
 

### 2015-11-20 graph_housing_exp1_distr_3_5.tex
updated graphs

@@
 			        ytick={0,0.05,...,0.51},
+			        ylabel=probability density,
+			        y label style={at={(axis description cs:6.5,0.5)},rotate=180,anchor=north},
 			        yticklabel style={

### 2015-11-20 graph_wine_exp1_distr_5_11.tex
updated graphs

@@
 			colorbar style={
-			        ytick={0,0.05,...,0.5},
+			        ytick={0,0.05,...,0.51},
+			        ylabel=probability density,
+			        y label style={at={(axis description cs:6.5,0.5)},rotate=180,anchor=north},
 			        yticklabel style={

### 2015-11-20 table_autoMPG_1_old.tex
updated graphs

\scriptsize
\begin{tabular}{@{}cccc@{}}
    \toprule
    Var. & Optimal Bayesian & Heuristic Bayesian & MDL \\
    \midrule
    $A$ & \numlist[list-final-separator = {, }]{15.25; 17.65; 20.90; 25.65; 28.90} & \numlist[list-final-separator = {, }]{15.25; 17.65; 20.90; 25.65; 28.90} & - \\
    $C$ & \numlist[list-final-separator = {, }]{70.5; 93.5; 109.0; 159.5; 259.0; 284.5} & \numlist[list-final-separator = {, }]{70.5;93.5;109.0;159.5;259.0;284.5} & - \\
    $D$ & \numlist[list-final-separator = {, }]{71.5;99.0;127.0} & \numlist[list-final-separator = {, }]{71.5;99.0; 127.0} & - \\
    $E$ & \numlist[list-final-separator = {, }]{2115;2481;2960;3658} & \numlist[list-final-separator = {, }]{2115;2481;2960;3658} & - \\
    $F$ & \numlist[list-final-separator = {, }]{12.35;13.75;16.05;22.85} & \numlist[list-final-separator = {, }]{12.35;13.75;16.05;22.85} & - \\
    \addlinespace[0.5em]
    % Logl & \num{-10210} & \num{-10210} & \num{-11918} \\
    Logl & \num{-26.04} & \num{-26.04} & \num{-30.40} \\
    \bottomrule
\end{tabular}

### 2015-11-20 BN_discretizer_paper.tex
misc

--- 2015-11-20 BN_discretizer_paper.tex
@@
 
-\newcommand{\bigo}{\mathcal{O}} % NOTE(tim): if you prefer normal O change it here.
+\newcommand{\bigo}{O} % NOTE(tim): if you prefer normal O change it here.
 
@@
 Bayesian methods maximize the probability of the model given the data, $P(\textit{Model} \mid \textit{Data})$.
-An application of Bayes' rule and constant $P(\textit{Data})$ shows that this is equivalent to maximizing
-
-\begin{align}
-P(\textit{Model}) \cdot P(\textit{Data} \mid \textit{Model})\text{,}
-\end{align}
-
-\noindent
-where $P(\textit{Model})$ is a prior over models and ${P(\textit{Data} \mid \textit{Model})}$ is the data likelihood.
+An application of Bayes' rule and constant $P(\textit{Data})$ shows that this is equivalent to maximizing ${P(\textit{Model}) \cdot P(\textit{Data} \mid \textit{Model})}$, where $P(\textit{Model})$ is a prior over models and ${P(\textit{Data} \mid \textit{Model})}$ is the data likelihood.
 The data likelihood usually increases with the number of discretization intervals, as more intervals allow for richer representations.
@@
 Let $\cX$ be a continuous variable and let $\cx$ be a specific instance of $\cX$.
-A discretization policy $\Lambda_{\cX} = \curly{e_1 < e_2 < \ldots < e_{k-1}}$ for $\cX$ is a mapping from $\mathbb{R}$ to $\curly{1,2,3,\ldots,k}$ such that
+A discretization policy $\Lambda_{\cX} = \anglebrackets{e_1 < e_2 < \ldots < e_{k-1}}$ for $\cX$ is a mapping from $\mathbb{R}$ to $\curly{1,2,3,\ldots,k}$ such that
 
@@
 Thus, each edge $e_i = \paren{\cu_{j} + \cu_{{j+1}}}/2$ for some $j$.
-Two useful integer representation of $\Lambda_{\cX}$ can be written
+Two useful integer representations of $\Lambda_{\cX}$ can be written
 
@@
 \label{eq:disc_def}
-  \Lambda_{\cX} = \curly{\lambda_1 < \lambda_2  < \ldots < \lambda_k} \equiv \curly{\gamma_1 , \gamma_2  , \ldots , \gamma_k}\text{,}
+  \Lambda_{\cX} = \anglebrackets{\lambda_1 < \lambda_2  < \ldots < \lambda_k} \equiv \anglebrackets{\gamma_1 , \gamma_2  , \ldots , \gamma_k}\text{,}
 \end{equation}
@@
 
-This section describes experiments conducted to evaluate the proposed methods.
+This section describes experiments conducted to evaluate the Bayesian discretization method.
 All experiments were run on datasets from the publically available University of California, Irvine machine learning repository \citep{Lichman_2013}.
-Variables are labelled alphabetically in the order given on the dataset information webpage
+Variables are labeled alphabetically in the order given on the dataset information webpage.
 In the figures that follow, shaded nodes correspond to initially discrete variables and the subscripts indicate the number of discrete instantiations.
@@
 Two experiments were conducted on each dataset.
-The first experiment compares the performance of the optimal Bayesian discretization method, the heuristic Bayesian discretization method, and MDL on a known Bayesian network structure.
-The structure was obtained by prediscretizing each continuous variable into $k$ uniform-width intervals, where $k$ is the median number of instantiations of the discrete variables, and using the structure with the highest Bayesian score from one thousand runs of the K2 algorithm with random variable orderings.
+The first experiment compares the performance of the Bayesian and MDL discretization methods on a known Bayesian network structure.
+The structure was obtained by prediscretizing each continuous variable into $k$ uniform-width intervals, where $k$ is the median number of instantiations of the discrete variables, and using the structure with the highest Bayesian score from \num{1000} runs of the K2 algorithm with random variable orderings.
 The second experiment compares the same methods applied when simultaneously discretizing and learning network structure.
@@
 The discretizations are compared using the mean cross validated log-likelihood of the data $D$ given the graph structure $G$ and discretization policies $\discset$.
+Note that all log-likelihoods shown have been normalized by the number of data samples.
 The log-likelihood has two components,
@@
 
-The optimal discretization policy for MDL is found with dynamic programming in a similar manner as with the Bayesian method.
+The method for computing the MDL discretization policy is similar to the method for the Bayesian method.
 For a Bayesian network with a single continuous variable $\cX$, the MDL objective function is
@@
 
-The Bayesian approaches and the MDL discretization method were tested on the Auto MPG data using the network network shown in Figure~\ref{fig:auto_graph_1}.
-This structure was obtained by prediscretizing each continuous variable into five uniform-width intervals, where five is the median cardinality of the discrete variables, and then taking the structure with highest likelihood from one thousand runs of K2.
+The Bayesian and MDL discretization methods were tested on the Auto MPG data using the network shown in Figure~\ref{fig:auto_graph_1}.
+This structure was obtained by prediscretizing each continuous variable into five uniform-width intervals, where five is the median cardinality of the discrete variables, and then taking the structure with highest likelihood from \num{1000} runs of K2.
 
@@
 
-Table~\ref{table:auto_disc_table_1} lists the discretization edges and mean log-likelihoods under 10-fold cross validation of the discrete Bayesian network resulting from each discretization method.
-The results indicate that the heuristic Bayesian method produces exactly the same discretization policy as the optimal Bayesian method.
-The MDL method does not produce any discretization edges, assigning one continuous interval to each continuous variable, and produces the structure with the lowest score.
+Table~\ref{table:auto_disc_table_1} lists the discretization edges and mean log-likelihoods under \num{10}-fold cross validation of the discrete Bayesian network resulting from each discretization method.
+The MDL method does not produce any discretization edges, assigning one continuous interval to each continuous variable, and produces the structure with the lowest likelihood.
 The cause behind MDL's discretization policy is discussed in Section~\ref{subsec:discuss_exp}.
@@
     The last row lists the mean cross-validated log-likelihood; positive values are better.
-    The optimal and heuristic Bayesian discretization policies are identical and the MDL method does not produce any discretization edges.
+    The MDL method does not produce any discretization edges.
   }
@@
 
-Figure~\ref{fig:auto_exp1_distr_1_3} compares the Bayesian discretizaton policy for variables $A$ and $C$ with the original Auto MPG data.
-The black marks are the original Auto MPG samples.
-The color of a discretized region indicates the marginal probability of a sample from $P(A,C)$ being drawn from that region.
-As shown in the figure, the discretization edges obtained by the optimal Bayesian approach and the resulting marginalized probability match the raw data well.
+Figure~\ref{fig:auto_exp1_distr_1_3} shows the marginal probability density for variables $A$ and $C$ under the Bayesian discretization policy overlaid with the original Auto MPG data.
+The resulting probability density is a good match to the original data.
 
@@
     Comparison of the Bayesian discretization policy for variables $A$ and $C$ to the original Auto MPG data learned with a fixed network.
-    The marginal probabilities of discretized regions closely match the raw data.
+    The marginal probability density closely matches the data.
   }
@@
 Figure~\ref{fig:auto_graph_2} shows a learned Bayesian network structure and the corresponding numbers of intervals after discretization for each continuous variable.
-This result was obtained by running Algorithm~\ref{alg:structure_learn} fifty times using the optimal Bayesian method and choosing the structure with the highest likelihood.
+This result was obtained by running Algorithm~\ref{alg:structure_learn} fifty times using the Bayesian method and choosing the structure with the highest likelihood.
 
@@
   \input{graph_autocar_2}
-  \caption{The discrete-valued Bayesian network learned from the Auto MPG dataset}
+  \caption{The discrete-valued Bayesian network learned from the Auto MPG dataset using the Bayesian method.}
   \label{fig:auto_graph_2}
@@
 Figure~\ref{fig:auto_exp2_distr_1_3} compares the Bayesian discretizaton policy for variables $A$ and $C$ in the learned network with the original Auto MPG data.
-The color of a discretized region indicates the marginal probability of a sample from $P(A,C)$ being drawn from that region.
+The color of a discretized region indicates the marginal probability density of a sample from $P(A,C)$ being drawn from that region.
 Although there are fewer discretization edges for $A$ and $C$ in the learned network, the marginal distribution is still captured.
-Although the discretization result of the optimal Bayesian approach may vary according to the network structure, it still produces high-quality discretizations.
+The discretization policy will vary according as the network structure changes, and it still produces high-quality discretizations.
 
@@
   \caption{
-    Comparison of the optimal Bayesian discretization policy for variables $A$ and $C$ to the original Auto MPG data learned along with the network structure.
+    Comparison of the Bayesian discretization policy for variables $A$ and $C$ to the original Auto MPG data learned simultaneously with the network structure.
     Although the number of discretization edges is less than those in Figure~\ref{fig:auto_exp1_distr_1_3}, the probability distribution still closely matches the original data.
@@
 
-The Bayesian approaches and the MDL discretization method were tested on the Wine data using the network network shown in Figure~\ref{fig:wine_graph_1}.
-This structure was obtained by prediscretizing each continuous variable into three uniform-width intervals, where three is the median cardinality of the discrete variables, and then taking the structure with highest likelihood from one thousand runs of K2.
-
-Table~\ref{table:wine_disc_table_1} lists the discretization edges and mean log-likelihoods under 10-fold cross validation of the discrete Bayesian network resulting from each discretization method.
-The Bayesian methods outperform the MDL method in likelihood by a significant margin.
-The heuristic method discretizes the variables $G$, $H$, and $J$ into one fewer interval and the variable $M$ into one more interval than the optimal Bayesian approach, resulting in a slightly lower mean cross validated log likelihood.
-The overall performance of the heuristic method is still very high, and if runtime is the primary concern, the heuristic method can be considered the better approach.
-\tim{Do we need to list runtime too?}
-
-Notice that there are some discretization edges which appear in all three discretization methods, such as \num{1.42} and \num{2.35} for variable $C$ and \num{0.785} for variable $L$.
+The Bayesian and MDL discretization methods were tested on the Wine data using the network shown in Figure~\ref{fig:wine_graph_1}.
+This structure was obtained by prediscretizing each continuous variable into three uniform-width intervals, where three is the median cardinality of the discrete variables, and then taking the structure with highest likelihood from \num{1000} runs of K2.
+
+Table~\ref{table:wine_disc_table_1} lists the discretization edges and mean log-likelihoods under \num{10}-fold cross validation of the Bayesian network resulting from each discretization method.
+The Bayesian method outperforms the MDL method in likelihood by a significant margin.
+The MDL method creates significantly fewer discretization edges.
+% The heuristic method discretizes the variables $G$, $H$, and $J$ into one fewer interval and the variable $M$ into one more interval than the optimal Bayesian approach, resulting in a slightly lower mean cross validated log likelihood.
+% The overall performance of the heuristic method is still very high, and if runtime is the primary concern, the heuristic method can be considered the better approach.
+% \tim{Do we need to list runtime too?}
+
+Some discretization edges appear in all three discretization methods, such as \num{1.42} and \num{2.35} for variable $C$ and \num{0.785} for variable $L$.
 This indicates that MDL indeed can find some important discretization edges, but it is not sensitive enough to find more edges.
@@
   \scalebox{0.8}{\input{graph_wine_1}}
-  \caption{Structure from prediscretized K2 structure learning to compare the methods for Wine dataset}
+  \caption{Bayesian network structure obtained from running K2 on the prediscretized Wine dataset}
   \label{fig:wine_graph_1}
@@
   \caption{
-    Results from discretization of the Wine MPG dataset with fixed structure from Figure~\ref{fig:wine_graph_1}.
-    The first thirteen rows list the discretization edges for each continuous variable.
-    The last row lists the mean cross-validated log-likelihood; positive values are better.
-    The optimal Bayesian approach has the best discretization result in terms of likelihood, but the heuristic method obtains a similar result with nearly the same likelihood.
-    The MDL method produces discretization edges for more than half of the continuous variables but does not produce enough discretization intervals.
-    Some discretization edges appear in the results of all three methods.
+    Results from discretization of the Wine MPG dataset with fixed structure.
+    % The first thirteen rows list the discretization edges for each continuous variable.
+    % The last row lists the mean cross-validated log-likelihood; positive values are better.
+    % The optimal Bayesian approach has the best discretization result in terms of likelihood, but the heuristic method obtains a similar result with nearly the same likelihood.
+    % The MDL method produces discretization edges for more than half of the continuous variables but does not produce enough discretization intervals.
+    % Some discretization edges appear in the results of all three methods.
+    Bold discretization edges were identified by both methods.
   }
@@
 
-Figure~\ref{fig:wine_exp1_distr} compares the optimal Bayesian and MODL discretizaton policies for variables $E$ and $K$ with the original Wine data.
+Figure~\ref{fig:wine_exp1_distr} compares the Bayesian and MDL discretizaton policies for variables $E$ and $K$ with the original Wine data.
 The discretization edges \num{17.9} for $E$ and \num{34.6} for $K$ appear in both plots.
@@
   \input{graph_wine_exp1_distr}
-  \caption{Comparison of the discretization policies for variables $A$ and $C$ obtained using optimal Bayesian and MDL methods}
+  \caption{Comparison of the discretization policies for variables $A$ and $C$ obtained using the Bayesian and MDL methods}
   \label{fig:wine_exp1_distr}
@@
 
-Figure~\ref{fig:wine_exp2_distr} shows the discretization policy for variables $E$ and $K$ obtained with the optimal Bayesian method.
-The discretization edge $E = 17.9$ also appears in all discretization policies from the fixed network (Figure~\ref{fig:wine_exp1_distr}).
-This indicates that some discretization edges are robust against the network structure.
+Figure~\ref{fig:wine_exp2_distr} shows the discretization policy for variables $E$ and $K$ obtained with the Bayesian method.
+The discretization edge also $E = 17.9$ appears in both discretization policies from the fixed network (Figure~\ref{fig:wine_exp1_distr}).
+This suggests that discretization edges can be robust against network structure.
 Furthermore, the discretization edge at $E = 23.5$ present in the fixed-structure case is missing in the learned structure.
 This is caused by $E$ having twice as many parents in the learned network structure.
-The more parents a variable has, the less discretization intervals it will be able to support, as the set of statistics required to define the resulting distribution increases exponentially with the number of parents.
+The more parents a variable has, the less discretization intervals it can to support, as the set of statistics required to define the resulting distribution increases exponentially with the number of parents.
 
@@
   \scalebox{0.7}{\input{graph_wine_2}}
-  \caption{The discrete-valued Bayesian network learned from the Wine dataset using the optimal Bayesian method.}
+  \caption{The discrete-valued Bayesian network learned from the Wine dataset using the Bayesian method.}
   \label{fig:wine_graph_2}
@@
   \caption{
-    The discretization policy for variables $E$ and $K$ on the learned network in Figure~\ref{fig:wine_graph_2}.
+    The discretization policy for variables $E$ and $K$ on the learned network.
     The discretization edge $E = 17.9$ also appears in the policies for the fixed network.
-    This indicates that some discretization edges are robust against changing network structure.
   }
@@
 Only variables $D$ and $I$ are discrete-valued, with \num{2} and \num{9} instantiations, respectively.
-Variable $A$ is the only discrete variable and has three instantiations.
 Despite their being continuous, several variables in the Housing dataset possess many repeated values.
-The following experiments were conducted with an upper limit of three on the number of parents per variable to prevent memory issues with MDL.
+The following experiments were conducted with a maximum of three parents per variable to prevent running out of memory when running MDL.
 
@@
 
-The Bayesian network structure in Figure~\ref{fig:housing_graph_1} was obtained by prediscretizing each continuous variable into five uniform-width interval and then running the K2 algorithm one thousand times and choosing the network with the highest likelihood.
+The Bayesian network structure in Figure~\ref{fig:housing_graph_1} was obtained by prediscretizing each continuous variable into five uniform-width intervals and then running the K2 algorithm \num{1000} times and choosing the network with the highest likelihood.
 Table~\ref{table:housing_disc_table_1} shows the numbers of intervals after discretization for each continuous variables and the log-likelihood of the dataset based on each discretization method.
 MDL method does not produce any discretization edges for most variables.
-The heuristic Bayesian method produces far more discretization edges than the optimal Bayesian method due to repeated instances in the dataset.
-These numbers of intervals returned by the three methods illustrate the over-sensitive nature of the heuristic method and the under-sensitive nature of the MDL method.
-\tim{I am not sure we are using `sensitive' correctly. Sensitive to what? Perhaps `biased towards higher edge counts'?}
-The relative sensitivity of each algorithm will be discussed in Section~\ref{subsec:discuss_exp}.
-
-The heurstic method produces the discretization with the highest cross-validated log likelihood, but although the heuristic method leads to a higher number of intervals, its likelihood is not significantly better than the optimal Bayesian approach.
-This shows that the optimal Bayesian approach captures the most important discretization edges.
+% The heuristic Bayesian method produces far more discretization edges than the Bayesian method due to repeated instances in the dataset.
+% The numbers of intervals returned by the each method illustrate the over-sensitive nature of the heuristic method and the under-sensitive nature of the MDL method.
+% \tim{I am not sure we are using `sensitive' correctly. Sensitive to what? Perhaps `biased towards higher edge counts'?}
+The relative weighting of each method's objective function will be discussed in Section~\ref{subsec:discuss_exp}.
+
+% The heurstic method produces the discretization with the highest cross-validated log-likelihood; and although the heuristic method leads to a higher number of intervals, its likelihood is not significantly better than the Bayesian approach.
+% This demonstrates that the Bayesian approach captures the most important discretization edges.
 
@@
   \scalebox{0.8}{\input{graph_housing_1}}
-  \caption{Structure from prediscretized K2 structure learning to compare the methods for Housing dataset}
+  \caption{Bayesian network structure obtained from running K2 on the prediscretized Housing dataset}
   \label{fig:housing_graph_1}
@@
   \caption{
-    Discretization policy summary of the Housing dataset based on the fixed network structure shown in Figure~\ref{fig:housing_graph_1}.
-    The first twelve rows show the numbers of intervals after discretization by each method.
-    The last row is the mean cross-validated log-likelihood of the dataset based on the discretization results.
-    The heuristic method is over-sensitive \todo{to what?} and discretizes some variables into too many intervals.
-    The MDL method is less sensitive and on many cases does not produce any discretization intervals.
-    The optimal Bayesian approach produces a reasonable number of discretization edges.
-  }
-  \scalebox{1.0}{\input{table_housing_1.tex}}
+    Discretization policy summary of the Housing dataset based on the fixed network structure shown.
+    The first twelve rows show the numbers of intervals after discretization for each method.
+    The last row is the mean cross-validated log-likelihood based on each discretization result.
+    % The heuristic method is over-sensitive \todo{to what?} and discretizes some variables into too many intervals.
+    % The MDL method is less sensitive and on many cases does not produce any discretization intervals.
+    % The optimal Bayesian approach produces a reasonable number of discretization edges.
+  }
+  \input{table_housing_1.tex}
   \label{table:housing_disc_table_1}
@@
 
-Figures~\ref{fig:housing_exp1_distr_3_5} and \ref{fig:housing_exp1_distr_8_5} show the discretization policy learned using the optimal Bayesian approach on the fixed network shown in Figure~\ref{fig:housing_graph_1}.
-In Figure~\ref{fig:housing_exp1_distr_3_5}, the scatter points corresponding to the original dataset have been jittered, because there are many repeated values for variables $C$ and $E$.
+Figures~\ref{fig:housing_exp1_distr_3_5} and \ref{fig:housing_exp1_distr_8_5} show the discretization policy learned using the Bayesian approach on the fixed network shown in Figure~\ref{fig:housing_graph_1}.
+The scatter points in Figure~\ref{fig:housing_exp1_distr_3_5} were jittered to show the quantity of repeated values for variables $C$ and $E$.
 Each repeated point forms a single discrete region, thereby encouraging discretization.
@@
   \caption{
-    The discretization policies for variables $C$ and $E$ learned using the optimal Bayesian approach on the fixed network shown in Figure~\ref{fig:housing_graph_1}.
+    The discretization policies for variables $C$ and $E$ learned using the Bayesian approach on the fixed network.
     The scatter points were jittered to reveal the repeated values in the dataset.
@@
 Figure~\ref{fig:housing_graph_2} shows a learned Bayesian network structure and the corresponding numbers of intervals after discretization for each continuous variable.
-Variable $D$ is neighborless is both the learned and fixed networks.
+Variable $D$ is neighborless in both the learned and fixed networks.
 The continuous variables $C$, $E$, $J$ and $K$, which are all connected through $C$, have many discretization intervals.
 Typically, when discretizing a variable, the expected number of discretization intervals is close to the highest cardinality among variables in its Markov blanket.
-This naturally leads to clusters of variables with high numbers of discretization intervals.
+This naturally leads to clusters of variables with many discretization intervals.
 
@@
     The discretization policy for variables $C$ and $E$ on the learned network in Figure~\ref{fig:housing_graph_2}.
-    The high number of discretization edges are caused by the repeated values in variables $C$ and $E$.
+    The high number of discretization edges are caused by repeated values in $C$ and $E$.
   }
@@
   \input{graph_exp_discuss}
-  \caption{A simple Bayesian network that is used to demonstrate the sensitivity of the three methods}
+  \caption{A simple Bayesian network used to demonstrate the sensitivity of each method}
   \label{fig:exp_discuss}
@@
 
-To quantatively discuss the sensitivity of the three methods to the number of discretization intervals, consider the Bayesian network in Figure~\ref{fig:exp_discuss}, where $\cX$ is continuous and $P_1$ and $P_2$ are discrete.
-If $\Pa_{\cX} = \curly{P_1, P_2}$ and $D_{\cX} = \curly{1.0,2.0,3.0, \ldots n}$, then the corresponding objective functions for the three discretization methods are:
+To quantatively discuss the sensitivity of each methods to the number of discretization intervals, consider the Bayesian network in Figure~\ref{fig:exp_discuss}, where $\cX$ is continuous and $P_1$ and $P_2$ are discrete.
+If $\Pa_{\cX} = \curly{P_1, P_2}$ and $D_{\cX} = \curly{1.0,2.0,3.0, \ldots n}$, then the corresponding objective functions for the discretization methods are:
 
@@
   f_{\text{MDL}} & = \overbrace{Z_1 \cdot k + \ln(k) + \ln {{n +k - 1}\choose{k -1}} }^{\text{Penalty Term}}+   \overbrace{\rule{0pt}{1.35em} \ln(N) \cdot I(X^*, \Pa_X)}^{\text{Edge Position Term}} \\
-  f_{\text{Bayesian}} &= \overbrace{\rule{0pt}{1.85em}  Z_2 \cdot k + \sum_{i=1}^k \ln {{\gamma_i + J_P - 1}\choose{J_P -1}}}^{\text{Penalty Term}} + \overbrace{\sum^k_{i=1} \ln \left(   {{\gamma_i !}\over{n^{(P)}_{i,1}!
+  f_{\text{Bayesian}} &= \underbrace{{\vrule width0pt height0pt depth1.48em\relax}  Z_2 \cdot k + \sum_{i=1}^k \ln {{\gamma_i + J_P - 1}\choose{J_P -1}}}_{\text{Penalty Term}} + \underbrace{\sum^k_{i=1} \ln \left(   {{\gamma_i !}\over{n^{(P)}_{i,1}!
 n^{(P)}_{i,2}!
 \cdots n^{(P)}_{i,J_P}!
-}} \right) }^{\text{Edge Position Term}}\\
-  f_{\text{Heuristic}} &= \overbrace{Z_2 \cdot k + \sum_{i=1}^k \ln {{\gamma_i + J_{P_1} - 1}\choose{J_{P_1} -1}} + \sum_{i=1}^k \ln {{\gamma_i + J_{P_2} - 1}\choose{J_{P_2} -1}} }^{\text{Penalty Term}}+\\
-  & \overbrace{\sum^k_{i=1}  \left[ \ln \left(   {{\gamma_i !}\over{n^{(P_1)}_{i,1}!
+}} \right) }_{\text{Edge Position Term}}
+  % f_{\text{Heuristic}} &= \overbrace{Z_2 \cdot k + \sum_{i=1}^k \ln {{\gamma_i + J_{P_1} - 1}\choose{J_{P_1} -1}} + \sum_{i=1}^k \ln {{\gamma_i + J_{P_2} - 1}\choose{J_{P_2} -1}} }^{\text{Penalty Term}}+\\
+  % & \overbrace{\sum^k_{i=1}  \left[ \ln \left(   {{\gamma_i !}\over{n^{(P_1)}_{i,1}!
 n^{(P_1)}_{i,2}!
@@
 \noindent
-where $Z_1$ and $Z_2$ are constant over discretizations, $k$ is the number of discretization intervals, and $I\paren{A, B} = \sum_{a,b} \hat{P}(a,b) \ln\frac{\hat{P}(a,b)}{\hat{P}(a)\hat{P}(b)}$ is the mutual information based on estimated probability1ies.
-Note that the third term of $f_\text{MDL}$ had been approximated using $H(p)$ (see Equation~\ref{eqn:MDL}) in the original work by \cite{Friedman_1996} but here is written without that approximation.
+where $Z_1$ and $Z_2$ are constant over discretizations, $k$ is the number of discretization intervals, and $I\paren{A, B} = \sum_{a,b} \hat{P}(a,b) \ln\frac{\hat{P}(a,b)}{\hat{P}(a)\hat{P}(b)}$ is the mutual information based on estimated probabilities.
+Note that the third term of $f_\text{MDL}$ had been approximated using $H(p)$ (see Equation~\ref{eqn:MDL}) in the original work by \cite{Friedman_1996}, but here is written without that approximation.
 

### 2015-11-22 graph_housing_exp1_distr_3_5.tex
Change all plots from probability to probability density

--- 2015-11-17 graph_housing_exp1_distr_3_5.tex
@@
 			zmin=0.0, zmax=1.0,
-			xlabel=$C$,
-			ylabel=$E$,
+			xlabel=C,
+			ylabel=E,
 			colorbar,
-			point meta min=0, point meta max=0.50,
+			point meta min=0, point meta max=1.2,
 			colormap={}{ gray(0cm)=(1); gray(1cm)=(0);},
 			colorbar style={
-			        ytick={0,0.05,...,0.51},
+			        ytick={0,0.3,...,1.3},
+			        ylabel={probability density$ \times 10^{-1}$},
+			        y label style={at={(axis description cs:6.5,0.5)},rotate=180,anchor=north},
 			        yticklabel style={
@@
 
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.3850,0.1710) (7.2250,0.3850,0.1710) (7.2250,0.4405,0.1710) (0.4600,0.4405,0.1710)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.4405,0.1080) (7.2250,0.4405,0.1080) (7.2250,0.4860,0.1080) (0.4600,0.4860,0.1080)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.4860,0.0250) (7.2250,0.4860,0.0250) (7.2250,0.4910,0.0250) (0.4600,0.4910,0.0250)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.4910,0.0000) (7.2250,0.4910,0.0000) (7.2250,0.4960,0.0000) (0.4600,0.4960,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.4960,0.0795) (7.2250,0.4960,0.0795) (7.2250,0.5190,0.0795) (0.4600,0.5190,0.0795)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.5190,0.0000) (7.2250,0.5190,0.0000) (7.2250,0.5220,0.0000) (0.4600,0.5220,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.5220,0.0000) (7.2250,0.5220,0.0000) (7.2250,0.5280,0.0000) (0.4600,0.5280,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.5280,0.0035) (7.2250,0.5280,0.0035) (7.2250,0.5410,0.0035) (0.4600,0.5410,0.0035)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.5410,0.0000) (7.2250,0.5410,0.0000) (7.2250,0.5455,0.0000) (0.4600,0.5455,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.5455,0.0045) (7.2250,0.5455,0.0045) (7.2250,0.5910,0.0045) (0.4600,0.5910,0.0045)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.5910,0.0000) (7.2250,0.5910,0.0000) (7.2250,0.6390,0.0000) (0.4600,0.6390,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.6390,0.0185) (7.2250,0.6390,0.0185) (7.2250,0.6510,0.0185) (0.4600,0.6510,0.0185)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.6510,0.0000) (7.2250,0.6510,0.0000) (7.2250,0.8205,0.0000) (0.4600,0.8205,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.8205,0.0000) (7.2250,0.8205,0.0000) (7.2250,0.8710,0.0000) (0.4600,0.8710,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.3850,0.045544) (7.2250,0.3850,0.045544) (7.2250,0.4405,0.0455) (0.4600,0.4405,0.0455)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.4405,0.035087) (7.2250,0.4405,0.035087) (7.2250,0.4860,0.0351) (0.4600,0.4860,0.0351)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.4860,0.073910) (7.2250,0.4860,0.073910) (7.2250,0.4910,0.0739) (0.4600,0.4910,0.0739)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.4910,0.000000) (7.2250,0.4910,0.000000) (7.2250,0.4960,0.0000) (0.4600,0.4960,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.4960,0.051094) (7.2250,0.4960,0.051094) (7.2250,0.5190,0.0511) (0.4600,0.5190,0.0511)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.5190,0.000000) (7.2250,0.5190,0.000000) (7.2250,0.5220,0.0000) (0.4600,0.5220,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.5220,0.000000) (7.2250,0.5220,0.000000) (7.2250,0.5280,0.0000) (0.4600,0.5280,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.5280,0.003980) (7.2250,0.5280,0.003980) (7.2250,0.5410,0.0040) (0.4600,0.5410,0.0040)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.5410,0.000000) (7.2250,0.5410,0.000000) (7.2250,0.5455,0.0000) (0.4600,0.5455,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.5455,0.001462) (7.2250,0.5455,0.001462) (7.2250,0.5910,0.0015) (0.4600,0.5910,0.0015)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.5910,0.000000) (7.2250,0.5910,0.000000) (7.2250,0.6390,0.0000) (0.4600,0.6390,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.6390,0.022789) (7.2250,0.6390,0.022789) (7.2250,0.6510,0.0228) (0.4600,0.6510,0.0228)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.6510,0.000000) (7.2250,0.6510,0.000000) (7.2250,0.8205,0.0000) (0.4600,0.8205,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.8205,0.000000) (7.2250,0.8205,0.000000) (7.2250,0.8710,0.0000) (0.4600,0.8710,0.0000)};
 
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.3850,0.0000) (8.0050,0.3850,0.0000) (8.0050,0.4405,0.0000) (7.2250,0.4405,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.4405,0.0000) (8.0050,0.4405,0.0000) (8.0050,0.4860,0.0000) (7.2250,0.4860,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.4860,0.0000) (8.0050,0.4860,0.0000) (8.0050,0.4910,0.0000) (7.2250,0.4910,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.4910,0.0145) (8.0050,0.4910,0.0145) (8.0050,0.4960,0.0145) (7.2250,0.4960,0.0145)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.4960,0.0000) (8.0050,0.4960,0.0000) (8.0050,0.5190,0.0000) (7.2250,0.5190,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.5190,0.0000) (8.0050,0.5190,0.0000) (8.0050,0.5220,0.0000) (7.2250,0.5220,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.5220,0.0120) (8.0050,0.5220,0.0120) (8.0050,0.5280,0.0120) (7.2250,0.5280,0.0120)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.5280,0.0000) (8.0050,0.5280,0.0000) (8.0050,0.5410,0.0000) (7.2250,0.5410,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.5410,0.0000) (8.0050,0.5410,0.0000) (8.0050,0.5455,0.0000) (7.2250,0.5455,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.5455,0.0000) (8.0050,0.5455,0.0000) (8.0050,0.5910,0.0000) (7.2250,0.5910,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.5910,0.0000) (8.0050,0.5910,0.0000) (8.0050,0.6390,0.0000) (7.2250,0.6390,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.6390,0.0000) (8.0050,0.6390,0.0000) (8.0050,0.6510,0.0000) (7.2250,0.6510,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.6510,0.0000) (8.0050,0.6510,0.0000) (8.0050,0.8205,0.0000) (7.2250,0.8205,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.8205,0.0000) (8.0050,0.8205,0.0000) (8.0050,0.8710,0.0000) (7.2250,0.8710,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.3850,0.000000) (8.0050,0.3850,0.000000) (8.0050,0.4405,0.0000) (7.2250,0.4405,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.4405,0.000000) (8.0050,0.4405,0.000000) (8.0050,0.4860,0.0000) (7.2250,0.4860,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.4860,0.000000) (8.0050,0.4860,0.000000) (8.0050,0.4910,0.0000) (7.2250,0.4910,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.4910,0.371795) (8.0050,0.4910,0.371795) (8.0050,0.4960,0.3718) (7.2250,0.4960,0.3718)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.4960,0.000000) (8.0050,0.4960,0.000000) (8.0050,0.5190,0.0000) (7.2250,0.5190,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.5190,0.000000) (8.0050,0.5190,0.000000) (8.0050,0.5220,0.0000) (7.2250,0.5220,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.5220,0.256410) (8.0050,0.5220,0.256410) (8.0050,0.5280,0.2564) (7.2250,0.5280,0.2564)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.5280,0.000000) (8.0050,0.5280,0.000000) (8.0050,0.5410,0.0000) (7.2250,0.5410,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.5410,0.000000) (8.0050,0.5410,0.000000) (8.0050,0.5455,0.0000) (7.2250,0.5455,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.5455,0.000000) (8.0050,0.5455,0.000000) (8.0050,0.5910,0.0000) (7.2250,0.5910,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.5910,0.000000) (8.0050,0.5910,0.000000) (8.0050,0.6390,0.0000) (7.2250,0.6390,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.6390,0.000000) (8.0050,0.6390,0.000000) (8.0050,0.6510,0.0000) (7.2250,0.6510,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.6510,0.000000) (8.0050,0.6510,0.000000) (8.0050,0.8205,0.0000) (7.2250,0.8205,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.8205,0.000000) (8.0050,0.8205,0.000000) (8.0050,0.8710,0.0000) (7.2250,0.8710,0.0000)};
 
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.0050,0.3850,0.0000) (8.3500,0.3850,0.0000) (8.3500,0.4405,0.0000) (8.0050,0.4405,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.0050,0.4405,0.0000) (8.3500,0.4405,0.0000) (8.3500,0.4860,0.0000) (8.0050,0.4860,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.0050,0.4860,0.0000) (8.3500,0.4860,0.0000) (8.3500,0.4910,0.0000) (8.0050,0.4910,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.0050,0.4910,0.0000) (8.3500,0.4910,0.0000) (8.3500,0.4960,0.0000) (8.0050,0.4960,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.0050,0.4960,0.0000) (8.3500,0.4960,0.0000) (8.3500,0.5190,0.0000) (8.0050,0.5190,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.0050,0.5190,0.0000) (8.3500,0.5190,0.0000) (8.3500,0.5220,0.0000) (8.0050,0.5220,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.0050,0.5220,0.0000) (8.3500,0.5220,0.0000) (8.3500,0.5280,0.0000) (8.0050,0.5280,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.0050,0.5280,0.0455) (8.3500,0.5280,0.0455) (8.3500,0.5410,0.0455) (8.0050,0.5410,0.0455)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.0050,0.5410,0.0000) (8.3500,0.5410,0.0000) (8.3500,0.5455,0.0000) (8.0050,0.5455,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.0050,0.5455,0.0000) (8.3500,0.5455,0.0000) (8.3500,0.5910,0.0000) (8.0050,0.5910,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.0050,0.5910,0.0000) (8.3500,0.5910,0.0000) (8.3500,0.6390,0.0000) (8.0050,0.6390,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.0050,0.6390,0.0000) (8.3500,0.6390,0.0000) (8.3500,0.6510,0.0000) (8.0050,0.6510,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.0050,0.6510,0.0000) (8.3500,0.6510,0.0000) (8.3500,0.8205,0.0000) (8.0050,0.8205,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.0050,0.8205,0.0000) (8.3500,0.8205,0.0000) (8.3500,0.8710,0.0000) (8.0050,0.8710,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.0050,0.3850,0.000000) (8.3500,0.3850,0.000000) (8.3500,0.4405,0.0000) (8.0050,0.4405,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.0050,0.4405,0.000000) (8.3500,0.4405,0.000000) (8.3500,0.4860,0.0000) (8.0050,0.4860,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.0050,0.4860,0.000000) (8.3500,0.4860,0.000000) (8.3500,0.4910,0.0000) (8.0050,0.4910,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.0050,0.4910,0.000000) (8.3500,0.4910,0.000000) (8.3500,0.4960,0.0000) (8.0050,0.4960,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.0050,0.4960,0.000000) (8.3500,0.4960,0.000000) (8.3500,0.5190,0.0000) (8.0050,0.5190,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.0050,0.5190,0.000000) (8.3500,0.5190,0.000000) (8.3500,0.5220,0.0000) (8.0050,0.5220,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.0050,0.5220,0.000000) (8.3500,0.5220,0.000000) (8.3500,0.5280,0.0000) (8.0050,0.5280,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.0050,0.5280,1.014493) (8.3500,0.5280,1.014493) (8.3500,0.5410,1.0145) (8.0050,0.5410,1.0145)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.0050,0.5410,0.000000) (8.3500,0.5410,0.000000) (8.3500,0.5455,0.0000) (8.0050,0.5455,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.0050,0.5455,0.000000) (8.3500,0.5455,0.000000) (8.3500,0.5910,0.0000) (8.0050,0.5910,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.0050,0.5910,0.000000) (8.3500,0.5910,0.000000) (8.3500,0.6390,0.0000) (8.0050,0.6390,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.0050,0.6390,0.000000) (8.3500,0.6390,0.000000) (8.3500,0.6510,0.0000) (8.0050,0.6510,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.0050,0.6510,0.000000) (8.3500,0.6510,0.000000) (8.3500,0.8205,0.0000) (8.0050,0.8205,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.0050,0.8205,0.000000) (8.3500,0.8205,0.000000) (8.3500,0.8710,0.0000) (8.0050,0.8710,0.0000)};
 
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.3500,0.3850,0.0000) (9.1250,0.3850,0.0000) (9.1250,0.4405,0.0000) (8.3500,0.4405,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.3500,0.4405,0.0000) (9.1250,0.4405,0.0000) (9.1250,0.4860,0.0000) (8.3500,0.4860,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.3500,0.4860,0.0000) (9.1250,0.4860,0.0000) (9.1250,0.4910,0.0000) (8.3500,0.4910,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.3500,0.4910,0.0000) (9.1250,0.4910,0.0000) (9.1250,0.4960,0.0000) (8.3500,0.4960,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.3500,0.4960,0.0000) (9.1250,0.4960,0.0000) (9.1250,0.5190,0.0000) (8.3500,0.5190,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.3500,0.5190,0.0150) (9.1250,0.5190,0.0150) (9.1250,0.5220,0.0150) (8.3500,0.5220,0.0150)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.3500,0.5220,0.0000) (9.1250,0.5220,0.0000) (9.1250,0.5280,0.0000) (8.3500,0.5280,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.3500,0.5280,0.0000) (9.1250,0.5280,0.0000) (9.1250,0.5410,0.0000) (8.3500,0.5410,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.3500,0.5410,0.0000) (9.1250,0.5410,0.0000) (9.1250,0.5455,0.0000) (8.3500,0.5455,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.3500,0.5455,0.0000) (9.1250,0.5455,0.0000) (9.1250,0.5910,0.0000) (8.3500,0.5910,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.3500,0.5910,0.0000) (9.1250,0.5910,0.0000) (9.1250,0.6390,0.0000) (8.3500,0.6390,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.3500,0.6390,0.0000) (9.1250,0.6390,0.0000) (9.1250,0.6510,0.0000) (8.3500,0.6510,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.3500,0.6510,0.0000) (9.1250,0.6510,0.0000) (9.1250,0.8205,0.0000) (8.3500,0.8205,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.3500,0.8205,0.0000) (9.1250,0.8205,0.0000) (9.1250,0.8710,0.0000) (8.3500,0.8710,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.3500,0.3850,0.000000) (9.1250,0.3850,0.000000) (9.1250,0.4405,0.0000) (8.3500,0.4405,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.3500,0.4405,0.000000) (9.1250,0.4405,0.000000) (9.1250,0.4860,0.0000) (8.3500,0.4860,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.3500,0.4860,0.000000) (9.1250,0.4860,0.000000) (9.1250,0.4910,0.0000) (8.3500,0.4910,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.3500,0.4910,0.000000) (9.1250,0.4910,0.000000) (9.1250,0.4960,0.0000) (8.3500,0.4960,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.3500,0.4960,0.000000) (9.1250,0.4960,0.000000) (9.1250,0.5190,0.0000) (8.3500,0.5190,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.3500,0.5190,0.645161) (9.1250,0.5190,0.645161) (9.1250,0.5220,0.6452) (8.3500,0.5220,0.6452)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.3500,0.5220,0.000000) (9.1250,0.5220,0.000000) (9.1250,0.5280,0.0000) (8.3500,0.5280,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.3500,0.5280,0.000000) (9.1250,0.5280,0.000000) (9.1250,0.5410,0.0000) (8.3500,0.5410,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.3500,0.5410,0.000000) (9.1250,0.5410,0.000000) (9.1250,0.5455,0.0000) (8.3500,0.5455,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.3500,0.5455,0.000000) (9.1250,0.5455,0.000000) (9.1250,0.5910,0.0000) (8.3500,0.5910,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.3500,0.5910,0.000000) (9.1250,0.5910,0.000000) (9.1250,0.6390,0.0000) (8.3500,0.6390,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.3500,0.6390,0.000000) (9.1250,0.6390,0.000000) (9.1250,0.6510,0.0000) (8.3500,0.6510,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.3500,0.6510,0.000000) (9.1250,0.6510,0.000000) (9.1250,0.8205,0.0000) (8.3500,0.8205,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.3500,0.8205,0.000000) (9.1250,0.8205,0.000000) (9.1250,0.8710,0.0000) (8.3500,0.8710,0.0000)};
 
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.3850,0.0330) (16.5700,0.3850,0.0330) (16.5700,0.4405,0.0330) (9.1250,0.4405,0.0330)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.4405,0.0065) (16.5700,0.4405,0.0065) (16.5700,0.4860,0.0065) (9.1250,0.4860,0.0065)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.4860,0.0210) (16.5700,0.4860,0.0210) (16.5700,0.4910,0.0210) (9.1250,0.4910,0.0210)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.4910,0.0000) (16.5700,0.4910,0.0000) (16.5700,0.4960,0.0000) (9.1250,0.4960,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.4960,0.0000) (16.5700,0.4960,0.0000) (16.5700,0.5190,0.0000) (9.1250,0.5190,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.5190,0.0000) (16.5700,0.5190,0.0000) (16.5700,0.5220,0.0000) (9.1250,0.5220,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.5220,0.0000) (16.5700,0.5220,0.0000) (16.5700,0.5280,0.0000) (9.1250,0.5280,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.5280,0.0000) (16.5700,0.5280,0.0000) (16.5700,0.5410,0.0000) (9.1250,0.5410,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.5410,0.0220) (16.5700,0.5410,0.0220) (16.5700,0.5455,0.0220) (9.1250,0.5455,0.0220)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.5455,0.0490) (16.5700,0.5455,0.0490) (16.5700,0.5910,0.0490) (9.1250,0.5910,0.0490)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.5910,0.0000) (16.5700,0.5910,0.0000) (16.5700,0.6390,0.0000) (9.1250,0.6390,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.6390,0.0000) (16.5700,0.6390,0.0000) (16.5700,0.6510,0.0000) (9.1250,0.6510,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.6510,0.0000) (16.5700,0.6510,0.0000) (16.5700,0.8205,0.0000) (9.1250,0.8205,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.8205,0.0000) (16.5700,0.8205,0.0000) (16.5700,0.8710,0.0000) (9.1250,0.8710,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.3850,0.007986) (16.5700,0.3850,0.007986) (16.5700,0.4405,0.0080) (9.1250,0.4405,0.0080)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.4405,0.001919) (16.5700,0.4405,0.001919) (16.5700,0.4860,0.0019) (9.1250,0.4860,0.0019)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.4860,0.056414) (16.5700,0.4860,0.056414) (16.5700,0.4910,0.0564) (9.1250,0.4910,0.0564)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.4910,0.000000) (16.5700,0.4910,0.000000) (16.5700,0.4960,0.0000) (9.1250,0.4960,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.4960,0.000000) (16.5700,0.4960,0.000000) (16.5700,0.5190,0.0000) (9.1250,0.5190,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.5190,0.000000) (16.5700,0.5190,0.000000) (16.5700,0.5220,0.0000) (9.1250,0.5220,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.5220,0.000000) (16.5700,0.5220,0.000000) (16.5700,0.5280,0.0000) (9.1250,0.5280,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.5280,0.000000) (16.5700,0.5280,0.000000) (16.5700,0.5410,0.0000) (9.1250,0.5410,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.5410,0.065667) (16.5700,0.5410,0.065667) (16.5700,0.5455,0.0657) (9.1250,0.5455,0.0657)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.5455,0.014465) (16.5700,0.5455,0.014465) (16.5700,0.5910,0.0145) (9.1250,0.5910,0.0145)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.5910,0.000000) (16.5700,0.5910,0.000000) (16.5700,0.6390,0.0000) (9.1250,0.6390,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.6390,0.000000) (16.5700,0.6390,0.000000) (16.5700,0.6510,0.0000) (9.1250,0.6510,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.6510,0.000000) (16.5700,0.6510,0.000000) (16.5700,0.8205,0.0000) (9.1250,0.8205,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.8205,0.000000) (16.5700,0.8205,0.000000) (16.5700,0.8710,0.0000) (9.1250,0.8710,0.0000)};
 
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.3850,0.0000) (18.8400,0.3850,0.0000) (18.8400,0.4405,0.0000) (16.5700,0.4405,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.4405,0.0000) (18.8400,0.4405,0.0000) (18.8400,0.4860,0.0000) (16.5700,0.4860,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.4860,0.0000) (18.8400,0.4860,0.0000) (18.8400,0.4910,0.0000) (16.5700,0.4910,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.4910,0.0000) (18.8400,0.4910,0.0000) (18.8400,0.4960,0.0000) (16.5700,0.4960,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.4960,0.0000) (18.8400,0.4960,0.0000) (18.8400,0.5190,0.0000) (16.5700,0.5190,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.5190,0.0000) (18.8400,0.5190,0.0000) (18.8400,0.5220,0.0000) (16.5700,0.5220,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.5220,0.0000) (18.8400,0.5220,0.0000) (18.8400,0.5280,0.0000) (16.5700,0.5280,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.5280,0.0095) (18.8400,0.5280,0.0095) (18.8400,0.5410,0.0095) (16.5700,0.5410,0.0095)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.5410,0.0000) (18.8400,0.5410,0.0000) (18.8400,0.5455,0.0000) (16.5700,0.5455,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.5455,0.0295) (18.8400,0.5455,0.0295) (18.8400,0.5910,0.0295) (16.5700,0.5910,0.0295)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.5910,0.0260) (18.8400,0.5910,0.0260) (18.8400,0.6390,0.0260) (16.5700,0.6390,0.0260)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.6390,0.0000) (18.8400,0.6390,0.0000) (18.8400,0.6510,0.0000) (16.5700,0.6510,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.6510,0.1955) (18.8400,0.6510,0.1955) (18.8400,0.8205,0.1955) (16.5700,0.8205,0.1955)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.8205,0.0000) (18.8400,0.8205,0.0000) (18.8400,0.8710,0.0000) (16.5700,0.8710,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.3850,0.000000) (18.8400,0.3850,0.000000) (18.8400,0.4405,0.0000) (16.5700,0.4405,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.4405,0.000000) (18.8400,0.4405,0.000000) (18.8400,0.4860,0.0000) (16.5700,0.4860,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.4860,0.000000) (18.8400,0.4860,0.000000) (18.8400,0.4910,0.0000) (16.5700,0.4910,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.4910,0.000000) (18.8400,0.4910,0.000000) (18.8400,0.4960,0.0000) (16.5700,0.4960,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.4960,0.000000) (18.8400,0.4960,0.000000) (18.8400,0.5190,0.0000) (16.5700,0.5190,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.5190,0.000000) (18.8400,0.5190,0.000000) (18.8400,0.5220,0.0000) (16.5700,0.5220,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.5220,0.000000) (18.8400,0.5220,0.000000) (18.8400,0.5280,0.0000) (16.5700,0.5280,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.5280,0.032192) (18.8400,0.5280,0.032192) (18.8400,0.5410,0.0322) (16.5700,0.5410,0.0322)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.5410,0.000000) (18.8400,0.5410,0.000000) (18.8400,0.5455,0.0000) (16.5700,0.5455,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.5455,0.028562) (18.8400,0.5455,0.028562) (18.8400,0.5910,0.0286) (16.5700,0.5910,0.0286)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.5910,0.023862) (18.8400,0.5910,0.023862) (18.8400,0.6390,0.0239) (16.5700,0.6390,0.0239)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.6390,0.000000) (18.8400,0.6390,0.000000) (18.8400,0.6510,0.0000) (16.5700,0.6510,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.6510,0.050810) (18.8400,0.6510,0.050810) (18.8400,0.8205,0.0508) (16.5700,0.8205,0.0508)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.8205,0.000000) (18.8400,0.8205,0.000000) (18.8400,0.8710,0.0000) (16.5700,0.8710,0.0000)};
 
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.3850,0.0000) (20.7350,0.3850,0.0000) (20.7350,0.4405,0.0000) (18.8400,0.4405,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.4405,0.0000) (20.7350,0.4405,0.0000) (20.7350,0.4860,0.0000) (18.8400,0.4860,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.4860,0.0000) (20.7350,0.4860,0.0000) (20.7350,0.4910,0.0000) (18.8400,0.4910,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.4910,0.0000) (20.7350,0.4910,0.0000) (20.7350,0.4960,0.0000) (18.8400,0.4960,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.4960,0.0000) (20.7350,0.4960,0.0000) (20.7350,0.5190,0.0000) (18.8400,0.5190,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.5190,0.0000) (20.7350,0.5190,0.0000) (20.7350,0.5220,0.0000) (18.8400,0.5220,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.5220,0.0000) (20.7350,0.5220,0.0000) (20.7350,0.5280,0.0000) (18.8400,0.5280,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.5280,0.0000) (20.7350,0.5280,0.0000) (20.7350,0.5410,0.0000) (18.8400,0.5410,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.5410,0.0000) (20.7350,0.5410,0.0000) (20.7350,0.5455,0.0000) (18.8400,0.5455,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.5455,0.0000) (20.7350,0.5455,0.0000) (20.7350,0.5910,0.0000) (18.8400,0.5910,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.5910,0.0335) (20.7350,0.5910,0.0335) (20.7350,0.6390,0.0335) (18.8400,0.6390,0.0335)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.6390,0.0000) (20.7350,0.6390,0.0000) (20.7350,0.6510,0.0000) (18.8400,0.6510,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.6510,0.0000) (20.7350,0.6510,0.0000) (20.7350,0.8205,0.0000) (18.8400,0.8205,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.8205,0.0300) (20.7350,0.8205,0.0300) (20.7350,0.8710,0.0300) (18.8400,0.8710,0.0300)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.3850,0.000000) (20.7350,0.3850,0.000000) (20.7350,0.4405,0.0000) (18.8400,0.4405,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.4405,0.000000) (20.7350,0.4405,0.000000) (20.7350,0.4860,0.0000) (18.8400,0.4860,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.4860,0.000000) (20.7350,0.4860,0.000000) (20.7350,0.4910,0.0000) (18.8400,0.4910,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.4910,0.000000) (20.7350,0.4910,0.000000) (20.7350,0.4960,0.0000) (18.8400,0.4960,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.4960,0.000000) (20.7350,0.4960,0.000000) (20.7350,0.5190,0.0000) (18.8400,0.5190,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.5190,0.000000) (20.7350,0.5190,0.000000) (20.7350,0.5220,0.0000) (18.8400,0.5220,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.5220,0.000000) (20.7350,0.5220,0.000000) (20.7350,0.5280,0.0000) (18.8400,0.5280,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.5280,0.000000) (20.7350,0.5280,0.000000) (20.7350,0.5410,0.0000) (18.8400,0.5410,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.5410,0.000000) (20.7350,0.5410,0.000000) (20.7350,0.5455,0.0000) (18.8400,0.5455,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.5455,0.000000) (20.7350,0.5455,0.000000) (20.7350,0.5910,0.0000) (18.8400,0.5910,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.5910,0.036829) (20.7350,0.5910,0.036829) (20.7350,0.6390,0.0368) (18.8400,0.6390,0.0368)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.6390,0.000000) (20.7350,0.6390,0.000000) (20.7350,0.6510,0.0000) (18.8400,0.6510,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.6510,0.000000) (20.7350,0.6510,0.000000) (20.7350,0.8205,0.0000) (18.8400,0.8205,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.8205,0.031349) (20.7350,0.8205,0.031349) (20.7350,0.8710,0.0313) (18.8400,0.8710,0.0313)};
 
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.3850,0.0000) (27.7400,0.3850,0.0000) (27.7400,0.4405,0.0000) (20.7350,0.4405,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.4405,0.0000) (27.7400,0.4405,0.0000) (27.7400,0.4860,0.0000) (20.7350,0.4860,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.4860,0.0000) (27.7400,0.4860,0.0000) (27.7400,0.4910,0.0000) (20.7350,0.4910,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.4910,0.0000) (27.7400,0.4910,0.0000) (27.7400,0.4960,0.0000) (20.7350,0.4960,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.4960,0.0000) (27.7400,0.4960,0.0000) (27.7400,0.5190,0.0000) (20.7350,0.5190,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.5190,0.0000) (27.7400,0.5190,0.0000) (27.7400,0.5220,0.0000) (20.7350,0.5220,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.5220,0.0000) (27.7400,0.5220,0.0000) (27.7400,0.5280,0.0000) (20.7350,0.5280,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.5280,0.0000) (27.7400,0.5280,0.0000) (27.7400,0.5410,0.0000) (20.7350,0.5410,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.5410,0.0000) (27.7400,0.5410,0.0000) (27.7400,0.5455,0.0000) (20.7350,0.5455,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.5455,0.0160) (27.7400,0.5455,0.0160) (27.7400,0.5910,0.0160) (20.7350,0.5910,0.0160)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.5910,0.0315) (27.7400,0.5910,0.0315) (27.7400,0.6390,0.0315) (20.7350,0.6390,0.0315)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.6390,0.0000) (27.7400,0.6390,0.0000) (27.7400,0.6510,0.0000) (20.7350,0.6510,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.6510,0.0000) (27.7400,0.6510,0.0000) (27.7400,0.8205,0.0000) (20.7350,0.8205,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.8205,0.0000) (27.7400,0.8205,0.0000) (27.7400,0.8710,0.0000) (20.7350,0.8710,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.3850,0.000000) (27.7400,0.3850,0.000000) (27.7400,0.4405,0.0000) (20.7350,0.4405,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.4405,0.000000) (27.7400,0.4405,0.000000) (27.7400,0.4860,0.0000) (20.7350,0.4860,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.4860,0.000000) (27.7400,0.4860,0.000000) (27.7400,0.4910,0.0000) (20.7350,0.4910,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.4910,0.000000) (27.7400,0.4910,0.000000) (27.7400,0.4960,0.0000) (20.7350,0.4960,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.4960,0.000000) (27.7400,0.4960,0.000000) (27.7400,0.5190,0.0000) (20.7350,0.5190,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.5190,0.000000) (27.7400,0.5190,0.000000) (27.7400,0.5220,0.0000) (20.7350,0.5220,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.5220,0.000000) (27.7400,0.5220,0.000000) (27.7400,0.5280,0.0000) (20.7350,0.5280,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.5280,0.000000) (27.7400,0.5280,0.000000) (27.7400,0.5410,0.0000) (20.7350,0.5410,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.5410,0.000000) (27.7400,0.5410,0.000000) (27.7400,0.5455,0.0000) (20.7350,0.5455,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.5455,0.005020) (27.7400,0.5455,0.005020) (27.7400,0.5910,0.0050) (20.7350,0.5910,0.0050)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.5910,0.009368) (27.7400,0.5910,0.009368) (27.7400,0.6390,0.0094) (20.7350,0.6390,0.0094)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.6390,0.000000) (27.7400,0.6390,0.000000) (27.7400,0.6510,0.0000) (20.7350,0.6510,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.6510,0.000000) (27.7400,0.6510,0.000000) (27.7400,0.8205,0.0000) (20.7350,0.8205,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.8205,0.000000) (27.7400,0.8205,0.000000) (27.7400,0.8710,0.0000) (20.7350,0.8710,0.0000)};
 

### 2015-11-22 graph_housing_exp1_distr_8_5.tex
Change all plots from probability to probability density

@@
 			zmin=0.0, zmax=1.0,
-			xlabel=$H$,
-			ylabel=$E$,
+			xlabel=H,
+			ylabel=E,
 			colorbar,
-			point meta min=0, point meta max=0.5,
+			point meta min=0, point meta max=1.0,
 			colormap={}{ gray(0cm)=(1); gray(1cm)=(0);},
 			colorbar style={
-			        ytick={0,0.05,...,0.51},
+			        ytick={0,0.2,...,1.01},
+			        ylabel={probability density$ \times 10^{-1}$},
+			        y label style={at={(axis description cs:6.5,0.5)},rotate=180,anchor=north},
 			        yticklabel style={
@@
 
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.3850,0.0000) (1.9204,0.3850,0.0000) (1.9204,0.4405,0.0000) (1.1296,0.4405,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.4405,0.0000) (1.9204,0.4405,0.0000) (1.9204,0.4860,0.0000) (1.1296,0.4860,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.4860,0.0000) (1.9204,0.4860,0.0000) (1.9204,0.4910,0.0000) (1.1296,0.4910,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.4910,0.0000) (1.9204,0.4910,0.0000) (1.9204,0.4960,0.0000) (1.1296,0.4960,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.4960,0.0000) (1.9204,0.4960,0.0000) (1.9204,0.5190,0.0000) (1.1296,0.5190,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.5190,0.0000) (1.9204,0.5190,0.0000) (1.9204,0.5220,0.0000) (1.1296,0.5220,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.5220,0.0000) (1.9204,0.5220,0.0000) (1.9204,0.5280,0.0000) (1.1296,0.5280,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.5280,0.0000) (1.9204,0.5280,0.0000) (1.9204,0.5410,0.0000) (1.1296,0.5410,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.5410,0.0000) (1.9204,0.5410,0.0000) (1.9204,0.5455,0.0000) (1.1296,0.5455,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.5455,0.0025) (1.9204,0.5455,0.0025) (1.9204,0.5910,0.0025) (1.1296,0.5910,0.0025)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.5910,0.0425) (1.9204,0.5910,0.0425) (1.9204,0.6390,0.0425) (1.1296,0.6390,0.0425)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.6390,0.0065) (1.9204,0.6390,0.0065) (1.9204,0.6510,0.0065) (1.1296,0.6510,0.0065)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.6510,0.1040) (1.9204,0.6510,0.1040) (1.9204,0.8205,0.1040) (1.1296,0.8205,0.1040)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.8205,0.0300) (1.9204,0.8205,0.0300) (1.9204,0.8710,0.0300) (1.1296,0.8710,0.0300)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.3850,0.000000) (1.9204,0.3850,0.000000) (1.9204,0.4405,0.0000) (1.1296,0.4405,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.4405,0.000000) (1.9204,0.4405,0.000000) (1.9204,0.4860,0.0000) (1.1296,0.4860,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.4860,0.000000) (1.9204,0.4860,0.000000) (1.9204,0.4910,0.0000) (1.1296,0.4910,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.4910,0.000000) (1.9204,0.4910,0.000000) (1.9204,0.4960,0.0000) (1.1296,0.4960,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.4960,0.000000) (1.9204,0.4960,0.000000) (1.9204,0.5190,0.0000) (1.1296,0.5190,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.5190,0.000000) (1.9204,0.5190,0.000000) (1.9204,0.5220,0.0000) (1.1296,0.5220,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.5220,0.000000) (1.9204,0.5220,0.000000) (1.9204,0.5280,0.0000) (1.1296,0.5280,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.5280,0.000000) (1.9204,0.5280,0.000000) (1.9204,0.5410,0.0000) (1.1296,0.5410,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.5410,0.000000) (1.9204,0.5410,0.000000) (1.9204,0.5455,0.0000) (1.1296,0.5455,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.5455,0.006948) (1.9204,0.5455,0.006948) (1.9204,0.5910,0.0069) (1.1296,0.5910,0.0069)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.5910,0.111972) (1.9204,0.5910,0.111972) (1.9204,0.6390,0.1120) (1.1296,0.6390,0.1120)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.6390,0.068500) (1.9204,0.6390,0.068500) (1.9204,0.6510,0.0685) (1.1296,0.6510,0.0685)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.6510,0.077593) (1.9204,0.6510,0.077593) (1.9204,0.8205,0.0776) (1.1296,0.8205,0.0776)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.8205,0.075126) (1.9204,0.8205,0.075126) (1.9204,0.8710,0.0751) (1.1296,0.8710,0.0751)};
 
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.3850,0.0000) (2.5884,0.3850,0.0000) (2.5884,0.4405,0.0000) (1.9204,0.4405,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.4405,0.0000) (2.5884,0.4405,0.0000) (2.5884,0.4860,0.0000) (1.9204,0.4860,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.4860,0.0000) (2.5884,0.4860,0.0000) (2.5884,0.4910,0.0000) (1.9204,0.4910,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.4910,0.0000) (2.5884,0.4910,0.0000) (2.5884,0.4960,0.0000) (1.9204,0.4960,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.4960,0.0000) (2.5884,0.4960,0.0000) (2.5884,0.5190,0.0000) (1.9204,0.5190,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.5190,0.0085) (2.5884,0.5190,0.0085) (2.5884,0.5220,0.0085) (1.9204,0.5220,0.0085)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.5220,0.0000) (2.5884,0.5220,0.0000) (2.5884,0.5280,0.0000) (1.9204,0.5280,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.5280,0.0000) (2.5884,0.5280,0.0000) (2.5884,0.5410,0.0000) (1.9204,0.5410,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.5410,0.0025) (2.5884,0.5410,0.0025) (2.5884,0.5455,0.0025) (1.9204,0.5455,0.0025)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.5455,0.0580) (2.5884,0.5455,0.0580) (2.5884,0.5910,0.0580) (1.9204,0.5910,0.0580)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.5910,0.0485) (2.5884,0.5910,0.0485) (2.5884,0.6390,0.0485) (1.9204,0.6390,0.0485)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.6390,0.0120) (2.5884,0.6390,0.0120) (2.5884,0.6510,0.0120) (1.9204,0.6510,0.0120)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.6510,0.0665) (2.5884,0.6510,0.0665) (2.5884,0.8205,0.0665) (1.9204,0.8205,0.0665)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.8205,0.0000) (2.5884,0.8205,0.0000) (2.5884,0.8710,0.0000) (1.9204,0.8710,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.3850,0.000000) (2.5884,0.3850,0.000000) (2.5884,0.4405,0.0000) (1.9204,0.4405,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.4405,0.000000) (2.5884,0.4405,0.000000) (2.5884,0.4860,0.0000) (1.9204,0.4860,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.4860,0.000000) (2.5884,0.4860,0.000000) (2.5884,0.4910,0.0000) (1.9204,0.4910,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.4910,0.000000) (2.5884,0.4910,0.000000) (2.5884,0.4960,0.0000) (1.9204,0.4960,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.4960,0.000000) (2.5884,0.4960,0.000000) (2.5884,0.5190,0.0000) (1.9204,0.5190,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.5190,0.424152) (2.5884,0.5190,0.424152) (2.5884,0.5220,0.4242) (1.9204,0.5220,0.4242)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.5220,0.000000) (2.5884,0.5220,0.000000) (2.5884,0.5280,0.0000) (1.9204,0.5280,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.5280,0.000000) (2.5884,0.5280,0.000000) (2.5884,0.5410,0.0000) (1.9204,0.5410,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.5410,0.083167) (2.5884,0.5410,0.083167) (2.5884,0.5455,0.0832) (1.9204,0.5455,0.0832)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.5455,0.190827) (2.5884,0.5455,0.190827) (2.5884,0.5910,0.1908) (1.9204,0.5910,0.1908)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.5910,0.151260) (2.5884,0.5910,0.151260) (2.5884,0.6390,0.1513) (1.9204,0.6390,0.1513)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.6390,0.149701) (2.5884,0.6390,0.149701) (2.5884,0.6510,0.1497) (1.9204,0.6510,0.1497)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.6510,0.058732) (2.5884,0.6510,0.058732) (2.5884,0.8205,0.0587) (1.9204,0.8205,0.0587)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.8205,0.000000) (2.5884,0.8205,0.000000) (2.5884,0.8710,0.0000) (1.9204,0.8710,0.0000)};
 
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.3850,0.0000) (3.0793,0.3850,0.0000) (3.0793,0.4405,0.0000) (2.5884,0.4405,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.4405,0.0000) (3.0793,0.4405,0.0000) (3.0793,0.4860,0.0000) (2.5884,0.4860,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.4860,0.0115) (3.0793,0.4860,0.0115) (3.0793,0.4910,0.0115) (2.5884,0.4910,0.0115)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.4910,0.0000) (3.0793,0.4910,0.0000) (3.0793,0.4960,0.0000) (2.5884,0.4960,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.4960,0.0160) (3.0793,0.4960,0.0160) (3.0793,0.5190,0.0160) (2.5884,0.5190,0.0160)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.5190,0.0065) (3.0793,0.5190,0.0065) (3.0793,0.5220,0.0065) (2.5884,0.5220,0.0065)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.5220,0.0000) (3.0793,0.5220,0.0000) (3.0793,0.5280,0.0000) (2.5884,0.5280,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.5280,0.0000) (3.0793,0.5280,0.0000) (3.0793,0.5410,0.0000) (2.5884,0.5410,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.5410,0.0040) (3.0793,0.5410,0.0040) (3.0793,0.5455,0.0040) (2.5884,0.5455,0.0040)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.5455,0.0250) (3.0793,0.5455,0.0250) (3.0793,0.5910,0.0250) (2.5884,0.5910,0.0250)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.5910,0.0000) (3.0793,0.5910,0.0000) (3.0793,0.6390,0.0000) (2.5884,0.6390,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.6390,0.0000) (3.0793,0.6390,0.0000) (3.0793,0.6510,0.0000) (2.5884,0.6510,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.6510,0.0250) (3.0793,0.6510,0.0250) (3.0793,0.8205,0.0250) (2.5884,0.8205,0.0250)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.8205,0.0000) (3.0793,0.8205,0.0000) (3.0793,0.8710,0.0000) (2.5884,0.8710,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.3850,0.000000) (3.0793,0.3850,0.000000) (3.0793,0.4405,0.0000) (2.5884,0.4405,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.4405,0.000000) (3.0793,0.4405,0.000000) (3.0793,0.4860,0.0000) (2.5884,0.4860,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.4860,0.468479) (3.0793,0.4860,0.468479) (3.0793,0.4910,0.4685) (2.5884,0.4910,0.4685)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.4910,0.000000) (3.0793,0.4910,0.000000) (3.0793,0.4960,0.0000) (2.5884,0.4960,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.4960,0.141695) (3.0793,0.4960,0.141695) (3.0793,0.5190,0.1417) (2.5884,0.5190,0.1417)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.5190,0.441321) (3.0793,0.5190,0.441321) (3.0793,0.5220,0.4413) (2.5884,0.5220,0.4413)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.5220,0.000000) (3.0793,0.5220,0.000000) (3.0793,0.5280,0.0000) (2.5884,0.5280,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.5280,0.000000) (3.0793,0.5280,0.000000) (3.0793,0.5410,0.0000) (2.5884,0.5410,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.5410,0.181055) (3.0793,0.5410,0.181055) (3.0793,0.5455,0.1811) (2.5884,0.5455,0.1811)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.5455,0.111916) (3.0793,0.5455,0.111916) (3.0793,0.5910,0.1119) (2.5884,0.5910,0.1119)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.5910,0.000000) (3.0793,0.5910,0.000000) (3.0793,0.6390,0.0000) (2.5884,0.6390,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.6390,0.000000) (3.0793,0.6390,0.000000) (3.0793,0.6510,0.0000) (2.5884,0.6510,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.6510,0.030042) (3.0793,0.6510,0.030042) (3.0793,0.8205,0.0300) (2.5884,0.8205,0.0300)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.8205,0.000000) (3.0793,0.8205,0.000000) (3.0793,0.8710,0.0000) (2.5884,0.8710,0.0000)};
 
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.3850,0.0100) (4.4802,0.3850,0.0100) (4.4802,0.4405,0.0100) (3.0793,0.4405,0.0100)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.4405,0.0495) (4.4802,0.4405,0.0495) (4.4802,0.4860,0.0495) (3.0793,0.4860,0.0495)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.4860,0.0345) (4.4802,0.4860,0.0345) (4.4802,0.4910,0.0345) (3.0793,0.4910,0.0345)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.4910,0.0000) (4.4802,0.4910,0.0000) (4.4802,0.4960,0.0000) (3.0793,0.4960,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.4960,0.0425) (4.4802,0.4960,0.0425) (4.4802,0.5190,0.0425) (3.0793,0.5190,0.0425)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.5190,0.0000) (4.4802,0.5190,0.0000) (4.4802,0.5220,0.0000) (3.0793,0.5220,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.5220,0.0000) (4.4802,0.5220,0.0000) (4.4802,0.5280,0.0000) (3.0793,0.5280,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.5280,0.0525) (4.4802,0.5280,0.0525) (4.4802,0.5410,0.0525) (3.0793,0.5410,0.0525)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.5410,0.0155) (4.4802,0.5410,0.0155) (4.4802,0.5455,0.0155) (3.0793,0.5455,0.0155)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.5455,0.0135) (4.4802,0.5455,0.0135) (4.4802,0.5910,0.0135) (3.0793,0.5910,0.0135)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.5910,0.0000) (4.4802,0.5910,0.0000) (4.4802,0.6390,0.0000) (3.0793,0.6390,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.6390,0.0000) (4.4802,0.6390,0.0000) (4.4802,0.6510,0.0000) (3.0793,0.6510,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.6510,0.0000) (4.4802,0.6510,0.0000) (4.4802,0.8205,0.0000) (3.0793,0.8205,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.8205,0.0000) (4.4802,0.8205,0.0000) (4.4802,0.8710,0.0000) (3.0793,0.8710,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.3850,0.012861) (4.4802,0.3850,0.012861) (4.4802,0.4405,0.0129) (3.0793,0.4405,0.0129)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.4405,0.077655) (4.4802,0.4405,0.077655) (4.4802,0.4860,0.0777) (3.0793,0.4860,0.0777)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.4860,0.492523) (4.4802,0.4860,0.492523) (4.4802,0.4910,0.4925) (3.0793,0.4910,0.4925)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.4910,0.000000) (4.4802,0.4910,0.000000) (4.4802,0.4960,0.0000) (3.0793,0.4960,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.4960,0.131898) (4.4802,0.4960,0.131898) (4.4802,0.5190,0.1319) (3.0793,0.5190,0.1319)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.5190,0.000000) (4.4802,0.5190,0.000000) (4.4802,0.5220,0.0000) (3.0793,0.5220,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.5220,0.000000) (4.4802,0.5220,0.000000) (4.4802,0.5280,0.0000) (3.0793,0.5280,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.5280,0.288266) (4.4802,0.5280,0.288266) (4.4802,0.5410,0.2883) (3.0793,0.5410,0.2883)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.5410,0.245865) (4.4802,0.5410,0.245865) (4.4802,0.5455,0.2459) (3.0793,0.5455,0.2459)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.5455,0.021179) (4.4802,0.5455,0.021179) (4.4802,0.5910,0.0212) (3.0793,0.5910,0.0212)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.5910,0.000000) (4.4802,0.5910,0.000000) (4.4802,0.6390,0.0000) (3.0793,0.6390,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.6390,0.000000) (4.4802,0.6390,0.000000) (4.4802,0.6510,0.0000) (3.0793,0.6510,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.6510,0.000000) (4.4802,0.6510,0.000000) (4.4802,0.8205,0.0000) (3.0793,0.8205,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.8205,0.000000) (4.4802,0.8205,0.000000) (4.4802,0.8710,0.0000) (3.0793,0.8710,0.0000)};
 
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.3850,0.0080) (4.7503,0.3850,0.0080) (4.7503,0.4405,0.0080) (4.4802,0.4405,0.0080)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.4405,0.0035) (4.7503,0.4405,0.0035) (4.7503,0.4860,0.0035) (4.4802,0.4860,0.0035)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.4860,0.0000) (4.7503,0.4860,0.0000) (4.7503,0.4910,0.0000) (4.4802,0.4910,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.4910,0.0100) (4.7503,0.4910,0.0100) (4.7503,0.4960,0.0100) (4.4802,0.4960,0.0100)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.4960,0.0000) (4.7503,0.4960,0.0000) (4.7503,0.5190,0.0000) (4.4802,0.5190,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.5190,0.0000) (4.7503,0.5190,0.0000) (4.7503,0.5220,0.0000) (4.4802,0.5220,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.5220,0.0000) (4.7503,0.5220,0.0000) (4.7503,0.5280,0.0000) (4.4802,0.5280,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.5280,0.0060) (4.7503,0.5280,0.0060) (4.7503,0.5410,0.0060) (4.4802,0.5410,0.0060)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.5410,0.0000) (4.7503,0.5410,0.0000) (4.7503,0.5455,0.0000) (4.4802,0.5455,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.5455,0.0000) (4.7503,0.5455,0.0000) (4.7503,0.5910,0.0000) (4.4802,0.5910,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.5910,0.0000) (4.7503,0.5910,0.0000) (4.7503,0.6390,0.0000) (4.4802,0.6390,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.6390,0.0000) (4.7503,0.6390,0.0000) (4.7503,0.6510,0.0000) (4.4802,0.6510,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.6510,0.0000) (4.7503,0.6510,0.0000) (4.7503,0.8205,0.0000) (4.4802,0.8205,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.8205,0.0000) (4.7503,0.8205,0.0000) (4.7503,0.8710,0.0000) (4.4802,0.8710,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.3850,0.053387) (4.7503,0.3850,0.053387) (4.7503,0.4405,0.0534) (4.4802,0.4405,0.0534)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.4405,0.028490) (4.7503,0.4405,0.028490) (4.7503,0.4860,0.0285) (4.4802,0.4860,0.0285)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.4860,0.000000) (4.7503,0.4860,0.000000) (4.7503,0.4910,0.0000) (4.4802,0.4910,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.4910,0.740741) (4.7503,0.4910,0.740741) (4.7503,0.4960,0.7407) (4.4802,0.4960,0.7407)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.4960,0.000000) (4.7503,0.4960,0.000000) (4.7503,0.5190,0.0000) (4.4802,0.5190,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.5190,0.000000) (4.7503,0.5190,0.000000) (4.7503,0.5220,0.0000) (4.4802,0.5220,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.5220,0.000000) (4.7503,0.5220,0.000000) (4.7503,0.5280,0.0000) (4.4802,0.5280,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.5280,0.170940) (4.7503,0.5280,0.170940) (4.7503,0.5410,0.1709) (4.4802,0.5410,0.1709)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.5410,0.000000) (4.7503,0.5410,0.000000) (4.7503,0.5455,0.0000) (4.4802,0.5455,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.5455,0.000000) (4.7503,0.5455,0.000000) (4.7503,0.5910,0.0000) (4.4802,0.5910,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.5910,0.000000) (4.7503,0.5910,0.000000) (4.7503,0.6390,0.0000) (4.4802,0.6390,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.6390,0.000000) (4.7503,0.6390,0.000000) (4.7503,0.6510,0.0000) (4.4802,0.6510,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.6510,0.000000) (4.7503,0.6510,0.000000) (4.7503,0.8205,0.0000) (4.4802,0.8205,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.8205,0.000000) (4.7503,0.8205,0.000000) (4.7503,0.8710,0.0000) (4.4802,0.8710,0.0000)};
 
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.7503,0.3850,0.1860) (12.1265,0.3850,0.1860) (12.1265,0.4405,0.1860) (4.7503,0.4405,0.1860)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.7503,0.4405,0.0615) (12.1265,0.4405,0.0615) (12.1265,0.4860,0.0615) (4.7503,0.4860,0.0615)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.7503,0.4860,0.0000) (12.1265,0.4860,0.0000) (12.1265,0.4910,0.0000) (4.7503,0.4910,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.7503,0.4910,0.0045) (12.1265,0.4910,0.0045) (12.1265,0.4960,0.0045) (4.7503,0.4960,0.0045)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.7503,0.4960,0.0210) (12.1265,0.4960,0.0210) (12.1265,0.5190,0.0210) (4.7503,0.5190,0.0210)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.7503,0.5190,0.0000) (12.1265,0.5190,0.0000) (12.1265,0.5220,0.0000) (4.7503,0.5220,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.7503,0.5220,0.0120) (12.1265,0.5220,0.0120) (12.1265,0.5280,0.0120) (4.7503,0.5280,0.0120)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.7503,0.5280,0.0000) (12.1265,0.5280,0.0000) (12.1265,0.5410,0.0000) (4.7503,0.5410,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.7503,0.5410,0.0000) (12.1265,0.5410,0.0000) (12.1265,0.5455,0.0000) (4.7503,0.5455,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.7503,0.5455,0.0000) (12.1265,0.5455,0.0000) (12.1265,0.5910,0.0000) (4.7503,0.5910,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.7503,0.5910,0.0000) (12.1265,0.5910,0.0000) (12.1265,0.6390,0.0000) (4.7503,0.6390,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.7503,0.6390,0.0000) (12.1265,0.6390,0.0000) (12.1265,0.6510,0.0000) (4.7503,0.6510,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.7503,0.6510,0.0000) (12.1265,0.6510,0.0000) (12.1265,0.8205,0.0000) (4.7503,0.8205,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.7503,0.8205,0.0000) (12.1265,0.8205,0.0000) (12.1265,0.8710,0.0000) (4.7503,0.8710,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.7503,0.3850,0.045434) (12.1265,0.3850,0.045434) (12.1265,0.4405,0.0454) (4.7503,0.4405,0.0454)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.7503,0.4405,0.018324) (12.1265,0.4405,0.018324) (12.1265,0.4860,0.0183) (4.7503,0.4860,0.0183)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.7503,0.4860,0.000000) (12.1265,0.4860,0.000000) (12.1265,0.4910,0.0000) (4.7503,0.4910,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.7503,0.4910,0.012201) (12.1265,0.4910,0.012201) (12.1265,0.4960,0.0122) (4.7503,0.4960,0.0122)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.7503,0.4960,0.012378) (12.1265,0.4960,0.012378) (12.1265,0.5190,0.0124) (4.7503,0.5190,0.0124)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.7503,0.5190,0.000000) (12.1265,0.5190,0.000000) (12.1265,0.5220,0.0000) (4.7503,0.5220,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.7503,0.5220,0.027114) (12.1265,0.5220,0.027114) (12.1265,0.5280,0.0271) (4.7503,0.5280,0.0271)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.7503,0.5280,0.000000) (12.1265,0.5280,0.000000) (12.1265,0.5410,0.0000) (4.7503,0.5410,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.7503,0.5410,0.000000) (12.1265,0.5410,0.000000) (12.1265,0.5455,0.0000) (4.7503,0.5455,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.7503,0.5455,0.000000) (12.1265,0.5455,0.000000) (12.1265,0.5910,0.0000) (4.7503,0.5910,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.7503,0.5910,0.000000) (12.1265,0.5910,0.000000) (12.1265,0.6390,0.0000) (4.7503,0.6390,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.7503,0.6390,0.000000) (12.1265,0.6390,0.000000) (12.1265,0.6510,0.0000) (4.7503,0.6510,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.7503,0.6510,0.000000) (12.1265,0.6510,0.000000) (12.1265,0.8205,0.0000) (4.7503,0.8205,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.7503,0.8205,0.000000) (12.1265,0.8205,0.000000) (12.1265,0.8710,0.0000) (4.7503,0.8710,0.0000)};
 

### 2015-11-22 graph_housing_exp2_distr_3_5.tex
Change all plots from probability to probability density

--- 2015-11-17 graph_housing_exp2_distr_3_5.tex
@@
 			zmin=0.0, zmax=1.0,
-			xlabel=$C$,
-			ylabel=$E$,
+			xlabel=C,
+			ylabel=E,
 			colorbar,
-			point meta min=0, point meta max=0.5,
+			point meta min=0, point meta max=1.2,
 			colormap={}{ gray(0cm)=(1); gray(1cm)=(0);},
 			colorbar style={
-			        ytick={0,0.05,...,0.51},
+			        ytick={0,0.24,...,1.3},
+			        ylabel={probability density$ \times 10^{-1}$},
+			        y label style={at={(axis description cs:6.5,0.5)},rotate=180,anchor=north},
 			        yticklabel style={
@@
 
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.3850,0.1105) (3.8750,0.3850,0.1105) (3.8750,0.4460,0.1105) (0.4600,0.4460,0.1105)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.4460,0.0000) (3.8750,0.4460,0.0000) (3.8750,0.4485,0.0000) (0.4600,0.4485,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.4485,0.0000) (3.8750,0.4485,0.0000) (3.8750,0.4555,0.0000) (0.4600,0.4555,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.4555,0.0130) (3.8750,0.4555,0.0130) (3.8750,0.4620,0.0130) (0.4600,0.4620,0.0130)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.4620,0.0000) (3.8750,0.4620,0.0000) (3.8750,0.4705,0.0000) (0.4600,0.4705,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.4705,0.0285) (3.8750,0.4705,0.0285) (3.8750,0.4910,0.0285) (0.4600,0.4910,0.0285)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.4910,0.0000) (3.8750,0.4910,0.0000) (3.8750,0.4960,0.0000) (0.4600,0.4960,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.4960,0.0000) (3.8750,0.4960,0.0000) (3.8750,0.5015,0.0000) (0.4600,0.5015,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.5015,0.0000) (3.8750,0.5015,0.0000) (3.8750,0.5085,0.0000) (0.4600,0.5085,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.5085,0.0000) (3.8750,0.5085,0.0000) (3.8750,0.5165,0.0000) (0.4600,0.5165,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.5165,0.0025) (3.8750,0.5165,0.0025) (3.8750,0.5410,0.0025) (0.4600,0.5410,0.0025)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.5410,0.0000) (3.8750,0.5410,0.0000) (3.8750,0.5485,0.0000) (0.4600,0.5485,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.5485,0.0000) (3.8750,0.5485,0.0000) (3.8750,0.5775,0.0000) (0.4600,0.5775,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.5775,0.0000) (3.8750,0.5775,0.0000) (3.8750,0.6010,0.0000) (0.4600,0.6010,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.6010,0.0000) (3.8750,0.6010,0.0000) (3.8750,0.6070,0.0000) (0.4600,0.6070,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.6070,0.0000) (3.8750,0.6070,0.0000) (3.8750,0.6115,0.0000) (0.4600,0.6115,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.6115,0.0000) (3.8750,0.6115,0.0000) (3.8750,0.6190,0.0000) (0.4600,0.6190,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.6190,0.0000) (3.8750,0.6190,0.0000) (3.8750,0.6275,0.0000) (0.4600,0.6275,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.6275,0.0000) (3.8750,0.6275,0.0000) (3.8750,0.6390,0.0000) (0.4600,0.6390,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.6390,0.0000) (3.8750,0.6390,0.0000) (3.8750,0.6510,0.0000) (0.4600,0.6510,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.6510,0.0000) (3.8750,0.6510,0.0000) (3.8750,0.8205,0.0000) (0.4600,0.8205,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.8205,0.0000) (3.8750,0.8205,0.0000) (3.8750,0.8710,0.0000) (0.4600,0.8710,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.3850,0.053045) (3.8750,0.3850,0.053045) (3.8750,0.4460,0.0530) (0.4600,0.4460,0.0530)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.4460,0.000000) (3.8750,0.4460,0.000000) (3.8750,0.4485,0.0000) (0.4600,0.4485,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.4485,0.000000) (3.8750,0.4485,0.000000) (3.8750,0.4555,0.0000) (0.4600,0.4555,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.4555,0.058565) (3.8750,0.4555,0.058565) (3.8750,0.4620,0.0586) (0.4600,0.4620,0.0586)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.4620,0.000000) (3.8750,0.4620,0.000000) (3.8750,0.4705,0.0000) (0.4600,0.4705,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.4705,0.040710) (3.8750,0.4705,0.040710) (3.8750,0.4910,0.0407) (0.4600,0.4910,0.0407)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.4910,0.000000) (3.8750,0.4910,0.000000) (3.8750,0.4960,0.0000) (0.4600,0.4960,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.4960,0.000000) (3.8750,0.4960,0.000000) (3.8750,0.5015,0.0000) (0.4600,0.5015,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.5015,0.000000) (3.8750,0.5015,0.000000) (3.8750,0.5085,0.0000) (0.4600,0.5085,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.5085,0.000000) (3.8750,0.5085,0.000000) (3.8750,0.5165,0.0000) (0.4600,0.5165,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.5165,0.002988) (3.8750,0.5165,0.002988) (3.8750,0.5410,0.0030) (0.4600,0.5410,0.0030)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.5410,0.000000) (3.8750,0.5410,0.000000) (3.8750,0.5485,0.0000) (0.4600,0.5485,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.5485,0.000000) (3.8750,0.5485,0.000000) (3.8750,0.5775,0.0000) (0.4600,0.5775,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.5775,0.000000) (3.8750,0.5775,0.000000) (3.8750,0.6010,0.0000) (0.4600,0.6010,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.6010,0.000000) (3.8750,0.6010,0.000000) (3.8750,0.6070,0.0000) (0.4600,0.6070,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.6070,0.000000) (3.8750,0.6070,0.000000) (3.8750,0.6115,0.0000) (0.4600,0.6115,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.6115,0.000000) (3.8750,0.6115,0.000000) (3.8750,0.6190,0.0000) (0.4600,0.6190,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.6190,0.000000) (3.8750,0.6190,0.000000) (3.8750,0.6275,0.0000) (0.4600,0.6275,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.6275,0.000000) (3.8750,0.6275,0.000000) (3.8750,0.6390,0.0000) (0.4600,0.6390,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.6390,0.000000) (3.8750,0.6390,0.000000) (3.8750,0.6510,0.0000) (0.4600,0.6510,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.6510,0.000000) (3.8750,0.6510,0.000000) (3.8750,0.8205,0.0000) (0.4600,0.8205,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.8205,0.000000) (3.8750,0.8205,0.000000) (3.8750,0.8710,0.0000) (0.4600,0.8710,0.0000)};
 
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.3850,0.0000) (3.9850,0.3850,0.0000) (3.9850,0.4460,0.0000) (3.8750,0.4460,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.4460,0.0000) (3.9850,0.4460,0.0000) (3.9850,0.4485,0.0000) (3.8750,0.4485,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.4485,0.0000) (3.9850,0.4485,0.0000) (3.9850,0.4555,0.0000) (3.8750,0.4555,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.4555,0.0000) (3.9850,0.4555,0.0000) (3.9850,0.4620,0.0000) (3.8750,0.4620,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.4620,0.0000) (3.9850,0.4620,0.0000) (3.9850,0.4705,0.0000) (3.8750,0.4705,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.4705,0.0000) (3.9850,0.4705,0.0000) (3.9850,0.4910,0.0000) (3.8750,0.4910,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.4910,0.0000) (3.9850,0.4910,0.0000) (3.9850,0.4960,0.0000) (3.8750,0.4960,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.4960,0.0000) (3.9850,0.4960,0.0000) (3.9850,0.5015,0.0000) (3.8750,0.5015,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.5015,0.0000) (3.9850,0.5015,0.0000) (3.9850,0.5085,0.0000) (3.8750,0.5085,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.5085,0.0000) (3.9850,0.5085,0.0000) (3.9850,0.5165,0.0000) (3.8750,0.5165,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.5165,0.0000) (3.9850,0.5165,0.0000) (3.9850,0.5410,0.0000) (3.8750,0.5410,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.5410,0.0000) (3.9850,0.5410,0.0000) (3.9850,0.5485,0.0000) (3.8750,0.5485,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.5485,0.0035) (3.9850,0.5485,0.0035) (3.9850,0.5775,0.0035) (3.8750,0.5775,0.0035)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.5775,0.0000) (3.9850,0.5775,0.0000) (3.9850,0.6010,0.0000) (3.8750,0.6010,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.6010,0.0000) (3.9850,0.6010,0.0000) (3.9850,0.6070,0.0000) (3.8750,0.6070,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.6070,0.0000) (3.9850,0.6070,0.0000) (3.9850,0.6115,0.0000) (3.8750,0.6115,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.6115,0.0000) (3.9850,0.6115,0.0000) (3.9850,0.6190,0.0000) (3.8750,0.6190,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.6190,0.0000) (3.9850,0.6190,0.0000) (3.9850,0.6275,0.0000) (3.8750,0.6275,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.6275,0.0000) (3.9850,0.6275,0.0000) (3.9850,0.6390,0.0000) (3.8750,0.6390,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.6390,0.0225) (3.9850,0.6390,0.0225) (3.9850,0.6510,0.0225) (3.8750,0.6510,0.0225)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.6510,0.0000) (3.9850,0.6510,0.0000) (3.9850,0.8205,0.0000) (3.8750,0.8205,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.8205,0.0000) (3.9850,0.8205,0.0000) (3.9850,0.8710,0.0000) (3.8750,0.8710,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.3850,0.000000) (3.9850,0.3850,0.000000) (3.9850,0.4460,0.0000) (3.8750,0.4460,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.4460,0.000000) (3.9850,0.4460,0.000000) (3.9850,0.4485,0.0000) (3.8750,0.4485,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.4485,0.000000) (3.9850,0.4485,0.000000) (3.9850,0.4555,0.0000) (3.8750,0.4555,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.4555,0.000000) (3.9850,0.4555,0.000000) (3.9850,0.4620,0.0000) (3.8750,0.4620,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.4620,0.000000) (3.9850,0.4620,0.000000) (3.9850,0.4705,0.0000) (3.8750,0.4705,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.4705,0.000000) (3.9850,0.4705,0.000000) (3.9850,0.4910,0.0000) (3.8750,0.4910,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.4910,0.000000) (3.9850,0.4910,0.000000) (3.9850,0.4960,0.0000) (3.8750,0.4960,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.4960,0.000000) (3.9850,0.4960,0.000000) (3.9850,0.5015,0.0000) (3.8750,0.5015,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.5015,0.000000) (3.9850,0.5015,0.000000) (3.9850,0.5085,0.0000) (3.8750,0.5085,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.5085,0.000000) (3.9850,0.5085,0.000000) (3.9850,0.5165,0.0000) (3.8750,0.5165,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.5165,0.000000) (3.9850,0.5165,0.000000) (3.9850,0.5410,0.0000) (3.8750,0.5410,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.5410,0.000000) (3.9850,0.5410,0.000000) (3.9850,0.5485,0.0000) (3.8750,0.5485,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.5485,0.109718) (3.9850,0.5485,0.109718) (3.9850,0.5775,0.1097) (3.8750,0.5775,0.1097)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.5775,0.000000) (3.9850,0.5775,0.000000) (3.9850,0.6010,0.0000) (3.8750,0.6010,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.6010,0.000000) (3.9850,0.6010,0.000000) (3.9850,0.6070,0.0000) (3.8750,0.6070,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.6070,0.000000) (3.9850,0.6070,0.000000) (3.9850,0.6115,0.0000) (3.8750,0.6115,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.6115,0.000000) (3.9850,0.6115,0.000000) (3.9850,0.6190,0.0000) (3.8750,0.6190,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.6190,0.000000) (3.9850,0.6190,0.000000) (3.9850,0.6275,0.0000) (3.8750,0.6275,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.6275,0.000000) (3.9850,0.6275,0.000000) (3.9850,0.6390,0.0000) (3.8750,0.6390,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.6390,1.704545) (3.9850,0.6390,1.704545) (3.9850,0.6510,1.7045) (3.8750,0.6510,1.7045)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.6510,0.000000) (3.9850,0.6510,0.000000) (3.9850,0.8205,0.0000) (3.8750,0.8205,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.8205,0.000000) (3.9850,0.8205,0.000000) (3.9850,0.8710,0.0000) (3.8750,0.8710,0.0000)};
 
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.3850,0.0680) (6.1450,0.3850,0.0680) (6.1450,0.4460,0.0680) (3.9850,0.4460,0.0680)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.4460,0.0000) (6.1450,0.4460,0.0000) (6.1450,0.4485,0.0000) (3.9850,0.4485,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.4485,0.0210) (6.1450,0.4485,0.0210) (6.1450,0.4555,0.0210) (3.9850,0.4555,0.0210)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.4555,0.0000) (6.1450,0.4555,0.0000) (6.1450,0.4620,0.0000) (3.9850,0.4620,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.4620,0.0000) (6.1450,0.4620,0.0000) (6.1450,0.4705,0.0000) (3.9850,0.4705,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.4705,0.0000) (6.1450,0.4705,0.0000) (6.1450,0.4910,0.0000) (3.9850,0.4910,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.4910,0.0000) (6.1450,0.4910,0.0000) (6.1450,0.4960,0.0000) (3.9850,0.4960,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.4960,0.0095) (6.1450,0.4960,0.0095) (6.1450,0.5015,0.0095) (3.9850,0.5015,0.0095)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.5015,0.0000) (6.1450,0.5015,0.0000) (6.1450,0.5085,0.0000) (3.9850,0.5085,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.5085,0.0300) (6.1450,0.5085,0.0300) (6.1450,0.5165,0.0300) (3.9850,0.5165,0.0300)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.5165,0.0000) (6.1450,0.5165,0.0000) (6.1450,0.5410,0.0000) (3.9850,0.5410,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.5410,0.0000) (6.1450,0.5410,0.0000) (6.1450,0.5485,0.0000) (3.9850,0.5485,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.5485,0.0000) (6.1450,0.5485,0.0000) (6.1450,0.5775,0.0000) (3.9850,0.5775,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.5775,0.0000) (6.1450,0.5775,0.0000) (6.1450,0.6010,0.0000) (3.9850,0.6010,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.6010,0.0000) (6.1450,0.6010,0.0000) (6.1450,0.6070,0.0000) (3.9850,0.6070,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.6070,0.0000) (6.1450,0.6070,0.0000) (6.1450,0.6115,0.0000) (3.9850,0.6115,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.6115,0.0000) (6.1450,0.6115,0.0000) (6.1450,0.6190,0.0000) (3.9850,0.6190,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.6190,0.0000) (6.1450,0.6190,0.0000) (6.1450,0.6275,0.0000) (3.9850,0.6275,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.6275,0.0000) (6.1450,0.6275,0.0000) (6.1450,0.6390,0.0000) (3.9850,0.6390,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.6390,0.0000) (6.1450,0.6390,0.0000) (6.1450,0.6510,0.0000) (3.9850,0.6510,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.6510,0.0000) (6.1450,0.6510,0.0000) (6.1450,0.8205,0.0000) (3.9850,0.8205,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.8205,0.0000) (6.1450,0.8205,0.0000) (6.1450,0.8710,0.0000) (3.9850,0.8710,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.3850,0.051609) (6.1450,0.3850,0.051609) (6.1450,0.4460,0.0516) (3.9850,0.4460,0.0516)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.4460,0.000000) (6.1450,0.4460,0.000000) (6.1450,0.4485,0.0000) (3.9850,0.4485,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.4485,0.138889) (6.1450,0.4485,0.138889) (6.1450,0.4555,0.1389) (3.9850,0.4555,0.1389)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.4555,0.000000) (6.1450,0.4555,0.000000) (6.1450,0.4620,0.0000) (3.9850,0.4620,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.4620,0.000000) (6.1450,0.4620,0.000000) (6.1450,0.4705,0.0000) (3.9850,0.4705,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.4705,0.000000) (6.1450,0.4705,0.000000) (6.1450,0.4910,0.0000) (3.9850,0.4910,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.4910,0.000000) (6.1450,0.4910,0.000000) (6.1450,0.4960,0.0000) (3.9850,0.4960,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.4960,0.079966) (6.1450,0.4960,0.079966) (6.1450,0.5015,0.0800) (3.9850,0.5015,0.0800)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.5015,0.000000) (6.1450,0.5015,0.000000) (6.1450,0.5085,0.0000) (3.9850,0.5085,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.5085,0.173611) (6.1450,0.5085,0.173611) (6.1450,0.5165,0.1736) (3.9850,0.5165,0.1736)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.5165,0.000000) (6.1450,0.5165,0.000000) (6.1450,0.5410,0.0000) (3.9850,0.5410,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.5410,0.000000) (6.1450,0.5410,0.000000) (6.1450,0.5485,0.0000) (3.9850,0.5485,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.5485,0.000000) (6.1450,0.5485,0.000000) (6.1450,0.5775,0.0000) (3.9850,0.5775,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.5775,0.000000) (6.1450,0.5775,0.000000) (6.1450,0.6010,0.0000) (3.9850,0.6010,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.6010,0.000000) (6.1450,0.6010,0.000000) (6.1450,0.6070,0.0000) (3.9850,0.6070,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.6070,0.000000) (6.1450,0.6070,0.000000) (6.1450,0.6115,0.0000) (3.9850,0.6115,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.6115,0.000000) (6.1450,0.6115,0.000000) (6.1450,0.6190,0.0000) (3.9850,0.6190,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.6190,0.000000) (6.1450,0.6190,0.000000) (6.1450,0.6275,0.0000) (3.9850,0.6275,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.6275,0.000000) (6.1450,0.6275,0.000000) (6.1450,0.6390,0.0000) (3.9850,0.6390,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.6390,0.000000) (6.1450,0.6390,0.000000) (6.1450,0.6510,0.0000) (3.9850,0.6510,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.6510,0.000000) (6.1450,0.6510,0.000000) (6.1450,0.8205,0.0000) (3.9850,0.8205,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.8205,0.000000) (6.1450,0.8205,0.000000) (6.1450,0.8710,0.0000) (3.9850,0.8710,0.0000)};
 
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.1450,0.3850,0.0000) (6.3050,0.3850,0.0000) (6.3050,0.4460,0.0000) (6.1450,0.4460,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.1450,0.4460,0.0000) (6.3050,0.4460,0.0000) (6.3050,0.4485,0.0000) (6.1450,0.4485,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.1450,0.4485,0.0000) (6.3050,0.4485,0.0000) (6.3050,0.4555,0.0000) (6.1450,0.4555,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.1450,0.4555,0.0000) (6.3050,0.4555,0.0000) (6.3050,0.4620,0.0000) (6.1450,0.4620,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.1450,0.4620,0.0000) (6.3050,0.4620,0.0000) (6.3050,0.4705,0.0000) (6.1450,0.4705,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.1450,0.4705,0.0000) (6.3050,0.4705,0.0000) (6.3050,0.4910,0.0000) (6.1450,0.4910,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.1450,0.4910,0.0000) (6.3050,0.4910,0.0000) (6.3050,0.4960,0.0000) (6.1450,0.4960,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.1450,0.4960,0.0000) (6.3050,0.4960,0.0000) (6.3050,0.5015,0.0000) (6.1450,0.5015,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.1450,0.5015,0.0410) (6.3050,0.5015,0.0410) (6.3050,0.5085,0.0410) (6.1450,0.5085,0.0410)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.1450,0.5085,0.0000) (6.3050,0.5085,0.0000) (6.3050,0.5165,0.0000) (6.1450,0.5165,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.1450,0.5165,0.0000) (6.3050,0.5165,0.0000) (6.3050,0.5410,0.0000) (6.1450,0.5410,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.1450,0.5410,0.0000) (6.3050,0.5410,0.0000) (6.3050,0.5485,0.0000) (6.1450,0.5485,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.1450,0.5485,0.0000) (6.3050,0.5485,0.0000) (6.3050,0.5775,0.0000) (6.1450,0.5775,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.1450,0.5775,0.0000) (6.3050,0.5775,0.0000) (6.3050,0.6010,0.0000) (6.1450,0.6010,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.1450,0.6010,0.0000) (6.3050,0.6010,0.0000) (6.3050,0.6070,0.0000) (6.1450,0.6070,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.1450,0.6070,0.0000) (6.3050,0.6070,0.0000) (6.3050,0.6115,0.0000) (6.1450,0.6115,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.1450,0.6115,0.0000) (6.3050,0.6115,0.0000) (6.3050,0.6190,0.0000) (6.1450,0.6190,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.1450,0.6190,0.0000) (6.3050,0.6190,0.0000) (6.3050,0.6275,0.0000) (6.1450,0.6275,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.1450,0.6275,0.0000) (6.3050,0.6275,0.0000) (6.3050,0.6390,0.0000) (6.1450,0.6390,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.1450,0.6390,0.0000) (6.3050,0.6390,0.0000) (6.3050,0.6510,0.0000) (6.1450,0.6510,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.1450,0.6510,0.0000) (6.3050,0.6510,0.0000) (6.3050,0.8205,0.0000) (6.1450,0.8205,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.1450,0.8205,0.0000) (6.3050,0.8205,0.0000) (6.3050,0.8710,0.0000) (6.1450,0.8710,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.1450,0.3850,0.000000) (6.3050,0.3850,0.000000) (6.3050,0.4460,0.0000) (6.1450,0.4460,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.1450,0.4460,0.000000) (6.3050,0.4460,0.000000) (6.3050,0.4485,0.0000) (6.1450,0.4485,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.1450,0.4485,0.000000) (6.3050,0.4485,0.000000) (6.3050,0.4555,0.0000) (6.1450,0.4555,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.1450,0.4555,0.000000) (6.3050,0.4555,0.000000) (6.3050,0.4620,0.0000) (6.1450,0.4620,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.1450,0.4620,0.000000) (6.3050,0.4620,0.000000) (6.3050,0.4705,0.0000) (6.1450,0.4705,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.1450,0.4705,0.000000) (6.3050,0.4705,0.000000) (6.3050,0.4910,0.0000) (6.1450,0.4910,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.1450,0.4910,0.000000) (6.3050,0.4910,0.000000) (6.3050,0.4960,0.0000) (6.1450,0.4960,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.1450,0.4960,0.000000) (6.3050,0.4960,0.000000) (6.3050,0.5015,0.0000) (6.1450,0.5015,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.1450,0.5015,3.660714) (6.3050,0.5015,3.660714) (6.3050,0.5085,3.6607) (6.1450,0.5085,3.6607)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.1450,0.5085,0.000000) (6.3050,0.5085,0.000000) (6.3050,0.5165,0.0000) (6.1450,0.5165,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.1450,0.5165,0.000000) (6.3050,0.5165,0.000000) (6.3050,0.5410,0.0000) (6.1450,0.5410,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.1450,0.5410,0.000000) (6.3050,0.5410,0.000000) (6.3050,0.5485,0.0000) (6.1450,0.5485,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.1450,0.5485,0.000000) (6.3050,0.5485,0.000000) (6.3050,0.5775,0.0000) (6.1450,0.5775,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.1450,0.5775,0.000000) (6.3050,0.5775,0.000000) (6.3050,0.6010,0.0000) (6.1450,0.6010,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.1450,0.6010,0.000000) (6.3050,0.6010,0.000000) (6.3050,0.6070,0.0000) (6.1450,0.6070,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.1450,0.6070,0.000000) (6.3050,0.6070,0.000000) (6.3050,0.6115,0.0000) (6.1450,0.6115,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.1450,0.6115,0.000000) (6.3050,0.6115,0.000000) (6.3050,0.6190,0.0000) (6.1450,0.6190,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.1450,0.6190,0.000000) (6.3050,0.6190,0.000000) (6.3050,0.6275,0.0000) (6.1450,0.6275,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.1450,0.6275,0.000000) (6.3050,0.6275,0.000000) (6.3050,0.6390,0.0000) (6.1450,0.6390,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.1450,0.6390,0.000000) (6.3050,0.6390,0.000000) (6.3050,0.6510,0.0000) (6.1450,0.6510,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.1450,0.6510,0.000000) (6.3050,0.6510,0.000000) (6.3050,0.8205,0.0000) (6.1450,0.8205,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.1450,0.8205,0.000000) (6.3050,0.8205,0.000000) (6.3050,0.8710,0.0000) (6.1450,0.8710,0.0000)};
 
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.3050,0.3850,0.0000) (7.2250,0.3850,0.0000) (7.2250,0.4460,0.0000) (6.3050,0.4460,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.3050,0.4460,0.0285) (7.2250,0.4460,0.0285) (7.2250,0.4485,0.0285) (6.3050,0.4485,0.0285)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.3050,0.4485,0.0000) (7.2250,0.4485,0.0000) (7.2250,0.4555,0.0000) (6.3050,0.4555,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.3050,0.4555,0.0000) (7.2250,0.4555,0.0000) (7.2250,0.4620,0.0000) (6.3050,0.4620,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.3050,0.4620,0.0165) (7.2250,0.4620,0.0165) (7.2250,0.4705,0.0165) (6.3050,0.4705,0.0165)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.3050,0.4705,0.0000) (7.2250,0.4705,0.0000) (7.2250,0.4910,0.0000) (6.3050,0.4910,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.3050,0.4910,0.0000) (7.2250,0.4910,0.0000) (7.2250,0.4960,0.0000) (6.3050,0.4960,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.3050,0.4960,0.0000) (7.2250,0.4960,0.0000) (7.2250,0.5015,0.0000) (6.3050,0.5015,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.3050,0.5015,0.0000) (7.2250,0.5015,0.0000) (7.2250,0.5085,0.0000) (6.3050,0.5085,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.3050,0.5085,0.0000) (7.2250,0.5085,0.0000) (7.2250,0.5165,0.0000) (6.3050,0.5165,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.3050,0.5165,0.0000) (7.2250,0.5165,0.0000) (7.2250,0.5410,0.0000) (6.3050,0.5410,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.3050,0.5410,0.0000) (7.2250,0.5410,0.0000) (7.2250,0.5485,0.0000) (6.3050,0.5485,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.3050,0.5485,0.0000) (7.2250,0.5485,0.0000) (7.2250,0.5775,0.0000) (6.3050,0.5775,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.3050,0.5775,0.0000) (7.2250,0.5775,0.0000) (7.2250,0.6010,0.0000) (6.3050,0.6010,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.3050,0.6010,0.0000) (7.2250,0.6010,0.0000) (7.2250,0.6070,0.0000) (6.3050,0.6070,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.3050,0.6070,0.0000) (7.2250,0.6070,0.0000) (7.2250,0.6115,0.0000) (6.3050,0.6115,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.3050,0.6115,0.0000) (7.2250,0.6115,0.0000) (7.2250,0.6190,0.0000) (6.3050,0.6190,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.3050,0.6190,0.0000) (7.2250,0.6190,0.0000) (7.2250,0.6275,0.0000) (6.3050,0.6275,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.3050,0.6275,0.0000) (7.2250,0.6275,0.0000) (7.2250,0.6390,0.0000) (6.3050,0.6390,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.3050,0.6390,0.0000) (7.2250,0.6390,0.0000) (7.2250,0.6510,0.0000) (6.3050,0.6510,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.3050,0.6510,0.0000) (7.2250,0.6510,0.0000) (7.2250,0.8205,0.0000) (6.3050,0.8205,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.3050,0.8205,0.0000) (7.2250,0.8205,0.0000) (7.2250,0.8710,0.0000) (6.3050,0.8710,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.3050,0.3850,0.000000) (7.2250,0.3850,0.000000) (7.2250,0.4460,0.0000) (6.3050,0.4460,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.3050,0.4460,1.239130) (7.2250,0.4460,1.239130) (7.2250,0.4485,1.2391) (6.3050,0.4485,1.2391)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.3050,0.4485,0.000000) (7.2250,0.4485,0.000000) (7.2250,0.4555,0.0000) (6.3050,0.4555,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.3050,0.4555,0.000000) (7.2250,0.4555,0.000000) (7.2250,0.4620,0.0000) (6.3050,0.4620,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.3050,0.4620,0.210997) (7.2250,0.4620,0.210997) (7.2250,0.4705,0.2110) (6.3050,0.4705,0.2110)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.3050,0.4705,0.000000) (7.2250,0.4705,0.000000) (7.2250,0.4910,0.0000) (6.3050,0.4910,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.3050,0.4910,0.000000) (7.2250,0.4910,0.000000) (7.2250,0.4960,0.0000) (6.3050,0.4960,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.3050,0.4960,0.000000) (7.2250,0.4960,0.000000) (7.2250,0.5015,0.0000) (6.3050,0.5015,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.3050,0.5015,0.000000) (7.2250,0.5015,0.000000) (7.2250,0.5085,0.0000) (6.3050,0.5085,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.3050,0.5085,0.000000) (7.2250,0.5085,0.000000) (7.2250,0.5165,0.0000) (6.3050,0.5165,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.3050,0.5165,0.000000) (7.2250,0.5165,0.000000) (7.2250,0.5410,0.0000) (6.3050,0.5410,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.3050,0.5410,0.000000) (7.2250,0.5410,0.000000) (7.2250,0.5485,0.0000) (6.3050,0.5485,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.3050,0.5485,0.000000) (7.2250,0.5485,0.000000) (7.2250,0.5775,0.0000) (6.3050,0.5775,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.3050,0.5775,0.000000) (7.2250,0.5775,0.000000) (7.2250,0.6010,0.0000) (6.3050,0.6010,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.3050,0.6010,0.000000) (7.2250,0.6010,0.000000) (7.2250,0.6070,0.0000) (6.3050,0.6070,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.3050,0.6070,0.000000) (7.2250,0.6070,0.000000) (7.2250,0.6115,0.0000) (6.3050,0.6115,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.3050,0.6115,0.000000) (7.2250,0.6115,0.000000) (7.2250,0.6190,0.0000) (6.3050,0.6190,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.3050,0.6190,0.000000) (7.2250,0.6190,0.000000) (7.2250,0.6275,0.0000) (6.3050,0.6275,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.3050,0.6275,0.000000) (7.2250,0.6275,0.000000) (7.2250,0.6390,0.0000) (6.3050,0.6390,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.3050,0.6390,0.000000) (7.2250,0.6390,0.000000) (7.2250,0.6510,0.0000) (6.3050,0.6510,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.3050,0.6510,0.000000) (7.2250,0.6510,0.000000) (7.2250,0.8205,0.0000) (6.3050,0.8205,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.3050,0.8205,0.000000) (7.2250,0.8205,0.000000) (7.2250,0.8710,0.0000) (6.3050,0.8710,0.0000)};
 
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.3850,0.0000) (7.6250,0.3850,0.0000) (7.6250,0.4460,0.0000) (7.2250,0.4460,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.4460,0.0000) (7.6250,0.4460,0.0000) (7.6250,0.4485,0.0000) (7.2250,0.4485,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.4485,0.0000) (7.6250,0.4485,0.0000) (7.6250,0.4555,0.0000) (7.2250,0.4555,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.4555,0.0000) (7.6250,0.4555,0.0000) (7.6250,0.4620,0.0000) (7.2250,0.4620,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.4620,0.0000) (7.6250,0.4620,0.0000) (7.6250,0.4705,0.0000) (7.2250,0.4705,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.4705,0.0000) (7.6250,0.4705,0.0000) (7.6250,0.4910,0.0000) (7.2250,0.4910,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.4910,0.0125) (7.6250,0.4910,0.0125) (7.6250,0.4960,0.0125) (7.2250,0.4960,0.0125)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.4960,0.0000) (7.6250,0.4960,0.0000) (7.6250,0.5015,0.0000) (7.2250,0.5015,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.5015,0.0000) (7.6250,0.5015,0.0000) (7.6250,0.5085,0.0000) (7.2250,0.5085,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.5085,0.0000) (7.6250,0.5085,0.0000) (7.6250,0.5165,0.0000) (7.2250,0.5165,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.5165,0.0000) (7.6250,0.5165,0.0000) (7.6250,0.5410,0.0000) (7.2250,0.5410,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.5410,0.0000) (7.6250,0.5410,0.0000) (7.6250,0.5485,0.0000) (7.2250,0.5485,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.5485,0.0000) (7.6250,0.5485,0.0000) (7.6250,0.5775,0.0000) (7.2250,0.5775,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.5775,0.0000) (7.6250,0.5775,0.0000) (7.6250,0.6010,0.0000) (7.2250,0.6010,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.6010,0.0000) (7.6250,0.6010,0.0000) (7.6250,0.6070,0.0000) (7.2250,0.6070,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.6070,0.0000) (7.6250,0.6070,0.0000) (7.6250,0.6115,0.0000) (7.2250,0.6115,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.6115,0.0000) (7.6250,0.6115,0.0000) (7.6250,0.6190,0.0000) (7.2250,0.6190,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.6190,0.0000) (7.6250,0.6190,0.0000) (7.6250,0.6275,0.0000) (7.2250,0.6275,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.6275,0.0000) (7.6250,0.6275,0.0000) (7.6250,0.6390,0.0000) (7.2250,0.6390,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.6390,0.0000) (7.6250,0.6390,0.0000) (7.6250,0.6510,0.0000) (7.2250,0.6510,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.6510,0.0000) (7.6250,0.6510,0.0000) (7.6250,0.8205,0.0000) (7.2250,0.8205,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.8205,0.0000) (7.6250,0.8205,0.0000) (7.6250,0.8710,0.0000) (7.2250,0.8710,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.3850,0.000000) (7.6250,0.3850,0.000000) (7.6250,0.4460,0.0000) (7.2250,0.4460,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.4460,0.000000) (7.6250,0.4460,0.000000) (7.6250,0.4485,0.0000) (7.2250,0.4485,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.4485,0.000000) (7.6250,0.4485,0.000000) (7.6250,0.4555,0.0000) (7.2250,0.4555,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.4555,0.000000) (7.6250,0.4555,0.000000) (7.6250,0.4620,0.0000) (7.2250,0.4620,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.4620,0.000000) (7.6250,0.4620,0.000000) (7.6250,0.4705,0.0000) (7.2250,0.4705,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.4705,0.000000) (7.6250,0.4705,0.000000) (7.6250,0.4910,0.0000) (7.2250,0.4910,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.4910,0.625000) (7.6250,0.4910,0.625000) (7.6250,0.4960,0.6250) (7.2250,0.4960,0.6250)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.4960,0.000000) (7.6250,0.4960,0.000000) (7.6250,0.5015,0.0000) (7.2250,0.5015,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.5015,0.000000) (7.6250,0.5015,0.000000) (7.6250,0.5085,0.0000) (7.2250,0.5085,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.5085,0.000000) (7.6250,0.5085,0.000000) (7.6250,0.5165,0.0000) (7.2250,0.5165,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.5165,0.000000) (7.6250,0.5165,0.000000) (7.6250,0.5410,0.0000) (7.2250,0.5410,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.5410,0.000000) (7.6250,0.5410,0.000000) (7.6250,0.5485,0.0000) (7.2250,0.5485,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.5485,0.000000) (7.6250,0.5485,0.000000) (7.6250,0.5775,0.0000) (7.2250,0.5775,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.5775,0.000000) (7.6250,0.5775,0.000000) (7.6250,0.6010,0.0000) (7.2250,0.6010,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.6010,0.000000) (7.6250,0.6010,0.000000) (7.6250,0.6070,0.0000) (7.2250,0.6070,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.6070,0.000000) (7.6250,0.6070,0.000000) (7.6250,0.6115,0.0000) (7.2250,0.6115,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.6115,0.000000) (7.6250,0.6115,0.000000) (7.6250,0.6190,0.0000) (7.2250,0.6190,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.6190,0.000000) (7.6250,0.6190,0.000000) (7.6250,0.6275,0.0000) (7.2250,0.6275,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.6275,0.000000) (7.6250,0.6275,0.000000) (7.6250,0.6390,0.0000) (7.2250,0.6390,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.6390,0.000000) (7.6250,0.6390,0.000000) (7.6250,0.6510,0.0000) (7.2250,0.6510,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.6510,0.000000) (7.6250,0.6510,0.000000) (7.6250,0.8205,0.0000) (7.2250,0.8205,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.8205,0.000000) (7.6250,0.8205,0.000000) (7.6250,0.8710,0.0000) (7.2250,0.8710,0.0000)};
 
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.6250,0.3850,0.0000) (9.1250,0.3850,0.0000) (9.1250,0.4460,0.0000) (7.6250,0.4460,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.6250,0.4460,0.0000) (9.1250,0.4460,0.0000) (9.1250,0.4485,0.0000) (7.6250,0.4485,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.6250,0.4485,0.0000) (9.1250,0.4485,0.0000) (9.1250,0.4555,0.0000) (7.6250,0.4555,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.6250,0.4555,0.0000) (9.1250,0.4555,0.0000) (9.1250,0.4620,0.0000) (7.6250,0.4620,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.6250,0.4620,0.0000) (9.1250,0.4620,0.0000) (9.1250,0.4705,0.0000) (7.6250,0.4705,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.6250,0.4705,0.0000) (9.1250,0.4705,0.0000) (9.1250,0.4910,0.0000) (7.6250,0.4910,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.6250,0.4910,0.0000) (9.1250,0.4910,0.0000) (9.1250,0.4960,0.0000) (7.6250,0.4960,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.6250,0.4960,0.0000) (9.1250,0.4960,0.0000) (9.1250,0.5015,0.0000) (7.6250,0.5015,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.6250,0.5015,0.0000) (9.1250,0.5015,0.0000) (9.1250,0.5085,0.0000) (7.6250,0.5085,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.6250,0.5085,0.0000) (9.1250,0.5085,0.0000) (9.1250,0.5165,0.0000) (7.6250,0.5165,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.6250,0.5165,0.0820) (9.1250,0.5165,0.0820) (9.1250,0.5410,0.0820) (7.6250,0.5410,0.0820)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.6250,0.5410,0.0000) (9.1250,0.5410,0.0000) (9.1250,0.5485,0.0000) (7.6250,0.5485,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.6250,0.5485,0.0000) (9.1250,0.5485,0.0000) (9.1250,0.5775,0.0000) (7.6250,0.5775,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.6250,0.5775,0.0000) (9.1250,0.5775,0.0000) (9.1250,0.6010,0.0000) (7.6250,0.6010,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.6250,0.6010,0.0000) (9.1250,0.6010,0.0000) (9.1250,0.6070,0.0000) (7.6250,0.6070,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.6250,0.6070,0.0000) (9.1250,0.6070,0.0000) (9.1250,0.6115,0.0000) (7.6250,0.6115,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.6250,0.6115,0.0000) (9.1250,0.6115,0.0000) (9.1250,0.6190,0.0000) (7.6250,0.6190,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.6250,0.6190,0.0000) (9.1250,0.6190,0.0000) (9.1250,0.6275,0.0000) (7.6250,0.6275,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.6250,0.6275,0.0000) (9.1250,0.6275,0.0000) (9.1250,0.6390,0.0000) (7.6250,0.6390,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.6250,0.6390,0.0000) (9.1250,0.6390,0.0000) (9.1250,0.6510,0.0000) (7.6250,0.6510,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.6250,0.6510,0.0000) (9.1250,0.6510,0.0000) (9.1250,0.8205,0.0000) (7.6250,0.8205,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.6250,0.8205,0.0000) (9.1250,0.8205,0.0000) (9.1250,0.8710,0.0000) (7.6250,0.8710,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.6250,0.3850,0.000000) (9.1250,0.3850,0.000000) (9.1250,0.4460,0.0000) (7.6250,0.4460,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.6250,0.4460,0.000000) (9.1250,0.4460,0.000000) (9.1250,0.4485,0.0000) (7.6250,0.4485,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.6250,0.4485,0.000000) (9.1250,0.4485,0.000000) (9.1250,0.4555,0.0000) (7.6250,0.4555,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.6250,0.4555,0.000000) (9.1250,0.4555,0.000000) (9.1250,0.4620,0.0000) (7.6250,0.4620,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.6250,0.4620,0.000000) (9.1250,0.4620,0.000000) (9.1250,0.4705,0.0000) (7.6250,0.4705,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.6250,0.4705,0.000000) (9.1250,0.4705,0.000000) (9.1250,0.4910,0.0000) (7.6250,0.4910,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.6250,0.4910,0.000000) (9.1250,0.4910,0.000000) (9.1250,0.4960,0.0000) (7.6250,0.4960,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.6250,0.4960,0.000000) (9.1250,0.4960,0.000000) (9.1250,0.5015,0.0000) (7.6250,0.5015,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.6250,0.5015,0.000000) (9.1250,0.5015,0.000000) (9.1250,0.5085,0.0000) (7.6250,0.5085,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.6250,0.5085,0.000000) (9.1250,0.5085,0.000000) (9.1250,0.5165,0.0000) (7.6250,0.5165,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.6250,0.5165,0.223129) (9.1250,0.5165,0.223129) (9.1250,0.5410,0.2231) (7.6250,0.5410,0.2231)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.6250,0.5410,0.000000) (9.1250,0.5410,0.000000) (9.1250,0.5485,0.0000) (7.6250,0.5485,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.6250,0.5485,0.000000) (9.1250,0.5485,0.000000) (9.1250,0.5775,0.0000) (7.6250,0.5775,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.6250,0.5775,0.000000) (9.1250,0.5775,0.000000) (9.1250,0.6010,0.0000) (7.6250,0.6010,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.6250,0.6010,0.000000) (9.1250,0.6010,0.000000) (9.1250,0.6070,0.0000) (7.6250,0.6070,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.6250,0.6070,0.000000) (9.1250,0.6070,0.000000) (9.1250,0.6115,0.0000) (7.6250,0.6115,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.6250,0.6115,0.000000) (9.1250,0.6115,0.000000) (9.1250,0.6190,0.0000) (7.6250,0.6190,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.6250,0.6190,0.000000) (9.1250,0.6190,0.000000) (9.1250,0.6275,0.0000) (7.6250,0.6275,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.6250,0.6275,0.000000) (9.1250,0.6275,0.000000) (9.1250,0.6390,0.0000) (7.6250,0.6390,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.6250,0.6390,0.000000) (9.1250,0.6390,0.000000) (9.1250,0.6510,0.0000) (7.6250,0.6510,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.6250,0.6510,0.000000) (9.1250,0.6510,0.000000) (9.1250,0.8205,0.0000) (7.6250,0.8205,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.6250,0.8205,0.000000) (9.1250,0.8205,0.000000) (9.1250,0.8710,0.0000) (7.6250,0.8710,0.0000)};
 
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.3850,0.0000) (9.7950,0.3850,0.0000) (9.7950,0.4460,0.0000) (9.1250,0.4460,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.4460,0.0000) (9.7950,0.4460,0.0000) (9.7950,0.4485,0.0000) (9.1250,0.4485,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.4485,0.0000) (9.7950,0.4485,0.0000) (9.7950,0.4555,0.0000) (9.1250,0.4555,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.4555,0.0000) (9.7950,0.4555,0.0000) (9.7950,0.4620,0.0000) (9.1250,0.4620,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.4620,0.0000) (9.7950,0.4620,0.0000) (9.7950,0.4705,0.0000) (9.1250,0.4705,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.4705,0.0000) (9.7950,0.4705,0.0000) (9.7950,0.4910,0.0000) (9.1250,0.4910,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.4910,0.0000) (9.7950,0.4910,0.0000) (9.7950,0.4960,0.0000) (9.1250,0.4960,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.4960,0.0000) (9.7950,0.4960,0.0000) (9.7950,0.5015,0.0000) (9.1250,0.5015,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.5015,0.0000) (9.7950,0.5015,0.0000) (9.7950,0.5085,0.0000) (9.1250,0.5085,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.5085,0.0000) (9.7950,0.5085,0.0000) (9.7950,0.5165,0.0000) (9.1250,0.5165,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.5165,0.0000) (9.7950,0.5165,0.0000) (9.7950,0.5410,0.0000) (9.1250,0.5410,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.5410,0.0000) (9.7950,0.5410,0.0000) (9.7950,0.5485,0.0000) (9.1250,0.5485,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.5485,0.0000) (9.7950,0.5485,0.0000) (9.7950,0.5775,0.0000) (9.1250,0.5775,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.5775,0.0200) (9.7950,0.5775,0.0200) (9.7950,0.6010,0.0200) (9.1250,0.6010,0.0200)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.6010,0.0000) (9.7950,0.6010,0.0000) (9.7950,0.6070,0.0000) (9.1250,0.6070,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.6070,0.0000) (9.7950,0.6070,0.0000) (9.7950,0.6115,0.0000) (9.1250,0.6115,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.6115,0.0000) (9.7950,0.6115,0.0000) (9.7950,0.6190,0.0000) (9.1250,0.6190,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.6190,0.0000) (9.7950,0.6190,0.0000) (9.7950,0.6275,0.0000) (9.1250,0.6275,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.6275,0.0000) (9.7950,0.6275,0.0000) (9.7950,0.6390,0.0000) (9.1250,0.6390,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.6390,0.0000) (9.7950,0.6390,0.0000) (9.7950,0.6510,0.0000) (9.1250,0.6510,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.6510,0.0000) (9.7950,0.6510,0.0000) (9.7950,0.8205,0.0000) (9.1250,0.8205,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.8205,0.0000) (9.7950,0.8205,0.0000) (9.7950,0.8710,0.0000) (9.1250,0.8710,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.3850,0.000000) (9.7950,0.3850,0.000000) (9.7950,0.4460,0.0000) (9.1250,0.4460,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.4460,0.000000) (9.7950,0.4460,0.000000) (9.7950,0.4485,0.0000) (9.1250,0.4485,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.4485,0.000000) (9.7950,0.4485,0.000000) (9.7950,0.4555,0.0000) (9.1250,0.4555,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.4555,0.000000) (9.7950,0.4555,0.000000) (9.7950,0.4620,0.0000) (9.1250,0.4620,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.4620,0.000000) (9.7950,0.4620,0.000000) (9.7950,0.4705,0.0000) (9.1250,0.4705,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.4705,0.000000) (9.7950,0.4705,0.000000) (9.7950,0.4910,0.0000) (9.1250,0.4910,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.4910,0.000000) (9.7950,0.4910,0.000000) (9.7950,0.4960,0.0000) (9.1250,0.4960,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.4960,0.000000) (9.7950,0.4960,0.000000) (9.7950,0.5015,0.0000) (9.1250,0.5015,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.5015,0.000000) (9.7950,0.5015,0.000000) (9.7950,0.5085,0.0000) (9.1250,0.5085,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.5085,0.000000) (9.7950,0.5085,0.000000) (9.7950,0.5165,0.0000) (9.1250,0.5165,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.5165,0.000000) (9.7950,0.5165,0.000000) (9.7950,0.5410,0.0000) (9.1250,0.5410,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.5410,0.000000) (9.7950,0.5410,0.000000) (9.7950,0.5485,0.0000) (9.1250,0.5485,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.5485,0.000000) (9.7950,0.5485,0.000000) (9.7950,0.5775,0.0000) (9.1250,0.5775,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.5775,0.127024) (9.7950,0.5775,0.127024) (9.7950,0.6010,0.1270) (9.1250,0.6010,0.1270)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.6010,0.000000) (9.7950,0.6010,0.000000) (9.7950,0.6070,0.0000) (9.1250,0.6070,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.6070,0.000000) (9.7950,0.6070,0.000000) (9.7950,0.6115,0.0000) (9.1250,0.6115,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.6115,0.000000) (9.7950,0.6115,0.000000) (9.7950,0.6190,0.0000) (9.1250,0.6190,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.6190,0.000000) (9.7950,0.6190,0.000000) (9.7950,0.6275,0.0000) (9.1250,0.6275,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.6275,0.000000) (9.7950,0.6275,0.000000) (9.7950,0.6390,0.0000) (9.1250,0.6390,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.6390,0.000000) (9.7950,0.6390,0.000000) (9.7950,0.6510,0.0000) (9.1250,0.6510,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.6510,0.000000) (9.7950,0.6510,0.000000) (9.7950,0.8205,0.0000) (9.1250,0.8205,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.8205,0.000000) (9.7950,0.8205,0.000000) (9.7950,0.8710,0.0000) (9.1250,0.8710,0.0000)};
 
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.7950,0.3850,0.0000) (10.7000,0.3850,0.0000) (10.7000,0.4460,0.0000) (9.7950,0.4460,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.7950,0.4460,0.0000) (10.7000,0.4460,0.0000) (10.7000,0.4485,0.0000) (9.7950,0.4485,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.7950,0.4485,0.0000) (10.7000,0.4485,0.0000) (10.7000,0.4555,0.0000) (9.7950,0.4555,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.7950,0.4555,0.0000) (10.7000,0.4555,0.0000) (10.7000,0.4620,0.0000) (9.7950,0.4620,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.7950,0.4620,0.0000) (10.7000,0.4620,0.0000) (10.7000,0.4705,0.0000) (9.7950,0.4705,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.7950,0.4705,0.0230) (10.7000,0.4705,0.0230) (10.7000,0.4910,0.0230) (9.7950,0.4910,0.0230)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.7950,0.4910,0.0000) (10.7000,0.4910,0.0000) (10.7000,0.4960,0.0000) (9.7950,0.4960,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.7950,0.4960,0.0000) (10.7000,0.4960,0.0000) (10.7000,0.5015,0.0000) (9.7950,0.5015,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.7950,0.5015,0.0000) (10.7000,0.5015,0.0000) (10.7000,0.5085,0.0000) (9.7950,0.5085,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.7950,0.5085,0.0000) (10.7000,0.5085,0.0000) (10.7000,0.5165,0.0000) (9.7950,0.5165,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.7950,0.5165,0.0000) (10.7000,0.5165,0.0000) (10.7000,0.5410,0.0000) (9.7950,0.5410,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.7950,0.5410,0.0350) (10.7000,0.5410,0.0350) (10.7000,0.5485,0.0350) (9.7950,0.5485,0.0350)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.7950,0.5485,0.0000) (10.7000,0.5485,0.0000) (10.7000,0.5775,0.0000) (9.7950,0.5775,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.7950,0.5775,0.0000) (10.7000,0.5775,0.0000) (10.7000,0.6010,0.0000) (9.7950,0.6010,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.7950,0.6010,0.0000) (10.7000,0.6010,0.0000) (10.7000,0.6070,0.0000) (9.7950,0.6070,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.7950,0.6070,0.0000) (10.7000,0.6070,0.0000) (10.7000,0.6115,0.0000) (9.7950,0.6115,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.7950,0.6115,0.0000) (10.7000,0.6115,0.0000) (10.7000,0.6190,0.0000) (9.7950,0.6190,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.7950,0.6190,0.0000) (10.7000,0.6190,0.0000) (10.7000,0.6275,0.0000) (9.7950,0.6275,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.7950,0.6275,0.0000) (10.7000,0.6275,0.0000) (10.7000,0.6390,0.0000) (9.7950,0.6390,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.7950,0.6390,0.0000) (10.7000,0.6390,0.0000) (10.7000,0.6510,0.0000) (9.7950,0.6510,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.7950,0.6510,0.0000) (10.7000,0.6510,0.0000) (10.7000,0.8205,0.0000) (9.7950,0.8205,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.7950,0.8205,0.0000) (10.7000,0.8205,0.0000) (10.7000,0.8710,0.0000) (9.7950,0.8710,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.7950,0.3850,0.000000) (10.7000,0.3850,0.000000) (10.7000,0.4460,0.0000) (9.7950,0.4460,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.7950,0.4460,0.000000) (10.7000,0.4460,0.000000) (10.7000,0.4485,0.0000) (9.7950,0.4485,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.7950,0.4485,0.000000) (10.7000,0.4485,0.000000) (10.7000,0.4555,0.0000) (9.7950,0.4555,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.7950,0.4555,0.000000) (10.7000,0.4555,0.000000) (10.7000,0.4620,0.0000) (9.7950,0.4620,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.7950,0.4620,0.000000) (10.7000,0.4620,0.000000) (10.7000,0.4705,0.0000) (9.7950,0.4705,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.7950,0.4705,0.123973) (10.7000,0.4705,0.123973) (10.7000,0.4910,0.1240) (9.7950,0.4910,0.1240)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.7950,0.4910,0.000000) (10.7000,0.4910,0.000000) (10.7000,0.4960,0.0000) (9.7950,0.4960,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.7950,0.4960,0.000000) (10.7000,0.4960,0.000000) (10.7000,0.5015,0.0000) (9.7950,0.5015,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.7950,0.5015,0.000000) (10.7000,0.5015,0.000000) (10.7000,0.5085,0.0000) (9.7950,0.5085,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.7950,0.5085,0.000000) (10.7000,0.5085,0.000000) (10.7000,0.5165,0.0000) (9.7950,0.5165,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.7950,0.5165,0.000000) (10.7000,0.5165,0.000000) (10.7000,0.5410,0.0000) (9.7950,0.5410,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.7950,0.5410,0.515654) (10.7000,0.5410,0.515654) (10.7000,0.5485,0.5157) (9.7950,0.5485,0.5157)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.7950,0.5485,0.000000) (10.7000,0.5485,0.000000) (10.7000,0.5775,0.0000) (9.7950,0.5775,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.7950,0.5775,0.000000) (10.7000,0.5775,0.000000) (10.7000,0.6010,0.0000) (9.7950,0.6010,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.7950,0.6010,0.000000) (10.7000,0.6010,0.000000) (10.7000,0.6070,0.0000) (9.7950,0.6070,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.7950,0.6070,0.000000) (10.7000,0.6070,0.000000) (10.7000,0.6115,0.0000) (9.7950,0.6115,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.7950,0.6115,0.000000) (10.7000,0.6115,0.000000) (10.7000,0.6190,0.0000) (9.7950,0.6190,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.7950,0.6190,0.000000) (10.7000,0.6190,0.000000) (10.7000,0.6275,0.0000) (9.7950,0.6275,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.7950,0.6275,0.000000) (10.7000,0.6275,0.000000) (10.7000,0.6390,0.0000) (9.7950,0.6390,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.7950,0.6390,0.000000) (10.7000,0.6390,0.000000) (10.7000,0.6510,0.0000) (9.7950,0.6510,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.7950,0.6510,0.000000) (10.7000,0.6510,0.000000) (10.7000,0.8205,0.0000) (9.7950,0.8205,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.7950,0.8205,0.000000) (10.7000,0.8205,0.000000) (10.7000,0.8710,0.0000) (9.7950,0.8710,0.0000)};
 
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.7000,0.3850,0.0295) (16.5700,0.3850,0.0295) (16.5700,0.4460,0.0295) (10.7000,0.4460,0.0295)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.7000,0.4460,0.0000) (16.5700,0.4460,0.0000) (16.5700,0.4485,0.0000) (10.7000,0.4485,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.7000,0.4485,0.0000) (16.5700,0.4485,0.0000) (16.5700,0.4555,0.0000) (10.7000,0.4555,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.7000,0.4555,0.0000) (16.5700,0.4555,0.0000) (16.5700,0.4620,0.0000) (10.7000,0.4620,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.7000,0.4620,0.0060) (16.5700,0.4620,0.0060) (16.5700,0.4705,0.0060) (10.7000,0.4705,0.0060)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.7000,0.4705,0.0000) (16.5700,0.4705,0.0000) (16.5700,0.4910,0.0000) (10.7000,0.4910,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.7000,0.4910,0.0000) (16.5700,0.4910,0.0000) (16.5700,0.4960,0.0000) (10.7000,0.4960,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.7000,0.4960,0.0000) (16.5700,0.4960,0.0000) (16.5700,0.5015,0.0000) (10.7000,0.5015,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.7000,0.5015,0.0000) (16.5700,0.5015,0.0000) (16.5700,0.5085,0.0000) (10.7000,0.5085,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.7000,0.5085,0.0000) (16.5700,0.5085,0.0000) (16.5700,0.5165,0.0000) (10.7000,0.5165,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.7000,0.5165,0.0000) (16.5700,0.5165,0.0000) (16.5700,0.5410,0.0000) (10.7000,0.5410,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.7000,0.5410,0.0000) (16.5700,0.5410,0.0000) (16.5700,0.5485,0.0000) (10.7000,0.5485,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.7000,0.5485,0.0190) (16.5700,0.5485,0.0190) (16.5700,0.5775,0.0190) (10.7000,0.5775,0.0190)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.7000,0.5775,0.0000) (16.5700,0.5775,0.0000) (16.5700,0.6010,0.0000) (10.7000,0.6010,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.7000,0.6010,0.0000) (16.5700,0.6010,0.0000) (16.5700,0.6070,0.0000) (10.7000,0.6070,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.7000,0.6070,0.0000) (16.5700,0.6070,0.0000) (16.5700,0.6115,0.0000) (10.7000,0.6115,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.7000,0.6115,0.0000) (16.5700,0.6115,0.0000) (16.5700,0.6190,0.0000) (10.7000,0.6190,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.7000,0.6190,0.0000) (16.5700,0.6190,0.0000) (16.5700,0.6275,0.0000) (10.7000,0.6275,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.7000,0.6275,0.0000) (16.5700,0.6275,0.0000) (16.5700,0.6390,0.0000) (10.7000,0.6390,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.7000,0.6390,0.0000) (16.5700,0.6390,0.0000) (16.5700,0.6510,0.0000) (10.7000,0.6510,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.7000,0.6510,0.0000) (16.5700,0.6510,0.0000) (16.5700,0.8205,0.0000) (10.7000,0.8205,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.7000,0.8205,0.0000) (16.5700,0.8205,0.0000) (16.5700,0.8710,0.0000) (10.7000,0.8710,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.7000,0.3850,0.008239) (16.5700,0.3850,0.008239) (16.5700,0.4460,0.0082) (10.7000,0.4460,0.0082)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.7000,0.4460,0.000000) (16.5700,0.4460,0.000000) (16.5700,0.4485,0.0000) (10.7000,0.4485,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.7000,0.4485,0.000000) (16.5700,0.4485,0.000000) (16.5700,0.4555,0.0000) (10.7000,0.4555,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.7000,0.4555,0.000000) (16.5700,0.4555,0.000000) (16.5700,0.4620,0.0000) (10.7000,0.4620,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.7000,0.4620,0.012025) (16.5700,0.4620,0.012025) (16.5700,0.4705,0.0120) (10.7000,0.4705,0.0120)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.7000,0.4705,0.000000) (16.5700,0.4705,0.000000) (16.5700,0.4910,0.0000) (10.7000,0.4910,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.7000,0.4910,0.000000) (16.5700,0.4910,0.000000) (16.5700,0.4960,0.0000) (10.7000,0.4960,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.7000,0.4960,0.000000) (16.5700,0.4960,0.000000) (16.5700,0.5015,0.0000) (10.7000,0.5015,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.7000,0.5015,0.000000) (16.5700,0.5015,0.000000) (16.5700,0.5085,0.0000) (10.7000,0.5085,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.7000,0.5085,0.000000) (16.5700,0.5085,0.000000) (16.5700,0.5165,0.0000) (10.7000,0.5165,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.7000,0.5165,0.000000) (16.5700,0.5165,0.000000) (16.5700,0.5410,0.0000) (10.7000,0.5410,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.7000,0.5410,0.000000) (16.5700,0.5410,0.000000) (16.5700,0.5485,0.0000) (10.7000,0.5485,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.7000,0.5485,0.011161) (16.5700,0.5485,0.011161) (16.5700,0.5775,0.0112) (10.7000,0.5775,0.0112)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.7000,0.5775,0.000000) (16.5700,0.5775,0.000000) (16.5700,0.6010,0.0000) (10.7000,0.6010,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.7000,0.6010,0.000000) (16.5700,0.6010,0.000000) (16.5700,0.6070,0.0000) (10.7000,0.6070,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.7000,0.6070,0.000000) (16.5700,0.6070,0.000000) (16.5700,0.6115,0.0000) (10.7000,0.6115,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.7000,0.6115,0.000000) (16.5700,0.6115,0.000000) (16.5700,0.6190,0.0000) (10.7000,0.6190,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.7000,0.6190,0.000000) (16.5700,0.6190,0.000000) (16.5700,0.6275,0.0000) (10.7000,0.6275,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.7000,0.6275,0.000000) (16.5700,0.6275,0.000000) (16.5700,0.6390,0.0000) (10.7000,0.6390,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.7000,0.6390,0.000000) (16.5700,0.6390,0.000000) (16.5700,0.6510,0.0000) (10.7000,0.6510,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.7000,0.6510,0.000000) (16.5700,0.6510,0.000000) (16.5700,0.8205,0.0000) (10.7000,0.8205,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.7000,0.8205,0.000000) (16.5700,0.8205,0.000000) (16.5700,0.8710,0.0000) (10.7000,0.8710,0.0000)};
 
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.3850,0.0000) (18.8400,0.3850,0.0000) (18.8400,0.4460,0.0000) (16.5700,0.4460,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.4460,0.0000) (18.8400,0.4460,0.0000) (18.8400,0.4485,0.0000) (16.5700,0.4485,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.4485,0.0000) (18.8400,0.4485,0.0000) (18.8400,0.4555,0.0000) (16.5700,0.4555,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.4555,0.0000) (18.8400,0.4555,0.0000) (18.8400,0.4620,0.0000) (16.5700,0.4620,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.4620,0.0000) (18.8400,0.4620,0.0000) (18.8400,0.4705,0.0000) (16.5700,0.4705,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.4705,0.0000) (18.8400,0.4705,0.0000) (18.8400,0.4910,0.0000) (16.5700,0.4910,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.4910,0.0000) (18.8400,0.4910,0.0000) (18.8400,0.4960,0.0000) (16.5700,0.4960,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.4960,0.0000) (18.8400,0.4960,0.0000) (18.8400,0.5015,0.0000) (16.5700,0.5015,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.5015,0.0000) (18.8400,0.5015,0.0000) (18.8400,0.5085,0.0000) (16.5700,0.5085,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.5085,0.0000) (18.8400,0.5085,0.0000) (18.8400,0.5165,0.0000) (16.5700,0.5165,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.5165,0.0135) (18.8400,0.5165,0.0135) (18.8400,0.5410,0.0135) (16.5700,0.5410,0.0135)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.5410,0.0000) (18.8400,0.5410,0.0000) (18.8400,0.5485,0.0000) (16.5700,0.5485,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.5485,0.0000) (18.8400,0.5485,0.0000) (18.8400,0.5775,0.0000) (16.5700,0.5775,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.5775,0.0445) (18.8400,0.5775,0.0445) (18.8400,0.6010,0.0445) (16.5700,0.6010,0.0445)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.6010,0.0000) (18.8400,0.6010,0.0000) (18.8400,0.6070,0.0000) (16.5700,0.6070,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.6070,0.0000) (18.8400,0.6070,0.0000) (18.8400,0.6115,0.0000) (16.5700,0.6115,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.6115,0.0120) (18.8400,0.6115,0.0120) (18.8400,0.6190,0.0120) (16.5700,0.6190,0.0120)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.6190,0.0000) (18.8400,0.6190,0.0000) (18.8400,0.6275,0.0000) (16.5700,0.6275,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.6275,0.0080) (18.8400,0.6275,0.0080) (18.8400,0.6390,0.0080) (16.5700,0.6390,0.0080)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.6390,0.0000) (18.8400,0.6390,0.0000) (18.8400,0.6510,0.0000) (16.5700,0.6510,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.6510,0.1855) (18.8400,0.6510,0.1855) (18.8400,0.8205,0.1855) (16.5700,0.8205,0.1855)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.8205,0.0000) (18.8400,0.8205,0.0000) (18.8400,0.8710,0.0000) (16.5700,0.8710,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.3850,0.000000) (18.8400,0.3850,0.000000) (18.8400,0.4460,0.0000) (16.5700,0.4460,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.4460,0.000000) (18.8400,0.4460,0.000000) (18.8400,0.4485,0.0000) (16.5700,0.4485,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.4485,0.000000) (18.8400,0.4485,0.000000) (18.8400,0.4555,0.0000) (16.5700,0.4555,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.4555,0.000000) (18.8400,0.4555,0.000000) (18.8400,0.4620,0.0000) (16.5700,0.4620,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.4620,0.000000) (18.8400,0.4620,0.000000) (18.8400,0.4705,0.0000) (16.5700,0.4705,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.4705,0.000000) (18.8400,0.4705,0.000000) (18.8400,0.4910,0.0000) (16.5700,0.4910,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.4910,0.000000) (18.8400,0.4910,0.000000) (18.8400,0.4960,0.0000) (16.5700,0.4960,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.4960,0.000000) (18.8400,0.4960,0.000000) (18.8400,0.5015,0.0000) (16.5700,0.5015,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.5015,0.000000) (18.8400,0.5015,0.000000) (18.8400,0.5085,0.0000) (16.5700,0.5085,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.5085,0.000000) (18.8400,0.5085,0.000000) (18.8400,0.5165,0.0000) (16.5700,0.5165,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.5165,0.024274) (18.8400,0.5165,0.024274) (18.8400,0.5410,0.0243) (16.5700,0.5410,0.0243)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.5410,0.000000) (18.8400,0.5410,0.000000) (18.8400,0.5485,0.0000) (16.5700,0.5485,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.5485,0.000000) (18.8400,0.5485,0.000000) (18.8400,0.5775,0.0000) (16.5700,0.5775,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.5775,0.083419) (18.8400,0.5775,0.083419) (18.8400,0.6010,0.0834) (16.5700,0.6010,0.0834)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.6010,0.000000) (18.8400,0.6010,0.000000) (18.8400,0.6070,0.0000) (16.5700,0.6070,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.6070,0.000000) (18.8400,0.6070,0.000000) (18.8400,0.6115,0.0000) (16.5700,0.6115,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.6115,0.070485) (18.8400,0.6115,0.070485) (18.8400,0.6190,0.0705) (16.5700,0.6190,0.0705)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.6190,0.000000) (18.8400,0.6190,0.000000) (18.8400,0.6275,0.0000) (16.5700,0.6275,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.6275,0.030645) (18.8400,0.6275,0.030645) (18.8400,0.6390,0.0306) (16.5700,0.6390,0.0306)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.6390,0.000000) (18.8400,0.6390,0.000000) (18.8400,0.6510,0.0000) (16.5700,0.6510,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.6510,0.048211) (18.8400,0.6510,0.048211) (18.8400,0.8205,0.0482) (16.5700,0.8205,0.0482)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.8205,0.000000) (18.8400,0.8205,0.000000) (18.8400,0.8710,0.0000) (16.5700,0.8710,0.0000)};
 
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.3850,0.0000) (20.7350,0.3850,0.0000) (20.7350,0.4460,0.0000) (18.8400,0.4460,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.4460,0.0000) (20.7350,0.4460,0.0000) (20.7350,0.4485,0.0000) (18.8400,0.4485,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.4485,0.0000) (20.7350,0.4485,0.0000) (20.7350,0.4555,0.0000) (18.8400,0.4555,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.4555,0.0000) (20.7350,0.4555,0.0000) (20.7350,0.4620,0.0000) (18.8400,0.4620,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.4620,0.0000) (20.7350,0.4620,0.0000) (20.7350,0.4705,0.0000) (18.8400,0.4705,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.4705,0.0000) (20.7350,0.4705,0.0000) (20.7350,0.4910,0.0000) (18.8400,0.4910,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.4910,0.0000) (20.7350,0.4910,0.0000) (20.7350,0.4960,0.0000) (18.8400,0.4960,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.4960,0.0000) (20.7350,0.4960,0.0000) (20.7350,0.5015,0.0000) (18.8400,0.5015,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.5015,0.0000) (20.7350,0.5015,0.0000) (20.7350,0.5085,0.0000) (18.8400,0.5085,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.5085,0.0000) (20.7350,0.5085,0.0000) (20.7350,0.5165,0.0000) (18.8400,0.5165,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.5165,0.0000) (20.7350,0.5165,0.0000) (20.7350,0.5410,0.0000) (18.8400,0.5410,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.5410,0.0000) (20.7350,0.5410,0.0000) (20.7350,0.5485,0.0000) (18.8400,0.5485,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.5485,0.0000) (20.7350,0.5485,0.0000) (20.7350,0.5775,0.0000) (18.8400,0.5775,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.5775,0.0000) (20.7350,0.5775,0.0000) (20.7350,0.6010,0.0000) (18.8400,0.6010,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.6010,0.0260) (20.7350,0.6010,0.0260) (20.7350,0.6070,0.0260) (18.8400,0.6070,0.0260)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.6070,0.0000) (20.7350,0.6070,0.0000) (20.7350,0.6115,0.0000) (18.8400,0.6115,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.6115,0.0000) (20.7350,0.6115,0.0000) (20.7350,0.6190,0.0000) (18.8400,0.6190,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.6190,0.0000) (20.7350,0.6190,0.0000) (20.7350,0.6275,0.0000) (18.8400,0.6275,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.6275,0.0000) (20.7350,0.6275,0.0000) (20.7350,0.6390,0.0000) (18.8400,0.6390,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.6390,0.0000) (20.7350,0.6390,0.0000) (20.7350,0.6510,0.0000) (18.8400,0.6510,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.6510,0.0000) (20.7350,0.6510,0.0000) (20.7350,0.8205,0.0000) (18.8400,0.8205,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.8205,0.0370) (20.7350,0.8205,0.0370) (20.7350,0.8710,0.0370) (18.8400,0.8710,0.0370)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.3850,0.000000) (20.7350,0.3850,0.000000) (20.7350,0.4460,0.0000) (18.8400,0.4460,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.4460,0.000000) (20.7350,0.4460,0.000000) (20.7350,0.4485,0.0000) (18.8400,0.4485,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.4485,0.000000) (20.7350,0.4485,0.000000) (20.7350,0.4555,0.0000) (18.8400,0.4555,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.4555,0.000000) (20.7350,0.4555,0.000000) (20.7350,0.4620,0.0000) (18.8400,0.4620,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.4620,0.000000) (20.7350,0.4620,0.000000) (20.7350,0.4705,0.0000) (18.8400,0.4705,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.4705,0.000000) (20.7350,0.4705,0.000000) (20.7350,0.4910,0.0000) (18.8400,0.4910,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.4910,0.000000) (20.7350,0.4910,0.000000) (20.7350,0.4960,0.0000) (18.8400,0.4960,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.4960,0.000000) (20.7350,0.4960,0.000000) (20.7350,0.5015,0.0000) (18.8400,0.5015,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.5015,0.000000) (20.7350,0.5015,0.000000) (20.7350,0.5085,0.0000) (18.8400,0.5085,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.5085,0.000000) (20.7350,0.5085,0.000000) (20.7350,0.5165,0.0000) (18.8400,0.5165,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.5165,0.000000) (20.7350,0.5165,0.000000) (20.7350,0.5410,0.0000) (18.8400,0.5410,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.5410,0.000000) (20.7350,0.5410,0.000000) (20.7350,0.5485,0.0000) (18.8400,0.5485,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.5485,0.000000) (20.7350,0.5485,0.000000) (20.7350,0.5775,0.0000) (18.8400,0.5775,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.5775,0.000000) (20.7350,0.5775,0.000000) (20.7350,0.6010,0.0000) (18.8400,0.6010,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.6010,0.228672) (20.7350,0.6010,0.228672) (20.7350,0.6070,0.2287) (18.8400,0.6070,0.2287)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.6070,0.000000) (20.7350,0.6070,0.000000) (20.7350,0.6115,0.0000) (18.8400,0.6115,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.6115,0.000000) (20.7350,0.6115,0.000000) (20.7350,0.6190,0.0000) (18.8400,0.6190,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.6190,0.000000) (20.7350,0.6190,0.000000) (20.7350,0.6275,0.0000) (18.8400,0.6275,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.6275,0.000000) (20.7350,0.6275,0.000000) (20.7350,0.6390,0.0000) (18.8400,0.6390,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.6390,0.000000) (20.7350,0.6390,0.000000) (20.7350,0.6510,0.0000) (18.8400,0.6510,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.6510,0.000000) (20.7350,0.6510,0.000000) (20.7350,0.8205,0.0000) (18.8400,0.8205,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.8205,0.038663) (20.7350,0.8205,0.038663) (20.7350,0.8710,0.0387) (18.8400,0.8710,0.0387)};
 
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.3850,0.0000) (23.7700,0.3850,0.0000) (23.7700,0.4460,0.0000) (20.7350,0.4460,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.4460,0.0000) (23.7700,0.4460,0.0000) (23.7700,0.4485,0.0000) (20.7350,0.4485,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.4485,0.0000) (23.7700,0.4485,0.0000) (23.7700,0.4555,0.0000) (20.7350,0.4555,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.4555,0.0000) (23.7700,0.4555,0.0000) (23.7700,0.4620,0.0000) (20.7350,0.4620,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.4620,0.0000) (23.7700,0.4620,0.0000) (23.7700,0.4705,0.0000) (20.7350,0.4705,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.4705,0.0000) (23.7700,0.4705,0.0000) (23.7700,0.4910,0.0000) (20.7350,0.4910,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.4910,0.0000) (23.7700,0.4910,0.0000) (23.7700,0.4960,0.0000) (20.7350,0.4960,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.4960,0.0000) (23.7700,0.4960,0.0000) (23.7700,0.5015,0.0000) (20.7350,0.5015,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.5015,0.0000) (23.7700,0.5015,0.0000) (23.7700,0.5085,0.0000) (20.7350,0.5085,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.5085,0.0000) (23.7700,0.5085,0.0000) (23.7700,0.5165,0.0000) (20.7350,0.5165,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.5165,0.0000) (23.7700,0.5165,0.0000) (23.7700,0.5410,0.0000) (20.7350,0.5410,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.5410,0.0000) (23.7700,0.5410,0.0000) (23.7700,0.5485,0.0000) (20.7350,0.5485,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.5485,0.0000) (23.7700,0.5485,0.0000) (23.7700,0.5775,0.0000) (20.7350,0.5775,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.5775,0.0000) (23.7700,0.5775,0.0000) (23.7700,0.6010,0.0000) (20.7350,0.6010,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.6010,0.0000) (23.7700,0.6010,0.0000) (23.7700,0.6070,0.0000) (20.7350,0.6070,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.6070,0.0000) (23.7700,0.6070,0.0000) (23.7700,0.6115,0.0000) (20.7350,0.6115,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.6115,0.0000) (23.7700,0.6115,0.0000) (23.7700,0.6190,0.0000) (20.7350,0.6190,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.6190,0.0325) (23.7700,0.6190,0.0325) (23.7700,0.6275,0.0325) (20.7350,0.6275,0.0325)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.6275,0.0000) (23.7700,0.6275,0.0000) (23.7700,0.6390,0.0000) (20.7350,0.6390,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.6390,0.0000) (23.7700,0.6390,0.0000) (23.7700,0.6510,0.0000) (20.7350,0.6510,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.6510,0.0000) (23.7700,0.6510,0.0000) (23.7700,0.8205,0.0000) (20.7350,0.8205,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.8205,0.0000) (23.7700,0.8205,0.0000) (23.7700,0.8710,0.0000) (20.7350,0.8710,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.3850,0.000000) (23.7700,0.3850,0.000000) (23.7700,0.4460,0.0000) (20.7350,0.4460,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.4460,0.000000) (23.7700,0.4460,0.000000) (23.7700,0.4485,0.0000) (20.7350,0.4485,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.4485,0.000000) (23.7700,0.4485,0.000000) (23.7700,0.4555,0.0000) (20.7350,0.4555,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.4555,0.000000) (23.7700,0.4555,0.000000) (23.7700,0.4620,0.0000) (20.7350,0.4620,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.4620,0.000000) (23.7700,0.4620,0.000000) (23.7700,0.4705,0.0000) (20.7350,0.4705,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.4705,0.000000) (23.7700,0.4705,0.000000) (23.7700,0.4910,0.0000) (20.7350,0.4910,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.4910,0.000000) (23.7700,0.4910,0.000000) (23.7700,0.4960,0.0000) (20.7350,0.4960,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.4960,0.000000) (23.7700,0.4960,0.000000) (23.7700,0.5015,0.0000) (20.7350,0.5015,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.5015,0.000000) (23.7700,0.5015,0.000000) (23.7700,0.5085,0.0000) (20.7350,0.5085,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.5085,0.000000) (23.7700,0.5085,0.000000) (23.7700,0.5165,0.0000) (20.7350,0.5165,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.5165,0.000000) (23.7700,0.5165,0.000000) (23.7700,0.5410,0.0000) (20.7350,0.5410,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.5410,0.000000) (23.7700,0.5410,0.000000) (23.7700,0.5485,0.0000) (20.7350,0.5485,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.5485,0.000000) (23.7700,0.5485,0.000000) (23.7700,0.5775,0.0000) (20.7350,0.5775,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.5775,0.000000) (23.7700,0.5775,0.000000) (23.7700,0.6010,0.0000) (20.7350,0.6010,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.6010,0.000000) (23.7700,0.6010,0.000000) (23.7700,0.6070,0.0000) (20.7350,0.6070,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.6070,0.000000) (23.7700,0.6070,0.000000) (23.7700,0.6115,0.0000) (20.7350,0.6115,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.6115,0.000000) (23.7700,0.6115,0.000000) (23.7700,0.6190,0.0000) (20.7350,0.6190,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.6190,0.125981) (23.7700,0.6190,0.125981) (23.7700,0.6275,0.1260) (20.7350,0.6275,0.1260)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.6275,0.000000) (23.7700,0.6275,0.000000) (23.7700,0.6390,0.0000) (20.7350,0.6390,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.6390,0.000000) (23.7700,0.6390,0.000000) (23.7700,0.6510,0.0000) (20.7350,0.6510,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.6510,0.000000) (23.7700,0.6510,0.000000) (23.7700,0.8205,0.0000) (20.7350,0.8205,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.8205,0.000000) (23.7700,0.8205,0.000000) (23.7700,0.8710,0.0000) (20.7350,0.8710,0.0000)};
 
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.7700,0.3850,0.0000) (27.7400,0.3850,0.0000) (27.7400,0.4460,0.0000) (23.7700,0.4460,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.7700,0.4460,0.0000) (27.7400,0.4460,0.0000) (27.7400,0.4485,0.0000) (23.7700,0.4485,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.7700,0.4485,0.0000) (27.7400,0.4485,0.0000) (27.7400,0.4555,0.0000) (23.7700,0.4555,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.7700,0.4555,0.0000) (27.7400,0.4555,0.0000) (27.7400,0.4620,0.0000) (23.7700,0.4620,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.7700,0.4620,0.0000) (27.7400,0.4620,0.0000) (27.7400,0.4705,0.0000) (23.7700,0.4705,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.7700,0.4705,0.0000) (27.7400,0.4705,0.0000) (27.7400,0.4910,0.0000) (23.7700,0.4910,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.7700,0.4910,0.0000) (27.7400,0.4910,0.0000) (27.7400,0.4960,0.0000) (23.7700,0.4960,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.7700,0.4960,0.0000) (27.7400,0.4960,0.0000) (27.7400,0.5015,0.0000) (23.7700,0.5015,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.7700,0.5015,0.0000) (27.7400,0.5015,0.0000) (27.7400,0.5085,0.0000) (23.7700,0.5085,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.7700,0.5085,0.0000) (27.7400,0.5085,0.0000) (27.7400,0.5165,0.0000) (23.7700,0.5165,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.7700,0.5165,0.0000) (27.7400,0.5165,0.0000) (27.7400,0.5410,0.0000) (23.7700,0.5410,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.7700,0.5410,0.0000) (27.7400,0.5410,0.0000) (27.7400,0.5485,0.0000) (23.7700,0.5485,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.7700,0.5485,0.0000) (27.7400,0.5485,0.0000) (27.7400,0.5775,0.0000) (23.7700,0.5775,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.7700,0.5775,0.0105) (27.7400,0.5775,0.0105) (27.7400,0.6010,0.0105) (23.7700,0.6010,0.0105)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.7700,0.6010,0.0000) (27.7400,0.6010,0.0000) (27.7400,0.6070,0.0000) (23.7700,0.6070,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.7700,0.6070,0.0085) (27.7400,0.6070,0.0085) (27.7400,0.6115,0.0085) (23.7700,0.6115,0.0085)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.7700,0.6115,0.0000) (27.7400,0.6115,0.0000) (27.7400,0.6190,0.0000) (23.7700,0.6190,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.7700,0.6190,0.0000) (27.7400,0.6190,0.0000) (27.7400,0.6275,0.0000) (23.7700,0.6275,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.7700,0.6275,0.0000) (27.7400,0.6275,0.0000) (27.7400,0.6390,0.0000) (23.7700,0.6390,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.7700,0.6390,0.0000) (27.7400,0.6390,0.0000) (27.7400,0.6510,0.0000) (23.7700,0.6510,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.7700,0.6510,0.0000) (27.7400,0.6510,0.0000) (27.7400,0.8205,0.0000) (23.7700,0.8205,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.7700,0.8205,0.0000) (27.7400,0.8205,0.0000) (27.7400,0.8710,0.0000) (23.7700,0.8710,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.7700,0.3850,0.000000) (27.7400,0.3850,0.000000) (27.7400,0.4460,0.0000) (23.7700,0.4460,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.7700,0.4460,0.000000) (27.7400,0.4460,0.000000) (27.7400,0.4485,0.0000) (23.7700,0.4485,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.7700,0.4485,0.000000) (27.7400,0.4485,0.000000) (27.7400,0.4555,0.0000) (23.7700,0.4555,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.7700,0.4555,0.000000) (27.7400,0.4555,0.000000) (27.7400,0.4620,0.0000) (23.7700,0.4620,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.7700,0.4620,0.000000) (27.7400,0.4620,0.000000) (27.7400,0.4705,0.0000) (23.7700,0.4705,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.7700,0.4705,0.000000) (27.7400,0.4705,0.000000) (27.7400,0.4910,0.0000) (23.7700,0.4910,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.7700,0.4910,0.000000) (27.7400,0.4910,0.000000) (27.7400,0.4960,0.0000) (23.7700,0.4960,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.7700,0.4960,0.000000) (27.7400,0.4960,0.000000) (27.7400,0.5015,0.0000) (23.7700,0.5015,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.7700,0.5015,0.000000) (27.7400,0.5015,0.000000) (27.7400,0.5085,0.0000) (23.7700,0.5085,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.7700,0.5085,0.000000) (27.7400,0.5085,0.000000) (27.7400,0.5165,0.0000) (23.7700,0.5165,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.7700,0.5165,0.000000) (27.7400,0.5165,0.000000) (27.7400,0.5410,0.0000) (23.7700,0.5410,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.7700,0.5410,0.000000) (27.7400,0.5410,0.000000) (27.7400,0.5485,0.0000) (23.7700,0.5485,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.7700,0.5485,0.000000) (27.7400,0.5485,0.000000) (27.7400,0.5775,0.0000) (23.7700,0.5775,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.7700,0.5775,0.011255) (27.7400,0.5775,0.011255) (27.7400,0.6010,0.0113) (23.7700,0.6010,0.0113)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.7700,0.6010,0.000000) (27.7400,0.6010,0.000000) (27.7400,0.6070,0.0000) (23.7700,0.6070,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.7700,0.6070,0.047579) (27.7400,0.6070,0.047579) (27.7400,0.6115,0.0476) (23.7700,0.6115,0.0476)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.7700,0.6115,0.000000) (27.7400,0.6115,0.000000) (27.7400,0.6190,0.0000) (23.7700,0.6190,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.7700,0.6190,0.000000) (27.7400,0.6190,0.000000) (27.7400,0.6275,0.0000) (23.7700,0.6275,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.7700,0.6275,0.000000) (27.7400,0.6275,0.000000) (27.7400,0.6390,0.0000) (23.7700,0.6390,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.7700,0.6390,0.000000) (27.7400,0.6390,0.000000) (27.7400,0.6510,0.0000) (23.7700,0.6510,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.7700,0.6510,0.000000) (27.7400,0.6510,0.000000) (27.7400,0.8205,0.0000) (23.7700,0.8205,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.7700,0.8205,0.000000) (27.7400,0.8205,0.000000) (27.7400,0.8710,0.0000) (23.7700,0.8710,0.0000)};
 

### 2015-11-22 graph_housing_exp2_distr_8_5.tex
Change all plots from probability to probability density

--- 2015-11-17 graph_housing_exp2_distr_8_5.tex
@@
 			zmin=0.0, zmax=1.0,
-			xlabel=$H$,
-			ylabel=$E$,
+			xlabel=H,
+			ylabel=E,
 			colorbar,
-			point meta min=0, point meta max=0.5,
+			point meta min=0, point meta max=0.4,
 			colormap={}{ gray(0cm)=(1); gray(1cm)=(0);},
 			colorbar style={
-			        ytick={0,0.05,...,0.51},
+			        ytick={0,0.08,...,0.41},
+			        ylabel={probability density$ \times 10^{-1}$},
+			        y label style={at={(axis description cs:6.5,0.5)},rotate=180,anchor=north},
 			        yticklabel style={
@@
 
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.3850,0.0060) (2.5884,0.3850,0.0060) (2.5884,0.4460,0.0060) (1.1296,0.4460,0.0060)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.4460,0.0000) (2.5884,0.4460,0.0000) (2.5884,0.4485,0.0000) (1.1296,0.4485,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.4485,0.0000) (2.5884,0.4485,0.0000) (2.5884,0.4555,0.0000) (1.1296,0.4555,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.4555,0.0000) (2.5884,0.4555,0.0000) (2.5884,0.4620,0.0000) (1.1296,0.4620,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.4620,0.0025) (2.5884,0.4620,0.0025) (2.5884,0.4705,0.0025) (1.1296,0.4705,0.0025)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.4705,0.0040) (2.5884,0.4705,0.0040) (2.5884,0.4910,0.0040) (1.1296,0.4910,0.0040)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.4910,0.0000) (2.5884,0.4910,0.0000) (2.5884,0.4960,0.0000) (1.1296,0.4960,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.4960,0.0000) (2.5884,0.4960,0.0000) (2.5884,0.5015,0.0000) (1.1296,0.5015,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.5015,0.0000) (2.5884,0.5015,0.0000) (2.5884,0.5085,0.0000) (1.1296,0.5085,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.5085,0.0000) (2.5884,0.5085,0.0000) (2.5884,0.5165,0.0000) (1.1296,0.5165,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.5165,0.0215) (2.5884,0.5165,0.0215) (2.5884,0.5410,0.0215) (1.1296,0.5410,0.0215)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.5410,0.0055) (2.5884,0.5410,0.0055) (2.5884,0.5485,0.0055) (1.1296,0.5485,0.0055)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.5485,0.0070) (2.5884,0.5485,0.0070) (2.5884,0.5775,0.0070) (1.1296,0.5775,0.0070)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.5775,0.0645) (2.5884,0.5775,0.0645) (2.5884,0.6010,0.0645) (1.1296,0.6010,0.0645)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.6010,0.0260) (2.5884,0.6010,0.0260) (2.5884,0.6070,0.0260) (1.1296,0.6070,0.0260)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.6070,0.0085) (2.5884,0.6070,0.0085) (2.5884,0.6115,0.0085) (1.1296,0.6115,0.0085)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.6115,0.0100) (2.5884,0.6115,0.0100) (2.5884,0.6190,0.0100) (1.1296,0.6190,0.0100)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.6190,0.0325) (2.5884,0.6190,0.0325) (2.5884,0.6275,0.0325) (1.1296,0.6275,0.0325)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.6275,0.0060) (2.5884,0.6275,0.0060) (2.5884,0.6390,0.0060) (1.1296,0.6390,0.0060)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.6390,0.0210) (2.5884,0.6390,0.0210) (2.5884,0.6510,0.0210) (1.1296,0.6510,0.0210)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.6510,0.1560) (2.5884,0.6510,0.1560) (2.5884,0.8205,0.1560) (1.1296,0.8205,0.1560)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.8205,0.0370) (2.5884,0.8205,0.0370) (2.5884,0.8710,0.0370) (1.1296,0.8710,0.0370)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.3850,0.006743) (2.5884,0.3850,0.006743) (2.5884,0.4460,0.0067) (1.1296,0.4460,0.0067)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.4460,0.000000) (2.5884,0.4460,0.000000) (2.5884,0.4485,0.0000) (1.1296,0.4485,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.4485,0.000000) (2.5884,0.4485,0.000000) (2.5884,0.4555,0.0000) (1.1296,0.4555,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.4555,0.000000) (2.5884,0.4555,0.000000) (2.5884,0.4620,0.0000) (1.1296,0.4620,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.4620,0.020162) (2.5884,0.4620,0.020162) (2.5884,0.4705,0.0202) (1.1296,0.4705,0.0202)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.4705,0.013376) (2.5884,0.4705,0.013376) (2.5884,0.4910,0.0134) (1.1296,0.4910,0.0134)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.4910,0.000000) (2.5884,0.4910,0.000000) (2.5884,0.4960,0.0000) (1.1296,0.4960,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.4960,0.000000) (2.5884,0.4960,0.000000) (2.5884,0.5015,0.0000) (1.1296,0.5015,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.5015,0.000000) (2.5884,0.5015,0.000000) (2.5884,0.5085,0.0000) (1.1296,0.5085,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.5085,0.000000) (2.5884,0.5085,0.000000) (2.5884,0.5165,0.0000) (1.1296,0.5165,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.5165,0.060158) (2.5884,0.5165,0.060158) (2.5884,0.5410,0.0602) (1.1296,0.5410,0.0602)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.5410,0.050271) (2.5884,0.5410,0.050271) (2.5884,0.5485,0.0503) (1.1296,0.5485,0.0503)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.5485,0.016547) (2.5884,0.5485,0.016547) (2.5884,0.5775,0.0165) (1.1296,0.5775,0.0165)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.5775,0.188153) (2.5884,0.5775,0.188153) (2.5884,0.6010,0.1882) (1.1296,0.6010,0.1882)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.6010,0.297058) (2.5884,0.6010,0.297058) (2.5884,0.6070,0.2971) (1.1296,0.6070,0.2971)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.6070,0.129487) (2.5884,0.6070,0.129487) (2.5884,0.6115,0.1295) (1.1296,0.6115,0.1295)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.6115,0.091402) (2.5884,0.6115,0.091402) (2.5884,0.6190,0.0914) (1.1296,0.6190,0.0914)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.6190,0.262110) (2.5884,0.6190,0.262110) (2.5884,0.6275,0.2621) (1.1296,0.6275,0.2621)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.6275,0.035766) (2.5884,0.6275,0.035766) (2.5884,0.6390,0.0358) (1.1296,0.6390,0.0358)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.6390,0.119966) (2.5884,0.6390,0.119966) (2.5884,0.6510,0.1200) (1.1296,0.6510,0.1200)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.6510,0.063092) (2.5884,0.6510,0.063092) (2.5884,0.8205,0.0631) (1.1296,0.8205,0.0631)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.8205,0.050226) (2.5884,0.8205,0.050226) (2.5884,0.8710,0.0502) (1.1296,0.8710,0.0502)};
 
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.3850,0.0775) (4.9150,0.3850,0.0775) (4.9150,0.4460,0.0775) (2.5884,0.4460,0.0775)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.4460,0.0150) (4.9150,0.4460,0.0150) (4.9150,0.4485,0.0150) (2.5884,0.4485,0.0150)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.4485,0.0050) (4.9150,0.4485,0.0050) (4.9150,0.4555,0.0050) (2.5884,0.4555,0.0050)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.4555,0.0040) (4.9150,0.4555,0.0040) (4.9150,0.4620,0.0040) (2.5884,0.4620,0.0040)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.4620,0.0080) (4.9150,0.4620,0.0080) (4.9150,0.4705,0.0080) (2.5884,0.4705,0.0080)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.4705,0.0290) (4.9150,0.4705,0.0290) (4.9150,0.4910,0.0290) (2.5884,0.4910,0.0290)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.4910,0.0095) (4.9150,0.4910,0.0095) (4.9150,0.4960,0.0095) (2.5884,0.4960,0.0095)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.4960,0.0025) (4.9150,0.4960,0.0025) (4.9150,0.5015,0.0025) (2.5884,0.5015,0.0025)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.5015,0.0410) (4.9150,0.5015,0.0410) (4.9150,0.5085,0.0410) (2.5884,0.5085,0.0410)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.5085,0.0100) (4.9150,0.5085,0.0100) (4.9150,0.5165,0.0100) (2.5884,0.5165,0.0100)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.5165,0.0605) (4.9150,0.5165,0.0605) (4.9150,0.5410,0.0605) (2.5884,0.5410,0.0605)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.5410,0.0295) (4.9150,0.5410,0.0295) (4.9150,0.5485,0.0295) (2.5884,0.5485,0.0295)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.5485,0.0095) (4.9150,0.5485,0.0095) (4.9150,0.5775,0.0095) (2.5884,0.5775,0.0095)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.5775,0.0105) (4.9150,0.5775,0.0105) (4.9150,0.6010,0.0105) (2.5884,0.6010,0.0105)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.6010,0.0000) (4.9150,0.6010,0.0000) (4.9150,0.6070,0.0000) (2.5884,0.6070,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.6070,0.0000) (4.9150,0.6070,0.0000) (4.9150,0.6115,0.0000) (2.5884,0.6115,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.6115,0.0020) (4.9150,0.6115,0.0020) (4.9150,0.6190,0.0020) (2.5884,0.6190,0.0020)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.6190,0.0000) (4.9150,0.6190,0.0000) (4.9150,0.6275,0.0000) (2.5884,0.6275,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.6275,0.0020) (4.9150,0.6275,0.0020) (4.9150,0.6390,0.0020) (2.5884,0.6390,0.0020)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.6390,0.0015) (4.9150,0.6390,0.0015) (4.9150,0.6510,0.0015) (2.5884,0.6510,0.0015)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.6510,0.0295) (4.9150,0.6510,0.0295) (4.9150,0.8205,0.0295) (2.5884,0.8205,0.0295)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.8205,0.0000) (4.9150,0.8205,0.0000) (4.9150,0.8710,0.0000) (2.5884,0.8710,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.3850,0.054607) (4.9150,0.3850,0.054607) (4.9150,0.4460,0.0546) (2.5884,0.4460,0.0546)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.4460,0.257887) (4.9150,0.4460,0.257887) (4.9150,0.4485,0.2579) (2.5884,0.4485,0.2579)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.4485,0.030701) (4.9150,0.4485,0.030701) (4.9150,0.4555,0.0307) (2.5884,0.4555,0.0307)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.4555,0.026450) (4.9150,0.4555,0.026450) (4.9150,0.4620,0.0264) (2.5884,0.4620,0.0264)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.4620,0.040453) (4.9150,0.4620,0.040453) (4.9150,0.4705,0.0405) (2.5884,0.4705,0.0405)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.4705,0.060803) (4.9150,0.4705,0.060803) (4.9150,0.4910,0.0608) (2.5884,0.4910,0.0608)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.4910,0.081664) (4.9150,0.4910,0.081664) (4.9150,0.4960,0.0817) (2.5884,0.4960,0.0817)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.4960,0.019537) (4.9150,0.4960,0.019537) (4.9150,0.5015,0.0195) (2.5884,0.5015,0.0195)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.5015,0.251747) (4.9150,0.5015,0.251747) (4.9150,0.5085,0.2517) (2.5884,0.5085,0.2517)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.5085,0.053726) (4.9150,0.5085,0.053726) (4.9150,0.5165,0.0537) (2.5884,0.5165,0.0537)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.5165,0.106137) (4.9150,0.5165,0.106137) (4.9150,0.5410,0.1061) (2.5884,0.5410,0.1061)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.5410,0.169059) (4.9150,0.5410,0.169059) (4.9150,0.5485,0.1691) (2.5884,0.5485,0.1691)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.5485,0.014080) (4.9150,0.5485,0.014080) (4.9150,0.5775,0.0141) (2.5884,0.5775,0.0141)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.5775,0.019204) (4.9150,0.5775,0.019204) (4.9150,0.6010,0.0192) (2.5884,0.6010,0.0192)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.6010,0.000000) (4.9150,0.6010,0.000000) (4.9150,0.6070,0.0000) (2.5884,0.6070,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.6070,0.000000) (4.9150,0.6070,0.000000) (4.9150,0.6115,0.0000) (2.5884,0.6115,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.6115,0.011462) (4.9150,0.6115,0.011462) (4.9150,0.6190,0.0115) (2.5884,0.6190,0.0115)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.6190,0.000000) (4.9150,0.6190,0.000000) (4.9150,0.6275,0.0000) (2.5884,0.6275,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.6275,0.007475) (4.9150,0.6275,0.007475) (4.9150,0.6390,0.0075) (2.5884,0.6390,0.0075)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.6390,0.005373) (4.9150,0.6390,0.005373) (4.9150,0.6510,0.0054) (2.5884,0.6510,0.0054)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.6510,0.007480) (4.9150,0.6510,0.007480) (4.9150,0.8205,0.0075) (2.5884,0.8205,0.0075)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.8205,0.000000) (4.9150,0.8205,0.000000) (4.9150,0.8710,0.0000) (2.5884,0.8710,0.0000)};
 
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.3850,0.1245) (12.1265,0.3850,0.1245) (12.1265,0.4460,0.1245) (4.9150,0.4460,0.1245)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.4460,0.0135) (12.1265,0.4460,0.0135) (12.1265,0.4485,0.0135) (4.9150,0.4485,0.0135)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.4485,0.0160) (12.1265,0.4485,0.0160) (12.1265,0.4555,0.0160) (4.9150,0.4555,0.0160)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.4555,0.0090) (12.1265,0.4555,0.0090) (12.1265,0.4620,0.0090) (4.9150,0.4620,0.0090)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.4620,0.0120) (12.1265,0.4620,0.0120) (12.1265,0.4705,0.0120) (4.9150,0.4705,0.0120)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.4705,0.0185) (12.1265,0.4705,0.0185) (12.1265,0.4910,0.0185) (4.9150,0.4910,0.0185)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.4910,0.0030) (12.1265,0.4910,0.0030) (12.1265,0.4960,0.0030) (4.9150,0.4960,0.0030)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.4960,0.0070) (12.1265,0.4960,0.0070) (12.1265,0.5015,0.0070) (4.9150,0.5015,0.0070)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.5015,0.0000) (12.1265,0.5015,0.0000) (12.1265,0.5085,0.0000) (4.9150,0.5085,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.5085,0.0200) (12.1265,0.5085,0.0200) (12.1265,0.5165,0.0200) (4.9150,0.5165,0.0200)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.5165,0.0160) (12.1265,0.5165,0.0160) (12.1265,0.5410,0.0160) (4.9150,0.5410,0.0160)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.5410,0.0000) (12.1265,0.5410,0.0000) (12.1265,0.5485,0.0000) (4.9150,0.5485,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.5485,0.0060) (12.1265,0.5485,0.0060) (12.1265,0.5775,0.0060) (4.9150,0.5775,0.0060)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.5775,0.0000) (12.1265,0.5775,0.0000) (12.1265,0.6010,0.0000) (4.9150,0.6010,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.6010,0.0000) (12.1265,0.6010,0.0000) (12.1265,0.6070,0.0000) (4.9150,0.6070,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.6070,0.0000) (12.1265,0.6070,0.0000) (12.1265,0.6115,0.0000) (4.9150,0.6115,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.6115,0.0000) (12.1265,0.6115,0.0000) (12.1265,0.6190,0.0000) (4.9150,0.6190,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.6190,0.0000) (12.1265,0.6190,0.0000) (12.1265,0.6275,0.0000) (4.9150,0.6275,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.6275,0.0000) (12.1265,0.6275,0.0000) (12.1265,0.6390,0.0000) (4.9150,0.6390,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.6390,0.0000) (12.1265,0.6390,0.0000) (12.1265,0.6510,0.0000) (4.9150,0.6510,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.6510,0.0000) (12.1265,0.6510,0.0000) (12.1265,0.8205,0.0000) (4.9150,0.8205,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.8205,0.0000) (12.1265,0.8205,0.0000) (12.1265,0.8710,0.0000) (4.9150,0.8710,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.3850,0.028302) (12.1265,0.3850,0.028302) (12.1265,0.4460,0.0283) (4.9150,0.4460,0.0283)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.4460,0.074880) (12.1265,0.4460,0.074880) (12.1265,0.4485,0.0749) (4.9150,0.4485,0.0749)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.4485,0.031695) (12.1265,0.4485,0.031695) (12.1265,0.4555,0.0317) (4.9150,0.4555,0.0317)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.4555,0.019200) (12.1265,0.4555,0.019200) (12.1265,0.4620,0.0192) (4.9150,0.4620,0.0192)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.4620,0.019576) (12.1265,0.4620,0.019576) (12.1265,0.4705,0.0196) (4.9150,0.4705,0.0196)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.4705,0.012514) (12.1265,0.4705,0.012514) (12.1265,0.4910,0.0125) (4.9150,0.4910,0.0125)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.4910,0.008320) (12.1265,0.4910,0.008320) (12.1265,0.4960,0.0083) (4.9150,0.4960,0.0083)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.4960,0.017648) (12.1265,0.4960,0.017648) (12.1265,0.5015,0.0176) (4.9150,0.5015,0.0176)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.5015,0.000000) (12.1265,0.5015,0.000000) (12.1265,0.5085,0.0000) (4.9150,0.5085,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.5085,0.034667) (12.1265,0.5085,0.034667) (12.1265,0.5165,0.0347) (4.9150,0.5165,0.0347)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.5165,0.009056) (12.1265,0.5165,0.009056) (12.1265,0.5410,0.0091) (4.9150,0.5410,0.0091)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.5410,0.000000) (12.1265,0.5410,0.000000) (12.1265,0.5485,0.0000) (4.9150,0.5485,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.5485,0.002869) (12.1265,0.5485,0.002869) (12.1265,0.5775,0.0029) (4.9150,0.5775,0.0029)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.5775,0.000000) (12.1265,0.5775,0.000000) (12.1265,0.6010,0.0000) (4.9150,0.6010,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.6010,0.000000) (12.1265,0.6010,0.000000) (12.1265,0.6070,0.0000) (4.9150,0.6070,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.6070,0.000000) (12.1265,0.6070,0.000000) (12.1265,0.6115,0.0000) (4.9150,0.6115,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.6115,0.000000) (12.1265,0.6115,0.000000) (12.1265,0.6190,0.0000) (4.9150,0.6190,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.6190,0.000000) (12.1265,0.6190,0.000000) (12.1265,0.6275,0.0000) (4.9150,0.6275,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.6275,0.000000) (12.1265,0.6275,0.000000) (12.1265,0.6390,0.0000) (4.9150,0.6390,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.6390,0.000000) (12.1265,0.6390,0.000000) (12.1265,0.6510,0.0000) (4.9150,0.6510,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.6510,0.000000) (12.1265,0.6510,0.000000) (12.1265,0.8205,0.0000) (4.9150,0.8205,0.0000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.8205,0.000000) (12.1265,0.8205,0.000000) (12.1265,0.8710,0.0000) (4.9150,0.8710,0.0000)};
 

### 2015-11-22 probability_plot_old/graph_housing_exp1_distr.tex
Change all plots from probability to probability density

\begin{tikzpicture}
  \begin{groupplot}[group style={group size=1 by 2}]%,xmin=0,ymin=0,height=4cm,width=5cm,no markers]
  \nextgroupplot[
			view={0}{90},
			enlargelimits=0,
			zmin=0.0, zmax=1.0,
			ylabel=E,
			colorbar right,
    every colorbar/.append style={height=
        2*\pgfkeysvalueof{/pgfplots/parent axis height}+
        \pgfkeysvalueof{/pgfplots/group/vertical sep}},
			point meta min=0, point meta max=0.5,
			colormap={}{ gray(0cm)=(1); gray(1cm)=(0);},
			colorbar style={
			        ytick={0,0.05,...,0.5},
			        yticklabel style={
			            text width=2.5em,
			            align=right,
			            /pgf/number format/.cd,
			                fixed,
			                fixed zerofill
			        }
			    }
			]

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.3850,0.1710) (7.2250,0.3850,0.1710) (7.2250,0.4405,0.1710) (0.4600,0.4405,0.1710)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.4405,0.1080) (7.2250,0.4405,0.1080) (7.2250,0.4860,0.1080) (0.4600,0.4860,0.1080)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.4860,0.0250) (7.2250,0.4860,0.0250) (7.2250,0.4910,0.0250) (0.4600,0.4910,0.0250)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.4910,0.0000) (7.2250,0.4910,0.0000) (7.2250,0.4960,0.0000) (0.4600,0.4960,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.4960,0.0795) (7.2250,0.4960,0.0795) (7.2250,0.5190,0.0795) (0.4600,0.5190,0.0795)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.5190,0.0000) (7.2250,0.5190,0.0000) (7.2250,0.5220,0.0000) (0.4600,0.5220,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.5220,0.0000) (7.2250,0.5220,0.0000) (7.2250,0.5280,0.0000) (0.4600,0.5280,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.5280,0.0035) (7.2250,0.5280,0.0035) (7.2250,0.5410,0.0035) (0.4600,0.5410,0.0035)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.5410,0.0000) (7.2250,0.5410,0.0000) (7.2250,0.5455,0.0000) (0.4600,0.5455,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.5455,0.0045) (7.2250,0.5455,0.0045) (7.2250,0.5910,0.0045) (0.4600,0.5910,0.0045)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.5910,0.0000) (7.2250,0.5910,0.0000) (7.2250,0.6390,0.0000) (0.4600,0.6390,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.6390,0.0185) (7.2250,0.6390,0.0185) (7.2250,0.6510,0.0185) (0.4600,0.6510,0.0185)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.6510,0.0000) (7.2250,0.6510,0.0000) (7.2250,0.8205,0.0000) (0.4600,0.8205,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.8205,0.0000) (7.2250,0.8205,0.0000) (7.2250,0.8710,0.0000) (0.4600,0.8710,0.0000)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.3850,0.0000) (8.0050,0.3850,0.0000) (8.0050,0.4405,0.0000) (7.2250,0.4405,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.4405,0.0000) (8.0050,0.4405,0.0000) (8.0050,0.4860,0.0000) (7.2250,0.4860,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.4860,0.0000) (8.0050,0.4860,0.0000) (8.0050,0.4910,0.0000) (7.2250,0.4910,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.4910,0.0145) (8.0050,0.4910,0.0145) (8.0050,0.4960,0.0145) (7.2250,0.4960,0.0145)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.4960,0.0000) (8.0050,0.4960,0.0000) (8.0050,0.5190,0.0000) (7.2250,0.5190,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.5190,0.0000) (8.0050,0.5190,0.0000) (8.0050,0.5220,0.0000) (7.2250,0.5220,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.5220,0.0120) (8.0050,0.5220,0.0120) (8.0050,0.5280,0.0120) (7.2250,0.5280,0.0120)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.5280,0.0000) (8.0050,0.5280,0.0000) (8.0050,0.5410,0.0000) (7.2250,0.5410,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.5410,0.0000) (8.0050,0.5410,0.0000) (8.0050,0.5455,0.0000) (7.2250,0.5455,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.5455,0.0000) (8.0050,0.5455,0.0000) (8.0050,0.5910,0.0000) (7.2250,0.5910,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.5910,0.0000) (8.0050,0.5910,0.0000) (8.0050,0.6390,0.0000) (7.2250,0.6390,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.6390,0.0000) (8.0050,0.6390,0.0000) (8.0050,0.6510,0.0000) (7.2250,0.6510,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.6510,0.0000) (8.0050,0.6510,0.0000) (8.0050,0.8205,0.0000) (7.2250,0.8205,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.2250,0.8205,0.0000) (8.0050,0.8205,0.0000) (8.0050,0.8710,0.0000) (7.2250,0.8710,0.0000)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.0050,0.3850,0.0000) (8.3500,0.3850,0.0000) (8.3500,0.4405,0.0000) (8.0050,0.4405,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.0050,0.4405,0.0000) (8.3500,0.4405,0.0000) (8.3500,0.4860,0.0000) (8.0050,0.4860,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.0050,0.4860,0.0000) (8.3500,0.4860,0.0000) (8.3500,0.4910,0.0000) (8.0050,0.4910,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.0050,0.4910,0.0000) (8.3500,0.4910,0.0000) (8.3500,0.4960,0.0000) (8.0050,0.4960,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.0050,0.4960,0.0000) (8.3500,0.4960,0.0000) (8.3500,0.5190,0.0000) (8.0050,0.5190,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.0050,0.5190,0.0000) (8.3500,0.5190,0.0000) (8.3500,0.5220,0.0000) (8.0050,0.5220,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.0050,0.5220,0.0000) (8.3500,0.5220,0.0000) (8.3500,0.5280,0.0000) (8.0050,0.5280,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.0050,0.5280,0.0455) (8.3500,0.5280,0.0455) (8.3500,0.5410,0.0455) (8.0050,0.5410,0.0455)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.0050,0.5410,0.0000) (8.3500,0.5410,0.0000) (8.3500,0.5455,0.0000) (8.0050,0.5455,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.0050,0.5455,0.0000) (8.3500,0.5455,0.0000) (8.3500,0.5910,0.0000) (8.0050,0.5910,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.0050,0.5910,0.0000) (8.3500,0.5910,0.0000) (8.3500,0.6390,0.0000) (8.0050,0.6390,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.0050,0.6390,0.0000) (8.3500,0.6390,0.0000) (8.3500,0.6510,0.0000) (8.0050,0.6510,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.0050,0.6510,0.0000) (8.3500,0.6510,0.0000) (8.3500,0.8205,0.0000) (8.0050,0.8205,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.0050,0.8205,0.0000) (8.3500,0.8205,0.0000) (8.3500,0.8710,0.0000) (8.0050,0.8710,0.0000)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.3500,0.3850,0.0000) (9.1250,0.3850,0.0000) (9.1250,0.4405,0.0000) (8.3500,0.4405,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.3500,0.4405,0.0000) (9.1250,0.4405,0.0000) (9.1250,0.4860,0.0000) (8.3500,0.4860,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.3500,0.4860,0.0000) (9.1250,0.4860,0.0000) (9.1250,0.4910,0.0000) (8.3500,0.4910,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.3500,0.4910,0.0000) (9.1250,0.4910,0.0000) (9.1250,0.4960,0.0000) (8.3500,0.4960,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.3500,0.4960,0.0000) (9.1250,0.4960,0.0000) (9.1250,0.5190,0.0000) (8.3500,0.5190,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.3500,0.5190,0.0150) (9.1250,0.5190,0.0150) (9.1250,0.5220,0.0150) (8.3500,0.5220,0.0150)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.3500,0.5220,0.0000) (9.1250,0.5220,0.0000) (9.1250,0.5280,0.0000) (8.3500,0.5280,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.3500,0.5280,0.0000) (9.1250,0.5280,0.0000) (9.1250,0.5410,0.0000) (8.3500,0.5410,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.3500,0.5410,0.0000) (9.1250,0.5410,0.0000) (9.1250,0.5455,0.0000) (8.3500,0.5455,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.3500,0.5455,0.0000) (9.1250,0.5455,0.0000) (9.1250,0.5910,0.0000) (8.3500,0.5910,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.3500,0.5910,0.0000) (9.1250,0.5910,0.0000) (9.1250,0.6390,0.0000) (8.3500,0.6390,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.3500,0.6390,0.0000) (9.1250,0.6390,0.0000) (9.1250,0.6510,0.0000) (8.3500,0.6510,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.3500,0.6510,0.0000) (9.1250,0.6510,0.0000) (9.1250,0.8205,0.0000) (8.3500,0.8205,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(8.3500,0.8205,0.0000) (9.1250,0.8205,0.0000) (9.1250,0.8710,0.0000) (8.3500,0.8710,0.0000)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.3850,0.0330) (16.5700,0.3850,0.0330) (16.5700,0.4405,0.0330) (9.1250,0.4405,0.0330)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.4405,0.0065) (16.5700,0.4405,0.0065) (16.5700,0.4860,0.0065) (9.1250,0.4860,0.0065)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.4860,0.0210) (16.5700,0.4860,0.0210) (16.5700,0.4910,0.0210) (9.1250,0.4910,0.0210)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.4910,0.0000) (16.5700,0.4910,0.0000) (16.5700,0.4960,0.0000) (9.1250,0.4960,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.4960,0.0000) (16.5700,0.4960,0.0000) (16.5700,0.5190,0.0000) (9.1250,0.5190,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.5190,0.0000) (16.5700,0.5190,0.0000) (16.5700,0.5220,0.0000) (9.1250,0.5220,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.5220,0.0000) (16.5700,0.5220,0.0000) (16.5700,0.5280,0.0000) (9.1250,0.5280,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.5280,0.0000) (16.5700,0.5280,0.0000) (16.5700,0.5410,0.0000) (9.1250,0.5410,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.5410,0.0220) (16.5700,0.5410,0.0220) (16.5700,0.5455,0.0220) (9.1250,0.5455,0.0220)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.5455,0.0490) (16.5700,0.5455,0.0490) (16.5700,0.5910,0.0490) (9.1250,0.5910,0.0490)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.5910,0.0000) (16.5700,0.5910,0.0000) (16.5700,0.6390,0.0000) (9.1250,0.6390,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.6390,0.0000) (16.5700,0.6390,0.0000) (16.5700,0.6510,0.0000) (9.1250,0.6510,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.6510,0.0000) (16.5700,0.6510,0.0000) (16.5700,0.8205,0.0000) (9.1250,0.8205,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.1250,0.8205,0.0000) (16.5700,0.8205,0.0000) (16.5700,0.8710,0.0000) (9.1250,0.8710,0.0000)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.3850,0.0000) (18.8400,0.3850,0.0000) (18.8400,0.4405,0.0000) (16.5700,0.4405,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.4405,0.0000) (18.8400,0.4405,0.0000) (18.8400,0.4860,0.0000) (16.5700,0.4860,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.4860,0.0000) (18.8400,0.4860,0.0000) (18.8400,0.4910,0.0000) (16.5700,0.4910,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.4910,0.0000) (18.8400,0.4910,0.0000) (18.8400,0.4960,0.0000) (16.5700,0.4960,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.4960,0.0000) (18.8400,0.4960,0.0000) (18.8400,0.5190,0.0000) (16.5700,0.5190,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.5190,0.0000) (18.8400,0.5190,0.0000) (18.8400,0.5220,0.0000) (16.5700,0.5220,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.5220,0.0000) (18.8400,0.5220,0.0000) (18.8400,0.5280,0.0000) (16.5700,0.5280,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.5280,0.0095) (18.8400,0.5280,0.0095) (18.8400,0.5410,0.0095) (16.5700,0.5410,0.0095)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.5410,0.0000) (18.8400,0.5410,0.0000) (18.8400,0.5455,0.0000) (16.5700,0.5455,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.5455,0.0295) (18.8400,0.5455,0.0295) (18.8400,0.5910,0.0295) (16.5700,0.5910,0.0295)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.5910,0.0260) (18.8400,0.5910,0.0260) (18.8400,0.6390,0.0260) (16.5700,0.6390,0.0260)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.6390,0.0000) (18.8400,0.6390,0.0000) (18.8400,0.6510,0.0000) (16.5700,0.6510,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.6510,0.1955) (18.8400,0.6510,0.1955) (18.8400,0.8205,0.1955) (16.5700,0.8205,0.1955)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(16.5700,0.8205,0.0000) (18.8400,0.8205,0.0000) (18.8400,0.8710,0.0000) (16.5700,0.8710,0.0000)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.3850,0.0000) (20.7350,0.3850,0.0000) (20.7350,0.4405,0.0000) (18.8400,0.4405,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.4405,0.0000) (20.7350,0.4405,0.0000) (20.7350,0.4860,0.0000) (18.8400,0.4860,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.4860,0.0000) (20.7350,0.4860,0.0000) (20.7350,0.4910,0.0000) (18.8400,0.4910,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.4910,0.0000) (20.7350,0.4910,0.0000) (20.7350,0.4960,0.0000) (18.8400,0.4960,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.4960,0.0000) (20.7350,0.4960,0.0000) (20.7350,0.5190,0.0000) (18.8400,0.5190,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.5190,0.0000) (20.7350,0.5190,0.0000) (20.7350,0.5220,0.0000) (18.8400,0.5220,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.5220,0.0000) (20.7350,0.5220,0.0000) (20.7350,0.5280,0.0000) (18.8400,0.5280,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.5280,0.0000) (20.7350,0.5280,0.0000) (20.7350,0.5410,0.0000) (18.8400,0.5410,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.5410,0.0000) (20.7350,0.5410,0.0000) (20.7350,0.5455,0.0000) (18.8400,0.5455,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.5455,0.0000) (20.7350,0.5455,0.0000) (20.7350,0.5910,0.0000) (18.8400,0.5910,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.5910,0.0335) (20.7350,0.5910,0.0335) (20.7350,0.6390,0.0335) (18.8400,0.6390,0.0335)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.6390,0.0000) (20.7350,0.6390,0.0000) (20.7350,0.6510,0.0000) (18.8400,0.6510,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.6510,0.0000) (20.7350,0.6510,0.0000) (20.7350,0.8205,0.0000) (18.8400,0.8205,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(18.8400,0.8205,0.0300) (20.7350,0.8205,0.0300) (20.7350,0.8710,0.0300) (18.8400,0.8710,0.0300)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.3850,0.0000) (27.7400,0.3850,0.0000) (27.7400,0.4405,0.0000) (20.7350,0.4405,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.4405,0.0000) (27.7400,0.4405,0.0000) (27.7400,0.4860,0.0000) (20.7350,0.4860,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.4860,0.0000) (27.7400,0.4860,0.0000) (27.7400,0.4910,0.0000) (20.7350,0.4910,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.4910,0.0000) (27.7400,0.4910,0.0000) (27.7400,0.4960,0.0000) (20.7350,0.4960,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.4960,0.0000) (27.7400,0.4960,0.0000) (27.7400,0.5190,0.0000) (20.7350,0.5190,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.5190,0.0000) (27.7400,0.5190,0.0000) (27.7400,0.5220,0.0000) (20.7350,0.5220,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.5220,0.0000) (27.7400,0.5220,0.0000) (27.7400,0.5280,0.0000) (20.7350,0.5280,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.5280,0.0000) (27.7400,0.5280,0.0000) (27.7400,0.5410,0.0000) (20.7350,0.5410,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.5410,0.0000) (27.7400,0.5410,0.0000) (27.7400,0.5455,0.0000) (20.7350,0.5455,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.5455,0.0160) (27.7400,0.5455,0.0160) (27.7400,0.5910,0.0160) (20.7350,0.5910,0.0160)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.5910,0.0315) (27.7400,0.5910,0.0315) (27.7400,0.6390,0.0315) (20.7350,0.6390,0.0315)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.6390,0.0000) (27.7400,0.6390,0.0000) (27.7400,0.6510,0.0000) (20.7350,0.6510,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.6510,0.0000) (27.7400,0.6510,0.0000) (27.7400,0.8205,0.0000) (20.7350,0.8205,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.7350,0.8205,0.0000) (27.7400,0.8205,0.0000) (27.7400,0.8710,0.0000) (20.7350,0.8710,0.0000)};

			\addplot3[mark=+, draw=none, mark size=0.7] coordinates {
(2.310,0.538,1) (7.070,0.469,1) (7.070,0.469,1) (2.180,0.458,1) (2.180,0.458,1) (2.180,0.458,1) (7.870,0.524,1) (7.870,0.524,1) (7.870,0.524,1) (7.870,0.524,1) (7.870,0.524,1) (7.870,0.524,1) (7.870,0.524,1) (8.140,0.538,1) (8.140,0.538,1) (8.140,0.538,1) (8.140,0.538,1) (8.140,0.538,1) (8.140,0.538,1) (8.140,0.538,1) (8.140,0.538,1) (8.140,0.538,1) (8.140,0.538,1) (8.140,0.538,1) (8.140,0.538,1) (8.140,0.538,1) (8.140,0.538,1) (8.140,0.538,1) (8.140,0.538,1) (8.140,0.538,1) (8.140,0.538,1) (8.140,0.538,1) (8.140,0.538,1) (8.140,0.538,1) (8.140,0.538,1) (5.960,0.499,1) (5.960,0.499,1) (5.960,0.499,1) (5.960,0.499,1) (2.950,0.428,1) (2.950,0.428,1) (6.910,0.448,1) (6.910,0.448,1) (6.910,0.448,1) (6.910,0.448,1) (6.910,0.448,1) (6.910,0.448,1) (6.910,0.448,1) (6.910,0.448,1) (6.910,0.448,1) (5.640,0.439,1) (5.640,0.439,1) (5.640,0.439,1) (5.640,0.439,1) (4.000,0.410,1) (1.220,0.403,1) (0.740,0.410,1) (1.320,0.411,1) (5.130,0.453,1) (5.130,0.453,1) (5.130,0.453,1) (5.130,0.453,1) (5.130,0.453,1) (5.130,0.453,1) (1.380,0.416,1) (3.370,0.398,1) (3.370,0.398,1) (6.070,0.409,1) (6.070,0.409,1) (6.070,0.409,1) (10.810,0.413,1) (10.810,0.413,1) (10.810,0.413,1) (10.810,0.413,1) (12.830,0.437,1) (12.830,0.437,1) (12.830,0.437,1) (12.830,0.437,1) (12.830,0.437,1) (12.830,0.437,1) (4.860,0.426,1) (4.860,0.426,1) (4.860,0.426,1) (4.860,0.426,1) (4.490,0.449,1) (4.490,0.449,1) (4.490,0.449,1) (4.490,0.449,1) (3.410,0.489,1) (3.410,0.489,1) (3.410,0.489,1) (3.410,0.489,1) (15.040,0.464,1) (15.040,0.464,1) (15.040,0.464,1) (2.890,0.445,1) (2.890,0.445,1) (2.890,0.445,1) (2.890,0.445,1) (2.890,0.445,1) (8.560,0.520,1) (8.560,0.520,1) (8.560,0.520,1) (8.560,0.520,1) (8.560,0.520,1) (8.560,0.520,1) (8.560,0.520,1) (8.560,0.520,1) (8.560,0.520,1) (8.560,0.520,1) (8.560,0.520,1) (10.010,0.547,1) (10.010,0.547,1) (10.010,0.547,1) (10.010,0.547,1) (10.010,0.547,1) (10.010,0.547,1) (10.010,0.547,1) (10.010,0.547,1) (10.010,0.547,1) (25.650,0.581,1) (25.650,0.581,1) (25.650,0.581,1) (25.650,0.581,1) (25.650,0.581,1) (25.650,0.581,1) (25.650,0.581,1) (21.890,0.624,1) (21.890,0.624,1) (21.890,0.624,1) (21.890,0.624,1) (21.890,0.624,1) (21.890,0.624,1) (21.890,0.624,1) (21.890,0.624,1) (21.890,0.624,1) (21.890,0.624,1) (21.890,0.624,1) (21.890,0.624,1) (21.890,0.624,1) (21.890,0.624,1) (21.890,0.624,1) (19.580,0.871,1) (19.580,0.871,1) (19.580,0.871,1) (19.580,0.871,1) (19.580,0.871,1) (19.580,0.871,1) (19.580,0.871,1) (19.580,0.871,1) (19.580,0.871,1) (19.580,0.871,1) (19.580,0.871,1) (19.580,0.871,1) (19.580,0.871,1) (19.580,0.871,1) (19.580,0.871,1) (19.580,0.605,1) (19.580,0.605,1) (19.580,0.871,1) (19.580,0.605,1) (19.580,0.605,1) (19.580,0.605,1) (19.580,0.605,1) (19.580,0.605,1) (19.580,0.605,1) (19.580,0.605,1) (19.580,0.605,1) (19.580,0.605,1) (19.580,0.605,1) (19.580,0.605,1) (19.580,0.605,1) (4.050,0.510,1) (4.050,0.510,1) (4.050,0.510,1) (4.050,0.510,1) (4.050,0.510,1) (4.050,0.510,1) (4.050,0.510,1) (2.460,0.488,1) (2.460,0.488,1) (2.460,0.488,1) (2.460,0.488,1) (2.460,0.488,1) (2.460,0.488,1) (2.460,0.488,1) (2.460,0.488,1) (3.440,0.437,1) (3.440,0.437,1) (3.440,0.437,1) (3.440,0.437,1) (3.440,0.437,1) (3.440,0.437,1) (2.930,0.401,1) (2.930,0.401,1) (0.460,0.422,1) (1.520,0.404,1) (1.520,0.404,1) (1.520,0.404,1) (1.470,0.403,1) (1.470,0.403,1) (2.030,0.415,1) (2.030,0.415,1) (2.680,0.416,1) (2.680,0.416,1) (10.590,0.489,1) (10.590,0.489,1) (10.590,0.489,1) (10.590,0.489,1) (10.590,0.489,1) (10.590,0.489,1) (10.590,0.489,1) (10.590,0.489,1) (10.590,0.489,1) (10.590,0.489,1) (10.590,0.489,1) (13.890,0.550,1) (13.890,0.550,1) (13.890,0.550,1) (13.890,0.550,1) (6.200,0.507,1) (6.200,0.507,1) (6.200,0.507,1) (6.200,0.507,1) (6.200,0.504,1) (6.200,0.504,1) (6.200,0.504,1) (6.200,0.504,1) (6.200,0.504,1) (6.200,0.504,1) (6.200,0.504,1) (6.200,0.504,1) (6.200,0.507,1) (6.200,0.507,1) (6.200,0.507,1) (6.200,0.507,1) (6.200,0.507,1) (6.200,0.507,1) (4.930,0.428,1) (4.930,0.428,1) (4.930,0.428,1) (4.930,0.428,1) (4.930,0.428,1) (4.930,0.428,1) (5.860,0.431,1) (5.860,0.431,1) (5.860,0.431,1) (5.860,0.431,1) (5.860,0.431,1) (5.860,0.431,1) (5.860,0.431,1) (5.860,0.431,1) (5.860,0.431,1) (5.860,0.431,1) (3.640,0.392,1) (3.640,0.392,1) (3.750,0.394,1) (3.970,0.647,1) (3.970,0.647,1) (3.970,0.647,1) (3.970,0.647,1) (3.970,0.647,1) (3.970,0.647,1) (3.970,0.647,1) (3.970,0.647,1) (3.970,0.647,1) (3.970,0.647,1) (3.970,0.575,1) (3.970,0.575,1) (6.960,0.464,1) (6.960,0.464,1) (6.960,0.464,1) (6.960,0.464,1) (6.960,0.464,1) (6.410,0.447,1) (6.410,0.447,1) (6.410,0.447,1) (6.410,0.447,1) (6.410,0.447,1) (3.330,0.443,1) (3.330,0.443,1) (3.330,0.443,1) (3.330,0.443,1) (1.210,0.401,1) (2.970,0.400,1) (2.250,0.389,1) (1.760,0.385,1) (5.320,0.405,1) (5.320,0.405,1) (5.320,0.405,1) (4.950,0.411,1) (4.950,0.411,1) (4.950,0.411,1) (13.920,0.437,1) (13.920,0.437,1) (13.920,0.437,1) (13.920,0.437,1) (13.920,0.437,1) (2.240,0.400,1) (2.240,0.400,1) (2.240,0.400,1) (6.090,0.433,1) (6.090,0.433,1) (6.090,0.433,1) (2.180,0.472,1) (2.180,0.472,1) (2.180,0.472,1) (2.180,0.472,1) (9.900,0.544,1) (9.900,0.544,1) (9.900,0.544,1) (9.900,0.544,1) (9.900,0.544,1) (9.900,0.544,1) (9.900,0.544,1) (9.900,0.544,1) (9.900,0.544,1) (9.900,0.544,1) (9.900,0.544,1) (9.900,0.544,1) (7.380,0.493,1) (7.380,0.493,1) (7.380,0.493,1) (7.380,0.493,1) (7.380,0.493,1) (7.380,0.493,1) (7.380,0.493,1) (7.380,0.493,1) (3.240,0.460,1) (3.240,0.460,1) (3.240,0.460,1) (6.060,0.438,1) (6.060,0.438,1) (5.190,0.515,1) (5.190,0.515,1) (5.190,0.515,1) (5.190,0.515,1) (5.190,0.515,1) (5.190,0.515,1) (5.190,0.515,1) (5.190,0.515,1) (1.520,0.442,1) (1.890,0.518,1) (3.780,0.484,1) (3.780,0.484,1) (4.390,0.442,1) (4.390,0.442,1) (4.150,0.429,1) (2.010,0.435,1) (1.250,0.429,1) (1.250,0.429,1) (1.690,0.411,1) (1.690,0.411,1) (2.020,0.410,1) (1.910,0.413,1) (1.910,0.413,1) (18.100,0.770,1) (18.100,0.770,1) (18.100,0.770,1) (18.100,0.770,1) (18.100,0.770,1) (18.100,0.770,1) (18.100,0.770,1) (18.100,0.770,1) (18.100,0.718,1) (18.100,0.718,1) (18.100,0.718,1) (18.100,0.631,1) (18.100,0.631,1) (18.100,0.631,1) (18.100,0.631,1) (18.100,0.631,1) (18.100,0.668,1) (18.100,0.668,1) (18.100,0.668,1) (18.100,0.671,1) (18.100,0.671,1) (18.100,0.671,1) (18.100,0.671,1) (18.100,0.671,1) (18.100,0.671,1) (18.100,0.671,1) (18.100,0.700,1) (18.100,0.700,1) (18.100,0.700,1) (18.100,0.700,1) (18.100,0.700,1) (18.100,0.700,1) (18.100,0.700,1) (18.100,0.700,1) (18.100,0.700,1) (18.100,0.700,1) (18.100,0.700,1) (18.100,0.693,1) (18.100,0.693,1) (18.100,0.693,1) (18.100,0.693,1) (18.100,0.693,1) (18.100,0.693,1) (18.100,0.693,1) (18.100,0.693,1) (18.100,0.693,1) (18.100,0.693,1) (18.100,0.693,1) (18.100,0.693,1) (18.100,0.693,1) (18.100,0.659,1) (18.100,0.659,1) (18.100,0.597,1) (18.100,0.597,1) (18.100,0.597,1) (18.100,0.597,1) (18.100,0.597,1) (18.100,0.597,1) (18.100,0.693,1) (18.100,0.679,1) (18.100,0.679,1) (18.100,0.679,1) (18.100,0.679,1) (18.100,0.718,1) (18.100,0.718,1) (18.100,0.718,1) (18.100,0.614,1) (18.100,0.614,1) (18.100,0.584,1) (18.100,0.679,1) (18.100,0.584,1) (18.100,0.679,1) (18.100,0.679,1) (18.100,0.679,1) (18.100,0.584,1) (18.100,0.584,1) (18.100,0.584,1) (18.100,0.713,1) (18.100,0.713,1) (18.100,0.740,1) (18.100,0.740,1) (18.100,0.740,1) (18.100,0.740,1) (18.100,0.740,1) (18.100,0.740,1) (18.100,0.740,1) (18.100,0.740,1) (18.100,0.740,1) (18.100,0.740,1) (18.100,0.740,1) (18.100,0.740,1) (18.100,0.740,1) (18.100,0.713,1) (18.100,0.713,1) (18.100,0.713,1) (18.100,0.713,1) (18.100,0.713,1) (18.100,0.713,1) (18.100,0.713,1) (18.100,0.713,1) (18.100,0.713,1) (18.100,0.713,1) (18.100,0.713,1) (18.100,0.713,1) (18.100,0.713,1) (18.100,0.713,1) (18.100,0.713,1) (18.100,0.713,1) (18.100,0.655,1) (18.100,0.655,1) (18.100,0.655,1) (18.100,0.584,1) (18.100,0.580,1) (18.100,0.580,1) (18.100,0.580,1) (18.100,0.532,1) (18.100,0.580,1) (18.100,0.614,1) (18.100,0.584,1) (18.100,0.584,1) (18.100,0.614,1) (18.100,0.614,1) (18.100,0.614,1) (18.100,0.614,1) (18.100,0.532,1) (18.100,0.532,1) (18.100,0.532,1) (18.100,0.532,1) (18.100,0.583,1) (18.100,0.583,1) (18.100,0.583,1) (18.100,0.583,1) (27.740,0.609,1) (27.740,0.609,1) (27.740,0.609,1) (27.740,0.609,1) (27.740,0.609,1) (9.690,0.585,1) (9.690,0.585,1) (9.690,0.585,1) (9.690,0.585,1) (9.690,0.585,1) (9.690,0.585,1) (9.690,0.585,1) (9.690,0.585,1) (11.930,0.573,1) (11.930,0.573,1) (11.930,0.573,1) (11.930,0.573,1) (11.930,0.573,1) };

    \nextgroupplot[
			view={0}{90},
			enlargelimits=0,
			zmin=0.0, zmax=1.0,
			xlabel=E,
			ylabel=K,
			%colorbar,
			point meta min=0, point meta max=0.5,
			colormap={}{ gray(0cm)=(1); gray(1cm)=(0);}
			%colorbar style={
			 %       ytick={0,0.05,...,0.5},
			  %      yticklabel style={
			   %         text width=2.5em,
			    %        align=right,
			     %       /pgf/number format/.cd,
			      %          fixed,
			       %         fixed zerofill
			        %}
			    %}
			]

    		\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.5610,2.9000,0.0035) (3.7120,2.9000,0.0035) (3.7120,51.4000,0.0035) (3.5610,51.4000,0.0035)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.5610,51.4000,0.0015) (3.7120,51.4000,0.0015) (3.7120,77.7500,0.0015) (3.5610,77.7500,0.0015)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.5610,77.7500,0.0050) (3.7120,77.7500,0.0050) (3.7120,100.0000,0.0050) (3.5610,100.0000,0.0050)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.7120,2.9000,0.1580) (6.5425,2.9000,0.1580) (6.5425,51.4000,0.1580) (3.7120,51.4000,0.1580)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.7120,51.4000,0.1440) (6.5425,51.4000,0.1440) (6.5425,77.7500,0.1440) (3.7120,77.7500,0.1440)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.7120,77.7500,0.4130) (6.5425,77.7500,0.4130) (6.5425,100.0000,0.4130) (3.7120,100.0000,0.4130)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.5425,2.9000,0.0950) (7.4370,2.9000,0.0950) (7.4370,51.4000,0.0950) (6.5425,51.4000,0.0950)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.5425,51.4000,0.0550) (7.4370,51.4000,0.0550) (7.4370,77.7500,0.0550) (6.5425,77.7500,0.0550)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.5425,77.7500,0.0710) (7.4370,77.7500,0.0710) (7.4370,100.0000,0.0710) (6.5425,100.0000,0.0710)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.4370,2.9000,0.0350) (8.7800,2.9000,0.0350) (8.7800,51.4000,0.0350) (7.4370,51.4000,0.0350)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.4370,51.4000,0.0085) (8.7800,51.4000,0.0085) (8.7800,77.7500,0.0085) (7.4370,77.7500,0.0085)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(7.4370,77.7500,0.0105) (8.7800,77.7500,0.0105) (8.7800,100.0000,0.0105) (7.4370,100.0000,0.0105)};

			\addplot3[mark=+, draw=none, mark size=0.7] coordinates {
(6.575,65.200,1) (6.421,78.900,1) (7.185,61.100,1) (6.998,45.800,1) (7.147,54.200,1) (6.430,58.700,1) (6.012,66.600,1) (6.172,96.100,1) (5.631,100.000,1) (6.004,85.900,1) (6.377,94.300,1) (6.009,82.900,1) (5.889,39.000,1) (5.949,61.800,1) (6.096,84.500,1) (5.834,56.500,1) (5.935,29.300,1) (5.990,81.700,1) (5.456,36.600,1) (5.727,69.500,1) (5.570,98.100,1) (5.965,89.200,1) (6.142,91.700,1) (5.813,100.000,1) (5.924,94.100,1) (5.599,85.700,1) (5.813,90.300,1) (6.047,88.800,1) (6.495,94.400,1) (6.674,87.300,1) (5.713,94.100,1) (6.072,100.000,1) (5.950,82.000,1) (5.701,95.000,1) (6.096,96.900,1) (5.933,68.200,1) (5.841,61.400,1) (5.850,41.500,1) (5.966,30.200,1) (6.595,21.800,1) (7.024,15.800,1) (6.770,2.900,1) (6.169,6.600,1) (6.211,6.500,1) (6.069,40.000,1) (5.682,33.800,1) (5.786,33.300,1) (6.030,85.500,1) (5.399,95.300,1) (5.602,62.000,1) (5.963,45.700,1) (6.115,63.000,1) (6.511,21.100,1) (5.998,21.400,1) (5.888,47.600,1) (7.249,21.900,1) (6.383,35.700,1) (6.816,40.500,1) (6.145,29.200,1) (5.927,47.200,1) (5.741,66.200,1) (5.966,93.400,1) (6.456,67.800,1) (6.762,43.400,1) (7.104,59.500,1) (6.290,17.800,1) (5.787,31.100,1) (5.878,21.400,1) (5.594,36.800,1) (5.885,33.000,1) (6.417,6.600,1) (5.961,17.500,1) (6.065,7.800,1) (6.245,6.200,1) (6.273,6.000,1) (6.286,45.000,1) (6.279,74.500,1) (6.140,45.800,1) (6.232,53.700,1) (5.874,36.600,1) (6.727,33.500,1) (6.619,70.400,1) (6.302,32.200,1) (6.167,46.700,1) (6.389,48.000,1) (6.630,56.100,1) (6.015,45.100,1) (6.121,56.800,1) (7.007,86.300,1) (7.079,63.100,1) (6.417,66.100,1) (6.405,73.900,1) (6.442,53.600,1) (6.211,28.900,1) (6.249,77.300,1) (6.625,57.800,1) (6.163,69.600,1) (8.069,76.000,1) (7.820,36.900,1) (7.416,62.500,1) (6.727,79.900,1) (6.781,71.300,1) (6.405,85.400,1) (6.137,87.400,1) (6.167,90.000,1) (5.851,96.700,1) (5.836,91.900,1) (6.127,85.200,1) (6.474,97.100,1) (6.229,91.200,1) (6.195,54.400,1) (6.715,81.600,1) (5.913,92.900,1) (6.092,95.400,1) (6.254,84.200,1) (5.928,88.200,1) (6.176,72.500,1) (6.021,82.600,1) (5.872,73.100,1) (5.731,65.200,1) (5.870,69.700,1) (6.004,84.100,1) (5.961,92.900,1) (5.856,97.000,1) (5.879,95.800,1) (5.986,88.400,1) (5.613,95.600,1) (5.693,96.000,1) (6.431,98.800,1) (5.637,94.700,1) (6.458,98.900,1) (6.326,97.700,1) (6.372,97.900,1) (5.822,95.400,1) (5.757,98.400,1) (6.335,98.200,1) (5.942,93.500,1) (6.454,98.400,1) (5.857,98.200,1) (6.151,97.900,1) (6.174,93.600,1) (5.019,100.000,1) (5.403,100.000,1) (5.468,100.000,1) (4.903,97.800,1) (6.130,100.000,1) (5.628,100.000,1) (4.926,95.700,1) (5.186,93.800,1) (5.597,94.900,1) (6.122,97.300,1) (5.404,100.000,1) (5.012,88.000,1) (5.709,98.500,1) (6.129,96.000,1) (6.152,82.600,1) (5.272,94.000,1) (6.943,97.400,1) (6.066,100.000,1) (6.510,100.000,1) (6.250,92.600,1) (7.489,90.800,1) (7.802,98.200,1) (8.375,93.900,1) (5.854,91.800,1) (6.101,93.000,1) (7.929,96.200,1) (5.877,79.200,1) (6.319,96.100,1) (6.402,95.200,1) (5.875,94.600,1) (5.880,97.300,1) (5.572,88.500,1) (6.416,84.100,1) (5.859,68.700,1) (6.546,33.100,1) (6.020,47.200,1) (6.315,73.400,1) (6.860,74.400,1) (6.980,58.400,1) (7.765,83.300,1) (6.144,62.200,1) (7.155,92.200,1) (6.563,95.600,1) (5.604,89.800,1) (6.153,68.800,1) (7.831,53.600,1) (6.782,41.100,1) (6.556,29.100,1) (7.185,38.900,1) (6.951,21.500,1) (6.739,30.800,1) (7.178,26.300,1) (6.800,9.900,1) (6.604,18.800,1) (7.875,32.000,1) (7.287,34.100,1) (7.107,36.600,1) (7.274,38.300,1) (6.975,15.300,1) (7.135,13.900,1) (6.162,38.400,1) (7.610,15.700,1) (7.853,33.200,1) (8.034,31.900,1) (5.891,22.300,1) (6.326,52.500,1) (5.783,72.700,1) (6.064,59.100,1) (5.344,100.000,1) (5.960,92.100,1) (5.404,88.600,1) (5.807,53.800,1) (6.375,32.300,1) (5.412,9.800,1) (6.182,42.400,1) (5.888,56.000,1) (6.642,85.100,1) (5.951,93.800,1) (6.373,92.400,1) (6.951,88.500,1) (6.164,91.300,1) (6.879,77.700,1) (6.618,80.800,1) (8.266,78.300,1) (8.725,83.000,1) (8.040,86.500,1) (7.163,79.900,1) (7.686,17.000,1) (6.552,21.400,1) (5.981,68.100,1) (7.412,76.900,1) (8.337,73.300,1) (8.247,70.400,1) (6.726,66.500,1) (6.086,61.500,1) (6.631,76.500,1) (7.358,71.600,1) (6.481,18.500,1) (6.606,42.200,1) (6.897,54.300,1) (6.095,65.100,1) (6.358,52.900,1) (6.393,7.800,1) (5.593,76.500,1) (5.605,70.200,1) (6.108,34.900,1) (6.226,79.200,1) (6.433,49.100,1) (6.718,17.500,1) (6.487,13.000,1) (6.438,8.900,1) (6.957,6.800,1) (8.259,8.400,1) (6.108,32.000,1) (5.876,19.100,1) (7.454,34.200,1) (8.704,86.900,1) (7.333,100.000,1) (6.842,100.000,1) (7.203,81.800,1) (7.520,89.400,1) (8.398,91.500,1) (7.327,94.500,1) (7.206,91.600,1) (5.560,62.800,1) (7.014,84.600,1) (8.297,67.000,1) (7.470,52.600,1) (5.920,61.500,1) (5.856,42.100,1) (6.240,16.300,1) (6.538,58.700,1) (7.691,51.800,1) (6.758,32.900,1) (6.854,42.800,1) (7.267,49.000,1) (6.826,27.600,1) (6.482,32.100,1) (6.812,32.200,1) (7.820,64.500,1) (6.968,37.200,1) (7.645,49.700,1) (7.923,24.800,1) (7.088,20.800,1) (6.453,31.900,1) (6.230,31.500,1) (6.209,31.300,1) (6.315,45.600,1) (6.565,22.900,1) (6.861,27.900,1) (7.148,27.700,1) (6.630,23.400,1) (6.127,18.400,1) (6.009,42.300,1) (6.678,31.100,1) (6.549,51.000,1) (5.790,58.000,1) (6.345,20.100,1) (7.041,10.000,1) (6.871,47.400,1) (6.590,40.400,1) (6.495,18.400,1) (6.982,17.700,1) (7.236,41.100,1) (6.616,58.100,1) (7.420,71.900,1) (6.849,70.300,1) (6.635,82.500,1) (5.972,76.700,1) (4.973,37.800,1) (6.122,52.800,1) (6.023,90.400,1) (6.266,82.800,1) (6.567,87.300,1) (5.705,77.700,1) (5.914,83.200,1) (5.782,71.700,1) (6.382,67.200,1) (6.113,58.800,1) (6.426,52.300,1) (6.376,54.300,1) (6.041,49.900,1) (5.708,74.300,1) (6.415,40.100,1) (6.431,14.700,1) (6.312,28.900,1) (6.083,43.700,1) (5.868,25.800,1) (6.333,17.200,1) (6.144,32.200,1) (5.706,28.400,1) (6.031,23.300,1) (6.316,38.100,1) (6.310,38.500,1) (6.037,34.500,1) (5.869,46.300,1) (5.895,59.600,1) (6.059,37.300,1) (5.985,45.400,1) (5.968,58.500,1) (7.241,49.300,1) (6.540,59.700,1) (6.696,56.400,1) (6.874,28.100,1) (6.014,48.500,1) (5.898,52.300,1) (6.516,27.700,1) (6.635,29.700,1) (6.939,34.500,1) (6.490,44.400,1) (6.579,35.900,1) (5.884,18.500,1) (6.728,36.100,1) (5.663,21.900,1) (5.936,19.500,1) (6.212,97.400,1) (6.395,91.000,1) (6.127,83.400,1) (6.112,81.300,1) (6.398,88.000,1) (6.251,91.100,1) (5.362,96.200,1) (5.803,89.000,1) (8.780,82.900,1) (3.561,87.900,1) (4.963,91.400,1) (3.863,100.000,1) (4.970,100.000,1) (6.683,96.800,1) (7.016,97.500,1) (6.216,100.000,1) (5.875,89.600,1) (4.906,100.000,1) (4.138,100.000,1) (7.313,97.900,1) (6.649,93.300,1) (6.794,98.800,1) (6.380,96.200,1) (6.223,100.000,1) (6.968,91.900,1) (6.545,99.100,1) (5.536,100.000,1) (5.520,100.000,1) (4.368,91.200,1) (5.277,98.100,1) (4.652,100.000,1) (5.000,89.500,1) (4.880,100.000,1) (5.390,98.900,1) (5.713,97.000,1) (6.051,82.500,1) (5.036,97.000,1) (6.193,92.600,1) (5.887,94.700,1) (6.471,98.800,1) (6.405,96.000,1) (5.747,98.900,1) (5.453,100.000,1) (5.852,77.800,1) (5.987,100.000,1) (6.343,100.000,1) (6.404,100.000,1) (5.349,96.000,1) (5.531,85.400,1) (5.683,100.000,1) (4.138,100.000,1) (5.608,100.000,1) (5.617,97.900,1) (6.852,100.000,1) (5.757,100.000,1) (6.657,100.000,1) (4.628,100.000,1) (5.155,100.000,1) (4.519,100.000,1) (6.434,100.000,1) (6.782,90.800,1) (5.304,89.100,1) (5.957,100.000,1) (6.824,76.500,1) (6.411,100.000,1) (6.006,95.300,1) (5.648,87.600,1) (6.103,85.100,1) (5.565,70.600,1) (5.896,95.400,1) (5.837,59.700,1) (6.202,78.700,1) (6.193,78.100,1) (6.380,95.600,1) (6.348,86.100,1) (6.833,94.300,1) (6.425,74.800,1) (6.436,87.900,1) (6.208,95.000,1) (6.629,94.600,1) (6.461,93.300,1) (6.152,100.000,1) (5.935,87.900,1) (5.627,93.900,1) (5.818,92.400,1) (6.406,97.200,1) (6.219,100.000,1) (6.485,100.000,1) (5.854,96.600,1) (6.459,94.800,1) (6.341,96.400,1) (6.251,96.600,1) (6.185,98.700,1) (6.417,98.300,1) (6.749,92.600,1) (6.655,98.200,1) (6.297,91.800,1) (7.393,99.300,1) (6.728,94.100,1) (6.525,86.500,1) (5.976,87.900,1) (5.936,80.300,1) (6.301,83.700,1) (6.081,84.400,1) (6.701,90.000,1) (6.376,88.400,1) (6.317,83.000,1) (6.513,89.900,1) (6.209,65.400,1) (5.759,48.200,1) (5.952,84.700,1) (6.003,94.500,1) (5.926,71.000,1) (5.713,56.700,1) (6.167,84.000,1) (6.229,90.700,1) (6.437,75.000,1) (6.980,67.600,1) (5.427,95.400,1) (6.162,97.400,1) (6.484,93.600,1) (5.304,97.300,1) (6.185,96.700,1) (6.229,88.000,1) (6.242,64.700,1) (6.750,74.900,1) (7.061,77.000,1) (5.762,40.300,1) (5.871,41.900,1) (6.312,51.900,1) (6.114,79.800,1) (5.905,53.200,1) (5.454,92.700,1) (5.414,98.300,1) (5.093,98.000,1) (5.983,98.800,1) (5.983,83.500,1) (5.707,54.000,1) (5.926,42.600,1) (5.670,28.800,1) (5.390,72.900,1) (5.794,70.600,1) (6.019,65.300,1) (5.569,73.500,1) (6.027,79.700,1) (6.593,69.100,1) (6.120,76.700,1) (6.976,91.000,1) (6.794,89.300,1) (6.030,80.800,1) };
  \end{groupplot}
\end{tikzpicture}

### 2015-11-22 probability_plot_old/graph_housing_exp1_distr_8_5.tex
Change all plots from probability to probability density

\begin{tikzpicture}
		\begin{axis}[
			view={0}{90},
			enlargelimits=0,
			zmin=0.0, zmax=1.0,
			xlabel=$H$,
			ylabel=$E$,
			colorbar,
			point meta min=0, point meta max=0.5,
			colormap={}{ gray(0cm)=(1); gray(1cm)=(0);},
			colorbar style={
			        ytick={0,0.05,...,0.51},
			        ylabel=probability density,
			        y label style={at={(axis description cs:6.5,0.5)},rotate=180,anchor=north},
			        yticklabel style={
			            text width=2.5em,
			            align=right,
			            /pgf/number format/.cd,
			                fixed,
			                fixed zerofill
			        }
			    }
			]

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.3850,0.0000) (1.9204,0.3850,0.0000) (1.9204,0.4405,0.0000) (1.1296,0.4405,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.4405,0.0000) (1.9204,0.4405,0.0000) (1.9204,0.4860,0.0000) (1.1296,0.4860,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.4860,0.0000) (1.9204,0.4860,0.0000) (1.9204,0.4910,0.0000) (1.1296,0.4910,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.4910,0.0000) (1.9204,0.4910,0.0000) (1.9204,0.4960,0.0000) (1.1296,0.4960,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.4960,0.0000) (1.9204,0.4960,0.0000) (1.9204,0.5190,0.0000) (1.1296,0.5190,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.5190,0.0000) (1.9204,0.5190,0.0000) (1.9204,0.5220,0.0000) (1.1296,0.5220,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.5220,0.0000) (1.9204,0.5220,0.0000) (1.9204,0.5280,0.0000) (1.1296,0.5280,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.5280,0.0000) (1.9204,0.5280,0.0000) (1.9204,0.5410,0.0000) (1.1296,0.5410,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.5410,0.0000) (1.9204,0.5410,0.0000) (1.9204,0.5455,0.0000) (1.1296,0.5455,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.5455,0.0025) (1.9204,0.5455,0.0025) (1.9204,0.5910,0.0025) (1.1296,0.5910,0.0025)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.5910,0.0425) (1.9204,0.5910,0.0425) (1.9204,0.6390,0.0425) (1.1296,0.6390,0.0425)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.6390,0.0065) (1.9204,0.6390,0.0065) (1.9204,0.6510,0.0065) (1.1296,0.6510,0.0065)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.6510,0.1040) (1.9204,0.6510,0.1040) (1.9204,0.8205,0.1040) (1.1296,0.8205,0.1040)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.8205,0.0300) (1.9204,0.8205,0.0300) (1.9204,0.8710,0.0300) (1.1296,0.8710,0.0300)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.3850,0.0000) (2.5884,0.3850,0.0000) (2.5884,0.4405,0.0000) (1.9204,0.4405,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.4405,0.0000) (2.5884,0.4405,0.0000) (2.5884,0.4860,0.0000) (1.9204,0.4860,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.4860,0.0000) (2.5884,0.4860,0.0000) (2.5884,0.4910,0.0000) (1.9204,0.4910,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.4910,0.0000) (2.5884,0.4910,0.0000) (2.5884,0.4960,0.0000) (1.9204,0.4960,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.4960,0.0000) (2.5884,0.4960,0.0000) (2.5884,0.5190,0.0000) (1.9204,0.5190,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.5190,0.0085) (2.5884,0.5190,0.0085) (2.5884,0.5220,0.0085) (1.9204,0.5220,0.0085)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.5220,0.0000) (2.5884,0.5220,0.0000) (2.5884,0.5280,0.0000) (1.9204,0.5280,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.5280,0.0000) (2.5884,0.5280,0.0000) (2.5884,0.5410,0.0000) (1.9204,0.5410,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.5410,0.0025) (2.5884,0.5410,0.0025) (2.5884,0.5455,0.0025) (1.9204,0.5455,0.0025)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.5455,0.0580) (2.5884,0.5455,0.0580) (2.5884,0.5910,0.0580) (1.9204,0.5910,0.0580)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.5910,0.0485) (2.5884,0.5910,0.0485) (2.5884,0.6390,0.0485) (1.9204,0.6390,0.0485)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.6390,0.0120) (2.5884,0.6390,0.0120) (2.5884,0.6510,0.0120) (1.9204,0.6510,0.0120)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.6510,0.0665) (2.5884,0.6510,0.0665) (2.5884,0.8205,0.0665) (1.9204,0.8205,0.0665)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.8205,0.0000) (2.5884,0.8205,0.0000) (2.5884,0.8710,0.0000) (1.9204,0.8710,0.0000)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.3850,0.0000) (3.0793,0.3850,0.0000) (3.0793,0.4405,0.0000) (2.5884,0.4405,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.4405,0.0000) (3.0793,0.4405,0.0000) (3.0793,0.4860,0.0000) (2.5884,0.4860,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.4860,0.0115) (3.0793,0.4860,0.0115) (3.0793,0.4910,0.0115) (2.5884,0.4910,0.0115)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.4910,0.0000) (3.0793,0.4910,0.0000) (3.0793,0.4960,0.0000) (2.5884,0.4960,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.4960,0.0160) (3.0793,0.4960,0.0160) (3.0793,0.5190,0.0160) (2.5884,0.5190,0.0160)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.5190,0.0065) (3.0793,0.5190,0.0065) (3.0793,0.5220,0.0065) (2.5884,0.5220,0.0065)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.5220,0.0000) (3.0793,0.5220,0.0000) (3.0793,0.5280,0.0000) (2.5884,0.5280,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.5280,0.0000) (3.0793,0.5280,0.0000) (3.0793,0.5410,0.0000) (2.5884,0.5410,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.5410,0.0040) (3.0793,0.5410,0.0040) (3.0793,0.5455,0.0040) (2.5884,0.5455,0.0040)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.5455,0.0250) (3.0793,0.5455,0.0250) (3.0793,0.5910,0.0250) (2.5884,0.5910,0.0250)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.5910,0.0000) (3.0793,0.5910,0.0000) (3.0793,0.6390,0.0000) (2.5884,0.6390,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.6390,0.0000) (3.0793,0.6390,0.0000) (3.0793,0.6510,0.0000) (2.5884,0.6510,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.6510,0.0250) (3.0793,0.6510,0.0250) (3.0793,0.8205,0.0250) (2.5884,0.8205,0.0250)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.8205,0.0000) (3.0793,0.8205,0.0000) (3.0793,0.8710,0.0000) (2.5884,0.8710,0.0000)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.3850,0.0100) (4.4802,0.3850,0.0100) (4.4802,0.4405,0.0100) (3.0793,0.4405,0.0100)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.4405,0.0495) (4.4802,0.4405,0.0495) (4.4802,0.4860,0.0495) (3.0793,0.4860,0.0495)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.4860,0.0345) (4.4802,0.4860,0.0345) (4.4802,0.4910,0.0345) (3.0793,0.4910,0.0345)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.4910,0.0000) (4.4802,0.4910,0.0000) (4.4802,0.4960,0.0000) (3.0793,0.4960,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.4960,0.0425) (4.4802,0.4960,0.0425) (4.4802,0.5190,0.0425) (3.0793,0.5190,0.0425)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.5190,0.0000) (4.4802,0.5190,0.0000) (4.4802,0.5220,0.0000) (3.0793,0.5220,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.5220,0.0000) (4.4802,0.5220,0.0000) (4.4802,0.5280,0.0000) (3.0793,0.5280,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.5280,0.0525) (4.4802,0.5280,0.0525) (4.4802,0.5410,0.0525) (3.0793,0.5410,0.0525)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.5410,0.0155) (4.4802,0.5410,0.0155) (4.4802,0.5455,0.0155) (3.0793,0.5455,0.0155)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.5455,0.0135) (4.4802,0.5455,0.0135) (4.4802,0.5910,0.0135) (3.0793,0.5910,0.0135)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.5910,0.0000) (4.4802,0.5910,0.0000) (4.4802,0.6390,0.0000) (3.0793,0.6390,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.6390,0.0000) (4.4802,0.6390,0.0000) (4.4802,0.6510,0.0000) (3.0793,0.6510,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.6510,0.0000) (4.4802,0.6510,0.0000) (4.4802,0.8205,0.0000) (3.0793,0.8205,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.8205,0.0000) (4.4802,0.8205,0.0000) (4.4802,0.8710,0.0000) (3.0793,0.8710,0.0000)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.3850,0.0080) (4.7503,0.3850,0.0080) (4.7503,0.4405,0.0080) (4.4802,0.4405,0.0080)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.4405,0.0035) (4.7503,0.4405,0.0035) (4.7503,0.4860,0.0035) (4.4802,0.4860,0.0035)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.4860,0.0000) (4.7503,0.4860,0.0000) (4.7503,0.4910,0.0000) (4.4802,0.4910,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.4910,0.0100) (4.7503,0.4910,0.0100) (4.7503,0.4960,0.0100) (4.4802,0.4960,0.0100)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.4960,0.0000) (4.7503,0.4960,0.0000) (4.7503,0.5190,0.0000) (4.4802,0.5190,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.5190,0.0000) (4.7503,0.5190,0.0000) (4.7503,0.5220,0.0000) (4.4802,0.5220,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.5220,0.0000) (4.7503,0.5220,0.0000) (4.7503,0.5280,0.0000) (4.4802,0.5280,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.5280,0.0060) (4.7503,0.5280,0.0060) (4.7503,0.5410,0.0060) (4.4802,0.5410,0.0060)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.5410,0.0000) (4.7503,0.5410,0.0000) (4.7503,0.5455,0.0000) (4.4802,0.5455,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.5455,0.0000) (4.7503,0.5455,0.0000) (4.7503,0.5910,0.0000) (4.4802,0.5910,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.5910,0.0000) (4.7503,0.5910,0.0000) (4.7503,0.6390,0.0000) (4.4802,0.6390,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.6390,0.0000) (4.7503,0.6390,0.0000) (4.7503,0.6510,0.0000) (4.4802,0.6510,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.6510,0.0000) (4.7503,0.6510,0.0000) (4.7503,0.8205,0.0000) (4.4802,0.8205,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.8205,0.0000) (4.7503,0.8205,0.0000) (4.7503,0.8710,0.0000) (4.4802,0.8710,0.0000)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.7503,0.3850,0.1860) (12.1265,0.3850,0.1860) (12.1265,0.4405,0.1860) (4.7503,0.4405,0.1860)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.7503,0.4405,0.0615) (12.1265,0.4405,0.0615) (12.1265,0.4860,0.0615) (4.7503,0.4860,0.0615)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.7503,0.4860,0.0000) (12.1265,0.4860,0.0000) (12.1265,0.4910,0.0000) (4.7503,0.4910,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.7503,0.4910,0.0045) (12.1265,0.4910,0.0045) (12.1265,0.4960,0.0045) (4.7503,0.4960,0.0045)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.7503,0.4960,0.0210) (12.1265,0.4960,0.0210) (12.1265,0.5190,0.0210) (4.7503,0.5190,0.0210)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.7503,0.5190,0.0000) (12.1265,0.5190,0.0000) (12.1265,0.5220,0.0000) (4.7503,0.5220,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.7503,0.5220,0.0120) (12.1265,0.5220,0.0120) (12.1265,0.5280,0.0120) (4.7503,0.5280,0.0120)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.7503,0.5280,0.0000) (12.1265,0.5280,0.0000) (12.1265,0.5410,0.0000) (4.7503,0.5410,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.7503,0.5410,0.0000) (12.1265,0.5410,0.0000) (12.1265,0.5455,0.0000) (4.7503,0.5455,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.7503,0.5455,0.0000) (12.1265,0.5455,0.0000) (12.1265,0.5910,0.0000) (4.7503,0.5910,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.7503,0.5910,0.0000) (12.1265,0.5910,0.0000) (12.1265,0.6390,0.0000) (4.7503,0.6390,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.7503,0.6390,0.0000) (12.1265,0.6390,0.0000) (12.1265,0.6510,0.0000) (4.7503,0.6510,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.7503,0.6510,0.0000) (12.1265,0.6510,0.0000) (12.1265,0.8205,0.0000) (4.7503,0.8205,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.7503,0.8205,0.0000) (12.1265,0.8205,0.0000) (12.1265,0.8710,0.0000) (4.7503,0.8710,0.0000)};

			\addplot3[mark=+, draw=none, mark size=1.0, jitter = 0.1] coordinates {
(4.090,0.538,1) (4.967,0.469,1) (4.967,0.469,1) (6.062,0.458,1) (6.062,0.458,1) (6.062,0.458,1) (5.561,0.524,1) (5.950,0.524,1) (6.082,0.524,1) (6.592,0.524,1) (6.347,0.524,1) (6.227,0.524,1) (5.451,0.524,1) (4.707,0.538,1) (4.462,0.538,1) (4.499,0.538,1) (4.499,0.538,1) (4.258,0.538,1) (3.796,0.538,1) (3.796,0.538,1) (3.798,0.538,1) (4.012,0.538,1) (3.977,0.538,1) (4.095,0.538,1) (4.400,0.538,1) (4.455,0.538,1) (4.682,0.538,1) (4.453,0.538,1) (4.455,0.538,1) (4.239,0.538,1) (4.233,0.538,1) (4.175,0.538,1) (3.990,0.538,1) (3.787,0.538,1) (3.760,0.538,1) (3.360,0.499,1) (3.378,0.499,1) (3.934,0.499,1) (3.847,0.499,1) (5.401,0.428,1) (5.401,0.428,1) (5.721,0.448,1) (5.721,0.448,1) (5.721,0.448,1) (5.721,0.448,1) (5.100,0.448,1) (5.100,0.448,1) (5.689,0.448,1) (5.870,0.448,1) (6.088,0.448,1) (6.815,0.439,1) (6.815,0.439,1) (6.815,0.439,1) (6.815,0.439,1) (7.320,0.410,1) (8.697,0.403,1) (9.188,0.410,1) (8.325,0.411,1) (7.815,0.453,1) (6.932,0.453,1) (7.225,0.453,1) (6.819,0.453,1) (7.226,0.453,1) (7.981,0.453,1) (9.223,0.416,1) (6.612,0.398,1) (6.612,0.398,1) (6.498,0.409,1) (6.498,0.409,1) (6.498,0.409,1) (5.287,0.413,1) (5.287,0.413,1) (5.287,0.413,1) (5.287,0.413,1) (4.252,0.437,1) (4.503,0.437,1) (4.052,0.437,1) (4.090,0.437,1) (5.014,0.437,1) (4.503,0.437,1) (5.401,0.426,1) (5.401,0.426,1) (5.401,0.426,1) (5.401,0.426,1) (4.779,0.449,1) (4.438,0.449,1) (4.427,0.449,1) (3.748,0.449,1) (3.422,0.489,1) (3.414,0.489,1) (3.092,0.489,1) (3.092,0.489,1) (3.666,0.464,1) (3.666,0.464,1) (3.615,0.464,1) (3.495,0.445,1) (3.495,0.445,1) (3.495,0.445,1) (3.495,0.445,1) (3.495,0.445,1) (2.778,0.520,1) (2.856,0.520,1) (2.715,0.520,1) (2.715,0.520,1) (2.421,0.520,1) (2.107,0.520,1) (2.211,0.520,1) (2.122,0.520,1) (2.433,0.520,1) (2.545,0.520,1) (2.778,0.520,1) (2.678,0.547,1) (2.353,0.547,1) (2.548,0.547,1) (2.256,0.547,1) (2.463,0.547,1) (2.730,0.547,1) (2.747,0.547,1) (2.478,0.547,1) (2.759,0.547,1) (2.258,0.581,1) (2.197,0.581,1) (2.087,0.581,1) (1.944,0.581,1) (2.006,0.581,1) (1.993,0.581,1) (1.757,0.581,1) (1.788,0.624,1) (1.813,0.624,1) (1.980,0.624,1) (2.119,0.624,1) (2.271,0.624,1) (2.327,0.624,1) (2.470,0.624,1) (2.346,0.624,1) (2.111,0.624,1) (1.967,0.624,1) (1.850,0.624,1) (1.669,0.624,1) (1.669,0.624,1) (1.612,0.624,1) (1.439,0.624,1) (1.322,0.871,1) (1.412,0.871,1) (1.346,0.871,1) (1.419,0.871,1) (1.517,0.871,1) (1.461,0.871,1) (1.530,0.871,1) (1.526,0.871,1) (1.618,0.871,1) (1.592,0.871,1) (1.610,0.871,1) (1.623,0.871,1) (1.749,0.871,1) (1.746,0.871,1) (1.736,0.871,1) (1.877,0.605,1) (1.757,0.605,1) (1.766,0.871,1) (1.798,0.605,1) (1.971,0.605,1) (2.041,0.605,1) (2.162,0.605,1) (2.422,0.605,1) (2.283,0.605,1) (2.046,0.605,1) (2.426,0.605,1) (2.100,0.605,1) (2.263,0.605,1) (2.426,0.605,1) (2.389,0.605,1) (2.596,0.510,1) (2.646,0.510,1) (2.702,0.510,1) (3.132,0.510,1) (3.555,0.510,1) (3.317,0.510,1) (2.915,0.510,1) (2.829,0.488,1) (2.741,0.488,1) (2.598,0.488,1) (2.701,0.488,1) (2.847,0.488,1) (2.988,0.488,1) (3.280,0.488,1) (3.199,0.488,1) (3.789,0.437,1) (4.567,0.437,1) (4.567,0.437,1) (6.480,0.437,1) (6.480,0.437,1) (6.480,0.437,1) (6.220,0.401,1) (6.220,0.401,1) (5.648,0.422,1) (7.309,0.404,1) (7.309,0.404,1) (7.309,0.404,1) (7.653,0.403,1) (7.653,0.403,1) (6.270,0.415,1) (6.270,0.415,1) (5.118,0.416,1) (5.118,0.416,1) (3.945,0.489,1) (4.355,0.489,1) (4.355,0.489,1) (4.239,0.489,1) (3.875,0.489,1) (3.877,0.489,1) (3.665,0.489,1) (3.653,0.489,1) (3.945,0.489,1) (3.587,0.489,1) (3.945,0.489,1) (3.112,0.550,1) (3.421,0.550,1) (2.889,0.550,1) (3.363,0.550,1) (2.862,0.507,1) (3.048,0.507,1) (3.272,0.507,1) (3.272,0.507,1) (2.894,0.504,1) (2.894,0.504,1) (3.216,0.504,1) (3.216,0.504,1) (3.375,0.504,1) (3.375,0.504,1) (3.671,0.504,1) (3.671,0.504,1) (3.838,0.507,1) (3.652,0.507,1) (3.652,0.507,1) (3.652,0.507,1) (4.148,0.507,1) (4.148,0.507,1) (6.190,0.428,1) (6.190,0.428,1) (6.336,0.428,1) (6.336,0.428,1) (7.035,0.428,1) (7.035,0.428,1) (7.955,0.431,1) (7.955,0.431,1) (8.056,0.431,1) (8.056,0.431,1) (7.827,0.431,1) (7.827,0.431,1) (7.397,0.431,1) (7.397,0.431,1) (8.907,0.431,1) (8.907,0.431,1) (9.220,0.392,1) (9.220,0.392,1) (6.336,0.394,1) (1.801,0.647,1) (1.895,0.647,1) (2.011,0.647,1) (2.112,0.647,1) (2.140,0.647,1) (2.288,0.647,1) (2.079,0.647,1) (1.930,0.647,1) (1.986,0.647,1) (2.133,0.647,1) (2.422,0.575,1) (2.872,0.575,1) (3.917,0.464,1) (4.429,0.464,1) (4.429,0.464,1) (3.917,0.464,1) (4.367,0.464,1) (4.078,0.447,1) (4.267,0.447,1) (4.787,0.447,1) (4.863,0.447,1) (4.140,0.447,1) (4.101,0.443,1) (4.695,0.443,1) (5.245,0.443,1) (5.212,0.443,1) (5.885,0.401,1) (7.307,0.400,1) (7.307,0.389,1) (9.089,0.385,1) (7.317,0.405,1) (7.317,0.405,1) (7.317,0.405,1) (5.117,0.411,1) (5.117,0.411,1) (5.117,0.411,1) (5.503,0.437,1) (5.503,0.437,1) (5.960,0.437,1) (5.960,0.437,1) (6.320,0.437,1) (7.828,0.400,1) (7.828,0.400,1) (7.828,0.400,1) (5.492,0.433,1) (5.492,0.433,1) (5.492,0.433,1) (4.022,0.472,1) (3.370,0.472,1) (3.099,0.472,1) (3.183,0.472,1) (3.317,0.544,1) (3.103,0.544,1) (2.519,0.544,1) (2.640,0.544,1) (2.834,0.544,1) (3.263,0.544,1) (3.602,0.544,1) (3.945,0.544,1) (3.999,0.544,1) (4.032,0.544,1) (3.533,0.544,1) (4.002,0.544,1) (4.540,0.493,1) (4.540,0.493,1) (4.721,0.493,1) (4.721,0.493,1) (4.721,0.493,1) (5.416,0.493,1) (5.416,0.493,1) (5.416,0.493,1) (5.215,0.460,1) (5.215,0.460,1) (5.874,0.460,1) (6.641,0.438,1) (6.641,0.438,1) (6.458,0.515,1) (6.458,0.515,1) (5.985,0.515,1) (5.231,0.515,1) (5.615,0.515,1) (4.812,0.515,1) (4.812,0.515,1) (4.812,0.515,1) (7.038,0.442,1) (6.267,0.518,1) (5.732,0.484,1) (6.465,0.484,1) (8.014,0.442,1) (8.014,0.442,1) (8.535,0.429,1) (8.344,0.435,1) (8.792,0.429,1) (8.792,0.429,1) (10.710,0.411,1) (10.710,0.411,1) (12.127,0.410,1) (10.586,0.413,1) (10.586,0.413,1) (2.122,0.770,1) (2.505,0.770,1) (2.723,0.770,1) (2.509,0.770,1) (2.518,0.770,1) (2.296,0.770,1) (2.104,0.770,1) (1.905,0.770,1) (1.905,0.718,1) (1.613,0.718,1) (1.752,0.718,1) (1.511,0.631,1) (1.333,0.631,1) (1.357,0.631,1) (1.202,0.631,1) (1.169,0.631,1) (1.130,0.668,1) (1.174,0.668,1) (1.137,0.668,1) (1.316,0.671,1) (1.345,0.671,1) (1.358,0.671,1) (1.386,0.671,1) (1.386,0.671,1) (1.417,0.671,1) (1.519,0.671,1) (1.580,0.700,1) (1.533,0.700,1) (1.440,0.700,1) (1.426,0.700,1) (1.467,0.700,1) (1.518,0.700,1) (1.589,0.700,1) (1.728,0.700,1) (1.927,0.700,1) (2.168,0.700,1) (1.770,0.700,1) (1.791,0.693,1) (1.782,0.693,1) (1.726,0.693,1) (1.677,0.693,1) (1.633,0.693,1) (1.490,0.693,1) (1.500,0.693,1) (1.589,0.693,1) (1.574,0.693,1) (1.639,0.693,1) (1.703,0.693,1) (1.607,0.693,1) (1.425,0.693,1) (1.178,0.659,1) (1.285,0.659,1) (1.455,0.597,1) (1.466,0.597,1) (1.413,0.597,1) (1.528,0.597,1) (1.554,0.597,1) (1.589,0.597,1) (1.658,0.693,1) (1.835,0.679,1) (1.819,0.679,1) (1.647,0.679,1) (1.803,0.679,1) (1.794,0.718,1) (1.859,0.718,1) (1.875,0.718,1) (1.951,0.614,1) (2.022,0.614,1) (2.063,0.584,1) (1.910,0.679,1) (1.998,0.584,1) (1.863,0.679,1) (1.936,0.679,1) (1.968,0.679,1) (2.053,0.584,1) (2.088,0.584,1) (2.200,0.584,1) (2.316,0.713,1) (2.222,0.713,1) (2.125,0.740,1) (2.003,0.740,1) (1.914,0.740,1) (1.821,0.740,1) (1.817,0.740,1) (1.866,0.740,1) (2.065,0.740,1) (2.005,0.740,1) (1.978,0.740,1) (1.896,0.740,1) (1.988,0.740,1) (2.072,0.740,1) (2.198,0.740,1) (2.262,0.713,1) (2.185,0.713,1) (2.324,0.713,1) (2.355,0.713,1) (2.368,0.713,1) (2.453,0.713,1) (2.496,0.713,1) (2.436,0.713,1) (2.581,0.713,1) (2.779,0.713,1) (2.783,0.713,1) (2.717,0.713,1) (2.598,0.713,1) (2.567,0.713,1) (2.734,0.713,1) (2.802,0.713,1) (2.963,0.655,1) (3.067,0.655,1) (2.872,0.655,1) (2.540,0.584,1) (2.908,0.580,1) (2.824,0.580,1) (3.033,0.580,1) (3.099,0.532,1) (2.897,0.580,1) (2.533,0.614,1) (2.430,0.584,1) (2.206,0.584,1) (2.305,0.614,1) (2.101,0.614,1) (2.171,0.614,1) (1.951,0.614,1) (3.424,0.532,1) (3.332,0.532,1) (3.411,0.532,1) (4.098,0.532,1) (3.724,0.583,1) (3.992,0.583,1) (3.546,0.583,1) (3.152,0.583,1) (1.821,0.609,1) (1.755,0.609,1) (1.823,0.609,1) (1.868,0.609,1) (2.110,0.609,1) (2.382,0.585,1) (2.382,0.585,1) (2.799,0.585,1) (2.799,0.585,1) (2.893,0.585,1) (2.409,0.585,1) (2.400,0.585,1) (2.498,0.585,1) (2.479,0.573,1) (2.288,0.573,1) (2.167,0.573,1) (2.389,0.573,1) (2.505,0.573,1) };
		\end{axis}
	\end{tikzpicture}

### 2015-11-22 probability_plot_old/graph_wine_exp1_distr.tex
Change all plots from probability to probability density

--- 2015-11-17 graph_wine_exp1_distr.tex
@@
   \begin{groupplot}[
-	  	group style={group size=2 by 1,horizontal sep=1cm,
+	  	group style={group size=2 by 1,horizontal sep=1.5em,
   		},
-  		width = 1/2*\textwidth - 1cm,
+  		width = 1/2*\textwidth - 1em,
   		height = 6 cm ]%,xmin=0,ymin=0,height=4cm,width=5cm,no markers]
@@
 			        ytick={0,0.05,...,0.51},
+			        ylabel=probability density,
+			        y label style={at={(axis description cs:6.0,0.5)},rotate=180,anchor=north},
 			        yticklabel style={

### 2015-11-22 BN_discretizer_paper.tex
modify graphs
Change all plots from probability to probability density
Add appendix

@@
 Forward sampling is often used to draw samples from the joint distribution represented by a Bayesian network.
-Variables are sampled in topological order such that parental instantiations are always known~\citep{algo_2009}.
+Variables are sampled in topological order such that parental instantiations are always known~\citep{PGM_2009}.
 Furthermore, the parent $\rightarrow$ child sampling order can be reversed if the marginal probability of the child variable is known.
@@
       + \sum_{i=1}^{k}
-      L \cdot \frac{\cx_{\lambda_{i}} - \cx_{\lambda_{i-1} + 1}}{\cx_n - \cx_1} \\
+      L \cdot \frac{\cx_{\lambda_{i}} - \cx_{\lambda_{i-1} + 1}}{\cx_n - \cx_1} + \\
   & \sum_{i=1}^{k} \brock{
@@
 For example, in the right-hand graph of Figure~\ref{fig:example_networks}, assume $S_2$ is the only discrete variable.
-The discretization of $P_1$ involves both $P_2$ and $\cX$, whereas the discretization of $C_1$ only involves $\cX$.
+The discretization of $P_1$ involves both $P_2$ and $X$, whereas the discretization of $C_1$ only involves $X$.
+
+\begin{figure}[ht]
+ \centering
+     \input{graph2_right}
+  \caption{An example network}
+   \label{fig:example_networks}
+\end{figure}
 
@@
 The MDL method does not produce any discretization edges, assigning one continuous interval to each continuous variable, and produces the structure with the lowest likelihood.
-The cause behind MDL's discretization policy is discussed in Section~\ref{subsec:discuss_exp}.
+\todo{The cause behind MDL's discretization policy is discussed in Section~\ref{subsec:discuss_exp}.} \yichun{Mykel has rephrased it?}.
+On the other hand, there is a netowrk structure where the MDL has a comparable result with the Bayesian method.
+Please refer to Appendix.
 
@@
 
-\subsubsection{Discretization while Learning Structure}
+%\subsubsection{Discretization while Learning Structure}
 \label{subsubsec:auto_exp2}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-% WINE
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%
+%% WINE
+%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
 \subsection{Dataset 2: Wine}
@@
 \end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-% Housing
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%
+%% Housing
+%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
 \subsection{Data 3: Housing}
@@
 
-% \section*{Appendix}
-
-% \begin{algorithm}
-%   \caption{ Calculation of $h(u,v)$ for all $u \leq v$}
-%   \label{alg:h}
-%   \begin{algorithmic}[1]
-%   \State Initialize $H$ as an $N \times N$ matrix such that all elements are 0.
-%   \State $count_p$ is an $N \times N \times \|\Pa_X\|$ matrix such that $count_p [u,v,w]$ is the number of instances from $x_u$ to $x_v$ with $w$th value of $\Pa_X$.
-This matrix can be calculated in $O(\|\Pa_X\| \cdot N^2)$
-%   \For {$u = 1$ to $N$}
-%     \For {$v = u$ to $N$}
-%       \State $H(u,v) \leftarrow H(u,v) + \ln((v-u + J_p)!) - \ln((J_p -1)!)$
-%       \For {$w = 1$ to $\|\Pa_X\|$}
-%         \State $H(u,v) \leftarrow H(u,v) - \ln( count_p(u,v,w)!)$
-%       \EndFor
-%     \EndFor
-%   \EndFor
-%   \For {$j = 1$ to $n_c$}
-%     \State \todo{XXX}
-%   \EndFor
-%   \end{algorithmic}
-% \end{algorithm}
-
+\section*{Appendix}
+\label{sec:appendix}
+
+The following Bayesian network structure in Figure \ref{fig:auto_graph_3} and the discretization results in Table \ref{table:auto_disc_table_3} demonstrate that the MDL method does not always return smaller number of discretization intervals than the Bayesian approach and also the MDL method can return a comparable result in terms of likelihood.
+The Bayesian network in Figure \ref{fig:auto_graph_3} is obtained by running Algorithm \ref{alg:structure_learn} fifty times with $u_{\text{parent}} = 2$.
+Therefore, the network can be considered well-structured, since the \todo{to be continued}.
+Many edges appears in both discretization results, as the bold numbers in Table \ref{table:auto_disc_table_3}. 
+\begin{figure}[ht]
+  \centering
+  \scalebox{0.8}{
+   \input{graph_autocar_3}}
+   \caption{A Bayesian network structure for Auto MPG dataset that leads to a comparable discretization result of the MDL method with the Bayesian method}
+  \label{fig:auto_graph_3}
+\end{figure}
+
+\begin{table}[h]
+  \centering
+  \caption{
+    Results from discretization of the Auto MPG dataset with fixed structure from Figure~\ref{fig:auto_graph_3}.
+    The first five rows list the discretization edges for each continuous variable.
+    The last row lists the mean cross-validated log-likelihood; positive values are better.
+    The MDL method does not produce any discretization edges.
+  }
+\input{table_autoMPG_3.tex}
+  \label{table:auto_disc_table_3}
+\end{table}
 \end{document}

### 2015-11-22 probability_plot_old/graph_auto_exp1_distr_1_3_old.tex
Add appendix

--- 2015-11-16 graph_auto_exp2_distr_1_3.tex
@@
 			colorbar,
-			point meta min=0, point meta max=0.5,
+			point meta min=0, point meta max=1.2,
 			colormap={}{ gray(0cm)=(1); gray(1cm)=(0);},
 			colorbar style={
-			        ytick={0,0.05,...,0.5},
+			        ytick={0,0.24,...,1.3},
+			        ylabel={probability density $\times 10^3$},
+			        y label style={at={(axis description cs:6.5,0.5)},rotate=180,anchor=north},
 			        yticklabel style={
@@
 
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,68.0000,0.0000) (17.5500,68.0000,0.0000) (17.5500,134.5000,0.0000) (9.0000,134.5000,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,134.5000,0.0010) (17.5500,134.5000,0.0010) (17.5500,159.5000,0.0010) (9.0000,159.5000,0.0010)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,159.5000,0.0010) (17.5500,159.5000,0.0010) (17.5500,169.5000,0.0010) (9.0000,169.5000,0.0010)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,169.5000,0.0395) (17.5500,169.5000,0.0395) (17.5500,259.0000,0.0395) (9.0000,259.0000,0.0395)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,259.0000,0.0045) (17.5500,259.0000,0.0045) (17.5500,264.5000,0.0045) (9.0000,264.5000,0.0045)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,264.5000,0.2220) (17.5500,264.5000,0.2220) (17.5500,455.0000,0.2220) (9.0000,455.0000,0.2220)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,68.0000-0.1,0.000000) (15.2500,68.0000-0.1,0.000000) (15.2500,70.5000,0.000000) (9.0000,70.5000,0.000000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,70.5000,0.000000) (15.2500,70.5000,0.000000) (15.2500,93.5000,0.000000) (9.0000,93.5000,0.000000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,93.5000,0.000000) (15.2500,93.5000,0.000000) (15.2500,109.0000,0.000000) (9.0000,109.0000,0.000000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,109.0000,0.006337) (15.2500,109.0000,0.006337) (15.2500,159.5000,0.006337) (9.0000,159.5000,0.006337)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,159.5000,0.037789) (15.2500,159.5000,0.037789) (15.2500,259.0000,0.037789) (9.0000,259.0000,0.037789)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,259.0000,0.018824) (15.2500,259.0000,0.018824) (15.2500,284.5000,0.018824) (9.0000,284.5000,0.018824)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,284.5000,0.126217) (15.2500,284.5000,0.126217) (15.2500,455.0000,0.126217) (9.0000,455.0000,0.126217)};
 
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.5500,68.0000,0.0765) (23.9500,68.0000,0.0765) (23.9500,134.5000,0.0765) (17.5500,134.5000,0.0765)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.5500,134.5000,0.0260) (23.9500,134.5000,0.0260) (23.9500,159.5000,0.0260) (17.5500,159.5000,0.0260)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.5500,159.5000,0.0085) (23.9500,159.5000,0.0085) (23.9500,169.5000,0.0085) (17.5500,169.5000,0.0085)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.5500,169.5000,0.1225) (23.9500,169.5000,0.1225) (23.9500,259.0000,0.1225) (17.5500,259.0000,0.1225)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.5500,259.0000,0.0070) (23.9500,259.0000,0.0070) (23.9500,264.5000,0.0070) (17.5500,264.5000,0.0070)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.5500,264.5000,0.0355) (23.9500,264.5000,0.0355) (23.9500,455.0000,0.0355) (17.5500,455.0000,0.0355)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(15.2500,68.0000-0.1,0.000000) (17.6500,68.0000-0.1,0.000000) (17.6500,70.5000,0.000000) (15.2500,70.5000,0.000000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(15.2500,70.5000,0.000000) (17.6500,70.5000,0.000000) (17.6500,93.5000,0.000000) (15.2500,93.5000,0.000000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(15.2500,93.5000,0.000000) (17.6500,93.5000,0.000000) (17.6500,109.0000,0.000000) (15.2500,109.0000,0.000000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(15.2500,109.0000,0.016502) (17.6500,109.0000,0.016502) (17.6500,159.5000,0.016502) (15.2500,159.5000,0.016502)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(15.2500,159.5000,0.096315) (17.6500,159.5000,0.096315) (17.6500,259.0000,0.096315) (15.2500,259.0000,0.096315)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(15.2500,259.0000,0.049020) (17.6500,259.0000,0.049020) (17.6500,284.5000,0.049020) (15.2500,284.5000,0.049020)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(15.2500,284.5000,0.152737) (17.6500,284.5000,0.152737) (17.6500,455.0000,0.152737) (15.2500,455.0000,0.152737)};
 
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.9500,68.0000,0.3525) (46.6000,68.0000,0.3525) (46.6000,134.5000,0.3525) (23.9500,134.5000,0.3525)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.9500,134.5000,0.0770) (46.6000,134.5000,0.0770) (46.6000,159.5000,0.0770) (23.9500,159.5000,0.0770)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.9500,159.5000,0.0020) (46.6000,159.5000,0.0020) (46.6000,169.5000,0.0020) (23.9500,169.5000,0.0020)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.9500,169.5000,0.0210) (46.6000,169.5000,0.0210) (46.6000,259.0000,0.0210) (23.9500,259.0000,0.0210)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.9500,259.0000,0.0000) (46.6000,259.0000,0.0000) (46.6000,264.5000,0.0000) (23.9500,264.5000,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.9500,264.5000,0.0035) (46.6000,264.5000,0.0035) (46.6000,455.0000,0.0035) (23.9500,455.0000,0.0035)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.6500,68.0000-0.1,0.000000) (20.9000,68.0000-0.1,0.000000) (20.9000,70.5000,0.000000) (17.6500,70.5000,0.000000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.6500,70.5000,0.000000) (20.9000,70.5000,0.000000) (20.9000,93.5000,0.000000) (17.6500,93.5000,0.000000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.6500,93.5000,0.138958) (20.9000,93.5000,0.138958) (20.9000,109.0000,0.138958) (17.6500,109.0000,0.138958)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.6500,109.0000,0.261995) (20.9000,109.0000,0.261995) (20.9000,159.5000,0.261995) (17.6500,159.5000,0.261995)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.6500,159.5000,0.272130) (20.9000,159.5000,0.272130) (20.9000,259.0000,0.272130) (17.6500,259.0000,0.272130)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.6500,259.0000,0.114630) (20.9000,259.0000,0.114630) (20.9000,284.5000,0.114630) (17.6500,284.5000,0.114630)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.6500,284.5000,0.040605) (20.9000,284.5000,0.040605) (20.9000,455.0000,0.040605) (17.6500,455.0000,0.040605)};
 
-			\addplot3[mark=+, draw=none, mark size=0.7] coordinates {
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.9000,68.0000-0.1,0.126316) (25.6500,68.0000-0.1,0.126316) (25.6500,70.5000,0.126316) (20.9000,70.5000,0.126316)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.9000,70.5000,0.054920) (25.6500,70.5000,0.054920) (25.6500,93.5000,0.054920) (20.9000,93.5000,0.054920)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.9000,93.5000,0.434635) (25.6500,93.5000,0.434635) (25.6500,109.0000,0.434635) (20.9000,109.0000,0.434635)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.9000,109.0000,0.393955) (25.6500,109.0000,0.393955) (25.6500,159.5000,0.393955) (20.9000,159.5000,0.393955)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.9000,159.5000,0.096271) (25.6500,159.5000,0.096271) (25.6500,259.0000,0.096271) (20.9000,259.0000,0.096271)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.9000,259.0000,0.000000) (25.6500,259.0000,0.000000) (25.6500,284.5000,0.000000) (20.9000,284.5000,0.000000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.9000,284.5000,0.008643) (25.6500,284.5000,0.008643) (25.6500,455.0000,0.008643) (20.9000,455.0000,0.008643)};
+
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(25.6500,68.0000-0.1,0.676923) (28.9000,68.0000-0.1,0.676923) (28.9000,70.5000,0.676923) (25.6500,70.5000,0.676923)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(25.6500,70.5000,0.147157) (28.9000,70.5000,0.147157) (28.9000,93.5000,0.147157) (25.6500,93.5000,0.147157)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(25.6500,93.5000,0.744417) (28.9000,93.5000,0.744417) (28.9000,109.0000,0.744417) (25.6500,109.0000,0.744417)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(25.6500,109.0000,0.332064) (28.9000,109.0000,0.332064) (28.9000,159.5000,0.332064) (25.6500,159.5000,0.332064)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(25.6500,159.5000,0.051024) (28.9000,159.5000,0.051024) (28.9000,259.0000,0.051024) (25.6500,259.0000,0.051024)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(25.6500,259.0000,0.000000) (28.9000,259.0000,0.000000) (28.9000,284.5000,0.000000) (25.6500,284.5000,0.000000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(25.6500,284.5000,0.006316) (28.9000,284.5000,0.006316) (28.9000,455.0000,0.006316) (25.6500,455.0000,0.006316)};
+
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(28.9000,68.0000-0.1,0.067797) (46.6000,68.0000-0.1,0.067797) (46.6000,70.5000,0.067797) (28.9000,70.5000,0.067797)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(28.9000,70.5000,0.244412) (46.6000,70.5000,0.244412) (46.6000,93.5000,0.244412) (28.9000,93.5000,0.244412)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(28.9000,93.5000,0.313468) (46.6000,93.5000,0.313468) (46.6000,109.0000,0.313468) (28.9000,109.0000,0.313468)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(28.9000,109.0000,0.067685) (46.6000,109.0000,0.067685) (46.6000,159.5000,0.067685) (28.9000,159.5000,0.067685)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(28.9000,159.5000,0.006814) (46.6000,159.5000,0.006814) (46.6000,259.0000,0.006814) (28.9000,259.0000,0.006814)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(28.9000,259.0000,0.000000) (46.6000,259.0000,0.000000) (46.6000,284.5000,0.000000) (28.9000,284.5000,0.000000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(28.9000,284.5000,0.000166) (46.6000,284.5000,0.000166) (46.6000,455.0000,0.000166) (28.9000,455.0000,0.000166)};
+
+			\addplot3[mark=+, draw=none, mark size=1.0, jitter = 0.1] coordinates {
 (18.000,307.000,1) (15.000,350.000,1) (18.000,318.000,1) (16.000,304.000,1) (17.000,302.000,1) (15.000,429.000,1) (14.000,454.000,1) (14.000,440.000,1) (14.000,455.000,1) (15.000,390.000,1) (15.000,383.000,1) (14.000,340.000,1) (15.000,400.000,1) (14.000,455.000,1) (24.000,113.000,1) (22.000,198.000,1) (18.000,199.000,1) (21.000,200.000,1) (27.000,97.000,1) (26.000,97.000,1) (25.000,110.000,1) (24.000,107.000,1) (25.000,104.000,1) (26.000,121.000,1) (21.000,199.000,1) (10.000,360.000,1) (10.000,307.000,1) (11.000,318.000,1) (9.000,304.000,1) (27.000,97.000,1) (28.000,140.000,1) (25.000,113.000,1) (19.000,232.000,1) (16.000,225.000,1) (17.000,250.000,1) (19.000,250.000,1) (18.000,232.000,1) (14.000,350.000,1) (14.000,400.000,1) (14.000,351.000,1) (14.000,318.000,1) (12.000,383.000,1) (13.000,400.000,1) (13.000,400.000,1) (18.000,258.000,1) (22.000,140.000,1) (19.000,250.000,1) (18.000,250.000,1) (23.000,122.000,1) (28.000,116.000,1) (30.000,79.000,1) (30.000,88.000,1) (31.000,71.000,1) (35.000,72.000,1) (27.000,97.000,1) (26.000,91.000,1) (24.000,113.000,1) (25.000,97.500,1) (23.000,97.000,1) (20.000,140.000,1) (21.000,122.000,1) (13.000,350.000,1) (14.000,400.000,1) (15.000,318.000,1) (14.000,351.000,1) (17.000,304.000,1) (11.000,429.000,1) (13.000,350.000,1) (12.000,350.000,1) (13.000,400.000,1) (19.000,70.000,1) (15.000,304.000,1) (13.000,307.000,1) (13.000,302.000,1) (14.000,318.000,1) (18.000,121.000,1) (22.000,121.000,1) (21.000,120.000,1) (26.000,96.000,1) (22.000,122.000,1) (28.000,97.000,1) (23.000,120.000,1) (28.000,98.000,1) (27.000,97.000,1) (13.000,350.000,1) (14.000,304.000,1) (13.000,350.000,1) (14.000,302.000,1) (15.000,318.000,1) (12.000,429.000,1) (13.000,400.000,1) (13.000,351.000,1) (14.000,318.000,1) (13.000,440.000,1) (12.000,455.000,1) (13.000,360.000,1) (18.000,225.000,1) (16.000,250.000,1) (18.000,232.000,1) (18.000,250.000,1) (23.000,198.000,1) (26.000,97.000,1) (11.000,400.000,1) (12.000,400.000,1) (13.000,360.000,1) (12.000,350.000,1) (18.000,232.000,1) (20.000,97.000,1) (21.000,140.000,1) (22.000,108.000,1) (18.000,70.000,1) (19.000,122.000,1) (21.000,155.000,1) (26.000,98.000,1) (15.000,350.000,1) (16.000,400.000,1) (29.000,68.000,1) (24.000,116.000,1) (20.000,114.000,1) (19.000,121.000,1) (15.000,318.000,1) (24.000,121.000,1) (20.000,156.000,1) (11.000,350.000,1) (20.000,198.000,1) (19.000,232.000,1) (15.000,250.000,1) (31.000,79.000,1) (26.000,122.000,1) (32.000,71.000,1) (25.000,140.000,1) (16.000,250.000,1) (16.000,258.000,1) (18.000,225.000,1) (16.000,302.000,1) (13.000,350.000,1) (14.000,318.000,1) (14.000,302.000,1) (14.000,304.000,1) (29.000,98.000,1) (26.000,79.000,1) (26.000,97.000,1) (31.000,76.000,1) (32.000,83.000,1) (28.000,90.000,1) (24.000,90.000,1) (26.000,116.000,1) (24.000,120.000,1) (26.000,108.000,1) (31.000,79.000,1) (19.000,225.000,1) (18.000,250.000,1) (15.000,250.000,1) (15.000,250.000,1) (16.000,400.000,1) (15.000,350.000,1) (16.000,318.000,1) (14.000,351.000,1) (17.000,231.000,1) (16.000,250.000,1) (15.000,258.000,1) (18.000,225.000,1) (21.000,231.000,1) (20.000,262.000,1) (13.000,302.000,1) (29.000,97.000,1) (23.000,140.000,1) (20.000,232.000,1) (23.000,140.000,1) (24.000,134.000,1) (25.000,90.000,1) (24.000,119.000,1) (18.000,171.000,1) (29.000,90.000,1) (19.000,232.000,1) (23.000,115.000,1) (23.000,120.000,1) (22.000,121.000,1) (25.000,121.000,1) (33.000,91.000,1) (28.000,107.000,1) (25.000,116.000,1) (25.000,140.000,1) (26.000,98.000,1) (27.000,101.000,1) (17.500,305.000,1) (16.000,318.000,1) (15.500,304.000,1) (14.500,351.000,1) (22.000,225.000,1) (22.000,250.000,1) (24.000,200.000,1) (22.500,232.000,1) (29.000,85.000,1) (24.500,98.000,1) (29.000,90.000,1) (33.000,91.000,1) (20.000,225.000,1) (18.000,250.000,1) (18.500,250.000,1) (17.500,258.000,1) (29.500,97.000,1) (32.000,85.000,1) (28.000,97.000,1) (26.500,140.000,1) (20.000,130.000,1) (13.000,318.000,1) (19.000,120.000,1) (19.000,156.000,1) (16.500,168.000,1) (16.500,350.000,1) (13.000,350.000,1) (13.000,302.000,1) (13.000,318.000,1) (31.500,98.000,1) (30.000,111.000,1) (36.000,79.000,1) (25.500,122.000,1) (33.500,85.000,1) (17.500,305.000,1) (17.000,260.000,1) (15.500,318.000,1) (15.000,302.000,1) (17.500,250.000,1) (20.500,231.000,1) (19.000,225.000,1) (18.500,250.000,1) (16.000,400.000,1) (15.500,350.000,1) (15.500,400.000,1) (16.000,351.000,1) (29.000,97.000,1) (24.500,151.000,1) (26.000,97.000,1) (25.500,140.000,1) (30.500,98.000,1) (33.500,98.000,1) (30.000,97.000,1) (30.500,97.000,1) (22.000,146.000,1) (21.500,121.000,1) (21.500,80.000,1) (43.100,90.000,1) (36.100,98.000,1) (32.800,78.000,1) (39.400,85.000,1) (36.100,91.000,1) (19.900,260.000,1) (19.400,318.000,1) (20.200,302.000,1) (19.200,231.000,1) (20.500,200.000,1) (20.200,200.000,1) (25.100,140.000,1) (20.500,225.000,1) (19.400,232.000,1) (20.600,231.000,1) (20.800,200.000,1) (18.600,225.000,1) (18.100,258.000,1) (19.200,305.000,1) (17.700,231.000,1) (18.100,302.000,1) (17.500,318.000,1) (30.000,98.000,1) (27.500,134.000,1) (27.200,119.000,1) (30.900,105.000,1) (21.100,134.000,1) (23.200,156.000,1) (23.800,151.000,1) (23.900,119.000,1) (20.300,131.000,1) (17.000,163.000,1) (21.600,121.000,1) (16.200,163.000,1) (31.500,89.000,1) (29.500,98.000,1) (21.500,231.000,1) (19.800,200.000,1) (22.300,140.000,1) (20.200,232.000,1) (20.600,225.000,1) (17.000,305.000,1) (17.600,302.000,1) (16.500,351.000,1) (18.200,318.000,1) (16.900,350.000,1) (15.500,351.000,1) (19.200,267.000,1) (18.500,360.000,1) (31.900,89.000,1) (34.100,86.000,1) (35.700,98.000,1) (27.400,121.000,1) (25.400,183.000,1) (23.000,350.000,1) (27.200,141.000,1) (23.900,260.000,1) (34.200,105.000,1) (34.500,105.000,1) (31.800,85.000,1) (37.300,91.000,1) (28.400,151.000,1) (28.800,173.000,1) (26.800,173.000,1) (33.500,151.000,1) (41.500,98.000,1) (38.100,89.000,1) (32.100,98.000,1) (37.200,86.000,1) (28.000,151.000,1) (26.400,140.000,1) (24.300,151.000,1) (19.100,225.000,1) (34.300,97.000,1) (29.800,134.000,1) (31.300,120.000,1) (37.000,119.000,1) (32.200,108.000,1) (46.600,86.000,1) (27.900,156.000,1) (40.800,85.000,1) (44.300,90.000,1) (43.400,90.000,1) (36.400,121.000,1) (30.000,146.000,1) (44.600,91.000,1) (33.800,97.000,1) (29.800,89.000,1) (32.700,168.000,1) (23.700,70.000,1) (35.000,122.000,1) (32.400,107.000,1) (27.200,135.000,1) (26.600,151.000,1) (25.800,156.000,1) (23.500,173.000,1) (30.000,135.000,1) (39.100,79.000,1) (39.000,86.000,1) (35.100,81.000,1) (32.300,97.000,1) (37.000,85.000,1) (37.700,89.000,1) (34.100,91.000,1) (34.700,105.000,1) (34.400,98.000,1) (29.900,98.000,1) (33.000,105.000,1) (33.700,107.000,1) (32.400,108.000,1) (32.900,119.000,1) (31.600,120.000,1) (28.100,141.000,1) (30.700,145.000,1) (25.400,168.000,1) (24.200,146.000,1) (22.400,231.000,1) (26.600,350.000,1) (20.200,200.000,1) (17.600,225.000,1) (28.000,112.000,1) (27.000,112.000,1) (34.000,112.000,1) (31.000,112.000,1) (29.000,135.000,1) (27.000,151.000,1) (24.000,140.000,1) (36.000,105.000,1) (37.000,91.000,1) (31.000,91.000,1) (38.000,105.000,1) (36.000,98.000,1) (36.000,120.000,1) (36.000,107.000,1) (34.000,108.000,1) (38.000,91.000,1) (32.000,91.000,1) (38.000,91.000,1) (25.000,181.000,1) (38.000,262.000,1) (26.000,156.000,1) (22.000,232.000,1) (32.000,144.000,1) (36.000,135.000,1) (27.000,151.000,1) (27.000,140.000,1) (44.000,97.000,1) (32.000,135.000,1) (28.000,120.000,1) (31.000,119.000,1) };

### 2015-11-23 BN_discretizer_paper.tex
Do the todos

@@
 The proposed method optimizes the discretization policy relative to the network and takes parents, children, and spouse variables into account.
-The optimal single-variable discretization method is derived in Section~\ref{sec:single_var}, and a second heuristic method is proposed which reduces the runtime from exponential to polynomial.
+The optimal single-variable discretization method is derived in Section~\ref{sec:single_var}.
 Section~\ref{sec:multi_var} covers Bayesian networks with multiple continuous variables and discretization while simultaneously learning network structure.
@@
 
-Let $J_P$ be the number of instantiations of the parents of $\cX$, and let $n^{(\text{p})}_{i,j}$ be the number of instances of $\cX$ within the $i$th discretization interval of $\Lambda$ given the $j$th parental instantiation.
-Note that $\gamma_i = \sum_j n^{(\text{p})}_{i,j}$.
+Let $J_P$ be the number of instantiations of the parents of $\cX$, and let $n^{(P)}_{i,j}$ be the number of instances of $\cX$ within the $i$th discretization interval of $\Lambda$ given the $j$th parental instantiation.
+Note that $\gamma_i = \sum_j n^{(P)}_{i,j}$.
 It follows that
@@
 Let ${n^{(j)}_{i,l} = \sum_{m=1}^{J_j} n^{(j)}_{i,m,l}}$.
-Note that ${\gamma_i = \sum_l n^{(j)}_{i,l}}$.
+Note that ${\gamma_i = \sum_l n^{(j)}_{i,l}}$ for all $j$.
 It follows that
@@
 
-The evaluation of $h(u,v)$ for all $u \leq v$ is summarized in Algorithm~\ref{alg:h} in the appendix.
-\todo{The calculation has a $\bigo \paren{ n_c  {L'} \cdot N^2 + {L'}^{n_p} \cdot N^2 }$ runtime, where $n_c$ and $n_p$ are the numbers of child and parent variables respectively, and $L'$ is the largest cardinality of variables that directly connect to $X$.}
+The calculation of $h(u,v)$ for all $u \leq v$ has a $\bigo \paren{ n_c \, {L}^{n_s} \cdot N^2 + {L}^{n_p} \cdot N^2 }$ runtime, where $n_c$ and $n_p$ are the numbers of child and parent variables respectively, $L$ is the largest cardinality of variables in $X$'s Markov blanket, and $n_s = \text{max}^{n_c}_{j=1}  J^{(j)}_{S}$.
 
@@
 It takes three inputs: $\cX$, the continuous variable; $D$, the joint data instances over all variables sorted in ascending order according to $D_X$; and $G$, the network structure.
-The runtime of Algorithm~\ref{alg:disc_one} is also $O(n_c  {L'} \cdot N^2 + {L'}^{n_p} \cdot N^2)$, because the runtime of the dynamic programming procedure is less than the runtime for computing $h(u,v)$.
+The runtime of Algorithm~\ref{alg:disc_one} is also $\bigo \paren{ n_c \, {L}^{n_s} \cdot N^2 + {L}^{n_p} \cdot N^2 }$, because the runtime of the dynamic programming procedure is less than the runtime for computing $h(u,v)$.
 Algorithm~\ref{alg:disc_one} is guaranteed to be optimal.
@@
 The iterative approach uses a prediscretization policy in order to initialize the process.
-This work prediscretizes all continuous variables into $k$ equal-width intervals, where $k$ is the median value of the number of intervals of initially discrete variables in the network.
+This work prediscretizes all continuous variables into $k$ equal-width intervals, where $k$ is largest value of the number of intervals of initially discrete variables in the network.
 
@@
 Reverse topological order has the advantage of relying on fewer prediscretizations of the continuous variables during the first pass.
-For example, in the right-hand graph of Figure~\ref{fig:example_networks}, assume $S_2$ is the only discrete variable.
-The discretization of $P_1$ involves both $P_2$ and $X$, whereas the discretization of $C_1$ only involves $X$.
+For example, in the network of Figure~\ref{fig:example_networks}, if $S_2$ is the only discrete variable, then the discretization of $P_1$ involves both $P_2$ and $X$, whereas the discretization of $C_1$ only involves $X$.
 
@@
 The algorithm typically converges within a few passes when tested on real-world data.
-In cases where it does not converge, \tim{only observed when also learning structure}, ten passes usually produce decent discretization results.
+In cases where it does not converge, usually observed when also learning structure, ten passes produce decent discretization results.
 
@@
     \State $D^* \leftarrow $ the dataset $D$ discretized according to $\discset$
-    \State $k \leftarrow \textsc{Median}\paren{\curly{ |X| \text{ s.t. } X \text{ does not have corresponding } \cX \text{ in } \bm{\cX} }}$
+    \State $k \leftarrow \textsc{Max}\paren{\curly{ |X| \text{ s.t. } X \text{ does not have corresponding } \cX \text{ in } \bm{\cX} }}$
     \For {$\paren{\cX, X}$ such that $\cX \in \bm{\cX}$ and $X$ is the discretized version of $\cX$}
@@
     \State $m \leftarrow$ the number of variables in the Bayesian network
-    \State $k \leftarrow median\{ \|v\|, v\notin C\}$
+    \State $k \leftarrow max\{ \|v\|, v\notin C\}$
     \State $\Lambda^{(i)} \leftarrow$ the discretization policy for the continuous variable $X_i$
@@
   \label{eqn:MDL}
-  \todo{
   \begin{aligned}
-  \frac{1}{2} \ln(n) \left\lbrace  \lvert \Pa_{X_i} \rvert (\lvert X_i \rvert - 1) +
-   {\sum_{j,\cX_i \in \Pa_{X_i}}} \lvert \Pa_{X_j} \rvert (\lvert \cX_j \rvert - 1) \right\rbrace + \ln(\lvert {\cX_i} \rvert) \\
-   + (N_i-1) H \paren{\frac{|X^*_i| - 1}{N_i -1}} -n \cdot \left[ I(X_i,\Pa_{X_i}) + {\sum_{j,\cX_i \in \Pa_{\cX_i}}} I(\cX_j, \Pa_{X_j}) \right]\text{,}
+  \frac{1}{2} \ln(n) \left\lbrace  \lvert \Pa_{\cX} \rvert (\lvert X \rvert - 1) +
+   {\sum_{j,\cX \in \Pa_{X_j}}} \lvert \Pa_{X_j} \rvert (\lvert X_j \rvert - 1) \right\rbrace + \ln(|X|) \\
+   + (m-1) H \paren{\frac{|X| - 1}{m -1}} -n \cdot \left[ I(X,\Pa_{\cX}) + {\sum_{j,\cX \in \Pa_{X_j}}} I(X_j, \Pa_{X_j}) \right]\text{,}
   \end{aligned}
-  }
-\end{equation}
-
-where $I(A,B)$ is the mutual information between two discrete variables $A$ and $B$, ${H(p) = -p \ln(p) - (1-p) \ln(1-p)}$, and \todo{$X^*_i$ is the discretized version of the $i$th sample of $X$}.
+\end{equation}
+where $I(A,B)$ is the mutual information between two discrete variable sets $A$ and $B$, ${H(p) = -p \ln(p) - (1-p) \ln(1-p)}$, and $X$ is the discretized version of $\cX$.
 
@@
 
-Table~\ref{table:auto_disc_table_1} lists the discretization edges and mean log-likelihoods under \num{10}-fold cross validation of the discrete Bayesian network resulting from each discretization method.
-The MDL method does not produce any discretization edges, assigning one continuous interval to each continuous variable, and produces the structure with the lowest likelihood.
-\todo{The cause behind MDL's discretization policy is discussed in Section~\ref{subsec:discuss_exp}.} \yichun{Mykel has rephrased it?}.
-On the other hand, there is a netowrk structure where the MDL has a comparable result with the Bayesian method.
+Table~\ref{table:auto_disc_table_1} lists the discretization edges and mean log-likelihoods under \num{10}-fold cross validation of the discrete Bayesian network resulting from two discretization methods.
+The MDL method does not produce any discretization edges, assigning one continuous interval to each continuous variable, and produces the result with the lower likelihood.
+The cause of low number of discretization edges behind the MDL method is discussed in Section~\ref{subsec:discuss_exp}.
+On the other hand, there is a network structure where the MDL has a comparable result with the Bayesian method.
 Please refer to Appendix.
@@
 Figure~\ref{fig:auto_graph_2} shows a learned Bayesian network structure and the corresponding numbers of intervals after discretization for each continuous variable.
-This result was obtained by running Algorithm~\ref{alg:structure_learn} fifty times using the Bayesian method and choosing the structure with the highest likelihood.
+This result was obtained by running Algorithm~\ref{alg:structure_learn} fifty times using the Bayesian method and choosing the structure with the highest K2 score (Equation \ref{eq:BayesianScore}).
 
@@
 The MDL term uses emperical probability distributions, based off of ratios of counts, whereas the Bayesian methods use factorial terms, and thus vary less severely.
-Futhermore, the term for the heuristic Bayesian method varies more aggresively than the term for the optimal Bayesian method, as it has two terms.
-The MDL method is thus the least sensitive to the discretization edges and the heuristic Bayesian method is over-sensitive.
-This sensitivity gives rise to the relative performance of each method in the experiments conducted above.
+The MDL method is therefore less sensitive to the discretization edges.
+This sensitivity gives rise to the relative performance of the two methods in the experiments conducted above.
 
@@
 
-The following Bayesian network structure in Figure \ref{fig:auto_graph_3} and the discretization results in Table \ref{table:auto_disc_table_3} demonstrate that the MDL method does not always return smaller number of discretization intervals than the Bayesian approach and also the MDL method can return a comparable result in terms of likelihood.
+The Bayesian network structure in Figure \ref{fig:auto_graph_3} and the discretization results in Table \ref{table:auto_disc_table_3} demonstrate that the MDL method does not always return smaller number of discretization intervals than the Bayesian approach and also the MDL method can return a comparable result in terms of likelihood.
 The Bayesian network in Figure \ref{fig:auto_graph_3} is obtained by running Algorithm \ref{alg:structure_learn} fifty times with $u_{\text{parent}} = 2$.
-Therefore, the network can be considered well-structured, since the \todo{to be continued}.
+Therefore, this network can be considered more well-structured than the one in Figure \ref{fig:auto_graph_1}, since the effect of discretization policies has already been considered in the learning process.
 Many edges appears in both discretization results, as the bold numbers in Table \ref{table:auto_disc_table_3}. 
@@
     The first five rows list the discretization edges for each continuous variable.
-    The last row lists the mean cross-validated log-likelihood; positive values are better.
-    The MDL method does not produce any discretization edges.
+    The last row lists the mean cross-validated log-likelihood.
+    Two methods have same discretization result on variable $A$.
+    Log-likelihood shows that the MDL method is just slightly worse than the Bayesian method.
   }

### 2015-11-23 BN_discretizer_paper.tex
Rewrite Algorithm3

@@
 
-The optimal discretization policy is found with dynamic programming.
+The optimal discretization policy is found with dynamic programming, and it takes runtime $\bigo\paren{n^3 + q \cdot n^2}$, where $n$ is the number of data instances and $q$ is a constant that exponentially depends on cardinalities of variables in Bayesian networks and will be discussed in Section \ref{sec:experiments}.
 For Bayesian networks with multiple continuous variables, MDL discretization is iteratively applied to each continuous variables.
@@
 
-The MODL method uses dynamic programming to find the optimal discretization policy, and has an $\bigo\paren{n^3 + r \cdot n^2}$ runtime, where $n$ is the of number of data instances and $r$ is the number of instances for the class variable.
+The MODL method uses dynamic programming to find the optimal discretization policy, and has an $\bigo\paren{n^3 + r \cdot n^2}$ runtime, where $r$ is the number of instances for the class variable.
 \cite{Lustgarten_2011} suggest several formulations for the prior term $P(\text{Model})$.
@@
 
-A Bayesian network $B$ is defined by a pair $(G,\bm{\theta})$, where $G$ is a directed acyclic graph whose $n$ nodes $X_{1:n}$ are random variables.
+A Bayesian network $B$ is defined by a pair $(G,\bm{\theta})$, where $G$ is a directed acyclic graph whose $N$ nodes $X_{1:N}$ are random variables.
 The edges in a Bayesian network represent probabilistic dependencies among nodes and encode the Markov property: each node $X_i$ is independent of its non-descendants given its parents $\Pa_{X_i}$ in $G$.
@@
 \begin{equation}
-P(X_{1:n}) = \prod_{i=1}^n P(X_i \mid \Pa_{X_i})\text{.}
+P(X_{1:N}) = \prod_{i=1}^N P(X_i \mid \Pa_{X_i})\text{.}
 \end{equation}
@@
 \begin{equation}
-P(D\mid \bm{\theta}, G) = \prod_{i=1}^n \prod_{j=1}^{q_i} \prod_{k=1}^{r_i} \brock{\theta_{ij}^{(k)}}^{\beta_{ij}^{(k)}}\text{.}
+P(D\mid \bm{\theta}, G) = \prod_{i=1}^N \prod_{j=1}^{q_i} \prod_{k=1}^{r_i} \brock{\theta_{ij}^{(k)}}^{\beta_{ij}^{(k)}}\text{.}
 \end{equation}
@@
 \label{eq:BayesianScore}
-  \ln P(D\mid G) = \ln P(G) + \sum_{i=1}^n \sum_{j=1}^{q_i} \ln \paren{
+  \ln P(D\mid G) = \ln P(G) + \sum_{i=1}^N \sum_{j=1}^{q_i} \ln \paren{
     \frac{
@@
 
-The calculation of $h(u,v)$ for all $u \leq v$ has a $\bigo \paren{ n_c \, {L}^{n_s} \cdot N^2 + {L}^{n_p} \cdot N^2 }$ runtime, where $n_c$ and $n_p$ are the numbers of child and parent variables respectively, $L$ is the largest cardinality of variables in $X$'s Markov blanket, and $n_s = \text{max}^{n_c}_{j=1}  J^{(j)}_{S}$.
+The calculation of $h(u,v)$ for all $u \leq v$ has a $\bigo \paren{ n_c \cdot {L}^{n_s} \cdot n^2 + {L}^{n_p} \cdot n^2 }$ runtime, where $n_c$ and $n_p$ are the numbers of child and parent variables respectively, $L$ is the largest cardinality of variables in $X$'s Markov blanket, and $n_s = \text{max}_j  |\Pa_{C_j}|$.
 
@@
 It takes three inputs: $\cX$, the continuous variable; $D$, the joint data instances over all variables sorted in ascending order according to $D_X$; and $G$, the network structure.
-The runtime of Algorithm~\ref{alg:disc_one} is also $\bigo \paren{ n_c \, {L}^{n_s} \cdot N^2 + {L}^{n_p} \cdot N^2 }$, because the runtime of the dynamic programming procedure is less than the runtime for computing $h(u,v)$.
+The runtime of Algorithm~\ref{alg:disc_one} is also $\bigo \paren{ n_c \cdot {L}^{n_s} \cdot n^2 + {L}^{n_p} \cdot n^2 }$, because the runtime of the dynamic programming procedure is less than the runtime for computing $h(u,v)$.
 Algorithm~\ref{alg:disc_one} is guaranteed to be optimal.
@@
 It takes five inputs: $D$, a dataset of samples from the joint distribution; $\bm{\cX}$, the set of all continuous variables; $\texttt{order}$, a permutation of the variables in $D$; $\hat{n}_\text{parent}$, an upper bound on the number of parents per node; and $\maxpasses$, an upper bound on the number of complete passes.
+The function $g$ in Algorithm~\ref{alg:structure_learn} computes a component of the Bayesian score (Equation~\ref{eq:BayesianScore}):
+
+\begin{equation}
+  \label{eq:B_Score_one}
+  g\paren{X_i, \Pa_{X_i}} =  \sum_{j=1}^{q_i} \ln\paren{
+    \frac{
+      \Gamma\paren{\alpha_{ij}^{(0)}}
+    }{
+      \Gamma\paren{\alpha_{ij}^{(0)} + \beta_{ij}^{(0)}}
+    }
+  } + \sum_{k=1}^{r_i} \ln \paren{
+    \frac{
+      \Gamma\paren{\alpha_{ij}^{(k)} + \beta_{ij}^{(k)}}
+    }{
+      \Gamma\paren{\alpha_{ij}^{(k)}}
+    }
+  }\text{.}
+\end{equation}
 
@@
   \begin{algorithmic}[5]
-  \Function{Learn\_DBN}{$D$, $C$, $order$, $u_{parent}$, $C$, $\maxpasses$}
-    \State $m \leftarrow$ the number of variables in the Bayesian network
-    \State $k \leftarrow max\{ \|v\|, v\notin C\}$
-    \State $\Lambda^{(i)} \leftarrow$ the discretization policy for the continuous variable $X_i$
-    \State $D^*_{X_i} \leftarrow \Lambda^{(i)} (D_{X_i})$, list of instances of $X_i$ discretized by $\Lambda^{(i)}$
-    \State $D^* \leftarrow $ the discretized data for all variables, where $D^*_{X_j} \leftarrow D_{X_j}$ if $X_j \notin C$
+  \Function{Learn\_DVBN}{$D$, $\bm{\cX}$, $\texttt{order}$, $\hat{n}_\text{parent}$, $\maxpasses$}
+    \State $N \leftarrow$ the number of variables in the Bayesian network
+    \State $k \leftarrow \textsc{Max} \{ \|v\|, v\notin C\}$
+    \State $\discset \leftarrow$ the discretization policies for each $\cX$ in $\bm{\cX}$
+    \State $D^* \leftarrow $ the dataset $D$ discretized according to $\discset$
     \State $G \leftarrow$ the initial edgeless graph structure
-    \For {$i \leftarrow 1$ to $n$}
-      \If {$X_i \in C$}
-        \State $\Lambda^{(i)} \leftarrow$ equal-width discretization with $k$ intervals
-        \State $D^*_{X_i} \leftarrow  \Lambda^{(i)} (D_{X_i})$
-      \EndIf
+	\For {$\paren{\cX, X}$ such that $\cX \in \bm{\cX}$ and $X$ is the discretized version of $\cX$}
+      \State $\Lambda_{\cX} \leftarrow$ equal-width discretization of $\cX$ with $k$ intervals
+      \State $D^*_{X} \leftarrow \Lambda_{\cX} \paren{D_{\cX}}$
     \EndFor
-    \For {$i \leftarrow 1$ to $n$}
-      \State $P_{old} \leftarrow g(X^*_i,\Pa^*_X)$ as Equation~\ref{eq:B_Score_one}
+    \For {$i \leftarrow 1$ to $N$}
+      \State $P_{old} \leftarrow g(X_i,\Pa_{X_i})$ as Equation~\ref{eq:B_Score_one}
       \State OKToProceed $\leftarrow$ \textbf{true}
-      \While {OKToProceed \textbf{and} $\|\Pa_{X_i}\| < u_{parent}$}
-        \State $Y \leftarrow$ an element from the set $order[1:i] \backslash \Pa_X$
-        \State $P_{new} \leftarrow g(X^*_i,\Pa^*_{X_i} \cup Y^*)$
+      \While {OKToProceed \textbf{and} $\|\Pa_{X_i}\| < \hat{n}_\text{parent}$}
+        \State $Y \leftarrow$ an element from the set $\texttt{order}[1:i] \backslash \Pa_X$
+        \State $P_{new} \leftarrow g(X_i,\Pa_{X_i} \cup Y)$
         \If {$P_{new} > P_{old}$}
@@
           \State $\Pa_{X_i} \leftarrow \Pa_{X_i} \cup Y $
-          \State $C' \leftarrow$ sorting variables in $C$ by a reverse topological order of current $G$
-          \State $\Lambda \leftarrow$ \textsc{DiscretizeAll}({$D$, $G$, $C'$, $\maxpasses$}): Algorithm~\ref{alg:disc_two}
-          \State $D*_{X_i} \leftarrow \Lambda^{(i)}(D_{X_i})$ for all $i$
+          \State $\bm{\cX '} \leftarrow$ sorted $\bm{\cX}$ by a reverse topological order of current $G$
+          \State $\Lambda \leftarrow$ \textsc{DiscretizeAll}({$D$, $G$, $\bm{\cX '}$, $\maxpasses$}): Algorithm~\ref{alg:disc_two}
+          \State $D^* \leftarrow \Lambda \paren{D_{\bm{\cX }}}$
         \Else
@@
 \end{algorithm}
-
-The function $g$ in Algorithm~\ref{alg:structure_learn} computes a component of the Bayesian score (Equation~\ref{eq:BayesianScore}):
-
-\begin{equation}
-  \label{eq:B_Score_one}
-  g\paren{X_i, \Pa_{X_i}} =  \sum_{j=1}^{q_i} \ln\paren{
-    \frac{
-      \Gamma\paren{\alpha_{ij}^{(0)}}
-    }{
-      \Gamma\paren{\alpha_{ij}^{(0)} + \beta_{ij}^{(0)}}
-    }
-  } + \sum_{k=1}^{r_i} \ln \paren{
-    \frac{
-      \Gamma\paren{\alpha_{ij}^{(k)} + \beta_{ij}^{(k)}}
-    }{
-      \Gamma\paren{\alpha_{ij}^{(k)}}
-    }
-  }\text{.}
-\end{equation}
 

### 2015-11-23 BN_discretizer_paper.tex
Add runtime of MDL method

@@
 \subsection{Algorithm}
+\label{subsec:algo}
 
@@
   \begin{equation}
+  \label{eqn:h_function}
   \begin{aligned}
@@
 where $I(A,B)$ is the mutual information between two discrete variable sets $A$ and $B$, ${H(p) = -p \ln(p) - (1-p) \ln(1-p)}$, and $X$ is the discretized version of $\cX$.
+The minimum of Equation \ref{eqn:MDL} can be found by dynamical programming.
+It takes runtime $\bigo \paren{ n^3 + \paren{ n_c \cdot {L}^{n_s}  + {L}^{n_p}} \cdot n^2 }$, where the parameters are defined in Section \ref{subsec:algo}.
+Therefore, the runtime of the proposed method in this paper is shorter than MDL discretization method by $\bigo \paren{n^3}$.
 

### 2015-11-24 BN_discretizer_paper.tex
Do all todos
Change the description of Lustgarten's paper in the introduction

@@
 % your LaTeX will extract the file if required
-\begin{filecontents*}{example.eps}
+%\begin{filecontents*}{example.eps}
   %!PS-Adobe-3.0 EPSF-3.0
@@
   %%EndComments
-  gsave
-  newpath
-    20 20 moveto
-    20 220 lineto
-    220 220 lineto
-    220 20 lineto
-  closepath
-  2 setlinewidth
-  gsave
-    .4 setgray fill
-  grestore
-  stroke
-  grestore
-\end{filecontents*}
+%  gsave
+%  newpath
+%    20 20 moveto
+%    20 220 lineto
+%    220 220 lineto
+%    220 20 lineto
+%  closepath
+%  2 setlinewidth
+%  gsave
+%    .4 setgray fill
+%  grestore
+%  stroke
+%  grestore
+%\end{filecontents*}
 %
@@
 There are three common approaches to extending Bayesian networks to continuous variables.
-The first is to model the conditional probability density of each continuous variable using specific families of parametric distributions, and then to redesign Bayesian network learning algorithms based on their parameters.
+The first is to model the conditional probability density of each continuous variable using specific families of parametric distributions, and then to redesign Bayesian network learning and inference algorithms based on their parameters.
 One successful example are Gaussian graphical models \citep{Weiss_2011}.
@@
 Their approach selects a discretization policy that minimizes the sum of the description lengths of the discretized Bayesian network and the information necessary for recovering the continuous values from the discretized data.
-Results in this work suggest that the MDL method suffers from \todo{fill this out.}
+Results in this work suggest that the MDL method suffers from low sensitivity to discretization edges and returns low numbers of discretization intervals on continuous variables.
 
@@
 \cite{Lustgarten_2011} suggest several formulations for the prior term $P(\text{Model})$.
-Under a uniform prior probability over discretizations the runtime can be reduced to $\bigo\paren{r \cdot n^2}$ without sacrificing optimality.
+Under the suggested prior, which includes the uniform prior probabilities in MODL as a special case, the runtime can be reduced to $\bigo\paren{r \cdot n^2}$ without sacrificing optimality.
 
@@
   \label{eq:p_D_given_M}
-  P\paren{D_{-\cX} \mid \Lambda} \propto P\paren{D_{\Pa_\cX} \mid \Lambda} \cdot \prod_{C_i} P\paren{D_{C_i} \mid \Lambda, D_{\bm{S}_i}}\text{.}
+  P\paren{D_{-\cX} \mid \Lambda} \propto P\paren{D_{\Pa_\cX} \mid \Lambda} \cdot \prod_{i} P\paren{D_{C_i} \mid \Lambda, D_{\bm{S}_i}}\text{.}
 \end{equation}
@@
 
-\todo{
-\begin{equation}
-  \ln p\paren{D\mid \discset, D^*} = \sum_{i=1}^n
-  1\curly{X_i \text{ orig. cont.}}
-  \sum_{j=1}^{q_i} \sum_{k=1}^{r_i} m_{ijk} \ln\paren{
+\begin{equation}
+  \ln p\paren{D\mid \discset, D^*} = \sum_{i=1}^N
+  1_{\curly{ \cX_i \in \bm{\cX }}}\cdot \sum_{k=1}^{r_i}  \sum_{j=1}^{q_i} \beta_{ij}^{(k)} \ln \paren{
     \frac{
@@
     }{
-      e^{\Lambda_{\cX_i}}_{k+1} - e^{\Lambda_{\cX_i}}_{k}
+      e^{\Lambda_{\cX_i}}_{k} - e^{\Lambda_{\cX_i}}_{k-1}
     }
@@
 \end{equation}
-}
-
+Note that $e^{\Lambda_{\cX_i}}_{0} = \textsc{Min}\paren{D_{\cX_i}}$ and $e^{\Lambda_{\cX_i}}_{r_i} = \textsc{Max}\paren{D_{\cX_i}}$.
+%, where $\brock{ e^{\Lambda_{\cX_i}}_{k-1} , e^{\Lambda_{\cX_i}}_{k} }$ is the discretization interval that $\cx_i$ falls in.
+If $\cx_i < e^{\Lambda_{\cX_i}}_{1}$, then the corresponding interval is $\brock{ \textsc{Min}\paren{D_{X_i}} , e^{\Lambda_{\cX_i}}_{1}}$.
+If $\cx_i \leq e^{\Lambda_{\cX_i}}_{r_i - 1}$, then the corresponding interval is $\brock{  e^{\Lambda_{\cX_i}}_{r_i - 1},\textsc{Max}\paren{D_{X_i}}}$.
 \noindent

### 2015-11-24 BN_discretizer_paper.tex
intro update

@@
 
-Bayesian networks \citep{Pearl_1988, PGM_2009} are an increasingly popular method for modeling uncertainty and causality in science and engineering.
-They provide an efficient factorization of the joint probability distribution over a set of random variables.
-Bayesian networks first emerged from artificial intelligence research and have been applied to a wide variety of problems, ranging from decision-making systems \citep{kochenderfer2012next} to medical diagnoses \citep{Lustgarten_2011}.
-In many application, it is assume that all random variables in Bayesian networks are discrete, since many Bayesian network algorithms are unable to deal with continuous variables efficiently.
+Bayesian networks \citep{Pearl_1988, PGM_2009}, which first first emerged from artificial intelligence research, are an increasingly popular method for modeling uncertainty and causality with applications ranging from decision-making systems \citep{kochenderfer2012next} to medical diagnoses \citep{Lustgarten_2011}.
+Bayesian networks provide an efficient factorization of the joint probability distribution over a set of random variables.
+In most cases, one assumes that the random variables in a Bayesian network are discrete, since many Bayesian network learning algorithms are unable to efficiently handle continuous variables.
 In addition, many of the commonly used Bayesian network software packages, such as Netica \citep{netica1992}, SMILearn \citep{druzdzel1999smile}, and bnlearn \citep{bnlearn2010}, are geared towards discrete variables.
@@
 There are three common approaches to extending Bayesian networks to continuous variables.
-The first is to model the conditional probability density of each continuous variable using specific families of parametric distributions, and then to redesign Bayesian network learning and inference algorithms based on their parameters.
-One successful example are Gaussian graphical models \citep{Weiss_2011}.
-For other parametric distributions and non-linear functions \citep{Ihler_2009}, these redesigned algorithms are computationally expensive and do not perform well.
-The second is to use nonparametric distributions, such as particle representations and Gaussian processes \citep{Ickstadt_2010}.
+The first is to model the conditional probability density of each continuous variable using specific families of parametric distributions, and then to redesign Bayesian network learning and inference algorithms based on the distribution parameters.
+One successful example of parametric continuous distributions in Bayesian networks is the Gaussian graphical model \citep{Weiss_2011}.
+For other parametric distributions and non-linear functions \citep{Ihler_2009}, however, these redesigned algorithms are computationally expensive and the Gaussian assumption on the underlying data does not always hold.
+
+The second approach is to use nonparametric distributions, such as particle representations and Gaussian processes \citep{Ickstadt_2010}.
 Unlike parametric methods, nonparametric methods do not make assumptions about the probability distributions being used.
@@
 Automated discretization methods have been studied in machine learning and statistics for many years \citep{Dougherty_1995, Kerber_1992, Holte_1993, Fayyad_1993}, primarily for classification problems.
-They search for the best discretization policy of a continuous attribute by considering its interation with the target class variable.
-Interations and dependencies between variables in Bayesian networks are more complicated, where discretization requires considering the impact on the variable's Markov blanket.
+These methods search for the best discretization policy for a continuous attribute by considering its interation with a class variable.
+Today it is common practice to discretize all continuous variables before learning a Bayesian network structure, which does not consider variable interactions, as interations and dependencies between variables in Bayesian networks are more complicated; discretization of a variable in a network requires considering the impact on the variable's Markov blanket.
 Prior work exists for discretizing continuous variables in naive Bayesian networks and tree-augmented networks \citep{Fried_naive}, but only a few discretization methods for general Bayesian networks have been proposed \citep{Friedman_1996, Kozlov_1997, Monti_1998, Steck_2007}.
 
-This work is primarily concerned with the minimum description length (MDL) principle discretization \citep{Friedman_1996} and MODL discretization \citep{Boulle_2006} methods.
-The former is the predominant discretization method for continuous variables in Bayesian networks, and is compared to our proposed Bayesian method in Section~\ref{sec:experiments}.
-The latter is a Bayesian discretization method for one continuous variable against a discrete target class, which our proposed method generalizes to Bayesian networks.
-The asymptotical equivalence between MDL and MODL was examined in \citep{VL_2000}.
-
+The predominant discretization method for continuous variables in Bayesian networks is the minimum description length (MDL) principle discretization method \citep{Friedman_1996}.
 The MDL principle was first proposed by \cite{MDL_1978} and states that the best model for a dataset is one that minimizes the amount of information needed to describe it \citep{Grunwald_2009}.
@@
 In the context of Bayesian networks, \cite{Friedman_1996} applied the MDL principle to determine the optimal number of discretization intervals for continuous variables and the optimal positions of their discretization edges.
-Their approach selects a discretization policy that minimizes the sum of the description lengths of the discretized Bayesian network and the information necessary for recovering the continuous values from the discretized data.
-Results in this work suggest that the MDL method suffers from low sensitivity to discretization edges and returns low numbers of discretization intervals on continuous variables.
-
-The optimal discretization policy is found with dynamic programming, and it takes runtime $\bigo\paren{n^3 + q \cdot n^2}$, where $n$ is the number of data instances and $q$ is a constant that exponentially depends on cardinalities of variables in Bayesian networks and will be discussed in Section \ref{sec:experiments}.
-For Bayesian networks with multiple continuous variables, MDL discretization is iteratively applied to each continuous variables.
-While iterating, only one variable is treated as continuous while all other continuous variables are treated as discretized based on an initial discretization policy or the discretization result from a previous iteration.
-
-The network structure is not always known in advance.
-Bayesian network structure learning can be extended to distributions including continuous variables by alternating between traditional discrete structure learning and optimal discretization.
-Starting with some preliminary discretization policy, one applys a structure learning algorithm to identify the locally optimal graph structure.
-The discretization policy is refined based on the learned network.
-The cycle is continued until convergence.
-
-MODL discretization \citep{Boulle_2006} is a Bayesian method for discretizing a continuous feature according to a class variable.
-Bayesian methods maximize the probability of the model given the data, $P(\textit{Model} \mid \textit{Data})$.
+Their approach selects a discretization policy that minimizes the sum of the description length of the discretized Bayesian network and the information necessary for recovering the continuous values from the discretized data.
+
+The optimal discretization policy of a single continuous variable under MDL is found using dynamic programming, and has runtime $\bigo\paren{n^3 + q \cdot n^2}$, where $n$ is the number of data samples and $q$ is a constant with exponential dependency on the cardinalities of the variables in the Bayesian network.
+For Bayesian networks with multiple continuous variables, MDL discretization is iteratively applied to each continuous variable.
+While iterating, only one variable is treated as continuous, while all other continuous variables are treated as discretized based on an initial discretization policy or the discretization result from a previous iteration.
+
+MDL discretization requires that the network structure be known in advance, but can be incorporated into the structure learning process which would otherwise have required pre-discretized variables.
+This approach alternates between traditional discrete structure learning and optimal discretization. \tim{Is this something this paper proposes or was this done with MDL before?}
+Starting with some preliminary discretization policy, one first applys a structure learning algorithm to identify the locally optimal graph structure.
+One then refines the discretization policy based on the learned network.
+The cycle is repeated until convergence.
+
+Results in this work suggest that the MDL method suffers from low sensitivity to discretization edges location and returns low numbers of discretization intervals on continuous variables.
+\tim{We need another sentence to make this a \P.}
+
+MODL \citep{Boulle_2006} is a Bayesian method for discretizing a continuous feature according to a class variable.
+Bayesian methods select the model with maximum posterior probability given the data, $P(\textit{Model} \mid \textit{Data})$.
 An application of Bayes' rule and constant $P(\textit{Data})$ shows that this is equivalent to maximizing ${P(\textit{Model}) \cdot P(\textit{Data} \mid \textit{Model})}$, where $P(\textit{Model})$ is a prior over models and ${P(\textit{Data} \mid \textit{Model})}$ is the data likelihood.
 The data likelihood usually increases with the number of discretization intervals, as more intervals allow for richer representations.
-The prior is chosen to decrease as the number of discretization intervals increases to favor simpler models and prevent overfitting.
+The prior is chosen to influence the relative merit between models, and for discretization policies the prior is negatively correlated with the number of discretization intervals to favor simpler models and prevent overfitting.
 Maximizing ${P(\textit{Model}) \cdot P(\textit{Data} \mid \textit{Model})}$ requires a trade-off when determining the number of discretization intervals.
 
-The MODL method uses dynamic programming to find the optimal discretization policy, and has an $\bigo\paren{n^3 + r \cdot n^2}$ runtime, where $r$ is the number of instances for the class variable.
-\cite{Lustgarten_2011} suggest several formulations for the prior term $P(\text{Model})$.
-Under the suggested prior, which includes the uniform prior probabilities in MODL as a special case, the runtime can be reduced to $\bigo\paren{r \cdot n^2}$ without sacrificing optimality.
+The MODL method uses dynamic programming to find the optimal discretization policy for a continuous variable given a discrete class variable, and has an $\bigo\paren{n^3 + r \cdot n^2}$ runtime, where $r$ is the number of instances for the class variable.
+\cite{Lustgarten_2011} suggest several formulations for the prior term $P(\text{Model})$, and the asymptotical equivalence between MDL and MODL on the single-variable, single-class problem was examined in \citep{VL_2000}.
 
@@
 The proposed method optimizes the discretization policy relative to the network and takes parents, children, and spouse variables into account.
-The optimal single-variable discretization method is derived in Section~\ref{sec:single_var}.
-Section~\ref{sec:multi_var} covers Bayesian networks with multiple continuous variables and discretization while simultaneously learning network structure.
+The optimal single-variable discretization method is derived in Section~\ref{sec:single_var}, using a prior which reduces the discretization runtime to $\bigo\paren{r \cdot n^2}$ without sacrificing optimality.
+Section~\ref{sec:multi_var} covers Bayesian networks with multiple continuous variables and how to discretize while simultaneously learning network structure.
 The paper concludes with a comparison against the existing minimum-description length \citep{Friedman_1996} method on real-world datasets in Section~\ref{sec:experiments}.

### 2015-11-24 graph_wine_exp2_distr_5_11.tex
intro update

--- 2015-11-17 graph_wine_exp2_distr_5_11.tex
@@
 			colorbar,
-			point meta min=0, point meta max=0.5,
+			point meta min=0, point meta max=2.5,
 			colormap={}{ gray(0cm)=(1); gray(1cm)=(0);},
 			colorbar style={
-			        ytick={0,0.05,...,0.5},
+			        ytick={0,0.5,...,2.6},
+			        ylabel={probability density $\times 10^2$},
+			        y label style={at={(axis description cs:6.5,0.5)},rotate=180,anchor=north},
 			        yticklabel style={
@@
 
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.6000,1.2800,0.0440) (17.9000,1.2800,0.0440) (17.9000,3.4600,0.0440) (10.6000,3.4600,0.0440)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.6000,3.4600,0.0820) (17.9000,3.4600,0.0820) (17.9000,4.8500,0.0820) (10.6000,4.8500,0.0820)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.6000,4.8500,0.1480) (17.9000,4.8500,0.1480) (17.9000,7.4000,0.1480) (10.6000,7.4000,0.1480)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.6000,7.4000,0.0195) (17.9000,7.4000,0.0195) (17.9000,13.0000,0.0195) (10.6000,13.0000,0.0195)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.6000,1.2800,0.276486) (17.9000,1.2800,0.276486) (17.9000,3.4600,0.2765) (10.6000,3.4600,0.2765)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.6000,3.4600,0.808121) (17.9000,3.4600,0.808121) (17.9000,4.8500,0.8081) (10.6000,4.8500,0.8081)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.6000,4.8500,0.795058) (17.9000,4.8500,0.795058) (17.9000,7.4000,0.7951) (10.6000,7.4000,0.7951)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.6000,7.4000,0.047701) (17.9000,7.4000,0.047701) (17.9000,13.0000,0.0477) (10.6000,13.0000,0.0477)};
 
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.9000,1.2800,0.2565) (30.0000,1.2800,0.2565) (30.0000,3.4600,0.2565) (17.9000,3.4600,0.2565)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.9000,3.4600,0.1320) (30.0000,3.4600,0.1320) (30.0000,4.8500,0.1320) (17.9000,4.8500,0.1320)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.9000,4.8500,0.1640) (30.0000,4.8500,0.1640) (30.0000,7.4000,0.1640) (17.9000,7.4000,0.1640)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.9000,7.4000,0.1540) (30.0000,7.4000,0.1540) (30.0000,13.0000,0.1540) (17.9000,13.0000,0.1540)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.9000,1.2800,0.972401) (30.0000,1.2800,0.972401) (30.0000,3.4600,0.9724) (17.9000,3.4600,0.9724)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.9000,3.4600,0.784827) (30.0000,3.4600,0.784827) (30.0000,4.8500,0.7848) (17.9000,4.8500,0.7848)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.9000,4.8500,0.531518) (30.0000,4.8500,0.531518) (30.0000,7.4000,0.5315) (17.9000,7.4000,0.5315)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.9000,7.4000,0.227273) (30.0000,7.4000,0.227273) (30.0000,13.0000,0.2273) (17.9000,13.0000,0.2273)};
 
-			\addplot3[mark=+, draw=none, mark size=0.7] coordinates {
+			\addplot3[mark=+, draw=none, mark size=1.0, jitter = 0.1] coordinates {
 (15.600,5.640,1) (11.200,4.380,1) (18.600,5.680,1) (16.800,7.800,1) (21.000,4.320,1) (15.200,6.750,1) (14.600,5.250,1) (17.600,5.050,1) (14.000,5.200,1) (16.000,7.220,1) (18.000,5.750,1) (16.800,5.000,1) (16.000,5.600,1) (11.400,5.400,1) (12.000,7.500,1) (17.200,7.300,1) (20.000,6.200,1) (20.000,6.600,1) (16.500,8.700,1) (15.200,5.100,1) (16.000,5.650,1) (18.600,4.500,1) (16.600,3.800,1) (17.800,3.930,1) (20.000,3.520,1) (25.000,3.580,1) (16.100,4.800,1) (17.000,3.950,1) (19.400,4.500,1) (16.000,4.700,1) (22.500,5.700,1) (19.100,6.900,1) (17.200,3.840,1) (19.500,5.400,1) (19.000,4.200,1) (20.500,5.100,1) (15.500,4.600,1) (18.000,4.250,1) (15.500,3.700,1) (13.200,5.100,1) (16.200,6.130,1) (18.800,4.280,1) (15.000,5.430,1) (17.500,4.360,1) (17.000,5.040,1) (18.900,5.240,1) (16.000,4.900,1) (16.000,6.100,1) (18.800,6.200,1) (17.400,8.900,1) (12.400,7.200,1) (17.200,5.600,1) (14.000,7.050,1) (17.100,6.300,1) (16.400,5.850,1) (20.500,6.250,1) (16.300,6.380,1) (16.800,6.000,1) (16.700,6.800,1) (10.600,1.950,1) (16.000,3.270,1) (16.800,5.750,1) (18.000,3.800,1) (19.000,4.450,1) (19.000,2.950,1) (18.100,4.600,1) (15.000,5.300,1) (19.600,4.680,1) (17.000,3.170,1) (16.800,2.850,1) (20.400,3.050,1) (25.000,3.380,1) (24.000,3.740,1) (30.000,3.350,1) (21.000,3.210,1) (16.000,3.800,1) (16.000,4.600,1) (18.000,2.650,1) (14.800,3.400,1) (23.000,2.570,1) (19.000,2.500,1) (18.800,3.900,1) (24.000,2.200,1) (22.500,4.800,1) (18.000,3.050,1) (18.000,2.620,1) (22.800,2.450,1) (26.000,2.600,1) (21.600,2.800,1) (23.600,1.740,1) (18.500,2.400,1) (22.000,3.600,1) (20.700,3.050,1) (18.000,2.150,1) (18.000,3.250,1) (19.000,2.600,1) (21.500,2.500,1) (16.000,2.900,1) (18.500,4.500,1) (18.000,2.300,1) (17.500,3.300,1) (18.500,2.450,1) (21.000,2.800,1) (19.500,2.060,1) (20.500,2.940,1) (22.000,2.700,1) (19.000,3.400,1) (22.500,3.300,1) (19.000,2.700,1) (20.000,2.650,1) (19.500,2.900,1) (21.000,2.000,1) (20.000,3.800,1) (21.000,3.080,1) (22.500,2.900,1) (21.500,1.900,1) (20.800,1.950,1) (22.500,2.060,1) (16.000,3.400,1) (19.000,1.280,1) (20.000,3.250,1) (28.500,6.000,1) (26.500,2.080,1) (21.500,2.600,1) (21.000,2.800,1) (21.000,2.760,1) (21.500,3.940,1) (28.500,3.000,1) (24.500,2.120,1) (22.000,2.600,1) (18.000,4.100,1) (20.000,5.400,1) (24.000,5.700,1) (21.500,5.000,1) (17.500,5.450,1) (18.500,7.100,1) (21.000,3.850,1) (25.000,5.000,1) (19.500,5.700,1) (24.000,4.920,1) (21.000,4.600,1) (20.000,5.600,1) (23.500,4.350,1) (20.000,4.400,1) (18.500,8.210,1) (21.000,4.000,1) (20.000,4.900,1) (21.500,7.650,1) (21.500,8.420,1) (21.500,9.400,1) (24.000,8.600,1) (22.000,10.800,1) (25.500,7.100,1) (18.500,10.520,1) (20.000,7.600,1) (22.000,7.900,1) (19.500,9.010,1) (27.000,7.500,1) (25.000,13.000,1) (22.500,11.750,1) (21.000,7.650,1) (20.000,5.880,1) (22.000,5.580,1) (18.500,5.280,1) (22.000,9.580,1) (22.500,6.620,1) (23.000,10.680,1) (19.500,10.260,1) (24.500,8.660,1) (25.000,8.500,1) (19.000,5.500,1) (19.500,9.900,1) (20.000,9.700,1) (20.500,7.700,1) (23.000,7.300,1) (20.000,10.200,1) (20.000,9.300,1) (24.500,9.200,1) };

### 2015-11-24 BN_discretizer_paper.tex
find a typo

@@
 where $\lambda_1 = s_1$, $\lambda_i \in s_{1:m}$, $\gamma_1 = \lambda_1$, and $\gamma_i = \lambda_i - \lambda_{i-1}$.
-The $\lambda_{1:k}$ representation is the number of instances before every discretization edge whereas the $\lambda$ representation is the number of instances within each discretization interval.
+The $\lambda_{1:k}$ representation is the number of instances before every discretization edge whereas the $\gamma_{1:k}$ representation is the number of instances within each discretization interval.
 

### 2015-11-24 BN_discretizer_paper.tex
incorporated TCP's suggestions

--- 2015-11-24 BN_discretizer_paper.tex
@@
 The optimal single-variable discretization method is derived in Section~\ref{sec:single_var}, using a prior which reduces the discretization runtime to $\bigo\paren{r \cdot n^2}$ without sacrificing optimality.
-Section~\ref{sec:multi_var} covers Bayesian networks with multiple continuous variables and how to discretize while simultaneously learning network structure.
+Section~\ref{sec:multi_var} covers Bayesian networks with multiple continuous variables and Section~\ref{sec:structure_learning} covers discretization while simultaneously learning network structure.
 The paper concludes with a comparison against the existing minimum-description length \citep{Friedman_1996} method on real-world datasets in Section~\ref{sec:experiments}.
@@
 This section covers the notation used throughout the paper and provides a brief overview of Bayesian networks, including the factorization of joint probability distributions, sampling from a Bayesian network, and structure learning.
-These concepts will be used in later sections.
 The formal definition of a discretization policy for a continuous variable is also given.
@@
 Structure search for a Bayesian network seeks the graph structure $G$ that maximizes ${P(G\mid D)}$.
-In practice one maximizes the log-likelihood, also known as the Bayesian score~\cite{cooper1992bayesian}:
+In practice, one maximizes the log-likelihood, also known as the Bayesian score~\citep{cooper1992bayesian}:
 
@@
 
-The space of acyclic graphcs is superexponential in the number of nodes so it is common to rely on heuristic search strategies \citep{PGM_2009}.
+The space of acyclic graphs is superexponential in the number of nodes, and it is common to rely on heuristic search strategies \citep{PGM_2009}.
 The K2 algorithm assumes a topological ordering of variables and greedily adds parents to nodes to maximally increase the Bayesian score.
 A fixed ordering ensures acyclicity but does not guarantee a globally optimal network structure.
-K2 is typically run multiple times with random variable orderings and the network with the highest likelihood is retained.
+K2 is typically run multiple times with random variable orderings, and the network with the highest likelihood is retained.
 
@@
 The discretization edges $e_{1:k-1}$ mark the boundaries between discretization intervals.
-In this work they are restricted to the midpoints between unique ascending instances of $\cX$.
+In this paper, as with MODL, they are restricted to the midpoints between unique ascending instances of $\cX$.
 Thus, each edge $e_i = \paren{\cu_{j} + \cu_{{j+1}}}/2$ for some $j$.
@@
 
-Finally, when discussing the discretization of a particular continuous variable $\cX$, let $P_i$ be the $i$th parent of $\cX$, let $C_i$ be the $i$th child of $\cX$, and let $\bm{S}_i$ be set of spouses of $\cX$ corresponding to the $i$th child.
-Context should make it clear when $P$ refers to a discrete probability and when it refers to a variable's parent.
+When discussing the discretization of a particular continuous variable $\cX$, let $P_i$ be the $i$th parent of $\cX$, let $C_i$ be the $i$th child of $\cX$, and let $\bm{S}_i$ be the set of spouses of $\cX$ corresponding to the $i$th child.
+The context should make it clear when $P$ refers to a discrete probability and when it refers to a variable's parent.
 
@@
 
-The two factors on the right hand side comes from the second principle: all distributions of values of $\Pa_{\cX}$ in a given interval are equiprobable.
+The two factors on the right hand side come from the second principle: all distributions of values of $\Pa_{\cX}$ in a given interval are equiprobable.
 According to the fourth principle, the distribution in each interval is independent, so the two factors can be multiplied together.
@@
 
-\subsection{Algorithm}
+\subsection{Single-Variable Discretization Algorithm}
 \label{subsec:algo}
@@
 This section describes the procedure used to minimize the objective function.
-Note that the objective function is cumulative over intervals, thus, if a partition of $X$ into $k$ intervals by $\Lambda = \curly{\gamma_1 , \gamma_2  , \ldots , \gamma_k}$ is an optimal discretization policy, then any subinterval is optimal for the corresponding subproblem.
+Note that because the objective function is cumulative over intervals; if a partition of $X$ into $k$ intervals by $\Lambda = \curly{\gamma_1 , \gamma_2  , \ldots , \gamma_k}$ is an optimal discretization policy, then any subinterval is optimal for the corresponding subproblem.
 It follows that dynamic programming can be used to solve the optimization problem exactly.
@@
 Precomputation reduces runtime.
-Compute $h(u,v)$ for each interval $\gamma_q$ starting from $x_{u}$ to $x_{v}$ for all $u$, $v$ satisfying $u \leq v$:
+Hence, $h(u,v)$ is computed first for each interval $\gamma_q$ starting from $x_{u}$ to $x_{v}$ for all $u$, $v$ satisfying $u \leq v$:
 
@@
 Algorithm~\ref{alg:disc_one} is guaranteed to be optimal.
-For faster methods with suboptimal results please refer to the work of \cite{Boulle_2006}.
+For faster methods with suboptimal results, see \citet{Boulle_2006}.
 
@@
 
-\subsection{Discretization of Multiple Continuous Variables}
-
 The single-variable discretization method can be extended to Bayesian networks with multiple continuous variables by iteratively discretizing individual variables.
@@
 The iterative approach uses a prediscretization policy in order to initialize the process.
-This work prediscretizes all continuous variables into $k$ equal-width intervals, where $k$ is largest value of the number of intervals of initially discrete variables in the network.
+In this paper, prediscretization assigns $k$ equal-width intervals to each continuous variables, where $k$ is largest value of the number of intervals of initially discrete variables in the network.
 
@@
 The algorithm typically converges within a few passes when tested on real-world data.
-In cases where it does not converge, usually observed when also learning structure, ten passes produce decent discretization results.
+In cases where it does not converge, usually observed when also learning structure, ten passes produce sufficient discretization results.
+\tim{If it only fails to converge with structure learning, perhaps we should take out the max upper bound in Alg~\ref{alg:disc_two}.}
 
@@
 
-\subsection{Combining Discretization with Structure Learning}
-
-In many situations the network structure is not known in advance and must be learned from data.
+\section{Combining Discretization with Structure Learning}
+\label{sec:structure_learning}
+
+\todo{move relevant notation here}
+
+In many situations, the network structure is not known in advance and must be learned from data.
 Traditional Bayesian structure learning algorithms require discretized data, whereas the proposed discretization algorithm requires a known network structure.
-This section combines the proposed discretization method with the K2 structure learning algorithm \citep{K2} in an interative fassion to simultaneously perform Bayesian structure learning and discretization of continuous variables.
+This section describes how the proposed discretization method can be combined with the K2 structure learning algorithm \citep{K2} to simultaneously perform Bayesian structure learning and discretization of continuous variables.
 
 The proposed algorithm alternates between K2 structure learning and discretization.
-K2 is run on the discretized dataset corresponding to prediscretizations for all continuous variables.
+The dataset is prediscretized as was described in Section~\ref{sec:multi_var}, and K2 is run to obtain an initial network structure.
 The affected continuous variables are rediscretized every time an edge is added by K2.
 The resulting discretization policies are used to update the discretized dataset, and the next step of the K2 algorithm is executed.
-This cycle is repeated until the K2 algorithm reaches a local maximum.
-
-This procedure is given in Algorithm~\ref{alg:structure_learn}.
-It takes five inputs: $D$, a dataset of samples from the joint distribution; $\bm{\cX}$, the set of all continuous variables; $\texttt{order}$, a permutation of the variables in $D$; $\hat{n}_\text{parent}$, an upper bound on the number of parents per node; and $\maxpasses$, an upper bound on the number of complete passes.
+This cycle is repeated until the K2 algorithm converges.
+
+This procedure is given in Algorithm~\ref{alg:structure_learn}, and takes five inputs: $D$, a dataset of samples from the joint distribution; $\bm{\cX}$, the set of all continuous variables; $\texttt{order}$, a permutation of the variables in $D$; $\hat{n}_\text{parent}$, an upper bound on the number of parents per node; and $\maxpasses$, an upper bound on the number of complete passes.
+The upper bound on the number of parents is common practice, and is done to prevent computing conditional distribtions with excessively large parameter sets. \tim{cite?}
 The function $g$ in Algorithm~\ref{alg:structure_learn} computes a component of the Bayesian score (Equation~\ref{eq:BayesianScore}):
@@
 It is common practice to run K2 multiple times with different variable permutations and to then choose the structure with the highest score.
-As such, Algorithm~\ref{alg:structure_learn} is run multiple times with different variable permutations and the discretized Bayesian network with the highest score is retaiend.
+As such, Algorithm~\ref{alg:structure_learn} is run multiple times with different variable permutations and the discretized Bayesian network with the highest score is retained.
 

### 2015-11-24 BN_discretizer_paper.tex
appendix text

@@
 
-The Bayesian network structure in Figure \ref{fig:auto_graph_3} and the discretization results in Table \ref{table:auto_disc_table_3} demonstrate that the MDL method does not always return smaller number of discretization intervals than the Bayesian approach and also the MDL method can return a comparable result in terms of likelihood.
-The Bayesian network in Figure \ref{fig:auto_graph_3} is obtained by running Algorithm \ref{alg:structure_learn} fifty times with $u_{\text{parent}} = 2$.
-Therefore, this network can be considered more well-structured than the one in Figure \ref{fig:auto_graph_1}, since the effect of discretization policies has already been considered in the learning process.
-Many edges appears in both discretization results, as the bold numbers in Table \ref{table:auto_disc_table_3}.
-\begin{figure}[ht]
-  \centering
-  \scalebox{0.8}{
-   \input{graph_autocar_3}}
-   \caption{A Bayesian network structure for Auto MPG dataset that leads to a comparable discretization result of the MDL method with the Bayesian method}
+The Bayesian network structure in Figure~\ref{fig:auto_graph_3} and the discretization results in Table~\ref{table:auto_disc_table_3} demonstrate that the MDL method does not always produce fewer discretization intervals than the Bayesian approach and that the MDL method can produce discretization policies with comparable likelihood.
+The Bayesian network in Figure~\ref{fig:auto_graph_3} was obtained by running Algorithm~\ref{alg:structure_learn} fifty times on the Auto MPG dataset with a maximum of two parents per variable.
+The network is more well-structured than the one in Figure~\ref{fig:auto_graph_1}, because the discretization policies were simultaneously learned with the network structure.
+Many edges appears in both discretization results, and are bolded in Table~\ref{table:auto_disc_table_3}.
+
+\begin{figure}[ht]
+  \centering
+  \scalebox{0.8}{\input{graph_autocar_3}}
+  \caption{A Bayesian network structure for the Auto MPG dataset that leads to comparable discretization policies from the MDL and Bayesian methods.}
   \label{fig:auto_graph_3}
@@
   \caption{
-    Results from discretization of the Auto MPG dataset with fixed structure from Figure~\ref{fig:auto_graph_3}.
+    The discretization policies for the Auto MPG dataset with the fixed structure shown in Figure~\ref{fig:auto_graph_3}.
     The first five rows list the discretization edges for each continuous variable.
-    The last row lists the mean cross-validated log-likelihood.
-    Two methods have same discretization result on variable $A$.
-    Log-likelihood shows that the MDL method is just slightly worse than the Bayesian method.
+    The last row shows the mean cross-validated log-likelihood under each policy.
+    The methods have same discretization result on variable $A$, and the log-likelihood for the MDL method only just slightly worse than that of the Bayesian method.
   }

### 2015-11-24 BN_discretizer_paper.tex
Two changes suggested in Mykel's comment

@@
 The MODL method uses dynamic programming to find the optimal discretization policy for a continuous variable given a discrete class variable, and has an $\bigo\paren{n^3 + r \cdot n^2}$ runtime, where $r$ is the number of instances for the class variable.
-\cite{Lustgarten_2011} suggest several formulations for the prior term $P(\text{Model})$, and the asymptotical equivalence between MDL and MODL on the single-variable, single-class problem was examined in \citep{VL_2000}.
+\cite{Lustgarten_2011} suggest several formulations for the prior term $P(\text{Model})$, and the asymptotical equivalence between MDL and MODL on the single-variable, single-class problem was examined by \citet{VL_2000}.
 
@@
     The scatter points were jittered to reveal the repeated values in the dataset.
-    The repeated values lead to a high number of discretization edges, because repeated values can easily form discretized regions by their own.
+    The repeated values lead to a high number of discretization edges, because repeated values can easily form discretized regions on their own.
   }

### 2015-11-24 BN_discretizer_paper.tex
incorporating Yi-Chun's comments

--- 2015-11-24 BN_discretizer_paper.tex
@@
 
-MDL discretization requires that the network structure be known in advance, but can be incorporated into the structure learning process which would otherwise have required pre-discretized variables.
-This approach alternates between traditional discrete structure learning and optimal discretization. \tim{Is this something this paper proposes or was this done with MDL before?}
+MDL discretization requires that the network structure be known in advance, but can be incorporated into the structure learning process.
+Simultaneous structure learning and discretization alternates between traditional discrete structure learning and optimal discretization.
 Starting with some preliminary discretization policy, one first applys a structure learning algorithm to identify the locally optimal graph structure.
@@
 
-Results in this work suggest that the MDL method suffers from low sensitivity to discretization edges location and returns low numbers of discretization intervals on continuous variables.
-\tim{We need another sentence to make this a \P.}
+Results in this work suggest that the MDL method suffers from low sensitivity to discretization edge locations and returns low numbers of discretization intervals on continuous variables.
+This is caused by the MDL's use of mutual information to rate discretization edges.
+Mutual information, which is composed of empirical probabilities computed using event count ratios, varies less severely with the positions of discretization edges than the method proposed below.
 

### 2015-11-24 BN_discretizer_paper.tex
another runthrough. We still need to do the ref section

@@
 \usepackage{boondox-cal} % for lowercase caligraphic
+
 % \usepackage[capitalize]{cleveref}
@@
 \DeclareMathOperator{\Pa}{pa} % parents of a var in a BN
+\DeclareMathOperator{\Ch}{ch} % children of a var in a BN
 \newcommand{\cX}{\mathcal{X}} % continuous X
@@
 
-Bayesian networks \citep{Pearl_1988, PGM_2009}, which first first emerged from artificial intelligence research, are an increasingly popular method for modeling uncertainty and causality with applications ranging from decision-making systems \citep{kochenderfer2012next} to medical diagnoses \citep{Lustgarten_2011}.
+Bayesian networks \citep{Pearl_1988, PGM_2009}, which first emerged from artificial intelligence research, are an increasingly popular method for modeling uncertainty and causality, with applications ranging from decision-making systems \citep{kochenderfer2012next} to medical diagnosis \citep{Lustgarten_2011}.
 Bayesian networks provide an efficient factorization of the joint probability distribution over a set of random variables.
-In most cases, one assumes that the random variables in a Bayesian network are discrete, since many Bayesian network learning algorithms are unable to efficiently handle continuous variables.
+In most cases, one assumes that the random variables in a Bayesian network are discrete, since many Bayesian network learning and inference algorithms are unable to efficiently handle continuous variables.
 In addition, many of the commonly used Bayesian network software packages, such as Netica \citep{netica1992}, SMILearn \citep{druzdzel1999smile}, and bnlearn \citep{bnlearn2010}, are geared towards discrete variables.
-However, various applications require the use of continuous variables, such as position and velocity in dynamic systems \citep{kochenderfer2010airspace}.
+However, many applications require the use of continuous variables, such as position and velocity in dynamic systems \citep{kochenderfer2010airspace}.
 
 There are three common approaches to extending Bayesian networks to continuous variables.
-The first is to model the conditional probability density of each continuous variable using specific families of parametric distributions, and then to redesign Bayesian network learning and inference algorithms based on the distribution parameters.
-One successful example of parametric continuous distributions in Bayesian networks is the Gaussian graphical model \citep{Weiss_2011}.
-For other parametric distributions and non-linear functions \citep{Ihler_2009}, however, these redesigned algorithms are computationally expensive and the Gaussian assumption on the underlying data does not always hold.
+The first is to model the conditional probability density of each continuous variable using specific families of parametric distributions, and then to redesign Bayesian network learning and inference algorithms based on the parameterization.
+One successful example of parametric, continuous distributions in Bayesian networks is the Gaussian graphical model \citep{Weiss_2011}.
+For other parametric distributions and non-linear functions \citep{Ihler_2009}, however, these redesigned algorithms are computationally expensive, and the Gaussian assumption on the underlying data does not always hold.
 
 The second approach is to use nonparametric distributions, such as particle representations and Gaussian processes \citep{Ickstadt_2010}.
-Unlike parametric methods, nonparametric methods do not make assumptions about the probability distributions being used.
+Unlike parametric methods, nonparametric methods can often fit any underlying probability distribution given sufficient data.
 Parametric models have a fixed number of parameters, whereas the number of parameters in a nonparametric model grow with the amount of training data.
+Inference algorithms on nonparametric models are often inefficient due to the large number of parameters they must refer to.
 
@@
 These methods search for the best discretization policy for a continuous attribute by considering its interation with a class variable.
-Today it is common practice to discretize all continuous variables before learning a Bayesian network structure, which does not consider variable interactions, as interations and dependencies between variables in Bayesian networks are more complicated; discretization of a variable in a network requires considering the impact on the variable's Markov blanket.
+Today it is common practice to discretize all continuous variables before learning a Bayesian network structure to avoid having to consider variable interactions, as interations and dependencies between variables in Bayesian networks are more complicated.
+The discretization of a variable in a network requires considering the impact on the variable's Markov blanket.
 Prior work exists for discretizing continuous variables in naive Bayesian networks and tree-augmented networks \citep{Fried_naive}, but only a few discretization methods for general Bayesian networks have been proposed \citep{Friedman_1996, Kozlov_1997, Monti_1998, Steck_2007}.
@@
 The predominant discretization method for continuous variables in Bayesian networks is the minimum description length (MDL) principle discretization method \citep{Friedman_1996}.
-The MDL principle was first proposed by \cite{MDL_1978} and states that the best model for a dataset is one that minimizes the amount of information needed to describe it \citep{Grunwald_2009}.
+The MDL principle was first proposed by \cite{MDL_1978}, and states that the best model for a dataset is the one that minimizes the amount of information needed to describe it \citep{Grunwald_2009}.
 MDL methods trade off goodness-of-fit against model complexity to reduce generalization error.
@@
 
-The optimal discretization policy of a single continuous variable under MDL is found using dynamic programming, and has runtime $\bigo\paren{n^3 + q \cdot n^2}$, where $n$ is the number of data samples and $q$ is a constant with exponential dependency on the cardinalities of the variables in the Bayesian network.
+The optimal discretization policy of a single continuous variable under MDL is found using dynamic programming in runtime $\bigo\paren{n^3 + q \cdot n^2}$, where $n$ is the number of data samples and $q$ is a constant with exponential dependency on the cardinalities of the variables in the Bayesian network.
 For Bayesian networks with multiple continuous variables, MDL discretization is iteratively applied to each continuous variable.
@@
 
-MDL discretization requires that the network structure be known in advance, but can be incorporated into the structure learning process.
+MDL discretization requires that the network structure be known in advance, but an iterative approach allows it to be incorporated into the structure learning process.
 Simultaneous structure learning and discretization alternates between traditional discrete structure learning and optimal discretization.
-Starting with some preliminary discretization policy, one first applys a structure learning algorithm to identify the locally optimal graph structure.
+Starting with some preliminary discretization policy, one first applies a structure learning algorithm to identify the locally optimal graph structure.
 One then refines the discretization policy based on the learned network.
@@
 
-Results in this work suggest that the MDL method suffers from low sensitivity to discretization edge locations and returns low numbers of discretization intervals on continuous variables.
-This is caused by the MDL's use of mutual information to rate discretization edges.
+Results in this work suggest that the MDL method suffers from low sensitivity to discretization edge locations and returns low numbers of discretization intervals for continuous variables.
+This is caused by MDL's use of mutual information to rate discretization edges.
 Mutual information, which is composed of empirical probabilities computed using event count ratios, varies less severely with the positions of discretization edges than the method proposed below.
@@
 The prior is chosen to influence the relative merit between models, and for discretization policies the prior is negatively correlated with the number of discretization intervals to favor simpler models and prevent overfitting.
-Maximizing ${P(\textit{Model}) \cdot P(\textit{Data} \mid \textit{Model})}$ requires a trade-off when determining the number of discretization intervals.
+Maximizing ${P(\textit{Model}) \cdot P(\textit{Data} \mid \textit{Model})}$ thus requires a trade-off when determining the number of discretization intervals.
 
 The MODL method uses dynamic programming to find the optimal discretization policy for a continuous variable given a discrete class variable, and has an $\bigo\paren{n^3 + r \cdot n^2}$ runtime, where $r$ is the number of instances for the class variable.
-\cite{Lustgarten_2011} suggest several formulations for the prior term $P(\text{Model})$, and the asymptotical equivalence between MDL and MODL on the single-variable, single-class problem was examined by \citet{VL_2000}.
+\cite{Lustgarten_2011} suggest several formulations for the prior term $P(\textit{Model})$, and the asymptotical equivalence between MDL and MODL on the single-variable, single-class problem was examined by \citet{VL_2000}.
 
@@
 \label{sec:preliminaries}
-This section covers the notation used throughout the paper and provides a brief overview of Bayesian networks, including the factorization of joint probability distributions, sampling from a Bayesian network, and structure learning.
-The formal definition of a discretization policy for a continuous variable is also given.
-
-\subsection{Bayesian Networks and Sampling}
+This section covers the notation used throughout the paper to describe discretization policies.
+This section also provides a brief overview of Bayesian networks.
+
+\subsection{Discretization Policies}
+\label{subsec:disc_policy}
+
+Let $\cX$ be a continuous variable and let $\cx$ be a specific instance of $\cX$.
+A discretization policy $\Lambda_{\cX} = \anglebrackets{e_1 < e_2 < \ldots < e_{k-1}}$ for $\cX$ is a mapping from $\mathbb{R}$ to $\curly{1,2,3,\ldots,k}$ such that
+
+\begin{equation}
+  \Lambda_{\cX}(\cx) = \begin{cases}
+    1, & \text{if $x<e_1$}\\
+    i, & \text{if $e_{i-1} \leq x < e_i$}\\
+    k, & \text{otherwise.}
+  \end{cases}
+\end{equation}
+
+\noindent
+The discretization policy discretizes $\cX$ into $k$ intervals.
+Let the samples of $\cX$ in a given dataset $D$ be sorted in ascending order, ${\cx_{1:n} = \curly{\cx_1 \leq \cx_2 \leq \ldots \leq \cx_n}}$, and let the unique values be ${\cu_{1:m} = \curly{\cu_1 \leq \cu_2 \leq \ldots \leq \cu_{m}}}$.
+The index of the last occurence of $\cu_i$ in $\cx_{1:n}$ is denoted $s_i$.
+
+The discretization edges $e_{1:k-1}$ mark the boundaries between discretization intervals.
+In this paper, as with MODL, they are restricted to the midpoints between unique ascending instances of $\cX$.
+Thus, each edge $e_i = \paren{\cu_{j} + \cu_{{j+1}}}/2$ for some $j$.
+Two useful integer representations of $\Lambda_{\cX}$ can be written
+
+\begin{equation}
+\label{eq:disc_def}
+  \Lambda_{\cX} = \anglebrackets{\lambda_1 < \lambda_2  < \ldots < \lambda_k} \equiv \anglebrackets{\gamma_1, \gamma_2, \ldots, \gamma_k}\text{,}
+\end{equation}
+
+\noindent
+where $\lambda_1 = s_1$, $\lambda_i \in s_{1:m}$, $\gamma_1 = \lambda_1$, and $\gamma_i = \lambda_i - \lambda_{i-1}$.
+The $\lambda_{1:k}$ representation is the number of instances before every discretization edge whereas the $\gamma_{1:k}$ representation is the number of instances within each discretization interval.
+
+When discussing the discretization of a particular continuous variable $\cX$, let $P_i$ be the $i$th parent of $\cX$, let $C_i$ be the $i$th child of $\cX$, and let $\bm{S}_i$ be the set of spouses of $\cX$ corresponding to the $i$th child.
+The context should make it clear when $P$ refers to a discrete probability and when it refers to a variable's parent.
+
+\subsection{Bayesian Networks}
 
@@
 The $j$th instantiation of the parents of $X_i$ is denoted $\bm{\pi}_{ij}$.
-
-The conditional relations are parameterized by the elements of $\bm{\theta}$, written $\theta_{ij}^{(k)}$, which determines
-
-\begin{equation}
-P(X_i = k \mid \bm{\pi}_{ij}) = \theta_{ij}^{(k)}\text{.}
-\end{equation}
-
-The joint distribution over the variables in the Bayesian network factors according to the Markov property:
-
-\begin{equation}
-P(X_{1:N}) = \prod_{i=1}^N P(X_i \mid \Pa_{X_i})\text{.}
-\end{equation}
-
-Forward sampling is often used to draw samples from the joint distribution represented by a Bayesian network.
-Variables are sampled in topological order such that parental instantiations are always known~\citep{PGM_2009}.
-Furthermore, the parent $\rightarrow$ child sampling order can be reversed if the marginal probability of the child variable is known.
-% By Bayes' rule,
-
-% \begin{equation}
-% P(X_i \mid \Pa_{X_i}) \cdot \prod_{Y \in \Pa_{X_i}} P(Y) = P(X_i) \cdot P(\Pa_{X_i} \mid X_i)\text{.}
-% \end{equation}
-
-\subsection{Structure Learning}
-
-It is often necessary to infer the structure of a Bayesian network from data.
-Three common approaches to Bayesian network structure learning are constraint-based, score-based, and Bayesian model averaging \citep[see][chap.~18]{PGM_2009}.
-This work uses the K2 structure learning algorithm \citep{K2}, one of the most successful score-based structure learning methods.
-Score-based structure learning methods over discrete variables commonly evaluate candidate structures according to their likelihood against a dataset $D$.
-Let $\beta_{ij}^{(k)}$ be the number of times $X_i = k$ given $\bm{\pi}_{ij}$ in $D$.
-The likelihood is given by
-
-\begin{equation}
-P(D\mid \bm{\theta}, G) = \prod_{i=1}^N \prod_{j=1}^{q_i} \prod_{k=1}^{r_i} \brock{\theta_{ij}^{(k)}}^{\beta_{ij}^{(k)}}\text{.}
-\end{equation}
-
-Structure search for a Bayesian network seeks the graph structure $G$ that maximizes ${P(G\mid D)}$.
-In practice, one maximizes the log-likelihood, also known as the Bayesian score~\citep{cooper1992bayesian}:
-
-\begin{small}
-\begin{equation}
-\label{eq:BayesianScore}
-  \ln P(D\mid G) = \ln P(G) + \sum_{i=1}^N \sum_{j=1}^{q_i} \ln \paren{
-    \frac{
-      \Gamma\paren{\alpha_{ij}^{(0)}}
-    }{
-      \Gamma\paren{\alpha_{ij}^{(0)} + \beta_{ij}^{(0)}}
-    }
-  } + \sum_{k=1}^{r_i} \ln \paren{
-    \frac{
-      \Gamma\paren{\alpha_{ij}^{(k)} + \beta_{ij}^{(k)}}
-    }{
-      \Gamma\paren{\alpha_{ij}^{(k)}}
-    }
-  }\text{.}
-\end{equation}
-\end{small}
-
-In the equation above,
-
-\begin{equation}
-\alpha_{ij}^{(0)} = \sum_{k=1}^{r_i} \alpha_{ij}^{(k)} \quad \qquad \beta_{ij}^{(0)} = \sum_{k=1}^{r_i} \beta_{ij}^{(k)}\text{.}
-\end{equation}
-
-The space of acyclic graphs is superexponential in the number of nodes, and it is common to rely on heuristic search strategies \citep{PGM_2009}.
-The K2 algorithm assumes a topological ordering of variables and greedily adds parents to nodes to maximally increase the Bayesian score.
-A fixed ordering ensures acyclicity but does not guarantee a globally optimal network structure.
-K2 is typically run multiple times with random variable orderings, and the network with the highest likelihood is retained.
-
-\subsection{Discretization Policies}
-\label{subsec:disc_policy}
-
-Let $\cX$ be a continuous variable and let $\cx$ be a specific instance of $\cX$.
-A discretization policy $\Lambda_{\cX} = \anglebrackets{e_1 < e_2 < \ldots < e_{k-1}}$ for $\cX$ is a mapping from $\mathbb{R}$ to $\curly{1,2,3,\ldots,k}$ such that
-
-\begin{equation}
-  \Lambda_{\cX}(\cx) = \begin{cases}
-    1, & \text{if $x<e_1$}\\
-    i, & \text{if $e_{i-1} \leq x < e_i$}\\
-    k, & \text{otherwise.}
-  \end{cases}
-\end{equation}
-
-\noindent
-The discretization policy discretizes $\cX$ into $k$ intervals.
-Let the samples of $\cX$ in a given dataset $D$ be sorted in ascending order, ${\cx_{1:n} = \curly{\cx_1 \leq \cx_2 \leq \ldots \leq \cx_n}}$, and let the unique values be ${\cu_{1:m} = \curly{\cu_1 \leq \cu_2 \leq \ldots \leq \cu_{m}}}$.
-The index of the last occurence of $\cu_i$ in $\cx_{1:n}$ is denoted $s_i$.
-
-The discretization edges $e_{1:k-1}$ mark the boundaries between discretization intervals.
-In this paper, as with MODL, they are restricted to the midpoints between unique ascending instances of $\cX$.
-Thus, each edge $e_i = \paren{\cu_{j} + \cu_{{j+1}}}/2$ for some $j$.
-Two useful integer representations of $\Lambda_{\cX}$ can be written
-
-\begin{equation}
-\label{eq:disc_def}
-  \Lambda_{\cX} = \anglebrackets{\lambda_1 < \lambda_2  < \ldots < \lambda_k} \equiv \anglebrackets{\gamma_1 , \gamma_2  , \ldots , \gamma_k}\text{,}
-\end{equation}
-
-\noindent
-where $\lambda_1 = s_1$, $\lambda_i \in s_{1:m}$, $\gamma_1 = \lambda_1$, and $\gamma_i = \lambda_i - \lambda_{i-1}$.
-The $\lambda_{1:k}$ representation is the number of instances before every discretization edge whereas the $\gamma_{1:k}$ representation is the number of instances within each discretization interval.
-
-When discussing the discretization of a particular continuous variable $\cX$, let $P_i$ be the $i$th parent of $\cX$, let $C_i$ be the $i$th child of $\cX$, and let $\bm{S}_i$ be the set of spouses of $\cX$ corresponding to the $i$th child.
-The context should make it clear when $P$ refers to a discrete probability and when it refers to a variable's parent.
+The children of node $X_i$ are denoted $\Ch_{X_i}$.
 
@@
 
-Let $D_{\bm{Y}}$ be the subset of the data corresponding to $\bm{Y}$.
-Four principles for the optimal discretization policy enable the formulation of $P(\Lambda)$ and $P(D_{-\cX} \mid \Lambda)$, where $D_{-\cX}$ is the subset of the dataset for all variables but $\cX$ and the probability of the data associated with the target variable $P(D_{\cX})$ is already captured in $P(\Lambda)$.
+Let $D_{\bm{Y}}$ be the subset of the training data corresponding to variable subset $\bm{Y}$.
+Four principles for the optimal discretization policy enable the formulation of $P(\Lambda)$ and $P(D_{-\cX} \mid \Lambda)$, where $D_{-\cX}$ is the subset of the dataset for all variables but $\cX$ and the probability of the data associated with the target variable, $P(D_{\cX})$, is already captured in $P(\Lambda)$.
 The four principles, motivated by MODL and \cite{Lustgarten_2011}, are:
@@
 
-\item For a given discretization interval, every distribution over $\Pa_{\cX}$ is equiprobable.
+\item For a given discretization interval, every distribution over the parents of $\cX$ is equiprobable.
 \item For each pair $\anglebrackets{C_i,\bm{S}_i}$ and a given discretization interval, every distribution over $C_i$ given an instance of $\bm{S}_i$ is equiprobable.
-\item The distributions over each child and each parent in each discretization interval with each instance of $\bm{S}_i$ are independent from each other.
+\item The distributions over $\cX$ given each child, parent, and spouse instantiation are independent.
 \end{enumerate}
 
-From the first principle one obtains the $P(\Lambda)$ of $\Lambda$ described in Equation~\ref{eq:disc_def}
+From the first principle one obtains the prior over the discretization policy:
 
@@
 
-The Bayesian network graph structure causes the likelihood term $P(D_{-\cX} \mid \Lambda)$ to factorizes according to $\cX$'s Markov blanket:
+The Bayesian network graph structure causes the likelihood term ${P(D_{-\cX} \mid \Lambda)}$ to factor according to $\cX$'s Markov blanket:
 
@@
 
-The two factors on the right hand side come from the second principle: all distributions of values of $\Pa_{\cX}$ in a given interval are equiprobable.
-According to the fourth principle, the distribution in each interval is independent, so the two factors can be multiplied together.
+The two factors on the right hand side come from the second principle: all distributions of values of the parents of $\cX$ in a given interval are equiprobable.
+The fourth principle is that the distributions for each interval are independent, so the factors can be multiplied together.
 
 \subsubsection{Evaluation of $P(D_{C_j} \mid \Lambda, D_{\bm{S}_j})$}
-Let $J_{C_j}$ be the number of instantiations of the $j$th child of $\cX$, let $J_S^{(j)}$ be the number instantiations of the $j$th spouse set $\bm{S}_j$, and let $n^{(j)}_{i,m,l}$ be the number of instances of $\cX$ in the $i$th discretization interval of $\Lambda$ given the $m$th instantiation of $C_j$ and the $l$th instantiation of $\boldsymbol{S_j}$.
-Let ${n^{(j)}_{i,l} = \sum_{m=1}^{J_j} n^{(j)}_{i,m,l}}$.
-Note that ${\gamma_i = \sum_l n^{(j)}_{i,l}}$ for all $j$.
+Let $J_{C_j}$ be the number of instantiations of the $j$th child of $\cX$, let $J_{\bm{S}}^{(j)}$ be the number of instantiations of the $j$th spouse set $\bm{S}_j$, and let $n^{(j)}_{i,m,\ell}$ be the number of instances of $\cX$ in the $i$th discretization interval of $\Lambda$ given the $m$th instantiation of $C_j$ and the $\ell$th instantiation of $\bm{S}_j$.
+Let ${n^{(j)}_{i,\ell} = \sum_{m=1}^{J_j} n^{(j)}_{i,m,\ell}}$.
+\tim{Is this correct: Note that ${\gamma_i = \sum_l n^{(j)}_{i,\ell}}$ for all $j$.}
 It follows that
@@
   P(D_{C_j} \mid \Lambda, D_{\bm{S}_j}) =
-  \overbrace{\prod_{i=1}^{k} \prod_{l=1}^{J_S^{(j)}}}^{\text{Principle 4}}
+  \overbrace{\prod_{i=1}^{k} \prod_{\ell=1}^{J_{\bm{S}}^{(j)}}}^{\text{Principle 4}}
     \overbrace{\rule{0pt}{2.3em}
@@
         \frac{1}{
-          {{n^{(j)}_{i,l} + J_{C_j} - 1}\choose{J_{C_j}-1}}}
+          {{n^{(j)}_{i,\ell} + J_{C_j} - 1}\choose{J_{C_j}-1}}}
         }
@@
           \frac{
-            {n^{(j)}_{i,l}}!
+            {n^{(j)}_{i,\ell}}!
           }{
-            {n^{(j)}_{i,1,l}!} \; {n^{(j)}_{i,2,l}!} \; \cdots \; {n^{(j)}_{i,J_{C_j},l}!}
+            {n^{(j)}_{i,1,\ell}!} \; {n^{(j)}_{i,2,\ell}!} \; \cdots \; {n^{(j)}_{i,J_{C_j},\ell}!}
           }
@@
   \label{eq:likelihood_three}
-  P(D_{C_j} \mid \Lambda) =
+  P(D_{C_j} \mid \Lambda, \bm{S}_j = \emptyset) =
   \overbrace{\prod_{i=1}^{k}}^{\text{Principle 4}}
@@
 The objective function can be formulated given equations~\ref{eq:p_M},~\ref{eq:p_D_given_M},~\ref{eq:likelihood_one}, and~\ref{eq:likelihood_three}.
+\tim{Why not Eq~\ref{eq:likelihood_two}?}
 The log-inverse of $P(\Lambda) \cdot P(D_{-\cX} \mid \Lambda)$ is minimized for computational convenience:
@@
   } \\
-  & \sum_{j=1}^{n_c} \sum_{i=1}^k \sum_{l=1}^{J^{(j)}_S} \brock{
+  & \sum_{j=1}^{n_c} \sum_{i=1}^k \sum_{\ell=1}^{J^{(j)}_{\bm{S}}} \brock{
   { \ln
-          {{n^{(j)}_{i,l} + J_{C_j} - 1}\choose{J_{C_j}-1}}}
+          {{n^{(j)}_{i,\ell} + J_{C_j} - 1}\choose{J_{C_j}-1}}}
     +
@@
 All parameters and variables in the objective function are explained in previous subsections.
+\tim{Stress that this is an original contribution}
+\tim{Maybe stress the runtime complexity?}
 
@@
 This section describes the procedure used to minimize the objective function.
-Note that because the objective function is cumulative over intervals; if a partition of $X$ into $k$ intervals by $\Lambda = \curly{\gamma_1 , \gamma_2  , \ldots , \gamma_k}$ is an optimal discretization policy, then any subinterval is optimal for the corresponding subproblem.
+Note that because the objective function is cumulative over intervals, if a partition of $\cX$ into $k$ intervals by $\Lambda = \anglebrackets{\gamma_1, \gamma_2, \ldots, \gamma_k}$ is an optimal discretization policy, then any subinterval is optimal for the corresponding subproblem.
 It follows that dynamic programming can be used to solve the optimization problem exactly.
@@
   h(u,v) &=  \ln {{\gamma_{q} + J_P - 1}\choose{J_P-1}} + \ln \left( { {{\gamma_q}!}\over{ {n^{(p)}_{q,1} !} {n^{(p)}_{q,2} !} \cdots {n^{(p)}_{q,J_p} !}} } \right) \\
-  & + \sum_{j=1}^{n_c} \sum_{l=1}^{J^{(j)}_S} \brock{
+  & + \sum_{j=1}^{n_c} \sum_{\ell=1}^{J^{(j)}_{\bm{S}}} \brock{
     { \ln
-            {{n^{(j)}_{i,l} + J_{C_j} - 1}\choose{J_{C_j}-1}}}
+            {{n^{(j)}_{i,\ell} + J_{C_j} - 1}\choose{J_{C_j}-1}}}
       +
@@
             \frac{
-              {n^{(j)}_{i,l}}!
+              {n^{(j)}_{i,\ell}}!
             }{
-              {n^{(j)}_{i,1,l}!} \; {n^{(j)}_{i,2,l}!} \; \cdots \; {n^{(j)}_{i,J_{C_j},l}!}
+              {n^{(j)}_{i,1,\ell}!} \; {n^{(j)}_{i,2,\ell}!} \; \cdots \; {n^{(j)}_{i,J_{C_j},\ell}!}
             }
@@
               \State $\hat{S}, \hat{u} \leftarrow \tilde{S}, u$
-              \State $\text{DiscEdge} \leftarrow ({x_{s_u} + x_{s_u+1}}) / 2$
+              \State $\text{DiscEdge} \leftarrow ({\cx_{s_u} + \cx_{s_u+1}}) / 2$
             \EndIf
@@
           \State $S[v] \leftarrow \hat{S}$
-          \State $\Lambda[v] \leftarrow \Lambda[u] \cup \{ \text{DiscEdge} \}$
+          \State $\Lambda[v] \leftarrow \Lambda[\hat{u}] \cup \{ \text{DiscEdge} \}$
         \EndIf
@@
 %     } \\
-%     & \sum_{j=1}^{n_c} \sum_{i=1}^k \sum_{l=1}^{J^{(j)}_S} \brock{
+%     & \sum_{j=1}^{n_c} \sum_{i=1}^k \sum_{\ell=1}^{J^{(j)}_\bm{S}} \brock{
 %     { \ln
-%             {{n^{(j)}_{i,l} + J_{C_j} - 1}\choose{J_{C_j}-1}}}
+%             {{n^{(j)}_{i,\ell} + J_{C_j} - 1}\choose{J_{C_j}-1}}}
 %       +
@@
 %             \frac{
-%               {n^{(j)}_{i,l}}!
+%               {n^{(j)}_{i,\ell}}!
 %             }{
-%               {n^{(j)}_{i,1,l}!} \; {n^{(j)}_{i,2,l}!} \; \cdots \; {n^{(j)}_{i,J_{C_j},l}!}
+%               {n^{(j)}_{i,1,\ell}!} \; {n^{(j)}_{i,2,\ell}!} \; \cdots \; {n^{(j)}_{i,J_{C_j},\ell}!}
 %             }
@@
 The iterative approach uses a prediscretization policy in order to initialize the process.
-In this paper, prediscretization assigns $k$ equal-width intervals to each continuous variables, where $k$ is largest value of the number of intervals of initially discrete variables in the network.
+In this paper, prediscretization assigns $k$ equal-width intervals to each continuous variable, where $k$ is the largest number of intervals of initially discrete variables in the network.
 
@@
 
-\todo{move relevant notation here}
-
-In many situations, the network structure is not known in advance and must be learned from data.
+It is often necessary to infer the structure of a Bayesian network from data.
+Three common approaches to Bayesian network structure learning are constraint-based, score-based, and Bayesian model averaging \citep[see][chap.~18]{PGM_2009}.
+This work uses the K2 structure learning algorithm \citep{K2}, one of the most successful score-based structure learning methods.
+Score-based structure learning methods over discrete variables commonly evaluate candidate structures according to their likelihood against a dataset $D$.
+In practice, one maximizes the log-likelihood, also known as the Bayesian score~\citep{cooper1992bayesian}:
+
+\begin{small}
+\begin{equation}
+\label{eq:BayesianScore}
+  \ln P(D\mid G) = \ln P(G) + \sum_{i=1}^N \sum_{j=1}^{q_i} \ln \paren{
+    \frac{
+      \mathrm{\Gamma}\paren{\alpha_{ij}^{(0)}}
+    }{
+      \mathrm{\Gamma}\paren{\alpha_{ij}^{(0)} + \beta_{ij}^{(0)}}
+    }
+  } + \sum_{k=1}^{r_i} \ln \paren{
+    \frac{
+      \mathrm{\Gamma}\paren{\alpha_{ij}^{(k)} + \beta_{ij}^{(k)}}
+    }{
+      \mathrm{\Gamma}\paren{\alpha_{ij}^{(k)}}
+    }
+  }\text{,}
+\end{equation}
+\end{small}
+
+\noindent
+where $\mathrm{\Gamma}$ is the gamma function, $\alpha_{ij}^{(k)}$ is a Dirichlet prior count and $\beta_{ij}^{(k)}$ is the observed sample count for the $k$th instantiation of $X_i$ and the $j$th instantiation of $\Pa_{X_i}$.
+In the equation above,
+
+\begin{equation}
+\alpha_{ij}^{(0)} = \sum_{k=1}^{r_i} \alpha_{ij}^{(k)} \quad \qquad \beta_{ij}^{(0)} = \sum_{k=1}^{r_i} \beta_{ij}^{(k)}\text{.}
+\end{equation}
+
+The space of acyclic graphs is superexponential in the number of nodes; it is common to rely on heuristic search strategies \citep{PGM_2009}.
+The K2 algorithm assumes a given topological ordering of variables and greedily adds parents to nodes to maximally increase the Bayesian score.
+A fixed ordering ensures acyclicity but does not guarantee a globally optimal network structure.
+K2 is typically run multiple times with different topological orderings, and the network with the highest likelihood is retained.
+
 Traditional Bayesian structure learning algorithms require discretized data, whereas the proposed discretization algorithm requires a known network structure.
-This section describes how the proposed discretization method can be combined with the K2 structure learning algorithm \citep{K2} to simultaneously perform Bayesian structure learning and discretization of continuous variables.
+The discretization methods can be combined with the K2 structure learning algorithm \citep{K2} to simultaneously perform Bayesian structure learning and discretization of continuous variables.
 
@@
     \frac{
-      \Gamma\paren{\alpha_{ij}^{(0)}}
+      \mathrm{\Gamma}\paren{\alpha_{ij}^{(0)}}
     }{
-      \Gamma\paren{\alpha_{ij}^{(0)} + \beta_{ij}^{(0)}}
+      \mathrm{\Gamma}\paren{\alpha_{ij}^{(0)} + \beta_{ij}^{(0)}}
     }
@@
     \frac{
-      \Gamma\paren{\alpha_{ij}^{(k)} + \beta_{ij}^{(k)}}
+      \mathrm{\Gamma}\paren{\alpha_{ij}^{(k)} + \beta_{ij}^{(k)}}
     }{
-      \Gamma\paren{\alpha_{ij}^{(k)}}
+      \mathrm{\Gamma}\paren{\alpha_{ij}^{(k)}}
     }
@@
     \State $D^* \leftarrow $ the dataset $D$ discretized according to $\discset$
-    \State $G \leftarrow$ the initial edgeless graph structure
+    \State $G \leftarrow$ the initially edgeless graph structure
 	\For {$\paren{\cX, X}$ such that $\cX \in \bm{\cX}$ and $X$ is the discretized version of $\cX$}
@@
     \For {$i \leftarrow 1$ to $N$}
-      \State $P_{old} \leftarrow g(X_i,\Pa_{X_i})$ as Equation~\ref{eq:B_Score_one}
+      \State $P_\text{old} \leftarrow g(X_i,\Pa_{X_i})$ per Equation~\ref{eq:B_Score_one}
       \State OKToProceed $\leftarrow$ \textbf{true}
       \While {OKToProceed \textbf{and} $\|\Pa_{X_i}\| < \hat{n}_\text{parent}$}
-        \State $Y \leftarrow$ an element from the set $\texttt{order}[1:i] \backslash \Pa_X$
-        \State $P_{new} \leftarrow g(X_i,\Pa_{X_i} \cup Y)$
-        \If {$P_{new} > P_{old}$}
-          \State $P_{old} \leftarrow P_{new}$
-          \State $\Pa_{X_i} \leftarrow \Pa_{X_i} \cup Y $
-          \State $\bm{\cX '} \leftarrow$ sorted $\bm{\cX}$ by a reverse topological order of current $G$
-          \State $\Lambda \leftarrow$ \textsc{DiscretizeAll}({$D$, $G$, $\bm{\cX '}$, $\maxpasses$}): Algorithm~\ref{alg:disc_two}
+        \State $Y \leftarrow$ an element from the set $\texttt{order}[1:i] \backslash \paren{\Pa_X}$
+        \State $P_\text{new} \leftarrow \paren{g(X_i,\Pa_{X_i}} \cup \paren{Y})$
+        \If {$P_\text{new} > P_\text{old}$}
+          \State $P_\text{old} \leftarrow P_\text{new}$
+          \State $\Pa_{X_i} \leftarrow \paren{\Pa_{X_i}} \cup \paren{Y} $
+          \State $\bm{\cX '} \leftarrow$ $\bm{\cX}$ sorted in reverse-topological order given $G$
+          \State $\Lambda \leftarrow$ \textsc{DiscretizeAll}({$D$, $G$, $\bm{\cX '}$, $\maxpasses$}): see Algorithm~\ref{alg:disc_two}
           \State $D^* \leftarrow \Lambda \paren{D_{\bm{\cX }}}$
@@
 The first experiment compares the performance of the Bayesian and MDL discretization methods on a known Bayesian network structure.
-The structure was obtained by prediscretizing each continuous variable into $k$ uniform-width intervals, where $k$ is the median number of instantiations of the discrete variables, and using the structure with the highest Bayesian score from \num{1000} runs of the K2 algorithm with random variable orderings.
+The structure was obtained by prediscretizing each continuous variable into $k$ uniform-width intervals, where $k$ is the median number of instantiations of the discrete variables, and using the structure with the highest Bayesian score from \num{1000} runs of the K2 algorithm with random topological orderings.
 The second experiment compares the same methods applied when simultaneously discretizing and learning network structure.
@@
 \noindent
-The mean cross-validated log-likelihood is the mean log-likelihood on the witheld dataset among cross-validation folds.
-Cross-validation directly estimates generalization error.
+The mean cross-validated log-likelihood is the mean log-likelihood on the witheld dataset among cross-validation folds, and acts as an estimate of generalization error.
 Ten folds were used in each experiment.
@@
 where $I(A,B)$ is the mutual information between two discrete variable sets $A$ and $B$, ${H(p) = -p \ln(p) - (1-p) \ln(1-p)}$, and $X$ is the discretized version of $\cX$.
-The minimum of Equation \ref{eqn:MDL} can be found by dynamical programming.
-It takes runtime $\bigo \paren{ n^3 + \paren{ n_c \cdot {L}^{n_s}  + {L}^{n_p}} \cdot n^2 }$, where the parameters are defined in Section \ref{subsec:algo}.
+Equation \ref{eqn:MDL} can be minimized using dynamical programming with runtime $\bigo \paren{ n^3 + \paren{ n_c \cdot {L}^{n_s}  + {L}^{n_p}} \cdot n^2 }$.
+All variables are defined in Section \ref{subsec:algo}.
 Therefore, the runtime of the proposed method in this paper is shorter than MDL discretization method by $\bigo \paren{n^3}$.
+\tim{It seems weird having this result being explained in the experiments section.}
 
@@
 
-Table~\ref{table:auto_disc_table_1} lists the discretization edges and mean log-likelihoods under \num{10}-fold cross validation of the discrete Bayesian network resulting from two discretization methods.
+Table~\ref{table:auto_disc_table_1} lists the discretization edges and mean log-likelihoods under \num{10}-fold cross validation of the discrete Bayesian network resulting from the two discretization methods.
 The MDL method does not produce any discretization edges, assigning one continuous interval to each continuous variable, and produces the result with the lower likelihood.
-The cause of low number of discretization edges behind the MDL method is discussed in Section~\ref{subsec:discuss_exp}.
-On the other hand, there is a network structure where the MDL has a comparable result with the Bayesian method.
-Please refer to Appendix.
+The reason why MDL produces fewer discretization edges is discussed in Section~\ref{subsec:discuss_exp}.
+An example of a network structure where MDL produces a comparable result to the Bayesian method is given in the Appendix.
 
@@
 
-To quantatively discuss the sensitivity of each methods to the number of discretization intervals, consider the Bayesian network in Figure~\ref{fig:exp_discuss}, where $\cX$ is continuous and $P_1$ and $P_2$ are discrete.
+To quantatively discuss the sensitivity of each method to the number of discretization intervals, consider the Bayesian network in Figure~\ref{fig:exp_discuss}, where $\cX$ is continuous and $P_1$ and $P_2$ are discrete.
 If $\Pa_{\cX} = \curly{P_1, P_2}$ and $D_{\cX} = \curly{1.0,2.0,3.0, \ldots n}$, then the corresponding objective functions for the discretization methods are:
@@
 The sensitivities of each method to the discretization edges are captured in the edge position terms, as the penalty terms are similar across methods.
-The value of the edge position term for MDL is primarly determined by the mutual information, which varies less severely than the corresponding terms for the Bayesian methods.
-The MDL term uses emperical probability distributions, based off of ratios of counts, whereas the Bayesian methods use factorial terms, and thus vary less severely.
+The value of the edge position term for MDL is primarly determined by the mutual information, which varies less severely than the corresponding terms for the Bayesian method.
+The MDL term uses emperical probability distributions, based off of ratios of counts, whereas the Bayesian method uses factorial terms, and thus vary less severely.
 The MDL method is therefore less sensitive to the discretization edges.
@@
 The proposed method was incorporated and its superior performance was empirically demonstrated.
-\todo{All software is publically available to support discretization research.}
+All software is publically available to support discretization research, \todo{and can be found at.}
 

### 2015-11-25 BN_discretizer_paper.tex
Do Tim's comments and Find a typo

@@
 Let ${n^{(j)}_{i,\ell} = \sum_{m=1}^{J_j} n^{(j)}_{i,m,\ell}}$.
-\tim{Is this correct: Note that ${\gamma_i = \sum_l n^{(j)}_{i,\ell}}$ for all $j$.}
+Note that ${\gamma_i = \sum_{\ell} n^{(j)}_{i,\ell}}$ for all $j$.
 It follows that
@@
 
-The objective function can be formulated given equations~\ref{eq:p_M},~\ref{eq:p_D_given_M},~\ref{eq:likelihood_one}, and~\ref{eq:likelihood_three}.
-\tim{Why not Eq~\ref{eq:likelihood_two}?}
+The objective function can be formulated given equations~\ref{eq:p_M},~\ref{eq:p_D_given_M},~\ref{eq:likelihood_one},~\ref{eq:likelihood_two} and~\ref{eq:likelihood_three}.
 The log-inverse of $P(\Lambda) \cdot P(D_{-\cX} \mid \Lambda)$ is minimized for computational convenience:
@@
       }}
-  } \\
+  } + \\
   & \sum_{j=1}^{n_c} \sum_{i=1}^k \sum_{\ell=1}^{J^{(j)}_{\bm{S}}} \brock{

### 2015-11-25 BN_discretizer_paper.tex
Find typo

@@
 The discretization policy discretizes $\cX$ into $k$ intervals.
-Let the samples of $\cX$ in a given dataset $D$ be sorted in ascending order, ${\cx_{1:n} = \curly{\cx_1 \leq \cx_2 \leq \ldots \leq \cx_n}}$, and let the unique values be ${\cu_{1:m} = \curly{\cu_1 \leq \cu_2 \leq \ldots \leq \cu_{m}}}$.
+Let the samples of $\cX$ in a given dataset $D$ be sorted in ascending order, ${\cx_{1:n} = \curly{\cx_1 \leq \cx_2 \leq \ldots \leq \cx_n}}$, and let the unique values be ${\cu_{1:m} = \curly{\cu_1 < \cu_2 < \ldots < \cu_{m}}}$.
 The index of the last occurence of $\cu_i$ in $\cx_{1:n}$ is denoted $s_i$.
@@
 \label{eq:BayesianScore}
-  \ln P(D\mid G) = \ln P(G) + \sum_{i=1}^N \sum_{j=1}^{q_i} \ln \paren{
+  \ln P(G\mid D) = \ln P(G) + \sum_{i=1}^N \sum_{j=1}^{q_i} \ln \paren{
     \frac{

### 2015-11-25 BN_discretizer_paper.tex
fixed the things we discussed

@@
 The edges in a Bayesian network represent probabilistic dependencies among nodes and encode the Markov property: each node $X_i$ is independent of its non-descendants given its parents $\Pa_{X_i}$ in $G$.
-For a Bayesian network over discrete and discretized variables, $r_i$ represents the number of instantiations of $X_i$, and $q_i$ represents the number of instantiations of the parents of $X_i$.
-If $X_i$ has no parents, then $q_i = 1$.
-The $j$th instantiation of the parents of $X_i$ is denoted $\bm{\pi}_{ij}$.
 The children of node $X_i$ are denoted $\Ch_{X_i}$.
@@
 
-All parameters and variables in the objective function are explained in previous subsections.
-\tim{Stress that this is an original contribution}
-\tim{Maybe stress the runtime complexity?}
+All parameters and variables in the objective function have been previously explained.
 
@@
 The runtime of Algorithm~\ref{alg:disc_one} is also $\bigo \paren{ n_c \cdot {L}^{n_s} \cdot n^2 + {L}^{n_p} \cdot n^2 }$, because the runtime of the dynamic programming procedure is less than the runtime for computing $h(u,v)$.
+As will be discussed in Section~\ref{sec:experiments}, the MDL discretization method has a runtime of $\bigo\paren{ n^3 + \paren{ n_c \cdot {L}^{n_s} + {L}^{n_p}} \cdot n^2 }$, which includes an extra $\bigo\paren{ n^3}$ term.
+The Bayesian discretization method is quadratic in the sample count $n$, whereas the MDL discretization method is cubic.
+
 Algorithm~\ref{alg:disc_one} is guaranteed to be optimal.
@@
 
-% The approximation reduces the runtime of Algorithm~\ref{alg:disc_one} to a polynomial, $\todo{\bigo\paren{ {v'_\text{max}} \cdot (n_c + n_p) \cdot n^2}}$.
+% The approximation reduces the runtime of Algorithm~\ref{alg:disc_one} to a polynomial, $\bigo\paren{ {v'_\text{max}} \cdot (n_c + n_p) \cdot n^2}$.
 % It will be shown in Section~\ref{sec:experiments} that the approximation is more sensitive to the distribution over other variables and is biased towards slightly higher interval counts.
-% \tim{We need to have a more specific thing to say along the lines of `When does it fail?'}
 
@@
 In cases where it does not converge, usually observed when also learning structure, ten passes produce sufficient discretization results.
-\tim{If it only fails to converge with structure learning, perhaps we should take out the max upper bound in Alg~\ref{alg:disc_two}.}
 
@@
 Score-based structure learning methods over discrete variables commonly evaluate candidate structures according to their likelihood against a dataset $D$.
-In practice, one maximizes the log-likelihood, also known as the Bayesian score~\citep{cooper1992bayesian}:
+In practice, one maximizes the log-likelihood, also known as the Bayesian score, $\ln P(G\mid D)$~\citep{cooper1992bayesian}.
+
+For a Bayesian network over $N$ discrete and discretized variables $X_{1:N}$, $r_i$ represents the number of instantiations of $X_i$, and $q_i$ represents the number of instantiations of the parents of $X_i$.
+If $X_i$ has no parents, then $q_i = 1$.
+The Bayesian score is:
 
@@
 This procedure is given in Algorithm~\ref{alg:structure_learn}, and takes five inputs: $D$, a dataset of samples from the joint distribution; $\bm{\cX}$, the set of all continuous variables; $\texttt{order}$, a permutation of the variables in $D$; $\hat{n}_\text{parent}$, an upper bound on the number of parents per node; and $\maxpasses$, an upper bound on the number of complete passes.
-The upper bound on the number of parents is common practice, and is done to prevent computing conditional distribtions with excessively large parameter sets. \tim{cite?}
+The upper bound on the number of parents is common practice, and is used to prevent computing conditional distribtions with excessively large parameter sets.
 The function $g$ in Algorithm~\ref{alg:structure_learn} computes a component of the Bayesian score (Equation~\ref{eq:BayesianScore}):
@@
 where $D$ is the original dataset and $D^*$ is the dataset discretized according to $\discset$.
-The log-likelihood of the discretized dataset is the Bayesian score (Equation~\ref{eq:BayesianScore}) evaluated with a uniform prior over graph structures and a uniform Dirichlet prior ($\alpha_{ijk} = 1$ for all $i$, $j$, and $k$).
+
+The log-likelihood of the discretized dataset given the Bayesian network is
+
+\begin{equation}
+P(D^* \mid \bm{\alpha}, \bm{\beta}, G) = \prod_{i=1}^N \prod_{j=1}^{q_i} \prod_{k=1}^{r_i}
+\paren{
+  \frac{
+    \alpha_{ij}^{(k)} + \beta_{ij}^{(k)}
+  }{
+    \alpha_{ij}^{(0)} + \beta_{ij}^{(0)}
+    }
+}^{\beta_{ij}^{*(k)}}\text{,}
+\end{equation}
+
+\noindent
+where $\bm{\alpha}$ and $\bm{\beta}$ were previously defined for the Bayesian score (Equation~\ref{eq:BayesianScore}), and $\bm{\beta}^*$ is the set of observed counts in $D^*$.
+The experiments below used a uniform Dirichlet prior of $\alpha_{ijk} = 1$ for all $i$, $j$, and $k$.
+
 The log-likelihood of the original dataset given the discrete dataset is
@@
   \ln p\paren{D\mid \discset, D^*} = \sum_{i=1}^N
-  1_{\curly{ \cX_i \in \bm{\cX }}}\cdot \sum_{k=1}^{r_i}  \sum_{j=1}^{q_i} \beta_{ij}^{(k)} \ln \paren{
+  1_{\curly{ \cX_i \in \bm{\cX }}}\cdot \sum_{k=1}^{r_i}  \sum_{j=1}^{q_i} \beta_{ij}^{*(k)} \ln \paren{
     \frac{
@@
 Therefore, the runtime of the proposed method in this paper is shorter than MDL discretization method by $\bigo \paren{n^3}$.
-\tim{It seems weird having this result being explained in the experiments section.}
 
@@
 % The overall performance of the heuristic method is still very high, and if runtime is the primary concern, the heuristic method can be considered the better approach.
-% \tim{Do we need to list runtime too?}
 
@@
 % The numbers of intervals returned by the each method illustrate the over-sensitive nature of the heuristic method and the under-sensitive nature of the MDL method.
-% \tim{I am not sure we are using `sensitive' correctly. Sensitive to what? Perhaps `biased towards higher edge counts'?}
 The relative weighting of each method's objective function will be discussed in Section~\ref{subsec:discuss_exp}.
@@
     The last row is the mean cross-validated log-likelihood based on each discretization result.
-    % The heuristic method is over-sensitive \todo{to what?} and discretizes some variables into too many intervals.
+    % The heuristic method is over-sensitive and discretizes some variables into too many intervals.
     % The MDL method is less sensitive and on many cases does not produce any discretization intervals.

### 2015-11-25 graph_housing_exp2_distr_3_5.tex
colorbar fix

@@
 			colorbar,
-			point meta min=0, point meta max=1.2,
+			point meta min=0, point meta max=1,
 			colormap={}{ gray(0cm)=(1); gray(1cm)=(0);},
 			colorbar style={
-			        ytick={0,0.24,...,1.3},
+			        ytick={0,0.2,...,1.01},
 			        ylabel={probability density$ \times 10^{-1}$},
 			        y label style={at={(axis description cs:6.5,0.5)},rotate=180,anchor=north},
+			        yticklabels={\num{0.00},\num{0.20},\num{0.40},\num{0.60},\num{0.80},$\geq 1$},
 			        yticklabel style={
@@
 			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.6275,0.000000) (3.9850,0.6275,0.000000) (3.9850,0.6390,0.0000) (3.8750,0.6390,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.6390,1.704545) (3.9850,0.6390,1.704545) (3.9850,0.6510,1.7045) (3.8750,0.6510,1.7045)};
+			% \addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.6390,1.704545) (3.9850,0.6390,1.704545) (3.9850,0.6510,1.7045) (3.8750,0.6510,1.7045)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.6390,1.000000) (3.9850,0.6390,1.000000) (3.9850,0.6510,1.0000) (3.8750,0.6510,1.0000)};
 			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.6510,0.000000) (3.9850,0.6510,0.000000) (3.9850,0.8205,0.0000) (3.8750,0.8205,0.0000)};
@@
 			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.3050,0.3850,0.000000) (7.2250,0.3850,0.000000) (7.2250,0.4460,0.0000) (6.3050,0.4460,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.3050,0.4460,1.239130) (7.2250,0.4460,1.239130) (7.2250,0.4485,1.2391) (6.3050,0.4485,1.2391)};
+			% \addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.3050,0.4460,1.239130) (7.2250,0.4460,1.239130) (7.2250,0.4485,1.2391) (6.3050,0.4485,1.2391)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.3050,0.4460,1.000000) (7.2250,0.4460,1.000000) (7.2250,0.4485,1.0000) (6.3050,0.4485,1.0000)};
 			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(6.3050,0.4485,0.000000) (7.2250,0.4485,0.000000) (7.2250,0.4555,0.0000) (6.3050,0.4555,0.0000)};

### 2015-11-25 BN_discretizer_paper.tex
colorbar fix
moved it
misc

@@
 
+\subsection{Bayesian Networks}
+
+A Bayesian network $B$ over $N$ random variables $X_{1:N}$ is defined by a directed acyclic graph $G$ whose nodes are the random variables and a conditional probability distribution for each node given its parents.
+The edges in a Bayesian network represent probabilistic dependencies among nodes and encode the Markov property: each node $X_i$ is independent of its non-descendants given its parents $\Pa_{X_i}$ in $G$.
+The children of node $X_i$ are denoted $\Ch_{X_i}$.
+
 When discussing the discretization of a particular continuous variable $\cX$, let $P_i$ be the $i$th parent of $\cX$, let $C_i$ be the $i$th child of $\cX$, and let $\bm{S}_i$ be the set of spouses of $\cX$ corresponding to the $i$th child.
 The context should make it clear when $P$ refers to a discrete probability and when it refers to a variable's parent.
-
-\subsection{Bayesian Networks}
-
-A Bayesian network $B$ is defined by a pair $(G,\bm{\theta})$, where $G$ is a directed acyclic graph whose $N$ nodes $X_{1:N}$ are random variables.
-The edges in a Bayesian network represent probabilistic dependencies among nodes and encode the Markov property: each node $X_i$ is independent of its non-descendants given its parents $\Pa_{X_i}$ in $G$.
-The children of node $X_i$ are denoted $\Ch_{X_i}$.
 
@@
     The high number of discretization edges are caused by repeated values in $C$ and $E$.
+    Note that the two regions at $(C,E) = (3.9,0.65)$ and $(6.8,0.44)$ are color-saturated due to the high concentration of repeated values.
   }

### 2015-11-25 BN_discretizer_paper.tex
changed to B

@@
 
-The discretizations are compared using the mean cross validated log-likelihood of the data $D$ given the graph structure $G$ and discretization policies $\discset$.
+The discretizations are compared using the mean cross validated log-likelihood of the data $D$ given the Bayesian network $B$ and discretization policies $\discset$.
 Note that all log-likelihoods shown have been normalized by the number of data samples.
@@
 \begin{equation}
-\ln p(D\mid G, \discset) = \ln P(D^*\mid G) + \ln p(D\mid \discset, D^*)\text{,}
+\ln p(D\mid B, \discset) = \ln P(D^*\mid B) + \ln p(D\mid \discset, D^*)\text{,}
 \end{equation}
@@
 \noindent
-where $D$ is the original dataset and $D^*$ is the dataset discretized according to $\discset$.
+where $D$ is the original test dataset and $D^*$ is the test dataset discretized according to $\discset$.
 
@@
 \begin{equation}
-P(D^* \mid \bm{\alpha}, \bm{\beta}, G) = \prod_{i=1}^N \prod_{j=1}^{q_i} \prod_{k=1}^{r_i}
+P(D^* \mid B) = \prod_{i=1}^N \prod_{j=1}^{q_i} \prod_{k=1}^{r_i}
 \paren{
@@
 \noindent
-where $\bm{\alpha}$ and $\bm{\beta}$ were previously defined for the Bayesian score (Equation~\ref{eq:BayesianScore}), and $\bm{\beta}^*$ is the set of observed counts in $D^*$.
+where $\bm{\alpha}$ and $\bm{\beta}$ are the Dirichlet prior counts and observed counts in the training set for $B$, and $\bm{\beta}^*$ is the set of observed counts in the test set $D^*$.
 The experiments below used a uniform Dirichlet prior of $\alpha_{ijk} = 1$ for all $i$, $j$, and $k$.

### 2015-11-25 information_sheet.tex
Info sheet

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[round]{natbib}
\usepackage{graphicx}

\title{Information Sheet}
\author{Yi-Chun Chen, Tim A. Wheeler, Mykel J. Kochenderfer}

\begin{document}

\maketitle

This paper introduces a principled discretization method to continuous variables in Bayesian network. It learns the discretization policy for each continuous variable from mixed data and also takes the network structure into account in the learning process. Compared with a predominant existing method \citep{Friedman_1996}, which has cubic time complexity, the proposed method learns the discretization with quadratic complexity.

The tests on the real-world data \citep{Lichman_2013} demonstrates that the proposed method is superior to the work of \cite{Friedman_1996}. The latter usually discretizes continuous variables with low numbers of intervals, and it is unable to match the distribution of original dataset. The former, on the other hand, finds more necessary discretization edges for recovering the distribution of orginal data. The recovering is illustrated by cross-validated likelihood and comparisons of original data with the learned marginalized probability density.

This paper also shows how to incorporate the proposed discretization method to the structure learning process \cite{k2}, and therefore learn a discrete-valued Bayesian network.

The proposed method is related to \cite{Boulle_2006} and \cite{Lustgarten_2011}. These two works is to discretize continuous attribute accroding to one class variable by Bayesian statistics method. The proposed method can be considered an extension of these two works to general Bayesian network case.

\bibliographystyle{spbasic}
\bibliography{my_bib}
\end{document}

### 2015-11-25 information_sheet.tex
progress

@@
 \usepackage{graphicx}
+\usepackage{color}
 
-\title{Information Sheet}
-\author{Yi-Chun Chen, Tim A. Wheeler, Mykel J. Kochenderfer}
+\newcommand{\todo}[1]{\textcolor{magenta}{#1}}
+\newcommand{\yichun}[1]{\textit{\textcolor{green}{#1}}}
+\newcommand{\tim}[1]{\textit{\textcolor{blue}{#1}}}
+\newcommand{\mykel}[1]{\textit{\textcolor{cyan}{#1}}}
+
+\title{Information Sheet \\ {\large Learning Discrete-valued Bayesian Networks from Mixed Data}}
+\author{\normalsize Yi-Chun Chen, Tim A. Wheeler, Mykel J. Kochenderfer}
+\date{}
 
@@
 
-This paper introduces a principled discretization method to continuous variables in Bayesian network.
-It learns the discretization policy for each continuous variable from mixed data and also takes the network structure into account in the learning process.
-Compared with a predominant existing method \citep{Friedman_1996}, which has cubic time complexity, the proposed method learns the discretization with quadratic complexity.
+\noindent
+\textbf{What is the main claim of the paper?}
 
+This paper introduces a principled Bayesian discretization method for continuous variables in Bayesian networks with quadratic complexity instead of the cubic complexity of the standard minimum-discription length (MDL) technique.
+In addition, this paper shows how to incorporate existing methods into the structure learning process to discretize all continuous variables and simultaneously learn Bayesian network structures.\\[0em]
+
+\noindent
+\textbf{Why is this an important contribution to the machine learning literature?}
+
+Bayesian networks are an increasingly popular method for modeling uncertainty and causality.
+In most cases, one assumes that the random variables in a Bayesian network are discrete, since many Bayesian network learning and inference algorithms are unable to efficiently handle continuous variables.
+However, many applications require the use of continuous variables, in which case one must adopt Bayesian networks with continuous parametric distributions or discretize all continuous variables.
+
+The proposed method learns discretization policies for continuous variables from mixed data while taking the Bayesian network structure into account.
+Prior Bayesian methods, such as MODL (\citep{Boulle_2006, Lustgarten_2011}), only considered the discretization of a single continuous variable with respect to another single discrete variable.
+The predominant existing method for discretizing continuous variables in Bayesian networks is based on MDL~\citep{Friedman_1996}, and has cubic time complexity in the number of data samples.
+The proposed method learns the discretization with quadratic complexity in the number of data samples, allowing it to scale to larger datasets more effectively.
+Furthermore, emperical demonstrations show that the proposed method produces superior discretization schemes in terms, evalated using the cross-validated log-likelihood.\\[0em]
+
+\noindent
+\textbf{What is the evidence you provide to support your claim?}
+
+\todo{
 The tests on the real-world data \citep{Lichman_2013} demonstrates that the proposed method is superior to the work of \cite{Friedman_1996}.
@@
 The former, on the other hand, finds more necessary discretization edges for recovering the distribution of orginal data.
-The recovering is illustrated by cross-validated likelihood and comparisons of original data with the learned marginalized probability density.
+The recovering is illustrated by cross-validated likelihood and comparisons of original data with the learned marginalized probability density.\\[0em]
+}
 
-This paper also shows how to incorporate the proposed discretization method to the structure learning process \cite{k2}, and therefore learn a discrete-valued Bayesian network.
+\noindent
+\textbf{What papers by other authors make the most closely related contributions, and how is your paper related to them?}
 
+\todo{
 The proposed method is related to \cite{Boulle_2006} and \cite{Lustgarten_2011}.
 These two works is to discretize continuous attribute accroding to one class variable by Bayesian statistics method.
-The proposed method can be considered an extension of these two works to general Bayesian network case.
+The proposed method can be considered an extension of these two works to general Bayesian network case.\\[0em]
+}
+
+\noindent
+\textbf{Have you published parts of your paper before?}
+
+No parts of this paper have been previously published.
 

### 2015-11-25 BN_discretizer_paper.tex
info sheet runthrough

@@
 \usepackage{pgfplotstable}
-\usepgfplotslibrary{groupplots}
 \usepackage{tikz}
@@
 
-% \usepackage[capitalize]{cleveref}
 \usetikzlibrary{bayesnet}
@@
 Continuous and hybrid variables are often discretized, but the choice of discretization policy has significant impact on the accuracy, speed, and interpretability of the resulting models.
-This paper introduces a principled discretization method for continuous variables in Bayesian networks with quadratic complexity instead of the cubic complexity of other standard techniques.
+This paper introduces a principled Bayesian discretization method for continuous variables in Bayesian networks with quadratic complexity instead of the cubic complexity of other standard techniques.
 Emperical demonstrations show that the proposed method is superior to the state of the art.
@@
 All variables are defined in Section \ref{subsec:algo}.
-Therefore, the runtime of the proposed method in this paper is shorter than MDL discretization method by $\bigo \paren{n^3}$.
+Therefore, the runtime of the proposed method in this paper is shorter than the MDL discretization method by $\bigo \paren{n^3}$.
 

### 2015-11-25 information_sheet.tex
info sheet runthrough

@@
 This paper introduces a principled Bayesian discretization method for continuous variables in Bayesian networks with quadratic complexity instead of the cubic complexity of the standard minimum-discription length (MDL) technique.
-In addition, this paper shows how to incorporate existing methods into the structure learning process to discretize all continuous variables and simultaneously learn Bayesian network structures.\\[0em]
+In addition, this paper shows how to incorporate existing methods into the structure learning process to discretize all continuous variables while simultaneously learning Bayesian network structures.\\[0em]
 
@@
 In most cases, one assumes that the random variables in a Bayesian network are discrete, since many Bayesian network learning and inference algorithms are unable to efficiently handle continuous variables.
-However, many applications require the use of continuous variables, in which case one must adopt Bayesian networks with continuous parametric distributions or discretize all continuous variables.
+However, many applications require the use of continuous variables, in which case one must use Bayesian networks with continuous parametric distributions or discretize all continuous variables.
 
 The proposed method learns discretization policies for continuous variables from mixed data while taking the Bayesian network structure into account.
-Prior Bayesian methods, such as MODL (\citep{Boulle_2006, Lustgarten_2011}), only considered the discretization of a single continuous variable with respect to another single discrete variable.
-The predominant existing method for discretizing continuous variables in Bayesian networks is based on MDL~\citep{Friedman_1996}, and has cubic time complexity in the number of data samples.
-The proposed method learns the discretization with quadratic complexity in the number of data samples, allowing it to scale to larger datasets more effectively.
-Furthermore, emperical demonstrations show that the proposed method produces superior discretization schemes in terms, evalated using the cross-validated log-likelihood.\\[0em]
+Prior Bayesian methods, such as MODL \citep{Boulle_2006, Lustgarten_2011}, only consider the discretization of a single continuous variable with respect to another single discrete variable.
+The predominant existing method for discretizing continuous variables in Bayesian networks is based on MDL~\citep{Friedman_1996}, and has cubic runtime in the number of data samples.
+The proposed method learns the discretization with quadratic runtime in the number of data samples, allowing it to more efficiently scale to larger datasets.
+Furthermore, emperical demonstrations show that the proposed method produces superior discretization schemes, evalated using the cross-validated log-likelihood.\\[0em]
 
@@
 
-\todo{
-The tests on the real-world data \citep{Lichman_2013} demonstrates that the proposed method is superior to the work of \cite{Friedman_1996}.
-The latter usually discretizes continuous variables with low numbers of intervals, and it is unable to match the distribution of original dataset.
-The former, on the other hand, finds more necessary discretization edges for recovering the distribution of orginal data.
-The recovering is illustrated by cross-validated likelihood and comparisons of original data with the learned marginalized probability density.\\[0em]
-}
+The Bayesian discretization algorithm is derived from base priors and the pseudocode is given.
+Experiments were conducted on three datasets from the University of California, Irvine machine learning repository~\citep{Lichman_2013}.
+Each dataset possesses different qualities which affect the behavior of the discretization algorithms.
+
+Two experiments were conducted for each dataset: one experiment in which the continuous variables are discretized with a known Bayesian network structure, and a second experiment in which the network structure is simultaneously learned along with the discretization policy.
+The resulting discretization policies are given and discussed for each dataset.
+
+Results demonstrate that the proposed method is superior to the MDL work of \cite{Friedman_1996}.
+The latter tends to produce discretization policies with low numbers of intervals, and the models produced by the proposed Bayesian method have significantly higher validation log-likelihood.\\[0em]
 
@@
 
-\todo{
 The proposed method is related to \cite{Boulle_2006} and \cite{Lustgarten_2011}.
-These two works is to discretize continuous attribute accroding to one class variable by Bayesian statistics method.
-The proposed method can be considered an extension of these two works to general Bayesian network case.\\[0em]
-}
+These two works discuss the discretization of a continuous variable given a single class variable using a principled Bayesian method.
+This paper is an extension of these two works to discretization in a general Bayesian network, where the discretization of a particular variable requires considering that variable's Markov blanket.\\[0em]
 

### 2015-11-25 BN_discretizer_paper.tex
Reference check and change label of plot

@@
 Three common approaches to Bayesian network structure learning are constraint-based, score-based, and Bayesian model averaging \citep[see][chap.~18]{PGM_2009}.
-This work uses the K2 structure learning algorithm \citep{K2}, one of the most successful score-based structure learning methods.
+This work uses the K2 structure learning algorithm \citep{cooper1992bayesian}, one of the most successful score-based structure learning methods.
 Score-based structure learning methods over discrete variables commonly evaluate candidate structures according to their likelihood against a dataset $D$.
@@
 Traditional Bayesian structure learning algorithms require discretized data, whereas the proposed discretization algorithm requires a known network structure.
-The discretization methods can be combined with the K2 structure learning algorithm \citep{K2} to simultaneously perform Bayesian structure learning and discretization of continuous variables.
+The discretization methods can be combined with the K2 structure learning algorithm \citep{cooper1992bayesian} to simultaneously perform Bayesian structure learning and discretization of continuous variables.
 
@@
 
+Note that the preliminary discretization and the discretization order of variables can be arbitrary for the MDL discretization method, as stated in the original work \citep{Friedman_1996}.
+In order to make a fair comparison between the Bayesian and MDL method, the preliminary discretization and the discretization order follows the same procedure as in Section \ref{sec:multi_var}.
+
 \subsection{Auto MPG Dataset}

### 2015-11-25 graph_housing_exp1_distr_3_5.tex
Reference check and change label of plot

@@
 			colorbar,
-			point meta min=0, point meta max=1.2,
+			point meta min=0, point meta max=1.0,
 			colormap={}{ gray(0cm)=(1); gray(1cm)=(0);},
 			colorbar style={
-			        ytick={0,0.3,...,1.3},
+			        ytick={0,0.2,...,1.01},
 			        ylabel={probability density$ \times 10^{-1}$},
+			        y label style={at={(axis description cs:6.5,0.5)},rotate=180,anchor=north},
+			        yticklabels={\num{0.00},\num{0.20},\num{0.40},\num{0.60},\num{0.80},$\geq 1$},
 			        y label style={at={(axis description cs:6.5,0.5)},rotate=180,anchor=north},

### 2015-11-26 BN_discretizer_paper.tex
Add group plots
updated and sending to mykel

@@
 \usepackage{tikz}
+\usepgfplotslibrary{groupplots}
 \usepackage{lscape}
@@
 \usepackage{boondox-cal} % for lowercase caligraphic
+\usepackage[font=small,skip=5pt]{caption}
 
@@
 
-\keywords{Discretization \and Bayesian Network \and Continuous Variable \and }
+\keywords{Discretization \and Bayesian Network \and Continuous Variable}
   % \PACS{PACS code1 \and PACS code2 \and more}
@@
 There are three common approaches to extending Bayesian networks to continuous variables.
-The first is to model the conditional probability density of each continuous variable using specific families of parametric distributions, and then to redesign Bayesian network learning and inference algorithms based on the parameterization.
+The first is to model the conditional probability density of each continuous variable using specific families of parametric distributions, and then to redesign Bayesian network learning and inference algorithms based on the parameterizations.
 One successful example of parametric, continuous distributions in Bayesian networks is the Gaussian graphical model \citep{Weiss_2011}.
@@
 These methods search for the best discretization policy for a continuous attribute by considering its interation with a class variable.
-Today it is common practice to discretize all continuous variables before learning a Bayesian network structure to avoid having to consider variable interactions, as interations and dependencies between variables in Bayesian networks are more complicated.
+Today it is common practice to discretize all continuous variables before learning a Bayesian network structure to avoid having to consider variable interactions, as the interations and dependencies between variables in Bayesian networks introduce complexity.
 The discretization of a variable in a network requires considering the impact on the variable's Markov blanket.
@@
 The optimal discretization policy of a single continuous variable under MDL is found using dynamic programming in runtime $\bigo\paren{n^3 + q \cdot n^2}$, where $n$ is the number of data samples and $q$ is a constant with exponential dependency on the cardinalities of the variables in the Bayesian network.
-For Bayesian networks with multiple continuous variables, MDL discretization is iteratively applied to each continuous variable.
-While iterating, only one variable is treated as continuous, while all other continuous variables are treated as discretized based on an initial discretization policy or the discretization result from a previous iteration.
+For Bayesian networks with multiple continuous variables, MDL discretization can be iteratively applied to each continuous variable.
+Only one variable is treated as continuous at a time, while all other continuous variables are treated as discretized based on an initial discretization policy or the discretization result from a previous iteration.
 
@@
 In this paper, as with MODL, they are restricted to the midpoints between unique ascending instances of $\cX$.
-Thus, each edge $e_i = \paren{\cu_{j} + \cu_{{j+1}}}/2$ for some $j$.
+Thus, each edge $e_i$ equals $\paren{\cu_{j} + \cu_{{j+1}}}/2$ for some $j$.
 Two useful integer representations of $\Lambda_{\cX}$ can be written
@@
   \begin{equation}
-  1 - {\exp(- L \cdot {\frac{\cu_{i+1} - \cu_i}{\cu_m - \cu_1}})}\text{,}
+  1 - \exp \paren{- L \cdot \frac{\cu_{i+1} - \cu_i}{\cu_m - \cu_1}}\text{,}
   \end{equation}
@@
 The parents are not necessarily individually independent, and thus the parental term $P(D_{\Pa_{\cX}} \mid \Lambda)$ cannot be factored further.
-The children of $\cX$ are similarly independent given $\cX$ and the corresponding spouses, leading to their factored product $\prod_{C_i} P(D_{C_i} \mid \Lambda, D_{\bm{S}_i})$.
+The children of $\cX$ are similarly independent given $\cX$ and the corresponding spouses, leading to their factored product $\prod_{i} P(D_{C_i} \mid \Lambda, D_{\bm{S}_i})$.
 Each component in the decomposition can be evaluated given a discretization policy and a dataset.
@@
 
-Let $J_P$ be the number of instantiations of the parents of $\cX$, and let $n^{(P)}_{i,j}$ be the number of instances of $\cX$ within the $i$th discretization interval of $\Lambda$ given the $j$th parental instantiation.
-Note that $\gamma_i = \sum_j n^{(P)}_{i,j}$.
+Let $J_\text{P}$ be the number of instantiations of the parents of $\cX$, and let $n^{(\text{P})}_{i,j}$ be the number of instances of $\cX$ within the $i$th discretization interval of $\Lambda$ given the $j$th parental instantiation.
+Note that $\gamma_i = \sum_j n^{(\text{P})}_{i,j}$.
 It follows that
@@
     \overbrace{\rule{0pt}{2em}
-      \frac{1}{{{\gamma_i + J_P - 1}\choose{J_P - 1}}}
+      \frac{1}{{{\gamma_i + J_\text{P} - 1}\choose{J_\text{P} - 1}}}
       \frac{1}{
@@
         }{
-          {n^{({P})}_{i,1}}! \; {n^{({P})}_{i,2}}! \; \cdots \; {n^{({P})}_{i,J_P}}!
+          {n^{(\text{P})}_{i,1}}! \; {n^{(\text{P})}_{i,2}}! \; \cdots \; {n^{(\text{P})}_{i,J_\text{P}}}!
         }
@@
   \overbrace{\prod_{i=1}^{k}}^{\text{Principle 4}}
-  \overbrace{{
+  \overbrace{\rule{0pt}{2.3em}{
     {1}\over{
@@
   & \sum_{i=1}^{k} \brock{
-  \ln{{\gamma_i + J_P - 1}\choose{J_P - 1}}
+  \ln{{\gamma_i + J_\text{P} - 1}\choose{J_\text{P} - 1}}
   +{ \ln \paren{
@@
         }{
-          {n^{({P})}_{i,1}}! \; {n^{({P})}_{i,2}}! \; \cdots \; {n^{({P})}_{i,J_P}}!
+          {n^{({P})}_{i,1}}! \; {n^{({P})}_{i,2}}! \; \cdots \; {n^{({P})}_{i,J_\text{P}}}!
         }
@@
   \begin{aligned}
-  h(u,v) &=  \ln {{\gamma_{q} + J_P - 1}\choose{J_P-1}} + \ln \left( { {{\gamma_q}!}\over{ {n^{(p)}_{q,1} !} {n^{(p)}_{q,2} !} \cdots {n^{(p)}_{q,J_p} !}} } \right) \\
+  h(u,v) &=  \ln {{\gamma_{q} + J_\text{P} - 1}\choose{J_\text{P}-1}} + \ln \left( { {{\gamma_q}!}\over{ {n^{(p)}_{q,1} !} {n^{(p)}_{q,2} !} \cdots {n^{(p)}_{q,J_p} !}} } \right) \\
   & + \sum_{j=1}^{n_c} \sum_{\ell=1}^{J^{(j)}_{\bm{S}}} \brock{
@@
 
-The calculation of $h(u,v)$ for all $u \leq v$ has a $\bigo \paren{ n_c \cdot {L}^{n_s} \cdot n^2 + {L}^{n_p} \cdot n^2 }$ runtime, where $n_c$ and $n_p$ are the numbers of child and parent variables respectively, $L$ is the largest cardinality of variables in $X$'s Markov blanket, and $n_s = \text{max}_j  |\Pa_{C_j}|$.
+The calculation of $h(u,v)$ for all $u \leq v$ has a $\bigo \paren{ n_c \cdot {L}^{n_s} \cdot n^2 + {L}^{n_p} \cdot n^2 }$ runtime, where $n_c$ and $n_p$ are the number of child and parent variables respectively, $L$ is the largest cardinality of variables in $X$'s Markov blanket, and $n_s = \text{max}_j  |\Pa_{C_j}|$.
 
@@
 % \begin{equation}
-% {\frac{{\gamma_i}!}{ {n^{(P)}_{i,1} !} {n^{(P)}_{i,2} !} \cdots {n^{(P)}_{i,J_P} !}}} \approx \prod_{r=1}^{n_p} { {{{\gamma}_i}!}\over{ {n^{(P_r)}_{i,1} !} {n^{(P_r)}_{i,2} !} \cdots {n^{(P_r)}_{i,J_{P_r}} !}}}\text{,}
+% {\frac{{\gamma_i}!}{ {n^{\text{P}}_{i,1} !} {n^{\text{P}}_{i,2} !} \cdots {n^{\text{P}}_{i,J_\text{P}} !}}} \approx \prod_{r=1}^{n_p} { {{{\gamma}_i}!}\over{ {n^{(P_r)}_{i,1} !} {n^{(P_r)}_{i,2} !} \cdots {n^{(P_r)}_{i,J_{P_r}} !}}}\text{,}
 % \end{equation}
@@
 %     & \sum_{i=1}^{k} \brock{
-%     \ln{{\gamma_i + J_P - 1}\choose{J_P - 1}}
+%     \ln{{\gamma_i + J_\text{P} - 1}\choose{J_\text{P} - 1}}
 %     +{ \ln \paren{
@@
 %   &  \left.
-\left[  \ln {{\gamma_{i} + J_P - 1}\choose{J_P-1}} +  \ln \left( { {{{\gamma}_i}!}\over{ {n^{(P_1)}_{i,1} !}\cdots {n^{(P_1)}_{i,J_{P_1}} !}}} \right) +\ln \paren{{ {{{\gamma}_i}!}\over{ {n^{(P_2}_{i,1} !}\cdots {n^{(P_2)}_{i,J_{P_2}} !}}} } \right] \right\rbrace \text{.}
+\left[  \ln {{\gamma_{i} + J_\text{P} - 1}\choose{J_\text{P}-1}} +  \ln \left( { {{{\gamma}_i}!}\over{ {n^{(P_1)}_{i,1} !}\cdots {n^{(P_1)}_{i,J_{P_1}} !}}} \right) +\ln \paren{{ {{{\gamma}_i}!}\over{ {n^{(P_2}_{i,1} !}\cdots {n^{(P_2)}_{i,J_{P_2}} !}}} } \right] \right\rbrace \text{.}
 %   \end{aligned}
@@
 The algorithm typically converges within a few passes when tested on real-world data.
-In cases where it does not converge, usually observed when also learning structure, ten passes produce sufficient discretization results.
+% In cases where it does not converge, usually observed when also learning structure, ten passes produce sufficient discretization results.
 
@@
 where $\bm{\alpha}$ and $\bm{\beta}$ are the Dirichlet prior counts and observed counts in the training set for $B$, and $\bm{\beta}^*$ is the set of observed counts in the test set $D^*$.
-The experiments below used a uniform Dirichlet prior of $\alpha_{ijk} = 1$ for all $i$, $j$, and $k$.
+All experiments used a uniform Dirichlet prior of $\alpha_{ijk} = 1$ for all $i$, $j$, and $k$.
 
@@
 where $I(A,B)$ is the mutual information between two discrete variable sets $A$ and $B$, ${H(p) = -p \ln(p) - (1-p) \ln(1-p)}$, and $X$ is the discretized version of $\cX$.
-Equation \ref{eqn:MDL} can be minimized using dynamical programming with runtime $\bigo \paren{ n^3 + \paren{ n_c \cdot {L}^{n_s}  + {L}^{n_p}} \cdot n^2 }$.
+Equation \ref{eqn:MDL} can be minimized using dynamic programming with runtime $\bigo \paren{ n^3 + \paren{ n_c \cdot {L}^{n_s}  + {L}^{n_p}} \cdot n^2 }$.
 All variables are defined in Section \ref{subsec:algo}.
@@
 
-\begin{table}[h]
+\begin{table}[ht]
   \centering
@@
 
-%\subsubsection{Discretization while Learning Structure}
+\subsubsection{Discretization while Learning Structure}
 \label{subsubsec:auto_exp2}
@@
 Although there are fewer discretization edges for $A$ and $C$ in the learned network, the marginal distribution is still captured.
-The discretization policy will vary according as the network structure changes, and it still produces high-quality discretizations.
+The discretization policy will vary as the network structure changes, and it still produces high-quality discretizations.
 
@@
 Figure~\ref{fig:wine_exp2_distr} shows the discretization policy for variables $E$ and $K$ obtained with the Bayesian method.
-The discretization edge also $E = 17.9$ appears in both discretization policies from the fixed network (Figure~\ref{fig:wine_exp1_distr}).
+The discretization edge $E = 17.9$ also appears in both discretization policies from the fixed network (Figure~\ref{fig:wine_exp1_distr}).
 This suggests that discretization edges can be robust against network structure.
-Furthermore, the discretization edge at $E = 23.5$ present in the fixed-structure case is missing in the learned structure.
+Furthermore, the discretization edge at $E = 23.5$ in the fixed-structure case is missing in the learned structure.
 This is caused by $E$ having twice as many parents in the learned network structure.
-The more parents a variable has, the less discretization intervals it can to support, as the set of statistics required to define the resulting distribution increases exponentially with the number of parents.
+The more parents a variable has, the fewer discretization intervals it can to support, as the number of sufficient statistics required to define the resulting distribution increases exponentially with the number of parents.
 
@@
 The Bayesian network structure in Figure~\ref{fig:housing_graph_1} was obtained by prediscretizing each continuous variable into five uniform-width intervals and then running the K2 algorithm \num{1000} times and choosing the network with the highest likelihood.
-Table~\ref{table:housing_disc_table_1} shows the numbers of intervals after discretization for each continuous variables and the log-likelihood of the dataset based on each discretization method.
+Table~\ref{table:housing_disc_table_1} shows the numbers of interval after discretization for each continuous variable and the log-likelihood of the dataset based on each discretization method.
 MDL method does not produce any discretization edges for most variables.
@@
 
-\begin{figure}[ht]
-  \centering
-  \input{graph_housing_exp1_distr_8_5}
-  \caption{
-    The discretization policies for variables $H$ and $E$ learned using the optimal Bayesian approach on the fixed network shown in Figure~\ref{fig:housing_graph_1}.
-    The variable $H$ possesses no overly repeated values, thus producing a cleaner discretization policy.
-  }
-  \label{fig:housing_exp1_distr_8_5}
-\end{figure}
-
 \subsubsection{Discretization while Learning Structure}
@@
 
-\begin{figure}[ht]
+Figures~\ref{fig:housing_exp2_distr_3_5} and \ref{fig:housing_exp2_distr_8_5} show the discretization result for variables in the network shown in Figure~\ref{fig:housing_graph_2}.
+Again, variable $C$ and $E$ have many discretization edges due to repeated values.
+Although the number of intervals after discretization on $H$ is less the number in Figure~\ref{fig:housing_exp1_distr_8_5}, it still captures the distribution of the raw data along with the discretization edges for $E$.
+
+\begin{figure}[H]
+  \centering
+  \input{graph_housing_exp1_distr_8_5}
+  \caption{
+    The discretization policies for variables $H$ and $E$ learned using the optimal Bayesian approach on the fixed network shown in Figure~\ref{fig:housing_graph_1}.
+    The variable $H$ possesses no overly repeated values, thus producing a cleaner discretization policy.
+  }
+  \label{fig:housing_exp1_distr_8_5}
+\end{figure}
+
+\begin{figure}[H]
   \centering
@@
 
-Figure~\ref{fig:housing_exp2_distr_3_5} and Figure~\ref{fig:housing_exp2_distr_8_5} show the discretization result on variables of the network in Figure~\ref{fig:housing_graph_2}.
-Again, variable $C$ and $E$ have many discretization edges due to the repeated values.
-Although the number of intervals after discretization on $H$ is less the number in Figure~\ref{fig:housing_exp1_distr_8_5}, it still captures the distribution of the raw data along with the discretization edges on $E$.
-
-\begin{figure}[ht]
+\begin{figure}[H]
   \centering
@@
 
-\begin{figure}[ht]
+\begin{figure}[H]
   \centering
@@
 
-To quantatively discuss the sensitivity of each method to the number of discretization intervals, consider the Bayesian network in Figure~\ref{fig:exp_discuss}, where $\cX$ is continuous and $P_1$ and $P_2$ are discrete.
+To quantatively discuss the sensitivity of each method to the number and position of discretization intervals, consider the Bayesian network in Figure~\ref{fig:exp_discuss}, where $\cX$ is continuous and $P_1$ and $P_2$ are discrete.
 If $\Pa_{\cX} = \curly{P_1, P_2}$ and $D_{\cX} = \curly{1.0,2.0,3.0, \ldots n}$, then the corresponding objective functions for the discretization methods are:
@@
   f_{\text{MDL}} & = \overbrace{Z_1 \cdot k + \ln(k) + \ln {{n +k - 1}\choose{k -1}} }^{\text{Penalty Term}}+   \overbrace{\rule{0pt}{1.35em} \ln(N) \cdot I(X^*, \Pa_X)}^{\text{Edge Position Term}} \\
-  f_{\text{Bayesian}} &= \underbrace{{\vrule width0pt height0pt depth1.48em\relax}  Z_2 \cdot k + \sum_{i=1}^k \ln {{\gamma_i + J_P - 1}\choose{J_P -1}}}_{\text{Penalty Term}} + \underbrace{\sum^k_{i=1} \ln \left(   {{\gamma_i !}\over{n^{(P)}_{i,1}!
-n^{(P)}_{i,2}!
-\cdots n^{(P)}_{i,J_P}!
+  f_{\text{Bayesian}} &= \underbrace{{\vrule width0pt height0pt depth1.48em\relax}  Z_2 \cdot k + \sum_{i=1}^k \ln {{\gamma_i + J_\text{P} - 1}\choose{J_\text{P} -1}}}_{\text{Penalty Term}} + \underbrace{\sum^k_{i=1} \ln \left(   {{\gamma_i !}\over{n^{\text{P}}_{i,1}!
+n^{\text{P}}_{i,2}!
+\cdots n^{\text{P}}_{i,J_\text{P}}!
 }} \right) }_{\text{Edge Position Term}}
@@
 
-The sensitivities of each method to the discretization edges are captured in the edge position terms, as the penalty terms are similar across methods.
-The value of the edge position term for MDL is primarly determined by the mutual information, which varies less severely than the corresponding terms for the Bayesian method.
-The MDL term uses emperical probability distributions, based off of ratios of counts, whereas the Bayesian method uses factorial terms, and thus vary less severely.
+The sensitivity of each method to the discretization edges are captured in the edge position terms, as the penalty terms are similar across methods.
+The value of the edge position term for MDL is primarily determined by the mutual information, which varies less severely than the corresponding terms in the Bayesian method.
+The MDL term uses emperical probability distributions, based off of ratios of counts, whereas the Bayesian method uses factorial terms, and thus varies less.
 The MDL method is therefore less sensitive to the discretization edges.
@@
 The methods developed in this paper increase the accuracy of Bayesian networks learned on datasets with continuous and mixed variables.
-An automated process for simultaneously constructing Bayesian networks and discretization policies is appearing because of the potential to significantly reduce development time and cost.
+An automated process for simultaneously constructing Bayesian networks and discretization policies is appealing because of the potential to significantly reduce development time and cost when developing models for uncertainty and causality.
 Future work will investigate edge positions at locations other than the midpoints between samples and using different discretization policies for the same variable in different conditional probablity distributions.
@@
 The Bayesian network in Figure~\ref{fig:auto_graph_3} was obtained by running Algorithm~\ref{alg:structure_learn} fifty times on the Auto MPG dataset with a maximum of two parents per variable.
-The network is more well-structured than the one in Figure~\ref{fig:auto_graph_1}, because the discretization policies were simultaneously learned with the network structure.
-Many edges appears in both discretization results, and are bolded in Table~\ref{table:auto_disc_table_3}.
+The network is more well-structured than the one in Figure~\ref{fig:auto_graph_1} because the discretization policies were simultaneously learned with the network structure.
+Many edges appear in both discretization results, and are bolded in Table~\ref{table:auto_disc_table_3}.
 
@@
   \scalebox{0.8}{\input{graph_autocar_3}}
-  \caption{A Bayesian network structure for the Auto MPG dataset that leads to comparable discretization policies from the MDL and Bayesian methods.}
+  \caption{A Bayesian network structure for the Auto MPG dataset that leads to comparable discretization policies for the MDL and Bayesian methods.}
   \label{fig:auto_graph_3}
@@
     The last row shows the mean cross-validated log-likelihood under each policy.
-    The methods have same discretization result on variable $A$, and the log-likelihood for the MDL method only just slightly worse than that of the Bayesian method.
+    The methods have the same discretization for variable $A$, and the log-likelihood for the Bayesian method is only slightly better than that for the MDL method.
   }

### 2015-11-26 information_sheet.tex
updated and sending to mykel

@@
 \noindent
-\textbf{Why is this an important contribution to the machine learning literature?}
+\textbf{How is this a contribution to the machine learning literature?}
 
@@
 The proposed method learns the discretization with quadratic runtime in the number of data samples, allowing it to more efficiently scale to larger datasets.
-Furthermore, emperical demonstrations show that the proposed method produces superior discretization schemes, evalated using the cross-validated log-likelihood.\\[0em]
+Furthermore, emperical demonstrations show that the proposed method produces superior discretization policies, which was objectively evalated using the cross-validated log-likelihood.\\[0em]
 

### 2015-11-27 BN_discretizer_paper.tex
Modify based on Mykel's feedback

@@
 
-Real data often contains a mixture of discrete, continuous, and hybrid variables, but many Bayesian network structure learning and inference algorithms assume all random variables are discrete.
+Real data often contains a mixture of discrete and continuous variables, but many Bayesian network structure learning and inference algorithms assume all random variables are discrete.
 Continuous and hybrid variables are often discretized, but the choice of discretization policy has significant impact on the accuracy, speed, and interpretability of the resulting models.
 This paper introduces a principled Bayesian discretization method for continuous variables in Bayesian networks with quadratic complexity instead of the cubic complexity of other standard techniques.
-Emperical demonstrations show that the proposed method is superior to the state of the art.
+Empirical demonstrations show that the proposed method is superior to the state of the art.
 In addition, this paper shows how to incorporate existing methods into the structure learning process to discretize all continuous variables and simultaneously learn Bayesian network structures.
-The proposed method was incorporated and its superior performance was empirically demonstrated.
-All software is publically available to support discretization research.
+The proposed method was incorporated and its performance was empirically demonstrated.
 
@@
 
-Bayesian networks \citep{Pearl_1988, PGM_2009}, which first emerged from artificial intelligence research, are an increasingly popular method for modeling uncertainty and causality, with applications ranging from decision-making systems \citep{kochenderfer2012next} to medical diagnosis \citep{Lustgarten_2011}.
+Bayesian networks \citep{Pearl_1988, PGM_2009} are often used to model uncertainty and causality, with applications ranging from decision-making systems \citep{kochenderfer2012next} to medical diagnosis \citep{Lustgarten_2011}.
 Bayesian networks provide an efficient factorization of the joint probability distribution over a set of random variables.
-In most cases, one assumes that the random variables in a Bayesian network are discrete, since many Bayesian network learning and inference algorithms are unable to efficiently handle continuous variables.
+It is common to assume that the random variables in a Bayesian network are discrete, since many Bayesian network learning and inference algorithms are unable to efficiently handle continuous variables.
 In addition, many of the commonly used Bayesian network software packages, such as Netica \citep{netica1992}, SMILearn \citep{druzdzel1999smile}, and bnlearn \citep{bnlearn2010}, are geared towards discrete variables.
@@
 One successful example of parametric, continuous distributions in Bayesian networks is the Gaussian graphical model \citep{Weiss_2011}.
-For other parametric distributions and non-linear functions \citep{Ihler_2009}, however, these redesigned algorithms are computationally expensive, and the Gaussian assumption on the underlying data does not always hold.
+For other parametric distributions and non-linear functions \citep{Ihler_2009}, however, these redesigned algorithms can be computationally expensive.
 
@@
 Parametric models have a fixed number of parameters, whereas the number of parameters in a nonparametric model grow with the amount of training data.
-Inference algorithms on nonparametric models are often inefficient due to the large number of parameters they must refer to.
+Inference algorithms on nonparametric models can be also inefficient.
 
@@
 These methods search for the best discretization policy for a continuous attribute by considering its interation with a class variable.
-Today it is common practice to discretize all continuous variables before learning a Bayesian network structure to avoid having to consider variable interactions, as the interations and dependencies between variables in Bayesian networks introduce complexity.
+It is common to discretize all continuous variables before learning a Bayesian network structure to avoid having to consider variable interactions, as the interations and dependencies between variables in Bayesian networks introduce complexity.
 The discretization of a variable in a network requires considering the impact on the variable's Markov blanket.
@@
 
-The predominant discretization method for continuous variables in Bayesian networks is the minimum description length (MDL) principle discretization method \citep{Friedman_1996}.
-The MDL principle was first proposed by \cite{MDL_1978}, and states that the best model for a dataset is the one that minimizes the amount of information needed to describe it \citep{Grunwald_2009}.
+A common discretization method for continuous variables in Bayesian networks is the minimum description length (MDL) principle discretization method \citep{Friedman_1996}.
+The MDL principle \cite{MDL_1978} states that the best model for a dataset is the one that minimizes the amount of information needed to describe it \citep{Grunwald_2009}.
 MDL methods trade off goodness-of-fit against model complexity to reduce generalization error.
@@
 
-Results in this work suggest that the MDL method suffers from low sensitivity to discretization edge locations and returns low numbers of discretization intervals for continuous variables.
-This is caused by MDL's use of mutual information to rate discretization edges.
-Mutual information, which is composed of empirical probabilities computed using event count ratios, varies less severely with the positions of discretization edges than the method proposed below.
+Results in this work suggest that the MDL method suffers from low sensitivity to discretization edge locations and returns too few discretization intervals for continuous variables.
+This is caused by MDL's use of mutual information to measure the quality of discretization edges.
+Mutual information, which is composed of empirical probabilities computed using event count ratios, varies less severely with the positions of discretization edges than the method we suggest in this article.
 
@@
 
-When discussing the discretization of a particular continuous variable $\cX$, let $P_i$ be the $i$th parent of $\cX$, let $C_i$ be the $i$th child of $\cX$, and let $\bm{S}_i$ be the set of spouses of $\cX$ corresponding to the $i$th child.
-The context should make it clear when $P$ refers to a discrete probability and when it refers to a variable's parent.
+When discussing the discretization of a particular continuous variable $\cX$, let $P_i$ be the $i$th parent of $\cX$, let $C_i$ be the $i$th child of $\cX$, and let $\bm{S}_i$ be the set of spouses of $\cX$ associated with the $i$th child.
+%The context should make it clear when $P$ refers to a discrete probability and when it refers to a variable's parent.
 
@@
 
-All parameters and variables in the objective function have been previously explained.
+%All parameters and variables in the objective function have been previously explained.
 
@@
 
-This section describes the procedure used to minimize the objective function.
+The procedure used to minimize the objective function involves \todo{dynamical programming}.
 Note that because the objective function is cumulative over intervals, if a partition of $\cX$ into $k$ intervals by $\Lambda = \anglebrackets{\gamma_1, \gamma_2, \ldots, \gamma_k}$ is an optimal discretization policy, then any subinterval is optimal for the corresponding subproblem.
@@
 It takes three inputs: $\cX$, the continuous variable; $D$, the joint data instances over all variables sorted in ascending order according to $D_X$; and $G$, the network structure.
-The runtime of Algorithm~\ref{alg:disc_one} is also $\bigo \paren{ n_c \cdot {L}^{n_s} \cdot n^2 + {L}^{n_p} \cdot n^2 }$, because the runtime of the dynamic programming procedure is less than the runtime for computing $h(u,v)$.
+The runtime of Algorithm~\ref{alg:disc_one} is also $\bigo \paren{ n_c \cdot {L}^{n_s} \cdot n^2 + {L}^{n_p} \cdot n^2 }$ because the runtime of the dynamic programming procedure is less than the runtime for computing $h(u,v)$.
 As will be discussed in Section~\ref{sec:experiments}, the MDL discretization method has a runtime of $\bigo\paren{ n^3 + \paren{ n_c \cdot {L}^{n_s} + {L}^{n_p}} \cdot n^2 }$, which includes an extra $\bigo\paren{ n^3}$ term.
@@
 Three common approaches to Bayesian network structure learning are constraint-based, score-based, and Bayesian model averaging \citep[see][chap.~18]{PGM_2009}.
-This work uses the K2 structure learning algorithm \citep{cooper1992bayesian}, one of the most successful score-based structure learning methods.
+This work uses the K2 structure learning algorithm \citep{cooper1992bayesian}, a frequently used score-based structure learning method.
 Score-based structure learning methods over discrete variables commonly evaluate candidate structures according to their likelihood against a dataset $D$.
@@
 \noindent
-where $\mathrm{\Gamma}$ is the gamma function, $\alpha_{ij}^{(k)}$ is a Dirichlet prior count and $\beta_{ij}^{(k)}$ is the observed sample count for the $k$th instantiation of $X_i$ and the $j$th instantiation of $\Pa_{X_i}$.
+where $\mathrm{\Gamma}$ is the gamma function, $\alpha_{ij}^{(k)}$ is a Dirichlet parameter and $\beta_{ij}^{(k)}$ is the observed sample count for the $k$th instantiation of $X_i$ and the $j$th instantiation of $\Pa_{X_i}$.
 In the equation above,
@@
 
-This procedure is given in Algorithm~\ref{alg:structure_learn}, and takes five inputs: $D$, a dataset of samples from the joint distribution; $\bm{\cX}$, the set of all continuous variables; $\texttt{order}$, a permutation of the variables in $D$; $\hat{n}_\text{parent}$, an upper bound on the number of parents per node; and $\maxpasses$, an upper bound on the number of complete passes.
-The upper bound on the number of parents is common practice, and is used to prevent computing conditional distribtions with excessively large parameter sets.
+This procedure is given in Algorithm~\ref{alg:structure_learn}, and takes five inputs: $D$, a dataset of samples from the joint distribution; $\bm{\cX}$, the set of all continuous variables; \todo{$\texttt{order}$}, a permutation of the variables in $D$; $\hat{n}_\text{parent}$, an upper bound on the number of parents per node; and $\maxpasses$, an upper bound on the number of complete passes.
+The upper bound on the number of parents is common practice, and is used to prevent computing conditional distributions with excessively large parameter sets.
 The function $g$ in Algorithm~\ref{alg:structure_learn} computes a component of the Bayesian score (Equation~\ref{eq:BayesianScore}):
@@
     \For {$i \leftarrow 1$ to $N$}
-      \State $P_\text{old} \leftarrow g(X_i,\Pa_{X_i})$ per Equation~\ref{eq:B_Score_one}
+      \State $P_\text{old} \leftarrow g(X_i,\Pa_{X_i})$ \quad ( Equation~\ref{eq:B_Score_one})
       \State OKToProceed $\leftarrow$ \textbf{true}
@@
           \State $\bm{\cX '} \leftarrow$ $\bm{\cX}$ sorted in reverse-topological order given $G$
-          \State $\Lambda \leftarrow$ \textsc{DiscretizeAll}({$D$, $G$, $\bm{\cX '}$, $\maxpasses$}): see Algorithm~\ref{alg:disc_two}
+          \State $\Lambda \leftarrow$ \textsc{DiscretizeAll}({$D$, $G$, $\bm{\cX '}$, $\maxpasses$}): \quad (Algorithm~\ref{alg:disc_two})
           \State $D^* \leftarrow \Lambda \paren{D_{\bm{\cX }}}$
@@
    \input{graph_autocar_1}
-   \caption{Bayesian network structure obtained from running K2 on the prediscretized Auto MPG dataset}
+   \caption{Bayesian network structure obtained from running K2 on the prediscretized Auto MPG dataset.}
   \label{fig:auto_graph_1}
@@
 
-In this experiment the network structure was not fixed in advance and was learned simultaneously with the discretization policies.
+In this experiment, the network structure was not fixed in advance and was learned simultaneously with the discretization policies.
 Figure~\ref{fig:auto_graph_2} shows a learned Bayesian network structure and the corresponding numbers of intervals after discretization for each continuous variable.
@@
     The discretization policies for variables $H$ and $E$ learned using the optimal Bayesian approach on the fixed network shown in Figure~\ref{fig:housing_graph_1}.
-    The variable $H$ possesses no overly repeated values, thus producing a cleaner discretization policy.
+    The variable $H$ possesses no \todo{overly} repeated values, thus producing a cleaner discretization policy.
   }
@@
 
-To quantatively discuss the sensitivity of each method to the number and position of discretization intervals, consider the Bayesian network in Figure~\ref{fig:exp_discuss}, where $\cX$ is continuous and $P_1$ and $P_2$ are discrete.
+To quantatively assess the sensitivity of each method to the number and position of discretization intervals, consider the Bayesian network in Figure~\ref{fig:exp_discuss}, where $\cX$ is continuous and $P_1$ and $P_2$ are discrete.
 If $\Pa_{\cX} = \curly{P_1, P_2}$ and $D_{\cX} = \curly{1.0,2.0,3.0, \ldots n}$, then the corresponding objective functions for the discretization methods are:
@@
 where $Z_1$ and $Z_2$ are constant over discretizations, $k$ is the number of discretization intervals, and $I\paren{A, B} = \sum_{a,b} \hat{P}(a,b) \ln\frac{\hat{P}(a,b)}{\hat{P}(a)\hat{P}(b)}$ is the mutual information based on estimated probabilities.
-Note that the third term of $f_\text{MDL}$ had been approximated using $H(p)$ (see Equation~\ref{eqn:MDL}) in the original work by \cite{Friedman_1996}, but here is written without that approximation.
+Note that the third term of $f_\text{MDL}$ had been approximated using $H(p)$ (see Equation~\ref{eqn:MDL}) in the original work by \cite{Friedman_1996}, but it is written here without that approximation.
 
@@
 The value of the edge position term for MDL is primarily determined by the mutual information, which varies less severely than the corresponding terms in the Bayesian method.
-The MDL term uses emperical probability distributions, based off of ratios of counts, whereas the Bayesian method uses factorial terms, and thus varies less.
+The MDL term uses empirical probability distributions, based off of ratios of counts, whereas the Bayesian method uses factorial terms, and thus varies less.
 The MDL method is therefore less sensitive to the discretization edges.

### 2015-11-27 graph_auto_exp1_distr_1_3.tex
Modify based on Mykel's feedback

--- 2015-11-17 graph_auto_exp1_distr_1_3.tex
@@
 			colorbar,
-			point meta min=0, point meta max=0.5,
+			point meta min=0, point meta max=1.2,
 			colormap={}{ gray(0cm)=(1); gray(1cm)=(0);},
 			colorbar style={
-			        ytick={0,0.05,...,0.51},
+			        ytick={0,0.24,...,1.3},
+			        ylabel={probability density $\times 10^3$},
+			        y label style={at={(axis description cs:6.5,0.5)},rotate=180,anchor=north},
 			        yticklabel style={
@@
 
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,68.0000,0.0000) (15.2500,68.0000,0.0000) (15.2500,70.5000,0.0000) (9.0000,70.5000,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,70.5000,0.0000) (15.2500,70.5000,0.0000) (15.2500,93.5000,0.0000) (9.0000,93.5000,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,93.5000,0.0000) (15.2500,93.5000,0.0000) (15.2500,109.0000,0.0000) (9.0000,109.0000,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,109.0000,0.0020) (15.2500,109.0000,0.0020) (15.2500,159.5000,0.0020) (9.0000,159.5000,0.0020)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,159.5000,0.0235) (15.2500,159.5000,0.0235) (15.2500,259.0000,0.0235) (9.0000,259.0000,0.0235)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,259.0000,0.0030) (15.2500,259.0000,0.0030) (15.2500,284.5000,0.0030) (9.0000,284.5000,0.0030)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,284.5000,0.1345) (15.2500,284.5000,0.1345) (15.2500,455.0000,0.1345) (9.0000,455.0000,0.1345)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,68.0000,0.000000) (15.2500,68.0000,0.000000) (15.2500,70.5000,0.000000) (9.0000,70.5000,0.000000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,70.5000,0.000000) (15.2500,70.5000,0.000000) (15.2500,93.5000,0.000000) (9.0000,93.5000,0.000000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,93.5000,0.000000) (15.2500,93.5000,0.000000) (15.2500,109.0000,0.000000) (9.0000,109.0000,0.000000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,109.0000,0.004752) (15.2500,109.0000,0.004752) (15.2500,159.5000,0.004752) (9.0000,159.5000,0.004752)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,159.5000,0.031357) (15.2500,159.5000,0.031357) (15.2500,259.0000,0.031357) (9.0000,259.0000,0.031357)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,259.0000,0.031373) (15.2500,259.0000,0.031373) (15.2500,284.5000,0.031373) (9.0000,284.5000,0.031373)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,284.5000,0.142639) (15.2500,284.5000,0.142639) (15.2500,455.0000,0.142639) (9.0000,455.0000,0.142639)};
 
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(15.2500,68.0000,0.0000) (17.6500,68.0000,0.0000) (17.6500,70.5000,0.0000) (15.2500,70.5000,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(15.2500,70.5000,0.0000) (17.6500,70.5000,0.0000) (17.6500,93.5000,0.0000) (15.2500,93.5000,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(15.2500,93.5000,0.0000) (17.6500,93.5000,0.0000) (17.6500,109.0000,0.0000) (15.2500,109.0000,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(15.2500,109.0000,0.0020) (17.6500,109.0000,0.0020) (17.6500,159.5000,0.0020) (15.2500,159.5000,0.0020)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(15.2500,159.5000,0.0230) (17.6500,159.5000,0.0230) (17.6500,259.0000,0.0230) (15.2500,259.0000,0.0230)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(15.2500,259.0000,0.0030) (17.6500,259.0000,0.0030) (17.6500,284.5000,0.0030) (15.2500,284.5000,0.0030)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(15.2500,284.5000,0.0625) (17.6500,284.5000,0.0625) (17.6500,455.0000,0.0625) (15.2500,455.0000,0.0625)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(15.2500,68.0000,0.000000) (17.6500,68.0000,0.000000) (17.6500,70.5000,0.000000) (15.2500,70.5000,0.000000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(15.2500,70.5000,0.000000) (17.6500,70.5000,0.000000) (17.6500,93.5000,0.000000) (15.2500,93.5000,0.000000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(15.2500,93.5000,0.000000) (17.6500,93.5000,0.000000) (17.6500,109.0000,0.000000) (15.2500,109.0000,0.000000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(15.2500,109.0000,0.028878) (17.6500,109.0000,0.028878) (17.6500,159.5000,0.028878) (15.2500,159.5000,0.028878)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(15.2500,159.5000,0.092127) (17.6500,159.5000,0.092127) (17.6500,259.0000,0.092127) (15.2500,259.0000,0.092127)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(15.2500,259.0000,0.016340) (17.6500,259.0000,0.016340) (17.6500,284.5000,0.016340) (15.2500,284.5000,0.016340)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(15.2500,284.5000,0.167400) (17.6500,284.5000,0.167400) (17.6500,455.0000,0.167400) (15.2500,455.0000,0.167400)};
 
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.6500,68.0000,0.0000) (20.9000,68.0000,0.0000) (20.9000,70.5000,0.0000) (17.6500,70.5000,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.6500,70.5000,0.0000) (20.9000,70.5000,0.0000) (20.9000,93.5000,0.0000) (17.6500,93.5000,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.6500,93.5000,0.0070) (20.9000,93.5000,0.0070) (20.9000,109.0000,0.0070) (17.6500,109.0000,0.0070)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.6500,109.0000,0.0430) (20.9000,109.0000,0.0430) (20.9000,159.5000,0.0430) (17.6500,159.5000,0.0430)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.6500,159.5000,0.0880) (20.9000,159.5000,0.0880) (20.9000,259.0000,0.0880) (17.6500,259.0000,0.0880)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.6500,259.0000,0.0095) (20.9000,259.0000,0.0095) (20.9000,284.5000,0.0095) (17.6500,284.5000,0.0095)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.6500,284.5000,0.0225) (20.9000,284.5000,0.0225) (20.9000,455.0000,0.0225) (17.6500,455.0000,0.0225)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.6500,68.0000,0.000000) (20.9000,68.0000,0.000000) (20.9000,70.5000,0.000000) (17.6500,70.5000,0.000000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.6500,70.5000,0.033445) (20.9000,70.5000,0.033445) (20.9000,93.5000,0.033445) (17.6500,93.5000,0.033445)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.6500,93.5000,0.168734) (20.9000,93.5000,0.168734) (20.9000,109.0000,0.168734) (17.6500,109.0000,0.168734)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.6500,109.0000,0.240670) (20.9000,109.0000,0.240670) (20.9000,159.5000,0.240670) (17.6500,159.5000,0.240670)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.6500,159.5000,0.252029) (20.9000,159.5000,0.252029) (20.9000,259.0000,0.252029) (17.6500,259.0000,0.252029)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.6500,259.0000,0.072398) (20.9000,259.0000,0.072398) (20.9000,284.5000,0.072398) (17.6500,284.5000,0.072398)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.6500,284.5000,0.054139) (20.9000,284.5000,0.054139) (20.9000,455.0000,0.054139) (17.6500,455.0000,0.054139)};
 
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.9000,68.0000,0.0015) (25.6500,68.0000,0.0015) (25.6500,70.5000,0.0015) (20.9000,70.5000,0.0015)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.9000,70.5000,0.0060) (25.6500,70.5000,0.0060) (25.6500,93.5000,0.0060) (20.9000,93.5000,0.0060)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.9000,93.5000,0.0320) (25.6500,93.5000,0.0320) (25.6500,109.0000,0.0320) (20.9000,109.0000,0.0320)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.9000,109.0000,0.0945) (25.6500,109.0000,0.0945) (25.6500,159.5000,0.0945) (20.9000,159.5000,0.0945)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.9000,159.5000,0.0455) (25.6500,159.5000,0.0455) (25.6500,259.0000,0.0455) (20.9000,259.0000,0.0455)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.9000,259.0000,0.0000) (25.6500,259.0000,0.0000) (25.6500,284.5000,0.0000) (20.9000,284.5000,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.9000,284.5000,0.0070) (25.6500,284.5000,0.0070) (25.6500,455.0000,0.0070) (20.9000,455.0000,0.0070)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.9000,68.0000,0.168421) (25.6500,68.0000,0.168421) (25.6500,70.5000,0.168421) (20.9000,70.5000,0.168421)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.9000,70.5000,0.077803) (25.6500,70.5000,0.077803) (25.6500,93.5000,0.077803) (20.9000,93.5000,0.077803)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.9000,93.5000,0.407470) (25.6500,93.5000,0.407470) (25.6500,109.0000,0.407470) (20.9000,109.0000,0.407470)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.9000,109.0000,0.385618) (25.6500,109.0000,0.385618) (25.6500,159.5000,0.385618) (20.9000,159.5000,0.385618)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.9000,159.5000,0.086750) (25.6500,159.5000,0.086750) (25.6500,259.0000,0.086750) (20.9000,259.0000,0.086750)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.9000,259.0000,0.020640) (25.6500,259.0000,0.020640) (25.6500,284.5000,0.020640) (20.9000,284.5000,0.020640)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.9000,284.5000,0.006791) (25.6500,284.5000,0.006791) (25.6500,455.0000,0.006791) (20.9000,455.0000,0.006791)};
 
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(25.6500,68.0000,0.0055) (28.9000,68.0000,0.0055) (28.9000,70.5000,0.0055) (25.6500,70.5000,0.0055)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(25.6500,70.5000,0.0110) (28.9000,70.5000,0.0110) (28.9000,93.5000,0.0110) (25.6500,93.5000,0.0110)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(25.6500,93.5000,0.0375) (28.9000,93.5000,0.0375) (28.9000,109.0000,0.0375) (25.6500,109.0000,0.0375)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(25.6500,109.0000,0.0545) (28.9000,109.0000,0.0545) (28.9000,159.5000,0.0545) (25.6500,159.5000,0.0545)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(25.6500,159.5000,0.0165) (28.9000,159.5000,0.0165) (28.9000,259.0000,0.0165) (25.6500,259.0000,0.0165)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(25.6500,259.0000,0.0000) (28.9000,259.0000,0.0000) (28.9000,284.5000,0.0000) (25.6500,284.5000,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(25.6500,284.5000,0.0035) (28.9000,284.5000,0.0035) (28.9000,455.0000,0.0035) (25.6500,455.0000,0.0035)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(25.6500,68.0000,0.369231) (28.9000,68.0000,0.369231) (28.9000,70.5000,0.369231) (25.6500,70.5000,0.369231)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(25.6500,70.5000,0.193980) (28.9000,70.5000,0.193980) (28.9000,93.5000,0.193980) (25.6500,93.5000,0.193980)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(25.6500,93.5000,0.545906) (28.9000,93.5000,0.545906) (28.9000,109.0000,0.545906) (25.6500,109.0000,0.545906)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(25.6500,109.0000,0.332064) (28.9000,109.0000,0.332064) (28.9000,159.5000,0.332064) (25.6500,159.5000,0.332064)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(25.6500,159.5000,0.041747) (28.9000,159.5000,0.041747) (28.9000,259.0000,0.041747) (25.6500,259.0000,0.041747)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(25.6500,259.0000,0.012066) (28.9000,259.0000,0.012066) (28.9000,284.5000,0.012066) (25.6500,284.5000,0.012066)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(25.6500,284.5000,0.008121) (28.9000,284.5000,0.008121) (28.9000,455.0000,0.008121) (25.6500,455.0000,0.008121)};
 
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(28.9000,68.0000,0.0030) (46.6000,68.0000,0.0030) (46.6000,70.5000,0.0030) (28.9000,70.5000,0.0030)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(28.9000,70.5000,0.0995) (46.6000,70.5000,0.0995) (46.6000,93.5000,0.0995) (28.9000,93.5000,0.0995)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(28.9000,93.5000,0.0860) (46.6000,93.5000,0.0860) (46.6000,109.0000,0.0860) (28.9000,109.0000,0.0860)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(28.9000,109.0000,0.0605) (46.6000,109.0000,0.0605) (46.6000,159.5000,0.0605) (28.9000,159.5000,0.0605)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(28.9000,159.5000,0.0120) (46.6000,159.5000,0.0120) (46.6000,259.0000,0.0120) (28.9000,259.0000,0.0120)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(28.9000,259.0000,0.0000) (46.6000,259.0000,0.0000) (46.6000,284.5000,0.0000) (28.9000,284.5000,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(28.9000,284.5000,0.0005) (46.6000,284.5000,0.0005) (46.6000,455.0000,0.0005) (28.9000,455.0000,0.0005)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(28.9000,68.0000,0.124294) (46.6000,68.0000,0.124294) (46.6000,70.5000,0.124294) (28.9000,70.5000,0.124294)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(28.9000,70.5000,0.262835) (46.6000,70.5000,0.262835) (46.6000,93.5000,0.262835) (28.9000,93.5000,0.262835)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(28.9000,93.5000,0.302533) (46.6000,93.5000,0.302533) (46.6000,109.0000,0.302533) (28.9000,109.0000,0.302533)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(28.9000,109.0000,0.054819) (46.6000,109.0000,0.054819) (46.6000,159.5000,0.054819) (28.9000,159.5000,0.054819)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(28.9000,159.5000,0.007665) (46.6000,159.5000,0.007665) (46.6000,259.0000,0.007665) (28.9000,259.0000,0.007665)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(28.9000,259.0000,0.000000) (46.6000,259.0000,0.000000) (46.6000,284.5000,0.000000) (28.9000,284.5000,0.000000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(28.9000,284.5000,0.000166) (46.6000,284.5000,0.000166) (46.6000,455.0000,0.000166) (28.9000,455.0000,0.000166)};
 
-			\addplot3[mark=+, draw=none, mark size=1.0] coordinates {
+			\addplot3[mark=+, draw=none, mark size=1.0, jitter = 0.1] coordinates {
 (18.000,307.000,1) (15.000,350.000,1) (18.000,318.000,1) (16.000,304.000,1) (17.000,302.000,1) (15.000,429.000,1) (14.000,454.000,1) (14.000,440.000,1) (14.000,455.000,1) (15.000,390.000,1) (15.000,383.000,1) (14.000,340.000,1) (15.000,400.000,1) (14.000,455.000,1) (24.000,113.000,1) (22.000,198.000,1) (18.000,199.000,1) (21.000,200.000,1) (27.000,97.000,1) (26.000,97.000,1) (25.000,110.000,1) (24.000,107.000,1) (25.000,104.000,1) (26.000,121.000,1) (21.000,199.000,1) (10.000,360.000,1) (10.000,307.000,1) (11.000,318.000,1) (9.000,304.000,1) (27.000,97.000,1) (28.000,140.000,1) (25.000,113.000,1) (19.000,232.000,1) (16.000,225.000,1) (17.000,250.000,1) (19.000,250.000,1) (18.000,232.000,1) (14.000,350.000,1) (14.000,400.000,1) (14.000,351.000,1) (14.000,318.000,1) (12.000,383.000,1) (13.000,400.000,1) (13.000,400.000,1) (18.000,258.000,1) (22.000,140.000,1) (19.000,250.000,1) (18.000,250.000,1) (23.000,122.000,1) (28.000,116.000,1) (30.000,79.000,1) (30.000,88.000,1) (31.000,71.000,1) (35.000,72.000,1) (27.000,97.000,1) (26.000,91.000,1) (24.000,113.000,1) (25.000,97.500,1) (23.000,97.000,1) (20.000,140.000,1) (21.000,122.000,1) (13.000,350.000,1) (14.000,400.000,1) (15.000,318.000,1) (14.000,351.000,1) (17.000,304.000,1) (11.000,429.000,1) (13.000,350.000,1) (12.000,350.000,1) (13.000,400.000,1) (19.000,70.000,1) (15.000,304.000,1) (13.000,307.000,1) (13.000,302.000,1) (14.000,318.000,1) (18.000,121.000,1) (22.000,121.000,1) (21.000,120.000,1) (26.000,96.000,1) (22.000,122.000,1) (28.000,97.000,1) (23.000,120.000,1) (28.000,98.000,1) (27.000,97.000,1) (13.000,350.000,1) (14.000,304.000,1) (13.000,350.000,1) (14.000,302.000,1) (15.000,318.000,1) (12.000,429.000,1) (13.000,400.000,1) (13.000,351.000,1) (14.000,318.000,1) (13.000,440.000,1) (12.000,455.000,1) (13.000,360.000,1) (18.000,225.000,1) (16.000,250.000,1) (18.000,232.000,1) (18.000,250.000,1) (23.000,198.000,1) (26.000,97.000,1) (11.000,400.000,1) (12.000,400.000,1) (13.000,360.000,1) (12.000,350.000,1) (18.000,232.000,1) (20.000,97.000,1) (21.000,140.000,1) (22.000,108.000,1) (18.000,70.000,1) (19.000,122.000,1) (21.000,155.000,1) (26.000,98.000,1) (15.000,350.000,1) (16.000,400.000,1) (29.000,68.000,1) (24.000,116.000,1) (20.000,114.000,1) (19.000,121.000,1) (15.000,318.000,1) (24.000,121.000,1) (20.000,156.000,1) (11.000,350.000,1) (20.000,198.000,1) (19.000,232.000,1) (15.000,250.000,1) (31.000,79.000,1) (26.000,122.000,1) (32.000,71.000,1) (25.000,140.000,1) (16.000,250.000,1) (16.000,258.000,1) (18.000,225.000,1) (16.000,302.000,1) (13.000,350.000,1) (14.000,318.000,1) (14.000,302.000,1) (14.000,304.000,1) (29.000,98.000,1) (26.000,79.000,1) (26.000,97.000,1) (31.000,76.000,1) (32.000,83.000,1) (28.000,90.000,1) (24.000,90.000,1) (26.000,116.000,1) (24.000,120.000,1) (26.000,108.000,1) (31.000,79.000,1) (19.000,225.000,1) (18.000,250.000,1) (15.000,250.000,1) (15.000,250.000,1) (16.000,400.000,1) (15.000,350.000,1) (16.000,318.000,1) (14.000,351.000,1) (17.000,231.000,1) (16.000,250.000,1) (15.000,258.000,1) (18.000,225.000,1) (21.000,231.000,1) (20.000,262.000,1) (13.000,302.000,1) (29.000,97.000,1) (23.000,140.000,1) (20.000,232.000,1) (23.000,140.000,1) (24.000,134.000,1) (25.000,90.000,1) (24.000,119.000,1) (18.000,171.000,1) (29.000,90.000,1) (19.000,232.000,1) (23.000,115.000,1) (23.000,120.000,1) (22.000,121.000,1) (25.000,121.000,1) (33.000,91.000,1) (28.000,107.000,1) (25.000,116.000,1) (25.000,140.000,1) (26.000,98.000,1) (27.000,101.000,1) (17.500,305.000,1) (16.000,318.000,1) (15.500,304.000,1) (14.500,351.000,1) (22.000,225.000,1) (22.000,250.000,1) (24.000,200.000,1) (22.500,232.000,1) (29.000,85.000,1) (24.500,98.000,1) (29.000,90.000,1) (33.000,91.000,1) (20.000,225.000,1) (18.000,250.000,1) (18.500,250.000,1) (17.500,258.000,1) (29.500,97.000,1) (32.000,85.000,1) (28.000,97.000,1) (26.500,140.000,1) (20.000,130.000,1) (13.000,318.000,1) (19.000,120.000,1) (19.000,156.000,1) (16.500,168.000,1) (16.500,350.000,1) (13.000,350.000,1) (13.000,302.000,1) (13.000,318.000,1) (31.500,98.000,1) (30.000,111.000,1) (36.000,79.000,1) (25.500,122.000,1) (33.500,85.000,1) (17.500,305.000,1) (17.000,260.000,1) (15.500,318.000,1) (15.000,302.000,1) (17.500,250.000,1) (20.500,231.000,1) (19.000,225.000,1) (18.500,250.000,1) (16.000,400.000,1) (15.500,350.000,1) (15.500,400.000,1) (16.000,351.000,1) (29.000,97.000,1) (24.500,151.000,1) (26.000,97.000,1) (25.500,140.000,1) (30.500,98.000,1) (33.500,98.000,1) (30.000,97.000,1) (30.500,97.000,1) (22.000,146.000,1) (21.500,121.000,1) (21.500,80.000,1) (43.100,90.000,1) (36.100,98.000,1) (32.800,78.000,1) (39.400,85.000,1) (36.100,91.000,1) (19.900,260.000,1) (19.400,318.000,1) (20.200,302.000,1) (19.200,231.000,1) (20.500,200.000,1) (20.200,200.000,1) (25.100,140.000,1) (20.500,225.000,1) (19.400,232.000,1) (20.600,231.000,1) (20.800,200.000,1) (18.600,225.000,1) (18.100,258.000,1) (19.200,305.000,1) (17.700,231.000,1) (18.100,302.000,1) (17.500,318.000,1) (30.000,98.000,1) (27.500,134.000,1) (27.200,119.000,1) (30.900,105.000,1) (21.100,134.000,1) (23.200,156.000,1) (23.800,151.000,1) (23.900,119.000,1) (20.300,131.000,1) (17.000,163.000,1) (21.600,121.000,1) (16.200,163.000,1) (31.500,89.000,1) (29.500,98.000,1) (21.500,231.000,1) (19.800,200.000,1) (22.300,140.000,1) (20.200,232.000,1) (20.600,225.000,1) (17.000,305.000,1) (17.600,302.000,1) (16.500,351.000,1) (18.200,318.000,1) (16.900,350.000,1) (15.500,351.000,1) (19.200,267.000,1) (18.500,360.000,1) (31.900,89.000,1) (34.100,86.000,1) (35.700,98.000,1) (27.400,121.000,1) (25.400,183.000,1) (23.000,350.000,1) (27.200,141.000,1) (23.900,260.000,1) (34.200,105.000,1) (34.500,105.000,1) (31.800,85.000,1) (37.300,91.000,1) (28.400,151.000,1) (28.800,173.000,1) (26.800,173.000,1) (33.500,151.000,1) (41.500,98.000,1) (38.100,89.000,1) (32.100,98.000,1) (37.200,86.000,1) (28.000,151.000,1) (26.400,140.000,1) (24.300,151.000,1) (19.100,225.000,1) (34.300,97.000,1) (29.800,134.000,1) (31.300,120.000,1) (37.000,119.000,1) (32.200,108.000,1) (46.600,86.000,1) (27.900,156.000,1) (40.800,85.000,1) (44.300,90.000,1) (43.400,90.000,1) (36.400,121.000,1) (30.000,146.000,1) (44.600,91.000,1) (33.800,97.000,1) (29.800,89.000,1) (32.700,168.000,1) (23.700,70.000,1) (35.000,122.000,1) (32.400,107.000,1) (27.200,135.000,1) (26.600,151.000,1) (25.800,156.000,1) (23.500,173.000,1) (30.000,135.000,1) (39.100,79.000,1) (39.000,86.000,1) (35.100,81.000,1) (32.300,97.000,1) (37.000,85.000,1) (37.700,89.000,1) (34.100,91.000,1) (34.700,105.000,1) (34.400,98.000,1) (29.900,98.000,1) (33.000,105.000,1) (33.700,107.000,1) (32.400,108.000,1) (32.900,119.000,1) (31.600,120.000,1) (28.100,141.000,1) (30.700,145.000,1) (25.400,168.000,1) (24.200,146.000,1) (22.400,231.000,1) (26.600,350.000,1) (20.200,200.000,1) (17.600,225.000,1) (28.000,112.000,1) (27.000,112.000,1) (34.000,112.000,1) (31.000,112.000,1) (29.000,135.000,1) (27.000,151.000,1) (24.000,140.000,1) (36.000,105.000,1) (37.000,91.000,1) (31.000,91.000,1) (38.000,105.000,1) (36.000,98.000,1) (36.000,120.000,1) (36.000,107.000,1) (34.000,108.000,1) (38.000,91.000,1) (32.000,91.000,1) (38.000,91.000,1) (25.000,181.000,1) (38.000,262.000,1) (26.000,156.000,1) (22.000,232.000,1) (32.000,144.000,1) (36.000,135.000,1) (27.000,151.000,1) (27.000,140.000,1) (44.000,97.000,1) (32.000,135.000,1) (28.000,120.000,1) (31.000,119.000,1) };

### 2015-11-27 graph_auto_exp2_distr_1_3.tex
Modify based on Mykel's feedback

--- 2015-11-16 graph_auto_exp2_distr_1_3.tex
@@
 			zmin=0.0, zmax=1.0,
-			xlabel=A,
-			ylabel=C,
+			xlabel=$A$,
+			ylabel=$C$,
 			colorbar,
-			point meta min=0, point meta max=0.5,
+			point meta min=0, point meta max=1.2,
 			colormap={}{ gray(0cm)=(1); gray(1cm)=(0);},
 			colorbar style={
-			        ytick={0,0.05,...,0.5},
+			        ytick={0,0.24,...,1.3},
+			        ylabel={probability density $\times 10^3$},
+			        y label style={at={(axis description cs:6.5,0.5)},rotate=180,anchor=north},
 			        yticklabel style={
@@
 
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,68.0000,0.0000) (17.5500,68.0000,0.0000) (17.5500,134.5000,0.0000) (9.0000,134.5000,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,134.5000,0.0010) (17.5500,134.5000,0.0010) (17.5500,159.5000,0.0010) (9.0000,159.5000,0.0010)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,159.5000,0.0010) (17.5500,159.5000,0.0010) (17.5500,169.5000,0.0010) (9.0000,169.5000,0.0010)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,169.5000,0.0395) (17.5500,169.5000,0.0395) (17.5500,259.0000,0.0395) (9.0000,259.0000,0.0395)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,259.0000,0.0045) (17.5500,259.0000,0.0045) (17.5500,264.5000,0.0045) (9.0000,264.5000,0.0045)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,264.5000,0.2220) (17.5500,264.5000,0.2220) (17.5500,455.0000,0.2220) (9.0000,455.0000,0.2220)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,68.0000,0.000000) (17.5500,68.0000,0.000000) (17.5500,134.5000,0.000000) (9.0000,134.5000,0.000000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,134.5000,0.004678) (17.5500,134.5000,0.004678) (17.5500,159.5000,0.004678) (9.0000,159.5000,0.004678)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,159.5000,0.011696) (17.5500,159.5000,0.011696) (17.5500,169.5000,0.011696) (9.0000,169.5000,0.011696)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,169.5000,0.051619) (17.5500,169.5000,0.051619) (17.5500,259.0000,0.051619) (9.0000,259.0000,0.051619)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,259.0000,0.095694) (17.5500,259.0000,0.095694) (17.5500,264.5000,0.095694) (9.0000,264.5000,0.095694)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,264.5000,0.136299) (17.5500,264.5000,0.136299) (17.5500,455.0000,0.136299) (9.0000,455.0000,0.136299)};
 
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.5500,68.0000,0.0765) (23.9500,68.0000,0.0765) (23.9500,134.5000,0.0765) (17.5500,134.5000,0.0765)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.5500,134.5000,0.0260) (23.9500,134.5000,0.0260) (23.9500,159.5000,0.0260) (17.5500,159.5000,0.0260)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.5500,159.5000,0.0085) (23.9500,159.5000,0.0085) (23.9500,169.5000,0.0085) (17.5500,169.5000,0.0085)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.5500,169.5000,0.1225) (23.9500,169.5000,0.1225) (23.9500,259.0000,0.1225) (17.5500,259.0000,0.1225)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.5500,259.0000,0.0070) (23.9500,259.0000,0.0070) (23.9500,264.5000,0.0070) (17.5500,264.5000,0.0070)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.5500,264.5000,0.0355) (23.9500,264.5000,0.0355) (23.9500,455.0000,0.0355) (17.5500,455.0000,0.0355)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.5500,68.0000,0.179746) (23.9500,68.0000,0.179746) (23.9500,134.5000,0.179746) (17.5500,134.5000,0.179746)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.5500,134.5000,0.162500) (23.9500,134.5000,0.162500) (23.9500,159.5000,0.162500) (17.5500,159.5000,0.162500)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.5500,159.5000,0.132813) (23.9500,159.5000,0.132813) (23.9500,169.5000,0.132813) (17.5500,169.5000,0.132813)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.5500,169.5000,0.213862) (23.9500,169.5000,0.213862) (23.9500,259.0000,0.213862) (17.5500,259.0000,0.213862)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.5500,259.0000,0.198864) (23.9500,259.0000,0.198864) (23.9500,264.5000,0.198864) (17.5500,264.5000,0.198864)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.5500,264.5000,0.029117) (23.9500,264.5000,0.029117) (23.9500,455.0000,0.029117) (17.5500,455.0000,0.029117)};
 
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.9500,68.0000,0.3525) (46.6000,68.0000,0.3525) (46.6000,134.5000,0.3525) (23.9500,134.5000,0.3525)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.9500,134.5000,0.0770) (46.6000,134.5000,0.0770) (46.6000,159.5000,0.0770) (23.9500,159.5000,0.0770)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.9500,159.5000,0.0020) (46.6000,159.5000,0.0020) (46.6000,169.5000,0.0020) (23.9500,169.5000,0.0020)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.9500,169.5000,0.0210) (46.6000,169.5000,0.0210) (46.6000,259.0000,0.0210) (23.9500,259.0000,0.0210)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.9500,259.0000,0.0000) (46.6000,259.0000,0.0000) (46.6000,264.5000,0.0000) (23.9500,264.5000,0.0000)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.9500,264.5000,0.0035) (46.6000,264.5000,0.0035) (46.6000,455.0000,0.0035) (23.9500,455.0000,0.0035)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.9500,68.0000,0.234029) (46.6000,68.0000,0.234029) (46.6000,134.5000,0.234029) (23.9500,134.5000,0.234029)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.9500,134.5000,0.135982) (46.6000,134.5000,0.135982) (46.6000,159.5000,0.135982) (23.9500,159.5000,0.135982)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.9500,159.5000,0.008830) (46.6000,159.5000,0.008830) (46.6000,169.5000,0.008830) (23.9500,169.5000,0.008830)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.9500,169.5000,0.010359) (46.6000,169.5000,0.010359) (46.6000,259.0000,0.010359) (23.9500,259.0000,0.010359)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.9500,259.0000,0.000000) (46.6000,259.0000,0.000000) (46.6000,264.5000,0.000000) (23.9500,264.5000,0.000000)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.9500,264.5000,0.000811) (46.6000,264.5000,0.000811) (46.6000,455.0000,0.000811) (23.9500,455.0000,0.000811)};
 
-			\addplot3[mark=+, draw=none, mark size=0.7] coordinates {
+			\addplot3[mark=+, draw=none, mark size=1.0, jitter = 0.1] coordinates {
 (18.000,307.000,1) (15.000,350.000,1) (18.000,318.000,1) (16.000,304.000,1) (17.000,302.000,1) (15.000,429.000,1) (14.000,454.000,1) (14.000,440.000,1) (14.000,455.000,1) (15.000,390.000,1) (15.000,383.000,1) (14.000,340.000,1) (15.000,400.000,1) (14.000,455.000,1) (24.000,113.000,1) (22.000,198.000,1) (18.000,199.000,1) (21.000,200.000,1) (27.000,97.000,1) (26.000,97.000,1) (25.000,110.000,1) (24.000,107.000,1) (25.000,104.000,1) (26.000,121.000,1) (21.000,199.000,1) (10.000,360.000,1) (10.000,307.000,1) (11.000,318.000,1) (9.000,304.000,1) (27.000,97.000,1) (28.000,140.000,1) (25.000,113.000,1) (19.000,232.000,1) (16.000,225.000,1) (17.000,250.000,1) (19.000,250.000,1) (18.000,232.000,1) (14.000,350.000,1) (14.000,400.000,1) (14.000,351.000,1) (14.000,318.000,1) (12.000,383.000,1) (13.000,400.000,1) (13.000,400.000,1) (18.000,258.000,1) (22.000,140.000,1) (19.000,250.000,1) (18.000,250.000,1) (23.000,122.000,1) (28.000,116.000,1) (30.000,79.000,1) (30.000,88.000,1) (31.000,71.000,1) (35.000,72.000,1) (27.000,97.000,1) (26.000,91.000,1) (24.000,113.000,1) (25.000,97.500,1) (23.000,97.000,1) (20.000,140.000,1) (21.000,122.000,1) (13.000,350.000,1) (14.000,400.000,1) (15.000,318.000,1) (14.000,351.000,1) (17.000,304.000,1) (11.000,429.000,1) (13.000,350.000,1) (12.000,350.000,1) (13.000,400.000,1) (19.000,70.000,1) (15.000,304.000,1) (13.000,307.000,1) (13.000,302.000,1) (14.000,318.000,1) (18.000,121.000,1) (22.000,121.000,1) (21.000,120.000,1) (26.000,96.000,1) (22.000,122.000,1) (28.000,97.000,1) (23.000,120.000,1) (28.000,98.000,1) (27.000,97.000,1) (13.000,350.000,1) (14.000,304.000,1) (13.000,350.000,1) (14.000,302.000,1) (15.000,318.000,1) (12.000,429.000,1) (13.000,400.000,1) (13.000,351.000,1) (14.000,318.000,1) (13.000,440.000,1) (12.000,455.000,1) (13.000,360.000,1) (18.000,225.000,1) (16.000,250.000,1) (18.000,232.000,1) (18.000,250.000,1) (23.000,198.000,1) (26.000,97.000,1) (11.000,400.000,1) (12.000,400.000,1) (13.000,360.000,1) (12.000,350.000,1) (18.000,232.000,1) (20.000,97.000,1) (21.000,140.000,1) (22.000,108.000,1) (18.000,70.000,1) (19.000,122.000,1) (21.000,155.000,1) (26.000,98.000,1) (15.000,350.000,1) (16.000,400.000,1) (29.000,68.000,1) (24.000,116.000,1) (20.000,114.000,1) (19.000,121.000,1) (15.000,318.000,1) (24.000,121.000,1) (20.000,156.000,1) (11.000,350.000,1) (20.000,198.000,1) (19.000,232.000,1) (15.000,250.000,1) (31.000,79.000,1) (26.000,122.000,1) (32.000,71.000,1) (25.000,140.000,1) (16.000,250.000,1) (16.000,258.000,1) (18.000,225.000,1) (16.000,302.000,1) (13.000,350.000,1) (14.000,318.000,1) (14.000,302.000,1) (14.000,304.000,1) (29.000,98.000,1) (26.000,79.000,1) (26.000,97.000,1) (31.000,76.000,1) (32.000,83.000,1) (28.000,90.000,1) (24.000,90.000,1) (26.000,116.000,1) (24.000,120.000,1) (26.000,108.000,1) (31.000,79.000,1) (19.000,225.000,1) (18.000,250.000,1) (15.000,250.000,1) (15.000,250.000,1) (16.000,400.000,1) (15.000,350.000,1) (16.000,318.000,1) (14.000,351.000,1) (17.000,231.000,1) (16.000,250.000,1) (15.000,258.000,1) (18.000,225.000,1) (21.000,231.000,1) (20.000,262.000,1) (13.000,302.000,1) (29.000,97.000,1) (23.000,140.000,1) (20.000,232.000,1) (23.000,140.000,1) (24.000,134.000,1) (25.000,90.000,1) (24.000,119.000,1) (18.000,171.000,1) (29.000,90.000,1) (19.000,232.000,1) (23.000,115.000,1) (23.000,120.000,1) (22.000,121.000,1) (25.000,121.000,1) (33.000,91.000,1) (28.000,107.000,1) (25.000,116.000,1) (25.000,140.000,1) (26.000,98.000,1) (27.000,101.000,1) (17.500,305.000,1) (16.000,318.000,1) (15.500,304.000,1) (14.500,351.000,1) (22.000,225.000,1) (22.000,250.000,1) (24.000,200.000,1) (22.500,232.000,1) (29.000,85.000,1) (24.500,98.000,1) (29.000,90.000,1) (33.000,91.000,1) (20.000,225.000,1) (18.000,250.000,1) (18.500,250.000,1) (17.500,258.000,1) (29.500,97.000,1) (32.000,85.000,1) (28.000,97.000,1) (26.500,140.000,1) (20.000,130.000,1) (13.000,318.000,1) (19.000,120.000,1) (19.000,156.000,1) (16.500,168.000,1) (16.500,350.000,1) (13.000,350.000,1) (13.000,302.000,1) (13.000,318.000,1) (31.500,98.000,1) (30.000,111.000,1) (36.000,79.000,1) (25.500,122.000,1) (33.500,85.000,1) (17.500,305.000,1) (17.000,260.000,1) (15.500,318.000,1) (15.000,302.000,1) (17.500,250.000,1) (20.500,231.000,1) (19.000,225.000,1) (18.500,250.000,1) (16.000,400.000,1) (15.500,350.000,1) (15.500,400.000,1) (16.000,351.000,1) (29.000,97.000,1) (24.500,151.000,1) (26.000,97.000,1) (25.500,140.000,1) (30.500,98.000,1) (33.500,98.000,1) (30.000,97.000,1) (30.500,97.000,1) (22.000,146.000,1) (21.500,121.000,1) (21.500,80.000,1) (43.100,90.000,1) (36.100,98.000,1) (32.800,78.000,1) (39.400,85.000,1) (36.100,91.000,1) (19.900,260.000,1) (19.400,318.000,1) (20.200,302.000,1) (19.200,231.000,1) (20.500,200.000,1) (20.200,200.000,1) (25.100,140.000,1) (20.500,225.000,1) (19.400,232.000,1) (20.600,231.000,1) (20.800,200.000,1) (18.600,225.000,1) (18.100,258.000,1) (19.200,305.000,1) (17.700,231.000,1) (18.100,302.000,1) (17.500,318.000,1) (30.000,98.000,1) (27.500,134.000,1) (27.200,119.000,1) (30.900,105.000,1) (21.100,134.000,1) (23.200,156.000,1) (23.800,151.000,1) (23.900,119.000,1) (20.300,131.000,1) (17.000,163.000,1) (21.600,121.000,1) (16.200,163.000,1) (31.500,89.000,1) (29.500,98.000,1) (21.500,231.000,1) (19.800,200.000,1) (22.300,140.000,1) (20.200,232.000,1) (20.600,225.000,1) (17.000,305.000,1) (17.600,302.000,1) (16.500,351.000,1) (18.200,318.000,1) (16.900,350.000,1) (15.500,351.000,1) (19.200,267.000,1) (18.500,360.000,1) (31.900,89.000,1) (34.100,86.000,1) (35.700,98.000,1) (27.400,121.000,1) (25.400,183.000,1) (23.000,350.000,1) (27.200,141.000,1) (23.900,260.000,1) (34.200,105.000,1) (34.500,105.000,1) (31.800,85.000,1) (37.300,91.000,1) (28.400,151.000,1) (28.800,173.000,1) (26.800,173.000,1) (33.500,151.000,1) (41.500,98.000,1) (38.100,89.000,1) (32.100,98.000,1) (37.200,86.000,1) (28.000,151.000,1) (26.400,140.000,1) (24.300,151.000,1) (19.100,225.000,1) (34.300,97.000,1) (29.800,134.000,1) (31.300,120.000,1) (37.000,119.000,1) (32.200,108.000,1) (46.600,86.000,1) (27.900,156.000,1) (40.800,85.000,1) (44.300,90.000,1) (43.400,90.000,1) (36.400,121.000,1) (30.000,146.000,1) (44.600,91.000,1) (33.800,97.000,1) (29.800,89.000,1) (32.700,168.000,1) (23.700,70.000,1) (35.000,122.000,1) (32.400,107.000,1) (27.200,135.000,1) (26.600,151.000,1) (25.800,156.000,1) (23.500,173.000,1) (30.000,135.000,1) (39.100,79.000,1) (39.000,86.000,1) (35.100,81.000,1) (32.300,97.000,1) (37.000,85.000,1) (37.700,89.000,1) (34.100,91.000,1) (34.700,105.000,1) (34.400,98.000,1) (29.900,98.000,1) (33.000,105.000,1) (33.700,107.000,1) (32.400,108.000,1) (32.900,119.000,1) (31.600,120.000,1) (28.100,141.000,1) (30.700,145.000,1) (25.400,168.000,1) (24.200,146.000,1) (22.400,231.000,1) (26.600,350.000,1) (20.200,200.000,1) (17.600,225.000,1) (28.000,112.000,1) (27.000,112.000,1) (34.000,112.000,1) (31.000,112.000,1) (29.000,135.000,1) (27.000,151.000,1) (24.000,140.000,1) (36.000,105.000,1) (37.000,91.000,1) (31.000,91.000,1) (38.000,105.000,1) (36.000,98.000,1) (36.000,120.000,1) (36.000,107.000,1) (34.000,108.000,1) (38.000,91.000,1) (32.000,91.000,1) (38.000,91.000,1) (25.000,181.000,1) (38.000,262.000,1) (26.000,156.000,1) (22.000,232.000,1) (32.000,144.000,1) (36.000,135.000,1) (27.000,151.000,1) (27.000,140.000,1) (44.000,97.000,1) (32.000,135.000,1) (28.000,120.000,1) (31.000,119.000,1) };

### 2015-11-30 BN_discretizer_paper.tex
ran spellcheck

@@
 Automated discretization methods have been studied in machine learning and statistics for many years \citep{Dougherty_1995, Kerber_1992, Holte_1993, Fayyad_1993}, primarily for classification problems.
-These methods search for the best discretization policy for a continuous attribute by considering its interation with a class variable.
-It is common to discretize all continuous variables before learning a Bayesian network structure to avoid having to consider variable interactions, as the interations and dependencies between variables in Bayesian networks introduce complexity.
+These methods search for the best discretization policy for a continuous attribute by considering its interaction with a class variable.
+It is common to discretize all continuous variables before learning a Bayesian network structure to avoid having to consider variable interactions, as the interactions and dependencies between variables in Bayesian networks introduce complexity.
 The discretization of a variable in a network requires considering the impact on the variable's Markov blanket.
@@
 The MODL method uses dynamic programming to find the optimal discretization policy for a continuous variable given a discrete class variable, and has an $\bigo\paren{n^3 + r \cdot n^2}$ runtime, where $r$ is the number of instances for the class variable.
-\cite{Lustgarten_2011} suggest several formulations for the prior term $P(\textit{Model})$, and the asymptotical equivalence between MDL and MODL on the single-variable, single-class problem was examined by \citet{VL_2000}.
+\cite{Lustgarten_2011} suggest several formulations for the prior term $P(\textit{Model})$, and the asymptotic equivalence between MDL and MODL on the single-variable, single-class problem was examined by \citet{VL_2000}.
 
@@
 Let the samples of $\cX$ in a given dataset $D$ be sorted in ascending order, ${\cx_{1:n} = \curly{\cx_1 \leq \cx_2 \leq \ldots \leq \cx_n}}$, and let the unique values be ${\cu_{1:m} = \curly{\cu_1 < \cu_2 < \ldots < \cu_{m}}}$.
-The index of the last occurence of $\cu_i$ in $\cx_{1:n}$ is denoted $s_i$.
+The index of the last occurrence of $\cu_i$ in $\cx_{1:n}$ is denoted $s_i$.
 

### 2015-11-30 information_sheet.tex
ran spellcheck

@@
 
-This paper introduces a principled Bayesian discretization method for continuous variables in Bayesian networks with quadratic complexity instead of the cubic complexity of the standard minimum-discription length (MDL) technique.
+This paper introduces a principled Bayesian discretization method for continuous variables in Bayesian networks with quadratic complexity instead of the cubic complexity of the standard minimum-description length (MDL) technique.
 In addition, this paper shows how to incorporate existing methods into the structure learning process to discretize all continuous variables while simultaneously learning Bayesian network structures.\\[0em]
@@
 The proposed method learns the discretization with quadratic runtime in the number of data samples, allowing it to more efficiently scale to larger datasets.
-Furthermore, emperical demonstrations show that the proposed method produces superior discretization policies, which was objectively evalated using the cross-validated log-likelihood.\\[0em]
+Furthermore, empirical demonstrations show that the proposed method produces superior discretization policies, which was objectively evalated using the cross-validated log-likelihood.\\[0em]
 

### 2015-12-01 BN_discretizer_paper.tex
Partially update

@@
 
-\title{Learning Discrete-valued Bayesian Networks from Mixed Data%\thanks{Grants or other notes
+\title{Learning Discrete Bayesian Networks from Continuous Data%\thanks{Grants or other notes
 %about the article that should go on the front page should be
@@
 Real data often contains a mixture of discrete and continuous variables, but many Bayesian network structure learning and inference algorithms assume all random variables are discrete.
-Continuous and hybrid variables are often discretized, but the choice of discretization policy has significant impact on the accuracy, speed, and interpretability of the resulting models.
+Continuous variables are often discretized, but the choice of discretization policy has significant impact on the accuracy, speed, and interpretability of the resulting models.
 This paper introduces a principled Bayesian discretization method for continuous variables in Bayesian networks with quadratic complexity instead of the cubic complexity of other standard techniques.
@@
 One successful example of parametric, continuous distributions in Bayesian networks is the Gaussian graphical model \citep{Weiss_2011}.
-For other parametric distributions and non-linear functions \citep{Ihler_2009}, however, these redesigned algorithms can be computationally expensive.
+\yichun{Is the comma between parametric and continuous necessay?}
+%For other parametric distributions and non-linear functions \citep{Ihler_2009}, however, these redesigned algorithms can be computationally expensive.
 
@@
 Parametric models have a fixed number of parameters, whereas the number of parameters in a nonparametric model grow with the amount of training data.
-Inference algorithms on nonparametric models can be also inefficient.
+%Inference algorithms on nonparametric models can be also inefficient.
+\yichun{I comment out all computational cost issues}
 
@@
 It is common to discretize all continuous variables before learning a Bayesian network structure to avoid having to consider variable interactions, as the interactions and dependencies between variables in Bayesian networks introduce complexity.
-The discretization of a variable in a network requires considering the impact on the variable's Markov blanket.
+%The discretization of a variable in a network requires considering the impact on the variable's Markov blanket.
 Prior work exists for discretizing continuous variables in naive Bayesian networks and tree-augmented networks \citep{Fried_naive}, but only a few discretization methods for general Bayesian networks have been proposed \citep{Friedman_1996, Kozlov_1997, Monti_1998, Steck_2007}.
 
-A common discretization method for continuous variables in Bayesian networks is the minimum description length (MDL) principle discretization method \citep{Friedman_1996}.
-The MDL principle \cite{MDL_1978} states that the best model for a dataset is the one that minimizes the amount of information needed to describe it \citep{Grunwald_2009}.
+\yichun{A common discretization method for Bayesian networks is to split continuous variables with uniform width or to decide discretization edges based on expert knowledge.
+A more principled method is the minimum description length (MDL) principle discretization \citep{Friedman_1996}.}
+The MDL principle proposed by \cite{MDL_1978} states that the best model for a dataset is the one that minimizes the amount of information needed to describe it \citep{Grunwald_2009}.
 MDL methods trade off goodness-of-fit against model complexity to reduce generalization error.
@@
 
-The optimal discretization policy of a single continuous variable under MDL is found using dynamic programming in runtime $\bigo\paren{n^3 + q \cdot n^2}$, where $n$ is the number of data samples and $q$ is a constant with exponential dependency on the cardinalities of the variables in the Bayesian network.
+The optimal discretization policy of a single continuous variable under MDL can be found using dynamic programming \yichun{with cubic runtime of number of data instances.}
 For Bayesian networks with multiple continuous variables, MDL discretization can be iteratively applied to each continuous variable.
@@
 
-Results in this work suggest that the MDL method suffers from low sensitivity to discretization edge locations and returns too few discretization intervals for continuous variables.
+Results in this work suggest that the MDL method suffers from low \yichun{sensitivity} to discretization edge locations and returns too few discretization intervals for continuous variables.
 This is caused by MDL's use of mutual information to measure the quality of discretization edges.
@@
 
-MODL \citep{Boulle_2006} is a Bayesian method for discretizing a continuous feature according to a class variable.
-Bayesian methods select the model with maximum posterior probability given the data, $P(\textit{Model} \mid \textit{Data})$.
-An application of Bayes' rule and constant $P(\textit{Data})$ shows that this is equivalent to maximizing ${P(\textit{Model}) \cdot P(\textit{Data} \mid \textit{Model})}$, where $P(\textit{Model})$ is a prior over models and ${P(\textit{Data} \mid \textit{Model})}$ is the data likelihood.
-The data likelihood usually increases with the number of discretization intervals, as more intervals allow for richer representations.
-The prior is chosen to influence the relative merit between models, and for discretization policies the prior is negatively correlated with the number of discretization intervals to favor simpler models and prevent overfitting.
-Maximizing ${P(\textit{Model}) \cdot P(\textit{Data} \mid \textit{Model})}$ thus requires a trade-off when determining the number of discretization intervals.
+MODL \citep{Boulle_2006} is a Bayesian method for discretizing a continuous feature according to a class variable. \yichun{
+It selects the model with maximum posterior probability given the data. 
+Along with Bayes' rule, this is equivalent to maximize ${P(\textit{Model}) \cdot P(\textit{Data} \mid \textit{Model})}$, where ${P(\textit{Data} \mid \textit{Model})}$ usually increases with the number of discretization intervals and $P(\textit{Model})$ is chosen to decrease with the number of discretization intervals.
+Maximizing ${P(\textit{Model}) \cdot P(\textit{Data} \mid \textit{Model})}$ thus requires a trade-off when determining the number of discretization intervals.}
+
+%Bayesian methods select the model with maximum posterior probability given the data, %$P(\textit{Model} \mid \textit{Data})$.
+%An application of Bayes' rule and constant $P(\textit{Data})$ shows that this is %equivalent to maximizing ${P(\textit{Model}) \cdot P(\textit{Data} \mid %\textit{Model})}$, where $P(\textit{Model})$ is a prior over models and ${P(\textit{Data} %\mid \textit{Model})}$ is the data likelihood.
+%The data likelihood usually increases with the number of discretization intervals, as %more intervals allow for richer representations.
+%The prior is chosen to influence the relative merit between models, and for %discretization policies the prior is negatively correlated with the number of %discretization intervals to favor simpler models and prevent overfitting.
+%Maximizing ${P(\textit{Model}) \cdot P(\textit{Data} \mid \textit{Model})}$ thus requires %a trade-off when determining the number of discretization intervals.
 
@@
 Four principles for the optimal discretization policy enable the formulation of $P(\Lambda)$ and $P(D_{-\cX} \mid \Lambda)$, where $D_{-\cX}$ is the subset of the dataset for all variables but $\cX$ and the probability of the data associated with the target variable, $P(D_{\cX})$, is already captured in $P(\Lambda)$.
-The four principles, motivated by MODL and \cite{Lustgarten_2011}, are:
+The four principles,\yichun{ which can be considered an extension of the priors in MODL and \cite{Lustgarten_2011} to Bayesian networks}, are:
 
@@
 
-The procedure used to minimize the objective function involves \todo{dynamical programming}.
+The procedure used to minimize the objective function involves \yichun{dynamical programming}.
 Note that because the objective function is cumulative over intervals, if a partition of $\cX$ into $k$ intervals by $\Lambda = \anglebrackets{\gamma_1, \gamma_2, \ldots, \gamma_k}$ is an optimal discretization policy, then any subinterval is optimal for the corresponding subproblem.
@@
     \For {$i \leftarrow 1$ to $N$}
-      \State $P_\text{old} \leftarrow g(X_i,\Pa_{X_i})$ \quad ( Equation~\ref{eq:B_Score_one})
+      \State $P_\text{old} \leftarrow g(X_i,\Pa_{X_i})$ \quad (Equation~\ref{eq:B_Score_one})
       \State OKToProceed $\leftarrow$ \textbf{true}
@@
           \State $\bm{\cX '} \leftarrow$ $\bm{\cX}$ sorted in reverse-topological order given $G$
-          \State $\Lambda \leftarrow$ \textsc{DiscretizeAll}({$D$, $G$, $\bm{\cX '}$, $\maxpasses$}): \quad (Algorithm~\ref{alg:disc_two})
+          \State $\Lambda \leftarrow$ \textsc{DiscretizeAll}({$D$, $G$, $\bm{\cX '}$, $\maxpasses$}) \quad (see Algorithm~\ref{alg:disc_two})
           \State $D^* \leftarrow \Lambda \paren{D_{\bm{\cX }}}$

### 2015-12-01 BN_discretizer_paper.tex
Finish the update

@@
 \usepackage[font=small,skip=5pt]{caption}
+\usepackage[hyphens]{url}
 
@@
 One successful example of parametric, continuous distributions in Bayesian networks is the Gaussian graphical model \citep{Weiss_2011}.
-\yichun{Is the comma between parametric and continuous necessay?}
+\yichun{Is the comma between ``parametric" and ``continuous" necessay?}
 %For other parametric distributions and non-linear functions \citep{Ihler_2009}, however, these redesigned algorithms can be computationally expensive.
@@
 
-\yichun{A common discretization method for Bayesian networks is to split continuous variables with uniform width or to decide discretization edges based on expert knowledge.
+\yichun{A common discretization method for Bayesian networks is to split continuous variables by uniform width or by expertises from application fields.
 A more principled method is the minimum description length (MDL) principle discretization \citep{Friedman_1996}.}
@@
 Four principles for the optimal discretization policy enable the formulation of $P(\Lambda)$ and $P(D_{-\cX} \mid \Lambda)$, where $D_{-\cX}$ is the subset of the dataset for all variables but $\cX$ and the probability of the data associated with the target variable, $P(D_{\cX})$, is already captured in $P(\Lambda)$.
-The four principles,\yichun{ which can be considered an extension of the priors in MODL and \cite{Lustgarten_2011} to Bayesian networks}, are:
+The four principles, \yichun{ which can be considered an extension of the priors in MODL and \cite{Lustgarten_2011} to Bayesian networks}, are:
 
@@
 
-The procedure used to minimize the objective function involves \yichun{dynamical programming}.
-Note that because the objective function is cumulative over intervals, if a partition of $\cX$ into $k$ intervals by $\Lambda = \anglebrackets{\gamma_1, \gamma_2, \ldots, \gamma_k}$ is an optimal discretization policy, then any subinterval is optimal for the corresponding subproblem.
+The procedure used to minimize the objective function involves dynamical programming.
+Note that because the objective function is cumulative over intervals, if a partition $\Lambda = \anglebrackets{\gamma_1, \gamma_2, \ldots, \gamma_k}$ of $\cX$ is an optimal discretization policy, then any subinterval is optimal for the corresponding subproblem.
 It follows that dynamic programming can be used to solve the optimization problem exactly.
@@
 The first experiment compares the performance of the Bayesian and MDL discretization methods on a known Bayesian network structure.
-The structure was obtained by prediscretizing each continuous variable into $k$ uniform-width intervals, where $k$ is the median number of instantiations of the discrete variables, and using the structure with the highest Bayesian score from \num{1000} runs of the K2 algorithm with random topological orderings.
+The structure was obtained by discretizing each continuous variable into $k$ uniform-width intervals, where $k$ is the median number of instantiations of the discrete variables, and using the structure with the highest Bayesian score from \num{1000} runs of the K2 algorithm with random topological orderings.
 The second experiment compares the same methods applied when simultaneously discretizing and learning network structure.
@@
 where $I(A,B)$ is the mutual information between two discrete variable sets $A$ and $B$, ${H(p) = -p \ln(p) - (1-p) \ln(1-p)}$, and $X$ is the discretized version of $\cX$.
-Equation \ref{eqn:MDL} can be minimized using dynamic programming with runtime $\bigo \paren{ n^3 + \paren{ n_c \cdot {L}^{n_s}  + {L}^{n_p}} \cdot n^2 }$.
+
+\yichun{Equation \ref{eqn:MDL} can be minimized exactly using dynamic programming.
+For a given Bayesian network, the first three terms only depends on the number of discretization intervals $\lvert X \rvert$ and the fourth term is cumulative on the intervals.
+Hence, if $\Lambda = \anglebrackets{\gamma_1, \gamma_2, \ldots, \gamma_k}$ is a MDL optimal discretization policy with $k$ intervals, then  $\Lambda' = \anglebrackets{\gamma_1, \gamma_2, \ldots, \gamma_{k-1}}$ is a MDL optimal discretization policy of the corresponding subproblems with $k-1$ intervals.}
+This procedure takes runtime $\bigo \paren{ n^3 + \paren{ n_c \cdot {L}^{n_s}  + {L}^{n_p}} \cdot n^2 }$. 
 All variables are defined in Section \ref{subsec:algo}.
-Therefore, the runtime of the proposed method in this paper is shorter than the MDL discretization method by $\bigo \paren{n^3}$.
+Therefore, the runtime of the proposed method in this paper is shorter than the MDL discretization method by $\bigo \paren{n^3}$, since the former has a more efficient form of dynamical programming.
 
@@
   \caption{
-    Results from discretization of the Auto MPG dataset with fixed structure from Figure~\ref{fig:auto_graph_1}.
-    The first five rows list the discretization edges for each continuous variable.
-    The last row lists the mean cross-validated log-likelihood; positive values are better.
-    The MDL method does not produce any discretization edges.
+    Discretization result of the Auto MPG dataset with fixed structure from Figure~\ref{fig:auto_graph_1}.
+    The first five rows list the discretization edges and the last row lists the mean cross-validated log-likelihood; positive values are better.
+    %The MDL method does not produce any discretization edges.
   }
@@
     Discretization policy summary of the Housing dataset based on the fixed network structure shown.
-    The first twelve rows show the numbers of intervals after discretization for each method.
-    The last row is the mean cross-validated log-likelihood based on each discretization result.
+    The first twelve rows show the numbers of discretization intervals and the last row is the mean cross-validated log-likelihood.% based on each discretization result.
     % The heuristic method is over-sensitive and discretizes some variables into too many intervals.
@@
     The discretization policies for variables $H$ and $E$ learned using the optimal Bayesian approach on the fixed network shown in Figure~\ref{fig:housing_graph_1}.
-    The variable $H$ possesses no \todo{overly} repeated values, thus producing a cleaner discretization policy.
+    \yichun{The variable $H$ possesses less frequenly repeated values, thus producing less number of discretization intervals than $E$.}
   }
@@
 This paper introduced a principled discretization method for continuous variables in Bayesian networks with quadratic complexity instead of the cubic complexity of other standard techniques.
-Emperical demonstrations show that the proposed method is superior to the state of the art.
+Empirical demonstrations show that the proposed method is superior to the state of the art.
 In addition, this paper shows how to incorporate existing methods into the structure learning process to discretize all continuous variables and simultaneously learn Bayesian network structures.
 The proposed method was incorporated and its superior performance was empirically demonstrated.
-All software is publically available to support discretization research, \todo{and can be found at.}
+All software is publically available to support discretization research, and \yichun{can be found at \url{github.com/sisl/LearnDiscreteBayesNets.jl}}.
 

### 2015-12-01 BN_discretizer_paper.tex
quantative ->qualitative

@@
 
-To quantatively assess the sensitivity of each method to the number and position of discretization intervals, consider the Bayesian network in Figure~\ref{fig:exp_discuss}, where $\cX$ is continuous and $P_1$ and $P_2$ are discrete.
+To qualitatively assess the sensitivity of each method to the number and position of discretization intervals, consider the Bayesian network in Figure~\ref{fig:exp_discuss}, where $\cX$ is continuous and $P_1$ and $P_2$ are discrete.
 If $\Pa_{\cX} = \curly{P_1, P_2}$ and $D_{\cX} = \curly{1.0,2.0,3.0, \ldots n}$, then the corresponding objective functions for the discretization methods are:

### 2015-12-01 BN_discretizer_paper.tex
update

@@
 The first is to model the conditional probability density of each continuous variable using specific families of parametric distributions, and then to redesign Bayesian network learning and inference algorithms based on the parameterizations.
-One successful example of parametric, continuous distributions in Bayesian networks is the Gaussian graphical model \citep{Weiss_2011}.
-\yichun{Is the comma between ``parametric" and ``continuous" necessay?}
+One successful example of parametric continuous distributions in Bayesian networks is the Gaussian graphical model \citep{Weiss_2011}.
 %For other parametric distributions and non-linear functions \citep{Ihler_2009}, however, these redesigned algorithms can be computationally expensive.
@@
 %Inference algorithms on nonparametric models can be also inefficient.
-\yichun{I comment out all computational cost issues}
 
@@
 
-\yichun{A common discretization method for Bayesian networks is to split continuous variables by uniform width or by expertises from application fields.
-A more principled method is the minimum description length (MDL) principle discretization \citep{Friedman_1996}.}
+A common discretization method for Bayesian networks is to split continuous variables into uniform-width intervals or by using field-specific expertise.
+A more principled method is the minimum description length (MDL) principle discretization \citep{Friedman_1996}.
 The MDL principle proposed by \cite{MDL_1978} states that the best model for a dataset is the one that minimizes the amount of information needed to describe it \citep{Grunwald_2009}.
@@
 
-The optimal discretization policy of a single continuous variable under MDL can be found using dynamic programming \yichun{with cubic runtime of number of data instances.}
+The optimal discretization policy of a single continuous variable under MDL can be found using dynamic programming in cubic runtime with the number of data instances.
 For Bayesian networks with multiple continuous variables, MDL discretization can be iteratively applied to each continuous variable.
@@
 Mutual information, which is composed of empirical probabilities computed using event count ratios, varies less severely with the positions of discretization edges than the method we suggest in this article.
-
-MODL \citep{Boulle_2006} is a Bayesian method for discretizing a continuous feature according to a class variable. \yichun{
-It selects the model with maximum posterior probability given the data. 
-Along with Bayes' rule, this is equivalent to maximize ${P(\textit{Model}) \cdot P(\textit{Data} \mid \textit{Model})}$, where ${P(\textit{Data} \mid \textit{Model})}$ usually increases with the number of discretization intervals and $P(\textit{Model})$ is chosen to decrease with the number of discretization intervals.
-Maximizing ${P(\textit{Model}) \cdot P(\textit{Data} \mid \textit{Model})}$ thus requires a trade-off when determining the number of discretization intervals.}
+\tim{Let's discuss sensitivity tomorrow}
+
+% The probability of the data given the model typically increases with the number of discretization intervals, and the model prior is chosen to decrease with the number of discretization intervals
+% Maximizing the model likelihood thus requires a trade-off in the number of discretization intervals.
 
@@
 
-The MODL method uses dynamic programming to find the optimal discretization policy for a continuous variable given a discrete class variable, and has an $\bigo\paren{n^3 + r \cdot n^2}$ runtime, where $r$ is the number of instances for the class variable.
+MODL \citep{Boulle_2006} is a Bayesian method for discretizing a continuous feature according to a class variable, which selects the model with maximum probability given the data.
+The MODL method uses dynamic programming to find the optimal discretization policy for a continuous variable given a discrete class variable, and has an $\bigo\paren{n^3 + r \cdot n^2}$ runtime, where $r$ is the number of class variable instantiations.
 \cite{Lustgarten_2011} suggest several formulations for the prior term $P(\textit{Model})$, and the asymptotic equivalence between MDL and MODL on the single-variable, single-class problem was examined by \citet{VL_2000}.
@@
 Let $D_{\bm{Y}}$ be the subset of the training data corresponding to variable subset $\bm{Y}$.
-Four principles for the optimal discretization policy enable the formulation of $P(\Lambda)$ and $P(D_{-\cX} \mid \Lambda)$, where $D_{-\cX}$ is the subset of the dataset for all variables but $\cX$ and the probability of the data associated with the target variable, $P(D_{\cX})$, is already captured in $P(\Lambda)$.
-The four principles, \yichun{ which can be considered an extension of the priors in MODL and \cite{Lustgarten_2011} to Bayesian networks}, are:
+Four principles for the optimal discretization policy enable the formulation of $P(\Lambda)$ and $P(D_{-\cX} \mid \Lambda)$, where $D_{-\cX}$ is the subset of the dataset for all variables but $\cX$, and the probability of the data associated with the target variable, $P(D_{\cX})$, is already captured in $P(\Lambda)$.
+The four principles, which can be considered an extension of the priors in MODL and \cite{Lustgarten_2011} to Bayesian networks, are:
 
@@
 
-\yichun{Equation \ref{eqn:MDL} can be minimized exactly using dynamic programming.
-For a given Bayesian network, the first three terms only depends on the number of discretization intervals $\lvert X \rvert$ and the fourth term is cumulative on the intervals.
-Hence, if $\Lambda = \anglebrackets{\gamma_1, \gamma_2, \ldots, \gamma_k}$ is a MDL optimal discretization policy with $k$ intervals, then  $\Lambda' = \anglebrackets{\gamma_1, \gamma_2, \ldots, \gamma_{k-1}}$ is a MDL optimal discretization policy of the corresponding subproblems with $k-1$ intervals.}
+Equation~\ref{eqn:MDL} can be minimized exactly using dynamic programming.
+For a given Bayesian network, the first three terms only depend on the number of discretization intervals $|X|$ and the fourth term is cumulative over the intervals.
+Hence, if $\Lambda = \anglebrackets{\gamma_1, \gamma_2, \ldots, \gamma_k}$ is a MDL optimal discretization policy with $k$ intervals, then $\Lambda' = \anglebrackets{\gamma_1, \gamma_2, \ldots, \gamma_{k-1}}$ is a MDL optimal discretization policy for the corresponding subproblem with $k-1$ intervals.
 This procedure takes runtime $\bigo \paren{ n^3 + \paren{ n_c \cdot {L}^{n_s}  + {L}^{n_p}} \cdot n^2 }$.
@@
     The discretization policies for variables $H$ and $E$ learned using the optimal Bayesian approach on the fixed network shown in Figure~\ref{fig:housing_graph_1}.
-    \yichun{The variable $H$ possesses less frequenly repeated values, thus producing less number of discretization intervals than $E$.}
+    The values for variable $H$ are less frequently repeated, thus producing fewer discretization intervals than $E$.
   }
@@
 The value of the edge position term for MDL is primarily determined by the mutual information, which varies less severely than the corresponding terms in the Bayesian method.
-The MDL term uses empirical probability distributions, based off of ratios of counts, whereas the Bayesian method uses factorial terms, and thus varies less.
+The MDL term uses empirical probability distributions, based off of ratios of counts, whereas the Bayesian method uses factorial terms, and thus the MDL method varies less.
 The MDL method is therefore less sensitive to the discretization edges.
@@
 The proposed method was incorporated and its superior performance was empirically demonstrated.
-All software is publically available to support discretization research, and \yichun{can be found at \url{github.com/sisl/LearnDiscreteBayesNets.jl}}.
+All software is publically available to support discretization research, and can be found at \url{github.com/sisl/LearnDiscreteBayesNets.jl}.
 

### 2015-12-01 information_sheet.tex
update

@@
 The proposed method learns the discretization with quadratic runtime in the number of data samples, allowing it to more efficiently scale to larger datasets.
-Furthermore, empirical demonstrations show that the proposed method produces superior discretization policies, which was objectively evalated using the cross-validated log-likelihood.\\[0em]
+Furthermore, empirical demonstrations show that the proposed method produces superior discretization policies, which was objectively evaluated using the cross-validated log-likelihood.\\[0em]
 

### 2015-12-01 BN_discretizer_paper.tex
misc

@@
 
-Results in this work suggest that the MDL method suffers from low \yichun{sensitivity} to discretization edge locations and returns too few discretization intervals for continuous variables.
+Results in this work suggest that the MDL method suffers from low sensitivity to discretization edge locations and returns too few discretization intervals for continuous variables.
 This is caused by MDL's use of mutual information to measure the quality of discretization edges.
 Mutual information, which is composed of empirical probabilities computed using event count ratios, varies less severely with the positions of discretization edges than the method we suggest in this article.
-\tim{Let's discuss sensitivity tomorrow}
 
@@
 
-This procedure is given in Algorithm~\ref{alg:structure_learn}, and takes five inputs: $D$, a dataset of samples from the joint distribution; $\bm{\cX}$, the set of all continuous variables; \todo{$\texttt{order}$}, a permutation of the variables in $D$; $\hat{n}_\text{parent}$, an upper bound on the number of parents per node; and $\maxpasses$, an upper bound on the number of complete passes.
+This procedure is given in Algorithm~\ref{alg:structure_learn}, and takes five inputs: $D$, a dataset of samples from the joint distribution; $\bm{\cX}$, the set of all continuous variables; $\texttt{order}$, a permutation of the variables in $D$; $\hat{n}_\text{parent}$, an upper bound on the number of parents per node; and $\maxpasses$, an upper bound on the number of complete passes.
 The upper bound on the number of parents is common practice, and is used to prevent computing conditional distributions with excessively large parameter sets.
@@
   \begin{aligned}
-  f_{\text{MDL}} & = \overbrace{Z_1 \cdot k + \ln(k) + \ln {{n +k - 1}\choose{k -1}} }^{\text{Penalty Term}}+   \overbrace{\rule{0pt}{1.35em} \ln(N) \cdot I(X^*, \Pa_X)}^{\text{Edge Position Term}} \\
+  f_{\text{MDL}} & = \overbrace{Z_1 \cdot k + \ln(k) + \ln {{n +k - 1}\choose{k -1}} }^{\text{Penalty Term}}+   \overbrace{\rule{0pt}{1.35em} \ln(n) \cdot I(X^*, \Pa_X)}^{\text{Edge Position Term}} \\
   f_{\text{Bayesian}} &= \underbrace{{\vrule width0pt height0pt depth1.48em\relax}  Z_2 \cdot k + \sum_{i=1}^k \ln {{\gamma_i + J_\text{P} - 1}\choose{J_\text{P} -1}}}_{\text{Penalty Term}} + \underbrace{\sum^k_{i=1} \ln \left(   {{\gamma_i !}\over{n^{\text{P}}_{i,1}!
@@
 
-The sensitivity of each method to the discretization edges are captured in the edge position terms, as the penalty terms are similar across methods.
+The penalty terms tend to increase with the number of discretization intervals; the edge position terms vary with the position and number of the discretization edges.
+A policy with a larger number of discretization edges is only optimal if the edge position term varies enough with respect to the penalty term in order to produce a local minimum of sufficiently low value.
+
 The value of the edge position term for MDL is primarily determined by the mutual information, which varies less severely than the corresponding terms in the Bayesian method.

### 2015-12-01 Fig12.tex
Change plot name

--- 2015-11-22 graph_housing_exp1_distr_3_5.tex
@@
 			zmin=0.0, zmax=1.0,
-			xlabel=C,
-			ylabel=E,
+			xlabel=$C$,
+			ylabel=$E$,
 			colorbar,
-			point meta min=0, point meta max=1.2,
+			point meta min=0, point meta max=1.0,
 			colormap={}{ gray(0cm)=(1); gray(1cm)=(0);},
 			colorbar style={
-			        ytick={0,0.3,...,1.3},
+			        ytick={0,0.2,...,1.01},
 			        ylabel={probability density$ \times 10^{-1}$},
+			        y label style={at={(axis description cs:6.5,0.5)},rotate=180,anchor=north},
+			        yticklabels={\num{0.00},\num{0.20},\num{0.40},\num{0.60},\num{0.80},$\geq 1$},
 			        y label style={at={(axis description cs:6.5,0.5)},rotate=180,anchor=north},

### 2015-12-01 Fig8.tex
Change plot name

--- 2015-11-24 graph_wine_exp2_distr_5_11.tex
@@
 \begin{tikzpicture}
-		\begin{axis}[
+  \begin{groupplot}[
+	  	group style={group size=2 by 1,horizontal sep=1.5em,
+  		},
+  		width = 1/2*\textwidth - 1em,
+  		height = 6 cm ]%,xmin=0,ymin=0,height=4cm,width=5cm,no markers]
+  \nextgroupplot[
 			view={0}{90},
@@
 			zmin=0.0, zmax=1.0,
-			xlabel=E,
-			ylabel=K,
+			ylabel=$K$,
+			xlabel=$E$,
+			%colorbar,
+    %every colorbar/.append style={height=
+    %    2*\pgfkeysvalueof{/pgfplots/parent axis height}+
+     %   \pgfkeysvalueof{/pgfplots/group/vertical sep}},
+		    point meta min=0, point meta max=2.5,
+			colormap={}{ gray(0cm)=(1); gray(1cm)=(0);}
+			%colorbar style={
+			%        ytick={0,0.05,...,0.51},
+			%        yticklabel style={
+			%            text width=2.5em,
+			%            align=right,
+			%            /pgf/number format/.cd,
+			%                fixed,
+			%                fixed zerofill
+			%        }
+			%    }
+			]
+
+\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.6000,1.2800,0.311047) (17.9000,1.2800,0.311047) (17.9000,3.4600,0.3110) (10.6000,3.4600,0.3110)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.6000,3.4600,0.714497) (17.9000,3.4600,0.714497) (17.9000,4.8500,0.7145) (10.6000,4.8500,0.7145)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.6000,4.8500,0.776256) (17.9000,4.8500,0.776256) (17.9000,7.4000,0.7763) (10.6000,7.4000,0.7763)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.6000,7.4000,0.050147) (17.9000,7.4000,0.050147) (17.9000,13.0000,0.0501) (10.6000,13.0000,0.0501)};
+
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.9000,1.2800,1.766269) (23.2500,1.2800,1.766269) (23.2500,3.4600,1.7663) (17.9000,3.4600,1.7663)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.9000,3.4600,1.472467) (23.2500,3.4600,1.472467) (23.2500,4.8500,1.4725) (17.9000,4.8500,1.4725)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.9000,4.8500,1.172806) (23.2500,4.8500,1.172806) (23.2500,7.4000,1.1728) (17.9000,7.4000,1.1728)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.9000,7.4000,0.367156) (23.2500,7.4000,0.367156) (23.2500,13.0000,0.3672) (17.9000,13.0000,0.3672)};
+
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.2500,1.2800,0.329596) (30.0000,1.2800,0.329596) (30.0000,3.4600,0.3296) (23.2500,3.4600,0.3296)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.2500,3.4600,0.271783) (30.0000,3.4600,0.271783) (30.0000,4.8500,0.2718) (23.2500,4.8500,0.2718)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.2500,4.8500,0.133624) (30.0000,4.8500,0.133624) (30.0000,7.4000,0.1336) (23.2500,7.4000,0.1336)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.2500,7.4000,0.080688) (30.0000,7.4000,0.080688) (30.0000,13.0000,0.0807) (23.2500,13.0000,0.0807)};
+
+			\addplot3[mark=+, draw=none, mark size=1.0, jitter = 0.1] coordinates {
+(15.600,5.640,1) (11.200,4.380,1) (18.600,5.680,1) (16.800,7.800,1) (21.000,4.320,1) (15.200,6.750,1) (14.600,5.250,1) (17.600,5.050,1) (14.000,5.200,1) (16.000,7.220,1) (18.000,5.750,1) (16.800,5.000,1) (16.000,5.600,1) (11.400,5.400,1) (12.000,7.500,1) (17.200,7.300,1) (20.000,6.200,1) (20.000,6.600,1) (16.500,8.700,1) (15.200,5.100,1) (16.000,5.650,1) (18.600,4.500,1) (16.600,3.800,1) (17.800,3.930,1) (20.000,3.520,1) (25.000,3.580,1) (16.100,4.800,1) (17.000,3.950,1) (19.400,4.500,1) (16.000,4.700,1) (22.500,5.700,1) (19.100,6.900,1) (17.200,3.840,1) (19.500,5.400,1) (19.000,4.200,1) (20.500,5.100,1) (15.500,4.600,1) (18.000,4.250,1) (15.500,3.700,1) (13.200,5.100,1) (16.200,6.130,1) (18.800,4.280,1) (15.000,5.430,1) (17.500,4.360,1) (17.000,5.040,1) (18.900,5.240,1) (16.000,4.900,1) (16.000,6.100,1) (18.800,6.200,1) (17.400,8.900,1) (12.400,7.200,1) (17.200,5.600,1) (14.000,7.050,1) (17.100,6.300,1) (16.400,5.850,1) (20.500,6.250,1) (16.300,6.380,1) (16.800,6.000,1) (16.700,6.800,1) (10.600,1.950,1) (16.000,3.270,1) (16.800,5.750,1) (18.000,3.800,1) (19.000,4.450,1) (19.000,2.950,1) (18.100,4.600,1) (15.000,5.300,1) (19.600,4.680,1) (17.000,3.170,1) (16.800,2.850,1) (20.400,3.050,1) (25.000,3.380,1) (24.000,3.740,1) (30.000,3.350,1) (21.000,3.210,1) (16.000,3.800,1) (16.000,4.600,1) (18.000,2.650,1) (14.800,3.400,1) (23.000,2.570,1) (19.000,2.500,1) (18.800,3.900,1) (24.000,2.200,1) (22.500,4.800,1) (18.000,3.050,1) (18.000,2.620,1) (22.800,2.450,1) (26.000,2.600,1) (21.600,2.800,1) (23.600,1.740,1) (18.500,2.400,1) (22.000,3.600,1) (20.700,3.050,1) (18.000,2.150,1) (18.000,3.250,1) (19.000,2.600,1) (21.500,2.500,1) (16.000,2.900,1) (18.500,4.500,1) (18.000,2.300,1) (17.500,3.300,1) (18.500,2.450,1) (21.000,2.800,1) (19.500,2.060,1) (20.500,2.940,1) (22.000,2.700,1) (19.000,3.400,1) (22.500,3.300,1) (19.000,2.700,1) (20.000,2.650,1) (19.500,2.900,1) (21.000,2.000,1) (20.000,3.800,1) (21.000,3.080,1) (22.500,2.900,1) (21.500,1.900,1) (20.800,1.950,1) (22.500,2.060,1) (16.000,3.400,1) (19.000,1.280,1) (20.000,3.250,1) (28.500,6.000,1) (26.500,2.080,1) (21.500,2.600,1) (21.000,2.800,1) (21.000,2.760,1) (21.500,3.940,1) (28.500,3.000,1) (24.500,2.120,1) (22.000,2.600,1) (18.000,4.100,1) (20.000,5.400,1) (24.000,5.700,1) (21.500,5.000,1) (17.500,5.450,1) (18.500,7.100,1) (21.000,3.850,1) (25.000,5.000,1) (19.500,5.700,1) (24.000,4.920,1) (21.000,4.600,1) (20.000,5.600,1) (23.500,4.350,1) (20.000,4.400,1) (18.500,8.210,1) (21.000,4.000,1) (20.000,4.900,1) (21.500,7.650,1) (21.500,8.420,1) (21.500,9.400,1) (24.000,8.600,1) (22.000,10.800,1) (25.500,7.100,1) (18.500,10.520,1) (20.000,7.600,1) (22.000,7.900,1) (19.500,9.010,1) (27.000,7.500,1) (25.000,13.000,1) (22.500,11.750,1) (21.000,7.650,1) (20.000,5.880,1) (22.000,5.580,1) (18.500,5.280,1) (22.000,9.580,1) (22.500,6.620,1) (23.000,10.680,1) (19.500,10.260,1) (24.500,8.660,1) (25.000,8.500,1) (19.000,5.500,1) (19.500,9.900,1) (20.000,9.700,1) (20.500,7.700,1) (23.000,7.300,1) (20.000,10.200,1) (20.000,9.300,1) (24.500,9.200,1) };
+
+    \nextgroupplot[
+			view={0}{90},
+			enlargelimits=0,
+			zmin=0.0, zmax=1.0,
+			xlabel=$E$,
+			%ylabel=K,
 			colorbar,
@@
 			        ylabel={probability density $\times 10^2$},
-			        y label style={at={(axis description cs:6.5,0.5)},rotate=180,anchor=north},
+			        y label style={at={(axis description cs:6.0,0.5)},rotate=180,anchor=north},
 			        yticklabel style={
-			            text width=2.5em,
+			            text width=1.5em,
 			            align=right,
@@
 
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.6000,1.2800,0.276486) (17.9000,1.2800,0.276486) (17.9000,3.4600,0.2765) (10.6000,3.4600,0.2765)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.6000,3.4600,0.808121) (17.9000,3.4600,0.808121) (17.9000,4.8500,0.8081) (10.6000,4.8500,0.8081)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.6000,4.8500,0.795058) (17.9000,4.8500,0.795058) (17.9000,7.4000,0.7951) (10.6000,7.4000,0.7951)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.6000,7.4000,0.047701) (17.9000,7.4000,0.047701) (17.9000,13.0000,0.0477) (10.6000,13.0000,0.0477)};
+    		\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.6000,1.2800,0.355033) (17.9000,1.2800,0.355033) (17.9000,3.4600,0.3550) (10.6000,3.4600,0.3550)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.6000,3.4600,0.740195) (17.9000,3.4600,0.740195) (17.9000,7.5500,0.7402) (10.6000,7.5500,0.7402)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(10.6000,7.5500,0.036446) (17.9000,7.5500,0.036446) (17.9000,13.0000,0.0364) (10.6000,13.0000,0.0364)};
 
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.9000,1.2800,0.972401) (30.0000,1.2800,0.972401) (30.0000,3.4600,0.9724) (17.9000,3.4600,0.9724)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.9000,3.4600,0.784827) (30.0000,3.4600,0.784827) (30.0000,4.8500,0.7848) (17.9000,4.8500,0.7848)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.9000,4.8500,0.531518) (30.0000,4.8500,0.531518) (30.0000,7.4000,0.5315) (17.9000,7.4000,0.5315)};
-			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.9000,7.4000,0.227273) (30.0000,7.4000,0.227273) (30.0000,13.0000,0.2273) (17.9000,13.0000,0.2273)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.9000,1.2800,0.925013) (30.0000,1.2800,0.925013) (30.0000,3.4600,0.9250) (17.9000,3.4600,0.9250)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.9000,3.4600,0.645598) (30.0000,3.4600,0.645598) (30.0000,7.5500,0.6456) (17.9000,7.5500,0.6456)};
+			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.9000,7.5500,0.219122) (30.0000,7.5500,0.219122) (30.0000,13.0000,0.2191) (17.9000,13.0000,0.2191)};
 
@@
 (15.600,5.640,1) (11.200,4.380,1) (18.600,5.680,1) (16.800,7.800,1) (21.000,4.320,1) (15.200,6.750,1) (14.600,5.250,1) (17.600,5.050,1) (14.000,5.200,1) (16.000,7.220,1) (18.000,5.750,1) (16.800,5.000,1) (16.000,5.600,1) (11.400,5.400,1) (12.000,7.500,1) (17.200,7.300,1) (20.000,6.200,1) (20.000,6.600,1) (16.500,8.700,1) (15.200,5.100,1) (16.000,5.650,1) (18.600,4.500,1) (16.600,3.800,1) (17.800,3.930,1) (20.000,3.520,1) (25.000,3.580,1) (16.100,4.800,1) (17.000,3.950,1) (19.400,4.500,1) (16.000,4.700,1) (22.500,5.700,1) (19.100,6.900,1) (17.200,3.840,1) (19.500,5.400,1) (19.000,4.200,1) (20.500,5.100,1) (15.500,4.600,1) (18.000,4.250,1) (15.500,3.700,1) (13.200,5.100,1) (16.200,6.130,1) (18.800,4.280,1) (15.000,5.430,1) (17.500,4.360,1) (17.000,5.040,1) (18.900,5.240,1) (16.000,4.900,1) (16.000,6.100,1) (18.800,6.200,1) (17.400,8.900,1) (12.400,7.200,1) (17.200,5.600,1) (14.000,7.050,1) (17.100,6.300,1) (16.400,5.850,1) (20.500,6.250,1) (16.300,6.380,1) (16.800,6.000,1) (16.700,6.800,1) (10.600,1.950,1) (16.000,3.270,1) (16.800,5.750,1) (18.000,3.800,1) (19.000,4.450,1) (19.000,2.950,1) (18.100,4.600,1) (15.000,5.300,1) (19.600,4.680,1) (17.000,3.170,1) (16.800,2.850,1) (20.400,3.050,1) (25.000,3.380,1) (24.000,3.740,1) (30.000,3.350,1) (21.000,3.210,1) (16.000,3.800,1) (16.000,4.600,1) (18.000,2.650,1) (14.800,3.400,1) (23.000,2.570,1) (19.000,2.500,1) (18.800,3.900,1) (24.000,2.200,1) (22.500,4.800,1) (18.000,3.050,1) (18.000,2.620,1) (22.800,2.450,1) (26.000,2.600,1) (21.600,2.800,1) (23.600,1.740,1) (18.500,2.400,1) (22.000,3.600,1) (20.700,3.050,1) (18.000,2.150,1) (18.000,3.250,1) (19.000,2.600,1) (21.500,2.500,1) (16.000,2.900,1) (18.500,4.500,1) (18.000,2.300,1) (17.500,3.300,1) (18.500,2.450,1) (21.000,2.800,1) (19.500,2.060,1) (20.500,2.940,1) (22.000,2.700,1) (19.000,3.400,1) (22.500,3.300,1) (19.000,2.700,1) (20.000,2.650,1) (19.500,2.900,1) (21.000,2.000,1) (20.000,3.800,1) (21.000,3.080,1) (22.500,2.900,1) (21.500,1.900,1) (20.800,1.950,1) (22.500,2.060,1) (16.000,3.400,1) (19.000,1.280,1) (20.000,3.250,1) (28.500,6.000,1) (26.500,2.080,1) (21.500,2.600,1) (21.000,2.800,1) (21.000,2.760,1) (21.500,3.940,1) (28.500,3.000,1) (24.500,2.120,1) (22.000,2.600,1) (18.000,4.100,1) (20.000,5.400,1) (24.000,5.700,1) (21.500,5.000,1) (17.500,5.450,1) (18.500,7.100,1) (21.000,3.850,1) (25.000,5.000,1) (19.500,5.700,1) (24.000,4.920,1) (21.000,4.600,1) (20.000,5.600,1) (23.500,4.350,1) (20.000,4.400,1) (18.500,8.210,1) (21.000,4.000,1) (20.000,4.900,1) (21.500,7.650,1) (21.500,8.420,1) (21.500,9.400,1) (24.000,8.600,1) (22.000,10.800,1) (25.500,7.100,1) (18.500,10.520,1) (20.000,7.600,1) (22.000,7.900,1) (19.500,9.010,1) (27.000,7.500,1) (25.000,13.000,1) (22.500,11.750,1) (21.000,7.650,1) (20.000,5.880,1) (22.000,5.580,1) (18.500,5.280,1) (22.000,9.580,1) (22.500,6.620,1) (23.000,10.680,1) (19.500,10.260,1) (24.500,8.660,1) (25.000,8.500,1) (19.000,5.500,1) (19.500,9.900,1) (20.000,9.700,1) (20.500,7.700,1) (23.000,7.300,1) (20.000,10.200,1) (20.000,9.300,1) (24.500,9.200,1) };
-		\end{axis}
+  \end{groupplot}
 \end{tikzpicture}

### 2015-12-01 BN_discretizer_paper.tex
updated bib
Change plot name
minor

@@
 \usepackage{lscape}
-\usepackage{caption}
+% \usepackage{caption}
 \usepackage{siunitx}
 \usepackage{booktabs}
-\usepackage{boondox-cal} % for lowercase caligraphic
+\usepackage{BOONDOX-cal} % for lowercase caligraphic
 \usepackage[font=small,skip=5pt]{caption}
@@
 %
+
+\pgfplotsset{compat=1.11}
 \pgfplotsset{
@@
 
-Equation~\ref{eqn:MDL} can be minimized exactly using dynamic programming.
+The global minimum of Equation~\ref{eqn:MDL} can be found using using dynamic programming.
 For a given Bayesian network, the first three terms only depend on the number of discretization intervals $|X|$ and the fourth term is cumulative over the intervals.
@@
     The discretization policies for the Auto MPG dataset with the fixed structure shown in Figure~\ref{fig:auto_graph_3}.
-    The first five rows list the discretization edges for each continuous variable.
-    The last row shows the mean cross-validated log-likelihood under each policy.
+    % The first five rows list the discretization edges for each continuous variable.
+    % The last row shows the mean cross-validated log-likelihood under each policy.
     The methods have the same discretization for variable $A$, and the log-likelihood for the Bayesian method is only slightly better than that for the MDL method.

### 2015-12-02 BN_discretizer_paper.tex
A partial update according to Mykel's comments

@@
 \usepackage{tikz}
+\usetikzlibrary{arrows.meta}
 \usepgfplotslibrary{groupplots}
@@
 In addition, this paper shows how to incorporate existing methods into the structure learning process to discretize all continuous variables and simultaneously learn Bayesian network structures.
-The proposed method was incorporated and its performance was empirically demonstrated.
+%The proposed method was incorporated and its performance was empirically demonstrated.
 
@@
 The first is to model the conditional probability density of each continuous variable using specific families of parametric distributions, and then to redesign Bayesian network learning and inference algorithms based on the parameterizations.
-One successful example of parametric continuous distributions in Bayesian networks is the Gaussian graphical model \citep{Weiss_2011}.
+One example of parametric continuous distributions in Bayesian networks is the Gaussian graphical model \citep{Weiss_2011}.
 %For other parametric distributions and non-linear functions \citep{Ihler_2009}, however, these redesigned algorithms can be computationally expensive.
@@
 This is caused by MDL's use of mutual information to measure the quality of discretization edges.
-Mutual information, which is composed of empirical probabilities computed using event count ratios, varies less severely with the positions of discretization edges than the method we suggest in this article.
+Mutual information, which is composed of empirical probabilities computed using event count ratios, varies less significantly with the positions of discretization edges than the method we suggest in this article.
 
@@
 The MODL method uses dynamic programming to find the optimal discretization policy for a continuous variable given a discrete class variable, and has an $\bigo\paren{n^3 + r \cdot n^2}$ runtime, where $r$ is the number of class variable instantiations.
-\cite{Lustgarten_2011} suggest several formulations for the prior term $P(\textit{Model})$, and the asymptotic equivalence between MDL and MODL on the single-variable, single-class problem was examined by \citet{VL_2000}.
+\cite{Lustgarten_2011} suggest several formulations for the prior over models.
+The asymptotic equivalence between MDL and MODL on the single-variable, single-class problem was examined by \citet{VL_2000}.
 
@@
   \centering
-  \input{graph1}
-  \caption{Factorization of $P(_{-\cX} \mid \Lambda)$}
+  \input{Fig1}
+  \caption{Factorization of $P(_{-\cX} \mid \Lambda)$.}
   \label{fig:example_factorization}
@@
  \centering
-     \input{graph2_right}
-  \caption{An example network}
+     \input{Fig2}
+  \caption{An example network.}
    \label{fig:example_networks}
@@
 
-The global minimum of Equation~\ref{eqn:MDL} can be found using using dynamic programming.
+The global minimum of Equation~\ref{eqn:MDL} can be found using dynamic programming.
 For a given Bayesian network, the first three terms only depend on the number of discretization intervals $|X|$ and the fourth term is cumulative over the intervals.
@@
   \centering
-   \input{graph_autocar_1}
+   \input{Fig3}
    \caption{Bayesian network structure obtained from running K2 on the prediscretized Auto MPG dataset.}
@@
   }
-  \input{table_autoMPG_1.tex}
+  \input{Table1.tex}
   \label{table:auto_disc_table_1}
@@
   \centering
-  \input{graph_auto_exp1_distr_1_3}
+  \input{Fig4}
   \caption{
@@
   \centering
-  \input{graph_autocar_2}
+  \input{Fig5}
   \caption{The discrete-valued Bayesian network learned from the Auto MPG dataset using the Bayesian method.}
@@
   \centering
-  \input{graph_auto_exp2_distr_1_3}
+  \input{Fig6}
   \caption{
@@
 Some discretization edges appear in all three discretization methods, such as \num{1.42} and \num{2.35} for variable $C$ and \num{0.785} for variable $L$.
-This indicates that MDL indeed can find some important discretization edges, but it is not sensitive enough to find more edges.
+This indicates sufficiently MDL indeed can find some important discretization edges, but it is not sensitive to find more edges.
 
@@
   \centering
-  \scalebox{0.8}{\input{graph_wine_1}}
-  \caption{Bayesian network structure obtained from running K2 on the prediscretized Wine dataset}
+  \scalebox{0.8}{\input{Fig7}}
+  \caption{Bayesian network structure obtained from running K2 on the prediscretized Wine dataset.}
   \label{fig:wine_graph_1}
@@
   \scalebox{1.0}{
-  \input{table_wine_1.tex}
+  \input{Table2.tex}
   }
@@
   \centering
-  \input{graph_wine_exp1_distr}
-  \caption{Comparison of the discretization policies for variables $A$ and $C$ obtained using the Bayesian and MDL methods}
+  \input{Fig8}
+  \caption{Comparison of the discretization policies for variables $A$ and $C$ obtained using the Bayesian and MDL methods.}
   \label{fig:wine_exp1_distr}
@@
   \centering
-  \scalebox{0.7}{\input{graph_wine_2}}
+  \scalebox{0.7}{\input{Fig9}}
   \caption{The discrete-valued Bayesian network learned from the Wine dataset using the Bayesian method.}
@@
   \centering
-  \input{graph_wine_exp2_distr_5_11}
+  \input{Fig10}
   \caption{
@@
   \centering
-  \scalebox{0.8}{\input{graph_housing_1}}
-  \caption{Bayesian network structure obtained from running K2 on the prediscretized Housing dataset}
+  \scalebox{0.8}{\input{Fig11}}
+  \caption{Bayesian network structure obtained from running K2 on the prediscretized Housing dataset.}
   \label{fig:housing_graph_1}
@@
   }
-  \input{table_housing_1.tex}
+  \input{Table3.tex}
   \label{table:housing_disc_table_1}
@@
   \centering
-  \input{graph_housing_exp1_distr_3_5}
+  \input{Fig12}
   \caption{
@@
     The scatter points were jittered to reveal the repeated values in the dataset.
-    The repeated values lead to a high number of discretization edges, because repeated values can easily form discretized regions on their own.
+    The repeated values lead to many discretization edges because repeated values can easily form \todo{discretized regions on their own.}
   }
@@
   \centering
-  \input{graph_housing_exp1_distr_8_5}
+  \input{Fig13}
   \caption{
     The discretization policies for variables $H$ and $E$ learned using the optimal Bayesian approach on the fixed network shown in Figure~\ref{fig:housing_graph_1}.
-    The values for variable $H$ are less frequently repeated, thus producing fewer discretization intervals than $E$.
+    The values for variable $H$ are not as repeated, thus producing fewer discretization intervals than $E$.
   }
@@
   \centering
-  \scalebox{0.8}{\input{graph_housing_2}}
+  \scalebox{0.8}{\input{Fig14}}
   \caption{
@@
   \centering
-  \input{graph_housing_exp2_distr_3_5}
+  \input{Fig15}
   \caption{
     The discretization policy for variables $C$ and $E$ on the learned network in Figure~\ref{fig:housing_graph_2}.
-    The high number of discretization edges are caused by repeated values in $C$ and $E$.
-    Note that the two regions at $(C,E) = (3.9,0.65)$ and $(6.8,0.44)$ are color-saturated due to the high concentration of repeated values.
+    The large number of discretization edges are due to repeated values in $C$ and $E$.
+    The two regions at $(C,E) = (3.9,0.65)$ and $(6.8,0.44)$ are color-saturated due to the high concentration of repeated values.
   }
@@
   \centering
-  \input{graph_housing_exp2_distr_8_5}
+  \input{Fig16}
   \caption{
     The discretization policy for variables $H$ and $E$ on the learned network in Figure~\ref{fig:housing_graph_2}.
-    The number of discretization intervals for $H$ is less than it was for the fixed network structure in Figure~\ref{fig:housing_exp1_distr_8_5}, but the discretization policy still matches the raw data.
+    There are fewer discretization intervals for $H$ than for the fixed network structure in Figure~\ref{fig:housing_exp1_distr_8_5}, but the discretization result still closely models the raw data.
   }
@@
   \centering
-  \input{graph_exp_discuss}
+  \input{Fig17}
   \caption{A simple Bayesian network used to demonstrate the sensitivity of each method}
@@
 To qualitatively assess the sensitivity of each method to the number and position of discretization intervals, consider the Bayesian network in Figure~\ref{fig:exp_discuss}, where $\cX$ is continuous and $P_1$ and $P_2$ are discrete.
-If $\Pa_{\cX} = \curly{P_1, P_2}$ and $D_{\cX} = \curly{1.0,2.0,3.0, \ldots n}$, then the corresponding objective functions for the discretization methods are:
+If $\Pa_{\cX} = \curly{P_1, P_2}$ and $D_{\cX} = \curly{1,2,3, \ldots n}$, then the corresponding objective functions for the discretization methods are:
 
@@
 The value of the edge position term for MDL is primarily determined by the mutual information, which varies less severely than the corresponding terms in the Bayesian method.
-The MDL term uses empirical probability distributions, based off of ratios of counts, whereas the Bayesian method uses factorial terms, and thus the MDL method varies less.
+The MDL term uses empirical probability distributions based off of ratios of counts, whereas the Bayesian method uses factorial terms, and thus the MDL method varies less.
 The MDL method is therefore less sensitive to the discretization edges.
@@
 The proposed method was incorporated and its superior performance was empirically demonstrated.
-All software is publically available to support discretization research, and can be found at \url{github.com/sisl/LearnDiscreteBayesNets.jl}.
+All software is publicly available at \url{github.com/sisl/LearnDiscreteBayesNets.jl}.
 
@@
 The Bayesian network in Figure~\ref{fig:auto_graph_3} was obtained by running Algorithm~\ref{alg:structure_learn} fifty times on the Auto MPG dataset with a maximum of two parents per variable.
-The network is more well-structured than the one in Figure~\ref{fig:auto_graph_1} because the discretization policies were simultaneously learned with the network structure.
-Many edges appear in both discretization results, and are bolded in Table~\ref{table:auto_disc_table_3}.
+The network is better-structured than the one in Figure~\ref{fig:auto_graph_1} because the discretization policies were simultaneously learned with the network structure.
+Many edges appear in both discretization results and are bolded in Table~\ref{table:auto_disc_table_3}.
 
@@
   \centering
-  \scalebox{0.8}{\input{graph_autocar_3}}
+  \scalebox{0.8}{\input{Fig18}}
   \caption{A Bayesian network structure for the Auto MPG dataset that leads to comparable discretization policies for the MDL and Bayesian methods.}
@@
   }
-\input{table_autoMPG_3.tex}
+\input{Table4.tex}
   \label{table:auto_disc_table_3}

### 2015-12-02 Fig10.tex
A partial update according to Mykel's comments

--- 2015-11-24 graph_wine_exp2_distr_5_11.tex
@@
 			colorbar style={
-			        ytick={0,0.5,...,2.6},
+			        ytick={0,0.5,...,2.51},
 			        ylabel={probability density $\times 10^2$},
-			        y label style={at={(axis description cs:6.5,0.5)},rotate=180,anchor=north},
+			        y label style={at={(axis description cs:4.5,0.5)},rotate=180,anchor=north},
 			        yticklabel style={

### 2015-12-02 Fig12.tex
A partial update according to Mykel's comments

--- 2015-11-22 graph_housing_exp1_distr_3_5.tex
@@
 			zmin=0.0, zmax=1.0,
-			xlabel=C,
-			ylabel=E,
+			xlabel=$C$,
+			ylabel=$E$,
 			colorbar,
-			point meta min=0, point meta max=1.2,
+			point meta min=0, point meta max=1.0,
 			colormap={}{ gray(0cm)=(1); gray(1cm)=(0);},
 			colorbar style={
-			        ytick={0,0.3,...,1.3},
+			        ytick={0,0.2,...,1.01},
 			        ylabel={probability density$ \times 10^{-1}$},
-			        y label style={at={(axis description cs:6.5,0.5)},rotate=180,anchor=north},
+			        y label style={at={(axis description cs:4.5,0.5)},rotate=180,anchor=north},
+			        yticklabels={\num{0.00},\num{0.20},\num{0.40},\num{0.60},\num{0.80},$\geq 1$},
 			        yticklabel style={

### 2015-12-02 Fig13.tex
A partial update according to Mykel's comments

--- 2015-11-22 graph_housing_exp1_distr_8_5.tex
@@
 			        ylabel={probability density$ \times 10^{-1}$},
-			        y label style={at={(axis description cs:6.5,0.5)},rotate=180,anchor=north},
+			        y label style={at={(axis description cs:4.5,0.5)},rotate=180,anchor=north},
 			        yticklabel style={

### 2015-12-02 Fig15.tex
A partial update according to Mykel's comments

--- 2015-11-25 graph_housing_exp2_distr_3_5.tex
@@
 			        ylabel={probability density$ \times 10^{-1}$},
-			        y label style={at={(axis description cs:6.5,0.5)},rotate=180,anchor=north},
+			        y label style={at={(axis description cs:4.5,0.5)},rotate=180,anchor=north},
 			        yticklabels={\num{0.00},\num{0.20},\num{0.40},\num{0.60},\num{0.80},$\geq 1$},

### 2015-12-02 Fig4.tex
A partial update according to Mykel's comments

--- 2015-11-27 graph_auto_exp1_distr_1_3.tex
@@
 			colorbar style={
-			        ytick={0,0.24,...,1.3},
+			        ytick={0,0.3,...,1.21},
 			        ylabel={probability density $\times 10^3$},
-			        y label style={at={(axis description cs:6.5,0.5)},rotate=180,anchor=north},
+			        y label style={at={(axis description cs:4.5,0.5)},rotate=180,anchor=north},
 			        yticklabel style={

### 2015-12-02 Fig8.tex
A partial update according to Mykel's comments

@@
 			colorbar style={
-			        ytick={0,0.5,...,2.6},
+			        ytick={0,0.5,...,2.51},
 			        ylabel={probability density $\times 10^2$},
-			        y label style={at={(axis description cs:6.0,0.5)},rotate=180,anchor=north},
+			        y label style={at={(axis description cs:3.7,0.5)},rotate=180,anchor=north},
 			        yticklabel style={

### 2015-12-02 auto_MPG/tikz_gridmap.jl
remove some old files

@@ -1,103 +1,0 @@
-using DataFrames
-using Discretizers
-
-const OUTPUT_FILE = "output.tex"
-
-raw = readtable("autoMPG_raw.dat", header=false)
-our1 = readtable("autoMPG_exp1_ourmethod.dat", header=false)
-our2 = readtable("autoMPG_exp2_ourmethod.dat", header=false)
-MDL1 = readtable("autoMPG_exp1_MDLmethod.dat", header=false)
-
-disc_our1 = Dict{Int, LinearDiscretizer}()
-disc_our1[1] = LinearDiscretizer([9.0,15.25,17.65,20.9,25.65,28.9,46.6])
-disc_our1[3] = LinearDiscretizer([68.0,70.5,93.5,109.0,159.5,259.0,284.5,455.0])
-disc_our1[4] = LinearDiscretizer([46.0,71.5,99.0,127.0,230.0])
-disc_our1[5] = LinearDiscretizer([1613.0,2115.0,2480.5,2959.5,3657.5,5140.0])
-disc_our1[6] = LinearDiscretizer([8.0,12.35,13.75,16.05,22.85,24.8])
-
-
-function export_plot(
-	io::IO,
-	var_x::Int, # variable for x axis
-	var_y::Int, # variable for y axis
-	disc::Dict{Int, LinearDiscretizer}, # set of linear discretizers
-	pdf_pts::DataFrame, # points used to compute heatmap pdf
-	scatter_pts::DataFrame; # points we will scatter on top
-	colorbar_max::Float64=0.25
-	)
-
-
-	disc_x = disc[var_x]
-	disc_y = disc[var_y]
-
-	nbins_x = nlabels(disc_x)
-	nbins_y = nlabels(disc_y)
-	counts = zeros(Float64, nbins_x, nbins_y)
-	for i in 1 : nrow(pdf_pts)
-		x = encode(disc_x, pdf_pts[i, var_x])
-		y = encode(disc_y, pdf_pts[i, var_y])
-		counts[x,y] += 1
-	end
-	counts ./= sum(counts)
-
-	varnamex = string('A' - 1 + var_x)
-	varnamey = string('A' - 1 + var_y)
-
-	println(io, "\\documentclass[crop,tikz]{standalone}\n")
-	println(io, "\\usepackage{pgfplots}")
-	println(io, "\\pgfplotsset{compat=1.12}")
-	println(io, "\\begin{document}")
[…]

### 2015-12-02 BN_discretizer_paper.tex
misc

@@
     The scatter points were jittered to reveal the repeated values in the dataset.
-    The repeated values lead to many discretization edges because repeated values can easily form \todo{discretized regions on their own.}
+    Values perfectly repeated in $C$ and $E$ lead to high correlation and concentrated densities in the marginal distribution.
+    % The repeated values lead to many discretization edges because repeated values can easily form \todo{discretized regions on their own.}
   }
@@
 The proposed method was incorporated and its superior performance was empirically demonstrated.
+Future work will investigate edge positions at locations other than the midpoints between samples and will extend the approach to cluster categorical variables with very many levels.
 All software is publicly available at \url{github.com/sisl/LearnDiscreteBayesNets.jl}.
 
-The methods developed in this paper increase the accuracy of Bayesian networks learned on datasets with continuous and mixed variables.
-An automated process for simultaneously constructing Bayesian networks and discretization policies is appealing because of the potential to significantly reduce development time and cost when developing models for uncertainty and causality.
-Future work will investigate edge positions at locations other than the midpoints between samples and using different discretization policies for the same variable in different conditional probablity distributions.
+% The methods developed in this paper increase the accuracy of Bayesian networks learned on datasets with continuous and mixed variables.
+% An automated process for simultaneously constructing Bayesian networks and discretization policies is appealing because of the potential to significantly reduce development time and cost when developing models for uncertainty and causality.
 

### 2015-12-02 BN_discretizer_paper.tex
Add IRIS experiment and Modify BN graphs

@@
 The reason why MDL produces fewer discretization edges is discussed in Section~\ref{subsec:discuss_exp}.
-An example of a network structure where MDL produces a comparable result to the Bayesian method is given in the Appendix.
+Two examples of Bayesian networks where MDL produces comparable results to the Bayesian method are given in the Appendix.
 
@@
 
+Two examples of Bayesian networks where MDL produces comparable results to the Bayesian method are given in this section.
+The first example is on the Auto MPG dataset.
+Instead of testing on the network obtained by prediscretization and structure learning, the tested network is obtained by Algorithm \ref{alg:structure_learn}, which can be considered better-structured than the network in Figure \ref{fig:auto_graph_1}.
+The second example is on the IRIS dataset \citep{Lichman_2013}.
+In the work of \cite{Friedman_1996}, the IRIS dataset was tested on the navie Bayes and the prediction accuracy was shown.
+The same test is reproduced to compare the Bayesian method with the MDL discretization method.
+
+\subsection{Example 1}
 The Bayesian network structure in Figure~\ref{fig:auto_graph_3} and the discretization results in Table~\ref{table:auto_disc_table_3} demonstrate that the MDL method does not always produce fewer discretization intervals than the Bayesian approach and that the MDL method can produce discretization policies with comparable likelihood.
@@
 \end{table}
+
+\subsection{Example 2}
+The Iris dataset contains variables related to the morphologic variation of three Iris flower species.
+The dataset has \num{150} samples over five variables.
+Only variables $E$ is discrete-valued, which corresponds to the three species.
+The following experiment was conducted on the naive Bayes: variable $E$ is the parent of variable $A$, $B$, $C$, and $D$.
+Table \ref{table:iris_table_1} shows the discretization edges and the prediction accuracy of the learned classifiers using 10-fold cross validation.
+The MDL discretization method and the Bayesian method have same discretization result: all discretization edges coincide.
+In addition, both methods have $94 \% $ accuarcy, which matches the number in \cite{Friedman_1996}.
+
+\begin{table}[ht]
+  \centering
+  \caption{
+    The discretization policies for the Iris dataset with the naive Bayes structure. 
+    Two methods produce same discretization policy on each continuous variable and have same prediction accuracy.
+  }
+\input{Table5.tex}
+  \label{table:iris_table_1}
+\end{table}
 \end{document}

### 2015-12-02 BN_discretizer_paper.tex
Add loglikihood to IRIS

@@
 The following experiment was conducted on the naive Bayes: variable $E$ is the parent of variable $A$, $B$, $C$, and $D$.
-Table \ref{table:iris_table_1} shows the discretization edges and the prediction accuracy of the learned classifiers using 10-fold cross validation.
+Table \ref{table:iris_table_1} shows the discretization edges, the prediction accuracy of the learned classifiers, and the mean log-likelihood.
+The latter two use 10-fold cross validation.
 The MDL discretization method and the Bayesian method have same discretization result: all discretization edges coincide.
 In addition, both methods have $94 \% $ accuarcy, which matches the number in \cite{Friedman_1996}.
+The log-likelihood for the Bayesian method is only slightly better than the MDL method.
 

### 2015-12-02 BN_discretizer_paper.tex
Add suboptimal cite

@@
 Algorithm~\ref{alg:disc_one} is guaranteed to be optimal.
-For faster methods with suboptimal results, see \citet{Boulle_2006}.
+For faster methods with suboptimal results, see \citet{Friedman_1996} and \citet{Boulle_2006}.
 
@@
     The discretization policies for the Iris dataset with the naive Bayes structure. 
-    Two methods produce same discretization policy on each continuous variable and have same prediction accuracy.
+    Two methods produce same discretization policy on each continuous variable and have close 10-fold prediction accuracy and log-likelihood.
   }

### 2015-12-02 BN_discretizer_paper.tex
misc

--- 2015-12-02 BN_discretizer_paper.tex
@@
 The reason why MDL produces fewer discretization edges is discussed in Section~\ref{subsec:discuss_exp}.
-Two examples of Bayesian networks where MDL produces comparable results to the Bayesian method are given in the Appendix.
+Two examples of MDL producing comparble results to the Bayesian method are given in the Appendix.
 
@@
 
-Two examples of Bayesian networks where MDL produces comparable results to the Bayesian method are given in this section.
-The first example is on the Auto MPG dataset.
-Instead of testing on the network obtained by prediscretization and structure learning, the tested network is obtained by Algorithm \ref{alg:structure_learn}, which can be considered better-structured than the network in Figure \ref{fig:auto_graph_1}.
-The second example is on the IRIS dataset \citep{Lichman_2013}.
-In the work of \cite{Friedman_1996}, the IRIS dataset was tested on the navie Bayes and the prediction accuracy was shown.
-The same test is reproduced to compare the Bayesian method with the MDL discretization method.
-
-\subsection{Example 1}
 The Bayesian network structure in Figure~\ref{fig:auto_graph_3} and the discretization results in Table~\ref{table:auto_disc_table_3} demonstrate that the MDL method does not always produce fewer discretization intervals than the Bayesian approach and that the MDL method can produce discretization policies with comparable likelihood.
 The Bayesian network in Figure~\ref{fig:auto_graph_3} was obtained by running Algorithm~\ref{alg:structure_learn} fifty times on the Auto MPG dataset with a maximum of two parents per variable.
-The network is better-structured than the one in Figure~\ref{fig:auto_graph_1} because the discretization policies were simultaneously learned with the network structure.
+The network is structured more favorably with regards to discretization than the network in Figure~\ref{fig:auto_graph_1}, as the discretization policies were simultaneously learned with the network structure, resulting in higher data likelihood.
 Many edges appear in both discretization results and are bolded in Table~\ref{table:auto_disc_table_3}.
@@
 \end{table}
-
-\subsection{Example 2}
-The Iris dataset contains variables related to the morphologic variation of three Iris flower species.
-The dataset has \num{150} samples over five variables.
-Only variables $E$ is discrete-valued, which corresponds to the three species.
-The following experiment was conducted on the naive Bayes: variable $E$ is the parent of variable $A$, $B$, $C$, and $D$.
-Table \ref{table:iris_table_1} shows the discretization edges and the prediction accuracy of the learned classifiers using 10-fold cross validation.
-The MDL discretization method and the Bayesian method have same discretization result: all discretization edges coincide.
-In addition, both methods have $94 \% $ accuarcy, which matches the number in \cite{Friedman_1996}.
-
-\begin{table}[ht]
-  \centering
-  \caption{
-    The discretization policies for the Iris dataset with the naive Bayes structure. 
-    Two methods produce same discretization policy on each continuous variable and have same prediction accuracy.
-  }
-\input{Table5.tex}
-  \label{table:iris_table_1}
-\end{table}
 \end{document}

### 2015-12-02 BN_discretizer_paper.tex

--- 2015-12-02 BN_discretizer_paper.tex
@@
 The Bayesian network in Figure~\ref{fig:auto_graph_3} was obtained by running Algorithm~\ref{alg:structure_learn} fifty times on the Auto MPG dataset with a maximum of two parents per variable.
-The network is better-structured than the one in Figure~\ref{fig:auto_graph_1} because the discretization policies were simultaneously learned with the network structure.
+The network is structured more favorably with regards to discretization than the network in Figure~\ref{fig:auto_graph_1}, as the discretization policies were simultaneously learned with the network structure, resulting in higher data likelihood.
 Many edges appear in both discretization results and are bolded in Table~\ref{table:auto_disc_table_3}.

### 2015-12-02 BN_discretizer_paper.tex
minor

@@
 Instead of testing on the network obtained by prediscretization and structure learning, the tested network is obtained by Algorithm \ref{alg:structure_learn}, which can be considered better-structured than the network in Figure \ref{fig:auto_graph_1}.
-The second example is on the IRIS dataset \citep{Lichman_2013}.
-In the work of \cite{Friedman_1996}, the IRIS dataset was tested on the navie Bayes and the prediction accuracy was shown.
-The same test is reproduced to compare the Bayesian method with the MDL discretization method.
+The second example is on the Iris dataset \citep{Lichman_2013}.
+In the work of \cite{Friedman_1996}, the Iris dataset was tested on the naive Bayes network structure and the prediction accuracy was shown.
+The same test is reproduced below to compare the Bayesian method to the MDL discretization method.
 
@@
 The dataset has \num{150} samples over five variables.
-Only variables $E$ is discrete-valued, which corresponds to the three species.
-The following experiment was conducted on the naive Bayes: variable $E$ is the parent of variable $A$, $B$, $C$, and $D$.
+Only variables $E$ is discrete-valued, and corresponds to the species category.
+The following experiment was conducted on the naive Bayes structure: variable $E$ is the parent of variable $A$, $B$, $C$, and $D$.
 Table \ref{table:iris_table_1} shows the discretization edges, the prediction accuracy of the learned classifiers, and the mean log-likelihood.
-The latter two use 10-fold cross validation.
+The discretization policy shown is for running the algorithms on the full dataset; the likelihood and prediction accuracies were found with 10-fold cross validation.
 The MDL discretization method and the Bayesian method have same discretization result: all discretization edges coincide.
-In addition, both methods have $94 \% $ accuarcy, which matches the number in \cite{Friedman_1996}.
-The log-likelihood for the Bayesian method is only slightly better than the MDL method.
+In addition, both methods have $94 \%$ accuarcy, which matches the number in \cite{Friedman_1996}.
+The Bayesian method likelihood is slightly higher across folds than the MDL method likelihood.
 
@@
     The discretization policies for the Iris dataset with the naive Bayes structure.
-    Two methods produce same discretization policy on each continuous variable and have close 10-fold prediction accuracy and log-likelihood.
+    The two methods produce the same discretization policy on each continuous variable and have close 10-fold prediction accuracy and log-likelihood.
   }

### 2015-12-03 BN_discretizer_paper.tex
incorporated Mykel's comments

@@
 The discretization process for a single variable requires that all other variables be discrete.
-The iterative approach uses a prediscretization policy in order to initialize the process.
-In this paper, prediscretization assigns $k$ equal-width intervals to each continuous variable, where $k$ is the largest number of intervals of initially discrete variables in the network.
-
-After prediscretization, the one-variable discretization method is iteratively applied over each continuous variable in reverse topoligical order, from the leaves to the root.
-Reverse topological order has the advantage of relying on fewer prediscretizations of the continuous variables during the first pass.
+The iterative approach uses an initial discretization policy in order to start the process which assigns $k$ equal-width intervals to each continuous variable, where $k$ is the largest number of intervals of initially discrete variables in the network.
+
+After the initial discretization, the one-variable discretization method is iteratively applied over each continuous variable in reverse topoligical order, from the leaves to the root.
+Reverse topological order has the advantage of relying on fewer initial discretizations of the continuous variables during the first pass.
 For example, in the network of Figure~\ref{fig:example_networks}, if $S_2$ is the only discrete variable, then the discretization of $P_1$ involves both $P_2$ and $X$, whereas the discretization of $C_1$ only involves $X$.
@@
 The proposed algorithm alternates between K2 structure learning and discretization.
-The dataset is prediscretized as was described in Section~\ref{sec:multi_var}, and K2 is run to obtain an initial network structure.
+The dataset is initially discretized as was described in Section~\ref{sec:multi_var}, and K2 is run to obtain an initial network structure.
 The affected continuous variables are rediscretized every time an edge is added by K2.
@@
 The Bayesian and MDL discretization methods were tested on the Auto MPG data using the network shown in Figure~\ref{fig:auto_graph_1}.
-This structure was obtained by prediscretizing each continuous variable into five uniform-width intervals, where five is the median cardinality of the discrete variables, and then taking the structure with highest likelihood from \num{1000} runs of K2.
+This structure was obtained by initially discretizing each continuous variable into five uniform-width intervals, where five is the median cardinality of the discrete variables, and then taking the structure with highest likelihood from \num{1000} runs of K2.
 
@@
    \input{Fig3}
-   \caption{Bayesian network structure obtained from running K2 on the prediscretized Auto MPG dataset.}
+   \caption{Bayesian network structure obtained from running K2 on the initially uniformly discretized Auto MPG dataset.}
   \label{fig:auto_graph_1}
@@
 The Bayesian and MDL discretization methods were tested on the Wine data using the network shown in Figure~\ref{fig:wine_graph_1}.
-This structure was obtained by prediscretizing each continuous variable into three uniform-width intervals, where three is the median cardinality of the discrete variables, and then taking the structure with highest likelihood from \num{1000} runs of K2.
+This structure was obtained by initially discretizing each continuous variable into three uniform-width intervals, where three is the median cardinality of the discrete variables, and then taking the structure with highest likelihood from \num{1000} runs of K2.
 
@@
   \scalebox{0.8}{\input{Fig7}}
-  \caption{Bayesian network structure obtained from running K2 on the prediscretized Wine dataset.}
+  \caption{Bayesian network structure obtained from running K2 on the initially uniformly discretized Wine dataset.}
   \label{fig:wine_graph_1}
@@
 Figure~\ref{fig:wine_graph_2} is the discrete-valued Bayesian network learned from the Wine dataset, obtained by running Algorithm~\ref{alg:structure_learn} fifty times.
-A comparison of Figures~\ref{fig:wine_graph_2} and \ref{fig:wine_graph_1} show that the Bayesian network learned during the discretization process has more edges than the network learned on the prediscretized data.
+A comparison of Figures~\ref{fig:wine_graph_2} and \ref{fig:wine_graph_1} show that the Bayesian network learned during the discretization process has more edges than the network learned on the initially discretized data.
 When a network is learned along with discretization, the algorithm has more freedom to adjust the structure and the discretization policy simultaneously to identify useful correlations and produce a denser structure.
@@
 
-The Bayesian network structure in Figure~\ref{fig:housing_graph_1} was obtained by prediscretizing each continuous variable into five uniform-width intervals and then running the K2 algorithm \num{1000} times and choosing the network with the highest likelihood.
+The Bayesian network structure in Figure~\ref{fig:housing_graph_1} was obtained by initially discretizing each continuous variable into five uniform-width intervals and then running the K2 algorithm \num{1000} times and choosing the network with the highest likelihood.
 Table~\ref{table:housing_disc_table_1} shows the numbers of interval after discretization for each continuous variable and the log-likelihood of the dataset based on each discretization method.
@@
   \scalebox{0.8}{\input{Fig11}}
-  \caption{Bayesian network structure obtained from running K2 on the prediscretized Housing dataset.}
+  \caption{Bayesian network structure obtained from running K2 on the initially uniformly discretized Housing dataset.}
   \label{fig:housing_graph_1}
@@
 
-Two examples of Bayesian networks where MDL produces comparable results to the Bayesian method are given in this section.
-The first example is on the Auto MPG dataset.
-Instead of testing on the network obtained by prediscretization and structure learning, the tested network is obtained by Algorithm \ref{alg:structure_learn}, which can be considered better-structured than the network in Figure \ref{fig:auto_graph_1}.
+This section gives two examples of Bayesian networks where MDL produces comparable results to the Bayesian method.
+The first example used the Auto MPG dataset.
+Instead of testing on the network obtained using initially uniform discretization and structure learning, the tested network is obtained by Algorithm \ref{alg:structure_learn}, which can be considered better-structured than the network in Figure \ref{fig:auto_graph_1}.
 The second example is on the Iris dataset \citep{Lichman_2013}.
@@
 
-\subsection{Example 1}
+\subsection{Auto MPG with Comparable MDL Performance}
 The Bayesian network structure in Figure~\ref{fig:auto_graph_3} and the discretization results in Table~\ref{table:auto_disc_table_3} demonstrate that the MDL method does not always produce fewer discretization intervals than the Bayesian approach and that the MDL method can produce discretization policies with comparable likelihood.
@@
 
-\subsection{Example 2}
+\subsection{Reproducing MDL Results from the Literature}
+
 The Iris dataset contains variables related to the morphologic variation of three Iris flower species.

### 2015-12-03 BN_discretizer_paper.tex
Fix inconsistency

@@
         }{
-          {n^{({P})}_{i,1}}! \; {n^{({P})}_{i,2}}! \; \cdots \; {n^{({P})}_{i,J_\text{P}}}!
+          {n^{(\text{P})}_{i,1}}! \; {n^{(\text{P})}_{i,2}}! \; \cdots \; {n^{(\text{P})}_{i,J_\text{P}}}!
         }
@@
   \begin{aligned}
-  h(u,v) &=  \ln {{\gamma_{q} + J_\text{P} - 1}\choose{J_\text{P}-1}} + \ln \left( { {{\gamma_q}!}\over{ {n^{(p)}_{q,1} !} {n^{(p)}_{q,2} !} \cdots {n^{(p)}_{q,J_p} !}} } \right) \\
+  h(u,v) &=  \ln {{\gamma_{q} + J_\text{P} - 1}\choose{J_\text{P}-1}} + \ln \left( { {{\gamma_q}!}\over{ {n^{(\text{P})}_{q,1} !} {n^{(\text{P})}_{q,2} !} \cdots {n^{(\text{P})}_{q,J_p} !}} } \right) \\
   & + \sum_{j=1}^{n_c} \sum_{\ell=1}^{J^{(j)}_{\bm{S}}} \brock{
@@
 
-\subsection{Auto MPG Dataset}
+\subsection{Dataset 1: Auto MPG}
 \label{subsec:auto}
@@
 
-\subsubsection{Discretization with fixed Structure}
+\subsubsection{Discretization with Fixed Structure}
 \label{subsubsec:auto_exp1}
@@
 The reason why MDL produces fewer discretization edges is discussed in Section~\ref{subsec:discuss_exp}.
-Two examples of MDL producing comparble results to the Bayesian method are given in the Appendix.
+Two examples that MDL produces comparble results to the Bayesian method are given in the Appendix.
 
@@
   \centering
-  \input{Fig5}
+  \scalebox{0.9}{
+  \input{Fig5}}
   \caption{The discrete-valued Bayesian network learned from the Auto MPG dataset using the Bayesian method.}
@@
 
-\subsubsection{Discretization with fixed Structure}
+\subsubsection{Discretization with Fixed Structure}
 \label{subsubsec:wine_exp1}
@@
 %
-\subsection{Data 3: Housing}
+\subsection{Dataset 3: Housing}
 \label{subsec:housing}
@@
   \input{Fig17}
-  \caption{A simple Bayesian network used to demonstrate the sensitivity of each method}
+  \caption{A simple Bayesian network used to demonstrate the sensitivity of each method.}
   \label{fig:exp_discuss}
@@
 
-\subsection{Auto MPG with Comparable MDL Performance}
+\subsection*{Auto MPG with Comparable MDL Performance}
 The Bayesian network structure in Figure~\ref{fig:auto_graph_3} and the discretization results in Table~\ref{table:auto_disc_table_3} demonstrate that the MDL method does not always produce fewer discretization intervals than the Bayesian approach and that the MDL method can produce discretization policies with comparable likelihood.
@@
 
-\subsection{Reproducing MDL Results from the Literature}
+\subsection*{Reproducing MDL Results from the Literature}
 

### 2015-12-04 information_sheet.tex
update info sheet

@@
 
-\title{Information Sheet \\ {\large Learning Discrete-valued Bayesian Networks from Mixed Data}}
+\title{Information Sheet \\ {\large Learning Discrete Bayesian Networks from Continuous Data}}
 \author{\normalsize Yi-Chun Chen, Tim A. Wheeler, Mykel J. Kochenderfer}
@@
 
-The proposed method learns discretization policies for continuous variables from mixed data while taking the Bayesian network structure into account.
+The proposed method learns discretization policies for continuous variables from continuous data while taking the Bayesian network structure into account.
 Prior Bayesian methods, such as MODL \citep{Boulle_2006, Lustgarten_2011}, only consider the discretization of a single continuous variable with respect to another single discrete variable.
-The predominant existing method for discretizing continuous variables in Bayesian networks is based on MDL~\citep{Friedman_1996}, and has cubic runtime in the number of data samples.
+The predominant existing method for discretizing continuous variables in Bayesian networks is based on MDL~\citep{Friedman_1996}, and has cubic runtime in the number of data samples for optimal discretization.
 The proposed method learns the discretization with quadratic runtime in the number of data samples, allowing it to more efficiently scale to larger datasets.

### 2015-12-04 information_sheet.tex
tiny changes

@@
 Prior Bayesian methods, such as MODL \citep{Boulle_2006, Lustgarten_2011}, only consider the discretization of a single continuous variable with respect to another single discrete variable.
-The predominant existing method for discretizing continuous variables in Bayesian networks is based on MDL~\citep{Friedman_1996}, and has cubic runtime in the number of data samples for optimal discretization.
+The predominant existing method for discretizing continuous variables in Bayesian networks is based on MDL~\citep{Friedman_1996}, and has cubic runtime in the number of data samples.
 The proposed method learns the discretization with quadratic runtime in the number of data samples, allowing it to more efficiently scale to larger datasets.

### 2015-12-08 information_sheet.tex
update

@@
 Prior Bayesian methods, such as MODL \citep{Boulle_2006, Lustgarten_2011}, only consider the discretization of a single continuous variable with respect to another single discrete variable.
-The predominant existing method for discretizing continuous variables in Bayesian networks is based on MDL~\citep{Friedman_1996}, and has cubic runtime in the number of data samples.
+A common discretization method for Bayesian networks is to split continuous variables into uniform-width intervals or to use field-specific expertise.
+A more principled method is the minimum description length (MDL) principle discretization \citep{Friedman_1996} which has cubic runtime in the number of data samples.
+
 The proposed method learns the discretization with quadratic runtime in the number of data samples, allowing it to more efficiently scale to larger datasets.

### 2015-12-09 Learning_Discrete_Bayesian_Networks_from_Continuous_Data.tex
latest version

--- 2015-12-03 BN_discretizer_paper.tex
@@
 
-A common discretization method for Bayesian networks is to split continuous variables into uniform-width intervals or by using field-specific expertise.
+A common discretization method for Bayesian networks is to split continuous variables into uniform-width intervals or to use field-specific expertise.
 A more principled method is the minimum description length (MDL) principle discretization \citep{Friedman_1996}.
@@
 Algorithm~\ref{alg:disc_one} is guaranteed to be optimal.
-For faster methods with suboptimal results, see \citet{Friedman_1996} and \citet{Boulle_2006}.
+For faster methods with suboptimal results, see \citet{Boulle_2006}.
 
@@
 Therefore, the runtime of the proposed method in this paper is shorter than the MDL discretization method by $\bigo \paren{n^3}$, since the former has a more efficient form of dynamical programming.
+For faster methods of MDL discretization with suboptimal results, see \citet{Friedman_1996}.
 

### 2016-07-15 Learning_Discrete_Bayesian_Networks_from_Continuous_Data.tex
Revision
Section 2.1, 6.4, and 6.5 are revised.

@@
 \usepackage{lscape}
-% \usepackage{caption}
 \usepackage{siunitx}
@@
 \usepackage[hyphens]{url}
+\usepackage{subcaption}
+\captionsetup{compatibility=false}
+\usepackage{tabularx}
 
@@
 The $\lambda_{1:k}$ representation is the number of instances before every discretization edge whereas the $\gamma_{1:k}$ representation is the number of instances within each discretization interval.
+Table \ref{table:data_demo} and \ref{table:data_demo_2} make an example of variables defined in this subsection.
+
+%For example, Table \ref{table:data_demo} is a dataset that mixes continuous variable $\cX$ and discrete variables $A$ and $B$.
+Data samples are arranged in an ascending order of $\cX$.
+Therefore, $n = 10$, $m =6$, $\cx_{1:10} = \curly{ 1.1, 1.2, 1.2, 2.9, 2.9, 2.9, 3.5, 4.3, 4.3, 5.0} $, and  $\cu_{1:6} = \curly{ 1.1,1.2,2.9,3.5,4.3,5.0}$.
+The corresponding index $s$ of $\cu$ in $\cx$ is $s_{1:6} = \curly{1,3,6,7,9,10}$.
+In addition, a three-interval discretization policy $\Lambda^0_{\cX}$ with edges $e_1 = 1.55$ and $e_2 = 4.65$ can be represented as
+%\begin{equation}
+%\Lambda^0_{\cX} = \anglebrackets{\lambda_1 = 3 , \lambda_2 = 9, \lambda_{3} = 10 } \equiv \anglebrackets{\gamma_1 = 3, \gamma_2 = 6, \gamma_3 = 1} \text{.}
+%\end{equation}
+
+\begin{table}[ht]
+  \centering
+  \caption{
+    An example dataset that demonstrates variables defined in Section \ref{subsec:disc_policy} to discretize continuous variable $\cX$.
+  }
+  \input{Table0.tex}
+  \label{table:data_demo}
+  \bigskip
+  \centering
+  \caption{
+  	Illustrate variables defined in Section \ref{subsec:disc_policy} along with the dataset in Table \ref{table:data_demo}.
+Note that $\Lambda^{\text{ex}}_{\cX}$ is an example of a valid discretization policy.
+$\anglebrackets{}_{e}$, $\anglebrackets{}_{\lambda}$, and $\anglebrackets{}_{\gamma}$ are the three equivalent representations of discretization policies.
+ }
+  	\begin{tabular}{cc}
+  		\toprule
+  		Variable &  Value \\
+  		\midrule
+  		$n$ &  \num{10} \\
+  		$m$ &  \num{6} \\
+  		$\cx_{1:10}$ & $\curly{ 1.1, 1.2, 1.2, 2.9, 2.9, 2.9, 3.5, 4.3, 4.3, 5.0} $\\
+  		$\cu_{1:6} $ & $\curly{ 1.1,1.2,2.9,3.5,4.3,5.0}$\\
+  		$s_{1:6}$ & $\curly{1,3,6,7,9,10}$\\
+  		$\Lambda^{\text{ex}}_{\cX}$ & $\anglebrackets{1.55,4.65}_{e}$, $ \anglebrackets{3 ,9,10}_{\lambda}$, $\anglebrackets{3, 6, 1}_{\gamma} $\\
+  		\bottomrule
+  	\end{tabular}
+  \label{table:data_demo_2}
+\end{table}
 
@@
   \input{Fig8}
-  \caption{Comparison of the discretization policies for variables $A$ and $C$ obtained using the Bayesian and MDL methods.}
+  \caption{Comparison of the discretization policies for variables $E$ and $K$ obtained using the Bayesian and MDL methods.}
   \label{fig:wine_exp1_distr}
@@
 
+\subsection{Results on More Datasets}
+
+Six additional datasets \citep{Lichman_2013} are tested to compare the proposed Bayesian approach and MDL discretization method.
+The results are summarized in Table \ref{table:more_data_set}.
+For each dataset, number of samples $n$, number of variables $m$, the fixed network to execute discretization, and resulted log-likelihood by the two methods are shown in the same row.
+Note that the fixed network structures are obtained by the same principle as in previous three datasets.
+The network representation in Table \ref{table:more_data_set} records the parent variables of each variable.
+For example, in the first row, the representation $\curly{\emptyset,A,BE,AB,B,AH,BDG,B}$ indicates that $\Pa_A = \emptyset$, $\Pa_B = A$, $\Pa_c = \curly{B,E}$, etc.
+Again, the results show that the proposed Bayesian discretization method outperforms the MDL method in terms of likelihood.
+
+\begin{table}[ht]
+	\centering
+	\caption{
+		The discretization results on several datasets.
+	    Each row corresponds to a dataset.
+Names of datasets, numbers of samples, numbers of variables, network structures for discretization, log-likelihood obtained by the proposed Bayesian method and MDL method are shown.
+	}
+	\input{Table3_2.tex}
+	\label{table:more_data_set}
+\end{table}
+
 \subsection{Discussion}
@@
   \begin{aligned}
-  f_{\text{MDL}} & = \overbrace{Z_1 \cdot k + \ln(k) + \ln {{n +k - 1}\choose{k -1}} }^{\text{Penalty Term}}+   \overbrace{\rule{0pt}{1.35em} \ln(n) \cdot I(X^*, \Pa_X)}^{\text{Edge Position Term}} \\
+  f_{\text{MDL}} & = \overbrace{Z_1 \cdot k + \ln(k) + \ln {{n +k - 1}\choose{k -1}} }^{\text{Penalty Term}}+   \overbrace{\rule{0pt}{1.35em} n \cdot I(X^*, \Pa_X)}^{\text{Edge Position Term}} \\
   f_{\text{Bayesian}} &= \underbrace{{\vrule width0pt height0pt depth1.48em\relax}  Z_2 \cdot k + \sum_{i=1}^k \ln {{\gamma_i + J_\text{P} - 1}\choose{J_\text{P} -1}}}_{\text{Penalty Term}} + \underbrace{\sum^k_{i=1} \ln \left(   {{\gamma_i !}\over{n^{\text{P}}_{i,1}!
@@
 
+To further demonstrate the above discussion, the discretization results on Iris dataset with respect to different cropped data sizes are analyzed.
+As shown in Appendix, the results of the two methods coincide on Iris dataset under naive Bayes structure.
+However, if the dataset is cropped and the distribution pattern of data samples becomes less obvious, the two discretization methods would have different outcomes.
+
+Figure \ref{fig:iris_four} shows the relation between number of samples in cropped datasets and number of resulted discretization edges on each continuous variable.
+Samples are drawn randomly from the dataset and the result of number of edges are averaged over one thousand times.
+On variable $C$ and $D$, since data distribution is easier to discriminate, both methods have already located two discretization edges even if there were only thirty samples (one fifth of the entire dataset).
+On variable $A$ and $B$, more data samples are required to locate the discretization edges.
+Under this case, the proposed Bayesian method is more sensitive than the MDL method and able to lay down more discretization edges even if the data distribution is still vague for the MDL method.
+
+\begin{figure}
+	\begin{subfigure}{0.45\textwidth}
+		\centering
+		\scalebox{0.6}{\input{Fig_edges_A}}
+		%\caption{A}
+		%\label{fig:iris_a}
+	\end{subfigure}%
+	\begin{subfigure}{0.45\textwidth}
+		\centering
+		\scalebox{0.6}{\input{Fig_edges_B}}
+		%\caption{B}
+		%\label{fig:iris_b}
+	\end{subfigure}
+
+	\begin{subfigure}{0.45\textwidth}
+		\centering
+		\scalebox{0.6}{\input{Fig_edges_C}}
+		%\caption{C}
+		%\label{fig:iris_c}
+	\end{subfigure}%
+	\begin{subfigure}{0.45\textwidth}
+		\centering
+		\scalebox{0.6}{\input{Fig_edges_D}}
+		%\caption{D}
+		%\label{fig:iris_d}
+	\end{subfigure}
+	\caption{Number of resulted discretization edges on each continuous variable with respect to number of data samples}
+	\label{fig:iris_four}
+\end{figure}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \end{table}
+
+%\subsection*{Results on More Datasets}
+%
+%In this subsection, six additional datasets \citep{Lichman_2013} are tested as a supplementary to Section \ref{sec:experiments}.
+For each dataset, a comparison between the proposed method and MDL-principle method has been made.
+The discretization results of two methods are shown in terms of discretization edges and likelihood on a given network structure, which is obtained by uniform discretization and K2 structure learning, same as in Section \ref{sec:experiments}.
+The results still indicates that the proposed method outperforms than the MDL-principle discretization, in which the latter suffers from low number of discretization edges.
+%
+%\subsubsection*{Dataset: Seeds}
+%
+%The Seeds data sets contains variables related to the shape of seeds of two species.
+The dataset has 210 samples over eight variables.
+Only variable $H$ is discrete-valued.
+The discretization methods are tested on the fixed network structure: $\Pa_A = \curly{\emptyset}$, $\Pa_B = \curly{ A }$, $\Pa_C = \curly{B, E}$, $\Pa_D = \curly{A,B}$, $\Pa_E = \curly{B}$, $\Pa_F = \curly{A,H}$, $\Pa_G = \curly{B,D,H}$, and $\Pa_H = \curly{B}$.
+This network is obtained by first uniformly discretizing each variable by two intervals then running K2 structure learning.
+%
+%\begin{table}[ht]
+%	\centering
+%	\caption{
+%		The discretization policies for the Seeds dataset with a fixed structure.
+%		The methods have the same discretization for variable $G$, close discretization edge for variable $F$, and the log-likelihood for the Bayesian method is better than that for the MDL method.
+%	}
+%	\input{Table6.tex}
+%	\label{table:auto_disc_seeds}
+%\end{table}
+%
+%\subsubsection*{Dataset: Glasses}
+%
+%\subsubsection*{Dataset: Heart}
+%
+%\subsubsection*{Dataset: Liver Disorder}
+%
+%\subsubsection*{Dataset: Indian Liver Patient}
+%
+%\subsubsection*{Dataset: Banknote authentication}
 \end{document}

### 2016-07-16 Learning_Discrete_Bayesian_Networks_from_Continuous_Data.tex
proofreading of rebuttal edits

@@
 The $\lambda_{1:k}$ representation is the number of instances before every discretization edge whereas the $\gamma_{1:k}$ representation is the number of instances within each discretization interval.
-Table \ref{table:data_demo} and \ref{table:data_demo_2} make an example of variables defined in this subsection.
+Table \ref{table:data_demo} and \ref{table:data_demo_2} demonstrate variable assignments for an example dataset.
 
@@
   \caption{
-    An example dataset that demonstrates variables defined in Section \ref{subsec:disc_policy} to discretize continuous variable $\cX$.
+    An example dataset used to demonstrate the variables defined in Section \ref{subsec:disc_policy}. Rows are assignments to continuous variable $\cX$ and discrete variables $A$ and $B$.
   }
@@
   \caption{
-  	Illustrate variables defined in Section \ref{subsec:disc_policy} along with the dataset in Table \ref{table:data_demo}.
+    Assignments for variables defined in Section~\ref{subsec:disc_policy} according to the dataset in Table~\ref{table:data_demo}.
   	Note that $\Lambda^{\text{ex}}_{\cX}$ is an example of a valid discretization policy.
-$\anglebrackets{}_{e}$, $\anglebrackets{}_{\lambda}$, and $\anglebrackets{}_{\gamma}$ are the three equivalent representations of discretization policies.
+Discretization policies can be represented by their edges $\anglebrackets{}_{e}$, their sorted unique dataset indeces $\anglebrackets{}_{\lambda}$, or by the interval between sorted unique dataset indeces $\anglebrackets{}_{\gamma}$.
   }
@@
 
-The Bayesian network graph structure causes the likelihood term ${P(D_{-\cX} \mid \Lambda)}$ to factor according to $\cX$'s Markov blanket:
+The likelihood term ${P(D_{-\cX} \mid \Lambda)}$ for a Bayesian network graph structure factors according to $\cX$'s Markov blanket:
 
@@
 
-\subsection{Results on More Datasets}
-
-Six additional datasets \citep{Lichman_2013} are tested to compare the proposed Bayesian approach and MDL discretization method.
-The results are summarized in Table \ref{table:more_data_set}.
-For each dataset, number of samples $n$, number of variables $m$, the fixed network to execute discretization, and resulted log-likelihood by the two methods are shown in the same row.
-Note that the fixed network structures are obtained by the same principle as in previous three datasets.
-The network representation in Table \ref{table:more_data_set} records the parent variables of each variable.
+\subsection{Results on Additional Datasets}
+
+Six additional datasets \citep{Lichman_2013} are tested to compare the Bayesian and MDL discretization methods.
+The results are summarized in Table~\ref{table:more_data_set}.
+Each row corresponds to a dataset and provides the number of samples $n$, the number of variables $m$, the fixed network structure, and the log-likelihood for each method.
+Fixed network structures are obtained by the same principle as in previous three datasets and are represented in the table by listing the parents for each variable.
 For example, in the first row, the representation $\curly{\emptyset,A,BE,AB,B,AH,BDG,B}$ indicates that $\Pa_A = \emptyset$, $\Pa_B = A$, $\Pa_c = \curly{B,E}$, etc.
-Again, the results show that the proposed Bayesian discretization method outperforms the MDL method in terms of likelihood.
+The Bayesian discretization method has higher mean cross-validated log likelihood in all cases.
 
@@
 	\caption{
-		The discretization results on several datasets.
-	    Each row corresponds to a dataset.
-Names of datasets, numbers of samples, numbers of variables, network structures for discretization, log-likelihood obtained by the proposed Bayesian method and MDL method are shown.
+		Discretization results for several datasets.
+    The number of samples, number of variables, network structure, and mean cross-validated log-likelihood under each discretization method are given.
 	}
@@
 where $Z_1$ and $Z_2$ are constant over discretizations, $k$ is the number of discretization intervals, and $I\paren{A, B} = \sum_{a,b} \hat{P}(a,b) \ln\frac{\hat{P}(a,b)}{\hat{P}(a)\hat{P}(b)}$ is the mutual information based on estimated probabilities.
-Note that the third term of $f_\text{MDL}$ had been approximated using $H(p)$ (see Equation~\ref{eqn:MDL}) in the original work by \cite{Friedman_1996}, but it is written here without that approximation.
+Note that the third term of $f_\text{MDL}$ was approximated using $H(p)$ (see Equation~\ref{eqn:MDL}) in the original work by \cite{Friedman_1996}, but it is written here without that approximation.
 
@@
 
-To further demonstrate the above discussion, the discretization results on Iris dataset with respect to different cropped data sizes are analyzed.
-As shown in Appendix, the results of the two methods coincide on Iris dataset under naive Bayes structure.
-However, if the dataset is cropped and the distribution pattern of data samples becomes less obvious, the two discretization methods would have different outcomes.
-
-Figure \ref{fig:iris_four} shows the relation between number of samples in cropped datasets and number of resulted discretization edges on each continuous variable.
-Samples are drawn randomly from the dataset and the result of number of edges are averaged over one thousand times.
-On variable $C$ and $D$, since data distribution is easier to discriminate, both methods have already located two discretization edges even if there were only thirty samples (one fifth of the entire dataset).
-On variable $A$ and $B$, more data samples are required to locate the discretization edges.
-Under this case, the proposed Bayesian method is more sensitive than the MDL method and able to lay down more discretization edges even if the data distribution is still vague for the MDL method.
+We use the Iris dataset to support this discussion.
+In the appendix we show that the Bayesian and MDL methods produce equivalent results under a naive Bayes structure.
+However, if a subset of the samples are used then the distribution pattern of data samples becomes less obvious, and the two discretization methods have different outcomes.
+
+Figure \ref{fig:iris_four} shows the relation between the number of samples and the number of \todo{I thought this would be likelihood?} discretization edges on each continuous variable.
+Samples are drawn randomly from the dataset \tim{without replacement?} and the result of number of edges are averaged over a thousand runs.
+For the variables $C$ and $D$, the correct discretization policy is easier to obtain, and both methods locate two discretization edges within thirty samples, one fifth of the full Iris dataset.
+For the variables $A$ and $B$, more data samples are required before settling on the final discretization edges.
+Under this case, the proposed Bayesian method is more sensitive than the MDL method and produces discretizations with higher cross-validated likelihood.
 
@@
 	\end{subfigure}
-	\caption{Number of resulted discretization edges on each continuous variable with respect to number of data samples}
+	\caption{Number of \todo{discretization edges} for each continuous variable in the Iris dataset as the number of samples used in training are varied.}
 	\label{fig:iris_four}

### 2016-07-21 Fig_demo_edge.tex
Add an experiment on a synthetic dataset

\begin{tikzpicture}
\begin{axis}[
		xlabel = Number of Samples,
		ylabel = Number of Edges,
		legend style={at={(0.99,0.02)},anchor=south east},
		ymin= 2, ymax= 7
]
\addplot+[solid ,black,thick] coordinates {
(150, 3.34)
(200, 3.48)
(250, 3.86)
(300, 4.36)
(350, 4.6)
(400, 5.12)
(450, 5.6)
(500, 5.8)
(550, 5.98)
(600, 5.98)
(650, 6.0)
(700, 6.0)
};
\addlegendentry{Bayesian};

\addplot+[solid ,black,thick] coordinates {
(150, 2.3)
(200, 2.88)
(250, 3.12)
(300, 3.42)
(350, 3.64)
(400, 3.84)
(450, 4.4)
(500, 4.5)
(550, 5.06)
(600, 5.48)
(650, 5.82)
(700, 5.98)
(750, 6.0)
};
\addlegendentry{MDL};
\end{axis}
\end{tikzpicture}

### 2016-07-21 Learning_Discrete_Bayesian_Networks_from_Continuous_Data.tex
Add an experiment on a synthetic dataset

@@
 
-We use the Iris dataset to support this discussion.
-In the appendix we show that the Bayesian and MDL methods produce equivalent results under a naive Bayes structure.
-However, if a subset of the samples are used then the distribution pattern of data samples becomes less obvious, and the two discretization methods have different outcomes.
-
-Figure \ref{fig:iris_four} shows the relation between the number of samples and the number of \todo{I thought this would be likelihood?} discretization edges on each continuous variable.
-Samples are drawn randomly from the dataset \tim{without replacement?} and the result of number of edges are averaged over a thousand runs.
-For the variables $C$ and $D$, the correct discretization policy is easier to obtain, and both methods locate two discretization edges within thirty samples, one fifth of the full Iris dataset.
-For the variables $A$ and $B$, more data samples are required before settling on the final discretization edges.
-Under this case, the proposed Bayesian method is more sensitive than the MDL method and produces discretizations with higher cross-validated likelihood.
+To support the argument, a synthetic dataset with $800$ samples and under the network structure in Figure~\ref{fig:exp_discuss} is tested.
+Data samples are generated by the distribution described in Table~\ref{table:distri_exp}: both $P_1$ and $P_2$ take two discrete values with equal probability.
+$\cX$ samples numeric numbers given the value of $P_1$ and $P_2$.
+Note that the symbol $\sim U[a,b]$ in Table~\ref{table:distri_exp} represents an uniform distribution from value $a$ to $b$.
+The optimal discretization policy on $\cX$ should have six edges $\curly{2.0,3.0,4.0,4.5,5.0,6.0}$, since $\cX$ takes numeric values from $1.0$ to $7.5$ and there are seven intervals corresponding to different joint distribution of $P_1$ and $P_2$.
+
+\begin{table}[ht]
+	\centering
+	\caption{The distribution of variables in Figure~\ref{fig:exp_discuss} for the proposed experiment. $P_1$ and $P_2$ are discrete variable. $\cX$ is continuous valued.}
+	\label{table:distri_exp}
+	\begin{tabular}{cl}
+		\toprule
+		Variable               & Distribution                                   \\ \midrule
+		\multirow{2}{*}{$P_1$}&$P(p^{(1)}_1) = 0.5$     \\
+		                                       & $P(p^{(2)}_1) = 0.5$     \\ \midrule
+		\multirow{2}{*}{$P_2$}&$P(p^{(1)}_2) = 0.5$     \\
+		                                       &$P(p^{(2)}_2) = 0.5$     \\ \midrule
+		\multirow{4}{*}{$\cX$} & $p(\cx \mid p^{(1)}_1,p^{(1)}_2) \sim U[2,6]$\\
+		                                     & $p(\cx \mid p^{(1)}_1,p^{(2)}_2) \sim U[1,3]$ \\
+		                                     & $p(\cx \mid p^{(2)}_1,p^{(1)}_2) \sim U[4,5]$ \\
+		                                     & $p(\cx \mid p^{(2)}_1,p^{(2)}_2) \sim U[4.5,7.5]$\\
+		\bottomrule
+	\end{tabular}
+\end{table}
+
+Figure~\ref{fig:synthetic} shows how the likelihood of tested data and number of discretization edges on $\cX$ vary with respect to the size of trained data.
+Trained data are drawn randomly from the synthetic dataset.
+The remaining ones are tested data.
+If the size of the trained data is small, it is hard to recognize the underlying pattern of data samples and discretize the continuous variable $\cX$ accordingly.
+In this case, both likelihood of the trained data and number of discretization edges is small.
+However, since the Bayesian method is more sensitive to the data distribution, it has better performance of the MDL method in terms of likelihood and lays down more discretization edges.
+As the size of the trained data grows, both methods improve their accuracy and approach to optimal number of discretization edges.
+The Bayesian method finds the six discretization edges faster than the MDL method.
+Finally, as the size of the trained data is large enough to capture the data distribution, both methods can locate the six discretization edges and lead to same accuracy to the tested data.
+The curves in Figure~\ref{fig:synthetic} demonstrate that the Bayesian method is indeed more sensitive to the dataset than the MDL method.
+Note that all the results in Figure~\ref{fig:synthetic} are averaged over one hundred times.
+
+%We use the Iris dataset to support this discussion.
+%In the appendix we show that the Bayesian and MDL methods produce equivalent results under a naive Bayes structure.
+%However, if a subset of the samples are used then the distribution pattern of data samples becomes less obvious, and the two discretization methods have different outcomes.
+
+%Figure \ref{fig:iris_four} shows the relation between the number of samples and the number of \todo{I thought this would be likelihood?} discretization edges on each continuous variable.
+%Samples are drawn randomly from the dataset \tim{without replacement?} and the result of number of edges are averaged over a thousand runs.
+%For the variables $C$ and $D$, the correct discretization policy is easier to obtain, and both methods locate two discretization edges within thirty samples, one fifth of the full Iris dataset.
+%For the variables $A$ and $B$, more data samples are required before settling on the final discretization edges.
+%Under this case, the proposed Bayesian method is more sensitive than the MDL method and produces discretizations with higher cross-validated likelihood.
 
@@
 		\centering
-		\scalebox{0.6}{\input{Fig_edges_A}}
+		\scalebox{0.6}{\input{Fig_demo_like}}
 		%\caption{A}
@@
 		\centering
-		\scalebox{0.6}{\input{Fig_edges_B}}
+		\scalebox{0.6}{\input{Fig_demo_edge}}
 		%\caption{B}
@@
 
-	\begin{subfigure}{0.45\textwidth}
-		\centering
-		\scalebox{0.6}{\input{Fig_edges_C}}
-		%\caption{C}
-		%\label{fig:iris_c}
-	\end{subfigure}%
-	\begin{subfigure}{0.45\textwidth}
-		\centering
-		\scalebox{0.6}{\input{Fig_edges_D}}
-		%\caption{D}
-		%\label{fig:iris_d}
-	\end{subfigure}
-	\caption{Number of \todo{discretization edges} for each continuous variable in the Iris dataset as the number of samples used in training are varied.}
-	\label{fig:iris_four}
+	\caption{The average log-likelihood of the trained data and the average number of discretization edges for $\cX$ as the number of trained data is varied.
+Trained data are drawn randomly from the synthetic dataset.
+The remaining ones are tested data.
+Results are averaged over one hundred times.}
+	\label{fig:synthetic}
 \end{figure}

### 2016-07-28 Learning_Discrete_Bayesian_Networks_from_Continuous_Data.tex
some edits, particularly to new Discussion section

@@
 Section~\ref{sec:multi_var} covers Bayesian networks with multiple continuous variables and Section~\ref{sec:structure_learning} covers discretization while simultaneously learning network structure.
-The paper concludes with a comparison against the existing minimum-description length \citep{Friedman_1996} method on real-world datasets in Section~\ref{sec:experiments}.
+The paper concludes with a comparison against the existing minimum-description length \citep{Friedman_1996} method on real-world and synthetic datasets in Section~\ref{sec:experiments}.
 
@@
 The discretizations are compared using the mean cross validated log-likelihood of the data $D$ given the Bayesian network $B$ and discretization policies $\discset$.
+\tim{Did we also normalize each variable to be zero mean and unit covariance?}
 Note that all log-likelihoods shown have been normalized by the number of data samples.
@@
 The results are summarized in Table~\ref{table:more_data_set}.
-Each row corresponds to a dataset and provides the number of samples $n$, the number of variables $m$, the fixed network structure, and the log-likelihood for each method.
+Each row corresponds to a dataset and provides the number of samples $n$, the number of variables $N$, the fixed network structure, and the log-likelihood for each method.
 Fixed network structures are obtained by the same principle as in previous three datasets and are represented in the table by listing the parents for each variable.
@@
 	}
+  \resizebox{\textwidth}{!}{
 	 \input{Table3_2.tex}
+  }
 	\label{table:more_data_set}
@@
 
-To support the argument, a synthetic dataset with $800$ samples and under the network structure in Figure~\ref{fig:exp_discuss} is tested.
-Data samples are generated by the distribution described in Table~\ref{table:distri_exp}: both $P_1$ and $P_2$ take two discrete values with equal probability.
-$\cX$ samples numeric numbers given the value of $P_1$ and $P_2$.
-Note that the symbol $\sim U[a,b]$ in Table~\ref{table:distri_exp} represents an uniform distribution from value $a$ to $b$.
-The optimal discretization policy on $\cX$ should have six edges $\curly{2.0,3.0,4.0,4.5,5.0,6.0}$, since $\cX$ takes numeric values from $1.0$ to $7.5$ and there are seven intervals corresponding to different joint distribution of $P_1$ and $P_2$.
+To support this argument, we test a synthetic dataset with $800$ samples using the network structure in Figure~\ref{fig:exp_discuss}.
+Data samples are generated by the distribution described in Table~\ref{table:distri_exp}: both $P_1$ and $P_2$ are fair coins.
+The continuous variable $\cX$ is conditionally dependent on $P_1$ and $P_2$.
+Note that the symbol $\sim U[a,b]$ in Table~\ref{table:distri_exp} represents a uniform distribution from $a$ to $b$.
+The optimal discretization policy on $\cX$ has six edges, $\curly{2.0,3.0,4.0,4.5,5.0,6.0}$, since $\cX$ takes numeric values from $1.0$ to $7.5$ and there are seven intervals corresponding to different joint distributions of $P_1$ and $P_2$.
 
@@
 	\centering
-	\caption{The distribution of variables in Figure~\ref{fig:exp_discuss} for the proposed experiment. $P_1$ and $P_2$ are discrete variable. $\cX$ is continuous valued.}
+	\caption{Probability distributions for the variables in Figure~\ref{fig:exp_discuss}.
+           $P_1$ and $P_2$ are discrete whereas $\cX$ is continuous.}
 	\label{table:distri_exp}
@@
 
-Figure~\ref{fig:synthetic} shows how the likelihood of tested data and number of discretization edges on $\cX$ vary with respect to the size of trained data.
+Figure~\ref{fig:synthetic} shows how the test likelihood and the number of discretization edges for $\cX$ vary with respect to the number of training samples.
 Trained data are drawn randomly from the synthetic dataset.
-The remaining ones are tested data.
-If the size of the trained data is small, it is hard to recognize the underlying pattern of data samples and discretize the continuous variable $\cX$ accordingly.
-In this case, both likelihood of the trained data and number of discretization edges is small.
-However, since the Bayesian method is more sensitive to the data distribution, it has better performance of the MDL method in terms of likelihood and lays down more discretization edges.
-As the size of the trained data grows, both methods improve their accuracy and approach to optimal number of discretization edges.
-The Bayesian method finds the six discretization edges faster than the MDL method.
-Finally, as the size of the trained data is large enough to capture the data distribution, both methods can locate the six discretization edges and lead to same accuracy to the tested data.
+\todo{The remaining ones are tested data.}
+When the training set is small, it is difficult to recognize the underlying pattern and discretize the continuous variable $\cX$ accordingly.
+In this case, both the likelihood of the training data and number of discretization edges is small.
+However, the Bayesian method is more sensitive to variation in the data and produces a distribution both with higher likelihood and more discretization edges.
+As the size of the training set grows, both methods converge towards the optimal discretization policy.
+The Bayesian method finds the six discretization edges faster than the MDL method and consistently outperforms in likelihood.
 The curves in Figure~\ref{fig:synthetic} demonstrate that the Bayesian method is indeed more sensitive to the dataset than the MDL method.
-Note that all the results in Figure~\ref{fig:synthetic} are averaged over one hundred times.
+The results in Figure~\ref{fig:synthetic} are averaged over one hundred trials.
 
@@
 
-	\caption{The average log-likelihood of the trained data and the average number of discretization edges for $\cX$ as the number of trained data is varied.
-Trained data are drawn randomly from the synthetic dataset.
-The remaining ones are tested data.
-Results are averaged over one hundred times.}
+	\caption{The average log-likelihood of the trained data and the average number of discretization edges for $\cX$ as the number of training samples is varied.
+Training data are drawn randomly from the synthetic distribution.
+\todo{The remaining ones are tested data.} \tim{$\leftarrow$ What does this mean?} Results are averaged over one hundred trials.
+  \tim{Why do we plot training set likelihood and not test set likelihood?}}
 	\label{fig:synthetic}

### 2016-08-09 Learning_Discrete_Bayesian_Networks_from_Continuous_Data.tex
cited 4 BayesBlocks related papers and added some sentences to prior 1 discussion

@@
 
-A common discretization method for Bayesian networks is to split continuous variables into uniform-width intervals or to use field-specific expertise.
+A common discretization method for Bayesian networks is to split continuous variables into uniform-width intervals or to use field-specific expertise \citep{scott1979optimal, freedman1981histogram, knuth2013optimal, scargle2013studies}.
 A more principled method is the minimum description length (MDL) principle discretization \citep{Friedman_1996}.
@@
 
-where $L$ is the largest number of intervals among discrete variables in $\cX$'s Markov blanket.
-This encourages edges between well-separated values over edges between closely packed samples.
+where larger values of $L$ encourage more discretization intervals.
+This prior encourages edges between well-separated values over edges between closely packed samples.
+All experiments set $L$ to the largest number of intervals among discrete variables in $\cX$'s Markov blanket, which encourages Bayesian networks with consistent interval counts.
+In some cases it may be desirable to use higher values for $L$, such as when discrete variables are binary and the continuous variable requires higher fidelity.
 

### 2016-08-09 Learning_Discrete_Bayesian_Networks_from_Continuous_Data.tex
appendix

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section*{Appendix}
+\section*{Appendix A}
+
+This section provides a counterexample of marginal discretization methods.
+Different from more principled methods, as such the MDL discretization or the proposed Bayesian approach, the marginal discretization methods ignore the dependency of data samples between different variables.
+Therefore, it might lead to worse discretization outcomes.
+Here is an example: consider a synthetic dataset with two variable $A$ and $B$, with $500$ data samples generated by the Bayesian network $A \rightarrow B$ and the probability distribution shown in Table \ref{table:marginal_counter}.
+Following the experiment procedure in Section \ref{sec:experiments}, both the MDL method and the proposed Bayesian approach find a discretization edge of $B$ around $1.0$ and have log likelihood $-0.023$.
+On the other hand, while discretizing variable $B$ based on its marginal distribution of samples, the Bayesian block and other marginal discretization can not locate a discretization edge and result in log likelihood $-0.69$.
+This example shows that the discretization method without considering the dependency between variables might lead to fatal outcomes.
+
+\begin{table}[ht]
+	\centering
+	\caption{Probability distributions for the variables in the network $A \rightarrow B$, in which $A$ is a discrete variable and $B$ is a continuous one
+	}
+	\label{table:marginal_counter}
+	\begin{tabular}{cl}
+		\toprule
+		Variable               & Distribution                                   \\ \midrule
+		\multirow{2}{*}{$A$}&$P(a^1) = 0.5$     \\
+		& $P( a^2) = 0.5$     \\ \midrule
+
+		\multirow{2}{*}{$B$} & $p(b \mid A = a^1 \sim U[0,1]$\\
+		& $p(b \mid A = a^2 \sim U[1,2]$\\
+		\bottomrule
+	\end{tabular}
+\end{table}
+
+\section*{Appendix B}
 \label{sec:appendix}

### 2016-08-09 rebuttal/rebuttal.tex
adding rebuttal

\documentclass{article}
\title{Response to the Reviewer's Comments}
\author{Yi-Chun Chen \and Tim Wheeler \and Mykel Kochenderfer}
\begin{document}

\maketitle

The authors thank the reviewers for their anonymous reviews.
We have restructured the paper to include additional experimental results and have added clarifications in areas identified by the reviewers.
Below is a summary of our responses.

\noindent\rule{8cm}{0.4pt}\\
{\bf Reviewer \#1} \\

1. I do not understand based on what the proposed method is superior. What is the evaluation criterion? such as KL divergence between the original continuous BN and the obtained discretized BN, or How many edges are missing and extra? Note that Log-Likelihood values such as in Tables 1 and 2 can be zero
(maximum)  if each variable has only one interval when discretization
completes, and should not be used as a final evaluation.
\\

2. I think that the goal  is to estimate the true DAG of the original continuous BN. Because even if the variables are discretized, the conditional  independence (CI) relations should remain the same if the discretization is appropriate.  I do not understand why alternating between K2 structure learning  and discretization until K2 algorithm converges yields a good estimation of the CI relations.  Just because K2 falls into a local optimum does not mean that a good estimation is obtained.  I think that the processes of discretization and structure learning should be at the same time rather than alternately.

\noindent\rule{8cm}{0.4pt}\\
{\bf Response}:\\

There seems to be an important misunderstanding.
The goal of the paper is to learn discrete Bayesian networks from continuous data.
All datasets are raw data and there is no true Bayesian network underlying the data.
Therefore, we are not trying to recover the true \textit{continuous} Bayesian network, but are trying to infer the best discrete Bayesian network and discretization policies for each continuous variable.

Our criterion for model performance is the likelihood of withheld data.
There seems to be a misunderstanding of the likelihood calculation of continuous variables.
If a variable is continuous, the corresponding likelihood is based on the probability density rather than a discrete probability.
Therefore, even if all continuous variables have only one interval, the likelihood is not $1$, but $1$ divided by the product of each variable's discretization interval.

\noindent\rule{8cm}{0.4pt}\\
{\bf Reviewer \#1} \\

3. It seems that  the author compares with an old and inferior method (Friedman and Goldszmidt).
There are many other better way of continuous structure learning.

\begin{itemize}
\item S Imoto, S Kim, T Goto, S Aburatani, K Tashiro, S Kuhara, S Miyano, ``Bayesian  network and nonparametric heteroscedastic regression for nonlinear modeling of  genetic network'', Journal of bioinformatics and computational biology 1, 02,  pages 231-252 (2003)
\item K. Zhang, J. Peters, D. Janzing, and B. Scholkopf, ``Kernel-based Conditional Independence Test and  Application in Causal Discovery''. In the proceedings of Uncertainty in Artificial Intelligence: 804-813 (2011).
\item J. Suzuki, ``Consistency of Learning Bayesian Network Structures with Continuous Variables: An Information  Theoretic Approach'', Entropy 17(8): 5752-5770 (2015).
\end{itemize}

\noindent\rule{8cm}{0.4pt}\\
{\bf Response}:\\

As discussed earlier, the goal is to learn \textit{discrete} Bayesian networks from continuous data.
All the papers listed by Reviewer \#1 are about learning \textit{continuous} Bayesian networks.

\noindent\rule{8cm}{0.4pt}\\
{\bf Reviewer \#1} \\

4. The author claimed that ``the MDL suffers from low sensitivity to discretization edge locations and returns too few discretization intervals for continuous variables'', which I think is false. In fact, as in Introduction, MDL and MODL are asymptotically equivalent for a single variable and a single class  (Vitanyi-Li, 2000).  Why is the statement wrong for multiple variables? Explain it. The author claims that the MDL varies less significantly with the positions than the proposed method.  If the author thinks so in general, the statement should be proved.

\noindent\rule{8cm}{0.4pt}\\
{\bf Response}:\\

% The asymptotic equivalence between methods only holds for large enough datasets, as the definition defined.
We are not claiming that MDL and MODL are asymptotically different.
We are only showing empirically that the size of the dataset heavily influences the outcome, and is independent of the number of variables.
To justify this claim we have added an additional experiment with results shown in Section 6.5.

\noindent\rule{8cm}{0.4pt}\\
{\bf Reviewer \#1} \\

5. Comparing (18) and (19), the term  $ln(n)\cdot I(X^*,pa_X)$ should be $n\cdot I(X^*,pa_X)$ for $f_{MDL}$.  If the latter is correct, the MDL will choose more complicated model and improve very much, and the conclusion may change.

\noindent\rule{8cm}{0.4pt}\\
{\bf Response}:\\

We thank the reviewer for helping us find a typo.
It has been corrected in the most recent version.
However, this change does not change the argument being made.
First, our argument is based on the correct equation.
Second, since both $n$ and $\log(n)$ are constant during the optimization process, where $n$ is the size of dataset, the argument still holds.
These results are reflected in our experiments.

\noindent\rule{8cm}{0.4pt}\\
{\bf Reviewer \#1} \\

6. The author claims that the proposed method takes $O(n^2)$ time rather than $O(n^3)$. However, for the problem setting, there are many possibilities for choosing the prior with $O(n^2)$ time that yields a good estimation. If the author thinks that there exists no such a prior, state and prove it.  I think that K2 algorithm consumes much more time than discretization.

\noindent\rule{8cm}{0.4pt}\\
{\bf Response}:\\

% There is no need to prove other Bayesian priors do not work.
% Bayesian priors indeed are non-unique.
% However, by certain standard criteria such as cross validation, we can tell which one performs better.

% The runtime mentioned in this paper only concerns the discretization processes, not structure learning.
% The K2 algorithm was used due to its simplicity and ubiquity.

The original MODL method and the priors suggested by Lustgarten et al. are both Bayesian methods.
The extensions by Lustgarten et al. replaced the first prior in MODL to yield better results.
Bayesian priors in this case express the beliefs over the sought-after discretization policy.
We suggest a prior that produces discretizations with higher cross validated likelihood and an algorithm with $O(n^2)$ runtime.
The runtime of the discretization method is the bottleneck for the iterative structure learning process.

\noindent\rule{8cm}{0.4pt}\\
{\bf Reviewer \#2} \\

 The paper considers the problem of learning discrete Bayesian networks (BN) from complete continuous data, where the paper considers simultaneously learning the BN structure and learning the discretization of the data. More specifically, the paper first generalizes previous work by [1] on single-variable discretization to multi-variable discretization, and proposes an EM-style algorithm to learn a multi-variable discretization by iteratively discretize the variables with the single-variable discretization method. The paper then assumes that a topological ordering that the learned BN needs to be compatible with is given, and combines the approximate multi-variable discretization method with the K2 algorithm (which learns an optimal BN from complete discrete data, given a topological ordering), and proposes an algorithm to learn an optimal BN from complete continuous data. Finally, the paper evaluates that the proposed algorithm against the state-of-the-art.\\

 Below summarize my comments to the current version of the manuscript:\\

1. If I understand the paper and [1] correctly, the relation between a continuous variable $X$ and its discretization $Z$ can be conceptually
understood as $X \rightarrow Z$, i.e., the value of discrete variable $Z$ depends on $X$. Moreover, when a BN is learned, the relationship between the $Z$'s are learned.

For example, if we have two continuous variables $X_1$ and $X_2$ that are discretized into $Z_1$ and $Z_2$, and learn the BN over $Z_1$ and $Z_2$ as DAG: $Z_1 \rightarrow Z_2$, then the relationship of the four involved variables $X_1$, $X_2$, $Z_1$, and $Z_2$ can modeled as the following BN

$$X_1 \rightarrow Z_1 \rightarrow Z_2 \leftarrow X_2$$

In this BN, even though the two discrete variables $Z_1$ and $Z_2$ are related, the two continuous variables $X_1$ and $X_2$ are not (they are d-separated). In this case, I wonder if this is the intended semantics of the discretization, i.e., after the discretization, then the continuous variables $X_1$ and $X_2$, which are what we are truly interested in, become independent. In general, I would much appreciated a clarification on the semantics of the discretization in structure learning (for example, [2] provides the semantics of such discretization).

On the other hand, if the relation between $X$ and $Z$ is understood as $X \leftarrow Z$, then $X_1$ and $X_2$ are not d-separated:

$$X_1 \leftarrow Z_1 \rightarrow Z_2 \rightarrow X_2$$

However, if this is the case, the framework discussed in this paper appears to be closely related to [2]. More specifically, [2] also considers learning the BN structure and learning the discretization of the data simultaneously, consider the same type of discretization policy as this paper. However [2] only sets up the learning problem, but do not provide any algorithm to solve it.\\

[1] Lustgarten, Jonathan L., et al. "Application of an efficient Bayesian discretization method to biomedical data." BMC bioinformatics 12.1 (2011): 1.

[2] Monti, Stefano, and Gregory F. Cooper. "A multivariate discretization method for learning Bayesian networks from mixed data." UAI. 1998.

\noindent\rule{8cm}{0.4pt}\\
{\bf Response}:\\

The difference between our proposed method and [2] is that we did not introduce an additional augmented variable $Z$ for continuous variable $X$ during discretization and optimization process.
For example, if we have a Bayesian network as follows: $A \rightarrow X \rightarrow C$, where both $A$ and $C$ are discrete and $X$ is continuous, then our proposed method replaces $X$ by its discretized version $Z$ as $A \rightarrow Z \rightarrow C$.
The prior 1 in our proposed method provides the prior for $P(Z)$, and the priors 2-4 provide the calculation for $P(D_{A,C} \mid Z)$, where $D_{A,C}$ is the data of variables $A$ and $C$.
Therefore, the mechanism in this paper is different from the method in [2].

\noindent\rule{8cm}{0.4pt}\\
{\bf Reviewer \#2} \\

In the experiment session, three datasets with known network structures are used to show that the proposed method learns better than previous work on MDL-based discretization by [3]. More specifically, the paper first assumes given Bayesian network structures, and compares its discretization results with the MDL discretization in [3]. The experiment results show that the proposed approach learns a discretization with a notable higher log-likelihood than the MDL discretization (i.e., the proposed approach learns a discretization such that the known BN structure with the discretized variable has a higher log-likelihood). The paper then learns BNs with both its proposed discretization and an uniform discretization, and compare the learned BNs. Here, in the current form of the manuscript, it does not appear to be clear if the proposed discretization learned a better BN (in terms of say comparing to the ground truth). Moreover, I believe the effectiveness of the proposed method would be more strongly supported if the scale of the experiment is larger, especially given the experimental results on two additional dataset in the appendix, where the performance of the proposed approach is similar to the MDL approach by [3].

In sum, I believe this paper has some promising ideas. However, I would appreciate if the proposed approach is justified better (such as the semantics of the discretization), and its relation to prior work clarified better (particularly with [2]). Further, I would appreciate if the experiments provide a broader evaluation to claim that the paper improves on the state-of-the-art.\\

[3] Friedman, Nir, and Moises Goldszmidt. "Discretizing continuous attributes while learning Bayesian networks." Icml. 1996.

\noindent\rule{8cm}{0.4pt}\\
{\bf Response}:\\

As the reviewer suggested, we added an illustration of discretization semantics in Section 2.1.
We also added a larger and more diverse set of test datasets in the end of section 6.5.
In order to facilitate a comparison with a known underlying structure, we have added an experiment on a synthetic dataset, also in Section 6.5.
This additional test shows that as the dataset size becomes large, the results of MDL and the proposed method do indeed converge to the same discretization scheme.
This demonstrates the asymptotic equivalence between the two methods.
On the other hand, when the data samples are small and not sufficiently representative, the two methods have significantly different outcomes and the proposed method outperforms the MDL method, as is observed in all other experiments on real datasets.

As mentioned earlier, all datasets are raw data and there are no true Bayesian networks behind them. Therefore, no ground truth can be compared to the learned discrete network. We use cross-validated likelihood to measure the effectiveness of each discretization method.

\end{document}

### 2016-08-09 rebuttal/rebuttal.tex
tim edits

@@
 Therefore, even if all continuous variables have only one interval, the likelihood is not $1$, but $1$ divided by the product of each variable's discretization interval.
+Please refer to Equation 15 and the surrounding discussion.
 
@@
 We are not claiming that MDL and MODL are asymptotically different.
-We are only showing empirically that the size of the dataset heavily influences the outcome, and is independent of the number of variables.
+We are showing empirically that the size of the dataset heavily influences the outcome, and is independent of the number of variables.
 To justify this claim we have added an additional experiment with results shown in Section 6.5.
@@
 5.
-Comparing (18) and (19), the term  $ln(n)\cdot I(X^*,pa_X)$ should be $n\cdot I(X^*,pa_X)$ for $f_{MDL}$.
+Comparing (18) and (19), the term  $\ln(n)\cdot I(X^*,pa_X)$ should be $n\cdot I(X^*,pa_X)$ for $f_{MDL}$.
 If the latter is correct, the MDL will choose more complicated model and improve very much, and the conclusion may change.
@@
 First, our argument is based on the correct equation.
-Second, since both $n$ and $\log(n)$ are constant during the optimization process, where $n$ is the size of dataset, the argument still holds.
+Second, since both $n$ and $\ln(n)$ are constant during the optimization process, where $n$ is the size of dataset, the argument still holds.
 These results are reflected in our experiments.
@@
 
-The original MODL method and the priors suggested by Lustgarten et al. are both Bayesian methods.
-The extensions by Lustgarten et al. replaced the first prior in MODL to yield better results.
-Bayesian priors in this case express the beliefs over the sought-after discretization policy.
-We suggest a prior that produces discretizations with higher cross validated likelihood and an algorithm with $O(n^2)$ runtime.
-The runtime of the discretization method is the bottleneck for the iterative structure learning process.
+Bayesian priors express one's beliefs about the result before evidence is taken into account and they can be different among different methods.
+For example, the original MODL method and the priors suggested by Lustgarten et al. are both for discretizing one continous variable with respect to one categorical variable.
+Both methods have four priors, and their priors are different.
+Both methods are shown to do well on a variety of datasets, even though their differing choice of priors lead to sightly different outcomes.
+The effectiveness of a choice of priors are evaluated by cross validation or other standard statistical criteria.
+Priors are thus often non-unique.
+
+In this paper we propose a discretization method with $O(n^2)$ runtime.
+This is better than the traditional MDL discretization method, which has a $O(n^3)$ runtime.
+Discretization is in the inner loop of the K2 algorithm, and thus is a bottleneck during the combined discretization-structure learning process.
+Due to the nested relation, it is not correct to compare the runtime of $K2$ with the runtime of the discretization procedure.
 
@@
 As the reviewer suggested, we added an illustration of discretization semantics in Section 2.1.
-We also added a larger and more diverse set of test datasets in the end of section 6.5.
+We also added a larger and more diverse set of test datasets in the end of Section 6.5.
 In order to facilitate a comparison with a known underlying structure, we have added an experiment on a synthetic dataset, also in Section 6.5.
@@
 
-As mentioned earlier, all datasets are raw data and there are no true Bayesian networks behind them.
+As mentioned earlier, all real-world datasets lack known underlying Bayesian networks.
 Therefore, no ground truth can be compared to the learned discrete network.

### 2016-08-09 Fig_demo_edge.tex
tim edits

@@
 ]
-\addplot+[solid ,black,thick] coordinates {
+\addplot+[solid ,black,thick, mark options={black}] coordinates {
 (150, 3.34)
@@
 
-\addplot+[solid ,black,thick] coordinates {
+\addplot+[solid ,black,thick, mark options={black!50}] coordinates {
 (150, 2.3)

### 2016-08-09 Learning_Discrete_Bayesian_Networks_from_Continuous_Data.tex
tim edits

--- 2016-07-28 Learning_Discrete_Bayesian_Networks_from_Continuous_Data.tex
@@
 
+\DeclareCaptionLabelFormat{andtable}{#1~#2  \&  \tablename~\thetable}
+
 \usetikzlibrary{bayesnet}
@@
 A common discretization method for Bayesian networks is to split continuous variables into uniform-width intervals or to use field-specific expertise.
+Several Bayesian methods exist to discretize according to the marginal distribution \citep{scott1979optimal, freedman1981histogram, knuth2013optimal, scargle2013studies}, but this ignores dependencies between variables and leads to suboptimal performance, as demonstrated in Appendix A.
 A more principled method is the minimum description length (MDL) principle discretization \citep{Friedman_1996}.
@@
   	Note that $\Lambda^{\text{ex}}_{\cX}$ is an example of a valid discretization policy.
-Discretization policies can be represented by their edges $\anglebrackets{}_{e}$, their sorted unique dataset indeces $\anglebrackets{}_{\lambda}$, or by the interval between sorted unique dataset indeces $\anglebrackets{}_{\gamma}$.
+Discretization policies can be represented by their edges $\anglebrackets{}_{e}$, their sorted unique dataset indices $\anglebrackets{}_{\lambda}$, or by the interval between sorted unique dataset indices $\anglebrackets{}_{\gamma}$.
   }
@@
 
-where $L$ is the largest number of intervals among discrete variables in $\cX$'s Markov blanket.
-This encourages edges between well-separated values over edges between closely packed samples.
+where larger values of $L$ encourage more discretization intervals.
+This prior encourages edges between well-separated values over edges between closely packed samples.
+All following content sets $L$ to the largest number of intervals among discrete variables in $\cX$'s Markov blanket, which encourages Bayesian networks with consistent interval counts.
+Higher values of $L$ can be used when the continuous variable requires more discretization intervals than its Markov blanket.
 
@@
 
-The procedure used to minimize the objective function involves dynamical programming.
+The procedure used to minimize the objective function involves dynamic programming.
 Note that because the objective function is cumulative over intervals, if a partition $\Lambda = \anglebrackets{\gamma_1, \gamma_2, \ldots, \gamma_k}$ of $\cX$ is an optimal discretization policy, then any subinterval is optimal for the corresponding subproblem.
@@
   \begin{algorithmic}[5]
-  \Function{Learn\_DVBN}{$D$, $\bm{\cX}$, $\texttt{order}$, $\hat{n}_\text{parent}$, $\maxpasses$}
+  \Function{LearnDVBN}{$D$, $\bm{\cX}$, $\texttt{order}$, $\hat{n}_\text{parent}$, $\maxpasses$}
     \State $N \leftarrow$ the number of variables in the Bayesian network
@@
 The discretizations are compared using the mean cross validated log-likelihood of the data $D$ given the Bayesian network $B$ and discretization policies $\discset$.
-\tim{Did we also normalize each variable to be zero mean and unit covariance?}
+% \tim{Did we also normalize each variable to be zero mean and unit covariance?} - No, we did not
 Note that all log-likelihoods shown have been normalized by the number of data samples.
@@
 All variables are defined in Section \ref{subsec:algo}.
-Therefore, the runtime of the proposed method in this paper is shorter than the MDL discretization method by $\bigo \paren{n^3}$, since the former has a more efficient form of dynamical programming.
+Therefore, the runtime of the proposed method in this paper is less than the MDL discretization method by $\bigo \paren{n^3}$, since the former has a more efficient form of dynamical programming.
 For faster methods of MDL discretization with suboptimal results, see \citet{Friedman_1996}.
@@
 The reason why MDL produces fewer discretization edges is discussed in Section~\ref{subsec:discuss_exp}.
-Two examples that MDL produces comparble results to the Bayesian method are given in the Appendix.
+Two examples that MDL produces comparble results to the Bayesian method are given in Appendix B.
 
@@
 Table~\ref{table:housing_disc_table_1} shows the numbers of interval after discretization for each continuous variable and the log-likelihood of the dataset based on each discretization method.
-MDL method does not produce any discretization edges for most variables.
+The MDL method does not produce any discretization edges for most variables.
 % The heuristic Bayesian method produces far more discretization edges than the Bayesian method due to repeated instances in the dataset.
@@
 Each row corresponds to a dataset and provides the number of samples $n$, the number of variables $N$, the fixed network structure, and the log-likelihood for each method.
-Fixed network structures are obtained by the same principle as in previous three datasets and are represented in the table by listing the parents for each variable.
+Fixed network structures are obtained by the same principle as with the previous three datasets and are represented by listing the parents for each variable.
 For example, in the first row, the representation $\curly{\emptyset,A,BE,AB,B,AH,BDG,B}$ indicates that $\Pa_A = \emptyset$, $\Pa_B = A$, $\Pa_c = \curly{B,E}$, etc.
@@
     The number of samples, number of variables, network structure, and mean cross-validated log-likelihood under each discretization method are given.
+    The Bayesian method consitently has highest likelihood.
 	}
@@
 Figure~\ref{fig:synthetic} shows how the test likelihood and the number of discretization edges for $\cX$ vary with respect to the number of training samples.
-Trained data are drawn randomly from the synthetic dataset.
-\todo{The remaining ones are tested data.}
+A dataset of \num{800} samples is drawn from the synthetic distribution.
+The size of the subset used for training is varied, and the remaining samples are used as the test set.
 When the training set is small, it is difficult to recognize the underlying pattern and discretize the continuous variable $\cX$ accordingly.
-In this case, both the likelihood of the training data and number of discretization edges is small.
+In this case, both the likelihood of the training data and number of discretization edges are small.
 However, the Bayesian method is more sensitive to variation in the data and produces a distribution both with higher likelihood and more discretization edges.
@@
 
-	\caption{The average log-likelihood of the trained data and the average number of discretization edges for $\cX$ as the number of training samples is varied.
-Training data are drawn randomly from the synthetic distribution.
-\todo{The remaining ones are tested data.} \tim{$\leftarrow$ What does this mean?} Results are averaged over one hundred trials.
-  \tim{Why do we plot training set likelihood and not test set likelihood?}}
+	\caption{The average test log-likelihood and the average number of discretization edges for $\cX$ as the number of training samples is varied.
+  The complete dataset size is fixed at \num{800} samples, drawn randomly from the synthetic distribution.
+  The size of the subset used for training is varied, and the remaining samples are used as the test set.
+  }
 	\label{fig:synthetic}
@@
 
-% The methods developed in this paper increase the accuracy of Bayesian networks learned on datasets with continuous and mixed variables.
-% An automated process for simultaneously constructing Bayesian networks and discretization policies is appealing because of the potential to significantly reduce development time and cost when developing models for uncertainty and causality.
+The methods developed in this paper increase the accuracy of Bayesian networks learned on datasets with continuous and mixed variables.
+An automated process for simultaneously constructing Bayesian networks and discretization policies is appealing because of the potential to significantly reduce development time and cost when developing models for uncertainty and causality.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section*{Appendix}
-\label{sec:appendix}
+\section*{Appendix A}
+\label{sec:appendixA}
+
+This section illustrates the advantage of structure-aware discretization methods over marginal discretization methods \citep{scott1979optimal, freedman1981histogram, knuth2013optimal, scargle2013studies}.
+Marginal discretization methods ignore intervariable dependencies and can thus lead to suboptimal discretizations for the joint distribution.
+Consider a synthetic dataset with two variables, discrete $A$ and continuous $B$, with \num{500} data samples sampled from the Bayesian network $A \rightarrow B$ described in Table~8.
+%~\ref{table:marginal_counter}.
+Following the experiment procedure in Section~\ref{sec:experiments}, both the MDL method and the proposed Bayesian approach find the true discretization edge for $B$ near $1.0$ and have log likelihood \num{-0.023}.
+They recover the discretization shown in Figure~\ref{fig:marginal_counter}.
+The Bayesian Blocks method~\citep{scargle2013studies}, as with any marginal method, cannot distinguish between the different conditional distributions and thus does not locate a discretization edge.
+The resulting log likelihood is worse, at \num{-0.69}.
+This example shows that structure-aware discretization methods can leverage additional information and thus produce better joint representations.
+
+\begin{minipage}{\textwidth}
+  \begin{minipage}[b]{0.49\textwidth}
+    \centering
+    \begin{tabular}{cl}
+      \toprule
+      Variable               & Distribution                                   \\ \midrule
+      \multirow{2}{*}{$A$}&$P(a^1) = 0.5$     \\
+      & $P( a^2) = 0.5$     \\ \midrule
+
+      \multirow{2}{*}{$B$} & $p(b \mid A = a^1) \sim U[0,1]$\\
+      & $p(b \mid A = a^2) \sim U[1,2]$\\
+      \bottomrule
+    \end{tabular}
+    \vspace{1cm}
+    \captionof{table}{Probability distributions for $A \rightarrow B$, in which $A$ is discrete and $B$ is continuous. The marginal distribution for $B$ is $U[0,2]$.}
+    \label{table:marginal_counter}
+  \end{minipage}
+  \hfill
+  \begin{minipage}[b]{0.49\textwidth}
+    \centering
+    \vspace{1em}
+    \resizebox {\columnwidth}{!}{
+      \begin{tikzpicture}
+      \begin{axis}[xlabel=$b$, ylabel=probability density, ymin=0, ymax=1.5,
+        legend style={
+          draw=none,
+          at={(0.95,0.85)},
+          anchor=east,
+          legend columns=1,
+          font=\small,
+          /tikz/every even column/.append style={column sep=0.5cm},
+          /pgfplots/legend image code/.code={%
+            \draw[##1,/tikz/.cd,yshift=-0.25em]
+            (0cm,0cm) rectangle (0.8em,0.8em);
+          },
+        },
+      ]
+      \addplot+[ybar interval, mark=none, black!80, fill=black!80] plot coordinates
+        {(0,1) (1,1)};
+        \addplot+[ybar interval, mark=none, black!40, fill=black!40] plot coordinates
+        {(1,1) (2,1)};
+        \legend{$P(b\mid a^1)$, $P(b\mid a^2)$}
+      \end{axis}
+      \end{tikzpicture}
+    }
+    \captionof{figure}{The resulting conditional probability distribution for $B$. Marginal methods see one uniform distribution.}
+    \label{fig:marginal_counter}
+  \end{minipage}
+\end{minipage}
+
+\section*{Appendix B}
+\label{sec:appendixB}
 
@@
 The discretization policy shown is for running the algorithms on the full dataset; the likelihood and prediction accuracies were found with 10-fold cross validation.
-The MDL discretization method and the Bayesian method have same discretization result: all discretization edges coincide.
+The MDL discretization method and the Bayesian method have the same discretization result: all discretization edges coincide.
 In addition, both methods have $94 \%$ accuarcy, which matches the number in \cite{Friedman_1996}.
@@
     The discretization policies for the Iris dataset with the naive Bayes structure.
-    The two methods produce the same discretization policy on each continuous variable and have close 10-fold prediction accuracy and log-likelihood.
+    The two methods produce the same discretization policy on each continuous variable and have nearly identical 10-fold prediction accuracy and log-likelihood.
   }

### 2016-08-09 Learning_Discrete_Bayesian_Networks_from_Continuous_Data.tex
minor

@@
     The number of samples, number of variables, network structure, and mean cross-validated log-likelihood under each discretization method are given.
-    The Bayesian method consitently has highest likelihood.
+    The Bayesian method consitently has higher likelihood.
 	}
@@
 
-The methods developed in this paper increase the accuracy of Bayesian networks learned on datasets with continuous and mixed variables.
-An automated process for simultaneously constructing Bayesian networks and discretization policies is appealing because of the potential to significantly reduce development time and cost when developing models for uncertainty and causality.
+% The methods developed in this paper increase the accuracy of Bayesian networks learned on datasets with continuous and mixed variables.
+% An automated process for simultaneously constructing Bayesian networks and discretization policies is appealing because of the potential to significantly reduce development time and cost when developing models for uncertainty and causality.
 

### 2016-08-09 rebuttal/rebuttal.tex
incorporating Mykel edits

@@
 
-[1] Lustgarten, Jonathan L., et al. "Application of an efficient Bayesian discretization method to biomedical data." BMC bioinformatics 12.1 (2011): 1.
+[1] Lustgarten, Jonathan L., et al. ``Application of an efficient Bayesian discretization method to biomedical data.'' BMC bioinformatics 12.1 (2011): 1.
 
-[2] Monti, Stefano, and Gregory F. Cooper. "A multivariate discretization method for learning Bayesian networks from mixed data." UAI. 1998.
+[2] Monti, Stefano, and Gregory F. Cooper. ``A multivariate discretization method for learning Bayesian networks from mixed data.'' UAI. 1998.
 
@@
 
-[3] Friedman, Nir, and Moises Goldszmidt. "Discretizing continuous attributes while learning Bayesian networks." Icml. 1996.
+[3] Friedman, Nir, and Moises Goldszmidt. ``Discretizing continuous attributes while learning Bayesian networks.'' Icml. 1996.
 

### 2016-08-09 Learning_Discrete_Bayesian_Networks_from_Continuous_Data.tex
incorporating Mykel edits

@@
 This prior encourages edges between well-separated values over edges between closely packed samples.
-All following content sets $L$ to the largest number of intervals among discrete variables in $\cX$'s Markov blanket, which encourages Bayesian networks with consistent interval counts.
+The experiments in this paper set $L$ to the largest number of intervals among discrete variables in $\cX$'s Markov blanket, which encourages Bayesian networks with consistent interval counts.
 Higher values of $L$ can be used when the continuous variable requires more discretization intervals than its Markov blanket.

### 2016-10-17 Learning_Discrete_Bayesian_Networks_from_Continuous_Data.tex
update abs&intro

@@
 
-Real data often contains a mixture of discrete and continuous variables, but many Bayesian network structure learning and inference algorithms assume all random variables are discrete.
+Learning Bayesian networks from raw data can help users to interpret the relations between variables and acquire knowledge without field-specific experts.
+While real data often contains a mixture of discrete and continuous-valued variables, many Bayesian network structure learning algorithms assume all random variables are discrete. 
+Thus, continuous variables are often discretized while learning a Bayesian network. 
+However, the choice of discretization policy has significant impact on the accuracy, speed, and interpretability of the resulting models.
+This paper introduces a principled Bayesian discretization method for continuous variables in Bayesian networks with quadratic complexity instead of the cubic complexity of other standard techniques.
+Empirical demonstrations show that the proposed method is superior to the classic method.
+In addition, this paper shows how to incorporate existing methods into the structure learning process to discretize all continuous variables and simultaneously learn Bayesian network structures.
+
+%%%%%% Old Abstract %%%%%
+%Real data often contains a mixture of discrete and continuous variables, but many Bayesian network structure learning and inference algorithms assume all random variables are discrete.
 Continuous variables are often discretized, but the choice of discretization policy has significant impact on the accuracy, speed, and interpretability of the resulting models.
@@
 In addition, this paper shows how to incorporate existing methods into the structure learning process to discretize all continuous variables and simultaneously learn Bayesian network structures.
-%The proposed method was incorporated and its performance was empirically demonstrated.
+%%%%%%%%%%%%%%%%%%
 
@@
 Bayesian networks \citep{Pearl_1988, PGM_2009} are often used to model uncertainty and causality, with applications ranging from decision-making systems \citep{kochenderfer2012next} to medical diagnosis \citep{Lustgarten_2011}.
+Learning Bayesian networks from raw data can help users to discover knowledge without field-specific experts, such as causality and probabilistic relation between variables.
+It is common to assume that the random variables in a Bayesian network are discrete, since many Bayesian network learning algorithms are unable to efficiently handle continuous variables.
+In addition, many of the commonly used Bayesian network software packages, such as Netica \citep{netica1992}, SMILearn \citep{druzdzel1999smile}, and bnlearn \citep{bnlearn2010}, are geared towards discrete variables.
+However, many applications require the use of continuous data, such as position and velocity in dynamic systems \citep{kochenderfer2010airspace}.
+
+%Bayesian networks \citep{Pearl_1988, PGM_2009} are often used to model uncertainty and causality, with applications ranging from decision-making systems \citep{kochenderfer2012next} to medical diagnosis \citep{Lustgarten_2011}.
 Bayesian networks provide an efficient factorization of the joint probability distribution over a set of random variables.
@@
 
-There are three common approaches to extending Bayesian networks to continuous variables.
+There are three common approaches to extending Bayesian network learning algorithms to continuous variables.
+The first is to model the conditional probability density of each continuous variable using specific families of parametric distributions, and then to redesign Bayesian network learning algorithms based on the parameterizations.
+One example of parametric continuous distributions in Bayesian networks is the Gaussian graphical model \citep{Weiss_2011}.
+
+%There are three common approaches to extending Bayesian networks to continuous variables.
 The first is to model the conditional probability density of each continuous variable using specific families of parametric distributions, and then to redesign Bayesian network learning and inference algorithms based on the parameterizations.
 One example of parametric continuous distributions in Bayesian networks is the Gaussian graphical model \citep{Weiss_2011}.
-%For other parametric distributions and non-linear functions \citep{Ihler_2009}, however, these redesigned algorithms can be computationally expensive.
 
@@
 Automated discretization methods have been studied in machine learning and statistics for many years \citep{Dougherty_1995, Kerber_1992, Holte_1993, Fayyad_1993}, primarily for classification problems.
-These methods search for the best discretization policy for a continuous attribute by considering its interaction with a class variable.
+These methods learn for the best discretization policy for a continuous attribute by considering its interaction with a class variable.
 It is common to discretize all continuous variables before learning a Bayesian network structure to avoid having to consider variable interactions, as the interactions and dependencies between variables in Bayesian networks introduce complexity.
@@
 
-A common discretization method for Bayesian networks is to split continuous variables into uniform-width intervals or to use field-specific expertise.
+A common discretization method for Bayesian networks is to split continuous data into uniform-width intervals or to use field-specific expertise.
 Several Bayesian methods exist to discretize according to the marginal distribution \citep{scott1979optimal, freedman1981histogram, knuth2013optimal, scargle2013studies}, but this ignores dependencies between variables and leads to suboptimal performance, as demonstrated in Appendix A.

### 2016-10-17 Learning_Discrete_Bayesian_Networks_from_Continuous_Data.tex
update abs&intro
minor

@@
 
-Learning Bayesian networks from raw data can help users to interpret the relations between variables and acquire knowledge without field-specific experts.
+Learning Bayesian networks from raw data can help interpret the variable iterrelationships and structure without relying on field-specific experts.
 While real data often contains a mixture of discrete and continuous-valued variables, many Bayesian network structure learning algorithms assume all random variables are discrete.
-Thus, continuous variables are often discretized while learning a Bayesian network. 
+Thus, continuous variables are often discretized when learning a Bayesian network.
 However, the choice of discretization policy has significant impact on the accuracy, speed, and interpretability of the resulting models.
 This paper introduces a principled Bayesian discretization method for continuous variables in Bayesian networks with quadratic complexity instead of the cubic complexity of other standard techniques.
-Empirical demonstrations show that the proposed method is superior to the classic method.
+Empirical demonstrations show that the proposed method is superior to the established minimum description length algorithm.
 In addition, this paper shows how to incorporate existing methods into the structure learning process to discretize all continuous variables and simultaneously learn Bayesian network structures.
@@
 Parametric models have a fixed number of parameters, whereas the number of parameters in a nonparametric model grow with the amount of training data.
-%Inference algorithms on nonparametric models can be also inefficient.
 
@@
 Automated discretization methods have been studied in machine learning and statistics for many years \citep{Dougherty_1995, Kerber_1992, Holte_1993, Fayyad_1993}, primarily for classification problems.
-These methods learn for the best discretization policy for a continuous attribute by considering its interaction with a class variable.
+These methods learn the best discretization policy for a continuous attribute by considering its interaction with a class variable.
 It is common to discretize all continuous variables before learning a Bayesian network structure to avoid having to consider variable interactions, as the interactions and dependencies between variables in Bayesian networks introduce complexity.
-%The discretization of a variable in a network requires considering the impact on the variable's Markov blanket.
 Prior work exists for discretizing continuous variables in naive Bayesian networks and tree-augmented networks \citep{Fried_naive}, but only a few discretization methods for general Bayesian networks have been proposed \citep{Friedman_1996, Kozlov_1997, Monti_1998, Steck_2007}.
@@
 Mutual information, which is composed of empirical probabilities computed using event count ratios, varies less significantly with the positions of discretization edges than the method we suggest in this article.
-
-% The probability of the data given the model typically increases with the number of discretization intervals, and the model prior is chosen to decrease with the number of discretization intervals
-% Maximizing the model likelihood thus requires a trade-off in the number of discretization intervals.
-
-%Bayesian methods select the model with maximum posterior probability given the data, %$P(\textit{Model} \mid \textit{Data})$.
-%An application of Bayes' rule and constant $P(\textit{Data})$ shows that this is %equivalent to maximizing ${P(\textit{Model}) \cdot P(\textit{Data} \mid %\textit{Model})}$, where $P(\textit{Model})$ is a prior over models and ${P(\textit{Data} %\mid \textit{Model})}$ is the data likelihood.
-%The data likelihood usually increases with the number of discretization intervals, as %more intervals allow for richer representations.
-%The prior is chosen to influence the relative merit between models, and for %discretization policies the prior is negatively correlated with the number of %discretization intervals to favor simpler models and prevent overfitting.
-%Maximizing ${P(\textit{Model}) \cdot P(\textit{Data} \mid \textit{Model})}$ thus requires %a trade-off when determining the number of discretization intervals.
 

### 2017-05-08 jair_Learning_Discrete_Bayesian_Networks_from_Continuous_Data.tex
JAIR & Approx paragraph

--- 2016-10-17 Learning_Discrete_Bayesian_Networks_from_Continuous_Data.tex
@@
-%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
-%
-% This is a general template file for the LaTeX package SVJour3
-% for Springer journals.          Springer Heidelberg 2010/09/16
-%
-% Copy it to a new file with a new name and use it as the basis
-% for your article. Delete % signs as needed.
-%
-% This template includes a few options for different layouts and
-% content for various journals. Please consult a previous issue of
-% your journal as needed.
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-% First comes an example EPS file -- just ignore it and
-% proceed on the \documentclass line
-% your LaTeX will extract the file if required
-%\begin{filecontents*}{example.eps}
-  %!PS-Adobe-3.0 EPSF-3.0
-  %%BoundingBox: 19 19 221 221
-  %%CreationDate: Mon Sep 29 1997
-  %%Creator: programmed by hand (JK)
-  %%EndComments
-%  gsave
-%  newpath
-%    20 20 moveto
-%    20 220 lineto
-%    220 220 lineto
-%    220 20 lineto
-%  closepath
-%  2 setlinewidth
-%  gsave
-%    .4 setgray fill
-%  grestore
-%  stroke
-%  grestore
-%\end{filecontents*}
-%
 \RequirePackage{fix-cm}
-%
-%\documentclass{svjour3}                     % onecolumn (standard format)
-%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
-\documentclass[smallextended]{svjour3}       % onecolumn (second format)
-%\documentclass[twocolumn]{svjour3}          % twocolumn
-%
-\smartqed  % flush right qed marks, e.g. at end of proof
-%
+
+\documentclass[twoside,11pt]{article}
+\usepackage{jair, theapa, rawfonts}
+
 \usepackage{amsmath}
@@
 
+%\jairheading{X}{XXXX}{XXX}{MM/YY}{MM/YY}
+%\ShortHeadings{Learning Discrete Bayesian Networks from Continuous Data}
+%{Chen, Wheeler, \& Kochenderfer}
+%\firstpageno{25}
+
 \begin{document}
@@
 
-\author{Yi-Chun Chen           \and
-        Tim A. Wheeler         \and
-        Mykel J. Kochenderfer
-}
-
+\author{\name Yi-Chun Chen \email yichunc@stanford.edu \\
+	\addr Institute of Computational and Mathematical Engineering, Stanford University,\\
+	Stanford, CA  94035 USA
+	\AND
+	\name Tim A. Wheeler \email wheelert@stanford.edu \\
+	\addr Department of Aeronautics and Astronautics, Stanford University,\\
+	Stanford, CA  94035 USA\\
+	\AND
+	\name Mykel J. Kochenderfer \email mykel@stanford.edu \\
+	\addr Department of Aeronautics and Astronautics, Stanford University,\\
+	Stanford, CA  94035 USA}
 %\authorrunning{Short form of author list} % if too long for running head
 
-\institute{Yi-Chun Chen \at
-              Institute of Computational and Mathematical Engineering, Stanford University \\
-              \email{yichunc@stanford.edu}
-           \and
-              Tim A. Wheeler \at
-              Department of Aeronautics and Astronautics, Stanford University\\
-              \email{wheelert@stanford.edu}
-           \and
-              Mykel J. Kochenderfer \at
-              Department of Aeronautics and Astronautics, Stanford University\\
-              \email{mykel@stanford.edu}
-}
-
-\date{Received: date / Accepted: date}
-% The correct dates will be entered by the editor
-
 \maketitle
@@
 
-Learning Bayesian networks from raw data can help interpret the variable iterrelationships and structure without relying on field-specific experts.
+Learning Bayesian networks from raw data can help interpret the variable interrelationships and structure without relying on field-specific experts.
 While real data often contains a mixture of discrete and continuous-valued variables, many Bayesian network structure learning algorithms assume all random variables are discrete.
@@
 
-\keywords{Discretization \and Bayesian Network \and Continuous Variable}
-  % \PACS{PACS code1 \and PACS code2 \and more}
-  % \subclass{MSC code1 \and MSC code2 \and more}
 \end{abstract}
@@
 The $\lambda_{1:k}$ representation is the number of instances before every discretization edge whereas the $\gamma_{1:k}$ representation is the number of instances within each discretization interval.
+Both $\lambda_{1:k}$ and $\gamma_{1:k}$ representations will be used in the following content.
+The former makes the dynamic programming algorithm more succinct, and the latter makes equations more compact when calculating data instantiations.
 Table \ref{table:data_demo} and \ref{table:data_demo_2} demonstrate variable assignments for an example dataset.
-
-%For example, Table \ref{table:data_demo} is a dataset that mixes continuous variable $\cX$ and discrete variables $A$ and $B$.
-Data samples are arranged in an ascending order of $\cX$.
-Therefore, $n = 10$, $m =6$, $\cx_{1:10} = \curly{ 1.1, 1.2, 1.2, 2.9, 2.9, 2.9, 3.5, 4.3, 4.3, 5.0} $, and  $\cu_{1:6} = \curly{ 1.1,1.2,2.9,3.5,4.3,5.0}$.
-The corresponding index $s$ of $\cu$ in $\cx$ is $s_{1:6} = \curly{1,3,6,7,9,10}$.
-In addition, a three-interval discretization policy $\Lambda^0_{\cX}$ with edges $e_1 = 1.55$ and $e_2 = 4.65$ can be represented as
-%\begin{equation}
-%\Lambda^0_{\cX} = \anglebrackets{\lambda_1 = 3 , \lambda_2 = 9, \lambda_{3} = 10 } \equiv \anglebrackets{\gamma_1 = 3, \gamma_2 = 6, \gamma_3 = 1} \text{.}
-%\end{equation}
 
@@
 Discretization policies can be represented by their edges $\anglebrackets{}_{e}$, their sorted unique dataset indices $\anglebrackets{}_{\lambda}$, or by the interval between sorted unique dataset indices $\anglebrackets{}_{\gamma}$.
+That is to say, in the edge representation, $e_1 = 1.55$ and $e_2 = 4.65$.
+In the $\lambda_{1:k}$ representation, $\lambda_1 = 3$, $\lambda_2 = 9$, and $\lambda_3 = 10$.
+In the $\gamma_{1:k}$ representation, $\gamma_1 = 3$, $\gamma_2 = 6$, and $\gamma_3 = 10$.
+Furthermore, one can check that $\lambda_1 = \gamma_1 = 3$, $\lambda_2 - \lambda_1 = \gamma_2$, and $\lambda_3 - \lambda_2 = \gamma_2$.
+
   }
@@
 
-A Bayesian network $B$ over $N$ random variables $X_{1:N}$ is defined by a directed acyclic graph $G$ whose nodes are the random variables and a conditional probability distribution for each node given its parents.
+A Bayesian Network $B$ over $N$ random variables $X_{1:N}$ is defined by a directed acyclic graph $G$ containing one node for each variable $X_i$, and each node is associated with a conditional probability distribution $P(x_i \mid \parents(i))$ for the node given its parents in $G$.
 The edges in a Bayesian network represent probabilistic dependencies among nodes and encode the Markov property: each node $X_i$ is independent of its non-descendants given its parents $\Pa_{X_i}$ in $G$.
@@
 When discussing the discretization of a particular continuous variable $\cX$, let $P_i$ be the $i$th parent of $\cX$, let $C_i$ be the $i$th child of $\cX$, and let $\bm{S}_i$ be the set of spouses of $\cX$ associated with the $i$th child.
+Note that the set of variables $P \cup C \cup \bm{S}$ is called Markov blanket.
 %The context should make it clear when $P$ refers to a discrete probability and when it refers to a variable's parent.
@@
   \label{eq:p_M}
-  P(\Lambda) = \prod_{i=1}^{k-1}
+  P(\Lambda) \propto \prod_{i=1}^{k-1}
     \brock{
@@
 
-The two factors on the right hand side come from the third principle: all distribution of values of $C_j$ in a given interval and with a given value of $S_j$ are equiprobable.
+Both factors on the right hand side come from the third principle: all distributions of values of $C_j$ in a given interval and with a given value of $S_j$ are equiprobable.
 According to the fourth prior, these distributions are independent from each other, and one can thus take their product.
@@
 Precomputation reduces runtime.
-Hence, $h(u,v)$ is computed first for each interval $\gamma_q$ starting from $x_{u}$ to $x_{v}$ for all $u$, $v$ satisfying $u \leq v$:
+Hence, $h(u,v)$ is computed first for each interval $\gamma_q = \gamma_q^{(u,v)}$ starting from $x_{u}$ to $x_{v}$ for all $u$, $v$ satisfying $u \leq v$:
 
@@
 The calculation of $h(u,v)$ for all $u \leq v$ has a $\bigo \paren{ n_c \cdot {L}^{n_s} \cdot n^2 + {L}^{n_p} \cdot n^2 }$ runtime, where $n_c$ and $n_p$ are the number of child and parent variables respectively, $L$ is the largest cardinality of variables in $X$'s Markov blanket, and $n_s = \text{max}_j  |\Pa_{C_j}|$.
+The $n^2$ factor in the runtime comes from the fact that both $x_u$ and $x_v$ have to run over all possible values of $\cX$, which has $n$ instantiations.
 
@@
 
-% \subsection{Approximation}
-
-% Algorithm~\ref{alg:disc_one} has an exponential $\bigo\paren{\paren{L'}^{n_p} \cdot N^2}$ runtime which severely limits discretization in networks with a large number of discretization intervals or parent variables.
-% This section introduces an approximation to the objective function that significantly reduces the runtime and still preserves the quality of discretization.
-% The approximation replaces the dominator of the last factor in Equation~\ref{eq:likelihood_one} with
-
-% \begin{equation}
-% {\frac{{\gamma_i}!}{ {n^{\text{P}}_{i,1} !} {n^{\text{P}}_{i,2} !} \cdots {n^{\text{P}}_{i,J_\text{P}} !}}} \approx \prod_{r=1}^{n_p} { {{{\gamma}_i}!}\over{ {n^{(P_r)}_{i,1} !} {n^{(P_r)}_{i,2} !} \cdots {n^{(P_r)}_{i,J_{P_r}} !}}}\text{,}
-% \end{equation}
-
-% \noindent
-% where $P_r$ is the $r$th parent variable, $J_{p_r} = \| P_r\|$, and ${n^{(P_r)}_{i,j} !}$ is the number of instances in the $i$th interval with the $j$th value of $P_r$.
-Note that $\gamma_i = \sum_j {n^{(P_r)}_{i,j}}$ for all $r$.
-% The approximated objective function is
-
-% \begin{small}
-%   \begin{equation}
-%   \label{eq:opt_prob_approx}
-%   \begin{aligned}
-%     & \sum_{i=1}^{k-1}
-%      - \ln
-%       \paren{
-%         1 - \exp
-%         \paren{
-%           - L \cdot  \frac{
-%                            \cx_{\lambda_i +1} - \cx_{\lambda_i}
-%                          }{
-%                            \cx_n - \cx_1
-%                           }
-%         }
-%       }
-%         + \sum_{i=1}^{k}
-%         L \cdot \frac{\cx_{\lambda_{i}} - \cx_{\lambda_{i-1} + 1}}{\cx_n - \cx_1} \\
-%     & \sum_{i=1}^{k} \brock{
-%     \ln{{\gamma_i + J_\text{P} - 1}\choose{J_\text{P} - 1}}
-%     +{ \ln \paren{
-%           \frac{
-%             {\gamma_i}!
-%           }{ \sum_{r=1}^{n_p}
-%             {n^{({P_r})}_{i,1}}! \; {n^{({P_r})}_{i,2}}! \; \cdots \; {n^{({P_r})}_{i,J_{P_r}}}!
-%           }
-%         }}
-%     } \\
-%     & \sum_{j=1}^{n_c} \sum_{i=1}^k \sum_{\ell=1}^{J^{(j)}_\bm{S}} \brock{
-%     { \ln
-%             {{n^{(j)}_{i,\ell} + J_{C_j} - 1}\choose{J_{C_j}-1}}}
-%       +
-%       \ln \paren{ {
-%             \frac{
-%               {n^{(j)}_{i,\ell}}!
-%             }{
-%               {n^{(j)}_{i,1,\ell}!} \; {n^{(j)}_{i,2,\ell}!} \; \cdots \; {n^{(j)}_{i,J_{C_j},\ell}!}
-%             }
-%           }
-%           } }
-%   \end{aligned}
-%   \end{equation}
-% \end{small}
-
-% The approximation reduces the runtime of Algorithm~\ref{alg:disc_one} to a polynomial, $\bigo\paren{ {v'_\text{max}} \cdot (n_c + n_p) \cdot n^2}$.
-% It will be shown in Section~\ref{sec:experiments} that the approximation is more sensitive to the distribution over other variables and is biased towards slightly higher interval counts.
-
-% The approximated objective function, Equation~\ref{eq:opt_prob_approx}, provides intuition into how child and parent variables contribute to the objective function.
-% For example, in the left graph of Figure~\ref{fig:example_networks}, the corresponding square brackets in the approximated objective function are
-
-% \begin{small}
-%   \begin{equation}
-%   \begin{aligned}
-%   \label{eq:example_approx}
-%    \sum_{i=1}^k & \left\lbrace   \left[ \ln{{\gamma_{i} + J_{C_1} - 1}\choose{J_{C_1}-1}} + \ln \left(  {{{\gamma_i}!} \over { {n^{(1)}_{i,1,\emptyset} !} \cdots {n^{(1)}_{i,J_{C_1},\emptyset} !}} }  \right)  +  \right.
-\right.\\
-%   & \left.  \ln{{\gamma_{i} + J_{C_2} - 1}\choose{J_{C_2}-1}} + \ln \left(  {{{n_i}!} \over { {n^{(2)}_{i,1,\emptyset} !} \cdots {n^{(2)}_{i,J_{C_1},\emptyset} !}} }  \right)  \right] + \\
-%   &  \left.
-\left[  \ln {{\gamma_{i} + J_\text{P} - 1}\choose{J_\text{P}-1}} +  \ln \left( { {{{\gamma}_i}!}\over{ {n^{(P_1)}_{i,1} !}\cdots {n^{(P_1)}_{i,J_{P_1}} !}}} \right) +\ln \paren{{ {{{\gamma}_i}!}\over{ {n^{(P_2}_{i,1} !}\cdots {n^{(P_2)}_{i,J_{P_2}} !}}} } \right] \right\rbrace \text{.}
-%   \end{aligned}
-%   \end{equation}
-% \end{small}
-
-% In Equation~\ref{eq:example_approx}, each child carries two terms, as shown in the first set of square brackets, but the two parent variables only carry a total of three terms, as shown in the second set of square brackets.
-% In this case the child variables have greater effect on the optimal discretization than the parent variables, even though the number of child and parent variables are the same.
-% However, if $C_2$ has an additional parent $S_2$, as shown in the right graph of Figure~\ref{fig:example_networks}, the importances of $C_2$ will be reduced.
-% This is due to the additional influence of $S_2$ on $C_2$.
-% This phenomenon arrises because the Bayesian method, but with and without the heuristic, incorporates graph structure when discretizing continuous variables.
-
-% \begin{figure}[ht]
-%   \centering
-%   \begin{tabular}{cc}
-%     \input{graph2_left}
-%     \end{tabular}
-%     \hspace{5em}
-%     \begin{tabular}{cc}
-%     \input{graph2_right}
-%   \end{tabular}
-%   \caption{Two example networks}
-%   \label{fig:example_networks}
-% \end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \section{Multi-Variable Discretization}
@@
     The number of samples, number of variables, network structure, and mean cross-validated log-likelihood under each discretization method are given.
-    The Bayesian method consitently has higher likelihood.
+    The Bayesian method consistently has higher likelihood.
 	}
@@
 \end{table}
+
+Finding optimal discretization policy to \cref{eq:opt_prob} through dynamic programming leads to high computation time when the datasets have more than $100$ variables.
+The runtime issue becomes more severe if one adapts the MDL approach instead of the proposed Bayesian method in this paper.
+Thus, approximation approaches are reasonable alternatives, and one possibility is the greedy heuristic \cite{Friedman_1996}.
+Other approximation methods to dynamic programming are also applicable to solve \cref{eq:opt_prob}
 
@@
 %\begin{thebibliography}{}
-\bibliographystyle{spbasic}
-\bibliography{my_bib}
 
@@
 
-%\subsection*{Results on More Datasets}
-%
-%In this subsection, six additional datasets \citep{Lichman_2013} are tested as a supplementary to Section \ref{sec:experiments}.
-For each dataset, a comparison between the proposed method and MDL-principle method has been made.
-The discretization results of two methods are shown in terms of discretization edges and likelihood on a given network structure, which is obtained by uniform discretization and K2 structure learning, same as in Section \ref{sec:experiments}.
-The results still indicates that the proposed method outperforms than the MDL-principle discretization, in which the latter suffers from low number of discretization edges.
-%
-%\subsubsection*{Dataset: Seeds}
-%
-%The Seeds data sets contains variables related to the shape of seeds of two species.
-The dataset has 210 samples over eight variables.
-Only variable $H$ is discrete-valued.
-The discretization methods are tested on the fixed network structure: $\Pa_A = \curly{\emptyset}$, $\Pa_B = \curly{ A }$, $\Pa_C = \curly{B, E}$, $\Pa_D = \curly{A,B}$, $\Pa_E = \curly{B}$, $\Pa_F = \curly{A,H}$, $\Pa_G = \curly{B,D,H}$, and $\Pa_H = \curly{B}$.
-This network is obtained by first uniformly discretizing each variable by two intervals then running K2 structure learning.
-%
-%\begin{table}[ht]
-%	\centering
-%	\caption{
-%		The discretization policies for the Seeds dataset with a fixed structure.
-%		The methods have the same discretization for variable $G$, close discretization edge for variable $F$, and the log-likelihood for the Bayesian method is better than that for the MDL method.
-%	}
-%	\input{Table6.tex}
-%	\label{table:auto_disc_seeds}
-%\end{table}
-%
-%\subsubsection*{Dataset: Glasses}
-%
-%\subsubsection*{Dataset: Heart}
-%
-%\subsubsection*{Dataset: Liver Disorder}
-%
-%\subsubsection*{Dataset: Indian Liver Patient}
-%
-%\subsubsection*{Dataset: Banknote authentication}
+\vskip 0.2in
+\bibliography{my_bib}
+\bibliographystyle{theapa}
+
 \end{document}

### 2017-05-08 jair_Learning_Discrete_Bayesian_Networks_from_Continuous_Data.tex
more update

@@
 Furthermore, one can check that $\lambda_1 = \gamma_1 = 3$, $\lambda_2 - \lambda_1 = \gamma_2$, and $\lambda_3 - \lambda_2 = \gamma_2$.
-
   }
@@
 
-A Bayesian Network $B$ over $N$ random variables $X_{1:N}$ is defined by a directed acyclic graph $G$ containing one node for each variable $X_i$, and each node is associated with a conditional probability distribution $P(x_i \mid \parents(i))$ for the node given its parents in $G$.
+A Bayesian Network $B$ over $N$ random variables $X_{1:N}$ is defined by a directed acyclic graph $G$ containing one node for each variable $X_i$, and each node is associated with a conditional probability distribution $P(X_i \mid \Pa_{X_i})$ for the node given its parents in $G$.
 The edges in a Bayesian network represent probabilistic dependencies among nodes and encode the Markov property: each node $X_i$ is independent of its non-descendants given its parents $\Pa_{X_i}$ in $G$.
@@
 
-Finding optimal discretization policy to \cref{eq:opt_prob} through dynamic programming leads to high computation time when the datasets have more than $100$ variables.
+Finding optimal discretization policy to equation \ref{eq:opt_prob} through dynamic programming leads to high computation time when the datasets have more than $100$ variables.
 The runtime issue becomes more severe if one adapts the MDL approach instead of the proposed Bayesian method in this paper.
 Thus, approximation approaches are reasonable alternatives, and one possibility is the greedy heuristic \cite{Friedman_1996}.
-Other approximation methods to dynamic programming are also applicable to solve \cref{eq:opt_prob}
+Other approximation methods to dynamic programming are also applicable to solve equation \ref{eq:opt_prob}
 

### 2017-05-10 jair_Learning_Discrete_Bayesian_Networks_from_Continuous_Data.tex
compile fixes

@@
 \usepackage[noend]{algpseudocode}
-\usepackage[round]{natbib}
 \usepackage{multirow}
@@
 \usetikzlibrary{bayesnet}
-\setcitestyle{aysep={ }} %Author-Year Separator
+
+\newcommand{\citep}[1]{\cite{#1}}
+\newcommand{\citet}[1]{\citeauthor{#1} \citeyear{#1}}
+
 %
@@
 
-Bayesian networks \citep{Pearl_1988, PGM_2009} are often used to model uncertainty and causality, with applications ranging from decision-making systems \citep{kochenderfer2012next} to medical diagnosis \citep{Lustgarten_2011}.
+Bayesian networks \citep{Pearl_1988,PGM_2009} are often used to model uncertainty and causality, with applications ranging from decision-making systems \citep{kochenderfer2012next} to medical diagnosis \citep{Lustgarten_2011}.
 Learning Bayesian networks from raw data can help users to discover knowledge without field-specific experts, such as causality and probabilistic relation between variables.
@@
 The third approach is discretization.
-Automated discretization methods have been studied in machine learning and statistics for many years \citep{Dougherty_1995, Kerber_1992, Holte_1993, Fayyad_1993}, primarily for classification problems.
+Automated discretization methods have been studied in machine learning and statistics for many years \citep{Dougherty_1995,Kerber_1992,Holte_1993,Fayyad_1993}, primarily for classification problems.
 These methods learn the best discretization policy for a continuous attribute by considering its interaction with a class variable.
 It is common to discretize all continuous variables before learning a Bayesian network structure to avoid having to consider variable interactions, as the interactions and dependencies between variables in Bayesian networks introduce complexity.
-Prior work exists for discretizing continuous variables in naive Bayesian networks and tree-augmented networks \citep{Fried_naive}, but only a few discretization methods for general Bayesian networks have been proposed \citep{Friedman_1996, Kozlov_1997, Monti_1998, Steck_2007}.
+Prior work exists for discretizing continuous variables in naive Bayesian networks and tree-augmented networks \citep{Fried_naive}, but only a few discretization methods for general Bayesian networks have been proposed \citep{Friedman_1996,Kozlov_1997,Monti_1998,Steck_2007}.
 
 A common discretization method for Bayesian networks is to split continuous data into uniform-width intervals or to use field-specific expertise.
-Several Bayesian methods exist to discretize according to the marginal distribution \citep{scott1979optimal, freedman1981histogram, knuth2013optimal, scargle2013studies}, but this ignores dependencies between variables and leads to suboptimal performance, as demonstrated in Appendix A.
+Several Bayesian methods exist to discretize according to the marginal distribution \citep{scott1979optimal,freedman1981histogram,knuth2013optimal,scargle2013studies}, but this ignores dependencies between variables and leads to suboptimal performance, as demonstrated in Appendix A.
 A more principled method is the minimum description length (MDL) principle discretization \citep{Friedman_1996}.
@@
 It is often necessary to infer the structure of a Bayesian network from data.
-Three common approaches to Bayesian network structure learning are constraint-based, score-based, and Bayesian model averaging \citep[see][chap.~18]{PGM_2009}.
+Three common approaches to Bayesian network structure learning are constraint-based, score-based, and Bayesian model averaging \citep{PGM_2009}.
 This work uses the K2 structure learning algorithm \citep{cooper1992bayesian}, a frequently used score-based structure learning method.
@@
 
-This section illustrates the advantage of structure-aware discretization methods over marginal discretization methods \citep{scott1979optimal, freedman1981histogram, knuth2013optimal, scargle2013studies}.
+This section illustrates the advantage of structure-aware discretization methods over marginal discretization methods \citep{scott1979optimal,freedman1981histogram,knuth2013optimal,scargle2013studies}.
 Marginal discretization methods ignore intervariable dependencies and can thus lead to suboptimal discretizations for the joint distribution.

### 2017-05-10 jair_Learning_Discrete_Bayesian_Networks_from_Continuous_Data.tex
tim edits

@@
 \usepackage{booktabs}
-\usepackage{BOONDOX-cal} % for lowercase caligraphic
+% \usepackage{BOONDOX-cal} % for lowercase caligraphic
 \usepackage[font=small,skip=5pt]{caption}
@@
 	\addr Department of Aeronautics and Astronautics, Stanford University,\\
-	Stanford, CA  94035 USA\\
+	Stanford, CA  94035 USA
 	\AND
@@
 
-Finding optimal discretization policy to equation \ref{eq:opt_prob} through dynamic programming leads to high computation time when the datasets have more than $100$ variables.
-The runtime issue becomes more severe if one adapts the MDL approach instead of the proposed Bayesian method in this paper.
-Thus, approximation approaches are reasonable alternatives, and one possibility is the greedy heuristic \cite{Friedman_1996}.
-Other approximation methods to dynamic programming are also applicable to solve equation \ref{eq:opt_prob}
+Finding optimal discretization policies according to equation~\ref{eq:opt_prob} via dynamic programming requires long computation times when the dataset has more than \num{100} variables.
+The runtime for the MDL approach is even more severe.
+Approximation approaches are reasonable alternatives for datasets with more variables, including a greedy heuristic~\cite{Friedman_1996}.
+Approximations can also be applied during dynamic programming when solving equation~\ref{eq:opt_prob}.
 

### 2017-05-10 jair_Learning_Discrete_Bayesian_Networks_from_Continuous_Data.tex
cite -> citet

@@
 \usepackage{booktabs}
-% \usepackage{BOONDOX-cal} % for lowercase caligraphic
+\usepackage{BOONDOX-cal} % for lowercase caligraphic
 \usepackage[font=small,skip=5pt]{caption}
@@
 
-%\jairheading{X}{XXXX}{XXX}{MM/YY}{MM/YY}
-%\ShortHeadings{Learning Discrete Bayesian Networks from Continuous Data}
-%{Chen, Wheeler, \& Kochenderfer}
-%\firstpageno{25}
+\jairheading{X}{XXXX}{XXX}{MM/YY}{MM/YY}
+\ShortHeadings{Learning Discrete Bayesian Networks from Continuous Data}
+{Chen, Wheeler, \& Kochenderfer}
+\firstpageno{25}
 
@@
 
-\author{\name Yi-Chun Chen \email yichunc@stanford.edu \\
+\author{\name Yi-Chun Chen \email yichunc0419@alumni.stanford.edu \\
 	\addr Institute of Computational and Mathematical Engineering, Stanford University,\\
@@
 
-%Bayesian networks \citep{Pearl_1988, PGM_2009} are often used to model uncertainty and causality, with applications ranging from decision-making systems \citep{kochenderfer2012next} to medical diagnosis \citep{Lustgarten_2011}.
-Bayesian networks provide an efficient factorization of the joint probability distribution over a set of random variables.
-It is common to assume that the random variables in a Bayesian network are discrete, since many Bayesian network learning and inference algorithms are unable to efficiently handle continuous variables.
-In addition, many of the commonly used Bayesian network software packages, such as Netica \citep{netica1992}, SMILearn \citep{druzdzel1999smile}, and bnlearn \citep{bnlearn2010}, are geared towards discrete variables.
-However, many applications require the use of continuous variables, such as position and velocity in dynamic systems \citep{kochenderfer2010airspace}.
-
 There are three common approaches to extending Bayesian network learning algorithms to continuous variables.
 The first is to model the conditional probability density of each continuous variable using specific families of parametric distributions, and then to redesign Bayesian network learning algorithms based on the parameterizations.
-One example of parametric continuous distributions in Bayesian networks is the Gaussian graphical model \citep{Weiss_2011}.
-
-%There are three common approaches to extending Bayesian networks to continuous variables.
-The first is to model the conditional probability density of each continuous variable using specific families of parametric distributions, and then to redesign Bayesian network learning and inference algorithms based on the parameterizations.
 One example of parametric continuous distributions in Bayesian networks is the Gaussian graphical model \citep{Weiss_2011}.
@@
 A more principled method is the minimum description length (MDL) principle discretization \citep{Friedman_1996}.
-The MDL principle proposed by \cite{MDL_1978} states that the best model for a dataset is the one that minimizes the amount of information needed to describe it \citep{Grunwald_2009}.
+The MDL principle proposed by \citet{MDL_1978} states that the best model for a dataset is the one that minimizes the amount of information needed to describe it \citep{Grunwald_2009}.
 MDL methods trade off goodness-of-fit against model complexity to reduce generalization error.
-In the context of Bayesian networks, \cite{Friedman_1996} applied the MDL principle to determine the optimal number of discretization intervals for continuous variables and the optimal positions of their discretization edges.
+In the context of Bayesian networks, \citet{Friedman_1996} applied the MDL principle to determine the optimal number of discretization intervals for continuous variables and the optimal positions of their discretization edges.
 Their approach selects a discretization policy that minimizes the sum of the description length of the discretized Bayesian network and the information necessary for recovering the continuous values from the discretized data.
@@
 The MODL method uses dynamic programming to find the optimal discretization policy for a continuous variable given a discrete class variable, and has an $\bigo\paren{n^3 + r \cdot n^2}$ runtime, where $r$ is the number of class variable instantiations.
-\cite{Lustgarten_2011} suggest several formulations for the prior over models.
+\citet{Lustgarten_2011} suggested several formulations for the prior over models.
 The asymptotic equivalence between MDL and MODL on the single-variable, single-class problem was examined by \citet{VL_2000}.
@@
 Four principles for the optimal discretization policy enable the formulation of $P(\Lambda)$ and $P(D_{-\cX} \mid \Lambda)$, where $D_{-\cX}$ is the subset of the dataset for all variables but $\cX$, and the probability of the data associated with the target variable, $P(D_{\cX})$, is already captured in $P(\Lambda)$.
-The four principles, which can be considered an extension of the priors in MODL and \cite{Lustgarten_2011} to Bayesian networks, are:
+The four principles, which can be considered an extension of the priors in MODL \citep{Boulle_2006} and \citet{Lustgarten_2011} to Bayesian networks, are:
 
@@
 The fourth principle is that the distributions for each interval are independent, so the factors can be multiplied together.
+Note that the combinatorics of factors ${{\gamma_i + J_\text{P} - 1}\choose{J_\text{P} - 1}}$ and $\frac{
+	{\gamma_i}!}{{n^{(\text{P})}_{i,1}}! \cdots \; {n^{(\text{P})}_{i,J_\text{P}}}!}$ are explained in MODL \citep{Boulle_2006}.
 
@@
 The runtime for the MDL approach is even more severe.
-Approximation approaches are reasonable alternatives for datasets with more variables, including a greedy heuristic~\cite{Friedman_1996}.
-Approximations can also be applied during dynamic programming when solving equation~\ref{eq:opt_prob}.
+Approximation approaches are reasonable alternatives for datasets with more variables, including a greedy heuristic~\citep{Friedman_1996}.
+Approximations can also be applied during dynamic programming when solving equation~\ref{eq:opt_prob} \citep{Boulle_2006}.
 
@@
 where $Z_1$ and $Z_2$ are constant over discretizations, $k$ is the number of discretization intervals, and $I\paren{A, B} = \sum_{a,b} \hat{P}(a,b) \ln\frac{\hat{P}(a,b)}{\hat{P}(a)\hat{P}(b)}$ is the mutual information based on estimated probabilities.
-Note that the third term of $f_\text{MDL}$ was approximated using $H(p)$ (see Equation~\ref{eqn:MDL}) in the original work by \cite{Friedman_1996}, but it is written here without that approximation.
+Note that the third term of $f_\text{MDL}$ was approximated using $H(p)$ (see Equation~\ref{eqn:MDL}) in the original work by \citet{Friedman_1996}, but it is written here without that approximation.
 
@@
 The second example is on the Iris dataset \citep{Lichman_2013}.
-In the work of \cite{Friedman_1996}, the Iris dataset was tested on the naive Bayes network structure and the prediction accuracy was shown.
+In the work of \citet{Friedman_1996}, the Iris dataset was tested on the naive Bayes network structure and the prediction accuracy was shown.
 The same test is reproduced below to compare the Bayesian method to the MDL discretization method.
@@
 The MDL discretization method and the Bayesian method have the same discretization result: all discretization edges coincide.
-In addition, both methods have $94 \%$ accuarcy, which matches the number in \cite{Friedman_1996}.
+In addition, both methods have $94 \%$ accuarcy, which matches the number in \citet{Friedman_1996}.
 The Bayesian method likelihood is slightly higher across folds than the MDL method likelihood.

### 2017-05-11 jair_Learning_Discrete_Bayesian_Networks_from_Continuous_Data.tex
YC update
typo

@@
 The fourth principle is that the distributions for each interval are independent, so the factors can be multiplied together.
-Note that the combinatorics of factors ${{\gamma_i + J_\text{P} - 1}\choose{J_\text{P} - 1}}$ and $\frac{
-	{\gamma_i}!}{{n^{(\text{P})}_{i,1}}! \cdots \; {n^{(\text{P})}_{i,J_\text{P}}}!}$ are explained in MODL \citep{Boulle_2006}.
+Note that the combinatorics of factors ${{\gamma_i + J_\text{P} - 1}\choose{J_\text{P} - 1}}$ and ${
+	{\gamma_i}!}/{{n^{(\text{P})}_{i,1}}! \cdots \; {n^{(\text{P})}_{i,J_\text{P}}}!}$ are explained in MODL \citep{Boulle_2006}.
 
@@
 Approximation approaches are reasonable alternatives for datasets with more variables, including a greedy heuristic~\citep{Friedman_1996}.
-Approximations can also be applied during dynamic programming when solving equation~\ref{eq:opt_prob} \citep{Boulle_2006}.
+Approximations can also be applied during dynamic programming when solving Equation~\ref{eq:opt_prob} \citep{Boulle_2006}.
 

### 2017-05-11 jair_Learning_Discrete_Bayesian_Networks_from_Continuous_Data.tex
tim edits

@@
 \usepackage{booktabs}
-\usepackage{BOONDOX-cal} % for lowercase caligraphic
 \usepackage[font=small,skip=5pt]{caption}
@@
 \usepackage{tabularx}
+\usepackage{boondox-cal} % for lowercase caligraphic
 
@@
 A discretization policy $\Lambda_{\cX} = \anglebrackets{e_1 < e_2 < \ldots < e_{k-1}}$ for $\cX$ is a mapping from $\mathbb{R}$ to $\curly{1,2,3,\ldots,k}$ such that
-
 \begin{equation}
@@
 \end{equation}
-
-\noindent
 The discretization policy discretizes $\cX$ into $k$ intervals.
@@
 Two useful integer representations of $\Lambda_{\cX}$ can be written
-
 \begin{equation}
@@
 \end{equation}
-
-\noindent
 where $\lambda_1 = s_1$, $\lambda_i \in s_{1:m}$, $\gamma_1 = \lambda_1$, and $\gamma_i = \lambda_i - \lambda_{i-1}$.
@@
 When discussing the discretization of a particular continuous variable $\cX$, let $P_i$ be the $i$th parent of $\cX$, let $C_i$ be the $i$th child of $\cX$, and let $\bm{S}_i$ be the set of spouses of $\cX$ associated with the $i$th child.
-Note that the set of variables $P \cup C \cup \bm{S}$ is called Markov blanket.
+The parents, children, and spouses of a variable form its Markov blanket.
 %The context should make it clear when $P$ refers to a discrete probability and when it refers to a variable's parent.
@@
 \item The prior probability of a discretization edge between two consecutive unique values $\cu_i$ and $\cu_{i+1}$ is proportional to their difference:
-
   \begin{equation}
@@
 From the first principle one obtains the prior over the discretization policy:
-
 \begin{small}
@@
 The likelihood term ${P(D_{-\cX} \mid \Lambda)}$ for a Bayesian network graph structure factors according to $\cX$'s Markov blanket:
-
 \begin{equation}
@@
 For example, in Figure~\ref{fig:example_factorization}, $P(D_{-\cX} \mid \Lambda)$ factors according to
-
 \begin{equation}
@@
 It follows that
-
 \begin{equation}
@@
 
-The two factors on the right hand side come from the second principle: all distributions of values of the parents of $\cX$ in a given interval are equiprobable.
+Both factors on the right hand side come from the second principle: all distributions of values of the parents of $\cX$ in a given interval are equiprobable.
 The fourth principle is that the distributions for each interval are independent, so the factors can be multiplied together.
 Note that the combinatorics of factors ${{\gamma_i + J_\text{P} - 1}\choose{J_\text{P} - 1}}$ and ${
-	{\gamma_i}!}/{{n^{(\text{P})}_{i,1}}! \cdots \; {n^{(\text{P})}_{i,J_\text{P}}}!}$ are explained in MODL \citep{Boulle_2006}.
+	{\gamma_i}!}/{{n^{(\text{P})}_{i,1}}! \cdots \; {n^{(\text{P})}_{i,J_\text{P}}}!}$ are explained in the MODL paper~\citep{Boulle_2006}.
 
@@
 If $\bm{S}_j = \emptyset$, then Equation~\ref{eq:likelihood_two} is equivalent to
-
 \begin{equation}
@@
 \end{equation}
-
-\noindent
 where $n^{(j)}_{i,m,\emptyset}$ is the number of instances of $\cX$ in the $i$th discretization interval of $\Lambda$ given the $m$th instantiation of $C_j$.
@@
 The log-inverse of $P(\Lambda) \cdot P(D_{-\cX} \mid \Lambda)$ is minimized for computational convenience:
-
 \begin{equation}
@@
 Hence, $h(u,v)$ is computed first for each interval $\gamma_q = \gamma_q^{(u,v)}$ starting from $x_{u}$ to $x_{v}$ for all $u$, $v$ satisfying $u \leq v$:
-
 \begin{small}
@@
 The Bayesian score is:
-
 \begin{small}
@@
 \end{small}
-
-\noindent
 where $\mathrm{\Gamma}$ is the gamma function, $\alpha_{ij}^{(k)}$ is a Dirichlet parameter and $\beta_{ij}^{(k)}$ is the observed sample count for the $k$th instantiation of $X_i$ and the $j$th instantiation of $\Pa_{X_i}$.
 In the equation above,
-
 \begin{equation}
@@
 The function $g$ in Algorithm~\ref{alg:structure_learn} computes a component of the Bayesian score (Equation~\ref{eq:BayesianScore}):
-
 \begin{equation}
@@
 The log-likelihood has two components,
-
 \begin{equation}
@@
 The log-likelihood of the discretized dataset given the Bayesian network is
-
 \begin{equation}
@@
 The log-likelihood of the original dataset given the discrete dataset is
-
 \begin{equation}
@@
 For a Bayesian network with a single continuous variable $\cX$, the MDL objective function is
-
 \begin{equation}
@@
 For a given Bayesian network, the first three terms only depend on the number of discretization intervals $|X|$ and the fourth term is cumulative over the intervals.
-Hence, if $\Lambda = \anglebrackets{\gamma_1, \gamma_2, \ldots, \gamma_k}$ is a MDL optimal discretization policy with $k$ intervals, then $\Lambda' = \anglebrackets{\gamma_1, \gamma_2, \ldots, \gamma_{k-1}}$ is a MDL optimal discretization policy for the corresponding subproblem with $k-1$ intervals.
+Hence, if ${\Lambda = \anglebrackets{\gamma_1, \gamma_2, \ldots, \gamma_k}}$ is an MDL optimal discretization policy with $k$ intervals, then ${\Lambda' = \anglebrackets{\gamma_1, \gamma_2, \ldots, \gamma_{k-1}}}$ is an MDL optimal discretization policy for the corresponding subproblem with $k-1$ intervals.
 This procedure takes runtime $\bigo \paren{ n^3 + \paren{ n_c \cdot {L}^{n_s}  + {L}^{n_p}} \cdot n^2 }$.
@@
 
-Finding optimal discretization policies according to equation~\ref{eq:opt_prob} via dynamic programming requires long computation times when the dataset has more than \num{100} variables.
-The runtime for the MDL approach is even more severe.
-Approximation approaches are reasonable alternatives for datasets with more variables, including a greedy heuristic~\citep{Friedman_1996}.
+Finding optimal discretization policies according to Equation~\ref{eq:opt_prob} via dynamic programming requires computation times on the order of days on a personal laptop on datasets with more than \num{100} variables.
+The runtime for the MDL approach is significantly worse.
+Approximation approaches are reasonable options for such large datasets, for example a greedy heuristic~\citep{Friedman_1996}.
 Approximations can also be applied during dynamic programming when solving Equation~\ref{eq:opt_prob} \citep{Boulle_2006}.
@@
 If $\Pa_{\cX} = \curly{P_1, P_2}$ and $D_{\cX} = \curly{1,2,3, \ldots n}$, then the corresponding objective functions for the discretization methods are:
-
 \begin{small}
@@
 n^{(P_2)}_{i,2} \cdots n^{(P_2)}_{i,J_{P_2}} }} \right) \right]}^{\text{Edge Position Term}}
-  \end{aligned}\text{,}
+  \end{aligned}
   \end{equation}
@@
 
-\noindent
-where $Z_1$ and $Z_2$ are constant over discretizations, $k$ is the number of discretization intervals, and $I\paren{A, B} = \sum_{a,b} \hat{P}(a,b) \ln\frac{\hat{P}(a,b)}{\hat{P}(a)\hat{P}(b)}$ is the mutual information based on estimated probabilities.
+Here, $Z_1$ and $Z_2$ are constant over discretizations, $k$ is the number of discretization intervals, and $I\paren{A, B} = \sum_{a,b} \hat{P}(a,b) \ln\frac{\hat{P}(a,b)}{\hat{P}(a)\hat{P}(b)}$ is the mutual information based on estimated probabilities.
 Note that the third term of $f_\text{MDL}$ was approximated using $H(p)$ (see Equation~\ref{eqn:MDL}) in the original work by \citet{Friedman_1996}, but it is written here without that approximation.

### 2017-05-11 jair_Learning_Discrete_Bayesian_Networks_from_Continuous_Data.tex
mjk edits

@@
 
-Learning Bayesian networks from raw data can help interpret the variable interrelationships and structure without relying on field-specific experts.
+Learning Bayesian networks from raw data can help provide insights into the relationships between variables. 
 While real data often contains a mixture of discrete and continuous-valued variables, many Bayesian network structure learning algorithms assume all random variables are discrete.
@@
 Bayesian networks \citep{Pearl_1988,PGM_2009} are often used to model uncertainty and causality, with applications ranging from decision-making systems \citep{kochenderfer2012next} to medical diagnosis \citep{Lustgarten_2011}.
-Learning Bayesian networks from raw data can help users to discover knowledge without field-specific experts, such as causality and probabilistic relation between variables.
+Learning Bayesian networks from raw data can help users discover knowledge without field-specific experts, such as causality and probabilistic relation between variables.
 It is common to assume that the random variables in a Bayesian network are discrete, since many Bayesian network learning algorithms are unable to efficiently handle continuous variables.
-In addition, many of the commonly used Bayesian network software packages, such as Netica \citep{netica1992}, SMILearn \citep{druzdzel1999smile}, and bnlearn \citep{bnlearn2010}, are geared towards discrete variables.
-However, many applications require the use of continuous data, such as position and velocity in dynamic systems \citep{kochenderfer2010airspace}.
+In addition, many of the commonly used Bayesian network software packages, such as Netica \citep{netica1992}, SMILearn \citep{druzdzel1999smile}, and bnlearn \citep{bnlearn2010}, are designed for discrete variables.
+However, many applications require the use of continuous data, such as positions and velocities in dynamic systems \citep{kochenderfer2010airspace}.
 
@@
 Let $\cX$ be a continuous variable and let $\cx$ be a specific instance of $\cX$.
-A discretization policy $\Lambda_{\cX} = \anglebrackets{e_1 < e_2 < \ldots < e_{k-1}}$ for $\cX$ is a mapping from $\mathbb{R}$ to $\curly{1,2,3,\ldots,k}$ such that
+A discretization policy $\Lambda_{\cX} = \anglebrackets{e_1 < e_2 < \ldots < e_{k-1}}$ for $\cX$ is a mapping from $\mathbb{R}$ to $\curly{1,2,\ldots,k}$ such that
 \begin{equation}
@@
   \input{Fig1}
-  \caption{Factorization of $P(_{-\cX} \mid \Lambda)$.}
+  \caption{Factorization of $P(D_{-\cX} \mid \Lambda)$.}
   \label{fig:example_factorization}
@@
 Some discretization edges appear in all three discretization methods, such as \num{1.42} and \num{2.35} for variable $C$ and \num{0.785} for variable $L$.
-This indicates sufficiently MDL indeed can find some important discretization edges, but it is not sensitive to find more edges.
+MDL can find some important discretization edges, but it is not sensitive to find more edges.
 
@@
 	\caption{
-		Discretization results for several datasets.
-    The number of samples, number of variables, network structure, and mean cross-validated log-likelihood under each discretization method are given.
+		Discretization results for several datasets, summarizing the number of samples, number of variables, network structure, and mean cross-validated log-likelihood under each discretization method.
     The Bayesian method consistently has higher likelihood.

### 2017-05-12 jair_Learning_Discrete_Bayesian_Networks_from_Continuous_Data.tex
modify the sentence

@@
 
-Some discretization edges appear in all three discretization methods, such as \num{1.42} and \num{2.35} for variable $C$ and \num{0.785} for variable $L$.
+Some discretization edges appear in both discretization methods, such as \num{1.42} and \num{2.35} for variable $C$ and \num{0.785} for variable $L$.
 MDL can find some important discretization edges, but it is not sensitive to find more edges.
+Actually, as shown later in Section \ref{subsec:discuss_exp}, while the MDL and Bayesian methods both produce the optimal discretization as the training data grows, the Bayesian method can produce these discretizations with fewer data samples.
 

### 2017-05-26 jair_Learning_Discrete_Bayesian_Networks_from_Continuous_Data.tex
minor change

@@
 
-\jairheading{X}{XXXX}{XXX}{MM/YY}{MM/YY}
+\jairheading{59}{2017}{XXX}{10/16}{05/17}
 \ShortHeadings{Learning Discrete Bayesian Networks from Continuous Data}
@@
 \author{\name Yi-Chun Chen \email yichunc0419@alumni.stanford.edu \\
-	\addr Institute of Computational and Mathematical Engineering, Stanford University,\\
-	Stanford, CA  94035 USA
+	\addr Institute of Computational and Mathematical Engineering,\\
+	Stanford University, Stanford, CA  94035 USA
 	\AND
@@
 
-\section{Multi-Variable Discretization}
+\section{Multi-variable Discretization}
 \label{sec:multi_var}
@@
 Therefore, the runtime of the proposed method in this paper is less than the MDL discretization method by $\bigo \paren{n^3}$, since the former has a more efficient form of dynamical programming.
-For faster methods of MDL discretization with suboptimal results, see \citet{Friedman_1996}.
+For faster methods of MDL discretization with suboptimal results also, see \citet{Friedman_1996}.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Appendix A}
+\section*{Appendix A.}
 \label{sec:appendixA}
@@
 
-\section*{Appendix B}
+\section*{Appendix B.}
 \label{sec:appendixB}
@@
 
-\subsection*{Auto MPG with Comparable MDL Performance}
+\subsection*{B.1 Auto MPG with Comparable MDL Performance}
 The Bayesian network structure in Figure~\ref{fig:auto_graph_3} and the discretization results in Table~\ref{table:auto_disc_table_3} demonstrate that the MDL method does not always produce fewer discretization intervals than the Bayesian approach and that the MDL method can produce discretization policies with comparable likelihood.
@@
 
-\subsection*{Reproducing MDL Results from the Literature}
+\subsection*{B.2 Reproducing MDL Results from the Literature}
 

### 2017-05-26 jair_Learning_Discrete_Bayesian_Networks_from_Continuous_Data.tex
one more sentence

@@
 
-After the initial discretization, the one-variable discretization method is iteratively applied over each continuous variable in reverse topoligical order, from the leaves to the root.
+After the initial discretization, the one-variable discretization method is iteratively applied over each continuous variable in reverse topological order, from the leaves to the root.
 Reverse topological order has the advantage of relying on fewer initial discretizations of the continuous variables during the first pass.
@@
 This section describes experiments conducted to evaluate the Bayesian discretization method.
-All experiments were run on datasets from the publically available University of California, Irvine machine learning repository \citep{Lichman_2013}.
+All experiments were run on datasets from the publicly available University of California, Irvine machine learning repository \citep{Lichman_2013}.
 Variables are labeled alphabetically in the order given on the dataset information webpage.
@@
 The reason why MDL produces fewer discretization edges is discussed in Section~\ref{subsec:discuss_exp}.
-Two examples that MDL produces comparble results to the Bayesian method are given in Appendix B.
+Two examples that MDL produces comparable results to the Bayesian method are given in Appendix B.
 
@@
 The MDL discretization method and the Bayesian method have the same discretization result: all discretization edges coincide.
-In addition, both methods have $94 \%$ accuarcy, which matches the number in \citet{Friedman_1996}.
+In addition, both methods have $94 \%$ accuracy, which matches the number in the literature \citep{Friedman_1996}.
 The Bayesian method likelihood is slightly higher across folds than the MDL method likelihood.

### 2017-06-06 jair_Learning_Discrete_Bayesian_Networks_from_Continuous_Data.tex
might be last push
last update?
page number and table/figure rearrange

@@
 
-\jairheading{59}{2017}{XXX}{10/16}{05/17}
+\jairheading{59}{2017}{103-132}{10/16}{06/17}
 \ShortHeadings{Learning Discrete Bayesian Networks from Continuous Data}
 {Chen, Wheeler, \& Kochenderfer}
-\firstpageno{25}
+\firstpageno{103}
 
@@
 	\name Tim A. Wheeler \email wheelert@stanford.edu \\
-	\addr Department of Aeronautics and Astronautics, Stanford University,\\
+	\addr Department of Aeronautics and Astronautics,\\ Stanford University,
 	Stanford, CA  94035 USA
@@
 	\name Mykel J. Kochenderfer \email mykel@stanford.edu \\
-	\addr Department of Aeronautics and Astronautics, Stanford University,\\
+	\addr Department of Aeronautics and Astronautics,\\ Stanford University,
 	Stanford, CA  94035 USA}
@@
 
-%%%%%% Old Abstract %%%%%
-%Real data often contains a mixture of discrete and continuous variables, but many Bayesian network structure learning and inference algorithms assume all random variables are discrete.
-Continuous variables are often discretized, but the choice of discretization policy has significant impact on the accuracy, speed, and interpretability of the resulting models.
-This paper introduces a principled Bayesian discretization method for continuous variables in Bayesian networks with quadratic complexity instead of the cubic complexity of other standard techniques.
-Empirical demonstrations show that the proposed method is superior to the state of the art.
-In addition, this paper shows how to incorporate existing methods into the structure learning process to discretize all continuous variables and simultaneously learn Bayesian network structures.
-%%%%%%%%%%%%%%%%%%
-
 \end{abstract}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 An optimal discretization policy for a dataset $D$ maximizes $P(\Lambda)\cdot P(D\mid \Lambda)$ for some prior $P(\Lambda)$ and likelihood $P(D\mid \Lambda)$.
-
-% Let $n_p$ and $n_c$ respectively refer to the number of parents and number of children of $X$.
-
-% Let $D$ be a dataset of $N$ samples from which the discretization will be learned, sorted in ascending order according to $X$.
-% Let $D_{\boldsymbol{Y}}$ will refer to the data instances associated with variables $\boldsymbol{Y}$, thus $D_X = \{ x_1,x_2,x_3,\ldots,x_n \}$.
-% In order to facilitate understanding, we temporarily assume all values in $D_X$ are unique, that is, $x_1 < x_2 < \ldots < x_n$.
-% It follows that a discretization policy $\Lambda$ on $X$ can be written as $M_X = \brock{n_1,n_2,\ldots,n_k}$, where $k$, $n_1$, $n_2$, $\ldots,n_k$ are positive integers satisfying $N = \sum_{i=1}^k n_i$.
-
-%Furthermore, since there might have repeated values for $D_x$, we assume there are $N'$ unique values of $D_x$ and $N' \leq N$.
-Note that the allowable discretization edges happens between two consective values of non-repeated value of $D_x$.
-For example, if $D_X = \{ 1.0,1.0,2.0\}$, then the only possible discretization edge is on $1.5$.
 
@@
 Therefore, the runtime of the proposed method in this paper is less than the MDL discretization method by $\bigo \paren{n^3}$, since the former has a more efficient form of dynamical programming.
-For faster methods of MDL discretization with suboptimal results also, see \citet{Friedman_1996}.
+There also exist faster methods of MDL discretization, but they lead to suboptimal results \citep{Friedman_1996}.
 
@@
 
-\begin{minipage}{\textwidth}
-  \begin{minipage}[b]{0.49\textwidth}
+\begin{table}
 	\centering
@@
 	\vspace{1cm}
-    \captionof{table}{Probability distributions for $A \rightarrow B$, in which $A$ is discrete and $B$ is continuous. The marginal distribution for $B$ is $U[0,2]$.}
+	\caption{Probability distributions for $A \rightarrow B$, in which $A$ is discrete and $B$ is continuous. The marginal distribution for $B$ is $U[0,2]$.}
 \label{table:marginal_counter}
-  \end{minipage}
-  \hfill
-  \begin{minipage}[b]{0.49\textwidth}
+\end{table}
+
+\begin{figure}[ht]
     \centering
     \vspace{1em}
-    \resizebox {\columnwidth}{!}{
+%    \resizebox {\columnwidth}{!}{
     	\begin{tikzpicture}
@@
     	\end{tikzpicture}
-    }
-    \captionof{figure}{The resulting conditional probability distribution for $B$. Marginal methods see one uniform distribution.}
+%    }
+    \caption{The resulting conditional probability distribution for $B$. Marginal methods see one uniform distribution.}
     \label{fig:marginal_counter}
-  \end{minipage}
-\end{minipage}
+\end{figure}
+
+%
+%\begin{minipage}{\textwidth}
+%  \begin{minipage}[b]{0.49\textwidth}
+%    \centering
+%    \begin{tabular}{cl}
+%      \toprule
+%      Variable               & Distribution                                   \\ \midrule
+%      \multirow{2}{*}{$A$}&$P(a^1) = 0.5$     \\
+%      & $P( a^2) = 0.5$     \\ \midrule
+%
+%      \multirow{2}{*}{$B$} & $p(b \mid A = a^1) \sim U[0,1]$\\
+%      & $p(b \mid A = a^2) \sim U[1,2]$\\
+%      \bottomrule
+%    \end{tabular}
+%    \vspace{1cm}
+%    \captionof{table}{Probability distributions for $A \rightarrow B$, in which $A$ is discrete and $B$ is continuous. The marginal distribution for $B$ is $U[0,2]$.}
+%    \label{table:marginal_counter}
+%  \end{minipage}
+%  \hfill
+%  \begin{minipage}[b]{0.49\textwidth}
+%    \centering
+%    \vspace{1em}
+%    \resizebox {\columnwidth}{!}{
+%      \begin{tikzpicture}
+%      \begin{axis}[xlabel=$b$, ylabel=probability density, ymin=0, ymax=1.5,
+%        legend style={
+%          draw=none,
+%          at={(0.95,0.85)},
+%          anchor=east,
+%          legend columns=1,
+%          font=\small,
+%          /tikz/every even column/.append style={column sep=0.5cm},
+%          /pgfplots/legend image code/.code={%
+%            \draw[##1,/tikz/.cd,yshift=-0.25em]
+%            (0cm,0cm) rectangle (0.8em,0.8em);
+%          },
+%        },
+%      ]
+%      \addplot+[ybar interval, mark=none, black!80, fill=black!80] plot coordinates
+%        {(0,1) (1,1)};
+%        \addplot+[ybar interval, mark=none, black!40, fill=black!40] plot coordinates
+%        {(1,1) (2,1)};
+%        \legend{$P(b\mid a^1)$, $P(b\mid a^2)$}
+%      \end{axis}
+%      \end{tikzpicture}
+%    }
+%    \captionof{figure}{The resulting conditional probability distribution for $B$. Marginal methods see one uniform distribution.}
+%    \label{fig:marginal_counter}
+%  \end{minipage}
+%\end{minipage}
 
